### 2016-07-19 latex/stackoverflow.tex
Updated latex

% This is LLNCS.DOC the documentation file of
% the LaTeX2e class from Springer-Verlag
% for Lecture Notes in Computer Science, version 2.4
%\documentclass{llncs}
\documentclass{IEEEtran}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{listings}  
\usepackage{array}
\usepackage{multirow}
\usepackage[table]{xcolor}
\usepackage{float}
\usepackage{array}
\usepackage{ragged2e}
\newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\@makecaption}
{\scshape}
{}
{}
{}
\makeatother

\lstdefinestyle{base}{
	language=C,
	emptylines=1,
	breaklines=true,
	basicstyle=\ttfamily\color{black},
	moredelim=**[is][\color{red}]{@}{@},
}

\def\tablename{Table}

\usepackage[justification=centering]{caption}

\newcommand{\squeezeup}{\vspace{-2.5mm}}
\newcommand\FIXME[1]{\textbf{FIXME: #1}}
%
\begin{document}

\onecolumn

\title{Online Source Code Reuse: A Case Study of Stackoverflow \textit{vs.~}Qualitas OSS}
\maketitle

\section*{Raw statistics}
The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below. There are 2 tools selected: Simian and NiCad. They are configured using three different settings: default settings, settings from FSE'13 paper, and settings from CloPlag experiment. Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.

Manual investigation of Simian's clone report showed that there were problematic fragments (6 for defaults, 0 for FSE'13, and 11 for CloPlag). These fragments generate false clone containing array initialisation. Hence, they were removed from the result set before analysis.

\begin{table*}[h]
	\centering
	\caption{Simian clone results}
	\label{t_simian_raw_results}
	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
		\hline
		\multirow{4}{*}{} 
		& \multicolumn{4}{c|}{Default settings} 
		& \multicolumn{4}{c|}{Default settings*} 
		& \multicolumn{4}{c}{FSE'13 settings} \\ \cline{2-13} % & \multicolumn{4}{c}{CloPlag settings} \\
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c|}{threshold=6} 
		& \multicolumn{4}{c}{threshold=5}  \\  % & \multicolumn{4}{c}{threshold=5} \\
		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} &
		\multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC,bSqBrck} & \multicolumn{4}{c}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} \\\cline{2-13}  %  & \multicolumn{4}{c}{iId} \\
		% \hline
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
		\hline
		Removed & 6 & -- & -- & -- & 0 & -- & -- & -- & 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
		Total          & 647       & 24,802       & --         & --  & 3   & 10 & -- & -- &  152 & 7,289,272 & -- & --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
		Mean           & --        & 38           & 7.53       & 0.27   & -- & 3.33 & 8 & 0.29 & -- & 47,956 & 4.76 & 0.27 \\ % & -- & 9,356 & 4.74 & 0.26 \\
		Std Dev.       & -- 		  & 87		& 3.87 & 0.22 & -- & 2.62 & 1.41 & 0.18 & -- & 433,467 & 0.93 & 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
		Max            & --       & 551         & 63          & 0.94  & -- & 7	& 10 & 0.54 & -- & 5,278,408 & 8 & 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
		Min            & --       & 1           & 5           & 0.01  & -- & 1 & 7 & 0.10 & -- & 1 & 4 & 0.01 \\ % & -- & 1 & 4 & 0.002 \\
		Median         & --       & 3           & 7           & 0.22  & -- & 2 & 7 & 0.24 & -- & 22.5 & 4 & 0.23 \\ % & -- & 27 & 4 & 0.22 \\
		Mode           & --       & 1           & 7           & 0.25  & -- & N/A & 7 & N/A & -- & 1 & 4 & 0.50 \\ % & -- & 1 & 4 & 0.50 \\
		\hline
	\end{tabular} 
\end{table*}

\begin{table*}[h]
	\centering
	\caption{NiCad clone results}
	\label{t_nicad_raw_results}
		\begin{tabular}{l|r|r|r|r|r|r|r|r}
			\hline
			\multirow{4}{*}{} & \multicolumn{4}{c|}{Default settings} & \multicolumn{4}{c}{FSE'13 settings} \\ \cline{2-9} 
			%& \multicolumn{4}{c|}{Default settings} & \multicolumn{4}{c|}{FSE'13 settings}  & \multicolumn{4}{c}{CloPlag settings} \\
			%\hline
			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} & \multicolumn{4}{c}{threshold=5, UPI=0.2} \\ % & \multicolumn{4}{c}{threshold=6, UPI=0.4} \\
			& \multicolumn{4}{c|}{rename=none,abstract=none} & \multicolumn{4}{c}{rename=blind,abstract=literal} \\ \cline{2-9} % & \multicolumn{4}{c}{rename=blind,abstract=declaration} \\
			%\hline
			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
			\hline
			Total & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --    \\
			Mean & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\
			Std Dev. & 	& 200.49 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\
			Max & -- & 1816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88 \\
			Min & -- & 1 & 7 & 0.02 & -- & 1 & 3	 & 0.01 \\
			Median & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\
			Mode & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\
			\hline
		\end{tabular} 
\end{table*}

\section*{Agreed Cloned Fragments}
The results from both tools are compared to find clone pairs that they mutually agree.  Theses agreed clone pairs will be manually investigated. The results of agreed clone pairs found by different parameter settings of Simian and NiCad are shown in Table \ref{t_agreed_clone}.

\begin{table}[h]
	\centering
	\caption{Agreed cloned fragments between Simian and Nicad}
	\label{t_agreed_clone}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 92          & 1        \\%      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 155         & 25           \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

Relationships between the cloned fragments are displayed in Fig.~\ref{fig:venn4}.

\begin{figure}[H]
\centering
\includegraphics[width=0.5\linewidth]{venn4}
\caption[Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings]{Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings}
\label{fig:venn4}
\end{figure}

\section*{Agreed Clone Pairs}
The investigation of the clone pairs using Bellon's \textit{good-match(p)} and \textit{ok-match(p)} criteria are listed in  Table \ref{t_agreed_good_clone_pairs} and Table \ref{t_agreed_ok_clone_pairs}. We use the threshold \textit{p} of 0.7 for both \textit{good-match} and \textit{ok-match}. Visualisation of \textit{good-match} common clone pairs between sets of parameter settings can be seen from Figure \ref{fig:venn4_pairs}. There are 14 \textit{good-match} pairs. The \textit{ok-match} subsumes the \textit{good-match} resulting in totally 528 common clone pairs. I think I can manually investigate all of the \textit{good-match} ones and 86 samples of the \textit{ok-match} ones.

\begin{table}[h]
	\centering
	\caption{Agreed good-match(0.7) cloned pairs between Simian and Nicad}
	\label{t_agreed_good_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 1 \\ %      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 3 & 5 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{table}[h]
	\centering
	\caption{Agreed ok-match(0.7) cloned pairs between Simian and Nicad}
	\label{t_agreed_ok_clone_pairs}
	\begin{tabular}{l|r|r}
		\hline
		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
		\hline
		NiCad$_{\mathrm{\textit{default}}}$ & 373 & 1 \\%      & 709             \\
		NiCad$_{\mathrm{\textit{fse13}}}$   & 118 & 36 \\ % & 4680            \\
		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
		\hline
	\end{tabular}
\end{table}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.5\linewidth]{venn4_pairs}
	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
	\label{fig:venn4_pairs}
\end{figure}

\section*{Simian's Parameters}

We have carefully investigated the effects of the Simian's parameter \texttt{-balanceSquareBrackets+}. I found that it works in the expected way of handling a pair of brackets (\texttt{[},\texttt{]}) that span over multiple lines. For example, the two code fragments in Figure \ref{fig:two_frags} would match by having \texttt{-balanceSquareBrackets+} enabled.

\noindent\begin{figure}[H]
	\scriptsize
	\begin{lstlisting}[frame=single,style=base]
1           public class MagicSquare {                             public class MagicSquare2 {
2               private int[][] square;                                @private int[@
3               private boolean[] possible;                                        @][@
4               private int totalSqs;                                              @] square;@
5               private int sum;                                       private boolean[] possible;
6               private int numsquares;                                private int totalSqs;
7               public static void main ( String[] args ) {            private int sum;
8               MagicSquare m = new MagicSquare ( 3 );                 private int numsquares;
9                                                                      public static void main ( String[] args ) {
10                                                                     MagicSquare m = new MagicSquare ( 3 );
	\end{lstlisting}
	\caption{Two identical fragments with only differences in locations of the square brackets. All 7 lines are reported by Simian if \small\texttt{-balanceSquareBrackets+} \normalsize is enabled. If not, the clone pairs is reported as \newline (MagicSquare.java [3,8], MagicSquare2.java [5,10]).} 
	\label{fig:two_frags}
\end{figure}

However, the -balanceSquareBrackets+ parameter only works on a small testing environment having toy programs or only small pairs from the full datasets. It does not work with the full complete set of 144,075 Stackoverflow fragments and Qualitas projects. Please find the summary of all the testing scenarios in Table \ref{tab:summary}. %I found that this pair is missing if I turned on \texttt{-balanceSquareBrackets+}.

\begin{table}[H]
	\caption{Simian's \texttt{-balanceSquareBrackets+} (\texttt{-bsb+}) is observed to have unpredictable behaviours when running against big datasets. $\textrm{\textit{CP}}_2$ means the reported clone(s) do not contain lines having dislocated brackets ($L_b$) (i.e. $\textrm{\textit{CP}}_2 = \textrm{\textit{CP}}_1 - L_b$).}
	\label{tab:summary}
	\centering
	\small\begin{tabular}{l|p{6cm}|c|c|c}
		\hline 
		\multirow{2}{*}{\textbf{Project 1}} & \multirow{2}{*}{\textbf{Project 2}} & \textbf{Dislocated} & \multirow{2}{*}{\textbf{-bsb+}} & \textbf{Clones pair} \\ 
		& & \textbf{brackets?} & & \textbf{reported} \\
		\hline
		\hline
		\multicolumn{5}{l}{\textit{Only run Simian against the pair}} \\
		\hline
		MagicSquare.java & MagicSquare\_exact\_copy.java & no & 0,1 & $\textrm{\textit{CP}}_1$ \\
		MagicSquare.java & MagicSquare2.java & yes & 0 & $\textrm{\textit{CP}}_2$ \\ 
		MagicSquare.java & MagicSquare2.java & yes & 1 & $\textrm{\textit{CP}}_1$ \\
		\hline
		%\hline
		%\multicolumn{5}{c}{\textit{Only run Simian against the pair}} \\
		%\hline
		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 0 & $\textrm{\textit{CP}}_3$ \\ 
		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 1 & $\textrm{\textit{CP}}_3$ \\ 
		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 0 & $\textrm{\textit{CP}}_4$ \\ 
		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 1 & $\textrm{\textit{CP}}_4$ \\ 
		\hline 
		\hline
		\multicolumn{5}{l}{\textit{Run Simian against the complete stackoverflow data and the project}} \\
		\hline
		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 0 & $\textrm{\textit{CP}}_3$ \\ 
		\cellcolor{red!10}stackoverflow/4298836\_0.java & \cellcolor{red!10}Qualitas/aoisrc281/../ExprModule.java & \cellcolor{red!10}no & \cellcolor{red!10}1 & \cellcolor{red!10}-- \\ 
		\hline
		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 0 & $\textrm{\textit{CP}}_4$ \\ 
		\cellcolor{red!10}stackoverflow/4533682\_1.java & \cellcolor{red!10}Qualitas/cobertura-1/../TouchCollector.java & \cellcolor{red!10}no & \cellcolor{red!10}1 & \cellcolor{red!10}-- \\
		\hline 
	\end{tabular} 
\end{table}

\end{document}

### 2016-07-19 latex/stackoverflow.tex
Updated results

@@
 The \textit{ok-match} subsumes the \textit{good-match} resulting in totally 528 common clone pairs.
-I think I can manually investigate all of the \textit{good-match} ones and 86 samples of the \textit{ok-match} ones.
 
@@
 \end{figure}
+
+I have manually investigated all of the 14 \textit{good-match} ones and 183 samples of the \textit{ok-match} ones.
+The classification results are shown in Table \ref{tab:classification}.
+The selected 183 pairs are results of filtering fragments with the same starting and ending clone lines by keeping only one of them (i.e.
+strict version).
+Then, we found a lot of similar clone pairs having the same classification results.
+If we only keep unique Stackoverflow fragments (with the largest Qualitas clone size), it results in 82 pairs (i.e.
+loose version).
+
+\begin{table}
+	\centering
+	\caption{Classification results of 14 \textit{good} and 183 \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
+	\label{tab:classification}
+		\begin{tabular}{|l|r|r|r|r|r|r|r|}
+			\hline 
+			Classification & A & B & C & D & E & F & Total \\ 
+			\hline 
+		    \multirow{2}{*}{\textit{good-match(0.7)}} & 1 & 2 & 2 & 2 & 7 & 0 & 14 \\ \cline{2-8}
+			 & 7.14\%	& 14.29\%	& 14.29\%	& 14.29\%	& 50.00\%	& 0.00\%	& 100.00\% \\ 
+			\hline
+			\multirow{2}{*}{\textit{ok-match(0.7) - strict}} & 2 & 2 & 2 & 21 & 146 & 10 & 183 \\ \cline{2-8}
+			& 1.09\%	& 1.09\%	&	1.09\%	&	11.48\%	&	79.78\%	&	5.46\%	&	100.00\%  \\ 
+			\hline
+			\multirow{2}{*}{\textit{ok-match(0.7) - loose}}  & 1 & 2 & 2 & 20 & 48 & 9 & 82 \\ \cline{2-8}
+			& 1.22\%	&	2.44\%	&	2.44\%	&	24.39\%	&	58.54\%	&	10.98\%	&	100.00\% \\
+			\hline 
+		\end{tabular} 
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Classifications of clone creation}
+\begin{tabular}{|c|p{13cm}|}
+	\hline 
+	Category & Descriptions \\ 
+	\hline 
+	A & Code in Stackoverflow is copied from Qualitas (S ← Q). \\ 
+	\hline 
+	B & Code is copied either from each other or a third source (unknown) (S ←→ Q).
+	\\ 
+	\hline 
+	C & Code in both places are copied from a third source T (known) (S, Q ← T ).
+	\\ 
+	\hline 
+	D & Code is a boiler-plate or IDE auto-generated.
+	\\ 
+	\hline 
+	E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
+	\\ 
+	\hline 
+	F & Accidental similarity  \\ 
+	\hline 
+\end{tabular} 
+\end{table}
+
+\section*{Investigation of Missing A/B Clone Pairs Reported by Simian (df)}
+We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
+The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{fse13}$, NiCad$_{df}$, NiCad$_{fse13}$.
+The investigation results are shown in Table \ref{tab:search}.
+
+\begin{table}[H]
+	\centering
+	\caption{Search results of 41 Simian(df) pairs in the new 4 result sets}
+	\label{tab:search}
+\begin{tabular}{l|r|r}
+	\hline 
+	Settings & Found & Not found \\ 
+	\hline 
+	Simian$_{df}$  &  40 & 1 \\ 
+	\hline 
+	Simian$_{fse13}$ & 0 & 41  \\ 
+	\hline 
+	NiCad$_{df}$  & 9 & 32 \\ 
+	\hline 
+	NiCad$_{fse13}$ &  9 & 32 \\ 
+	\hline 
+\end{tabular} 
+\end{table}
+
+Figure \ref{fig:1} shows a clone pairs that is reported by only Simian$_{df}$.
+
+\begin{figure}[H]
+\centering
+\includegraphics[width=1.0\linewidth]{images/1}
+\caption{A clone pair solely reported by Simian$_{df}$}
+\label{fig:1}
+\end{figure}
+
+Figure \ref{fig:2} shows a clone pair that is reported by Simian$_{df}$, NiCad$_{df}$, NiCad$_{fse13}$.
+
+\begin{figure}[H]
+\centering
+\includegraphics[angle=90,origin=c,width=0.6\linewidth]{images/2}
+\caption{A clone pair that is reported by Simian$_{df}$, NiCad$_{df}$, NiCad$_{fse13}$.}
+\label{fig:2}
+\end{figure}
+
+\newpage
 

### 2016-07-23 latex/stackoverflow.tex
Added updated results

@@
 
-Figure \ref{fig:1} shows a clone pairs that is reported by only Simian$_{df}$.
-
-\begin{figure}[H]
-\centering
-\includegraphics[width=1.0\linewidth]{images/1}
-\caption{A clone pair solely reported by Simian$_{df}$}
-\label{fig:1}
-\end{figure}
-
-Figure \ref{fig:2} shows a clone pair that is reported by Simian$_{df}$, NiCad$_{df}$, NiCad$_{fse13}$.
-
-\begin{figure}[H]
-\centering
-\includegraphics[angle=90,origin=c,width=0.6\linewidth]{images/2}
-\caption{A clone pair that is reported by Simian$_{df}$, NiCad$_{df}$, NiCad$_{fse13}$.}
-\label{fig:2}
-\end{figure}
-
-\newpage
-
 \section*{Simian's Parameters}

### 2016-07-23 latex/stackoverflow.tex
Updated the venn diagram (not finished) and the 528 ok pairs (not finished of finding duplicates)

@@
 	\centering
-	\caption{Agreed good-match(0.7) cloned pairs between Simian and Nicad}
+	\caption{18 agreed good-match(0.7) cloned pairs between Simian and Nicad (14 are unique)}
 	\label{t_agreed_good_clone_pairs}
@@
 	\centering
-	\caption{Agreed ok-match(0.7) cloned pairs between Simian and Nicad}
+	\caption{528 agreed ok-match(0.7) cloned pairs between Simian and Nicad (510 are unique)}
 	\label{t_agreed_ok_clone_pairs}

### 2016-07-24 latex/stackoverflow.tex
Updated after finishing analysing 528 ok pairs (fixed some problems)

@@
 
-\section*{Agreed Cloned Fragments}
-The results from both tools are compared to find clone pairs that they mutually agree.
+%\section*{Agreed Cloned Fragments}
+%The results from both tools are compared to find clone pairs that they mutually agree.
 Theses agreed clone pairs will be manually investigated.
@@
 
-\begin{table}[h]
-	\centering
-	\caption{Agreed cloned fragments between Simian and Nicad}
-	\label{t_agreed_clone}
-	\begin{tabular}{l|r|r}
-		\hline
-		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-		\hline
-		NiCad$_{\mathrm{\textit{default}}}$ & 92          & 1        \\%      & 709             \\
-		NiCad$_{\mathrm{\textit{fse13}}}$   & 155         & 25           \\ % & 4680            \\
+%\begin{table}[h]
+%	\centering
+%	\caption{Agreed cloned fragments between Simian and Nicad}
+%	\label{t_agreed_clone}
+%	\begin{tabular}{l|r|r}
+%		\hline
+%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+%		\hline
+%		NiCad$_{\mathrm{\textit{default}}}$ & 92          & 1        \\%      & 709             \\
+%		NiCad$_{\mathrm{\textit{fse13}}}$   & 155         & 25           \\ % & 4680            \\
 		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
-		\hline
-	\end{tabular}
-\end{table}
+%		\hline
+%	\end{tabular}
+%\end{table}
 
-Relationships between the cloned fragments are displayed in Fig.~\ref{fig:venn4}.
+%Relationships between the cloned fragments are displayed in Fig.~\ref{fig:venn4}.
 
-\begin{figure}[H]
-\centering
-\includegraphics[width=0.5\linewidth]{venn4}
-\caption[Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings]{Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings}
-\label{fig:venn4}
-\end{figure}
+%\begin{figure}[H]
+%\centering
+%\includegraphics[width=0.5\linewidth]{venn4}
+%\caption[Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings]{Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings}
+%\label{fig:venn4}
+%\end{figure}
 
@@
 
+\section*{Duplicated Agreed Clone Pairs}
+
+\begin{table}[H]
+	\centering
+	\caption{Duplicated agreed \textit{good}-pairs between pairs of Simian and NiCad settings}
+	\label{t_dup_agreed_good_clone_pairs}
+	\begin{tabular}{l|r|r|r|r}
+		\hline
+		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+		\hline
+		$S_dN_d$ & 9 & 3 & 0 & 0 \\%      & 709             \\
+		$S_dN_f$ & 3 & 3 & 0 & 0 \\ % & 4680            \\
+		$S_fN_d$ & 0 & 0 & 1 & 1 \\
+		$S_fN_f$ & 0 & 0 & 1 & 5 \\	
+		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
+		\hline
+	\end{tabular}
+\end{table}
+
 \begin{figure}[H]
 	\centering
-	\includegraphics[width=0.5\linewidth]{venn4_pairs}
+	\includegraphics[width=0.5\linewidth]{venn4_pairs_good}
 	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
+	\label{fig:venn4_pairs}
+\end{figure}
+
+\begin{table}[h]
+	\centering
+	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings}
+	\label{t_dup_agreed_ok_clone_pairs}
+	\begin{tabular}{l|r|r|r|r}
+		\hline
+		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+		\hline
+		$S_dN_d$ & 373 & 17 & 0 & 0 \\%      & 709             \\
+		$S_dN_f$ & 17 & 118 & 0 & 0 \\ % & 4680            \\
+		$S_fN_d$ & 0 & 0 & 1 & 1 \\
+		$S_fN_f$ & 0 & 0 & 1 & 36 \\	
+		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok}
+	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
 	\label{fig:venn4_pairs}
@@
 			\hline
-			\multirow{2}{*}{\textit{ok-match(0.7) - strict}} & 2 & 2 & 2 & 21 & 146 & 10 & 183 \\ \cline{2-8}
-			& 1.09\%	& 1.09\%	&	1.09\%	&	11.48\%	&	79.78\%	&	5.46\%	&	100.00\%  \\ 
-			\hline
-			\multirow{2}{*}{\textit{ok-match(0.7) - loose}}  & 1 & 2 & 2 & 20 & 48 & 9 & 82 \\ \cline{2-8}
-			& 1.22\%	&	2.44\%	&	2.44\%	&	24.39\%	&	58.54\%	&	10.98\%	&	100.00\% \\
+			\multirow{2}{*}{\textit{ok-match(0.7)}} & 4 & 42 & 8 & 351 & 28 & 77 & 510 \\ \cline{2-8}
+			& 0.78\%	& 8.24\%	&	1.57\%	&	68.82\%	&	5.49\%	&	15.10\%	&	100.00\%  \\ 
 			\hline

### 2016-07-26 manual/script.sh
After investigation of 19051537_0.java

@@ -1,0 +1,8 @@
+while IFS='' read -r line || [[ -n "$line" ]]; do
+    #echo "Text read from file: $line"
+    size=`echo $line | cut -d',' -f9 | cut -d'.' -f1`
+    #echo $size
+    if [ $size -gt 10 ]; then
+        echo $line
+    fi
+done < "$1"

### 2016-07-26 src/eu/giuswhite/beans/SimianLog.java

@@ -26,8 +26,11 @@ public class SimianLog {
         boolean result = false;
         boolean thereIsStackOverflowFile = false;
         boolean thereIsSrcFile = false;
-        for (LogFragment logFragment : this.fragmentList
-                ) {
+        for (LogFragment logFragment : this.fragmentList) {
+//            if (logFragment.getFilePath().contains("19051537_0.java"))
+//                System.out.println("**** YES: 19051537_0.java ****");
+//            if (logFragment.getFilePath().contains("src/apache-ant-1.8.4/src/main/org/apache/tools/bzip2/CRC.java"))
+//                System.out.println("**** YES: " + logFragment.getFilePath() + " ****");
             if (logFragment.getFilePath().contains(CommonUtils.stackoverflow_path)) {
                 thereIsStackOverflowFile = true;
             } else if (logFragment.getFilePath().contains(CommonUtils.qualitas_path)) {
@@ -35,6 +38,7 @@ public class SimianLog {
             }
         }
         result = thereIsSrcFile && thereIsStackOverflowFile;
+
         return result;
     }
 

### 2016-07-26 src/eu/giuswhite/utils/CommonUtils.java

@@ -22,16 +22,16 @@ public class CommonUtils {
         // 22041769_1.java
         // "12124636_0.java"
         // "21655588_0.java"
-//        if (fragId.contains("16327677_0.java") || fragId.contains("25018225_0.java")
-//                || fragId.contains("21535828_0.java") || fragId.contains("22041769_1.java")
-//                || fragId.contains("12124636_0.java") || fragId.contains("21655588_0.java")
-//                || fragId.contains("5066587_0.java")  || fragId.contains("19051537_0.java")
-//                || fragId.contains("18877151_0.java") || fragId.contains("3215448_0.java")
-//                || fragId.contains("25703453_0.java")) {
-//            System.out.println("Found error fragment: skipping ... ");
-//            return true;
-//        } else
-//            return false;
-        return false;
+        if (fragId.contains("16327677_0.java") || fragId.contains("25018225_0.java")
+                || fragId.contains("21535828_0.java") || fragId.contains("22041769_1.java")
+                || fragId.contains("12124636_0.java") || fragId.contains("21655588_0.java")
+                || fragId.contains("5066587_0.java")  || fragId.contains("19051537_0.java")
+                || fragId.contains("18877151_0.java") || fragId.contains("3215448_0.java")
+                || fragId.contains("25703453_0.java")) {
+            System.out.println("Found error fragment: skipping ... ");
+            return true;
+        } else
+            return false;
+//        return false;
     }
 }

### 2016-07-26 src/eu/giuswhite/utils/XmlFileWriter.java

@@ -24,7 +24,7 @@ public class XmlFileWriter {
             for (SimianLog simianLog : content) {
                 Element sL = new Element("SIMIAN_LOG");
                 sL.setAttribute("ID", String.valueOf(simianLog.id));
-
+                boolean foundErrorFrag = false;
                 for (SimianLog.LogFragment logFragment : simianLog.fragmentList) {
                     // TODO: have to check this list of error fragments everytime before running!
                     // check if the fragment is in the error list, skip it
@@ -35,8 +35,14 @@ public class XmlFileWriter {
                         lF.setAttribute("end", String.valueOf(logFragment.end));
                         sL.addContent(lF);
                     }
+                    else {
+                        // found error pairs, skip the whole cluster
+                        foundErrorFrag = true;
+                    }
                 }
-                root.addContent(sL);
+
+                if (!foundErrorFrag)
+                    root.addContent(sL);
             }
 
             doc.setRootElement(root);

### 2016-07-26 latex/stackoverflow.tex
Updated the report

@@
 
-\begin{table}[h]
-	\centering
-	\caption{528 agreed ok-match(0.7) cloned pairs between Simian and Nicad (510 are unique)}
-	\label{t_agreed_ok_clone_pairs}
-	\begin{tabular}{l|r|r}
-		\hline
-		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-		\hline
-		NiCad$_{\mathrm{\textit{default}}}$ & 373 & 1 \\%      & 709             \\
-		NiCad$_{\mathrm{\textit{fse13}}}$   & 118 & 36 \\ % & 4680            \\
-		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
-		\hline
-	\end{tabular}
-\end{table}
-
-\section*{Duplicated Agreed Clone Pairs}
-
 \begin{table}[H]
@@
 	\centering
-	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings}
+	\caption{528 agreed ok-match(0.7) cloned pairs between Simian and Nicad (510 are unique)}
+	\label{t_agreed_ok_clone_pairs}
+	\begin{tabular}{l|r|r}
+		\hline
+		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+		\hline
+		NiCad$_{\mathrm{\textit{default}}}$ & 373 & 1 \\%      & 709             \\
+		NiCad$_{\mathrm{\textit{fse13}}}$   & 118 & 36 \\ % & 4680            \\
+		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{table}[h]
+	\centering
+	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings  (510 are unique)}
 	\label{t_dup_agreed_ok_clone_pairs}
@@
 
-I have manually investigated all of the 14 \textit{good-match} ones and 183 samples of the \textit{ok-match} ones.
+\section*{Investigation of Missing A/B Clone Pairs Reported by Simian (df)}
+We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
+The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{fse13}$, NiCad$_{df}$, NiCad$_{fse13}$.
+The investigation results are shown in Table \ref{tab:search}.
+
+\begin{table}[H]
+	\centering
+	\caption{Results of matching the original 41 Simian(default) pairs in the pretty-printed result sets}
+	\label{tab:search}
+	\begin{tabular}{l|r|r}
+		\hline 
+		Settings & Found & Not found \\ 
+		\hline 
+		Simian$_{df}$  &  40 & 1* \\ 
+		\hline 
+		Simian$_{fse13}$ & 0 & 41  \\ 
+		\hline 
+		NiCad$_{df}$  & 9 & 32 \\ 
+		\hline 
+		NiCad$_{fse13}$ &  9 & 32 \\ 
+		\hline 
+	\end{tabular} 
+\end{table}
+
+The single missing Stackoverflow fragment (19051537\_0.java) (denoted by *) is one of the 6 false clones generated by Simian.
+It is removed from the results of the pretty-printed version because it is an outlier.
+The rest are missing because of different parameter settings.
+
+\section*{Manual Investigation}
+
+\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
+I have manually investigated all of the 14 \textit{good-match} ones and 510 \textit{ok-match} ones.
+The classification schems is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}.
+
+Since we are not certain about the direction of copying in the B-classified pairs, we checked the modification time of each Java file in Qualitas project and compare it to the timestamp of Stackoverflow answers.
+We found that all Stackoverflow code fragments were posted after their respectively similar Java files in Qualitas project.
+This means that the copying can only be either (1) S $\leftarrow$ Q or (2) from a third source to both S and Q independently.
+
+\subsection{Investigation of extra 100 clone pairs}
+In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations classified in .
+However, only 10 of them appear in the new agreement-based results.
+Thus, we decided to investigate clone pairs reported by Simian and NiCad without agreement from each other.
+With our 4 settings, we investigated the largest 25 clone pairs (according to their average SLOC) resulting in 100 more manually investigated pairs.
 The classification results are shown in Table \ref{tab:classification}.
-The selected 183 pairs are results of filtering fragments with the same starting and ending clone lines by keeping only one of them (i.e.
-strict version).
-Then, we found a lot of similar clone pairs having the same classification results.
-If we only keep unique Stackoverflow fragments (with the largest Qualitas clone size), it results in 82 pairs (i.e.
-loose version).
 
-\begin{table}
+\begin{table}[H]
 	\centering
-	\caption{Classification results of 14 \textit{good} and 183 \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
+	\caption{Classification results of 14 \textit{good} and 510 \textit{ok}-matches (including the subsumed \textit{good}-match pairs).}
 	\label{tab:classification}
@@
 		\hline
+		\multirow{2}{*}{100 indv. pairs} & 12 & 6 & 1 & 18 & 1 & 62 & 100 \\ \cline{2-8}
+		& 12\%	& 6\%	&	1\%	&	18\%	&	1\%	&	62\%	&	100\%  \\ 
+		\hline
 	\end{tabular} 
@@
 
-\begin{table}
+\begin{table}[H]
 	\centering
 	\caption{Classifications of clone creation}
+	\label{tab:classification_scheme}
 	\begin{tabular}{|c|p{13cm}|}
@@
 		\hline 
-	A & Code in Stackoverflow is copied from Qualitas (S ← Q). \\ 
+		A & Code in Stackoverflow is copied from Qualitas (S $\leftarrow$ Q). \\ 
 		\hline 
-	B & Code is copied either from each other or a third source (unknown) (S ←→ Q).
+		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q).
 		\\ 
 		\hline 
-	C & Code in both places are copied from a third source T (known) (S, Q ← T ).
+		C & Code in both places are copied from a third source T (known) (S, Q $\leftarrow$ T ).
 		\\ 
@@
 		F & Accidental similarity  \\ 
-	\hline 
-\end{tabular} 
-\end{table}
-
-\section*{Investigation of Missing A/B Clone Pairs Reported by Simian (df)}
-We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
-The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{fse13}$, NiCad$_{df}$, NiCad$_{fse13}$.
-The investigation results are shown in Table \ref{tab:search}.
-
-\begin{table}[H]
-	\centering
-	\caption{Search results of 41 Simian(df) pairs in the new 4 result sets}
-	\label{tab:search}
-\begin{tabular}{l|r|r}
-	\hline 
-	Settings & Found & Not found \\ 
-	\hline 
-	Simian$_{df}$  &  40 & 1 \\ 
-	\hline 
-	Simian$_{fse13}$ & 0 & 41  \\ 
-	\hline 
-	NiCad$_{df}$  & 9 & 32 \\ 
-	\hline 
-	NiCad$_{fse13}$ &  9 & 32 \\ 
 		\hline 

### 2016-08-09 latex/stackoverflow.tex
Updated manual results of individual tools

@@
 \subsection{Investigation of extra 100 clone pairs}
-In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations classified in .
-However, only 10 of them appear in the new agreement-based results.
-Thus, we decided to investigate clone pairs reported by Simian and NiCad without agreement from each other.
+In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
+However, only 10 of them appear in the new results using tool's agreement.
+Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.
 With our 4 settings, we investigated the largest 25 clone pairs (according to their average SLOC) resulting in 100 more manually investigated pairs.
-The classification results are shown in Table \ref{tab:classification}.
+The classification results are shown in Table \ref{tab:classification} and Table \ref{tab:classification_breakdown}.
 
@@
 		& 12\%	& 6\%	&	1\%	&	18\%	&	1\%	&	62\%	&	100\%  \\ 
+		\hline
+	\end{tabular} 
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\caption{Breakdowns of 100 individual clone pairs}
+	\label{tab:classification_breakdown}
+	\begin{tabular}{|l|r|r|r|r|r|r|r|}
+		\hline 
+		Classification & A & B & C & D & E & F & Total \\ 
+		\hline 
+		Simian$_df$ & 12 & 6 & 1 & 2 & 0 & 4 & 25 \\ 
+		\hline
+		Simian$_fse13$ & 0 & 0 & 0 & 0 & 0 & 25 & 25 \\
+		\hline
+		NiCad$_df$ & 0 & 0 & 0 & 11 & 0 & 14 & 25 \\
+		\hline
+		NiCad$_fse13$ & 0 & 0 & 0 & 5 & 1 & 19 & 25 \\
+		\hline
+		Total & 12 & 6 & 1 & 18 & 1 & 62 & 100 \\
 		\hline
@@
 \end{table}
+
+\newpage
 

### 2016-08-11 latex/stackoverflow.tex
Updated results

@@
 
-\title{Online Source Code Reuse: A Case Study of Stackoverflow \textit{vs.~}Qualitas OSS}
+\title{Code Overflow: An empirical study of online code reuse between Stackoverflow \textit{vs.~}Qualitas OSS}
 \maketitle
@@
 	\centering
-	\caption{Simian clone results}
+	\caption{Qualitas (2013-09-01r): Simian and NiCad clone results}
 	\label{t_simian_raw_results}
-	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
 		\hline
-		\multirow{4}{*}{} 
-		& \multicolumn{4}{c|}{Default settings} 
-		& \multicolumn{4}{c|}{Default settings*} 
-		& \multicolumn{4}{c}{FSE'13 settings} \\ \cline{2-13} % & \multicolumn{4}{c}{CloPlag settings} \\
+		\multirow{4}{*}{Statistics} 
+		& \multicolumn{4}{c|}{Simian Default settings} 
+		& \multicolumn{4}{c|}{Simian FSE'13 settings}
+		& \multicolumn{4}{c|}{Simian Default settings} 
+		& \multicolumn{4}{c}{Simian FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
 		& \multicolumn{4}{c|}{threshold=6} 
-		& \multicolumn{4}{c|}{threshold=6} 
-		& \multicolumn{4}{c}{threshold=5}  \\  % & \multicolumn{4}{c}{threshold=5} \\
-		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} &
-		\multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC,bSqBrck} & \multicolumn{4}{c}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} \\\cline{2-13}  %  & \multicolumn{4}{c}{iId} \\
+		& \multicolumn{4}{c|}{threshold=5}  
+		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
+		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
+		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
+		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
+		& \multicolumn{4}{c|}{rename=none,abstract=none} 
+		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
 		% \hline
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
 		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
@@
 		\hline
-		Removed & 6 & -- & -- & -- & 0 & -- & -- & -- & 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-		Total          & 647       & 24,802       & --         & --  & 3   & 10 & -- & -- &  152 & 7,289,272 & -- & --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
-		Mean           & --        & 38           & 7.53       & 0.27   & -- & 3.33 & 8 & 0.29 & -- & 47,956 & 4.76 & 0.27 \\ % & -- & 9,356 & 4.74 & 0.26 \\
-		Std Dev.       & -- 		  & 87		& 3.87 & 0.22 & -- & 2.62 & 1.41 & 0.18 & -- & 433,467 & 0.93 & 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
-		Max            & --       & 551         & 63          & 0.94  & -- & 7	& 10 & 0.54 & -- & 5,278,408 & 8 & 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
-		Min            & --       & 1           & 5           & 0.01  & -- & 1 & 7 & 0.10 & -- & 1 & 4 & 0.01 \\ % & -- & 1 & 4 & 0.002 \\
-		Median         & --       & 3           & 7           & 0.22  & -- & 2 & 7 & 0.24 & -- & 22.5 & 4 & 0.23 \\ % & -- & 27 & 4 & 0.22 \\
-		Mode           & --       & 1           & 7           & 0.25  & -- & N/A & 7 & N/A & -- & 1 & 4 & 0.50 \\ % & -- & 1 & 4 & 0.50 \\
+		%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
+		Total & 647 & 24,802 & -- & -- &  152 & 7,289,272 & -- & -- & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
+		Mean & -- & 38 & 7.53 & 0.27 & -- & 47,956 & 4.76 & 0.27 & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\ % & -- & 9,356 & 4.74 & 0.26 \\
+		Std Dev. & -- & 87 & 3.87 & 0.22 & -- & 433,467 & 0.93 & 0.18 & 	& 200 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\ % & -- & 96,038	& 0.99 & 0.18 \\
+		Max & -- & 551 & 63 & 0.94 & -- & 5,278,408 & 8 & 0.83 & -- & 1,816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88\\ % & -- & 7,837,204 & 28 & 0.94 \\
+		Min & -- & 1 & 5 & 0.01 & -- & 1 & 4 & 0.01 & -- & 1 & 7 & 0.02 & -- & 1 & 3 & 0.01 \\ % & -- & 1 & 4 & 0.002 \\
+		Median & -- & 3 & 7 & 0.22 & -- & 22.5 & 4 & 0.23 & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\ % & -- & 27 & 4 & 0.22 \\
+		Mode & -- & 1 & 7 & 0.25 & -- & 1 & 4 & 0.50 & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\ % & -- & 1 & 4 & 0.50 \\
 		\hline
-	\end{tabular} 
+	\end{tabular} %
+}
 \end{table*}
@@
 	\centering
-	\caption{NiCad clone results}
-	\label{t_nicad_raw_results}
-		\begin{tabular}{l|r|r|r|r|r|r|r|r}
+	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (45 new + 18 old Qualitas projects)}
+	\label{t_simian_raw_results}
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
 		\hline
-			\multirow{4}{*}{} & \multicolumn{4}{c|}{Default settings} & \multicolumn{4}{c}{FSE'13 settings} \\ \cline{2-9} 
-			%& \multicolumn{4}{c|}{Default settings} & \multicolumn{4}{c|}{FSE'13 settings}  & \multicolumn{4}{c}{CloPlag settings} \\
-			%\hline
-			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} & \multicolumn{4}{c}{threshold=5, UPI=0.2} \\ % & \multicolumn{4}{c}{threshold=6, UPI=0.4} \\
-			& \multicolumn{4}{c|}{rename=none,abstract=none} & \multicolumn{4}{c}{rename=blind,abstract=literal} \\ \cline{2-9} % & \multicolumn{4}{c}{rename=blind,abstract=declaration} \\
-			%\hline
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+		\multirow{4}{*}{Statistics} 
+		& \multicolumn{4}{c|}{Simian Default settings} 
+		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
+		& \multicolumn{4}{c|}{NiCad Default settings} 
+		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
+		& \multicolumn{4}{c|}{threshold=6} 
+		& \multicolumn{4}{c|}{threshold=5} 
+		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
+		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
+		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
+		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
+		& \multicolumn{4}{c|}{rename=none,abstract=none} 
+		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
+		% \hline
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
 		\hline
-			Total & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --    \\
-			Mean & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\
-			Std Dev. & 	& 200.49 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\
-			Max & -- & 1816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88 \\
-			Min & -- & 1 & 7 & 0.02 & -- & 1 & 3	 & 0.01 \\
-			Median & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\
-			Mode & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\
+		%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
+		Total 	& 789 	& 61,164 & -- 	& -- 	&  170 	& 11,915,544 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
+		Mean 	& -- 	& 78 	& 7.32 	& 0.26 	& -- 	& 70,091 	& 4.76 	& 0.29 \\ % & -- & 9,356 & 4.74 & 0.26 \\
+		Std Dev. & -- 	& 208 	& 2.71 	& 0.21 	& -- 	& 703,788 	& 0.89 	& 0.19 \\ % & -- & 96,038	& 0.99 & 0.18 \\
+		Max 	& -- 	& 1,300 & 49 	& 0.94 	& -- 	& 9,065,774 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
+		Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
+		Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 17 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
+		Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
+		\hline
+	\end{tabular} %
+}
+\end{table*}
+
+\begin{table*}[h]
+	\centering
+	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 45 new Qualitas projects)}
+	\label{t_simian_raw_results}
+	\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
+			\hline
+			\multirow{4}{*}{Statistics} 
+			& \multicolumn{4}{c|}{Simian Default settings} 
+			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
+			& \multicolumn{4}{c|}{NiCad Default settings} 
+			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
+			& \multicolumn{4}{c|}{threshold=6} 
+			& \multicolumn{4}{c|}{threshold=5} 
+			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
+			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
+			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
+			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
+			& \multicolumn{4}{c|}{rename=none,abstract=none} 
+			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
+			% \hline
+			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+			\hline
+			%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
+			Total 	& 736 	& 60,678 & -- 	& -- 	&  166 	& 10,273,534 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
+			Mean 	& -- 	& 82 	& 7.26 	& 0.26 	& -- 	& 61,889 	& 4.77 	& 0.28 \\ % & -- & 9,356 & 4.74 & 0.26 \\
+			Std Dev. & -- 	& 214 	& 2.24 	& 0.21 	& -- 	& 607,074 	& 0.89 	& 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
+			Max 	& -- 	& 1,298 & 32 	& 0.94 	& -- 	& 7,720,970 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
+			Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
+			Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 16.5 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
+			Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
+			\hline
+		\end{tabular} %
+	}
+\end{table*}
+
+\begin{table}[h]
+	\centering
+	\caption{63 Qualitas projects (new versions checked on 2016-08-05)}
+	\label{t:new_and_old}
+\begin{tabular}{l|r|r|l}
+	\hline 
+	Projects & Old version & New versions & License \\
+	\hline
+	ArgoUML & 0.34 & \\
+	Compiere & 330 & \\
+	FitLibrary20100806 & & \\
+	JGroups & 2 & \\
+	Vuze & 4812 & \\
+	antlr & 4-4.0 & \\
+	aoisrc & 281 & \\
+	apache-ant & 1.8.4 & \\
+	aspectj & 1.6.9 & \\
+	axion & 1.0-M2 & \\
+	batik & 1.7 & \\
+	c-jdbc & 2 & \\
+	castor & 1 & \\
+	cayenne & 3 & \\
+	checkstyle & 5 & \\
+	cobertura & 1 & \\
+	colt & 1 & \\
+	columba & 1 & \\
+	commons-collections & 3 & \\
+	db-derby & 10 & \\
+	displaytag & 1 & \\
+	drawswf & 1 & \\
+	drjava & 20100913-r5387-src & \\
+	eXoPortal & v1 & \\
+	emma & 2 & \\
+	findbugs & 1 & \\
+	fit-java & 1 & \\
+	freecol & 0 & \\
+	freecs & 1 & \\
+	freemind & 0 & \\
+	galleon & 2 & \\
+	ganttproject & 2 & \\
+	geotools & 2 & \\
+	hadoop & 1 & \\
+	heritrix & 1 & \\
+	hibernate & release-4 & \\
+	hsqldb & 2 & \\
+	htmlunit & 2 & \\
+	iReport & 3 & \\
+	iText & 5 & \\
+	informa & 0 & \\
+	ivatagroupware & 0 & \\
+	jFin DateMath & R1\_0\_1 & \\
+	jOggPlayer & 114s & \\
+	jag & 6 & \\
+	james & 2 & \\
+	jasml & 0 & \\
+	jasperreports & 3 & \\
+	javacc & 5 & \\
+	jboss & 5 & \\
+	jchempaint & 3 & \\
+	jedit & 4 & \\
+	jena & 2 & \\
+	jext & 5 & \\
+	jfreechart & 1 & \\
+	jgraph & latest-bsd & \\
+	jgraphpad & 5 & \\
+	jgrapht & 0 & \\
+	jmoney & 0 & \\
+	jparse & & \\
+	jpf & 1 & \\
+	junit & 4 & \\
+	shiftone-jrat & 0 & \\
 	\hline 
 \end{tabular} 
-\end{table*}
-
-%\section*{Agreed Cloned Fragments}
-%The results from both tools are compared to find clone pairs that they mutually agree.
-Theses agreed clone pairs will be manually investigated.
-The results of agreed clone pairs found by different parameter settings of Simian and NiCad are shown in Table \ref{t_agreed_clone}.
-
-%\begin{table}[h]
-%	\centering
-%	\caption{Agreed cloned fragments between Simian and Nicad}
-%	\label{t_agreed_clone}
-%	\begin{tabular}{l|r|r}
-%		\hline
-%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-%		\hline
-%		NiCad$_{\mathrm{\textit{default}}}$ & 92          & 1        \\%      & 709             \\
-%		NiCad$_{\mathrm{\textit{fse13}}}$   & 155         & 25           \\ % & 4680            \\
-		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
-%		\hline
-%	\end{tabular}
-%\end{table}
-
-%Relationships between the cloned fragments are displayed in Fig.~\ref{fig:venn4}.
-
-%\begin{figure}[H]
-%\centering
-%\includegraphics[width=0.5\linewidth]{venn4}
-%\caption[Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings]{Agreed clone fragments reported by Simian and NiCad with default and FSE'13 settings}
-%\label{fig:venn4}
-%\end{figure}
+\end{table}
 
@@
 
-The single missing Stackoverflow fragment (19051537\_0.java) (denoted by *) is one of the 6 false clones generated by Simian.
+The single missing Stackoverflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian.
 It is removed from the results of the pretty-printed version because it is an outlier.
@@
 We found that all Stackoverflow code fragments were posted after their respectively similar Java files in Qualitas project.
-This means that the copying can only be either (1) S $\leftarrow$ Q or (2) from a third source to both S and Q independently.
+This means that the copying can only be either (1) Q $\rightarrow$ S or (2) from a third source to both S and Q independently.
 
-\subsection{Investigation of extra 100 clone pairs}
+\subsection{Investigation of the largest unique 172 clone pairs}
 In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
@@
 Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.
-With our 4 settings, we investigated the largest 25 clone pairs (according to their average SLOC) resulting in 100 more manually investigated pairs.
+With our 4 settings, we investigated the largest 172 clone pairs according to their average SLOC (larger than or equals to 15 SLOC).
+These clone pairs are pairs of Stackoverflow fragments and Java files from Qualitas projects that NEVER been looked at before in the previous investigation.
+The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stackoverflow fragments or Qualitas files.
 The classification results are shown in Table \ref{tab:classification} and Table \ref{tab:classification_breakdown}.
@@
 		\hline
-		\multirow{2}{*}{100 indv. pairs} & 12 & 6 & 1 & 18 & 1 & 62 & 100 \\ \cline{2-8}
-		& 12\%	& 6\%	&	1\%	&	18\%	&	1\%	&	62\%	&	100\%  \\ 
+		\multirow{2}{*}{172 indv. pairs} & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\ \cline{2-8}
+		& 9.88\% & 4.07\% & 1.74\% & 12.21\% & 2.91\% & 69.19\% & 100.00\%  \\ 
 		\hline
@@
 	\centering
-	\caption{Breakdowns of 100 individual clone pairs}
+	\caption{Breakdowns of the biggest 172 individual clone pairs}
 	\label{tab:classification_breakdown}
@@
 		\hline 
-		Simian$_df$ & 12 & 6 & 1 & 2 & 0 & 4 & 25 \\ 
+		Simian$_{df}$ & 16 & 7 & 3 & 7 & 4 & 3 & 40 \\ 
 		\hline
-		Simian$_fse13$ & 0 & 0 & 0 & 0 & 0 & 25 & 25 \\
+		Simian$_{fse13}$ & 1 & 0 & 0 & 1 & 0 & 53 & 55 \\
 		\hline
-		NiCad$_df$ & 0 & 0 & 0 & 11 & 0 & 14 & 25 \\
+		NiCad$_{df}$ & 0 & 0 & 0 & 13 & 0 & 22 & 35 \\
 		\hline
-		NiCad$_fse13$ & 0 & 0 & 0 & 5 & 1 & 19 & 25 \\
+		NiCad$_{fse13}$ & 0 & 0 & 0 & 0 & 1 & 41 & 42 \\
 		\hline
-		Total & 12 & 6 & 1 & 18 & 1 & 62 & 100 \\
+		Total & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\
 		\hline
@@
 		\hline 
-		A & Code in Stackoverflow is copied from Qualitas (S $\leftarrow$ Q). \\ 
+		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
 		\hline 
-		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q).
+		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
+		\hline 
+		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
 		\\ 
 		\hline 
-		C & Code in both places are copied from a third source T (known) (S, Q $\leftarrow$ T ).
+		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
 		\\ 
@@
 		\hline 
-		F & Accidental similarity  \\ 
+		F & Accidental similarity, false clone \\ 
 		\hline 

### 2016-08-11 src/eu/giuswhite/utils/CommonUtils.java

@@ -28,7 +28,7 @@ public class CommonUtils {
                 || fragId.contains("5066587_0.java")  || fragId.contains("19051537_0.java")
                 || fragId.contains("18877151_0.java") || fragId.contains("3215448_0.java")
                 || fragId.contains("25703453_0.java")) {
-            System.out.println("Found error fragment: skipping ... ");
+            System.out.println("Found error fragment " + fragId + ": skipping ... ");
             return true;
         } else
             return false;

### 2016-08-11 latex/stackoverflow.tex
Added licenses

@@
 
-\title{Code Overflow: An empirical study of online code reuse between Stackoverflow \textit{vs.~}Qualitas OSS}
+\title{Code Overflow: \\
+	An empirical study of online code reuse}
 \maketitle
@@
 
-\begin{table}[h]
+\begin{table}[H]
 	\centering
@@
 	\label{t:new_and_old}
-\begin{tabular}{l|r|r|l}
+\begin{tabular}{l|r|r|c|p{5cm}|p{3cm}}
 	\hline 
-	Projects & Old version & New versions & License \\
+	Projects & Old version & New versions & Latest change & License & Notes \\
 	\hline
-	ArgoUML & 0.34 & \\
-	Compiere & 330 & \\
-	FitLibrary20100806 & & \\
-	JGroups & 2 & \\
-	Vuze & 4812 & \\
-	antlr & 4-4.0 & \\
-	aoisrc & 281 & \\
-	apache-ant & 1.8.4 & \\
-	aspectj & 1.6.9 & \\
-	axion & 1.0-M2 & \\
-	batik & 1.7 & \\
-	c-jdbc & 2 & \\
-	castor & 1 & \\
-	cayenne & 3 & \\
-	checkstyle & 5 & \\
-	cobertura & 1 & \\
-	colt & 1 & \\
-	columba & 1 & \\
-	commons-collections & 3 & \\
-	db-derby & 10 & \\
-	displaytag & 1 & \\
-	drawswf & 1 & \\
-	drjava & 20100913-r5387-src & \\
-	eXoPortal & v1 & \\
-	emma & 2 & \\
-	findbugs & 1 & \\
-	fit-java & 1 & \\
-	freecol & 0 & \\
-	freecs & 1 & \\
-	freemind & 0 & \\
-	galleon & 2 & \\
-	ganttproject & 2 & \\
-	geotools & 2 & \\
-	hadoop & 1 & \\
-	heritrix & 1 & \\
-	hibernate & release-4 & \\
-	hsqldb & 2 & \\
-	htmlunit & 2 & \\
-	iReport & 3 & \\
-	iText & 5 & \\
-	informa & 0 & \\
-	ivatagroupware & 0 & \\
-	jFin DateMath & R1\_0\_1 & \\
-	jOggPlayer & 114s & \\
-	jag & 6 & \\
-	james & 2 & \\
-	jasml & 0 & \\
-	jasperreports & 3 & \\
-	javacc & 5 & \\
-	jboss & 5 & \\
-	jchempaint & 3 & \\
-	jedit & 4 & \\
-	jena & 2 & \\
-	jext & 5 & \\
-	jfreechart & 1 & \\
-	jgraph & latest-bsd & \\
-	jgraphpad & 5 & \\
-	jgrapht & 0 & \\
-	jmoney & 0 & \\
-	jparse & & \\
-	jpf & 1 & \\
-	junit & 4 & \\
-	shiftone-jrat & 0 & \\
+	ArgoUML & 0.34 & 0.35.1 & 15/01/2014 & Eclipse Public License v.1.0 & \\
+	Compiere & 330 & -- & 01/06/2010 &  GNU General Public License v.2.0 & No longer OSS \\
+	FitLibrary & 20100806 & 20111026 & 12/07/2014 & GNU General Public License v.2.0 & \\
+	JGroups & 2.10.0.GA & 3.6.10 & 27/06/2016  & Apache License, v.2.0 & \\
+	Vuze & 4812 & 5721-20 & 12/05/2016 & GNU General Public License v.2.0 &  \\
+	antlr4 & 4.0 & 4.2.1 & 15/01/2014 & BSD License & \\
+	aoisrc & 281 & 302 & 12/01/2015 &  GNU General Public License v.2.0 & \\
+	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & Apache License, v.2.0 & \\
+	aspectj & 1.6.9 & 1.8.9 & 14/03/2015 & Eclipse Public License 1.0 & \\
+	axion & 1.0-M2 & -- & 08/03/2013 & Proprietary (BSD/Apache-style) & \\
+	batik & 1.7 & 1.8 & 16/03/2015 & Apache License, v.2.0 & \\
+	c-jdbc & 2.0.2 & -- & 16/09/2005 & GNU Lesser General Public License, v.2.1 & \\
+	castor & 1.3.1 & 1.4.2 & 20/06/2016 & Apache License, v.2.0 & \\
+	cayenne & 3.0.1 & 4.0.M4 &  27/07/2016 & Apache License, v.2.0 & \\
+	checkstyle & 5.1 & 7.2  & 04/08/2016 & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
+	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2015 & GNU General Public License v.2.0  & \\
+	colt & 1.2.0 & -- & 09/09/2014 &  Proprietary (CERN) & \\
+	columba & 1.4 & -- & 20/04/2007 & Mozilla Public License 1.1  & \\
+	commons-collections & 3.2.1 & 4.1 & 25/11/2015 & Apache License, v.2.0 & \\
+	db-derby & 10.6.1.0 & 10.12.1.1 & 13/09/2015 & Apache License, v.2.0 & \\
+	displaytag & 1.2 & 2.0 & 17/08/2014 & MIT License & \\
+	drawswf & 1.2.9 & -- & 02/04/2013 & GNU General Public License v.2.0 & \\
+	drjava & 20100913-r5387 & 20140826-r5761 & 26/08/2014 & BSD License & \\
+	eXoPortal & ??? & 4.4 & 24/06/2016 & GNU Lesser General Public License v.3.0 \& proprietary & \\
+	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & Common Public License 1.0 & \\
+	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & GNU Lesser General Public License, v.2.0 & \\
+	fit-java & 1.1 & -- & 04/06/2013 & GNU General Public License v.2.0 & \\
+	freecol & 0.10.7 & 0.11.6 & 04/08/2016 & GNU General Public License v.2.0 &  \\
+	freecs & 1.3.20100406 & -- & 22/04/2013 & GNU General Public License v.3.0 &   \\
+	freemind & 0.9.0 & 1.0.0 & 26/06/2016 & GNU General Public License v.2.0+ &  \\
+	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & GNU General Public License v.2.0 & \\
+	ganttproject & 2.0.9 & 2.8.1 & 05/08/2016 & GNU General Public License v.3.0 &  \\
+	geotools & 2.7-M3 & 16 & 02/08/2016 & GNU Lesser General Public License, v.2.0 & \\
+	hadoop & 1.0.0 & 2.6.4 & 11/02/2016 & Apache License, v.2.0 & \\
+	heritrix & 1.14.4 & -- & 05/06/2013 & GNU Lesser General Public License, v.2.1 & \\
+	hibernate & 4.2.2 & 5.2.2 & 04/08/2016 & GNU Lesser General Public License, v.2.1+ & \\
+	hsqldb & 2.0.0 & 2.3.4 & 16/05/2016 & BSD License & \\
+	htmlunit & 2.8 & 2.24 & 27/07/2016 & Apache License, v.2.0 & \\
+	iReport & 3.7.5 & -- & 28/05/2014 & Affero GNU Public License, v.3.0 & \\
+	iText & 5.0.3 & 7.0.0 & 02/05/2016 & Affero GNU Public License, v.3.0 & \\
+	informa & 0.7.0-alpha2 & -- & 07/11/2008 & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 & \\
+	ivatagroupware & 0.11.3 & -- & 27/02/2013  & GNU General Public License v.2.0 & \\
+	jFin DateMath & R1\_0\_1 & -- & 25/04/2013  & GNU General Public License v.2.0 & \\
+	jOggPlayer & 114s & -- &  15/04/2013   & GNU General Public License v.2.0 & \\
+	jag & 6.1 & 6.2 & 08/04/2013   & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries they use. \\
+	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & Apache License, v.2.0 & \\
+	jasml & 0.10 & -- & 08/03/2013 & Apache Software License & \\
+	jasperreports & 3.7.4 & 6.3.1 & 20/06/2016 & GNU Lesser General Public License, v.3.0 &  \\
+	javacc & 5.0.0 & 7.0.0 & 07/07/2016 & Proprietary (Sun) & \\
+	jboss (Wildfly) & 5.1.0.GA & 10.0.0 & 29/01/2016 & GNU Lesser General Public License, v.2.1 & It is renamed to Wildfly. \\
+	jchempaint & 3.0.1 & 3.1.3 & 18/04/2016 & GNU Lesser General Public License, v.2.1+ &  \\
+	jedit & 4.3.2 & 5.3.0 & 20/10/2015  & GNU General Public License v.2.0 &  \\
+	jena & 2.6.3 & 3.1.0 & 10/05/2016 & Apache License, v.2.0 & \\
+	jext & 5.0 & -- & 18/08/2004   & GNU General Public License v.2.0 &  \\
+	jfreechart & 1.0.13 & 1.2.0-ea1 & 08/05/2016  & GNU Lesser General Public License, v.2.0 &   \\
+	jgraph & 5.13.0.0 & 3.5.1.5 & 20/07/2016 & Proprietary (mxGraph License) & \\
+	jgraphpad & 5.10.0.2 & -- & 10/11/2006 & GNU General Public License  \& GNU Lesser General Public License (derivatives) & \\
+	jgrapht & 0.8.1 & 0.9.2 & 03/04/2016 & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 & \\
+	jmoney & 0.4.4 & -- & 17/04/2016 & GNU General Public License v.2.0 &  \\
+	jparse & 0.96 & -- & 29/07/2004 & GNU Lesser General Public License, v.2.1 & \\
+	jpf & 1.5.1 & ??? & 13/01/2012 & Apache License, v.2.0 & \\
+	junit & 4.11 & 4.12 & 04/12/2014 & Eclipse Public License, v.1.0 & \\
+	shiftone-jrat & 0.6 & 1-beta-1 & 25/04/2013 & GNU Lesser General Public License, v.2.0 &  \\
 	\hline 

### 2016-08-11 src/eu/giuswhite/utils/CommonUtils.java
Moved old stuffs (before fixing the comment problem) to old_stuffs

@@ -16,22 +16,16 @@ public class CommonUtils {
     public static final String qualitas_path = "src/";
 
     public static boolean isError(String fragId) {
-        // 16327677_0.java
-        // 25018225_0.java
-        // 21535828_0.java
-        // 22041769_1.java
-        // "12124636_0.java"
-        // "21655588_0.java"
+        // check for 11 fragments generating Simian's sliding error clones.
         if (fragId.contains("16327677_0.java") || fragId.contains("25018225_0.java")
                 || fragId.contains("21535828_0.java") || fragId.contains("22041769_1.java")
                 || fragId.contains("12124636_0.java") || fragId.contains("21655588_0.java")
-                || fragId.contains("5066587_0.java")  || fragId.contains("19051537_0.java")
+                || fragId.contains("5066587_0.java") || fragId.contains("19051537_0.java")
                 || fragId.contains("18877151_0.java") || fragId.contains("3215448_0.java")
                 || fragId.contains("25703453_0.java")) {
             System.out.println("Found error fragment " + fragId + ": skipping ... ");
             return true;
         } else
             return false;
-//        return false;
     }
 }

### 2016-08-11 src/eu/giuswhite/utils/CsvFileWriter.java

@@ -71,7 +71,7 @@ public class CsvFileWriter {
             for (SimianStackoverflowFragment fragment : list) {
                 System.out.print(".");
                 // skip if they're false clones generated from simian's bug
-                if (! CommonUtils.isError(fragment.fragmentName)) {
+                if (!CommonUtils.isError(fragment.fragmentName)) {
                     listWriter.write(fragment.fragmentName, fragment.numberOfTimeIsUsed,
                             fragment.projectsWhereIsUsed.size(), fragment.getSLOC(), fragment.getCloneLines(),
                             ((double) fragment.getCloneLines()) / fragment.getSLOC());

### 2016-08-14 latex/stackoverflow.tex
Many changes. Added new results after fixing comment problems

--- 2016-08-11 latex/stackoverflow.tex
@@
 
-Manual investigation of Simian's clone report showed that there were problematic fragments (6 for defaults, 0 for FSE'13, and 11 for CloPlag).
+Manual investigation of Simian's clone report showed that there were problematic 11 fragments.
 These fragments generate false clone containing array initialisation.
@@
 		%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-		Total & 647 & 24,802 & -- & -- &  152 & 7,289,272 & -- & -- & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
-		Mean & -- & 38 & 7.53 & 0.27 & -- & 47,956 & 4.76 & 0.27 & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\ % & -- & 9,356 & 4.74 & 0.26 \\
-		Std Dev. & -- & 87 & 3.87 & 0.22 & -- & 433,467 & 0.93 & 0.18 & 	& 200 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\ % & -- & 96,038	& 0.99 & 0.18 \\
-		Max & -- & 551 & 63 & 0.94 & -- & 5,278,408 & 8 & 0.83 & -- & 1,816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88\\ % & -- & 7,837,204 & 28 & 0.94 \\
-		Min & -- & 1 & 5 & 0.01 & -- & 1 & 4 & 0.01 & -- & 1 & 7 & 0.02 & -- & 1 & 3 & 0.01 \\ % & -- & 1 & 4 & 0.002 \\
-		Median & -- & 3 & 7 & 0.22 & -- & 22.5 & 4 & 0.23 & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\ % & -- & 27 & 4 & 0.22 \\
-		Mode & -- & 1 & 7 & 0.25 & -- & 1 & 4 & 0.50 & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\ % & -- & 1 & 4 & 0.50 \\
+		Total  	& 654 	& 24,929 	& -- 	& --	& 1,175 & 16,957,362 & --	& --	& 985 	& 105,118 	& --	& --	& 12,084	& 113,557,298 & --		& -- \\
+		Mean  	& --	& 38 		& 7.54 	& 0.27 	& --	& 14,444 	& 4.80 	& 0.28 	& --	& 107 		& 9.52 	& 0.25 	& -- 		& 9,397 	& 5.21 		& 0.20 \\
+		Std Dev. & --  	& 87 		& 3.21 	& 0.22 	& --	& 281,747 	& 1.22 	& 0.18 	& --	& 198 		& 3.07 	& 0.18 	& --		& 12,098 	& 1.73 		& 0.16 \\
+		Max  	& --	& 551 		& 49.00 & 0.94 	& --	& 9,599,676 & 18.00 & 0.89 	& --	& 1,792 	& 39.00 & 0.80 	& --		& 227,077 	& 44.00 	& 0.86 \\
+		Min  	& --	& 1 		& 5.00 	& 0.01 	& --	& 1 		& 4.00 	& 0.02 	& --	& 1 		& 7.00 	& 0.02 	& --		& 1 		& 3.00 		& 0.01 \\
+		Median  & --	& 3 		& 7.00 	& 0.23 	& --	& 22 		& 5.00 & 0.24 	& --	& 15 		& 8.00 	& 0.19 	& --		& 6,105 	& 5.00 		& 0.15 \\
+		Mode  	& --	& 1 		& 7.00 	& 0.25 	& --	& 1 		& 4.00 	& 0.50 	& --	& 1 		& 8.00 	& 0.53 	& --		& 1 		& 4.00 		& 0.33 \\
 		\hline
@@
 	\label{t:new_and_old}
-\begin{tabular}{l|r|r|l}
+\begin{tabular}{l|r|r|c|p{5cm}|p{3cm}}
 	\hline 
-	Projects & Old version & New versions & License \\
+	Projects & Old version & New versions & Latest change & License & Notes \\
 	\hline
-	ArgoUML & 0.34 & \\
-	Compiere & 330 & \\
-	FitLibrary20100806 & & \\
-	JGroups & 2 & \\
-	Vuze & 4812 & \\
-	antlr & 4-4.0 & \\
-	aoisrc & 281 & \\
-	apache-ant & 1.8.4 & \\
-	aspectj & 1.6.9 & \\
-	axion & 1.0-M2 & \\
-	batik & 1.7 & \\
-	c-jdbc & 2 & \\
-	castor & 1 & \\
-	cayenne & 3 & \\
-	checkstyle & 5 & \\
-	cobertura & 1 & \\
-	colt & 1 & \\
-	columba & 1 & \\
-	commons-collections & 3 & \\
-	db-derby & 10 & \\
-	displaytag & 1 & \\
-	drawswf & 1 & \\
-	drjava & 20100913-r5387-src & \\
-	eXoPortal & v1 & \\
-	emma & 2 & \\
-	findbugs & 1 & \\
-	fit-java & 1 & \\
-	freecol & 0 & \\
-	freecs & 1 & \\
-	freemind & 0 & \\
-	galleon & 2 & \\
-	ganttproject & 2 & \\
-	geotools & 2 & \\
-	hadoop & 1 & \\
-	heritrix & 1 & \\
-	hibernate & release-4 & \\
-	hsqldb & 2 & \\
-	htmlunit & 2 & \\
-	iReport & 3 & \\
-	iText & 5 & \\
-	informa & 0 & \\
-	ivatagroupware & 0 & \\
-	jFin DateMath & R1\_0\_1 & \\
-	jOggPlayer & 114s & \\
-	jag & 6 & \\
-	james & 2 & \\
-	jasml & 0 & \\
-	jasperreports & 3 & \\
-	javacc & 5 & \\
-	jboss & 5 & \\
-	jchempaint & 3 & \\
-	jedit & 4 & \\
-	jena & 2 & \\
-	jext & 5 & \\
-	jfreechart & 1 & \\
-	jgraph & latest-bsd & \\
-	jgraphpad & 5 & \\
-	jgrapht & 0 & \\
-	jmoney & 0 & \\
-	jparse & & \\
-	jpf & 1 & \\
-	junit & 4 & \\
-	shiftone-jrat & 0 & \\
+	ArgoUML & 0.34 & 0.35.1 & 15/01/2014 & Eclipse Public License v.1.0 \\
+	Compiere & 330 & -- & 01/06/2010 &  GNU General Public License v.2.0 & No longer OSS \\
+	FitLibrary & 20100806 & 20111026 & 12/07/2014 & GNU General Public License v.2.0 \\
+	JGroups & 2.10.0.GA & 3.6.10 & 27/06/2016  & Apache License, v.2.0 \\
+	Vuze & 4812 & 5721-20 & 12/05/2016 & GNU General Public License v.2.0 &  \\
+	antlr4 & 4.0 & 4.2.1 & 15/01/2014 & BSD License \\
+	aoisrc & 281 & 302 & 12/01/2015 &  GNU General Public License v.2.0 \\
+	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & Apache License, v.2.0 \\
+	aspectj & 1.6.9 & 1.8.9 & 14/03/2015 & Eclipse Public License 1.0 \\
+	axion & 1.0-M2 & -- & 08/03/2013 & Proprietary (BSD/Apache-style) \\
+	batik & 1.7 & 1.8 & 16/03/2015 & Apache License, v.2.0 \\
+	c-jdbc & 2.0.2 & -- & 16/09/2005 & GNU Lesser General Public License, v.2.1 \\
+	castor & 1.3.1 & 1.4.2 & 20/06/2016 & Apache License, v.2.0 \\
+	cayenne & 3.0.1 & 4.0.M4 &  27/07/2016 & Apache License, v.2.0 \\
+	checkstyle & 5.1 & 7.2  & 04/08/2016 & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
+	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2015 & GNU General Public License v.2.0  \\
+	colt & 1.2.0 & -- & 09/09/2014 &  Proprietary (CERN) \\
+	columba & 1.4 & -- & 20/04/2007 & Mozilla Public License 1.1  \\
+	commons-collections & 3.2.1 & 4.1 & 25/11/2015 & Apache License, v.2.0 \\
+	db-derby & 10.6.1.0 & 10.12.1.1 & 13/09/2015 & Apache License, v.2.0 \\
+	displaytag & 1.2 & 2.0 & 17/08/2014 & MIT License \\
+	drawswf & 1.2.9 & -- & 02/04/2013 & GNU General Public License v.2.0 \\
+	drjava & 20100913-r5387 & 20140826-r5761 & 26/08/2014 & BSD License \\
+	eXoPortal & ??? & 4.4 & 24/06/2016 & GNU Lesser General Public License v.3.0 \& proprietary \\
+	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & Common Public License 1.0 \\
+	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & GNU Lesser General Public License, v.2.0 \\
+	fit-java & 1.1 & -- & 04/06/2013 & GNU General Public License v.2.0 \\
+	freecol & 0.10.7 & 0.11.6 & 04/08/2016 & GNU General Public License v.2.0 &  \\
+	freecs & 1.3.20100406 & -- & 22/04/2013 & GNU General Public License v.3.0 &   \\
+	freemind & 0.9.0 & 1.0.0 & 26/06/2016 & GNU General Public License v.2.0+ &  \\
+	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & GNU General Public License v.2.0 \\
+	ganttproject & 2.0.9 & 2.8.1 & 05/08/2016 & GNU General Public License v.3.0 &  \\
+	geotools & 2.7-M3 & 16 & 02/08/2016 & GNU Lesser General Public License, v.2.0 \\
+	hadoop & 1.0.0 & 2.6.4 & 11/02/2016 & Apache License, v.2.0 \\
+	heritrix & 1.14.4 & -- & 05/06/2013 & GNU Lesser General Public License, v.2.1 \\
+	hibernate & 4.2.2 & 5.2.2 & 04/08/2016 & GNU Lesser General Public License, v.2.1+ \\
+	hsqldb & 2.0.0 & 2.3.4 & 16/05/2016 & BSD License \\
+	htmlunit & 2.8 & 2.24 & 27/07/2016 & Apache License, v.2.0 \\
+	iReport & 3.7.5 & -- & 28/05/2014 & Affero GNU Public License, v.3.0 \\
+	iText & 5.0.3 & 7.0.0 & 02/05/2016 & Affero GNU Public License, v.3.0 \\
+	informa & 0.7.0-alpha2 & -- & 07/11/2008 & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
+	ivatagroupware & 0.11.3 & -- & 27/02/2013  & GNU General Public License v.2.0 \\
+	jFin DateMath & R1\_0\_1 & -- & 25/04/2013  & GNU General Public License v.2.0 \\
+	jOggPlayer & 114s & -- &  15/04/2013   & GNU General Public License v.2.0 \\
+	jag & 6.1 & 6.2 & 08/04/2013   & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries they use. \\
+	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & Apache License, v.2.0 \\
+	jasml & 0.10 & -- & 08/03/2013 & Apache Software License \\
+	jasperreports & 3.7.4 & 6.3.1 & 20/06/2016 & GNU Lesser General Public License, v.3.0 &  \\
+	javacc & 5.0.0 & 7.0.0 & 07/07/2016 & Proprietary (Sun) \\
+	jboss (Wildfly) & 5.1.0.GA & 10.0.0 & 29/01/2016 & GNU Lesser General Public License, v.2.1 & It is renamed to Wildfly. \\
+	jchempaint & 3.0.1 & 3.1.3 & 18/04/2016 & GNU Lesser General Public License, v.2.1+ &  \\
+	jedit & 4.3.2 & 5.3.0 & 20/10/2015  & GNU General Public License v.2.0 &  \\
+	jena & 2.6.3 & 3.1.0 & 10/05/2016 & Apache License, v.2.0 \\
+	jext & 5.0 & -- & 18/08/2004   & GNU General Public License v.2.0 &  \\
+	jfreechart & 1.0.13 & 1.2.0-ea1 & 08/05/2016  & GNU Lesser General Public License, v.2.0 &   \\
+	jgraph & 5.13.0.0 & 3.5.1.5 & 20/07/2016 & Proprietary (mxGraph License) \\
+	jgraphpad & 5.10.0.2 & -- & 10/11/2006 & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
+	jgrapht & 0.8.1 & 0.9.2 & 03/04/2016 & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
+	jmoney & 0.4.4 & -- & 17/04/2016 & GNU General Public License v.2.0 &  \\
+	jparse & 0.96 & -- & 29/07/2004 & GNU Lesser General Public License, v.2.1 \\
+	jpf & 1.5.1 & ??? & 13/01/2012 & Apache License, v.2.0 \\
+	junit & 4.11 & 4.12 & 04/12/2014 & Eclipse Public License, v.1.0 \\
+	shiftone-jrat & 0.6 & 1-beta-1 & 25/04/2013 & GNU Lesser General Public License, v.2.0 &  \\
 	\hline 
@@
 
+However, for the 2 NiCad settings, we found some renaming and clustering errors which resulted in fewer projects having clone reports.
+For NiCad default settings, 6 projects had clustering failed errors: \textit{cayenne,checkstyle, db-derby, geotools, hibernate, iReport}.
+For NiCad FSE13 settings, 4 projects had renaming failed errors: \textit{Vuze, aspectj, eXoPortal, hibernate} and 13 projects had clustering failed errors: \textit{ArgoUML, castor, cayenne, checkstyle, db-derby, drjava, ganttproject, geotools, iReport, ivatagroupware, jasperreports, jboss, jchempaint} as depicted in Table \ref{tab:projects_missing}.
+So these projects are also missing from agreed clone pairs.
+
 \begin{table}[h]
 	\centering
-	\caption{18 agreed good-match(0.7) cloned pairs between Simian and Nicad (14 are unique)}
+	\caption{Qualitas projects successfully analysed by Simian and NiCad}
+	\label{tab:projects_missing}
+	\begin{tabular}{r|r|r|r}
+		\hline
+		Simian$_{df}$ & NiCad$_{df}$ & Simian$_{fse13}$ & NiCad$_{fse13}$ \\ \hline
+		63	& 57 & 63 & 46 \\
+		\hline
+		& \textit{6 clustering failed} &  & \textit{13 clustering failed} \\
+		\hline
+		& cayenne   &	& cayenne \\
+		& checkstyle &  & checkstyle \\
+		& db-derby 	& & db-derby \\
+		& geotools 	& & geotools \\
+		& iReport 	& & iReport \\
+		& hibernate & & ArgoUML \\
+		&			& & castor \\
+		&			& & drjava \\
+		&			& & ganttproject \\
+		&			& & ivatagroupware \\
+		&			& & jasperreports \\
+		&			& & jboss \\
+		&			& & jchempaint \\
+		\hline
+		& \textit{renaming failed} & &  \textit{4 renaming failed} \\
+		\hline
+		&			& & Vuze \\
+		&			& & aspectj \\
+		&			& & eXoPortal \\
+		&			& &  hibernate \\
+		\hline
+	\end{tabular}
+\end{table}
+
+\begin{table}[h]
+	\centering
+	\caption{1,415 agreed good-match(0.7) cloned pairs between Simian and Nicad (1,406 are unique)}
 	\label{t_agreed_good_clone_pairs}
@@
 		\hline
-		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 1 \\ %      & 709             \\
-		NiCad$_{\mathrm{\textit{fse13}}}$   & 3 & 5 \\ % & 4680            \\
+		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 6 \\ %      & 709             \\
+		NiCad$_{\mathrm{\textit{fse13}}}$   & 12 & 1388 \\ % & 4680            \\
 		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
@@
 
-\begin{table}[H]
-	\centering
-	\caption{Duplicated agreed \textit{good}-pairs between pairs of Simian and NiCad settings}
-	\label{t_dup_agreed_good_clone_pairs}
-	\begin{tabular}{l|r|r|r|r}
-		\hline
-		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-		\hline
-		$S_dN_d$ & 9 & 3 & 0 & 0 \\%      & 709             \\
-		$S_dN_f$ & 3 & 3 & 0 & 0 \\ % & 4680            \\
-		$S_fN_d$ & 0 & 0 & 1 & 1 \\
-		$S_fN_f$ & 0 & 0 & 1 & 5 \\	
-		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
-		\hline
-	\end{tabular}
-\end{table}
+%\begin{table}[H]
+%	\centering
+%	\caption{Duplicated agreed \textit{good}-pairs between pairs of Simian and NiCad settings}
+%	\label{t_dup_agreed_good_clone_pairs}
+%	\begin{tabular}{l|r|r|r|r}
+%		\hline
+%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+%		\hline
+%		$S_dN_d$ & 9 &    &   &      \\%      & 709             \\
+%		$S_dN_f$ & 9 & 12 &   &      \\ % & 4680            \\
+%		$S_fN_d$ & 0 & 0  & 6 &      \\
+%		$S_fN_f$ & 0 & 0  & 0 & 1388 \\	
+%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
+%		\hline
+%	\end{tabular}
+%\end{table}
 
@@
 	\centering
-	\caption{528 agreed ok-match(0.7) cloned pairs between Simian and Nicad (510 are unique)}
+	\caption{11,165 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
 	\label{t_agreed_ok_clone_pairs}
@@
 		\hline
-		NiCad$_{\mathrm{\textit{default}}}$ & 373 & 1 \\%      & 709             \\
-		NiCad$_{\mathrm{\textit{fse13}}}$   & 118 & 36 \\ % & 4680            \\
+		NiCad$_{\mathrm{\textit{default}}}$ & 481 & 60 \\%      & 709             \\
+		NiCad$_{\mathrm{\textit{fse13}}}$   & 418 & 10,206 \\ % & 4680            \\
 		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
@@
 	\centering
-	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings  (510 are unique)}
+	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (10,879 are different, 286 are duplicates)}
 	\label{t_dup_agreed_ok_clone_pairs}
-	\begin{tabular}{l|r|r|r|r}
+	\begin{tabular}{l|r|r|r|r|r}
 		\hline
-		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
 		\hline
-		$S_dN_d$ & 373 & 17 & 0 & 0 \\%      & 709             \\
-		$S_dN_f$ & 17 & 118 & 0 & 0 \\ % & 4680            \\
-		$S_fN_d$ & 0 & 0 & 1 & 1 \\
-		$S_fN_f$ & 0 & 0 & 1 & 36 \\	
+		$S_dN_d$ & 214 	& 267 	& 0		& 0 		& 481 \\
+		$S_dN_f$ & 267 	& 150 	& 0 	& 1 		& 418 \\ 
+		$S_fN_d$ & 0 	& 0 	& 42 	& 18  		& 60 \\
+		$S_fN_f$ & 0 	& 1 	& 18 	& 10,187 	& 10,206 \\	
+		\hline
+		Total 	 & 481  & 418	& 60	& 10,206	& \\
 		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
@@
 		\hline 
-		NiCad$_{df}$  & 9 & 32 \\ 
+		NiCad$_{df}$  & 17 & 24 \\ 
 		\hline 
-		NiCad$_{fse13}$ &  9 & 32 \\ 
+		NiCad$_{fse13}$ &  24 & 17 \\ 
 		\hline 

### 2016-08-14 find_missing_pair.sh

@@ -1,0 +1,5 @@
+#!/bin/bash
+while IFS='' read -r line || [[ -n "$line" ]]; do
+    #echo "Text read from file: $line"
+    cat fragments_nicad_fse13_160813.xml | grep $line	
+done < "$1"

### 2016-08-14 open_vim.sh

@@ -1,0 +1,5 @@
+echo "Hi"
+for i in 1 2 3; do
+	vim a.txt
+done
+echo "yes"

### 2016-08-14 src/eu/giuswhite/utils/CsvFileWriter.java

@@ -63,7 +63,7 @@ public class CsvFileWriter {
         return result;
     }
 
-    public static void writeSimianLogsStatsOnCsv(List<SimianStackoverflowFragment> list, String filename) {
+    public static void writeSimianLogsStatsOnCsv(List<SimianStackoverflowFragment> list, String filename, String tool, String setting) {
         System.out.println("\nStart writing to csv ...");
         StringWriter output = new StringWriter();
         try (ICsvListWriter listWriter = new CsvListWriter(output,
@@ -81,7 +81,7 @@ public class CsvFileWriter {
             e.printStackTrace();
         }
         String result = "fragment, used, inprojects, sloc, usedsloc, percent\n" + output.toString();
-        FileManager.getInstance().createAndWriteFile(CommonUtils.PROJECT_FOLDER_PATH + "/stats", filename + ".csv", result, false);
+        FileManager.getInstance().createAndWriteFile(CommonUtils.PROJECT_FOLDER_PATH + "/stats_" + tool + "_" + setting, filename + ".csv", result, false);
         System.out.println("done");
     }
 }

### 2016-08-15 latex/stackoverflow.tex
Added changes from iMac

--- 2016-08-11 latex/stackoverflow.tex
@@
 		& \multicolumn{4}{c|}{Simian FSE'13 settings}
-		& \multicolumn{4}{c|}{Simian Default settings} 
-		& \multicolumn{4}{c}{Simian FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
+		& \multicolumn{4}{c|}{NiCad Default settings} 
+		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} 
 		& \multicolumn{4}{c|}{threshold=6} 
@@
 		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
-		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
+		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\ 
 		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
@@
 		& \multicolumn{4}{c|}{rename=none,abstract=none} 
-		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
-		% \hline
+		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  
 		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
@@
 		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
 		\hline
-		%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-		Total & 647 & 24,802 & -- & -- &  152 & 7,289,272 & -- & -- & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
-		Mean & -- & 38 & 7.53 & 0.27 & -- & 47,956 & 4.76 & 0.27 & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\ % & -- & 9,356 & 4.74 & 0.26 \\
-		Std Dev. & -- & 87 & 3.87 & 0.22 & -- & 433,467 & 0.93 & 0.18 & 	& 200 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\ % & -- & 96,038	& 0.99 & 0.18 \\
-		Max & -- & 551 & 63 & 0.94 & -- & 5,278,408 & 8 & 0.83 & -- & 1,816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88\\ % & -- & 7,837,204 & 28 & 0.94 \\
-		Min & -- & 1 & 5 & 0.01 & -- & 1 & 4 & 0.01 & -- & 1 & 7 & 0.02 & -- & 1 & 3 & 0.01 \\ % & -- & 1 & 4 & 0.002 \\
-		Median & -- & 3 & 7 & 0.22 & -- & 22.5 & 4 & 0.23 & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\ % & -- & 27 & 4 & 0.22 \\
-		Mode & -- & 1 & 7 & 0.25 & -- & 1 & 4 & 0.50 & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\ % & -- & 1 & 4 & 0.50 \\
+		Total	   & 654 & 24,929 & -- & -- &  1,175 & 16,957,362 & -- & -- & 983 & 106,091 & -- & -- & 8,100 & 31,141,599 & -- & --  \\ 
+		Mean	  & -- & 38 & 7.54 & 0.27 & -- & 14,444 & 4.80 & 0.28 & -- & 108 & 9.48 & 0.25 & -- & 3,845 & 5.52 & 0.19 \\ 
+		Std Dev. & -- & 87 & 3.21 & 0.22 & -- & 281,747 & 1.22 & 0.18 & 	& 200 & 3.04	& 0.18 & -- & 4,305 & 2.49 & 0.15 \\
+		Max        & -- & 551 & 49 & 0.94 & -- & 9,599,676 & 18 & 0.89 & -- & 1,816 & 39 & 0.80 & -- & 46,469 & 111 & 0.88\\ 
+		Min        & -- & 1 & 5 & 0.01 & -- & 1 & 4 & 0.02 & -- & 1 & 7 & 0.02 & -- & 1 & 3 & 0.01 \\ 
+		Median  & -- & 3 & 7 & 0.23 & -- & 22 & 5 & 0.24 & -- & 14 & 8 & 0.19 & -- & 3,095 & 5 & 0.14 \\ 
+		Mode    & -- & 1 & 7 & 0.25 & -- & 1 & 4 & 0.50 & -- & 1 & 8 & 0.53 & -- & 1 & 4 & 0.33 \\ 
 		\hline
@@
 	\centering
-	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (45 new + 18 old Qualitas projects)}
+	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
 	\label{t_simian_raw_results}
@@
 	\centering
-	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 45 new Qualitas projects)}
+	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
 	\label{t_simian_raw_results}

### 2016-08-15 latex/stackoverflow.tex

--- 2016-08-14 latex/stackoverflow.tex
@@
 		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
 		\hline

### 2016-08-17 latex/stackoverflow.tex

@@
 The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stackoverflow fragments or Qualitas files.
-The classification results are shown in Table \ref{tab:classification} and Table \ref{tab:classification_breakdown}.
+The classification results are shown in Table \ref{tab:classification} and Table \ref{tab:good_classification}.
 
@@
 	\centering
-	\caption{Classification results of 14 \textit{good} and 510 \textit{ok}-matches (including the subsumed \textit{good}-match pairs).}
+	\caption{Classification results of 1,406 \textit{good} and ??? \textit{ok}-matches (including the subsumed \textit{good}-match pairs).}
 	\label{tab:classification}
-	\begin{tabular}{|l|r|r|r|r|r|r|r|}
+	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
 		\hline 
-		Classification & A & B & C & D & E & F & Total \\ 
+		Classification & A & A' & B & C & D & E & F & Total \\ 
 		\hline 
-		\multirow{2}{*}{\textit{good-match(0.7)}} & 1 & 2 & 2 & 2 & 7 & 0 & 14 \\ \cline{2-8}
-		& 7.14\%	& 14.29\%	& 14.29\%	& 14.29\%	& 50.00\%	& 0.00\%	& 100.00\% \\ 
+		\multirow{1}{*}{\textit{good-match(0.7)}} & 1 & 0 & 1 & 3 & 26 & 6 & 1,369 & 1,406 \\ \cline{2-8}
+		%& 7.14\%	& & 14.29\%	& 14.29\%	& 14.29\%	& 50.00\%	& 0.00\%	& 100.00\% \\ 
 		\hline
-		\multirow{2}{*}{\textit{ok-match(0.7)}} & 4 & 42 & 8 & 351 & 28 & 77 & 510 \\ \cline{2-8}
-		& 0.78\%	& 8.24\%	&	1.57\%	&	68.82\%	&	5.49\%	&	15.10\%	&	100.00\%  \\ 
+		\multirow{1}{*}{\textit{ok-match(0.7)}} &  & &  &  &  &  &  &  \\ \cline{2-8}
+		%& 0.78\%	& & 8.24\%	&	1.57\%	&	68.82\%	&	5.49\%	&	15.10\%	&	100.00\%  \\ 
 		\hline
-		\multirow{2}{*}{172 indv. pairs} & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\ \cline{2-8}
-		& 9.88\% & 4.07\% & 1.74\% & 12.21\% & 2.91\% & 69.19\% & 100.00\%  \\ 
+		\multirow{1}{*}{172 indv. pairs} &  & &  &  &  &  &  &  \\ \cline{2-8}
+		%& 9.88\% & & 4.07\% & 1.74\% & 12.21\% & 2.91\% & 69.19\% & 100.00\%  \\ 
 		\hline
@@
 	\centering
-	\caption{Breakdowns of the biggest 172 individual clone pairs}
-	\label{tab:classification_breakdown}
-	\begin{tabular}{|l|r|r|r|r|r|r|r|}
+	\caption{Breakdown of each category A--F according to agreement}
+	\label{tab:good_classification}
+\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
 	\hline 
-		Classification & A & B & C & D & E & F & Total \\ 
+	Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
 	\hline
-		Simian$_{df}$ & 16 & 7 & 3 & 7 & 4 & 3 & 40 \\ 
+	Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
+	Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
+	Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
+	Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,368 & 1,387 \\
 	\hline
-		Simian$_{fse13}$ & 1 & 0 & 0 & 1 & 0 & 53 & 55 \\
-		\hline
-		NiCad$_{df}$ & 0 & 0 & 0 & 13 & 0 & 22 & 35 \\
-		\hline
-		NiCad$_{fse13}$ & 0 & 0 & 0 & 0 & 1 & 41 & 42 \\
-		\hline
-		Total & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\
+	Total   &   1   &   0   &   1   &   3   &   26   &   6   & 1,369  & 1,406 \\
 	\hline
@@
 \end{table}
+
+%\begin{table}[H]
+%	\centering
+%	\caption{Breakdowns of the biggest 172 individual clone pairs}
+%	\label{tab:classification_breakdown}
+%	\begin{tabular}{|l|r|r|r|r|r|r|r|}
+%		\hline 
+%		Classification & A & B & C & D & E & F & Total \\ 
+%		\hline 
+%		Simian$_{df}$ & 16 & 7 & 3 & 7 & 4 & 3 & 40 \\ 
+%		\hline
+%		Simian$_{fse13}$ & 1 & 0 & 0 & 1 & 0 & 53 & 55 \\
+%		\hline
+%		NiCad$_{df}$ & 0 & 0 & 0 & 13 & 0 & 22 & 35 \\
+%		\hline
+%		NiCad$_{fse13}$ & 0 & 0 & 0 & 0 & 1 & 41 & 42 \\
+%		\hline
+%		Total & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\
+%		\hline
+%	\end{tabular} 
+%\end{table}
 

### 2016-08-18 latex/stackoverflow.tex
latest update

@@
 
-\begin{table*}[h]
-	\centering
-	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
-	\label{t_simian_raw_results}
-	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
-		\hline
-		\multirow{4}{*}{Statistics} 
-		& \multicolumn{4}{c|}{Simian Default settings} 
-		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
-		& \multicolumn{4}{c|}{NiCad Default settings} 
-		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
-		& \multicolumn{4}{c|}{threshold=6} 
-		& \multicolumn{4}{c|}{threshold=5} 
-		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
-		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
-		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
-		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
-		& \multicolumn{4}{c|}{rename=none,abstract=none} 
-		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
+%\begin{table*}[h]
+%	\centering
+%	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
+%	\label{t_simian_raw_results}
+%	\resizebox{\columnwidth}{!}{%
+%	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
 %		\hline
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
-		\hline
-		%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-		Total 	& 789 	& 61,164 & -- 	& -- 	&  170 	& 11,915,544 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
-		Mean 	& -- 	& 78 	& 7.32 	& 0.26 	& -- 	& 70,091 	& 4.76 	& 0.29 \\ % & -- & 9,356 & 4.74 & 0.26 \\
-		Std Dev. & -- 	& 208 	& 2.71 	& 0.21 	& -- 	& 703,788 	& 0.89 	& 0.19 \\ % & -- & 96,038	& 0.99 & 0.18 \\
-		Max 	& -- 	& 1,300 & 49 	& 0.94 	& -- 	& 9,065,774 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
-		Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
-		Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 17 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
-		Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
-		\hline
-	\end{tabular} %
-}
-\end{table*}
+%		\multirow{4}{*}{Statistics} 
+%		& \multicolumn{4}{c|}{Simian Default settings} 
+%		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
+%		& \multicolumn{4}{c|}{NiCad Default settings} 
+%		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
+%		& \multicolumn{4}{c|}{threshold=6} 
+%		& \multicolumn{4}{c|}{threshold=5} 
+%		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
+%		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
+%		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
+%		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
+%		& \multicolumn{4}{c|}{rename=none,abstract=none} 
+%		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
+%		% \hline
+%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+%		\hline
+%		%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
+%		Total 	& 789 	& 61,164 & -- 	& -- 	&  170 	& 11,915,544 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
+%		Mean 	& -- 	& 78 	& 7.32 	& 0.26 	& -- 	& 70,091 	& 4.76 	& 0.29 \\ % & -- & 9,356 & 4.74 & 0.26 \\
+%		Std Dev. & -- 	& 208 	& 2.71 	& 0.21 	& -- 	& 703,788 	& 0.89 	& 0.19 \\ % & -- & 96,038	& 0.99 & 0.18 \\
+%		Max 	& -- 	& 1,300 & 49 	& 0.94 	& -- 	& 9,065,774 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
+%		Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
+%		Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 17 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
+%		Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
+%		\hline
+%	\end{tabular} %
+%}
+%\end{table*}
+%
+%\begin{table*}[h]
+%	\centering
+%	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
+%	\label{t_simian_raw_results}
+%	\resizebox{\columnwidth}{!}{%
+%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
+%			\hline
+%			\multirow{4}{*}{Statistics} 
+%			& \multicolumn{4}{c|}{Simian Default settings} 
+%			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
+%			& \multicolumn{4}{c|}{NiCad Default settings} 
+%			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
+%			& \multicolumn{4}{c|}{threshold=6} 
+%			& \multicolumn{4}{c|}{threshold=5} 
+%			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
+%			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
+%			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
+%			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
+%			& \multicolumn{4}{c|}{rename=none,abstract=none} 
+%			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
+%			% \hline
+%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+%			\hline
+%			%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
+%			Total 	& 736 	& 60,678 & -- 	& -- 	&  166 	& 10,273,534 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
+%			Mean 	& -- 	& 82 	& 7.26 	& 0.26 	& -- 	& 61,889 	& 4.77 	& 0.28 \\ % & -- & 9,356 & 4.74 & 0.26 \\
+%			Std Dev. & -- 	& 214 	& 2.24 	& 0.21 	& -- 	& 607,074 	& 0.89 	& 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
+%			Max 	& -- 	& 1,298 & 32 	& 0.94 	& -- 	& 7,720,970 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
+%			Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
+%			Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 16.5 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
+%			Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
+%			\hline
+%		\end{tabular} %
+%	}
+%\end{table*}
 
-\begin{table*}[h]
-	\centering
-	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
-	\label{t_simian_raw_results}
-	\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
-			\hline
-			\multirow{4}{*}{Statistics} 
-			& \multicolumn{4}{c|}{Simian Default settings} 
-			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
-			& \multicolumn{4}{c|}{NiCad Default settings} 
-			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
-			& \multicolumn{4}{c|}{threshold=6} 
-			& \multicolumn{4}{c|}{threshold=5} 
-			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
-			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
-			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
-			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
-			& \multicolumn{4}{c|}{rename=none,abstract=none} 
-			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
-			% \hline
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
-			\hline
-			%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-			Total 	& 736 	& 60,678 & -- 	& -- 	&  166 	& 10,273,534 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
-			Mean 	& -- 	& 82 	& 7.26 	& 0.26 	& -- 	& 61,889 	& 4.77 	& 0.28 \\ % & -- & 9,356 & 4.74 & 0.26 \\
-			Std Dev. & -- 	& 214 	& 2.24 	& 0.21 	& -- 	& 607,074 	& 0.89 	& 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
-			Max 	& -- 	& 1,298 & 32 	& 0.94 	& -- 	& 7,720,970 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
-			Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
-			Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 16.5 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
-			Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
-			\hline
-		\end{tabular} %
-	}
-\end{table*}
-
-\begin{table}[H]
+\begin{table}[h]
 	\centering
@@
 		\hline
-		Total 	 & 481  & 418	& 60	& 10,206	& \\
+		Total 	 & 481  & 418	& 60	& 10,206	& 11,165 \\
 		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
@@
 \subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
-I have manually investigated all of the 14 \textit{good-match} ones and 510 \textit{ok-match} ones.
-The classification schems is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}.
+The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}.
+We have manually investigated all of the 1,406 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.
+However, for the \textit{ok-match}, we could not investigate all of the 10,879 pairs manually.
+According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ produces a large number, 1,387, of false positive results (D, E, and F).
+Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs.
+There are totally 664 \textit{ok-match} pairs that were investigated.
+The 57 true positive pairs found are combinations of 10 unique Stackoverflow fragments, and 13 unique Qualitas Java files.
 
@@
 
-\subsection{Investigation of the largest unique 172 clone pairs}
+\subsection{Investigation of the unique clone pairs}
 In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
@@
 The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stackoverflow fragments or Qualitas files.
-The classification results are shown in Table \ref{tab:classification} and Table \ref{tab:good_classification}.
+The classification results are shown in Table \ref{tab:classification}, \ref{tab:good_classification} and Table \ref{tab:good_classification}.
 
@@
 	\centering
-	\caption{Classification results of 1,406 \textit{good} and ??? \textit{ok}-matches (including the subsumed \textit{good}-match pairs).}
+	\caption{Classification results of 1,406 \textit{good-} and 664 \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
 	\label{tab:classification}
@@
 		\hline
-		\multirow{1}{*}{\textit{ok-match(0.7)}} &  & &  &  &  &  &  &  \\ \cline{2-8}
+		\multirow{1}{*}{\textit{ok-match(0.7)}} & 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 \\ \cline{2-8}
 		%& 0.78\%	& & 8.24\%	&	1.57\%	&	68.82\%	&	5.49\%	&	15.10\%	&	100.00\%  \\ 
 		\hline
-		\multirow{1}{*}{172 indv. pairs} &  & &  &  &  &  &  &  \\ \cline{2-8}
-		%& 9.88\% & & 4.07\% & 1.74\% & 12.21\% & 2.91\% & 69.19\% & 100.00\%  \\ 
+		\multirow{1}{*}{??? indv. pairs} &  & &  &  &  &  &  &  \\
+		\hline
+		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070 \\ 
+	    & \multicolumn{4}{l|}{\textit{10 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
+	    & \multicolumn{4}{l|}{\textit{13 unique Q files}} & \multicolumn{3}{c|}{} & \\
 		\hline
@@
 	\centering
-	\caption{Breakdown of each category A--F according to agreement}
+	\caption{Distribution of classification category A--F according to \textit{good}-match pairs}
 	\label{tab:good_classification}
@@
 	Total   &   1   &   0   &   1   &   3   &   26   &   6   & 1,369  & 1,406 \\
+	\hline
+\end{tabular} 
+\end{table}
+
+\begin{table}[H]
+	\centering
+	\caption{Distribution of classification category A--F  according to the \textit{ok}-match pairs}
+	\label{tab:ok_classification}
+	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+		\hline 
+		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
+		\hline
+		Simian$_{df}$--NiCad$_{df}$   																	& 3 	& 0 	& 17	& 1 	& 428  & 6 		& 7 	&  462 \\
+		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 5 	& 0 	& 18 	& 7 	& 17 	 & 51 	  & 50 		&  148 \\
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
+		%Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 	& 0 	& 3 	& 0 	& 6 	  & 0 		& 0 	& \\
+		\hline
+		Total   &   8  &   0   &  36   &  8   &   474   &   57   & 81  & 664 \\
 		\hline

### 2016-08-23 latex/stackoverflow.tex
Added individual results

--- 2016-08-17 latex/stackoverflow.tex
@@
 	\label{t:new_and_old}
-\begin{tabular}{l|r|r|c|p{5cm}|p{3cm}}
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|c|c|p{5cm}|p{3cm}}
 	\hline 
-	Projects & Old version & New versions & Latest change & License & Notes \\
+	Projects & Old version & New versions & Latest change & Repo. & License & Notes \\
 	\hline
-	ArgoUML & 0.34 & 0.35.1 & 15/01/2014 & Eclipse Public License v.1.0 \\
-	Compiere & 330 & -- & 01/06/2010 &  GNU General Public License v.2.0 & No longer OSS \\
-	FitLibrary & 20100806 & 20111026 & 12/07/2014 & GNU General Public License v.2.0 \\
-	JGroups & 2.10.0.GA & 3.6.10 & 27/06/2016  & Apache License, v.2.0 \\
-	Vuze & 4812 & 5721-20 & 12/05/2016 & GNU General Public License v.2.0 &  \\
-	antlr4 & 4.0 & 4.2.1 & 15/01/2014 & BSD License \\
-	aoisrc & 281 & 302 & 12/01/2015 &  GNU General Public License v.2.0 \\
-	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & Apache License, v.2.0 \\
-	aspectj & 1.6.9 & 1.8.9 & 14/03/2015 & Eclipse Public License 1.0 \\
-	axion & 1.0-M2 & -- & 08/03/2013 & Proprietary (BSD/Apache-style) \\
-	batik & 1.7 & 1.8 & 16/03/2015 & Apache License, v.2.0 \\
-	c-jdbc & 2.0.2 & -- & 16/09/2005 & GNU Lesser General Public License, v.2.1 \\
-	castor & 1.3.1 & 1.4.2 & 20/06/2016 & Apache License, v.2.0 \\
-	cayenne & 3.0.1 & 4.0.M4 &  27/07/2016 & Apache License, v.2.0 \\
-	checkstyle & 5.1 & 7.2  & 04/08/2016 & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
-	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2015 & GNU General Public License v.2.0  \\
-	colt & 1.2.0 & -- & 09/09/2014 &  Proprietary (CERN) \\
-	columba & 1.4 & -- & 20/04/2007 & Mozilla Public License 1.1  \\
-	commons-collections & 3.2.1 & 4.1 & 25/11/2015 & Apache License, v.2.0 \\
-	db-derby & 10.6.1.0 & 10.12.1.1 & 13/09/2015 & Apache License, v.2.0 \\
-	displaytag & 1.2 & 2.0 & 17/08/2014 & MIT License \\
-	drawswf & 1.2.9 & -- & 02/04/2013 & GNU General Public License v.2.0 \\
-	drjava & 20100913-r5387 & 20140826-r5761 & 26/08/2014 & BSD License \\
-	eXoPortal & ??? & 4.4 & 24/06/2016 & GNU Lesser General Public License v.3.0 \& proprietary \\
-	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & Common Public License 1.0 \\
-	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & GNU Lesser General Public License, v.2.0 \\
-	fit-java & 1.1 & -- & 04/06/2013 & GNU General Public License v.2.0 \\
-	freecol & 0.10.7 & 0.11.6 & 04/08/2016 & GNU General Public License v.2.0 &  \\
-	freecs & 1.3.20100406 & -- & 22/04/2013 & GNU General Public License v.3.0 &   \\
-	freemind & 0.9.0 & 1.0.0 & 26/06/2016 & GNU General Public License v.2.0+ &  \\
-	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & GNU General Public License v.2.0 \\
-	ganttproject & 2.0.9 & 2.8.1 & 05/08/2016 & GNU General Public License v.3.0 &  \\
-	geotools & 2.7-M3 & 16 & 02/08/2016 & GNU Lesser General Public License, v.2.0 \\
-	hadoop & 1.0.0 & 2.6.4 & 11/02/2016 & Apache License, v.2.0 \\
-	heritrix & 1.14.4 & -- & 05/06/2013 & GNU Lesser General Public License, v.2.1 \\
-	hibernate & 4.2.2 & 5.2.2 & 04/08/2016 & GNU Lesser General Public License, v.2.1+ \\
-	hsqldb & 2.0.0 & 2.3.4 & 16/05/2016 & BSD License \\
-	htmlunit & 2.8 & 2.24 & 27/07/2016 & Apache License, v.2.0 \\
-	iReport & 3.7.5 & -- & 28/05/2014 & Affero GNU Public License, v.3.0 \\
-	iText & 5.0.3 & 7.0.0 & 02/05/2016 & Affero GNU Public License, v.3.0 \\
-	informa & 0.7.0-alpha2 & -- & 07/11/2008 & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
-	ivatagroupware & 0.11.3 & -- & 27/02/2013  & GNU General Public License v.2.0 \\
-	jFin DateMath & R1\_0\_1 & -- & 25/04/2013  & GNU General Public License v.2.0 \\
-	jOggPlayer & 114s & -- &  15/04/2013   & GNU General Public License v.2.0 \\
-	jag & 6.1 & 6.2 & 08/04/2013   & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries they use. \\
-	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & Apache License, v.2.0 \\
-	jasml & 0.10 & -- & 08/03/2013 & Apache Software License \\
-	jasperreports & 3.7.4 & 6.3.1 & 20/06/2016 & GNU Lesser General Public License, v.3.0 &  \\
-	javacc & 5.0.0 & 7.0.0 & 07/07/2016 & Proprietary (Sun) \\
-	jboss (Wildfly) & 5.1.0.GA & 10.0.0 & 29/01/2016 & GNU Lesser General Public License, v.2.1 & It is renamed to Wildfly. \\
-	jchempaint & 3.0.1 & 3.1.3 & 18/04/2016 & GNU Lesser General Public License, v.2.1+ &  \\
-	jedit & 4.3.2 & 5.3.0 & 20/10/2015  & GNU General Public License v.2.0 &  \\
-	jena & 2.6.3 & 3.1.0 & 10/05/2016 & Apache License, v.2.0 \\
-	jext & 5.0 & -- & 18/08/2004   & GNU General Public License v.2.0 &  \\
-	jfreechart & 1.0.13 & 1.2.0-ea1 & 08/05/2016  & GNU Lesser General Public License, v.2.0 &   \\
-	jgraph & 5.13.0.0 & 3.5.1.5 & 20/07/2016 & Proprietary (mxGraph License) \\
-	jgraphpad & 5.10.0.2 & -- & 10/11/2006 & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
-	jgrapht & 0.8.1 & 0.9.2 & 03/04/2016 & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
-	jmoney & 0.4.4 & -- & 17/04/2016 & GNU General Public License v.2.0 &  \\
-	jparse & 0.96 & -- & 29/07/2004 & GNU Lesser General Public License, v.2.1 \\
-	jpf & 1.5.1 & ??? & 13/01/2012 & Apache License, v.2.0 \\
-	junit & 4.11 & 4.12 & 04/12/2014 & Eclipse Public License, v.1.0 \\
-	shiftone-jrat & 0.6 & 1-beta-1 & 25/04/2013 & GNU Lesser General Public License, v.2.0 &  \\
+	ArgoUML & 0.34 & 0.35.1 & 15/01/2014 	& & Eclipse Public License v.1.0 \\
+	Compiere & 330 & -- & 01/06/2010 		& git & GNU General Public License v.2.0 & No longer OSS \\
+	FitLibrary & 20100806 & 20111026 & 12/07/2014 & & GNU General Public License v.2.0 \\
+	JGroups & 2.10.0.GA & 3.6.10 & 27/06/2016 & & Apache License, v.2.0 \\
+	Vuze & 4812 & 5721-20 & 12/05/2016 & & GNU General Public License v.2.0 &  \\
+	antlr4 & 4.0 & 4.2.1 & 15/01/2014 & & BSD License \\
+	aoisrc & 281 & 302 & 12/01/2015 & & GNU General Public License v.2.0 \\
+	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache License, v.2.0 \\
+	aspectj & 1.6.9 & 1.8.9 & 14/03/2015 & & Eclipse Public License 1.0 \\
+	axion & 1.0-M2 & -- & 08/03/2013 & & Proprietary (BSD/Apache-style) \\
+	batik & 1.7 & 1.8 & 16/03/2015 & & Apache License, v.2.0 \\
+	c-jdbc & 2.0.2 & -- & 16/09/2005 & & GNU Lesser General Public License, v.2.1 \\
+	castor & 1.3.1 & 1.4.2 & 20/06/2016 & git & Apache License, v.2.0 \\
+	cayenne & 3.0.1 & 4.0.M4 &  27/07/2016 & git & Apache License, v.2.0 \\
+	checkstyle & 5.1 & 7.2  & 04/08/2016 & git & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
+	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2015 & git & GNU General Public License v.2.0  \\
+	colt & 1.2.0 & -- & 09/09/2014 & & Proprietary (CERN) \\
+	columba & 1.4 & -- & 20/04/2007 & & Mozilla Public License 1.1  \\
+	commons-collections & 3.2.1 & 4.1 & 25/11/2015 & & Apache License, v.2.0 \\
+	db-derby & 10.6.1.0 & 10.12.1.1 & 13/09/2015 & & Apache License, v.2.0 \\
+	displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT License \\
+	drawswf & 1.2.9 & -- & 02/04/2013 & & GNU General Public License v.2.0 \\
+	drjava & 20100913-r5387 & 20140826-r5761 & 26/08/2014 & & BSD License \\
+	eXoPortal & ??? & 4.4 & 24/06/2016 & git & GNU Lesser General Public License v.3.0 \& proprietary \\
+	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & & Common Public License 1.0 \\
+	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & & GNU Lesser General Public License, v.2.0 \\
+	fit-java & 1.1 & -- & 04/06/2013 & & GNU General Public License v.2.0 \\
+	freecol & 0.10.7 & 0.11.6 & 04/08/2016 & git & GNU General Public License v.2.0 &  \\
+	freecs & 1.3.20100406 & -- & 22/04/2013 & & GNU General Public License v.3.0 &   \\
+	freemind & 0.9.0 & 1.0.0 & 26/06/2016 & & GNU General Public License v.2.0+ &  \\
+	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & & GNU General Public License v.2.0 \\
+	ganttproject & 2.0.9 & 2.8.1 & 05/08/2016 & & GNU General Public License v.3.0 &  \\
+	geotools & 2.7-M3 & 16 & 02/08/2016 & git & GNU Lesser General Public License, v.2.0 \\
+	hadoop & 1.0.0 & 2.6.4 & 11/02/2016 & & Apache License, v.2.0 \\
+	heritrix & 1.14.4 & -- & 05/06/2013 & & GNU Lesser General Public License, v.2.1 \\
+	hibernate & 4.2.2 & 5.2.2 & 04/08/2016 & git & GNU Lesser General Public License, v.2.1+ \\
+	hsqldb & 2.0.0 & 2.3.4 & 16/05/2016 & svn & BSD License \\
+	htmlunit & 2.8 & 2.24 & 27/07/2016 & svn & Apache License, v.2.0 \\
+	iReport & 3.7.5 & -- & 28/05/2014 & & Affero GNU Public License, v.3.0 \\
+	iText & 5.0.3 & 7.0.0 & 02/05/2016 & & Affero GNU Public License, v.3.0 \\
+	informa & 0.7.0-alpha2 & -- & 07/11/2008 & & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
+	ivatagroupware & 0.11.3 & -- & 27/02/2013 & & GNU General Public License v.2.0 \\
+	jFin DateMath & R1\_0\_1 & -- & 25/04/2013 & & GNU General Public License v.2.0 \\
+	jOggPlayer & 114s & -- &  15/04/2013 &  & GNU General Public License v.2.0 \\
+	jag & 6.1 & 6.2 & 08/04/2013  & & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries. \\
+	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & & Apache License, v.2.0 \\
+	jasml & 0.10 & -- & 08/03/2013 & & Apache Software License \\
+	jasperreports & 3.7.4 & 6.3.1 & 20/06/2016 & git & GNU Lesser General Public License, v.3.0 &  \\
+	javacc & 5.0.0 & 7.0.0 & 07/07/2016 & svn & Proprietary (Sun) \\
+	jboss (Wildfly) & 5.1.0.GA & 10.0.0 & 29/01/2016 & & GNU Lesser General Public License, v.2.1 & Renamed to Wildfly. \\
+	jchempaint & 3.0.1 & 3.1.3 & 18/04/2016 & git & GNU Lesser General Public License, v.2.1+ &  \\
+	jedit & 4.3.2 & 5.3.0 & 20/10/2015 & & GNU General Public License v.2.0 &  \\
+	jena & 2.6.3 & 3.1.0 & 10/05/2016 & & Apache License, v.2.0 \\
+	jext & 5.0 & -- & 18/08/2004 &  & GNU General Public License v.2.0 &  \\
+	jfreechart & 1.0.13 & 1.2.0-ea1 & 08/05/2016 & svn & GNU Lesser General Public License, v.2.0 &   \\
+	jgraph & 5.13.0.0 & 3.5.1.5 & 20/07/2016 & git & Proprietary (mxGraph License) \\
+	jgraphpad & 5.10.0.2 & -- & 10/11/2006 & & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
+	jgrapht & 0.8.1 & 0.9.2 & 03/04/2016 & & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
+	jmoney & 0.4.4 & -- & 17/04/2016 & & GNU General Public License v.2.0 &  \\
+	jparse & 0.96 & -- & 29/07/2004 & & GNU Lesser General Public License, v.2.1 \\
+	jpf & 1.5.1 & ??? & 13/01/2012 & & Apache License, v.2.0 \\
+	junit & 4.11 & 4.12 & 04/12/2014 & & Eclipse Public License, v.1.0 \\
+	shiftone-jrat & 0.6 & 1-beta-1 & 25/04/2013 & svn & GNU Lesser General Public License, v.2.0 &  \\
 	\hline 
-\end{tabular} 
+\end{tabular} %
+}
 \end{table}
+
+\newpage
 

### 2016-09-01 latex/stackoverflow.tex
Latest update

@@
 \usepackage{array}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 \usepackage{multirow}
@@
 There are 2 tools selected: Simian and NiCad.
-They are configured using three different settings: default settings, settings from FSE'13 paper, and settings from CloPlag experiment.
+They are configured using two different settings: default settings, and settings from another study \cite{Wang2013}.
 Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.
@@
 
-%\begin{table*}[h]
-%	\centering
-%	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
-%	\label{t_simian_raw_results}
-%	\resizebox{\columnwidth}{!}{%
-%	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
+\begin{table*}[h]
+	\centering
+	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
+	\label{t_simian_raw_results}
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
+		\hline
+		\multirow{4}{*}{Statistics} 
+		& \multicolumn{4}{c|}{Simian Default settings} 
+		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
+		& \multicolumn{4}{c|}{NiCad Default settings} 
+		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
+		& \multicolumn{4}{c|}{threshold=6} 
+		& \multicolumn{4}{c|}{threshold=5} 
+		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
+		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
+		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
+		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
+		& \multicolumn{4}{c|}{rename=none,abstract=none} 
+		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
 		% \hline
-%		\multirow{4}{*}{Statistics} 
-%		& \multicolumn{4}{c|}{Simian Default settings} 
-%		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
-%		& \multicolumn{4}{c|}{NiCad Default settings} 
-%		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
-%		& \multicolumn{4}{c|}{threshold=6} 
-%		& \multicolumn{4}{c|}{threshold=5} 
-%		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
-%		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
-%		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
-%		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
-%		& \multicolumn{4}{c|}{rename=none,abstract=none} 
-%		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
-%		% \hline
-%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-%		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
-%		\hline
-%		%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-%		Total 	& 789 	& 61,164 & -- 	& -- 	&  170 	& 11,915,544 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
-%		Mean 	& -- 	& 78 	& 7.32 	& 0.26 	& -- 	& 70,091 	& 4.76 	& 0.29 \\ % & -- & 9,356 & 4.74 & 0.26 \\
-%		Std Dev. & -- 	& 208 	& 2.71 	& 0.21 	& -- 	& 703,788 	& 0.89 	& 0.19 \\ % & -- & 96,038	& 0.99 & 0.18 \\
-%		Max 	& -- 	& 1,300 & 49 	& 0.94 	& -- 	& 9,065,774 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
-%		Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
-%		Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 17 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
-%		Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
-%		\hline
-%	\end{tabular} %
-%}
-%\end{table*}
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+		\hline
+		Total 	& 792 & 61,268 & -- & -- 	& 1,229 & 25,725,857 & -- & -- & 1,141 	& 666,140 & -- 	& -- 	&  12,400 	& 615,263,639 & -- 	& --  \\ 
+		Mean 	& -- & 78 & 7.31 & 0.26 	& -- & 20,932 & 4.86 & 0.28 & -- 	& 584 	& 9.49 	& 0.25 	& -- 	& 49,618 	& 5.25 	& 0.20 \\ 
+		Std Dev. & -- & 208 & 2.70 & 0.21 	& -- & 382,015 & 1.30 & 0.19 & -- 	& 1,488 & 3.11 	& 0.18 	& -- 	& 62,659 	& 2.80 	& 0.16 \\ 
+		Max 	& -- & 1,300 & 49.00 & 0.94 & -- & 13,202,807 & 21.00 & 0.92 & -- 	& 10,980 & 39.00 	& 0.84 	& -- 	& 1,319,242 & 250.00	& 0.96 \\
+		Min 	& -- & 1 & 5.00 & 0.01 		& -- & 1 & 4.00 & 0.12 & -- 	& 1 	& 7.00 	& 0.02 	& -- 	& 1 		& 2.00 	& 0.01 \\ 
+		Median 	& -- & 2 & 7.00 & 0.20 		& -- & 21 & 5.00 & 0.25 & -- 	& 25 	& 8.00 	& 0.19 	& -- 	& 52,329 	& 5.00 	& 0.16 \\ 
+		Mode 	& -- & 1 & 7.00 & 0.33 		& -- & 1 & 4.00 & 0.50 & -- 	& 1 	& 8.00 	& 0.67 	& -- 	& 1 		& 4.00 	& 0.33 \\ 
+		\hline
+	\end{tabular} %
+}
+\end{table*}
 %
-%\begin{table*}[h]
-%	\centering
-%	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
-%	\label{t_simian_raw_results}
-%	\resizebox{\columnwidth}{!}{%
-%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
-%			\hline
-%			\multirow{4}{*}{Statistics} 
-%			& \multicolumn{4}{c|}{Simian Default settings} 
-%			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
-%			& \multicolumn{4}{c|}{NiCad Default settings} 
-%			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
-%			& \multicolumn{4}{c|}{threshold=6} 
-%			& \multicolumn{4}{c|}{threshold=5} 
-%			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
-%			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
-%			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
-%			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
-%			& \multicolumn{4}{c|}{rename=none,abstract=none} 
-%			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
-%			% \hline
-%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-%			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ % & Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
-%			\hline
-%			%Removed & 11 	& -- 	& -- 	& -- 	& 0 & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-%			Total 	& 736 	& 60,678 & -- 	& -- 	&  166 	& 10,273,534 & -- 	& --  \\ % & 26,699 & 24,9702,821 & -- & --  \\
-%			Mean 	& -- 	& 82 	& 7.26 	& 0.26 	& -- 	& 61,889 	& 4.77 	& 0.28 \\ % & -- & 9,356 & 4.74 & 0.26 \\
-%			Std Dev. & -- 	& 214 	& 2.24 	& 0.21 	& -- 	& 607,074 	& 0.89 	& 0.18 \\ % & -- & 96,038	& 0.99 & 0.18 \\
-%			Max 	& -- 	& 1,298 & 32 	& 0.94 	& -- 	& 7,720,970 & 9		& 0.83 \\ % & -- & 7,837,204 & 28 & 0.94 \\
-%			Min 	& -- 	& 1 	& 5 	& 0.01 	& -- 	& 1 		& 4 	& 0.01 \\ % & -- & 1 & 4 & 0.002 \\
-%			Median 	& -- 	& 2 	& 7 	& 0.20 	& -- 	& 16.5 		& 5 	& 0.26 \\ % & -- & 27 & 4 & 0.22 \\
-%			Mode 	& -- 	& 1 	& 7 	& 0.33 	& -- 	& 1 		& 4 	& 0.33 \\ % & -- & 1 & 4 & 0.50 \\
-%			\hline
-%		\end{tabular} %
-%	}
-%\end{table*}
+\begin{table*}[h]
+	\centering
+	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
+	\label{t_simian_raw_results}
+	\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
+			\hline
+			\multirow{4}{*}{Statistics} 
+			& \multicolumn{4}{c|}{Simian Default settings} 
+			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
+			& \multicolumn{4}{c|}{NiCad Default settings} 
+			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
+			& \multicolumn{4}{c|}{threshold=6} 
+			& \multicolumn{4}{c|}{threshold=5} 
+			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
+			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
+			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
+			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
+			& \multicolumn{4}{c|}{rename=none,abstract=none} 
+			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  
+			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+			\hline
+			Total 	& 707 	& 60,536 & -- 	& -- 	&  1,205 & 22,797,190 & -- 	& --  & 1,068 & 648,165 & -- & -- & 10,231 & 573,438,528 & -- & -- \\ 
+			Mean 	& -- 	& 86 	& 7.37 	& 0.26 	& -- 	& 18,919 	& 4.85 	& 0.28 & -- & 607 & 9.39 & 0.25 & -- & 47663 & 5.22 & 0.20 \\
+			Std Dev. & -- 	& 217 	& 2.22 	& 0.21 	& -- 	& 326,588 	& 1.31 	& 0.19 & -- & 1,499 & 2.98 & 1.81 & -- & 58,833 & 2.77 & 0.15 \\
+			Max 	& -- 	& 1,298 & 32.00 & 0.94 	& -- 	& 11,127,286 & 21.00 & 0.92 & -- & 10,550 & 36.00 & 0.84 & -- & 1,246,598 & 250 & 0.96 \\
+			Min 	& -- 	& 1 	& 5.00 	& 0.01 	& -- 	& 1 		& 4.00 	& 0.02 & -- & 1 & 7 & 0.02 & -- & 1 & 2.00 & 0.01\\
+			Median 	& -- 	& 2 	& 7.00 	& 0.21 	& -- 	& 20		& 5.00 	& 0.25 & -- & 33 & 8 & 0.19 & -- & 52,077 & 5.00 & 0.15 \\
+			Mode 	& -- 	& 1 	& 7.00 	& 0.25 	& -- 	& 1 		& 4.00 	& 0.50 & -- & 1 & 8 & 0.67 & -- & 1 & 4.00 & 0.33 \\
+			\hline
+		\end{tabular} %
+	}
+\end{table*}
 
@@
 \section*{Agreed Clone Pairs}
-The investigation of the clone pairs using Bellon's \textit{good-match(p)} and \textit{ok-match(p)} criteria are listed in  Table \ref{t_agreed_good_clone_pairs} and Table \ref{t_agreed_ok_clone_pairs}.
-We use the threshold \textit{p} of 0.7 for both \textit{good-match} and \textit{ok-match}.
-Visualisation of \textit{good-match} common clone pairs between sets of parameter settings can be seen from Figure \ref{fig:venn4_pairs}.
-There are 14 \textit{good-match} pairs.
-The \textit{ok-match} subsumes the \textit{good-match} resulting in totally 528 common clone pairs.
 
-However, for the 2 NiCad settings, we found some renaming and clustering errors which resulted in fewer projects having clone reports.
-For NiCad default settings, 6 projects had clustering failed errors: \textit{cayenne,checkstyle, db-derby, geotools, hibernate, iReport}.
-For NiCad FSE13 settings, 4 projects had renaming failed errors: \textit{Vuze, aspectj, eXoPortal, hibernate} and 13 projects had clustering failed errors: \textit{ArgoUML, castor, cayenne, checkstyle, db-derby, drjava, ganttproject, geotools, iReport, ivatagroupware, jasperreports, jboss, jchempaint} as depicted in Table \ref{tab:projects_missing}.
+The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria are listed in  Table \ref{t_agreed_good_clone_pairs}.
+We use the threshold of 0.7 for both \textit{good}-match and \textit{ok}-match.
+Visualisation of \textit{good}-match common clone pairs between sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}.
+There are 1,406 unique \textit{good}-match pairs.
+The \textit{ok}-match subsumes the \textit{good}-match resulting in totally 10,879 common clone pairs (Figure \ref{fig:venn4_orig_ok}).
+
+However, for NiCad's settings, we found a few renaming and clustering errors which resulted in fewer projects with clone reports.
+For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors.
+For NiCad FSE13 settings (NiCad$_{\textrm{\textit{fse13}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}.
 So these projects are also missing from agreed clone pairs.
+\FIXME{Report the errors.}
+
+We are interested in discovering reused code in the latest versions of Qualitas projects.
+So, we downloaded the newest release of each project and found 44 of them having newer updates.
+Then, we reran the experiment again on these 44 projects.
+Several projects triggered NiCad problem of clustering and renaming again as listed in Table \ref{tab:projects_missing}.
+The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria of this new dataset are also listed in Table \ref{t_agreed_good_clone_pairs}.
 
@@
 	\centering
-	\caption{Qualitas projects successfully analysed by Simian and NiCad}
+	\caption{No.~of projects in Qualitas Original~(Qualitas-\textit{O}) and New (Qualitas-\textit{N}) successfully analysed by Simian and NiCad}
 	\label{tab:projects_missing}
-	\begin{tabular}{r|r|r|r}
+	\begin{tabular}{r|r|r|r|r|r|r|r}
 		\hline
-		Simian$_{df}$ & NiCad$_{df}$ & Simian$_{fse13}$ & NiCad$_{fse13}$ \\ \hline
-		63	& 57 & 63 & 46 \\
+		\multicolumn{4}{c|}{Qualitas-\textit{O}} & \multicolumn{4}{c}{Qualitas-\textit{N}} \\
 		\hline
-		& \textit{6 clustering failed} &  & \textit{13 clustering failed} \\
+		Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ \\ \hline
+		63	& 63 & 57 & 46 & 44 & 44 & 40 & 34 \\
 		\hline
-		& cayenne   &	& cayenne \\
-		& checkstyle &  & checkstyle \\
-		& db-derby 	& & db-derby \\
-		& geotools 	& & geotools \\
-		& iReport 	& & iReport \\
-		& hibernate & & ArgoUML \\
-		&			& & castor \\
-		&			& & drjava \\
-		&			& & ganttproject \\
-		&			& & ivatagroupware \\
-		&			& & jasperreports \\
-		&			& & jboss \\
-		&			& & jchempaint \\
+		& & \textit{6 clustering failed} & \textit{13 clustering failed} & & & \textit{4 clustering failed} & \textit{6 clustering failed} \\
+		& & cayenne   & cayenne 	& & & jboss (wildfly) & ArgoUML \\
+		& & checkstyle & checkstyle & & & hadoop & checkstyle \\
+		& & db-derby 	& db-derby 	& & & db-derby & db-derby \\
+		& & geotools 	& geotools  & & & hibernate & cayenne \\
+		& & iReport 	& iReport   & & & & jena \\
+		& & hibernate & ArgoUML 	& & & & geotools \\
+		& &			& castor 		& & & & \\
+		& &			& drjava 		& & & & \\
+		& &			& ganttproject 	& & & & \\
+		& &			& ivatagroupware & & & &  \\
+		& &			& jasperreports & & & & \\
+		& &			& jboss 		& & & & \\
+		& &			& jchempaint 	& & & & \\
 		\hline
-		& \textit{renaming failed} & &  \textit{4 renaming failed} \\
-		\hline
-		&			& & Vuze \\
-		&			& & aspectj \\
-		&			& & eXoPortal \\
-		&			& &  hibernate \\
-		\hline
-	\end{tabular}
-\end{table}
-
-\begin{table}[H]
-	\centering
-	\caption{1,415 agreed good-match(0.7) cloned pairs between Simian and Nicad (1,406 are unique)}
-	\label{t_agreed_good_clone_pairs}
-	\begin{tabular}{l|r|r}
-		\hline
-		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-		\hline
-		NiCad$_{\mathrm{\textit{default}}}$ & 9 & 6 \\ %      & 709             \\
-		NiCad$_{\mathrm{\textit{fse13}}}$   & 12 & 1388 \\ % & 4680            \\
-		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
+		& 			& &  \textit{4 renaming failed} & & & & \\
+		&			& & Vuze 		& & & & Vuze \\
+		&			& & aspectj 	& & & & hadoop \\
+		&			& & eXoPortal 	& & & & jboss (wildfly) \\
+		&			& &  hibernate 	& & & & hibernate \\
 		\hline
@@
 %	\centering
-%	\caption{Duplicated agreed \textit{good}-pairs between pairs of Simian and NiCad settings}
-%	\label{t_dup_agreed_good_clone_pairs}
-%	\begin{tabular}{l|r|r|r|r}
+%	\caption{Qualitas projects (2016-08-16) successfully analysed by Simian and NiCad}
+%	\label{tab:projects_missing_new}
+%	\begin{tabular}{r|r|r|r}
 %		\hline
-%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+%		Simian$_{df}$ & NiCad$_{df}$ & Simian$_{fse13}$ & NiCad$_{fse13}$ \\ \hline
+%		44	& 40 & 44 & 34 \\
 %		\hline
-%		$S_dN_d$ & 9 &    &   &      \\%      & 709             \\
-%		$S_dN_f$ & 9 & 12 &   &      \\ % & 4680            \\
-%		$S_fN_d$ & 0 & 0  & 6 &      \\
-%		$S_fN_f$ & 0 & 0  & 0 & 1388 \\	
+%		& \textit{4 clustering failed} &  & \textit{6 clustering failed} \\
+%		\hline
+%		& jboss (wildfly) &	& ArgoUML \\
+%		& db-derby 	&  &  db-derby \\
+%		& hadoop 	& &  checkstyle \\
+%		& hibernate & &  cayenne \\
+%		&  			& &  geotools \\
+%		&  			& &  jena \\
+%		\hline
+%		& \textit{no renaming failed} & &  \textit{4 renaming failed} \\
+%		\hline
+%		&			& & Vuze \\
+%		&			& & hadoop \\
+%		&			& & hibernate \\
+%		&			& & jboss (wildfly) \\
+%		\hline
+%	\end{tabular}
+%\end{table}
+
+\begin{table}[H]
+	\centering
+	\caption{Distribution of clone pairs reported based on \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria}
+	\label{t_agreed_good_clone_pairs}
+	\begin{tabular}{l|l|r|r|r|r}
+		\hline
+		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c|}{Qualitas-\textit{O}} & \multicolumn{2}{c}{Qualitas-\textit{N}} \\
+		\hline
+		Simian & NiCad & \textit{good}-match & \textit{ok}-match & \textit{good}-match & \textit{ok}-match \\
+		%\hline
+		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+		\hline
+		\textit{default} & \textit{default} & 9 	& 481 	& 0 & 6,640 \\ 
+		\textit{default} & \textit{fse13} 	& 12 	& 418 	& 0 & 416 \\ 
+		\textit{fse13} 	& \textit{default} 	& 6 	& 60 	& 0 & 23 \\
+		\textit{fse13} 	& \textit{fse13} 	& 1,388 & 10,206 & 1,170 & 6,690 \\ 
+		\hline
+		\multicolumn{2}{l|}{Total} & 1,415 & 11,165 & 1,170 & 13,386 \\
+		\multicolumn{2}{l|}{Total (unique)} & 1,406 & 10,879 & 1,170 & 10,879 \\
+		\hline
+	\end{tabular}
+\end{table}
+
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{venn4_pairs_good}
+%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
+%	\label{fig:venn4_pairs_good}
+%\end{figure}
+
+%\begin{table}[H]
+%	\centering
+%	\caption{11,165 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
+%	\label{t_agreed_ok_clone_pairs}
+%	\begin{tabular}{l|r|r}
+%		\hline
+%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+%		\hline
+%		NiCad$_{\mathrm{\textit{default}}}$ & 481 & 60 \\%      & 709             \\
+%		NiCad$_{\mathrm{\textit{fse13}}}$   & 418 & 10,206 \\ % & 4680            \\
 %		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
@@
 
-\begin{figure}[H]
+\begin{figure}
 	\centering
-	\includegraphics[width=0.5\linewidth]{venn4_pairs_good}
-	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
-	\label{fig:venn4_pairs}
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
+		\captionof{figure}{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
+		\label{fig:venn4_orig_good}
+	\end{minipage}%
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
+		\captionof{figure}{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
+		\label{fig:venn4_orig_ok}
+	\end{minipage}
 \end{figure}
 
+%\begin{table}[H]
+%	\centering
+%	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (10,879 are different, 286 are duplicates)}
+%	\label{t_dup_agreed_ok_clone_pairs}
+%	\begin{tabular}{l|r|r|r|r|r}
+%		\hline
+%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+%		\hline
+%		$S_dN_d$ & 214 	& 267 	& 0		& 0 		& 481 \\
+%		$S_dN_f$ & 267 	& 150 	& 0 	& 1 		& 418 \\ 
+%		$S_fN_d$ & 0 	& 0 	& 42 	& 18  		& 60 \\
+%		$S_fN_f$ & 0 	& 1 	& 18 	& 10,187 	& 10,206 \\	
+%		\hline
+%		Total 	 & 481  & 418	& 60	& 10,206	& 11,165 \\
+%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
+%		\hline
+%	\end{tabular}
+%\end{table}
+
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok}
+%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
+%	\label{fig:venn4_pairs}
+%\end{figure}
+
+%The statistics of the results from Simian and NiCad are shown in Table \ref{t_agreed_good_clone_pairs_new}, \ref{t_agreed_ok_clone_pairs_new}, and Figure \ref{fig:venn4_pairs_good_new}, and \ref{fig:venn4_pairs_ok_new}.
+%
+%\begin{table}[H]
+%	\centering
+%	\caption{1,170 agreed good-match(0.7) cloned pairs between Simian and Nicad (1,170 are unique)}
+%	\label{t_agreed_good_clone_pairs_new}
+%	\begin{tabular}{l|r|r}
+%		\hline
+%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\
+%		\hline
+%		NiCad$_{\mathrm{\textit{default}}}$ & 0 & 0 \\ 
+%		NiCad$_{\mathrm{\textit{fse13}}}$   & 0 & 1,170 \\ 
+%		\hline
+%	\end{tabular}
+%\end{table}
+
+\begin{figure}
+	\centering
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{venn4_pairs_good_new}
+		\captionof{figure}{Qualitas-\textit{N} \textit{good}-match(0.7) pairs}
+		\label{fig:venn4_new_good}
+	\end{minipage}%
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok_new}
+		\captionof{figure}{Qualitas-\textit{N} \textit{ok}-match(0.7) pairs}
+		\label{fig:venn4_new_ok}
+	\end{minipage}
+\end{figure}
+
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{venn4_pairs_good_new}
+%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
+%	\label{fig:venn4_pairs_good_new}
+%\end{figure}
+
+%\begin{table}[H]
+%	\centering
+%	\caption{13,733 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
+%	\label{t_agreed_ok_clone_pairs_new}
+%	\begin{tabular}{l|r|r}
+%		\hline
+%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ 
+%		\hline
+%		NiCad$_{\mathrm{\textit{default}}}$ & 6604 & 23 \\
+%		NiCad$_{\mathrm{\textit{fse13}}}$   & 416 & 6690 \\
+%		\hline
+%	\end{tabular}
+%\end{table}
+
+%\begin{table}[H]
+%	\centering
+%	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (13,386 are different, 347 are duplicates)}
+%	\label{t_dup_agreed_ok_clone_pairs}
+%	\begin{tabular}{l|r|r|r|r|r}
+%		\hline
+%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+%		\hline
+%		$S_dN_d$ & 6267	& 337	& 0		& 	0	&  6604 \\
+%		$S_dN_f$ & 337 	& 79	& 0 	&  	0	&  416 \\ 
+%		$S_fN_d$ & 0 	& 0		& 13 	&   10	&  23 \\
+%		$S_fN_f$ & 0 	& 0 	& 10	&  	6680 &  6690 \\	
+%		\hline
+%		Total 	 & 6604  & 416	& 23	& 6690	& 13733 \\
+%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
+%		\hline
+%	\end{tabular}
+%\end{table}
+
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok_new}
+%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
+%	\label{fig:venn4_pairs_ok_new}
+%\end{figure}
+
+\section*{Manual Investigation}
+
+\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
+\subsubsection{Qualitas Original (v. 2013-09-01r)}
 \begin{table}[H]
 	\centering
-	\caption{11,165 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
-	\label{t_agreed_ok_clone_pairs}
-	\begin{tabular}{l|r|r}
+	\caption{Classifications of clone creation}
+	\label{tab:classification_scheme}
+	\begin{tabular}{|c|p{13cm}|}
 		\hline 
-		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+		Category & Descriptions \\ 
 		\hline 
-		NiCad$_{\mathrm{\textit{default}}}$ & 481 & 60 \\%      & 709             \\
-		NiCad$_{\mathrm{\textit{fse13}}}$   & 418 & 10,206 \\ % & 4680            \\
-		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
+		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
+		\hline 
+		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
+		\hline 
+		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
+		\\ 
+		\hline 
+		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
+		\\ 
+		\hline 
+		D & Code is a boiler-plate or IDE auto-generated.
+		\\ 
+		\hline 
+		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
+		\\ 
+		\hline 
+		F & Accidental similarity, false clone \\ 
 		\hline 
@@
 
-\begin{table}[H]
-	\centering
-	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (10,879 are different, 286 are duplicates)}
-	\label{t_dup_agreed_ok_clone_pairs}
-	\begin{tabular}{l|r|r|r|r|r}
-		\hline
-		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-		\hline
-		$S_dN_d$ & 214 	& 267 	& 0		& 0 		& 481 \\
-		$S_dN_f$ & 267 	& 150 	& 0 	& 1 		& 418 \\ 
-		$S_fN_d$ & 0 	& 0 	& 42 	& 18  		& 60 \\
-		$S_fN_f$ & 0 	& 1 	& 18 	& 10,187 	& 10,206 \\	
-		\hline
-		Total 	 & 481  & 418	& 60	& 10,206	& 11,165 \\
-		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
-		\hline
-	\end{tabular}
-\end{table}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok}
-	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
-	\label{fig:venn4_pairs}
-\end{figure}
-
-\section*{Investigation of Missing A/B Clone Pairs Reported by Simian (df)}
-We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
-The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{fse13}$, NiCad$_{df}$, NiCad$_{fse13}$.
-The investigation results are shown in Table \ref{tab:search}.
-
-\begin{table}[H]
-	\centering
-	\caption{Results of matching the original 41 Simian(default) pairs in the pretty-printed result sets}
-	\label{tab:search}
-	\begin{tabular}{l|r|r}
-		\hline 
-		Settings & Found & Not found \\ 
-		\hline 
-		Simian$_{df}$  &  40 & 1* \\ 
-		\hline 
-		Simian$_{fse13}$ & 0 & 41  \\ 
-		\hline 
-		NiCad$_{df}$  & 17 & 24 \\ 
-		\hline 
-		NiCad$_{fse13}$ &  24 & 17 \\ 
-		\hline 
-	\end{tabular} 
-\end{table}
-
-The single missing Stackoverflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian.
-It is removed from the results of the pretty-printed version because it is an outlier.
-The rest are missing because of different parameter settings.
-
-\section*{Manual Investigation}
-
-\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
 The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}.
@@
 
-\subsection{Investigation of the unique clone pairs}
-In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
-However, only 10 of them appear in the new results using tool's agreement.
-Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.
-With our 4 settings, we investigated the largest 172 clone pairs according to their average SLOC (larger than or equals to 15 SLOC).
-These clone pairs are pairs of Stackoverflow fragments and Java files from Qualitas projects that NEVER been looked at before in the previous investigation.
-The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stackoverflow fragments or Qualitas files.
-The classification results are shown in Table \ref{tab:classification}, \ref{tab:good_classification} and Table \ref{tab:good_classification}.
-
 \begin{table}[H]
 	\centering
-	\caption{Classification results of 1,406 \textit{good-} and 664 \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
+	\caption{Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
 	\label{tab:classification}
-	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{5mm}|R{3mm}|R{7mm}|R{7mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{7mm}|R{3mm}|R{7mm}|R{7mm}|}
 		\hline
-		Classification & A & A' & B & C & D & E & F & Total \\ 
+		\multirow{2}{*}{Classification}	& \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ 	\cline{2-17}
+		 & A & A' & B & C & D & E & F & Total 
+		 & A & A' & B & C & D & E & F & Total \\ 
 		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}} & 1 & 0 & 1 & 3 & 26 & 6 & 1,369 & 1,406 \\ \cline{2-8}
-		%& 7.14\%	& & 14.29\%	& 14.29\%	& 14.29\%	& 50.00\%	& 0.00\%	& 100.00\% \\ 
+		\multirow{1}{*}{\textit{good-match(0.7)}} 
+		& 1 & 0 & 1  & 3 & 26  & 6 & 1,369 & 1,406 
+		& -- & -- & -- & -- & -- & -- & -- & --  \\ \cline{2-8}
 		\hline
-		\multirow{1}{*}{\textit{ok-match(0.7)}} & 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 \\ \cline{2-8}
-		%& 0.78\%	& & 8.24\%	&	1.57\%	&	68.82\%	&	5.49\%	&	15.10\%	&	100.00\%  \\ 
+		\multirow{1}{*}{\textit{ok-match(0.7)}} 
+		& 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 
+		& 2 & 0 & 0 & 0 & 6,676 & 1 & 27 & 6,706 \\ \cline{2-8}
 		\hline
-		\multirow{1}{*}{??? indv. pairs} &  & &  &  &  &  &  &  \\
+		TP/FP
+		& \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070
+		& \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{6,704} & 6,706 \\ 
 		\hline
-		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070 \\ 
-	    & \multicolumn{4}{l|}{\textit{10 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
-	    & \multicolumn{4}{l|}{\textit{13 unique Q files}} & \multicolumn{3}{c|}{} & \\
+		Unique SO fragments & \multicolumn{4}{c|}{10} & & & & & \multicolumn{4}{c|}{1} & & & & \\
+		\hline
+		Unique Q files & \multicolumn{4}{c|}{13} & & & & & \multicolumn{4}{c|}{1} & & & & \\
+		\hline
+		Unique Q files & \multicolumn{4}{c|}{8} & & & & & \multicolumn{4}{c|}{1} & & & & \\
 		\hline
@@
 		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
-		%Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 	& 0 	& 3 	& 0 	& 6 	  & 0 		& 0 	& \\
 		\hline
@@
 
-%\begin{table}[H]
-%	\centering
-%	\caption{Breakdowns of the biggest 172 individual clone pairs}
-%	\label{tab:classification_breakdown}
-%	\begin{tabular}{|l|r|r|r|r|r|r|r|}
-%		\hline 
-%		Classification & A & B & C & D & E & F & Total \\ 
-%		\hline 
-%		Simian$_{df}$ & 16 & 7 & 3 & 7 & 4 & 3 & 40 \\ 
-%		\hline
-%		Simian$_{fse13}$ & 1 & 0 & 0 & 1 & 0 & 53 & 55 \\
-%		\hline
-%		NiCad$_{df}$ & 0 & 0 & 0 & 13 & 0 & 22 & 35 \\
-%		\hline
-%		NiCad$_{fse13}$ & 0 & 0 & 0 & 0 & 1 & 41 & 42 \\
-%		\hline
-%		Total & 17 & 7 & 3 & 21 & 5 & 119 & 172 \\
-%		\hline
-%	\end{tabular} 
-%\end{table}
+\subsubsection{Qualitas New (v. 2016-08-05)}
+We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$.
+We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
+The number of pairs that have been looked at is 6,706 (excluding duplicates).
+The results are shown in Table.
 
@@
 	\centering
-	\caption{Classifications of clone creation}
-	\label{tab:classification_scheme}
-	\begin{tabular}{|c|p{13cm}|}
+	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$.}
+	\label{tab:classification_new}
+	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
 		\hline 
-		Category & Descriptions \\ 
+		Classification & A & A' & B & C & D & E & F & Total \\ 
 		\hline
-		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
+		\multirow{1}{*}{\textit{good-match(0.7)}} & -- & -- & -- & -- & -- & -- & -- & -- \\ \cline{2-8}
 		\hline
-		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
+		\multirow{1}{*}{\textit{ok-match(0.7)}}  \\ \cline{2-8}
 		\hline
-		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
-		\\ 
-		\hline 
-		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
-		\\ 
-		\hline 
-		D & Code is a boiler-plate or IDE auto-generated.
-		\\ 
-		\hline 
-		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
-		\\ 
-		\hline 
-		F & Accidental similarity, false clone \\ 
+		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{\multirow{3}{*}{6704}} & \multirow{3}{*}{6706} \\ 
+		& \multicolumn{4}{l|}{\textit{1 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
+		& \multicolumn{4}{l|}{\textit{1 unique Q files}} & \multicolumn{3}{c|}{} & \\
 		\hline
@@
 
+\begin{table}[H]
+	\centering
+	\caption{Distribution of classification category A--F  according to the \textit{ok}-match pairs}
+	\label{tab:ok_classification_new}
+	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+		\hline 
+		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
+		\hline
+		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
+		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$ 
+		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									
+		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
+		\hline
+		Total   & 2  	&   0   & 0   	&  0   &   6676   &   1   & 27  & 6706 \\
+		\hline
+	\end{tabular} 
+\end{table}
+
+\subsection{Investigation of the unique clone pairs}
+\subsubsection{Qualitas Original (v. 2013-09-01r)}
+In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
+However, only 10 of them appear in the new results using tool's agreement.
+Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.
+
+With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{fse13}$ and NiCad$_{fse13}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}.
+With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.
+
+We selected only Stackoverflow fragment and Qualitas files that have never been looked at before in the previous investigation.
+If many clone pairs having the same Stackoverflow fragment and Qualitas file, we keep only the largest one.
+The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stackoverflow fragments or Qualitas files.
+The classification results are shown in Table \ref{tab:classification_indv}.
+
+\begin{table}[H]
+	\centering
+	\caption{Classification results of 202 Simian$_{df}$ and 222 NiCad$_{df}$ individual unique pairs.}
+	\label{tab:classification_indv}
+	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+		\hline 
+		Classification & A & A' & B & C & D & E & F & Total \\ 
+		\hline 
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 25 & 0 & 15 & 3 & 29 & 9 & 121 & 202 \\ \cline{2-8}
+		\hline
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 1 & 0 & 34 & 1 & 186 & 222 \\ \cline{2-8}
+		\hline
+		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & \multirow{3}{*}{424} \\ 
+		& \multicolumn{4}{l|}{\textit{44 unique SO fragments}} & \multicolumn{3}{l|}{380 unique SO fragments} & \\
+		& \multicolumn{4}{l|}{\textit{44 unique Q files}} & \multicolumn{3}{l|}{380 unique Q files} & \\
+		\hline
+	\end{tabular} 
+\end{table}
+
+\subsubsection{Qualitas New (v. 2016-08-05)}
+
+\begin{table}[H]
+	\centering
+	\caption{Distributions of true positive pairs from the investigation of Qualitas (2013-09-01r)}
+	\label{tab:tp_pairs}
+	\begin{tabular}{l|r|r|r|r|p{5cm}}
+	\hline
+	Project		& \textit{good}-match & TP & \textit{ok}-match & TP & Reason of missing results \\
+	\hline
+	%& \multicolumn{5}{c}{\textit{Not included in the latest version}} \\
+	%\hline
+	jboss		& 2 	& 	0	& 63 	& 1 & NiCad's failure \\
+	db-derby 	& 0 	&	0	& 0		& 0 & NiCad's failure \\
+	hadoop		& 191 	& 1 	& 2432 	& 5 & NiCad's failure \\
+	hibernate 	& 19 	& 	0	& 11 	& 0 & NiCad's failure \\
+	ArgoUML		& 0		& 	0	& 0		& 0 & NiCad's failure \\
+	checkstyle	& 0		&	0	& 0		& 0 & NiCad's failure \\
+	cayenne		& 0		& 	0	& 0		& 0 & NiCad's failure \\
+	geotools	& 0		& 	0	& 0		& 0 & NiCad's failure \\
+	jena		& 0		& 	0	& 0		& 0 & NiCad's failure \\
+	Vuze		& 0		&	0	& 0		& 0 & NiCad's failure \\
+	Compiere	& 127	& 2		& 178	& 8 & No update \\
+	axion		& 7		& 	0	& 12	& 0 & No update \\
+	c-jdbc		& 66	&	0	& 768	& 0 & No update \\
+	colt		& 0		& 	0	& 5		& 0 & No update \\
+	columba		& 14	&	0	& 177	& 0 & No update \\
+	drawswf		& 0		&	0	& 0		& 0 & No update \\
+	fit-java	& 0		& 0		& 2 	& 0 & No update \\
+	freecs		& 5		& 0		& 22	& 0 & No update \\
+	heritrix	& 16	& 0		& 190 	& 0 & No update \\
+	iReport		& 0		& 0 	& 0		& 0 & No update \\
+	informa		& 31	& 0 	& 22	& 0 & No update \\
+	ivatagroupware	& 0	& 0		& 0		& 0 & No update \\
+	jFin		& 15	& 0		& 72	& 0 & No update \\
+	jOggPlayer	& 12 	& 0		& 52	& 0 & No update \\
+	jasml		& 23	& 0		& 47	& 0 & No update \\
+	jext		& 80	& 0		& 85	& 0 & No update \\
+	jgraphpad	& 1		& 1		& 55	& 0 & No update \\
+	jmoney		& 0		& 0		& 0		& 0 & No update \\
+	jparse		& 0		& 0		& 0		& 0 & No update \\
+	\hline
+	%& \multicolumn{5}{c}{\textit{Included in the latest version}} \\
+	%\hline
+	freecol		& 1		& 1		& 0		& 0		& \textit{FreeColMenuTest.java} exists with the \textit{createImageIcon()} method. Still can't find the reason why it is not reported. \\		
+	aoisrc281	& 0		& 0		& 33	& 33 	& \textit{MovieEncoder.java} (in 2 locations) are missing from the latest version. \\
+	findbugs	& 0		& 0		& 2		& 2 	& \textit{UnionBugs.java} has been changed. \\
+	jgraph		& 0		& 0		& 3		& 3 	& \textit{HelloWorld.java} has been changed. \\
+	\hline
+	Total		& 610	& 5		& 4231	& 52 	&\\
+	\hline
+\end{tabular}
+\end{table}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Sankey}
+	\caption{Relationships between similar code found from Stackoverflow and Qualitas projects}
+	\label{fig:sankey}
+\end{figure}
+
 \newpage
+
+\section*{Investigation of Missing A/B Clone Pairs Reported by Simian (df)}
+We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
+The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{fse13}$, NiCad$_{df}$, NiCad$_{fse13}$.
+The investigation results are shown in Table \ref{tab:search}.
+
+\begin{table}[H]
+	\centering
+	\caption{Results of matching the original 41 Simian(default) pairs in the pretty-printed result sets}
+	\label{tab:search}
+	\begin{tabular}{l|r|r}
+		\hline 
+		Settings & Found & Not found \\ 
+		\hline 
+		Simian$_{df}$  &  40 & 1* \\ 
+		\hline 
+		Simian$_{fse13}$ & 0 & 41  \\ 
+		\hline 
+		NiCad$_{df}$  & 17 & 24 \\ 
+		\hline 
+		NiCad$_{fse13}$ &  24 & 17 \\ 
+		\hline 
+	\end{tabular} 
+\end{table}
+
+The single missing Stackoverflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian.
+It is removed from the results of the pretty-printed version because it is an outlier.
+The rest are missing because of different parameter settings.
 
@@
 
+\bibliographystyle{plain}
+\bibliography{references}
+
 \end{document}

### 2016-09-01 src/eu/giuswhite/beans/SimianLog.java

@@ -64,6 +64,8 @@ public class SimianLog {
                 // System.out.println("Checking fragment: " + lF.filePath);
                 /* Check if it exists in the result list.*/
                 if(lF.isStackoverflowFragment){
+                    if (count == 2241)
+                        System.out.println(lF.getFilePath());
                     boolean exist = false;
                     SimianStackoverflowFragment simianStackoverflowFragment = new SimianStackoverflowFragment();
                     if (result.containsKey(lF.filePath)) {

### 2016-09-23 latex/stackoverflow.tex
Updated Sankey chart

@@
 
-\section*{Raw statistics}
-The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below.
+\section*{Dataset}
+In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{Qualitas}.
+
+\section*{Stackoverflow-Qualitas Clones}
+The results of 2 clone detectors: Simian and NiCad to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset are presented below.
 There are 2 tools selected: Simian and NiCad.
@@
 \subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
-\subsubsection{Qualitas Original (v. 2013-09-01r)}
+
 \begin{table}[H]
@@
 
-The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}.
+\textbf{Qualitas-\textit{O}:} The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}.
 We have manually investigated all of the 1,406 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.
@@
 This means that the copying can only be either (1) Q $\rightarrow$ S or (2) from a third source to both S and Q independently.
+
+\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$.
+We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
+The number of pairs that have been looked at is 6,706 (excluding duplicates).
+The results are shown in Table.
 
@@
 	\centering
-	\caption{Distribution of classification category A--F according to \textit{good}-match pairs}
+	\caption{Qualitas-\textit{O}: Distribution of classification category A--F according to \textit{good}-match pairs}
 	\label{tab:good_classification}
@@
 	\centering
-	\caption{Distribution of classification category A--F  according to the \textit{ok}-match pairs}
+	\caption{Qualitas-\textit{O}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
 	\label{tab:ok_classification}
@@
 
-\subsubsection{Qualitas New (v. 2016-08-05)}
-We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$.
-We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
-The number of pairs that have been looked at is 6,706 (excluding duplicates).
-The results are shown in Table.
+%\begin{table}[H]
+%	\centering
+%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$.}
+%	\label{tab:classification_new}
+%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+%		\hline 
+%		Classification & A & A' & B & C & D & E & F & Total \\ 
+%		\hline
+%		\multirow{1}{*}{\textit{good-match(0.7)}} & -- & -- & -- & -- & -- & -- & -- & -- \\ \cline{2-8}
+%		\hline
+%		\multirow{1}{*}{\textit{ok-match(0.7)}}  \\ \cline{2-8}
+%		\hline
+%		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{\multirow{3}{*}{6704}} & \multirow{3}{*}{6706} \\ 
+%		& \multicolumn{4}{l|}{\textit{1 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
+%		& \multicolumn{4}{l|}{\textit{1 unique Q files}} & \multicolumn{3}{c|}{} & \\
+%		\hline
+%	\end{tabular} 
+%\end{table}
 
@@
 	\centering
-	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$.}
-	\label{tab:classification_new}
+	\caption{Qualitas-\textit{N}: Distribution of classification category A--F according to \textit{good}-match pairs}
+	\label{tab:good_classification}
 	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
 		\hline 
-		Classification & A & A' & B & C & D & E & F & Total \\ 
+		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
 		\hline
-		\multirow{1}{*}{\textit{good-match(0.7)}} & -- & -- & -- & -- & -- & -- & -- & -- \\ \cline{2-8}
+		Simian$_{df}$--NiCad$_{df}$   & - & - & - & - & - & - & - & - \\
+		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & - & - & - & - & - & - & - & - \\
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & - & - & - & - & - & - & - & - \\
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ & - & - & - & - & - & - & - & - \\
 		\hline
-		\multirow{1}{*}{\textit{ok-match(0.7)}}  \\ \cline{2-8}
-		\hline
-		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{\multirow{3}{*}{6704}} & \multirow{3}{*}{6706} \\ 
-		& \multicolumn{4}{l|}{\textit{1 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
-		& \multicolumn{4}{l|}{\textit{1 unique Q files}} & \multicolumn{3}{c|}{} & \\
+		Total & - & - & - & - & - & - & - & - \\
 		\hline
@@
 	\centering
-	\caption{Distribution of classification category A--F  according to the \textit{ok}-match pairs}
+	\caption{Qualitas-\textit{N}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
 	\label{tab:ok_classification_new}
@@
 \subsection{Investigation of the unique clone pairs}
-\subsubsection{Qualitas Original (v. 2013-09-01r)}
-In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
+
+\textbf{Qualitas-\textit{O}:} In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
 However, only 10 of them appear in the new results using tool's agreement.
@@
 
+\textbf{Qualitas-N:}
+
 \begin{table}[H]
 	\centering
-	\caption{Classification results of 202 Simian$_{df}$ and 222 NiCad$_{df}$ individual unique pairs.}
+	\caption{Classification results of Simian$_{df}$ NiCad$_{df}$ individual unique pairs.}
 	\label{tab:classification_indv}
-	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{6mm}|R{8mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{8mm}|}
 		\hline 
-		Classification & A & A' & B & C & D & E & F & Total \\ 
+		\multirow{2}{*}{Classification} & \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ \cline{2-17}
+		 & A & A' & B & C & D & E & F & Total & A & A' & B & C & D & E & F & Total \\ 
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 25 & 0 & 15 & 3 & 29 & 9 & 121 & 202 \\ \cline{2-8}
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 25 & 0 & 15 & 3 & 29 & 9 & 121 & 9,272 & & & & & & & & \\ \cline{2-8}
 		\hline
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 1 & 0 & 34 & 1 & 186 & 222 \\ \cline{2-8}
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 1 & 0 & 34 & 1 & 186 & 6,831 & & & & & & & & \\ \cline{2-8}
 		\hline
-		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & \multirow{3}{*}{424} \\ 
-		& \multicolumn{4}{l|}{\textit{44 unique SO fragments}} & \multicolumn{3}{l|}{380 unique SO fragments} & \\
-		& \multicolumn{4}{l|}{\textit{44 unique Q files}} & \multicolumn{3}{l|}{380 unique Q files} & \\
+		TP/FP & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & 424 & & & & & & & &  \\
+
+		\hline
+		Unique SO fragments & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & & \multicolumn{4}{c|}{??} & & & & \\
+		\hline
+		Unique Q files & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & & \multicolumn{4}{c|}{??} & & & & \\
+		\hline
+		Unique Q files & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & & \multicolumn{4}{c|}{??} & & & & \\
 		\hline
@@
 
-\subsubsection{Qualitas New (v. 2016-08-05)}
-
 \begin{table}[H]
 	\centering
-	\caption{Distributions of true positive pairs from the investigation of Qualitas (2013-09-01r)}
+	\caption{Projects that do not have resutls in Qualitas-\textit{N} but do have results in Qualitas-\textit{O}}
 	\label{tab:tp_pairs}
@@
 	\hline
-	Project		& \textit{good}-match & TP & \textit{ok}-match & TP & Reason of missing results \\
+	\multirow{2}{*}{Project} & \multicolumn{4}{c|}{Qualitas-\textit{O}} & \multicolumn{1}{c}{Qualitas-\textit{N}} \\ \cline{2-6}
+			& \textit{good}-match & TP & \textit{ok}-match & TP & Reason of missing results \\
 	\hline
@@
 	\includegraphics[width=1\linewidth]{Sankey}
+	\caption{Relationships between similar code found from Stackoverflow and Qualitas files}
+	\label{fig:sankey}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Sankey_proj}
 	\caption{Relationships between similar code found from Stackoverflow and Qualitas projects}
@@
 
-However, the -balanceSquareBrackets+ parameter only works on a small testing environment having toy programs or only small pairs from the full datasets.
+However, the \texttt{-balanceSquareBrackets+} parameter only works on a small testing environment having toy programs or only small pairs from the full datasets.
 It does not work with the full complete set of 144,075 Stackoverflow fragments and Qualitas projects.

### 2016-09-23 latex/stackoverflow.tex
Latest version

--- 2016-09-01 latex/stackoverflow.tex
@@
 
+\newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
+
 \lstdefinestyle{base}{
@@
 
-\title{Code Overflow: \\
-	An empirical study of online code reuse}
+\title{Clone Overflow: \\
+	An empirical study of online code clone}
 \maketitle
 
-\section*{Raw statistics}
+\section*{Research Questions}
+\begin{itemize}
+	\item \textbf{RQ1 (online code clone):} \textit{can we find any reused source code fragments between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened or has been happening and at what scale.
+	\item \textbf{RQ2 (Direction of online code clone flow):} \textit{in which direction source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
+Is it from Q\&A site to open source projects, or the other way around, or both?
+	\item \textbf{RQ3 (Online code clone classification):} \textit{what are categories of online code clone?} How and why did these online code clone happen?
+	\item \textbf{RQ4 (Effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
+\end{itemize}
+
+\section*{Experimental Results}
 The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below.
@@
 	\centering
-	\caption{Qualitas (2013-09-01r): Simian and NiCad clone results}
+	\caption{Qualitas-\textit{O} (2013-09-01r): Simian and NiCad clone results}
 	\label{t_simian_raw_results}
@@
 	\centering
-	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
+	\caption{Qualitas-\textit{N} (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
 	\label{t_simian_raw_results}
@@
 	\centering
-	\caption{Qualitas (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
+	\caption{Qualitas-\textit{N} (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
 	\label{t_simian_raw_results}
@@
 
-%\begin{table}[H]
-%	\centering
-%	\caption{Qualitas projects (2016-08-16) successfully analysed by Simian and NiCad}
-%	\label{tab:projects_missing_new}
-%	\begin{tabular}{r|r|r|r}
-%		\hline
-%		Simian$_{df}$ & NiCad$_{df}$ & Simian$_{fse13}$ & NiCad$_{fse13}$ \\ \hline
-%		44	& 40 & 44 & 34 \\
-%		\hline
-%		& \textit{4 clustering failed} &  & \textit{6 clustering failed} \\
-%		\hline
-%		& jboss (wildfly) &	& ArgoUML \\
-%		& db-derby 	&  &  db-derby \\
-%		& hadoop 	& &  checkstyle \\
-%		& hibernate & &  cayenne \\
-%		&  			& &  geotools \\
-%		&  			& &  jena \\
-%		\hline
-%		& \textit{no renaming failed} & &  \textit{4 renaming failed} \\
-%		\hline
-%		&			& & Vuze \\
-%		&			& & hadoop \\
-%		&			& & hibernate \\
-%		&			& & jboss (wildfly) \\
-%		\hline
-%	\end{tabular}
-%\end{table}
-
 \begin{table}[H]
@@
 		\hline
-		\textit{default} & \textit{default} & 9 	& 481 	& 0 & 6,640 \\ 
-		\textit{default} & \textit{fse13} 	& 12 	& 418 	& 0 & 416 \\ 
+		\textit{default} & \textit{default} & 9 	& 481 	& 0 & 6,604 \\ 
+		\textit{default} & \textit{fse13} 	& 12 	& 418 	& 0 & 79 \\ 
 		\textit{fse13} 	& \textit{default} 	& 6 	& 60 	& 0 & 23 \\
@@
 		\hline
-		\multicolumn{2}{l|}{Total} & 1,415 & 11,165 & 1,170 & 13,386 \\
-		\multicolumn{2}{l|}{Total (unique)} & 1,406 & 10,879 & 1,170 & 10,879 \\
+		\multicolumn{2}{l|}{Total} & 1,415 & 11,165 & 1,170 & 13,396 \\
+		\multicolumn{2}{l|}{Total (unique)} & 1,406 & 10,879 & 1,170 & 13,386 \\
 		\hline
@@
 \end{table}
-
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{venn4_pairs_good}
-%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
-%	\label{fig:venn4_pairs_good}
-%\end{figure}
-
-%\begin{table}[H]
-%	\centering
-%	\caption{11,165 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
-%	\label{t_agreed_ok_clone_pairs}
-%	\begin{tabular}{l|r|r}
-%		\hline
-%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-%		\hline
-%		NiCad$_{\mathrm{\textit{default}}}$ & 481 & 60 \\%      & 709             \\
-%		NiCad$_{\mathrm{\textit{fse13}}}$   & 418 & 10,206 \\ % & 4680            \\
-%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
-%		\hline
-%	\end{tabular}
-%\end{table}
 
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
+		\includegraphics[width=0.7\linewidth]{venn4_pairs_good}
 		\captionof{figure}{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
+		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok}
 		\captionof{figure}{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
@@
 
-%\begin{table}[H]
-%	\centering
-%	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (10,879 are different, 286 are duplicates)}
-%	\label{t_dup_agreed_ok_clone_pairs}
-%	\begin{tabular}{l|r|r|r|r|r}
-%		\hline
-%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-%		\hline
-%		$S_dN_d$ & 214 	& 267 	& 0		& 0 		& 481 \\
-%		$S_dN_f$ & 267 	& 150 	& 0 	& 1 		& 418 \\ 
-%		$S_fN_d$ & 0 	& 0 	& 42 	& 18  		& 60 \\
-%		$S_fN_f$ & 0 	& 1 	& 18 	& 10,187 	& 10,206 \\	
-%		\hline
-%		Total 	 & 481  & 418	& 60	& 10,206	& 11,165 \\
-%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
-%		\hline
-%	\end{tabular}
-%\end{table}
-
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok}
-%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
-%	\label{fig:venn4_pairs}
-%\end{figure}
-
-%The statistics of the results from Simian and NiCad are shown in Table \ref{t_agreed_good_clone_pairs_new}, \ref{t_agreed_ok_clone_pairs_new}, and Figure \ref{fig:venn4_pairs_good_new}, and \ref{fig:venn4_pairs_ok_new}.
-%
-%\begin{table}[H]
-%	\centering
-%	\caption{1,170 agreed good-match(0.7) cloned pairs between Simian and Nicad (1,170 are unique)}
-%	\label{t_agreed_good_clone_pairs_new}
-%	\begin{tabular}{l|r|r}
-%		\hline
-%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\
-%		\hline
-%		NiCad$_{\mathrm{\textit{default}}}$ & 0 & 0 \\ 
-%		NiCad$_{\mathrm{\textit{fse13}}}$   & 0 & 1,170 \\ 
-%		\hline
-%	\end{tabular}
-%\end{table}
-
 \begin{figure}
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{venn4_pairs_good_new}
+		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_new}
 		\captionof{figure}{Qualitas-\textit{N} \textit{good}-match(0.7) pairs}
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok_new}
+		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_new}
 		\captionof{figure}{Qualitas-\textit{N} \textit{ok}-match(0.7) pairs}
@@
 
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{venn4_pairs_good_new}
-%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using good-match(0.7) criterion}
-%	\label{fig:venn4_pairs_good_new}
-%\end{figure}
-
-%\begin{table}[H]
-%	\centering
-%	\caption{13,733 agreed \textit{ok}-match(0.7) cloned pairs between Simian and Nicad (10,879 are different, 286 are duplicates). They contain all \textit{good}-match pairs}
-%	\label{t_agreed_ok_clone_pairs_new}
-%	\begin{tabular}{l|r|r}
-%		\hline
-%		& Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ 
-%		\hline
-%		NiCad$_{\mathrm{\textit{default}}}$ & 6604 & 23 \\
-%		NiCad$_{\mathrm{\textit{fse13}}}$   & 416 & 6690 \\
-%		\hline
-%	\end{tabular}
-%\end{table}
-
-%\begin{table}[H]
-%	\centering
-%	\caption{Duplicated agreed \textit{ok}-pairs between Simian and NiCad settings (13,386 are different, 347 are duplicates)}
-%	\label{t_dup_agreed_ok_clone_pairs}
-%	\begin{tabular}{l|r|r|r|r|r}
-%		\hline
-%		& $S_dN_d$ & $S_dN_f$ & $S_fN_d$ & $S_fN_f$ & Total \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-%		\hline
-%		$S_dN_d$ & 6267	& 337	& 0		& 	0	&  6604 \\
-%		$S_dN_f$ & 337 	& 79	& 0 	&  	0	&  416 \\ 
-%		$S_fN_d$ & 0 	& 0		& 13 	&   10	&  23 \\
-%		$S_fN_f$ & 0 	& 0 	& 10	&  	6680 &  6690 \\	
-%		\hline
-%		Total 	 & 6604  & 416	& 23	& 6690	& 13733 \\
-%		%NiCad$_{\mathrm{\textit{cloplag}}}$ &             &               \\ % &                \\
-%		\hline
-%	\end{tabular}
-%\end{table}
-
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.5\linewidth]{venn4_pairs_ok_new}
-%	\caption[Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion]{Agreed clone pairs reported by Simian and NiCad with default and FSE'13 settings using ok-match(0.7) criterion}
-%	\label{fig:venn4_pairs_ok_new}
-%\end{figure}
-
 \section*{Manual Investigation}
@@
 \subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
-\subsubsection{Qualitas Original (v. 2013-09-01r)}
+\subsubsection{Qualitas-\textit{O} (v. 2013-09-01r)}
 \begin{table}[H]
@@
 
-The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification}.
+The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification_good_o}.
 We have manually investigated all of the 1,406 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.
@@
 	\centering
-	\caption{Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
-	\label{tab:classification}
-	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{5mm}|R{3mm}|R{7mm}|R{7mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{7mm}|R{3mm}|R{7mm}|R{7mm}|}
+	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
+	\label{tab:classification_good_o}
+	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
 		\hline
-		\multirow{2}{*}{Classification}	& \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ 	\cline{2-17}
-		 & A & A' & B & C & D & E & F & Total 
-		 & A & A' & B & C & D & E & F & Total \\ 
+		Classificaiton & A & A' & B & C & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & Total  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
 		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}} 
-		& 1 & 0 & 1  & 3 & 26  & 6 & 1,369 & 1,406 
-		& -- & -- & -- & -- & -- & -- & -- & --  \\ \cline{2-8}
-		\hline
-		\multirow{1}{*}{\textit{ok-match(0.7)}} 
-		& 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 
-		& 2 & 0 & 0 & 0 & 6,676 & 1 & 27 & 6,706 \\ \cline{2-8}
-		\hline
-		TP/FP
-		& \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070
-		& \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{6,704} & 6,706 \\ 
-		\hline
-		Unique SO fragments & \multicolumn{4}{c|}{10} & & & & & \multicolumn{4}{c|}{1} & & & & \\
-		\hline
-		Unique Q files & \multicolumn{4}{c|}{13} & & & & & \multicolumn{4}{c|}{1} & & & & \\
-		\hline
-		Unique Q files & \multicolumn{4}{c|}{8} & & & & & \multicolumn{4}{c|}{1} & & & & \\
+		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & 5 & 5 & 4 & 4 & 26  & 6 & 1369 & 1401 & 56 & 416 & 31 & 1406 & 61 & 420 & 32 \\
+		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 36  & 8 & 52 & 8 & 10 & 6 & 474 & 57 & 81 & 612 & 77 & 62 & 17 & 664 & 84 & 70 & 20 \\
 		\hline
@@
 \end{table}
+
+%\begin{table}[H]
+%	\centering
+%	\caption{Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
+%	\label{tab:classification}
+%	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{5mm}|R{3mm}|R{7mm}|R{7mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{7mm}|R{3mm}|R{7mm}|R{7mm}|}
+%		\hline
+%		\multirow{2}{*}{Classification}	& \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ 	\cline{2-17}
+%		 & A & A' & B & C & D & E & F & Total 
+%		 & A & A' & B & C & D & E & F & Total \\ 
+%		\hline 
+%		\multirow{1}{*}{\textit{good-match(0.7)}} 
+%		& 1 & 0 & 1  & 3 & 26  & 6 & 1,369 & 1,406 
+%		& -- & -- & -- & -- & -- & -- & -- & --  \\ \cline{2-8}
+%		\hline
+%		\multirow{1}{*}{\textit{ok-match(0.7)}} 
+%		& 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 
+%		& 2 & 0 & 0 & 0 & 6,676 & 1 & 27 & 6,706 \\ \cline{2-8}
+%		\hline
+%		TP/FP
+%		& \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070
+%		& \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{6,704} & 6,706 \\ 
+%		\hline
+%		Unique SO fragments & \multicolumn{4}{c|}{10} & & & & & \multicolumn{4}{c|}{1} & & & & \\
+%		\hline
+%		Unique Q files & \multicolumn{4}{c|}{13} & & & & & \multicolumn{4}{c|}{1} & & & & \\
+%		\hline
+%		Unique Q projects & \multicolumn{4}{c|}{8} & & & & & \multicolumn{4}{c|}{1} & & & & \\
+%		\hline
+%	\end{tabular} 
+%\end{table}
 
@@
 
-\subsubsection{Qualitas New (v. 2016-08-05)}
+\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
 We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive.
@@
 The number of pairs that have been looked at is 6,706 (excluding duplicates).
-The results are shown in Table.
+The results are shown in Table \ref{tab:classification_good_n}.
 
@@
 	\centering
-	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$.}
-	\label{tab:classification_new}
-	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+	\caption{Qualitas-\textit{N}: Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
+	\label{tab:classification_good_n}
+	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
 		\hline
-		Classification & A & A' & B & C & D & E & F & Total \\ 
+		Classificaiton & A & A' & B & C & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & Total  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
 		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}} & -- & -- & -- & -- & -- & -- & -- & -- \\ \cline{2-8}
-		\hline
-		\multirow{1}{*}{\textit{ok-match(0.7)}}  \\ \cline{2-8}
-		\hline
-		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{\multirow{3}{*}{6704}} & \multirow{3}{*}{6706} \\ 
-		& \multicolumn{4}{l|}{\textit{1 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
-		& \multicolumn{4}{l|}{\textit{1 unique Q files}} & \multicolumn{3}{c|}{} & \\
+		\multirow{1}{*}{\textit{good-match(0.7)}}  & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - \\
+		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 2 & 0 & 0 & 0 & & & & & 6676 & 1 & 27 & & & & & 6706 & & & \\
 		\hline
@@
 \end{table}
+
+%\begin{table}[H]
+%	\centering
+%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$.}
+%	\label{tab:classification_new}
+%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+%		\hline 
+%		Classification & A & A' & B & C & D & E & F & Total \\ 
+%		\hline
+%		\multirow{1}{*}{\textit{good-match(0.7)}} & -- & -- & -- & -- & -- & -- & -- & -- \\ \cline{2-8}
+%		\hline
+%		\multirow{1}{*}{\textit{ok-match(0.7)}}  \\ \cline{2-8}
+%		\hline
+%		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{\multirow{3}{*}{6704}} & \multirow{3}{*}{6706} \\ 
+%		& \multicolumn{4}{l|}{\textit{1 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
+%		& \multicolumn{4}{l|}{\textit{1 unique Q files}} & \multicolumn{3}{c|}{} & \\
+%		\hline
+%	\end{tabular} 
+%\end{table}
 
@@
 
-\subsection{Investigation of the unique clone pairs}
-\subsubsection{Qualitas Original (v. 2013-09-01r)}
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{n+v}
+	\caption{Qualitas projects categorised by NiCad's results and their versions}
+	\label{fig:n+v}
+\end{figure}
+
+\subsection{Evolution of clone pairs from Qualitas-\textit{O} to Qualitas-\textit{N}}
+
+\subsection{Investigation of Simian and NiCad clone pairs}
+\subsubsection{Qualitas-\textit{O} (v. 2013-09-01r)}
 In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
@@
 
-We selected only Stackoverflow fragment and Qualitas files that have never been looked at before in the previous investigation.
+For Simian$_{df}$, there were 9,393 clone pairs reported by the tool.
+Out of 9,393 pairs, 143 of them are the ones found in \textit{ok-}pairs using agreement-based detection.
+We filtered the results further by removing false positives such as similar equals(), hashCode() methods, getters and setters out by using regular expression.
+We managed to remove 8,958 pairs using this method.
+Eventually, there were 292 clone pairs remaining for manual investigation.
+For NiCad$_{df}$, we obtained 7,062 clone pairs to look at which is infeasible for manual investigation.
+Hence, result filtering was also needed.
+However, regular expressions could not be used effectively as in Simian's case since NiCad allowed clones that are different at keywords/variable names or even added/deleted lines.
+So we decided to filter the results by selecting pairs that pass stricter clone criteria with $\mathrm{UPI} = 0.2$.
+By reducing the UPI to 0.2, there were totally 171 pairs left.
+Out of 171, 57 are \textit{ok}-pairs and 114 are remaining pairs for manual check (18 pairs are from \textit{cayenne} and \textit{iReport} that could not be analysed using UPI = 0.3).
+The statistics of the clones and classification results are reported in Table \ref{tab:classification_indv_stats} and \ref{tab:classification_indv}.
+
+%We selected only Stackoverflow fragment and Qualitas files that have never been looked at before in the previous investigation.
 If many clone pairs having the same Stackoverflow fragment and Qualitas file, we keep only the largest one.
@@
 	\centering
-	\caption{Classification results of 202 Simian$_{df}$ and 222 NiCad$_{df}$ individual unique pairs.}
-	\label{tab:classification_indv}
-	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+	\caption{Statistics of Simian$_{df}$ and NiCad$_{df}$ clone pairs.}
+	\label{tab:classification_indv_stats}
+	\begin{tabular}{l|r|r|r|r}
 		\hline 
-		Classification & A & A' & B & C & D & E & F & Total \\ 
+		Tool & Clone pairs & \textit{ok}-pairs & filtered pairs & remaining pairs \\ 
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 25 & 0 & 15 & 3 & 29 & 9 & 121 & 202 \\ \cline{2-8}
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 9393 & 143 & 8958 & 292 \\
 		\hline
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 1 & 0 & 34 & 1 & 186 & 222 \\ \cline{2-8}
-		\hline
-		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{44} & \multicolumn{3}{c|}{380} & \multirow{3}{*}{424} \\ 
-		& \multicolumn{4}{l|}{\textit{44 unique SO fragments}} & \multicolumn{3}{l|}{380 unique SO fragments} & \\
-		& \multicolumn{4}{l|}{\textit{44 unique Q files}} & \multicolumn{3}{l|}{380 unique Q files} & \\
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 7062  & 231 & 6717 & 114 \\
 		\hline
@@
 
-\subsubsection{Qualitas New (v. 2016-08-05)}
+\begin{table}[H]
+	\centering
+	\caption{Classification results of 292 Simian$_{df}$ and 114 NiCad$_{df}$ individual unique pairs. NiCad$_{df}$* shows the classification without cayenne and iReport.}
+	\label{tab:classification_indv}
+	\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|}
+		\hline 
+		Tool/Classification & A & A' & B & C & Sum & S$_{u}$ & Q$_{u}$ & Q$_{up}$ & D & E & F & Sum  & S$_{u}$ & Q$_{u}$ & Q$_{up}$ & Total & S$_{u}$ & Q$_{u}$  & Q$_{up}$  \\ 
+		\hline 
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & 133 & 68 & 59 & 23 & 13 & 12 & 134 & 159 & 39 & 72 & 23 & 292 & 103 & 125 & 31 \\
+		\hline
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & 9 & 9 & 5 & 4 & 24 & 3 & 78 & 105 & 41 & 39 & 12 & 114 & 48 & 44 & 14 \\ 
+		\hline
+		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & 5 & 4 & 5 & 3 & 23 & 1 & 67 & 91 & 28 & 31 & 10 & 96 & 33 & 37 & 13 \\ 
+		\hline
+	\end{tabular} 
+\end{table}
+
+\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
 
@@
 	\label{tab:tp_pairs}
-	\begin{tabular}{l|r|r|r|r|p{5cm}}
+	\begin{tabular}{l|r|r|r|r|p{6cm}}
 	\hline

### 2016-09-23 latex/stackoverflow.tex

@@
 \end{itemize}
+
+\section*{Dataset}
+In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{Qualitas}.
 
@@
 \subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
+
 \subsubsection{Qualitas-\textit{O} (v. 2013-09-01r)}
+
 \begin{table}[H]
@@
 
+\textbf{Qualitas-N:}
+
 \begin{table}[H]
@@
 	\centering
-	\caption{Distributions of true positive pairs from the investigation of Qualitas (2013-09-01r)}
+	\caption{Projects that do not have resutls in Qualitas-\textit{N} but do have results in Qualitas-\textit{O}}
 	\label{tab:tp_pairs}

### 2016-09-23 latex/stackoverflow.tex
Latest updates

@@
 \section*{Dataset}
-In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{Qualitas}.
+In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{QualitasCorpus}.
+However, we found that \textit{eclipse} project does not contain source code so we removed it from the dataset resulting in totally 63 projects being analysed.
+The details of the 63 Qualitas projects are listed in Table \ref{t:new_and_old}.
+
+\section*{Clone Detectors}
+We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info}
 
@@
 	\label{tab:projects_missing}
-	\begin{tabular}{r|r|r|r|r|r|r|r}
+	\begin{tabular}{r|r|r|r|r|r}
 		\hline
-		\multicolumn{4}{c|}{Qualitas-\textit{O}} & \multicolumn{4}{c}{Qualitas-\textit{N}} \\
+		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
 		\hline
-		Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ \\ \hline
-		63	& 63 & 57 & 46 & 44 & 44 & 40 & 34 \\
+		Simian$_{\textrm{\textit{df}}}$/Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ & Simian$_{\textrm{\textit{df}}}$/Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ \\ \hline
+		63	& 57 & 46 & 44 & 40 & 34 \\
 		\hline
-		& & \textit{6 clustering failed} & \textit{13 clustering failed} & & & \textit{4 clustering failed} & \textit{6 clustering failed} \\
-		& & cayenne   & cayenne 	& & & jboss (wildfly) & ArgoUML \\
-		& & checkstyle & checkstyle & & & hadoop & checkstyle \\
-		& & db-derby 	& db-derby 	& & & db-derby & db-derby \\
-		& & geotools 	& geotools  & & & hibernate & cayenne \\
-		& & iReport 	& iReport   & & & & jena \\
-		& & hibernate & ArgoUML 	& & & & geotools \\
-		& &			& castor 		& & & & \\
-		& &			& drjava 		& & & & \\
-		& &			& ganttproject 	& & & & \\
-		& &			& ivatagroupware & & & &  \\
-		& &			& jasperreports & & & & \\
-		& &			& jboss 		& & & & \\
-		& &			& jchempaint 	& & & & \\
+		& \textit{6 clustering failed} & \textit{13 clustering failed} & & \textit{4 clustering failed} & \textit{6 clustering failed} \\
+		& cayenne   & cayenne 	& & jboss (wildfly) & ArgoUML \\
+		& checkstyle & checkstyle & & hadoop & checkstyle \\
+		& db-derby 	& db-derby 	& & db-derby & db-derby \\
+		& geotools 	& geotools  & & hibernate & cayenne \\
+		& iReport 	& iReport   & & & jena \\
+		& hibernate & ArgoUML 	& & & geotools \\
+		&			& castor 		& & & \\
+		&			& drjava 		& & & \\
+		&			& ganttproject 	& & & \\
+		&			& ivatagroupware & & &  \\
+		&			& jasperreports & & & \\
+		&			& jboss 		& & & \\
+		&			& jchempaint 	& & & \\
 		\hline
-		& 			& &  \textit{4 renaming failed} & & & & \\
-		&			& & Vuze 		& & & & Vuze \\
-		&			& & aspectj 	& & & & hadoop \\
-		&			& & eXoPortal 	& & & & jboss (wildfly) \\
-		&			& &  hibernate 	& & & & hibernate \\
+		& 			&  \textit{4 renaming failed} & & & \textit{4 renaming failed} \\
+		&			& Vuze 		& & & Vuze \\
+		&			& aspectj 	& & & hadoop \\
+		&			& eXoPortal 	& & & jboss (wildfly) \\
+		&			&  hibernate 	& & & hibernate \\
 		\hline
@@
 
-\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$.
+\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{df}}}$, Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{df}}}$.
 We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
@@
 	\centering
-	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
+	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-match pairs which excludes the subsumed \textit{good}-match and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ pairs.}
 	\label{tab:classification_good_o}
@@
 		\hline
-		Classificaiton & A & A' & B & C & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & Total  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
+		Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
 		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & 5 & 5 & 4 & 4 & 26  & 6 & 1369 & 1401 & 56 & 416 & 31 & 1406 & 61 & 420 & 32 \\
-		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 36  & 8 & 52 & 8 & 10 & 6 & 474 & 57 & 81 & 612 & 77 & 62 & 17 & 664 & 84 & 70 & 20 \\
+		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & \textbf{5} & 5 & 4 & 4 & 26  & 6 & 1369 & \textbf{1401} & 56 & 416 & 31 & \textbf{1406} & 61 & 420 & 32 \\
+		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 36  & 8 & \textbf{52} & 8 & 10 & 6 & 474 & 57 & 81 & \textbf{612} & 77 & 62 & 17 & \textbf{664} & 84 & 70 & 20 \\
 		\hline
@@
 		\hline
-		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
-		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
 		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,368 & 1,387 \\
@@
 		\hline
-		Simian$_{df}$--NiCad$_{df}$  & 3 	& 0 	& 17	& 1 	& 428  & 6 		& 7 	&  462 \\
-		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 5 	& 0 	& 18 	& 7 	& 17 	 & 51 	  & 50 		&  148 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$  & 3 	& 0 	& 17	& 1 	& 428  & 6 		& 7 	&  462 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 5 	& 0 	& 18 	& 7 	& 17 	 & 51 	  & 50 		&  148 \\
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
 		\hline
@@
 \subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
-We decided to filter out the agreed clone pairs reported by agreement of Simian$_{fse13}$-NiCad$_{fse13}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$, and Simian$_{fse13}$-NiCad$_{df}$.
+We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{df}}}$, Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{df}}}$.
 We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
@@
 %	\centering
-%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{fse13}$.}
+%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{df}}}$, Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{fse13}}}$.}
 %	\label{tab:classification_new}
@@
 		\hline
-		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
-		Simian$_{df}$--NiCad$_{\textrm{\textit{fse13}}}$ 
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$ 
 		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{df}$   									
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   									
 		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
@@
 
-\subsection{Evolution of clone pairs from Qualitas-\textit{O} to Qualitas-\textit{N}}
-
 \subsection{Investigation of Simian and NiCad clone pairs}
@@
 
-With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{fse13}$ and NiCad$_{fse13}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}.
+With our 4 settings, we decided to investigate only 2 settings, Simian$_{\mathrm{\textit{df}}}$, and NiCad$_{\mathrm{\textit{df}}}$, and drop Simian$_{\mathrm{\textit{fse13}}}$ and NiCad$_{\mathrm{\textit{fse13}}}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}.
 With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.
 
-For Simian$_{df}$, there were 9,393 clone pairs reported by the tool.
+For Simian$_{\mathrm{\textit{df}}}$, there were 9,393 clone pairs reported by the tool.
 Out of 9,393 pairs, 143 of them are the ones found in \textit{ok-}pairs using agreement-based detection.
@@
 Eventually, there were 292 clone pairs remaining for manual investigation.
-For NiCad$_{df}$, we obtained 7,062 clone pairs to look at which is infeasible for manual investigation.
+For NiCad$_{\mathrm{\textit{df}}}$, we obtained 7,062 clone pairs to look at which is infeasible for manual investigation.
 Hence, result filtering was also needed.
@@
 
-\textbf{Qualitas-N:}
-
 \begin{table}[H]
 	\centering
-	\caption{Statistics of Simian$_{df}$ and NiCad$_{df}$ clone pairs.}
+	\caption{Statistics of Simian$_{\mathrm{\textit{df}}}$ and NiCad$_{\mathrm{\textit{df}}}$ clone pairs.}
 	\label{tab:classification_indv_stats}
@@
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 9393 & 143 & 8958 & 292 \\
+		\multirow{1}{*}{\textit{Simian$_{\mathrm{\textit{df}}}$}} & 9393 & 143 & 8958 & 292 \\
 		\hline
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 7062  & 231 & 6717 & 114 \\
+		\multirow{1}{*}{\textit{NiCad$_{\mathrm{\textit{df}}}$}} & 7062  & 231 & 6717 & 114 \\
 		\hline
@@
 	\centering
-	\caption{Classification results of 292 Simian$_{df}$ and 114 NiCad$_{df}$ individual unique pairs. NiCad$_{df}$* shows the classification without cayenne and iReport.}
+	\caption{Classification results of 292 Simian$_{\mathrm{\textit{df}}}$ and 114 NiCad$_{\mathrm{\textit{df}}}$ individual unique pairs.
+NiCad$_{\mathrm{\textit{df}}}$* shows the classification without cayenne and iReport.}
 	\label{tab:classification_indv}
@@
 		\hline 
-		Tool/Classification & A & A' & B & C & Sum & S$_{u}$ & Q$_{u}$ & Q$_{up}$ & D & E & F & Sum  & S$_{u}$ & Q$_{u}$ & Q$_{up}$ & Total & S$_{u}$ & Q$_{u}$  & Q$_{up}$  \\ 
+		Tool/Classification & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_{u}$ & Q$_{up}$ & D & E & F & \textbf{Sum}  & S$_{u}$ & Q$_{u}$ & Q$_{up}$ & \textbf{Total} & S$_{u}$ & Q$_{u}$  & Q$_{up}$  \\ 
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & 133 & 68 & 59 & 23 & 13 & 12 & 134 & 159 & 39 & 72 & 23 & 292 & 103 & 125 & 31 \\
+		\multirow{1}{*}{\textit{Simian$_{\mathrm{\textit{df}}}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
 		\hline
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & 9 & 9 & 5 & 4 & 24 & 3 & 78 & 105 & 41 & 39 & 12 & 114 & 48 & 44 & 14 \\ 
+		\multirow{1}{*}{\textit{NiCad$_{\mathrm{\textit{df}}}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
 		\hline
-		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & 5 & 4 & 5 & 3 & 23 & 1 & 67 & 91 & 28 & 31 & 10 & 96 & 33 & 37 & 13 \\ 
+		\multirow{1}{*}{\textit{NiCad$_{\mathrm{\textit{df}}}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
 		\hline
@@
 
-\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
+\begin{table}[H]
+	\centering
+	\caption{Numbers of true online clone pairs (A+A'+B+C) found by manual investigation}
+	\label{tab:classification_indv_summary}
+	\begin{tabular}{r|r|r|r|r}
+		\hline 
+		\textit{good}-pairs & \textit{ok}-pairs & Simian$_{\mathrm{\textit{df}}}$ pairs & NiCad$_{\mathrm{\textit{df}}}$ pairs & Total \\ 
+		\hline 
+		5 & 52 & 133 & 9 & 199 \\
+		\hline
+	\end{tabular} 
+\end{table}
+
+%\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
+
+\subsection{Evolution of clone pairs from Qualitas-\textit{O} to Qualitas-\textit{N}}
+After located and classified all the online clone pairs, we are now interested in analysing the evolution of true online clone pairs.
+This is to answer RQ4.
+In this setting, we only focus on 44 projects in the region in V in Figure \ref{fig:n+v}.
+They are projects which can be analysed Simian and also have newer versions than the versions in Qualitas-\textit{O}.
+After filtering, there are 45 pairs removed because they do not have new versions (7 from c-jdbc, 21 from Compiere, 7 from heritrix, and 10 from iReport) and 154 pairs remaining.
 
@@
 	\centering
-	\includegraphics[width=1\linewidth]{Sankey}
-	\caption{Relationships between similar code found from Stackoverflow and Qualitas files}
-	\label{fig:sankey}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
 	\includegraphics[width=1\linewidth]{Sankey_proj}
-	\caption{Relationships between similar code found from Stackoverflow and Qualitas projects}
+	\caption{Relationships between 199 true online code clone found between Stackoverflow and Qualitas projects}
 	\label{fig:sankey}
@@
 We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
-The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{fse13}$, NiCad$_{df}$, NiCad$_{fse13}$.
+The 41 pairs were searched for in 4 new results sets: Simian$_{\mathrm{\textit{df}}}$, Simian$_{\mathrm{\textit{fse13}}}$, NiCad$_{\mathrm{\textit{df}}}$, NiCad$_{\mathrm{\textit{fse13}}}$.
 The investigation results are shown in Table \ref{tab:search}.
@@
 		\hline 
-		Simian$_{df}$  &  40 & 1* \\ 
+		Simian$_{\mathrm{\textit{df}}}$  &  40 & 1* \\ 
 		\hline 
-		Simian$_{fse13}$ & 0 & 41  \\ 
+		Simian$_{\mathrm{\textit{fse13}}}$ & 0 & 41  \\ 
 		\hline 
-		NiCad$_{df}$  & 17 & 24 \\ 
+		NiCad$_{\mathrm{\textit{df}}}$  & 17 & 24 \\ 
 		\hline 
-		NiCad$_{fse13}$ &  24 & 17 \\ 
+		NiCad$_{\mathrm{\textit{fse13}}}$ &  24 & 17 \\ 
 		\hline 

### 2016-09-27 latex/stackoverflow.tex
Fixed the problem of AoISrc duplicates

@@
 	\centering
-	\caption{63 Qualitas projects (new versions checked on 2016-08-05)}
+	\caption{63 Qualitas projects (new versions checked on 2016-09-27)}
 	\label{t:new_and_old}
@@
 	\hline
-	ArgoUML & 0.34 & 0.35.1 & 15/01/2014 	& & Eclipse Public License v.1.0 \\
-	Compiere & 330 & -- & 01/06/2010 		& git & GNU General Public License v.2.0 & No longer OSS \\
-	FitLibrary & 20100806 & 20111026 & 12/07/2014 & & GNU General Public License v.2.0 \\
-	JGroups & 2.10.0.GA & 3.6.10 & 27/06/2016 & & Apache License, v.2.0 \\
-	Vuze & 4812 & 5721-20 & 12/05/2016 & & GNU General Public License v.2.0 &  \\
-	antlr4 & 4.0 & 4.2.1 & 15/01/2014 & & BSD License \\
-	aoisrc & 281 & 302 & 12/01/2015 & & GNU General Public License v.2.0 \\
+	antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD License \\
 	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache License, v.2.0 \\
-	aspectj & 1.6.9 & 1.8.9 & 14/03/2015 & & Eclipse Public License 1.0 \\
-	axion & 1.0-M2 & -- & 08/03/2013 & & Proprietary (BSD/Apache-style) \\
-	batik & 1.7 & 1.8 & 16/03/2015 & & Apache License, v.2.0 \\
-	c-jdbc & 2.0.2 & -- & 16/09/2005 & & GNU Lesser General Public License, v.2.1 \\
-	castor & 1.3.1 & 1.4.2 & 20/06/2016 & git & Apache License, v.2.0 \\
-	cayenne & 3.0.1 & 4.0.M4 &  27/07/2016 & git & Apache License, v.2.0 \\
-	checkstyle & 5.1 & 7.2  & 04/08/2016 & git & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
-	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2015 & git & GNU General Public License v.2.0  \\
-	colt & 1.2.0 & -- & 09/09/2014 & & Proprietary (CERN) \\
-	columba & 1.4 & -- & 20/04/2007 & & Mozilla Public License 1.1  \\
-	commons-collections & 3.2.1 & 4.1 & 25/11/2015 & & Apache License, v.2.0 \\
-	db-derby & 10.6.1.0 & 10.12.1.1 & 13/09/2015 & & Apache License, v.2.0 \\
+	argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse Public License v.1.0 \\
+	artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GNU General Public License v.2.0 \\
+	aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse Public License 1.0 \\
+	axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) \\
+	batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache License, v.2.0 \\
+	c-jdbc & 2.0.2 & - & 16/09/2005 & - & GNU Lesser General Public License, v.2.1 \\
+	castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache License, v.2.0 \\
+	cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache License, v.2.0 \\
+	checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
+	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GNU General Public License v.2.0  \\
+	colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
+	columba & 1.4 & - & 20/04/2007 & - & Mozilla Public License 1.1  \\
+	commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache License, v.2.0 \\
+	compiere & 330 & - & - & - & GNU General Public License v.2.0 & No longer OSS \\
+	db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache License, v.2.0 \\
 	displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT License \\
-	drawswf & 1.2.9 & -- & 02/04/2013 & & GNU General Public License v.2.0 \\
-	drjava & 20100913-r5387 & 20140826-r5761 & 26/08/2014 & & BSD License \\
-	eXoPortal & ??? & 4.4 & 24/06/2016 & git & GNU Lesser General Public License v.3.0 \& proprietary \\
-	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & & Common Public License 1.0 \\
-	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & & GNU Lesser General Public License, v.2.0 \\
-	fit-java & 1.1 & -- & 04/06/2013 & & GNU General Public License v.2.0 \\
-	freecol & 0.10.7 & 0.11.6 & 04/08/2016 & git & GNU General Public License v.2.0 &  \\
-	freecs & 1.3.20100406 & -- & 22/04/2013 & & GNU General Public License v.3.0 &   \\
-	freemind & 0.9.0 & 1.0.0 & 26/06/2016 & & GNU General Public License v.2.0+ &  \\
-	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & & GNU General Public License v.2.0 \\
-	ganttproject & 2.0.9 & 2.8.1 & 05/08/2016 & & GNU General Public License v.3.0 &  \\
-	geotools & 2.7-M3 & 16 & 02/08/2016 & git & GNU Lesser General Public License, v.2.0 \\
-	hadoop & 1.0.0 & 2.6.4 & 11/02/2016 & & Apache License, v.2.0 \\
-	heritrix & 1.14.4 & -- & 05/06/2013 & & GNU Lesser General Public License, v.2.1 \\
-	hibernate & 4.2.2 & 5.2.2 & 04/08/2016 & git & GNU Lesser General Public License, v.2.1+ \\
-	hsqldb & 2.0.0 & 2.3.4 & 16/05/2016 & svn & BSD License \\
-	htmlunit & 2.8 & 2.24 & 27/07/2016 & svn & Apache License, v.2.0 \\
-	iReport & 3.7.5 & -- & 28/05/2014 & & Affero GNU Public License, v.3.0 \\
-	iText & 5.0.3 & 7.0.0 & 02/05/2016 & & Affero GNU Public License, v.3.0 \\
-	informa & 0.7.0-alpha2 & -- & 07/11/2008 & & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
-	ivatagroupware & 0.11.3 & -- & 27/02/2013 & & GNU General Public License v.2.0 \\
-	jFin DateMath & R1\_0\_1 & -- & 25/04/2013 & & GNU General Public License v.2.0 \\
-	jOggPlayer & 114s & -- &  15/04/2013 &  & GNU General Public License v.2.0 \\
-	jag & 6.1 & 6.2 & 08/04/2013  & & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries. \\
-	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & & Apache License, v.2.0 \\
-	jasml & 0.10 & -- & 08/03/2013 & & Apache Software License \\
-	jasperreports & 3.7.4 & 6.3.1 & 20/06/2016 & git & GNU Lesser General Public License, v.3.0 &  \\
-	javacc & 5.0.0 & 7.0.0 & 07/07/2016 & svn & Proprietary (Sun) \\
-	jboss (Wildfly) & 5.1.0.GA & 10.0.0 & 29/01/2016 & & GNU Lesser General Public License, v.2.1 & Renamed to Wildfly. \\
-	jchempaint & 3.0.1 & 3.1.3 & 18/04/2016 & git & GNU Lesser General Public License, v.2.1+ &  \\
-	jedit & 4.3.2 & 5.3.0 & 20/10/2015 & & GNU General Public License v.2.0 &  \\
-	jena & 2.6.3 & 3.1.0 & 10/05/2016 & & Apache License, v.2.0 \\
-	jext & 5.0 & -- & 18/08/2004 &  & GNU General Public License v.2.0 &  \\
-	jfreechart & 1.0.13 & 1.2.0-ea1 & 08/05/2016 & svn & GNU Lesser General Public License, v.2.0 &   \\
-	jgraph & 5.13.0.0 & 3.5.1.5 & 20/07/2016 & git & Proprietary (mxGraph License) \\
-	jgraphpad & 5.10.0.2 & -- & 10/11/2006 & & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
-	jgrapht & 0.8.1 & 0.9.2 & 03/04/2016 & & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
-	jmoney & 0.4.4 & -- & 17/04/2016 & & GNU General Public License v.2.0 &  \\
-	jparse & 0.96 & -- & 29/07/2004 & & GNU Lesser General Public License, v.2.1 \\
-	jpf & 1.5.1 & ??? & 13/01/2012 & & Apache License, v.2.0 \\
-	junit & 4.11 & 4.12 & 04/12/2014 & & Eclipse Public License, v.1.0 \\
-	shiftone-jrat & 0.6 & 1-beta-1 & 25/04/2013 & svn & GNU Lesser General Public License, v.2.0 &  \\
+	drawswf & 1.2.9 & - & 02/04/2013 & - & GNU General Public License v.2.0 \\
+	drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD License & Build to see version? \\
+	exoportal & ??? & ??? &  & git & GNU Lesser General Public License v.3.0 \& proprietary & Too many new projects \\
+	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common Public License 1.0 \\
+	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GNU Lesser General Public License, v.2.0 \\
+	fit-java & 1.1 & - & 04/06/2013 & - & GNU General Public License v.2.0 \\
+	fitlibrary & 20100806 & ??? & 29/07/2014 & git & GNU General Public License v.2.0 \\
+	freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GNU General Public License v.2.0 &  \\
+	freecs & 1.3.20100406 & - & 22/04/2013 & - & GNU General Public License v.3.0 &   \\
+	freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GNU General Public License v.2.0+ &  \\
+	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GNU General Public License v.2.0 \\
+	ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GNU General Public License v.3.0 &  \\
+	geotools & 2.7-M3 & 16 & 27/09/2016 & git & GNU Lesser General Public License, v.2.0 \\
+	hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache License, v.2.0 \\
+	heritrix & 1.14.4 & - & 05/06/2013 & - & GNU Lesser General Public License, v.2.1 \\
+	hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GNU Lesser General Public License, v.2.1+ \\
+	hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD License \\
+	htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache License, v.2.0 \\
+	ireport & 3.7.5 & - & 28/05/2014 & - & Affero GNU Public License, v.3.0 \\
+	itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GNU Public License, v.3.0 \\
+	informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
+	ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GNU General Public License v.2.0 \\
+	jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GNU General Public License v.2.0 \\
+	joggplayer & 114s & - &  15/04/2013 & - & GNU General Public License v.2.0 \\
+	jag & 6.1 & 6.2 & 08/04/2013  & - & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries. \\
+	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache License, v.2.0 \\
+	jasml & 0.10 & - & 08/03/2013 & - & Apache Software License \\
+	jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GNU Lesser General Public License, v.3.0 &  \\
+	javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) \\
+	jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GNU Lesser General Public License, v.2.1 & Renamed to Wildfly. \\
+	jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GNU Lesser General Public License, v.2.1+ &  \\
+	jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GNU General Public License v.2.0 &  \\
+	jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache License, v.2.0 \\
+	jext & 5.0 & - & 18/08/2004 & - & GNU General Public License v.2.0 &  \\
+	jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GNU Lesser General Public License, v.2.0 &   \\
+	jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph License) \\
+	jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
+	jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
+	jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache License, v.2.0 \\
+	jmoney & 0.4.4 & ??? & 27/12/2015 & git & GNU General Public License v.2.0 &  \\
+	jparse & 0.96 & - & 29/07/2004 & - & GNU Lesser General Public License, v.2.1 \\
+	jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache License, v.2.0 \\
+	junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse Public License, v.1.0 \\
+	shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GNU Lesser General Public License, v.2.0 &  \\
+	vuze & 4812 & 5730 & 23/09/2016 & svn & GNU General Public License v.2.0 & \\
 	\hline 
@@
 		\hline
-		\textit{default} & \textit{default} & 9 	& 481 	& 0 & 6,604 \\ 
-		\textit{default} & \textit{fse13} 	& 12 	& 418 	& 0 & 79 \\ 
-		\textit{fse13} 	& \textit{default} 	& 6 	& 60 	& 0 & 23 \\
-		\textit{fse13} 	& \textit{fse13} 	& 1,388 & 10,206 & 1,170 & 6,690 \\ 
+		\textit{default} & \textit{default} & 9 	& 473 	& 0 & 6,604 \\ 
+		\textit{default} & \textit{fse13} 	& 12 	& 353 	& 0 & 79 \\ 
+		\textit{fse13} 	& \textit{default} 	& 7 	& 60 	& 0 & 23 \\
+		\textit{fse13} 	& \textit{fse13} 	& 1,338 & 9528 & 1,170 & 6,690 \\ 
 		\hline
-		\multicolumn{2}{l|}{Total} & 1,415 & 11,165 & 1,170 & 13,396 \\
-		\multicolumn{2}{l|}{Total (unique)} & 1,406 & 10,879 & 1,170 & 13,386 \\
+		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 & 1,170 & 13,396 \\
+		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 & 1,170 & 13,386 \\
 		\hline
@@
 The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification_good_o}.
-We have manually investigated all of the 1,406 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.
-However, for the \textit{ok-match}, we could not investigate all of the 10,879 pairs manually.
-According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ produces a large number, 1,387, of false positive results (D, E, and F).
+We have manually investigated all of the 1,357 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.
+However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.
+According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ produces a large number, 1,338, of false positive results (D, E, and F).
 Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs.
-There are totally 664 \textit{ok-match} pairs that were investigated.
-The 57 true positive pairs found are combinations of 10 unique Stackoverflow fragments, and 13 unique Qualitas Java files.
+There are totally 608 \textit{ok-match} pairs that were investigated.
+The 39 true positive pairs found are combinations of 8 unique Stackoverflow fragments, and 9 unique Qualitas Java files from 6 different projects.
 
@@
 		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & \textbf{5} & 5 & 4 & 4 & 26  & 6 & 1369 & \textbf{1401} & 56 & 416 & 31 & \textbf{1406} & 61 & 420 & 32 \\
-		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 36  & 8 & \textbf{52} & 8 & 10 & 6 & 474 & 57 & 81 & \textbf{612} & 77 & 62 & 17 & \textbf{664} & 84 & 70 & 20 \\
+		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & \textbf{5} & 5 & 4 & 4 & 26  & 6 & 1320 & \textbf{1352} & 56 & 402 & 31 & \textbf{1357} & 61 & 406 & 32 \\
+		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 23  & 8 & \textbf{39} & 8 & 9 & 6 & 480 & 28 & 61 & \textbf{569} & 76 & 60 & 16 & \textbf{608} & 83 & 68 & 19 \\
 		\hline
@@
 		\hline
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$   & 1 & 0 & 1 & 0 & 0 & 4 & 0 & 6 \\
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 3 & 1 & 1 & 1 & 6 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
 		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,368 & 1,387 \\
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,319 & 1,338 \\
 		\hline
-		Total   &   1   &   0   &   1   &   3   &   26   &   6   & 1,369  & 1,406 \\
+		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1,320  & 1,366 \\
+		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1,320  & 1,352 \\
 		\hline
@@
 		\hline
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$  & 3 	& 0 	& 17	& 1 	& 428  & 6 		& 7 	&  462 \\
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 5 	& 0 	& 18 	& 7 	& 17 	 & 51 	  & 50 		&  148 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   									& 0 	& 0 	& 1 	& 0 	 & 29 	  & 0 		& 24 	& 54 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
+		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
+		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   									& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
 		\hline
-		Total   &   8  &   0   &  36   &  8   &   474   &   57   & 81  & 664 \\
+		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
+		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
 		\hline
@@
 	\centering
-	\includegraphics[width=0.7\linewidth]{n+v}
-	\caption{Qualitas projects categorised by NiCad's results and their versions}
-	\label{fig:n+v}
+	\includegraphics[width=0.7\linewidth]{n+v+g}
+	\caption{Qualitas projects categorised by NiCad's results, existence of newer versions, and version control}
+	\label{fig:n+v+g}
 \end{figure}
@@
 		\hline 
-		5 & 52 & 133 & 9 & 199 \\
+		5 & 52 & 133 & 9 & 183 \\
 		\hline
@@
 This is to answer RQ4.
-In this setting, we only focus on 44 projects in the region in V in Figure \ref{fig:n+v}.
-They are projects which can be analysed Simian and also have newer versions than the versions in Qualitas-\textit{O}.
-After filtering, there are 45 pairs removed because they do not have new versions (7 from c-jdbc, 21 from Compiere, 7 from heritrix, and 10 from iReport) and 154 pairs remaining.
+In this setting, we only focus on 39 projects in the X region in Figure \ref{fig:n+v+g}.
+We decided to ignore NiCad results from this analysis due to its failure of clone clustering and renaming on some projects.
+Thus, the 18 projects are the ones that can be analysed by Simian, have newer versions than the versions in Qualitas-\textit{O}, and have code version control system (either git or svn).
+After filtering, there are 141 pairs removed because 45 of them do not have new versions (7 from c-jdbc, 21 from Compiere, 7 from heritrix, and 10 from iReport) and 4 of them we could not find source code with version control (2 from findbugs, 1 from jag, and 1 from jgraphpad).
+Finally there were 134  pairs remaining.
+%We are interested in clone pairs that were changed after they appeared on Stackoverflow.
 

### 2016-09-28 latex/stackoverflow.tex
Updates

@@
 For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors.
-For NiCad FSE13 settings (NiCad$_{\textrm{\textit{fse13}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}.
+For NiCad FSE13 settings (NiCad$_{fse13}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}.
 So these projects are also missing from agreed clone pairs.
@@
 		\hline
-		Simian$_{\textrm{\textit{df}}}$/Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ & Simian$_{\textrm{\textit{df}}}$/Simian$_{\textrm{\textit{fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{fse13}}}$ \\ \hline
+		Simian$_{\textrm{\textit{df}}}$/Simian$_{fse13}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ & Simian$_{\textrm{\textit{df}}}$/Simian$_{fse13}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ \\ \hline
 		63	& 57 & 46 & 44 & 40 & 34 \\
@@
 \end{figure}
-
-\begin{figure}
-	\centering
-	\begin{minipage}{.5\textwidth}
-		\centering
-		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_new}
-		\captionof{figure}{Qualitas-\textit{N} \textit{good}-match(0.7) pairs}
-		\label{fig:venn4_new_good}
-	\end{minipage}%
-	\begin{minipage}{.5\textwidth}
-		\centering
-		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_new}
-		\captionof{figure}{Qualitas-\textit{N} \textit{ok}-match(0.7) pairs}
-		\label{fig:venn4_new_ok}
-	\end{minipage}
-\end{figure}
+%
+%\begin{figure}
+%	\centering
+%	\begin{minipage}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_new}
+%		\captionof{figure}{Qualitas-\textit{N} \textit{good}-match(0.7) pairs}
+%		\label{fig:venn4_new_good}
+%	\end{minipage}%
+%	\begin{minipage}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_new}
+%		\captionof{figure}{Qualitas-\textit{N} \textit{ok}-match(0.7) pairs}
+%		\label{fig:venn4_new_ok}
+%	\end{minipage}
+%\end{figure}
 
@@
 However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.
-According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$ produces a large number, 1,338, of false positive results (D, E, and F).
+According to the distribution of category from \textit{good-match} results, we can see that Simian$_{fse13}$--NiCad$_{fse13}$ produces a large number, 1,338, of false positive results (D, E, and F).
 Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs.
@@
 
-\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{df}}}$, Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{df}}}$.
+%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{df}$.
 We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
@@
 		\hline
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\textrm{\textit{fse13}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,319 & 1,338 \\
+		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
+		Simian$_{df}$--NiCad$_{fse13}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
+		Simian$_{fse13}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
+		Simian$_{fse13}$--NiCad$_{fse13}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,319 & 1,338 \\
 		\hline
@@
 		\hline
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$   									& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   									& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
+		Simian$_{df}$--NiCad$_{df}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
+		Simian$_{df}$--NiCad$_{fse13}$   									& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
+		Simian$_{fse13}$--NiCad$_{df}$   									& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
 		\hline
@@
 
-\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
-We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{df}}}$, Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{df}}}$.
+%\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
+%We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{df}$.
 We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
@@
 The results are shown in Table \ref{tab:classification_good_n}.
-
-\begin{table}[H]
-	\centering
-	\caption{Qualitas-\textit{N}: Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
-	\label{tab:classification_good_n}
-	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
-		\hline
-		Classificaiton & A & A' & B & C & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & Total  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
-		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}}  & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - \\
-		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 2 & 0 & 0 & 0 & & & & & 6676 & 1 & 27 & & & & & 6706 & & & \\
-		\hline
-	\end{tabular} 
-\end{table}
+%
+%\begin{table}[H]
+%	\centering
+%	\caption{Qualitas-\textit{N}: Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
+%	\label{tab:classification_good_n}
+%	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
+%		\hline
+%		Classificaiton & A & A' & B & C & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & Total  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
+%		\hline 
+%		\multirow{1}{*}{\textit{good-match(0.7)}}  & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - \\
+%		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 2 & 0 & 0 & 0 & & & & & 6676 & 1 & 27 & & & & & 6706 & & & \\
+%		\hline
+%	\end{tabular} 
+%\end{table}
 
@@
 %	\centering
-%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{df}}}$, Simian$_{\mathrm{\textit{df}}}$-NiCad$_{\mathrm{\textit{fse13}}}$.}
+%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{fse13}}}$.}
 %	\label{tab:classification_new}
@@
 
-\begin{table}[H]
-	\centering
-	\caption{Qualitas-\textit{N}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
-	\label{tab:ok_classification_new}
-	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
-		\hline 
-		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
-		\hline
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\mathrm{\textit{df}}}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
-		Simian$_{\mathrm{\textit{df}}}$--NiCad$_{\textrm{\textit{fse13}}}$ 
-		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
-		Simian$_{\textrm{\textit{fse13}}}$--NiCad$_{\mathrm{\textit{df}}}$   									
-		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
-		\hline
-		Total   & 2  	&   0   & 0   	&  0   &   6676   &   1   & 27  & 6706 \\
-		\hline
-	\end{tabular} 
-\end{table}
+%\begin{table}[H]
+%	\centering
+%	\caption{Qualitas-\textit{N}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
+%	\label{tab:ok_classification_new}
+%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+%		\hline 
+%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
+%		\hline
+%		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
+%		Simian$_{df}$--NiCad$_{fse13}$ 
+%		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
+%		Simian$_{fse13}$--NiCad$_{df}$   									
+%		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
+%		\hline
+%		Total   & 2  	&   0   & 0   	&  0   &   6676   &   1   & 27  & 6706 \\
+%		\hline
+%	\end{tabular} 
+%\end{table}
 
@@
 
-With our 4 settings, we decided to investigate only 2 settings, Simian$_{\mathrm{\textit{df}}}$, and NiCad$_{\mathrm{\textit{df}}}$, and drop Simian$_{\mathrm{\textit{fse13}}}$ and NiCad$_{\mathrm{\textit{fse13}}}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}.
+With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{fse13}}}$ and NiCad$_{\mathrm{\textit{fse13}}}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}.
 With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.
 
-For Simian$_{\mathrm{\textit{df}}}$, there were 9,393 clone pairs reported by the tool.
+For Simian$_{df}$, there were 9,393 clone pairs reported by the tool.
 Out of 9,393 pairs, 143 of them are the ones found in \textit{ok-}pairs using agreement-based detection.
@@
 Eventually, there were 292 clone pairs remaining for manual investigation.
-For NiCad$_{\mathrm{\textit{df}}}$, we obtained 7,062 clone pairs to look at which is infeasible for manual investigation.
+For NiCad$_{df}$, we obtained 7,062 clone pairs to look at which is infeasible for manual investigation.
 Hence, result filtering was also needed.
@@
 	\centering
-	\caption{Statistics of Simian$_{\mathrm{\textit{df}}}$ and NiCad$_{\mathrm{\textit{df}}}$ clone pairs.}
+	\caption{Statistics of Simian$_{df}$ and NiCad$_{df}$ clone pairs.}
 	\label{tab:classification_indv_stats}
@@
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{\mathrm{\textit{df}}}$}} & 9393 & 143 & 8958 & 292 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 9383 & 140 & 8956 & 287 \\
 		\hline
-		\multirow{1}{*}{\textit{NiCad$_{\mathrm{\textit{df}}}$}} & 7062  & 231 & 6717 & 114 \\
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 7040  & 226 & 6700 & 114 \\
 		\hline
@@
 	\centering
-	\caption{Classification results of 292 Simian$_{\mathrm{\textit{df}}}$ and 114 NiCad$_{\mathrm{\textit{df}}}$ individual unique pairs.
-NiCad$_{\mathrm{\textit{df}}}$* shows the classification without cayenne and iReport.}
+	\caption{Classification results of 292 Simian$_{df}$ and 114 NiCad$_{df}$ individual unique pairs.}
 	\label{tab:classification_indv}
@@
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{\mathrm{\textit{df}}}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
 		\hline
-		\multirow{1}{*}{\textit{NiCad$_{\mathrm{\textit{df}}}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
 		\hline
-		\multirow{1}{*}{\textit{NiCad$_{\mathrm{\textit{df}}}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
-		\hline
+%		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
+%		\hline
 	\end{tabular} 
@@
 		\hline 
-		\textit{good}-pairs & \textit{ok}-pairs & Simian$_{\mathrm{\textit{df}}}$ pairs & NiCad$_{\mathrm{\textit{df}}}$ pairs & Total \\ 
+		\textit{good}-pairs & \textit{ok}-pairs & Simian$_{df}$ pairs & NiCad$_{df}$ pairs & Total \\ 
 		\hline 
@@
 We decided to ignore NiCad results from this analysis due to its failure of clone clustering and renaming on some projects.
-Thus, the 18 projects are the ones that can be analysed by Simian, have newer versions than the versions in Qualitas-\textit{O}, and have code version control system (either git or svn).
-After filtering, there are 141 pairs removed because 45 of them do not have new versions (7 from c-jdbc, 21 from Compiere, 7 from heritrix, and 10 from iReport) and 4 of them we could not find source code with version control (2 from findbugs, 1 from jag, and 1 from jgraphpad).
+Thus, the 39 projects are the ones that can be analysed by Simian, have newer versions than the versions in Qualitas-\textit{O}, and have code version control system (either git or svn).
+%After filtering, there are 141 pairs removed because 45 of them do not have new versions (7 from c-jdbc, 21 from Compiere, 7 from heritrix, and 10 from iReport) and 4 of them we could not find source code with version control (2 from findbugs, 1 from jag, and 1 from jgraphpad).
 Finally there were 134  pairs remaining.
@@
 We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
-The 41 pairs were searched for in 4 new results sets: Simian$_{\mathrm{\textit{df}}}$, Simian$_{\mathrm{\textit{fse13}}}$, NiCad$_{\mathrm{\textit{df}}}$, NiCad$_{\mathrm{\textit{fse13}}}$.
+The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{\mathrm{\textit{fse13}}}$, NiCad$_{df}$, NiCad$_{\mathrm{\textit{fse13}}}$.
 The investigation results are shown in Table \ref{tab:search}.
@@
 		\hline 
-		Simian$_{\mathrm{\textit{df}}}$  &  40 & 1* \\ 
+		Simian$_{df}$  &  40 & 1* \\ 
 		\hline 
@@
 		\hline 
-		NiCad$_{\mathrm{\textit{df}}}$  & 17 & 24 \\ 
+		NiCad$_{df}$  & 17 & 24 \\ 
 		\hline 

### 2016-09-29 latex/stackoverflow.tex
Latest update of the report

@@
 \begin{itemize}
-	\item \textbf{RQ1 (online code clone):} \textit{can we find any reused source code fragments between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened or has been happening and at what scale.
-	\item \textbf{RQ2 (Direction of online code clone flow):} \textit{in which direction source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
+	\item \textbf{RQ1 (online code clone):} \textit{How source code are reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale.
+	\item \textbf{RQ2 (flow of online code clone):} \textit{what are the directions source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
 Is it from Q\&A site to open source projects, or the other way around, or both?
-	\item \textbf{RQ3 (Online code clone classification):} \textit{what are categories of online code clone?} How and why did these online code clone happen?
-	\item \textbf{RQ4 (Effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
+	\item \textbf{RQ3 (classification of online code clone):} \textit{How and why did these online code clone happen?} Can we categorise them?
+	\item \textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
 \end{itemize}
 
-\section*{Dataset}
+\section*{Experimental Setup}
+
+\subsection*{Dataset}
 In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{QualitasCorpus}.
-However, we found that \textit{eclipse} project does not contain source code so we removed it from the dataset resulting in totally 63 projects being analysed.
+However, we found that \textit{eclipse} project does not contain source code so we removed it from the dataset.
+This results in totally 63 projects being analysed.
 The details of the 63 Qualitas projects are listed in Table \ref{t:new_and_old}.
 
-\section*{Clone Detectors}
-We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info}
+\subsection*{Clone Detectors}
+We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info about clone detection tools in general and more details of these two tools}
 
-\section*{Experimental Results}
+\section*{Results}
 The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below.
@@
 
-\section*{Agreed Clone Pairs}
+\subsection{Agreement based clone pairs vs. Non-agreement based clone pairs}
 
-The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria are listed in  Table \ref{t_agreed_good_clone_pairs}.
-We use the threshold of 0.7 for both \textit{good}-match and \textit{ok}-match.
+The agreement-based clone pairs are the ones discovered using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria as listed in  Table \ref{t_agreed_good_clone_pairs}.
+Non-agreement based clone pairs are the ones that are solely reported by a single tool.
+The agreement-based pairs provide higher confident that they are real clones than the non-agreement based ones.
+
+\subsection{Agreement based clone pairs}
+
+For agreement-based clone pairs, we use the threshold of 0.7 for both \textit{good}-match and \textit{ok}-match.
 Visualisation of \textit{good}-match common clone pairs between sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}.
-There are 1,406 unique \textit{good}-match pairs.
-The \textit{ok}-match subsumes the \textit{good}-match resulting in totally 10,879 common clone pairs (Figure \ref{fig:venn4_orig_ok}).
+There are 1,357 unique \textit{good}-match pairs.
+The \textit{ok}-match subsumes the \textit{good}-match resulting in totally 10,139 common clone pairs (Figure \ref{fig:venn4_orig_ok}).
 
@@
 So these projects are also missing from agreed clone pairs.
-\FIXME{Report the errors.}
+\FIXME{Report the errors to NiCad creator.}
 
-We are interested in discovering reused code in the latest versions of Qualitas projects.
+\FIXME{Maybe no longer needed?} We are interested in discovering reused code in the latest versions of Qualitas projects.
 So, we downloaded the newest release of each project and found 44 of them having newer updates.
@@
 	\centering
-	\caption{Distribution of clone pairs reported based on \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria}
+	\caption{Distribution of agreement-based clone pairs reported using Bellon's criteria}
 	\label{t_agreed_good_clone_pairs}
@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{venn4_pairs_good}
+		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
 		\captionof{figure}{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok}
+		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
 		\captionof{figure}{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
@@
 
-\section*{Manual Investigation}
+\subsection{Manual investigation of agreement-based clone pairs}
+%\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
 
-\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
-
-\subsubsection{Qualitas-\textit{O} (v. 2013-09-01r)}
+%\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
 
@@
 
-\subsection{Investigation of Simian and NiCad clone pairs}
-\subsubsection{Qualitas-\textit{O} (v. 2013-09-01r)}
+\subsection{Non-agreement based clone pairs}
 In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
@@
 
-For Simian$_{df}$, there were 9,393 clone pairs reported by the tool.
-Out of 9,393 pairs, 143 of them are the ones found in \textit{ok-}pairs using agreement-based detection.
+For Simian$_{df}$, there were 9,383 clone pairs reported by the tool.
+Out of 9,383 pairs, 140 of them are the ones found in \textit{ok-}pairs using agreement-based detection.
 We filtered the results further by removing false positives such as similar equals(), hashCode() methods, getters and setters out by using regular expression.
-We managed to remove 8,958 pairs using this method.
-Eventually, there were 292 clone pairs remaining for manual investigation.
-For NiCad$_{df}$, we obtained 7,062 clone pairs to look at which is infeasible for manual investigation.
+We managed to remove 8,956 pairs using this method.
+Eventually, there were 287 clone pairs remaining for manual investigation.
+For NiCad$_{df}$, we obtained 7,040 clone pairs to look at which is infeasible for manual investigation.
 Hence, result filtering was also needed.
@@
 So we decided to filter the results by selecting pairs that pass stricter clone criteria with $\mathrm{UPI} = 0.2$.
-By reducing the UPI to 0.2, there were totally 171 pairs left.
-Out of 171, 57 are \textit{ok}-pairs and 114 are remaining pairs for manual check (18 pairs are from \textit{cayenne} and \textit{iReport} that could not be analysed using UPI = 0.3).
+By reducing the UPI to 0.2, there were totally 166 pairs left.
+Out of 166, 52 are \textit{ok}-pairs and 114 are remaining pairs for manual check (18 pairs are from \textit{cayenne} and \textit{iReport} that could not be analysed using UPI = 0.3).
 The statistics of the clones and classification results are reported in Table \ref{tab:classification_indv_stats} and \ref{tab:classification_indv}.
@@
 
+\subsection{Manual investigation of non-agreement based clone pairs}
+%\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
+We performed manual investigation of the clone pairs reported by Simian$_{df}$ and NiCad$_{df}$ in the same way as the agreement-based clone pairs.
+The results of the manual investigation is reported in Table \ref{tab:classification_indv}.
+
 \begin{table}[H]
@@
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 89 & 7 & \textbf{133} & 68 & 57 & 23 & 13 & 10 & 133 & \textbf{159} & 39 & 69 & 23 & \textbf{287} & 103 & 121 & 31 \\
 		\hline
@@
 
+\newpage
+\subsection{Summary of true online clone pairs}
 \begin{table}[H]
@@
 	\caption{Numbers of true online clone pairs (A+A'+B+C) found by manual investigation}
-	\label{tab:classification_indv_summary}
-	\begin{tabular}{r|r|r|r|r}
+	\label{tab:classification_true_pairs_summary}
+	\begin{tabular}{l|r|r|r|r|r}
 		\hline 
-		\textit{good}-pairs & \textit{ok}-pairs & Simian$_{df}$ pairs & NiCad$_{df}$ pairs & Total \\ 
+		Tool & A & A' & B & C & Total \\
 		\hline
-		5 & 52 & 133 & 9 & 183 \\
+		\textit{good}-pairs & 1 & 0 & 1 & 3 & 5 \\
+		\textit{ok}-pairs & 8 & 0 & 23 & 8 & 39 \\
+		Simian$_{df}$ pairs & 35 & 0 & 89 & 7 & 131 \\
+		NiCad$_{df}$ pairs & 4 & 0 & 5 & 0 & 9 \\
+		\hline 
+		Total & 48 & 0 & 118 & 18 & 184 \\
 		\hline
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=1\linewidth]{Sankey_proj}
+	\caption{Relationships between 184 true online code clone found between Stackoverflow and Qualitas projects}
+	\label{fig:sankey}
+\end{figure}
+
 %\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
 
-\subsection{Evolution of clone pairs from Qualitas-\textit{O} to Qualitas-\textit{N}}
-After located and classified all the online clone pairs, we are now interested in analysing the evolution of true online clone pairs.
-This is to answer RQ4.
-In this setting, we only focus on 39 projects in the X region in Figure \ref{fig:n+v+g}.
-We decided to ignore NiCad results from this analysis due to its failure of clone clustering and renaming on some projects.
+\subsection{Effects of online code clone}
+
+\subsection*{Issue~1:~outdated online code}
+After located and classified all the online clone pairs, we are now interested in analysing the true online clone pairs that are copied in the direction of Q $\rightarrow$ S (class-\textit{A} online clone pairs) in Table \ref{tab:classification_true_pairs_summary} which results in 48 pairs selected.
+We restricted it further to only the ones having versioning system so we can trace changes made to these clone pairs.
+Fortunately, all of the pairs were from projects with either git or svn so we did not remove any pair from this set.
+
+Our intuition behind his issue comes from a situation where a piece of code has been copied from a Qualitas project and posted on Stackoverflow.
+Later, that piece of code has been modified further to accommodate changes in the projects (or any other reasons).
+However, even the code in Qualitas project is already updated, the one posted on Stackoverflow is not changed.
+This results in outdated online code which can cause problems when programmers copy and use it in their projects.
+
+%We decided to ignore NiCad results from this analysis due to its failure of clone clustering and renaming on some projects.
 Thus, the 39 projects are the ones that can be analysed by Simian, have newer versions than the versions in Qualitas-\textit{O}, and have code version control system (either git or svn).
@@
 %We are interested in clone pairs that were changed after they appeared on Stackoverflow.
+\subsection*{Issue~2:~software licensing violation}
 
+\newpage
 \begin{table}[H]
@@
 \end{table}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=1\linewidth]{Sankey_proj}
-	\caption{Relationships between 199 true online code clone found between Stackoverflow and Qualitas projects}
-	\label{fig:sankey}
-\end{figure}
-
-\newpage
 

### 2016-09-30 latex-acm/cloneoverflow.tex
Added ACM-style paper

--- 2016-09-29 latex/stackoverflow.tex
@@
-% This is LLNCS.DOC the documentation file of
-% the LaTeX2e class from Springer-Verlag
-% for Lecture Notes in Computer Science, version 2.4
-%\documentclass{llncs}
-\documentclass{IEEEtran}
+\documentclass{sig-alternate-05-2015}
 \usepackage{graphicx}
@@
 
-\def\tablename{Table}
-
-\usepackage[justification=centering]{caption}
-
 \newcommand{\squeezeup}{\vspace{-2.5mm}}
 \newcommand\FIXME[1]{\textbf{FIXME: #1}}
-%
+
 \begin{document}
 
-\onecolumn
+% Copyright
+\setcopyright{acmcopyright}
+%\setcopyright{acmlicensed}
+%\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
 
-\title{Clone Overflow: \\
-	An empirical study of online code clone}
+%% DOI
+%\doi{10.475/123_4}
+
+%% ISBN
+%\isbn{123-4567-24-567/08/06}
+
+%Conference
+\conferenceinfo{MSR '17}{May 20--21, 2017, Buenos Aires, Argentina}
+
+%\acmPrice{\$15.00}
+
+%
+% --- Author Metadata here ---
+%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
+%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+% --- End of Author Metadata ---
+
+\title{Clone Overflow: \\ Code Reuse in Online Corpora and Its Effects}
+
+\numberofauthors{1}
+\author{
+	\alignauthor
+	Chaiyong Ragkhitwetsagul, Jens Krinke \\
+	\affaddr{University College London}\\
+	\affaddr{London, UK}
+}
+
 \maketitle
+\begin{abstract}
+This paper provides a sample of a \LaTeX\ document which conforms,
+somewhat loosely, to the formatting guidelines for
+ACM SIG Proceedings. It is an {\em alternate} style which produces
+a {\em tighter-looking} paper and was designed in response to
+concerns expressed, by authors, over page-budgets.
+It complements the document \textit{Author's (Alternate) Guide to
+Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
+This source file has been written with the intention of being
+compiled under \LaTeX$2_\epsilon$\ and BibTeX.
 
-\section*{Research Questions}
-\begin{itemize}
-	\item \textbf{RQ1 (online code clone):} \textit{How source code are reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale.
-	\item \textbf{RQ2 (flow of online code clone):} \textit{what are the directions source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
+The developers have tried to include every imaginable sort
+of ``bells and whistles", such as a subtitle, footnotes on
+title, subtitle and authors, as well as in the text, and
+every optional component (e.g. Acknowledgments, Additional
+Authors, Appendices), not to mention examples of
+equations, theorems, tables and figures.
+
+To make best use of this sample document, run it through \LaTeX\
+and BibTeX, and compare this source code with the printed
+output produced by the dvi file. A compiled PDF version
+is available on the web page to help you with the
+`look and feel'.
+\end{abstract}
+
+\section{Introduction}
+
+\section{Research Questions}
+\textbf{RQ1 (online code clone):} \textit{How source code are reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale.
+\newline
+\textbf{RQ2 (flow of online code clone):} \textit{what are the directions source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
 Is it from Q\&A site to open source projects, or the other way around, or both?
-	\item \textbf{RQ3 (classification of online code clone):} \textit{How and why did these online code clone happen?} Can we categorise them?
-	\item \textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
-\end{itemize}
+\newline
+\textbf{RQ3 (classification of online code clone):} \textit{How and why did these online code clone happen?} Can we categorise them? \newline
+\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
 
-\section*{Experimental Setup}
+\section{Experimental Setup}
 
-\subsection*{Dataset}
+\subsection{Dataset}
 In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{QualitasCorpus}.
@@
 
-\subsection*{Clone Detectors}
+\subsection{Code Similarity Measurement}
 We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info about clone detection tools in general and more details of these two tools}
 
-\section*{Results}
+\section{Results}
 The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below.
@@
 	\centering
-	\caption{Qualitas-\textit{O} (2013-09-01r): Simian and NiCad clone results}
+	\caption{Qualitas-\textit{O} (2013-09-01r) clone results}
 	\label{t_simian_raw_results}
-	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
+%	\resizebox{\columnwidth}{!}{%
+	\small
+		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
 			\hline
-		\multirow{4}{*}{Statistics} 
-		& \multicolumn{4}{c|}{Simian Default settings} 
-		& \multicolumn{4}{c|}{Simian FSE'13 settings}
-		& \multicolumn{4}{c|}{NiCad Default settings} 
-		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} 
-		& \multicolumn{4}{c|}{threshold=6} 
-		& \multicolumn{4}{c|}{threshold=5}  
-		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
-		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\ 
-		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
-		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
-		& \multicolumn{4}{c|}{rename=none,abstract=none} 
-		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
+			\multirow{3}{*}{Statistics} 
+			& \multicolumn{3}{c|}{Simian Default settings} 
+			& \multicolumn{3}{c|}{Simian FSE'13 settings}
+			& \multicolumn{3}{c|}{NiCad Default settings} 
+			& \multicolumn{3}{c}{NiCad FSE'13 settings} \\ \cline{2-13} 
+			& \multicolumn{3}{c|}{792 fragments} 
+			& \multicolumn{3}{c|}{1229 fragments}  
+			& \multicolumn{3}{c|}{1141 fragments} 
+			& \multicolumn{3}{c}{12400 fragments} \\ \cline{2-13}
+			%& \multicolumn{3}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
+			%& \multicolumn{3}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
+			%& \multicolumn{3}{c|}{rename=none,abstract=none} 
+			%& \multicolumn{3}{c}{rename=blind,abstract=literal} \\ %\cline{2-17}  
+			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
 			\hline
 			%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-		Total  	& 654 	& 24,929 	& -- 	& --	& 1,175 & 16,957,362 & --	& --	& 985 	& 105,118 	& --	& --	& 12,084	& 113,557,298 & --		& -- \\
-		Mean  	& --	& 38 		& 7.54 	& 0.27 	& --	& 14,444 	& 4.80 	& 0.28 	& --	& 107 		& 9.52 	& 0.25 	& -- 		& 9,397 	& 5.21 		& 0.20 \\
-		Std Dev. & --  	& 87 		& 3.21 	& 0.22 	& --	& 281,747 	& 1.22 	& 0.18 	& --	& 198 		& 3.07 	& 0.18 	& --		& 12,098 	& 1.73 		& 0.16 \\
-		Max  	& --	& 551 		& 49.00 & 0.94 	& --	& 9,599,676 & 18.00 & 0.89 	& --	& 1,792 	& 39.00 & 0.80 	& --		& 227,077 	& 44.00 	& 0.86 \\
-		Min  	& --	& 1 		& 5.00 	& 0.01 	& --	& 1 		& 4.00 	& 0.02 	& --	& 1 		& 7.00 	& 0.02 	& --		& 1 		& 3.00 		& 0.01 \\
-		Median  & --	& 3 		& 7.00 	& 0.23 	& --	& 22 		& 5.00 & 0.24 	& --	& 15 		& 8.00 	& 0.19 	& --		& 6,105 	& 5.00 		& 0.15 \\
-		Mode  	& --	& 1 		& 7.00 	& 0.25 	& --	& 1 		& 4.00 	& 0.50 	& --	& 1 		& 8.00 	& 0.53 	& --		& 1 		& 4.00 		& 0.33 \\
+			Total & 24,929 & -- & -- & 16,957,362 & --	& -- & 105,118 	& -- & -- & 113,557,298 & -- & -- \\
+			Mean & 38 & 7.54 & 0.27 & 14,444 & 4.80 & 0.28 & 107 & 9.52 & 0.25 & 9,397 & 5.21 & 0.20 \\
+			Std Dev. & 87 & 3.21 & 0.22 & 281,747 & 1.22 & 0.18 & 198 & 3.07 & 0.18 & 12,098 & 1.73 & 0.16 \\
+			Max  & 551 & 49.00 & 0.94 & 9,599,676 & 18.00 & 0.89 & 1,792 & 39.00 & 0.80 & 227,077 & 44.00 & 0.86 \\
+			Min  & 1 & 5.00 & 0.01 & 1 & 4.00 & 0.02 & 1 & 7.00 & 0.02 & 1 & 3.00 & 0.01 \\
+			Median  & 3 & 7.00 & 0.23 & 22 & 5.00 & 0.24 & 15 & 8.00 & 0.19 & 6,105 & 5.00 	& 0.15 \\
+			Mode  & 1 & 7.00 & 0.25 & 1 & 4.00 & 0.50 & 1 & 8.00 & 0.53 & 1 & 4.00 & 0.33 \\
 			\hline
 		\end{tabular} %
-}
+%	}
 \end{table*}
 
-\begin{table*}[h]
+\begin{table*}
 	\centering
-	\caption{Qualitas-\textit{N} (2016-08-05): Simian and NiCad clone results (44 new + 19 old Qualitas projects)}
+	\caption{Qualitas-\textit{N} (2016-08-05) clone results (44 new Qualitas projects)}
 	\label{t_simian_raw_results}
-	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
+%	\resizebox{\columnwidth}{!}{%
+	\small
+		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
 			\hline
-		\multirow{4}{*}{Statistics} 
-		& \multicolumn{4}{c|}{Simian Default settings} 
-		& \multicolumn{4}{c|}{Simian FSE'13 settings} 
-		& \multicolumn{4}{c|}{NiCad Default settings} 
-		& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
-		& \multicolumn{4}{c|}{threshold=6} 
-		& \multicolumn{4}{c|}{threshold=5} 
-		& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
-		& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
-		& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
-		& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
-		& \multicolumn{4}{c|}{rename=none,abstract=none} 
-		& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  %  & \multicolumn{4}{c}{iId} \\
-		% \hline
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-		& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+			\multirow{3}{*}{Statistics} 
+			& \multicolumn{3}{c|}{Simian Default settings} 
+			& \multicolumn{3}{c|}{Simian FSE'13 settings} 
+			& \multicolumn{3}{c|}{NiCad Default settings} 
+			& \multicolumn{3}{c}{NiCad FSE'13 settings} \\ \cline{2-13} 
+			& \multicolumn{3}{c|}{707 fragments} 
+			& \multicolumn{3}{c|}{1205 fragments} 
+			& \multicolumn{3}{c|}{1068 fragments} 
+			& \multicolumn{3}{c}{10231 fragments} \\  \cline{2-13}
+			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
 			\hline
-		Total 	& 792 & 61,268 & -- & -- 	& 1,229 & 25,725,857 & -- & -- & 1,141 	& 666,140 & -- 	& -- 	&  12,400 	& 615,263,639 & -- 	& --  \\ 
-		Mean 	& -- & 78 & 7.31 & 0.26 	& -- & 20,932 & 4.86 & 0.28 & -- 	& 584 	& 9.49 	& 0.25 	& -- 	& 49,618 	& 5.25 	& 0.20 \\ 
-		Std Dev. & -- & 208 & 2.70 & 0.21 	& -- & 382,015 & 1.30 & 0.19 & -- 	& 1,488 & 3.11 	& 0.18 	& -- 	& 62,659 	& 2.80 	& 0.16 \\ 
-		Max 	& -- & 1,300 & 49.00 & 0.94 & -- & 13,202,807 & 21.00 & 0.92 & -- 	& 10,980 & 39.00 	& 0.84 	& -- 	& 1,319,242 & 250.00	& 0.96 \\
-		Min 	& -- & 1 & 5.00 & 0.01 		& -- & 1 & 4.00 & 0.12 & -- 	& 1 	& 7.00 	& 0.02 	& -- 	& 1 		& 2.00 	& 0.01 \\ 
-		Median 	& -- & 2 & 7.00 & 0.20 		& -- & 21 & 5.00 & 0.25 & -- 	& 25 	& 8.00 	& 0.19 	& -- 	& 52,329 	& 5.00 	& 0.16 \\ 
-		Mode 	& -- & 1 & 7.00 & 0.33 		& -- & 1 & 4.00 & 0.50 & -- 	& 1 	& 8.00 	& 0.67 	& -- 	& 1 		& 4.00 	& 0.33 \\ 
+			Total & 60,536 & -- 	& -- 	& 22,797,190 & -- 	& --  & 648,165 & -- & -- & 573,438,528 & -- & -- \\ 
+			Mean 	& 86 	& 7.37 	& 0.26 	& 18,919 	& 4.85 	& 0.28 & 607 & 9.39 & 0.25 & 47663 & 5.22 & 0.20 \\
+			Std Dev. & 217 	& 2.22 	& 0.21 	& 326,588 	& 1.31 	& 0.19 & 1,499 & 2.98 & 1.81 & 58,833 & 2.77 & 0.15 \\
+			Max 	& 1,298 & 32.00 & 0.94 & 11,127,286 & 21.00 & 0.92 & 10,550 & 36.00 & 0.84 & 1,246,598 & 250 & 0.96 \\
+			Min 	& 1 	& 5.00 	& 0.01 	& 1 & 4.00 	& 0.02 & 1 & 7 & 0.02 & 1 & 2.00 & 0.01\\
+			Median 	& 2 & 7.00 	& 0.21 	& 20		& 5.00 	& 0.25 & 33 & 8 & 0.19 & 52,077 & 5.00 & 0.15 \\
+			Mode & 1 	& 7.00 	& 0.25 	& 1 		& 4.00 	& 0.50 & 1 & 8 & 0.67 & 1 & 4.00 & 0.33 \\
 			\hline
 		\end{tabular} %
-}
-\end{table*}
-%
-\begin{table*}[h]
-	\centering
-	\caption{Qualitas-\textit{N} (2016-08-05): Simian and NiCad clone results (only 44 new Qualitas projects)}
-	\label{t_simian_raw_results}
-	\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r}
-			\hline
-			\multirow{4}{*}{Statistics} 
-			& \multicolumn{4}{c|}{Simian Default settings} 
-			& \multicolumn{4}{c|}{Simian FSE'13 settings} 
-			& \multicolumn{4}{c|}{NiCad Default settings} 
-			& \multicolumn{4}{c}{NiCad FSE'13 settings} \\ \cline{2-17} % & \multicolumn{4}{c}{CloPlag settings} \\
-			& \multicolumn{4}{c|}{threshold=6} 
-			& \multicolumn{4}{c|}{threshold=5} 
-			& \multicolumn{4}{c|}{threshold=6, UPI=0.30} 
-			& \multicolumn{4}{c}{threshold=5, UPI=0.2} \\  % & \multicolumn{4}{c}{threshold=5} \\
-			& \multicolumn{4}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
-			& \multicolumn{4}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
-			& \multicolumn{4}{c|}{rename=none,abstract=none} 
-			& \multicolumn{4}{c}{rename=blind,abstract=literal} \\\cline{2-17}  
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-			& Frag.~ & $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
-			\hline
-			Total 	& 707 	& 60,536 & -- 	& -- 	&  1,205 & 22,797,190 & -- 	& --  & 1,068 & 648,165 & -- & -- & 10,231 & 573,438,528 & -- & -- \\ 
-			Mean 	& -- 	& 86 	& 7.37 	& 0.26 	& -- 	& 18,919 	& 4.85 	& 0.28 & -- & 607 & 9.39 & 0.25 & -- & 47663 & 5.22 & 0.20 \\
-			Std Dev. & -- 	& 217 	& 2.22 	& 0.21 	& -- 	& 326,588 	& 1.31 	& 0.19 & -- & 1,499 & 2.98 & 1.81 & -- & 58,833 & 2.77 & 0.15 \\
-			Max 	& -- 	& 1,298 & 32.00 & 0.94 	& -- 	& 11,127,286 & 21.00 & 0.92 & -- & 10,550 & 36.00 & 0.84 & -- & 1,246,598 & 250 & 0.96 \\
-			Min 	& -- 	& 1 	& 5.00 	& 0.01 	& -- 	& 1 		& 4.00 	& 0.02 & -- & 1 & 7 & 0.02 & -- & 1 & 2.00 & 0.01\\
-			Median 	& -- 	& 2 	& 7.00 	& 0.21 	& -- 	& 20		& 5.00 	& 0.25 & -- & 33 & 8 & 0.19 & -- & 52,077 & 5.00 & 0.15 \\
-			Mode 	& -- 	& 1 	& 7.00 	& 0.25 	& -- 	& 1 		& 4.00 	& 0.50 & -- & 1 & 8 & 0.67 & -- & 1 & 4.00 & 0.33 \\
-			\hline
-		\end{tabular} %
-	}
+	%}
 \end{table*}
 
-\begin{table}[h]
+\begin{table*}
 	\centering
@@
 	\label{t:new_and_old}
-	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|c|c|p{5cm}|p{3cm}}
+%	\resizebox{\columnwidth}{!}{%
+	\small
+		\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
 			\hline 
@@
 			\hline
-	antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD License \\
-	apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache License, v.2.0 \\
-	argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse Public License v.1.0 \\
-	artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GNU General Public License v.2.0 \\
-	aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse Public License 1.0 \\
+			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD \\
+			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 \\
+			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 \\
+			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 \\
+			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 \\
 			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) \\
-	batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache License, v.2.0 \\
-	c-jdbc & 2.0.2 & - & 16/09/2005 & - & GNU Lesser General Public License, v.2.1 \\
-	castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache License, v.2.0 \\
-	cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache License, v.2.0 \\
-	checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GNU Lesser General Public License, v.2.1 \& Apache License, v.2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
-	cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GNU General Public License v.2.0  \\
+			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 \\
+			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 \\
+			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 \\
+			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 \\
+			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GLGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
+			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  \\
 			colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
-	columba & 1.4 & - & 20/04/2007 & - & Mozilla Public License 1.1  \\
-	commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache License, v.2.0 \\
-	compiere & 330 & - & - & - & GNU General Public License v.2.0 & No longer OSS \\
-	db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache License, v.2.0 \\
-	displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT License \\
-	drawswf & 1.2.9 & - & 02/04/2013 & - & GNU General Public License v.2.0 \\
-	drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD License & Build to see version? \\
-	exoportal & ??? & ??? &  & git & GNU Lesser General Public License v.3.0 \& proprietary & Too many new projects \\
-	emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common Public License 1.0 \\
-	findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GNU Lesser General Public License, v.2.0 \\
-	fit-java & 1.1 & - & 04/06/2013 & - & GNU General Public License v.2.0 \\
-	fitlibrary & 20100806 & ??? & 29/07/2014 & git & GNU General Public License v.2.0 \\
-	freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GNU General Public License v.2.0 &  \\
-	freecs & 1.3.20100406 & - & 22/04/2013 & - & GNU General Public License v.3.0 &   \\
-	freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GNU General Public License v.2.0+ &  \\
-	galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GNU General Public License v.2.0 \\
-	ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GNU General Public License v.3.0 &  \\
-	geotools & 2.7-M3 & 16 & 27/09/2016 & git & GNU Lesser General Public License, v.2.0 \\
-	hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache License, v.2.0 \\
-	heritrix & 1.14.4 & - & 05/06/2013 & - & GNU Lesser General Public License, v.2.1 \\
-	hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GNU Lesser General Public License, v.2.1+ \\
-	hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD License \\
-	htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache License, v.2.0 \\
-	ireport & 3.7.5 & - & 28/05/2014 & - & Affero GNU Public License, v.3.0 \\
-	itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GNU Public License, v.3.0 \\
-	informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GNU Lesser General Public License, v.2.1 \& Apache Software License, v.1.1 \\
-	ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GNU General Public License v.2.0 \\
-	jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GNU General Public License v.2.0 \\
-	joggplayer & 114s & - &  15/04/2013 & - & GNU General Public License v.2.0 \\
-	jag & 6.1 & 6.2 & 08/04/2013  & - & GNU General Public License v.2.0 \& BSD License & BSD License is for libraries. \\
-	james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache License, v.2.0 \\
-	jasml & 0.10 & - & 08/03/2013 & - & Apache Software License \\
-	jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GNU Lesser General Public License, v.3.0 &  \\
+			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  \\
+			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 \\
+			compiere & 330 & - & - & - & GPL 2.0 & No longer OSS \\
+			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 \\
+			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  \\
+			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 \\
+			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
+			exoportal & ??? & ??? &  & git & GLGPL 3.0 \& proprietary & Too many new projects \\
+			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 \\
+			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 \\
+			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 \\
+			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 \\
+			freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GPL 2.0 &  \\
+			freecs & 1.3.20100406 & - & 22/04/2013 & - & GPL 3.0 &   \\
+			freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GPL 2.0+ &  \\
+			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 \\
+			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
+			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 \\
+			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 \\
+			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 \\
+			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ \\
+			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  \\
+			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 \\
+			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 \\
+			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 \\
+			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 \\
+			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 \\
+			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 \\
+			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 \\
+			jag & 6.1 & 6.2 & 08/04/2013  & - & GPL 2.0 \& BSD  & BSD  is for libraries. \\
+			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 \\
+			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  \\
+			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0 &  \\
 			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) \\
-	jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GNU Lesser General Public License, v.2.1 & Renamed to Wildfly. \\
-	jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GNU Lesser General Public License, v.2.1+ &  \\
-	jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GNU General Public License v.2.0 &  \\
-	jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache License, v.2.0 \\
-	jext & 5.0 & - & 18/08/2004 & - & GNU General Public License v.2.0 &  \\
-	jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GNU Lesser General Public License, v.2.0 &   \\
-	jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph License) \\
-	jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GNU General Public License  \& GNU Lesser General Public License (derivatives) \\
-	jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GNU Lesser General Public License, v.2.1 \& Eclipse Public License, v.1.0 \\
-	jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache License, v.2.0 \\
-	jmoney & 0.4.4 & ??? & 27/12/2015 & git & GNU General Public License v.2.0 &  \\
-	jparse & 0.96 & - & 29/07/2004 & - & GNU Lesser General Public License, v.2.1 \\
-	jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache License, v.2.0 \\
-	junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse Public License, v.1.0 \\
-	shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GNU Lesser General Public License, v.2.0 &  \\
-	vuze & 4812 & 5730 & 23/09/2016 & svn & GNU General Public License v.2.0 & \\
+			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GLGPL 2.1 & Renamed to Wildfly. \\
+			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GLGPL 2.1+ &  \\
+			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
+			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 \\
+			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
+			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0 &   \\
+			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) \\
+			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) \\
+			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 \\
+			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 \\
+			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
+			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 \\
+			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 \\
+			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 \\
+			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GLGPL 2.0 &  \\
+			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
 			\hline 
 		\end{tabular} %
-}
-\end{table}
+%	}
+\end{table*}
 
-\newpage
-
-\subsection{Agreement based clone pairs vs. Non-agreement based clone pairs}
+\subsection{Agreement based clone pairs vs. Non agreement based clone pairs}
 
@@
 
-\begin{table}[H]
+\begin{table*}
 	\centering
@@
 	\label{tab:projects_missing}
+	\small
 	\begin{tabular}{r|r|r|r|r|r}
@@
 		\hline
-		Simian$_{\textrm{\textit{df}}}$/Simian$_{fse13}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ & Simian$_{\textrm{\textit{df}}}$/Simian$_{fse13}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ \\ \hline
+		Simian$_{\textrm{\textit{df/fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ & Simian$_{\textrm{\textit{df/fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ \\ \hline
 		63	& 57 & 46 & 44 & 40 & 34 \\
@@
 	\end{tabular}
-\end{table}
+\end{table*}
 
-\begin{table}[H]
+\begin{table}
 	\centering
@@
 	\label{t_agreed_good_clone_pairs}
-	\begin{tabular}{l|l|r|r|r|r}
+	\begin{tabular}{l|l|r|r}
 		\hline
-		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c|}{Qualitas-\textit{O}} & \multicolumn{2}{c}{Qualitas-\textit{N}} \\
+		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{Qualitas-\textit{O}} \\
 		\hline
-		Simian & NiCad & \textit{good}-match & \textit{ok}-match & \textit{good}-match & \textit{ok}-match \\
+		Simian & NiCad & \textit{good}-match & \textit{ok}-match \\
 		%\hline
@@
 		\hline
-		\textit{default} & \textit{default} & 9 	& 473 	& 0 & 6,604 \\ 
-		\textit{default} & \textit{fse13} 	& 12 	& 353 	& 0 & 79 \\ 
-		\textit{fse13} 	& \textit{default} 	& 7 	& 60 	& 0 & 23 \\
-		\textit{fse13} 	& \textit{fse13} 	& 1,338 & 9528 & 1,170 & 6,690 \\ 
+		\textit{default} & \textit{default} & 9 	& 473 \\ 
+		\textit{default} & \textit{fse13} 	& 12 	& 353 \\ 
+		\textit{fse13} 	& \textit{default} 	& 7 	& 60 \\
+		\textit{fse13} 	& \textit{fse13} 	& 1,338 & 9528 \\ 
 		\hline
-		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 & 1,170 & 13,396 \\
-		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 & 1,170 & 13,386 \\
+		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 \\
+		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 \\
 		\hline
@@
 
-\begin{figure}
+\begin{figure*}
 	\centering
@@
 		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
-		\captionof{figure}{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
+		\caption{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
 		\label{fig:venn4_orig_good}
@@
 		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
-		\captionof{figure}{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
+		\caption{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
 		\label{fig:venn4_orig_ok}
 	\end{minipage}
-\end{figure}
-%
-%\begin{figure}
-%	\centering
-%	\begin{minipage}{.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_new}
-%		\captionof{figure}{Qualitas-\textit{N} \textit{good}-match(0.7) pairs}
-%		\label{fig:venn4_new_good}
-%	\end{minipage}%
-%	\begin{minipage}{.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_new}
-%		\captionof{figure}{Qualitas-\textit{N} \textit{ok}-match(0.7) pairs}
-%		\label{fig:venn4_new_ok}
-%	\end{minipage}
-%\end{figure}
+\end{figure*}
 
@@
 	\end{tabular} 
-\end{table}
+\end{table*}
 
@@
 	\label{tab:classification_good_o}
+	\small
 	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
@@
 	\end{tabular} 
-\end{table}
+\end{table*}
 
-%\begin{table}[H]
+%\begin{table}
 %	\centering
@@
 	\label{tab:good_classification}
+	\small
 	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
@@
 	\end{tabular} 
-\end{table}
+\end{table*}
 
-\begin{table}[H]
+\begin{table*}
 	\centering
@@
 	\label{tab:ok_classification}
+	\small
 	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
@@
 %
-%\begin{table}[H]
+%\begin{table}
 %	\centering
@@
 
-%\begin{table}[H]
+%\begin{table}
 %	\centering
@@
 	\label{fig:n+v+g}
-\end{figure}
+\end{figure*}
 
@@
 	\label{tab:classification_indv_stats}
+	\small
 	\begin{tabular}{l|r|r|r|r}
@@
 	\label{tab:classification_indv}
+	\small
 	\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|}
@@
 	\end{tabular} 
-\end{table}
+\end{table*}
 
-\newpage
-\subsection{Summary of true online clone pairs}
+%\subsection{Summary of true online clone pairs}
 \begin{table}[H]
@@
 
-\begin{figure}[H]
+\begin{figure*}
 	\centering
@@
 	\label{fig:sankey}
-\end{figure}
+\end{figure*}
 
@@
 
-\subsection{Effects of online code clone}
+\section{Effects of online code clone}
 
-\subsection*{Issue~1:~outdated online code}
+\subsection{Issue~1:~outdated online code}
 After located and classified all the online clone pairs, we are now interested in analysing the true online clone pairs that are copied in the direction of Q $\rightarrow$ S (class-\textit{A} online clone pairs) in Table \ref{tab:classification_true_pairs_summary} which results in 48 pairs selected.
@@
 %We are interested in clone pairs that were changed after they appeared on Stackoverflow.
-\subsection*{Issue~2:~software licensing violation}
+\subsection{Issue~2:~software licensing violation}
+\FIXME{Add more content here}
 
-\newpage
-\begin{table}[H]
-	\centering
-	\caption{Projects that do not have resutls in Qualitas-\textit{N} but do have results in Qualitas-\textit{O}}
-	\label{tab:tp_pairs}
-	\begin{tabular}{l|r|r|r|r|p{6cm}}
-	\hline
-	\multirow{2}{*}{Project} & \multicolumn{4}{c|}{Qualitas-\textit{O}} & \multicolumn{1}{c}{Qualitas-\textit{N}} \\ \cline{2-6}
-			& \textit{good}-match & TP & \textit{ok}-match & TP & Reason of missing results \\
-	\hline
-	%& \multicolumn{5}{c}{\textit{Not included in the latest version}} \\
-	%\hline
-	jboss		& 2 	& 	0	& 63 	& 1 & NiCad's failure \\
-	db-derby 	& 0 	&	0	& 0		& 0 & NiCad's failure \\
-	hadoop		& 191 	& 1 	& 2432 	& 5 & NiCad's failure \\
-	hibernate 	& 19 	& 	0	& 11 	& 0 & NiCad's failure \\
-	ArgoUML		& 0		& 	0	& 0		& 0 & NiCad's failure \\
-	checkstyle	& 0		&	0	& 0		& 0 & NiCad's failure \\
-	cayenne		& 0		& 	0	& 0		& 0 & NiCad's failure \\
-	geotools	& 0		& 	0	& 0		& 0 & NiCad's failure \\
-	jena		& 0		& 	0	& 0		& 0 & NiCad's failure \\
-	Vuze		& 0		&	0	& 0		& 0 & NiCad's failure \\
-	Compiere	& 127	& 2		& 178	& 8 & No update \\
-	axion		& 7		& 	0	& 12	& 0 & No update \\
-	c-jdbc		& 66	&	0	& 768	& 0 & No update \\
-	colt		& 0		& 	0	& 5		& 0 & No update \\
-	columba		& 14	&	0	& 177	& 0 & No update \\
-	drawswf		& 0		&	0	& 0		& 0 & No update \\
-	fit-java	& 0		& 0		& 2 	& 0 & No update \\
-	freecs		& 5		& 0		& 22	& 0 & No update \\
-	heritrix	& 16	& 0		& 190 	& 0 & No update \\
-	iReport		& 0		& 0 	& 0		& 0 & No update \\
-	informa		& 31	& 0 	& 22	& 0 & No update \\
-	ivatagroupware	& 0	& 0		& 0		& 0 & No update \\
-	jFin		& 15	& 0		& 72	& 0 & No update \\
-	jOggPlayer	& 12 	& 0		& 52	& 0 & No update \\
-	jasml		& 23	& 0		& 47	& 0 & No update \\
-	jext		& 80	& 0		& 85	& 0 & No update \\
-	jgraphpad	& 1		& 1		& 55	& 0 & No update \\
-	jmoney		& 0		& 0		& 0		& 0 & No update \\
-	jparse		& 0		& 0		& 0		& 0 & No update \\
-	\hline
-	%& \multicolumn{5}{c}{\textit{Included in the latest version}} \\
-	%\hline
-	freecol		& 1		& 1		& 0		& 0		& \textit{FreeColMenuTest.java} exists with the \textit{createImageIcon()} method. Still can't find the reason why it is not reported. \\		
-	aoisrc281	& 0		& 0		& 33	& 33 	& \textit{MovieEncoder.java} (in 2 locations) are missing from the latest version. \\
-	findbugs	& 0		& 0		& 2		& 2 	& \textit{UnionBugs.java} has been changed. \\
-	jgraph		& 0		& 0		& 3		& 3 	& \textit{HelloWorld.java} has been changed. \\
-	\hline
-	Total		& 610	& 5		& 4231	& 52 	&\\
-	\hline
-\end{tabular}
-\end{table}
-
-\section*{Investigation of Missing A/B Clone Pairs Reported by Simian (df)}
+\section{Investigation of Missing A/B Clone Pairs Reported by Simian$_{df}$}
 We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
@@
 
-\begin{table}[H]
+\begin{table}
 	\centering
@@
 
-\section*{Simian's Parameters}
+\section{Simian's Parameters}
 
@@
 For example, the two code fragments in Figure \ref{fig:two_frags} would match by having \texttt{-balanceSquareBrackets+} enabled.
+However, the \texttt{-balanceSquareBrackets+} parameter only works on a small testing environment having toy programs or only small pairs from the full datasets.
+It does not work with the full complete set of 144,075 Stackoverflow fragments and Qualitas projects.
+Please find the summary of all the testing scenarios in Table \ref{tab:summary}.
+%I found that this pair is missing if I turned on \texttt{-balanceSquareBrackets+}.
 
-\noindent\begin{figure}[H]
+\noindent\begin{figure*}
 	\scriptsize
@@
 	\label{fig:two_frags}
-\end{figure}
+\end{figure*}
 
-However, the \texttt{-balanceSquareBrackets+} parameter only works on a small testing environment having toy programs or only small pairs from the full datasets.
-It does not work with the full complete set of 144,075 Stackoverflow fragments and Qualitas projects.
-Please find the summary of all the testing scenarios in Table \ref{tab:summary}.
-%I found that this pair is missing if I turned on \texttt{-balanceSquareBrackets+}.
-
-\begin{table}[H]
+\begin{table*}
 	\caption{Simian's \texttt{-balanceSquareBrackets+} (\texttt{-bsb+}) is observed to have unpredictable behaviours when running against big datasets.
@@
 	\end{tabular} 
-\end{table}
+\end{table*}
 
-\bibliographystyle{plain}
-\bibliography{references}
+\section{Threats to Validity}
+
+\section{Conclusions}
+This paragraph will end the body of this sample document.
+Remember that you might still have Acknowledgments or
+Appendices; brief samples of these
+follow.  There is still the Bibliography to deal with; and
+we will make a disclaimer about that here: with the exception
+of the reference to the \LaTeX\ book, the citations in
+this paper are to articles which have nothing to
+do with the present subject and are used as
+examples only.
+%\end{document}  % This is where a 'short' article might terminate
+
+%ACKNOWLEDGMENTS are optional
+\section{Acknowledgments}
+This section is optional; it is a location for you
+to acknowledge grants, funding, editing assistance and
+what have you.  In the present case, for example, the
+authors would like to thank Gerald Murray of ACM for
+his help in codifying this \textit{Author's Guide}
+and the \textbf{.cls} and \textbf{.tex} files that it describes.
+
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{abbrv}
+\bibliography{sigproc}
 

### 2016-10-20 latex-acm/cloneoverflow.tex
Updated latex

@@
 \documentclass{sig-alternate-05-2015}
+\usepackage[utf8]{inputenc}
+\usepackage[italian]{babel}
+\usepackage[T1]{fontenc}
 \usepackage{graphicx}
@@
 
-\title{Clone Overflow: \\ Code Reuse in Online Corpora and Its Effects}
+\title{CloneOverflow: \\ Discovery of Online Code Clones between \\Stackoverflow and Open Source Projects}
 
@@
 	\alignauthor
-	Chaiyong Ragkhitwetsagul, Jens Krinke \\
-	\affaddr{University College London}\\
-	\affaddr{London, UK}
+	$^1$Chaiyong Ragkhitwetsagul, $^1$Jens Krinke, $^2$Giuseppe Bianco \\
+	\affaddr{$^1$University College London, London, UK}\\
+	\affaddr{$^2$Università degli Studi del Molise, Campobasso, Italy}
 }
@@
 \section{Introduction}
+\begin{itemize}
+	\item Definition of code clones, online code clones, pros \& cons
+	\item Roles of Q\&A websites in supporting software development and education
+	\item Problems of code reuse (bug propagation, licensing conflicts)
+\end{itemize}
+
+This paper makes the following  primary contributions:
+
+\vspace{0.5ex}%
+\noindent\textbf{1.~A manual study of online code clone between Stackoverflow and open source projects:} 
+We manually investigate 2,371 clone pairs found between Java code fragments obtained from Stackoverflow accepted answers, and 63 Java open source projects.
+
+\vspace{0.5ex}%
+\noindent\textbf{2.~Addressing the problems of reusing online code clones:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license.
+Moreover, out of 48 clones, there are 27 clones in Stackoverflow that are outdated and dangerous for being reused.
 
 \section{Research Questions}
+The study aims to answer the following research questions: \\ 
 \textbf{RQ1 (online code clone):} \textit{How source code are reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale.
@@
 In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{QualitasCorpus}.
-However, we found that \textit{eclipse} project does not contain source code so we removed it from the dataset.
+We found that \textit{eclipse} project does not contain source code so we removed it from the dataset.
 This results in totally 63 projects being analysed.
-The details of the 63 Qualitas projects are listed in Table \ref{t:new_and_old}.
+The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.
 
-\subsection{Code Similarity Measurement}
+\subsection{Clone Detectors}
 We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info about clone detection tools in general and more details of these two tools}
+
+\subsection{Agreement-based Clone Detection}
+We adopted an idea of clone agreement normally used in clone research \cite{Wang2013,Funaro2010}.
 
@@
 			& \multicolumn{3}{c|}{Simian Default settings} 
-			& \multicolumn{3}{c|}{Simian FSE'13 settings}
+			& \multicolumn{3}{c|}{Simian EvaClone settings}
 			& \multicolumn{3}{c|}{NiCad Default settings} 
-			& \multicolumn{3}{c}{NiCad FSE'13 settings} \\ \cline{2-13} 
+			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
 			& \multicolumn{3}{c|}{792 fragments} 
@@
 			& \multicolumn{3}{c|}{Simian Default settings} 
-			& \multicolumn{3}{c|}{Simian FSE'13 settings} 
+			& \multicolumn{3}{c|}{Simian EvaClone settings} 
 			& \multicolumn{3}{c|}{NiCad Default settings} 
-			& \multicolumn{3}{c}{NiCad FSE'13 settings} \\ \cline{2-13} 
+			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
 			& \multicolumn{3}{c|}{707 fragments} 
@@
 	\centering
-	\caption{63 Qualitas projects (new versions checked on 2016-09-27)}
+	\caption{63 Qualitas projects (new versions retrieved on 2016-09-27)}
 	\label{t:new_and_old}
@@
 
-For agreement-based clone pairs, we use the threshold of 0.7 for both \textit{good}-match and \textit{ok}-match.
-Visualisation of \textit{good}-match common clone pairs between sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}.
+For agreement-based clone pairs, we use a threshold of 0.7 for both \textit{good} and \textit{ok}-match.
+A visualisation of \textit{good}-match common clone pairs between four sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}.
 There are 1,357 unique \textit{good}-match pairs.
-The \textit{ok}-match subsumes the \textit{good}-match resulting in totally 10,139 common clone pairs (Figure \ref{fig:venn4_orig_ok}).
+The distribution of 10,139 \textit{ok}-match pairs, which subsume the \textit{good}-match pairs, is depicted in Figure \ref{fig:venn4_orig_ok}.
 
-However, for NiCad's settings, we found a few renaming and clustering errors which resulted in fewer projects with clone reports.
+Nevertheless,  NiCad produced renaming and clustering errors for some of the settings.
+This resulted in not all 63 projects had NiCad clone reports.
 For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors.
-For NiCad FSE13 settings (NiCad$_{fse13}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}.
+For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvaClone}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}.
 So these projects are also missing from agreed clone pairs.
@@
 		\hline
-		Simian$_{\textrm{\textit{df/fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ & Simian$_{\textrm{\textit{df/fse13}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{fse13}$ \\ \hline
+		Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvaClone}}}$ & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvaClone}}}$ \\ \hline
 		63	& 57 & 46 & 44 & 40 & 34 \\
@@
 		%\hline
-		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{fse13}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
 		\hline
 		\textit{default} & \textit{default} & 9 	& 473 \\ 
-		\textit{default} & \textit{fse13} 	& 12 	& 353 \\ 
-		\textit{fse13} 	& \textit{default} 	& 7 	& 60 \\
-		\textit{fse13} 	& \textit{fse13} 	& 1,338 & 9528 \\ 
+		\textit{default} & \textit{EvaClone} 	& 12 	& 353 \\ 
+		\textit{EvaClone} 	& \textit{default} 	& 7 	& 60 \\
+		\textit{EvaClone} 	& \textit{EvaClone} 	& 1,338 & 9528 \\ 
 		\hline
@@
 		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
-		\caption{Qualitas-\textit{O} \textit{good}-match(0.7) pairs}
+		\caption{\textit{good}-match(0.7) pairs}
 		\label{fig:venn4_orig_good}
@@
 		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
-		\caption{Qualitas-\textit{O} \textit{ok}-match(0.7) pairs}
+		\caption{\textit{ok}-match(0.7) pairs}
 		\label{fig:venn4_orig_ok}
@@
 However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.
-According to the distribution of category from \textit{good-match} results, we can see that Simian$_{fse13}$--NiCad$_{fse13}$ produces a large number, 1,338, of false positive results (D, E, and F).
+According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{\textrm{\textit{EvaClone}}}$ produces a large number, 1,338, of false positive results (D, E, and F).
 Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs.
@@
 
-%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{df}$.
+%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvaClone}}}$, and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{df}$.
 We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
@@
 	\centering
-	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-match pairs which excludes the subsumed \textit{good}-match and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ pairs.}
+	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-match pairs which excludes the subsumed \textit{good}-match and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ pairs.}
 	\label{tab:classification_good_o}
@@
 		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
-		Simian$_{df}$--NiCad$_{fse13}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
-		Simian$_{fse13}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
-		Simian$_{fse13}$--NiCad$_{fse13}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,319 & 1,338 \\
+		Simian$_{df}$--NiCad$_{\textrm{\textit{EvaClone}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
+		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
+		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{\textrm{\textit{EvaClone}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,319 & 1,338 \\
 		\hline
@@
 		Simian$_{df}$--NiCad$_{df}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
-		Simian$_{df}$--NiCad$_{fse13}$   									& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
-		Simian$_{fse13}$--NiCad$_{df}$   									& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
+		Simian$_{df}$--NiCad$_{\textrm{\textit{EvaClone}}}$   									& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
+		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{df}$   									& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
 		\hline
@@
 %\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
-%We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{\mathrm{\textit{fse13}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{fse13}}}$, and Simian$_{\mathrm{\textit{fse13}}}$-NiCad$_{df}$.
+%We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvaClone}}}$, and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{df}$.
 We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
@@
 %	\centering
-%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{fse13}}}$.}
+%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvaClone}}}$.}
 %	\label{tab:classification_new}
@@
 %		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
-%		Simian$_{df}$--NiCad$_{fse13}$ 
+%		Simian$_{df}$--NiCad$_{\textrm{\textit{EvaClone}}}$ 
 %		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
-%		Simian$_{fse13}$--NiCad$_{df}$   									
+%		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{df}$   									
 %		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
@@
 
-With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{fse13}}}$ and NiCad$_{\mathrm{\textit{fse13}}}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}.
+With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvaClone}}}$ and NiCad$_{\mathrm{\textit{EvaClone}}}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}.
 With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.
@@
 
-\subsection{Issue~1:~outdated online code}
-After located and classified all the online clone pairs, we are now interested in analysing the true online clone pairs that are copied in the direction of Q $\rightarrow$ S (class-\textit{A} online clone pairs) in Table \ref{tab:classification_true_pairs_summary} which results in 48 pairs selected.
+In this study, we are interested in the effects of online code clones to software development.
+From the manual investigation of 184 true online clone pairs, we found that there are two potential issues: stale online code, and software licensing violation.
+
+\subsection{Issue~1:~stale online code}
+Stale online code occurs when a piece of code has been copied from a software project to Stackoverflow, and later it has been changed in the original project.
+However, in this situation, the copy is still unchanged.
+Since the code were updated due to various possible reasons including bug fixing, this can cause a problem if developers reuse stale online code from Q\&A websites such as Stackoverflow.
+They might also introduce the same unfixed bug(s) into the software.
+To discover stale online code, we focus on the true online clone pairs that are copied in the direction of Q $\rightarrow$ S (class-\textit{A} online clone pairs) in Table \ref{tab:classification_true_pairs_summary} which results in 48 pairs selected.
 We restricted it further to only the ones having versioning system so we can trace changes made to these clone pairs.
@@
 
-Our intuition behind his issue comes from a situation where a piece of code has been copied from a Qualitas project and posted on Stackoverflow.
+%Our intuition behind his issue comes from a situation where a piece of code has been copied from a Qualitas project and posted on Stackoverflow.
 Later, that piece of code has been modified further to accommodate changes in the projects (or any other reasons).
@@
 %We are interested in clone pairs that were changed after they appeared on Stackoverflow.
+
+The manual investigation of 48 class-A online clone pairs reveals that there are 27 stale clones.
+They are clone pairs that were copied from Qualitas projects to Stackoverflow and marked as \textit{accepted} answers.
+The investigation results are described in Table \ref{tab:stale_code}.
+
+\begin{table}[H]
+	\centering
+	\caption{Investigation of sale code clones from the online clone pairs}
+	\label{tab:stale_code}
+	\begin{tabular}{l|r|r|r}
+		\hline 
+		Project & Pairs & Stale & Fresh \\
+		\hline
+		apache-ant & 1 & 0 & 1 \\
+		aspectj & 2 & 2 & 0 \\
+		hadoop & 14 & 9 & 5 \\
+		hibernate & 16 & 2 & 14 \\
+		jasperreports & 2 & 2 & 0 \\
+		jfreechart & 4 & 4 & 0 \\
+		jgraph & 5 & 5 & 0 \\
+		jgrapht & 1 & 0 & 1 \\
+		junit & 3 & 3 & 0 \\
+		\hline
+		Total & 48 & 27 & 21 \\
+		\hline
+	\end{tabular} 
+\end{table}
+
 \subsection{Issue~2:~software licensing violation}
-\FIXME{Add more content here}
+Software licensing is vital in software industry.
+Violation of software license can have a major impact to the delivery of the software and also lead to legal issues.
+It is an emerging area that software engineering research community is paying attention to.
+For example, there are studies of automatic technique to identify software licensing from source code files \cite{German2010} and the evolution of licenses in open source projects \cite{DiPenta2010}.
+
+In our study, we tackle another possible situation of software licensing issue caused by code cloning to Q\&A websites.
+We found that there are at least 48 pieces of code have been copied from 9 open source projects to Stackoverflow as examples.
+These 9 open source projects come with software licenses.
+However, the licensing information are mostly missing from these clones.
+If developers copy and reuse these pieces of code in their projects, a licensing conflict can quietly happen without realisation of the developers.
 
@@
 We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
-The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{\mathrm{\textit{fse13}}}$, NiCad$_{df}$, NiCad$_{\mathrm{\textit{fse13}}}$.
+The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{\mathrm{\textit{EvaClone}}}$, NiCad$_{df}$, NiCad$_{\mathrm{\textit{EvaClone}}}$.
 The investigation results are shown in Table \ref{tab:search}.
@@
 		\hline 
-		Simian$_{\mathrm{\textit{fse13}}}$ & 0 & 41  \\ 
+		Simian$_{\mathrm{\textit{EvaClone}}}$ & 0 & 41  \\ 
 		\hline 
@@
 		\hline 
-		NiCad$_{\mathrm{\textit{fse13}}}$ &  24 & 17 \\ 
+		NiCad$_{\mathrm{\textit{EvaClone}}}$ &  24 & 17 \\ 
 		\hline 
@@
 
+\section{Related Work}
+\begin{itemize}
+	\item Code clones 
+		\begin{itemize}
+			\item Definition: Baxter et al. \cite{Baxter1998}
+			\item Comparison of clone detectors: \cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}
+			\item NiCad \cite{Roy2008,Cordy}
+			\item Simian \cite{simian}
+			\item Clone taxonomy \cite{Kapser2003}
+			\item Clone evolution \cite{Pate2013,Mondal2011}
+			\item Comparing Quality Metrics for Cloned and non cloned Java Methods : A Large Scale Empirical Study \cite{Saini2016}.
+		\end{itemize}
+	\item Agreement-based Clone Detection
+	\begin{itemize}
+		\item Bellon's framework \cite{Bellon2007}.
+		\item EvaClone \cite{Wang2013}
+		\item Hybrid \cite{Funaro2010}
+	\end{itemize}
+	\item Software licensing
+	\begin{itemize}
+		\item Code siblings \cite{German2009}, Ninka -- Automatic indification of SW license \cite{German2010}, Evolution of SW licensing \cite{DiPenta2010}
+	\end{itemize}
+
+	\item Stackoverflow
+	\begin{itemize}
+		\item Code example \cite{Nasehi2012}
+		\item Search for code in Stackoverflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014}
+	\end{itemize}
+\end{itemize}
+
 \section{Conclusions}

### 2016-10-20 latex-acm/cloneoverflow.tex
Updated stale clones

@@
 
-The manual investigation of 48 class-A online clone pairs reveals that there are 27 stale clones.
+The manual investigation of 48 class-A online clone pairs reveals that there are 30 stale clones.
 They are clone pairs that were copied from Qualitas projects to Stackoverflow and marked as \textit{accepted} answers.
@@
 	\centering
-	\caption{Investigation of sale code clones from the online clone pairs}
+	\caption{Investigation of stale code clones from the online clone pairs}
 	\label{tab:stale_code}
@@
 		hadoop & 14 & 9 & 5 \\
-		hibernate & 16 & 2 & 14 \\
+		hibernate & 16 & 5 & 11 \\
 		jasperreports & 2 & 2 & 0 \\
@@
 		\hline
-		Total & 48 & 27 & 21 \\
+		Total & 48 & 30 & 18 \\
 		\hline
@@
 \end{table}
+
+\begin{table*}
+	\centering
+	\caption{30 stale code clones found by a manual investigation}
+	\label{tab:stale_code_details}
+	\begin{tabular}{r|l|r|r}
+		\hline 
+		No. & File & Stackoverflow Q\&A & Change date \\
+		\hline
+		1 & aspectjtools1.6.9-src/../Agent.java & 18303692 & 2015-09-08 \\
+		2 & aspectjweaver1.6.9-src/../Agent.java & 18303692 & 2015-09-08 \\
+		3 & hadoop-1.0.0/../WritableComparator.java & 22315734 & 2014-11-20 \\
+		4 & hadoop-1.0.0/../StringUtils.java & 801987 & 2013-02-04 \\
+		5 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & 2011-06-12 \\
+		6 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & 2011-06-12 \\
+		7 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & 2011-07-25 \\
+		8 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & 2011-07-25 \\
+		9 & hadoop-1.0.0/../JobSubmissionFiles.java & 14845581 & 2012-06-25 \\
+		10 & hadoop-1.0.0/../TextOutputFormat.java & 16928749 & 2011-06-12 \\
+		11 & hadoop-1.0.0/../TestJobCounters.java & 18833798 & 2011-06-12 \\
+		12 & hibernate-release-4.2.2.Final/../SettingsFactory.java & 8257554 & 2011-03-11 (deleted) \\
+		13 & hibernate-release-4.2.2.Final/../Example.java & 24924255 & 2013-04-23 \\
+		14 & hibernate-release-4.2.2.Final/../SQLServer2005LimitHandler.java.java & 23967852 & 2013-04-23 \\
+		15 & hibernate-release-4.2.2.Final/../ConnectionProviderInitiator.java & 15168494 & 2016-02-24 \\
+		16 & hibernate-release-4.2.2.Final/../SchemaUpdate.java & 23520731 & 2016-02-05 \\
+		17 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & 2011-05-20 (deleted) \\
+		18 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & 2013-12-08 \\
+		19 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & 2013-11-22 \\
+		20 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & 2013-11-22 \\
+		21 & jasperreports-3.7.4/../AbstractXYItemRenderer.java & 12936580 & 2016-01-16 \\
+		22 & jfreechart-1.0.13/../KeyToGroupMap.java & 16058183 & 2013-07-03 \\
+		23 & jgraph-latest-bsd-src/../GroupingRemoving.java & 6722760 & 2005-xx-xx (rewritten) \\
+		24 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & 2005-xx-xx (rewritten) \\
+		25 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & 2005-xx-xx (rewritten) \\
+		26 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & 2005-xx-xx (rewritten) \\
+		27 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & 2005-xx-xx (rewritten) \\
+		28 & junit-4/org/junit/Assert.java & 23586872 & 2015-05-12 \\
+		29 & junit-4/../ExpectException.java & 8802082 & 2014-05-26 \\
+		30 & junit-4/../ExternalResource.java & 7504040 & 2016-06-25 \\
+		\hline
+	\end{tabular} 
+\end{table*}
 

### 2016-10-20 latex-acm/cloneoverflow.tex
Updates

--- 2016-10-20 latex-acm/cloneoverflow.tex
@@
 	\item Definition of code clones, online code clones, pros \& cons
+	\item Problems of code reuse (bug propagation, licensing conflicts)
 	\item Roles of Q\&A websites in supporting software development and education
-	\item Problems of code reuse (bug propagation, licensing conflicts)
 \end{itemize}
@@
 \vspace{0.5ex}%
-\noindent\textbf{1.~A manual study of online code clone between Stackoverflow and open source projects:} 
-We manually investigate 2,371 clone pairs found between Java code fragments obtained from Stackoverflow accepted answers, and 63 Java open source projects.
+\noindent\textbf{1.~A manual study of online code clones:} 
+We processed 130,644,707 clone pairs and manually investigated 2,371 clone pairs between Java code fragments obtained from Stackoverflow accepted answers and 63 Java open source projects.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of reusing online code clones:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license.
+\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and online Q\&A websites:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license.
 Moreover, out of 48 clones, there are 27 clones in Stackoverflow that are outdated and dangerous for being reused.
@@
 The study aims to answer the following research questions: \\ 
-\textbf{RQ1 (online code clone):} \textit{How source code are reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale.
+\textbf{RQ1 (online code clone):} \textit{To what extent  source code is reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale.
 \newline
-\textbf{RQ2 (flow of online code clone):} \textit{what are the directions source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
+\textbf{RQ2 (flow of online code clone):} \textit{what are the directions that source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
 Is it from Q\&A site to open source projects, or the other way around, or both?
 \newline
-\textbf{RQ3 (classification of online code clone):} \textit{How and why did these online code clone happen?} Can we categorise them? \newline
-\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful and how?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
+\textbf{RQ3 (classification of online code clone):} \textit{How do the online code clones happen?} What are the major causes creating the online code clones? \newline
+\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
 
@@
 \subsection{Dataset}
-In our study, we selected Qualitas corpus containing 64 Java open source projects \cite{QualitasCorpus}.
-We found that \textit{eclipse} project does not contain source code so we removed it from the dataset.
-This results in totally 63 projects being analysed.
+In our study, we selected the latest version of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects.
+\textit{eclipse} project does not contain source code so it has been removed from the study resulting in totally 63 projects.
 The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.
@@
 There are 2 tools selected: Simian and NiCad.
-They are configured using two different settings: default settings, and settings from another study \cite{Wang2013}.
-Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.
+They are configured using two different settings: default settings, and settings from a study by Wang et al.~\cite{Wang2013}.
+%Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.
+
+\begin{table}[H]
+	\centering
+	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
+	\label{tab:projects_missing}
+	\small
+	\begin{tabular}{l|r|r|r|r}
+		\hline
+		%		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
+		%		\hline
+		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ % & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ \hline
+		\hline
+		\textit{Successful} & 63 & 63 & 57 & 46 \\ %& 44 & 40 & 34 \\
+		\textit{Clust.~fail} & - & - & 6 & 13 \\
+		\textit{Ren.~fail} & - &  - & 0 & 4 \\
+		\hline
+		%		& \textit{6 clustering failed} & \textit{13 clustering failed} \\ %& & \textit{4 clustering failed} & \textit{6 clustering failed} \\
+		%		& cayenne   & cayenne 	\\ %& & jboss (wildfly) & ArgoUML \\
+		%		& checkstyle & checkstyle \\ %& & hadoop & checkstyle \\
+		%		& db-derby 	& db-derby 	\\ %& & db-derby & db-derby \\
+		%		& geotools 	& geotools  \\ %& & hibernate & cayenne \\
+		%		& iReport 	& iReport   \\ %& & & jena \\
+		%		& hibernate & ArgoUML 	\\ %& & & geotools \\
+		%		&			& castor 		\\ %& & & \\
+		%		&			& drjava 		\\ %& & & \\
+		%		&			& ganttproject 	\\ %& & & \\
+		%		&			& ivatagroupware \\ %& & &  \\
+		%		&			& jasperreports \\ %& & & \\
+		%		&			& jboss 		\\ %& & & \\
+		%		&			& jchempaint 	\\ %& & & \\
+		%		\hline
+		%		& 			&  \textit{4 renaming failed} \\ %& & & \textit{4 renaming failed} \\
+		%		&			& Vuze 		\\ %& & & Vuze \\
+		%		&			& aspectj 	\\ %& & & hadoop \\
+		%		&			& eXoPortal 	\\ %& & & jboss (wildfly) \\
+		%		&			&  hibernate 	\\ %& & & hibernate \\
+		%		\hline
+	\end{tabular}
+\end{table}
 
@@
 	\centering
-	\caption{Qualitas-\textit{O} (2013-09-01r) clone results}
+	\caption{Statistics of clones found between Stackoverflow and Qualitas projects using Simian and NiCad}
 	\label{t_simian_raw_results}
@@
 			\multirow{3}{*}{Statistics} 
-			& \multicolumn{3}{c|}{Simian Default settings} 
-			& \multicolumn{3}{c|}{Simian EvaClone settings}
-			& \multicolumn{3}{c|}{NiCad Default settings} 
-			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
+			& \multicolumn{3}{c|}{Simian$_{df}$} 
+			& \multicolumn{3}{c|}{Simian$_{\textrm{\textit{EvCl}}}$}
+			& \multicolumn{3}{c|}{NiCad$_{df}$} 
+			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
 			& \multicolumn{3}{c|}{792 fragments} 
@@
 
-\begin{table*}
-	\centering
-	\caption{Qualitas-\textit{N} (2016-08-05) clone results (44 new Qualitas projects)}
-	\label{t_simian_raw_results}
-%	\resizebox{\columnwidth}{!}{%
-	\small
-		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
-			\hline
-			\multirow{3}{*}{Statistics} 
-			& \multicolumn{3}{c|}{Simian Default settings} 
-			& \multicolumn{3}{c|}{Simian EvaClone settings} 
-			& \multicolumn{3}{c|}{NiCad Default settings} 
-			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
-			& \multicolumn{3}{c|}{707 fragments} 
-			& \multicolumn{3}{c|}{1205 fragments} 
-			& \multicolumn{3}{c|}{1068 fragments} 
-			& \multicolumn{3}{c}{10231 fragments} \\  \cline{2-13}
-			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
-			\hline
-			Total & 60,536 & -- 	& -- 	& 22,797,190 & -- 	& --  & 648,165 & -- & -- & 573,438,528 & -- & -- \\ 
-			Mean 	& 86 	& 7.37 	& 0.26 	& 18,919 	& 4.85 	& 0.28 & 607 & 9.39 & 0.25 & 47663 & 5.22 & 0.20 \\
-			Std Dev. & 217 	& 2.22 	& 0.21 	& 326,588 	& 1.31 	& 0.19 & 1,499 & 2.98 & 1.81 & 58,833 & 2.77 & 0.15 \\
-			Max 	& 1,298 & 32.00 & 0.94 & 11,127,286 & 21.00 & 0.92 & 10,550 & 36.00 & 0.84 & 1,246,598 & 250 & 0.96 \\
-			Min 	& 1 	& 5.00 	& 0.01 	& 1 & 4.00 	& 0.02 & 1 & 7 & 0.02 & 1 & 2.00 & 0.01\\
-			Median 	& 2 & 7.00 	& 0.21 	& 20		& 5.00 	& 0.25 & 33 & 8 & 0.19 & 52,077 & 5.00 & 0.15 \\
-			Mode & 1 	& 7.00 	& 0.25 	& 1 		& 4.00 	& 0.50 & 1 & 8 & 0.67 & 1 & 4.00 & 0.33 \\
-			\hline
-		\end{tabular} %
-	%}
-\end{table*}
+%\begin{table*}
+%	\centering
+%	\caption{Qualitas-\textit{N} (2016-08-05) clone results (44 new Qualitas projects)}
+%	\label{t_simian_raw_results}
+%%	\resizebox{\columnwidth}{!}{%
+%	\small
+%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
+%			\hline
+%			\multirow{3}{*}{Statistics} 
+%			& \multicolumn{3}{c|}{Simian Default settings} 
+%			& \multicolumn{3}{c|}{Simian EvaClone settings} 
+%			& \multicolumn{3}{c|}{NiCad Default settings} 
+%			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
+%			& \multicolumn{3}{c|}{707 fragments} 
+%			& \multicolumn{3}{c|}{1205 fragments} 
+%			& \multicolumn{3}{c|}{1068 fragments} 
+%			& \multicolumn{3}{c}{10231 fragments} \\  \cline{2-13}
+%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
+%			\hline
+%			Total & 60,536 & -- 	& -- 	& 22,797,190 & -- 	& --  & 648,165 & -- & -- & 573,438,528 & -- & -- \\ 
+%			Mean 	& 86 	& 7.37 	& 0.26 	& 18,919 	& 4.85 	& 0.28 & 607 & 9.39 & 0.25 & 47663 & 5.22 & 0.20 \\
+%			Std Dev. & 217 	& 2.22 	& 0.21 	& 326,588 	& 1.31 	& 0.19 & 1,499 & 2.98 & 1.81 & 58,833 & 2.77 & 0.15 \\
+%			Max 	& 1,298 & 32.00 & 0.94 & 11,127,286 & 21.00 & 0.92 & 10,550 & 36.00 & 0.84 & 1,246,598 & 250 & 0.96 \\
+%			Min 	& 1 	& 5.00 	& 0.01 	& 1 & 4.00 	& 0.02 & 1 & 7 & 0.02 & 1 & 2.00 & 0.01\\
+%			Median 	& 2 & 7.00 	& 0.21 	& 20		& 5.00 	& 0.25 & 33 & 8 & 0.19 & 52,077 & 5.00 & 0.15 \\
+%			Mode & 1 	& 7.00 	& 0.25 	& 1 		& 4.00 	& 0.50 & 1 & 8 & 0.67 & 1 & 4.00 & 0.33 \\
+%			\hline
+%		\end{tabular} %
+%	%}
+%\end{table*}
 
@@
 			\hline 
-			Projects & Old version & New versions & Latest change & Repo. & License & Notes \\
+			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
 			\hline
@@
 \subsection{Agreement based clone pairs}
-
 For agreement-based clone pairs, we use a threshold of 0.7 for both \textit{good} and \textit{ok}-match.
@@
 For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors.
-For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvaClone}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}.
+For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvCl}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}.
 So these projects are also missing from agreed clone pairs.
@@
 
-\FIXME{Maybe no longer needed?} We are interested in discovering reused code in the latest versions of Qualitas projects.
+%\FIXME{Maybe no longer needed?} We are interested in discovering reused code in the latest versions of Qualitas projects.
 So, we downloaded the newest release of each project and found 44 of them having newer updates.
@@
 
-\begin{table*}
-	\centering
-	\caption{No.~of projects in Qualitas Original~(Qualitas-\textit{O}) and New (Qualitas-\textit{N}) successfully analysed by Simian and NiCad}
-	\label{tab:projects_missing}
-	\small
-	\begin{tabular}{r|r|r|r|r|r}
-		\hline
-		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
-		\hline
-		Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvaClone}}}$ & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvaClone}}}$ \\ \hline
-		63	& 57 & 46 & 44 & 40 & 34 \\
-		\hline
-		& \textit{6 clustering failed} & \textit{13 clustering failed} & & \textit{4 clustering failed} & \textit{6 clustering failed} \\
-		& cayenne   & cayenne 	& & jboss (wildfly) & ArgoUML \\
-		& checkstyle & checkstyle & & hadoop & checkstyle \\
-		& db-derby 	& db-derby 	& & db-derby & db-derby \\
-		& geotools 	& geotools  & & hibernate & cayenne \\
-		& iReport 	& iReport   & & & jena \\
-		& hibernate & ArgoUML 	& & & geotools \\
-		&			& castor 		& & & \\
-		&			& drjava 		& & & \\
-		&			& ganttproject 	& & & \\
-		&			& ivatagroupware & & &  \\
-		&			& jasperreports & & & \\
-		&			& jboss 		& & & \\
-		&			& jchempaint 	& & & \\
-		\hline
-		& 			&  \textit{4 renaming failed} & & & \textit{4 renaming failed} \\
-		&			& Vuze 		& & & Vuze \\
-		&			& aspectj 	& & & hadoop \\
-		&			& eXoPortal 	& & & jboss (wildfly) \\
-		&			&  hibernate 	& & & hibernate \\
-		\hline
-	\end{tabular}
-\end{table*}
-
-\begin{table}
+\begin{table}[H]
 	\centering
@@
 	\label{t_agreed_good_clone_pairs}
+	\small
 	\begin{tabular}{l|l|r|r}
@@
 		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 \\
+		\hline
 		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 \\
@@
 
-\begin{figure*}
-	\centering
-	\begin{minipage}{.5\textwidth}
+\begin{figure}
 		\centering
@@
 		\label{fig:venn4_orig_good}
-	\end{minipage}%
-	\begin{minipage}{.5\textwidth}
+\end{figure}
+
+\begin{figure}
 		\centering
@@
 		\label{fig:venn4_orig_ok}
-	\end{minipage}
-\end{figure*}
+\end{figure}
 
@@
 However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.
-According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{\textrm{\textit{EvaClone}}}$ produces a large number, 1,338, of false positive results (D, E, and F).
+According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number, 1,338, of false positive results (D, E, and F).
 Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs.
@@
 
-\begin{table*}
+\begin{table}
 	\centering
-	\caption{Qualitas-\textit{O}: Distribution of classification category A--F according to \textit{good}-match pairs}
+	\caption{Distribution of classification category A--F according to \textit{good}- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
 	\label{tab:good_classification}
@@
 		\hline
-		Simian$_{df}$--NiCad$_{df}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
-		Simian$_{df}$--NiCad$_{\textrm{\textit{EvaClone}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
-		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
-		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{\textrm{\textit{EvaClone}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1,319 & 1,338 \\
 		\hline
-		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1,320  & 1,366 \\
-		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1,320  & 1,352 \\
+		\multicolumn{9}{|c|}{\textit{good}-match pairs} \\
 		\hline
-	\end{tabular} 
-\end{table*}
-
-\begin{table*}
-	\centering
-	\caption{Qualitas-\textit{O}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
-	\label{tab:ok_classification}
-	\small
-	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+		S$_{df}$--N$_{df}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
+		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
+		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
+		S$_{\textrm{\textit{EvCl}}}$--N$_{\textrm{\textit{EvCl}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1319 & 1338 \\
 		\hline
-		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
+		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1320  & 1366 \\
+		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1320  & 1352 \\
 		\hline
-		Simian$_{df}$--NiCad$_{df}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
-		Simian$_{df}$--NiCad$_{\textrm{\textit{EvaClone}}}$   									& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
-		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{df}$   									& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
+		\hline 
+%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
+%		\hline
+		\multicolumn{9}{|c|}{\textit{ok}-match pairs} \\
+		\hline
+		S$_{df}$--N$_{df}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
+		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   	& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
+		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   	& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
 		\hline
@@
 	\end{tabular} 
-\end{table*}
+\end{table}
 
@@
 %		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
-%		Simian$_{df}$--NiCad$_{\textrm{\textit{EvaClone}}}$ 
+%		Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$ 
 %		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
-%		Simian$_{\textrm{\textit{EvaClone}}}$--NiCad$_{df}$   									
+%		Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$   									
 %		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.7\linewidth]{n+v+g}
-	\caption{Qualitas projects categorised by NiCad's results, existence of newer versions, and version control}
-	\label{fig:n+v+g}
-\end{figure*}
+%\begin{figure*}
+%	\centering
+%	\includegraphics[width=0.7\linewidth]{n+v+g}
+%	\caption{Qualitas projects categorised by NiCad's results, existence of newer versions, and version control}
+%	\label{fig:n+v+g}
+%\end{figure*}
 
@@
 
-\begin{table*}
+\begin{table}
 	\centering
-	\caption{Statistics of Simian$_{df}$ and NiCad$_{df}$ clone pairs.}
+	\caption{Statistics of Simian$_{df}$ and NiCad$_{df}$ non agreement-based clone pairs.}
 	\label{tab:classification_indv_stats}
@@
 		\hline 
-		Tool & Clone pairs & \textit{ok}-pairs & filtered pairs & remaining pairs \\ 
+		Tool & Clone pairs & \textit{ok}-pairs & filtered & remaining \\ 
 		\hline 
@@
 	\end{tabular} 
-\end{table*}
+\end{table}
 
-\subsection{Manual investigation of non-agreement based clone pairs}
+\subsection{Manual investigation of non agreement-based clone pairs}
 %\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
@@
 	\centering
-	\caption{Classification results of 292 Simian$_{df}$ and 114 NiCad$_{df}$ individual unique pairs.}
+	\caption{Classification results of 292 Simian$_{df}$ and 114 NiCad$_{df}$ non agreement-based clone pairs.}
 	\label{tab:classification_indv}
@@
 	\centering
-	\caption{Numbers of true online clone pairs (A+A'+B+C) found by manual investigation}
+	\caption{Numbers of true positives online clone pairs found by manual investigation}
 	\label{tab:classification_true_pairs_summary}
+	\small
 	\begin{tabular}{l|r|r|r|r|r}
@@
 
-\subsection{Issue~1:~stale online code}
+\subsection{Issue~1:~stale online code clones}
 Stale online code occurs when a piece of code has been copied from a software project to Stackoverflow, and later it has been changed in the original project.
@@
 
-\begin{table}[H]
+\begin{table}
 	\centering
-	\caption{Investigation of sale code clones from the online clone pairs}
+	\caption{Summary of stale code clones found}
 	\label{tab:stale_code}
+	\small
 	\begin{tabular}{l|r|r|r}
@@
 
-\subsection{Issue~2:~software licensing violation}
+\begin{table*}
+	\centering
+	\caption{30 stale code clones in Stackoverflow found by a manual investigation}
+	\label{tab:stale_code_details}
+	\small
+	\begin{tabular}{r|l|r|c|l}
+		\hline 
+		No. & File & Stackoverflow Q\&A & Changes made & Date \\
+		\hline
+		1 & aspectjtools1.6.9-src/../Agent.java & 18303692 & alteration & 2015-09-08 \\
+		2 & aspectjweaver1.6.9-src/../Agent.java & 18303692 & alteration & 2015-09-08 \\
+		3 & hadoop-1.0.0/../WritableComparator.java & 22315734 & alteration & 2014-11-20 \\
+		4 & hadoop-1.0.0/../StringUtils.java & 801987 & alteration & 2013-02-04 \\
+		5 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & alteration & 2011-06-12 \\
+		6 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & alteration & 2011-06-12 \\
+		7 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & alteration & 2011-07-25 \\
+		8 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & alteration & 2011-07-25 \\
+		9 & hadoop-1.0.0/../JobSubmissionFiles.java & 14845581 & alteration & 2012-06-25 \\
+		10 & hadoop-1.0.0/../TextOutputFormat.java & 16928749 & alteration & 2011-06-12 \\
+		11 & hadoop-1.0.0/../TestJobCounters.java & 18833798 & alteration & 2011-06-12 \\
+		12 & hibernate-release-4.2.2.Final/../SettingsFactory.java & 8257554 & removal & 2011-03-11 \\
+		13 & hibernate-release-4.2.2.Final/../Example.java & 24924255 & alteration & 2013-04-23 \\
+		14 & hibernate-release-4.2.2.Final/../SQLServer2005LimitHandler.java.java & 23967852 & alteration & 2013-04-23 \\
+		15 & hibernate-release-4.2.2.Final/../ConnectionProviderInitiator.java & 15168494 & alteration & 2016-02-24 \\
+		16 & hibernate-release-4.2.2.Final/../SchemaUpdate.java & 23520731 & alteration & 2016-02-05 \\
+		17 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & removal & 2011-05-20 \\
+		18 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & alteration & 2013-12-08 \\
+		19 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & alteration & 2013-11-22 \\
+		20 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & alteration & 2013-11-22 \\
+		21 & jasperreports-3.7.4/../AbstractXYItemRenderer.java & 12936580 & alteration & 2016-01-16 \\
+		22 & jfreechart-1.0.13/../KeyToGroupMap.java & 16058183 & alteration & 2013-07-03 \\
+		23 & jgraph-latest-bsd-src/../GroupingRemoving.java & 6722760 & rewriting & 2005 \\
+		24 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
+		25 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
+		26 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
+		27 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
+		28 & junit-4/org/junit/Assert.java & 23586872 & alteration & 2015-05-12 \\
+		29 & junit-4/../ExpectException.java & 8802082 & alteration & 2014-05-26 \\
+		30 & junit-4/../ExternalResource.java & 7504040 & alteration & 2016-06-25 \\
+		\hline
+	\end{tabular} 
+\end{table*}
+
+\subsection{Issue~2:~clones with software licensing violations}
 Software licensing is vital in software industry.
@@
 
-\section{Investigation of Missing A/B Clone Pairs Reported by Simian$_{df}$}
-We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
+%\section{Investigation of Missing A/B Clone Pairs Reported by Simian$_{df}$}
+%We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
 The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{\mathrm{\textit{EvaClone}}}$, NiCad$_{df}$, NiCad$_{\mathrm{\textit{EvaClone}}}$.
 The investigation results are shown in Table \ref{tab:search}.
-
-\begin{table}
-	\centering
-	\caption{Results of matching the original 41 Simian(default) pairs in the pretty-printed result sets}
-	\label{tab:search}
-	\begin{tabular}{l|r|r}
-		\hline 
-		Settings & Found & Not found \\ 
-		\hline 
-		Simian$_{df}$  &  40 & 1* \\ 
-		\hline 
-		Simian$_{\mathrm{\textit{EvaClone}}}$ & 0 & 41  \\ 
-		\hline 
-		NiCad$_{df}$  & 17 & 24 \\ 
-		\hline 
-		NiCad$_{\mathrm{\textit{EvaClone}}}$ &  24 & 17 \\ 
-		\hline 
-	\end{tabular} 
-\end{table}
-
-The single missing Stackoverflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian.
+%
+%\begin{table}
+%	\centering
+%	\caption{Results of matching the original 41 Simian(default) pairs in the pretty-printed result sets}
+%	\label{tab:search}
+%	\begin{tabular}{l|r|r}
+%		\hline 
+%		Settings & Found & Not found \\ 
+%		\hline 
+%		Simian$_{df}$  &  40 & 1* \\ 
+%		\hline 
+%		Simian$_{\mathrm{\textit{EvaClone}}}$ & 0 & 41  \\ 
+%		\hline 
+%		NiCad$_{df}$  & 17 & 24 \\ 
+%		\hline 
+%		NiCad$_{\mathrm{\textit{EvaClone}}}$ &  24 & 17 \\ 
+%		\hline 
+%	\end{tabular} 
+%\end{table}
+%
+%The single missing Stackoverflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian.
 It is removed from the results of the pretty-printed version because it is an outlier.
 The rest are missing because of different parameter settings.
-
-\section{Simian's Parameters}
-
-We have carefully investigated the effects of the Simian's parameter \texttt{-balanceSquareBrackets+}.
+%
+%\section{Simian's Parameters}
+%
+%We have carefully investigated the effects of the Simian's parameter \texttt{-balanceSquareBrackets+}.
 I found that it works in the expected way of handling a pair of brackets (\texttt{[},\texttt{]}) that span over multiple lines.
@@
 %I found that this pair is missing if I turned on \texttt{-balanceSquareBrackets+}.
-
-\noindent\begin{figure*}
-	\scriptsize
-	\begin{lstlisting}[frame=single,style=base]
-	1   public class MagicSquare {                           public class MagicSquare2 {
-	2       private int[][] square;                              @private int[@
-	3       private boolean[] possible;                                      @][@
-	4       private int totalSqs;                                            @] square;@
-	5       private int sum;                                     private boolean[] possible;
-	6       private int numsquares;                              private int totalSqs;
-	7       public static void main ( String[] args ) {          private int sum;
-	8       MagicSquare m = new MagicSquare ( 3 );               private int numsquares;
-	9                                                            public static void main ( String[] args ) {
-	10                                                           MagicSquare m = new MagicSquare ( 3 );
-	\end{lstlisting}
-	\caption{Two identical fragments with only differences in locations of the square brackets.
+%
+%\noindent\begin{figure*}
+%	\scriptsize
+%	\begin{lstlisting}[frame=single,style=base]
+%	1   public class MagicSquare {                           public class MagicSquare2 {
+%	2       private int[][] square;                              @private int[@
+%	3       private boolean[] possible;                                      @][@
+%	4       private int totalSqs;                                            @] square;@
+%	5       private int sum;                                     private boolean[] possible;
+%	6       private int numsquares;                              private int totalSqs;
+%	7       public static void main ( String[] args ) {          private int sum;
+%	8       MagicSquare m = new MagicSquare ( 3 );               private int numsquares;
+%	9                                                            public static void main ( String[] args ) {
+%	10                                                           MagicSquare m = new MagicSquare ( 3 );
+%	\end{lstlisting}
+%	\caption{Two identical fragments with only differences in locations of the square brackets.
 All 7 lines are reported by Simian if \small\texttt{-balanceSquareBrackets+} \normalsize is enabled.
 If not, the clone pairs is reported as \newline (MagicSquare.java [3,8], MagicSquare2.java [5,10]).}
-	\label{fig:two_frags}
-\end{figure*}
-
-\begin{table*}
-	\caption{Simian's \texttt{-balanceSquareBrackets+} (\texttt{-bsb+}) is observed to have unpredictable behaviours when running against big datasets.
+%	\label{fig:two_frags}
+%\end{figure*}
+%
+%\begin{table*}
+%	\caption{Simian's \texttt{-balanceSquareBrackets+} (\texttt{-bsb+}) is observed to have unpredictable behaviours when running against big datasets.
 $\textrm{\textit{CP}}_2$ means the reported clone(s) do not contain lines having dislocated brackets ($L_b$) (i.e.
 $\textrm{\textit{CP}}_2 = \textrm{\textit{CP}}_1 - L_b$).}
-	\label{tab:summary}
-	\centering
-	\small\begin{tabular}{l|p{6cm}|c|c|c}
-		\hline 
-		\multirow{2}{*}{\textbf{Project 1}} & \multirow{2}{*}{\textbf{Project 2}} & \textbf{Dislocated} & \multirow{2}{*}{\textbf{-bsb+}} & \textbf{Clones pair} \\ 
-		& & \textbf{brackets?} & & \textbf{reported} \\
-		\hline
-		\hline
-		\multicolumn{5}{l}{\textit{Only run Simian against the pair}} \\
-		\hline
-		MagicSquare.java & MagicSquare\_exact\_copy.java & no & 0,1 & $\textrm{\textit{CP}}_1$ \\
-		MagicSquare.java & MagicSquare2.java & yes & 0 & $\textrm{\textit{CP}}_2$ \\ 
-		MagicSquare.java & MagicSquare2.java & yes & 1 & $\textrm{\textit{CP}}_1$ \\
-		\hline
-		%\hline
-		%\multicolumn{5}{c}{\textit{Only run Simian against the pair}} \\
-		%\hline
-		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 0 & $\textrm{\textit{CP}}_3$ \\ 
-		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 1 & $\textrm{\textit{CP}}_3$ \\ 
-		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 0 & $\textrm{\textit{CP}}_4$ \\ 
-		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 1 & $\textrm{\textit{CP}}_4$ \\ 
-		\hline 
-		\hline
-		\multicolumn{5}{l}{\textit{Run Simian against the complete stackoverflow data and the project}} \\
-		\hline
-		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 0 & $\textrm{\textit{CP}}_3$ \\ 
-		\cellcolor{red!10}stackoverflow/4298836\_0.java & \cellcolor{red!10}Qualitas/aoisrc281/../ExprModule.java & \cellcolor{red!10}no & \cellcolor{red!10}1 & \cellcolor{red!10}-- \\ 
-		\hline
-		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 0 & $\textrm{\textit{CP}}_4$ \\ 
-		\cellcolor{red!10}stackoverflow/4533682\_1.java & \cellcolor{red!10}Qualitas/cobertura-1/../TouchCollector.java & \cellcolor{red!10}no & \cellcolor{red!10}1 & \cellcolor{red!10}-- \\
-		\hline 
-	\end{tabular} 
-\end{table*}
+%	\label{tab:summary}
+%	\centering
+%	\small\begin{tabular}{l|p{6cm}|c|c|c}
+%		\hline 
+%		\multirow{2}{*}{\textbf{Project 1}} & \multirow{2}{*}{\textbf{Project 2}} & \textbf{Dislocated} & \multirow{2}{*}{\textbf{-bsb+}} & \textbf{Clones pair} \\ 
+%		& & \textbf{brackets?} & & \textbf{reported} \\
+%		\hline
+%		\hline
+%		\multicolumn{5}{l}{\textit{Only run Simian against the pair}} \\
+%		\hline
+%		MagicSquare.java & MagicSquare\_exact\_copy.java & no & 0,1 & $\textrm{\textit{CP}}_1$ \\
+%		MagicSquare.java & MagicSquare2.java & yes & 0 & $\textrm{\textit{CP}}_2$ \\ 
+%		MagicSquare.java & MagicSquare2.java & yes & 1 & $\textrm{\textit{CP}}_1$ \\
+%		\hline
+%		%\hline
+%		%\multicolumn{5}{c}{\textit{Only run Simian against the pair}} \\
+%		%\hline
+%		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 0 & $\textrm{\textit{CP}}_3$ \\ 
+%		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 1 & $\textrm{\textit{CP}}_3$ \\ 
+%		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 0 & $\textrm{\textit{CP}}_4$ \\ 
+%		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 1 & $\textrm{\textit{CP}}_4$ \\ 
+%		\hline 
+%		\hline
+%		\multicolumn{5}{l}{\textit{Run Simian against the complete stackoverflow data and the project}} \\
+%		\hline
+%		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 0 & $\textrm{\textit{CP}}_3$ \\ 
+%		\cellcolor{red!10}stackoverflow/4298836\_0.java & \cellcolor{red!10}Qualitas/aoisrc281/../ExprModule.java & \cellcolor{red!10}no & \cellcolor{red!10}1 & \cellcolor{red!10}-- \\ 
+%		\hline
+%		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 0 & $\textrm{\textit{CP}}_4$ \\ 
+%		\cellcolor{red!10}stackoverflow/4533682\_1.java & \cellcolor{red!10}Qualitas/cobertura-1/../TouchCollector.java & \cellcolor{red!10}no & \cellcolor{red!10}1 & \cellcolor{red!10}-- \\
+%		\hline 
+%	\end{tabular} 
+%\end{table*}
 

### 2016-10-21 latex-acm/cloneoverflow.tex
Updates

@@
 \section{Introduction}
-\begin{itemize}
-	\item Definition of code clones, online code clones, pros \& cons
-	\item Problems of code reuse (bug propagation, licensing conflicts)
-	\item Roles of Q\&A websites in supporting software development and education
-\end{itemize}
+Code cloning is an activity of reusing source code by copy and paste.
+It normally occurs in software development and account from 7\% to 23\% in typical software systems \cite{Bellon2007}.
+The benefits and drawbacks of clones are still controversial.
+Several authors state that clones lead to bug propagations and software maintenance issues \cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial \cite{Saini2016,Kapser2006}.
+Importantly, carelessly cloning code from one project and reusing it in another project can also cause software licensing conflict \cite{German2009}.
+
+The rise of the Internet ignites tremendous amount of source code sharing online.
+This online code artefacts are very useful for software development and also valuable for educational purposes \cite{x}.
+Nonetheless, the process of sharing source code on the web is very similar to code cloning.
+On question-and-answer (Q\&A) websites such as Stackoverflow, most of the answers contain at least one code snippet showing how to solve a specific programming problem.
+The code snippet that is given as an example is usually copied from somewhere else.
+It can be cloned and modified from the question, copied from the answerer's own projects, or from other locations including open source software (OSS) systems.
+
+In this study, we focus on a special type of code clones between software projects and Q\&A websites which we call ``online code clones''.
+There are three ways to create online code clones: 1) code is cloned from a software project to Q\&A website as an example; 2) code is cloned from Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; and 3) code is implicitly cloned from one software project to another by having Q\&A website as a medium.
+Online code clones can similarly lead to the problem of bug propagation as the classical code clones.
+However, they are harder to locate and fix since the search scope is no longer contained in a local repository.
+%Since reusing source code from Stackoverflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
+This is an emerging and challenging problem to address and there is still limited studies in this area. %We are interested to gain more insights of online code clone in this study.
 
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We processed 130,644,707 clone pairs and manually investigated 2,371 clone pairs between Java code fragments obtained from Stackoverflow accepted answers and 63 Java open source projects.
+We used clone detection tools to discover 130,644,707 clone pairs and manually investigated 2,371 meaningful clone pairs between Java code fragments obtained from Stackoverflow accepted answers and 63 Java open source projects.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and online Q\&A websites:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license.
-Moreover, out of 48 clones, there are 27 clones in Stackoverflow that are outdated and dangerous for being reused.
+\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and online Q\&A websites:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which violate their software licenses.
+Furthermore, 30 out of the 48 clones are outdated and dangerous for being reused.
 
-\section{Research Questions}
+\section{Empirical Study}
+We perform and empirical study of online code clones between Stackoverflow Java accepted answers and 63 Java open source projects.
+
 The study aims to answer the following research questions: \\ 
-\textbf{RQ1 (online code clone):} \textit{To what extent  source code is reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale.
+\textbf{RQ1 (online code clone):} \textit{To what extent  source code is reused between Q\&A websites and open source projects?} We would like analyse quantitatively the number of online code clones between a Q\&A website, Stackoverflow, and open source projects.
 \newline
-\textbf{RQ2 (flow of online code clone):} \textit{what are the directions that source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
-Is it from Q\&A site to open source projects, or the other way around, or both?
+\textbf{RQ2 (flow of online code clone):} \textit{what are the directions that source code is cloned?} If clones between the two locations exist, we would like to observe in which direction the code has been copied.
+Is it from Q\&A websites to open source projects, or the other way around, or both?
 \newline
-\textbf{RQ3 (classification of online code clone):} \textit{How do the online code clones happen?} What are the major causes creating the online code clones? \newline
-\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
+\textbf{RQ3 (classification of online code clone):} \textit{Are there any differences among online code clones?} We would like to classify and group them to gain insights of their common properties.
+\newline
+\textbf{RQ4 (effects of online code clone):} \textit{Are online codes clone harmful?} Is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
 
-\section{Experimental Setup}
+\subsection{Experimental Framework}
+The experimental framework is depicted in Figure \ref{}.
+We deploy clone detection tools to locate clones between two locations: code snippets obtained from a Q\&A website, and open source projects.
+The clone report is pruned to contain only inter clone pairs between the two locations.
+All intra clone pairs within the Q\&A website and open source projects are removed.
+Clone pairs reported from the two clone detectors are matched to find agreements using Bellon's criteria \cite{Bellon2007}.
+This step generates \textbf{agreement-based clone pairs}.
+Next, clone pairs from each of the clone detection tools that do not agree with the other tool are ranked and selected.
+This step generates \textbf{non agreement-based clone pairs}.
+Agreement-based and non agreement-based clone pairs are looked at and classified manually.
 
-\subsection{Dataset}
-In our study, we selected the latest version of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects.
+Later, we compare licensing information of manually identified true positive clone pairs to see if they have any licensing conflicts.
+Moreover, we look forward through history of the clones from the projects' versioning systems to see if there is any changes made to the clones after it has been copied.
+
+\subsection{Experimental Setup}
+\subsubsection{Datasets}
+\textbf{Stackoverflow}: we extracted 144,075 Java code snippets from accepted answers in a snapshot of Stackoverflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
+The data dump is in XML format containing information regarding Stackoverflow questions and answers and supporting data such as user accounts and timestamps.
+Code snippet is a piece of code located between \texttt{<code>} tags.
+These snippets are extracted from the XML dump using regular expressions.
+We then filtered the snippets with two filtering criteria.
+First, we ignore snippets that are less than 6 lines.
+Second, we are only interested in code snippets from answers that are marked as ``accepted'' since they have high chance to be reused.
+
+\textbf{Qualitas corpus}: we selected the latest version of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects.
 \textit{eclipse} project does not contain source code so it has been removed from the study resulting in totally 63 projects.
@@
 
-\subsection{Clone Detectors}
-We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info about clone detection tools in general and more details of these two tools}
+\subsubsection{Clone Detectors}
+We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}.
+There is a few restrictions in terms of choosing clone detection tools for this study.
+First, due to nature of code snippets posted on Stackoverflow, some of them are not complete Java classes or methods.
+Hence, the tool must be flexible enough to process code snippets which are not in a complete block or compilable.
+This restriction forces us to remove two well-known clone detectors; CCFinder \cite{Kamiya2002}, and DECKARD \cite{Jiang2007a}; from our study since they failed to analyse the complete 144,075 Stackoverflow snippets.
+Second, since the amount of code that have to be process are large \FIXME{Find SLOC of 144,075 SO snippets and 63 projects}, the clone detector must be scalable enough to execute and report clones in a reasonable amount of time.
+We found that both Simian and NiCad are able to handle clones in this situation with an acceptable running time.
 
-\subsection{Agreement-based Clone Detection}
-We adopted an idea of clone agreement normally used in clone research \cite{Wang2013,Funaro2010}.
+\subsubsection{Agreement-based Clone Detection}
+Since we did not have the clone oracle of the two datasets, we adopted an idea of clone agreement used in clone research \cite{Wang2013,Funaro2010} to help filtering the reported clones for manual investigation.
 

### 2016-10-29 latex-acm/cloneoverflow.tex
Latest update after finish processing part 2

--- 2016-10-20 latex-acm/cloneoverflow.tex
@@
 
-\title{CloneOverflow: \\ Discovery of Online Code Clones between \\Stackoverflow and Open Source Projects}
+\title{Are We Reusing Outdated Code from Stack Overflow?}
 
@@
 \section{Introduction}
-\begin{itemize}
-	\item Definition of code clones, online code clones, pros \& cons
-	\item Problems of code reuse (bug propagation, licensing conflicts)
-	\item Roles of Q\&A websites in supporting software development and education
-\end{itemize}
+%The popularity of the Internet encourages tremendous amount of source code being shared online. 
+Stack Overflow is a popular online programming community with 6.3 million users.
+It allows programmers to ask questions and give answers to programming problems.
+The website has found to be useful for software development and also valuable for educational purposes \cite{x}.
+On Stack Overflow, each conversation contains a question and answer(s).
+The answers normally contain at least one code snippet as a solution to the question asked.
+The code snippet is usually not written directly on Stack Overflow website but copied from another location.
+It can be copied and modified from the problematic code snippet in the question, copied from an answerer's own code, or borrowed from other locations including open source software (OSS) systems.
+As a result, the process of posting and answering questions on Stack Overflow which involves copying and pasting source code can be considered as ``code cloning''.
+
+Code cloning is an activity of reusing source code by copying and pasting.
+It normally occurs in software development and account from 7\% to 23\% in typical software systems \cite{Bellon2007}.
+The benefits and drawbacks of clones are still controversial.
+Several authors state that clones lead to bug propagations and software maintenance issues \cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial \cite{Saini2016,Kapser2006}.
+Code cloning can also have side effects of violating software licenses.
+Carelessly cloning code from one project and reusing it in another project with different license may cause software licensing violation \cite{German2009}.
+
+In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones.
+We call them ``online code clones''.
+There are three ways to create online code clones: 1) code is cloned from a software project to Stack Overflow as an example; 2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; and 3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium.
+Online code clones can similarly lead to a problem of bug propagation.
+However, they are harder to locate and fix since the search scope is no longer contained in a local repository.
+%Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
+This is an emerging and challenging problem.
+Since studies in this area are still limited, we aim to address this problem in this study.
+%We are interested to gain more insights of online code clone in this study.
 
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We processed 130,644,707 clone pairs and manually investigated 2,371 clone pairs between Java code fragments obtained from Stackoverflow accepted answers and 63 Java open source projects.
+We used two clone detection tools to discover 130,644,707 clone pairs and manually investigated 2,371 meaningful clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 63 Java open source projects.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and online Q\&A websites:} Our study shows that there are at least 48 clones that have been copied from open source projects to Stackoverflow as code examples which may violate their software license.
-Moreover, out of 48 clones, there are 27 clones in Stackoverflow that are outdated and dangerous for being reused.
+\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 48 clones that have been obviously copied from open source projects to Stack Overflow as code examples which violate their software licenses.
+Furthermore, 30 out of the 48 clones are outdated and dangerous for being reused.
 
-\section{Research Questions}
-The study aims to answer the following research questions: \\ 
-\textbf{RQ1 (online code clone):} \textit{To what extent  source code is reused between between Q\&A sites and open source projects?} We would like to observe whether this phenomenon has happened and at what scale.
+\section{Empirical Study}
+We perform an empirical study of online code clones between Stack Overflow and 63 Java open source projects to answer the following research questions: \\ 
+\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We would like to quantitatively measure the number of online code clones between Stack Overflow and open source projects.
 \newline
-\textbf{RQ2 (flow of online code clone):} \textit{what are the directions that source code have been reused?} If the code reuse between the two locations exist, we would like to discover the which direction the code that have been copied.
-Is it from Q\&A site to open source projects, or the other way around, or both?
+%\textbf{RQ2 (flow of online code clones):} \textit{what are the directions that source code is cloned?} If clones between the two locations exist, we would like to observe in which direction the code has been copied.
+Is it mostly from Stack Overflow to open source projects, or the other way around, or equally both?
 \newline
-\textbf{RQ3 (classification of online code clone):} \textit{How do the online code clones happen?} What are the major causes creating the online code clones? \newline
-\textbf{RQ4 (effects of online code clone):} \textit{ Is this phenomenon of online code clone harmful?} is there any evidence of problems caused by reusing code between Q\&A sites and open source projects?
+\textbf{RQ2 (classification of online code clones):} \textit{What are the main characteristics among the set of online code clones?} We group them into seven groups according to our pre-defined classification scheme.
+So we can understand the motivation of cloning.
+Some of the clones are copy from open source projects to Stack Overflow, while some are copied from a third-party location, and some are accidental clones containing boiler-plate code generated by IDE.
+\newline
+\textbf{RQ3 (effects of online code clones):} \textit{Are online code clones harmful?} Is there observable problems caused by clones between Stack Overflow and open source projects?
 
-\section{Experimental Setup}
+\subsection{Experimental Framework}
+The experimental framework is depicted in Figure \ref{}.
+We deploy two clone detection tools, Simian \cite{simian} and NICAD \cite{Roy2008,Cordy}, to locate clones between two locations: code snippets from Stack Overflow, and 63 open source projects.
+The clone report is pruned to contain only inter clone pairs between the two locations.
+In this step, all intra clone pairs within Stack Overflow and open source projects are removed.
+Next, clone pairs reported from the two clone detectors are matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
+This step generates \textbf{agreement-based clone pairs}.
+They are clones with highest confidence since they receive agreement from both of the tools.
+Then, clone pairs reported by Simian and NICAD that do not find agreement are ranked and selected.
+This step generates \textbf{non agreement-based clone pairs}.
+The non agreement-based clone pairs are clones with less confidence than agreement-based ones.
+Finally, agreement-based and selected non agreement-based clone pairs are looked at and classified manually.
 
-\subsection{Dataset}
-In our study, we selected the latest version of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects.
+In manual inspection process, we classify clones into categories according to their properties.
+This process took around three months until we successfully classified 2,371 clone pairs into categories.
+By ignoring clone pairs manually classified as false clones, we compare licensing information of remaining clone pairs to see if they have any licensing conflicts.
+Moreover, we look forward through history of the clones from the projects' versioning systems (GIT) to see if there is any changes made to the clones after it has been copied.
+
+\subsection{Experimental Setup}
+\subsubsection{Datasets}
+\textbf{Stack Overflow}: we extracted 144,075 Java code snippets from accepted answers in a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
+The archived dump has a size of 9 gigabytes.
+The data dump is in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts.
+We are interested in code snippets embedded in posts.
+Code snippet is a piece of code located between \texttt{<code></code>} tags.
+We filtered the snippets with two filtering criteria.
+First, we ignore snippets that are less than 6 lines since they are usually ignored by clone detection research \cite{something}.
+Second, we are only interested in code snippets from posts that are marked as ``accepted answer'' since they have high chances to be reused than snippets in questions and other answers.
+Each snippets is extracted from the dump using regular expressions and stored in a file with post ID as the file's name.
+We add \texttt{.java} as files' suffix so the clone detectors can recognise them.
+If a Stack Overflow conversation has more than one code snippet in an accepted answer, we append an indexing number starting from zero behind the ID (e.g.
+45051109\_0.java, and 45051109\_1.java).
+
+\textbf{Qualitas corpus}: we selected the latest version (20130901r) of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects.
 \textit{eclipse} project does not contain source code so it has been removed from the study resulting in totally 63 projects.
@@
 
-\subsection{Clone Detectors}
-We selected two clone detectors for this study: Simian \cite{simian} and NiCad \cite{Cordy,Roy2008}. \FIXME{Add more info about clone detection tools in general and more details of these two tools}
+\subsubsection{Clone Detectors}
+We selected two clone detectors for this study: Simian \cite{simian} and NICAD \cite{Cordy,Roy2008}.
+There is a few restrictions in terms of choosing clone detection tools for this study.
+First, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods.
+Hence, the tool must be flexible enough to process code snippets which are not in a complete block or compilable.
+This restriction forces us to remove two well-known clone detectors; CCFinder \cite{Kamiya2002}, and DECKARD \cite{Jiang2007a}; from our study since they failed to analyse the complete 144,075 Stack Overflow snippets.
+Second, since the amount of code that have to be process are large \FIXME{Find SLOC of 144,075 SO snippets and 63 projects}, the clone detector must be scalable enough to execute and report clones in a reasonable amount of time.
+We found that both Simian and NICAD are able to handle clones in this situation with an acceptable running time.
 
-\subsection{Agreement-based Clone Detection}
-We adopted an idea of clone agreement normally used in clone research \cite{Wang2013,Funaro2010}.
+\subsubsection{Agreement-based Clone Detection}
+Since we did not have the clone oracle of the two datasets, we adopted an idea of clone agreement used in clone research \cite{Wang2013,Funaro2010} to help filtering the reported clones for manual investigation.
 
 \section{Results}
-The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stackoverflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below.
+The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stack Overflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below.
 There are 2 tools selected: Simian and NiCad.
@@
 	\centering
-	\caption{Statistics of clones found between Stackoverflow and Qualitas projects using Simian and NiCad}
+	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
 	\label{t_simian_raw_results}
@@
 		\hline 
-		A & Code in Stackoverflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
+		A & Code in Stack Overflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
 		\hline 
-		A' & Code in Qualitas is copied from Stackoverflow (S $\rightarrow$ Q). \\ 
+		A' & Code in Qualitas is copied from Stack Overflow (S $\rightarrow$ Q). \\ 
 		\hline 
@@
 There are totally 608 \textit{ok-match} pairs that were investigated.
-The 39 true positive pairs found are combinations of 8 unique Stackoverflow fragments, and 9 unique Qualitas Java files from 6 different projects.
+The 39 true positive pairs found are combinations of 8 unique Stack Overflow fragments, and 9 unique Qualitas Java files from 6 different projects.
 
-Since we are not certain about the direction of copying in the B-classified pairs, we checked the modification time of each Java file in Qualitas project and compare it to the timestamp of Stackoverflow answers.
-We found that all Stackoverflow code fragments were posted after their respectively similar Java files in Qualitas project.
+Since we are not certain about the direction of copying in the B-classified pairs, we checked the modification time of each Java file in Qualitas project and compare it to the timestamp of Stack Overflow answers.
+We found that all Stack Overflow code fragments were posted after their respectively similar Java files in Qualitas project.
 This means that the copying can only be either (1) Q $\rightarrow$ S or (2) from a third source to both S and Q independently.
@@
 \subsection{Non-agreement based clone pairs}
-In the preliminary stage of our experiment, we found that there are 41 Stackoverflow fragments reported by Simian with default configurations.
+In the preliminary stage of our experiment, we found that there are 41 Stack Overflow fragments reported by Simian with default configurations.
 However, only 10 of them appear in the new results using tool's agreement.
@@
 
-%We selected only Stackoverflow fragment and Qualitas files that have never been looked at before in the previous investigation.
-If many clone pairs having the same Stackoverflow fragment and Qualitas file, we keep only the largest one.
-The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stackoverflow fragments or Qualitas files.
+%We selected only Stack Overflow fragment and Qualitas files that have never been looked at before in the previous investigation.
+If many clone pairs having the same Stack Overflow fragment and Qualitas file, we keep only the largest one.
+The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stack Overflow fragments or Qualitas files.
 The classification results are shown in Table \ref{tab:classification_indv}.
@@
 	\includegraphics[width=1\linewidth]{Sankey_proj}
-	\caption{Relationships between 184 true online code clone found between Stackoverflow and Qualitas projects}
+	\caption{Relationships between 184 true online code clone found between Stack Overflow and Qualitas projects}
 	\label{fig:sankey}
@@
 \subsection{Issue~1:~stale online code clones}
-Stale online code occurs when a piece of code has been copied from a software project to Stackoverflow, and later it has been changed in the original project.
+Stale online code occurs when a piece of code has been copied from a software project to Stack Overflow, and later it has been changed in the original project.
 However, in this situation, the copy is still unchanged.
-Since the code were updated due to various possible reasons including bug fixing, this can cause a problem if developers reuse stale online code from Q\&A websites such as Stackoverflow.
+Since the code were updated due to various possible reasons including bug fixing, this can cause a problem if developers reuse stale online code from Q\&A websites such as Stack Overflow.
 They might also introduce the same unfixed bug(s) into the software.
@@
 
-%Our intuition behind his issue comes from a situation where a piece of code has been copied from a Qualitas project and posted on Stackoverflow.
+%Our intuition behind his issue comes from a situation where a piece of code has been copied from a Qualitas project and posted on Stack Overflow.
 Later, that piece of code has been modified further to accommodate changes in the projects (or any other reasons).
-However, even the code in Qualitas project is already updated, the one posted on Stackoverflow is not changed.
+However, even the code in Qualitas project is already updated, the one posted on Stack Overflow is not changed.
 This results in outdated online code which can cause problems when programmers copy and use it in their projects.
@@
 Finally there were 134  pairs remaining.
-%We are interested in clone pairs that were changed after they appeared on Stackoverflow.
+%We are interested in clone pairs that were changed after they appeared on Stack Overflow.
 
 The manual investigation of 48 class-A online clone pairs reveals that there are 30 stale clones.
-They are clone pairs that were copied from Qualitas projects to Stackoverflow and marked as \textit{accepted} answers.
+They are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as \textit{accepted} answers.
 The investigation results are described in Table \ref{tab:stale_code}.
@@
 	\centering
-	\caption{30 stale code clones in Stackoverflow found by a manual investigation}
+	\caption{30 stale code clones in Stack Overflow found by a manual investigation}
 	\label{tab:stale_code_details}
@@
 		\hline 
-		No. & File & Stackoverflow Q\&A & Changes made & Date \\
+		No. & File & Stack Overflow Q\&A & Changes made & Date \\
 		\hline
@@
 In our study, we tackle another possible situation of software licensing issue caused by code cloning to Q\&A websites.
-We found that there are at least 48 pieces of code have been copied from 9 open source projects to Stackoverflow as examples.
+We found that there are at least 48 pieces of code have been copied from 9 open source projects to Stack Overflow as examples.
 These 9 open source projects come with software licenses.
@@
 %
-%The single missing Stackoverflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian.
+%The single missing Stack Overflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian.
 It is removed from the results of the pretty-printed version because it is an outlier.
@@
 However, the \texttt{-balanceSquareBrackets+} parameter only works on a small testing environment having toy programs or only small pairs from the full datasets.
-It does not work with the full complete set of 144,075 Stackoverflow fragments and Qualitas projects.
+It does not work with the full complete set of 144,075 Stack Overflow fragments and Qualitas projects.
 Please find the summary of all the testing scenarios in Table \ref{tab:summary}.
@@
 
-	\item Stackoverflow
+	\item Stack Overflow
 	\begin{itemize}
 		\item Code example \cite{Nasehi2012}
-		\item Search for code in Stackoverflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014}
+		\item Search for code in Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014}
 	\end{itemize}

### 2016-10-31 latex-acm/cloneoverflow.tex
Updated numbers

@@
 			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
-			& \multicolumn{3}{c|}{792 fragments} 
-			& \multicolumn{3}{c|}{1229 fragments}  
-			& \multicolumn{3}{c|}{1141 fragments} 
-			& \multicolumn{3}{c}{12400 fragments} \\ \cline{2-13}
+			& \multicolumn{3}{c|}{1406 fragments} 
+			& \multicolumn{3}{c|}{1360 fragments}  
+			& \multicolumn{3}{c|}{1197 fragments} 
+			& \multicolumn{3}{c}{12884 fragments} \\ \cline{2-13}
 			%& \multicolumn{3}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
@@
 			%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
-			Total & 24,929 & -- & -- & 16,957,362 & --	& -- & 105,118 	& -- & -- & 113,557,298 & -- & -- \\
-			Mean & 38 & 7.54 & 0.27 & 14,444 & 4.80 & 0.28 & 107 & 9.52 & 0.25 & 9,397 & 5.21 & 0.20 \\
-			Std Dev. & 87 & 3.21 & 0.22 & 281,747 & 1.22 & 0.18 & 198 & 3.07 & 0.18 & 12,098 & 1.73 & 0.16 \\
-			Max  & 551 & 49.00 & 0.94 & 9,599,676 & 18.00 & 0.89 & 1,792 & 39.00 & 0.80 & 227,077 & 44.00 & 0.86 \\
+			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
+			Mean & 52 & 7.45 & 0.28 		& 44104 & 4.81 & 0.29 		& 106 & 9.54 & 0.25 	& 16046 & 5.31 & 0.21 \\
+			Std Dev. & 147 & 3.22 & 0.23 	& 1040483 & 1.20 & 0.19 	& 209 & 3.10 & 0.18 	& 21890 & 1.92 & 0.16 \\
+			Max  & 1020 & 49.00 & 0.94 		& 38223637 & 18.00 & 0.89 	& 2100 & 39.00 & 0.81 	& 442655 & 50.00 & 0.93 \\
 			Min  & 1 & 5.00 & 0.01 			& 1 & 4.00 & 0.02 			& 1 & 7.00 & 0.02 		& 1 & 3.00 & 0.01 \\
-			Median  & 3 & 7.00 & 0.23 & 22 & 5.00 & 0.24 & 15 & 8.00 & 0.19 & 6,105 & 5.00 	& 0.15 \\
-			Mode  & 1 & 7.00 & 0.25 & 1 & 4.00 & 0.50 & 1 & 8.00 & 0.53 & 1 & 4.00 & 0.33 \\
+			Median  & 3 & 7.00 & 0.21 		& 24 & 5.00 & 0.25 			& 20 & 8.00 & 0.19 		& 8003 & 5.00 	& 0.16 \\
+			Mode  & 1 & 7.00 & 0.33 		& 1 & 4.00 & 0.50 			& 1 & 8.00 & 0.67 		& 1 & 4.00 & 0.33 \\
 			\hline
@@
 	\centering
-	\caption{63 Qualitas projects (new versions retrieved on 2016-09-27)}
+	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
 	\label{t:new_and_old}
@@
 		\hline
-		\textit{default} & \textit{default} & 9 	& 473 \\ 
-		\textit{default} & \textit{EvaClone} 	& 12 	& 353 \\ 
-		\textit{EvaClone} 	& \textit{default} 	& 7 	& 60 \\
-		\textit{EvaClone} 	& \textit{EvaClone} 	& 1,338 & 9528 \\ 
-		\hline
-		\multicolumn{2}{l|}{Total} & 1,366 & 10,414 \\
-		\hline
-		\multicolumn{2}{l|}{Total (unique)} & 1,357 & 10,139 \\
+		\textit{default} & \textit{default} & 10 	& 3800 \\ 
+		\textit{default} & \textit{EvaClone} 	& 26 	& 1017 \\ 
+		\textit{EvaClone} 	& \textit{default} 	& 10 	& 88 \\
+		\textit{EvaClone} 	& \textit{EvaClone} 	& 2228 & 19777 \\ 
+		\hline
+		\multicolumn{2}{l|}{Total} & 2274 & 24682 \\
+		\hline
+		\multicolumn{2}{l|}{Total (unique)} & 2261 & 23868 \\
 		\hline
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{venn4_pairs_good}
+		\includegraphics[width=0.9\linewidth]{venn4_pairs_good_pt1+2}
 		\caption{\textit{good}-match(0.7) pairs}
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok}
+		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok_pt1+2}
 		\caption{\textit{ok}-match(0.7) pairs}

### 2016-11-04 latex-acm/cloneoverflow.tex
Updated LaTeX

@@
 
+\FIXME{Add motivating example here}
+
 In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones.
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 130,644,707 clone pairs and manually investigated 2,371 meaningful clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 63 Java open source projects.
+We used two clone detection tools to discover 266,837,480 similar code fragment pairs and manually investigated x,xxx candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 109 Java open source projects.
 
@@
 We add \texttt{.java} as files' suffix so the clone detectors can recognise them.
-If a Stack Overflow conversation has more than one code snippet in an accepted answer, we append an indexing number starting from zero behind the ID (e.g.
+If a Stack Overflow conversation has more than one code snippet in the accepted answer, we append an indexing number starting from zero behind the ID (e.g.
 45051109\_0.java, and 45051109\_1.java).
 
-\textbf{Qualitas corpus}: we selected the latest version (20130901r) of Qualitas corpus \cite{QualitasCorpus} containing 64 Java open source projects.
-\textit{eclipse} project does not contain source code so it has been removed from the study resulting in totally 63 projects.
-The details of the 63 Qualitas projects with their respective licenses are listed in Table \ref{t:new_and_old}.
+\textbf{Qualitas corpus}: we selected the latest version (20130901r) of Qualitas corpus \cite{QualitasCorpus} containing 112 Java open source projects.
+Three projects (\textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}) do not contain source code so it has been removed from the study resulting in totally 109 projects.
+Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.
 
@@
 This restriction forces us to remove two well-known clone detectors; CCFinder \cite{Kamiya2002}, and DECKARD \cite{Jiang2007a}; from our study since they failed to analyse the complete 144,075 Stack Overflow snippets.
-Second, since the amount of code that have to be process are large \FIXME{Find SLOC of 144,075 SO snippets and 63 projects}, the clone detector must be scalable enough to execute and report clones in a reasonable amount of time.
+Second, since the amount of code that have to be process are large \FIXME{Find SLOC of 144,075 SO snippets and 109 projects}, the clone detector must be scalable enough to execute and report clones in a reasonable amount of time.
 We found that both Simian and NICAD are able to handle clones in this situation with an acceptable running time.
@@
 \section{Results}
-The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stack Overflow fragments (Java accepted answers) and 63 open-source projects in Qualitas dataset is presented below.
+The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stack Overflow fragments (Java accepted answers) and 109 open-source projects in Qualitas dataset is presented below.
 There are 2 tools selected: Simian and NiCad.
@@
 		\hline
-		\textit{Successful} & 63 & 63 & 57 & 46 \\ %& 44 & 40 & 34 \\
-		\textit{Clust.~fail} & - & - & 6 & 13 \\
-		\textit{Ren.~fail} & - &  - & 0 & 4 \\
+		\textit{Successful} & 109 & 109 & 97 & 82 \\ %& 44 & 40 & 34 \\
+		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
+		\textit{Renm.~fail} & -- &  -- & -- & 11 \\
 		\hline
@@
 			\hline
-			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD \\
-			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 \\
-			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 \\
-			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 \\
-			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 \\
-			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) \\
-			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 \\
-			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 \\
-			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 \\
-			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 \\
+			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD & \\
+			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 & \\
+			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 & \\
+			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 & \\
+			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 & \\
+			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) & \\
+			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
+			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 & \\
+			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
+			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\
 			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GLGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
-			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  \\
+			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\
 			colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
-			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  \\
-			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 \\
+			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  & \\
+			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 & \\
 			compiere & 330 & - & - & - & GPL 2.0 & No longer OSS \\
-			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 \\
-			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  \\
-			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 \\
+			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 & \\
+			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  & \\
+			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 & \\
 			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
 			exoportal & ??? & ??? &  & git & GLGPL 3.0 \& proprietary & Too many new projects \\
-			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 \\
-			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 \\
-			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 \\
-			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 \\
+			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
+			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 & \\
+			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
+			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 & \\
 			freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GPL 2.0 &  \\
@@
 			freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GPL 2.0+ &  \\
-			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 \\
+			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 & \\
 			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
-			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 \\
-			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 \\
-			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 \\
-			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ \\
-			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  \\
-			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 \\
-			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 \\
-			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 \\
-			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 \\
-			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 \\
-			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 \\
-			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 \\
+			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 & \\
+			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
+			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 & \\
+			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ & \\
+			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
+			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
+			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 & \\
+			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 & \\
+			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 & \\
+			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
+			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 & \\
+			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 & \\
 			jag & 6.1 & 6.2 & 08/04/2013  & - & GPL 2.0 \& BSD  & BSD  is for libraries. \\
-			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 \\
-			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  \\
+			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 & \\
+			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\
 			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0 &  \\
-			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) \\
+			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\
 			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GLGPL 2.1 & Renamed to Wildfly. \\
@@
 			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
-			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 \\
+			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 & \\
 			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
 			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0 &   \\
-			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) \\
-			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) \\
-			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 \\
-			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 \\
+			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
+			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) & \\
+			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 & \\
+			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\
 			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
-			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 \\
-			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 \\
-			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 \\
+			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 & \\
+			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
+			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\
 			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GLGPL 2.0 &  \\
 			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
+			\hline
+		\end{tabular} %
+%	}
+\end{table*}
+
+\begin{table*}
+	\centering
+	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
+	\label{t:new_and_old}
+	%	\resizebox{\columnwidth}{!}{%
+	\small
+	\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
+		\hline 
+			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
+			\hline
+			apache-jmeter & 2. 9 & & & & & \\
+			apache-log4j & 1.2.16 & & & & & \\
+			apache-maven & 3.0 & & & & & \\
+			apache-roller & 4.0.1 & & & & & \\
+			apache-tomcat & 7.0.2 & & & & & \\
+			jhotdraw & 7.5.1 & & & & & \\
+			jrefactory & 2.9.19 & & & & & \\
+			jruby & 1.5.2 & & & & & \\
+			jspwiki & 2.8.4 & & & & & \\
+			jstock & 1.0.7c & & & & & \\
+			jsxe & 04\_beta & & & & & \\
+			jtopen & 7\_1 & & & & & \\
+			jung2 & 2\_0\_1 & & & & & \\
+			lucene & 4.3.0 & & & & & \\
+			marauroa & 3.8.1 & & & & & \\
+			megamek & 0.35.18 & & & & & \\
+			mvnforum (mvnad) & 1.2.2 (1.0.1) & & & & & \\
+			myfaces-core & 2.0.2 & & & & & \\
+			nakedobjects & 4.0.0 & & & & & \\
+			nekohtml & 1.9.14 & & & & & \\
+			netbeans & 6.9.1 & & & & & \\
+			openjms & 0.7.7-beta-1 & & & & & \\
+			oscache & 2.4.1 & & & & & \\
+			picocontainer & 2.10.2 & & & & & \\
+			pmd & 4.2.5 & & & & & \\
+			poi & 3.6 & & & & & \\
+			pooka & 080505 & & & & & \\
+			proguard & 4.5.1 & & & & & \\
+			quartz & 1.8.3 & & & & & \\
+			quickserver & 1.4.7 & & & & & \\
+			quilt & 0.6-a-5 & & & & & \\
+			rssowl & 2.0.5 & & & & & \\
+			sablecc & 3.2 & & & & & \\
+			sandmark & & & & & & \\
+			spring-framework & 3.0.5 & & & & & \\
+			struts2 & 2.2.1-all & & & & & \\
+			sunflow & 0.07.2 & & & & & \\
+			tapestry & 5.1.0.5 & & & & & \\
+			trove & 2.1.0 & & & & & \\
+			velocity & 1.6.4 & & & & & \\
+			wct-package & 1.5.2 & & & & & \\
+			webmail & 0.7.10 & & & & & \\
+			weka & 3-7-9 & & & & & \\
+			xalan-j & 2\_7\_1 & & & & & \\
+			xerces-J & 2.10.0 & & & & & \\
+			xmojo & 5.0.0 & & & & & \\
 			\hline 
@@
 Nevertheless,  NiCad produced renaming and clustering errors for some of the settings.
-This resulted in not all 63 projects had NiCad clone reports.
+This resulted in not all 109 projects had NiCad clone reports.
 For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors.
@@
 	\small
+	\resizebox{2.1\columnwidth}{!}{%
 	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
@@
 		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 1  & 3 & \textbf{5} & 5 & 4 & 4 & 26  & 6 & 1320 & \textbf{1352} & 56 & 402 & 31 & \textbf{1357} & 61 & 406 & 32 \\
-		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 23  & 8 & \textbf{39} & 8 & 9 & 6 & 480 & 28 & 61 & \textbf{569} & 76 & 60 & 16 & \textbf{608} & 83 & 68 & 19 \\
+		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
+		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 33  & 8 & \textbf{49} & 12 & 14 & 10 & 4459 & 35 & 82 & \textbf{4576} & 99 & 136 & 29 & \textbf{4625} & 110 & 150 & 33 \\
 		\hline
 	\end{tabular} 
+}
 \end{table*}
@@
 %	\centering
-%	\caption{Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
-%	\label{tab:classification}
-%	\begin{tabular}{|l|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{5mm}|R{3mm}|R{7mm}|R{7mm}|R{3mm}|R{3mm}|R{3mm}|R{3mm}|R{7mm}|R{3mm}|R{7mm}|R{7mm}|}
-%		\hline
-%		\multirow{2}{*}{Classification}	& \multicolumn{8}{c|}{Qualitas-\textit{O}} & \multicolumn{8}{c|}{Qualitas-\textit{N}} \\ 	\cline{2-17}
-%		 & A & A' & B & C & D & E & F & Total 
-%		 & A & A' & B & C & D & E & F & Total \\ 
-%		\hline 
-%		\multirow{1}{*}{\textit{good-match(0.7)}} 
-%		& 1 & 0 & 1  & 3 & 26  & 6 & 1,369 & 1,406 
-%		& -- & -- & -- & -- & -- & -- & -- & --  \\ \cline{2-8}
-%		\hline
-%		\multirow{1}{*}{\textit{ok-match(0.7)}} 
-%		& 8  & 0 & 36 & 8 & 474 & 57 & 81 & 664 
-%		& 2 & 0 & 0 & 0 & 6,676 & 1 & 27 & 6,706 \\ \cline{2-8}
-%		\hline
-%		TP/FP
-%		& \multicolumn{4}{c|}{57} & \multicolumn{3}{c|}{2,013} & 2,070
-%		& \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{6,704} & 6,706 \\ 
-%		\hline
-%		Unique SO fragments & \multicolumn{4}{c|}{10} & & & & & \multicolumn{4}{c|}{1} & & & & \\
-%		\hline
-%		Unique Q files & \multicolumn{4}{c|}{13} & & & & & \multicolumn{4}{c|}{1} & & & & \\
-%		\hline
-%		Unique Q projects & \multicolumn{4}{c|}{8} & & & & & \multicolumn{4}{c|}{1} & & & & \\
+%	\caption{Distribution of classification category A--F according to \textit{good}- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
+%	\label{tab:good_classification}
+%	\small
+%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
+%		\hline 
+%		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
+%		\hline
+%		\hline
+%		\multicolumn{9}{|c|}{\textit{good}-match pairs} \\
+%		\hline
+%		S$_{df}$--N$_{df}$   & 1 & 0 & 1 & 0 & 1 & 4 & 0 & 7 \\
+%		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   & 1 & 0 & 0 & 3 & 14 & 1 & 1 & 20 \\
+%		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   & 0 & 0 & 3 & 0 & 7 & 0 & 0 & 10 \\
+%		S$_{\textrm{\textit{EvCl}}}$--N$_{\textrm{\textit{EvCl}}}$   & 0 & 0 & 1 & 0 & 20 & 0 & 2188 & 2228 \\
+%		\hline
+%		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1320  & 1366 \\
+%		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1320  & 1352 \\
+%		\hline
+%		\hline 
+%%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
+%%		\hline
+%		\multicolumn{9}{|c|}{\textit{ok}-match pairs} \\
+%		\hline
+%		S$_{df}$--N$_{df}$        & 3 	& 0 	& 12	& 6 	& 3755  & 8	& 7  &  3791 \\
+%		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   	& 8 	& 0 	& 28	& 4	& 904 & 29  & 32 &  1005 \\
+%		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   	& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
+%		\hline
+%		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
+%		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
 %		\hline
@@
 %\end{table}
-
-\begin{table}
-	\centering
-	\caption{Distribution of classification category A--F according to \textit{good}- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
-	\label{tab:good_classification}
-	\small
-	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
-		\hline 
-		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
-		\hline
-		\hline
-		\multicolumn{9}{|c|}{\textit{good}-match pairs} \\
-		\hline
-		S$_{df}$--N$_{df}$   & 1 & 0 & 1 & 3 & 0 & 4 & 0 & 9 \\
-		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   & 1 & 0 & 1 & 3 & 1 & 5 & 1 & 12 \\
-		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   & 0 & 0 & 0 & 0 & 7 & 0 & 0 & 7 \\
-		S$_{\textrm{\textit{EvCl}}}$--N$_{\textrm{\textit{EvCl}}}$   & 0 & 0 & 0 & 0 & 18 & 1 & 1319 & 1338 \\
-		\hline
-		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1320  & 1366 \\
-		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1320  & 1352 \\
-		\hline
-		\hline 
-%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
-%		\hline
-		\multicolumn{9}{|c|}{\textit{ok}-match pairs} \\
-		\hline
-		S$_{df}$--N$_{df}$        & 3 	& 0 	& 10	& 6 	& 433  & 5	& 7  &  464 \\
-		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   	& 8 	& 0 	& 22	& 4	& 250 & 25  & 32 &  341 \\
-		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   	& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
-		\hline
-		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
-		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
-		\hline
-	\end{tabular} 
-\end{table}
-
-%\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
-%We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvaClone}}}$, and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{df}$.
-We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
-The number of pairs that have been looked at is 6,706 (excluding duplicates).
-The results are shown in Table \ref{tab:classification_good_n}.
-%
-%\begin{table}
-%	\centering
-%	\caption{Qualitas-\textit{N}: Classification results of \textit{good-} and \textit{ok}-matches (excluding the subsumed \textit{good}-match pairs).}
-%	\label{tab:classification_good_n}
-%	\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
-%		\hline
-%		Classificaiton & A & A' & B & C & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & Sum & S$_{u}$ & Q$_u$ & Q$_{up}$ & Total  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
-%		\hline 
-%		\multirow{1}{*}{\textit{good-match(0.7)}}  & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - & - \\
-%		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 2 & 0 & 0 & 0 & & & & & 6676 & 1 & 27 & & & & & 6706 & & & \\
-%		\hline
-%	\end{tabular} 
-%\end{table}
-
-%\begin{table}
-%	\centering
-%	\caption{Classification results of 6,706 \textit{ok}-matches of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvaClone}}}$.}
-%	\label{tab:classification_new}
-%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
-%		\hline 
-%		Classification & A & A' & B & C & D & E & F & Total \\ 
-%		\hline
-%		\multirow{1}{*}{\textit{good-match(0.7)}} & -- & -- & -- & -- & -- & -- & -- & -- \\ \cline{2-8}
-%		\hline
-%		\multirow{1}{*}{\textit{ok-match(0.7)}}  \\ \cline{2-8}
-%		\hline
-%		\multirow{3}{*}{TP/FP} & \multicolumn{4}{c|}{2} & \multicolumn{3}{c|}{\multirow{3}{*}{6704}} & \multirow{3}{*}{6706} \\ 
-%		& \multicolumn{4}{l|}{\textit{1 unique SO fragments}} & \multicolumn{3}{c|}{} & \\
-%		& \multicolumn{4}{l|}{\textit{1 unique Q files}} & \multicolumn{3}{c|}{} & \\
-%		\hline
-%	\end{tabular} 
-%\end{table}
-
-%\begin{table}
-%	\centering
-%	\caption{Qualitas-\textit{N}: Distribution of classification category A--F  according to the \textit{ok}-match pairs}
-%	\label{tab:ok_classification_new}
-%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
-%		\hline 
-%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
-%		\hline
-%		Simian$_{df}$--NiCad$_{df}$ & 0 & 0	& 0 & 0 & 6603 & 1 & 0 & 6604 \\
-%		Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$ 
-%		& 2 	& 0 	& 0 	& 0 	& 73 	 & 0 	  & 4 		&  79 \\
-%		Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$   									
-%		& 0 	& 0 	& 0 	& 0 	 & 0 	  & 0 		& 23 	& 23 \\
-%		\hline
-%		Total   & 2  	&   0   & 0   	&  0   &   6676   &   1   & 27  & 6706 \\
-%		\hline
-%	\end{tabular} 
-%\end{table}
-
-%\begin{figure*}
-%	\centering
-%	\includegraphics[width=0.7\linewidth]{n+v+g}
-%	\caption{Qualitas projects categorised by NiCad's results, existence of newer versions, and version control}
-%	\label{fig:n+v+g}
-%\end{figure*}
 
@@
 		Tool & Clone pairs & \textit{ok}-pairs & filtered & remaining \\ 
-		\hline 
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 9383 & 140 & 8956 & 287 \\
-		\hline
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 7040  & 226 & 6700 & 114 \\
+		%\hline 
+		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
+		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
+		\hline
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 18425 & 140 & 17490 & 795 \\
+		\hline
+%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
+%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 29227  & 378 & 28690 & 159 \\
 		\hline
@@
 	\centering
-	\caption{Classification results of 292 Simian$_{df}$ and 114 NiCad$_{df}$ non agreement-based clone pairs.}
+	\caption{Classification results of 795 Simian$_{df}$ and 159 NiCad$_{df}$ non agreement-based clone pairs.}
 	\label{tab:classification_indv}
 	\small
+	\resizebox{2.1\columnwidth}{!}{%
 	\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|}
@@
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 89 & 7 & \textbf{133} & 68 & 57 & 23 & 13 & 10 & 133 & \textbf{159} & 39 & 69 & 23 & \textbf{287} & 103 & 121 & 31 \\
-		\hline
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
+%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
+%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 319 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
+		\hline
+%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
+%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 10 & 0 & \textbf{10} & 7 & 8 & 5 & 6 & 3 & 26 & \textbf{35} & 17 & 16 & 8 & \textbf{45} & 24 & 24 & 9 \\ 
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 15 & 0 & \textbf{19} & 15 & 13 & 9 & 30 & 6 & 104 & \textbf{140} & 51 & 55 & 20 & \textbf{159} & 66 & 68 & 23 \\ 
 		\hline
@@
 	\end{tabular} 
+}
 \end{table*}
@@
 	\centering
-	\caption{Numbers of true positives online clone pairs found by manual investigation}
+	\caption{Numbers of true positive online clone pairs found by manual investigation}
 	\label{tab:classification_true_pairs_summary}
@@
 		\hline
-		\textit{good}-pairs & 1 & 0 & 1 & 3 & 5 \\
-		\textit{ok}-pairs & 8 & 0 & 23 & 8 & 39 \\
-		Simian$_{df}$ pairs & 35 & 0 & 89 & 7 & 131 \\
-		NiCad$_{df}$ pairs & 4 & 0 & 5 & 0 & 9 \\
-		\hline 
-		Total & 48 & 0 & 118 & 18 & 184 \\
+		\textit{good}-pairs & 1 & 0 & 4 & 3 & 8 \\
+		\textit{ok}-pairs & 8 & 0 & 33 & 8 & 49 \\
+%		Simian$_{df}$ pairs-1 & 35 & 0 & 90 & 8 & 133 \\
+%		Simian$_{df}$ pairs-2 & 36 & 0 & 229 & 3 & 268 \\
+		Simian$_{df}$ pairs & 71 & 0 & 319 & 11 & 401 \\
+%		NiCad$_{df}$ pairs & 4 & 0 & 5 & 0 & 9 \\
+%		NiCad$_{df}$ pairs-2 & 0 & 0 & 10 & 0 & 10 \\
+		NiCad$_{df}$ pairs & 4 & 0 & 15 & 0 & 19 \\
+		\hline 
+		Total & 84 & 0 & 371 & 22 & 477 \\
 		\hline

### 2016-11-05 latex-acm/cloneoverflow.tex
Updated sankey diagram and latex file

@@
 
+%\begin{table*}
+%	\centering
+%	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
+%	\label{t:new_and_old}
+%%	\resizebox{\columnwidth}{!}{%
+%	\small
+%		\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
+%			\hline 
+%			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
+%			\hline
+%			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD & \\
+%			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 & \\
+%			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 & \\
+%			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 & \\
+%			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 & \\
+%			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) & \\
+%			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
+%			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 & \\
+%			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
+%			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\
+%			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GLGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
+%			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\
+%			colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
+%			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  & \\
+%			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 & \\
+%			compiere & 330 & - & - & - & GPL 2.0 & No longer OSS \\
+%			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 & \\
+%			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  & \\
+%			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 & \\
+%			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
+%			exoportal & ??? & ??? &  & git & GLGPL 3.0 \& proprietary & Too many new projects \\
+%			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
+%			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 & \\
+%			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
+%			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 & \\
+%			freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GPL 2.0 &  \\
+%			freecs & 1.3.20100406 & - & 22/04/2013 & - & GPL 3.0 &   \\
+%			freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GPL 2.0+ &  \\
+%			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 & \\
+%			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
+%			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 & \\
+%			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
+%			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 & \\
+%			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ & \\
+%			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
+%			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
+%			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 & \\
+%			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 & \\
+%			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 & \\
+%			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
+%			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 & \\
+%			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 & \\
+%			jag & 6.1 & 6.2 & 08/04/2013  & - & GPL 2.0 \& BSD  & BSD  is for libraries. \\
+%			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 & \\
+%			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\
+%			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0 &  \\
+%			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\
+%			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GLGPL 2.1 & Renamed to Wildfly. \\
+%			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GLGPL 2.1+ &  \\
+%			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
+%			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 & \\
+%			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
+%			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0 &   \\
+%			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
+%			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) & \\
+%			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 & \\
+%			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\
+%			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
+%			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 & \\
+%			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
+%			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\
+%			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GLGPL 2.0 &  \\
+%			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
+%			\hline
+%		\end{tabular} %
+%%	}
+%\end{table*}
+
 \begin{table*}
 	\centering
-	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
+	\caption{17 selected Qualitas projects (new versions retrieved on 2016-09-27)}
 	\label{t:new_and_old}
@@
 	\small
-		\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
-			\hline 
-			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
-			\hline
-			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD & \\
-			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 & \\
-			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 & \\
-			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 & \\
-			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 & \\
-			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) & \\
-			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
-			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 & \\
-			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
-			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\
-			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GLGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
-			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\
-			colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
-			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  & \\
-			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 & \\
-			compiere & 330 & - & - & - & GPL 2.0 & No longer OSS \\
-			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 & \\
-			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  & \\
-			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 & \\
-			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
-			exoportal & ??? & ??? &  & git & GLGPL 3.0 \& proprietary & Too many new projects \\
-			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
-			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 & \\
-			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
-			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 & \\
-			freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GPL 2.0 &  \\
-			freecs & 1.3.20100406 & - & 22/04/2013 & - & GPL 3.0 &   \\
-			freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GPL 2.0+ &  \\
-			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 & \\
-			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
-			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 & \\
-			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
-			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 & \\
-			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ & \\
-			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
-			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
-			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 & \\
-			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 & \\
-			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 & \\
-			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
-			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 & \\
-			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 & \\
-			jag & 6.1 & 6.2 & 08/04/2013  & - & GPL 2.0 \& BSD  & BSD  is for libraries. \\
-			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 & \\
-			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\
-			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0 &  \\
-			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\
-			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GLGPL 2.1 & Renamed to Wildfly. \\
-			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GLGPL 2.1+ &  \\
-			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
-			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 & \\
-			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
-			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0 &   \\
-			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
-			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) & \\
-			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 & \\
-			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\
-			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
-			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 & \\
-			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
-			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\
-			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GLGPL 2.0 &  \\
-			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
+	\begin{tabular}{l|r|r|c|c|p{3cm}}
+		\hline 
+		Projects & Old version & New versions & Latest change & CVS & License  \\
+		\hline
+		apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 \\
+		apache-log4j & 1.2.16 & & & & \\
+		apache-tomcat & 7.0.2 & & & & \\
+		aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse 1.0 \\
+		hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0\\
+		hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ \\
+		jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0  \\
+		jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0  \\
+		jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) \\
+		jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 \\
+		jstock & 1.0.7c & & & & \\
+		jung2 & 2\_0\_1 & & & & \\
+		junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 \\
+		poi & 3.6 & & & & \\
+		spring-framework & 3.0.5 & & & & \\
+		struts2 & 2.2.1-all & & & & \\
+		weka & 3-7-9 & & & & \\
 		\hline
@@
 
-\begin{table*}
-	\centering
-	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
-	\label{t:new_and_old}
-	%	\resizebox{\columnwidth}{!}{%
-	\small
-	\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
-		\hline 
-			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
-			\hline
-			apache-jmeter & 2. 9 & & & & & \\
-			apache-log4j & 1.2.16 & & & & & \\
-			apache-maven & 3.0 & & & & & \\
-			apache-roller & 4.0.1 & & & & & \\
-			apache-tomcat & 7.0.2 & & & & & \\
-			jhotdraw & 7.5.1 & & & & & \\
-			jrefactory & 2.9.19 & & & & & \\
-			jruby & 1.5.2 & & & & & \\
-			jspwiki & 2.8.4 & & & & & \\
-			jstock & 1.0.7c & & & & & \\
-			jsxe & 04\_beta & & & & & \\
-			jtopen & 7\_1 & & & & & \\
-			jung2 & 2\_0\_1 & & & & & \\
-			lucene & 4.3.0 & & & & & \\
-			marauroa & 3.8.1 & & & & & \\
-			megamek & 0.35.18 & & & & & \\
-			mvnforum (mvnad) & 1.2.2 (1.0.1) & & & & & \\
-			myfaces-core & 2.0.2 & & & & & \\
-			nakedobjects & 4.0.0 & & & & & \\
-			nekohtml & 1.9.14 & & & & & \\
-			netbeans & 6.9.1 & & & & & \\
-			openjms & 0.7.7-beta-1 & & & & & \\
-			oscache & 2.4.1 & & & & & \\
-			picocontainer & 2.10.2 & & & & & \\
-			pmd & 4.2.5 & & & & & \\
-			poi & 3.6 & & & & & \\
-			pooka & 080505 & & & & & \\
-			proguard & 4.5.1 & & & & & \\
-			quartz & 1.8.3 & & & & & \\
-			quickserver & 1.4.7 & & & & & \\
-			quilt & 0.6-a-5 & & & & & \\
-			rssowl & 2.0.5 & & & & & \\
-			sablecc & 3.2 & & & & & \\
-			sandmark & & & & & & \\
-			spring-framework & 3.0.5 & & & & & \\
-			struts2 & 2.2.1-all & & & & & \\
-			sunflow & 0.07.2 & & & & & \\
-			tapestry & 5.1.0.5 & & & & & \\
-			trove & 2.1.0 & & & & & \\
-			velocity & 1.6.4 & & & & & \\
-			wct-package & 1.5.2 & & & & & \\
-			webmail & 0.7.10 & & & & & \\
-			weka & 3-7-9 & & & & & \\
-			xalan-j & 2\_7\_1 & & & & & \\
-			xerces-J & 2.10.0 & & & & & \\
-			xmojo & 5.0.0 & & & & & \\
-			\hline 
-		\end{tabular} %
-%	}
-\end{table*}
+%\begin{table*}
+%	\centering
+%	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
+%	\label{t:new_and_old}
+%	%	\resizebox{\columnwidth}{!}{%
+%	\small
+%	\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
+%		\hline 
+%			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
+%			\hline
+%			apache-jmeter & 2. 9 & & & & & \\
+%			apache-log4j & 1.2.16 & & & & & \\
+%			apache-maven & 3.0 & & & & & \\
+%			apache-roller & 4.0.1 & & & & & \\
+%			apache-tomcat & 7.0.2 & & & & & \\
+%			jhotdraw & 7.5.1 & & & & & \\
+%			jrefactory & 2.9.19 & & & & & \\
+%			jruby & 1.5.2 & & & & & \\
+%			jspwiki & 2.8.4 & & & & & \\
+%			jstock & 1.0.7c & & & & & \\
+%			jsxe & 04\_beta & & & & & \\
+%			jtopen & 7\_1 & & & & & \\
+%			jung2 & 2\_0\_1 & & & & & \\
+%			lucene & 4.3.0 & & & & & \\
+%			marauroa & 3.8.1 & & & & & \\
+%			megamek & 0.35.18 & & & & & \\
+%			mvnforum (mvnad) & 1.2.2 (1.0.1) & & & & & \\
+%			myfaces-core & 2.0.2 & & & & & \\
+%			nakedobjects & 4.0.0 & & & & & \\
+%			nekohtml & 1.9.14 & & & & & \\
+%			netbeans & 6.9.1 & & & & & \\
+%			openjms & 0.7.7-beta-1 & & & & & \\
+%			oscache & 2.4.1 & & & & & \\
+%			picocontainer & 2.10.2 & & & & & \\
+%			pmd & 4.2.5 & & & & & \\
+%			poi & 3.6 & & & & & \\
+%			pooka & 080505 & & & & & \\
+%			proguard & 4.5.1 & & & & & \\
+%			quartz & 1.8.3 & & & & & \\
+%			quickserver & 1.4.7 & & & & & \\
+%			quilt & 0.6-a-5 & & & & & \\
+%			rssowl & 2.0.5 & & & & & \\
+%			sablecc & 3.2 & & & & & \\
+%			sandmark & & & & & & \\
+%			spring-framework & 3.0.5 & & & & & \\
+%			struts2 & 2.2.1-all & & & & & \\
+%			sunflow & 0.07.2 & & & & & \\
+%			tapestry & 5.1.0.5 & & & & & \\
+%			trove & 2.1.0 & & & & & \\
+%			velocity & 1.6.4 & & & & & \\
+%			wct-package & 1.5.2 & & & & & \\
+%			webmail & 0.7.10 & & & & & \\
+%			weka & 3-7-9 & & & & & \\
+%			xalan-j & 2\_7\_1 & & & & & \\
+%			xerces-J & 2.10.0 & & & & & \\
+%			xmojo & 5.0.0 & & & & & \\
+%			\hline 
+%		\end{tabular} %
+%%	}
+%\end{table*}
 
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=1\linewidth]{Sankey_proj}
-	\caption{Relationships between 184 true online code clone found between Stack Overflow and Qualitas projects}
+\begin{figure}
+	\centering
+	\includegraphics[width=1.2\linewidth]{Sankey_proj}
+	\caption{Relationships of 49 outdated clone pairs and 4 deleted clone pairs (depicted using (d) suffix)}
 	\label{fig:sankey}
-\end{figure*}
+\end{figure}
 
@@
 
-The manual investigation of 48 class-A online clone pairs reveals that there are 30 stale clones.
-They are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as \textit{accepted} answers.
-The investigation results are described in Table \ref{tab:stale_code}.
+Table \ref{tab:stale_code} shows the results of manual investigation of 84 class-A online clone pairs.
+The investigation reveals that there are 50 clone pairs that are outdate (i.e.
+``stale clone'').
+They are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as \textit{accepted} answers, and later have been changed during the development.
 
@@
 	\centering
-	\caption{Summary of stale code clones found}
+	\caption{Results from a manual investigation of 84 class-A online clone pairs}
 	\label{tab:stale_code}
 	\small
-	\begin{tabular}{l|r|r|r}
-		\hline 
-		Project & Pairs & Stale & Fresh \\
-		\hline
-		apache-ant & 1 & 0 & 1 \\
-		aspectj & 2 & 2 & 0 \\
-		hadoop & 14 & 9 & 5 \\
-		hibernate & 16 & 5 & 11 \\
-		jasperreports & 2 & 2 & 0 \\
-		jfreechart & 4 & 4 & 0 \\
-		jgraph & 5 & 5 & 0 \\
-		jgrapht & 1 & 0 & 1 \\
-		junit & 3 & 3 & 0 \\
-		\hline
-		Total & 48 & 30 & 18 \\
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r|r}
+		\hline 
+		Project & Pairs & Stale & Fresh & Del. & Others \\
+		\hline
+		ant & 1 & 0 & 1 & 0 & 0 \\
+		log4j & 4 & 0 & 4 & 0 & 0 \\
+		tomcat & 7 & 7 & 0 & 0 & 0 \\
+		aspectj & 2 & 2 & 0 & 0 & 0 \\
+		hadoop & 14 & 9 & 5 & 0 & 0 \\
+		hibernate & 16 & 4 & 11 & 1 & 0 \\
+		jasperreports & 2 & 2 & 0 & 0 & 0 \\
+		jfreechart & 4 & 4 & 0 & 0 & 0 \\
+		jgraph & 5 & 4 & 0 & 0 & 1 \\
+		jgrapht & 1 & 0 & 1 & 0 & 0 \\
+		jstock & 2 &  2 & 0 & 0 & 0 \\
+		jung & 2 & 2 & 0 & 0 & 0 \\
+		junit & 3 & 3 & 0 & 0 & 0 \\
+		poi & 3 & 1 & 2 & 0 & 0 \\
+		spring & 14 & 9 & 3 & 2 & 0 \\
+		struts & 1 & 1 & 0 & 0 & 0 \\
+		weka & 3 & 0 & 3 & 0 & 0 \\
+		\hline
+		Total & 84 & 50 & 30 & 3 & 1 \\
 		\hline
 	\end{tabular} 
+}
 \end{table}
@@
 	\centering
-	\caption{30 stale code clones in Stack Overflow found by a manual investigation}
+	\caption{53 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted}
 	\label{tab:stale_code_details}
 	\small
-	\begin{tabular}{r|l|r|c|l}
-		\hline 
-		No. & File & Stack Overflow Q\&A & Changes made & Date \\
-		\hline
-		1 & aspectjtools1.6.9-src/../Agent.java & 18303692 & alteration & 2015-09-08 \\
-		2 & aspectjweaver1.6.9-src/../Agent.java & 18303692 & alteration & 2015-09-08 \\
-		3 & hadoop-1.0.0/../WritableComparator.java & 22315734 & alteration & 2014-11-20 \\
-		4 & hadoop-1.0.0/../StringUtils.java & 801987 & alteration & 2013-02-04 \\
-		5 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & alteration & 2011-06-12 \\
-		6 & hadoop-1.0.0/../DBCountPageView.java & 21702608 & alteration & 2011-06-12 \\
-		7 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & alteration & 2011-07-25 \\
-		8 & hadoop-1.0.0/../LineRecordReader.java & 16180910 & alteration & 2011-07-25 \\
-		9 & hadoop-1.0.0/../JobSubmissionFiles.java & 14845581 & alteration & 2012-06-25 \\
-		10 & hadoop-1.0.0/../TextOutputFormat.java & 16928749 & alteration & 2011-06-12 \\
-		11 & hadoop-1.0.0/../TestJobCounters.java & 18833798 & alteration & 2011-06-12 \\
-		12 & hibernate-release-4.2.2.Final/../SettingsFactory.java & 8257554 & removal & 2011-03-11 \\
-		13 & hibernate-release-4.2.2.Final/../Example.java & 24924255 & alteration & 2013-04-23 \\
-		14 & hibernate-release-4.2.2.Final/../SQLServer2005LimitHandler.java.java & 23967852 & alteration & 2013-04-23 \\
-		15 & hibernate-release-4.2.2.Final/../ConnectionProviderInitiator.java & 15168494 & alteration & 2016-02-24 \\
-		16 & hibernate-release-4.2.2.Final/../SchemaUpdate.java & 23520731 & alteration & 2016-02-05 \\
-		17 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & removal & 2011-05-20 \\
-		18 & jasperreports-3.7.4/../JRVerifier.java & 8037824 & alteration & 2013-12-08 \\
-		19 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & alteration & 2013-11-22 \\
-		20 & jasperreports-3.7.4/../SpiderWebPlot.java & 21998949 & alteration & 2013-11-22 \\
-		21 & jasperreports-3.7.4/../AbstractXYItemRenderer.java & 12936580 & alteration & 2016-01-16 \\
-		22 & jfreechart-1.0.13/../KeyToGroupMap.java & 16058183 & alteration & 2013-07-03 \\
-		23 & jgraph-latest-bsd-src/../GroupingRemoving.java & 6722760 & rewriting & 2005 \\
-		24 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
-		25 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
-		26 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
-		27 & jgraph-latest-bsd-src/../HelloWorld.java & 6722760 & rewriting & 2005 \\
-		28 & junit-4/org/junit/Assert.java & 23586872 & alteration & 2015-05-12 \\
-		29 & junit-4/../ExpectException.java & 8802082 & alteration & 2014-05-26 \\
-		30 & junit-4/../ExternalResource.java & 7504040 & alteration & 2016-06-25 \\
+	\begin{tabular}{r|l|l|r|c|l}
+		\hline 
+		No. & Project & File & SO Post & Changes & Date \\
+		\hline
+		1 &  aspectj-1.6.9  &  Agent.java  & 18303692 &  alteration  & 2015-09-08 \\
+		2 &  aspectj-1.6.9   &  Agent.java  & 18303692 &  alteration  & 2015-09-08 \\
+		3 &  hadoop-1.0.0  &  DBCountPageView.java  & 21702608 &  alteration & 2011-06-12 \\
+		4 &  hadoop-1.0.0  &  DBCountPageView.java  & 21702608 &  alteration  & 2011-06-12 \\
+		5 &  hadoop-1.0.0  &  JobSubmissionFiles.java  & 14845581 &  alteration  & 2012-06-25 \\
+		6 &  hadoop-1.0.0  &  LineRecordReader.java  & 16180910 &  alteration & 2011-07-25 \\
+		7 &  hadoop-1.0.0  &  LineRecordReader.java  & 16180910 &  alteration  & 2011-07-25 \\
+		8 &  hadoop-1.0.0  &  StringUtils.java  & 801987 &  alteration & 2013-02-04 \\
+		9 &  hadoop-1.0.0  &  TestJobCounters.java  & 18833798 &  alteration  & 2011-06-12 \\
+		10 &  hadoop-1.0.0  &  TextOutputFormat.java  & 16928749 &  alteration  & 2011-06-12 \\
+		11 &  hadoop-1.0.0  &  WritableComparator.java  & 22315734 &  alteration & 2014-11-20 \\
+		12 &  hibernate-4.2.2  &  ConnectionProviderInitiator.java  & 15168494 &  alteration  & 2012-06-24 \\
+		13 &  hibernate-4.2.2  &  Example.java  & 24924255 &  alteration  & 2013-04-23 \\
+		14 &  hibernate-4.2.2  &  SchemaUpdate.java  & 23520731 &  alteration & 2016-02-05 \\
+		15 &  hibernate-4.2.2  &  SettingsFactory.java  & 8257554 &  removal & 2011-03-11 \\
+		16 &  hibernate-4.2.2  &  SQLServer2005LimitHandler.java  & 23967852 &  alteration  & 2015-03-12 \\
+		17 &  jasperreports-3.7.4  &  JRVerifier.java  & 8037824 &  alteration  & 2008-04-17 \\
+		18 &  jasperreports-3.7.4  &  JRVerifier.java  & 8037824 &  alteration & 2011-05-20 \\
+		19 &  jfreechart-1.0.13  &  AbstractXYItemRenderer.java  & 12936580 &  alteration  & 2016-02-19 \\
+		20 &  jfreechart-1.0.13  &  KeyToGroupMap.java  & 16058183 &  alteration  & 2013-07-03 \\
+		21 &  jfreechart-1.0.13  &  SpiderWebPlot.java  & 21998949 &  alteration  & 2008-06-02 \\
+		22 &  jfreechart-1.0.13  &  SpiderWebPlot.java  & 21998949 &  alteration  & 2008-06-02 \\
+		23 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
+		24 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
+		25 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
+		26 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
+		27 &  jstock-1.0.7c  &  GoogleMail.java  & 14940863 &  alteration & 2015-12-13 \\
+		28 &  jstock-1.0.7c  &  GoogleMail.java  & 24680923 &  alteration  & 2015-12-13 \\
+		29 &  jung2-2\_0\_1  &  ShortestPathDemo.java  & 6025026 &  alteration  & 2010-04-13 \\
+		30 &  jung2-2\_0\_1  &  ShortestPathDemo.java  & 6025026 &  alteration  & 2010-04-13 \\
+		31 &  junit-4  &  Assert.java  & 23586872 &  alteration  & 2015-05-12 \\
+		32 &  junit-4  &  ExternalResource.java  & 7504040 &  alteration & 2016-06-25 \\
+		33 &  junit-4.11  &  ExpectException.java  & 8802082 &  alteration & 2014-05-26 \\
+		34 &  poi-3.6-20091214  &  WorkbookFactory.java  & 12593810 &  alteration  & 2015-04-29 \\
+		35 &  spring-framework-3.0.5  &  AnnotationMethodHandlerExceptionResolver.java  & 5660519 &  removal & 2012-01-20 \\
+		36 &  spring-framework-3.0.5  &  AutowireUtils.java  & 20913543 &  alteration  & 2014-10-28 \\
+		37 &  spring-framework-3.0.5  &  CustomCollectionEditor.java  & 18623736 &  alteration  & 2013-11-21 \\
+		38 &  spring-framework-3.0.5  &  DefaultAnnotationHandlerMapping.java  & 3758110 &  removal  & 2012-01-20 \\
+		39 &  spring-framework-3.0.5  &  DefaultPropertiesPersister.java  & 6149818 &  alteration  & 2013-03-19 \\
+		40 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2016-07-15 \\
+		41 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2008-12-18 \\
+		42 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2008-12-18 \\
+		43 &  spring-framework-3.0.5  &  DispatcherServlet.java  & 4781746 &  alteration  & 2011-08-08 \\
+		44 &  spring-framework-3.0.5  &  Jaxb2Marshaller.java  & 10924700 &  alteration  & 2012-08-28 \\
+		45 &  spring-framework-3.0.5  &  ScheduledTasksBeanDefinitionParser.java  & 3751463 &  alteration  & 2016-07-05 \\
+		46 &  struts2-2.2.1  &  DefaultActionMapper.java  & 14019840 &  alteration  & 2013-10-18 \\
+		47 &  tomcat-7.0.2  &  BasicAuthenticator.java  & 21734562 &  alteration  & 2016-08-04 \\
+		48 &  tomcat-7.0.2  &  BasicAuthenticator.java  & 21734562 &  alteration & 2016-08-04 \\
+		49 &  tomcat-7.0.2  &  CoyoteAdapter.java  & 24404964 &  alteration  & 2012-11-18 \\
+		50 &  tomcat-7.0.2  &  CoyoteAdapter.java  & 24404964 &  alteration  & 2012-11-18 \\
+		51 &  tomcat-7.0.2  &  FormAuthenticator.java  & 21734562 &  alteration & 2016-08-04 \\
+		52 &  tomcat-7.0.2  &  HttpServlet.java  & 5266856 &  alteration  & 2011-10-22 \\
+		53 &  tomcat-7.0.2  &  JspRuntimeLibrary.java  & 10289462 &  alteration  & 2012-09-12 \\
 		\hline

### 2016-11-07 latex-acm/cloneoverflow.tex
Update LaTeX and Sankey diagram

@@
 \usepackage{ragged2e}
+\usepackage{cleveref}
 \newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
+
+\lstset{language=Java,tabsize=2,basicstyle=\ttfamily\scriptsize}
+
+\newcommand{\squeezeup}{\vspace{-0.5mm}}
 
@@
 
-\newcommand{\squeezeup}{\vspace{-2.5mm}}
 \newcommand\FIXME[1]{\textbf{FIXME: #1}}
@@
 It can be copied and modified from the problematic code snippet in the question, copied from an answerer's own code, or borrowed from other locations including open source software (OSS) systems.
-As a result, the process of posting and answering questions on Stack Overflow which involves copying and pasting source code can be considered as ``code cloning''.
+As a result, the process of posting and answering questions on Stack Overflow which involves copying and pasting source code can be considered as code cloning.
 
@@
 
-\FIXME{Add motivating example here}
-
 In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones.
-We call them ``online code clones''.
+We call them \textbf{online code clones}.
 There are three ways to create online code clones: 1) code is cloned from a software project to Stack Overflow as an example; 2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; and 3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium.
-Online code clones can similarly lead to a problem of bug propagation.
-However, they are harder to locate and fix since the search scope is no longer contained in a local repository.
+Online code clones can similarly lead to a problem of bug propagation as classical code clones.
+Unfortunately, they are more difficult to locate and fix since the search space from online corpora is larger and no longer confined in a local repository.
+
+A motivating example of problems caused by online code clones can be found in a Stack Overflow post regarding how to implement RawComparator in Hadoop\footnote{http://stackoverflow.com/questions/22262310}.
+In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
+The snippet shows how Hadoop implements \textit{compare} method in its \textit{WritableComparator} class.
+The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of Hadoop.
+We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, added in the latest version after \verb|key2.readFields(buffer);|.
+The added line is intended for cleaning up the reference in \verb|buffer| variable.
+While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged and outdated.
+This example shows that there can be inconsistencies between online code clones and its original.
 %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
 This is an emerging and challenging problem.
-Since studies in this area are still limited, we aim to address this problem in this study.
+Since studies in this area are still limited, we aim to gain more insight of the problem in this study.
 %We are interested to gain more insights of online code clone in this study.
+
+\begin{figure*}
+\begin{lstlisting}
+/* Code in Stack Overflow #22315734 */                      /* WritableComparator.java (2016-09-26) */
+1 public int compare (byte[] b1,int s1,int l1,              1 public int compare(byte[] b1,int s1,int l1,
+2                     byte[] b2,int s2,int l2) {            2                    byte[] b2,int s2,int l2) {
+3   try {                                                   3   try {
+4     buffer.reset(b1,s1,l1); /* parse key1 */              4     buffer.reset(b1,s1,l1); /* parse key1 */
+5     key1.readFields(buffer);                              5     key1.readFields(buffer);
+6     buffer.reset(b2,s2,l2); /* parse key2 */              6     buffer.reset(b2,s2,l2); /* parse key2 */
+7     key2.readFields(buffer);                              7     key2.readFields(buffer);
+8   } catch (IOException e) {                               8     buffer.reset(null,0,0); /* clean up reference */
+9     throw new RuntimeException(e);                        9   } catch (IOException e) {
+10   }                                                      10    throw new RuntimeException(e);
+11   return compare(key1,key2); /* compare them */          11  }
+12 }                                                        12  return compare(key1, key2); /* compare them */
+                                                            13 }
+\end{lstlisting}
+\caption{The same code fragments, WritableComparator.java, on Stack Overflow post 22315734 and latest version in hadoop code base}
+\label{fig:before-after}
+\end{figure*}
 
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 266,837,480 similar code fragment pairs and manually investigated x,xxx candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 109 Java open source projects.
+We used two clone detection tools to discover 266,837,480 similar code fragment pairs and manually investigated 7,840 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 109 Java open source projects.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 48 clones that have been obviously copied from open source projects to Stack Overflow as code examples which violate their software licenses.
-Furthermore, 30 out of the 48 clones are outdated and dangerous for being reused.
+\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 84 clones that have been obviously copied from open source projects to Stack Overflow as code examples which potentially violate their software licenses.
+Furthermore, 50 out of the 84 clones are outdated and questionable for being reused.
 
 \section{Empirical Study}
-We perform an empirical study of online code clones between Stack Overflow and 63 Java open source projects to answer the following research questions: \\ 
-\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We would like to quantitatively measure the number of online code clones between Stack Overflow and open source projects.
+We perform an empirical study of online code clones between Stack Overflow and 109 Java open source projects to answer the following research questions: \\ 
+\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We would like to quantitatively measure the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem.
 \newline
@@
 \newline
-\textbf{RQ2 (classification of online code clones):} \textit{What are the main characteristics among the set of online code clones?} We group them into seven groups according to our pre-defined classification scheme.
-So we can understand the motivation of cloning.
-Some of the clones are copy from open source projects to Stack Overflow, while some are copied from a third-party location, and some are accidental clones containing boiler-plate code generated by IDE.
+\textbf{RQ2 (classification of online code clones):} \textit{What are the main characteristics among the set of online code clones?} We group them into seven groups according to our pre-defined classification scheme so we can differentiate and understand the motivation of cloning.
+Some of the clones are copy from open source projects to Stack Overflow, while some are copied from a third-party location, and some are accidental clones containing boiler-plate code, and code stubs generated by IDE.
 \newline
-\textbf{RQ3 (effects of online code clones):} \textit{Are online code clones harmful?} Is there observable problems caused by clones between Stack Overflow and open source projects?
+\textbf{RQ3 (effects of online code clones):} \textit{what are the effects derived from online code clones?
+can they be harmful to software development?} Is there observable problems caused by clones between Stack Overflow and open source projects?
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.9\linewidth]{exp_framework}
+	\caption{Experimental framework}
+	\label{fig:exp_framework}
+\end{figure*}
 
 \subsection{Experimental Framework}
-The experimental framework is depicted in Figure \ref{}.
-We deploy two clone detection tools, Simian \cite{simian} and NICAD \cite{Roy2008,Cordy}, to locate clones between two locations: code snippets from Stack Overflow, and 63 open source projects.
-The clone report is pruned to contain only inter clone pairs between the two locations.
+To answer the three research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}.
+We process two datasets, Stack Overflow and open source projects from Qualitas corpus.
+Java code fragments are extracted from Stack Overflow posts using regular expressions.
+We pre-process Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection.
+Then, we deploy two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets.
+Due to a technical limit of Simian and NiCad to scale to large datasets, we partition the input and run the tools multiple times.
+Each run is composed of the whole Stack Overflow data and a single Qualitas project.
+We repeat the process until we cover 109 projects.
+
+We then convert the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combine them into a single file.
+GCF provides a common format for clones which enable us to reuse scripts that analyse clone reports from Simian and NiCad.
+Moreover, using GCF, other additional clone detectors can be adopted, if needed, without any changes in the analysis.
+Simian do not provide an option to detect inter clones between two locations.
+Hence the Simian GCF clone report is pruned to contain only inter clone pairs between Stack Overflow and Qualitas project.
 In this step, all intra clone pairs within Stack Overflow and open source projects are removed.
-Next, clone pairs reported from the two clone detectors are matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
+NiCad provides an option to detect inter clones so no pruning is needed.
+Next, clone pairs reported from the two clone detectors are pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
 This step generates \textbf{agreement-based clone pairs}.
-They are clones with highest confidence since they receive agreement from both of the tools.
-Then, clone pairs reported by Simian and NICAD that do not find agreement are ranked and selected.
+They are clones with highest confidence since they receive agreement from both tools.
+Then, clone pairs reported by Simian and NiCad that do not find agreement are filtered by size of minimum 10 lines.
 This step generates \textbf{non agreement-based clone pairs}.
 The non agreement-based clone pairs are clones with less confidence than agreement-based ones.
-Finally, agreement-based and selected non agreement-based clone pairs are looked at and classified manually.
-
-In manual inspection process, we classify clones into categories according to their properties.
-This process took around three months until we successfully classified 2,371 clone pairs into categories.
-By ignoring clone pairs manually classified as false clones, we compare licensing information of remaining clone pairs to see if they have any licensing conflicts.
-Moreover, we look forward through history of the clones from the projects' versioning systems (GIT) to see if there is any changes made to the clones after it has been copied.
+Finally, agreement-based and non agreement-based clone pairs are looked at and classified manually by the first author.
+
+In the manual inspection process, we classify clones into categories according to their properties.
+This process takes approximately a months until we successfully classified 7,840 clone pairs into categories.
+Some of the clone candidates are false clones due to being boiler-plate code or IDE-generated and are discarded for further analysis.
+By ignoring the false clones, we compare licensing information of x,xxx remaining clone pairs for possibility of software licensing violations.
+Moreover, we look forward through history of the clones from the projects' git versioning systems.
+This is to see if there is any changes made to the clones after it has been copied, hence resulting in outdated clones on Stack Overflow.
 
 \subsection{Experimental Setup}
+
 \subsubsection{Datasets}
-\textbf{Stack Overflow}: we extracted 144,075 Java code snippets from accepted answers in a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
+\begin{table}
+	\centering
+	\caption{Stack Overflow and Qualitas datasets}
+	\label{tab:datasets}
+	\small
+	\begin{tabular}{l|r|r}
+		\hline 
+		Dataset & No. of files & SLOC \\
+		\hline
+		Stack Overflow & 144,075 & 2,347,269 \\ 
+		\hline 
+		Qualitas &  138,238 & 16,081,899 \\ 
+		\hline 
+	\end{tabular} 
+\end{table}
+
+\textbf{Stack Overflow}: we extracted Java code snippets from accepted answers in a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
 The archived dump has a size of 9 gigabytes.
 The data dump is in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts.
-We are interested in code snippets embedded in posts.
-Code snippet is a piece of code located between \texttt{<code></code>} tags.
+We are interested in code snippets embedded in posts which are pieces of code located between \texttt{<code></code>} tags.
 We filtered the snippets with two filtering criteria.
-First, we ignore snippets that are less than 6 lines since they are usually ignored by clone detection research \cite{something}.
-Second, we are only interested in code snippets from posts that are marked as ``accepted answer'' since they have high chances to be reused than snippets in questions and other answers.
-Each snippets is extracted from the dump using regular expressions and stored in a file with post ID as the file's name.
-We add \texttt{.java} as files' suffix so the clone detectors can recognise them.
-If a Stack Overflow conversation has more than one code snippet in the accepted answer, we append an indexing number starting from zero behind the ID (e.g.
+First, we ignore snippets that are less than 6 lines since they are usually not considered as clones by clone detection research \cite{something}.
+Second, we are only interested in code snippets from posts that are marked accepted answer since they have high chances to be reused than snippets in questions and other answers.
+Each snippet is extracted from the dump using regular expressions and saved to a file using its post ID as the file's name.
+We use \texttt{.java} extension so that the clone detectors can recognise them.
+If a Stack Overflow conversation has more than one code snippet in the accepted answer, we append an indexing number starting from zero after the post ID (e.g.
 45051109\_0.java, and 45051109\_1.java).
-
-\textbf{Qualitas corpus}: we selected the latest version (20130901r) of Qualitas corpus \cite{QualitasCorpus} containing 112 Java open source projects.
-Three projects (\textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}) do not contain source code so it has been removed from the study resulting in totally 109 projects.
-Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.
+With the two filters, we finally obtained 144,075 Java code snippets which contain xxx lines of Java source code excluding comments and blank lines\footnote{measured by cloc: https://github.com/AlDanial/cloc}.
+
+\textbf{Qualitas corpus}: we selected an established corpus for empirical software engineering studies called Qualitas \cite{QualitasCorpus}.
+\FIXME{more details about Qualitas and why we chose it}.
+We selected the 20130901r version of Qualitas corpus containing 112 Java open source projects with releases no later than 1st September 2013.
+We chose the snapshot in 2013 since we are interested in online code clones from old releases of the software.
+Out of 112 Qualitas projects, there are 3 projects, \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}, that do not contain source code so they were removed from the study.
+This results in totally 109 projects analysed in the study.
+As shown in \Cref{tab:datasets}, the 109 Qualitas project have 138,238 Java files containing 16,081,899 lines of code.
+%Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.
 
 \subsubsection{Clone Detectors}
-We selected two clone detectors for this study: Simian \cite{simian} and NICAD \cite{Cordy,Roy2008}.
-There is a few restrictions in terms of choosing clone detection tools for this study.
-First, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods.
-Hence, the tool must be flexible enough to process code snippets which are not in a complete block or compilable.
-This restriction forces us to remove two well-known clone detectors; CCFinder \cite{Kamiya2002}, and DECKARD \cite{Jiang2007a}; from our study since they failed to analyse the complete 144,075 Stack Overflow snippets.
-Second, since the amount of code that have to be process are large \FIXME{Find SLOC of 144,075 SO snippets and 109 projects}, the clone detector must be scalable enough to execute and report clones in a reasonable amount of time.
-We found that both Simian and NICAD are able to handle clones in this situation with an acceptable running time.
+There are certain restrictions in terms of choosing clone detection tools for this study.
+Firstly, they have to compatible with Java.
+Secondly, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods.
+Hence, the tool must be flexible enough to process code snippets which are not in a complete block or not compilable.
+Thirdly, since the amount of code that have to be process are in a scale of millions line of source code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to be able to successfully complete the execution and report clones in a reasonable amount of time.
+These restrictions force us to remove three well-known clone detectors; CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a}; from our study since they failed to detect clones between 144,075 Stack Overflow code snippets and 109 Qualitas projects.
+We finally selected two clone detectors for this study: \textbf{Simian} \cite{simian} and \textbf{NiCad} \cite{Cordy,Roy2008}.
+We found that both of them are flexible enough to handle million-SLOC code corpus with method or class incompleteness.
+
+Simian is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies \cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}.
+It is a command-line tool which enables us to automate the detection.
+It also offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect clones of type 1 and type 2.
+NiCad is also a text-based clone detector which detects clones at method or code block granularity.
+It can detect clone up to type 3 and is used in several clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
+It utilises TXL for parsing and pretty-printing source code.
+It also provide code normalisation by variable renaming and abstractions.
+We use a variant of NiCad called \textit{nicadcross}.
+It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems.
 
 \subsubsection{Agreement-based Clone Detection}
-Since we did not have the clone oracle of the two datasets, we adopted an idea of clone agreement used in clone research \cite{Wang2013,Funaro2010} to help filtering the reported clones for manual investigation.
+Since we do not have clone oracle of the two datasets, we adopted an idea of clone agreement used in clone research \cite{Wang2013,Funaro2010,cr2016ssbse} to help reducing the number of clones for manual investigation.
+To find agreement of two clone pairs, we resort to an approach proposed by a study by another study~\cite{Bellon2007}.
+
+According to Bellon et al.~\cite{Bellon2007}, \textit{good} and \textit{ok}-match clone pairs are defined as follows.
+A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}: \textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).
+For each clone pair, we can define \textit{overlap} and \textit{contained} value of two clone pairs as
+\squeezeup
+\begin{multline}
+	overlap(CP_1, CP_2) = \frac{|lines(CF_1) \cap lines(CF_2)|}{|lines(CF_1) \cup lines(CF_2)|} 
+\end{multline}
+\squeezeup
+\begin{multline}
+	contained(CP_1, CP_2) = \frac{|lines(CF_1) \cap lines(CF_2)|}{|lines(CF_1)|}. 
+\end{multline}
+
+\textit{good-value} is then defined as
+\squeezeup
+\begin{align*}
+	good(CP_1, CP_2) = min(overlap(CP_1.CF_1,CP_2.CF_1), \\ overlap(CP_1.CF_2,CP_2.CF_2)).
+\end{align*}
+
+And \textit{ok-value} is defined as
+\squeezeup
+\begin{align*}
+	ok(CP_1,CP_2) = min(max(contained(CP_1.CF_1,CP_2.CF_1), \\ contained(CP_2.CF_1,CP_1.CF_1)),
+	\\ max(contained(CP_1.CF_2,CP_2.CF_2), \\contained(CP_2.CF_2,CP_1.CF_2))).
+\end{align*}
+
+Two clone pairs $CP_1$ and $CP_2$ are called a \textit{good-match(p)} iff, for $p \in [0,1]$ holds 
+\squeezeup
+\begin{equation}
+good(CP_1,CP_2) \geq p.
+\end{equation}
+
+Similarly for \textit{ok-match(p)} pair
+\squeezeup
+\begin{equation}
+ok(CP_1,CP_2) \geq p.
+\end{equation}
+
+Using this \textit{good-match} and \textit{ok-match} criteria, we can prioritise clone pairs for manual investigation.
+\textit{good-match} pairs are the ones with the highest confident to be true clones followed by \textit{ok-match} pairs.
+After finishing agreement-based clone pairs, the clone pairs without agreement with be manually looked at.
 
 \section{Results}
-The results of running 2 clone detectors: Simian and NiCad, to detect clones between 144,075 Stack Overflow fragments (Java accepted answers) and 109 open-source projects in Qualitas dataset is presented below.
-There are 2 tools selected: Simian and NiCad.
-They are configured using two different settings: default settings, and settings from a study by Wang et al.~\cite{Wang2013}.
-%Full Simian's parameter names can be found from the footnote\footnote{Simian's parameters: iChar = ignoreCharacters, iCurlB = ignoreCurlyBraces, iId = ignoreIdentifiers, iIdC = ignoreIdentifierCase, iMod = ignoreModifiers \newline iStrC = ignoreStringCase, iStr = ignoreStrings, iSbtNm = ignoreSubtypeNames, bSqBrck=balanceSquareBrackets}.
+
+We are aware of effects of configurations to clone detection results and needs for searching for optimised configurations.
+However, considering the size of the two datasets and search space of the Simian's and NiCad's parameters, we are hindered from finding the best configurations of the tools.
+Thus, we decided to configure Simian and NiCad using two established settings: 1) the tools' default settings (denoted as \textit{df}), and 2) settings from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}).
+With two tools and two sets of configurations, we look for agreements in four pair-wise combinations: Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{EvCl}$, Simian$_{EvCl}$-NiCad$_{df}$, and Simian$_{EvCl}$-NiCad$_{EvCl}$.
+
+The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} setting are presented in \Cref{tab:raw_stats}.
+Preliminary manual investigation of Simian's clone report showed that there were problematic 11 fragments.
+These fragments make Simian generating a large number of false clones involving array initialisation.
+Hence, they were removed from Simian's clone reports before the analysis.
+From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the full 144,075 Stack Overflow fragments, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{EvCl}$ respectively.
+NiCad$_{df}$ reports clones from 1,197 Stack Overflow fragments while NiCad$_{EvCl}$ reports clones from a large amount of 12,884 fragments due to its relaxed settings.
+In terms of number of clone pairs, EvaClone configurations prefer recall \cite{Wang2013} so Simian$_{EvCl}$ and NiCad$_{EvCl}$ report a large number of clone pairs of 59,936,722 and 206,718,663 respectively.
+The average clone size of Simian$_{df}$ is 7.45 which is bigger than the EvaClone counterpart of 4.81.
+Similarly, NiCad$_{df}$ has an average clone size of 9.54 which is also bigger than 5.31 reported by NiCad$_{EvCl}$.
+The statistics show that EvaClone tunes the tools in the way that they report smaller clones but result in higher agreements.
+The percentage of clone size compared to the size of Stack Overflow snippets reported by Simian$_{df}$, Simian$_{EvCl}$, NiCad$_{df}$, and NiCad$_{EvCl}$ is 28\%, 29\%, 25\% and 21\% accordingly.
 
@@
 		\hline
-		%		& \textit{6 clustering failed} & \textit{13 clustering failed} \\ %& & \textit{4 clustering failed} & \textit{6 clustering failed} \\
-		%		& cayenne   & cayenne 	\\ %& & jboss (wildfly) & ArgoUML \\
-		%		& checkstyle & checkstyle \\ %& & hadoop & checkstyle \\
-		%		& db-derby 	& db-derby 	\\ %& & db-derby & db-derby \\
-		%		& geotools 	& geotools  \\ %& & hibernate & cayenne \\
-		%		& iReport 	& iReport   \\ %& & & jena \\
-		%		& hibernate & ArgoUML 	\\ %& & & geotools \\
-		%		&			& castor 		\\ %& & & \\
-		%		&			& drjava 		\\ %& & & \\
-		%		&			& ganttproject 	\\ %& & & \\
-		%		&			& ivatagroupware \\ %& & &  \\
-		%		&			& jasperreports \\ %& & & \\
-		%		&			& jboss 		\\ %& & & \\
-		%		&			& jchempaint 	\\ %& & & \\
-		%		\hline
-		%		& 			&  \textit{4 renaming failed} \\ %& & & \textit{4 renaming failed} \\
-		%		&			& Vuze 		\\ %& & & Vuze \\
-		%		&			& aspectj 	\\ %& & & hadoop \\
-		%		&			& eXoPortal 	\\ %& & & jboss (wildfly) \\
-		%		&			&  hibernate 	\\ %& & & hibernate \\
-		%		\hline
 	\end{tabular}
@@
 
-Manual investigation of Simian's clone report showed that there were problematic 11 fragments.
-These fragments generate false clone containing array initialisation.
-Hence, they were removed from the result set before analysis.
-
 \begin{table*}[h]
@@
 	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
-	\label{t_simian_raw_results}
+	\label{tab:raw_stats}
 %	\resizebox{\columnwidth}{!}{%
@@
 			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
-			Mean & 52 & 7.45 & 0.28 		& 44104 & 4.81 & 0.29 		& 106 & 9.54 & 0.25 	& 16046 & 5.31 & 0.21 \\
-			Std Dev. & 147 & 3.22 & 0.23 	& 1040483 & 1.20 & 0.19 	& 209 & 3.10 & 0.18 	& 21890 & 1.92 & 0.16 \\
-			Max  & 1020 & 49.00 & 0.94 		& 38223637 & 18.00 & 0.89 	& 2100 & 39.00 & 0.81 	& 442655 & 50.00 & 0.93 \\
-			Min  & 1 & 5.00 & 0.01 			& 1 & 4.00 & 0.02 			& 1 & 7.00 & 0.02 		& 1 & 3.00 & 0.01 \\
-			Median  & 3 & 7.00 & 0.21 		& 24 & 5.00 & 0.25 			& 20 & 8.00 & 0.19 		& 8003 & 5.00 	& 0.16 \\
-			Mode  & 1 & 7.00 & 0.33 		& 1 & 4.00 & 0.50 			& 1 & 8.00 & 0.67 		& 1 & 4.00 & 0.33 \\
+			Mean & 52 & 7.45 & 28\% 		& 44104 & 4.81 & 29\% 		& 106 & 9.54 & 25\% 	& 16046 & 5.31 & 21\% \\
+			Std Dev. & 147 & 3.22 & 23\% 	& 1040483 & 1.20 & 19\% 	& 209 & 3.10 & 18\% 	& 21890 & 1.92 & 16\% \\
+			Max  & 1020 & 49.00 & 94\% 		& 38223637 & 18.00 & 89\% 	& 2100 & 39.00 & 81\% 	& 442655 & 50.00 & 93\% \\
+			Min  & 1 & 5.00 & 1\% 			& 1 & 4.00 & 2\% 			& 1 & 7.00 & 2\% 		& 1 & 3.00 & 1\% \\
+			Median  & 3 & 7.00 & 21\% 		& 24 & 5.00 & 25\% 			& 20 & 8.00 & 19\% 		& 8003 & 5.00 & 16\% \\
+			Mode  & 1 & 7.00 & 33\% 		& 1 & 4.00 & 50\% 			& 1 & 8.00 & 67\% 		& 1 & 4.00 & 33\% \\
 			\hline
@@
 \end{table*}
-
-%\begin{table*}
-%	\centering
-%	\caption{Qualitas-\textit{N} (2016-08-05) clone results (44 new Qualitas projects)}
-%	\label{t_simian_raw_results}
-%%	\resizebox{\columnwidth}{!}{%
-%	\small
-%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
-%			\hline
-%			\multirow{3}{*}{Statistics} 
-%			& \multicolumn{3}{c|}{Simian Default settings} 
-%			& \multicolumn{3}{c|}{Simian EvaClone settings} 
-%			& \multicolumn{3}{c|}{NiCad Default settings} 
-%			& \multicolumn{3}{c}{NiCad EvaClone settings} \\ \cline{2-13} 
-%			& \multicolumn{3}{c|}{707 fragments} 
-%			& \multicolumn{3}{c|}{1205 fragments} 
-%			& \multicolumn{3}{c|}{1068 fragments} 
-%			& \multicolumn{3}{c}{10231 fragments} \\  \cline{2-13}
-%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\
-%			\hline
-%			Total & 60,536 & -- 	& -- 	& 22,797,190 & -- 	& --  & 648,165 & -- & -- & 573,438,528 & -- & -- \\ 
-%			Mean 	& 86 	& 7.37 	& 0.26 	& 18,919 	& 4.85 	& 0.28 & 607 & 9.39 & 0.25 & 47663 & 5.22 & 0.20 \\
-%			Std Dev. & 217 	& 2.22 	& 0.21 	& 326,588 	& 1.31 	& 0.19 & 1,499 & 2.98 & 1.81 & 58,833 & 2.77 & 0.15 \\
-%			Max 	& 1,298 & 32.00 & 0.94 & 11,127,286 & 21.00 & 0.92 & 10,550 & 36.00 & 0.84 & 1,246,598 & 250 & 0.96 \\
-%			Min 	& 1 	& 5.00 	& 0.01 	& 1 & 4.00 	& 0.02 & 1 & 7 & 0.02 & 1 & 2.00 & 0.01\\
-%			Median 	& 2 & 7.00 	& 0.21 	& 20		& 5.00 	& 0.25 & 33 & 8 & 0.19 & 52,077 & 5.00 & 0.15 \\
-%			Mode & 1 	& 7.00 	& 0.25 	& 1 		& 4.00 	& 0.50 & 1 & 8 & 0.67 & 1 & 4.00 & 0.33 \\
-%			\hline
-%		\end{tabular} %
-%	%}
-%\end{table*}
 
@@
 
-\begin{table*}
-	\centering
-	\caption{17 selected Qualitas projects (new versions retrieved on 2016-09-27)}
+\begin{table}
+	\centering
+	\caption{13 Qualitas projects that have been cloned as examples on Stack Overflow}
 	\label{t:new_and_old}
@@
 	\small
-	\begin{tabular}{l|r|r|c|c|p{3cm}}
-		\hline 
-		Projects & Old version & New versions & Latest change & CVS & License  \\
-		\hline
-		apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 \\
-		apache-log4j & 1.2.16 & & & & \\
-		apache-tomcat & 7.0.2 & & & & \\
-		aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse 1.0 \\
-		hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0\\
-		hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ \\
-		jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0  \\
-		jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0  \\
-		jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) \\
-		jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 \\
-		jstock & 1.0.7c & & & & \\
-		jung2 & 2\_0\_1 & & & & \\
-		junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 \\
-		poi & 3.6 & & & & \\
-		spring-framework & 3.0.5 & & & & \\
-		struts2 & 2.2.1-all & & & & \\
-		weka & 3-7-9 & & & & \\
+	\begin{tabular}{l|r|p{3.5cm}}
+		\hline 
+		Project & Version & License  \\
+		\hline
+%		apache-ant & 1.8.4 & Apache2.0 \\
+%		apache-log4j & 1.2.16 & \\
+		apache-tomcat & 7.0.2 & \\
+		aspectj & 1.6.9 & Eclipse 1.0 \\
+		hadoop & 1.0.0 & Apache 2.0\\
+		hibernate & 4.2.2 & GLGPL 2.1+ \\
+		jasperreports & 3.7.4 & GLGPL 3.0  \\
+		jfreechart & 1.0.13 & GLGPL 2.0  \\
+		jgraph & 5.13.0.0 & Proprietary (mxGraph) \\
+%		jgrapht & 0.8.1 & GLGPL 2.1 \& Eclipse  1.0 \\
+		jstock & 1.0.7c & \\
+		jung2 & 2\_0\_1 & \\
+		junit & 4.11 & Eclipse  1.0 \\
+		poi & 3.6 & \\
+		spring-framework & 3.0.5 & \\
+		struts2 & 2.2.1-all & \\
+%		weka & 3-7-9 & \\
 		\hline
@@
 	%	}
-\end{table*}
+\end{table}
 
@@
 
-\subsection{Agreement based clone pairs vs. Non agreement based clone pairs}
-
-The agreement-based clone pairs are the ones discovered using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria as listed in  Table \ref{t_agreed_good_clone_pairs}.
+%\subsection{Agreement based clone pairs vs. Non agreement based clone pairs}
+
+%The agreement-based clone pairs are the ones discovered using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria as listed in  Table \ref{t_agreed_good_clone_pairs}.
 Non-agreement based clone pairs are the ones that are solely reported by a single tool.
@@
 \subsection{Agreement based clone pairs}
-For agreement-based clone pairs, we use a threshold of 0.7 for both \textit{good} and \textit{ok}-match.
-A visualisation of \textit{good}-match common clone pairs between four sets of parameter settings can be seen from Figure \ref{fig:venn4_orig_good}.
-There are 1,357 unique \textit{good}-match pairs.
-The distribution of 10,139 \textit{ok}-match pairs, which subsume the \textit{good}-match pairs, is depicted in Figure \ref{fig:venn4_orig_ok}.
+
+We use a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok}-match.
+A visualisation of \textit{good}-match clone pairs between four sets of parameter settings can be seen from \Cref{fig:venn4_orig_good}.
+There are 2,261 unique \textit{good}-match pairs.
+The distribution of 23,868 \textit{ok}-match pairs, which subsume the \textit{good}-match pairs, is depicted in \Cref{fig:venn4_orig_ok}.
 
@@
 For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors.
-For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvCl}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in Table \ref{tab:projects_missing}.
+For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvCl}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in \Cref{tab:projects_missing}.
 So these projects are also missing from agreed clone pairs.
@@
 Then, we reran the experiment again on these 44 projects.
-Several projects triggered NiCad problem of clustering and renaming again as listed in Table \ref{tab:projects_missing}.
-The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria of this new dataset are also listed in Table \ref{t_agreed_good_clone_pairs}.
+Several projects triggered NiCad problem of clustering and renaming again as listed in Table \{tab:projects_missing}.
+The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria of this new dataset are also listed in Table \{t_agreed_good_clone_pairs}.
 
@@
 	\centering
-	\caption{Distribution of agreement-based clone pairs reported using Bellon's criteria}
+	\caption{Distribution of agreement-based clone pairs using Bellon's criteria}
 	\label{t_agreed_good_clone_pairs}
@@
 		\hline
-		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{Qualitas-\textit{O}} \\
+		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{No.~of clone pairs} \\
 		\hline
@@
 
-\begin{figure}
-		\centering
-		\includegraphics[width=0.9\linewidth]{venn4_pairs_good_pt1+2}
-		\caption{\textit{good}-match(0.7) pairs}
+\begin{figure*}
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\linewidth]{venn4_pairs_good_pt1+2}
+		\caption{Distributions of \textit{good}-match(0.7) pairs}
 		\label{fig:venn4_orig_good}
-\end{figure}
-
-\begin{figure}
-		\centering
-		\includegraphics[width=0.9\linewidth]{venn4_pairs_ok_pt1+2}
-		\caption{\textit{ok}-match(0.7) pairs}
+	\end{minipage}
+	\begin{minipage}{.5\textwidth}
+		\centering
+		\includegraphics[width=0.8\linewidth]{venn4_pairs_ok_pt1+2}
+		\caption{Distributions of \textit{ok}-match(0.7) pairs}
 		\label{fig:venn4_orig_ok}
-\end{figure}
-
-\subsection{Manual investigation of agreement-based clone pairs}
-%\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
-
-%\subsection{Investigation of agreed \textit{good} and \textit{ok}-match clone pairs}
+	\end{minipage}
+\end{figure*}
+
+\subsubsection{Manual investigation of agreement-based clone pairs}
 
@@
 		\hline 
-		B & Code is copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
+		B & Clone pair is exactly identical or highly similar and may be copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
 		\\ 
@@
 
-The classification scheme is described in Table \ref{tab:classification_scheme} and the classification results are shown in Table \ref{tab:classification_good_o}.
-We have manually investigated all of the 1,357 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.
-However, for the \textit{ok-match}, we could not investigate all of the 10,139 pairs manually.
-According to the distribution of category from \textit{good-match} results, we can see that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number, 1,338, of false positive results (D, E, and F).
+The classification scheme is described in \Cref{tab:classification_scheme} and the classification results are shown in \Cref{tab:classification_good_o}.
+We have manually investigated all of the 2,261 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.
+However, for the \textit{ok-match}, we could not investigate all of the 23,868 pairs manually.
+According to the manual investigation of \textit{good-match} results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number, 2225 (99.87\%), of false positive results (category D, E, and F).
 Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs.
@@
 	\centering
-	\caption{Qualitas-\textit{O}: Classification results of \textit{good-} and \textit{ok}-match pairs which excludes the subsumed \textit{good}-match and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ pairs.}
+	\caption{Classification results of agreement-based and non agreement-based clone pairs)}
 	\label{tab:classification_good_o}
@@
 		\hline 
+		\hline
 		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
@@
 		\hline 
+		\hline 
+		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
+		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 319 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
+		\hline
+		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
+		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 10 & 0 & \textbf{10} & 7 & 8 & 5 & 6 & 3 & 26 & \textbf{35} & 17 & 16 & 8 & \textbf{45} & 24 & 24 & 9 \\ 
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 15 & 0 & \textbf{19} & 15 & 13 & 9 & 30 & 6 & 104 & \textbf{140} & 51 & 55 & 20 & \textbf{159} & 66 & 68 & 23 \\ 
+		\hline
+		%		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
+			%		\hline
 	\end{tabular} 
@@
 
-With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvaClone}}}$ and NiCad$_{\mathrm{\textit{EvaClone}}}$ due to their large number of false positives as shown in Table \ref{tab:good_classification} and \ref{tab:ok_classification}.
+With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvaClone}}}$ and NiCad$_{\mathrm{\textit{EvaClone}}}$ due to their large number of false positives as shown in \Cref{tab:good_classification} and \Cref{tab:ok_classification}.
 With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.
@@
 Out of 166, 52 are \textit{ok}-pairs and 114 are remaining pairs for manual check (18 pairs are from \textit{cayenne} and \textit{iReport} that could not be analysed using UPI = 0.3).
-The statistics of the clones and classification results are reported in Table \ref{tab:classification_indv_stats} and \ref{tab:classification_indv}.
+The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.
 
@@
 	\centering
-	\caption{Statistics of Simian$_{df}$ and NiCad$_{df}$ non agreement-based clone pairs.}
+	\caption{Statistics of non agreement-based clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
 	\label{tab:classification_indv_stats}
@@
 
-\subsection{Manual investigation of non agreement-based clone pairs}
+\subsubsection{Manual investigation of non agreement-based clone pairs}
 %\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
-We performed manual investigation of the clone pairs reported by Simian$_{df}$ and NiCad$_{df}$ in the same way as the agreement-based clone pairs.
-The results of the manual investigation is reported in Table \ref{tab:classification_indv}.
-
-\begin{table*}
-	\centering
-	\caption{Classification results of 795 Simian$_{df}$ and 159 NiCad$_{df}$ non agreement-based clone pairs.}
-	\label{tab:classification_indv}
-	\small
-	\resizebox{2.1\columnwidth}{!}{%
-	\begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|r|}
-		\hline 
-		Tool/Classification & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_{u}$ & Q$_{up}$ & D & E & F & \textbf{Sum}  & S$_{u}$ & Q$_{u}$ & Q$_{up}$ & \textbf{Total} & S$_{u}$ & Q$_{u}$  & Q$_{up}$  \\ 
-		\hline 
-%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
-%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 319 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
-		\hline
-%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
-%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 10 & 0 & \textbf{10} & 7 & 8 & 5 & 6 & 3 & 26 & \textbf{35} & 17 & 16 & 8 & \textbf{45} & 24 & 24 & 9 \\ 
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 15 & 0 & \textbf{19} & 15 & 13 & 9 & 30 & 6 & 104 & \textbf{140} & 51 & 55 & 20 & \textbf{159} & 66 & 68 & 23 \\ 
-		\hline
-		%		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
-		%		\hline
-	\end{tabular} 
-}
-\end{table*}
+We performed manual investigation and classified the clone pairs reported by Simian$_{df}$ and NiCad$_{df}$ in the same way as the agreement-based clone pairs.
+The results of the manual investigation is reported in \Cref{tab:classification_good_o}.
 
@@
 	\centering
-	\includegraphics[width=1.2\linewidth]{Sankey_proj}
-	\caption{Relationships of 49 outdated clone pairs and 4 deleted clone pairs (depicted using (d) suffix)}
+	\includegraphics[width=0.8\linewidth]{Sankey_proj}
+	\caption{Relationships of 53 Stack Overflow clone pairs to their original projects. 49 are outdated and 4 are deleted (shown using (d) suffix).}
 	\label{fig:sankey}
@@
 
-\subsection{Issue~1:~stale online code clones}
+\subsection{Issue~1 -- stale online code clones}
 Stale online code occurs when a piece of code has been copied from a software project to Stack Overflow, and later it has been changed in the original project.
 However, in this situation, the copy is still unchanged.
-Since the code were updated due to various possible reasons including bug fixing, this can cause a problem if developers reuse stale online code from Q\&A websites such as Stack Overflow.
+Since the code were updated due to various possible reasons including bug fixing, this can cause a problem if developers reuse stale online code from Stack Overflow.
 They might also introduce the same unfixed bug(s) into the software.
-To discover stale online code, we focus on the true online clone pairs that are copied in the direction of Q $\rightarrow$ S (class-\textit{A} online clone pairs) in Table \ref{tab:classification_true_pairs_summary} which results in 48 pairs selected.
-We restricted it further to only the ones having versioning system so we can trace changes made to these clone pairs.
+To discover stale online code, we focus on the true online clone pairs that are copied in the direction from Qualitas to Stack Overflow (category-\textit{A} online clone pairs) in \Cref{tab:classification_true_pairs_summary} which results in 84 pairs selected.
+%We restricted it further to only the ones having versioning system so we can trace changes made to these clone pairs.
 Fortunately, all of the pairs were from projects with either git or svn so we did not remove any pair from this set.
@@
 
-Table \ref{tab:stale_code} shows the results of manual investigation of 84 class-A online clone pairs.
+\Cref{tab:stale_code} shows the results of manual investigation of 84 category-A online clone pairs.
 The investigation reveals that there are 50 clone pairs that are outdate (i.e.
 ``stale clone'').
-They are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as \textit{accepted} answers, and later have been changed during the development.
+They are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as accepted answers, and later have been changed during the development.
 
@@
 	\centering
-	\caption{Results from a manual investigation of 84 class-A online clone pairs}
+	\caption{Results from a manual investigation of 84 category-A online clone pairs}
 	\label{tab:stale_code}
 	\small
-	\resizebox{\columnwidth}{!}{%
+%	\resizebox{\columnwidth}{!}{%
 	\begin{tabular}{l|r|r|r|r|r}
@@
 	\end{tabular} 
-}
+%}
 \end{table}
@@
 
-\subsection{Issue~2:~clones with software licensing violations}
-Software licensing is vital in software industry.
-Violation of software license can have a major impact to the delivery of the software and also lead to legal issues.
+\subsection{Issue~2 -- software licensing violations}
+Software licensing is a paramount factor in software development.
+Violation of software license can cause a major impact to the delivery of the software and also lead to legal issues.
 It is an emerging area that software engineering research community is paying attention to.
@@
 
-In our study, we tackle another possible situation of software licensing issue caused by code cloning to Q\&A websites.
-We found that there are at least 48 pieces of code have been copied from 9 open source projects to Stack Overflow as examples.
-These 9 open source projects come with software licenses.
-However, the licensing information are mostly missing from these clones.
+In our study, we reveal another possible situation of software licensing issue caused by code cloning to Stack Overflow.
+We found that there are at least 84 pieces of code have been copied from 13 open source projects in Qualitas dataset to Stack Overflow as examples.
+They are also marked as accepted answers which increase their probability of being reused.
+These 13 open source projects come with their respective software licenses.
+However, the licensing information are mostly missing from these clones when they are posted on Stack Overflow.
+Mostly one or a few methods from the full source file are cloned.
+This makes the license information at the top of the file mostly left uncopied.
 If developers copy and reuse these pieces of code in their projects, a licensing conflict can quietly happen without realisation of the developers.

### 2016-11-08 latex-acm/cloneoverflow.tex
Updated latex file

@@
 \usepackage{cleveref}
+
 \newcolumntype{P}[1]{>{\RaggedRight\hspace{0pt}}p{#1}}
@@
 
-\textbf{Qualitas corpus}: we selected an established corpus for empirical software engineering studies called Qualitas \cite{QualitasCorpus}.
+\textbf{Open source systems}: we selected an established corpus for empirical software engineering studies called \textbf{Qualitas} \cite{QualitasCorpus}.
 \FIXME{more details about Qualitas and why we chose it}.
 We selected the 20130901r version of Qualitas corpus containing 112 Java open source projects with releases no later than 1st September 2013.
-We chose the snapshot in 2013 since we are interested in online code clones from old releases of the software.
-Out of 112 Qualitas projects, there are 3 projects, \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}, that do not contain source code so they were removed from the study.
+We chose the snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow.
+The 20130901r snapshot provides Java code that is at least 3 years old which is sufficient for a number of code snippets to be copied onto Stack Overflow.
+Out of 112 Qualitas projects, there are 3 projects, \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}, that do not contain any Java source code file so they are removed from the study.
 This results in totally 109 projects analysed in the study.
@@
 \subsubsection{Clone Detectors}
-There are certain restrictions in terms of choosing clone detection tools for this study.
+There are a number of restrictions in terms of choosing clone detection tools for this study.
 Firstly, they have to compatible with Java.
@@
 Hence, the tool must be flexible enough to process code snippets which are not in a complete block or not compilable.
-Thirdly, since the amount of code that have to be process are in a scale of millions line of source code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to be able to successfully complete the execution and report clones in a reasonable amount of time.
-These restrictions force us to remove three well-known clone detectors; CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a}; from our study since they failed to detect clones between 144,075 Stack Overflow code snippets and 109 Qualitas projects.
-We finally selected two clone detectors for this study: \textbf{Simian} \cite{simian} and \textbf{NiCad} \cite{Cordy,Roy2008}.
+Thirdly, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
+We have tried running 5 state-of-the-arts clone detectors including Simian \cite{simian}, NiCad \cite{Cordy,Roy2008}, CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a} against the Stack Overflow and Qualitas datasets.
+CCFinder, iClones, and DECKARD failed to successfully detect clones between 144,075 Stack Overflow code snippets and 109 Qualitas projects.
+All of them reported execution errors after running for couple of hours.
+Thus, we removed them from the study.
+Simian and NiCad completed the detection with success.
 We found that both of them are flexible enough to handle million-SLOC code corpus with method or class incompleteness.
-
-Simian is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies \cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}.
+So, we decided to use both of them.
+
+\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies \cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}.
 It is a command-line tool which enables us to automate the detection.
 It also offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect clones of type 1 and type 2.
-NiCad is also a text-based clone detector which detects clones at method or code block granularity.
+\textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity.
 It can detect clone up to type 3 and is used in several clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
 It utilises TXL for parsing and pretty-printing source code.
-It also provide code normalisation by variable renaming and abstractions.
+It also provide code normalisation by variable renaming and code abstraction.
 We use a variant of NiCad called \textit{nicadcross}.
 It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems.
+NiCad is also a command-line tool which makes it suitable for automation.
 
 \subsubsection{Agreement-based Clone Detection}
-Since we do not have clone oracle of the two datasets, we adopted an idea of clone agreement used in clone research \cite{Wang2013,Funaro2010,cr2016ssbse} to help reducing the number of clones for manual investigation.
-To find agreement of two clone pairs, we resort to an approach proposed by a study by another study~\cite{Bellon2007}.
-
-According to Bellon et al.~\cite{Bellon2007}, \textit{good} and \textit{ok}-match clone pairs are defined as follows.
+The number of detected clones between the two datasets can be very large and infeasible for human to manually check all of them.
+Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish.
+Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}.
+By using this agreement-based clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the agreed clone pairs.
+To find agreement of two clone pairs, we resort to an approach proposed by a study by Bellon et al.~\cite{Bellon2007}.
+Two clone pairs which have overlapping clone lines can be considered as a good-match or an ok-match pair.
+A good-match clone pair has stronger agreement than an ok-match pair.
+We follow the same following definitions introduced in the original paper:
+
+%good and ok-match clone pairs are defined as follows. 
 A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}: \textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).
-For each clone pair, we can define \textit{overlap} and \textit{contained} value of two clone pairs as
-\squeezeup
+We can define \textit{overlap} and \textit{contained} value of two clone pairs as
+%\squeezeup
 \begin{multline}
@@
 \end{multline}
-\squeezeup
+%\squeezeup
 \begin{multline}
@@
 
-\textit{good-value} is then defined as
-\squeezeup
+\textit{good-value} of two clone pairs is then defined as
+%\squeezeup
 \begin{align*}
@@
 
-And \textit{ok-value} is defined as
-\squeezeup
+Furthermore, \textit{ok-value} is defined as
+%\squeezeup
 \begin{align*}
@@
 Two clone pairs $CP_1$ and $CP_2$ are called a \textit{good-match(p)} iff, for $p \in [0,1]$ holds 
-\squeezeup
+%\squeezeup
 \begin{equation}
@@
 
-Similarly for \textit{ok-match(p)} pair
-\squeezeup
+Similarly for an \textit{ok-match(p)} pair
+%\squeezeup
 \begin{equation}
@@
 
-Using this \textit{good-match} and \textit{ok-match} criteria, we can prioritise clone pairs for manual investigation.
-\textit{good-match} pairs are the ones with the highest confident to be true clones followed by \textit{ok-match} pairs.
-After finishing agreement-based clone pairs, the clone pairs without agreement with be manually looked at.
+Using this good-match and ok-match criteria with a predefined threshold \textit{p}, we prune the detected clone pairs for manual investigation.
+good-match pairs are the ones with the highest confident to be true clones, followed by ok-match pairs, and followed by clone pairs without agreement.
+
+\subsection{Clone detectors' parameter tuning}
+We are aware of effects of configurations to clone detection results and needs for searching for optimised configurations in empirical clone studies \cite{Wang2013,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
+However, considering the size of the two datasets and search space of at least 15 of Simian's and 5 of NiCad's parameters, we are hindered from finding the best configurations of the tools.
+Thus, we decided to configure Simian and NiCad using two established settings: 1) the tools' default settings chosen by the tools' creators (denoted as \textit{df}), and 2) the general settings for Java sets from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}).
+With our two tools and these two sets of configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.
 
 \section{Results}
-
-We are aware of effects of configurations to clone detection results and needs for searching for optimised configurations.
-However, considering the size of the two datasets and search space of the Simian's and NiCad's parameters, we are hindered from finding the best configurations of the tools.
-Thus, we decided to configure Simian and NiCad using two established settings: 1) the tools' default settings (denoted as \textit{df}), and 2) settings from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}).
-With two tools and two sets of configurations, we look for agreements in four pair-wise combinations: Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{EvCl}$, Simian$_{EvCl}$-NiCad$_{df}$, and Simian$_{EvCl}$-NiCad$_{EvCl}$.
-
-The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} setting are presented in \Cref{tab:raw_stats}.
+The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} settings are presented in \Cref{tab:raw_stats}.
 Preliminary manual investigation of Simian's clone report showed that there were problematic 11 fragments.
-These fragments make Simian generating a large number of false clones involving array initialisation.
+These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones of array initialisation.
 Hence, they were removed from Simian's clone reports before the analysis.
-From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the full 144,075 Stack Overflow fragments, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{EvCl}$ respectively.
-NiCad$_{df}$ reports clones from 1,197 Stack Overflow fragments while NiCad$_{EvCl}$ reports clones from a large amount of 12,884 fragments due to its relaxed settings.
-In terms of number of clone pairs, EvaClone configurations prefer recall \cite{Wang2013} so Simian$_{EvCl}$ and NiCad$_{EvCl}$ report a large number of clone pairs of 59,936,722 and 206,718,663 respectively.
-The average clone size of Simian$_{df}$ is 7.45 which is bigger than the EvaClone counterpart of 4.81.
-Similarly, NiCad$_{df}$ has an average clone size of 9.54 which is also bigger than 5.31 reported by NiCad$_{EvCl}$.
-The statistics show that EvaClone tunes the tools in the way that they report smaller clones but result in higher agreements.
-The percentage of clone size compared to the size of Stack Overflow snippets reported by Simian$_{df}$, Simian$_{EvCl}$, NiCad$_{df}$, and NiCad$_{EvCl}$ is 28\%, 29\%, 25\% and 21\% accordingly.
+From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively.
+NiCad$_{df}$ reports clones from 1,197 Stack Overflow code snippets while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones from a large amount of 12,884 snippets due to its relaxed settings.
+In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report a large number of clone pairs of 59,936,722 and 206,718,663 respectively.
+This is expected since EvaClone configurations prefer recall \cite{Wang2013}.
+The average clone size of Simian$_{df}$ is 7.45 which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81.
+Similarly, NiCad$_{df}$ has an average clone size of 9.54 which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$.
+We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones but result in higher agreements.
+The average percentage of code in Stack Overflow snippets that are clones reported by Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\% and 21\% accordingly.
 
@@
 		\hline
-		%		\multicolumn{3}{c|}{Qualitas-\textit{O}} & \multicolumn{3}{c}{Qualitas-\textit{N}} \\
-		%		\hline
-		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ % & Simian$_{\textrm{\textit{df/EvaClone}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ \hline
-		\hline
-		\textit{Successful} & 109 & 109 & 97 & 82 \\ %& 44 & 40 & 34 \\
+		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ 
+		\hline
+		\textit{Successful} & 109 & 109 & 97 & 82 \\ 
 		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
@@
 			& \multicolumn{3}{c}{12884 fragments} \\ \cline{2-13}
-			%& \multicolumn{3}{c|}{iCharC,iCurlB,iIdC,iMod,iStrC} 
-			%& \multicolumn{3}{c|}{iCurlB,iId,iIdC,iStr,iChar,iSbtNm,bSqBrck} 
-			%& \multicolumn{3}{c|}{rename=none,abstract=none} 
-			%& \multicolumn{3}{c}{rename=blind,abstract=literal} \\ %\cline{2-17}  
 			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
@@
 			\hline
-			%Removed & 11 & -- & -- & -- & 0 & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- & -- \\ %& 11 & -- & -- & -- \\
 			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
@@
 	\centering
-	\caption{13 Qualitas projects that have been cloned as examples on Stack Overflow}
+	\caption{13 Qualitas projects that have been cloned as examples on Stack Overflow with their respective licenses}
 	\label{t:new_and_old}
@@
 	\small
-	\begin{tabular}{l|r|p{3.5cm}}
-		\hline 
-		Project & Version & License  \\
+	\begin{tabular}{l|r|p{4cm}}
+		\hline 
+		Project & Version & Licenses (no.~of files) \\
 		\hline
@@
 %		apache-log4j & 1.2.16 & \\
-		apache-tomcat & 7.0.2 & \\
-		aspectj & 1.6.9 & Eclipse 1.0 \\
-		hadoop & 1.0.0 & Apache 2.0\\
-		hibernate & 4.2.2 & GLGPL 2.1+ \\
-		jasperreports & 3.7.4 & GLGPL 3.0  \\
-		jfreechart & 1.0.13 & GLGPL 2.0  \\
-		jgraph & 5.13.0.0 & Proprietary (mxGraph) \\
+		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
+		\hline
+		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
+		\hline
+		hibernate & 4.2.2 & Apache-2 (20), \newline GLGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
+		\hline
+		jasperreports & 3.7.4 & GLGPLv2.1+ (3), \newline GLGPLv3+ (1,581), \newline None (1), Unknown (4)\\
+		\hline
+		jfreechart & 1.0.13 & GLGPLv2.1+ (989) \\
+		\hline
+		jgraph & 5.13.0.0 & GLGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
+		\hline
 %		jgrapht & 0.8.1 & GLGPL 2.1 \& Eclipse  1.0 \\
-		jstock & 1.0.7c & \\
-		jung2 & 2\_0\_1 & \\
-		junit & 4.11 & Eclipse  1.0 \\
-		poi & 3.6 & \\
-		spring-framework & 3.0.5 & \\
-		struts2 & 2.2.1-all & \\
+		jstock & 1.0.7c & GLGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
+		\hline
+		jung2 & 2\_0\_1 & N/A \\
+		\hline
+		junit & 4.11 & None (160), Unknown (4)  \\
+		\hline
+		poi & 3.6 & Apache-2 (2,002), None (5) \\
+		\hline
+		spring & 3.0.5 & Apache-2 (2,982) \\
+		\hline
+		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
+		\hline
+		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
 %		weka & 3-7-9 & \\
@@
 
-%The agreement-based clone pairs are the ones discovered using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria as listed in  Table \ref{t_agreed_good_clone_pairs}.
+%The agreement-based clone pairs are the ones discovered using Bellon's good-match(0.7) and \textit{ok}-match(0.7) criteria as listed in  Table \ref{t_agreed_good_clone_pairs}.
 Non-agreement based clone pairs are the ones that are solely reported by a single tool.
@@
 
-We use a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok}-match.
-A visualisation of \textit{good}-match clone pairs between four sets of parameter settings can be seen from \Cref{fig:venn4_orig_good}.
-There are 2,261 unique \textit{good}-match pairs.
-The distribution of 23,868 \textit{ok}-match pairs, which subsume the \textit{good}-match pairs, is depicted in \Cref{fig:venn4_orig_ok}.
-
-Nevertheless,  NiCad produced renaming and clustering errors for some of the settings.
-This resulted in not all 109 projects had NiCad clone reports.
-For NiCad default settings (NiCad$_{\textrm{\textit{df}}}$), 6 projects had clustering failed errors.
-For NiCad EvaClone settings (NiCad$_{\textrm{\textit{EvCl}}}$), 4 projects had renaming failed errors and 13 projects had clustering failed errors as depicted in \Cref{tab:projects_missing}.
-So these projects are also missing from agreed clone pairs.
-\FIXME{Report the errors to NiCad creator.}
+We use a threshold \textit{p} of 0.7 for both good and ok-match.
+A visualisation of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} settings can be seen from \Cref{fig:venn4_orig_good}.
+We found that NiCad throws renaming and clustering errors while processing some Qualitas projects as listed in \Cref{tab:projects_missing}.
+%This resulted in not all 109 projects had NiCad clone reports.
+NiCad$_{\textrm{\textit{df}}}$, produced clustering errors for 6 projects.
+NiCad$_{\textrm{\textit{EvCl}}}$ produced renaming error for 4 projects, and clustering error for 13 projects.
+As a result, we did not have NiCad clone reports for these projects and hence they are missing from agreement-based clone pair calculation.
+\FIXME{Report the errors to NiCad creator.} There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$-NiCad$_{df}$, 26 pairs from Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.
+\Cref{fig:venn4_orig_ok} show the distribution of 23,868 unique ok-match pairs, which subsume the good-match pairs.
+There are 3,800 pairs from Simian$_{df}$-NiCad$_{df}$, 1,017 pairs from Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, 88 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and 19,777 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.
+Between the four sets, there are a few clone pairs that are common between two adjacent sets, but there is no clone pair that is agreed by all four combinations.
 
@@
 Several projects triggered NiCad problem of clustering and renaming again as listed in Table \{tab:projects_missing}.
-The agreed clone pairs using Bellon's \textit{good}-match(0.7) and \textit{ok}-match(0.7) criteria of this new dataset are also listed in Table \{t_agreed_good_clone_pairs}.
+The agreed clone pairs using Bellon's good-match(0.7) and ok-match(0.7) criteria of this new dataset are also listed in Table \{t_agreed_good_clone_pairs}.
 
@@
 	\centering
-	\caption{Distribution of agreement-based clone pairs using Bellon's criteria}
+	\caption{Distribution of agreement-based clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
 	\label{t_agreed_good_clone_pairs}
@@
 		\hline
-		Simian & NiCad & \textit{good}-match & \textit{ok}-match \\
+		Simian & NiCad & good-match & ok-match \\
 		%\hline
-		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvaClone}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-		\hline
-		\textit{default} & \textit{default} & 10 	& 3800 \\ 
-		\textit{default} & \textit{EvaClone} 	& 26 	& 1017 \\ 
-		\textit{EvaClone} 	& \textit{default} 	& 10 	& 88 \\
-		\textit{EvaClone} 	& \textit{EvaClone} 	& 2228 & 19777 \\ 
+		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
+		\hline
+		\textit{df} & \textit{df} & 10 	& 3800 \\ 
+		\textit{df} & \textit{EvCl} 	& 26 	& 1017 \\ 
+		\textit{EvCl} 	& \textit{df} 	& 10 	& 88 \\
+		\textit{EvCl} 	& \textit{EvCl} 	& 2228 & 19777 \\ 
 		\hline
@@
 		\includegraphics[width=0.8\linewidth]{venn4_pairs_good_pt1+2}
-		\caption{Distributions of \textit{good}-match(0.7) pairs}
+		\caption{Distributions of good-match(0.7) pairs}
 		\label{fig:venn4_orig_good}
@@
 		\includegraphics[width=0.8\linewidth]{venn4_pairs_ok_pt1+2}
-		\caption{Distributions of \textit{ok}-match(0.7) pairs}
+		\caption{Distributions of ok-match(0.7) pairs}
 		\label{fig:venn4_orig_ok}
@@
 The classification scheme is described in \Cref{tab:classification_scheme} and the classification results are shown in \Cref{tab:classification_good_o}.
-We have manually investigated all of the 2,261 \textit{good-match} ones reported by agreement of four different Simian and NiCad settings.
-However, for the \textit{ok-match}, we could not investigate all of the 23,868 pairs manually.
-According to the manual investigation of \textit{good-match} results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number, 2225 (99.87\%), of false positive results (category D, E, and F).
-Thus, we decided to leave them out of the manual investigation of \textit{ok-match} pairs.
-There are totally 608 \textit{ok-match} pairs that were investigated.
+We have manually investigated all of the 2,261 good-match ones reported by agreement of four different Simian and NiCad settings.
+However, for the ok-match, we could not investigate all of the 23,868 pairs manually.
+According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number, 2225 (99.87\%), of false positive results (category D, E, and F).
+Thus, we decided to leave them out of the manual investigation of ok-match pairs.
+There are totally 608 ok-match pairs that were investigated.
 The 39 true positive pairs found are combinations of 8 unique Stack Overflow fragments, and 9 unique Qualitas Java files from 6 different projects.
@@
 We found that all Stack Overflow code fragments were posted after their respectively similar Java files in Qualitas project.
-This means that the copying can only be either (1) Q $\rightarrow$ S or (2) from a third source to both S and Q independently.
-
-%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{\mathrm{\textit{EvaClone}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed \textit{ok}-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvaClone}}}$, and Simian$_{\mathrm{\textit{EvaClone}}}$-NiCad$_{df}$.
-We had not done any investigation of \textit{good}-match since there were no \textit{good}-match pairs for these 3 agreements.
+This means that the copying can only be either (1) from Qualitas to Stack Overflow or (2) from a third source to both Stack Overflow and Qualitas independently.
+
+%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvCl}}}$-NiCad$_{\mathrm{\textit{EvCl}}}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}$-NiCad$_{df}$.
+We had not done any investigation of good-match since there were no good-match pairs for these 3 agreements.
 The number of pairs that have been looked at is 6,706 (excluding duplicates).
@@
 %	\centering
-%	\caption{Distribution of classification category A--F according to \textit{good}- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
+%	\caption{Distribution of classification category A--F according to good- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
 %	\label{tab:good_classification}
@@
 %		\hline
-%		\multicolumn{9}{|c|}{\textit{good}-match pairs} \\
+%		\multicolumn{9}{|c|}{good-match pairs} \\
 %		\hline
@@
 %%		\hline
-%		\multicolumn{9}{|c|}{\textit{ok}-match pairs} \\
+%		\multicolumn{9}{|c|}{ok-match pairs} \\
 %		\hline
@@
 
-With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvaClone}}}$ and NiCad$_{\mathrm{\textit{EvaClone}}}$ due to their large number of false positives as shown in \Cref{tab:good_classification} and \Cref{tab:ok_classification}.
+With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their large number of false positives.
 With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.
@@
 Out of 9,383 pairs, 140 of them are the ones found in \textit{ok-}pairs using agreement-based detection.
-We filtered the results further by removing false positives such as similar equals(), hashCode() methods, getters and setters out by using regular expression.
+We filtered the results further by removing false positives such as similar \textit{equals()}, \textit{hashCode()} methods, getters and setters out by using regular expression.
 We managed to remove 8,956 pairs using this method.
@@
 By reducing the UPI to 0.2, there were totally 166 pairs left.
-Out of 166, 52 are \textit{ok}-pairs and 114 are remaining pairs for manual check (18 pairs are from \textit{cayenne} and \textit{iReport} that could not be analysed using UPI = 0.3).
+Out of 166, 52 are ok-pairs and 114 are remaining pairs for manual check (18 pairs are from \textit{cayenne} and \textit{iReport} that could not be analysed using UPI = 0.3).
 The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.
@@
 		\hline 
-		Tool & Clone pairs & \textit{ok}-pairs & filtered & remaining \\ 
+		Tool & Clone pairs & ok-pairs & filtered & remaining \\ 
 		%\hline 
@@
 		\hline
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 18425 & 140 & 17490 & 795 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 18422 & 140 & 17490 & 792 \\
 		\hline
@@
 		\hline
-		\textit{good}-pairs & 1 & 0 & 4 & 3 & 8 \\
-		\textit{ok}-pairs & 8 & 0 & 33 & 8 & 49 \\
+		good-pairs & 1 & 0 & 4 & 3 & 8 \\
+		ok-pairs & 8 & 0 & 33 & 8 & 49 \\
 %		Simian$_{df}$ pairs-1 & 35 & 0 & 90 & 8 & 133 \\
 %		Simian$_{df}$ pairs-2 & 36 & 0 & 229 & 3 & 268 \\
-		Simian$_{df}$ pairs & 71 & 0 & 319 & 11 & 401 \\
+		Simian$_{df}$ pairs & 71 & 0 & 318 & 10 & 399 \\
 %		NiCad$_{df}$ pairs & 4 & 0 & 5 & 0 & 9 \\
@@
 		\hline 
-		Total & 84 & 0 & 371 & 22 & 477 \\
+		Total & 84 & 0 & 370 & 21 & 475 \\
 		\hline
@@
 	\centering
-	\caption{53 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted}
+	\caption{53 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted and their respective licenses}
 	\label{tab:stale_code_details}
 	\small
-	\begin{tabular}{r|l|l|r|c|l}
-		\hline 
-		No. & Project & File & SO Post & Changes & Date \\
-		\hline
-		1 &  aspectj-1.6.9  &  Agent.java  & 18303692 &  alteration  & 2015-09-08 \\
-		2 &  aspectj-1.6.9   &  Agent.java  & 18303692 &  alteration  & 2015-09-08 \\
-		3 &  hadoop-1.0.0  &  DBCountPageView.java  & 21702608 &  alteration & 2011-06-12 \\
-		4 &  hadoop-1.0.0  &  DBCountPageView.java  & 21702608 &  alteration  & 2011-06-12 \\
-		5 &  hadoop-1.0.0  &  JobSubmissionFiles.java  & 14845581 &  alteration  & 2012-06-25 \\
-		6 &  hadoop-1.0.0  &  LineRecordReader.java  & 16180910 &  alteration & 2011-07-25 \\
-		7 &  hadoop-1.0.0  &  LineRecordReader.java  & 16180910 &  alteration  & 2011-07-25 \\
-		8 &  hadoop-1.0.0  &  StringUtils.java  & 801987 &  alteration & 2013-02-04 \\
-		9 &  hadoop-1.0.0  &  TestJobCounters.java  & 18833798 &  alteration  & 2011-06-12 \\
-		10 &  hadoop-1.0.0  &  TextOutputFormat.java  & 16928749 &  alteration  & 2011-06-12 \\
-		11 &  hadoop-1.0.0  &  WritableComparator.java  & 22315734 &  alteration & 2014-11-20 \\
-		12 &  hibernate-4.2.2  &  ConnectionProviderInitiator.java  & 15168494 &  alteration  & 2012-06-24 \\
-		13 &  hibernate-4.2.2  &  Example.java  & 24924255 &  alteration  & 2013-04-23 \\
-		14 &  hibernate-4.2.2  &  SchemaUpdate.java  & 23520731 &  alteration & 2016-02-05 \\
-		15 &  hibernate-4.2.2  &  SettingsFactory.java  & 8257554 &  removal & 2011-03-11 \\
-		16 &  hibernate-4.2.2  &  SQLServer2005LimitHandler.java  & 23967852 &  alteration  & 2015-03-12 \\
-		17 &  jasperreports-3.7.4  &  JRVerifier.java  & 8037824 &  alteration  & 2008-04-17 \\
-		18 &  jasperreports-3.7.4  &  JRVerifier.java  & 8037824 &  alteration & 2011-05-20 \\
-		19 &  jfreechart-1.0.13  &  AbstractXYItemRenderer.java  & 12936580 &  alteration  & 2016-02-19 \\
-		20 &  jfreechart-1.0.13  &  KeyToGroupMap.java  & 16058183 &  alteration  & 2013-07-03 \\
-		21 &  jfreechart-1.0.13  &  SpiderWebPlot.java  & 21998949 &  alteration  & 2008-06-02 \\
-		22 &  jfreechart-1.0.13  &  SpiderWebPlot.java  & 21998949 &  alteration  & 2008-06-02 \\
-		23 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
-		24 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
-		25 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
-		26 &  jgraph-5.13.0.0  &  HelloWorld.java  & 6722760 &  rewriting  & 2014-04-13 \\
-		27 &  jstock-1.0.7c  &  GoogleMail.java  & 14940863 &  alteration & 2015-12-13 \\
-		28 &  jstock-1.0.7c  &  GoogleMail.java  & 24680923 &  alteration  & 2015-12-13 \\
-		29 &  jung2-2\_0\_1  &  ShortestPathDemo.java  & 6025026 &  alteration  & 2010-04-13 \\
-		30 &  jung2-2\_0\_1  &  ShortestPathDemo.java  & 6025026 &  alteration  & 2010-04-13 \\
-		31 &  junit-4  &  Assert.java  & 23586872 &  alteration  & 2015-05-12 \\
-		32 &  junit-4  &  ExternalResource.java  & 7504040 &  alteration & 2016-06-25 \\
-		33 &  junit-4.11  &  ExpectException.java  & 8802082 &  alteration & 2014-05-26 \\
-		34 &  poi-3.6-20091214  &  WorkbookFactory.java  & 12593810 &  alteration  & 2015-04-29 \\
-		35 &  spring-framework-3.0.5  &  AnnotationMethodHandlerExceptionResolver.java  & 5660519 &  removal & 2012-01-20 \\
-		36 &  spring-framework-3.0.5  &  AutowireUtils.java  & 20913543 &  alteration  & 2014-10-28 \\
-		37 &  spring-framework-3.0.5  &  CustomCollectionEditor.java  & 18623736 &  alteration  & 2013-11-21 \\
-		38 &  spring-framework-3.0.5  &  DefaultAnnotationHandlerMapping.java  & 3758110 &  removal  & 2012-01-20 \\
-		39 &  spring-framework-3.0.5  &  DefaultPropertiesPersister.java  & 6149818 &  alteration  & 2013-03-19 \\
-		40 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2016-07-15 \\
-		41 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2008-12-18 \\
-		42 &  spring-framework-3.0.5  &  DelegatingServletInputStream.java  & 20996373 &  alteration  & 2008-12-18 \\
-		43 &  spring-framework-3.0.5  &  DispatcherServlet.java  & 4781746 &  alteration  & 2011-08-08 \\
-		44 &  spring-framework-3.0.5  &  Jaxb2Marshaller.java  & 10924700 &  alteration  & 2012-08-28 \\
-		45 &  spring-framework-3.0.5  &  ScheduledTasksBeanDefinitionParser.java  & 3751463 &  alteration  & 2016-07-05 \\
-		46 &  struts2-2.2.1  &  DefaultActionMapper.java  & 14019840 &  alteration  & 2013-10-18 \\
-		47 &  tomcat-7.0.2  &  BasicAuthenticator.java  & 21734562 &  alteration  & 2016-08-04 \\
-		48 &  tomcat-7.0.2  &  BasicAuthenticator.java  & 21734562 &  alteration & 2016-08-04 \\
-		49 &  tomcat-7.0.2  &  CoyoteAdapter.java  & 24404964 &  alteration  & 2012-11-18 \\
-		50 &  tomcat-7.0.2  &  CoyoteAdapter.java  & 24404964 &  alteration  & 2012-11-18 \\
-		51 &  tomcat-7.0.2  &  FormAuthenticator.java  & 21734562 &  alteration & 2016-08-04 \\
-		52 &  tomcat-7.0.2  &  HttpServlet.java  & 5266856 &  alteration  & 2011-10-22 \\
-		53 &  tomcat-7.0.2  &  JspRuntimeLibrary.java  & 10289462 &  alteration  & 2012-09-12 \\
-		\hline
-	\end{tabular} 
+	\resizebox{2.1\columnwidth}{!}{%
+	\begin{tabular}{r|l|l|l|l|c|l}
+		\hline 
+		No. & Project & File & License & SO Post & Changes & Date \\
+		\hline
+		1 & aspectj-1.6.9 & Agent.java & -- & 18303692 & alteration & 2015-09-08 \\
+		2 & aspectj-1.6.9 & Agent.java & -- & 18303692 & alteration & 2015-09-08 \\
+		3 & hadoop-1.0.0 & DBCountPageView.java & Apache-2 & 21702608 & alteration & 2011-06-12 \\
+		4 & hadoop-1.0.0 & DBCountPageView.java & Apache-2 & 21702608 & alteration & 2011-06-12 \\
+		5 & hadoop-1.0.0 & JobSubmissionFiles.java & Apache-2 & 14845581 & alteration & 2012-06-25 \\
+		6 & hadoop-1.0.0 & LineRecordReader.java & Apache-2 & 16180910 & alteration & 2011-07-25 \\
+		7 & hadoop-1.0.0 & LineRecordReader.java & Apache-2 & 16180910 & alteration & 2011-07-25 \\
+		8 & hadoop-1.0.0 & StringUtils.java & Apache-2 & 801987 & alteration & 2013-02-04 \\
+		9 & hadoop-1.0.0 & TestJobCounters.java & Apache-2 & 18833798 & alteration & 2011-06-12 \\
+		10 & hadoop-1.0.0 & TextOutputFormat.java & Apache-2 & 16928749 & alteration & 2011-06-12 \\
+		11 & hadoop-1.0.0 & WritableComparator.java & Apache-2 & 22315734 & alteration & 2014-11-20 \\
+		12 & hibernate-4.2.2 & ConnectionProviderInitiator.java & -- & 15168494 & alteration & 2012-06-24 \\
+		13 & hibernate-4.2.2 & Example.java & -- & 24924255 & alteration & 2013-04-23 \\
+		14 & hibernate-4.2.2 & SchemaUpdate.java & -- & 23520731 & alteration & 2016-02-05 \\
+		15 & hibernate-4.2.2 & SettingsFactory.java & -- & 8257554 & removal & 2011-03-11 \\
+		16 & hibernate-4.2.2 & SQLServer2005LimitHandler.java & -- & 23967852 & alteration & 2015-03-12 \\
+		17 & jasperreports-3.7.4 & JRVerifier.java & GLGPLv3+ & 8037824 & alteration & 2008-04-17 \\
+		18 & jasperreports-3.7.4 & JRVerifier.java & GLGPLv3+ & 8037824 & alteration & 2011-05-20 \\
+		19 & jfreechart-1.0.13 & AbstractXYItemRenderer.java & GLGPLv2.1+ & 12936580 & alteration & 2016-02-19 \\
+		20 & jfreechart-1.0.13 & KeyToGroupMap.java & GLGPLv2.1+ & 16058183 & alteration & 2013-07-03 \\
+		21 & jfreechart-1.0.13 & SpiderWebPlot.java & GLGPLv2.1+ & 21998949 & alteration & 2008-06-02 \\
+		22 & jfreechart-1.0.13 & SpiderWebPlot.java & GLGPLv2.1+ & 21998949 & alteration & 2008-06-02 \\
+		23 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
+		24 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
+		25 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
+		26 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
+		27 & jstock-1.0.7c & GoogleMail.java & GPLv2+ & 14940863 & alteration & 2015-12-13 \\
+		28 & jstock-1.0.7c & GoogleMail.java & GPLv2+ & 24680923 & alteration & 2015-12-13 \\
+		29 & jung2-2\_0\_1 & ShortestPathDemo.java & -- & 6025026 & alteration & 2010-04-13 \\
+		30 & jung2-2\_0\_1 & ShortestPathDemo.java & -- & 6025026 & alteration & 2010-04-13 \\
+		31 & junit-4 & Assert.java & -- & 23586872 & alteration & 2015-05-12 \\
+		32 & junit-4 & ExternalResource.java & -- & 7504040 & alteration & 2016-06-25 \\
+		33 & junit-4.11 & ExpectException.java & -- & 8802082 & alteration & 2014-05-26 \\
+		34 & poi-3.6-20091214 & WorkbookFactory.java & Apache-2 & 12593810 & alteration & 2015-04-29 \\
+		35 & spring-framework-3.0.5 & AnnotationMethodHandlerExceptionResolver.java & Apache-2 & 5660519 & removal & 2012-01-20 \\
+		36 & spring-framework-3.0.5 & AutowireUtils.java & Apache-2 & 20913543 & alteration & 2014-10-28 \\
+		37 & spring-framework-3.0.5 & CustomCollectionEditor.java & Apache-2 & 18623736 & alteration & 2013-11-21 \\
+		38 & spring-framework-3.0.5 & DefaultAnnotationHandlerMapping.java & Apache-2 & 3758110 & removal & 2012-01-20 \\
+		39 & spring-framework-3.0.5 & DefaultPropertiesPersister.java & Apache-2 & 6149818 & alteration & 2013-03-19 \\
+		40 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2016-07-15 \\
+		41 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2008-12-18 \\
+		42 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2008-12-18 \\
+		43 & spring-framework-3.0.5 & DispatcherServlet.java & Apache-2 & 4781746 & alteration & 2011-08-08 \\
+		44 & spring-framework-3.0.5 & Jaxb2Marshaller.java & Apache-2 & 10924700 & alteration & 2012-08-28 \\
+		45 & spring-framework-3.0.5 & ScheduledTasksBeanDefinitionParser.java & Apache-2 & 3751463 & alteration & 2016-07-05 \\
+		46 & struts2-2.2.1 & DefaultActionMapper.java & Apache-2 & 14019840 & alteration & 2013-10-18 \\
+		47 & tomcat-7.0.2 & BasicAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
+		48 & tomcat-7.0.2 & BasicAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
+		49 & tomcat-7.0.2 & CoyoteAdapter.java & Apache-2 & 24404964 & alteration & 2012-11-18 \\
+		50 & tomcat-7.0.2 & CoyoteAdapter.java & Apache-2 & 24404964 & alteration & 2012-11-18 \\
+		51 & tomcat-7.0.2 & FormAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
+		52 & tomcat-7.0.2 & HttpServlet.java & Apache-2 & 5266856 & alteration & 2011-10-22 \\
+		53 & tomcat-7.0.2 & JspRuntimeLibrary.java & Apache-2 & 10289462 & alteration & 2012-09-12 \\
+		\hline& 
+	\end{tabular} %
+}
 \end{table*}
@@
 %We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
-The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{\mathrm{\textit{EvaClone}}}$, NiCad$_{df}$, NiCad$_{\mathrm{\textit{EvaClone}}}$.
+The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{\mathrm{\textit{EvCl}}}$, NiCad$_{df}$, NiCad$_{\mathrm{\textit{EvCl}}}$.
 The investigation results are shown in Table \ref{tab:search}.
@@
 %		\hline 
-%		Simian$_{\mathrm{\textit{EvaClone}}}$ & 0 & 41  \\ 
+%		Simian$_{\mathrm{\textit{EvCl}}}$ & 0 & 41  \\ 
 %		\hline 
@@
 %		\hline 
-%		NiCad$_{\mathrm{\textit{EvaClone}}}$ &  24 & 17 \\ 
+%		NiCad$_{\mathrm{\textit{EvCl}}}$ &  24 & 17 \\ 
 %		\hline 

### 2016-11-09 latex-acm/cloneoverflow.tex
Latest updates
Updated the table of configurations

@@
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 84 clones that have been obviously copied from open source projects to Stack Overflow as code examples which potentially violate their software licenses.
+\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 238 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses.
 Furthermore, 50 out of the 84 clones are outdated and questionable for being reused.
@@
 Some of the clone candidates are false clones due to being boiler-plate code or IDE-generated and are discarded for further analysis.
-By ignoring the false clones, we compare licensing information of x,xxx remaining clone pairs for possibility of software licensing violations.
+By ignoring the false clones, we compare licensing information of 477 remaining clone pairs for possibility of software licensing violations.
 Moreover, we look forward through history of the clones from the projects' git versioning systems.
@@
 \begin{multline}
-	overlap(CP_1, CP_2) = \frac{|lines(CF_1) \cap lines(CF_2)|}{|lines(CF_1) \cup lines(CF_2)|} 
+	overlap(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|}
 \end{multline}
@@
 \begin{multline}
-	contained(CP_1, CP_2) = \frac{|lines(CF_1) \cap lines(CF_2)|}{|lines(CF_1)|}. 
+	contained(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}. 
 \end{multline}
@@
 \begin{align*}
-	good(CP_1, CP_2) = min(overlap(CP_1.CF_1,CP_2.CF_1), \\ overlap(CP_1.CF_2,CP_2.CF_2)).
+	good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2)).
 \end{align*}
@@
 \begin{align*}
-	ok(CP_1,CP_2) = min(max(contained(CP_1.CF_1,CP_2.CF_1), \\ contained(CP_2.CF_1,CP_1.CF_1)),
-	\\ max(contained(CP_1.CF_2,CP_2.CF_2), \\contained(CP_2.CF_2,CP_1.CF_2))).
+	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),
+	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2), \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2))).
 \end{align*}
 
-Two clone pairs $CP_1$ and $CP_2$ are called a \textit{good-match(p)} iff, for $p \in [0,1]$ holds 
+Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{good-match(p)} iff, for $p \in [0,1]$ holds 
 %\squeezeup
 \begin{equation}
-good(CP_1,CP_2) \geq p.
+good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
 \end{equation}
@@
 \begin{equation}
-ok(CP_1,CP_2) \geq p.
+ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
 \end{equation}
@@
 Thus, we decided to configure Simian and NiCad using two established settings: 1) the tools' default settings chosen by the tools' creators (denoted as \textit{df}), and 2) the general settings for Java sets from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}).
+The details of the two configurations are described in \Cref{t:param_tuning}.
 With our two tools and these two sets of configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.
 
+\begin{table}
+	\centering
+	\caption{Configurations of Simian and NiCad}
+	\label{t:param_tuning}
+	\resizebox{\columnwidth}{!}{%
+		\scriptsize
+\begin{tabular}{l|p{5.5cm}}
+	\hline 
+	Tool & Parameters \\
+	\hline
+	Simian$_{\textrm{\textit{df}}}$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
+	\hline
+	Simian$_{\textrm{\textit{EvCl}}}$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
+	\hline 
+	NiCad$_{\textrm{\textit{df}}}$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
+	\hline
+	NiCad$_{\textrm{\textit{EvCl}}}$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
+	\hline 
+\end{tabular} %
+}
+\end{table}
+
 \section{Results}
+
+\begin{table}
+	\centering
+	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
+	\label{tab:raw_stats}
+	\small
+	\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{l|r|r|r|r}
+			\hline
+			Stats & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\
+			\hline
+			Snippets & 1,406 & 1,360 & 1,197 & 12,884 \\
+			Total C$_{\textrm{\textit{pairs}}}$ & 54,790 & 59,936,722 & 127,305 & 206,718,663 \\
+			Avg.~C$_{\textrm{\textit{pairs}}}$ & 52 & 44,104 & 106 & 16,046 \\
+			Avg.~C$_{\textrm{\textit{size}}}$ & 7.45 & 4.81 & 9.54 & 5.31 \\
+			Avg.~C$_{\textrm{\textit{\%}}}$ & 28\% & 29\% & 25\% & 21\% \\
+			\hline
+		\end{tabular} %
+	}
+\end{table}
+
 The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} settings are presented in \Cref{tab:raw_stats}.
@@
 Hence, they were removed from Simian's clone reports before the analysis.
-From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively.
+From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively.
 NiCad$_{df}$ reports clones from 1,197 Stack Overflow code snippets while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones from a large amount of 12,884 snippets due to its relaxed settings.
@@
 
-\begin{table*}[h]
-	\centering
-	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
-	\label{tab:raw_stats}
-%	\resizebox{\columnwidth}{!}{%
-	\small
-		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
-			\hline
-			\multirow{3}{*}{Statistics} 
-			& \multicolumn{3}{c|}{Simian$_{df}$} 
-			& \multicolumn{3}{c|}{Simian$_{\textrm{\textit{EvCl}}}$}
-			& \multicolumn{3}{c|}{NiCad$_{df}$} 
-			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
-			& \multicolumn{3}{c|}{1406 fragments} 
-			& \multicolumn{3}{c|}{1360 fragments}  
-			& \multicolumn{3}{c|}{1197 fragments} 
-			& \multicolumn{3}{c}{12884 fragments} \\ \cline{2-13}
-			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
-			\hline
-			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
-			Mean & 52 & 7.45 & 28\% 		& 44104 & 4.81 & 29\% 		& 106 & 9.54 & 25\% 	& 16046 & 5.31 & 21\% \\
-			Std Dev. & 147 & 3.22 & 23\% 	& 1040483 & 1.20 & 19\% 	& 209 & 3.10 & 18\% 	& 21890 & 1.92 & 16\% \\
-			Max  & 1020 & 49.00 & 94\% 		& 38223637 & 18.00 & 89\% 	& 2100 & 39.00 & 81\% 	& 442655 & 50.00 & 93\% \\
-			Min  & 1 & 5.00 & 1\% 			& 1 & 4.00 & 2\% 			& 1 & 7.00 & 2\% 		& 1 & 3.00 & 1\% \\
-			Median  & 3 & 7.00 & 21\% 		& 24 & 5.00 & 25\% 			& 20 & 8.00 & 19\% 		& 8003 & 5.00 & 16\% \\
-			Mode  & 1 & 7.00 & 33\% 		& 1 & 4.00 & 50\% 			& 1 & 8.00 & 67\% 		& 1 & 4.00 & 33\% \\
-			\hline
-		\end{tabular} %
-%	}
-\end{table*}
+%\begin{table*}[h]
+%	\centering
+%	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
+%	\label{tab:raw_stats}
+%%	\resizebox{\columnwidth}{!}{%
+%	\small
+%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
+%			\hline
+%			\multirow{3}{*}{Statistics} 
+%			& \multicolumn{3}{c|}{Simian$_{df}$} 
+%			& \multicolumn{3}{c|}{Simian$_{\textrm{\textit{EvCl}}}$}
+%			& \multicolumn{3}{c|}{NiCad$_{df}$} 
+%			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
+%			& \multicolumn{3}{c|}{1406 fragments} 
+%			& \multicolumn{3}{c|}{1360 fragments}  
+%			& \multicolumn{3}{c|}{1197 fragments} 
+%			& \multicolumn{3}{c}{12884 fragments} \\ \cline{2-13}
+%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
+%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
+%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
+%			\hline
+%			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
+%			Mean & 52 & 7.45 & 28\% 		& 44104 & 4.81 & 29\% 		& 106 & 9.54 & 25\% 	& 16046 & 5.31 & 21\% \\
+%			Std Dev. & 147 & 3.22 & 23\% 	& 1040483 & 1.20 & 19\% 	& 209 & 3.10 & 18\% 	& 21890 & 1.92 & 16\% \\
+%			Max  & 1020 & 49.00 & 94\% 		& 38223637 & 18.00 & 89\% 	& 2100 & 39.00 & 81\% 	& 442655 & 50.00 & 93\% \\
+%			Min  & 1 & 5.00 & 1\% 			& 1 & 4.00 & 2\% 			& 1 & 7.00 & 2\% 		& 1 & 3.00 & 1\% \\
+%			Median  & 3 & 7.00 & 21\% 		& 24 & 5.00 & 25\% 			& 20 & 8.00 & 19\% 		& 8003 & 5.00 & 16\% \\
+%			Mode  & 1 & 7.00 & 33\% 		& 1 & 4.00 & 50\% 			& 1 & 8.00 & 67\% 		& 1 & 4.00 & 33\% \\
+%			\hline
+%		\end{tabular} %
+%%	}
+%\end{table*}
 
@@
 		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 319 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 318 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
 		\hline
@@
 		\hline 
-		Total & 84 & 0 & 370 & 21 & 475 \\
+		Total & 84 & 0 & 370 & 21 & 476 \\
 		\hline

### 2016-11-09 latex-acm/cloneoverflow.tex
Updated latex

@@
 The classification scheme is described in \Cref{tab:classification_scheme} and the classification results are shown in \Cref{tab:classification_good_o}.
-We have manually investigated all of the 2,261 good-match ones reported by agreement of four different Simian and NiCad settings.
-However, for the ok-match, we could not investigate all of the 23,868 pairs manually.
-According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number, 2225 (99.87\%), of false positive results (category D, E, and F).
-Thus, we decided to leave them out of the manual investigation of ok-match pairs.
-There are totally 608 ok-match pairs that were investigated.
-The 39 true positive pairs found are combinations of 8 unique Stack Overflow fragments, and 9 unique Qualitas Java files from 6 different projects.
+We have manually investigated all of the 2,261 good-match clone pairs.
+However, for the ok-match clone pairs, we could not feasibly investigate 23,868 pairs manually.
+According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,225 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs).
+We thus decided to leave them out of the manual investigation.
+There are totally 4,625 ok-match pairs that were investigated.
+The 49 true positive pairs found are combinations of 12 unique Stack Overflow fragments, and 14 unique Qualitas Java files from 10 different projects.
 

### 2016-11-10 latex-acm/cloneoverflow.tex
Updated the Stack Overflow related work

@@
 	\centering
-	\caption{Classifications of clone creation}
+	\caption{Classifications of online code clones}
 	\label{tab:classification_scheme}
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{Sankey_proj}
+	\includegraphics[width=0.9\linewidth]{Sankey_proj}
 	\caption{Relationships of 53 Stack Overflow clone pairs to their original projects. 49 are outdated and 4 are deleted (shown using (d) suffix).}
@@
 
+\subsection{Issue~3 -- external clones}
+
 \subsection{Issue~2 -- software licensing violations}
@@
 \begin{itemize}
+	\item Stack Overflow
+	\begin{itemize}
+		\item Code example \cite{Nasehi2012}
+		\item Search for code in Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014}
+		\item Stack Overflow to help developers \cite{Ponzanelli2013, Ponzanelli2014}
+		\item Improving Stack Oveflow \cite{Diamantopoulos2015, Wang2014, Bosu2013}
+		\item Developers' behaviours on Stack Overlow \cite{Wang2013, Movshovitz-Attias2013}
+	\end{itemize}
 	\item Code clones 
@@
 			\item Clone evolution \cite{Pate2013,Mondal2011}
-			\item Comparing Quality Metrics for Cloned and non cloned Java Methods : A Large Scale Empirical Study \cite{Saini2016}.
+			\item Comparing Quality Metrics for Cloned and non cloned Java Methods: A Large Scale Empirical Study \cite{Saini2016}.
 		\end{itemize}
@@
 
-	\item Stack Overflow
-	\begin{itemize}
-		\item Code example \cite{Nasehi2012}
-		\item Search for code in Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014}
-	\end{itemize}
 \end{itemize}

### 2016-11-10 latex-acm/cloneoverflow.tex
Updated the Qualitas corpus

--- 2016-11-09 latex-acm/cloneoverflow.tex
@@
 \textbf{Open source systems}: we selected an established corpus for empirical software engineering studies called \textbf{Qualitas} \cite{QualitasCorpus}.
-\FIXME{more details about Qualitas and why we chose it}.
-We selected the 20130901r version of Qualitas corpus containing 112 Java open source projects with releases no later than 1st September 2013.
+It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
+The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}.
+We selected the 20130901r version of Qualitas corpus containing 112 Java open source projects.
+This release contains projects with releases no later than 1st September 2013.
 We chose the snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow.
-The 20130901r snapshot provides Java code that is at least 3 years old which is sufficient for a number of code snippets to be copied onto Stack Overflow.
+The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (2016) which is sufficient for a number of code snippets to be copied onto Stack Overflow.
 Out of 112 Qualitas projects, there are 3 projects, \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}, that do not contain any Java source code file so they are removed from the study.
@@
 		\hline
-		jung2 & 2\_0\_1 & N/A \\
+		jung2 & 2-0-1 & N/A \\
 		\hline

### 2016-11-10 latex-acm/cloneoverflow.tex

--- 2016-11-10 latex-acm/cloneoverflow.tex
@@
 We call them \textbf{online code clones}.
-There are three ways to create online code clones: 1) code is cloned from a software project to Stack Overflow as an example; 2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; and 3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium.
+There are three ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; and (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium.
 Online code clones can similarly lead to a problem of bug propagation as classical code clones.
@@
 
-\textbf{Open source systems}: we selected an established corpus for empirical software engineering studies called \textbf{Qualitas} \cite{QualitasCorpus}.
-\FIXME{more details about Qualitas and why we chose it}.
-We selected the 20130901r version of Qualitas corpus containing 112 Java open source projects with releases no later than 1st September 2013.
-We chose the snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow.
-The 20130901r snapshot provides Java code that is at least 3 years old which is sufficient for a number of code snippets to be copied onto Stack Overflow.
-Out of 112 Qualitas projects, there are 3 projects, \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}, that do not contain any Java source code file so they are removed from the study.
+\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus}.
+It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
+The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}.
+We selected the 20130901r snapshot of Qualitas corpus containing 112 Java open source projects.
+This release contains projects with releases no later than 1st September 2013.
+We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow.
+The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment, January--December 2016.
+The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow.
+Out of 112 Qualitas projects, there are 3 projects; \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}; that do not contain Java source code so they are removed from the study.
 This results in totally 109 projects analysed in the study.
@@
 \subsubsection{Clone Detectors}
-There are a number of restrictions in terms of choosing clone detection tools for this study.
-Firstly, they have to compatible with Java.
+There is a number of restrictions in terms of choosing clone detection tools for this study.
+Firstly, they have to support Java.
 Secondly, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods.
-Hence, the tool must be flexible enough to process code snippets which are not in a complete block or not compilable.
+Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable.
 Thirdly, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
-We have tried running 5 state-of-the-arts clone detectors including Simian \cite{simian}, NiCad \cite{Cordy,Roy2008}, CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a} against the Stack Overflow and Qualitas datasets.
+We have tried running 5 state-of-the-art clone detectors including Simian \cite{simian}, NiCad \cite{Cordy,Roy2008}, CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a} against Stack Overflow and Qualitas datasets.
 CCFinder, iClones, and DECKARD failed to successfully detect clones between 144,075 Stack Overflow code snippets and 109 Qualitas projects.
@@
 Simian and NiCad completed the detection with success.
-We found that both of them are flexible enough to handle million-SLOC code corpus with method or class incompleteness.
+We found that both of them are also flexible enough to handle million-SLOC code corpus with method or class incompleteness.
 So, we decided to use both of them.
@@
 It is a command-line tool which enables us to automate the detection.
-It also offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect clones of type 1 and type 2.
+Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect clones of type 1 and type 2.
 \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity.
-It can detect clone up to type 3 and is used in several clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
+It can detect clones up to type 3 and is used in several clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
 It utilises TXL for parsing and pretty-printing source code.
@@
 
-\subsubsection{Agreement-based Clone Detection}
-The number of detected clones between the two datasets can be very large and infeasible for human to manually check all of them.
+\subsubsection{Agreement-based Clone Filtering}
+The number of detected clones between two datasets  can be very large.
+In our study, there are totally 266,837,480 clone pairs reported.
+It is infeasible for human to manually validate all of them.
+One can do sampling of clones from this huge clone pair set.
+However, they may end up having most of them false positive clones.
 Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish.
 Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}.
-By using this agreement-based clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the agreed clone pairs.
-To find agreement of two clone pairs, we resort to an approach proposed by a study by Bellon et al.~\cite{Bellon2007}.
-Two clone pairs which have overlapping clone lines can be considered as a good-match or an ok-match pair.
+By using this agreement-based clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
+To find agreement of two clone pairs, we resort to an approach proposed in a study by Bellon et al.~\cite{Bellon2007}.
+Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair.
 A good-match clone pair has stronger agreement than an ok-match pair.
-We follow the same following definitions introduced in the original paper:
+We follow the same following definitions introduced in the original paper.
 
 %good and ok-match clone pairs are defined as follows. 
-A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}: \textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).
+A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}, i.e.
+\textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).
 We can define \textit{overlap} and \textit{contained} value of two clone pairs as
@@
 
-Furthermore, \textit{ok-value} is defined as
+\textit{ok-value} is defined as
 %\squeezeup
@@
 
-Using this good-match and ok-match criteria with a predefined threshold \textit{p}, we prune the detected clone pairs for manual investigation.
-good-match pairs are the ones with the highest confident to be true clones, followed by ok-match pairs, and followed by clone pairs without agreement.
+Using this good-match and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266-million candidate clone pairs for manual investigation.
+good-match pairs are the ones with the highest confident and ranked the first to be looked at, followed by ok-match pairs, and followed by clone pairs without agreement.
 
 \subsection{Clone detectors' parameter tuning}
-We are aware of effects of configurations to clone detection results and needs for searching for optimised configurations in empirical clone studies \cite{Wang2013,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
-However, considering the size of the two datasets and search space of at least 15 of Simian's and 5 of NiCad's parameters, we are hindered from finding the best configurations of the tools.
-Thus, we decided to configure Simian and NiCad using two established settings: 1) the tools' default settings chosen by the tools' creators (denoted as \textit{df}), and 2) the general settings for Java sets from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}).
+We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2013,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
+However, considering the size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools.
+Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{df}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}).
 The details of the two configurations are described in \Cref{t:param_tuning}.
-With our two tools and these two sets of configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.
+Having two clone detectors multiplied by two chosen configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
 
@@
 
-The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} settings are presented in \Cref{tab:raw_stats}.
-Preliminary manual investigation of Simian's clone report showed that there were problematic 11 fragments.
+The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} configurations are presented in \Cref{tab:raw_stats}.
+Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments.
 These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones of array initialisation.
 Hence, they were removed from Simian's clone reports before the analysis.
-From \Cref{tab:raw_stats}, Simian clones are from approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively.
-NiCad$_{df}$ reports clones from 1,197 Stack Overflow code snippets while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones from a large amount of 12,884 snippets due to its relaxed settings.
-In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report a large number of clone pairs of 59,936,722 and 206,718,663 respectively.
+From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively.
+NiCad$_{df}$ reports clones in 1,197 Stack Overflow code snippets, while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones in a larger number of 12,884 snippets  mainly due to its relaxed configurations.
+In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report an enormous number of clone pairs of 59,936,722 and 206,718,663 respectively.
 This is expected since EvaClone configurations prefer recall \cite{Wang2013}.
-The average clone size of Simian$_{df}$ is 7.45 which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81.
-Similarly, NiCad$_{df}$ has an average clone size of 9.54 which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$.
-We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones but result in higher agreements.
-The average percentage of code in Stack Overflow snippets that are clones reported by Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\% and 21\% accordingly.
+The average clone size of Simian$_{df}$ is 7.45 lines which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81.
+Similarly, NiCad$_{df}$ has an average clone size of 9.54 lines which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$.
+We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones.
+The average percentage of Stack Overflow code snippets that are cloned according to Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\%, and 21\% accordingly.
 
@@
 
-\subsection{Agreement based clone pairs}
-
-We use a threshold \textit{p} of 0.7 for both good and ok-match.
-A visualisation of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} settings can be seen from \Cref{fig:venn4_orig_good}.
-We found that NiCad throws renaming and clustering errors while processing some Qualitas projects as listed in \Cref{tab:projects_missing}.
-%This resulted in not all 109 projects had NiCad clone reports.
-NiCad$_{\textrm{\textit{df}}}$, produced clustering errors for 6 projects.
-NiCad$_{\textrm{\textit{EvCl}}}$ produced renaming error for 4 projects, and clustering error for 13 projects.
-As a result, we did not have NiCad clone reports for these projects and hence they are missing from agreement-based clone pair calculation.
-\FIXME{Report the errors to NiCad creator.} There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$-NiCad$_{df}$, 26 pairs from Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.
-\Cref{fig:venn4_orig_ok} show the distribution of 23,868 unique ok-match pairs, which subsume the good-match pairs.
-There are 3,800 pairs from Simian$_{df}$-NiCad$_{df}$, 1,017 pairs from Simian$_{df}$-NiCad$_{\textrm{\textit{EvCl}}}$, 88 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{df}$, and 19,777 pairs from Simian$_{\textrm{\textit{EvCl}}}$-NiCad$_{\textrm{\textit{EvCl}}}$.
-Between the four sets, there are a few clone pairs that are common between two adjacent sets, but there is no clone pair that is agreed by all four combinations.
+\subsection{Agreement-based clone pairs}
+
+Agreement-based clone pairs are clone pairs that pass Bellon's criteria and selected for manual investigation.
+We select a threshold \textit{p} of 0.7 for both good and ok-match similar to the original study \cite{Bellon2007}.
+The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
+NiCad generated errors and stopped processing while it was analysing some Qualitas projects.
+\FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ unsuccessfully detected clones in 6 projects due to clustering errors.
+For NiCad$_{\textrm{\textit{EvCl}}}$, the tool generated renaming errors for 4 projects, and clustering errors for 13 projects.
+As a result, we did not have NiCad clone candidates for 6 (\textit{df}) and 27 projects (\textit{EvCl}) in the agreement-based clone pairs.
+Unfortunately, this also has an effect to Simian clone candidates of the same projects to be removed from the agreement-based clone pairs since they do not have matching clone pairs.
+The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are depicted in \Cref{fig:venn4_orig_good}.
+There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
+ok-match clone pairs subsume the good-match pairs according to the criteria.
+As a result, there are 23,868 clone pairs, which are 3,800 pairs from Simian$_{df}$--NiCad$_{df}$, 1,017 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 88 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 19,777 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
+Between the four configuration sets, there are a few clone pairs that are shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.
 
@@
 
-\subsubsection{Manual investigation of agreement-based clone pairs}
+\subsubsection{Classifications of online code clones}
 
@@
 
-The classification scheme is described in \Cref{tab:classification_scheme} and the classification results are shown in \Cref{tab:classification_good_o}.
-We have manually investigated all of the 2,261 good-match clone pairs.
-However, for the ok-match clone pairs, we could not feasibly investigate 23,868 pairs manually.
-According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,225 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs).
-We thus decided to leave them out of the manual investigation.
+We need an appropriate classification scheme to be able to meaningfully manually categorise the selected clone candidates.
+We adapted the classifications from a study by Kapser et al.
+\cite{Kapser2006}.
+The online code clone classification scheme is described in \Cref{tab:classification_scheme}.
+Due to differences in the experimental settings of the study, we adopted some of the original classifications and added a few more classifications to match with our datasets and context.
+The final seven categories (A--F) have been observed to be common clone patterns found from a manual check of 100 random sample clone pairs.
+Category A is a clone pair that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation or links in Stack Overflow post), and vice versa in category A'.
+Category B is a clone pair that is exactly identical or highly similar but without any attribution of copying.
+Category C is a clone pair that has information confirming of copying but from the same external source.
+Category D is a clone pair that is either boiler-plate code (e.g.
+\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.
+GUI initialisation).
+Category E are clones created by inheriting the same super class or implementing the same interface.
+They usually share similar overriding methods.
+The last category, category F, are false clones that have accidental similarity after code normalisation or other causes.
+Using this classification scheme, we consider clone pairs in category A, A', B, C as true positive, and clone pairs in category D, E, F as false positive.
+
+\subsubsection{Manual investigation of agreement-based clone pairs}
+
+The first author who has been working on clone detection research for two years takes the role of an investigator who performs manual investigation.
+Following the classification scheme, the investigator manually goes through each agreement-based clone pair, looks at the clones, and chooses the most appropriate category for the pair.
+A relevant and useful observation is also recorded for each clone pair.
+The classification results are shown in \Cref{tab:classification_good_o}.
+We have manually investigated 2,261 good-match clone pairs.
+There is one clone pair found to be copied from a Qualitas project to Stack Overflow, 4 pairs that are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code), and 3 pairs that are copied from external sources.
+The rest are false positive clones.
+58 clone pairs are found to \verb|equals()| methods, or getters and setters.
+Six pairs are similar code from inheritance of the same superclass or implementing the same interface.
+Finally, 2,189 clone pairs are false clones.
+
+For the ok-match clone pairs, we could not feasibly investigate 23,868 pairs manually.
+According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,253 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs) due to its recall preference.
+We thus decided to leave this configuration out of the ok-match manual investigation.
 There are totally 4,625 ok-match pairs that were investigated.
-The 49 true positive pairs found are combinations of 12 unique Stack Overflow fragments, and 14 unique Qualitas Java files from 10 different projects.
-
-Since we are not certain about the direction of copying in the B-classified pairs, we checked the modification time of each Java file in Qualitas project and compare it to the timestamp of Stack Overflow answers.
-We found that all Stack Overflow code fragments were posted after their respectively similar Java files in Qualitas project.
-This means that the copying can only be either (1) from Qualitas to Stack Overflow or (2) from a third source to both Stack Overflow and Qualitas independently.
-
-%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvCl}}}$-NiCad$_{\mathrm{\textit{EvCl}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of Simian$_{df}$-NiCad$_{df}$, Simian$_{df}$-NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}$-NiCad$_{df}$.
+The 49 true positive pairs found are combinations of 8, 33, and 8 clone pairs in category A, B, and C respectively.
+
+We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying.
+We thus checked the timestamp of each Java file in Qualitas project and compared it to their respective timestamp of Stack Overflow posts.
+We found that all Stack Overflow posts were created after their respectively Qualitas Java files \FIXME{check again since the dataset is updated}.
+This means that the copying can only be either (1) from Qualitas to Stack Overflow or (2) from an external source to both Stack Overflow and Qualitas independently.
+There is no clone pairs found in A' category.
+
+%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvCl}}}$--NiCad$_{\mathrm{\textit{EvCl}}}$ altogether due to its large number of false positive.
+With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}$--NiCad$_{df}$.
 We had not done any investigation of good-match since there were no good-match pairs for these 3 agreements.
@@
 	\centering
-	\caption{Classification results of agreement-based and non agreement-based clone pairs)}
+	\caption{Classification results of agreement-based and non agreement-based clone pairs.
+S$_u$ denotes a number of unique Stack Overflow snippets.
+Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
 	\label{tab:classification_good_o}
@@
 
-\subsection{Non-agreement based clone pairs}
-In the preliminary stage of our experiment, we found that there are 41 Stack Overflow fragments reported by Simian with default configurations.
+\subsection{Non agreement-based clone pairs}
+%In the preliminary stage of our experiment, we found that there are 41 Stack Overflow fragments reported by Simian with default configurations.
 However, only 10 of them appear in the new results using tool's agreement.
@@
 
-With our 4 settings, we decided to investigate only 2 settings, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their large number of false positives.
-With the 2 selected settings, we investigated clone pairs having the minimum clone size of 10 SLOC as they are meaningful and tend to be real clone in modern clone detection \cite{Sajnani2016}.
+The non agreement-based clone pairs are clone pairs that are reported by a single tool (either Simian or NiCad) and do not have agreement with another tool.
+The disagreement can be from misalignment of clone lines or different configurations that results in different clones reported.
+They are also clone pairs in projects that have NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl}).
+With the four configuration combinations, we decided to investigate only two, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively).
+They also have a high possibility of containing a large number of false positives due to relaxation of EvaClone configurations.
+
+Even choosing only the default configurations, the number of clone pairs are still very large.
+We hence apply two pruning filters: (1) clone size and (2) similarity threshold.
+For the clone size filter, we raise the minimum clone size to 10 line.
+The clone size filter is applied to Simian clone pairs only since its default configurations consider a minimum of 6 line as clones.
+On the other hand, a minimum of 10 lines is already a default configuration of NiCad.
+We found that this filter works well with Simian clone pairs resulting in a manageable amount of 795 clone pairs remaining.
+Regarding the similarity threshold filter, it is only applied to NiCad clone pairs since Simian does not provide this similarity threshold configuration.
+We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%.
+This results in 159 clone pairs remaining.
+The summary of non agreement-based clone pairs is shown in \Cref{tab:classification_indv_stats}.
 
@@
 Out of 9,383 pairs, 140 of them are the ones found in \textit{ok-}pairs using agreement-based detection.
-We filtered the results further by removing false positives such as similar \textit{equals()}, \textit{hashCode()} methods, getters and setters out by using regular expression.
+We filtered the results further by removing false positives such as similar \verb|equals()|, \verb|hashCode()| methods, getters and setters out by using regular expression.
 We managed to remove 8,956 pairs using this method.

### 2016-11-14 cloneoverflow-latex/cloneoverflow.tex
Updated Latex and a few results + diagrams

--- 2016-11-10 latex-acm/cloneoverflow.tex
@@
 Each run is composed of the whole Stack Overflow data and a single Qualitas project.
-We repeat the process until we cover 109 projects.
+We repeat the process until we cover 111 projects.
 
@@
 		\hline 
-		Qualitas &  138,238 & 16,081,899 \\ 
+		Qualitas &  160,937 & 19,086,883 \\ 
 		\hline 
@@
 The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow.
-Out of 112 Qualitas projects, there are 3 projects; \textit{eclipse}, \textit{jre}, and \textit{squirrel-sql}; that do not contain Java source code so they are removed from the study.
-This results in totally 109 projects analysed in the study.
-As shown in \Cref{tab:datasets}, the 109 Qualitas project have 138,238 Java files containing 16,081,899 lines of code.
+Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code so it is removed from the study.
+This results in totally 111 projects analysed in the study.
+As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code.
 %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.
@@
 			\hline
-			Snippets & 1,406 & 1,360 & 1,197 & 12,884 \\
-			Total C$_{\textrm{\textit{pairs}}}$ & 54,790 & 59,936,722 & 127,305 & 206,718,663 \\
-			Avg.~C$_{\textrm{\textit{pairs}}}$ & 52 & 44,104 & 106 & 16,046 \\
-			Avg.~C$_{\textrm{\textit{size}}}$ & 7.45 & 4.81 & 9.54 & 5.31 \\
-			Avg.~C$_{\textrm{\textit{\%}}}$ & 28\% & 29\% & 25\% & 21\% \\
+			Snippets & 1,086 & 1,530 & 1,240 & 12,886 \\
+			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,372,599 & 229,176 & 206,760,077 \\
+			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,447 & 185 & 16,047 \\
+			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.64 & 5.32 \\
+			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
 			\hline
@@
 		\hline
-		\textit{Successful} & 109 & 109 & 97 & 82 \\ 
+		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
 		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
@@
 		\hline
-		\textit{df} & \textit{df} & 10 	& 3800 \\ 
+		\textit{df} & \textit{df} & 10 	& 9062 \\ 
 		\textit{df} & \textit{EvCl} 	& 26 	& 1017 \\ 
@@
 		\hline
-		\multicolumn{2}{l|}{Total} & 2274 & 24682 \\
-		\hline
-		\multicolumn{2}{l|}{Total (unique)} & 2261 & 23868 \\
+		\multicolumn{2}{l|}{Total} & 2274 & 29944 \\
+		\hline
+		\multicolumn{2}{l|}{Total (unique)} & 2261 &  29091 \\
 		\hline
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{venn4_pairs_ok_pt1+2}
+		\includegraphics[width=0.8\linewidth]{venn4_pairs_ok_pt1+2+3}
 		\caption{Distributions of ok-match(0.7) pairs}
@@
 		\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
-		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 33  & 8 & \textbf{49} & 12 & 14 & 10 & 4459 & 35 & 82 & \textbf{4576} & 99 & 136 & 29 & \textbf{4625} & 110 & 150 & 33 \\
-		\hline 
-		\hline 
-		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 35 & 0 & 90 & 8 & \textbf{133} & 68 & 59 & 23 & 13 & 12 & 134 & \textbf{159} & 39 & 72 & 23 & \textbf{292} & 103 & 125 & 31 \\
-		%		\multirow{1}{*}{\textit{Simian$_{df}$}} & 36 & 0 & 229 & 3 & \textbf{268} & 76 & 151 & 14 & 169 & 52 & 14 & \textbf{235} & 92 & 119 & 22 & \textbf{503} & 164 & 261 & 24 \\
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 71 & 0 & 318 & 11 & \textbf{401} & 138 & 210 & 37 & 182 & 64 & 148 & \textbf{394} & 120 & 191 & 45 & \textbf{795} & 246 & 386 & 55 \\
-		\hline
-		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 5 & 0 & \textbf{9} & 9 & 5 & 4 & 24 & 3 & 78 & \textbf{105} & 41 & 39 & 12 & \textbf{114} & 48 & 44 & 14 \\ 
-		%		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 0  & 0 & 10 & 0 & \textbf{10} & 7 & 8 & 5 & 6 & 3 & 26 & \textbf{35} & 17 & 16 & 8 & \textbf{45} & 24 & 24 & 9 \\ 
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 4  & 0 & 15 & 0 & \textbf{19} & 15 & 13 & 9 & 30 & 6 & 104 & \textbf{140} & 51 & 55 & 20 & \textbf{159} & 66 & 68 & 23 \\ 
-		\hline
-		%		\multirow{1}{*}{\textit{NiCad$_{df}$}*} & 4  & 0 & 1 & 0 & \textbf{5} & 4 & 5 & 3 & 23 & 1 & 67 & \textbf{91} & 28 & 31 & 10 & \textbf{96} & 33 & 37 & 13 \\ 
-			%		\hline
+		\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
+		\hline 
+		\hline 
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 80 & 0 & 336 & 16 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
+		\hline
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
+		\hline
 	\end{tabular} 
@@
 \end{table*}
-
-%\begin{table}
-%	\centering
-%	\caption{Distribution of classification category A--F according to good- and \textit{ok-}match pairs. S denotes Simian and N denotes NiCad tool.}
-%	\label{tab:good_classification}
-%	\small
-%	\begin{tabular}{|l|r|r|r|r|r|r|r|r|}
-%		\hline 
-%		Category   & A   & 	A'   & 	B   & C   & D   &	E   &	F   & Total  \\
-%		\hline
-%		\hline
-%		\multicolumn{9}{|c|}{good-match pairs} \\
-%		\hline
-%		S$_{df}$--N$_{df}$   & 1 & 0 & 1 & 0 & 1 & 4 & 0 & 7 \\
-%		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   & 1 & 0 & 0 & 3 & 14 & 1 & 1 & 20 \\
-%		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   & 0 & 0 & 3 & 0 & 7 & 0 & 0 & 10 \\
-%		S$_{\textrm{\textit{EvCl}}}$--N$_{\textrm{\textit{EvCl}}}$   & 0 & 0 & 1 & 0 & 20 & 0 & 2188 & 2228 \\
-%		\hline
-%		Total   &   2   &   0   &  2   &  6   &   26   &   10   & 1320  & 1366 \\
-%		Total (unique)  &   1   &   0   &  1   &  3   &   26   &   6   & 1320  & 1352 \\
-%		\hline
-%		\hline 
-%%		Category   																										& A   	& 	A' 	& 	B  & C	   & D   	&	E   &	F   & Total  \\
-%%		\hline
-%		\multicolumn{9}{|c|}{ok-match pairs} \\
-%		\hline
-%		S$_{df}$--N$_{df}$        & 3 	& 0 	& 12	& 6 	& 3755  & 8	& 7  &  3791 \\
-%		S$_{df}$--N$_{\textrm{\textit{EvCl}}}$   	& 8 	& 0 	& 28	& 4	& 904 & 29  & 32 &  1005 \\
-%		S$_{\textrm{\textit{EvCl}}}$--N$_{df}$   	& 0 	& 0 	& 0 	& 0 	 & 29 	  & 0 		& 24 	& 53 \\
-%		\hline
-%		Total   &   11  &   0   &  32   &  10   &   712   &   30   & 63  & 858 \\
-%		Total (unique)  &   8  &   0   &  23   &  8   &  480  &  28  & 61  & 608 \\
-%		\hline
-%	\end{tabular} 
-%\end{table}
 
@@
 	\centering
-	\caption{Statistics of non agreement-based clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
+	\caption{Statistics of non-agreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
 	\label{tab:classification_indv_stats}
 	\small
-	\begin{tabular}{l|r|r|r|r}
-		\hline 
-		Tool & Clone pairs & ok-pairs & filtered & remaining \\ 
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|p{2.4cm}|r|r|r}
+		\hline 
+		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
 		%\hline 
@@
 		\hline
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 18422 & 140 & 17490 & 792 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline + reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
 		\hline
@@
 %		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & 29227  & 378 & 28690 & 159 \\
-		\hline
-	\end{tabular} 
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
+		\hline
+	\end{tabular} %
+	}
 \end{table}
 
-\subsubsection{Manual investigation of non agreement-based clone pairs}
+\subsubsection{Manual investigation of non-agreed clone pairs}
 %\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
@@
 		good-pairs & 1 & 0 & 4 & 3 & 8 \\
-		ok-pairs & 8 & 0 & 33 & 8 & 49 \\
-%		Simian$_{df}$ pairs-1 & 35 & 0 & 90 & 8 & 133 \\
-%		Simian$_{df}$ pairs-2 & 36 & 0 & 229 & 3 & 268 \\
-		Simian$_{df}$ pairs & 71 & 0 & 318 & 10 & 399 \\
-%		NiCad$_{df}$ pairs & 4 & 0 & 5 & 0 & 9 \\
-%		NiCad$_{df}$ pairs-2 & 0 & 0 & 10 & 0 & 10 \\
-		NiCad$_{df}$ pairs & 4 & 0 & 15 & 0 & 19 \\
-		\hline 
-		Total & 84 & 0 & 370 & 21 & 476 \\
+		ok-pairs & 8 & 0 & 29 & 10 & 47 \\
+		Simian$_{df}$ pairs & 80 & 0 & 336 & 16 & 432 \\
+		NiCad$_{df}$ pairs & 8 & 0 & 27 & 1 & 36 \\
+		\hline 
+		Total & 97 & 0 & 396 & 30 & 523 \\
 		\hline

### 2016-11-15 cloneoverflow-latex/cloneoverflow.tex
Updated sankey and latex to reflect changes to 2 new projects

@@
 		\hline 
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & 80 & 0 & 336 & 16 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & 19 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
 		\hline
@@
 		\hline
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline + reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
 		\hline
@@
 		ok-pairs & 8 & 0 & 29 & 10 & 47 \\
-		Simian$_{df}$ pairs & 80 & 0 & 336 & 16 & 432 \\
+		Simian$_{df}$ pairs & 79 & 0 & 336 & 17 & 432 \\
 		NiCad$_{df}$ pairs & 8 & 0 & 27 & 1 & 36 \\
 		\hline 
-		Total & 97 & 0 & 396 & 30 & 523 \\
+		Total & 96 & 0 & 396 & 31 & 523 \\
 		\hline
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{Sankey_proj}
-	\caption{Relationships of 53 Stack Overflow clone pairs to their original projects. 49 are outdated and 4 are deleted (shown using (d) suffix).}
+	\includegraphics[width=\linewidth]{Sankey_proj}
+	\caption{Relationships of 58 Stack Overflow clone pairs to their original projects. 55 are outdated and 3 are deleted (shown using (d) suffix).}
 	\label{fig:sankey}
@@
 		aspectj & 2 & 2 & 0 & 0 & 0 \\
+		eclipse-SDK & 12 & 5 & 7 & 0 & 0 \\
 		hadoop & 14 & 9 & 5 & 0 & 0 \\
@@
 		\hline
-		Total & 84 & 50 & 30 & 3 & 1 \\
+		Total & 96 & 55 & 37 & 3 & 1 \\
 		\hline
@@
 	\centering
-	\caption{53 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted and their respective licenses}
+	\caption{58 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted and their respective licenses}
 	\label{tab:stale_code_details}
@@
 			2 & aspectj-1.6.9  & Agent.java  & -- & 18303692 & alteration  & 2015-09-08 \\
-		3 & hadoop-1.0.0 & DBCountPageView.java & Apache-2 & 21702608 & alteration & 2011-06-12 \\
-		4 & hadoop-1.0.0 & DBCountPageView.java & Apache-2 & 21702608 & alteration & 2011-06-12 \\
-		5 & hadoop-1.0.0 & JobSubmissionFiles.java & Apache-2 & 14845581 & alteration & 2012-06-25 \\
-		6 & hadoop-1.0.0 & LineRecordReader.java & Apache-2 & 16180910 & alteration & 2011-07-25 \\
-		7 & hadoop-1.0.0 & LineRecordReader.java & Apache-2 & 16180910 & alteration & 2011-07-25 \\
-		8 & hadoop-1.0.0 & StringUtils.java & Apache-2 & 801987 & alteration & 2013-02-04 \\
-		9 & hadoop-1.0.0 & TestJobCounters.java & Apache-2 & 18833798 & alteration & 2011-06-12 \\
-		10 & hadoop-1.0.0 & TextOutputFormat.java & Apache-2 & 16928749 & alteration & 2011-06-12 \\
-		11 & hadoop-1.0.0 & WritableComparator.java & Apache-2 & 22315734 & alteration & 2014-11-20 \\
-		12 & hibernate-4.2.2 & ConnectionProviderInitiator.java & -- & 15168494 & alteration & 2012-06-24 \\
-		13 & hibernate-4.2.2 & Example.java & -- & 24924255 & alteration & 2013-04-23 \\
-		14 & hibernate-4.2.2 & SchemaUpdate.java & -- & 23520731 & alteration & 2016-02-05 \\
-		15 & hibernate-4.2.2 & SettingsFactory.java & -- & 8257554 & removal & 2011-03-11 \\
-		16 & hibernate-4.2.2 & SQLServer2005LimitHandler.java & -- & 23967852 & alteration & 2015-03-12 \\
-		17 & jasperreports-3.7.4 & JRVerifier.java & GLGPLv3+ & 8037824 & alteration & 2008-04-17 \\
-		18 & jasperreports-3.7.4 & JRVerifier.java & GLGPLv3+ & 8037824 & alteration & 2011-05-20 \\
-		19 & jfreechart-1.0.13 & AbstractXYItemRenderer.java & GLGPLv2.1+ & 12936580 & alteration & 2016-02-19 \\
-		20 & jfreechart-1.0.13 & KeyToGroupMap.java & GLGPLv2.1+ & 16058183 & alteration & 2013-07-03 \\
-		21 & jfreechart-1.0.13 & SpiderWebPlot.java & GLGPLv2.1+ & 21998949 & alteration & 2008-06-02 \\
-		22 & jfreechart-1.0.13 & SpiderWebPlot.java & GLGPLv2.1+ & 21998949 & alteration & 2008-06-02 \\
-		23 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
-		24 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
-		25 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
-		26 & jgraph-5.13.0.0 & HelloWorld.java & GLGPLv2.1+ & 6722760 & rewriting & 2014-04-13 \\
-		27 & jstock-1.0.7c & GoogleMail.java & GPLv2+ & 14940863 & alteration & 2015-12-13 \\
-		28 & jstock-1.0.7c & GoogleMail.java & GPLv2+ & 24680923 & alteration & 2015-12-13 \\
-		29 & jung2-2\_0\_1 & ShortestPathDemo.java & -- & 6025026 & alteration & 2010-04-13 \\
-		30 & jung2-2\_0\_1 & ShortestPathDemo.java & -- & 6025026 & alteration & 2010-04-13 \\
-		31 & junit-4 & Assert.java & -- & 23586872 & alteration & 2015-05-12 \\
-		32 & junit-4 & ExternalResource.java & -- & 7504040 & alteration & 2016-06-25 \\
-		33 & junit-4.11 & ExpectException.java & -- & 8802082 & alteration & 2014-05-26 \\
-		34 & poi-3.6-20091214 & WorkbookFactory.java & Apache-2 & 12593810 & alteration & 2015-04-29 \\
-		35 & spring-framework-3.0.5 & AnnotationMethodHandlerExceptionResolver.java & Apache-2 & 5660519 & removal & 2012-01-20 \\
-		36 & spring-framework-3.0.5 & AutowireUtils.java & Apache-2 & 20913543 & alteration & 2014-10-28 \\
-		37 & spring-framework-3.0.5 & CustomCollectionEditor.java & Apache-2 & 18623736 & alteration & 2013-11-21 \\
-		38 & spring-framework-3.0.5 & DefaultAnnotationHandlerMapping.java & Apache-2 & 3758110 & removal & 2012-01-20 \\
-		39 & spring-framework-3.0.5 & DefaultPropertiesPersister.java & Apache-2 & 6149818 & alteration & 2013-03-19 \\
-		40 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2016-07-15 \\
-		41 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2008-12-18 \\
-		42 & spring-framework-3.0.5 & DelegatingServletInputStream.java & Apache-2 & 20996373 & alteration & 2008-12-18 \\
-		43 & spring-framework-3.0.5 & DispatcherServlet.java & Apache-2 & 4781746 & alteration & 2011-08-08 \\
-		44 & spring-framework-3.0.5 & Jaxb2Marshaller.java & Apache-2 & 10924700 & alteration & 2012-08-28 \\
-		45 & spring-framework-3.0.5 & ScheduledTasksBeanDefinitionParser.java & Apache-2 & 3751463 & alteration & 2016-07-05 \\
-		46 & struts2-2.2.1 & DefaultActionMapper.java & Apache-2 & 14019840 & alteration & 2013-10-18 \\
-		47 & tomcat-7.0.2 & BasicAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
-		48 & tomcat-7.0.2 & BasicAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
-		49 & tomcat-7.0.2 & CoyoteAdapter.java & Apache-2 & 24404964 & alteration & 2012-11-18 \\
-		50 & tomcat-7.0.2 & CoyoteAdapter.java & Apache-2 & 24404964 & alteration & 2012-11-18 \\
-		51 & tomcat-7.0.2 & FormAuthenticator.java & Apache-2 & 21734562 & alteration & 2016-08-04 \\
-		52 & tomcat-7.0.2 & HttpServlet.java & Apache-2 & 5266856 & alteration & 2011-10-22 \\
-		53 & tomcat-7.0.2 & JspRuntimeLibrary.java & Apache-2 & 10289462 & alteration & 2012-09-12 \\
+			3 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1 & 2513183 & alteration  &  2015-03-17 \\
+			4 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  &  2015-03-17 \\
+			5 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  &  2015-03-17 \\
+			6 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  & 2011-03-01 \\
+			7 & eclipse-SDK  & WizardDialog.java  & EPLv1  &   11861598	 & alteration  &  2011-02-03 \\
+			8 & hadoop-1.0.0  & DBCountPageView.java  & Apache-2 & 21702608 & alteration  & 2011-06-12 \\
+			9 & hadoop-1.0.0  & DBCountPageView.java  & Apache-2 & 21702608 & alteration  & 2011-06-12 \\
+			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & Apache-2 & 14845581 & alteration  & 2012-06-25 \\
+			11 & hadoop-1.0.0  & LineRecordReader.java  & Apache-2 & 16180910 & alteration  & 2011-07-25 \\
+			12 & hadoop-1.0.0  & LineRecordReader.java  & Apache-2 & 16180910 & alteration  & 2011-07-25 \\
+			13 & hadoop-1.0.0  & StringUtils.java  & Apache-2 & 801987 & alteration  & 2013-02-04 \\
+			14 & hadoop-1.0.0  & TestJobCounters.java  & Apache-2 & 18833798 & alteration  & 2011-06-12 \\
+			15 & hadoop-1.0.0  & TextOutputFormat.java  & Apache-2 & 16928749 & alteration  & 2011-06-12 \\
+			16 & hadoop-1.0.0  & WritableComparator.java  & Apache-2 & 22315734 & alteration  & 2014-11-20 \\
+			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & -- & 15168494 & alteration  & 2012-06-24 \\
+			18 & hibernate-4.2.2  & Example.java  & -- & 24924255 & alteration  & 2013-04-23 \\
+			19 & hibernate-4.2.2  & SchemaUpdate.java  & -- & 23520731 & alteration  & 2016-02-05 \\
+			20 & hibernate-4.2.2  & SettingsFactory.java  & -- & 8257554 & removal  & 2011-03-11 \\
+			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & -- & 23967852 & alteration  & 2015-03-12 \\
+			22 & jasperreports-3.7.4  & JRVerifier.java  & GLGPLv3+ & 8037824 & alteration  & 2008-04-17 \\
+			23 & jasperreports-3.7.4  & JRVerifier.java  & GLGPLv3+ & 8037824 & alteration  & 2011-05-20 \\
+			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & GLGPLv2.1+ & 12936580 & alteration  & 2016-02-19 \\
+			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & GLGPLv2.1+ & 16058183 & alteration  & 2013-07-03 \\
+			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & GLGPLv2.1+ & 21998949 & alteration  & 2008-06-02 \\
+			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & GLGPLv2.1+ & 21998949 & alteration  & 2008-06-02 \\
+			28 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
+			29 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
+			30 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
+			31 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
+			32 & jstock-1.0.7c  & GoogleMail.java  & GPLv2+ & 14940863 & alteration  & 2015-12-13 \\
+			33 & jstock-1.0.7c  & GoogleMail.java  & GPLv2+ & 24680923 & alteration  & 2015-12-13 \\
+			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & -- & 6025026 & alteration  & 2010-04-13 \\
+			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & -- & 6025026 & alteration  & 2010-04-13 \\
+			36 & junit-4  & Assert.java  & -- & 23586872 & alteration  & 2015-05-12 \\
+			37 & junit-4  & ExternalResource.java  & -- & 7504040 & alteration  & 2016-06-25 \\
+			38 & junit-4.11  & ExpectException.java  & -- & 8802082 & alteration  & 2014-05-26 \\
+			39 & poi-3.6-20091214  & WorkbookFactory.java  & Apache-2 & 12593810 & alteration  & 2015-04-29 \\
+			40 & spring-framework-3.0.5  & AnnotationMethodHandlerExceptionResolver.java  & Apache-2 & 5660519 & removal  & 2012-01-20 \\
+			41 & spring-framework-3.0.5  & AutowireUtils.java  & Apache-2 & 20913543 & alteration  & 2014-10-28 \\
+			42 & spring-framework-3.0.5  & CustomCollectionEditor.java  & Apache-2 & 18623736 & alteration  & 2013-11-21 \\
+			43 & spring-framework-3.0.5  & DefaultAnnotationHandlerMapping.java  & Apache-2 & 3758110 & removal  & 2012-01-20 \\
+			44 & spring-framework-3.0.5  & DefaultPropertiesPersister.java  & Apache-2 & 6149818 & alteration  & 2013-03-19 \\
+			45 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2016-07-15 \\
+			46 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2008-12-18 \\
+			47 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2008-12-18 \\
+			48 & spring-framework-3.0.5  & DispatcherServlet.java  & Apache-2 & 4781746 & alteration  & 2011-08-08 \\
+			49 & spring-framework-3.0.5  & Jaxb2Marshaller.java  & Apache-2 & 10924700 & alteration  & 2012-08-28 \\
+			50 & spring-framework-3.0.5  & ScheduledTasksBeanDefinitionParser.java  & Apache-2 & 3751463 & alteration  & 2016-07-05 \\
+			51 & struts2-2.2.1  & DefaultActionMapper.java  & Apache-2 & 14019840 & alteration  & 2013-10-18 \\
+			52 & tomcat-7.0.2  & BasicAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
+			53 & tomcat-7.0.2  & BasicAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
+			54 & tomcat-7.0.2  & CoyoteAdapter.java  & Apache-2 & 24404964 & alteration  & 2012-11-18 \\
+			55 & tomcat-7.0.2  & CoyoteAdapter.java  & Apache-2 & 24404964 & alteration  & 2012-11-18 \\
+			56 & tomcat-7.0.2  & FormAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
+			57 & tomcat-7.0.2  & HttpServlet.java  & Apache-2 & 5266856 & alteration  & 2011-10-22 \\
+			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & Apache-2 & 10289462 & alteration  & 2012-09-12 \\
 		\hline& 
@@
 %
-%The single missing Stack Overflow fragment (19051537\_0.java) (denoted by *) is one of the 11 false clones generated by Simian.
+%The single missing Stack Overflow fragment (19051537\) (denoted by *) is one of the 11 false clones generated by Simian.
 It is removed from the results of the pretty-printed version because it is an outlier.

### 2016-11-16 cloneoverflow-latex/cloneoverflow.tex
Updated latex with chart

@@
 Next, clone pairs reported from the two clone detectors are pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
-This step generates \textbf{agreement-based clone pairs}.
+This step generates \textbf{agreed clone pairs}.
 They are clones with highest confidence since they receive agreement from both tools.
 Then, clone pairs reported by Simian and NiCad that do not find agreement are filtered by size of minimum 10 lines.
-This step generates \textbf{non agreement-based clone pairs}.
-The non agreement-based clone pairs are clones with less confidence than agreement-based ones.
-Finally, agreement-based and non agreement-based clone pairs are looked at and classified manually by the first author.
+This step generates \textbf{disagreed clone pairs}.
+The disagreed clone pairs are clones with less confidence than agreed ones.
+Finally, agreed and disagreed clone pairs are looked at and classified manually by the first author.
 
@@
 
-\subsubsection{Agreement-based Clone Filtering}
-The number of detected clones between two datasets  can be very large.
+\subsubsection{Clone Candidate Filtering Using Agreement}
+Usually a number of clones detected between two large-scale datasets  can be huge.
 In our study, there are totally 266,837,480 clone pairs reported.
@@
 Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}.
-By using this agreement-based clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
-To find agreement of two clone pairs, we resort to an approach proposed in a study by Bellon et al.~\cite{Bellon2007}.
+By using this agreed clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
+To find an agreement of two clone pairs, we resort to the approach of clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
 Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair.
 A good-match clone pair has stronger agreement than an ok-match pair.
-We follow the same following definitions introduced in the original paper.
+We follow the same following definitions of good- and ok-match introduced in the original paper.
 
@@
 
-\section{Results}
+\section{Results and discussion}
+
+We follow the experimental framework and detect clones between Stack Overflow and Qualitas corpus using the two selected clone detectors.
+To answer RQ1 and RQ2 together, we compute statistics of clone discovered by the tools and the true clone pairs confirmed by manual investigation.
+In the manual investigation process, we proposed an online clone classification scheme derived from common patterns found in online code clones.
+For RQ3, we look at the true positive clone pairs carefully and compare them to their latest versions.
+This is to see if the cloned code is still up-to-date.
+We also look at the license of each clone and observe a possibility of licensing violation because of cloning.
+\subsection{RQ1: Online code clones}
 
@@
 
-\begin{table}
-	\centering
-	\caption{13 Qualitas projects that have been cloned as examples on Stack Overflow with their respective licenses}
-	\label{t:new_and_old}
-	%	\resizebox{\columnwidth}{!}{%
-	\small
-	\begin{tabular}{l|r|p{4cm}}
-		\hline 
-		Project & Version & Licenses (no.~of files) \\
-		\hline
-%		apache-ant & 1.8.4 & Apache2.0 \\
-%		apache-log4j & 1.2.16 & \\
-		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
-		\hline
-		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
-		\hline
-		hibernate & 4.2.2 & Apache-2 (20), \newline GLGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
-		\hline
-		jasperreports & 3.7.4 & GLGPLv2.1+ (3), \newline GLGPLv3+ (1,581), \newline None (1), Unknown (4)\\
-		\hline
-		jfreechart & 1.0.13 & GLGPLv2.1+ (989) \\
-		\hline
-		jgraph & 5.13.0.0 & GLGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
-		\hline
-%		jgrapht & 0.8.1 & GLGPL 2.1 \& Eclipse  1.0 \\
-		jstock & 1.0.7c & GLGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
-		\hline
-		jung2 & 2-0-1 & N/A \\
-		\hline
-		junit & 4.11 & None (160), Unknown (4)  \\
-		\hline
-		poi & 3.6 & Apache-2 (2,002), None (5) \\
-		\hline
-		spring & 3.0.5 & Apache-2 (2,982) \\
-		\hline
-		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
-		\hline
-		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
-%		weka & 3-7-9 & \\
-		\hline
-	\end{tabular} %
-	%	}
-\end{table}
-
-%\begin{table*}
-%	\centering
-%	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
-%	\label{t:new_and_old}
-%	%	\resizebox{\columnwidth}{!}{%
-%	\small
-%	\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
-%		\hline 
-%			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
-%			\hline
-%			apache-jmeter & 2. 9 & & & & & \\
-%			apache-log4j & 1.2.16 & & & & & \\
-%			apache-maven & 3.0 & & & & & \\
-%			apache-roller & 4.0.1 & & & & & \\
-%			apache-tomcat & 7.0.2 & & & & & \\
-%			jhotdraw & 7.5.1 & & & & & \\
-%			jrefactory & 2.9.19 & & & & & \\
-%			jruby & 1.5.2 & & & & & \\
-%			jspwiki & 2.8.4 & & & & & \\
-%			jstock & 1.0.7c & & & & & \\
-%			jsxe & 04\_beta & & & & & \\
-%			jtopen & 7\_1 & & & & & \\
-%			jung2 & 2\_0\_1 & & & & & \\
-%			lucene & 4.3.0 & & & & & \\
-%			marauroa & 3.8.1 & & & & & \\
-%			megamek & 0.35.18 & & & & & \\
-%			mvnforum (mvnad) & 1.2.2 (1.0.1) & & & & & \\
-%			myfaces-core & 2.0.2 & & & & & \\
-%			nakedobjects & 4.0.0 & & & & & \\
-%			nekohtml & 1.9.14 & & & & & \\
-%			netbeans & 6.9.1 & & & & & \\
-%			openjms & 0.7.7-beta-1 & & & & & \\
-%			oscache & 2.4.1 & & & & & \\
-%			picocontainer & 2.10.2 & & & & & \\
-%			pmd & 4.2.5 & & & & & \\
-%			poi & 3.6 & & & & & \\
-%			pooka & 080505 & & & & & \\
-%			proguard & 4.5.1 & & & & & \\
-%			quartz & 1.8.3 & & & & & \\
-%			quickserver & 1.4.7 & & & & & \\
-%			quilt & 0.6-a-5 & & & & & \\
-%			rssowl & 2.0.5 & & & & & \\
-%			sablecc & 3.2 & & & & & \\
-%			sandmark & & & & & & \\
-%			spring-framework & 3.0.5 & & & & & \\
-%			struts2 & 2.2.1-all & & & & & \\
-%			sunflow & 0.07.2 & & & & & \\
-%			tapestry & 5.1.0.5 & & & & & \\
-%			trove & 2.1.0 & & & & & \\
-%			velocity & 1.6.4 & & & & & \\
-%			wct-package & 1.5.2 & & & & & \\
-%			webmail & 0.7.10 & & & & & \\
-%			weka & 3-7-9 & & & & & \\
-%			xalan-j & 2\_7\_1 & & & & & \\
-%			xerces-J & 2.10.0 & & & & & \\
-%			xmojo & 5.0.0 & & & & & \\
-%			\hline 
-%		\end{tabular} %
-%%	}
-%\end{table*}
-
-%\subsection{Agreement based clone pairs vs. Non agreement based clone pairs}
-
-%The agreement-based clone pairs are the ones discovered using Bellon's good-match(0.7) and \textit{ok}-match(0.7) criteria as listed in  Table \ref{t_agreed_good_clone_pairs}.
-Non-agreement based clone pairs are the ones that are solely reported by a single tool.
-The agreement-based pairs provide higher confident that they are real clones than the non-agreement based ones.
-
-\subsection{Agreement-based clone pairs}
-
-Agreement-based clone pairs are clone pairs that pass Bellon's criteria and selected for manual investigation.
-We select a threshold \textit{p} of 0.7 for both good and ok-match similar to the original study \cite{Bellon2007}.
+\subsubsection{Agreed clone pairs}
+
+Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.
+Similar to the original study, we select a threshold \textit{p} of 0.7 for both good and ok-match\cite{Bellon2007}.
 The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-NiCad generated errors and stopped processing while it was analysing some Qualitas projects.
-\FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ unsuccessfully detected clones in 6 projects due to clustering errors.
+We found that NiCad generates errors and stopped processing while it is analysing some Qualitas projects.
+\FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ could not detect clones in 6 projects due to clustering errors.
 For NiCad$_{\textrm{\textit{EvCl}}}$, the tool generated renaming errors for 4 projects, and clustering errors for 13 projects.
-As a result, we did not have NiCad clone candidates for 6 (\textit{df}) and 27 projects (\textit{EvCl}) in the agreement-based clone pairs.
-Unfortunately, this also has an effect to Simian clone candidates of the same projects to be removed from the agreement-based clone pairs since they do not have matching clone pairs.
-The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are depicted in \Cref{fig:venn4_orig_good}.
+As a result, we did not have NiCad clone candidates in the agreed clone pairs for 6 and 27 projects with \textit{df} and \textit{EvCl} configurations respectively.
+This affected Simian clone candidates of the same projects to be removed from the agreed clone pairs as well since they could not have matching clone pairs.
+
+The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}.
 There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
-ok-match clone pairs subsume the good-match pairs according to the criteria.
-As a result, there are 23,868 clone pairs, which are 3,800 pairs from Simian$_{df}$--NiCad$_{df}$, 1,017 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 88 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 19,777 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
-Between the four configuration sets, there are a few clone pairs that are shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.
+According to the definition, ok-match clone pairs always subsume the good-match pairs.
+As a result, there are 29,944 ok-match clone pairs.
+9,062 pairs are from Simian$_{df}$--NiCad$_{df}$, 1,017 pairs are from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 88 are pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 19,777 pairs are from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
+Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.
 
@@
 	\centering
-	\caption{Distribution of agreement-based clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
+	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
 	\label{t_agreed_good_clone_pairs}
@@
 
-\subsubsection{Classifications of online code clones}
-
-\begin{table*}
-	\centering
-	\caption{Classifications of online code clones}
+\subsubsection{Disagreed clone pairs}
+%In the preliminary stage of our experiment, we found that there are 41 Stack Overflow fragments reported by Simian with default configurations.
+However, only 10 of them appear in the new results using tool's agreement.
+Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.
+
+The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with another tool.
+The disagreement can be from misalignment of clone lines or different configurations that result in different clones reported.
+They are also clone pairs in projects with NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl} configurations) that are missing from the agreed clone pairs.
+With the four configuration combinations, we decided to investigate only two, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively).
+They also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.
+
+Even choosing only the default configurations, the number of clone pair candidates are still very large.
+We hence apply two pruning filters: clone size, and similarity threshold.
+For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}.
+The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines).
+The second filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration.
+%We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%.
+%Using the filter along with regular expressions to capture boiler-plate code clones such as \verb|equals()| and \verb|hashcode()|, we can reduce the number of Simian clone candidates to a manageable amount of 795 clone pairs.
+
+% It results in 159 clone pairs remaining. The summary of disagreed clone pairs before and after filtering is shown in \Cref{tab:classification_indv_stats}.
+% 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
+For Simian$_{df}$, there are 20,348 clone pairs after using 10--line filter.
+Out of 20,348 pairs, 2,546 of them are ok-match pairs which are discarded.
+We filtered the results further by removing false positives such as similar \verb|equals()|, \verb|hashCode()| methods, getters and setters out by using regular expressions.
+We managed to reduce the number to 871 clone pairs remaining for manual investigation.
+% 7062 + 22187 + 6755 =  36004 %
+For NiCad$_{df}$, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well.
+We thus filter NiCad's clones by using similarity threshold.
+We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2) and obtain 618 clone pairs.
+%However, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well.
+So .
+Using 80\% similarity, there are totally 166 pairs left.
+There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation.
+The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.
+
+%We selected only Stack Overflow fragment and Qualitas files that have never been looked at before in the previous investigation.
+If many clone pairs having the same Stack Overflow fragment and Qualitas file, we keep only the largest one.
+The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stack Overflow fragments or Qualitas files.
+The classification results are shown in Table \ref{tab:classification_indv}.
+
+\begin{table}
+	\centering
+	\caption{Statistics of disagreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
+	\label{tab:classification_indv_stats}
+	\small
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|p{2.4cm}|r|r|r}
+		\hline 
+		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
+		%\hline 
+		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
+		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
+		\hline
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
+		\hline
+%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
+%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
+		\hline
+	\end{tabular} %
+	}
+\end{table}
+
+\subsection{RQ2: Classifications of online code clones}
+
+\begin{table}
+	\centering
+	\caption{Seven categories of online code clones}
 	\label{tab:classification_scheme}
-	\begin{tabular}{|c|p{13cm}|}
-		\hline 
-		Category & Descriptions \\ 
-		\hline 
-		A & Code in Stack Overflow is copied from Qualitas (Q $\rightarrow$ S). \\ 
-		\hline 
-		A' & Code in Qualitas is copied from Stack Overflow (S $\rightarrow$ Q). \\ 
-		\hline 
-		B & Clone pair is exactly identical or highly similar and may be copied either from each other or a third source (unknown) (S $\leftrightarrow$ Q $\vee$ (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q)).
+	\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{|c|p{8cm}|}
+			\hline 
+			Cat. & Descriptions \\ 
+			\hline 
+			A & Cloned from Qualitas to Stack Overflow (Q $\rightarrow$ S). \\ 
+			\hline 
+			A' &Cloned from Stack Overflow to Qualitas (S $\rightarrow$ Q). \\ 
+			\hline 
+			B & Cloned from each other or from an external source \textit{X} (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
 			\\ 
 			\hline 
-		C & Code in both places are copied from a third source T (known) (T $\rightarrow$ S $\wedge$ T $\rightarrow$ Q).
+			C & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
 			\\ 
 			\hline 
-		D & Code is a boiler-plate or IDE auto-generated.
+			D & Boiler-plate or IDE auto-generated
 			\\ 
 			\hline 
-		E & Code in both places initialise a similar/the same object; extend the same class/its subclass; implement the same interface.
+			E & Inheritance, interface implementation 
 			\\ 
 			\hline 
-		F & Accidental similarity, false clone \\ 
-		\hline 
-	\end{tabular} 
-\end{table*}
-
-We need an appropriate classification scheme to be able to meaningfully manually categorise the selected clone candidates.
-We adapted the classifications from a study by Kapser et al.
+			F & Accidental similarity, false clones by normalisation \\ 
+			\hline 
+		\end{tabular}  %
+	}
+\end{table}
+
+We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand.
+We started by studying the 8 patterns of cloning from Kapser et al.
 \cite{Kapser2006}.
-The online code clone classification scheme is described in \Cref{tab:classification_scheme}.
-Due to differences in the experimental settings of the study, we adopted some of the original classifications and added a few more classifications to match with our datasets and context.
-The final seven categories (A--F) have been observed to be common clone patterns found from a manual check of 100 random sample clone pairs.
+We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments.
+This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study.
+Using Simian$_{df}$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size.
+We then picked the top 10 fragments from the 4 groups resulting in 34 Stack Overflow fragments chosen (there were some overlaps).
+The 34 selected snippets generate 697 clone pairs.
+Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating.
+Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.
+We adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as category D, and added 6 new categories observed as common cloning patterns from the manual investigation.
+The seven categories ranging from A--F presented in \Cref{tab:classification_scheme}.
 Category A is a clone pair that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation or links in Stack Overflow post), and vice versa in category A'.
 Category B is a clone pair that is exactly identical or highly similar but without any attribution of copying.
-Category C is a clone pair that has information confirming of copying but from the same external source.
-Category D is a clone pair that is either boiler-plate code (e.g.
-\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.
-GUI initialisation).
+Category C is a clone pair that has information confirming of copying from the same external source.
+Category D is a clone pair that is either boiler-plate code (e.g.~\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.~GUI initialisation).
 Category E are clones created by inheriting the same super class or implementing the same interface.
 They usually share similar overriding methods.
-The last category, category F, are false clones that have accidental similarity after code normalisation or other causes.
+The last category, category F, is a false clone pair.
+They can be either accidentally similar (e.g.~similar try-catch statements) or similar after code normalisation process.
 Using this classification scheme, we consider clone pairs in category A, A', B, C as true positive, and clone pairs in category D, E, F as false positive.
 
-\subsubsection{Manual investigation of agreement-based clone pairs}
-
-The first author who has been working on clone detection research for two years takes the role of an investigator who performs manual investigation.
-Following the classification scheme, the investigator manually goes through each agreement-based clone pair, looks at the clones, and chooses the most appropriate category for the pair.
+\subsubsection{Manual investigation of clone pair candidates}
+
+The first author who has been working on clone detection research for two years takes the role of an investigator performing manual investigation.
+Following the classification scheme, the investigator manually goes through each agreed clone pair, looks at the clones, and chooses the most appropriate category for the pair.
 A relevant and useful observation is also recorded for each clone pair.
-The classification results are shown in \Cref{tab:classification_good_o}.
+
+\textbf{Agreed clone pairs}: the classification results are shown in \Cref{tab:classification_good_o}.
 We have manually investigated 2,261 good-match clone pairs.
-There is one clone pair found to be copied from a Qualitas project to Stack Overflow, 4 pairs that are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code), and 3 pairs that are copied from external sources.
+There is one clone pair in category A which is found to be copied from a Qualitas project to Stack Overflow.
+Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as category B.
+We found 3 pairs in category C that are copied from external sources.
 The rest are false positive clones.
-58 clone pairs are found to \verb|equals()| methods, or getters and setters.
-Six pairs are similar code from inheritance of the same superclass or implementing the same interface.
-Finally, 2,189 clone pairs are false clones.
-
-For the ok-match clone pairs, we could not feasibly investigate 23,868 pairs manually.
-According to the manual investigation of good-match results, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,253 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs) due to its recall preference.
+58 clone pairs are found to be \verb|equals()| methods, or getters and setters, category D.
+Six pairs are similar code from inheritance of the same superclass or implementing the same interface, category E.
+Finally, 2,189 clone pairs are categorised to E which means they are false clones.
+
+For the ok-match clone pairs, we could not feasibly investigate all 23,868 pairs manually.
+According to the manual investigation of good-match pairs, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,253 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs) due to its recall preference.
 We thus decided to leave this configuration out of the ok-match manual investigation.
 There are totally 4,625 ok-match pairs that were investigated.
-The 49 true positive pairs found are combinations of 8, 33, and 8 clone pairs in category A, B, and C respectively.
-
-We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying.
+The 47 true positive pairs found are combinations of 8, 29, and 10 clone pairs in category A, B, and C respectively.
+
+\FIXME{Maybe remove?} We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying.
 We thus checked the timestamp of each Java file in Qualitas project and compared it to their respective timestamp of Stack Overflow posts.
@@
 	\centering
-	\caption{Classification results of agreement-based and non agreement-based clone pairs.
+	\caption{Classification results of agreed and disagreed clone pairs.
 S$_u$ denotes a number of unique Stack Overflow snippets.
@@
 
-\subsection{Non agreement-based clone pairs}
-%In the preliminary stage of our experiment, we found that there are 41 Stack Overflow fragments reported by Simian with default configurations.
-However, only 10 of them appear in the new results using tool's agreement.
-Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.
-
-The non agreement-based clone pairs are clone pairs that are reported by a single tool (either Simian or NiCad) and do not have agreement with another tool.
-The disagreement can be from misalignment of clone lines or different configurations that results in different clones reported.
-They are also clone pairs in projects that have NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl}).
-With the four configuration combinations, we decided to investigate only two, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively).
-They also have a high possibility of containing a large number of false positives due to relaxation of EvaClone configurations.
-
-Even choosing only the default configurations, the number of clone pairs are still very large.
-We hence apply two pruning filters: (1) clone size and (2) similarity threshold.
-For the clone size filter, we raise the minimum clone size to 10 line.
-The clone size filter is applied to Simian clone pairs only since its default configurations consider a minimum of 6 line as clones.
-On the other hand, a minimum of 10 lines is already a default configuration of NiCad.
-We found that this filter works well with Simian clone pairs resulting in a manageable amount of 795 clone pairs remaining.
-Regarding the similarity threshold filter, it is only applied to NiCad clone pairs since Simian does not provide this similarity threshold configuration.
-We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%.
-This results in 159 clone pairs remaining.
-The summary of non agreement-based clone pairs is shown in \Cref{tab:classification_indv_stats}.
-
-For Simian$_{df}$, there were 9,383 clone pairs reported by the tool.
-Out of 9,383 pairs, 140 of them are the ones found in \textit{ok-}pairs using agreement-based detection.
-We filtered the results further by removing false positives such as similar \verb|equals()|, \verb|hashCode()| methods, getters and setters out by using regular expression.
-We managed to remove 8,956 pairs using this method.
-Eventually, there were 287 clone pairs remaining for manual investigation.
-For NiCad$_{df}$, we obtained 7,040 clone pairs to look at which is infeasible for manual investigation.
-Hence, result filtering was also needed.
-However, regular expressions could not be used effectively as in Simian's case since NiCad allowed clones that are different at keywords/variable names or even added/deleted lines.
-So we decided to filter the results by selecting pairs that pass stricter clone criteria with $\mathrm{UPI} = 0.2$.
-By reducing the UPI to 0.2, there were totally 166 pairs left.
-Out of 166, 52 are ok-pairs and 114 are remaining pairs for manual check (18 pairs are from \textit{cayenne} and \textit{iReport} that could not be analysed using UPI = 0.3).
-The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.
-
-%We selected only Stack Overflow fragment and Qualitas files that have never been looked at before in the previous investigation.
-If many clone pairs having the same Stack Overflow fragment and Qualitas file, we keep only the largest one.
-The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stack Overflow fragments or Qualitas files.
-The classification results are shown in Table \ref{tab:classification_indv}.
-
-\begin{table}
-	\centering
-	\caption{Statistics of non-agreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
-	\label{tab:classification_indv_stats}
-	\small
-	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|p{2.4cm}|r|r|r}
-		\hline 
-		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
-		%\hline 
-		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
-		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
-		\hline
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
-		\hline
-%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
-%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
-		\hline
-	\end{tabular} %
-	}
-\end{table}
-
-\subsubsection{Manual investigation of non-agreed clone pairs}
 %\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
-We performed manual investigation and classified the clone pairs reported by Simian$_{df}$ and NiCad$_{df}$ in the same way as the agreement-based clone pairs.
-The results of the manual investigation is reported in \Cref{tab:classification_good_o}.
+\textbf{Disagreed clone pairs}: we performed a manual investigation and classification of 871 filtered clone pairs reported by Simian$_{df}$ and 168 by NiCad$_{df}$ in the same way as the agreed clone pairs.
+The results of investigation is reported in \Cref{tab:classification_good_o}.
+There are 432 true positive clone pairs found from Simian$_{df}$ consisting of 19 pairs in category A, 336 pairs in B, and 17 pairs in C.
+For NiCad$_{df}$, there are 36 true positive pairs consisting of 8 pairs in category A, 27 pairs in B, and 1 pair in C.
+The total number of true positive clone pairs is 523 as described in \Cref{tab:classification_true_pairs_summary}.
 
@@
 
+\begin{table}
+	\centering
+	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
+	\label{t:new_and_old}
+	%	\resizebox{\columnwidth}{!}{%
+	\small
+	\begin{tabular}{l|r|p{4cm}}
+		\hline 
+		Project & Version & Licenses (no.~of files) \\
+		\hline
+		%		apache-ant & 1.8.4 & Apache2.0 \\
+		%		apache-log4j & 1.2.16 & \\
+		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
+		\hline
+		eclipse-SDK &  4.1 & Apache-2 (2183), \newline BSD3NoWarranty (107), \newline CDDLorGPLv2 (296), \newline EPLv1 (18823), MPLv1.1 (93), \newline None (224), SeeFile (8), \newline spdxBSD3 (185), \newline spdxMIT (1), Unknown (714) \\
+		\hline
+		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
+		\hline
+		hibernate & 4.2.2 & Apache-2 (20), \newline GLGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
+		\hline
+		jasperreports & 3.7.4 & GLGPLv2.1+ (3), \newline GLGPLv3+ (1,581), \newline None (1), Unknown (4)\\
+		\hline
+		jfreechart & 1.0.13 & GLGPLv2.1+ (989) \\
+		\hline
+		jgraph & 5.13.0.0 & GLGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
+		\hline
+		%		jgrapht & 0.8.1 & GLGPL 2.1 \& Eclipse  1.0 \\
+		jstock & 1.0.7c & GLGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
+		\hline
+		jung2 & 2-0-1 & N/A \\
+		\hline
+		junit & 4.11 & None (160), Unknown (4)  \\
+		\hline
+		poi & 3.6 & Apache-2 (2,002), None (5) \\
+		\hline
+		spring & 3.0.5 & Apache-2 (2,982) \\
+		\hline
+		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
+		\hline
+		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
+		%		weka & 3-7-9 & \\
+		\hline
+	\end{tabular} %
+	%	}
+\end{table}
+
 %\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
 
-\section{Effects of online code clone}
-
-In this study, we are interested in the effects of online code clones to software development.
-From the manual investigation of 184 true online clone pairs, we found that there are two potential issues: stale online code, and software licensing violation.
-
-\subsection{Issue~1 -- stale online code clones}
-Stale online code occurs when a piece of code has been copied from a software project to Stack Overflow, and later it has been changed in the original project.
-However, in this situation, the copy is still unchanged.
-Since the code were updated due to various possible reasons including bug fixing, this can cause a problem if developers reuse stale online code from Stack Overflow.
-They might also introduce the same unfixed bug(s) into the software.
-To discover stale online code, we focus on the true online clone pairs that are copied in the direction from Qualitas to Stack Overflow (category-\textit{A} online clone pairs) in \Cref{tab:classification_true_pairs_summary} which results in 84 pairs selected.
+\subsection{RQ3: Effects of online code clones}
+
+In this study, we are interested in effects of having code clones between open source software systems and Stack Overflow.
+From the manual investigation, we found 523 true positive online clone pairs.
+With this set of true clones, we investigated further and found that there are two potential issues, outdated code and software licensing violation.
+
+\subsubsection{Outdated code clones}
+Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated.
+This is a normal issue driving the development of clone detection.
+We need to locate clones to be able to update them according to their updated original code \cite{somewhere,somewhere_else}.
+However, in this situation, the clones are more pervasive on Stack Overflow posts and more difficult to detect due to its large scale and the mix of natural language and source code.
+Since code can be updated due to various possible reasons including bug fixing, this poses a problem if developers reuse a cloned code snippet from Stack Overflow without knowing that it is outdated.
+%They might also introduce the same unfixed bug(s) into the software.
+They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce the same later-be-fixed bug(s) into their software.
+
+To check if the discovered Stack Overflow clones are outdated, we focus on the 96 category-A clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_true_pairs_summary}).
+For each code snippet, we can track its origin from its Qualitas counterpart.
+Using the file in Qualitas project, we locate the latest version of the file in its version control repository (all of them use git) and compare the snippet to its latest version to see if any change has been made to the source code.
+If we find any change, we use \textit{git blame} command to see who modified the source code and when.
+
 %We restricted it further to only the ones having versioning system so we can trace changes made to these clone pairs.
 Fortunately, all of the pairs were from projects with either git or svn so we did not remove any pair from this set.
-
 %Our intuition behind his issue comes from a situation where a piece of code has been copied from a Qualitas project and posted on Stack Overflow.
@@
 This results in outdated online code which can cause problems when programmers copy and use it in their projects.
-
 %We decided to ignore NiCad results from this analysis due to its failure of clone clustering and renaming on some projects.
@@
 
-\Cref{tab:stale_code} shows the results of manual investigation of 84 category-A online clone pairs.
-The investigation reveals that there are 50 clone pairs that are outdate (i.e.
-``stale clone'').
-They are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as accepted answers, and later have been changed during the development.
+\Cref{tab:stale_code} shows the findings of outdated clone investigation.
+The comparison with the clones' latest code reveals that there are 55 clone pairs that are outdated.
+These are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as accepted answers, and later have been changed during the development.
+\textit{hadoop} and \textit{spring} have the maximum number of 9 outdate code clones, followed by 6 clones from \textit{tomcat}, and 5 clones from \textit{eclipse-SDK}.
+An example of outdated code in hadoop's \textit{WritableComparator.java} is shown in \Cref{fig:before-after}.
+The newest version has one line added.
+We also found outdated code which contains more disruptive changes.
+The code snippet in Stack Overflow Post 23520731 which is a copy of \textit{SchemaUpdate.java} in \textit{hibernate} has been heavily modified (as shown in \Cref{fig:hibernate_outdated_code}).
+Moreover, there is a code snippet in Stack Overflow post 3758110 which is a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring.
+It was deleted in commit 02a4473c62d8240837bec297f0a1f3cb67ef8a7b by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted and the latest version of Spring does not contain the Java file anymore.
+
+The outdate code clones without latest changes can cause problems ranging from uncompilable code due to version difference to bug propagation.
+An outdated code with a subtle change such as the one in \textit{WritableComparator.java} can be copied and reused without awareness from developers.
+Fortunately, Stack Overflow has a natural voting mechanism that can mitigate this kind of outdated code.
+Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment.
+They can cast a down vote to that answer resulting in low vote for the answer with outdated code.
+However, if the answer is marked as accepted by the person who asks the question (which is our case), it is still attractive to naive developers who are not aware of the voting mechanism.
+
+\begin{figure*}
+	\begin{lstlisting}
+/* Code in Stack Overflow #23520731 */     /* SchemaUpdate.java (2016-09-26) */
+public void execute (Target target) {      public void execute(EnumSet<TargetType> targetTypes, 
+  LOG.runningHbm2ddlSchemaUpdate();                        Metadata metadata, ServiceRegistry serviceRegistry) {
+  Connection connection = null;              if ( targetTypes.isEmpty() ) {
+  Statement stmt = null;                       LOG.debug(""Skipping SchemaExport as no targets were specified"");
+  Writer outputFileWriter = null;              return;
+  exceptions.clear();                        }
+  try {                                      exceptions.clear();
+    DatabaseMetadata meta;                   LOG.runningHbm2ddlSchemaUpdate();
+    ...                                      ...
+	\end{lstlisting}
+	\caption{Outdated code fragment on Stack Overflow post 23520731 copied from SchemaUpdate.java and its latest version in hibernate code base with heavy modifications}
+	\label{fig:hibernate_outdated_code}
+\end{figure*}
 
@@
 	\centering
-	\caption{Results from a manual investigation of 84 category-A online clone pairs}
+	\caption{Breakdowns of findings from outdated code investigation of 96 category-A online clone pairs}
 	\label{tab:stale_code}
@@
 		\hline 
-		Project & Pairs & Stale & Fresh & Del. & Others \\
+		Project & Pairs & Outdated & Fresh & Del. & Others \\
 		\hline
@@
 
-\subsection{Issue~3 -- external clones}
-
-\subsection{Issue~2 -- software licensing violations}
+\subsubsection{Software licensing violation}
 Software licensing is a paramount factor in software development.
@@
 If developers copy and reuse these pieces of code in their projects, a licensing conflict can quietly happen without realisation of the developers.
+
+\subsubsection{Interesting finding: external clones}
 

### 2016-11-16 cloneoverflow-latex/StackoverflowCharts/Main.py

@@ -1,0 +1,27 @@
+#!/usr/bin/env python
+# a stacked bar plot with errorbars
+import numpy as np
+import matplotlib.pyplot as plt
+
+N = 18
+fresh =     (1, 4, 0, 7, 5, 11, 0, 0, 0, 1, 0, 0, 0, 2, 3, 0, 3, 0)
+outdated =  (0, 0, 2, 5, 9, 4,  2, 4, 4, 0, 2, 2, 3, 1, 9, 1, 0, 7)
+deleted =   (0, 0, 0, 0, 0, 1,  0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0)
+other =     (0, 0, 0, 0, 0, 0,  0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+
+ind = np.arange(N)    # the x locations for the groups
+width = 0.35       # the width of the bars: can also be len(x) sequence
+
+p1 = plt.bar(ind, outdated, width, color='yellow')
+p2 = plt.bar(ind, deleted, width, color='red', bottom=outdated)
+#p3 = plt.bar(ind, other, width, color="blue", bottom=deleted)
+#p4 = plt.bar(ind, fresh, width, color='green', bottom=other)
+
+plt.ylabel('Amount')
+#plt.title('Scores by group and gender')
+plt.xticks(ind + width/2., ('ant', 'log4j', 'aspectj', 'eclipse', 'hadoop', 'hibernate', 'jasperreports', 'jfreechart', 'jgraph', 'jgrapht', 'jstock', 'jung', 'junit', 'poi', 'spring', 'struts', 'tomcat', 'weka'),rotation=30)
+
+plt.yticks(np.arange(0, 16))
+#plt.legend((p1[0], p2[0], p3[0], p4[0]), ('Outdated', 'Deleted', 'Others', 'Fresh'), loc=2)
+
+plt.show()

### 2016-11-17 cloneoverflow-latex/cloneoverflow.tex
Latest update with stacked bar chart

@@
 
-\Cref{tab:stale_code} shows the findings of outdated clone investigation.
+\Cref{fig:outdated} shows the findings of outdated clone investigation.
 The comparison with the clones' latest code reveals that there are 55 clone pairs that are outdated.
@@
 
-\begin{table}
-	\centering
-	\caption{Breakdowns of findings from outdated code investigation of 96 category-A online clone pairs}
-	\label{tab:stale_code}
-	\small
-%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r|r}
-		\hline 
-		Project & Pairs & Outdated & Fresh & Del. & Others \\
-		\hline
-		ant & 1 & 0 & 1 & 0 & 0 \\
-		log4j & 4 & 0 & 4 & 0 & 0 \\
-		tomcat & 7 & 7 & 0 & 0 & 0 \\
-		aspectj & 2 & 2 & 0 & 0 & 0 \\
-		eclipse-SDK & 12 & 5 & 7 & 0 & 0 \\
-		hadoop & 14 & 9 & 5 & 0 & 0 \\
-		hibernate & 16 & 4 & 11 & 1 & 0 \\
-		jasperreports & 2 & 2 & 0 & 0 & 0 \\
-		jfreechart & 4 & 4 & 0 & 0 & 0 \\
-		jgraph & 5 & 4 & 0 & 0 & 1 \\
-		jgrapht & 1 & 0 & 1 & 0 & 0 \\
-		jstock & 2 &  2 & 0 & 0 & 0 \\
-		jung & 2 & 2 & 0 & 0 & 0 \\
-		junit & 3 & 3 & 0 & 0 & 0 \\
-		poi & 3 & 1 & 2 & 0 & 0 \\
-		spring & 14 & 9 & 3 & 2 & 0 \\
-		struts & 1 & 1 & 0 & 0 & 0 \\
-		weka & 3 & 0 & 3 & 0 & 0 \\
-		\hline
-		Total & 96 & 55 & 37 & 3 & 1 \\
-		\hline
-	\end{tabular} 
-%}
-\end{table}
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{outdated}
+	\caption{Findings from outdated code investigation of 96 category-A online clone pairs}
+	\label{fig:outdated}
+\end{figure}
+
+%\begin{table}
+%	\centering
+%	\caption{Breakdowns of findings from outdated code investigation of 96 category-A online clone pairs}
+%	\label{tab:stale_code}
+%	\small
+%%	\resizebox{\columnwidth}{!}{%
+%	\begin{tabular}{l|r|r|r|r|r}
+%		\hline 
+%		Project & Pairs & Outdated & Fresh & Del. & Others \\
+%		\hline
+%		ant & 1 & 0 & 1 & 0 & 0 \\
+%		log4j & 4 & 0 & 4 & 0 & 0 \\
+%		tomcat & 7 & 7 & 0 & 0 & 0 \\
+%		aspectj & 2 & 2 & 0 & 0 & 0 \\
+%		eclipse-SDK & 12 & 5 & 7 & 0 & 0 \\
+%		hadoop & 14 & 9 & 5 & 0 & 0 \\
+%		hibernate & 16 & 4 & 11 & 1 & 0 \\
+%		jasperreports & 2 & 2 & 0 & 0 & 0 \\
+%		jfreechart & 4 & 4 & 0 & 0 & 0 \\
+%		jgraph & 5 & 4 & 0 & 0 & 1 \\
+%		jgrapht & 1 & 0 & 1 & 0 & 0 \\
+%		jstock & 2 &  2 & 0 & 0 & 0 \\
+%		jung & 2 & 2 & 0 & 0 & 0 \\
+%		junit & 3 & 3 & 0 & 0 & 0 \\
+%		poi & 3 & 1 & 2 & 0 & 0 \\
+%		spring & 14 & 9 & 3 & 2 & 0 \\
+%		struts & 1 & 1 & 0 & 0 & 0 \\
+%		weka & 3 & 0 & 3 & 0 & 0 \\
+%		\hline
+%		Total & 96 & 55 & 37 & 3 & 1 \\
+%		\hline
+%	\end{tabular} 
+%%}
+%\end{table}
 
@@
 			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & Apache-2 & 10289462 & alteration  & 2012-09-12 \\
-		\hline& 
+		\hline
 	\end{tabular} %

### 2016-11-17 cloneoverflow-latex/StackoverflowCharts/StackedBar.py

@@ -1,0 +1,88 @@
+import pandas as pd
+import matplotlib.pyplot as plt
+import numpy as np
+from matplotlib.backends.backend_pdf import PdfPages
+
+raw_data = {'systems': ['ant', 'log4j', 'aspectj', 'eclipse', 'hadoop', 'hibernate', 'jasperreports', 'jfreechart', 'jgraph', 'jgrapht', 'jstock', 'jung', 'junit', 'poi', 'spring', 'struts', 'tomcat', 'weka'],
+            'fresh': [1, 4, 0, 7, 5, 11, 0, 0, 0, 1, 0, 0, 0, 2, 3, 0, 0, 3],
+            'outdated': [0, 0, 2, 5, 9, 4,  2, 4, 4, 0, 2, 2, 3, 1, 9, 1, 7, 0],
+            'deleted': [0, 0, 0, 0, 0, 1,  0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0],
+            'other': [0, 0, 0, 0, 0, 0,  0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0]}
+df = pd.DataFrame(raw_data, columns=['systems', 'fresh', 'outdated', 'deleted', 'other'])
+df
+
+# Create the general blog and the "subplots" i.e. the bars
+f, ax1 = plt.subplots(1, figsize=(10,5))
+
+# Set the bar width
+bar_width = 0.5
+
+# positions of the left bar-boundaries
+bar_l = [i+1 for i in range(len(df['fresh']))]
+
+# positions of the x-axis ticks (center of the bars as bar labels)
+tick_pos = [i+(bar_width/2) for i in bar_l]
+
+# Create a bar plot, in position bar_1
+ax1.bar(bar_l,
+        # using the fresh data
+        df['fresh'],
+        # set the width
+        width=bar_width,
+        # with the label pre score
+        label='Fresh',
+        # with color
+        color='green')
+
+# Create a bar plot, in position bar_1
+ax1.bar(bar_l,
+        # using the outdated data
+        df['outdated'],
+        # set the width
+        width=bar_width,
+        # with fresh on the bottom
+        bottom=df['fresh'],
+        # with the label mid score
+        label='Outdated',
+        # with color
+        color='yellow')
+
+# Create a bar plot, in position bar_1
+ax1.bar(bar_l,
+        # using the deleted data
+        df['deleted'],
+        # set the width
+        width=bar_width,
+        # with outdated and fresh on the bottom
[…]

### 2016-11-17 cloneoverflow-latex/StackoverflowCharts/StackedBar.py
Updated code

@@ -1,7 +1,5 @@
 import pandas as pd
 import matplotlib.pyplot as plt
-import numpy as np
-from matplotlib.backends.backend_pdf import PdfPages
 
 raw_data = {'systems': ['ant', 'log4j', 'aspectj', 'eclipse', 'hadoop', 'hibernate', 'jasperreports', 'jfreechart', 'jgraph', 'jgrapht', 'jstock', 'jung', 'junit', 'poi', 'spring', 'struts', 'tomcat', 'weka'],
             'fresh': [1, 4, 0, 7, 5, 11, 0, 0, 0, 1, 0, 0, 0, 2, 3, 0, 0, 3],
@@ -74,15 +72,16 @@ ax1.bar(bar_l,
         color='blue')
 
 # set the x ticks with names
-plt.xticks(tick_pos, df['systems'], rotation=30)
+plt.yticks(fontsize=14)
+plt.xticks(tick_pos, df['systems'], rotation=40, fontsize=14)
 
 # Set the label and legends
-ax1.set_ylabel("Amount")
+ax1.set_ylabel("Amount").set_fontsize(14)
 #ax1.set_xlabel("Systems")
-plt.legend(loc='upper center')
+plt.legend(loc='upper center', fontsize=14)
 
 # Set a buffer around the edge
 plt.xlim([min(tick_pos)-bar_width, max(tick_pos)+bar_width])
-plt.subplots_adjust(bottom=0.2)
+plt.subplots_adjust(bottom=0.3)
 #plt.show()
 plt.savefig(('/Users/Chaiyong/IdeasProjects/StackAnalyzer/cloneoverflow-latex/outdated.pdf'))

### 2016-11-21 cloneoverflow-latex/cloneoverflow.tex
Updated latex

@@
 	\centering
-	\caption{58 code clones in Stack Overflow that were altered, rewritten, or removed from the project after posted and their respective licenses}
+	\caption{58 code clones in Stack Overflow (SO) that were altered, rewritten, or removed from the project after posted and their respective licenses.
+Files can be changed ($C$) by modifications ($M$), deletion ($D$), and rewriting ($R$).}
 	\label{tab:stale_code_details}
-	\small
-	\resizebox{2.1\columnwidth}{!}{%
-	\begin{tabular}{r|l|l|l|l|c|l}
-		\hline 
-		No. & Project & File & License & SO Post & Changes & Date \\
-		\hline
-			1 & aspectj-1.6.9  & Agent.java  & -- & 18303692 & alteration  & 2015-09-08 \\
-			2 & aspectj-1.6.9  & Agent.java  & -- & 18303692 & alteration  & 2015-09-08 \\
-			3 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1 & 2513183 & alteration  &  2015-03-17 \\
-			4 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  &  2015-03-17 \\
-			5 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  &  2015-03-17 \\
-			6 & eclipse-SDK  & GenerateToStringAction.java  & EPLv1  &  2513183	 & alteration  & 2011-03-01 \\
-			7 & eclipse-SDK  & WizardDialog.java  & EPLv1  &   11861598	 & alteration  &  2011-02-03 \\
-			8 & hadoop-1.0.0  & DBCountPageView.java  & Apache-2 & 21702608 & alteration  & 2011-06-12 \\
-			9 & hadoop-1.0.0  & DBCountPageView.java  & Apache-2 & 21702608 & alteration  & 2011-06-12 \\
-			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & Apache-2 & 14845581 & alteration  & 2012-06-25 \\
-			11 & hadoop-1.0.0  & LineRecordReader.java  & Apache-2 & 16180910 & alteration  & 2011-07-25 \\
-			12 & hadoop-1.0.0  & LineRecordReader.java  & Apache-2 & 16180910 & alteration  & 2011-07-25 \\
-			13 & hadoop-1.0.0  & StringUtils.java  & Apache-2 & 801987 & alteration  & 2013-02-04 \\
-			14 & hadoop-1.0.0  & TestJobCounters.java  & Apache-2 & 18833798 & alteration  & 2011-06-12 \\
-			15 & hadoop-1.0.0  & TextOutputFormat.java  & Apache-2 & 16928749 & alteration  & 2011-06-12 \\
-			16 & hadoop-1.0.0  & WritableComparator.java  & Apache-2 & 22315734 & alteration  & 2014-11-20 \\
-			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & -- & 15168494 & alteration  & 2012-06-24 \\
-			18 & hibernate-4.2.2  & Example.java  & -- & 24924255 & alteration  & 2013-04-23 \\
-			19 & hibernate-4.2.2  & SchemaUpdate.java  & -- & 23520731 & alteration  & 2016-02-05 \\
-			20 & hibernate-4.2.2  & SettingsFactory.java  & -- & 8257554 & removal  & 2011-03-11 \\
-			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & -- & 23967852 & alteration  & 2015-03-12 \\
-			22 & jasperreports-3.7.4  & JRVerifier.java  & GLGPLv3+ & 8037824 & alteration  & 2008-04-17 \\
-			23 & jasperreports-3.7.4  & JRVerifier.java  & GLGPLv3+ & 8037824 & alteration  & 2011-05-20 \\
-			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & GLGPLv2.1+ & 12936580 & alteration  & 2016-02-19 \\
-			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & GLGPLv2.1+ & 16058183 & alteration  & 2013-07-03 \\
-			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & GLGPLv2.1+ & 21998949 & alteration  & 2008-06-02 \\
-			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & GLGPLv2.1+ & 21998949 & alteration  & 2008-06-02 \\
-			28 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
-			29 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
-			30 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
-			31 & jgraph-5.13.0.0  & HelloWorld.java  & GLGPLv2.1+ & 6722760 & rewriting  & 2014-04-13 \\
-			32 & jstock-1.0.7c  & GoogleMail.java  & GPLv2+ & 14940863 & alteration  & 2015-12-13 \\
-			33 & jstock-1.0.7c  & GoogleMail.java  & GPLv2+ & 24680923 & alteration  & 2015-12-13 \\
-			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & -- & 6025026 & alteration  & 2010-04-13 \\
-			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & -- & 6025026 & alteration  & 2010-04-13 \\
-			36 & junit-4  & Assert.java  & -- & 23586872 & alteration  & 2015-05-12 \\
-			37 & junit-4  & ExternalResource.java  & -- & 7504040 & alteration  & 2016-06-25 \\
-			38 & junit-4.11  & ExpectException.java  & -- & 8802082 & alteration  & 2014-05-26 \\
-			39 & poi-3.6-20091214  & WorkbookFactory.java  & Apache-2 & 12593810 & alteration  & 2015-04-29 \\
-			40 & spring-framework-3.0.5  & AnnotationMethodHandlerExceptionResolver.java  & Apache-2 & 5660519 & removal  & 2012-01-20 \\
-			41 & spring-framework-3.0.5  & AutowireUtils.java  & Apache-2 & 20913543 & alteration  & 2014-10-28 \\
-			42 & spring-framework-3.0.5  & CustomCollectionEditor.java  & Apache-2 & 18623736 & alteration  & 2013-11-21 \\
-			43 & spring-framework-3.0.5  & DefaultAnnotationHandlerMapping.java  & Apache-2 & 3758110 & removal  & 2012-01-20 \\
-			44 & spring-framework-3.0.5  & DefaultPropertiesPersister.java  & Apache-2 & 6149818 & alteration  & 2013-03-19 \\
-			45 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2016-07-15 \\
-			46 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2008-12-18 \\
-			47 & spring-framework-3.0.5  & DelegatingServletInputStream.java  & Apache-2 & 20996373 & alteration  & 2008-12-18 \\
-			48 & spring-framework-3.0.5  & DispatcherServlet.java  & Apache-2 & 4781746 & alteration  & 2011-08-08 \\
-			49 & spring-framework-3.0.5  & Jaxb2Marshaller.java  & Apache-2 & 10924700 & alteration  & 2012-08-28 \\
-			50 & spring-framework-3.0.5  & ScheduledTasksBeanDefinitionParser.java  & Apache-2 & 3751463 & alteration  & 2016-07-05 \\
-			51 & struts2-2.2.1  & DefaultActionMapper.java  & Apache-2 & 14019840 & alteration  & 2013-10-18 \\
-			52 & tomcat-7.0.2  & BasicAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
-			53 & tomcat-7.0.2  & BasicAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
-			54 & tomcat-7.0.2  & CoyoteAdapter.java  & Apache-2 & 24404964 & alteration  & 2012-11-18 \\
-			55 & tomcat-7.0.2  & CoyoteAdapter.java  & Apache-2 & 24404964 & alteration  & 2012-11-18 \\
-			56 & tomcat-7.0.2  & FormAuthenticator.java  & Apache-2 & 21734562 & alteration  & 2016-08-04 \\
-			57 & tomcat-7.0.2  & HttpServlet.java  & Apache-2 & 5266856 & alteration  & 2011-10-22 \\
-			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & Apache-2 & 10289462 & alteration  & 2012-09-12 \\
+	\scriptsize
+%	\resizebox{2.1\columnwidth}{!}{%
+	\begin{tabular}{r|l|p{4.5cm}|r|r|l|l|c|l}
+		\hline 
+		No. & Project & File & Start & End & License & SO No. & $C$ & C$_{\textit{\textrm{date}}}$ \\
+		\hline
+			1 & aspectj-1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & $M$  & 2015-09-08 \\
+			2 & aspectj-1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & $M$  & 2015-09-08 \\
+			3 & eclipse-SDK  & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & $M$  &  2015-03-17 \\
+			4 & eclipse-SDK  & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	 & $M$  &  2015-03-17 \\
+			5 & eclipse-SDK  & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	 & $M$  &  2015-03-17 \\
+			6 & eclipse-SDK  & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	 & $M$  & 2011-03-01 \\
+			7 & eclipse-SDK  & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	 & $M$  &  2011-02-03 \\
+			8 & hadoop-1.0.0  & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & $M$  & 2011-06-12 \\
+			9 & hadoop-1.0.0  & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & $M$  & 2011-06-12 \\
+			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & $M$  & 2012-06-25 \\
+			11 & hadoop-1.0.0  & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & $M$  & 2011-07-25 \\
+			12 & hadoop-1.0.0  & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & $M$  & 2011-07-25 \\
+			13 & hadoop-1.0.0  & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & $M$  & 2013-02-04 \\
+			14 & hadoop-1.0.0  & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & $M$  & 2011-06-12 \\
+			15 & hadoop-1.0.0  & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & $M$  & 2011-06-12 \\
+			16 & hadoop-1.0.0  & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & $M$  & 2014-11-20 \\
+			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & $M$  & 2012-06-24 \\
+			18 & hibernate-4.2.2  & Example.java  & 224 & 243 & -- & 24924255 & $M$  & 2013-04-23 \\
+			19 & hibernate-4.2.2  & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & $M$  & 2016-02-05 \\
+			20 & hibernate-4.2.2  & SettingsFactory.java  & 244 & 255 & -- & 8257554 & $D$  & 2011-03-11 \\
+			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & $M$  & 2015-03-12 \\
+			22 & jasperreports-3.7.4  & JRVerifier.java  & 982 & 998 & GLGPLv3+ & 8037824 & $M$  & 2008-04-17 \\
+			23 & jasperreports-3.7.4  & JRVerifier.java  & 1221 & 1240 & GLGPLv3+ & 8037824 & $M$  & 2011-05-20 \\
+			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & 532 & 569 & GLGPLv2.1+ & 12936580 & $M$  & 2016-02-19 \\
+			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & 18 & 30 & GLGPLv2.1+ & 16058183 & $M$  & 2013-07-03 \\
+			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & 502 & 520 & GLGPLv2.1+ & 21998949 & $M$  & 2008-06-02 \\
+			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & 522 & 536 & GLGPLv2.1+ & 21998949 & $M$  & 2008-06-02 \\
+			28 & jgraph-5.13.0.0  & HelloWorld.java  & 16 & 22 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
+			29 & jgraph-5.13.0.0  & HelloWorld.java  & 28 & 40 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
+			30 & jgraph-5.13.0.0  & HelloWorld.java  & 31 & 36 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
+			31 & jgraph-5.13.0.0  & HelloWorld.java  & 39 & 56 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
+			32 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & $M$  & 2015-12-13 \\
+			33 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & $M$  & 2015-12-13 \\
+			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & $M$  & 2010-04-13 \\
+			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & $M$  & 2010-04-13 \\
+			36 & junit-4  & Assert.java  & 33 & 52 & -- & 23586872 & $M$  & 2015-05-12 \\
+			37 & junit-4  & ExternalResource.java  & 4 & 23 & -- & 7504040 & $M$  & 2016-06-25 \\
+			38 & junit-4.11  & ExpectException.java  & 11 & 29 & -- & 8802082 & $M$  & 2014-05-26 \\
+			39 & poi-3.6  & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & $M$  & 2015-04-29 \\
+			40 & spring-3.0.5  & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & $D$  & 2012-01-20 \\
+			41 & spring-3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & $M$  & 2014-10-28 \\
+			42 & spring-3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & $M$  & 2013-11-21 \\
+			43 & spring-3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & $D$  & 2012-01-20 \\
+			44 & spring-3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & $M$  & 2013-03-19 \\
+			45 & spring-3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2016-07-15 \\
+			46 & spring-3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2008-12-18 \\
+			47 & spring-3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2008-12-18 \\
+			48 & spring-3.0.5  & DispatcherServlet.java  & 91 & 103 & Apache-2 & 4781746 & $M$  & 2011-08-08 \\
+			49 & spring-3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & Apache-2 & 10924700 & $M$  & 2012-08-28 \\
+			50 & spring-3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & Apache-2 & 3751463 & $M$  & 2016-07-05 \\
+			51 & struts2-2.2.1  & DefaultActionMapper.java  & 91 & 103 & Apache-2 & 14019840 & $M$  & 2013-10-18 \\
+			52 & tomcat-7.0.2  & BasicAuthenticator.java  & 25 & 73 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
+			53 & tomcat-7.0.2  & BasicAuthenticator.java  & 33 & 43 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
+			54 & tomcat-7.0.2  & CoyoteAdapter.java  & 543 & 553 & Apache-2 & 24404964 & $M$  & 2012-11-18 \\
+			55 & tomcat-7.0.2  & CoyoteAdapter.java  & 557 & 573 & Apache-2 & 24404964 & $M$  & 2012-11-18 \\
+			56 & tomcat-7.0.2  & FormAuthenticator.java  & 51 & 61 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
+			57 & tomcat-7.0.2  & HttpServlet.java  & 111 & 124 & Apache-2 & 5266856 & $M$  & 2011-10-22 \\
+			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & Apache-2 & 10289462 & $M$  & 2012-09-12 \\
 		\hline
 	\end{tabular} %
-}
+%}
 \end{table*}
@@
 Software licensing is a paramount factor in software development.
-Violation of software license can cause a major impact to the delivery of the software and also lead to legal issues.
+Violation of software license can cause a major impact to software delivery and also lead to legal issues.
 It is an emerging area that software engineering research community is paying attention to.

### 2016-11-29 cloneoverflow-latex/cloneoverflow.tex
added a FXIME of security aspect of SO
Updated on iMac

@@
 Carelessly cloning code from one project and reusing it in another project with different license may cause software licensing violation \cite{German2009}.
+Security is among the main concerns when code is copied from online source.
+A study finds that \FIXME{add this} \cite{Acar2016}.
 
@@
 We call them \textbf{online code clones}.
-There are three ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; and (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium.
+There are four ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium; and (4) code is cloned from an external source to both Stack Overflow and a software project.
 Online code clones can similarly lead to a problem of bug propagation as classical code clones.

### 2016-11-29 cloneoverflow-latex/cloneoverflow.tex
Updated the paper

--- 2016-11-21 cloneoverflow-latex/cloneoverflow.tex
@@
 On Stack Overflow, each conversation contains a question and answer(s).
-The answers normally contain at least one code snippet as a solution to the question asked.
+The answers frequently contain at least one code snippet as a solution to the question asked.
 The code snippet is usually not written directly on Stack Overflow website but copied from another location.
 It can be copied and modified from the problematic code snippet in the question, copied from an answerer's own code, or borrowed from other locations including open source software (OSS) systems.
-As a result, the process of posting and answering questions on Stack Overflow which involves copying and pasting source code can be considered as code cloning.
+The process of posting and answering questions on Stack Overflow, which involves copying and pasting source code, can be considered as code cloning.
 
@@
 Code cloning can also have side effects of violating software licenses.
-Carelessly cloning code from one project and reusing it in another project with different license may cause software licensing violation \cite{German2009}.
+Carelessly cloning code from one project to another project with different license may cause software licensing violation \cite{German2009}.
+Security is also among the main concerns when code is copied from online source.
+A study finds that \FIXME{add this} \cite{Acar2016}.
 
@@
 We call them \textbf{online code clones}.
-There are three ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; and (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium.
+There are four ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium; and (4) code is cloned from an external source to both a software project and Stack Overflow.
 Online code clones can similarly lead to a problem of bug propagation as classical code clones.
 Unfortunately, they are more difficult to locate and fix since the search space from online corpora is larger and no longer confined in a local repository.
-
-A motivating example of problems caused by online code clones can be found in a Stack Overflow post regarding how to implement RawComparator in Hadoop\footnote{http://stackoverflow.com/questions/22262310}.
+\FIXME{Add another motivation of security of reusing code from Stack Overflow}.
+
+A motivating example of problems caused by online code clones can be found in a Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}.
 In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 266,837,480 similar code fragment pairs and manually investigated 7,840 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 109 Java open source projects.
+We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,450 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 238 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses.
-Furthermore, 50 out of the 84 clones are outdated and questionable for being reused.
+\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 523 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses.
+Furthermore, 53 out of the 96 online code clones on Stack Overflow are outdated and questionable for being reused.
 
@@
 \newline
-\textbf{RQ2 (classification of online code clones):} \textit{What are the main characteristics among the set of online code clones?} We group them into seven groups according to our pre-defined classification scheme so we can differentiate and understand the motivation of cloning.
-Some of the clones are copy from open source projects to Stack Overflow, while some are copied from a third-party location, and some are accidental clones containing boiler-plate code, and code stubs generated by IDE.
+\textbf{RQ2 (classification of online code clones):} \textit{What are the reasons of creating online code clones?} We categorise online clones into seven groups according to our clone classification scheme.
+%so we can differentiate and understand the motivation of cloning.
+Clones can be copied from open source projects to Stack Overflow as examples, or vice versa.
+Furthermore, they can be cloned from a third-party location or clones containing boiler-plate code, and code stubs generated by IDE.
 \newline
@@
 Then, we deploy two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets.
-Due to a technical limit of Simian and NiCad to scale to large datasets, we partition the input and run the tools multiple times.
-Each run is composed of the whole Stack Overflow data and a single Qualitas project.
+Due to scalability of Simian and NiCad, we partition the input and run the tools multiple times.
+Each run is composed of the whole Stack Overflow data and single Qualitas project.
 We repeat the process until we cover 111 projects.
@@
 We then convert the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combine them into a single file.
-GCF provides a common format for clones which enable us to reuse scripts that analyse clone reports from Simian and NiCad.
+GCF provides a common format for clones which enable us to reuse the same scripts to analyse clone reports from both Simian and NiCad.
 Moreover, using GCF, other additional clone detectors can be adopted, if needed, without any changes in the analysis.
@@
 In this step, all intra clone pairs within Stack Overflow and open source projects are removed.
-NiCad provides an option to detect inter clones so no pruning is needed.
-Next, clone pairs reported from the two clone detectors are pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
+NiCad can detect inter clones so no pruning is needed.
+We do not have an oracle of clones in 111 Qualitas projects so we need a manual investigation to validate the reported clone candidates.
+However, the large amount of clone pairs hinder us from looking at all of them.
+Random samples can be done but may return mostly non-meaningful clones.
+Instead, we select clone pair candidates by relying on agreement of clone detectors.
+If a clone pairs is similarly reported by multiple tools, we have higher confidence that it is a real clone pair.
+To achieve this, clone pairs from the two clone detectors are pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
 This step generates \textbf{agreed clone pairs}.
-They are clones with highest confidence since they receive agreement from both tools.
-Then, clone pairs reported by Simian and NiCad that do not find agreement are filtered by size of minimum 10 lines.
-This step generates \textbf{disagreed clone pairs}.
+They are pairs with high confidence to be true clone pairs since they obtain agreement from both tools.
+Then, pairs reported by Simian and NiCad that do not find agreement are \textbf{disagreed clone pairs}.
 The disagreed clone pairs are clones with less confidence than agreed ones.
-Finally, agreed and disagreed clone pairs are looked at and classified manually by the first author.
-
-In the manual inspection process, we classify clones into categories according to their properties.
-This process takes approximately a months until we successfully classified 7,840 clone pairs into categories.
-Some of the clone candidates are false clones due to being boiler-plate code or IDE-generated and are discarded for further analysis.
-By ignoring the false clones, we compare licensing information of 477 remaining clone pairs for possibility of software licensing violations.
-Moreover, we look forward through history of the clones from the projects' git versioning systems.
-This is to see if there is any changes made to the clones after it has been copied, hence resulting in outdated clones on Stack Overflow.
+Finally, agreed and disagreed clone pairs are sampled and looked at manually by the first author.
+
+In the manual inspection process, we classify clones into seven categories according to information observed from code comments and text in Stack Overflow answer.
+This process takes approximately a months until we successfully investigate 3,450 clone pairs.
+Clone pairs that are classified as boiler-plate code or IDE-generated are not very interesting and are discarded for further analysis.
+We further compare licensing information of 523 remaining clone pairs for possibility of software licensing violations.
+Moreover, we look forward through history of each clone from its project's versioning systems.
+With this method we can observe whether there is any changes made to a clone after it has been copied.
+%hence resulting in outdated clones on Stack Overflow.
 
@@
 
-\textbf{Stack Overflow}: we extracted Java code snippets from accepted answers in a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
+\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
 The archived dump has a size of 9 gigabytes.
@@
 First, we ignore snippets that are less than 6 lines since they are usually not considered as clones by clone detection research \cite{something}.
-Second, we are only interested in code snippets from posts that are marked accepted answer since they have high chances to be reused than snippets in questions and other answers.
+Second, we are only interested in code snippets from posts that are marked as \textbf{accepted answer}.
+Posts on Stack Overflow are marked accepted by the questions' posters if the solutions in the posts solve their problems.
+We choose them because they have high chance to be reused than snippets in questions and other answers.
 Each snippet is extracted from the dump using regular expressions and saved to a file using its post ID as the file's name.
-We use \texttt{.java} extension so that the clone detectors can recognise them.
-If a Stack Overflow conversation has more than one code snippet in the accepted answer, we append an indexing number starting from zero after the post ID (e.g.
-45051109\_0.java, and 45051109\_1.java).
-With the two filters, we finally obtained 144,075 Java code snippets which contain xxx lines of Java source code excluding comments and blank lines\footnote{measured by cloc: https://github.com/AlDanial/cloc}.
+If an accepted answer has more than one code snippet, we append an indexing number, starting from zero, after the post ID (e.g.
+45051109\_0, and 45051109\_1.).
+Lastly, we add \texttt{.java} extension to the file's names so that clone detectors can recognise them.
+We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
 
@@
 The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}.
-We selected the 20130901r snapshot of Qualitas corpus containing 112 Java open source projects.
+We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects.
 This release contains projects with releases no later than 1st September 2013.
 We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow.
-The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment, January--December 2016.
+The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016).
 The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow.
-Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code so it is removed from the study.
+Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code due to its license \cite{QualitasCorpus} so it is removed from the study.
 This results in totally 111 projects analysed in the study.
@@
 \subsection{Clone detectors' parameter tuning}
-We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2013,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
+We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
 However, considering the size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools.
@@
 		\item Improving Stack Oveflow \cite{Diamantopoulos2015, Wang2014, Bosu2013}
-		\item Developers' behaviours on Stack Overlow \cite{Wang2013, Movshovitz-Attias2013}
+		\item Developers' behaviours on Stack Overlow \cite{Wang2013_StackOverflow, Movshovitz-Attias2013}
 	\end{itemize}

### 2016-12-05 cloneoverflow-latex/cloneoverflow.tex
Added updates
Updated with license numbers (still wrong, need fixing)

@@
 
+\FIXME{Can we say the inspected clone set is another benchmark?}
+
 \section{Empirical Study}
@@
 %			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
-%			c-jdbc & 2.0.2 & - & 16/09/2005 & - & GLGPL 2.1 & \\
+%			c-jdbc & 2.0.2 & - & 16/09/2005 & - & LGPL 2.1 & \\
 %			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
 %			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\
-%			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & GLGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
+%			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & LGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
 %			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\
@@
 %			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
-%			exoportal & ??? & ??? &  & git & GLGPL 3.0 \& proprietary & Too many new projects \\
+%			exoportal & ??? & ??? &  & git & LGPL 3.0 \& proprietary & Too many new projects \\
 %			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
-%			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & GLGPL 2.0 & \\
+%			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & LGPL 2.0 & \\
 %			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
@@
 %			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
-%			geotools & 2.7-M3 & 16 & 27/09/2016 & git & GLGPL 2.0 & \\
+%			geotools & 2.7-M3 & 16 & 27/09/2016 & git & LGPL 2.0 & \\
 %			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
-%			heritrix & 1.14.4 & - & 05/06/2013 & - & GLGPL 2.1 & \\
-%			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & GLGPL 2.1+ & \\
+%			heritrix & 1.14.4 & - & 05/06/2013 & - & LGPL 2.1 & \\
+%			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & LGPL 2.1+ & \\
 %			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
 %			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
-%			ireport & 3.7.5 & - & 28/05/2014 & - & Affero GLGPL 3.0 & \\
-%			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero GLGPL 3.0 & \\
-%			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & GLGPL 2.1 \& Apache Software 1.1 & \\
+%			ireport & 3.7.5 & - & 28/05/2014 & - & Affero LGPL 3.0 & \\
+%			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero LGPL 3.0 & \\
+%			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & LGPL 2.1 \& Apache Software 1.1 & \\
 %			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
@@
 %			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\
-%			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & GLGPL 3.0 &  \\
+%			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & LGPL 3.0 &  \\
 %			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\
-%			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & GLGPL 2.1 & Renamed to Wildfly. \\
-%			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & GLGPL 2.1+ &  \\
+%			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & LGPL 2.1 & Renamed to Wildfly. \\
+%			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & LGPL 2.1+ &  \\
 %			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
@@
 %			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
-%			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & GLGPL 2.0 &   \\
+%			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & LGPL 2.0 &   \\
 %			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
-%			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& GLGPL (derivatives) & \\
-%			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & GLGPL 2.1 \& Eclipse  1.0 & \\
+%			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& LGPL (derivatives) & \\
+%			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & LGPL 2.1 \& Eclipse  1.0 & \\
 %			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\
 %			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
-%			jparse & 0.96 & - & 29/07/2004 & - & GLGPL 2.1 & \\
+%			jparse & 0.96 & - & 29/07/2004 & - & LGPL 2.1 & \\
 %			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
 %			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\
-%			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & GLGPL 2.0 &  \\
+%			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & LGPL 2.0 &  \\
 %			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
@@
 We started by studying the 8 patterns of cloning from Kapser et al.
-\cite{Kapser2006}.
+\cite{Kapser2006,Kapser2008}.
 We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments.
@@
 			\hline 
-			\multirow{1}{*}{\textit{Simian$_{df}$}} & 19 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
+			\multirow{1}{*}{\textit{Simian$_{df}$}} & 79 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
 			\hline
@@
 	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
-	\label{t:new_and_old}
+	\label{t:q_projects_license}
 	%	\resizebox{\columnwidth}{!}{%
@@
 		\hline
-		hibernate & 4.2.2 & Apache-2 (20), \newline GLGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
-		\hline
-		jasperreports & 3.7.4 & GLGPLv2.1+ (3), \newline GLGPLv3+ (1,581), \newline None (1), Unknown (4)\\
-		\hline
-		jfreechart & 1.0.13 & GLGPLv2.1+ (989) \\
-		\hline
-		jgraph & 5.13.0.0 & GLGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
-		\hline
-		%		jgrapht & 0.8.1 & GLGPL 2.1 \& Eclipse  1.0 \\
-		jstock & 1.0.7c & GLGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
+		hibernate & 4.2.2 & Apache-2 (20), \newline LGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
+		\hline
+		jasperreports & 3.7.4 & LGPLv2.1+ (3), \newline LGPLv3+ (1,581), \newline None (1), Unknown (4)\\
+		\hline
+		jfreechart & 1.0.13 & LGPLv2.1+ (989) \\
+		\hline
+		jgraph & 5.13.0.0 & LGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
+		\hline
+		%		jgrapht & 0.8.1 & LGPL 2.1 \& Eclipse  1.0 \\
+		jstock & 1.0.7c & LGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
 		\hline
@@
 	\end{lstlisting}
-	\caption{Outdated code fragment on Stack Overflow post 23520731 copied from SchemaUpdate.java and its latest version in hibernate code base with heavy modifications}
+	\caption{Outdated code fragment on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains several modifications.}
 	\label{fig:hibernate_outdated_code}
@@
 	\scriptsize
-%	\resizebox{2.1\columnwidth}{!}{%
-	\begin{tabular}{r|l|p{4.5cm}|r|r|l|l|c|l}
-		\hline 
-		No. & Project & File & Start & End & License & SO No. & $C$ & C$_{\textit{\textrm{date}}}$ \\
-		\hline
-			1 & aspectj-1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & $M$  & 2015-09-08 \\
-			2 & aspectj-1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & $M$  & 2015-09-08 \\
-			3 & eclipse-SDK  & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & $M$  &  2015-03-17 \\
-			4 & eclipse-SDK  & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	 & $M$  &  2015-03-17 \\
-			5 & eclipse-SDK  & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	 & $M$  &  2015-03-17 \\
-			6 & eclipse-SDK  & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	 & $M$  & 2011-03-01 \\
-			7 & eclipse-SDK  & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	 & $M$  &  2011-02-03 \\
-			8 & hadoop-1.0.0  & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & $M$  & 2011-06-12 \\
-			9 & hadoop-1.0.0  & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & $M$  & 2011-06-12 \\
-			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & $M$  & 2012-06-25 \\
-			11 & hadoop-1.0.0  & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & $M$  & 2011-07-25 \\
-			12 & hadoop-1.0.0  & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & $M$  & 2011-07-25 \\
-			13 & hadoop-1.0.0  & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & $M$  & 2013-02-04 \\
-			14 & hadoop-1.0.0  & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & $M$  & 2011-06-12 \\
-			15 & hadoop-1.0.0  & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & $M$  & 2011-06-12 \\
-			16 & hadoop-1.0.0  & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & $M$  & 2014-11-20 \\
-			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & $M$  & 2012-06-24 \\
-			18 & hibernate-4.2.2  & Example.java  & 224 & 243 & -- & 24924255 & $M$  & 2013-04-23 \\
-			19 & hibernate-4.2.2  & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & $M$  & 2016-02-05 \\
-			20 & hibernate-4.2.2  & SettingsFactory.java  & 244 & 255 & -- & 8257554 & $D$  & 2011-03-11 \\
-			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & $M$  & 2015-03-12 \\
-			22 & jasperreports-3.7.4  & JRVerifier.java  & 982 & 998 & GLGPLv3+ & 8037824 & $M$  & 2008-04-17 \\
-			23 & jasperreports-3.7.4  & JRVerifier.java  & 1221 & 1240 & GLGPLv3+ & 8037824 & $M$  & 2011-05-20 \\
-			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & 532 & 569 & GLGPLv2.1+ & 12936580 & $M$  & 2016-02-19 \\
-			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & 18 & 30 & GLGPLv2.1+ & 16058183 & $M$  & 2013-07-03 \\
-			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & 502 & 520 & GLGPLv2.1+ & 21998949 & $M$  & 2008-06-02 \\
-			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & 522 & 536 & GLGPLv2.1+ & 21998949 & $M$  & 2008-06-02 \\
-			28 & jgraph-5.13.0.0  & HelloWorld.java  & 16 & 22 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
-			29 & jgraph-5.13.0.0  & HelloWorld.java  & 28 & 40 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
-			30 & jgraph-5.13.0.0  & HelloWorld.java  & 31 & 36 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
-			31 & jgraph-5.13.0.0  & HelloWorld.java  & 39 & 56 & GLGPLv2.1+ & 6722760 & $R$  & 2014-04-13 \\
-			32 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & $M$  & 2015-12-13 \\
-			33 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & $M$  & 2015-12-13 \\
-			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & $M$  & 2010-04-13 \\
-			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & $M$  & 2010-04-13 \\
-			36 & junit-4  & Assert.java  & 33 & 52 & -- & 23586872 & $M$  & 2015-05-12 \\
-			37 & junit-4  & ExternalResource.java  & 4 & 23 & -- & 7504040 & $M$  & 2016-06-25 \\
-			38 & junit-4.11  & ExpectException.java  & 11 & 29 & -- & 8802082 & $M$  & 2014-05-26 \\
-			39 & poi-3.6  & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & $M$  & 2015-04-29 \\
-			40 & spring-3.0.5  & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & $D$  & 2012-01-20 \\
-			41 & spring-3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & $M$  & 2014-10-28 \\
-			42 & spring-3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & $M$  & 2013-11-21 \\
-			43 & spring-3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & $D$  & 2012-01-20 \\
-			44 & spring-3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & $M$  & 2013-03-19 \\
-			45 & spring-3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2016-07-15 \\
-			46 & spring-3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2008-12-18 \\
-			47 & spring-3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & $M$  & 2008-12-18 \\
-			48 & spring-3.0.5  & DispatcherServlet.java  & 91 & 103 & Apache-2 & 4781746 & $M$  & 2011-08-08 \\
-			49 & spring-3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & Apache-2 & 10924700 & $M$  & 2012-08-28 \\
-			50 & spring-3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & Apache-2 & 3751463 & $M$  & 2016-07-05 \\
-			51 & struts2-2.2.1  & DefaultActionMapper.java  & 91 & 103 & Apache-2 & 14019840 & $M$  & 2013-10-18 \\
-			52 & tomcat-7.0.2  & BasicAuthenticator.java  & 25 & 73 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
-			53 & tomcat-7.0.2  & BasicAuthenticator.java  & 33 & 43 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
-			54 & tomcat-7.0.2  & CoyoteAdapter.java  & 543 & 553 & Apache-2 & 24404964 & $M$  & 2012-11-18 \\
-			55 & tomcat-7.0.2  & CoyoteAdapter.java  & 557 & 573 & Apache-2 & 24404964 & $M$  & 2012-11-18 \\
-			56 & tomcat-7.0.2  & FormAuthenticator.java  & 51 & 61 & Apache-2 & 21734562 & $M$  & 2016-08-04 \\
-			57 & tomcat-7.0.2  & HttpServlet.java  & 111 & 124 & Apache-2 & 5266856 & $M$  & 2011-10-22 \\
-			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & Apache-2 & 10289462 & $M$  & 2012-09-12 \\
+	\resizebox{2.1\columnwidth}{!}{%
+	\begin{tabular}{r|l|p{4.5cm}|r|r|l|l|l|c|l}
+		\hline 
+		No. & Project & File & Start & End & License & SO Post & License & $C$ & C$_{\textit{\textrm{date}}}$ \\
+		\hline
+			1 & aspectj-1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & -- & $M$  & 2015-09-08 \\
+			2 & aspectj-1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & & $M$  & 2015-09-08 \\
+			3 & eclipse-SDK  & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & EPLv1 & $M$  &  2015-03-17 \\
+			4 & eclipse-SDK  & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
+			5 & eclipse-SDK  & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
+			6 & eclipse-SDK  & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	& EPLv1 & $M$  & 2011-03-01 \\
+			7 & eclipse-SDK  & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	& -- & $M$  &  2011-02-03 \\
+			8 & hadoop-1.0.0  & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
+			9 & hadoop-1.0.0  & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
+			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & -- & $M$  & 2012-06-25 \\
+			11 & hadoop-1.0.0  & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
+			12 & hadoop-1.0.0  & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
+			13 & hadoop-1.0.0  & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & -- & $M$  & 2013-02-04 \\
+			14 & hadoop-1.0.0  & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & -- & $M$  & 2011-06-12 \\
+			15 & hadoop-1.0.0  & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & -- & $M$  & 2011-06-12 \\
+			16 & hadoop-1.0.0  & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & -- & $M$  & 2014-11-20 \\
+			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & -- & $M$  & 2012-06-24 \\
+			18 & hibernate-4.2.2  & Example.java  & 224 & 243 & -- & 24924255 & -- & $M$  & 2013-04-23 \\
+			19 & hibernate-4.2.2  & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & -- & $M$  & 2016-02-05 \\
+			20 & hibernate-4.2.2  & SettingsFactory.java  & 244 & 255 & -- & 8257554 & -- & $D$  & 2011-03-11 \\
+			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & -- & $M$  & 2015-03-12 \\
+			22 & jasperreports-3.7.4  & JRVerifier.java  & 982 & 998 & LGPLv3+ & 8037824 & -- & $M$  & 2008-04-17 \\
+			23 & jasperreports-3.7.4  & JRVerifier.java  & 1221 & 1240 & LGPLv3+ & 8037824 & -- & $M$  & 2011-05-20 \\
+			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & 532 & 569 & LGPLv2.1+ & 12936580 & -- & $M$  & 2016-02-19 \\
+			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & 18 & 30 & LGPLv2.1+ & 16058183 & -- & $M$  & 2013-07-03 \\
+			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & 502 & 520 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
+			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & 522 & 536 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
+			28 & jgraph-5.13.0.0  & HelloWorld.java  & 16 & 22 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
+			29 & jgraph-5.13.0.0  & HelloWorld.java  & 28 & 40 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
+			30 & jgraph-5.13.0.0  & HelloWorld.java  & 31 & 36 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
+			31 & jgraph-5.13.0.0  & HelloWorld.java  & 39 & 56 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
+			32 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & -- & $M$  & 2015-12-13 \\
+			33 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & -- & $M$  & 2015-12-13 \\
+			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
+			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
+			36 & junit-4  & Assert.java  & 33 & 52 & -- & 23586872 & -- & $M$  & 2015-05-12 \\
+			37 & junit-4  & ExternalResource.java  & 4 & 23 & -- & 7504040 & -- & $M$  & 2016-06-25 \\
+			38 & junit-4.11  & ExpectException.java  & 11 & 29 & -- & 8802082 & -- & $M$  & 2014-05-26 \\
+			39 & poi-3.6  & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & -- & $M$  & 2015-04-29 \\
+			40 & spring-3.0.5  & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & -- & $D$  & 2012-01-20 \\
+			41 & spring-3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & -- & $M$  & 2014-10-28 \\
+			42 & spring-3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & -- & $M$  & 2013-11-21 \\
+			43 & spring-3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & -- & $D$  & 2012-01-20 \\
+			44 & spring-3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & -- & $M$  & 2013-03-19 \\
+			45 & spring-3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2016-07-15 \\
+			46 & spring-3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
+			47 & spring-3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
+			48 & spring-3.0.5  & DispatcherServlet.java  & 91 & 103 & Apache-2 & 4781746 & -- & $M$  & 2011-08-08 \\
+			49 & spring-3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & Apache-2 & 10924700 & -- & $M$  & 2012-08-28 \\
+			50 & spring-3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & Apache-2 & 3751463 & -- & $M$  & 2016-07-05 \\
+			51 & struts2-2.2.1  & DefaultActionMapper.java  & 91 & 103 & Apache-2 & 14019840 & -- & $M$  & 2013-10-18 \\
+			52 & tomcat-7.0.2  & BasicAuthenticator.java  & 25 & 73 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
+			53 & tomcat-7.0.2  & BasicAuthenticator.java  & 33 & 43 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
+			54 & tomcat-7.0.2  & CoyoteAdapter.java  & 543 & 553 & Apache-2 & 24404964 & -- & $M$  & 2012-11-18 \\
+			55 & tomcat-7.0.2  & CoyoteAdapter.java  & 557 & 573 & Apache-2 & 24404964 & -- & $M$  & 2012-11-18 \\
+			56 & tomcat-7.0.2  & FormAuthenticator.java  & 51 & 61 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
+			57 & tomcat-7.0.2  & HttpServlet.java  & 111 & 124 & Apache-2 & 5266856 & -- & $M$  & 2011-10-22 \\
+			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & Apache-2 & 10289462 & -- & $M$  & 2012-09-12 \\
 		\hline
 	\end{tabular} %
-%}
+}
 \end{table*}
@@
 
+\begin{table}[]
+	\centering
+	\caption{Licenses of 488 clone pairs in category A, B, and C}
+	\label{tab:license_abc}
+	\small
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|l|p{2.2cm}|r|r|r}
+		\hline
+		Type                 & SO          & Qualitas          & A & B & C \\
+		\hline
+		No license           & None        & None              & 18 & 61 & 1 \\
+		\hline
+		\multirow{3}{*}{Compatible} & Apache2     & Apache2    & 0  & 1  & 0 \\
+		& EPLv1       & EPLv1                                  & 8  & 0  & 0 \\
+		& CC BY 3.0   & CC BY 3.0                              & 0  & 17 & 0 \\
+		\hline
+		\multirow{14}{*}{Incompat.} & None        & Apache2    & 41 & 34 & 1 \\
+		& None        & BSD3                                   & 0  & 1  & 0 \\
+		& None        & CDDLorGPLv2                            & 0  & 62 & 1 \\
+		& None        & EPLv1                                  & 6  & 0  & 0 \\
+		& None        & GPLv2/2+/3+                            & 5  & 57 & 14 \\
+		& None        & LGPL2.1+/3+                            & 18 & 33 & 2 \\
+		& None        & AGPLv3/3+                              & 0  & 9  & 1 \\
+		& None        & MPLv1\_1                               & 0  & 1  & 0 \\
+		& None        & spdxBSD3                               & 0  & 8  & 1 \\
+		& None        & BSD                                    & 0  & 63 & 0 \\
+		& None        & Unidentifiable                         & 0  & 1  & 0 \\
+		& Sun (prop.) & None                                   & 0  & 21 & 0 \\
+		& MIT         & None                                   & 0  & 0  & 1 \\
+		& spdxBSD3/4  & None                                   & 0  & 0  & 0 \\ 
+		& BSD3        & GPLv2+								   & 0  & 1  & 0 \\  
+		\hline
+		Total 	      &               &                       & 96 & 370 & 22 \\
+		\hline
+	\end{tabular} %
+}
+\end{table}
+
 In our study, we reveal another possible situation of software licensing issue caused by code cloning to Stack Overflow.
-We found that there are at least 84 pieces of code have been copied from 13 open source projects in Qualitas dataset to Stack Overflow as examples.
+We found with evidence that 96 pieces of code have been copied from 14 open source projects in Qualitas dataset to Stack Overflow as examples.
 They are also marked as accepted answers which increase their probability of being reused.
-These 13 open source projects come with their respective software licenses.
+The 14 open source projects come with their respective software licenses (shown in \Cref{t:q_projects_license}).
 However, the licensing information are mostly missing from these clones when they are posted on Stack Overflow.
 Mostly one or a few methods from the full source file are cloned.
-This makes the license information at the top of the file mostly left uncopied.
+This makes the licensing terms at the top of the file mostly left uncopied.
 If developers copy and reuse these pieces of code in their projects, a licensing conflict can quietly happen without realisation of the developers.

### 2016-12-05 cloneoverflow-latex/cloneoverflow.tex
Added the section of licensing issue and external clones

@@
 	\centering
-	\caption{Licenses of 488 clone pairs in category A, B, and C}
+	\caption{Licenses of 523 clone pairs in category A, B, and C}
 	\label{tab:license_abc}
@@
 	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|l|p{2.2cm}|r|r|r}
+	\begin{tabular}{p{1.5cm}|l|p{2.2cm}|r|r|r}
 		\hline
@@
 		\hline
-		No license           & None        & None              & 18 & 61 & 1 \\
-		\hline
-		\multirow{3}{*}{Compatible} & Apache2     & Apache2    & 0  & 1  & 0 \\
-		& EPLv1       & EPLv1                                  & 8  & 0  & 0 \\
-		& CC BY 3.0   & CC BY 3.0                              & 0  & 17 & 0 \\
-		\hline
-		\multirow{14}{*}{Incompat.} & None        & Apache2    & 41 & 34 & 1 \\
-		& None        & BSD3                                   & 0  & 1  & 0 \\
-		& None        & CDDLorGPLv2                            & 0  & 62 & 1 \\
-		& None        & EPLv1                                  & 6  & 0  & 0 \\
-		& None        & GPLv2/2+/3+                            & 5  & 57 & 14 \\
+		No license \newline (\textit{NL})                               & None        & None              					&  18 & 62 & 5 \\
+		\hline
+		Compatible  							 & Apache2     & Apache2  				      	&  0 & 1 & 0 \\
+		(\textit{CL})	   						     & EPLv1       & EPLv1                                	&  14 &  6 & 0 \\
+															& None        & CC BY 3.0                    		&  0 & 12 & 0 \\
+		\hline
+	    Incompat. 									& None       & Apache2  						   & 41 & 29 & 3 \\
+		(\textit{IL}) 								   & None        & BSD/BSD3                        & 0 & 64 & 0 \\
+															& None        & CDDLorGPLv2                & 0 & 63 & 4 \\
+															& None        & EPLv1                               & 0 & 33 & 0\\
+															& None        & GPLv2/2+/3+                  &  5 & 52 & 14 \\
 															& None        & LGPL2.1+/3+                   &  18 & 33 & 2 \\
-		& None        & AGPLv3/3+                              & 0  & 9  & 1 \\
-		& None        & MPLv1\_1                               & 0  & 1  & 0 \\
+															& None        & AGPLv3/3+                     & 0 & 9 &1  \\
+															& None        & MPLv1\_1                         & 0 & 1 & 0\\
 															& None        & spdxBSD3                      & 0 & 8 & 1 \\
-		& None        & BSD                                    & 0  & 63 & 0 \\
 															& None        & Unidentifiable                 & 0 & 1 & 0 \\
-		& Sun (prop.) & None                                   & 0  & 21 & 0 \\
-		& MIT         & None                                   & 0  & 0  & 1 \\
-		& spdxBSD3/4  & None                                   & 0  & 0  & 0 \\ 
+															& Proprietary & None                            & 0 & 21 & 1 \\
 															& BSD3        & GPLv2+							& 0 & 1 & 0 \\
 		\hline
-		Total 	      &               &                       & 96 & 370 & 22 \\
+		\multicolumn{3}{l|}{Total} 	       																&  96 & 396 & 31 \\
 		\hline
@@
 
+The summary of licensing information is listed in \Cref{tab:license_abc}.
+The licenses are extracted by an automatic license identification tool Ninka \cite{German2010}.
+For the ones that cannot be automatically identified by Ninka and have been reported as SeeFile and Unknown, we look at them manually.
+The table shows license of Stack Overflow snippets (denoted as SO) and Qualitas source code.
+The number of clone pairs according to each pair of license has been categorised by online clone category A, B, and C.
+In overall, we can see that most of the Stack Overflow snippets do not have licensing terms with them while their clone counterparts in Qualitas project do.
+
+\textbf{No license or compatible license:} There are 85 clone pairs in type \textit{NL} which do not have licensing information (None vs.~None) and 13 pairs in type \textit{CL} which have compatible licenses (Apache2 vs.~Apache2; EPLv1 vs.~EPLv1; None vs.~CC BY 3.0).
+They are safe for being reused.
+Since source code and text on Stack Overflow posted before 1st March 2016 are protected by CC BY 3.0 (and MIT license from 1st March 2016 onwards), we can treat Stack Overflow code snippets without licensing information as having CC BY 3.0 by default.
+CC BY 3.0 license is relaxed and it only request attribution when reuse.
+
+\textbf{Incompatible license:} there are a large number of clone pairs in type \textit{IL} which do not contain licensing information after they are posted on Stack Overflow or having different license that its Qualitas clone counterpart.
+96 category-A clones are the pairs that we have evidence of being copied from Qualitas to Stack Overflow.
+64 of them do not contain licensing terms after posted and are controversial for being reused.
+396 clone pairs in category B are highly similar clones that we do not have evidence of copying.
+315 of them have incompatible licenses.
+Interestingly, there are 21 clone pairs that Stack Overflow snippets contain Sun and MIT-like license while Qualitas clones do not have any license information.
+There is also one clone pair having BSD3 license on Stack Overflow while having GPLv2+ in Qualitas source code.
+Lastly, 26 out of 31 clone pairs in category C have incompatible license.
+They are clones that have been identified to be copied from an external source.
+Again, most of the clones in Qualitas contain license while the Stack Overflow snippets do not.
+
 \subsubsection{Interesting finding: external clones}
 
-%\section{Investigation of Missing A/B Clone Pairs Reported by Simian$_{df}$}
-%We investigated the 41 clone pairs previously reported by Simian with default configurations and manually investigated.
-The 41 pairs were searched for in 4 new results sets: Simian$_{df}$, Simian$_{\mathrm{\textit{EvCl}}}$, NiCad$_{df}$, NiCad$_{\mathrm{\textit{EvCl}}}$.
-The investigation results are shown in Table \ref{tab:search}.
-%
-%\begin{table}
-%	\centering
-%	\caption{Results of matching the original 41 Simian(default) pairs in the pretty-printed result sets}
-%	\label{tab:search}
-%	\begin{tabular}{l|r|r}
-%		\hline 
-%		Settings & Found & Not found \\ 
-%		\hline 
-%		Simian$_{df}$  &  40 & 1* \\ 
-%		\hline 
-%		Simian$_{\mathrm{\textit{EvCl}}}$ & 0 & 41  \\ 
-%		\hline 
-%		NiCad$_{df}$  & 17 & 24 \\ 
-%		\hline 
-%		NiCad$_{\mathrm{\textit{EvCl}}}$ &  24 & 17 \\ 
-%		\hline 
-%	\end{tabular} 
-%\end{table}
-%
-%The single missing Stack Overflow fragment (19051537\) (denoted by *) is one of the 11 false clones generated by Simian.
-It is removed from the results of the pretty-printed version because it is an outlier.
-The rest are missing because of different parameter settings.
-%
-%\section{Simian's Parameters}
-%
-%We have carefully investigated the effects of the Simian's parameter \texttt{-balanceSquareBrackets+}.
-I found that it works in the expected way of handling a pair of brackets (\texttt{[},\texttt{]}) that span over multiple lines.
-For example, the two code fragments in Figure \ref{fig:two_frags} would match by having \texttt{-balanceSquareBrackets+} enabled.
-However, the \texttt{-balanceSquareBrackets+} parameter only works on a small testing environment having toy programs or only small pairs from the full datasets.
-It does not work with the full complete set of 144,075 Stack Overflow fragments and Qualitas projects.
-Please find the summary of all the testing scenarios in Table \ref{tab:summary}.
-%I found that this pair is missing if I turned on \texttt{-balanceSquareBrackets+}.
-%
-%\noindent\begin{figure*}
-%	\scriptsize
-%	\begin{lstlisting}[frame=single,style=base]
-%	1   public class MagicSquare {                           public class MagicSquare2 {
-%	2       private int[][] square;                              @private int[@
-%	3       private boolean[] possible;                                      @][@
-%	4       private int totalSqs;                                            @] square;@
-%	5       private int sum;                                     private boolean[] possible;
-%	6       private int numsquares;                              private int totalSqs;
-%	7       public static void main ( String[] args ) {          private int sum;
-%	8       MagicSquare m = new MagicSquare ( 3 );               private int numsquares;
-%	9                                                            public static void main ( String[] args ) {
-%	10                                                           MagicSquare m = new MagicSquare ( 3 );
-%	\end{lstlisting}
-%	\caption{Two identical fragments with only differences in locations of the square brackets.
-All 7 lines are reported by Simian if \small\texttt{-balanceSquareBrackets+} \normalsize is enabled.
-If not, the clone pairs is reported as \newline (MagicSquare.java [3,8], MagicSquare2.java [5,10]).}
-%	\label{fig:two_frags}
-%\end{figure*}
-%
-%\begin{table*}
-%	\caption{Simian's \texttt{-balanceSquareBrackets+} (\texttt{-bsb+}) is observed to have unpredictable behaviours when running against big datasets.
-$\textrm{\textit{CP}}_2$ means the reported clone(s) do not contain lines having dislocated brackets ($L_b$) (i.e.
-$\textrm{\textit{CP}}_2 = \textrm{\textit{CP}}_1 - L_b$).}
-%	\label{tab:summary}
-%	\centering
-%	\small\begin{tabular}{l|p{6cm}|c|c|c}
-%		\hline 
-%		\multirow{2}{*}{\textbf{Project 1}} & \multirow{2}{*}{\textbf{Project 2}} & \textbf{Dislocated} & \multirow{2}{*}{\textbf{-bsb+}} & \textbf{Clones pair} \\ 
-%		& & \textbf{brackets?} & & \textbf{reported} \\
-%		\hline
-%		\hline
-%		\multicolumn{5}{l}{\textit{Only run Simian against the pair}} \\
-%		\hline
-%		MagicSquare.java & MagicSquare\_exact\_copy.java & no & 0,1 & $\textrm{\textit{CP}}_1$ \\
-%		MagicSquare.java & MagicSquare2.java & yes & 0 & $\textrm{\textit{CP}}_2$ \\ 
-%		MagicSquare.java & MagicSquare2.java & yes & 1 & $\textrm{\textit{CP}}_1$ \\
-%		\hline
-%		%\hline
-%		%\multicolumn{5}{c}{\textit{Only run Simian against the pair}} \\
-%		%\hline
-%		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 0 & $\textrm{\textit{CP}}_3$ \\ 
-%		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 1 & $\textrm{\textit{CP}}_3$ \\ 
-%		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 0 & $\textrm{\textit{CP}}_4$ \\ 
-%		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 1 & $\textrm{\textit{CP}}_4$ \\ 
-%		\hline 
-%		\hline
-%		\multicolumn{5}{l}{\textit{Run Simian against the complete stackoverflow data and the project}} \\
-%		\hline
-%		stackoverflow/4298836\_0.java & Qualitas/aoisrc281/../ExprModule.java & no & 0 & $\textrm{\textit{CP}}_3$ \\ 
-%		\cellcolor{red!10}stackoverflow/4298836\_0.java & \cellcolor{red!10}Qualitas/aoisrc281/../ExprModule.java & \cellcolor{red!10}no & \cellcolor{red!10}1 & \cellcolor{red!10}-- \\ 
-%		\hline
-%		stackoverflow/4533682\_1.java & Qualitas/cobertura-1/../TouchCollector.java & no & 0 & $\textrm{\textit{CP}}_4$ \\ 
-%		\cellcolor{red!10}stackoverflow/4533682\_1.java & \cellcolor{red!10}Qualitas/cobertura-1/../TouchCollector.java & \cellcolor{red!10}no & \cellcolor{red!10}1 & \cellcolor{red!10}-- \\
-%		\hline 
-%	\end{tabular} 
-%\end{table*}
+\begin{table}[]
+	\centering
+	\caption{31 external clones found in Stack Overflow posts}
+	\label{tab:ext_clones}
+	\begin{tabular}{l|r|r}
+		\hline
+		Type        & FOSS & Web \\ \hline
+		StackOverflow only     & 1    & 1   \\
+		StackOverflow + Qualitas & 15   & 14  \\ \hline
+	\end{tabular}
+\end{table}
+
+We found 31 clone pairs which either one of the clones or both of them are found to be a copy of code snippet from somewhere else besides Qualitas project.
+This compliments the findings of inter clones between software projects \cite{Svajlenko2014} by showing that clones can also be copied over different websites on the Internet.
+There are 15 clone pairs that are originated from programming websites.
+For example, we found a clone of code snippet to convert numbers into words which is copied from \url{http://www.rgagnon.com/javadetails/java-0426.html}.
+Both Stack Overflow and \textit{Compiere} project source code contain attribution to the original source.
+Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from \url{http://mrl.nyu.edu/~perlin/noise/}.
+This code is used in both Stack Overflow and \textit{AoI} project with attribution.
+The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
+However, there are 4 clone pairs that are cloned from \textit{JUnit} to both Stack Overflow and \textit{Eclipse} and 12 pairs cloned from other Java projects outside Qualitas corpus.
+They are originated from \textit{zxing} projects, Apache projects (ant, jasper), Java packages (\texttt{java.util}, \texttt{javax.servlet}, JUnit, and \texttt{org.bouncycastle.crypto} project.
 

### 2017-01-22 cloneoverflow-latex/cloneoverflow.tex
Added heatmap of licenses
Updated the paper.

@@
 \usepackage{cleveref}
+\usepackage{subcaption}
 
@@
 The data dump is in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts.
-We are interested in code snippets embedded in posts which are pieces of code located between \texttt{<code></code>} tags.
-We filtered the snippets with two filtering criteria.
-First, we ignore snippets that are less than 6 lines since they are usually not considered as clones by clone detection research \cite{something}.
-Second, we are only interested in code snippets from posts that are marked as \textbf{accepted answer}.
-Posts on Stack Overflow are marked accepted by the questions' posters if the solutions in the posts solve their problems.
-We choose them because they have high chance to be reused than snippets in questions and other answers.
+We are interested in code snippets embedded in posts which are located between \texttt{<code></code>} tags.
+A Stack Overflow thread contains a post of question and several posts of answers.
+Every answer has voting score from users.
+An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem.
+We collect Java code snippets using two criteria.
+First, we are only interested in code snippets with at least six lines.
+Snippets which are smaller than six lines are usually spurious clones \cite{Bellon2007}.
+Second, we are only interested in code snippets in accepted answer.
+We choose snippets in accept answers because they have proofs that they actually solve the problems.
+Moreover, they are always displayed just below the questions which makes them attractive to be reused than snippets in other answers.
 Each snippet is extracted from the dump using regular expressions and saved to a file using its post ID as the file's name.
@@
 			\hline
+			\hline
+			Total & 96 & 0 & 396 & 31 & \textbf{523} & -- & -- & -- & 9502 & 107 & 2520 & \textbf{12099} & -- & -- & -- & \textbf{12622} & -- & -- & -- \\ 
+			\hline
 		\end{tabular} 
@@
 
+\begin{figure*}
+	\minipage{0.32\textwidth}
+	\includegraphics[width=\linewidth]{heatmap_a}
+	\caption*{(1) category A}\label{fig:heatmap_a}
+	\endminipage\hspace{0.3cm}
+	\minipage{0.32\textwidth}
+	\includegraphics[width=\linewidth]{heatmap_b}
+	\caption*{(2) category B}\label{fig:heatmap_b}
+	\endminipage\hfill
+	\minipage{0.32\textwidth}%
+	\includegraphics[width=\linewidth]{heatmap_c}
+	\caption*{(3) category C}\label{fig:heatmap_c}
+	\endminipage
+	\caption{Licensing between Stack Overflow code snippets and Qualitas Java file of 523 true online clone pairs}
+\end{figure*}
+
 In our study, we reveal another possible situation of software licensing issue caused by code cloning to Stack Overflow.
@@
 \section{Related Work}
+
+Data on Stack Overflow can be exploited to support developers in several ways.
+Seahawk is an eclipse plug-in that can search and recommend relevant code snippets from Stack Overflow \cite{Ponzanelli2013}.
+Similarly, Prompter, ...
+\cite{Ponzanelli2014}.
+
 \begin{itemize}
@@
 		\item Developers' behaviours on Stack Overlow \cite{Wang2013_StackOverflow, Movshovitz-Attias2013}
+		\item Discuss \cite{Treude2016,Ahmed2015}
 	\end{itemize}
@@
 	\item Software licensing
+	\item Outdated code \cite{Xia2014}
 	\begin{itemize}

### 2017-01-22 cloneoverflow-latex/cloneoverflow.tex
substantially improved the Related Work section.

@@
 %Conference
-\conferenceinfo{MSR '17}{May 20--21, 2017, Buenos Aires, Argentina}
+\conferenceinfo{ESEC/FSE 2017}{September 4--8, 2017, Paderborn, Germany}
 
@@
 Security is also among the main concerns when code is copied from online source.
-A study finds that \FIXME{add this} \cite{Acar2016}.
+A study by Acar et al.~shows that Stack Overflow helps developers to solve Android programming problems more quickly than other resources.
+However, it gives less secure code than books and the official Android documentation \cite{Acar2016}.
 
@@
 /* Code in Stack Overflow #22315734 */                    /* WritableComparator.java (2016-09-26) */
-1 public int compare (byte[] b1,int s1,int l1,              1 public int compare(byte[] b1,int s1,int l1,
-2                     byte[] b2,int s2,int l2) {            2                    byte[] b2,int s2,int l2) {
-3   try {                                                   3   try {
-4     buffer.reset(b1,s1,l1); /* parse key1 */              4     buffer.reset(b1,s1,l1); /* parse key1 */
-5     key1.readFields(buffer);                              5     key1.readFields(buffer);
-6     buffer.reset(b2,s2,l2); /* parse key2 */              6     buffer.reset(b2,s2,l2); /* parse key2 */
-7     key2.readFields(buffer);                              7     key2.readFields(buffer);
-8   } catch (IOException e) {                               8     buffer.reset(null,0,0); /* clean up reference */
-9     throw new RuntimeException(e);                        9   } catch (IOException e) {
-10   }                                                      10    throw new RuntimeException(e);
-11   return compare(key1,key2); /* compare them */          11  }
-12 }                                                        12  return compare(key1, key2); /* compare them */
-                                                            13 }
+public int compare (byte[] b1,int s1,int l1,              public int compare(byte[] b1,int s1,int l1,
+                    byte[] b2,int s2,int l2) {                               byte[] b2,int s2,int l2) {
+  try {                                                     try {
+    buffer.reset(b1,s1,l1); /* parse key1 */                  buffer.reset(b1,s1,l1); /* parse key1 */
+    key1.readFields(buffer);                                  key1.readFields(buffer);
+    buffer.reset(b2,s2,l2); /* parse key2 */                  buffer.reset(b2,s2,l2); /* parse key2 */
+    key2.readFields(buffer);                                  key2.readFields(buffer);
+  } catch (IOException e) {                                   buffer.reset(null,0,0); /* clean up reference */
+    throw new RuntimeException(e);                          } catch (IOException e) {
+  }                                                           throw new RuntimeException(e);
+  return compare(key1,key2); /* compare them */             }
+}                                                           return compare(key1, key2); /* compare them */
+                                                          }
 \end{lstlisting}
@@
 \newline
-\textbf{RQ2 (classification of online code clones):} \textit{What are the reasons of creating online code clones?} We categorise online clones into seven groups according to our clone classification scheme.
+\textbf{RQ2 (reasons for creating online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven groups according to our classification scheme.
 %so we can differentiate and understand the motivation of cloning.
@@
 
-\subsubsection{Clone Candidate Filtering Using Agreement}
+\subsubsection{Prioritise Clone Candidates Using Agreement}
 Usually a number of clones detected between two large-scale datasets  can be huge.
 In our study, there are totally 266,837,480 clone pairs reported.
-It is infeasible for human to manually validate all of them.
-One can do sampling of clones from this huge clone pair set.
-However, they may end up having most of them false positive clones.
+It is almost infeasible for human to manually validate them all.
+One can do a random sampling of clones.
+However, they may end up having most of them being false positive clones.
 Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish.
@@
 
-\subsection{Clone detectors' parameter tuning}
+\subsection{Clone Detector's Parameter Tuning}
 We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
@@
 
-\section{Results and discussion}
+\section{Results and Discussion}
 
@@
 We also look at the license of each clone and observe a possibility of licensing violation because of cloning.
-\subsection{RQ1: Online code clones}
+\subsection{RQ1: Online Code Clones}
 
@@
 
+\begin{table}
+	\centering
+	\caption{The number of online clone pair condidates (mutually exclusive) after using clone agreement}
+	\label{tab:online_clone_pairs}
+	\small
+	\begin{tabular}{l|r}
+		\hline
+		Setting & No.~of clone pairs \\ 
+		\hline 
+		\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  \\
+		\multirow{1}{*}{\textit{ok-match(0.7)}}    & 29,099 \\
+		\multirow{1}{*}{\textit{Simian$_{df}$}}    & 871    \\
+		\multirow{1}{*}{\textit{NiCad$_{df}$}}     & 168    \\ 
+		\hline
+		Total                                      & 32,399 \\ 
+		\hline
+	\end{tabular} 
+\end{table}
+
 The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} configurations are presented in \Cref{tab:raw_stats}.
 Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments.
-These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones of array initialisation.
+These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
 Hence, they were removed from Simian's clone reports before the analysis.
@@
 
-%\begin{table*}[h]
-%	\centering
-%	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
-%	\label{tab:raw_stats}
-%%	\resizebox{\columnwidth}{!}{%
-%	\small
-%		\begin{tabular}{l|r|r|r|r|r|r|r|r|r|r|r|r}
-%			\hline
-%			\multirow{3}{*}{Statistics} 
-%			& \multicolumn{3}{c|}{Simian$_{df}$} 
-%			& \multicolumn{3}{c|}{Simian$_{\textrm{\textit{EvCl}}}$}
-%			& \multicolumn{3}{c|}{NiCad$_{df}$} 
-%			& \multicolumn{3}{c}{NiCad$_{\textrm{\textit{EvCl}}}$} \\ \cline{2-13} 
-%			& \multicolumn{3}{c|}{1406 fragments} 
-%			& \multicolumn{3}{c|}{1360 fragments}  
-%			& \multicolumn{3}{c|}{1197 fragments} 
-%			& \multicolumn{3}{c}{12884 fragments} \\ \cline{2-13}
-%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ 
-%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$
-%			& $C_{\mathrm{pairs}}$ & $C_{\mathrm{SLOC}}$ & $C_{\mathrm{\%}}$ \\ 
-%			\hline
-%			Total & 54790 & -- & -- 		& 59936722 & --	& -- 		& 127305 	& -- & -- 	& 206718663 & -- & -- \\
-%			Mean & 52 & 7.45 & 28\% 		& 44104 & 4.81 & 29\% 		& 106 & 9.54 & 25\% 	& 16046 & 5.31 & 21\% \\
-%			Std Dev. & 147 & 3.22 & 23\% 	& 1040483 & 1.20 & 19\% 	& 209 & 3.10 & 18\% 	& 21890 & 1.92 & 16\% \\
-%			Max  & 1020 & 49.00 & 94\% 		& 38223637 & 18.00 & 89\% 	& 2100 & 39.00 & 81\% 	& 442655 & 50.00 & 93\% \\
-%			Min  & 1 & 5.00 & 1\% 			& 1 & 4.00 & 2\% 			& 1 & 7.00 & 2\% 		& 1 & 3.00 & 1\% \\
-%			Median  & 3 & 7.00 & 21\% 		& 24 & 5.00 & 25\% 			& 20 & 8.00 & 19\% 		& 8003 & 5.00 & 16\% \\
-%			Mode  & 1 & 7.00 & 33\% 		& 1 & 4.00 & 50\% 			& 1 & 8.00 & 67\% 		& 1 & 4.00 & 33\% \\
-%			\hline
-%		\end{tabular} %
-%%	}
-%\end{table*}
-
-%\begin{table*}
-%	\centering
-%	\caption{109 Qualitas projects (new versions retrieved on 2016-09-27)}
-%	\label{t:new_and_old}
-%%	\resizebox{\columnwidth}{!}{%
-%	\small
-%		\begin{tabular}{l|r|r|c|c|p{3cm}|p{3cm}}
-%			\hline 
-%			Projects & Old version & New versions & Latest change & CVS & License & Notes \\
-%			\hline
-%			antlr4 & 4.0 & 4.5.4 & 25/09/2016 & git & BSD & \\
-%			apache-ant & 1.8.4 & 1.10.0 & 09/04/2016 & git & Apache2.0 & \\
-%			argouml & 0.34 & 0.35.4 & 11/01/2015 	& svn & Eclipse  1.0 & \\
-%			artofillusion & 2.8.1 & 3.0.2 & 27/08/2016 & svn & GPL 2.0 & \\
-%			aspectj & 1.6.9 & 1.8.9 & 12/05/2016 & git & Eclipse   1.0 & \\
-%			axion & 1.0-M2 & - & 08/03/2013 & - & Proprietary (BSD/Apache-style) & \\
-%			batik & 1.7 & 1.9.0 & 11/05/2016 & svn & Apache , v.2.0 & \\
-%			c-jdbc & 2.0.2 & - & 16/09/2005 & - & LGPL 2.1 & \\
-%			castor & 1.3.1 & 1.4.2 & 17/08/2016 & git & Apache 2.0 & \\
-%			cayenne & 3.0.1 & 4.0.M4 &  26/09/2016 & git & Apache 2.0 & \\
-%			checkstyle & 5.1 & 7.2  & 23/09/2016 & git & LGPL 2.1 \& Apache 2.0 & \textit{Cli, Logging and Beanutils} packages are from the Apache Commons project. \\
-%			cobertura & 1.9.4.1 & 2.1.2 & 01/06/2016 & git & GPL 2.0  & \\
-%			colt & 1.2.0 & - & 09/09/2014 & - & Proprietary (CERN) & Found multithreaded v. \\
-%			columba & 1.4 & - & 20/04/2007 & - & Mozilla   1.1  & \\
-%			commons-collections & 3.2.1 & 4.2 & 12/09/2016 & svn & Apache 2.0 & \\
-%			compiere & 330 & - & - & - & GPL 2.0 & No longer OSS \\
-%			db-derby & 10.6.1.0 & 10.12.1 & 13/08/2016 & svn & Apache 2.0 & \\
-%			displaytag & 1.2 & 2.0 & 17/08/2014 & svn & MIT  & \\
-%			drawswf & 1.2.9 & - & 02/04/2013 & - & GPL 2.0 & \\
-%			drjava & 20100913-r5387 & ??? & 03/09/2014 & svn & BSD  & Build to see version? \\
-%			exoportal & ??? & ??? &  & git & LGPL 3.0 \& proprietary & Too many new projects \\
-%			emma & 2.0.5312 & 2.0.5312 & 09/05/2013  & - & Common   1.0 & \\
-%			findbugs & 1.3.9 & 3.0.1 & 06/03/2015 & - & LGPL 2.0 & \\
-%			fit-java & 1.1 & - & 04/06/2013 & - & GPL 2.0 & \\
-%			fitlibrary & 20100806 & ??? & 29/07/2014 & git & GPL 2.0 & \\
-%			freecol & 0.10.7 & 0.11.6 & 26/09/2016 & git & GPL 2.0 &  \\
-%			freecs & 1.3.20100406 & - & 22/04/2013 & - & GPL 3.0 &   \\
-%			freemind & 0.9.0 & 1.0.0 & 16/08/2016 & git & GPL 2.0+ &  \\
-%			galleon & 2.3.0 & 2.5.6 & 29/04/2013 & - & GPL 2.0 & \\
-%			ganttproject & 2.0.9 & 2.8.1 & 16/08/2016 & git & GPL 3.0 &  \\
-%			geotools & 2.7-M3 & 16 & 27/09/2016 & git & LGPL 2.0 & \\
-%			hadoop & 1.0.0 & 3.0.0-alpha2 & 26/09/2016 & git & Apache 2.0 & \\
-%			heritrix & 1.14.4 & - & 05/06/2013 & - & LGPL 2.1 & \\
-%			hibernate & 4.2.2 & 5.2.3 & 22/09/2016 & git & LGPL 2.1+ & \\
-%			hsqldb & 2.0.0 & 2.3.4 & 13/09/2016 & svn & BSD  & \\
-%			htmlunit & 2.8 & 2.24 & 26/09/2016 & svn & Apache 2.0 & \\
-%			ireport & 3.7.5 & - & 28/05/2014 & - & Affero LGPL 3.0 & \\
-%			itext & 5.0.3 & 5.5.9 & 27/09/2016 & git & Affero LGPL 3.0 & \\
-%			informa & 0.7.0-alpha2 & - & 07/11/2008 & - & LGPL 2.1 \& Apache Software 1.1 & \\
-%			ivatagroupware & 0.11.3 & - & 27/02/2013 & - & GPL 2.0 & \\
-%			jfin\_datemath & R1\_0\_1 & - & 25/04/2013 & - & GPL 2.0 & \\
-%			joggplayer & 114s & - &  15/04/2013 & - & GPL 2.0 & \\
-%			jag & 6.1 & 6.2 & 08/04/2013  & - & GPL 2.0 \& BSD  & BSD  is for libraries. \\
-%			james & 2.2.0 & 2.3.2.1 & 14/08/2015 & - & Apache 2.0 & \\
-%			jasml & 0.10 & - & 08/03/2013 & - & Apache Software  & \\
-%			jasperreports & 3.7.4 & 6.3.1 & 27/09/2016 & git & LGPL 3.0 &  \\
-%			javacc & 5.0.0 & 7.0.0 & 15/08/2016 & svn & Proprietary (Sun) & \\
-%			jboss (wildfly) & 5.1.0.GA & 11.0.0.Alpha1 & 27/09/2016 & git & LGPL 2.1 & Renamed to Wildfly. \\
-%			jchempaint & 3.0.1 & 3.4 & 01/09/2016 & git & LGPL 2.1+ &  \\
-%			jedit & 4.3.2 & 5.3.1 & 20/09/2016 & svn & GPL 2.0 &  \\
-%			jena & 2.6.3 & 3.1.1 & 16/09/2016 & git & Apache 2.0 & \\
-%			jext & 5.0 & - & 18/08/2004 & - & GPL 2.0 &  \\
-%			jfreechart & 1.0.13 & 1.5.0 & 29/08/2016 & git & LGPL 2.0 &   \\
-%			jgraph & 5.13.0.0 & 3.6.0.0 & 07/09/2016 & git & Proprietary (mxGraph) & \\
-%			jgraphpad & 5.10.0.2 & - & 10/11/2006 & - & GPL   \& LGPL (derivatives) & \\
-%			jgrapht & 0.8.1 & 1.0.1 & 23/09/2016 & git & LGPL 2.1 \& Eclipse  1.0 & \\
-%			jgroups & 2.10.0.GA & 4.0.0 & 26/09/2016 & git & Apache 2.0 & \\
-%			jmoney & 0.4.4 & ??? & 27/12/2015 & git & GPL 2.0 &  \\
-%			jparse & 0.96 & - & 29/07/2004 & - & LGPL 2.1 & \\
-%			jpf & 1.5.1 & ??? & 13/01/2012 & - & Apache 2.0 & \\
-%			junit & 4.11 & 4.12 & 04/12/2014 & git & Eclipse  1.0 & \\
-%			shiftone-jrat & 0.6 & 1-beta-1 & 17/11/2007 & svn & LGPL 2.0 &  \\
-%			vuze & 4812 & 5730 & 23/09/2016 & svn & GPL 2.0 & \\
-%			\hline
-%		\end{tabular} %
-%%	}
-%\end{table*}
-
 \subsubsection{Agreed clone pairs}
@@
 		Simian          & NiCad             & good-match & ok-match \\
-		%\hline
-		%Settings & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ & Simian$_{\mathrm{\textit{default}}}$ & Simian$_{\mathrm{\textit{EvCl}}}$ \\ % & Simian$_{\mathrm{\textit{cloplag}}}$ \\
-		\hline
-		\textit{df} & \textit{df} & 10 	& 9062 \\ 
+		\hline
+		\textit{df}     & \textit{df}       & 10 	     & 9,062     \\ 
 		\textit{df}     & \textit{EvCl}     & 26 	     & 1017     \\ 
 		\textit{EvCl} 	& \textit{df} 	    & 10 	     & 88       \\
-		\textit{EvCl} 	& \textit{EvCl} 	& 2228 & 19777 \\ 
-		\hline
-		\multicolumn{2}{l|}{Total} & 2274 & 29944 \\
-		\hline
-		\multicolumn{2}{l|}{Total (unique)} & 2261 &  29091 \\
+		\textit{EvCl} 	& \textit{EvCl}     & 2,228      & 19,777    \\ 
+		\hline
+		\multicolumn{2}{l|}{Total}          & 2,274      & 29,944    \\
+		\hline
+		\multicolumn{2}{l|}{Total (unique)} & 2,261      & 29,099    \\
 		\hline
@@
 		\hline
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67570 & 2546 & 871 \\ %140 + 1482 + 926
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67,570 & 2,546 & 871 \\ %140 + 1482 + 926
 		\hline
@@
 %		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229176  & 450 & 168 \\
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229,176  & 450 & 168 \\
 		\hline
@@
 
-\subsection{RQ2: Classifications of online code clones}
+\subsection{RQ2: Reasons for Creating Online Code Clones}
 
@@
 
-We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand.
+This is an important question underpinning the motivation of creating online code clones.
+Due to an absent of clone oracle of the two data sets, we resort to manual investigation to validate the clone pair candidates as either true or false positives.
+At the same time, we select a reason that stimulates a creation of each online clone pair.
+%We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand.
 We started by studying the 8 patterns of cloning from Kapser et al.
@@
 	\end{lstlisting}
-	\caption{Outdated code fragment on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains several modifications.}
+	\caption{Outdated code fragment on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains heavy modifications.}
 	\label{fig:hibernate_outdated_code}
@@
 
-Data on Stack Overflow can be exploited to support developers in several ways.
-Seahawk is an eclipse plug-in that can search and recommend relevant code snippets from Stack Overflow \cite{Ponzanelli2013}.
-Similarly, Prompter, ...
-\cite{Ponzanelli2014}.
-
-\begin{itemize}
-	\item Stack Overflow
-	\begin{itemize}
-		\item Code example \cite{Nasehi2012}
-		\item Search for code in Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014}
-		\item Stack Overflow to help developers \cite{Ponzanelli2013, Ponzanelli2014}
-		\item Improving Stack Oveflow \cite{Diamantopoulos2015, Wang2014, Bosu2013}
-		\item Developers' behaviours on Stack Overlow \cite{Wang2013_StackOverflow, Movshovitz-Attias2013}
-		\item Discuss \cite{Treude2016,Ahmed2015}
-	\end{itemize}
-	\item Code clones 
-		\begin{itemize}
-			\item Definition: Baxter et al. \cite{Baxter1998}
-			\item Comparison of clone detectors: \cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}
-			\item NiCad \cite{Roy2008,Cordy}
-			\item Simian \cite{simian}
-			\item Clone taxonomy \cite{Kapser2003}
-			\item Clone evolution \cite{Pate2013,Mondal2011}
-			\item Comparing Quality Metrics for Cloned and non cloned Java Methods: A Large Scale Empirical Study \cite{Saini2016}.
-		\end{itemize}
-	\item Agreement-based Clone Detection
-	\begin{itemize}
-		\item Bellon's framework \cite{Bellon2007}.
-		\item EvaClone \cite{Wang2013}
-		\item Hybrid \cite{Funaro2010}
-	\end{itemize}
-	\item Software licensing
-	\item Outdated code \cite{Xia2014}
-	\begin{itemize}
-		\item Code siblings \cite{German2009}, Ninka -- Automatic indification of SW license \cite{German2010}, Evolution of SW licensing \cite{DiPenta2010}
-	\end{itemize}
-
-\end{itemize}
+Stack Overflow is a gold mine for software engineering research.
+Its rich and developer-driven data are valuable for software development.
+The data set has been put to use in several previous studies.
+In terms of developer-assisting tools, Seahawk is an eclipse plug-in that can search and recommend relevant code snippets from Stack Overflow \cite{Ponzanelli2013}.
+A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} is also an Eclipse plug-in for recommending relevant discussion from Stack Overflow but with improved algorithms.
+Several code search systems are proposed using whole or partial data from Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014}.
+Treude et al.~try to do something \cite{Treude2016}.
+
+Another aspect is knowledge extraction from Stack Overflow.
+Nasehi et al.~studied what makes a good code example by analysing answers from Stack Overflow \cite{Nasehi2012}.
+Studies to understand developers' behaviours on Stack Overlow include \cite{Wang2013_StackOverflow, Movshovitz-Attias2013,Rosen2016,Subramanian2013}.
+A study of copy and paste behaviour has been done by Ahmed et al.~\cite{Ahmed2015}. Some studies aim to improve Stack Overflow systems \cite{Diamantopoulos2015, Wang2014, Bosu2013}.
+
+Code clone detection is a long-standing research topic in software engineering.
+Whether clones are good or bad for software is still controversial \cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
+However, by only knowing how many code clones residing in software and how they evolve \cite{Pate2013,Mondal2011} can provide several insights into the systems.
+Clone detection has its several applications such as software plagiarism detection~\cite{Prechelt2002},
+source code provenance~\cite{Davies2013}, and software licensing conflicts~\cite{German2009}.
+
+Two code fragments are clones if they are similar similar enough according to a given definition of similarity \cite{Bellon2007}.
+Given an open interpretation of ``definition of similarity'', there are various clone detection tools and their siblings, code plagiarism detectors, invented.
+Some tools
+use string comparison techniques such as Simian \cite{simian}.
+NiCad \cite{Roy2008,Cordy} also exploits Longest Common Subsequence (LCS) to discover clones after applying code pretty-printing using TXL \cite{Cordy2006}.
+Many tools do not work on original source code directly but transform them into an
+intermediate representation such as tokens and apply similarity
+measurement on them. These tools include SourcererCC~\cite{Sajnani2016}, CCFinder~\cite{Kamiya2002},
+CP-Miner~\cite{Li2006}, iClones~\cite{Gode2009} and a few more~\cite{Burrows2007, Smith2009, Duric2012, Prechelt2002, Schleimer2003}. 
+To find more challenging clones such as type-3 clones, structural similarity of clones is needed.
+This structural similarity can be discovered by comparing AST as found in CloneDR~\cite{Baxter1998} and Deckard~\cite{Jiang2007a} or by using program dependence
+graphs~\cite{Krinke2001,Komondoor2001}.
+
+Kapser et al.~studied clones in Linux file system subsystems and create patterns of code cloning: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}.
+Our study partially adapted the online code clone classification scheme from their patterns.
+
+There are a few studies comparing different clone detection techniques on various data sets \cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}.
+Since clone detectors are different in their detection approaches, they behave differently and report different clones.
+Some researchers exploit different behaviours of clone detectors by finding agreement from them to obtain highly-confident clones \cite{Bellon2007}.
+Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are highly possible to be true clones than the ones reported by only a single tool \cite{Wang2013,Ragkhitwetsagul2016_ssbse,Funaro2010}.
+These studies also report that sensitivities of the tools' parameter settings have strong effects to the results \cite{Ragkhitwetsagul2016}.
+
+Software licensing is crucial for open source and industrial software development.
+Di Penta et al.~study an evolution of software licensing in six FOSS and found that licensing statements change over time \cite{DiPenta2010}.
+German et al.~performed an empirical study of code siblings, code clones among different systems coming from the same source, using CCFinderX clone detector.
+They found that licensing conflicts can occur between clone siblings.
+Ninka is a tool to automate identification of software license~\cite{German2010} from program source code.
+We use Ninka to analyse software license from Stack Overflow fragments and Qualitas projects.
+
+Reusing of third-party source code is very normal in software development.
+Xia et al.~\cite{Xia2014} show that a large number of open source systems reuse outdated third-party libraries of famous open source projects.
+Using outdated code give detrimental effects since they introduce vulnerability into the software.
+Our study discovers similar findings but in the context of reusing outdated code from Stack Overflow.
 

### 2017-01-22 cloneoverflow-latex/cloneoverflow.tex
Improved the paper.

@@
 	\alignauthor
-	$^1$Chaiyong Ragkhitwetsagul, $^1$Jens Krinke, $^2$Giuseppe Bianco \\
+	$^1$Chaiyong Ragkhitwetsagul, $^1$Jens Krinke, $^1$Matheus Paixao, $^2$Giuseppe Bianco \\
 	\affaddr{$^1$University College London, London, UK}\\
@@
 It allows programmers to ask questions and give answers to programming problems.
-The website has found to be useful for software development and also valuable for educational purposes \cite{x}.
+The website has found to be useful for software development \cite{Ponzanelli2013,Ponzanelli2014,Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for educational purposes \cite{Nasehi2012}.
 On Stack Overflow, each conversation contains a question and answer(s).
@@
 Several authors state that clones lead to bug propagations and software maintenance issues \cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial \cite{Saini2016,Kapser2006}.
-Code cloning can also have side effects of violating software licenses.
+
+Code cloning can also have side effects of violating software licenses and software vulnerabilities.
 Carelessly cloning code from one project to another project with different license may cause software licensing violation \cite{German2009}.
+This also happens within the context of online Q\&A website such as Stack Overflow.
+An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow have potential of violating software licenses.
 Security is also among the main concerns when code is copied from online source.
@@
 
+% INTERESTING NEWS: http://www.theverge.com/tldr/2016/5/4/11593084/dont-get-busted-copying-code-from-stack-overflow
+
 In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones.
-We call them \textbf{online code clones}.
+We call them \textbf{online code clones} (or sometimes only call \textbf{clones} for brevity).
 There are four ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium; and (4) code is cloned from an external source to both a software project and Stack Overflow.
-Online code clones can similarly lead to a problem of bug propagation as classical code clones.
-Unfortunately, they are more difficult to locate and fix since the search space from online corpora is larger and no longer confined in a local repository.
-\FIXME{Add another motivation of security of reusing code from Stack Overflow}.
-
-A motivating example of problems caused by online code clones can be found in a Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}.
-In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
-The snippet shows how Hadoop implements \textit{compare} method in its \textit{WritableComparator} class.
-The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of Hadoop.
-We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, added in the latest version after \verb|key2.readFields(buffer);|.
-The added line is intended for cleaning up the reference in \verb|buffer| variable.
-While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged and outdated.
-This example shows that there can be inconsistencies between online code clones and its original.
-%Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
-This is an emerging and challenging problem.
-Since studies in this area are still limited, we aim to gain more insight of the problem in this study.
-%We are interested to gain more insights of online code clone in this study.
+Online code clones can similarly lead to a problem of bug propagation, licensing violation, and software vulnerability as classical code clones.
+Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.
 
@@
 
+A motivating example of problems caused by online code clones can be found in the Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}.
+In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
+The snippet shows how Hadoop implements \textit{compare} method in its \textit{WritableComparator} class.
+The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of Hadoop.
+We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, is added in the latest version after \verb|key2.readFields(buffer);|.
+The added line is intended for cleaning up the reference in \verb|buffer| variable.
+While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged and outdated.
+This example shows that there can be inconsistencies between online code clones and its original resulting in outdated code on Stack Overflow.
+%Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
+%This is an emerging and challenging problem.
+Since studies in this area are still limited, we aim to gain more insight of the problem in this study.
+%We are interested to gain more insights of online code clone in this study.
+
 This paper makes the following  primary contributions:
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,450 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.
+We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,448 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.
 
@@
 
-\FIXME{Can we say the inspected clone set is another benchmark?}
+\vspace{0.5ex}%
+\noindent\textbf{3.~Online code clone oracle:} The 3,448 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.
 
@@
 \newline
-\textbf{RQ2 (reasons for creating online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven groups according to our classification scheme.
+\textbf{RQ2 (reasons for creating online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven categories according to our clone pattern classification scheme.
+The patterns of online cloning give more insights to why online code clones are created.
 %so we can differentiate and understand the motivation of cloning.
-Clones can be copied from open source projects to Stack Overflow as examples, or vice versa.
+%Clones can be copied from open source projects to Stack Overflow as examples, or vice versa.
 Furthermore, they can be cloned from a third-party location or clones containing boiler-plate code, and code stubs generated by IDE.
 \newline
-\textbf{RQ3 (effects of online code clones):} \textit{what are the effects derived from online code clones?
-can they be harmful to software development?} Is there observable problems caused by clones between Stack Overflow and open source projects?
+\newline
+\textbf{RQ3 (effects of online code clones):} \textit{what are the effects from reusing online code clones?
+can they be harmful to software development?} %Is there observable problems caused by clones between Stack Overflow and open source projects?
+We are interested to investigate the problem of software licensing and reusing outdated code.
 
@@
 	\centering
-	\includegraphics[width=0.9\linewidth]{exp_framework}
+	\includegraphics[width=0.8\linewidth]{exp_framework}
 	\caption{Experimental framework}
@@
 To answer the three research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}.
-We process two datasets, Stack Overflow and open source projects from Qualitas corpus.
+We process two datasets, Stack Overflow and 111 open source projects from Qualitas corpus.
 Java code fragments are extracted from Stack Overflow posts using regular expressions.
-We pre-process Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection.
+We prepare Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection.
 Then, we deploy two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets.
@@
 
-We then convert the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combine them into a single file.
+We then convert the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combine the 111 reports into a single GCF file.
 GCF provides a common format for clones which enable us to reuse the same scripts to analyse clone reports from both Simian and NiCad.
@@
 Simian do not provide an option to detect inter clones between two locations.
-Hence the Simian GCF clone report is pruned to contain only inter clone pairs between Stack Overflow and Qualitas project.
-In this step, all intra clone pairs within Stack Overflow and open source projects are removed.
-NiCad can detect inter clones so no pruning is needed.
-We do not have an oracle of clones in 111 Qualitas projects so we need a manual investigation to validate the reported clone candidates.
+Hence the Simian GCF clone report is pruned to contain only inter clone pairs between Stack Overflow and Qualitas projects.
+In this step, all intra clone pairs within either Stack Overflow or Qualitas are removed.
+NiCad can solely detects inter clones so no pruning is needed.
+We do not have an oracle of clones between the two data sets so we need a manual investigation to validate the reported clone candidates.
 However, the large amount of clone pairs hinder us from looking at all of them.
@@
 Instead, we select clone pair candidates by relying on agreement of clone detectors.
-If a clone pairs is similarly reported by multiple tools, we have higher confidence that it is a real clone pair.
+If a clone pair is similarly reported by multiple tools, we have higher confidence that it is a real clone pair.
 To achieve this, clone pairs from the two clone detectors are pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
 This step generates \textbf{agreed clone pairs}.
-They are pairs with high confidence to be true clone pairs since they obtain agreement from both tools.
+They are pairs with high confidence to be true clones since they obtain agreement from both tools.
 Then, pairs reported by Simian and NiCad that do not find agreement are \textbf{disagreed clone pairs}.
 The disagreed clone pairs are clones with less confidence than agreed ones.
-Finally, agreed and disagreed clone pairs are sampled and looked at manually by the first author.
-
-In the manual inspection process, we classify clones into seven categories according to information observed from code comments and text in Stack Overflow answer.
-This process takes approximately a months until we successfully investigate 3,450 clone pairs.
-Clone pairs that are classified as boiler-plate code or IDE-generated are not very interesting and are discarded for further analysis.
-We further compare licensing information of 523 remaining clone pairs for possibility of software licensing violations.
-Moreover, we look forward through history of each clone from its project's versioning systems.
-With this method we can observe whether there is any changes made to a clone after it has been copied.
+Finally, agreed and disagreed clone pairs have been looked at manually by the first and the third author.
+
+In the manual inspection process, we classify clones into seven categories according to information observed from code comments and natural text in Stack Overflow answer.
+This process takes approximately a months until we successfully investigate 3,448 clone pairs.
+Clone pairs that are classified as false clones, boiler-plate code, or IDE-generated are not very interesting and are discarded for further analysis.
+We compare licensing information of 523 remaining clone pairs for possibility of software licensing violations.
+Moreover, we look forward through history of each clone from its git repository.
+With this method, we discover \textbf{outdated code}, code that changes are made to them after it has been copied to Stack Overflow.
 %hence resulting in outdated clones on Stack Overflow.
@@
 \subsubsection{Datasets}
-\begin{table}
-	\centering
-	\caption{Stack Overflow and Qualitas datasets}
-	\label{tab:datasets}
-	\small
-	\begin{tabular}{l|r|r}
-		\hline 
-		Dataset & No. of files & SLOC \\
-		\hline
-		Stack Overflow & 144,075 & 2,347,269 \\ 
-		\hline 
-		Qualitas &  160,937 & 19,086,883 \\ 
-		\hline 
-	\end{tabular} 
-\end{table}
 
@@
 A Stack Overflow thread contains a post of question and several posts of answers.
-Every answer has voting score from users.
+Every answer has voting score from its users.
 An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem.
@@
 Snippets which are smaller than six lines are usually spurious clones \cite{Bellon2007}.
-Second, we are only interested in code snippets in accepted answer.
-We choose snippets in accept answers because they have proofs that they actually solve the problems.
+Second, we are only interested in code snippets in accepted answers.
+We choose snippets in accept answers because they actually solved the problems in the questions and has a check mark sign on them to notify other users.
 Moreover, they are always displayed just below the questions which makes them attractive to be reused than snippets in other answers.
@@
 
-\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus}.
+\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus} for this study.
 It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
@@
 The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow.
-Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code due to its license \cite{QualitasCorpus} so it is removed from the study.
-This results in totally 111 projects analysed in the study.
+Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code due to its licensing limitation \cite{QualitasCorpus} so it is removed from the study.
+This results in total of 111 projects analysed in the study.
 As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code.
@@
 
+\begin{table}
+	\centering
+	\caption{Stack Overflow and Qualitas datasets}
+	\label{tab:datasets}
+	\small
+	\begin{tabular}{l|r|r}
+		\hline 
+		Dataset & No. of files & SLOC \\
+		\hline
+		Stack Overflow & 144,075 & 2,347,269 \\ 
+		\hline 
+		Qualitas &  160,937 & 19,086,883 \\ 
+		\hline 
+	\end{tabular} 
+\end{table}
+
 \subsubsection{Clone Detectors}
 There is a number of restrictions in terms of choosing clone detection tools for this study.
-Firstly, they have to support Java.
-Secondly, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods.
+First, they have to support Java.
+Second, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods.
 Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable.
-Thirdly, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
+Third, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
 We have tried running 5 state-of-the-art clone detectors including Simian \cite{simian}, NiCad \cite{Cordy,Roy2008}, CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a} against Stack Overflow and Qualitas datasets.
-CCFinder, iClones, and DECKARD failed to successfully detect clones between 144,075 Stack Overflow code snippets and 109 Qualitas projects.
+CCFinder, iClones, and DECKARD failed to report clones between 144,075 Stack Overflow code snippets and 111 Qualitas projects.
 All of them reported execution errors after running for couple of hours.
@@
 Simian and NiCad completed the detection with success.
-We found that both of them are also flexible enough to handle million-SLOC code corpus with method or class incompleteness.
-So, we decided to use both of them.
+We found that both of them are also flexible enough to handle code with incomplete methods or classes.
+%So, we decided to use both of them.
 
@@
 It is a command-line tool which enables us to automate the detection.
-Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect clones of type 1 and type 2.
+Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect literal clones (type-1) and parameterised clones (type-2).
 \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity.
-It can detect clones up to type 3 and is used in several clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
-It utilises TXL for parsing and pretty-printing source code.
-It also provide code normalisation by variable renaming and code abstraction.
+It can detect clones of type-1, 2 up to type-3 (clones with added/removed/relocated/changed statements) and is also used in several empirical clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
+It utilises TXL \cite{Cordy2006} for parsing and pretty-printing source code.
+It also provide code normalisation by variable renaming and abstraction.
 We use a variant of NiCad called \textit{nicadcross}.
@@
 \subsubsection{Prioritise Clone Candidates Using Agreement}
-Usually a number of clones detected between two large-scale datasets  can be huge.
+A number of clones detected in large-scale datasets can be huge.
 In our study, there are totally 266,837,480 clone pairs reported.
@@
 One can do a random sampling of clones.
-However, they may end up having most of them being false positive clones.
-Therefore, we adopted an idea of clone agreement which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish.
+However, due to a very high number of false positives, they may end up looking at most of the false clones.
+Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish.
 Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}.
-By using this agreed clone detection approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
-To find an agreement of two clone pairs, we resort to the approach of clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
-Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair.
+By using this agreement-based approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
+To find an agreement between two clone pairs report by two different tools, we use clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
+Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair with a confident value between 0 and 1.
 A good-match clone pair has stronger agreement than an ok-match pair.
-We follow the same following definitions of good- and ok-match introduced in the original paper.
-
-%good and ok-match clone pairs are defined as follows. 
-A clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}, i.e.
-\textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}).
-We can define \textit{overlap} and \textit{contained} value of two clone pairs as
+We follow the following definitions of good- and ok-match introduced in the original paper.
+
+\vspace{0.5ex}
+Given that a clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}, i.e.~\textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}), we can define \textit{overlap} and \textit{contained} value of two clone pairs as
 %\squeezeup
@@
 
-\textit{good-value} of two clone pairs is then defined as
+\noindent\textit{good-value} of two clone pairs is then defined as
 %\squeezeup
@@
 
-\textit{ok-value} is defined as
+\noindent\textit{ok-value} is defined as
 %\squeezeup
@@
 We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
-However, considering the size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools.
+However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools.
 Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{df}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}).
 The details of the two configurations are described in \Cref{t:param_tuning}.
-Having two clone detectors multiplied by two chosen configurations, we look for agreements in four possible pair-wise combinations: Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
+Having two clone detectors with two chosen configurations each, we look for Bellon's good and ok-match in four possible pair-wise combinations: Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
 
@@
 We follow the experimental framework and detect clones between Stack Overflow and Qualitas corpus using the two selected clone detectors.
-To answer RQ1 and RQ2 together, we compute statistics of clone discovered by the tools and the true clone pairs confirmed by manual investigation.
-In the manual investigation process, we proposed an online clone classification scheme derived from common patterns found in online code clones.
-For RQ3, we look at the true positive clone pairs carefully and compare them to their latest versions.
-This is to see if the cloned code is still up-to-date.
-We also look at the license of each clone and observe a possibility of licensing violation because of cloning.
+To answer RQ1, we compute statistics of clone discovered by the tools.
+To answer RQ2, we manually investigated online clone pair candidates and categorise them using our patterns of online code cloning.
+The patterns are derived from Kapser et al.~\cite{Kapser2003} augmented by common patterns found in our data set.
+For RQ3, we look at the true positive clone pairs and check if they are still up-to-date.
+We also look at the license of each clone and observe a possibility of licensing violation.
+
 \subsection{RQ1: Online Code Clones}
@@
 	\centering
-	\caption{The number of online clone pair condidates (mutually exclusive) after using clone agreement}
+	\caption{The number of online clone pair condidates (mutually exclusive) found after filtering by clone agreement}
 	\label{tab:online_clone_pairs}
@@
 		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  \\
-		\multirow{1}{*}{\textit{ok-match(0.7)}}    & 29,099 \\
-		\multirow{1}{*}{\textit{Simian$_{df}$}}    & 871    \\
-		\multirow{1}{*}{\textit{NiCad$_{df}$}}     & 168    \\ 
+		%\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  \\
+		%\multirow{1}{*}{\textit{ok-match(0.7)}}    & 29,099 \\
+		\multirow{1}{*}{\textit{agreed clone pairs}}        & 31,360 \\
+		%\multirow{1}{*}{\textit{Simian$_{df}$}}       & 871    \\
+		%\multirow{1}{*}{\textit{NiCad$_{df}$}}        & 168    \\ 
+		\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
@@
 Hence, they were removed from Simian's clone reports before the analysis.
-From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,406 reported by Simain$_{df}$ and 1,360 from Simain$_{\textrm{\textit{EvCl}}}$ respectively.
-NiCad$_{df}$ reports clones in 1,197 Stack Overflow code snippets, while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones in a larger number of 12,884 snippets  mainly due to its relaxed configurations.
-In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report an enormous number of clone pairs of 59,936,722 and 206,718,663 respectively.
-This is expected since EvaClone configurations prefer recall \cite{Wang2013}.
-The average clone size of Simian$_{df}$ is 7.45 lines which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.81.
-Similarly, NiCad$_{df}$ has an average clone size of 9.54 lines which is bigger than 5.31 reported by NiCad$_{\textrm{\textit{EvCl}}}$.
+From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by Simain$_{df}$ and 1,530 from Simain$_{\textrm{\textit{EvCl}}}$ respectively.
+NiCad$_{df}$ reports clones in 1,240 Stack Overflow code snippets, while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations.
+In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report a large number of clone pairs of 63,372,599 and 206,760,077 respectively.
+This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}.
+The average clone size of Simian$_{df}$ is 7.72 lines which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.79.
+Similarly, NiCad$_{df}$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by NiCad$_{\textrm{\textit{EvCl}}}$.
 We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones.
-The average percentage of Stack Overflow code snippets that are cloned according to Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 28\%, 29\%, 25\%, and 21\% accordingly.
+The average percentage of Stack Overflow code snippets that are cloned according to Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 29\%, 28\%, 25\%, and 21\% accordingly.
+
+As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of agreed clone pairs using good-match and ok-match between combination of Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is reduced to 31,360.
+The number of disagreed clone pairs after filtering is 1,039.
+The details are as follows.
 
@@
 Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.
-Similar to the original study, we select a threshold \textit{p} of 0.7 for both good and ok-match\cite{Bellon2007}.
+Similar to the original study, we select a threshold \textit{p} of 0.7 for both good and ok-match \cite{Bellon2007}.
 The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-We found that NiCad generates errors and stopped processing while it is analysing some Qualitas projects.
+We found that NiCad generates errors and stopped processing against some Qualitas projects.
 \FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ could not detect clones in 6 projects due to clustering errors.
-For NiCad$_{\textrm{\textit{EvCl}}}$, the tool generated renaming errors for 4 projects, and clustering errors for 13 projects.
-As a result, we did not have NiCad clone candidates in the agreed clone pairs for 6 and 27 projects with \textit{df} and \textit{EvCl} configurations respectively.
-This affected Simian clone candidates of the same projects to be removed from the agreed clone pairs as well since they could not have matching clone pairs.
+NiCad$_{\textrm{\textit{EvCl}}}$ generated renaming errors for 11 projects, and clustering errors for 16 projects.
+Hence, we did not have NiCad clones in the agreed clone pairs for these 6 (NiCad$_{\textrm{\textit{df}}}$) and 27 projects (NiCad$_{\textrm{\textit{EvCl}}}$).
+This makes Simian clones of the same projects to be removed from the agreed clone pairs as well since they could not have matching online clone pairs.
 
 The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}.
-There are 2,261 unique good-match pairs consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
+There are 2,274 good-match pairs (2,261 uniquely) consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
 According to the definition, ok-match clone pairs always subsume the good-match pairs.
@@
 	\small
-	\begin{tabular}{l|l|r|r}
-		\hline
-		\multicolumn{2}{c|}{Tool} & \multicolumn{2}{c}{No.~of clone pairs} \\
-		\hline
-		Simian          & NiCad             & good-match & ok-match \\
-		\hline
-		\textit{df}     & \textit{df}       & 10 	     & 9,062     \\ 
-		\textit{df}     & \textit{EvCl}     & 26 	     & 1017     \\ 
-		\textit{EvCl} 	& \textit{df} 	    & 10 	     & 88       \\
-		\textit{EvCl} 	& \textit{EvCl}     & 2,228      & 19,777    \\ 
-		\hline
-		\multicolumn{2}{l|}{Total}          & 2,274      & 29,944    \\
-		\hline
-		\multicolumn{2}{l|}{Total (unique)} & 2,261      & 29,099    \\
+	\begin{tabular}{l|l|r|r|r}
+		\hline
+		\multicolumn{2}{c|}{Tool} & \multicolumn{3}{c}{No.~of clone pairs}   \\
+		\hline
+		Simian          & NiCad             & good-match & ok-match & Total  \\
+		\hline
+		\textit{df}     & \textit{df}       & 10 	     & 9,062    & 9,072  \\ 
+		\textit{df}     & \textit{EvCl}     & 26 	     & 1017     & 1,043  \\ 
+		\textit{EvCl} 	& \textit{df} 	    & 10 	     & 88       & 98     \\
+		\textit{EvCl} 	& \textit{EvCl}     & 2,228      & 19,777   & 22,005 \\ 
+		\hline
+		\multicolumn{2}{l|}{Total}          & 2,274      & 29,944   & 32,218 \\
+		\hline
+		\multicolumn{2}{l|}{Total (unique)} & 2,261      & 29,099   & 31,360 \\
 		\hline
@@
 		\hline
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline reg.~expressions & 67,570 & 2,546 & 871 \\ %140 + 1482 + 926
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline \& reg.~expressions & \multirow{2}{*}{67,570} & \multirow{2}{*}{2,546} & \multirow{2}{*}{871} \\ %140 + 1482 + 926
 		\hline
@@
 %		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ & 229,176  & 450 & 168 \\
+		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ \newline (i.e.~UPI=0.2) & \multirow{2}{*}{229,176} & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
+		\hline
+		\multicolumn{2}{l|}{Total} & 296,746 & 2,996 & 1,039 \\
 		\hline
@@
 	\centering
-	\caption{Seven categories of online code clones}
+	\caption{Seven patterns of online code cloning}
 	\label{tab:classification_scheme}
@@
 
-Stack Overflow is a gold mine for software engineering research.
-Its rich and developer-driven data are valuable for software development.
-The data set has been put to use in several previous studies.
-In terms of developer-assisting tools, Seahawk is an eclipse plug-in that can search and recommend relevant code snippets from Stack Overflow \cite{Ponzanelli2013}.
-A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} is also an Eclipse plug-in for recommending relevant discussion from Stack Overflow but with improved algorithms.
-Several code search systems are proposed using whole or partial data from Stack Overflow \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014}.
-Treude et al.~try to do something \cite{Treude2016}.
+\textbf{Stack Overflow} is a gold mine for software engineering research.
+Its rich and developer-driven data are invaluable.
+Since posts on Stack Overflow may contain code snippets embedded within natural language text, they become a huge database for source code and code-relevant information.
+The Stack Overflow data set has been put to use in several previous studies.
+In terms of developer-assisting tools, Seahawk is an Eclipse plug-in that searches and recommends relevant code snippets from Stack Overflow \cite{Ponzanelli2013}.
+A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} achieves the same goal but with improved algorithms.
+The code snippets on Stack Overflow are mostly examples or solutions to programming problems.
+Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
+Furthermore, Treude et al.~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation \cite{Treude2016}.
 
@@
 Nasehi et al.~studied what makes a good code example by analysing answers from Stack Overflow \cite{Nasehi2012}.
-Studies to understand developers' behaviours on Stack Overlow include \cite{Wang2013_StackOverflow, Movshovitz-Attias2013,Rosen2016,Subramanian2013}.
-A study of copy and paste behaviour has been done by Ahmed et al.~\cite{Ahmed2015}. Some studies aim to improve Stack Overflow systems \cite{Diamantopoulos2015, Wang2014, Bosu2013}.
-
-Code clone detection is a long-standing research topic in software engineering.
+Similarly, Yang et al.~\cite{Yang2016} analysed Stack Overflow snippets across various programming languages and observed that code snippets in Python and Javascript are the most usable.
+Wang et al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic modelling to analyse questions and answers from Stack Overflow so that they can automatically categorise new questions.
+There are also studies trying to understand developers' behaviours on Stack Overflow, e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}, while some studies aim to improve Stack Overflow itself \cite{Diamantopoulos2015, Wang2014}.
+
+\textbf{Code clone detection} is a long-standing research topic in software engineering.
 Whether clones are good or bad for software is still controversial \cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
-However, by only knowing how many code clones residing in software and how they evolve \cite{Pate2013,Mondal2011} can provide several insights into the systems.
-Clone detection has its several applications such as software plagiarism detection~\cite{Prechelt2002},
+However, by only knowing how many code clones residing in software and how they evolve \cite{Pate2013,Mondal2011} can provide several valuable insights into the software systems.
+Besides clones, clone detection has its several applications such as software plagiarism detection~\cite{Prechelt2002},
 source code provenance~\cite{Davies2013}, and software licensing conflicts~\cite{German2009}.
 
-Two code fragments are clones if they are similar similar enough according to a given definition of similarity \cite{Bellon2007}.
-Given an open interpretation of ``definition of similarity'', there are various clone detection tools and their siblings, code plagiarism detectors, invented.
+Two code fragments are clones if they are similar enough according to a given definition of similarity \cite{Bellon2007}.
+Given an open interpretation of ``definition of similarity'', there are various clone detection tools and their siblings, code plagiarism detectors, invented based on plethora of different code similarity measurements \cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}.
 Some tools
 use string comparison techniques such as Simian \cite{simian}.
-NiCad \cite{Roy2008,Cordy} also exploits Longest Common Subsequence (LCS) to discover clones after applying code pretty-printing using TXL \cite{Cordy2006}.
+NiCad \cite{Roy2008,Cordy} also exploits Longest Common Subsequence (LCS) string similarity measure to discover clones after applying code pretty-printing using TXL \cite{Cordy2006}.
 Many tools do not work on original source code directly but transform them into an
@@
 CP-Miner~\cite{Li2006}, iClones~\cite{Gode2009} and a few more~\cite{Burrows2007, Smith2009, Duric2012, Prechelt2002, Schleimer2003}. 
-To find more challenging clones such as type-3 clones, structural similarity of clones is needed.
+To find more challenging clones such as clones with added/deleted/reordered statements or equivalent loop and conditional statements (i.e.~type-3 clones), structural similarity of clones is needed.
 This structural similarity can be discovered by comparing AST as found in CloneDR~\cite{Baxter1998} and Deckard~\cite{Jiang2007a} or by using program dependence
@@
 
-Kapser et al.~studied clones in Linux file system subsystems and create patterns of code cloning: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}.
-Our study partially adapted the online code clone classification scheme from their patterns.
-
-There are a few studies comparing different clone detection techniques on various data sets \cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}.
-Since clone detectors are different in their detection approaches, they behave differently and report different clones.
-Some researchers exploit different behaviours of clone detectors by finding agreement from them to obtain highly-confident clones \cite{Bellon2007}.
-Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are highly possible to be true clones than the ones reported by only a single tool \cite{Wang2013,Ragkhitwetsagul2016_ssbse,Funaro2010}.
-These studies also report that sensitivities of the tools' parameter settings have strong effects to the results \cite{Ragkhitwetsagul2016}.
-
-Software licensing is crucial for open source and industrial software development.
+Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}.
+Our study partially adapted their patterns for our online code clone classification scheme.
+
+\textbf{Clone agreement} is useful in when clone oracle is absent.
+Since clone detectors are different in their detection approaches, they may behave differently and report different clones even on the same data set.
+Some researchers exploit these different behaviours of clone detectors by finding their agreement and obtain highly-confident clones \cite{Bellon2007,Wang2013}.
+Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are highly potential to be true clones than the ones reported by only a single tool \cite{Wang2013,cr2016ssbse,Funaro2010}.
+These studies also report that sensitivities of the tools' parameter settings have strong effects to the results \cite{Wang2013,cr2016ssbse}.
+
+\textbf{Software licensing} is crucial for open source and industrial software development.
 Di Penta et al.~study an evolution of software licensing in six FOSS and found that licensing statements change over time \cite{DiPenta2010}.
-German et al.~performed an empirical study of code siblings, code clones among different systems coming from the same source, using CCFinderX clone detector.
-They found that licensing conflicts can occur between clone siblings.
-Ninka is a tool to automate identification of software license~\cite{German2010} from program source code.
+German et al.~\cite{German2009} performed an empirical study of code siblings (code clones among different systems coming from the same source) and found that licensing conflicts can occur between the clone siblings.
+Later, German et al.~\cite{German2010} created Ninka, a tool to automate identification of software license from program source code.
 We use Ninka to analyse software license from Stack Overflow fragments and Qualitas projects.
 
-Reusing of third-party source code is very normal in software development.
-Xia et al.~\cite{Xia2014} show that a large number of open source systems reuse outdated third-party libraries of famous open source projects.
-Using outdated code give detrimental effects since they introduce vulnerability into the software.
-Our study discovers similar findings but in the context of reusing outdated code from Stack Overflow.
+\textbf{Reusing of outdated third-party source code} occurs in software development.
+Xia et al.~\cite{Xia2014} show that a large number of open source systems reuse outdated third-party libraries from famous open source projects.
+Using outdated code give detrimental effects to the software since they may introduce vulnerabilities.
+Our study discovers similar findings in the context of outdated code from Stack Overflow.
+
+The work that is closely similar to us is a study by An et al.~\cite{An2017}.
+The authors investigated clones between 399 Android apps and Stack Overflow posts.
+They found 1,226 code snippets which were reused from 68 Android apps.
+They also observed that there are 1,219 cases of potential license violations.
+However, the authors rely on the timestamp to judge whether the code has been copied from/to Stack Overflow along with confirmations from six developers.
+Instead of Android apps, we investigated clones between Stack Overflow and 111 open source projects.
+Our results confirm their findings that there are clones from software projects to Stack Overflow with potential licensing violations.
+In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,448 clone pairs.
+We discovered 96 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
+By comparing the clones to their latest versions in the software, we found that 58 code fragments on Stack Overflow are outdated and harmful for reuse.
 

### 2017-01-23 cloneoverflow-latex/cloneoverflow.tex
Updated throughout the paper

@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,448 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.
+We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,450 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.
 
@@
 \vspace{0.5ex}%
-\noindent\textbf{3.~Online code clone oracle:} The 3,448 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.
+\noindent\textbf{3.~Online code clone oracle:} The 3,450 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.
 
@@
 However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools.
-Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{df}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{EvCl}).
+Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}).
 The details of the two configurations are described in \Cref{t:param_tuning}.
-Having two clone detectors with two chosen configurations each, we look for Bellon's good and ok-match in four possible pair-wise combinations: Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
+Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we look for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.
 
@@
 	\hline
-	Simian$_{\textrm{\textit{EvCl}}}$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
-	\hline 
-	NiCad$_{\textrm{\textit{df}}}$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
-	\hline
-	NiCad$_{\textrm{\textit{EvCl}}}$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
+	$S_E$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
+	\hline 
+	$N_D$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
+	\hline
+	$N_E$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
 	\hline 
@@
 	\centering
-	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian and NiCad}
+	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
 	\label{tab:raw_stats}
@@
 			\hline
-			Stats & Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$ & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\
+			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
 			\hline
@@
 	\centering
-	\caption{The number of online clone pair condidates (mutually exclusive) found after filtering by clone agreement}
+	\caption{The number of online clone pair condidates (mutually exclusive) found after filtering by clone agreement and \texttt{equals()}}
 	\label{tab:online_clone_pairs}
 	\small
-	\begin{tabular}{l|r}
-		\hline
-		Setting & No.~of clone pairs \\ 
-		\hline 
-		%\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  \\
-		%\multirow{1}{*}{\textit{ok-match(0.7)}}    & 29,099 \\
-		\multirow{1}{*}{\textit{agreed clone pairs}}        & 31,360 \\
-		%\multirow{1}{*}{\textit{Simian$_{df}$}}       & 871    \\
-		%\multirow{1}{*}{\textit{NiCad$_{df}$}}        & 168    \\ 
-		\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\hline
-		Total                                               & 32,399 \\ 
+	\begin{tabular}{l|r|r|r}
+		\hline
+		Clone set & C$_{\textrm{\textit{pairs}}}$ & \texttt{equals()} & Manual \\ 
+		\hline 
+		\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  & 9 & 2,252 \\
+		\multirow{1}{*}{\textit{ok-match(0.7)}}    & 26,838 & 9,122 & 200 \\
+		%\multirow{1}{*}{\textit{agreed clone pairs}}        & 29,099 \\
+		\multirow{1}{*}{$S_D$}       & 17,801 & 16,930 & 871 \\
+		\multirow{1}{*}{$N_D$}       & 168 & 41 & 127 \\ 
+		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+		\hline
+		Total                                               & 47,068 & 26,102 & 3,450 \\ 
 		\hline
@@
 
-The clone statistics obtained from running Simian and NiCad with \textit{df} and \textit{EvCl} configurations are presented in \Cref{tab:raw_stats}.
+The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}.
 Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments.
@@
 Hence, they were removed from Simian's clone reports before the analysis.
-From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by Simain$_{df}$ and 1,530 from Simain$_{\textrm{\textit{EvCl}}}$ respectively.
-NiCad$_{df}$ reports clones in 1,240 Stack Overflow code snippets, while NiCad$_{\textrm{\textit{EvCl}}}$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations.
-In terms of number of clone pairs, Simian$_{\textrm{\textit{EvCl}}}$ and NiCad$_{\textrm{\textit{EvCl}}}$ report a large number of clone pairs of 63,372,599 and 206,760,077 respectively.
+From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,530 from $S_E$ respectively.
+$N_D$ reports clones in 1,240 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations.
+In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,372,599 and 206,760,077 respectively.
 This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}.
-The average clone size of Simian$_{df}$ is 7.72 lines which is bigger than its Simian$_{\textrm{\textit{EvCl}}}$ counterpart of 4.79.
-Similarly, NiCad$_{df}$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by NiCad$_{\textrm{\textit{EvCl}}}$.
+The average clone size of$S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79.
+Similarly, $N_D$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by $N_E$.
 We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones.
-The average percentage of Stack Overflow code snippets that are cloned according to Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is 29\%, 28\%, 25\%, and 21\% accordingly.
-
-As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of agreed clone pairs using good-match and ok-match between combination of Simian$_{df}$, Simian$_{\textrm{\textit{EvCl}}}$, NiCad$_{df}$, and NiCad$_{\textrm{\textit{EvCl}}}$ is reduced to 31,360.
-The number of disagreed clone pairs after filtering is 1,039.
+The average percentage of Stack Overflow code snippets that are cloned according to$S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
+
+As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of agreed clone pairs using good-match is reduced to 2,261 while ok-match is reduced to 26,838.
+The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 168 for Simian and NiCad respectively.
 The details are as follows.
@@
 		\hline
-		& Simian$_{\textrm{\textit{df}}}$ & Simian$_{\textrm{\textit{EvCl}}}$  & NiCad$_{\textrm{\textit{df}}}$ & NiCad$_{\textrm{\textit{EvCl}}}$ \\ 
+		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
 		\hline
 		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
-		\textit{Clust.~fail} & -- & -- & 6 & 16 \\
-		\textit{Renm.~fail} & -- &  -- & -- & 11 \\
+		\textit{Clustering fail} & -- & -- & 6 & 16 \\
+		\textit{Renaming fail} & -- &  -- & -- & 11 \\
 		\hline
@@
 We found that NiCad generates errors and stopped processing against some Qualitas projects.
-\FIXME{Report the errors to NiCad creator.}  NiCad$_{\textrm{\textit{df}}}$ could not detect clones in 6 projects due to clustering errors.
-NiCad$_{\textrm{\textit{EvCl}}}$ generated renaming errors for 11 projects, and clustering errors for 16 projects.
-Hence, we did not have NiCad clones in the agreed clone pairs for these 6 (NiCad$_{\textrm{\textit{df}}}$) and 27 projects (NiCad$_{\textrm{\textit{EvCl}}}$).
+\FIXME{Report the errors to NiCad creator.}  $N_D$ could not detect clones in 6 projects due to clustering errors.
+$N_E$ generated renaming errors for 11 projects, and clustering errors for 16 projects.
+Hence, we did not have NiCad clones in the agreed clone pairs for these 6 ($N_D$) and 27 projects ($N_E$).
 This makes Simian clones of the same projects to be removed from the agreed clone pairs as well since they could not have matching online clone pairs.
 
-The distributions of good-match clone pairs between four combinations of \textit{df} and \textit{EvCl} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}.
-There are 2,274 good-match pairs (2,261 uniquely) consisting of 10 pairs from Simian$_{df}$--NiCad$_{df}$, 26 pairs from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 10 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 2,228 pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
+The distributions of good-match clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}.
+There are 2,274 good-match pairs (2,261 uniquely) consisting of 10 pairs from$S_DN_D$, 26 pairs from$S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$.
 According to the definition, ok-match clone pairs always subsume the good-match pairs.
-As a result, there are 29,944 ok-match clone pairs.
-9,062 pairs are from Simian$_{df}$--NiCad$_{df}$, 1,017 pairs are from Simian$_{df}$--NiCad$_{\textrm{\textit{EvCl}}}$, 88 are pairs from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{df}$, and 19,777 pairs are from Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$.
+There are 26,838 ok-match clone pairs (excluding the 2,261 good-match pairs).
+9,052 pairs are from $S_DN_D$, 991 pairs are from $S_DN_E$, 78 are pairs from $S_EN_D$, and 17,549 pairs are from $S_EN_E$.
 Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.
+If we remove duplicates, the number of unique ok-match pairs is 26,838.
 
@@
 	\centering
-	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{df} and \textit{EvCl} settings}
+	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{D} and \textit{E} settings}
 	\label{t_agreed_good_clone_pairs}
 	\small
-	\begin{tabular}{l|l|r|r|r}
-		\hline
-		\multicolumn{2}{c|}{Tool} & \multicolumn{3}{c}{No.~of clone pairs}   \\
-		\hline
-		Simian          & NiCad             & good-match & ok-match & Total  \\
-		\hline
-		\textit{df}     & \textit{df}       & 10 	     & 9,062    & 9,072  \\ 
-		\textit{df}     & \textit{EvCl}     & 26 	     & 1017     & 1,043  \\ 
-		\textit{EvCl} 	& \textit{df} 	    & 10 	     & 88       & 98     \\
-		\textit{EvCl} 	& \textit{EvCl}     & 2,228      & 19,777   & 22,005 \\ 
-		\hline
-		\multicolumn{2}{l|}{Total}          & 2,274      & 29,944   & 32,218 \\
-		\hline
-		\multicolumn{2}{l|}{Total (unique)} & 2,261      & 29,099   & 31,360 \\
+	\begin{tabular}{l|r|r}
+		\hline
+		\multirow{2}{*}{Setting} & \multicolumn{2}{c}{No.~of clone pairs}   \\ \cline{2-3}
+		& good-match & ok-match \\
+		\hline
+		$S_DN_D$  & 10 & 9,052    \\ 
+		$S_DN_E$  & 26 & 991     \\ 
+		$S_EN_D$  & 10 & 78       \\
+		$S_EN_E$  & 2,228 & 17,549   \\ 
+		\hline
+		Total & 2,274 & 27,670   \\
+		\hline
+		Unique & 2,261 & 26,838  \\
 		\hline
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{venn4_pairs_good_pt1+2}
+		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3}
 		\caption{Distributions of good-match(0.7) pairs}
@@
 		\centering
-		\includegraphics[width=0.8\linewidth]{venn4_pairs_ok_pt1+2+3}
+		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3}
 		\caption{Distributions of ok-match(0.7) pairs}
@@
 They are also clone pairs in projects with NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl} configurations) that are missing from the agreed clone pairs.
-With the four configuration combinations, we decided to investigate only two, Simian$_{df}$, and NiCad$_{df}$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively).
+With the four configuration combinations, we decided to investigate only two,$S_D$, and $N_D$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively).
 They also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.
@@
 % 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
-For Simian$_{df}$, there are 20,348 clone pairs after using 10--line filter.
+For $S_D$, there are 20,348 clone pairs after using 10--line filter.
 Out of 20,348 pairs, 2,546 of them are ok-match pairs which are discarded.
-We filtered the results further by removing false positives such as similar \verb|equals()|, \verb|hashCode()| methods, getters and setters out by using regular expressions.
+We filtered the results further by removing false positives such as similar \verb|hashCode()| methods, getters and setters out by using regular expressions.
 We managed to reduce the number to 871 clone pairs remaining for manual investigation.
 % 7062 + 22187 + 6755 =  36004 %
-For NiCad$_{df}$, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well.
+For $N_D$, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well.
 We thus filter NiCad's clones by using similarity threshold.
@@
 	\centering
-	\caption{Statistics of disagreed clone pairs (Simian$_{df}$ and NiCad$_{df}$).}
+	\caption{No.~of disagreed clone pairs ($S_D$ and $N_D$).}
 	\label{tab:classification_indv_stats}
@@
 	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|p{2.4cm}|r|r|r}
-		\hline 
-		Tool & Filter & C$_{\textrm{\textit{pairs}}}$ & good/ok & remaining \\ 
+	\begin{tabular}{l|p{1.5cm}|r|r|r|r}
+		\hline 
+		Tool & Filter & \multicolumn{1}{c|}{Original} & \multicolumn{1}{c|}{Filtered} & \multicolumn{1}{c|}{good/ok} & \multicolumn{1}{c}{remaining} \\ 
 		%\hline 
@@
 		\hline
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & $minline \geq 10$ \newline \& reg.~expressions & \multirow{2}{*}{67,570} & \multirow{2}{*}{2,546} & \multirow{2}{*}{871} \\ %140 + 1482 + 926
-		\hline
-%		\multirow{1}{*}{\textit{NiCad$_{df}$}-1} & 7040  & 226 & 6700 & 114 \\
-%		\multirow{1}{*}{\textit{NiCad$_{df}$}-2} & 22187  & 152 & 21990 & 45 \\
-		\multirow{1}{*}{\textit{NiCad$_{df}$}} & $similarity \geq 80\%$ \newline (i.e.~UPI=0.2) & \multirow{2}{*}{229,176} & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
-		\hline
-		\multicolumn{2}{l|}{Total} & 296,746 & 2,996 & 1,039 \\
-		\hline
+		\multirow{1}{*}{\textit{Simian$_{df}$}} & $line \geq 10$ \newline \& reg.~exp & \multirow{2}{*}{67,570} & \multirow{2}{*}{47,223}  & \multirow{2}{*}{2,546} & \multirow{2}{*}{17,801} \\ %140 + 1482 + 926
+		\hline
+%		\multirow{1}{*}{\textit{$N_D$}-1} & 7040  & 226 & 6700 & 114 \\
+%		\multirow{1}{*}{\textit{$N_D$}-2} & 22187  & 152 & 21990 & 45 \\
+		\multirow{1}{*}{\textit{$N_D$}} & $sim \geq 80\%$ \newline (UPI=0.2) & \multirow{2}{*}{229,176} & \multirow{2}{*}{228,558}  & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
+		\hline
+		%\multicolumn{2}{l|}{Total} & 296,746 & 20,966 & 2,996 & 1,039 \\
+		%\hline
 	\end{tabular} %
@@
 
-\subsection{RQ2: Reasons for Creating Online Code Clones}
+\subsection{RQ2: Patterns of Online Code Cloning}
 
@@
 	\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{|c|p{8cm}|}
-			\hline 
-			Cat. & Descriptions \\ 
-			\hline 
-			A & Cloned from Qualitas to Stack Overflow (Q $\rightarrow$ S). \\ 
-			\hline 
-			A' &Cloned from Stack Overflow to Qualitas (S $\rightarrow$ Q). \\ 
-			\hline 
-			B & Cloned from each other or from an external source \textit{X} (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
+		\begin{tabular}{|c|p{8.4cm}|}
+			\hline 
+			Patt. & Descriptions \\ 
+			\hline 
+			A & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
+			\hline 
+			A' &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
+			\hline 
+			B & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
 			\\ 
@@
 
-This is an important question underpinning the motivation of creating online code clones.
-Due to an absent of clone oracle of the two data sets, we resort to manual investigation to validate the clone pair candidates as either true or false positives.
+This is an important question underpinning the motivation of online code cloning.
+Why are they created and how?
+Due to an absence of clone oracle of the two data sets, we resort to manual investigation to validate the clone pair candidates as either true or false positives.
 At the same time, we select a reason that stimulates a creation of each online clone pair.
 %We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand.
-We started by studying the 8 patterns of cloning from Kapser et al.
-\cite{Kapser2006,Kapser2008}.
+
+We started by studying the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008}.
 We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments.
 This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study.
-Using Simian$_{df}$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size.
+Using$S_D$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size.
 We then picked the top 10 fragments from the 4 groups resulting in 34 Stack Overflow fragments chosen (there were some overlaps).
@@
 Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating.
-Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.
-We adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as category D, and added 6 new categories observed as common cloning patterns from the manual investigation.
-The seven categories ranging from A--F presented in \Cref{tab:classification_scheme}.
-Category A is a clone pair that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation or links in Stack Overflow post), and vice versa in category A'.
-Category B is a clone pair that is exactly identical or highly similar but without any attribution of copying.
-Category C is a clone pair that has information confirming of copying from the same external source.
-Category D is a clone pair that is either boiler-plate code (e.g.~\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.~GUI initialisation).
-Category E are clones created by inheriting the same super class or implementing the same interface.
+Clearly \textbf{Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.}
+
+We adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as category D, and added 6 new patterns observed as common cloning patterns from our preliminary investigation.
+The seven patterns ranging from A--F as presented in \Cref{tab:classification_scheme}.
+Pattern A is a cloning that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post).
+Pattern A' is the opposite of A.
+Pattern B is a cloning that is exactly identical or highly similar but without any attribution of copying.
+Pattern C is a cloning that has an evidence of copying from the same external source.
+Pattern D is either boiler-plate code (e.g.~\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.~GUI initialisation).
+Pattern E is inheritance of the same super class or implementation of the same interface.
 They usually share similar overriding methods.
-The last category, category F, is a false clone pair.
+The last pattern, F, is a false clone pair.
 They can be either accidentally similar (e.g.~similar try-catch statements) or similar after code normalisation process.
-Using this classification scheme, we consider clone pairs in category A, A', B, C as true positive, and clone pairs in category D, E, F as false positive.
-
-\subsubsection{Manual investigation of clone pair candidates}
-
-The first author who has been working on clone detection research for two years takes the role of an investigator performing manual investigation.
-Following the classification scheme, the investigator manually goes through each agreed clone pair, looks at the clones, and chooses the most appropriate category for the pair.
+Using this cloning pattern classification scheme, we consider clone pairs in created by pattern A, A', B, C as true positive, and clone pairs in pattern D, E, F as false positive.
+
+\subsubsection{Manual Investigation of Clone Candidates}
+
+The first author who has been working on clone detection research for two years takes the role of a main investigator performing manual investigation of all 3,450 clone pairs.
+The third author takes the role of a second investigator performing 10\% validation of the clone pairs judged by the main investigator.
+Following the cloning patterns, the main investigator manually goes through each agreed clone pair, looks at the clones, and chooses the most appropriate cloning pattern for the pair.
 A relevant and useful observation is also recorded for each clone pair.
@@
 For the ok-match clone pairs, we could not feasibly investigate all 23,868 pairs manually.
-According to the manual investigation of good-match pairs, we found that Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ produces a large number of 2,253 false positive results (accounts for 99.87\% of Simian$_{\textrm{\textit{EvCl}}}$--NiCad$_{\textrm{\textit{EvCl}}}$ clone pairs) due to its recall preference.
+According to the manual investigation of good-match pairs, we found that $S_EN_E$ produces a large number of 2,253 false positive results (accounts for 99.87\% of $S_EN_E$ clone pairs) due to its recall preference.
 We thus decided to leave this configuration out of the ok-match manual investigation.
@@
 
-\FIXME{Maybe remove?} We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying.
+%\FIXME{Maybe remove?} We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying.
 We thus checked the timestamp of each Java file in Qualitas project and compared it to their respective timestamp of Stack Overflow posts.
@@
 %\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvCl}}}$--NiCad$_{\mathrm{\textit{EvCl}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of Simian$_{df}$--NiCad$_{df}$, Simian$_{df}$--NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}$--NiCad$_{df}$.
+With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of$S_DN_D$,$S_D$--NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}N_D$.
 We had not done any investigation of good-match since there were no good-match pairs for these 3 agreements.
@@
 	\caption{Classification results of agreed and disagreed clone pairs.
-S$_u$ denotes a number of unique Stack Overflow snippets.
+SO$_u$ denotes a number of unique Stack Overflow snippets.
 Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
@@
 			\hline
-			Classificaiton & A & A' & B & C & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & S$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & S$_{u}$ & Q$_u$ & Q$_{up}$\\ 
+			Classificaiton & A & A' & B & C & \textbf{Sum} & SO$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & SO$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & SO$_{u}$ & Q$_u$ & Q$_{up}$\\ 
 			\hline 
@@
 			\hline 
-			\multirow{1}{*}{\textit{Simian$_{df}$}} & 79 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
-			\hline
-			\multirow{1}{*}{\textit{NiCad$_{df}$}} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
+			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
+			\hline
+			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
 			\hline
@@
 %\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
-\textbf{Disagreed clone pairs}: we performed a manual investigation and classification of 871 filtered clone pairs reported by Simian$_{df}$ and 168 by NiCad$_{df}$ in the same way as the agreed clone pairs.
+\textbf{Disagreed clone pairs}: we performed a manual investigation and classification of 871 filtered clone pairs reported by$S_D$ and 168 by $N_D$ in the same way as the agreed clone pairs.
 The results of investigation is reported in \Cref{tab:classification_good_o}.
-There are 432 true positive clone pairs found from Simian$_{df}$ consisting of 19 pairs in category A, 336 pairs in B, and 17 pairs in C.
-For NiCad$_{df}$, there are 36 true positive pairs consisting of 8 pairs in category A, 27 pairs in B, and 1 pair in C.
-The total number of true positive clone pairs is 523 as described in \Cref{tab:classification_true_pairs_summary}.
+There are 432 true positive clone pairs found from$S_D$ consisting of 19 pairs in category A, 336 pairs in B, and 17 pairs in C.
+For $N_D$, there are 36 true positive pairs consisting of 8 pairs in category A, 27 pairs in B, and 1 pair in C.
+The total number of true positive clone pairs is 523 as described in \Cref{tab:classification_good_o}.
 
 %\subsection{Summary of true online clone pairs}
-\begin{table}[H]
-	\centering
-	\caption{Numbers of true positive online clone pairs found by manual investigation}
-	\label{tab:classification_true_pairs_summary}
-	\small
-	\begin{tabular}{l|r|r|r|r|r}
-		\hline 
-		Tool & A & A' & B & C & Total \\
-		\hline
-		good-pairs & 1 & 0 & 4 & 3 & 8 \\
-		ok-pairs & 8 & 0 & 29 & 10 & 47 \\
-		Simian$_{df}$ pairs & 79 & 0 & 336 & 17 & 432 \\
-		NiCad$_{df}$ pairs & 8 & 0 & 27 & 1 & 36 \\
-		\hline 
-		Total & 96 & 0 & 396 & 31 & 523 \\
-		\hline
-	\end{tabular} 
-\end{table}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{Sankey_proj}
-	\caption{Relationships of 58 Stack Overflow clone pairs to their original projects. 55 are outdated and 3 are deleted (shown using (d) suffix).}
-	\label{fig:sankey}
-\end{figure}
+%\begin{table}[H]
+%	\centering
+%	\caption{Numbers of true positive online clone pairs found by manual investigation}
+%	\label{tab:classification_true_pairs_summary}
+%	\small
+%	\begin{tabular}{l|r|r|r|r|r}
+%		\hline 
+%		Tool & A & A' & B & C & Total \\
+%		\hline
+%		good-pairs & 1 & 0 & 4 & 3 & 8 \\
+%		ok-pairs & 8 & 0 & 29 & 10 & 47 \\
+%		Simian$_{df}$ pairs & 79 & 0 & 336 & 17 & 432 \\
+%		$N_D$ pairs & 8 & 0 & 27 & 1 & 36 \\
+%		\hline 
+%		Total & 96 & 0 & 396 & 31 & 523 \\
+%		\hline
+%	\end{tabular} 
+%\end{table}
 
@@
 
-\subsubsection{Outdated code clones}
+\subsubsection{Outdated Clones}
 Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated.
 This is a normal issue driving the development of clone detection.
-We need to locate clones to be able to update them according to their updated original code \cite{somewhere,somewhere_else}.
+We need to locate clones to be able to update them according to their updated original code \cite{Bellon2007}.
 However, in this situation, the clones are more pervasive on Stack Overflow posts and more difficult to detect due to its large scale and the mix of natural language and source code.
-Since code can be updated due to various possible reasons including bug fixing, this poses a problem if developers reuse a cloned code snippet from Stack Overflow without knowing that it is outdated.
+Since code can be updated due to various possible reasons, e.g.~bug fixing, this poses a problem if developers reuse a cloned code snippet from Stack Overflow without knowing that it is outdated.
 %They might also introduce the same unfixed bug(s) into the software.
@@
 
-To check if the discovered Stack Overflow clones are outdated, we focus on the 96 category-A clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_true_pairs_summary}).
+To check if the discovered Stack Overflow clones are outdated, we focus on the 96 pattern-A clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}).
 For each code snippet, we can track its origin from its Qualitas counterpart.
@@
 We also found outdated code which contains more disruptive changes.
-The code snippet in Stack Overflow Post 23520731 which is a copy of \textit{SchemaUpdate.java} in \textit{hibernate} has been heavily modified (as shown in \Cref{fig:hibernate_outdated_code}).
+The code snippet in Stack Overflow post 23520731 which is a copy of \textit{SchemaUpdate.java} in \textit{hibernate} has been heavily modified (as shown in \Cref{fig:hibernate_outdated_code}).
 Moreover, there is a code snippet in Stack Overflow post 3758110 which is a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring.
-It was deleted in commit 02a4473c62d8240837bec297f0a1f3cb67ef8a7b by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted and the latest version of Spring does not contain the Java file anymore.
+It was deleted in the commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted and the latest version of Spring does not contain the Java file anymore.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{outdated}
-	\caption{Findings from outdated code investigation of 96 category-A online clone pairs}
+	\includegraphics[width=0.8\linewidth]{outdated}
+	\caption{Findings from outdated code investigation of 96 pattern-A online clone pairs}
 	\label{fig:outdated}
@@
 
-\subsubsection{Software licensing violation}
+\subsubsection{Software Licensing Violation}
 Software licensing is a paramount factor in software development.
@@
 
-\subsubsection{Interesting finding: external clones}
+\subsubsection{Interesting Finding: External Clones}
 
@@
 Our results confirm their findings that there are clones from software projects to Stack Overflow with potential licensing violations.
-In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,448 clone pairs.
+In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,450 clone pairs.
 We discovered 96 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
@@
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{Sankey_proj}
+	\caption{Relationships of 58 Stack Overflow clone pairs to their original projects. 55 are outdated and 3 are deleted (shown using (d) suffix).}
+	\label{fig:sankey}
+\end{figure}
+
 %

### 2017-01-24 cloneoverflow-latex/cloneoverflow.tex
Updated throughout the paper (again)

@@
 
-\title{Are We Reusing Outdated Code from Stack Overflow?}
+\title{Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?}
 
@@
 Security is also among the main concerns when code is copied from online source.
-A study by Acar et al.~shows that Stack Overflow helps developers to solve Android programming problems more quickly than other resources.
-However, it gives less secure code than books and the official Android documentation \cite{Acar2016}.
+Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, gives less secure code than books and the official Android documentation \cite{Acar2016}.
+Additionally, outdated and vulnerable third-party libraries from famous open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
 
@@
 There are four ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium; and (4) code is cloned from an external source to both a software project and Stack Overflow.
-Online code clones can similarly lead to a problem of bug propagation, licensing violation, and software vulnerability as classical code clones.
-Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.
+\textbf{Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.} Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.
 
@@
 	\end{lstlisting}
-	\caption{The same code fragments, WritableComparator.java, on Stack Overflow post 22315734 and latest version in hadoop code base}
+	\caption{A motivating example of the same code fragments, WritableComparator.java. The one on Stack Overflow post 22315734 is outdated when compared to its latest version in Hadoop code base}
 	\label{fig:before-after}
@@
 
-A motivating example of problems caused by online code clones can be found in the Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}.
+A motivating example of outdated code in online code clones can be found in the a Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}.
 In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
@@
 The added line is intended for cleaning up the reference in \verb|buffer| variable.
-While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged and outdated.
-This example shows that there can be inconsistencies between online code clones and its original resulting in outdated code on Stack Overflow.
+While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged.
+This example shows that there can be inconsistencies between online code clones and its original.
+The code snippet on Stack Overflow can be outdated.
 %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
@@
 
-This paper makes the following  primary contributions:
+While a lot of research has focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and whether these example snippets are still up-to-date.
+
+To fill this gap, this paper makes the following  primary contributions:
 
@@
 \newline
-\textbf{RQ2 (reasons for creating online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven categories according to our clone pattern classification scheme.
-The patterns of online cloning give more insights to why online code clones are created.
+\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven categories according to our online code cloning pattern scheme.
+This gives us more insights to why online code clones are created.
 %so we can differentiate and understand the motivation of cloning.
@@
 \newline
-\textbf{RQ3 (effects of online code clones):} \textit{what are the effects from reusing online code clones?
-can they be harmful to software development?} %Is there observable problems caused by clones between Stack Overflow and open source projects?
-We are interested to investigate the problem of software licensing and reusing outdated code.
+\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We are interested in the correctness of Stack Overflow code examples since millions of users are potentially reusing them.
+%Is there observable problems caused by clones between Stack Overflow and open source projects?
+%We are interested to investigate the problem of outdated code and software licensing conflicts caused by online code clones.
+
+\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We would like to investigate whether online code clones can be legally harmful to software reusing them.
 
@@
 \subsection{Experimental Framework}
-To answer the three research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}.
+To answer the four research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}.
 We process two datasets, Stack Overflow and 111 open source projects from Qualitas corpus.
@@
 To find an agreement between two clone pairs report by two different tools, we use clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
-Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair with a confident value between 0 and 1.
-A good-match clone pair has stronger agreement than an ok-match pair.
+Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1.
+A \textit{good} clone pair has stronger agreement than an \textit{ok} pair.
 We follow the following definitions of good- and ok-match introduced in the original paper.
@@
 
-Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{good-match(p)} iff, for $p \in [0,1]$ holds 
+Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(p)} iff, for $p \in [0,1]$ holds 
 %\squeezeup
@@
 
-Using this good-match and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266-million candidate clone pairs for manual investigation.
-good-match pairs are the ones with the highest confident and ranked the first to be looked at, followed by ok-match pairs, and followed by clone pairs without agreement.
+Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266-million candidate clone pairs for manual investigation.
+\textit{good} pairs are the ones with the highest confident and ranked the first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.
 
@@
 
-\begin{table}
-	\centering
-	\caption{The number of online clone pair condidates (mutually exclusive) found after filtering by clone agreement and \texttt{equals()}}
+\begin{table*}
+	\centering
+	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering. The last column shows the number of true positive clone pairs after the manual investigation.}
 	\label{tab:online_clone_pairs}
 	\small
-	\begin{tabular}{l|r|r|r}
-		\hline
-		Clone set & C$_{\textrm{\textit{pairs}}}$ & \texttt{equals()} & Manual \\ 
-		\hline 
-		\multirow{1}{*}{\textit{good-match(0.7)}}  & 2,261  & 9 & 2,252 \\
-		\multirow{1}{*}{\textit{ok-match(0.7)}}    & 26,838 & 9,122 & 200 \\
+	\begin{tabular}{l|r|l|r|r|r|r}
+		\hline
+		Clone set & Original & Filter & Candidates & \texttt{equals()} & Manual & TP \\ 
+		\hline 
+		\multirow{1}{*}{\textit{good}} & --  & -- & 2,261  & 9 & 2,252 & 8 \\
+		\multirow{1}{*}{\textit{ok}} & --  & -- & 26,838 & 9,122 & 200 & 47 \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}        & 29,099 \\
-		\multirow{1}{*}{$S_D$}       & 17,801 & 16,930 & 871 \\
-		\multirow{1}{*}{$N_D$}       & 168 & 41 & 127 \\ 
+		\multirow{1}{*}{$S_D$} & 67,570 & $Line \geq 10$, RegEx, good/ok & 17,801 & 16,930 & 871 & 432 \\
+		\multirow{1}{*}{$N_D$} & 229,176 & $Sim \geq 80\%$, RegEx, good/ok & 168 & 41 & 127 & 36 \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total                                               & 47,068 & 26,102 & 3,450 \\ 
+		Total  & 296,746 & & 47,068 & 26,102 & 3,450 & 523 \\ 
 		\hline
 	\end{tabular} 
-\end{table}
+\end{table*}
 
@@
 
-As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of agreed clone pairs using good-match is reduced to 2,261 while ok-match is reduced to 26,838.
+As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} agreed clone pairs is 2,261 while \textit{ok} is 26,838.
 The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 168 for Simian and NiCad respectively.
@@
 
+\subsubsection{Agreed clone pairs}
+
+Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.
+Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}.
+The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
+We found that NiCad generates errors and stopped processing against some Qualitas projects.
+\FIXME{Reported the errors to NiCad creator.
+Add response here.}  $N_D$ could not detect clones in 6 projects due to clustering errors.
+$N_E$ generated renaming and clustering errors for 11 and 16 projects respectively.
+As a result, we did not have NiCad clones from these project in the agreed clone pairs.
+Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.
+
 \begin{table}
 	\centering
-	\caption{No.~of projects in Qualitas successfully analysed by Simian and NiCad}
+	\caption{No.~of successfully analysed Qualitas projects}
 	\label{tab:projects_missing}
@@
 
-\subsubsection{Agreed clone pairs}
-
-Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.
-Similar to the original study, we select a threshold \textit{p} of 0.7 for both good and ok-match \cite{Bellon2007}.
-The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-We found that NiCad generates errors and stopped processing against some Qualitas projects.
-\FIXME{Report the errors to NiCad creator.}  $N_D$ could not detect clones in 6 projects due to clustering errors.
-$N_E$ generated renaming errors for 11 projects, and clustering errors for 16 projects.
-Hence, we did not have NiCad clones in the agreed clone pairs for these 6 ($N_D$) and 27 projects ($N_E$).
-This makes Simian clones of the same projects to be removed from the agreed clone pairs as well since they could not have matching online clone pairs.
-
-The distributions of good-match clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}.
-There are 2,274 good-match pairs (2,261 uniquely) consisting of 10 pairs from$S_DN_D$, 26 pairs from$S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$.
-According to the definition, ok-match clone pairs always subsume the good-match pairs.
-There are 26,838 ok-match clone pairs (excluding the 2,261 good-match pairs).
-9,052 pairs are from $S_DN_D$, 991 pairs are from $S_DN_E$, 78 are pairs from $S_EN_D$, and 17,549 pairs are from $S_EN_E$.
-Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets, but there is no clone pair that is agreed by all four combinations.
-If we remove duplicates, the number of unique ok-match pairs is 26,838.
+\begin{table}
+	\centering
+	\caption{Distribution of agreed clone pairs}
+	\label{t_agreed_good_clone_pairs}
+	\small
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r|r|r}
+		\hline
+		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Total & Unique \\
+		\hline
+		\textit{good} & 10 & 26 & 10 & 2,228 & 2,274 & 2,261 \\
+		\textit{ok} & 9,052 & 991 & 78 & 17,549 & 27,670 & 26,838 \\
+		\hline
+	\end{tabular} %
+}
+\end{table}
+
+The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}.
+There are 2,261 unique \textit{good} pairs consisting of 10 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$.
+There are 26,838 unique \textit{ok} pairs (excluding the subsumed 2,261 \textit{good} pairs).\footnote{According to the definition, \textit{ok} clone pairs always subsume the \textit{good} pairs.} We obtained 9,052; 991; 78; and 17,549 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively.
+Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:venn4_orig_ok}), but there is no clone pair that is agreed by all four combinations.
+%If we remove duplicates, the number of unique ok-match pairs is 26,838.
 
@@
 Several projects triggered NiCad problem of clustering and renaming again as listed in Table \{tab:projects_missing}.
-The agreed clone pairs using Bellon's good-match(0.7) and ok-match(0.7) criteria of this new dataset are also listed in Table \{t_agreed_good_clone_pairs}.
-
-\begin{table}[H]
-	\centering
-	\caption{Distribution of agreed clone pairs using Bellon's criteria for \textit{D} and \textit{E} settings}
-	\label{t_agreed_good_clone_pairs}
-	\small
-	\begin{tabular}{l|r|r}
-		\hline
-		\multirow{2}{*}{Setting} & \multicolumn{2}{c}{No.~of clone pairs}   \\ \cline{2-3}
-		& good-match & ok-match \\
-		\hline
-		$S_DN_D$  & 10 & 9,052    \\ 
-		$S_DN_E$  & 26 & 991     \\ 
-		$S_EN_D$  & 10 & 78       \\
-		$S_EN_E$  & 2,228 & 17,549   \\ 
-		\hline
-		Total & 2,274 & 27,670   \\
-		\hline
-		Unique & 2,261 & 26,838  \\
-		\hline
-	\end{tabular}
-\end{table}
+The agreed clone pairs using Bellon's \textit{good}(0.7) and ok-match(0.7) criteria of this new dataset are also listed in Table \{t_agreed_good_clone_pairs}.
 
@@
 		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3}
-		\caption{Distributions of good-match(0.7) pairs}
+		\caption{Distributions of \textit{good} pairs}
 		\label{fig:venn4_orig_good}
@@
 		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3}
-		\caption{Distributions of ok-match(0.7) pairs}
+		\caption{Distributions of \textit{ok} pairs}
 		\label{fig:venn4_orig_ok}
@@
 
-The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with another tool.
-The disagreement can be from misalignment of clone lines or different configurations that result in different clones reported.
-They are also clone pairs in projects with NiCad's errors (6 projects for \textit{df} and 27 for \textit{EvCl} configurations) that are missing from the agreed clone pairs.
-With the four configuration combinations, we decided to investigate only two,$S_D$, and $N_D$, and drop Simian$_{\mathrm{\textit{EvCl}}}$ and NiCad$_{\mathrm{\textit{EvCl}}}$ due to their enormous amount of clone pairs (59 millions and 206 millions respectively).
-They also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.
+The disagreed clone pairs are clone pairs that are reported by a tool, either Simian or NiCad, and do not have agreement with clones from another tool.
+The disagreement can be from misalignment of clone lines or different configurations that result in dissimilar clones reported.
+They also cover clone pairs in projects having NiCad's errors (6 projects for $N_D$ and 27 for $N_E$) that are automatically missing from the agreed clone pairs.
+With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and drop $S_E$ and $N_E$ due to their enormous amount of clone pairs (59 and 206 millions respectively).
+$S_E$ and $N_E$ also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.
 
 Even choosing only the default configurations, the number of clone pair candidates are still very large.
-We hence apply two pruning filters: clone size, and similarity threshold.
+We hence apply three filters: \textbf{clone size, regular expression, and similarity threshold}.
 For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}.
-The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines).
-The second filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration.
+The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods, getters and setters using regular expressions and removes them.
+The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration.
 %We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%.
@@
 % 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
-For $S_D$, there are 20,348 clone pairs after using 10--line filter.
-Out of 20,348 pairs, 2,546 of them are ok-match pairs which are discarded.
-We filtered the results further by removing false positives such as similar \verb|hashCode()| methods, getters and setters out by using regular expressions.
-We managed to reduce the number to 871 clone pairs remaining for manual investigation.
+As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and regular expressions.
+The combination of the two filters reduce the number of $S_D$ clones to 17,801 pairs for manual investigation.
 % 7062 + 22187 + 6755 =  36004 %
-For $N_D$, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well.
-We thus filter NiCad's clones by using similarity threshold.
-We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2) and obtain 618 clone pairs.
+For $N_D$, 10-line threshold is already a minimum NiCad's clone size.
+However, NiCad still reported much more clones than Simian since it can detect type-3 clones.
+Thus, we filtered NiCad's clones by using similarity threshold and regular expressions.
+We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2).
+We have tried varying the UPI from 70\%, 80\% and 90\% and we found that 80\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation.
+Using the two filters, we reduced the size of $N_D$ clones to 168 pairs.
+
 %However, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well.
@@
 Using 80\% similarity, there are totally 166 pairs left.
-There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation.
-The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.
+%There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation.
+%The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.
+
+In our manual investigation process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 26,102 pairs out of 47,068 (more than half of the \texttt{equals()} pairs came from $S_D$).
+Finally, there are 3,450 pairs remaining which we manually investigated them.
+\textbf{To answer RQ1, we found 47,068 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
+After a manual investigation, we found at least 523 online code clones pairs are true clones.}
 
@@
 
-\begin{table}
-	\centering
-	\caption{No.~of disagreed clone pairs ($S_D$ and $N_D$).}
-	\label{tab:classification_indv_stats}
-	\small
-	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|p{1.5cm}|r|r|r|r}
-		\hline 
-		Tool & Filter & \multicolumn{1}{c|}{Original} & \multicolumn{1}{c|}{Filtered} & \multicolumn{1}{c|}{good/ok} & \multicolumn{1}{c}{remaining} \\ 
-		%\hline 
-		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
-		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
-		\hline
-		\multirow{1}{*}{\textit{Simian$_{df}$}} & $line \geq 10$ \newline \& reg.~exp & \multirow{2}{*}{67,570} & \multirow{2}{*}{47,223}  & \multirow{2}{*}{2,546} & \multirow{2}{*}{17,801} \\ %140 + 1482 + 926
-		\hline
-%		\multirow{1}{*}{\textit{$N_D$}-1} & 7040  & 226 & 6700 & 114 \\
-%		\multirow{1}{*}{\textit{$N_D$}-2} & 22187  & 152 & 21990 & 45 \\
-		\multirow{1}{*}{\textit{$N_D$}} & $sim \geq 80\%$ \newline (UPI=0.2) & \multirow{2}{*}{229,176} & \multirow{2}{*}{228,558}  & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
-		\hline
-		%\multicolumn{2}{l|}{Total} & 296,746 & 20,966 & 2,996 & 1,039 \\
-		%\hline
-	\end{tabular} %
-	}
-\end{table}
+%\begin{table}
+%	\centering
+%	\caption{No.~of disagreed clone pairs ($S_D$ and $N_D$).}
+%	\label{tab:classification_indv_stats}
+%	\small
+%	\resizebox{\columnwidth}{!}{%
+%	\begin{tabular}{l|p{1.6cm}|r|r|r|r}
+%		\hline 
+%		Tool & Filter & \multicolumn{1}{c|}{Original} & \multicolumn{1}{c|}{Filtered} & \multicolumn{1}{c|}{good/ok} & \multicolumn{1}{c}{remaining} \\ 
+%		%\hline 
+%		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
+%		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
+%		\hline
+%		\multirow{1}{*}{\textit{Simian$_{df}$}} & $Line \geq 10$ \newline \& RegEx & \multirow{2}{*}{67,570} & \multirow{2}{*}{47,223}  & \multirow{2}{*}{2,546} & \multirow{2}{*}{17,801} \\ %140 + 1482 + 926
+%		\hline
+%%		\multirow{1}{*}{\textit{$N_D$}-1} & 7040  & 226 & 6700 & 114 \\
+%%		\multirow{1}{*}{\textit{$N_D$}-2} & 22187  & 152 & 21990 & 45 \\
+%		\multirow{1}{*}{\textit{$N_D$}} & $Sim \geq 80\%$ \newline \& RegEx & \multirow{2}{*}{229,176} & \multirow{2}{*}{228,558}  & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
+%		\hline
+%		%\multicolumn{2}{l|}{Total} & 296,746 & 20,966 & 2,996 & 1,039 \\
+%		%\hline
+%	\end{tabular} %
+%	}
+%\end{table}
 
@@
 
-This is an important question underpinning the motivation of online code cloning.
+Besides the quantitative analysis, we are also interested in a qualitative analysis of the online clones.
 Why are they created and how?
@@
 They can be either accidentally similar (e.g.~similar try-catch statements) or similar after code normalisation process.
-Using this cloning pattern classification scheme, we consider clone pairs in created by pattern A, A', B, C as true positive, and clone pairs in pattern D, E, F as false positive.
+Using this cloning pattern classification scheme, we consider clone pairs in created by pattern A, A', B, C, D, and E as true positive, and F as false positive.
 
@@
 \textbf{Agreed clone pairs}: the classification results are shown in \Cref{tab:classification_good_o}.
-We have manually investigated 2,261 good-match clone pairs.
-There is one clone pair in category A which is found to be copied from a Qualitas project to Stack Overflow.
-Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as category B.
-We found 3 pairs in category C that are copied from external sources.
-The rest are false positive clones.
-58 clone pairs are found to be \verb|equals()| methods, or getters and setters, category D.
-Six pairs are similar code from inheritance of the same superclass or implementing the same interface, category E.
-Finally, 2,189 clone pairs are categorised to E which means they are false clones.
-
-For the ok-match clone pairs, we could not feasibly investigate all 23,868 pairs manually.
-According to the manual investigation of good-match pairs, we found that $S_EN_E$ produces a large number of 2,253 false positive results (accounts for 99.87\% of $S_EN_E$ clone pairs) due to its recall preference.
-We thus decided to leave this configuration out of the ok-match manual investigation.
-There are totally 4,625 ok-match pairs that were investigated.
-The 47 true positive pairs found are combinations of 8, 29, and 10 clone pairs in category A, B, and C respectively.
+We have manually investigated 2,261 \textit{good} clone pairs.
+There is one clone pair in pattern A which is found to be copied from a Qualitas project to Stack Overflow.
+Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as pattern B.
+We observed 3 pairs in pattern C since they are copied from external sources.
+%The rest are boilter-plate, inherit/interface, and false positive clones.
+58 clone pairs are found to be pattern D: \verb|equals()| methods, or getters and setters.
+Six pairs are similar code from inheriting the same superclass or implementing the same interface, pattern E.
+Finally, 2,189 clone pairs are categorised to F which means they are false clones.
+
+For the \textit{ok} clone pairs, we could not feasibly investigate all 23,868 pairs manually.
+According to the manual investigation of \textit{good} pairs, we found that $S_EN_E$ produces a large number of 2,253 false positive results (accounts for 99.87\% of $S_EN_E$ clone pairs) due to its recall preference.
+We thus decided to leave this configuration out of the manual investigation.
+There are totally 4,625 \textit{ok} pairs that were investigated.
+We found 8, 29, and 10 in pattern A, B, and C respectively.
+There were 77 boilter-plate pairs, and 3 inherit/interface pairs.
+82 pairs were false positives.
+%The 47 true positive pairs found are combinations of 8, 29, and 10 clone pairs in category A, B, and C respectively.
 
@@
 With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of$S_DN_D$,$S_D$--NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}N_D$.
-We had not done any investigation of good-match since there were no good-match pairs for these 3 agreements.
+We had not done any investigation of \textit{good} since there were no \textit{good} pairs for these 3 agreements.
 The number of pairs that have been looked at is 6,706 (excluding duplicates).
@@
 
-\begin{table*}
-	\centering
-	\caption{Classification results of agreed and disagreed clone pairs.
-SO$_u$ denotes a number of unique Stack Overflow snippets.
-Q$_u$ and Q$_{up}$ denote a number of unique Qualitas Java files and unique Qualitas projects respectively.}
+\begin{table}
+	\centering
+	\caption{Classification results of agreed and disagreed clone pairs.}
 	\label{tab:classification_good_o}
 	\small
-	\resizebox{2.1\columnwidth}{!}{%
-		\begin{tabular}{|l"r|r|r|r|r|r|r|r"r|r|r|r|r|r|r"r|r|r|r|}
-			\hline
-			Classificaiton & A & A' & B & C & \textbf{Sum} & SO$_{u}$ & Q$_u$ & Q$_{up}$ & D  & E & F & \textbf{Sum} & SO$_{u}$ & Q$_u$ & Q$_{up}$ & \textbf{Total}  & SO$_{u}$ & Q$_u$ & Q$_{up}$\\ 
-			\hline 
-			\hline
-			\multirow{1}{*}{\textit{good-match(0.7)}}  & 1 & 0 & 4  & 3 & \textbf{8} & 7 & 6 & 6 & 58  & 6 & 2189 & \textbf{2253} & 81 & 693 & 58 & \textbf{2261} & 87 & 699 & 59 \\
-			\multirow{1}{*}{\textit{ok-match(0.7)}}  & 8 & 0 & 29  & 10 & \textbf{47} & 12 & 14 & 10 & 9158 & 35 & 82 & \textbf{9275} & 100 & 204 & 30 & \textbf{9322} & 112 & 218 & 35 \\
-			\hline 
-			\hline 
-			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & \textbf{432} & 148 & 229 & 38 & 209 & 63 & 167 & \textbf{439} & 136 & 214 & 49 & \textbf{871} & 271 & 428 & 58 \\
-			\hline
-			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & \textbf{36} & 16 & 15 & 5 & 77 & 3 & 82 & \textbf{132} & 52 & 55 & 17 & \textbf{168} & 67 & 69 & 19 \\ 
-			\hline
-			\hline
-			Total & 96 & 0 & 396 & 31 & \textbf{523} & -- & -- & -- & 9502 & 107 & 2520 & \textbf{12099} & -- & -- & -- & \textbf{12622} & -- & -- & -- \\ 
+	\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{l|r|r|r|r|r|r|r|r}
+			\hline
+			Set & A & A' & B & C & D  & E & F & Total \\ 
+			\hline 
+			\hline
+			\multirow{1}{*}{\textit{good}}  & 1 & 0 & 4  & 3 & 58  & 6 & 2,189 & 2,261 \\
+			\multirow{1}{*}{\textit{ok}}  & 8 & 0 & 29  & 10 & 9,158 & 35 & 82 & 9,322 \\
+			\hline 
+			\hline 
+			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & 209 & 63 & 167 & 871 \\
+			\hline
+			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & 77 & 3 & 82 & 168 \\ 
+			\hline
+			\hline
+			Total & 96 & 0 & 396 & 31 & 9,502 & 107 & 2,520 & 12,622 \\ 
 			\hline
@@
 	}
-\end{table*}
+\end{table}
 
 %\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
-\textbf{Disagreed clone pairs}: we performed a manual investigation and classification of 871 filtered clone pairs reported by$S_D$ and 168 by $N_D$ in the same way as the agreed clone pairs.
-The results of investigation is reported in \Cref{tab:classification_good_o}.
-There are 432 true positive clone pairs found from$S_D$ consisting of 19 pairs in category A, 336 pairs in B, and 17 pairs in C.
-For $N_D$, there are 36 true positive pairs consisting of 8 pairs in category A, 27 pairs in B, and 1 pair in C.
-The total number of true positive clone pairs is 523 as described in \Cref{tab:classification_good_o}.
-
-%\subsection{Summary of true online clone pairs}
-%\begin{table}[H]
-%	\centering
-%	\caption{Numbers of true positive online clone pairs found by manual investigation}
-%	\label{tab:classification_true_pairs_summary}
-%	\small
-%	\begin{tabular}{l|r|r|r|r|r}
-%		\hline 
-%		Tool & A & A' & B & C & Total \\
-%		\hline
-%		good-pairs & 1 & 0 & 4 & 3 & 8 \\
-%		ok-pairs & 8 & 0 & 29 & 10 & 47 \\
-%		Simian$_{df}$ pairs & 79 & 0 & 336 & 17 & 432 \\
-%		$N_D$ pairs & 8 & 0 & 27 & 1 & 36 \\
-%		\hline 
-%		Total & 96 & 0 & 396 & 31 & 523 \\
-%		\hline
-%	\end{tabular} 
-%\end{table}
+\textbf{Disagreed clone pairs}: we performed a manual investigation and classification of 871 $S_D$ and 168 $N_D$ clone pairs in the same way as the agreed ones.
+There were 19 pairs in pattern A, 336 pairs in B, 17 pairs in C, 209 in D, and 63 in E.
+167 pairs are false clones.
+For $N_D$, there are 8 pairs in pattern A, 27 pairs in B, 1 pair in C, 77 pairs in D, and 3 pairs in E.
+$N_D$ reported 82 false positive clones.
+%The total number of true positive clone pairs is 523 as described in \Cref{tab:classification_good_o}.
 
@@
 
-\subsection{RQ3: Effects of online code clones}
-
-In this study, we are interested in effects of having code clones between open source software systems and Stack Overflow.
+\subsection{RQ3: Outdated Online Code Clones}
+
+%In this study, we are interested in effects of having code clones between open source software systems and Stack Overflow.
 From the manual investigation, we found 523 true positive online clone pairs.
@@
 
-\subsubsection{Outdated Clones}
-Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated.
-This is a normal issue driving the development of clone detection.
-We need to locate clones to be able to update them according to their updated original code \cite{Bellon2007}.
+%\subsubsection{Outdated Clones}
+Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated \cite{Xia2014}.
+Usually code clone detection is used to locate clone instances and update them according to their updated original code \cite{Bellon2007}.
 However, in this situation, the clones are more pervasive on Stack Overflow posts and more difficult to detect due to its large scale and the mix of natural language and source code.
-Since code can be updated due to various possible reasons, e.g.~bug fixing, this poses a problem if developers reuse a cloned code snippet from Stack Overflow without knowing that it is outdated.
-%They might also introduce the same unfixed bug(s) into the software.
-They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce the same later-be-fixed bug(s) into their software.
-
-To check if the discovered Stack Overflow clones are outdated, we focus on the 96 pattern-A clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}).
-For each code snippet, we can track its origin from its Qualitas counterpart.
-Using the file in Qualitas project, we locate the latest version of the file in its version control repository (all of them use git) and compare the snippet to its latest version to see if any change has been made to the source code.
-If we find any change, we use \textit{git blame} command to see who modified the source code and when.
+Since code can be updated due to various possible reasons, e.g.~bug fixing or API changes, it is risky if developers reuse outdated code snippets from Stack Overflow.
+%They possibly also introduce vulnerabilities into the software.
+They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce bugs or vulnerabilities into their software.
+
+To check if the discovered Stack Overflow clones are outdated, we focused on the 96 pattern-A clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}).
+For each code snippet, we could track its origin from its Qualitas counterpart.
+Relying on git repositories of Qualitas projects, we located the latest version of the each file and compared to the Stack Overflow snippet to see if any change has been made to the source code.
+If we found any change, we used \textit{git blame} command to see who modified the source code and when.
 
@@
 \Cref{fig:outdated} shows the findings of outdated clone investigation.
-The comparison with the clones' latest code reveals that there are 55 clone pairs that are outdated.
-These are clone pairs that were copied from Qualitas projects to Stack Overflow and marked as accepted answers, and later have been changed during the development.
-\textit{hadoop} and \textit{spring} have the maximum number of 9 outdate code clones, followed by 6 clones from \textit{tomcat}, and 5 clones from \textit{eclipse-SDK}.
+The comparison with the clones' latest versions revealed that 55 clone pairs were outdated.
+These were clone pairs that were copied from Qualitas to Stack Overflow and later marked as accepted answers.
+Hadoop and Spring have the maximum number of 9 outdate code clones, followed by 6 clones from Tomcat, and 5 clones from Eclipse-SDK.
 An example of outdated code in hadoop's \textit{WritableComparator.java} is shown in \Cref{fig:before-after}.
 The newest version has one line added.
-We also found outdated code which contains more disruptive changes.
-The code snippet in Stack Overflow post 23520731 which is a copy of \textit{SchemaUpdate.java} in \textit{hibernate} has been heavily modified (as shown in \Cref{fig:hibernate_outdated_code}).
-Moreover, there is a code snippet in Stack Overflow post 3758110 which is a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring.
-It was deleted in the commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted and the latest version of Spring does not contain the Java file anymore.
-
-The outdate code clones without latest changes can cause problems ranging from uncompilable code due to version difference to bug propagation.
-An outdated code with a subtle change such as the one in \textit{WritableComparator.java} can be copied and reused without awareness from developers.
-Fortunately, Stack Overflow has a natural voting mechanism that can mitigate this kind of outdated code.
+We also found outdated code which contained heavy modifications.
+For example, the code snippet in Stack Overflow post 23520731, a copy of \textit{SchemaUpdate.java} in Hibernate, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
+Moreover, the code snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring, was deleted in the commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted.
+The latest version of Spring does not contain the Java file anymore.
+
+The outdate online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagation.
+An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers.
+Stack Overflow has a voting mechanism that may mitigate this outdated code issue.
 Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment.
-They can cast a down vote to that answer resulting in low vote for the answer with outdated code.
-However, if the answer is marked as accepted by the person who asks the question (which is our case), it is still attractive to naive developers who are not aware of the voting mechanism.
+They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated).
+However, if the answer is marked as accepted by the person who asks the question (which is our case), it is always ranked on the top and still attractive to naive developers who are ignorant.
 
@@
 
-\subsubsection{Software Licensing Violation}
-Software licensing is a paramount factor in software development.
-Violation of software license can cause a major impact to software delivery and also lead to legal issues.
-It is an emerging area that software engineering research community is paying attention to.
-For example, there are studies of automatic technique to identify software licensing from source code files \cite{German2010} and the evolution of licenses in open source projects \cite{DiPenta2010}.
+\subsection{RQ4: Software Licensing Violation}
+Software licensing is important in software development. Violation of software license can cause major impacts to software delivery and also lead to legal issues \cite{Sprigman2015}. 
+%It is an emerging area that software engineering research community is paying attention to. For example, 
+Software licenses keep evolving in open source projects \cite{DiPenta2010} and clones can have different license \cite{German2009}.
+This can lead to licensing violation if one does not check the license before integration third-party source code into their software.
+A study by An et al.~ \cite{An2017} found 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code.
+%there are studies of automatic technique to identify software licensing from source code files \cite{German2010}
 
@@
 
-In our study, we reveal another possible situation of software licensing issue caused by code cloning to Stack Overflow.
+In our study, we reveal another possible situation of software licensing issues caused by code cloning ``to Stack Overflow''.
 We found with evidence that 96 pieces of code have been copied from 14 open source projects in Qualitas dataset to Stack Overflow as examples.

### 2017-01-24 cloneoverflow-latex/cloneoverflow.tex
Changed most of the experiment section to past tense

@@
 
-While a lot of research has focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and whether these example snippets are still up-to-date.
+While a lot of research has focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and effects of reusing them such as outdated code and software licensing violation.
 
@@
 \noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 523 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses.
-Furthermore, 53 out of the 96 online code clones on Stack Overflow are outdated and questionable for being reused.
+Importantly, 53 out of the 96 online code clones on Stack Overflow are outdated and questionable for being reused.
 
@@
 \section{Empirical Study}
-We perform an empirical study of online code clones between Stack Overflow and 109 Java open source projects to answer the following research questions: \\ 
-\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We would like to quantitatively measure the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem.
+We performed an empirical study of online code clones between Stack Overflow and 109 Java open source projects to answer the following research questions: \\ 
+\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We quantitatively measured the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem.
 \newline
@@
 \newline
-\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorise online clones into seven categories according to our online code cloning pattern scheme.
-This gives us more insights to why online code clones are created.
+\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorised online clones into seven categories according to our online code cloning pattern scheme.
+This gave us more insights to why online code clones are created.
 %so we can differentiate and understand the motivation of cloning.
@@
 \newline
-\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We are interested in the correctness of Stack Overflow code examples since millions of users are potentially reusing them.
+\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We were interested in the correctness of Stack Overflow code examples since millions of users are potentially reusing them.
 %Is there observable problems caused by clones between Stack Overflow and open source projects?
@@
 
-\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We would like to investigate whether online code clones can be legally harmful to software reusing them.
+\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We investigated whether online code clones can be legally harmful to software reusing them.
 
@@
 \subsection{Experimental Framework}
-To answer the four research questions, an experimental framework is designed as depicted in \Cref{fig:exp_framework}.
-We process two datasets, Stack Overflow and 111 open source projects from Qualitas corpus.
-Java code fragments are extracted from Stack Overflow posts using regular expressions.
-We prepare Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection.
-Then, we deploy two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets.
-Due to scalability of Simian and NiCad, we partition the input and run the tools multiple times.
-Each run is composed of the whole Stack Overflow data and single Qualitas project.
-We repeat the process until we cover 111 projects.
-
-We then convert the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combine the 111 reports into a single GCF file.
-GCF provides a common format for clones which enable us to reuse the same scripts to analyse clone reports from both Simian and NiCad.
-Moreover, using GCF, other additional clone detectors can be adopted, if needed, without any changes in the analysis.
-Simian do not provide an option to detect inter clones between two locations.
-Hence the Simian GCF clone report is pruned to contain only inter clone pairs between Stack Overflow and Qualitas projects.
-In this step, all intra clone pairs within either Stack Overflow or Qualitas are removed.
-NiCad can solely detects inter clones so no pruning is needed.
-We do not have an oracle of clones between the two data sets so we need a manual investigation to validate the reported clone candidates.
-However, the large amount of clone pairs hinder us from looking at all of them.
-Random samples can be done but may return mostly non-meaningful clones.
-Instead, we select clone pair candidates by relying on agreement of clone detectors.
-If a clone pair is similarly reported by multiple tools, we have higher confidence that it is a real clone pair.
-To achieve this, clone pairs from the two clone detectors are pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
-This step generates \textbf{agreed clone pairs}.
-They are pairs with high confidence to be true clones since they obtain agreement from both tools.
-Then, pairs reported by Simian and NiCad that do not find agreement are \textbf{disagreed clone pairs}.
-The disagreed clone pairs are clones with less confidence than agreed ones.
-Finally, agreed and disagreed clone pairs have been looked at manually by the first and the third author.
-
-In the manual inspection process, we classify clones into seven categories according to information observed from code comments and natural text in Stack Overflow answer.
-This process takes approximately a months until we successfully investigate 3,448 clone pairs.
-Clone pairs that are classified as false clones, boiler-plate code, or IDE-generated are not very interesting and are discarded for further analysis.
-We compare licensing information of 523 remaining clone pairs for possibility of software licensing violations.
-Moreover, we look forward through history of each clone from its git repository.
-With this method, we discover \textbf{outdated code}, code that changes are made to them after it has been copied to Stack Overflow.
+To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}.
+We processed two datasets, Stack Overflow and 111 open source projects from Qualitas corpus.
+Java code fragments were extracted from Stack Overflow posts using regular expressions.
+We prepared Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection.
+Then, we deployed two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets.
+Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times.
+Each run was composed of the whole Stack Overflow data and single Qualitas project.
+We repeated the process until we cover 111 projects.
+
+We then converted the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file.
+GCF provides a common format for clones which enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad.
+Moreover, using GCF, other additional clone detectors could be adopted, if needed, without any changes in the analysis.
+Simian did not provide an option to detect inter clones between two locations.
+Hence the Simian GCF clone report was pruned to contain only inter clone pairs between Stack Overflow and Qualitas projects.
+In this step, all intra clone pairs within either Stack Overflow or Qualitas were removed.
+NiCad provided an option to detect inter clones so no pruning is needed.
+We did not have an oracle of clones between the two data sets so we rely on a manual investigation to validate the reported clone candidates.
+However, the large amount of clone pairs hindered us from looking at all of them.
+Random sampling of clones could be done but may return mostly non-meaningful clones.
+Instead, we selected clone pair candidates by relying on agreement of clone detectors.
+If a clone pair was similarly reported by multiple tools, we had a higher confidence that it was a real clone pair.
+To achieve this, clone pairs from the two clone detectors were pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
+This step generated \textbf{agreed clone pairs}.
+They were pairs with high confidence to be true clones since they obtained agreement from both tools.
+Then, pairs reported by Simian and NiCad that did not find agreement were \textbf{disagreed clone pairs}.
+The disagreed clone pairs were clones with less confidence than the agreed ones.
+Finally, agreed and disagreed clone pairs had been looked at manually by the first and the third author.
+
+In the manual inspection process, we classified clones into seven categories according to information observed from code comments and natural text in Stack Overflow answer.
+This process took approximately a months until we successfully investigated 3,450 clone pairs.
+Clone pairs that were classified as false clones, boiler-plate code, or IDE-generated were not very interesting and were ignore in the analysis of outdated code and licensing violation.
+We compared licensing information of 523 remaining clone pairs for possibility of software licensing violations.
+Moreover, we looked forward through history of each clone from its git repository.
+With this method, we discovered \textbf{outdated code}, code that changes are made to them after it had been copied to Stack Overflow.
 %hence resulting in outdated clones on Stack Overflow.
@@
 The archived dump has a size of 9 gigabytes.
-The data dump is in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts.
-We are interested in code snippets embedded in posts which are located between \texttt{<code></code>} tags.
+The data dump was in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts.
+We were interested in code snippets embedded in posts which were located between \texttt{<code></code>} tags.
 A Stack Overflow thread contains a post of question and several posts of answers.
@@
 An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem.
-We collect Java code snippets using two criteria.
-First, we are only interested in code snippets with at least six lines.
-Snippets which are smaller than six lines are usually spurious clones \cite{Bellon2007}.
-Second, we are only interested in code snippets in accepted answers.
-We choose snippets in accept answers because they actually solved the problems in the questions and has a check mark sign on them to notify other users.
-Moreover, they are always displayed just below the questions which makes them attractive to be reused than snippets in other answers.
-Each snippet is extracted from the dump using regular expressions and saved to a file using its post ID as the file's name.
-If an accepted answer has more than one code snippet, we append an indexing number, starting from zero, after the post ID (e.g.
+We collected Java code snippets using two criteria.
+First, we were only interested in code snippets with at least six lines.
+Snippets which were smaller than six lines were usually spurious clones \cite{Bellon2007}.
+Second, we only focused on code snippets in accepted answers.
+We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users.
+Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers.
+Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name.
+If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g.
 45051109\_0, and 45051109\_1.).
-Lastly, we add \texttt{.java} extension to the file's names so that clone detectors can recognise them.
+Lastly, we added \texttt{.java} extension to the file's names so that clone detectors could recognise them.
 We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
@@
 Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code due to its licensing limitation \cite{QualitasCorpus} so it is removed from the study.
-This results in total of 111 projects analysed in the study.
+This resulted in total of 111 projects analysed in the study.
 As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code.
@@
 Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}.
-By using this agreement-based approach, we can reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
-To find an agreement between two clone pairs report by two different tools, we use clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
+By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
+To find an agreement between two clone pairs report by two different tools, we used clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
 Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1.
@@
 \subsection{Clone Detector's Parameter Tuning}
-We are aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
-However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we are hindered from searching for the best configurations of the tools.
+We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
+However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we were hindered from searching for the best configurations of the tools.
 Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}).
 The details of the two configurations are described in \Cref{t:param_tuning}.
-Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we look for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.
+Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we looked for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.
 
@@
 
-We follow the experimental framework and detect clones between Stack Overflow and Qualitas corpus using the two selected clone detectors.
-To answer RQ1, we compute statistics of clone discovered by the tools.
-To answer RQ2, we manually investigated online clone pair candidates and categorise them using our patterns of online code cloning.
-The patterns are derived from Kapser et al.~\cite{Kapser2003} augmented by common patterns found in our data set.
-For RQ3, we look at the true positive clone pairs and check if they are still up-to-date.
-We also look at the license of each clone and observe a possibility of licensing violation.
+We followed the experimental framework and detected clones between Stack Overflow and Qualitas corpus using the two selected clone detectors.
+To answer RQ1, we computed statistics of clone discovered by the tools.
+To answer RQ2, we manually investigated online clone pair candidates and categorised them using our patterns of online code cloning.
+The patterns were derived from Kapser et al.~\cite{Kapser2003} augmented by common patterns found in our data set.
+For RQ3, we looked at the true positive clone pairs and check if they are still up-to-date.
+Similarly, for RQ4, we also looked at the license of each clone and observed a possibility of licensing violation.
 
@@
 Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments.
-These 11 fragments trigger Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
+These 11 fragments triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
 Hence, they were removed from Simian's clone reports before the analysis.
@@
 
-\begin{table}
-	\centering
-	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
-	\label{t:q_projects_license}
-	%	\resizebox{\columnwidth}{!}{%
-	\small
-	\begin{tabular}{l|r|p{4cm}}
-		\hline 
-		Project & Version & Licenses (no.~of files) \\
-		\hline
-		%		apache-ant & 1.8.4 & Apache2.0 \\
-		%		apache-log4j & 1.2.16 & \\
-		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
-		\hline
-		eclipse-SDK &  4.1 & Apache-2 (2183), \newline BSD3NoWarranty (107), \newline CDDLorGPLv2 (296), \newline EPLv1 (18823), MPLv1.1 (93), \newline None (224), SeeFile (8), \newline spdxBSD3 (185), \newline spdxMIT (1), Unknown (714) \\
-		\hline
-		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
-		\hline
-		hibernate & 4.2.2 & Apache-2 (20), \newline LGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
-		\hline
-		jasperreports & 3.7.4 & LGPLv2.1+ (3), \newline LGPLv3+ (1,581), \newline None (1), Unknown (4)\\
-		\hline
-		jfreechart & 1.0.13 & LGPLv2.1+ (989) \\
-		\hline
-		jgraph & 5.13.0.0 & LGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
-		\hline
-		%		jgrapht & 0.8.1 & LGPL 2.1 \& Eclipse  1.0 \\
-		jstock & 1.0.7c & LGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
-		\hline
-		jung2 & 2-0-1 & N/A \\
-		\hline
-		junit & 4.11 & None (160), Unknown (4)  \\
-		\hline
-		poi & 3.6 & Apache-2 (2,002), None (5) \\
-		\hline
-		spring & 3.0.5 & Apache-2 (2,982) \\
-		\hline
-		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
-		\hline
-		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
-		%		weka & 3-7-9 & \\
-		\hline
-	\end{tabular} %
-	%	}
-\end{table}
-
 %\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
@@
 Moreover, the code snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring, was deleted in the commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted.
-The latest version of Spring does not contain the Java file anymore.
+The latest version of Spring does not contain the file anymore.
 
@@
 %It is an emerging area that software engineering research community is paying attention to. For example, 
-Software licenses keep evolving in open source projects \cite{DiPenta2010} and clones can have different license \cite{German2009}.
+Software licenses keep evolving in open source projects \cite{DiPenta2010} and clones can have different license~\cite{German2009}.
 This can lead to licensing violation if one does not check the license before integration third-party source code into their software.
-A study by An et al.~ \cite{An2017} found 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code.
+A study by An et al.~\cite{An2017} found 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code.
 %there are studies of automatic technique to identify software licensing from source code files \cite{German2010}
+
+\begin{table}
+	\centering
+	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
+	\label{t:q_projects_license}
+	%	\resizebox{\columnwidth}{!}{%
+	\small
+	\begin{tabular}{l|r|p{4cm}}
+		\hline 
+		Project & Version & Licenses (no.~of files) \\
+		\hline
+		%		apache-ant & 1.8.4 & Apache2.0 \\
+		%		apache-log4j & 1.2.16 & \\
+		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
+		\hline
+		eclipse-SDK &  4.1 & Apache-2 (2183), \newline BSD3NoWarranty (107), \newline CDDLorGPLv2 (296), \newline EPLv1 (18823), MPLv1.1 (93), \newline None (224), SeeFile (8), \newline spdxBSD3 (185), \newline spdxMIT (1), Unknown (714) \\
+		\hline
+		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
+		\hline
+		hibernate & 4.2.2 & Apache-2 (20), \newline LGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
+		\hline
+		jasperreports & 3.7.4 & LGPLv2.1+ (3), \newline LGPLv3+ (1,581), \newline None (1), Unknown (4)\\
+		\hline
+		jfreechart & 1.0.13 & LGPLv2.1+ (989) \\
+		\hline
+		jgraph & 5.13.0.0 & LGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
+		\hline
+		%		jgrapht & 0.8.1 & LGPL 2.1 \& Eclipse  1.0 \\
+		jstock & 1.0.7c & LGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
+		\hline
+		jung2 & 2-0-1 & N/A \\
+		\hline
+		junit & 4.11 & None (160), Unknown (4)  \\
+		\hline
+		poi & 3.6 & Apache-2 (2,002), None (5) \\
+		\hline
+		spring & 3.0.5 & Apache-2 (2,982) \\
+		\hline
+		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
+		\hline
+		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
+		%		weka & 3-7-9 & \\
+		\hline
+	\end{tabular} %
+	%	}
+\end{table}
 
@@
 		Compatible  							 & Apache2     & Apache2  	   &  0 & 1 & 0 \\
-		(\textit{CL})	   						     & EPLv1       & EPLv1                                	&  14 &  6 & 0 \\
-															& None        & CC BY 3.0                    		&  0 & 12 & 0 \\
+		License	   						             & EPLv1       & EPLv1                 &  14 &  6 & 0 \\
+		(\textit{CL})													& None        & CC BY 3.0   &  0 & 12 & 0 \\
 		\hline
 	    Incompat. 								   & None       & Apache2  						& 41 & 29 & 3 \\
-		(\textit{IL}) 								   & None        & BSD/BSD3                        & 0 & 64 & 0 \\
-															& None        & CDDLorGPLv2                & 0 & 63 & 4 \\
+		License								         & None        & BSD/BSD3                      & 0 & 64 & 0 \\
+		(\textit{IL}) 								 & None        & CDDLorGPLv2                & 0 & 63 & 4 \\
 															& None        & EPLv1                               & 0 & 33 & 0\\
@@
 In our study, we reveal another possible situation of software licensing issues caused by code cloning ``to Stack Overflow''.
-We found with evidence that 96 pieces of code have been copied from 14 open source projects in Qualitas dataset to Stack Overflow as examples.
-They are also marked as accepted answers which increase their probability of being reused.
-The 14 open source projects come with their respective software licenses (shown in \Cref{t:q_projects_license}).
-However, the licensing information are mostly missing from these clones when they are posted on Stack Overflow.
-Mostly one or a few methods from the full source file are cloned.
-This makes the licensing terms at the top of the file mostly left uncopied.
-If developers copy and reuse these pieces of code in their projects, a licensing conflict can quietly happen without realisation of the developers.
+We found with evidence that 96 pieces of code had been copied from 14 Qualitas projects to Stack Overflow as code examples.
+They are also marked as accepted answers which increased their probabilities of being reused.
+The 14 open source projects came with their respective software licenses (shown in \Cref{t:q_projects_license}).
+However, the licensing information were mostly missing from these clones after they were posted on Stack Overflow.
+The licensing terms on the top of source code are not copied because mostly a small part of the file was cloned to Stack Overflow.
+If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
 
 The summary of licensing information is listed in \Cref{tab:license_abc}.
-The licenses are extracted by an automatic license identification tool Ninka \cite{German2010}.
-For the ones that cannot be automatically identified by Ninka and have been reported as SeeFile and Unknown, we look at them manually.
+The licenses were extracted by Ninka, an automatic license identification tool \cite{German2010}.
+For the ones that could not be automatically identified by Ninka and had been reported as \texttt{SeeFile} and \texttt{Unknown}, we looked at them manually.
 The table shows license of Stack Overflow snippets (denoted as SO) and Qualitas source code.
-The number of clone pairs according to each pair of license has been categorised by online clone category A, B, and C.
+The number of clone pairs of each license matching has been grouped according to online cloning patterns A, B, and C.
 In overall, we can see that most of the Stack Overflow snippets do not have licensing terms with them while their clone counterparts in Qualitas project do.

### 2017-01-24 cloneoverflow-latex/cloneoverflow.tex
Revamped Table 4.

@@
 \usepackage{subcaption}
+\usepackage{tikz}
 
@@
 	\label{t:param_tuning}
-	\resizebox{\columnwidth}{!}{%
-		\scriptsize
+%	\resizebox{\columnwidth}{!}{%
+	\small
 	\begin{tabular}{l|p{5.5cm}}
@@
 		\hline
-	Simian$_{\textrm{\textit{df}}}$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
+		$S_D$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
 		\hline
@@
 	\end{tabular} %
-}
+%}
 \end{table}
@@
 	\centering
-	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering. The last column shows the number of true positive clone pairs after the manual investigation.}
+	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering. The last column shows the number of true positive clone pairs after the manual investigation. }
 	\label{tab:online_clone_pairs}
 	\small
-	\begin{tabular}{l|r|l|r|r|r|r}
-		\hline
-		Clone set & Original & Filter & Candidates & \texttt{equals()} & Manual & TP \\ 
-		\hline 
-		\multirow{1}{*}{\textit{good}} & --  & -- & 2,261  & 9 & 2,252 & 8 \\
-		\multirow{1}{*}{\textit{ok}} & --  & -- & 26,838 & 9,122 & 200 & 47 \\
+	\begin{tabular}{l|r|c|c|c|c|r|r|r|r}
+		\hline
+		\multirow{2}{*}{Clone set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Candidates} & \multirow{2}{*}{\texttt{equals()}} & \multirow{2}{*}{Manual} & \multirow{2}{*}{TP} \\ \cline{3-6}
+		        		  & \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & & & & \\
+		\hline 
+		\multirow{1}{*}{\textit{good}} & & & & & & 2,261  & 9 & 2,252 & 72 \\
+		\multirow{1}{*}{\textit{ok}} &  & & & & & 9,322 & 9,122 & 200 & 9,240 \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}        & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 67,570 & $Line \geq 10$, RegEx, good/ok & 17,801 & 16,930 & 871 & 432 \\
-		\multirow{1}{*}{$N_D$} & 229,176 & $Sim \geq 80\%$, RegEx, good/ok & 168 & 41 & 127 & 36 \\ 
+		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 & 16,930 & 871 & 704 \\
+		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 & 41 & 127 & 116 \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total  & 296,746 & & 47,068 & 26,102 & 3,450 & 523 \\ 
-		\hline
+		Total  & 296,746 & & & & & 47,068 & 26,102 & 3,450 & 10,132 \\ 
+		\hline
+	 	\multicolumn{10}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 80\%$, \textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}}
 	\end{tabular} 
@@
 The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-We found that NiCad generates errors and stopped processing against some Qualitas projects.
+We encountered NiCad failures with some Qualitas projects.
 \FIXME{Reported the errors to NiCad creator.
-Add response here.}  $N_D$ could not detect clones in 6 projects due to clustering errors.
-$N_E$ generated renaming and clustering errors for 11 and 16 projects respectively.
+Cordy said it might be a long-path problem.
+Should we try fixing?}  $N_D$ could not detect clones in 12 projects due to clustering errors.
+$N_E$ generated renaming and clustering errors for 11 and 17 projects respectively.
 As a result, we did not have NiCad clones from these project in the agreed clone pairs.
@@
 		\hline
-		\textit{Successful} & 111 & 111 & 105 & 84 \\ 
-		\textit{Clustering fail} & -- & -- & 6 & 16 \\
+		\textit{Successful} & 111 & 111 & 99 & 83 \\ 
+		\textit{Clustering fail} & -- & -- & 12 & 17 \\
 		\textit{Renaming fail} & -- &  -- & -- & 11 \\

### 2017-01-25 cloneoverflow-latex/cloneoverflow.tex
Deleted a blank.
Deleted another blank
Updated the paper to reflect the newly added clone pairs from NiCad’s error.

@@
 The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}.
-Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments.
-These 11 fragments triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
-Hence, they were removed from Simian's clone reports before the analysis.
 From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,530 from $S_E$ respectively.
@@
 The average percentage of Stack Overflow code snippets that are cloned according to$S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
+Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments.
+These 11 fragments triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
+Hence, their clones were removed from further analyses.
 
@@
 Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}.
-The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-We encountered NiCad failures with some Qualitas projects.
-\FIXME{Reported the errors to NiCad creator.
-Cordy said it might be a long-path problem.
-Should we try fixing?}  $N_D$ could not detect clones in 12 projects due to clustering errors.
-$N_E$ generated renaming and clustering errors for 11 and 17 projects respectively.
+%The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
+We encountered NiCad failures with a few Qualitas projects. 
+%\FIXME{Reported the errors to NiCad creator. Cordy said it might be a long-path problem. Should we try fixing?}  
+$N_D$ could not detect clones in Hibernate due to clustering errors.
+$N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring.
+We had contacted the author of NiCad regarding the issues.
+They found that it was a problem of long file paths which will be fixed in the next NiCad releases.
 As a result, we did not have NiCad clones from these project in the agreed clone pairs.
@@
 		\hline
-		\textit{Successful} & 111 & 111 & 99 & 83 \\ 
-		\textit{Clustering fail} & -- & -- & 12 & 17 \\
-		\textit{Renaming fail} & -- &  -- & -- & 11 \\
+		\textit{Successful} & 111 & 111 & 100 & 96 \\ 
+		\textit{Clustering fail} & -- & -- & 1 & -- \\
+		\textit{Renaming fail} & -- &  -- & -- & 5 \\
 		\hline
@@
 		\hline
-		\textit{good} & 10 & 26 & 10 & 2,228 & 2,274 & 2,261 \\
-		\textit{ok} & 9,052 & 991 & 78 & 17,549 & 27,670 & 26,838 \\
+		\textit{good} & 10 & 26 & 10 & 2,228 & 2,321 & 2,308 \\
+		\textit{ok} & 9,042 & 991 & 78 & 17,549 & 27,670 & 26,838 \\
 		\hline
@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3}
+		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3+fixed_nicad-crop}
 		\caption{Distributions of \textit{good} pairs}
@@
 		\centering
-		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3}
+		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3+fixed_nicad-crop}
 		\caption{Distributions of \textit{ok} pairs}
@@
 \textbf{To answer RQ1, we found 47,068 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
-After a manual investigation, we found at least 523 online code clones pairs are true clones.}
+They are 2,261 \textit{good} pairs, 26,838 \textit{ok} pairs.
+XXX After a manual investigation, we found at least 523 online code clones pairs are true clones.}
 

### 2017-01-26 cloneoverflow-latex/cloneoverflow.tex
Added TXL problems
Update the clone stats of the 4 configurations.
Add "blocks" to NiCad settings.

@@
 	\small
-	\begin{tabular}{l|p{5.5cm}}
+	\begin{tabular}{l|p{7cm}}
 		\hline 
@@
 		\hline 
-		$N_D$ & MinLine=10, MaxLine=1000, UPI=0.30 \\
-		\hline
-		$N_E$ & MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
+		$N_D$ & Blocks, MinLine=10, MaxLine=1000, UPI=0.30 \\
+		\hline
+		$N_E$ & Blocks, MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
 		\hline 
@@
 			\hline
-			Snippets & 1,086 & 1,530 & 1,240 & 12,886 \\
-			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,372,599 & 229,176 & 206,760,077 \\
-			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,447 & 185 & 16,047 \\
-			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.64 & 5.32 \\
+			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
+			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
+			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
+			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
 			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
@@
 We had contacted the author of NiCad regarding the issues.
-They found that it was a problem of long file paths which will be fixed in the next NiCad releases.
+They found that there problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
 As a result, we did not have NiCad clones from these project in the agreed clone pairs.
@@
 			\hline
-			\hline
 			\multirow{1}{*}{\textit{good}}  & 1 & 0 & 4  & 3 & 58  & 6 & 2,189 & 2,261 \\
 			\multirow{1}{*}{\textit{ok}}  & 8 & 0 & 29  & 10 & 9,158 & 35 & 82 & 9,322 \\
-			\hline 
-			\hline 
 			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & 209 & 63 & 167 & 871 \\
-			\hline
 			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & 77 & 3 & 82 & 168 \\ 
-			\hline
 			\hline

### 2017-01-26 cloneoverflow-latex/cloneoverflow.tex
Changed the diagram of good/ok pairs to horizontal bar charts.
- fixed the number in Table 6 to be back to they were before adding missing ND projects (to avoid confusion). They'll be put back in when everything is done.

@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 270,429,422 similar code fragment pairs and manually investigated 3,450 candidate clone pairs between Java code fragments obtained from Stack Overflow accepted answers and 111 Java open source projects.
+We used two clone detection tools to discover 270,429,422 similar code snippet pairs and manually investigated 3,450 candidate clone pairs between Java code snippets obtained from Stack Overflow accepted answers and 111 Java open source projects.
 
@@
 
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.8\linewidth]{exp_framework}
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{exp_framework_new}
 	\caption{Experimental framework}
 	\label{fig:exp_framework}
-\end{figure*}
+\end{figure}
 
@@
 We processed two datasets, Stack Overflow and 111 open source projects from Qualitas corpus.
-Java code fragments were extracted from Stack Overflow posts using regular expressions.
+Java code snippets were extracted from Stack Overflow posts using regular expressions.
 We prepared Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection.
@@
 
-\begin{table*}
-	\centering
-	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering. The last column shows the number of true positive clone pairs after the manual investigation. }
-	\label{tab:online_clone_pairs}
-	\small
-	\begin{tabular}{l|r|c|c|c|c|r|r|r|r}
-		\hline
-		\multirow{2}{*}{Clone set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Candidates} & \multirow{2}{*}{\texttt{equals()}} & \multirow{2}{*}{Manual} & \multirow{2}{*}{TP} \\ \cline{3-6}
-		        		  & \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & & & & \\
-		\hline 
-		\multirow{1}{*}{\textit{good}} & & & & & & 2,261 & 9 & 2,252 & 72 \\
-		\multirow{1}{*}{\textit{ok}} &  & & & & & 9,322 & 9,122 & 200 & 9,240 \\
-		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 & 16,930 & 871 & 704 \\
-		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 & 41 & 127 & 116 \\ 
-		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\hline
-		Total  & 296,746 & & & & & 47,068 & 26,102 & 3,450 & 10,132 \\ 
-		\hline
-	 	\multicolumn{10}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 80\%$, \textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}}
-	\end{tabular} 
-\end{table*}
-
 The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}.
@@
 This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}.
-The average clone size of$S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79.
+The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79.
 Similarly, $N_D$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by $N_E$.
 We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones.
-The average percentage of Stack Overflow code snippets that are cloned according to$S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
-Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 fragments.
-These 11 fragments triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
+The average percentage of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
+Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 snippets.
+These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
 Hence, their clones were removed from further analyses.
@@
 The details are as follows.
+
+\begin{table}
+	\centering
+	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
+	\label{tab:online_clone_pairs}
+	\small
+%	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|c|c|c|c|r}
+		\hline
+		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
+		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
+		\hline 
+		\multirow{1}{*}{\textit{good}} & 2,261 & & & & & 2,261 \\
+		\multirow{1}{*}{\textit{ok}} & 9,322 & & & & & 9,322 \\
+		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
+		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
+		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 \\ 
+		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+		\hline
+		Total  & 296,746 & & & & & 28,832 \\ 
+		\hline
+		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 80\%$,}} \\
+		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
+	\end{tabular} %
+%}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{The online clone classification results}
+	\label{tab:online_clone_pairs}
+	\small
+	%	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r}
+		\hline
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
+		& & Auto & Manual & \\
+		\hline 
+		\multirow{1}{*}{\textit{good}} & 2,261 & 9 & 2,252 & 72 \\
+		\multirow{1}{*}{\textit{ok}} & 9,322 & 9,122 & 200 & 9,240 \\
+		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
+		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 704 \\
+		\multirow{1}{*}{$N_D$} & 168 & 41 & 127 & 116 \\ 
+		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+		\hline
+		Total  & 28,832 & 26,102 & 3,450 & 10,132 \\ 
+		\hline
+	\end{tabular} %
+	%}
+\end{table}
 
@@
 $N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring.
-We had contacted the author of NiCad regarding the issues.
-They found that there problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
+We had contacted the creator of NiCad regarding the issues.
+They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
 As a result, we did not have NiCad clones from these project in the agreed clone pairs.
@@
 
+%\begin{table}
+%	\centering
+%	\caption{No.~of successfully analysed Qualitas projects}
+%	\label{tab:projects_missing}
+%	\small
+%	\begin{tabular}{l|r|r|r|r}
+%		\hline
+%		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
+%		\hline
+%		\textit{Successful} & 111 & 111 & 100 & 96 \\ 
+%		\textit{Clustering fail} & -- & -- & 1 & -- \\
+%		\textit{Renaming fail} & -- &  -- & -- & 5 \\
+%		\hline
+%	\end{tabular}
+%\end{table}
+
 \begin{table}
 	\centering
-	\caption{No.~of successfully analysed Qualitas projects}
-	\label{tab:projects_missing}
-	\small
-	\begin{tabular}{l|r|r|r|r}
-		\hline
-		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
-		\hline
-		\textit{Successful} & 111 & 111 & 100 & 96 \\ 
-		\textit{Clustering fail} & -- & -- & 1 & -- \\
-		\textit{Renaming fail} & -- &  -- & -- & 5 \\
-		\hline
-	\end{tabular}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Distribution of agreed clone pairs}
+	\caption{Distribution of the agreed clone pairs}
 	\label{t_agreed_good_clone_pairs}
@@
 		\hline
-		\textit{good} & 10 & 26 & 10 & 2,228 & 2,321 & 2,308 \\
-		\textit{ok} & 9,042 & 991 & 78 & 17,549 & 27,670 & 26,838 \\
+		\textit{good} & 10 & 26 & 10 & 2,228 & 2,274 & 2,261 \\
+		\textit{ok} & 9,049 & 993 & 79 & 19,777 & 29,898 & 29,058 \\
 		\hline
@@
 
-The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:venn4_orig_good}.
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{good-ok_pairs-crop}
+	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) in 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
+	\label{fig:good-ok-pairs}
+\end{figure}
+
+The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:good-ok-pairs}.
 There are 2,261 unique \textit{good} pairs consisting of 10 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$.
 There are 26,838 unique \textit{ok} pairs (excluding the subsumed 2,261 \textit{good} pairs).\footnote{According to the definition, \textit{ok} clone pairs always subsume the \textit{good} pairs.} We obtained 9,052; 991; 78; and 17,549 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively.
-Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:venn4_orig_ok}), but there is no clone pair that is agreed by all four combinations.
+Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair that is agreed by all four combinations.
 %If we remove duplicates, the number of unique ok-match pairs is 26,838.
@@
 
-\begin{figure*}
-	\begin{minipage}{.5\textwidth}
-		\centering
-		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3+fixed_nicad-crop}
-		\caption{Distributions of \textit{good} pairs}
-		\label{fig:venn4_orig_good}
-	\end{minipage}
-	\begin{minipage}{.5\textwidth}
-		\centering
-		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3+fixed_nicad-crop}
-		\caption{Distributions of \textit{ok} pairs}
-		\label{fig:venn4_orig_ok}
-	\end{minipage}
-\end{figure*}
+%\begin{figure*}
+%	\begin{minipage}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3+fixed_nicad-crop}
+%		\caption{Distributions of \textit{good} pairs}
+%		\label{fig:venn4_orig_good}
+%	\end{minipage}
+%	\begin{minipage}{.5\textwidth}
+%		\centering
+%		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3+fixed_nicad-crop}
+%		\caption{Distributions of \textit{ok} pairs}
+%		\label{fig:venn4_orig_ok}
+%	\end{minipage}
+%\end{figure*}
 
@@
 They are 2,261 \textit{good} pairs, 26,838 \textit{ok} pairs.
-XXX After a manual investigation, we found at least 523 online code clones pairs are true clones.}
+After classification, we found at least 523 online code clones pairs that are true clones between Stack Overflow and Qualitas.}
 
@@
 We started by studying the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008}.
-We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow fragments.
+We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow snippets.
 This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study.
-Using$S_D$ clone report, fragments are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the fragment size.
-We then picked the top 10 fragments from the 4 groups resulting in 34 Stack Overflow fragments chosen (there were some overlaps).
+Using$S_D$ clone report, snippets are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the snippet size.
+We then picked the top 10 snippets from the 4 groups resulting in 34 Stack Overflow snippets chosen (there were some overlaps).
 The 34 selected snippets generate 697 clone pairs.
@@
 
-\subsubsection{Manual Investigation of Clone Candidates}
-
-The first author who has been working on clone detection research for two years takes the role of a main investigator performing manual investigation of all 3,450 clone pairs.
-The third author takes the role of a second investigator performing 10\% validation of the clone pairs judged by the main investigator.
-Following the cloning patterns, the main investigator manually goes through each agreed clone pair, looks at the clones, and chooses the most appropriate cloning pattern for the pair.
-A relevant and useful observation is also recorded for each clone pair.
+\subsubsection{Classification of Clone Candidates}
+
+There were 28,832 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}.
+We have use regular expressions to automatically classify \texttt{equals()} methods based on the method signature since they are not very interesting clones.
+It captured 26,102 clone pairs and classified them into pattern D.
+With help of the automatic classification, there were 3,450 pairs left for manual classification.
+
+The first author who has been working on clone detection research took the role of a main investigator performing manual classification of all the 3,450 clone pairs.
+The second author took the role of a second investigator performing 10\% validation of the clone pairs (345 pairs) judged by the main investigator.
+By consulting the cloning patterns, the main investigator manually went through each agreed clone pair, looked at the clones, and chose the most appropriate cloning pattern for the pair.
+A relevant and useful observation was also recorded for each clone pair.
+The two investigators discussed and resolved 51 classification conflicts.
+There are three conflicts which the investigators could not find consensuses hence the third author was involved to solve the conflicts.
 
@@
 	\end{lstlisting}
-	\caption{Outdated code fragment on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains heavy modifications.}
+	\caption{Outdated code snippet on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains heavy modifications.}
 	\label{fig:hibernate_outdated_code}
@@
 Later, German et al.~\cite{German2010} created Ninka, a tool to automate identification of software license from program source code.
-We use Ninka to analyse software license from Stack Overflow fragments and Qualitas projects.
+We use Ninka to analyse software license from Stack Overflow snippets and Qualitas projects.
 
@@
 We discovered 96 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
-By comparing the clones to their latest versions in the software, we found that 58 code fragments on Stack Overflow are outdated and harmful for reuse.
+By comparing the clones to their latest versions in the software, we found that 58 code snippets on Stack Overflow are outdated and harmful for reuse.
 

### 2017-01-29 cloneoverflow-latex/cloneoverflow.tex
Added Gabel and Su.
Updated the number of ok pairs

@@
 		\hline
-		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 80\%$,}} \\
+		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,}} \\
 		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
@@
 For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}.
+Moreover, Gabel and Su show that unique code tend to be larger than seven lines \cite{Gabel2010}.
 The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods, getters and setters using regular expressions and removes them.
@@
 An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers.
-Stack Overflow has a voting mechanism that may mitigate this outdated code issue.
-Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment.
+Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive to naive developers who are ignorant.
+%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment.
 They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated).
-However, if the answer is marked as accepted by the person who asks the question (which is our case), it is always ranked on the top and still attractive to naive developers who are ignorant.
+However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.
 

### 2017-01-30 cloneoverflow-latex/cloneoverflow.tex
Updated the paper.

@@
 The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}.
-From \Cref{tab:raw_stats}, Simian clones cover approximately 10\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,530 from $S_E$ respectively.
-$N_D$ reports clones in 1,240 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations.
-In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,372,599 and 206,760,077 respectively.
+From \Cref{tab:raw_stats}, Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,531 from $S_E$ respectively.
+$N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations.
+In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,635,844 and 251,449,849 respectively.
 This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}.
 The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79.
-Similarly, $N_D$ has an average clone size of 9.64 lines which is bigger than 5.32 reported by $N_E$.
+Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 reported by $N_E$.
 We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones.
 The average percentage of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
-Preliminary manual investigation of Simian's clone report revealed that there were problematic 11 snippets.
+A quick manual check of Simian's clone report revealed that there were problematic 11 snippets.
 These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
@@
 
-As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} agreed clone pairs is 2,261 while \textit{ok} is 26,838.
-The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 168 for Simian and NiCad respectively.
+As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} agreed clone pairs is 2,308 while \textit{ok} is 11,749.
+The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively.
+The total number of clone candidates is 32,039 pairs.
 The details are as follows.
@@
 		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,261 & & & & & 2,261 \\
-		\multirow{1}{*}{\textit{ok}} & 9,322 & & & & & 9,322 \\
+		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
+		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
 		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 168 \\ 
+		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 181 \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total  & 296,746 & & & & & 28,832 \\ 
+		Total  & 310,803 & & & & & 32,039 \\ 
 		\hline
@@
 	\caption{The online clone classification results}
-	\label{tab:online_clone_pairs}
+	\label{tab:online_clone_classification_results}
 	\small
@@
 		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,261 & 9 & 2,252 & 72 \\
-		\multirow{1}{*}{\textit{ok}} & 9,322 & 9,122 & 200 & 9,240 \\
+		\multirow{1}{*}{\textit{good}} & 2,308 & 9 & 2,299 & x \\
+		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,495 & 254 & x \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
 		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 704 \\
-		\multirow{1}{*}{$N_D$} & 168 & 41 & 127 & 116 \\ 
+		\multirow{1}{*}{$N_D$} & 181 & 10 & 171 & x \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total  & 28,832 & 26,102 & 3,450 & 10,132 \\ 
+		Total  & 32,039 & 28,444 & 3,595 & x \\ 
 		\hline
@@
 %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-We encountered NiCad failures with a few Qualitas projects. 
-%\FIXME{Reported the errors to NiCad creator. Cordy said it might be a long-path problem. Should we try fixing?}  
-$N_D$ could not detect clones in Hibernate due to clustering errors.
+We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in Hibernate due to clustering errors.
 $N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring.
@@
 They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
-As a result, we did not have NiCad clones from these project in the agreed clone pairs.
+As a result, we did not have NiCad clones from these projects in the agreed clone pairs.
 Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.
-
-%\begin{table}
-%	\centering
-%	\caption{No.~of successfully analysed Qualitas projects}
-%	\label{tab:projects_missing}
-%	\small
-%	\begin{tabular}{l|r|r|r|r}
-%		\hline
-%		Execution & $S_D$ & $S_E$  & $N_D$ & $N_E$ \\ 
-%		\hline
-%		\textit{Successful} & 111 & 111 & 100 & 96 \\ 
-%		\textit{Clustering fail} & -- & -- & 1 & -- \\
-%		\textit{Renaming fail} & -- &  -- & -- & 5 \\
-%		\hline
-%	\end{tabular}
-%\end{table}
 
@@
 		\hline
-		\textit{good} & 10 & 26 & 10 & 2,228 & 2,274 & 2,261 \\
-		\textit{ok} & 9,049 & 993 & 79 & 19,777 & 29,898 & 29,058 \\
+		\textit{good} & 18 & 26 & 10 & 2,267 & 2,321 & 2,308 \\
+		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 32,560 & 31,729  \\
 		\hline
@@
 The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:good-ok-pairs}.
-There are 2,261 unique \textit{good} pairs consisting of 10 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,228 pairs from $S_EN_E$.
-There are 26,838 unique \textit{ok} pairs (excluding the subsumed 2,261 \textit{good} pairs).\footnote{According to the definition, \textit{ok} clone pairs always subsume the \textit{good} pairs.} We obtained 9,052; 991; 78; and 17,549 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively.
+There are 2,321 (2,308 unique) \textit{good} pairs consisting of 18 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,267 pairs from $S_EN_E$.
+There are 32,560 (11,749 unique) \textit{ok} pairs\footnote{This excludes the subsumed 2,308 \textit{good} pairs.
+According to the definition, \textit{ok} pairs always subsume \textit{good} pairs.} We obtained 11,467; 993; 79; and 20,021 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively.
 Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair that is agreed by all four combinations.
-%If we remove duplicates, the number of unique ok-match pairs is 26,838.
-
-%\FIXME{Maybe no longer needed?} We are interested in discovering reused code in the latest versions of Qualitas projects.
-So, we downloaded the newest release of each project and found 44 of them having newer updates.
-Then, we reran the experiment again on these 44 projects.
-Several projects triggered NiCad problem of clustering and renaming again as listed in Table \{tab:projects_missing}.
-The agreed clone pairs using Bellon's \textit{good}(0.7) and ok-match(0.7) criteria of this new dataset are also listed in Table \{t_agreed_good_clone_pairs}.
-
-%\begin{figure*}
-%	\begin{minipage}{.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{venn4_pairs_good_pt1+2+3+fixed_nicad-crop}
-%		\caption{Distributions of \textit{good} pairs}
-%		\label{fig:venn4_orig_good}
-%	\end{minipage}
-%	\begin{minipage}{.5\textwidth}
-%		\centering
-%		\includegraphics[width=0.7\linewidth]{venn4_pairs_ok_pt1+2+3+fixed_nicad-crop}
-%		\caption{Distributions of \textit{ok} pairs}
-%		\label{fig:venn4_orig_ok}
-%	\end{minipage}
-%\end{figure*}
 
 \subsubsection{Disagreed clone pairs}
-%In the preliminary stage of our experiment, we found that there are 41 Stack Overflow fragments reported by Simian with default configurations.
-However, only 10 of them appear in the new results using tool's agreement.
-Thus, we further investigated the clone pairs reported by Simian and NiCad but \textit{without} an agreement.
-
-The disagreed clone pairs are clone pairs that are reported by a tool, either Simian or NiCad, and do not have agreement with clones from another tool.
-The disagreement can be from misalignment of clone lines or different configurations that result in dissimilar clones reported.
-They also cover clone pairs in projects having NiCad's errors (6 projects for $N_D$ and 27 for $N_E$) that are automatically missing from the agreed clone pairs.
-With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and drop $S_E$ and $N_E$ due to their enormous amount of clone pairs (59 and 206 millions respectively).
-$S_E$ and $N_E$ also have a high possibility of containing a large number of false positives due to relaxation of their EvaClone configurations.
-
-Even choosing only the default configurations, the number of clone pair candidates are still very large.
-We hence apply three filters: \textbf{clone size, regular expression, and similarity threshold}.
+
+The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with clones from another tool.
+The disagreement can be from misalignment of clone lines or totally dissimilar clones due to different configurations.
+Disagreed pairs from Simian also cover clone pairs in projects having NiCad's errors (1 projects for $N_D$ and 5 for $N_E$) that are automatically missing from the agreed clone pairs.
+With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and drop $S_E$ and $N_E$ due to their enormous amount of clone pairs (60 and 250 millions respectively).
+Moroever, without clone agreement, $S_E$ and $N_E$ contain a large number of false positives due to the recall preference of their EvaClone configurations.
+
+Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 229,176 pairs for $N_D$).
+We hence apply four filters: \textbf{clone size, regular expression, similarity threshold, and good/ok pairs}.
 For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}.
 Moreover, Gabel and Su show that unique code tend to be larger than seven lines \cite{Gabel2010}.
-The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clone pairs only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods, getters and setters using regular expressions and removes them.
+The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clones only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods and some of the obvious getters and setters using regular expressions and removes them.
 The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration.
-%We increase the similarity threshold of NiCad clone pairs from 70\% to 80\%.
-%Using the filter along with regular expressions to capture boiler-plate code clones such as \verb|equals()| and \verb|hashcode()|, we can reduce the number of Simian clone candidates to a manageable amount of 795 clone pairs.
-
-% It results in 159 clone pairs remaining. The summary of disagreed clone pairs before and after filtering is shown in \Cref{tab:classification_indv_stats}.
-% 9,383 (part 1) + 9,042 (part 2) + 1,923 (part 3) = 20,348 %
-As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and regular expressions.
-The combination of the two filters reduce the number of $S_D$ clones to 17,801 pairs for manual investigation.
-% 7062 + 22187 + 6755 =  36004 %
+The last filter, good/ok pairs, filters the pairs that already exist in \textit{good} or \textit{ok} set to avoid duplicates.
+
+As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs.
+The combination of the three filters reduce the number of $S_D$ clones to 17,801 pairs for manual investigation.
 For $N_D$, 10-line threshold is already a minimum NiCad's clone size.
-However, NiCad still reported much more clones than Simian since it can detect type-3 clones.
-Thus, we filtered NiCad's clones by using similarity threshold and regular expressions.
-We increase NiCad's similarity threshold from 70\% to 80\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.2).
-We have tried varying the UPI from 70\%, 80\% and 90\% and we found that 80\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation.
-Using the two filters, we reduced the size of $N_D$ clones to 168 pairs.
-
-%However, 10-line threshold is already a minimum NiCad's clone size and regular expressions could not be used effectively as in Simian's case since NiCad detects type-3 clones as well.
-So .
-Using 80\% similarity, there are totally 166 pairs left.
-%There are 450 ok-match pairs which we ignore, thus 168 clone pairs remaining for manual investigation.
-%The statistics of the clones and classification results are reported in \Cref{tab:classification_indv_stats}.
-
-In our manual investigation process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 26,102 pairs out of 47,068 (more than half of the \texttt{equals()} pairs came from $S_D$).
-Finally, there are 3,450 pairs remaining which we manually investigated them.
-\textbf{To answer RQ1, we found 47,068 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
-They are 2,261 \textit{good} pairs, 26,838 \textit{ok} pairs.
-After classification, we found at least 523 online code clones pairs that are true clones between Stack Overflow and Qualitas.}
+However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones.
+Thus, besides regular expressions and good/ok pair filters, we filtered NiCad's clones further by a stricter similarity threshold.
+We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.15).
+We have tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and we found that 85\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation.
+Using the three filters, we reduced the size of $N_D$ clones to 181 pairs.
+
+In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 32,039 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs).
+Finally, there are 3,595 pairs remaining which we manually classified them.
+The classification summary is shown in \Cref{tab:online_clone_classification_results}.
+
+\textbf{To answer RQ1, we found 32,039 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
+They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 181 $N_D$ pairs.
+After classification, we found at least \FIXME{NUMBER} online code clones pairs that are clones between Stack Overflow and Qualitas.}
 
@@
 			\hline 
-			A & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
-			\hline 
-			A' &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
-			\hline 
-			B & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
+			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
+			\hline 
+			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
+			\hline 
+			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
 			\\ 
 			\hline 
-			C & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
+			ES & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
 			\\ 
 			\hline 
-			D & Boiler-plate or IDE auto-generated
+			BP & Boiler-plate or IDE auto-generated
 			\\ 
 			\hline 
-			E & Inheritance, interface implementation 
+			IN & Inheritance, interface implementation 
 			\\ 
 			\hline 
-			F & Accidental similarity, false clones by normalisation \\ 
+			FC & Accidental similarity, false clones \\ 
 			\hline 
@@
 Besides the quantitative analysis, we are also interested in a qualitative analysis of the online clones.
-Why are they created and how?
-Due to an absence of clone oracle of the two data sets, we resort to manual investigation to validate the clone pair candidates as either true or false positives.
-At the same time, we select a reason that stimulates a creation of each online clone pair.
-%We need an appropriate clone classification scheme to meaningfully categorise the selected clone candidates by hand.
-
-We started by studying the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008}.
-We use the patterns to classify 697 clone pairs associated with 34 sampled Stack Overflow snippets.
+How are the clone pairs created?
+%Due to an absence of clone oracle of the two data sets, we resort to a manual investigation to classify the clone pair candidates using our 7 patterns of online code cloning.
+
+We started by a preliminary study of the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008}.
 This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study.
-Using$S_D$ clone report, snippets are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the snippet size.
-We then picked the top 10 snippets from the 4 groups resulting in 34 Stack Overflow snippets chosen (there were some overlaps).
-The 34 selected snippets generate 697 clone pairs.
-Using Kapser's cloning patterns, the 697 clone pairs were categorised into either Customisation or Templating.
-Clearly \textbf{Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.}
-
-We adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as category D, and added 6 new patterns observed as common cloning patterns from our preliminary investigation.
-The seven patterns ranging from A--F as presented in \Cref{tab:classification_scheme}.
-Pattern A is a cloning that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post).
-Pattern A' is the opposite of A.
-Pattern B is a cloning that is exactly identical or highly similar but without any attribution of copying.
-Pattern C is a cloning that has an evidence of copying from the same external source.
-Pattern D is either boiler-plate code (e.g.~\verb|equals()| methods, or getters and setters) or IDE-generated (e.g.~GUI initialisation).
-Pattern E is inheritance of the same super class or implementation of the same interface.
+Using $S_D$ clone report, snippets are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the snippet size.
+We selected these criteria so that we can cover clones across various aspects.
+We then picked the top 10 snippets from the 4 groups resulting in 34 unique Stack Overflow snippets chosen.
+The 34 snippets generate 697 clone pairs with Qualitas projects.
+Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating.
+\textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.}
+
+Nevertheless, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as pattern BP.
+We then added 6 new patterns observed as common cloning patterns from our preliminary study.
+The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}.
+QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post).
+Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS.
+UD (\textbf{U}nknown \textbf{D}irection) is a cloning that is exactly identical or highly similar but without any attribution of copying.
+ES (\textbf{E}xternal \textbf{S}ources) is a cloning that has an evidence of copying from an external source(s).
+Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components).
+Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface.
 They usually share similar overriding methods.
-The last pattern, F, is a false clone pair.
-They can be either accidentally similar (e.g.~similar try-catch statements) or similar after code normalisation process.
-Using this cloning pattern classification scheme, we consider clone pairs in created by pattern A, A', B, C, D, and E as true positive, and F as false positive.
+The last pattern, FC (\textbf{F}alse \textbf{C}lones), represents false clone pairs.
+They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools.
+Using the classification patterns, we can also calculate the number of true and false positives.
+We are looking for unique and meaningful clones in this study.
+Thus, we consider clone pairs classified into pattern QS, SQ, and UN as true positive, and BP, IN, and FC as false positive.
 
@@
 
-There were 28,832 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}.
+There were 32,039 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}.
 We have use regular expressions to automatically classify \texttt{equals()} methods based on the method signature since they are not very interesting clones.
-It captured 26,102 clone pairs and classified them into pattern D.
-With help of the automatic classification, there were 3,450 pairs left for manual classification.
-
-The first author who has been working on clone detection research took the role of a main investigator performing manual classification of all the 3,450 clone pairs.
-The second author took the role of a second investigator performing 10\% validation of the clone pairs (345 pairs) judged by the main investigator.
-By consulting the cloning patterns, the main investigator manually went through each agreed clone pair, looked at the clones, and chose the most appropriate cloning pattern for the pair.
+It captured 28,444 clone pairs and classified them into pattern D.
+With help of the automatic classification, there were 3,595 pairs left for manual classification.
+
+The first author who has been working on clone detection research for two years took the role of a main investigator performing a manual classification of all the 3,595 clone pairs.
+By consulting the cloning patterns, the main investigator manually went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair.
 A relevant and useful observation was also recorded for each clone pair.
-The two investigators discussed and resolved 51 classification conflicts.
-There are three conflicts which the investigators could not find consensuses hence the third author was involved to solve the conflicts.
-
-\textbf{Agreed clone pairs}: the classification results are shown in \Cref{tab:classification_good_o}.
-We have manually investigated 2,261 \textit{good} clone pairs.
-There is one clone pair in pattern A which is found to be copied from a Qualitas project to Stack Overflow.
-Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as pattern B.
-We observed 3 pairs in pattern C since they are copied from external sources.
-%The rest are boilter-plate, inherit/interface, and false positive clones.
-58 clone pairs are found to be pattern D: \verb|equals()| methods, or getters and setters.
-Six pairs are similar code from inheriting the same superclass or implementing the same interface, pattern E.
-Finally, 2,189 clone pairs are categorised to F which means they are false clones.
-
-For the \textit{ok} clone pairs, we could not feasibly investigate all 23,868 pairs manually.
-According to the manual investigation of \textit{good} pairs, we found that $S_EN_E$ produces a large number of 2,253 false positive results (accounts for 99.87\% of $S_EN_E$ clone pairs) due to its recall preference.
-We thus decided to leave this configuration out of the manual investigation.
-There are totally 4,625 \textit{ok} pairs that were investigated.
-We found 8, 29, and 10 in pattern A, B, and C respectively.
-There were 77 boilter-plate pairs, and 3 inherit/interface pairs.
-82 pairs were false positives.
-%The 47 true positive pairs found are combinations of 8, 29, and 10 clone pairs in category A, B, and C respectively.
-
-%\FIXME{Maybe remove?} We cannot be certain about the direction of copying in the category-B pairs, since there is no solid information of copying.
-We thus checked the timestamp of each Java file in Qualitas project and compared it to their respective timestamp of Stack Overflow posts.
-We found that all Stack Overflow posts were created after their respectively Qualitas Java files \FIXME{check again since the dataset is updated}.
-This means that the copying can only be either (1) from Qualitas to Stack Overflow or (2) from an external source to both Stack Overflow and Qualitas independently.
-There is no clone pairs found in A' category.
-
-%\textbf{Qualitas-\textbf{N}:} We decided to filter out the agreed clone pairs reported by agreement of Simian$_{\mathrm{\textit{EvCl}}}$--NiCad$_{\mathrm{\textit{EvCl}}}$ altogether due to its large number of false positive.
-With the remaining 3 agreements, we did manual investigation of agreed ok-match clone pairs from agreements of$S_DN_D$,$S_D$--NiCad$_{\mathrm{\textit{EvCl}}}$, and Simian$_{\mathrm{\textit{EvCl}}}N_D$.
-We had not done any investigation of \textit{good} since there were no \textit{good} pairs for these 3 agreements.
-The number of pairs that have been looked at is 6,706 (excluding duplicates).
-The results are shown in Table.
+The second author took the role of a validating investigator performing 10\% validation (359 pairs) of the clone pairs judged by the main investigator.
+The two investigators discussed 54 classification conflicts and resolved 51 of them.
+The 3 conflicts which the two investigators could not find consensuses are resolved after involving the third author.
+
+The classification results are shown in \Cref{tab:classification_good_o}.
+For \textit{good} pairs, 9 pairs were automatically classified by regular expressions and 2,299 pairs were manually classified.
+This resulted in one clone pair in pattern QS which is found to be copied from a Qualitas project to Stack Overflow.
+Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as pattern UD.
+We observed 3 pairs in pattern ES since they are copied from external sources.
+58 clone pairs are found to be pattern BP.
+Six pairs are similar code from inheriting the same superclass or implementing the same interface, pattern IN.
+Finally, 2,189 pairs are false clones and classified into FC.
+No clones were found in pattern SQ.
+This was expected since we selected a pretty old Qualitas snapshot dated back 2013 and most of the code could be written long before that.
+
+For the \textit{ok} clone pairs, we could not feasibly investigate all 31,729 pairs manually.
+Consulting the classification of \textit{good} pairs, we found that $S_EN_E$ produces a large number of x,xxx false positive results (accounts for xx.xx\% of $S_EN_E$ clone pairs) due to its recall preference.
+We thus decided to ignore this clone set in our \textit{ok}-pair classification.
+A large number of 11,495 clone pairs were automatically classified and 254 pairs were done manually.
+We found xx, xx, xx, xx, xx, and xx in QS, UD, ES, BP, IN and FC respectively.
+Similarly, no clone pairs were found in SQ.
 
@@
 
-%\subsubsection*{\textbf{Qualitas-\textit{O} (v. 2013-09-01r)}}
-\textbf{Disagreed clone pairs}: we performed a manual investigation and classification of 871 $S_D$ and 168 $N_D$ clone pairs in the same way as the agreed ones.
-There were 19 pairs in pattern A, 336 pairs in B, 17 pairs in C, 209 in D, and 63 in E.
-167 pairs are false clones.
-For $N_D$, there are 8 pairs in pattern A, 27 pairs in B, 1 pair in C, 77 pairs in D, and 3 pairs in E.
-$N_D$ reported 82 false positive clones.
-%The total number of true positive clone pairs is 523 as described in \Cref{tab:classification_good_o}.
-
-%\subsubsection{Qualitas-\textit{N} (v. 2016-08-05)}
+For disagreed clone pairs, an automatic and manual classification of 17,801 $S_D$ and 181 $N_D$ clone pairs results in xx pairs in pattern QS, xx pairs in UD, xx pairs in ES, xx in BP, xx in IN and xx in FC.
 
@@
 Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated \cite{Xia2014}.
-Usually code clone detection is used to locate clone instances and update them according to their updated original code \cite{Bellon2007}.
-However, in this situation, the clones are more pervasive on Stack Overflow posts and more difficult to detect due to its large scale and the mix of natural language and source code.
+Usually code clone detection is used to locate clone instances and update them to match with the original code \cite{Bellon2007}.
+However, in this situation, the clones are pervasive on Stack Overflow posts and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts.
+Moreover, Stack Overflow is not a software.
+There is no test suite to run and check whether the code snippets are still working as expected.
+Hence, if any change happens in the original code, our results show that the copies on Stack Overflow are still mostly left outdated.
+
+As far as we know, our work is possibly the first which discovers outdated code on Stack Overflow.
 Since code can be updated due to various possible reasons, e.g.~bug fixing or API changes, it is risky if developers reuse outdated code snippets from Stack Overflow.
-%They possibly also introduce vulnerabilities into the software.
 They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce bugs or vulnerabilities into their software.
 
-To check if the discovered Stack Overflow clones are outdated, we focused on the 96 pattern-A clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}).
-For each code snippet, we could track its origin from its Qualitas counterpart.
-Relying on git repositories of Qualitas projects, we located the latest version of the each file and compared to the Stack Overflow snippet to see if any change has been made to the source code.
+To check if the discovered Stack Overflow clones are outdated, we focused on the 96 QS clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}).
+For each code snippet, we tracked its original code in Qualitas projects.
+We located the latest version of the each file and compared to the Stack Overflow snippet to see if any change has been made to the source code.
 If we found any change, we used \textit{git blame} command to see who modified the source code and when.
 
-%We restricted it further to only the ones having versioning system so we can trace changes made to these clone pairs.
-Fortunately, all of the pairs were from projects with either git or svn so we did not remove any pair from this set.
-%Our intuition behind his issue comes from a situation where a piece of code has been copied from a Qualitas project and posted on Stack Overflow.
-Later, that piece of code has been modified further to accommodate changes in the projects (or any other reasons).
-However, even the code in Qualitas project is already updated, the one posted on Stack Overflow is not changed.
-This results in outdated online code which can cause problems when programmers copy and use it in their projects.
-%We decided to ignore NiCad results from this analysis due to its failure of clone clustering and renaming on some projects.
-Thus, the 39 projects are the ones that can be analysed by Simian, have newer versions than the versions in Qualitas-\textit{O}, and have code version control system (either git or svn).
-%After filtering, there are 141 pairs removed because 45 of them do not have new versions (7 from c-jdbc, 21 from Compiere, 7 from heritrix, and 10 from iReport) and 4 of them we could not find source code with version control (2 from findbugs, 1 from jag, and 1 from jgraphpad).
-Finally there were 134  pairs remaining.
-%We are interested in clone pairs that were changed after they appeared on Stack Overflow.
-
-\Cref{fig:outdated} shows the findings of outdated clone investigation.
-The comparison with the clones' latest versions revealed that 55 clone pairs were outdated.
-These were clone pairs that were copied from Qualitas to Stack Overflow and later marked as accepted answers.
-Hadoop and Spring have the maximum number of 9 outdate code clones, followed by 6 clones from Tomcat, and 5 clones from Eclipse-SDK.
-An example of outdated code in hadoop's \textit{WritableComparator.java} is shown in \Cref{fig:before-after}.
-The newest version has one line added.
-We also found outdated code which contained heavy modifications.
+\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow.
+The comparison with the clones' latest versions revealed that 55 clone pairs were outdated and they were all Stack Overflow accepted answers.
+Hadoop and Spring have the maximum number of 9 outdated code clones, followed by 6 from Tomcat, and 5 from Eclipse-SDK.
+An example of outdated code in hadoop's \textit{WritableComparator.java} is shown in \Cref{fig:before-after} as we discussed before.
+We also found a few outdated code which contained heavy modifications.
 For example, the code snippet in Stack Overflow post 23520731, a copy of \textit{SchemaUpdate.java} in Hibernate, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
-Moreover, the code snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring, was deleted in the commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02 two years after it was posted.
-The latest version of Spring does not contain the file anymore.
-
-The outdate online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagation.
+Lastly, we found some ``orphan'' snippets.
+These snippets cannot find their originals in the latest version of the projects anymore.
+For example, the snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted.
+%The latest version of Spring does not contain the file anymore.
+
+The outdated online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagations.
 An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers.
@@
 \subsection{RQ4: Software Licensing Violation}
-Software licensing is important in software development. Violation of software license can cause major impacts to software delivery and also lead to legal issues \cite{Sprigman2015}. 
+Software licensing plays an important role in software development. Violation of software licenses impacts software delivery and also leads to legal issues \cite{Sprigman2015}. 
 %It is an emerging area that software engineering research community is paying attention to. For example, 
-Software licenses keep evolving in open source projects \cite{DiPenta2010} and clones can have different license~\cite{German2009}.
-This can lead to licensing violation if one does not check the license before integration third-party source code into their software.
+One can run into licensing issue if they do not check before integration third-party source code into their software.
 A study by An et al.~\cite{An2017} found 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code.
@@
 We found with evidence that 96 pieces of code had been copied from 14 Qualitas projects to Stack Overflow as code examples.
-They are also marked as accepted answers which increased their probabilities of being reused.
+They are also marked as accepted answers which increased their chances of being reused.
 The 14 open source projects came with their respective software licenses (shown in \Cref{t:q_projects_license}).
@@
 The table shows license of Stack Overflow snippets (denoted as SO) and Qualitas source code.
-The number of clone pairs of each license matching has been grouped according to online cloning patterns A, B, and C.
+The number of clone pairs of each license matching has been grouped according to online cloning patterns QS, UD, and ES.
 In overall, we can see that most of the Stack Overflow snippets do not have licensing terms with them while their clone counterparts in Qualitas project do.
 
-\textbf{No license or compatible license:} There are 85 clone pairs in type \textit{NL} which do not have licensing information (None vs.~None) and 13 pairs in type \textit{CL} which have compatible licenses (Apache2 vs.~Apache2; EPLv1 vs.~EPLv1; None vs.~CC BY 3.0).
+\textbf{No license or compatible license:} There are 85 \textit{NL} clone pairs which do not have licensing information (None vs.~None) and 13 pairs in type \textit{CL} which have compatible licenses (Apache2 vs.~Apache2; EPLv1 vs.~EPLv1; None vs.~CC BY 3.0).
 They are safe for being reused.

### 2017-01-31 cloneoverflow-latex/cloneoverflow.tex
Improved the diagram and text

@@
 
-In this study, we treat code snippets that are copied from software systems to Stack Overflow, and vice versa, as code clones.
-We call them \textbf{online code clones} (or sometimes only call \textbf{clones} for brevity).
-There are four ways to create online code clones: (1) code is cloned from a software project to Stack Overflow as an example; (2) code is cloned from Stack Overflow to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having Stack Overflow as a medium; and (4) code is cloned from an external source to both a software project and Stack Overflow.
-\textbf{Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.} Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.
+We call code snippets that are copied from software systems to online Q\&A websites (such as Stack Overflow), and vice versa as ``online code clones'' (sometimes only ``clones'' for brevity).
+There are four ways to create online code clones: (1) code is cloned from a software project to a Q\&A website as an example; (2) code is cloned from a Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having a Q\&A website as a medium; and (4) code is cloned from an external source to both a software project and a Q\&A website.
+Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.
+Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.
+
+In this study, we are interested in locating online code clones on Stack Overflow that are cloned from open source projects and study them on two aspects: obsoleteness and licensing issues.
 
@@
 
-A motivating example of outdated code in online code clones can be found in the a Stack Overflow post regarding how to implement \textit{RawComparator} in Hadoop\footnote{http://stackoverflow.com/questions/22262310}.
+A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement \textit{RawComparator} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}.
 In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
-The snippet shows how Hadoop implements \textit{compare} method in its \textit{WritableComparator} class.
-The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of Hadoop.
+The snippet shows how \texttt{hadoop} implements \textit{compare} method in its \textit{WritableComparator} class.
+The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of \texttt{hadoop}.
 We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, is added in the latest version after \verb|key2.readFields(buffer);|.
 The added line is intended for cleaning up the reference in \verb|buffer| variable.
-While this change has already been introduced into \textit{compare} method in the latest version of Hadoop, the code example in Stack Overflow post is still unchanged.
+While this change has already been introduced into \textit{compare} method in the latest version of \texttt{hadoop}, the code example in Stack Overflow post is still unchanged.
 This example shows that there can be inconsistencies between online code clones and its original.
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 270,429,422 similar code snippet pairs and manually investigated 3,450 candidate clone pairs between Java code snippets obtained from Stack Overflow accepted answers and 111 Java open source projects.
+We used two clone detection tools to discover 315,786,118 similar code snippet pairs and manually investigated 3,595 candidate clone pairs between Java code snippets obtained from Stack Overflow accepted answers and 111 Java open source projects.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of reusing source code between open source projects and Stack Overflow:} Our study shows that there are at least 523 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses.
+\noindent\textbf{2.~Addressing the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 523 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses.
 Importantly, 53 out of the 96 online code clones on Stack Overflow are outdated and questionable for being reused.
@@
 \vspace{0.5ex}%
-\noindent\textbf{3.~Online code clone oracle:} The 3,450 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.
+\noindent\textbf{3.~Online code clone oracle:} The 3,595 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.
 
@@
 The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow.
-Out of 112 Qualitas projects, there is one project, \textit{jre}, that does not contain Java source code due to its licensing limitation \cite{QualitasCorpus} so it is removed from the study.
+Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation \cite{QualitasCorpus} so it is removed from the study.
 This resulted in total of 111 projects analysed in the study.
@@
 	\centering
-	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
+	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations \FIXME{boxplots here?}}
 	\label{tab:raw_stats}
@@
 %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in Hibernate due to clustering errors.
-$N_E$ generated renaming errors for 5 projects including Vuze, Hibernate, Myfaces, Netbeans, and Spring.
+We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \texttt{hibernate} due to clustering errors.
+$N_E$ generated renaming errors for 5 projects including \texttt{vuze}, \texttt{hibernate}, \texttt{myfaces}, \texttt{netbeans}, and \texttt{spring}.
 We had contacted the creator of NiCad regarding the issues.
@@
 They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 181 $N_D$ pairs.
-After classification, we found at least \FIXME{NUMBER} online code clones pairs that are clones between Stack Overflow and Qualitas.}
+After classification, we found at least \FIXME{NUMBER} online code clones pairs between Stack Overflow and Qualitas.}
 
@@
 	\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{|c|p{8.4cm}|}
+		\begin{tabular}{c|p{8.4cm}}
 			\hline 
@@
 Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS.
-UD (\textbf{U}nknown \textbf{D}irection) is a cloning that is exactly identical or highly similar but without any attribution of copying.
+UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones but without any attribution of copying.
+They are unique enough not be boiler-plate and inheritance or interface implementation.
 ES (\textbf{E}xternal \textbf{S}ources) is a cloning that has an evidence of copying from an external source(s).
@@
 
+\textbf{To answer RQ2, we found that ...}
+
 \subsection{RQ3: Outdated Online Code Clones}
@@
 The comparison with the clones' latest versions revealed that 55 clone pairs were outdated and they were all Stack Overflow accepted answers.
-Hadoop and Spring have the maximum number of 9 outdated code clones, followed by 6 from Tomcat, and 5 from Eclipse-SDK.
-An example of outdated code in hadoop's \textit{WritableComparator.java} is shown in \Cref{fig:before-after} as we discussed before.
+\texttt{hadoop} and Spring have the maximum number of 9 outdated code clones, followed by 6 from Tomcat, and 5 from \texttt{eclipse-SDK}.
+An example of outdated code in \texttt{hadoop}'s \textit{WritableComparator.java} is shown in \Cref{fig:before-after} as we discussed before.
 We also found a few outdated code which contained heavy modifications.
-For example, the code snippet in Stack Overflow post 23520731, a copy of \textit{SchemaUpdate.java} in Hibernate, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
+For example, the code snippet in Stack Overflow post 23520731, a copy of \textit{SchemaUpdate.java} in \texttt{hibernate}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
 Lastly, we found some ``orphan'' snippets.
 These snippets cannot find their originals in the latest version of the projects anymore.
-For example, the snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in Spring, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted.
+For example, the snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in \texttt{spring}, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted.
 %The latest version of Spring does not contain the file anymore.
@@
 Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive to naive developers who are ignorant.
+
+\textbf{For RQ3, we found 55 code snippets on Stack Overflow that are outdated and questionable for being reused.}
 %Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment.
@@
 	\resizebox{2.1\columnwidth}{!}{%
-	\begin{tabular}{r|l|p{4.5cm}|r|r|l|l|l|c|l}
-		\hline 
-		No. & Project & File & Start & End & License & SO Post & License & $C$ & C$_{\textit{\textrm{date}}}$ \\
-		\hline
-			1 & aspectj-1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & -- & $M$  & 2015-09-08 \\
-			2 & aspectj-1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & & $M$  & 2015-09-08 \\
-			3 & eclipse-SDK  & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & EPLv1 & $M$  &  2015-03-17 \\
-			4 & eclipse-SDK  & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
-			5 & eclipse-SDK  & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
-			6 & eclipse-SDK  & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	& EPLv1 & $M$  & 2011-03-01 \\
-			7 & eclipse-SDK  & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	& -- & $M$  &  2011-02-03 \\
-			8 & hadoop-1.0.0  & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
-			9 & hadoop-1.0.0  & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
-			10 & hadoop-1.0.0  & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & -- & $M$  & 2012-06-25 \\
-			11 & hadoop-1.0.0  & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
-			12 & hadoop-1.0.0  & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
-			13 & hadoop-1.0.0  & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & -- & $M$  & 2013-02-04 \\
-			14 & hadoop-1.0.0  & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & -- & $M$  & 2011-06-12 \\
-			15 & hadoop-1.0.0  & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & -- & $M$  & 2011-06-12 \\
-			16 & hadoop-1.0.0  & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & -- & $M$  & 2014-11-20 \\
-			17 & hibernate-4.2.2  & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & -- & $M$  & 2012-06-24 \\
-			18 & hibernate-4.2.2  & Example.java  & 224 & 243 & -- & 24924255 & -- & $M$  & 2013-04-23 \\
-			19 & hibernate-4.2.2  & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & -- & $M$  & 2016-02-05 \\
-			20 & hibernate-4.2.2  & SettingsFactory.java  & 244 & 255 & -- & 8257554 & -- & $D$  & 2011-03-11 \\
-			21 & hibernate-4.2.2  & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & -- & $M$  & 2015-03-12 \\
-			22 & jasperreports-3.7.4  & JRVerifier.java  & 982 & 998 & LGPLv3+ & 8037824 & -- & $M$  & 2008-04-17 \\
-			23 & jasperreports-3.7.4  & JRVerifier.java  & 1221 & 1240 & LGPLv3+ & 8037824 & -- & $M$  & 2011-05-20 \\
-			24 & jfreechart-1.0.13  & AbstractXYItemRenderer.java  & 532 & 569 & LGPLv2.1+ & 12936580 & -- & $M$  & 2016-02-19 \\
-			25 & jfreechart-1.0.13  & KeyToGroupMap.java  & 18 & 30 & LGPLv2.1+ & 16058183 & -- & $M$  & 2013-07-03 \\
-			26 & jfreechart-1.0.13  & SpiderWebPlot.java  & 502 & 520 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
-			27 & jfreechart-1.0.13  & SpiderWebPlot.java  & 522 & 536 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
-			28 & jgraph-5.13.0.0  & HelloWorld.java  & 16 & 22 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
-			29 & jgraph-5.13.0.0  & HelloWorld.java  & 28 & 40 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
-			30 & jgraph-5.13.0.0  & HelloWorld.java  & 31 & 36 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
-			31 & jgraph-5.13.0.0  & HelloWorld.java  & 39 & 56 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
-			32 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & -- & $M$  & 2015-12-13 \\
-			33 & jstock-1.0.7c  & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & -- & $M$  & 2015-12-13 \\
-			34 & jung2-2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
-			35 & jung2-2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
-			36 & junit-4  & Assert.java  & 33 & 52 & -- & 23586872 & -- & $M$  & 2015-05-12 \\
-			37 & junit-4  & ExternalResource.java  & 4 & 23 & -- & 7504040 & -- & $M$  & 2016-06-25 \\
-			38 & junit-4.11  & ExpectException.java  & 11 & 29 & -- & 8802082 & -- & $M$  & 2014-05-26 \\
-			39 & poi-3.6  & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & -- & $M$  & 2015-04-29 \\
-			40 & spring-3.0.5  & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & -- & $D$  & 2012-01-20 \\
-			41 & spring-3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & -- & $M$  & 2014-10-28 \\
-			42 & spring-3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & -- & $M$  & 2013-11-21 \\
-			43 & spring-3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & -- & $D$  & 2012-01-20 \\
-			44 & spring-3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & -- & $M$  & 2013-03-19 \\
-			45 & spring-3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2016-07-15 \\
-			46 & spring-3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
-			47 & spring-3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
-			48 & spring-3.0.5  & DispatcherServlet.java  & 91 & 103 & Apache-2 & 4781746 & -- & $M$  & 2011-08-08 \\
-			49 & spring-3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & Apache-2 & 10924700 & -- & $M$  & 2012-08-28 \\
-			50 & spring-3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & Apache-2 & 3751463 & -- & $M$  & 2016-07-05 \\
-			51 & struts2-2.2.1  & DefaultActionMapper.java  & 91 & 103 & Apache-2 & 14019840 & -- & $M$  & 2013-10-18 \\
-			52 & tomcat-7.0.2  & BasicAuthenticator.java  & 25 & 73 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
-			53 & tomcat-7.0.2  & BasicAuthenticator.java  & 33 & 43 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
-			54 & tomcat-7.0.2  & CoyoteAdapter.java  & 543 & 553 & Apache-2 & 24404964 & -- & $M$  & 2012-11-18 \\
-			55 & tomcat-7.0.2  & CoyoteAdapter.java  & 557 & 573 & Apache-2 & 24404964 & -- & $M$  & 2012-11-18 \\
-			56 & tomcat-7.0.2  & FormAuthenticator.java  & 51 & 61 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
-			57 & tomcat-7.0.2  & HttpServlet.java  & 111 & 124 & Apache-2 & 5266856 & -- & $M$  & 2011-10-22 \\
-			58 & tomcat-7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & Apache-2 & 10289462 & -- & $M$  & 2012-09-12 \\
+	\begin{tabular}{r|l|c|p{4.5cm}|r|r|l|l|l|c|l}
+		\hline 
+		No. & Project & Ver. & File & Start & End & License & SO Post & License & $C$ & C$_{\textit{\textrm{date}}}$ \\
+		\hline
+			1 & \texttt{aspectj} & 1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & -- & $M$  & 2015-09-08 \\
+			2 & \texttt{aspectj} & 1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & & $M$  & 2015-09-08 \\
+			3 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & EPLv1 & $M$  &  2015-03-17 \\
+			4 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
+			5 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
+			6 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	& EPLv1 & $M$  & 2011-03-01 \\
+			7 & \texttt{eclipse-SDK} & & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	& -- & $M$  &  2011-02-03 \\
+			8 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
+			9 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
+			10 & \texttt{hadoop} & 1.0.0 & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & -- & $M$  & 2012-06-25 \\
+			11 & \texttt{hadoop} & 1.0.0 & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
+			12 & \texttt{hadoop} & 1.0.0 & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
+			13 & \texttt{hadoop} & 1.0.0 & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & -- & $M$  & 2013-02-04 \\
+			14 & \texttt{hadoop} & 1.0.0 & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & -- & $M$  & 2011-06-12 \\
+			15 & \texttt{hadoop} & 1.0.0 & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & -- & $M$  & 2011-06-12 \\
+			16 & \texttt{hadoop} & 1.0.0 & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & -- & $M$  & 2014-11-20 \\
+			17 & \texttt{hibernate} & 4.2.2 & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & -- & $M$  & 2012-06-24 \\
+			18 & \texttt{hibernate} & 4.2.2 & Example.java  & 224 & 243 & -- & 24924255 & -- & $M$  & 2013-04-23 \\
+			19 & \texttt{hibernate} & 4.2.2 & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & -- & $M$  & 2016-02-05 \\
+			20 & \texttt{hibernate} & 4.2.2 & SettingsFactory.java  & 244 & 255 & -- & 8257554 & -- & $D$  & 2011-03-11 \\
+			21 & \texttt{hibernate} & 4.2.2 & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & -- & $M$  & 2015-03-12 \\
+			22 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 982 & 998 & LGPLv3+ & 8037824 & -- & $M$  & 2008-04-17 \\
+			23 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 1221 & 1240 & LGPLv3+ & 8037824 & -- & $M$  & 2011-05-20 \\
+			24 & \texttt{jfreechart} & 1.0.13 & AbstractXYItemRenderer.java  & 532 & 569 & LGPLv2.1+ & 12936580 & -- & $M$  & 2016-02-19 \\
+			25 & \texttt{jfreechart} & 1.0.13 & KeyToGroupMap.java  & 18 & 30 & LGPLv2.1+ & 16058183 & -- & $M$  & 2013-07-03 \\
+			26 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 502 & 520 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
+			27 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 522 & 536 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
+			28 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 16 & 22 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
+			29 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 28 & 40 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
+			30 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 31 & 36 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
+			31 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 39 & 56 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
+			32 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & -- & $M$  & 2015-12-13 \\
+			33 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & -- & $M$  & 2015-12-13 \\
+			34 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
+			35 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
+			36 & \texttt{junit} & 4.11 & Assert.java  & 33 & 52 & -- & 23586872 & -- & $M$  & 2015-05-12 \\
+			37 & \texttt{junit} & 4.11 & ExternalResource.java  & 4 & 23 & -- & 7504040 & -- & $M$  & 2016-06-25 \\
+			38 & \texttt{junit} & 4.11 & ExpectException.java  & 11 & 29 & -- & 8802082 & -- & $M$  & 2014-05-26 \\
+			39 & poi & 3.6 & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & -- & $M$  & 2015-04-29 \\
+			40 & \texttt{spring} & 3.0.5 & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & -- & $D$  & 2012-01-20 \\
+			41 & \texttt{spring} & 3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & -- & $M$  & 2014-10-28 \\
+			42 & \texttt{spring} & 3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & -- & $M$  & 2013-11-21 \\
+			43 & \texttt{spring} & 3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & -- & $D$  & 2012-01-20 \\
+			44 & \texttt{spring} & 3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & -- & $M$  & 2013-03-19 \\
+			45 & \texttt{spring} & 3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2016-07-15 \\
+			46 & \texttt{spring} & 3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
+			47 & \texttt{spring} & 3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
+			48 & \texttt{spring} & 3.0.5  & DispatcherServlet.java  & 91 & 103 & Apache-2 & 4781746 & -- & $M$  & 2011-08-08 \\
+			49 & \texttt{spring} & 3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & Apache-2 & 10924700 & -- & $M$  & 2012-08-28 \\
+			50 & \texttt{spring} & 3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & Apache-2 & 3751463 & -- & $M$  & 2016-07-05 \\
+			51 & \texttt{struts2} & 2.2.1  & DefaultActionMapper.java  & 91 & 103 & Apache-2 & 14019840 & -- & $M$  & 2013-10-18 \\
+			52 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 25 & 73 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
+			53 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 33 & 43 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
+			54 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 543 & 553 & Apache-2 & 24404964 & -- & $M$  & 2012-11-18 \\
+			55 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 557 & 573 & Apache-2 & 24404964 & -- & $M$  & 2012-11-18 \\
+			56 & \texttt{tomcat} & 7.0.2  & FormAuthenticator.java  & 51 & 61 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
+			57 & \texttt{tomcat} & 7.0.2  & HttpServlet.java  & 111 & 124 & Apache-2 & 5266856 & -- & $M$  & 2011-10-22 \\
+			58 & \texttt{tomcat} & 7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & Apache-2 & 10289462 & -- & $M$  & 2012-09-12 \\
 		\hline
@@
 
+\textbf{For RQ4, we observed xx code snippets on Stack Overflow that violate the license of their original software.
+Most of them do not contain licensing statements after copied to Stack Overflow.
+\FIXME{More}}
+
 \subsubsection{Interesting Finding: External Clones}
@@
 
-We found 31 clone pairs which either one of the clones or both of them are found to be a copy of code snippet from somewhere else besides Qualitas project.
-This compliments the findings of inter clones between software projects \cite{Svajlenko2014} by showing that clones can also be copied over different websites on the Internet.
+We found 31 clone pairs which either clones from Stack Overflow side or from both sides are found to be a copy of code snippet from somewhere else besides Qualitas projects.
+This complements the findings of inter clones between software projects \cite{Svajlenko2014} by showing that clones can also be copied over different websites on the Internet.
 There are 15 clone pairs that are originated from programming websites.

### 2017-02-02 cloneoverflow-latex/cloneoverflow.tex
Moved Matheus to 2nd author.

@@
 
-\title{Are We Reusing Outdated and License-violating Code \newline from Stack Overflow?}
+\title{Are We Reusing Outdated and License-Violating \newline Code Snippets from Stack Overflow?}
 
@@
 	\alignauthor
-	$^1$Chaiyong Ragkhitwetsagul, $^1$Jens Krinke, $^1$Matheus Paixao, $^2$Giuseppe Bianco \\
+	$^1$Chaiyong Ragkhitwetsagul, $^1$Matheus Paixao, $^1$Jens Krinke, $^2$Giuseppe Bianco \\
 	\affaddr{$^1$University College London, London, UK}\\
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{outdated}
+	\includegraphics[width=\linewidth]{outdated}
 	\caption{Findings from outdated code investigation of 96 pattern-A online clone pairs}

### 2017-02-05 cloneoverflow-latex/cloneoverflow.tex
Updated the numbers.
Updated the classification patterns according to Jens suggestions.

@@
 		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 181 \\ 
+		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 88 \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total  & 310,803 & & & & & 32,039 \\ 
+		Total  & 310,803 & & & & & 31,946 \\ 
 		\hline
@@
 		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,308 & 9 & 2,299 & x \\
-		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,495 & 254 & x \\
+		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
+		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 77 \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 704 \\
-		\multirow{1}{*}{$N_D$} & 181 & 10 & 171 & x \\ 
+		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 525 \\
+		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total  & 32,039 & 28,444 & 3,595 & x \\ 
+		Total  & 31,946 & 28,444 & 3,502 & 670 \\ 
 		\hline
@@
 We have tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and we found that 85\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation.
-Using the three filters, we reduced the size of $N_D$ clones to 181 pairs.
-
-In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 32,039 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs).
-Finally, there are 3,595 pairs remaining which we manually classified them.
+Using the three filters, we reduced the size of $N_D$ clones to 88 pairs.
+
+In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs).
+Finally, there are 3,502 pairs remaining which we manually classified them.
 The classification summary is shown in \Cref{tab:online_clone_classification_results}.
 
-\textbf{To answer RQ1, we found 32,039 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
-They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 181 $N_D$ pairs.
+\textbf{To answer RQ1, we found 31,946 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
+They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs.
 After classification, we found at least \FIXME{NUMBER} online code clones pairs between Stack Overflow and Qualitas.}
@@
 			\hline 
-			ES & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
+			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
 			\\ 
@@
 			\hline 
-			FC & Accidental similarity, false clones \\ 
+			AC & Accidental similarity, false clones \\ 
 			\hline 
@@
 They are unique enough not be boiler-plate and inheritance or interface implementation.
-ES (\textbf{E}xternal \textbf{S}ources) is a cloning that has an evidence of copying from an external source(s).
+ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from an external source(s).
 Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components).
@@
 They usually share similar overriding methods.
-The last pattern, FC (\textbf{F}alse \textbf{C}lones), represents false clone pairs.
+The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents false clone pairs.
 They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools.
@@
 We are looking for unique and meaningful clones in this study.
-Thus, we consider clone pairs classified into pattern QS, SQ, and UN as true positive, and BP, IN, and FC as false positive.
+Thus, we consider clone pairs classified into pattern QS, SQ, UD, and EX as true positive, and BP, IN, and AC as false positive.
 
@@
 			\hline
-			Set & A & A' & B & C & D  & E & F & Total \\ 
+			Set & QS & SQ & UD & EX & BP  & EX & AC & Total \\ 
 			\hline

### 2017-02-05 cloneoverflow-latex/cloneoverflow.tex
Updated the outdated pair table.

@@
 		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 525 \\
+		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 & 525 \\
 		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
@@
 		\hline
-		Total  & 31,946 & 28,444 & 3,502 & 670 \\ 
+		Total  & 31,946 & 28,314 & 3,632 & 670 \\ 
 		\hline
@@
 After classification, we found at least \FIXME{NUMBER} online code clones pairs between Stack Overflow and Qualitas.}
-
-%We selected only Stack Overflow fragment and Qualitas files that have never been looked at before in the previous investigation.
-If many clone pairs having the same Stack Overflow fragment and Qualitas file, we keep only the largest one.
-The reason for having this criteria is that we found a lot of duplicate clone pairs with the same classifications from either Stack Overflow fragments or Qualitas files.
-The classification results are shown in Table \ref{tab:classification_indv}.
-
-%\begin{table}
-%	\centering
-%	\caption{No.~of disagreed clone pairs ($S_D$ and $N_D$).}
-%	\label{tab:classification_indv_stats}
-%	\small
-%	\resizebox{\columnwidth}{!}{%
-%	\begin{tabular}{l|p{1.6cm}|r|r|r|r}
-%		\hline 
-%		Tool & Filter & \multicolumn{1}{c|}{Original} & \multicolumn{1}{c|}{Filtered} & \multicolumn{1}{c|}{good/ok} & \multicolumn{1}{c}{remaining} \\ 
-%		%\hline 
-%		%\multirow{1}{*}{\textit{Simian$_{df}$}-1} & 9383 & 140 & 8951 & 292 \\
-%		%\multirow{1}{*}{\textit{Simian$_{df}$}-2} & 9042 & 0 & 8539 & 503 \\
-%		\hline
-%		\multirow{1}{*}{\textit{Simian$_{df}$}} & $Line \geq 10$ \newline \& RegEx & \multirow{2}{*}{67,570} & \multirow{2}{*}{47,223}  & \multirow{2}{*}{2,546} & \multirow{2}{*}{17,801} \\ %140 + 1482 + 926
-%		\hline
-%%		\multirow{1}{*}{\textit{$N_D$}-1} & 7040  & 226 & 6700 & 114 \\
-%%		\multirow{1}{*}{\textit{$N_D$}-2} & 22187  & 152 & 21990 & 45 \\
-%		\multirow{1}{*}{\textit{$N_D$}} & $Sim \geq 80\%$ \newline \& RegEx & \multirow{2}{*}{229,176} & \multirow{2}{*}{228,558}  & \multirow{2}{*}{450} & \multirow{2}{*}{168} \\
-%		\hline
-%		%\multicolumn{2}{l|}{Total} & 296,746 & 20,966 & 2,996 & 1,039 \\
-%		%\hline
-%	\end{tabular} %
-%	}
-%\end{table}
 
@@
 
-There were 32,039 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}.
-We have use regular expressions to automatically classify \texttt{equals()} methods based on the method signature since they are not very interesting clones.
-It captured 28,444 clone pairs and classified them into pattern D.
-With help of the automatic classification, there were 3,595 pairs left for manual classification.
-
-The first author who has been working on clone detection research for two years took the role of a main investigator performing a manual classification of all the 3,595 clone pairs.
+There were 31,946 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}.
+We have use regular expressions to automatically classify \texttt{equals()}, getter and setter methods  based on the method signature since they are not very interesting clones.
+As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us captured 28,314 clone pairs and classified them into pattern BP.
+With help of the automatic classification, there were 3,632 pairs left for manual classification.
+
+The first author who has been working on clone detection research for two years took the role of a main investigator performing a manual classification of all the 3,632 clone pairs.
 By consulting the cloning patterns, the main investigator manually went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair.
 A relevant and useful observation was also recorded for each clone pair.
-The second author took the role of a validating investigator performing 10\% validation (359 pairs) of the clone pairs judged by the main investigator.
+The second author took the role of a validating investigator performing 10\% validation (363 pairs) of the clone pairs judged by the main investigator.
 The two investigators discussed 54 classification conflicts and resolved 51 of them.
-The 3 conflicts which the two investigators could not find consensuses are resolved after involving the third author.
+The 3 conflicts which the two investigators could not find consensuses were resolved by the third author.
 
 The classification results are shown in \Cref{tab:classification_good_o}.
-For \textit{good} pairs, 9 pairs were automatically classified by regular expressions and 2,299 pairs were manually classified.
-This resulted in one clone pair in pattern QS which is found to be copied from a Qualitas project to Stack Overflow.
+For \textit{good} pairs, 10 pairs were automatically classified by regular expressions and 2,298 pairs were manually classified.
+This resulted in 3 clone pairs in pattern QS which is found to be copied from a Qualitas project to Stack Overflow.
 Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as pattern UD.
-We observed 3 pairs in pattern ES since they are copied from external sources.
-58 clone pairs are found to be pattern BP.
-Six pairs are similar code from inheriting the same superclass or implementing the same interface, pattern IN.
-Finally, 2,189 pairs are false clones and classified into FC.
+Please note that we were conservative in this study when doing classification.
+Even the clone pairs were exactly or almost identical but we could not find an evidence that it was cloned in any particular direction, we classified them as UD instead of QS, SQ, or EX.
+We observed 4 pairs in pattern EX since they are copied from external sources.
+111 clone pairs are found to be pattern BP.
+Seven pairs are similar code from inheriting the same superclass or implementing the same interface, pattern IN.
+Finally, 2,172 pairs are false clones and classified into FC.
 No clones were found in pattern SQ.
@@
 
-For the \textit{ok} clone pairs, we could not feasibly investigate all 31,729 pairs manually.
-Consulting the classification of \textit{good} pairs, we found that $S_EN_E$ produces a large number of x,xxx false positive results (accounts for xx.xx\% of $S_EN_E$ clone pairs) due to its recall preference.
-We thus decided to ignore this clone set in our \textit{ok}-pair classification.
-A large number of 11,495 clone pairs were automatically classified and 254 pairs were done manually.
-We found xx, xx, xx, xx, xx, and xx in QS, UD, ES, BP, IN and FC respectively.
-Similarly, no clone pairs were found in SQ.
+For \textit{ok} clone pairs, we could not feasibly investigate all 31,729 pairs manually and decided to remove $S_EN_E$ from this round of classification.
+According to the classification of \textit{good} pairs, we found that $S_EN_E$ accounted for 98.9\% of all false positive pairs in \textit{good} pairs.
+This was not a surprise since EvaClone configurations prefered recall and hence offered relaxed configurations.
+We ignored them since we were more interested in meaningful clones.
+This resulted in 11,749 \textit{ok} pairs remaining.
+11,494 clone pairs were automatically classified and 255 pairs were looked at manually.
+We found 12, 42, 23, 11,459, 20, and 103 in QS, UD, EX, BP, IN and AC respectively. Similarly, no clone pairs were found in SQ.
 
@@
 			\hline
-			Set & QS & SQ & UD & EX & BP  & EX & AC & Total \\ 
-			\hline
-			\multirow{1}{*}{\textit{good}}  & 1 & 0 & 4  & 3 & 58  & 6 & 2,189 & 2,261 \\
-			\multirow{1}{*}{\textit{ok}}  & 8 & 0 & 29  & 10 & 9,158 & 35 & 82 & 9,322 \\
-			\multirow{1}{*}{$S_D$} & 79 & 0 & 336 & 17 & 209 & 63 & 167 & 871 \\
-			\multirow{1}{*}{$N_D$} & 8  & 0 & 27 & 1 & 77 & 3 & 82 & 168 \\ 
-			\hline
-			Total & 96 & 0 & 396 & 31 & 9,502 & 107 & 2,520 & 12,622 \\ 
+			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
+			\hline
+			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
+			\multirow{1}{*}{\textit{ok}}  & 12 & 0 & 42 & 23 & 11,549 & 20 & 103 & 11,749 \\
+			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
+			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
+			\hline
+			Total & 110 & 0 & 382 & 178 & 28,642 & 109 & 2,525 & 31,946 \\ 
 			\hline
@@
 
-For disagreed clone pairs, an automatic and manual classification of 17,801 $S_D$ and 181 $N_D$ clone pairs results in xx pairs in pattern QS, xx pairs in UD, xx pairs in ES, xx in BP, xx in IN and xx in FC.
-
-\textbf{To answer RQ2, we found that ...}
+For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code.
+Our regular expressions could automatically classified 16,800 of them into BP.
+The investigator checked the 1,001 remaining pairs manually.
+As a result, we found 86 QS, 294 UD, 145 EX, 17,074 BP, 74 IN and 128 AC pairs.
+For 88 $N_D$ clone pairs, 10 of them were automatically classified into BP and 78 were manually classified.
+We found 9 QS, 35 UD, 6 EX, 17 BP, 8 IN, and 13 AC respectively.
+
+\textbf{To answer RQ2, we used our patterns of online code cloning to classified 31,946 clone pairs.
+Our results showed that although most of the clone pairs were boiler-plate code (28,642), clones from inheritance/interface (109), or accidental clones (2,525); there were 670 pairs that were very interesting.
+110 pairs had strong evidences to be cloned from Qualitas to Stack Overflow.
+382 were non-trivial clones but without strong evidence of clone direction.
+178 pairs were found to be cloned from external sources outside Qualitas projects.
+Lastly, we did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
 
@@
 %\subsubsection{Outdated Clones}
+To the best of our knowledge, this work is the first to discuss a problem of outdated code on Stack Overflow.
 Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated \cite{Xia2014}.
 Usually code clone detection is used to locate clone instances and update them to match with the original code \cite{Bellon2007}.
-However, in this situation, the clones are pervasive on Stack Overflow posts and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts.
+However, for online code clones, the clones are pervasive and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts.
 Moreover, Stack Overflow is not a software.
 There is no test suite to run and check whether the code snippets are still working as expected.
-Hence, if any change happens in the original code, our results show that the copies on Stack Overflow are still mostly left outdated.
-
-As far as we know, our work is possibly the first which discovers outdated code on Stack Overflow.
-Since code can be updated due to various possible reasons, e.g.~bug fixing or API changes, it is risky if developers reuse outdated code snippets from Stack Overflow.
-They might later find out that the copied code does not work any more due to different API versions. Even worse, they might also introduce bugs or vulnerabilities into their software.
-
-To check if the discovered Stack Overflow clones are outdated, we focused on the 96 QS clone pairs that are copied in the direction from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}).
-For each code snippet, we tracked its original code in Qualitas projects.
-We located the latest version of the each file and compared to the Stack Overflow snippet to see if any change has been made to the source code.
-If we found any change, we used \textit{git blame} command to see who modified the source code and when.
+
+To check if our online code clones are outdated, we focused on the 110 QS clone pairs that were cloned from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}) and compared them with their latest versions.
+We cloned the latest version of the Qualitas projects from their repositories on 26 September 2016.
+For each online clone pair, we used the file name of Qualitas clone to search for its latest version.
+Once we found the file, we located the location of the cloned snippets in the file based on method names.
+So for Simian clones that may not contain in a single method, we looked further up and down the clone region to get the method name and its nearby methods.
+We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code.
+We also made sure that the changes did not come from modifications maded to Stack Overflow snippets by the posters but from the projects themselves.
+When we found inconsistent lines between the two versions, we used \texttt{git blame} command to see who modified those lines of code and noted down the details.
 
 \Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow.
-The comparison with the clones' latest versions revealed that 55 clone pairs were outdated and they were all Stack Overflow accepted answers.
-\texttt{hadoop} and Spring have the maximum number of 9 outdated code clones, followed by 6 from Tomcat, and 5 from \texttt{eclipse-SDK}.
-An example of outdated code in \texttt{hadoop}'s \textit{WritableComparator.java} is shown in \Cref{fig:before-after} as we discussed before.
+We discovered 59 outdated online clone pairs out of 110 pairs.
+\texttt{spring} and \texttt{hibernate} have the maximum number of 20 outdated pairs, followed by 15 from \texttt{eclipse}, and 12 from \texttt{hadoop}.
+An example of outdated code in \texttt{hadoop}'s \texttt{WritableComparator.java} has already been shown in \Cref{fig:before-after}.
 We also found a few outdated code which contained heavy modifications.
-For example, the code snippet in Stack Overflow post 23520731, a copy of \textit{SchemaUpdate.java} in \texttt{hibernate}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
-Lastly, we found some ``orphan'' snippets.
-These snippets cannot find their originals in the latest version of the projects anymore.
-For example, the snippet in Stack Overflow post 3758110, a copy of \textit{DefaultAnnotationHandlerMapping.java} in \texttt{spring}, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted.
+For example, the code snippet in Stack Overflow post 23520731, a copy of \texttt{SchemaUpdate.java} in \texttt{hibernate}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
+We also found 3 ``dead'' snippets.
+These snippets did not have their originals in the latest version of the projects anymore.
+For example, the snippet in Stack Overflow post 3758110, a copy of \texttt{DefaultAnnotationHandlerMapping.java} in \texttt{spring}, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted.
 %The latest version of Spring does not contain the file anymore.
 
-The outdated online code clones can cause problems ranging from uncompilable code due to different API usage to bug propagations.
+The outdated online code clones can cause problems ranging from uncompilable code (due to modifications and different API usage in the outdated code) to bug propagations.
 An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers.
-Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive to naive developers who are ignorant.
-
-\textbf{For RQ3, we found 55 code snippets on Stack Overflow that are outdated and questionable for being reused.}
+Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive enough for naive developers who are ignorant to copy and reuse the code.
+
+\textbf{For RQ3, our results show that more than half (59) of QS clone pairs on Stack Overflow are outdated.
+We observed that the newer versions of these outdated snippets contained various changes ranging from a slight modifications of variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures.
+Moreover, we found three dead snippets.
+They do not exist any more in the latest version.
+Both outdated and dead online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
+Even worse, they might also introduce bugs or vulnerabilities into their software.
+}
 %Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment.
@@
 	\end{lstlisting}
-	\caption{Outdated code snippet on Stack Overflow post 23520731. This code has been copied from SchemaUpdate.java and its latest version in hibernate code base contains heavy modifications.}
+	\caption{Outdated code snippet on Stack Overflow post 23520731. This code has been copied from \texttt{SchemaUpdate.java} and its latest version in hibernate code base contains heavy modifications.}
 	\label{fig:hibernate_outdated_code}
@@
 
+%\begin{table*}
+%	\centering
+%	\caption{62 QS outdated online code clones. Clones can be outdated by modifications ($M$), deletion ($D$), and rewriting ($R$).}
+%	\label{tab:stale_code_details}
+%	\scriptsize
+%	\resizebox{2.1\columnwidth}{!}{%
+%	\begin{tabular}{r|l|c|p{4.5cm}|r|r|l|c|l}
+%		\hline 
+%		No. & Project & Ver. & File & Start & End & SO Post & Cause & C$_{\textit{\textrm{date}}}$ \\
+%		\hline
+%			1 & \texttt{aspectj} & 1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & 18303692 & $M$  & 2015-09-08 \\
+%			2 & \texttt{aspectj} & 1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & 18303692 & $M$  & 2015-09-08 \\
+%			3 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 113 & 166 & 2513183 & $M$  &  2015-03-17 \\
+%			4 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 117 & 126 &  2513183	& $M$  &  2015-03-17 \\
+%			5 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 143 & 165 &  2513183	& $M$  &  2015-03-17 \\
+%			6 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 178 & 187 &  2513183	& $M$  & 2011-03-01 \\
+%			7 & \texttt{eclipse-SDK} & & WizardDialog.java  & 377 & 394 &   11861598	& $M$  &  2011-02-03 \\
+%			8 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 275 & 287 & 21702608 & $M$  & 2011-06-12 \\
+%			9 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 289 & 309 & 21702608 & $M$  & 2011-06-12 \\
+%			10 & \texttt{hadoop} & 1.0.0 & JobSubmissionFiles.java  & 46 & 55 & 14845581 & $M$  & 2012-06-25 \\
+%			11 & \texttt{hadoop} & 1.0.0 & mapred/../LineRecordReader.java  & 47 & 60 & 16180910 & $M$  & 2011-07-25 \\
+%			12 & \texttt{hadoop} & 1.0.0 & mapreduce/../LineRecordReader.java  & 75 & 99 & 16180910 & $M$  & 2011-07-25 \\
+%			13 & \texttt{hadoop} & 1.0.0 & StringUtils.java  & 40 & 56 & 801987 & $M$  & 2013-02-04 \\
+%			14 & \texttt{hadoop} & 1.0.0 & TestJobCounters.java  & 186 & 192 & 18833798 & $M$  & 2011-06-12 \\
+%			15 & \texttt{hadoop} & 1.0.0 & TextOutputFormat.java  & 75 & 99 & 16928749 & $M$  & 2011-06-12 \\
+%			16 & \texttt{hadoop} & 1.0.0 & WritableComparator.java  & 44 & 54 & 22315734 & $M$  & 2014-11-20 \\
+%			17 & \texttt{hibernate} & 4.2.2 & ConnectionProviderInitiator.java  & 65 & 93 & 15168494 & $M$  & 2012-06-24 \\
+%			18 & \texttt{hibernate} & 4.2.2 & Example.java  & 224 & 243 & 24924255 & $M$  & 2013-04-23 \\
+%			19 & \texttt{hibernate} & 4.2.2 & SchemaUpdate.java  & 115 & 168 & 23520731 & $M$  & 2016-02-05 \\
+%			20 & \texttt{hibernate} & 4.2.2 & SettingsFactory.java  & 244 & 255 & 8257554 & $D$  & 2011-03-11 \\
+%			21 & \texttt{hibernate} & 4.2.2 & SQLServer2005LimitHandler.java  & 43 & 61 & 23967852 & $M$  & 2015-03-12 \\
+%			22 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 982 & 998 & 8037824 & $M$  & 2008-04-17 \\
+%			23 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 1221 & 1240 & 8037824 & $M$  & 2011-05-20 \\
+%			24 & \texttt{jfreechart} & 1.0.13 & AbstractXYItemRenderer.java  & 532 & 569 & 12936580 & $M$  & 2016-02-19 \\
+%			25 & \texttt{jfreechart} & 1.0.13 & KeyToGroupMap.java  & 18 & 30 & 16058183 & $M$  & 2013-07-03 \\
+%			26 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 502 & 520 & 21998949 & $M$  & 2008-06-02 \\
+%			27 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 522 & 536 & 21998949 & $M$  & 2008-06-02 \\
+%			28 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 16 & 22 & 6722760 & $R$  & 2014-04-13 \\
+%			29 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 28 & 40 & 6722760 & $R$  & 2014-04-13 \\
+%			30 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 31 & 36 & 6722760 & $R$  & 2014-04-13 \\
+%			31 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 39 & 56 & 6722760 & $R$  & 2014-04-13 \\
+%			32 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & 14940863 & $M$  & 2015-12-13 \\
+%			33 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & 24680923 & $M$  & 2015-12-13 \\
+%			34 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & 6025026 & $M$  & 2010-04-13 \\
+%			35 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & 6025026 & $M$  & 2010-04-13 \\
+%			36 & \texttt{junit} & 4.11 & Assert.java  & 33 & 52 & 23586872 & $M$  & 2015-05-12 \\
+%			37 & \texttt{junit} & 4.11 & ExternalResource.java  & 4 & 23 & 7504040 & $M$  & 2016-06-25 \\
+%			38 & \texttt{junit} & 4.11 & ExpectException.java  & 11 & 29 & 8802082 & $M$  & 2014-05-26 \\
+%			39 & poi & 3.6 & WorkbookFactory.java  & 18 & 28 & 12593810 & $M$  & 2015-04-29 \\
+%			40 & \texttt{spring} & 3.0.5 & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & 5660519 & $D$  & 2012-01-20 \\
+%			41 & \texttt{spring} & 3.0.5  & AutowireUtils.java  & 32 & 42 & 20913543 & $M$  & 2014-10-28 \\
+%			42 & \texttt{spring} & 3.0.5  & CustomCollectionEditor.java  & 33 & 71 & 18623736 & $M$  & 2013-11-21 \\
+%			43 & \texttt{spring} & 3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & 3758110 & $D$  & 2012-01-20 \\
+%			44 & \texttt{spring} & 3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & 6149818 & $M$  & 2013-03-19 \\
+%			45 & \texttt{spring} & 3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2016-07-15 \\
+%			46 & \texttt{spring} & 3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2008-12-18 \\
+%			47 & \texttt{spring} & 3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2008-12-18 \\
+%			48 & \texttt{spring} & 3.0.5  & DispatcherServlet.java  & 91 & 103 & 4781746 & $M$  & 2011-08-08 \\
+%			49 & \texttt{spring} & 3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & 10924700 & $M$  & 2012-08-28 \\
+%			50 & \texttt{spring} & 3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & 3751463 & $M$  & 2016-07-05 \\
+%			51 & \texttt{struts2} & 2.2.1  & DefaultActionMapper.java  & 91 & 103 & 14019840 & $M$  & 2013-10-18 \\
+%			52 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 25 & 73 & 21734562 & $M$  & 2016-08-04 \\
+%			53 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 33 & 43 & 21734562 & $M$  & 2016-08-04 \\
+%			54 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 543 & 553 & 24404964 & $M$  & 2012-11-18 \\
+%			55 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 557 & 573 & 24404964 & $M$  & 2012-11-18 \\
+%			56 & \texttt{tomcat} & 7.0.2  & FormAuthenticator.java  & 51 & 61 & 21734562 & $M$  & 2016-08-04 \\
+%			57 & \texttt{tomcat} & 7.0.2  & HttpServlet.java  & 111 & 124 & 5266856 & $M$  & 2011-10-22 \\
+%			58 & \texttt{tomcat} & 7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & 10289462 & $M$  & 2012-09-12 \\
+%		\hline
+%	\end{tabular} %
+%}
+%\end{table*}
+
 \begin{table*}
 	\centering
-	\caption{58 code clones in Stack Overflow (SO) that were altered, rewritten, or removed from the project after posted and their respective licenses.
-Files can be changed ($C$) by modifications ($M$), deletion ($D$), and rewriting ($R$).}
+	\caption{62 QS outdated online clone pairs.
+Outdated clones are caused (\textit{C}) by statement modifications, added, deleted (\textit{sm}), file deletion (\textit{fd}), and method rewriting (\textit{rw}).}
 	\label{tab:stale_code_details}
-	\scriptsize
+	\small
 	\resizebox{2.1\columnwidth}{!}{%
-	\begin{tabular}{r|l|c|p{4.5cm}|r|r|l|l|l|c|l}
-		\hline 
-		No. & Project & Ver. & File & Start & End & License & SO Post & License & $C$ & C$_{\textit{\textrm{date}}}$ \\
-		\hline
-			1 & \texttt{aspectj} & 1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & -- & 18303692 & -- & $M$  & 2015-09-08 \\
-			2 & \texttt{aspectj} & 1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & -- & 18303692 & & $M$  & 2015-09-08 \\
-			3 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 113 & 166 & EPLv1 & 2513183 & EPLv1 & $M$  &  2015-03-17 \\
-			4 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 117 & 126 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
-			5 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 143 & 165 & EPLv1  &  2513183	& EPLv1 & $M$  &  2015-03-17 \\
-			6 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 178 & 187 & EPLv1  &  2513183	& EPLv1 & $M$  & 2011-03-01 \\
-			7 & \texttt{eclipse-SDK} & & WizardDialog.java  & 377 & 394 & EPLv1  &   11861598	& -- & $M$  &  2011-02-03 \\
-			8 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 275 & 287 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
-			9 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 289 & 309 & Apache-2 & 21702608 & -- & $M$  & 2011-06-12 \\
-			10 & \texttt{hadoop} & 1.0.0 & JobSubmissionFiles.java  & 46 & 55 & Apache-2 & 14845581 & -- & $M$  & 2012-06-25 \\
-			11 & \texttt{hadoop} & 1.0.0 & mapred/../LineRecordReader.java  & 47 & 60 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
-			12 & \texttt{hadoop} & 1.0.0 & mapreduce/../LineRecordReader.java  & 75 & 99 & Apache-2 & 16180910 & -- & $M$  & 2011-07-25 \\
-			13 & \texttt{hadoop} & 1.0.0 & StringUtils.java  & 40 & 56 & Apache-2 & 801987 & -- & $M$  & 2013-02-04 \\
-			14 & \texttt{hadoop} & 1.0.0 & TestJobCounters.java  & 186 & 192 & Apache-2 & 18833798 & -- & $M$  & 2011-06-12 \\
-			15 & \texttt{hadoop} & 1.0.0 & TextOutputFormat.java  & 75 & 99 & Apache-2 & 16928749 & -- & $M$  & 2011-06-12 \\
-			16 & \texttt{hadoop} & 1.0.0 & WritableComparator.java  & 44 & 54 & Apache-2 & 22315734 & -- & $M$  & 2014-11-20 \\
-			17 & \texttt{hibernate} & 4.2.2 & ConnectionProviderInitiator.java  & 65 & 93 & -- & 15168494 & -- & $M$  & 2012-06-24 \\
-			18 & \texttt{hibernate} & 4.2.2 & Example.java  & 224 & 243 & -- & 24924255 & -- & $M$  & 2013-04-23 \\
-			19 & \texttt{hibernate} & 4.2.2 & SchemaUpdate.java  & 115 & 168 & -- & 23520731 & -- & $M$  & 2016-02-05 \\
-			20 & \texttt{hibernate} & 4.2.2 & SettingsFactory.java  & 244 & 255 & -- & 8257554 & -- & $D$  & 2011-03-11 \\
-			21 & \texttt{hibernate} & 4.2.2 & SQLServer2005LimitHandler.java  & 43 & 61 & -- & 23967852 & -- & $M$  & 2015-03-12 \\
-			22 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 982 & 998 & LGPLv3+ & 8037824 & -- & $M$  & 2008-04-17 \\
-			23 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 1221 & 1240 & LGPLv3+ & 8037824 & -- & $M$  & 2011-05-20 \\
-			24 & \texttt{jfreechart} & 1.0.13 & AbstractXYItemRenderer.java  & 532 & 569 & LGPLv2.1+ & 12936580 & -- & $M$  & 2016-02-19 \\
-			25 & \texttt{jfreechart} & 1.0.13 & KeyToGroupMap.java  & 18 & 30 & LGPLv2.1+ & 16058183 & -- & $M$  & 2013-07-03 \\
-			26 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 502 & 520 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
-			27 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 522 & 536 & LGPLv2.1+ & 21998949 & -- & $M$  & 2008-06-02 \\
-			28 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 16 & 22 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
-			29 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 28 & 40 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
-			30 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 31 & 36 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
-			31 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 39 & 56 & LGPLv2.1+ & 6722760 & -- & $R$  & 2014-04-13 \\
-			32 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & GPLv2+ & 14940863 & -- & $M$  & 2015-12-13 \\
-			33 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & GPLv2+ & 24680923 & -- & $M$  & 2015-12-13 \\
-			34 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
-			35 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & -- & 6025026 & -- & $M$  & 2010-04-13 \\
-			36 & \texttt{junit} & 4.11 & Assert.java  & 33 & 52 & -- & 23586872 & -- & $M$  & 2015-05-12 \\
-			37 & \texttt{junit} & 4.11 & ExternalResource.java  & 4 & 23 & -- & 7504040 & -- & $M$  & 2016-06-25 \\
-			38 & \texttt{junit} & 4.11 & ExpectException.java  & 11 & 29 & -- & 8802082 & -- & $M$  & 2014-05-26 \\
-			39 & poi & 3.6 & WorkbookFactory.java  & 18 & 28 & Apache-2 & 12593810 & -- & $M$  & 2015-04-29 \\
-			40 & \texttt{spring} & 3.0.5 & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & Apache-2 & 5660519 & -- & $D$  & 2012-01-20 \\
-			41 & \texttt{spring} & 3.0.5  & AutowireUtils.java  & 32 & 42 & Apache-2 & 20913543 & -- & $M$  & 2014-10-28 \\
-			42 & \texttt{spring} & 3.0.5  & CustomCollectionEditor.java  & 33 & 71 & Apache-2 & 18623736 & -- & $M$  & 2013-11-21 \\
-			43 & \texttt{spring} & 3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & Apache-2 & 3758110 & -- & $D$  & 2012-01-20 \\
-			44 & \texttt{spring} & 3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & Apache-2 & 6149818 & -- & $M$  & 2013-03-19 \\
-			45 & \texttt{spring} & 3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2016-07-15 \\
-			46 & \texttt{spring} & 3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
-			47 & \texttt{spring} & 3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & Apache-2 & 20996373 & -- & $M$  & 2008-12-18 \\
-			48 & \texttt{spring} & 3.0.5  & DispatcherServlet.java  & 91 & 103 & Apache-2 & 4781746 & -- & $M$  & 2011-08-08 \\
-			49 & \texttt{spring} & 3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & Apache-2 & 10924700 & -- & $M$  & 2012-08-28 \\
-			50 & \texttt{spring} & 3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & Apache-2 & 3751463 & -- & $M$  & 2016-07-05 \\
-			51 & \texttt{struts2} & 2.2.1  & DefaultActionMapper.java  & 91 & 103 & Apache-2 & 14019840 & -- & $M$  & 2013-10-18 \\
-			52 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 25 & 73 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
-			53 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 33 & 43 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
-			54 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 543 & 553 & Apache-2 & 24404964 & -- & $M$  & 2012-11-18 \\
-			55 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 557 & 573 & Apache-2 & 24404964 & -- & $M$  & 2012-11-18 \\
-			56 & \texttt{tomcat} & 7.0.2  & FormAuthenticator.java  & 51 & 61 & Apache-2 & 21734562 & -- & $M$  & 2016-08-04 \\
-			57 & \texttt{tomcat} & 7.0.2  & HttpServlet.java  & 111 & 124 & Apache-2 & 5266856 & -- & $M$  & 2011-10-22 \\
-			58 & \texttt{tomcat} & 7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & Apache-2 & 10289462 & -- & $M$  & 2012-09-12 \\
+	\begin{tabular}{r|l|c|l|c|p{5.8cm}|r|r|c|c|c}
+		\hline 
+		No. & SO Post & SO Date & Q project & Ver. & File & Start & End & Q Date & \textit{C} & $C$ Date \\
+		\hline
+			1 & 18303692 & 18-Aug-13 & \texttt{aspectj} & 1.6.9  & \texttt{aspectjtools/../Agent.java}  & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
+			2 & 18303692 & 18-Aug-13 & \texttt{aspectj} & 1.6.9  & \texttt{aspectjweaver/../Agent.java}  & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
+			3 & 2513183 & 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 113 & 166 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
+			4 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 117 & 126 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
+			5 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 143 & 165 & 5-Jun-13 & \textit{sm} & 1-Mar-11 \\
+			6 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 178 & 187 & 5-Jun-13 & \textit{sm} & 5-Jun-13 \\
+			7 & 11861598 & 8-Aug-12 & \texttt{eclipse-SDK} & 4.3 & \texttt{WizardDialog.java}  & 377 & 394 & 1-May-13 & \textit{sm} & 21-Jun-13 \\
+			8 & 22315734 & 11-Mar-14 & \texttt{hadoop} & 1.0.0 & \texttt{WritableComparator.java}  & 44 & 54 & 25-Aug-11 & \textit{sm} & 20-Nov-14 \\
+			9 & 801987 & 29-Apr-09 & \texttt{hadoop} & 1.0.0 & \texttt{StringUtils.java}  & 40 & 56 & 15-Dec-11 & \textit{sm} & 4-Feb-13 \\
+			10 & 21702608 & 11-Feb-14 & \texttt{hadoop} & 1.0.0 & \texttt{DBCountPageView.java}  & 275 & 287 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
+			11 & 21702608 & 11-Feb-14 & \texttt{hadoop} & 1.0.0 & \texttt{DBCountPageView.java}  & 289 & 309 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
+			12 & 14845581 & 13-Feb-13 & \texttt{hadoop} & 1.0.0 & \texttt{JobSubmissionFiles.java}  & 46 & 55 & 15-Dec-11 & \textit{sm} & 25-Jun-12 \\
+			13 & 16180910 & 24-Apr-13 & \texttt{hadoop} & 1.0.0 & \texttt{mapred/../LineRecordReader.java}  & 47 & 60 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
+			14 & 16180910 & 24-Apr-13 & \texttt{hadoop} & 1.0.0 & \texttt{mapreduce/../LineRecordReader.java}  & 41 & 54 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
+			15 & 15168494 & 24-Feb-14 & \texttt{hibernate} & 4.2.2 & \texttt{ConnectionProviderInitiator.java}  & 65 & 93 & 22-May-13 & \textit{sm} & 26-Apr-13 \\
+			16 & 24924255 & 24-Jul-14 & \texttt{hibernate} & 4.2.2 & \texttt{Example.java}  & 224 & 243 & 22-May-13 & \textit{sm} & 23-Apr-13 \\
+			17 & 23520731 & 7-May-14 & \texttt{hibernate} & 4.2.2 & \texttt{SchemaUpdate.java}  & 115 & 168 & 22-May-13 & \textit{sm} & 5-Feb-16 \\
+			18 & 8257554 & 26-Nov-11 & \texttt{hibernate} & 4.2.2 & \texttt{SettingsFactory.java}  & 244 & 255 & 22-May-13 & \textit{fd} & 11-Mar-11 \\
+			19 & 23967852 & 31-Apr-14 & \texttt{hibernate} & 4.2.2 & \texttt{SQLServer2005LimitHandler.java}  & 43 & 61 & 22-May-13 & \textit{sm} & 11-May-16 \\
+			20 & 19298607 & 10-Oct-13 & \texttt{hibernate} & 4.2.2 & \texttt{Oracle9iDialect.java} & 23 & 32 & 22-May-13 & \textit{sm} & 12-Apr-15 \\
+			21 & 10031897 & 5-Apr-12 & \texttt{hibernate} & 4.2.2 & \texttt{AliasToBeanResultTransformer.java} & 44 & 61 & 22-May-13 & \textit{sm} & 4-Jun-15 \\ 
+			22 & 8037824 & 7-Nov-11 & \texttt{jasperreports} & 3.7.4 & \texttt{JRVerifier.java}  & 982 & 998 & 31-May-10 & \textit{sm} & 17-Apr-08 \\
+			23 & 8037824 & 7-Nov-11 & \texttt{jasperreports} & 3.7.4 & \texttt{JRVerifier.java}  & 1221 & 1240 & 31-May-10 & \textit{fd} & 20-May-11 \\
+			24 & 12936580 & 17-Oct-12 & \texttt{jfreechart} & 1.0.13 & \texttt{AbstractXYItemRenderer.java}  & 532 & 569 & 20-Apr-09 & \textit{sm} & 16-Jan-16 \\
+			25 & 16058183 & 17-Apr-13 & \texttt{jfreechart} & 1.0.13 & \texttt{KeyToGroupMap.java}  & 18 & 30 & 20-Apr-09 & \textit{sm} & 29-Jun-07 \\
+			26 & 21998949 & 24-Feb-14 & \texttt{jfreechart} & 1.0.13 & \texttt{SpiderWebPlot.java}  & 502 & 520 & 20-Apr-09 & \textit{sm} & 2-Jun-08 \\
+			27 & 21998949 & 24-Feb-14 & \texttt{jfreechart} & 1.0.13 & \texttt{SpiderWebPlot.java}  & 522 & 536 & 20-Apr-09 & \textit{sm} & 22-Nov-13 \\
+			28 & 6722760 & 17-Jul-11 & \texttt{jgraph} & 5.13.0.0 & \texttt{HelloWorld.java} (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{rw} & 13-Apr-14 \\
+			31 & 6025026 & 17-Jul-11 & \texttt{jung2} & 2\_0\_1  & \texttt{ShortestPathDemo.java}  & 106 & 117 & 20-Jun-08 & \textit{sm} & 13-Apr-10 \\
+			32 & 6025026 & 17-Jul-11 & \texttt{jung2} & 2\_0\_1  & \texttt{ShortestPathDemo.java}  & 158 & 172 & 20-Jun-08 & \textit{sm} & 29-Nov-15 \\
+			33 & 23586872 & 31-May-14 & \texttt{junit} & 4.11 & \texttt{Assert.java} & 33 & 52 & 11-Oct-12 & \textit{sm} & 12-May-15 \\
+			34 & 7504040 & 29-Sep-11 & \texttt{junit} & 4.11 & \texttt{ExternalResource.java}  & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
+			35 & 8802082 & 10-Jan-12 & \texttt{junit} & 4.11 & \texttt{ExpectException.java} (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
+			37 & 12593810 & 26-Sep-12 & poi & 3.6 & \texttt{WorkbookFactory.java}  & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
+			38 & 20913543 & 6-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{AutowireUtils.java} & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
+			39 & 18623736 & 4-Sep-13 & \texttt{spring} & 3.0.5  & \texttt{CustomCollectionEditor.java}  & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
+			40 & 22865824 & 4-Apr-14 & \texttt{spring} & 3.0.5  & \texttt{JavaMailSenderImpl.java} & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
+			41 & 22865824 & 4-Apr-14 & \texttt{spring} & 3.0.5  & \texttt{JavaMailSenderImpl.java} & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
+			42 & 20421869 & 6-Dec-13 & \texttt{spring} & 3.0.5  & \texttt{ClassPathScanningCandidate \newline ComponentProvider.java} (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
+			44 & 3751463 & 20-Sep-10 & \texttt{spring} & 3.0.5  & \texttt{ScheduledTasksBean \newline DefinitionParser.java}  & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
+			45 & 6149818 & 27-May-11 & \texttt{spring} & 3.0.5  & \texttt{DefaultPropertiesPersister.java}  & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
+			46 & 10952561 & 8-Jun-12 & \texttt{spring} & 3.0.5  & \texttt{HibernateTemplate.java}  & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
+			47 & 10952561 & 8-Jun-12 & \texttt{spring} & 3.0.5  & \texttt{Jaxb2Marshaller.java}  & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
+			48 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{test/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
+			49 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{web/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
+			50 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{servlet/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
+			51 & 5660519 & 15-Apr-11 & \texttt{spring} & 3.0.5 & \texttt{AnnotationMethodHandler \newline ExceptionResolver.java}  & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
+			52 & 4781746 & 24-Jan-11 & \texttt{spring} & 3.0.5  & \texttt{DispatcherServlet.java}  & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
+			53 & 3758110 & 21-Sep-10 & \texttt{spring} & 3.0.5  & \texttt{DefaultAnnotation \newline HandlerMapping.java}  & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
+			54 & 9003314 & 25-Jan-12 & \texttt{spring} & 3.0.5  & \texttt{WebDataBinder.java} & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
+			55 & 14019840 & 24-Dec-12 & \texttt{struts2} & 2.2.1  & \texttt{DefaultActionMapper.java}  & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
+			56 & 15131432 & 28-Feb-13 & \texttt{struts2} & 2.2.1  & \texttt{FreemarkerManager.java}  & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
+			57 & 15110171 & 27-Feb-13 & \texttt{struts2} & 2.2.1  & \texttt{StringLengthFieldValidator.java}  & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
+			58 & 21734562 & 12-Feb-14 & \texttt{tomcat} & 7.0.2  & \texttt{BasicAuthenticator.java} (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
+			60 & 21734562 & 12-Feb-14 & \texttt{tomcat} & 7.0.2  & \texttt{FormAuthenticator.java}  & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
+			61 & 24404964 & 25-Jun-14 & \texttt{tomcat} & 7.0.2  & \texttt{CoyoteAdapter.java}  & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
+			62 & 10289462 & 23-Apr-12 & \texttt{tomcat} & 7.0.2  & \texttt{JspRuntimeLibrary.java}  & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\
 			\hline
@@
 %It is an emerging area that software engineering research community is paying attention to. For example, 
-One can run into licensing issue if they do not check before integration third-party source code into their software.
+One can run into licensing issue if they do not check before integrating third-party source code into their software.
 A study by An et al.~\cite{An2017} found 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code.
@@
 In our study, we reveal another possible situation of software licensing issues caused by code cloning ``to Stack Overflow''.
-We found with evidence that 96 pieces of code had been copied from 14 Qualitas projects to Stack Overflow as code examples.
+We found with evidence that 110 pieces of code had been copied from 19 Qualitas projects to Stack Overflow as examples.
 They are also marked as accepted answers which increased their chances of being reused.
-The 14 open source projects came with their respective software licenses (shown in \Cref{t:q_projects_license}).
-However, the licensing information were mostly missing from these clones after they were posted on Stack Overflow.
+The 19 open source projects came with their respective software licenses (shown in \Cref{t:q_projects_license}).
+However, we found that the licensing information were mostly stripped from these clones after they were posted on Stack Overflow.
 The licensing terms on the top of source code are not copied because mostly a small part of the file was cloned to Stack Overflow.
@@
 
+We analysed licensing conflicts of online clones in QS, UD, and EX set.
 The summary of licensing information is listed in \Cref{tab:license_abc}.
 The licenses were extracted by Ninka, an automatic license identification tool \cite{German2010}.
+Since Ninka worked at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of clone pairs (duplicates were ignored).
 For the ones that could not be automatically identified by Ninka and had been reported as \texttt{SeeFile} and \texttt{Unknown}, we looked at them manually.
-The table shows license of Stack Overflow snippets (denoted as SO) and Qualitas source code.
-The number of clone pairs of each license matching has been grouped according to online cloning patterns QS, UD, and ES.
-In overall, we can see that most of the Stack Overflow snippets do not have licensing terms with them while their clone counterparts in Qualitas project do.
-
-\textbf{No license or compatible license:} There are 85 \textit{NL} clone pairs which do not have licensing information (None vs.~None) and 13 pairs in type \textit{CL} which have compatible licenses (Apache2 vs.~Apache2; EPLv1 vs.~EPLv1; None vs.~CC BY 3.0).
+The table shows license of Stack Overflow snippets and Qualitas source code.
+The results were reported in groups of QS, UD, and EX.
+Overall we can see that most of the Stack Overflow snippets do not contain licensing terms while their clone counterparts in Qualitas project do.
+
+\textbf{None or compatible license:} There are 85 \textit{NL} clone pairs which both clones do not have license (None vs.~None) and 13 pairs which have compatible licenses, i.e.~\textit{CL}, such as Apache2 vs.~Apache2; EPLv1 vs.~EPLv1; None vs.~CC BY 3.0.
 They are safe for being reused.

### 2017-02-06 cloneoverflow-latex/cloneoverflow.tex
Added a diagram of classification process and also improved the explanation of RQ2 findings.

@@
 They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs.
-After classification, we found at least \FIXME{NUMBER} online code clones pairs between Stack Overflow and Qualitas.}
+After classification, we found 670 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}
 
@@
 There were 31,946 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}.
-We have use regular expressions to automatically classify \texttt{equals()}, getter and setter methods  based on the method signature since they are not very interesting clones.
+We have use regular expressions to automatically classify \texttt{equals()}, getter and setter methods  based on the method signature since they are trivial clones and not very interesting.
 As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us captured 28,314 clone pairs and classified them into pattern BP.
-With help of the automatic classification, there were 3,632 pairs left for manual classification.
+There were 3,632 pairs left for manual check after the automatic classification.
 
@@
 A relevant and useful observation was also recorded for each clone pair.
-The second author took the role of a validating investigator performing 10\% validation (363 pairs) of the clone pairs judged by the main investigator.
-The two investigators discussed 54 classification conflicts and resolved 51 of them.
-The 3 conflicts which the two investigators could not find consensuses were resolved by the third author.
-
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.8\linewidth]{classification_process}
+	\caption{Online code clone classification process}
+	\label{fig:classification_process}
+\end{figure}
+
+The investigator followed the following steps to classify the clones (depicted in \Cref{fig:classification_process}).
+First, we looked at the source code to see their similarity.
+If they were accidentally similar after code normalisation or by relaxation of the clone detection tool's configurations, the pair was classified as AC.
+If they were boiler-plate code, the pair was classified as BP.
+If they implemented the same interface or inherited the same class and had similar code, the pair was classified as IN.
+If the pair was not UD, IN, or AC; we started a detailed investigation.
+The main investigator opened the Stack Overflow post using its post ID with a web browser, read through the post carefully both in natural text and source code, looked for any hints or evidence mentioning code copying.
+If an evidence(s) had been found and appeared to be a Qualitas project as reported in the clone pair, the pair was classified as QS.
+Several times questions, name of posters, tags were also considered to gain better understanding.
+If there was no evidence on Stack Overflow but on Qualitas project mentioning about copying from Stack Overflow, the pair was classified as SQ.
+If there was evidence(s) of copying, but from an external source(s) instead of Qualitas, the pair was classified as EX.
+Lastly, if there was no evidence of copying in any direction, but source code of the clone pair are almost identical or highly similar, we conservatively classified them as UD.
+
+To guarantee quality of the classification, the second author took the role of a validating investigator performing 10\% validation (363 pairs) of the clone pairs judged by the main investigator.
+After the validation, results from the two investigators were compared and 54 conflicts were found.
+The two investigators discussed and resolved 51 of them while 3 conflicts were resolved by the third author.
 The classification results are shown in \Cref{tab:classification_good_o}.
-For \textit{good} pairs, 10 pairs were automatically classified by regular expressions and 2,298 pairs were manually classified.
+
+\textbf{As an answer to RQ2, the classification results are explained and discussed below.}
+
+\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 110 online clone pairs with strong evidences of cloning from Qualitas projects to Stack Overflow.
+They include 3, 12, 86, and 9 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
+Most of them had statements in the Stack Overflow post saying that the code was ``copied'', ``modified'', ``adopted'' from a specific file or class in Qualitas.
+The most cloned projects were \texttt{hibernate} and \texttt{spring} having 20 clone pairs, followed by \texttt{eclipse} (15), and \texttt{hadoop} (12).
+The clones were mostly cloned as examples and were very similar to their original Qualitas code with limited modifications.
+
+\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find any clone pairs with strong evidences of cloning from Stack Overflow to Qualitas projects.
+
+\textbf{UD: Unknown Direction.} We found 382 online clone pairs with no evidence of cloning between Qualitas and Stack Overflow but with high code similarity.
+They include 11, 42, 294, and 35 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
+The most cloned projects in this pattern was \texttt{netbeans} which had 95 clone pairs.
+Most of the clones were large chunk of code involving GUI components which might also be auto-generated.
+However, we also did not have any evidence.
+The second most cloned project was \texttt{jung2} (62 pairs) that was a network and graph framework.
+There were several Stack Overflow snippets that were identical to code in \texttt{jung2}.
+The third project was \texttt{eclipse-SDK} (37 pairs).
+
+\textbf{EX: External Sources.} We found 178 online clone pairs with evidences of cloning from external sources to Stack Overflow.
+They include 4, 23, 145, and 6 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
+%\begin{table}[]
+%	\centering
+%	\caption{31 external clones found in Stack Overflow posts}
+%	\label{tab:ext_clones}
+%	\begin{tabular}{l|r|r}
+%		\hline
+%		Type        & FOSS & Web \\ \hline
+%		StackOverflow only     & 1    & 1   \\
+%		StackOverflow + Qualitas & 15   & 14  \\ \hline
+%	\end{tabular}
+%\end{table}
+This findings complement a study of inter clones between software projects \cite{Svajlenko2014}.
+We show that, besides software projects, clones can also be copied over different websites on the Internet.
+There are 15 clone pairs that are originated from programming websites.
+For example, we found a clone of code snippet to convert numbers into words which is copied from \texttt{www.rgagnon.com/javadetails/java-0426.html}.
+Both Stack Overflow and \texttt{compiere} project source code contain attribution to the original source.
+Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from \texttt{mrl.nyu.edu/\textasciitilde perlin/noise/}.
+This code is used in both Stack Overflow and \texttt{aoi} project with attribution.
+%The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
+There were 12 pairs cloned from \texttt{zxing}, \texttt{jasper}, \texttt{java.util}, \texttt{javax.servlet}, and \texttt{org.bouncycastle.crypto} project.
+
+\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs found in this study.
+Although we surly removed some of the boiler-plate code with filters before the analysis, we still observed 28,642 BP clone pairs which accounted for 89.7\% of all clone pairs we classified.
+The majority of them were \texttt{equals()} methods.
+
+\textbf{IN: Inheritance/interface.} There were 109 clone pairs found to be similar because they implemented the same interface or inheriting from the same class.
+An example was two implementations of \texttt{MouseListener} that share similar \texttt{@Override} methods of \texttt{mousePressed}, and \texttt{mouseReleased}.
+
+\textbf{AC: Accidental Clones.} 31,946 were clone pairs that were accidentally similar due to several reasons.
+Mainly, they were caused by the effects of code normalisation applied to the source code before detection.
+However, the original source code were still different enough when we manually classified them.
+Other causes include \texttt{finally} or \texttt{try-catch} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.
+
+%For \textit{good} pairs, 10 pairs were automatically classified by regular expressions and 2,298 pairs were manually classified.
 This resulted in 3 clone pairs in pattern QS which is found to be copied from a Qualitas project to Stack Overflow.
@@
 
-For \textit{ok} clone pairs, we could not feasibly investigate all 31,729 pairs manually and decided to remove $S_EN_E$ from this round of classification.
+%For \textit{ok} clone pairs, we could not feasibly investigate all 31,729 pairs manually and decided to remove $S_EN_E$ from this round of classification.
 According to the classification of \textit{good} pairs, we found that $S_EN_E$ accounted for 98.9\% of all false positive pairs in \textit{good} pairs.
@@
 11,494 clone pairs were automatically classified and 255 pairs were looked at manually.
-We found 12, 42, 23, 11,459, 20, and 103 in QS, UD, EX, BP, IN and AC respectively. Similarly, no clone pairs were found in SQ.
+%We found 12, 42, 23, 11,459, 20, and 103 in QS, UD, EX, BP, IN and AC respectively. Similarly, no clone pairs were found in SQ.
 
@@
 
-For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code.
+%For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code.
 Our regular expressions could automatically classified 16,800 of them into BP.
@@
 
-\textbf{To answer RQ2, we used our patterns of online code cloning to classified 31,946 clone pairs.
-Our results showed that although most of the clone pairs were boiler-plate code (28,642), clones from inheritance/interface (109), or accidental clones (2,525); there were 670 pairs that were very interesting.
+%\textbf{We answer RQ2 by using our patterns of online code cloning to classified 31,946 clone pairs.
+We found that a large amount of the clone pairs are boiler-plate code (28,642), clones from inheritance/interface (109), or accidental clones (2,525).
+Nevertheless, there were 670 pairs that were intentionally created.
 110 pairs had strong evidences to be cloned from Qualitas to Stack Overflow.
-382 were non-trivial clones but without strong evidence of clone direction.
-178 pairs were found to be cloned from external sources outside Qualitas projects.
-Lastly, we did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
+382 were highly-confident clones but without evidence of cloning direction.
+178 pairs were found to be cloned from external sources outside Qualitas projects.} %We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
 
@@
 
-\textbf{For RQ3, our results show that more than half (59) of QS clone pairs on Stack Overflow are outdated.
-We observed that the newer versions of these outdated snippets contained various changes ranging from a slight modifications of variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures.
-Moreover, we found three dead snippets.
+\textbf{For RQ3, our results show that more than half (62) of QS clone pairs on Stack Overflow are outdated.
+59 pairs differ from their newest versions by modifications applied to variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures.
+3 pairs are dead snippets.
 They do not exist any more in the latest version.
-Both outdated and dead online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
+These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
 Even worse, they might also introduce bugs or vulnerabilities into their software.
@@
 \end{figure}
-
-%\begin{table}
-%	\centering
-%	\caption{Breakdowns of findings from outdated code investigation of 96 category-A online clone pairs}
-%	\label{tab:stale_code}
-%	\small
-%%	\resizebox{\columnwidth}{!}{%
-%	\begin{tabular}{l|r|r|r|r|r}
-%		\hline 
-%		Project & Pairs & Outdated & Fresh & Del. & Others \\
-%		\hline
-%		ant & 1 & 0 & 1 & 0 & 0 \\
-%		log4j & 4 & 0 & 4 & 0 & 0 \\
-%		tomcat & 7 & 7 & 0 & 0 & 0 \\
-%		aspectj & 2 & 2 & 0 & 0 & 0 \\
-%		eclipse-SDK & 12 & 5 & 7 & 0 & 0 \\
-%		hadoop & 14 & 9 & 5 & 0 & 0 \\
-%		hibernate & 16 & 4 & 11 & 1 & 0 \\
-%		jasperreports & 2 & 2 & 0 & 0 & 0 \\
-%		jfreechart & 4 & 4 & 0 & 0 & 0 \\
-%		jgraph & 5 & 4 & 0 & 0 & 1 \\
-%		jgrapht & 1 & 0 & 1 & 0 & 0 \\
-%		jstock & 2 &  2 & 0 & 0 & 0 \\
-%		jung & 2 & 2 & 0 & 0 & 0 \\
-%		junit & 3 & 3 & 0 & 0 & 0 \\
-%		poi & 3 & 1 & 2 & 0 & 0 \\
-%		spring & 14 & 9 & 3 & 2 & 0 \\
-%		struts & 1 & 1 & 0 & 0 & 0 \\
-%		weka & 3 & 0 & 3 & 0 & 0 \\
-%		\hline
-%		Total & 96 & 55 & 37 & 3 & 1 \\
-%		\hline
-%	\end{tabular} 
-%%}
-%\end{table}
-
-%\begin{table*}
-%	\centering
-%	\caption{62 QS outdated online code clones. Clones can be outdated by modifications ($M$), deletion ($D$), and rewriting ($R$).}
-%	\label{tab:stale_code_details}
-%	\scriptsize
-%	\resizebox{2.1\columnwidth}{!}{%
-%	\begin{tabular}{r|l|c|p{4.5cm}|r|r|l|c|l}
-%		\hline 
-%		No. & Project & Ver. & File & Start & End & SO Post & Cause & C$_{\textit{\textrm{date}}}$ \\
-%		\hline
-%			1 & \texttt{aspectj} & 1.6.9  & aspectjtools/../Agent.java  & 7 & 18 & 18303692 & $M$  & 2015-09-08 \\
-%			2 & \texttt{aspectj} & 1.6.9  & aspectjweaver/../Agent.java  & 7 & 18 & 18303692 & $M$  & 2015-09-08 \\
-%			3 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 113 & 166 & 2513183 & $M$  &  2015-03-17 \\
-%			4 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 117 & 126 &  2513183	& $M$  &  2015-03-17 \\
-%			5 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 143 & 165 &  2513183	& $M$  &  2015-03-17 \\
-%			6 & \texttt{eclipse-SDK} & & GenerateToStringAction.java  & 178 & 187 &  2513183	& $M$  & 2011-03-01 \\
-%			7 & \texttt{eclipse-SDK} & & WizardDialog.java  & 377 & 394 &   11861598	& $M$  &  2011-02-03 \\
-%			8 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 275 & 287 & 21702608 & $M$  & 2011-06-12 \\
-%			9 & \texttt{hadoop} & 1.0.0 & DBCountPageView.java  & 289 & 309 & 21702608 & $M$  & 2011-06-12 \\
-%			10 & \texttt{hadoop} & 1.0.0 & JobSubmissionFiles.java  & 46 & 55 & 14845581 & $M$  & 2012-06-25 \\
-%			11 & \texttt{hadoop} & 1.0.0 & mapred/../LineRecordReader.java  & 47 & 60 & 16180910 & $M$  & 2011-07-25 \\
-%			12 & \texttt{hadoop} & 1.0.0 & mapreduce/../LineRecordReader.java  & 75 & 99 & 16180910 & $M$  & 2011-07-25 \\
-%			13 & \texttt{hadoop} & 1.0.0 & StringUtils.java  & 40 & 56 & 801987 & $M$  & 2013-02-04 \\
-%			14 & \texttt{hadoop} & 1.0.0 & TestJobCounters.java  & 186 & 192 & 18833798 & $M$  & 2011-06-12 \\
-%			15 & \texttt{hadoop} & 1.0.0 & TextOutputFormat.java  & 75 & 99 & 16928749 & $M$  & 2011-06-12 \\
-%			16 & \texttt{hadoop} & 1.0.0 & WritableComparator.java  & 44 & 54 & 22315734 & $M$  & 2014-11-20 \\
-%			17 & \texttt{hibernate} & 4.2.2 & ConnectionProviderInitiator.java  & 65 & 93 & 15168494 & $M$  & 2012-06-24 \\
-%			18 & \texttt{hibernate} & 4.2.2 & Example.java  & 224 & 243 & 24924255 & $M$  & 2013-04-23 \\
-%			19 & \texttt{hibernate} & 4.2.2 & SchemaUpdate.java  & 115 & 168 & 23520731 & $M$  & 2016-02-05 \\
-%			20 & \texttt{hibernate} & 4.2.2 & SettingsFactory.java  & 244 & 255 & 8257554 & $D$  & 2011-03-11 \\
-%			21 & \texttt{hibernate} & 4.2.2 & SQLServer2005LimitHandler.java  & 43 & 61 & 23967852 & $M$  & 2015-03-12 \\
-%			22 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 982 & 998 & 8037824 & $M$  & 2008-04-17 \\
-%			23 & \texttt{jasperreports} & 3.7.4 & JRVerifier.java  & 1221 & 1240 & 8037824 & $M$  & 2011-05-20 \\
-%			24 & \texttt{jfreechart} & 1.0.13 & AbstractXYItemRenderer.java  & 532 & 569 & 12936580 & $M$  & 2016-02-19 \\
-%			25 & \texttt{jfreechart} & 1.0.13 & KeyToGroupMap.java  & 18 & 30 & 16058183 & $M$  & 2013-07-03 \\
-%			26 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 502 & 520 & 21998949 & $M$  & 2008-06-02 \\
-%			27 & \texttt{jfreechart} & 1.0.13 & SpiderWebPlot.java  & 522 & 536 & 21998949 & $M$  & 2008-06-02 \\
-%			28 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 16 & 22 & 6722760 & $R$  & 2014-04-13 \\
-%			29 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 28 & 40 & 6722760 & $R$  & 2014-04-13 \\
-%			30 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 31 & 36 & 6722760 & $R$  & 2014-04-13 \\
-%			31 & \texttt{jgraph} & 5.13.0.0 & HelloWorld.java  & 39 & 56 & 6722760 & $R$  & 2014-04-13 \\
-%			32 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & 14940863 & $M$  & 2015-12-13 \\
-%			33 & \texttt{jstock} & 1.0.7c & GoogleMail.java  & 18 & 42 & 24680923 & $M$  & 2015-12-13 \\
-%			34 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 106 & 117 & 6025026 & $M$  & 2010-04-13 \\
-%			35 & \texttt{jung2} & 2\_0\_1  & ShortestPathDemo.java  & 158 & 172 & 6025026 & $M$  & 2010-04-13 \\
-%			36 & \texttt{junit} & 4.11 & Assert.java  & 33 & 52 & 23586872 & $M$  & 2015-05-12 \\
-%			37 & \texttt{junit} & 4.11 & ExternalResource.java  & 4 & 23 & 7504040 & $M$  & 2016-06-25 \\
-%			38 & \texttt{junit} & 4.11 & ExpectException.java  & 11 & 29 & 8802082 & $M$  & 2014-05-26 \\
-%			39 & poi & 3.6 & WorkbookFactory.java  & 18 & 28 & 12593810 & $M$  & 2015-04-29 \\
-%			40 & \texttt{spring} & 3.0.5 & AnnotationMethodHandler \newline ExceptionResolver.java  & 224 & 233 & 5660519 & $D$  & 2012-01-20 \\
-%			41 & \texttt{spring} & 3.0.5  & AutowireUtils.java  & 32 & 42 & 20913543 & $M$  & 2014-10-28 \\
-%			42 & \texttt{spring} & 3.0.5  & CustomCollectionEditor.java  & 33 & 71 & 18623736 & $M$  & 2013-11-21 \\
-%			43 & \texttt{spring} & 3.0.5  & DefaultAnnotation \newline HandlerMapping.java  & 78 & 92 & 3758110 & $D$  & 2012-01-20 \\
-%			44 & \texttt{spring} & 3.0.5  & DefaultPropertiesPersister.java  & 69 & 80 & 6149818 & $M$  & 2013-03-19 \\
-%			45 & \texttt{spring} & 3.0.5  & org.springframework.test/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2016-07-15 \\
-%			46 & \texttt{spring} & 3.0.5  & org.springframework.web/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2008-12-18 \\
-%			47 & \texttt{spring} & 3.0.5  & org.springframework.web.servlet/../ \newline DelegatingServletInputStream.java  & 6 & 20 & 20996373 & $M$  & 2008-12-18 \\
-%			48 & \texttt{spring} & 3.0.5  & DispatcherServlet.java  & 91 & 103 & 4781746 & $M$  & 2011-08-08 \\
-%			49 & \texttt{spring} & 3.0.5  & Jaxb2Marshaller.java  & 253 & 269 & 10924700 & $M$  & 2012-08-28 \\
-%			50 & \texttt{spring} & 3.0.5  & ScheduledTasksBean \newline DefinitionParser.java  & 42 & 52 & 3751463 & $M$  & 2016-07-05 \\
-%			51 & \texttt{struts2} & 2.2.1  & DefaultActionMapper.java  & 91 & 103 & 14019840 & $M$  & 2013-10-18 \\
-%			52 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 25 & 73 & 21734562 & $M$  & 2016-08-04 \\
-%			53 & \texttt{tomcat} & 7.0.2  & BasicAuthenticator.java  & 33 & 43 & 21734562 & $M$  & 2016-08-04 \\
-%			54 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 543 & 553 & 24404964 & $M$  & 2012-11-18 \\
-%			55 & \texttt{tomcat} & 7.0.2  & CoyoteAdapter.java  & 557 & 573 & 24404964 & $M$  & 2012-11-18 \\
-%			56 & \texttt{tomcat} & 7.0.2  & FormAuthenticator.java  & 51 & 61 & 21734562 & $M$  & 2016-08-04 \\
-%			57 & \texttt{tomcat} & 7.0.2  & HttpServlet.java  & 111 & 124 & 5266856 & $M$  & 2011-10-22 \\
-%			58 & \texttt{tomcat} & 7.0.2  & JspRuntimeLibrary.java  & 252 & 296 & 10289462 & $M$  & 2012-09-12 \\
-%		\hline
-%	\end{tabular} %
-%}
-%\end{table*}
 
@@
 	\includegraphics[width=\linewidth]{heatmap_a}
-	\caption*{(1) category A}\label{fig:heatmap_a}
+	\caption*{(1) QS clones}\label{fig:heatmap_a}
 	\endminipage\hspace{0.3cm}
@@
 	\includegraphics[width=\linewidth]{heatmap_b}
-	\caption*{(2) category B}\label{fig:heatmap_b}
+	\caption*{(2) UD clones}\label{fig:heatmap_b}
 	\endminipage\hfill
@@
 	\includegraphics[width=\linewidth]{heatmap_c}
-	\caption*{(3) category C}\label{fig:heatmap_c}
+	\caption*{(3) EX clones}\label{fig:heatmap_c}
 	\endminipage
-	\caption{Licensing between Stack Overflow code snippets and Qualitas Java file of 523 true online clone pairs}
+	\caption{Licensing between Stack Overflow code snippets and Qualitas Java file of QS, UD, and EX online clone files}
 \end{figure*}
@@
 \FIXME{More}}
-
-\subsubsection{Interesting Finding: External Clones}
-
-\begin{table}[]
-	\centering
-	\caption{31 external clones found in Stack Overflow posts}
-	\label{tab:ext_clones}
-	\begin{tabular}{l|r|r}
-		\hline
-		Type        & FOSS & Web \\ \hline
-		StackOverflow only     & 1    & 1   \\
-		StackOverflow + Qualitas & 15   & 14  \\ \hline
-	\end{tabular}
-\end{table}
-
-We found 31 clone pairs which either clones from Stack Overflow side or from both sides are found to be a copy of code snippet from somewhere else besides Qualitas projects.
-This complements the findings of inter clones between software projects \cite{Svajlenko2014} by showing that clones can also be copied over different websites on the Internet.
-There are 15 clone pairs that are originated from programming websites.
-For example, we found a clone of code snippet to convert numbers into words which is copied from \url{http://www.rgagnon.com/javadetails/java-0426.html}.
-Both Stack Overflow and \textit{Compiere} project source code contain attribution to the original source.
-Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from \url{http://mrl.nyu.edu/~perlin/noise/}.
-This code is used in both Stack Overflow and \textit{AoI} project with attribution.
-The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
-However, there are 4 clone pairs that are cloned from \textit{JUnit} to both Stack Overflow and \textit{Eclipse} and 12 pairs cloned from other Java projects outside Qualitas corpus.
-They are originated from \textit{zxing} projects, Apache projects (ant, jasper), Java packages (\texttt{java.util}, \texttt{javax.servlet}, JUnit, and \texttt{org.bouncycastle.crypto} project.
 

### 2017-02-08 cloneoverflow-latex/cloneoverflow.tex
Use ACM 2017 style.

--- 2017-02-05 cloneoverflow-latex/cloneoverflow.tex
@@
-\documentclass{sig-alternate-05-2015}
+%\documentclass{sig-alternate-05-2015}
+\documentclass[sigconf,review, anonymous]{acmart}
+\acmConference[ESEC/FSE 2017]{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--8 September, 2017}{Paderborn, Germany}
+
 \usepackage[utf8]{inputenc}
@@
 \usepackage{multirow}
-\usepackage[table]{xcolor}
+%\usepackage[table]{xcolor}
 \usepackage{float}
@@
 %Conference
-\conferenceinfo{ESEC/FSE 2017}{September 4--8, 2017, Paderborn, Germany}
+%\conferenceinfo{ESEC/FSE 2017}{September 4--8, 2017, Paderborn, Germany}
 
@@
 
-\title{Are We Reusing Outdated and License-Violating \newline Code Snippets from Stack Overflow?}
-
-\numberofauthors{1}
+\title{Are We Reusing Outdated and License-Violating Code Snippets from Stack Overflow?}
+
+%\numberofauthors{1}
 \author{
@@
 		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 88 \\ 
+		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 181 \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total  & 310,803 & & & & & 31,946 \\ 
+		Total  & 310,803 & & & & & 32,039 \\ 
 		\hline
@@
 		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
-		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 77 \\
+		\multirow{1}{*}{\textit{good}} & 2,308 & 9 & 2,299 & x \\
+		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,495 & 254 & x \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 525 \\
-		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
+		\multirow{1}{*}{$S_D$} & 17,801 & 16,930 & 871 & 704 \\
+		\multirow{1}{*}{$N_D$} & 181 & 10 & 171 & x \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total  & 31,946 & 28,444 & 3,502 & 670 \\ 
+		Total  & 32,039 & 28,444 & 3,595 & x \\ 
 		\hline
@@
 We have tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and we found that 85\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation.
-Using the three filters, we reduced the size of $N_D$ clones to 88 pairs.
-
-In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs).
-Finally, there are 3,502 pairs remaining which we manually classified them.
+Using the three filters, we reduced the size of $N_D$ clones to 181 pairs.
+
+In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 32,039 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs).
+Finally, there are 3,595 pairs remaining which we manually classified them.
 The classification summary is shown in \Cref{tab:online_clone_classification_results}.
 
-\textbf{To answer RQ1, we found 31,946 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
-They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs.
+\textbf{To answer RQ1, we found 32,039 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
+They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 181 $N_D$ pairs.
 After classification, we found at least \FIXME{NUMBER} online code clones pairs between Stack Overflow and Qualitas.}
@@
 			\hline 
-			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
+			ES & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
 			\\ 
@@
 			\hline 
-			AC & Accidental similarity, false clones \\ 
+			FC & Accidental similarity, false clones \\ 
 			\hline 
@@
 They are unique enough not be boiler-plate and inheritance or interface implementation.
-ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from an external source(s).
+ES (\textbf{E}xternal \textbf{S}ources) is a cloning that has an evidence of copying from an external source(s).
 Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components).
@@
 They usually share similar overriding methods.
-The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents false clone pairs.
+The last pattern, FC (\textbf{F}alse \textbf{C}lones), represents false clone pairs.
 They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools.
@@
 We are looking for unique and meaningful clones in this study.
-Thus, we consider clone pairs classified into pattern QS, SQ, UD, and EX as true positive, and BP, IN, and AC as false positive.
+Thus, we consider clone pairs classified into pattern QS, SQ, and UN as true positive, and BP, IN, and FC as false positive.
 
@@
 			\hline
-			Set & QS & SQ & UD & EX & BP  & EX & AC & Total \\ 
+			Set & A & A' & B & C & D  & E & F & Total \\ 
 			\hline
@@
 	\resizebox{2.1\columnwidth}{!}{%
-	\begin{tabular}{r|l|c|p{4.5cm}|r|r|l|l|l|c|l}
+	\begin{tabular}{r|l|c|p{3cm}|r|r|l|l|l|c|l}
 		\hline 

### 2017-02-08 cloneoverflow-latex/cloneoverflow.tex

--- 2017-02-06 cloneoverflow-latex/cloneoverflow.tex
@@
 
-A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement \textit{RawComparator} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}.
+A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement {\small{\texttt{RawComparator}}} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}.
 In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
-The snippet shows how \texttt{hadoop} implements \textit{compare} method in its \textit{WritableComparator} class.
-The code snippet on the right hand side shows another version of the same \textit{compare} method in \textit{WritableComparator} class but it is extracted from the latest version of \texttt{hadoop}.
-We can obviously see that they are highly similar except one line, \verb|buffer.reset(null,0,0);|, is added in the latest version after \verb|key2.readFields(buffer);|.
-The added line is intended for cleaning up the reference in \verb|buffer| variable.
-While this change has already been introduced into \textit{compare} method in the latest version of \texttt{hadoop}, the code example in Stack Overflow post is still unchanged.
+The snippet shows how {\small{\texttt{hadoop}}} implements {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}} class.
+The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class but it is extracted from the latest version of {\small{\texttt{hadoop}}}.
+We can obviously see that they are highly similar except one line, {\small{\verb|buffer.reset(null,0,0);|}}, is added in the latest version after {\small{\verb|key2.readFields(buffer);|}}.
+The added line is intended for cleaning up the reference in {\small{\verb|buffer|}} variable.
+While this change has already been introduced into {\small{\texttt{compare}}} method in the latest version of {\small{\texttt{hadoop}}}, the code example in Stack Overflow post is still unchanged.
 This example shows that there can be inconsistencies between online code clones and its original.
@@
 
-\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
+\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{{\small\texttt{https://archive.org/details/stackexchange}}} in January 2016.
 The archived dump has a size of 9 gigabytes.
-The data dump was in XML format containing information of \textit{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts.
-We were interested in code snippets embedded in posts which were located between \texttt{<code></code>} tags.
+The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts.
+We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags.
 A Stack Overflow thread contains a post of question and several posts of answers.
@@
 45051109\_0, and 45051109\_1.).
-Lastly, we added \texttt{.java} extension to the file's names so that clone detectors could recognise them.
-We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
+Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
+We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: {\small\texttt{https://github.com/AlDanial/cloc}}}.
 
@@
 	\small
-	\resizebox{\columnwidth}{!}{%
+%	\resizebox{\columnwidth}{!}{%
 		\begin{tabular}{l|r|r|r|r}
@@
 		\end{tabular} %
-	}
+%	}
 \end{table}
@@
 	\small
-	\resizebox{\columnwidth}{!}{%
+%	\resizebox{\columnwidth}{!}{%
 	\begin{tabular}{l|r|r|r|r|r|r}
@@
 
-In our clone classification process, we used a script to automatically classify \texttt{equals()} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the \texttt{equals()} pairs came from \textit{ok} and $S_D$ pairs).
+In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs).
 Finally, there are 3,502 pairs remaining which we manually classified them.
@@
 ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from an external source(s).
-Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of \verb|equals()| methods, getters and setters, or IDE-generated code (e.g.~GUI components).
+Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters and setters, or IDE-generated code (e.g.~GUI components).
 Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface.
@@
 The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents false clone pairs.
-They can be either accidentally similar clones (e.g.~similar \texttt{try-catch} statements), similar clones after code normalisation, or just false positives of the tools.
+They can be either accidentally similar clones (e.g.~similar {\small\texttt{try-catch}} statements), similar clones after code normalisation, or just false positives of the tools.
 Using the classification patterns, we can also calculate the number of true and false positives.
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{classification_process}
+	\includegraphics[width=0.6\linewidth]{classification_process}
 	\caption{Online code clone classification process}
@@
 They include 11, 42, 294, and 35 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
-The most cloned projects in this pattern was \texttt{netbeans} which had 95 clone pairs.
+The most cloned projects in this pattern was {\small{\texttt{netbeans}}} which had 95 clone pairs.
 Most of the clones were large chunk of code involving GUI components which might also be auto-generated.
 However, we also did not have any evidence.
-The second most cloned project was \texttt{jung2} (62 pairs) that was a network and graph framework.
-There were several Stack Overflow snippets that were identical to code in \texttt{jung2}.
-The third project was \texttt{eclipse-SDK} (37 pairs).
+The second most cloned project was {\small{\texttt{jung2}}} (62 pairs) that was a network and graph framework.
+There were several Stack Overflow snippets that were identical to code in {\small{\texttt{jung2}}}.
+The third project was {\small{\texttt{eclipse-SDK}}} (37 pairs).
 
@@
 There are 15 clone pairs that are originated from programming websites.
-For example, we found a clone of code snippet to convert numbers into words which is copied from \texttt{www.rgagnon.com/javadetails/java-0426.html}.
+For example, we found a clone of code snippet to convert numbers into words which is copied from {\small{\texttt{www.rgagnon.com/javadetails/java-0426.html}}}.
 Both Stack Overflow and \texttt{compiere} project source code contain attribution to the original source.
-Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from \texttt{mrl.nyu.edu/\textasciitilde perlin/noise/}.
+Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from {\small{\texttt{mrl.nyu.edu/\textasciitilde perlin/noise/}}}.
 This code is used in both Stack Overflow and \texttt{aoi} project with attribution.
 %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
-There were 12 pairs cloned from \texttt{zxing}, \texttt{jasper}, \texttt{java.util}, \texttt{javax.servlet}, and \texttt{org.bouncycastle.crypto} project.
+There were 12 pairs cloned from {\small{\texttt{zxing}}}, {\small{\texttt{jasper}}}, {\small{\texttt{java.util}}}, {\small{\texttt{javax.servlet}}}, and {\small{\texttt{org.bouncycastle.crypto}}} project.
 
@@
 Although we surly removed some of the boiler-plate code with filters before the analysis, we still observed 28,642 BP clone pairs which accounted for 89.7\% of all clone pairs we classified.
-The majority of them were \texttt{equals()} methods.
+The majority of them were {\small{\texttt{equals()}}} methods.
 
 \textbf{IN: Inheritance/interface.} There were 109 clone pairs found to be similar because they implemented the same interface or inheriting from the same class.
-An example was two implementations of \texttt{MouseListener} that share similar \texttt{@Override} methods of \texttt{mousePressed}, and \texttt{mouseReleased}.
+An example was two implementations of {\small{\texttt{MouseListener}}} that share similar {\small{\texttt{@Override}}} methods of {\small{\texttt{mousePressed}}}, and {\small{\texttt{mouseReleased}}}.
 
@@
 However, the original source code were still different enough when we manually classified them.
-Other causes include \texttt{finally} or \texttt{try-catch} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.
+Other causes include {\small{\texttt{finally}}} or {\small{\texttt{try-catch}}} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.
 
@@
 We discovered 59 outdated online clone pairs out of 110 pairs.
-\texttt{spring} and \texttt{hibernate} have the maximum number of 20 outdated pairs, followed by 15 from \texttt{eclipse}, and 12 from \texttt{hadoop}.
-An example of outdated code in \texttt{hadoop}'s \texttt{WritableComparator.java} has already been shown in \Cref{fig:before-after}.
+{\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}.
+An example of outdated code in {\small{texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} has already been shown in \Cref{fig:before-after}.
 We also found a few outdated code which contained heavy modifications.
-For example, the code snippet in Stack Overflow post 23520731, a copy of \texttt{SchemaUpdate.java} in \texttt{hibernate}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
+For example, the code snippet in Stack Overflow post 23520731, a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
 We also found 3 ``dead'' snippets.
 These snippets did not have their originals in the latest version of the projects anymore.
-For example, the snippet in Stack Overflow post 3758110, a copy of \texttt{DefaultAnnotationHandlerMapping.java} in \texttt{spring}, was deleted in commit \texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted.
+For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in {\small{\texttt{spring}}}, was deleted in commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted.
 %The latest version of Spring does not contain the file anymore.
@@
 	\resizebox{2.1\columnwidth}{!}{%
-	\begin{tabular}{r|l|c|l|c|p{5.8cm}|r|r|c|c|c}
+	\begin{tabular}{r|l|c|l|c|p{5cm}|r|r|c|c|c}
 		\hline 
@@
 The summary of licensing information is listed in \Cref{tab:license_abc}.
-The licenses were extracted by Ninka, an automatic license identification tool \cite{German2010}.
+The licenses were extracted by \textbf{Ninka}, an automatic license identification tool \cite{German2010}.
 Since Ninka worked at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of clone pairs (duplicates were ignored).
-For the ones that could not be automatically identified by Ninka and had been reported as \texttt{SeeFile} and \texttt{Unknown}, we looked at them manually.
+For the ones that could not be automatically identified by Ninka and had been reported as {\small\texttt{SeeFile}} and {\small\texttt{Unknown}}, we looked at them manually.
 The table shows license of Stack Overflow snippets and Qualitas source code.

### 2017-02-08 cloneoverflow-latex/cloneoverflow.tex
Fixed the size of figures
Update charts.

@@
 \vspace{0.5ex}%
-\noindent\textbf{3.~Online code clone oracle:} The 3,595 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://some.where} and can be used as a clone oracle.
+\noindent\textbf{3.~Online code clone oracle:} The 3,632 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://to.be.disclosed.after.review} and can be used as a clone oracle.
 
@@
 	\centering
-	\includegraphics[width=\linewidth]{exp_framework_new}
+	\includegraphics[width=0.8\linewidth]{exp_framework_new}
 	\caption{Experimental framework}
@@
 
-\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{{\small\texttt{https://archive.org/details/stackexchange}}} in January 2016.
+\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
 The archived dump has a size of 9 gigabytes.
@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: {\small\texttt{https://github.com/AlDanial/cloc}}}.
+We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
 
@@
 		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
-		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 77 \\
+		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 75 \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
@@
 		\hline
-		Total  & 31,946 & 28,314 & 3,632 & 670 \\ 
+		Total  & 31,946 & 28,314 & 3,632 & 668 \\ 
 		\hline
@@
 They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs.
-After classification, we found 670 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}
+After classification, we found 668 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}
 
@@
 There are 15 clone pairs that are originated from programming websites.
-For example, we found a clone of code snippet to convert numbers into words which is copied from {\small{\texttt{www.rgagnon.com/javadetails/java-0426.html}}}.
-Both Stack Overflow and \texttt{compiere} project source code contain attribution to the original source.
-Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from {\small{\texttt{mrl.nyu.edu/\textasciitilde perlin/noise/}}}.
-This code is used in both Stack Overflow and \texttt{aoi} project with attribution.
+For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html.
+Both Stack Overflow and {\small\texttt{compiere}} project source code contain attribution to the original source.
+Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/.
+This code is used in both Stack Overflow and {\small\texttt{aoi}} project with attribution.
 %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
-There were 12 pairs cloned from {\small{\texttt{zxing}}}, {\small{\texttt{jasper}}}, {\small{\texttt{java.util}}}, {\small{\texttt{javax.servlet}}}, and {\small{\texttt{org.bouncycastle.crypto}}} project.
+There were 12 pairs cloned from {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and {\small\texttt{org.bouncycastle.crypto}} project.
 
@@
 \textbf{IN: Inheritance/interface.} There were 109 clone pairs found to be similar because they implemented the same interface or inheriting from the same class.
-An example was two implementations of {\small{\texttt{MouseListener}}} that share similar {\small{\texttt{@Override}}} methods of {\small{\texttt{mousePressed}}}, and {\small{\texttt{mouseReleased}}}.
+An example was two implementations of {\small{\texttt{MouseListener}}} that share similar {\small\texttt{@Override}} methods of {\small\texttt{mousePressed}}, and {\small\texttt{mouseReleased}}.
 
@@
 However, the original source code were still different enough when we manually classified them.
-Other causes include {\small{\texttt{finally}}} or {\small{\texttt{try-catch}}} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.
+Other causes include {\small\texttt{finally}} or {\small\texttt{try-catch}} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.
 
@@
 			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
-			\multirow{1}{*}{\textit{ok}}  & 12 & 0 & 42 & 23 & 11,549 & 20 & 103 & 11,749 \\
+			\multirow{1}{*}{\textit{ok}}  & 12 & 0 & 40 & 23 & 11,547 & 22 & 105 & 11,749 \\
 			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
@@
 			\hline
-			Total & 110 & 0 & 382 & 178 & 28,642 & 109 & 2,525 & 31,946 \\ 
+			Total & 110 & 0 & 380 & 178 & 28,749 & 111 & 2,418 & 31,946 \\ 
 			\hline
@@
 	\centering
-	\includegraphics[width=\linewidth]{outdated}
-	\caption{Findings from outdated code investigation of 96 pattern-A online clone pairs}
+	\includegraphics[width=\linewidth]{freshness}
+	\caption{Freshness of 110 QS online clone pairs}
 	\label{fig:outdated}
@@
 	\caption{62 QS outdated online clone pairs.
-Outdated clones are caused (\textit{C}) by statement modifications, added, deleted (\textit{sm}), file deletion (\textit{fd}), and method rewriting (\textit{rw}).}
+Outdated clones are caused (\textit{C}) by modified/added/deleted statements (\textit{sm}), file deletion (\textit{fd}), and method rewriting (\textit{rw}).}
 	\label{tab:stale_code_details}
 	\small
-	\resizebox{2.1\columnwidth}{!}{%
-	\begin{tabular}{r|l|c|l|c|p{5cm}|r|r|c|c|c}
+	\resizebox{2\columnwidth}{!}{%
+	\begin{tabular}{r|l|c|l|c|p{5.8cm}|r|r|c|c|c}
 		\hline 
@@
 		\hline
-			1 & 18303692 & 18-Aug-13 & \texttt{aspectj} & 1.6.9  & \texttt{aspectjtools/../Agent.java}  & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
-			2 & 18303692 & 18-Aug-13 & \texttt{aspectj} & 1.6.9  & \texttt{aspectjweaver/../Agent.java}  & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
-			3 & 2513183 & 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 113 & 166 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
-			4 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 117 & 126 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
-			5 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 143 & 165 & 5-Jun-13 & \textit{sm} & 1-Mar-11 \\
-			6 & 2513183	& 25-Mar-10 & \texttt{eclipse-SDK} & 4.3 & \texttt{GenerateToStringAction.java}  & 178 & 187 & 5-Jun-13 & \textit{sm} & 5-Jun-13 \\
-			7 & 11861598 & 8-Aug-12 & \texttt{eclipse-SDK} & 4.3 & \texttt{WizardDialog.java}  & 377 & 394 & 1-May-13 & \textit{sm} & 21-Jun-13 \\
-			8 & 22315734 & 11-Mar-14 & \texttt{hadoop} & 1.0.0 & \texttt{WritableComparator.java}  & 44 & 54 & 25-Aug-11 & \textit{sm} & 20-Nov-14 \\
-			9 & 801987 & 29-Apr-09 & \texttt{hadoop} & 1.0.0 & \texttt{StringUtils.java}  & 40 & 56 & 15-Dec-11 & \textit{sm} & 4-Feb-13 \\
-			10 & 21702608 & 11-Feb-14 & \texttt{hadoop} & 1.0.0 & \texttt{DBCountPageView.java}  & 275 & 287 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
-			11 & 21702608 & 11-Feb-14 & \texttt{hadoop} & 1.0.0 & \texttt{DBCountPageView.java}  & 289 & 309 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
-			12 & 14845581 & 13-Feb-13 & \texttt{hadoop} & 1.0.0 & \texttt{JobSubmissionFiles.java}  & 46 & 55 & 15-Dec-11 & \textit{sm} & 25-Jun-12 \\
-			13 & 16180910 & 24-Apr-13 & \texttt{hadoop} & 1.0.0 & \texttt{mapred/../LineRecordReader.java}  & 47 & 60 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
-			14 & 16180910 & 24-Apr-13 & \texttt{hadoop} & 1.0.0 & \texttt{mapreduce/../LineRecordReader.java}  & 41 & 54 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
-			15 & 15168494 & 24-Feb-14 & \texttt{hibernate} & 4.2.2 & \texttt{ConnectionProviderInitiator.java}  & 65 & 93 & 22-May-13 & \textit{sm} & 26-Apr-13 \\
-			16 & 24924255 & 24-Jul-14 & \texttt{hibernate} & 4.2.2 & \texttt{Example.java}  & 224 & 243 & 22-May-13 & \textit{sm} & 23-Apr-13 \\
-			17 & 23520731 & 7-May-14 & \texttt{hibernate} & 4.2.2 & \texttt{SchemaUpdate.java}  & 115 & 168 & 22-May-13 & \textit{sm} & 5-Feb-16 \\
-			18 & 8257554 & 26-Nov-11 & \texttt{hibernate} & 4.2.2 & \texttt{SettingsFactory.java}  & 244 & 255 & 22-May-13 & \textit{fd} & 11-Mar-11 \\
-			19 & 23967852 & 31-Apr-14 & \texttt{hibernate} & 4.2.2 & \texttt{SQLServer2005LimitHandler.java}  & 43 & 61 & 22-May-13 & \textit{sm} & 11-May-16 \\
-			20 & 19298607 & 10-Oct-13 & \texttt{hibernate} & 4.2.2 & \texttt{Oracle9iDialect.java} & 23 & 32 & 22-May-13 & \textit{sm} & 12-Apr-15 \\
-			21 & 10031897 & 5-Apr-12 & \texttt{hibernate} & 4.2.2 & \texttt{AliasToBeanResultTransformer.java} & 44 & 61 & 22-May-13 & \textit{sm} & 4-Jun-15 \\ 
-			22 & 8037824 & 7-Nov-11 & \texttt{jasperreports} & 3.7.4 & \texttt{JRVerifier.java}  & 982 & 998 & 31-May-10 & \textit{sm} & 17-Apr-08 \\
-			23 & 8037824 & 7-Nov-11 & \texttt{jasperreports} & 3.7.4 & \texttt{JRVerifier.java}  & 1221 & 1240 & 31-May-10 & \textit{fd} & 20-May-11 \\
-			24 & 12936580 & 17-Oct-12 & \texttt{jfreechart} & 1.0.13 & \texttt{AbstractXYItemRenderer.java}  & 532 & 569 & 20-Apr-09 & \textit{sm} & 16-Jan-16 \\
-			25 & 16058183 & 17-Apr-13 & \texttt{jfreechart} & 1.0.13 & \texttt{KeyToGroupMap.java}  & 18 & 30 & 20-Apr-09 & \textit{sm} & 29-Jun-07 \\
-			26 & 21998949 & 24-Feb-14 & \texttt{jfreechart} & 1.0.13 & \texttt{SpiderWebPlot.java}  & 502 & 520 & 20-Apr-09 & \textit{sm} & 2-Jun-08 \\
-			27 & 21998949 & 24-Feb-14 & \texttt{jfreechart} & 1.0.13 & \texttt{SpiderWebPlot.java}  & 522 & 536 & 20-Apr-09 & \textit{sm} & 22-Nov-13 \\
-			28 & 6722760 & 17-Jul-11 & \texttt{jgraph} & 5.13.0.0 & \texttt{HelloWorld.java} (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{rw} & 13-Apr-14 \\
-			31 & 6025026 & 17-Jul-11 & \texttt{jung2} & 2\_0\_1  & \texttt{ShortestPathDemo.java}  & 106 & 117 & 20-Jun-08 & \textit{sm} & 13-Apr-10 \\
-			32 & 6025026 & 17-Jul-11 & \texttt{jung2} & 2\_0\_1  & \texttt{ShortestPathDemo.java}  & 158 & 172 & 20-Jun-08 & \textit{sm} & 29-Nov-15 \\
-			33 & 23586872 & 31-May-14 & \texttt{junit} & 4.11 & \texttt{Assert.java} & 33 & 52 & 11-Oct-12 & \textit{sm} & 12-May-15 \\
-			34 & 7504040 & 29-Sep-11 & \texttt{junit} & 4.11 & \texttt{ExternalResource.java}  & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
-			35 & 8802082 & 10-Jan-12 & \texttt{junit} & 4.11 & \texttt{ExpectException.java} (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
-			37 & 12593810 & 26-Sep-12 & poi & 3.6 & \texttt{WorkbookFactory.java}  & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
-			38 & 20913543 & 6-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{AutowireUtils.java} & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
-			39 & 18623736 & 4-Sep-13 & \texttt{spring} & 3.0.5  & \texttt{CustomCollectionEditor.java}  & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
-			40 & 22865824 & 4-Apr-14 & \texttt{spring} & 3.0.5  & \texttt{JavaMailSenderImpl.java} & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
-			41 & 22865824 & 4-Apr-14 & \texttt{spring} & 3.0.5  & \texttt{JavaMailSenderImpl.java} & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
-			42 & 20421869 & 6-Dec-13 & \texttt{spring} & 3.0.5  & \texttt{ClassPathScanningCandidate \newline ComponentProvider.java} (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
-			44 & 3751463 & 20-Sep-10 & \texttt{spring} & 3.0.5  & \texttt{ScheduledTasksBean \newline DefinitionParser.java}  & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
-			45 & 6149818 & 27-May-11 & \texttt{spring} & 3.0.5  & \texttt{DefaultPropertiesPersister.java}  & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
-			46 & 10952561 & 8-Jun-12 & \texttt{spring} & 3.0.5  & \texttt{HibernateTemplate.java}  & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
-			47 & 10952561 & 8-Jun-12 & \texttt{spring} & 3.0.5  & \texttt{Jaxb2Marshaller.java}  & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
-			48 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{test/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
-			49 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{web/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
-			50 & 20996373 & 8-Jan-14 & \texttt{spring} & 3.0.5  & \texttt{servlet/../\newline DelegatingServletInputStream.java}  & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
-			51 & 5660519 & 15-Apr-11 & \texttt{spring} & 3.0.5 & \texttt{AnnotationMethodHandler \newline ExceptionResolver.java}  & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
-			52 & 4781746 & 24-Jan-11 & \texttt{spring} & 3.0.5  & \texttt{DispatcherServlet.java}  & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
-			53 & 3758110 & 21-Sep-10 & \texttt{spring} & 3.0.5  & \texttt{DefaultAnnotation \newline HandlerMapping.java}  & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
-			54 & 9003314 & 25-Jan-12 & \texttt{spring} & 3.0.5  & \texttt{WebDataBinder.java} & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
-			55 & 14019840 & 24-Dec-12 & \texttt{struts2} & 2.2.1  & \texttt{DefaultActionMapper.java}  & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
-			56 & 15131432 & 28-Feb-13 & \texttt{struts2} & 2.2.1  & \texttt{FreemarkerManager.java}  & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
-			57 & 15110171 & 27-Feb-13 & \texttt{struts2} & 2.2.1  & \texttt{StringLengthFieldValidator.java}  & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
-			58 & 21734562 & 12-Feb-14 & \texttt{tomcat} & 7.0.2  & \texttt{BasicAuthenticator.java} (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
-			60 & 21734562 & 12-Feb-14 & \texttt{tomcat} & 7.0.2  & \texttt{FormAuthenticator.java}  & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
-			61 & 24404964 & 25-Jun-14 & \texttt{tomcat} & 7.0.2  & \texttt{CoyoteAdapter.java}  & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
-			62 & 10289462 & 23-Apr-12 & \texttt{tomcat} & 7.0.2  & \texttt{JspRuntimeLibrary.java}  & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\
+			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
+			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
+			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
+			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
+			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{sm} & 1-Mar-11 \\
+			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{sm} & 5-Jun-13 \\
+			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{sm} & 21-Jun-13 \\
+			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{sm} & 20-Nov-14 \\
+			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{sm} & 4-Feb-13 \\
+			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
+			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
+			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{sm} & 25-Jun-12 \\
+			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
+			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
+			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{sm} & 26-Apr-13 \\
+			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{sm} & 23-Apr-13 \\
+			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{sm} & 5-Feb-16 \\
+			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{fd} & 11-Mar-11 \\
+			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{sm} & 11-May-16 \\
+			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{sm} & 12-Apr-15 \\
+			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{sm} & 4-Jun-15 \\ 
+			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{sm} & 17-Apr-08 \\
+			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{fd} & 20-May-11 \\
+			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{sm} & 16-Jan-16 \\
+			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{sm} & 29-Jun-07 \\
+			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{sm} & 2-Jun-08 \\
+			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{sm} & 22-Nov-13 \\
+			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{rw} & 13-Apr-14 \\
+			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{sm} & 13-Apr-10 \\
+			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{sm} & 29-Nov-15 \\
+			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{sm} & 12-May-15 \\
+			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
+			35 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
+			37 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
+			38 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
+			39 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
+			40 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
+			41 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
+			42 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
+			44 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
+			45 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
+			46 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
+			47 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
+			48 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
+			49 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
+			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
+			51 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerExceptionResolver.java & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
+			52 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
+			53 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
+			54 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
+			55 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
+			56 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
+			57 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
+			58 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
+			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
+			61 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
+			62 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\
 			\hline

### 2017-02-08 cloneoverflow-latex/StackoverflowCharts/StackedBar.py

@@ -1,12 +1,14 @@
 import pandas as pd
 import matplotlib.pyplot as plt
 
-raw_data = {'systems': ['ant', 'log4j', 'aspectj', 'eclipse', 'hadoop', 'hibernate', 'jasperreports', 'jfreechart', 'jgraph', 'jgrapht', 'jstock', 'jung', 'junit', 'poi', 'spring', 'struts', 'tomcat', 'weka'],
-            'fresh': [1, 4, 0, 7, 5, 11, 0, 0, 0, 1, 0, 0, 0, 2, 3, 0, 0, 3],
-            'outdated': [0, 0, 2, 5, 9, 4,  2, 4, 4, 0, 2, 2, 3, 1, 9, 1, 7, 0],
-            'deleted': [0, 0, 0, 0, 0, 1,  0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0],
-            'other': [0, 0, 0, 0, 0, 0,  0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0]}
-df = pd.DataFrame(raw_data, columns=['systems', 'fresh', 'outdated', 'deleted', 'other'])
+raw_data = {'systems': ['hibernate', 'spring', 'eclipse-SDK', 'hadoop', 'tomcat',
+                        'log4j', 'jfreechart', 'junit', 'jgraph', 'jung2',
+                        'poi', 'struts2', 'weka', 'aspectj', 'jasperreports',
+                        'antlr', 'ant', 'itext', 'jgrapht'],
+            'fresh': [13, 3, 10, 5, 2, 5, 0, 0, 0, 1, 2, 0, 3, 0, 0, 1, 1, 1, 1],
+            'outdated': [6,	15,	5,	7,	5,	0,	4,	4,	3,	2,	1,	3,	0,	2,	1,	0,	0,	0,	0],
+            'deleted': [1,	2,	0,	0,	0,	0,	0,	0,	0,	0,	0,	0,	0,	0,	1,	0,	0,	0,	0]}
+df = pd.DataFrame(raw_data, columns=['systems', 'fresh', 'outdated', 'deleted'])
 df
 
 # Create the general blog and the "subplots" i.e. the bars
@@ -58,19 +60,6 @@ ax1.bar(bar_l,
         # with color
         color='red')
 
-# Create a bar plot, in position bar_1
-ax1.bar(bar_l,
-        # using the other data
-        df['other'],
-        # set the width
-        width=bar_width,
-        # with deleted and outdated on the bottom
[…]

### 2017-02-08 cloneoverflow-latex/freshness.m

@@ -1,0 +1,44 @@
+y = [13	6 1;
+3	15	2;
+10	5	0;
+5	7	0;
+2	5	0;
+5	0	0;
+0	4	0;
+0	4	0;
+0	3	0;
+1	2	0;
+2	1	0;
+0	3	0;
+3	0	0;
+0	2	0;
+0	1	1;
+1	0	0;
+1	0	0;
+1	0	0;
+1	0	0];
+bar(y,'stacked')
+
+P=findobj(gca,'type','patch');
+C=['w','k','m','g']; % make a colors list 
+for n=1:length(P) 
+set(P(n),'facecolor',C(n));
+end
+
+xticks([1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19])
+xticklabels({'hibernate', 'spring', 'eclipse-SDK', 'hadoop', 'tomcat', ...
+    'log4j', 'jfreechart', 'junit', 'jgraph', 'jung2', 'poi', 'struts2', ... 
+    'weka', 'aspectj', 'jasperreports', 'antlr', 'ant', 'itext', 'jgrapht'})
+%xlabel('Project','FontSize',15)
+ylabel('Clone pair','FontSize',15)
+t_legend=legend('Fresh', 'Outdated', 'Dead');
+set(t_legend,'FontSize',15);
+set(gca,'FontSize',15);
+set(gca,'XTickLabelRotation',45)
+box on
+
+h=gcf;
+set(h,'PaperPositionMode','auto');         
+set(h,'PaperOrientation','landscape');
+set(h,'Position',[50 50 1200 500]);
+print('freshness','-dpdf','-bestfit')

### 2017-02-11 cloneoverflow-latex/cloneoverflow.tex
We are writing in english, not italian...
Updated the license violation section

@@
 \usepackage[utf8]{inputenc}
-\usepackage[italian]{babel}
+\usepackage[english]{babel}
 \usepackage[T1]{fontenc}
@@
 	\centering
-	\includegraphics[width=0.6\linewidth]{classification_process}
+	\includegraphics[width=0.8\linewidth]{classification_process}
 	\caption{Online code clone classification process}
@@
 			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
-			\multirow{1}{*}{\textit{ok}}  & 12 & 0 & 40 & 23 & 11,547 & 22 & 105 & 11,749 \\
+			\multirow{1}{*}{\textit{ok}}  & 14 & 0 & 40 & 21 & 11,547 & 22 & 105 & 11,749 \\
 			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
@@
 			\hline
-			Total & 110 & 0 & 380 & 178 & 28,749 & 111 & 2,418 & 31,946 \\ 
+			Total & 112 & 0 & 380 & 176 & 28,749 & 111 & 2,418 & 31,946 \\ 
 			\hline
@@
 
-\textbf{For RQ3, our results show that more than half (62) of QS clone pairs on Stack Overflow are outdated.
-59 pairs differ from their newest versions by modifications applied to variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures.
-3 pairs are dead snippets.
+\textbf{For RQ3, our results show that more than half (64) of QS clone pairs on Stack Overflow are outdated.
+60 pairs differ from their newest versions by modifications applied to variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures.
+4 pairs are dead snippets.
 They do not exist any more in the latest version.
@@
 			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{sm} & 12-May-15 \\
-			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
-			35 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
-			37 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
-			38 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
-			39 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
-			40 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
-			41 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
-			42 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
-			44 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
-			45 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
-			46 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
-			47 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
-			48 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
-			49 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
-			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
-			51 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerExceptionResolver.java & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
-			52 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
-			53 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
-			54 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
-			55 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
-			56 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
-			57 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
-			58 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
-			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
-			61 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
-			62 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\
+			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
+			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
+			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
+			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
+			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
+			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
+			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
+			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
+			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
+			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
+			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
+			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
+			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
+			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
+			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
+			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerExceptionResolver.java & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
+			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
+			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
+			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
+			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
+			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
+			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
+			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
+			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
+			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
+			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\
 			\hline
@@
 	\centering
-	\caption{14 Qualitas projects with the highest number of true clones on Stack Overflow with their respective licenses}
+	\caption{Licenses of online clones (file-level) from Qualitas projects}
 	\label{t:q_projects_license}
@@
 	\small
-	\begin{tabular}{l|r|p{4cm}}
-		\hline 
-		Project & Version & Licenses (no.~of files) \\
-		\hline
-		%		apache-ant & 1.8.4 & Apache2.0 \\
-		%		apache-log4j & 1.2.16 & \\
-		aspectj & 1.6.9 & Apache-1.1 (182), CPLv1 (3), \newline EPLv1 (2011), None (23), \newline SeeFile (6), Unknown (286) \\
-		\hline
-		eclipse-SDK &  4.1 & Apache-2 (2183), \newline BSD3NoWarranty (107), \newline CDDLorGPLv2 (296), \newline EPLv1 (18823), MPLv1.1 (93), \newline None (224), SeeFile (8), \newline spdxBSD3 (185), \newline spdxMIT (1), Unknown (714) \\
-		\hline
-		hadoop & 1.0.0 & Apache-2 (1,935), \newline spxdBSD/Apache-2 (8) \newline None (33), Unknown (14) \\
-		\hline
-		hibernate & 4.2.2 & Apache-2 (20), \newline LGPLv2.1+ (31) \newline PublicDomain (1), \newline None (1,850), SeeFile (4), \newline Unknown (4,324) \\
-		\hline
-		jasperreports & 3.7.4 & LGPLv2.1+ (3), \newline LGPLv3+ (1,581), \newline None (1), Unknown (4)\\
-		\hline
-		jfreechart & 1.0.13 & LGPLv2.1+ (989) \\
-		\hline
-		jgraph & 5.13.0.0 & LGPLv2.1+ (4), \newline spdxBSD (2), Unknown (151), \newline None (24), SeeFile (9) \\
-		\hline
-		%		jgrapht & 0.8.1 & LGPL 2.1 \& Eclipse  1.0 \\
-		jstock & 1.0.7c & LGPLv2.1+ (1), \newline GPLv2+ (239), \newline Apache-2 (1), BSD3 (1), \newline None (23), SeeFile (1), \newline spdxMIT (3), Unknown (5)\\
-		\hline
-		jung2 & 2-0-1 & N/A \\
-		\hline
-		junit & 4.11 & None (160), Unknown (4)  \\
-		\hline
-		poi & 3.6 & Apache-2 (2,002), None (5) \\
-		\hline
-		spring & 3.0.5 & Apache-2 (2,982) \\
-		\hline
-		struts2 & 2.2.1-all & Apache-2 (1,717), \newline spdxBSD3 (6), \newline None (118), SeeFile (1), \newline Unknown (2) \\
-		\hline
-		tomcat & 7.0.2 & Apache-2 (1,313), None (11) \\
-		%		weka & 3-7-9 & \\
+	\begin{tabular}{l|l|r|r|r}
+		\hline 
+		Project & License & QS & UD & Total \\
+		\hline
+		netbeans &  CDDLorGPLv2 &  & 57 & 57 \\
+		&  N/A &  & 8 & 8 \\
+		&  spdxBSD3 &  & 6 & 6 \\
+		&  MPLv1.1 &  & 1 & 1 \\
+		&  unknown &  & 1 & 1 \\
+		\hline
+		jung2 &  BSD3 & 2 & 27 & 29 \\
+		\hline
+		eclipse-SDK & EPLv1 & 6 & 11 & 17 \\
+		& CDDLorGPLv2 & 1 & 1 & 2 \\
+		&  Apache-2 &  & 1 & 1 \\
+		& N/A & 1 &  & 1 \\
+		& unknown &  & 1 & 1 \\
+		\hline
+		hibernate & LesserGPLv2.1+ & 18 & 4 & 22 \\
+		\hline
+		spring & Apache-2 & 18 & 2 & 20 \\
+		\hline
+		vuze & GPLv2 &  & 11 & 11 \\
+		\hline
+		jstock & GPLv2+ &  & 9 & 9 \\
+		& unknown &  & 1 & 1 \\
+		\hline
+		tomcat & Apache-2 & 5 & 5 & 10 \\
+		\hline
+		hadoop & Apache-2 & 8 &  & 8 \\
+		& N/A & 1 &  & 1 \\
+		\hline
+		jfreechart & LesserGPLv2.1+ & 3 & 5 & 8 \\
 		\hline
@@
 	\centering
-	\caption{Licenses of 523 clone pairs in category A, B, and C}
+	\caption{License matching of online clones (file-level) in QS, UD, and EX}
 	\label{tab:license_abc}
@@
 	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{p{1.5cm}|l|p{2.2cm}|r|r|r}
-		\hline
-		Type                                           & SO          & Qualitas          	& A & B & C \\
-		\hline
-		No license \newline (\textit{NL})  & None        & None           &  18 & 62 & 5 \\
+	\begin{tabular}{p{2cm}|l|p{2.2cm}|r|r|r}
+		\hline
+		Type & Stack Overflow & Qualitas & QS & UD & EX \\
+		\hline
+		No license (\textit{NL})  & None & None &  5 & 22 & 4 \\
 		\hline
 		Compatible & Apache2 & Apache2 &  0 & 1 & 0 \\
-		License	   						             & EPLv1       & EPLv1                 &  14 &  6 & 0 \\
-		(\textit{CL})													& None        & CC BY 3.0   &  0 & 12 & 0 \\
-		\hline
-	    Incompat. 								   & None       & Apache2  						& 41 & 29 & 3 \\
-		License								         & None        & BSD/BSD3                      & 0 & 64 & 0 \\
-		(\textit{IL}) 								 & None        & CDDLorGPLv2                & 0 & 63 & 4 \\
-															& None        & EPLv1                               & 0 & 33 & 0\\
-															& None        & GPLv2/2+/3+                  &  5 & 52 & 14 \\
-															& None        & LGPL2.1+/3+                   &  18 & 33 & 2 \\
-															& None        & AGPLv3/3+                     & 0 & 9 &1  \\
-															& None        & MPLv1\_1                         & 0 & 1 & 0\\
-															& None        & spdxBSD3                      & 0 & 8 & 1 \\
-															& None        & Unidentifiable                 & 0 & 1 & 0 \\
-															& Proprietary & None                            & 0 & 21 & 1 \\
-															& BSD3        & GPLv2+							& 0 & 1 & 0 \\
-		\hline
-		\multicolumn{3}{l|}{Total} 	       																&  96 & 396 & 31 \\
+		License	& EPLv1 & EPLv1 &  1 & 1 & 0 \\
+		(\textit{CL}) & N/A & CC BY 3.0   &  0 & 0 & 5 \\
+		\hline
+	    Incompat. & BSD3 & GPLv2+ & 0 & 1 & 0 \\
+		License	& N/A & AGPLv3/3+ & 1 & 2 & 0 \\
+		(\textit{IL}) & N/A & Apache-2 & 41 & 23 & 5 \\
+		& N/A & BSD3 & 3 & 28 & 4 \\
+		& N/A & CDDL or GPLv2 & 1 & 58 & 0 \\
+		& N/A & CDDLv1 & 0 & 0 & 1 \\
+		& N/A & EPLv1 & 7 & 10 & 0 \\
+		& N/A & GPLv2/2+/3+ & 2 & 32 & 62 \\
+		& N/A & LGPLv2/2.1+/3+ & 24 & 32 & 0 \\
+		& N/A & MPLv1.1 & 0 & 1 & 0 \\
+		& N/A & spdxBSD3 & 0 & 10 & 0 \\
+		& N/A & SPLv1 & 0 & 0 & 1 \\
+		& N/A & unknown & 0 & 3 & 3 \\
+		& spdxBSD3 & AGPLv3+ & 0 & 2 & 0 \\
+		& unknown & MIT-like & 0 & 0 & 1 \\
+		& unknown & Sun & 0 & 0 & 1 \\
+		\hline
+		\multicolumn{3}{l|}{Total} &  85 & 226 & 87 \\
 		\hline
@@
 \begin{figure*}
-	\minipage{0.32\textwidth}
+		\centering
+		\begin{minipage}{.4\textwidth}
+			\centering
 			\includegraphics[width=\linewidth]{heatmap_a}
 			\caption*{(1) QS clones}\label{fig:heatmap_a}
-	\endminipage\hspace{0.3cm}
-	\minipage{0.32\textwidth}
-	\includegraphics[width=\linewidth]{heatmap_b}
-	\caption*{(2) UD clones}\label{fig:heatmap_b}
-	\endminipage\hfill
-	\minipage{0.32\textwidth}%
+		\end{minipage}%
+		\hspace{5ex}
+		\begin{minipage}{0.4\textwidth}
+			\centering
 			\includegraphics[width=\linewidth]{heatmap_c}
-	\caption*{(3) EX clones}\label{fig:heatmap_c}
-	\endminipage
-	\caption{Licensing between Stack Overflow code snippets and Qualitas Java file of QS, UD, and EX online clone files}
+			\caption*{(2) EX clones}\label{fig:heatmap_c}
+		\end{minipage}
+	\caption{License mapping of QS and EX online clones}
 \end{figure*}
@@
 In our study, we reveal another possible situation of software licensing issues caused by code cloning ``to Stack Overflow''.
-We found with evidence that 110 pieces of code had been copied from 19 Qualitas projects to Stack Overflow as examples.
+We found with evidence that 112 pieces of code had been copied from 19 Qualitas projects to Stack Overflow as examples.
 They are also marked as accepted answers which increased their chances of being reused.
-The 19 open source projects came with their respective software licenses (shown in \Cref{t:q_projects_license}).
+The projects came with their respective software licenses (shown in \Cref{t:q_projects_license}).
 However, we found that the licensing information were mostly stripped from these clones after they were posted on Stack Overflow.

### 2017-02-12 cloneoverflow-latex/cloneoverflow.tex
Updated the license part.

@@
 
-\title{Are We Reusing Outdated and License-Violating Code Snippets from Stack Overflow?}
+\title{Are We Reusing Outdated and License-Violating Code from Stack Overflow?}
 
@@
 \maketitle
+
 \begin{abstract}
@@
 		\hline
-		\multicolumn{7}{l}{\scriptsize{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,}} \\
-		\multicolumn{7}{l}{\scriptsize{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.}} \\
+		\multicolumn{7}{l}{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,} \\
+		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
 	\end{tabular} %
@@
 
-To check if our online code clones are outdated, we focused on the 110 QS clone pairs that were cloned from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}) and compared them with their latest versions.
+To check if our online code clones are outdated, we focused on the 112 QS clone pairs that were cloned from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}) and compared them with their latest versions.
 We cloned the latest version of the Qualitas projects from their repositories on 26 September 2016.
@@
 \Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow.
-We discovered 59 outdated online clone pairs out of 110 pairs.
+We discovered 64 outdated online clone pairs out of 112 pairs.
 {\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}.
@@
 For example, the code snippet in Stack Overflow post 23520731, a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
-We also found 3 ``dead'' snippets.
+In the 64 outdate pairs, we found 5 of them to be ``dead'' snippets.
 These snippets did not have their originals in the latest version of the projects anymore.
@@
 	\centering
-	\caption{62 QS outdated online clone pairs.
-Outdated clones are caused (\textit{C}) by modified/added/deleted statements (\textit{sm}), file deletion (\textit{fd}), and method rewriting (\textit{rw}).}
+	\caption{62 QS outdated online clone pairs. Outdated clones are caused by modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}).}
 	\label{tab:stale_code_details}
@@
 	\resizebox{2\columnwidth}{!}{%
-	\begin{tabular}{r|l|c|l|c|p{5.8cm}|r|r|c|c|c}
-		\hline 
-		No. & SO Post & SO Date & Q project & Ver. & File & Start & End & Q Date & \textit{C} & $C$ Date \\
-		\hline
-			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
-			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{sm} & 8-Sep-15 \\
-			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
-			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{sm} & 17-Mar-15 \\
-			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{sm} & 1-Mar-11 \\
-			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{sm} & 5-Jun-13 \\
-			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{sm} & 21-Jun-13 \\
-			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{sm} & 20-Nov-14 \\
-			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{sm} & 4-Feb-13 \\
-			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
-			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{sm} & 12-Jun-11 \\
-			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{sm} & 25-Jun-12 \\
-			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
-			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{rw} & 25-Jul-11 \\
-			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{sm} & 26-Apr-13 \\
-			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{sm} & 23-Apr-13 \\
-			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{sm} & 5-Feb-16 \\
-			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{fd} & 11-Mar-11 \\
-			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{sm} & 11-May-16 \\
-			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{sm} & 12-Apr-15 \\
-			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{sm} & 4-Jun-15 \\ 
-			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{sm} & 17-Apr-08 \\
-			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{fd} & 20-May-11 \\
-			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{sm} & 16-Jan-16 \\
-			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{sm} & 29-Jun-07 \\
-			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{sm} & 2-Jun-08 \\
-			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{sm} & 22-Nov-13 \\
-			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{rw} & 13-Apr-14 \\
-			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{sm} & 13-Apr-10 \\
-			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{sm} & 29-Nov-15 \\
-			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{sm} & 12-May-15 \\
-			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{sm} & 25-Jun-16 \\
-			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{sm} & 25-May-14 \\
-			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{rw} & 26-Jun-13 \\
-			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{sm} & 28-Oct-14 \\
-			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{sm} & 21-Nov-13 \\
-			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
-			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{sm} & 6-Oct-14 \\
-			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{rw} & 12-Aug-16 \\
-			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{sm} & 21-May-12 \\
-			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{sm} & 19-Mar-13 \\
-			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{sm} & 9-May-15 \\
-			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{sm} & 28-Aug-12 \\
-			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 18-Dec-08 \\
-			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
-			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{sm} & 15-Jul-16 \\
-			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerExceptionResolver.java & 224 & 233 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
-			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{sm} & 8-Aug-11 \\
-			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{fd} & 20-Jan-12 \\
-			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{fd} & 15-Aug-10 \\
-			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{sm} & 18-Oct-13 \\
-			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{sm} & 28-Oct-13 \\
-			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{sm} & 15-Jun-15 \\
-			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
-			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{rw} & 4-Aug-16 \\
-			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{sm} & 25-Sep-14 \\
-			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{sm} & 12-Sep-12 \\
+	\begin{tabular}{r|l|l|l|l|p{5.2cm}|r|r|l|c|l}
+		\hline 
+		\multirow{2}{*}{No.} & \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ \cline{2-11}
+		& Post & Date & Project & Ver. & File & Start & End & Date & Type & Date \\
+		\hline
+			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
+			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
+			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
+			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
+			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{S} & 1-Mar-11 \\
+			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{S} & 5-Jun-13 \\
+			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{S} & 21-Jun-13 \\
+			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
+			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{S} & 4-Feb-13 \\
+			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
+			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
+			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{S} & 25-Jun-12 \\
+			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
+			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
+			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{S} & 26-Apr-13 \\
+			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{S} & 23-Apr-13 \\
+			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
+			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{D} & 11-Mar-11 \\
+			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{S} & 11-May-16 \\
+			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{S} & 12-Apr-15 \\
+			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{S} & 4-Jun-15 \\ 
+			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{S} & 17-Apr-08 \\
+			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
+			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{S} & 16-Jan-16 \\
+			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{S} & 29-Jun-07 \\
+			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{S} & 2-Jun-08 \\
+			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{S} & 22-Nov-13 \\
+			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{R} & 13-Apr-14 \\
+			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{S} & 13-Apr-10 \\
+			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{S} & 29-Nov-15 \\
+			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{S} & 12-May-15 \\
+			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{S} & 25-Jun-16 \\
+			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{S} & 25-May-14 \\
+			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
+			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{S} & 28-Oct-14 \\
+			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{S} & 21-Nov-13 \\
+			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
+			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
+			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{R} & 12-Aug-16 \\
+			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{S} & 21-May-12 \\
+			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{S} & 19-Mar-13 \\
+			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{S} & 9-May-15 \\
+			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{S} & 28-Aug-12 \\
+			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 18-Dec-08 \\
+			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
+			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
+			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerException\newline Resolver.java & 224 & 233 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
+			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{S} & 8-Aug-11 \\
+			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
+			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{S} & 15-Aug-10 \\
+			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{S} & 18-Oct-13 \\
+			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{S} & 28-Oct-13 \\
+			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{S} & 15-Jun-15 \\
+			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
+			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
+			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{S} & 25-Sep-14 \\
+			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{S} & 12-Sep-12 \\
 			\hline
@@
 	\small
-	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{p{2cm}|l|p{2.2cm}|r|r|r}
+%	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|l|l|r|r|r}
 		\hline
@@
 		\hline
-		No license (\textit{NL})  & None & None &  5 & 22 & 4 \\
+		No license & None & None &  5 & 22 & 4 \\
+		(\textit{NL}) & & & & & \\
 		\hline
@@
 	\end{tabular} %
-}
+%}
 \end{table}
 
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{license_violation}
+	\caption{Summary of license matching in online code clones}
+	\label{fig:license_violation}
+\end{figure}
+
 \begin{figure*}
@@
 			\centering
-			\includegraphics[width=\linewidth]{heatmap_a}
+			\includegraphics[width=\linewidth]{heatmap_a-crop}
 			\caption*{(1) QS clones}\label{fig:heatmap_a}
@@
 		\hspace{5ex}
-		\begin{minipage}{0.4\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{heatmap_c}
+		\begin{minipage}{0.41\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{heatmap_c-crop}
 			\caption*{(2) EX clones}\label{fig:heatmap_c}
 		\end{minipage}
-	\caption{License mapping of QS and EX online clones}
+	\caption{Matrix of online code clone license mapping}
 \end{figure*}

### 2017-02-12 cloneoverflow-latex/license_violations.m

@@ -1,0 +1,24 @@
+y = [5 1 79; 22 2 202; 4 5 78;];
+bar(y,'stacked')
+
+P=findobj(gca,'type','patch');
+C=['w','k','m','g']; % make a colors list 
+for n=1:length(P) 
+set(P(n),'facecolor',C(n));
+end
+
+xticks([1 2 3])
+xticklabels({'QS', 'UD', 'EX'})
+%xlabel('Project','FontSize',15)
+ylabel('No. of file','FontSize',15)
+t_legend=legend('No license', 'Compatible license', 'Incompatible license');
+set(t_legend,'FontSize',15);
+set(gca,'FontSize',15);
+%set(gca,'XTickLabelRotation',45)
+box on
+
+h=gcf;
+set(h,'PaperPositionMode','auto');         
+set(h,'PaperOrientation','landscape');
+set(h,'Position',[50 50 800 500]);
+print('license_violation','-dpdf','-bestfit')

### 2017-02-12 cloneoverflow-latex/cloneoverflow.tex
A large update containing several changes (only abstract and conclusion is missing now).

@@
 
-\title{Are We Reusing Outdated and License-Violating Code from Stack Overflow?}
+\title{Are We Reusing Outdated and Licensed Code from Stack Overflow?}
 
@@
 It allows programmers to ask questions and give answers to programming problems.
-The website has found to be useful for software development \cite{Ponzanelli2013,Ponzanelli2014,Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for educational purposes \cite{Nasehi2012}.
+The website has found to be useful for software development~\cite{Ponzanelli2013,Ponzanelli2014,Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for educational purposes~\cite{Nasehi2012}.
 On Stack Overflow, each conversation contains a question and answer(s).
@@
 Code cloning is an activity of reusing source code by copying and pasting.
-It normally occurs in software development and account from 7\% to 23\% in typical software systems \cite{Bellon2007}.
+It normally occurs in software development and account from 7\% to 23\% in typical software systems~\cite{Bellon2007}.
 The benefits and drawbacks of clones are still controversial.
-Several authors state that clones lead to bug propagations and software maintenance issues \cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial \cite{Saini2016,Kapser2006}.
+Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial~\cite{Saini2016,Kapser2006}.
 
 Code cloning can also have side effects of violating software licenses and software vulnerabilities.
-Carelessly cloning code from one project to another project with different license may cause software licensing violation \cite{German2009}.
+Carelessly cloning code from one project to another project with different license may cause software licensing violation~\cite{German2009}.
 This also happens within the context of online Q\&A website such as Stack Overflow.
@@
 Security is also among the main concerns when code is copied from online source.
-Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, gives less secure code than books and the official Android documentation \cite{Acar2016}.
+Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, gives less secure code than books and the official Android documentation~\cite{Acar2016}.
 Additionally, outdated and vulnerable third-party libraries from famous open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
@@
 We prepared Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection.
-Then, we deployed two clone detection tools, Simian \cite{simian} and NiCad \cite{Roy2008,Cordy}, to locate clones between the two datasets.
+Then, we deployed two clone detection tools, Simian~\cite{simian} and NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets.
 Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times.
@@
 If a clone pair was similarly reported by multiple tools, we had a higher confidence that it was a real clone pair.
-To achieve this, clone pairs from the two clone detectors were pair-wise matched to find agreements using Bellon's clone overlapping criteria \cite{Bellon2007}.
+To achieve this, clone pairs from the two clone detectors were pair-wise matched to find agreements using Bellon's clone overlapping criteria~\cite{Bellon2007}.
 This step generated \textbf{agreed clone pairs}.
@@
 First, we were only interested in code snippets with at least six lines.
-Snippets which were smaller than six lines were usually spurious clones \cite{Bellon2007}.
+Snippets which were smaller than six lines were usually spurious clones~\cite{Bellon2007}.
 Second, we only focused on code snippets in accepted answers.
@@
 
-\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas} \cite{QualitasCorpus} for this study.
-It is a curated Java corpus that has been used in several software engineering studies \cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
-The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation \cite{QualitasCorpus}.
+\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study.
+It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
+The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation~\cite{QualitasCorpus}.
 We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects.
@@
 The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow.
-Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation \cite{QualitasCorpus} so it is removed from the study.
+Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study.
 This resulted in total of 111 projects analysed in the study.
@@
 Third, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
-We have tried running 5 state-of-the-art clone detectors including Simian \cite{simian}, NiCad \cite{Cordy,Roy2008}, CCFinder \cite{Kamiya2002}, iClones \cite{Gode2009}, and DECKARD \cite{Jiang2007a} against Stack Overflow and Qualitas datasets.
+We have tried running 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets.
 CCFinder, iClones, and DECKARD failed to report clones between 144,075 Stack Overflow code snippets and 111 Qualitas projects.
@@
 
-\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies \cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}.
+\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}.
 It is a command-line tool which enables us to automate the detection.
@@
 \textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity.
-It can detect clones of type-1, 2 up to type-3 (clones with added/removed/relocated/changed statements) and is also used in several empirical clone studies \cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
-It utilises TXL \cite{Cordy2006} for parsing and pretty-printing source code.
+It can detect clones of type-1, 2 up to type-3 (clones with added/removed/relocated/changed statements) and is also used in several empirical clone studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
+It utilises TXL~\cite{Cordy2006} for parsing and pretty-printing source code.
 It also provide code normalisation by variable renaming and abstraction.
@@
 However, due to a very high number of false positives, they may end up looking at most of the false clones.
-Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies \cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish.
-Clone pairs agreed by multiple clone detection tools have higher confident to be real clones \cite{cr2016ssbse}.
+Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish.
+Clone pairs agreed by multiple clone detection tools have higher confident to be real clones~\cite{cr2016ssbse}.
 By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
@@
 \subsection{Clone Detector's Parameter Tuning}
-We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies \cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
+We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies~\cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
 However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we were hindered from searching for the best configurations of the tools.
@@
 In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,635,844 and 251,449,849 respectively.
-This is expected since EvaClone configurations prefer recall so it tends to remote more clones \cite{Wang2013}.
+This is expected since EvaClone configurations prefer recall so it tends to remote more clones~\cite{Wang2013}.
 The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79.
@@
 Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.
-Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs \cite{Bellon2007}.
+Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.
 %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
@@
 We hence apply four filters: \textbf{clone size, regular expression, similarity threshold, and good/ok pairs}.
-For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones \cite{Saini2016}.
-Moreover, Gabel and Su show that unique code tend to be larger than seven lines \cite{Gabel2010}.
+For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones~\cite{Saini2016}.
+Moreover, Gabel and Su show that unique code tend to be larger than seven lines~\cite{Gabel2010}.
 The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clones only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods and some of the obvious getters and setters using regular expressions and removes them.
@@
 %\end{table}
-This findings complement a study of inter clones between software projects \cite{Svajlenko2014}.
+This findings complement a study of inter clones between software projects~\cite{Svajlenko2014}.
 We show that, besides software projects, clones can also be copied over different websites on the Internet.
@@
 			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
-			\multirow{1}{*}{\textit{ok}}  & 14 & 0 & 40 & 21 & 11,547 & 22 & 105 & 11,749 \\
-			\multirow{1}{*}{$S_D$} & 86 & 0 & 294 & 145 & 17,074 & 74 & 128 & 17,801 \\
+			\multirow{1}{*}{\textit{ok}}  & 14 & 0 & 20 & 41 & 11,547 & 22 & 105 & 11,749 \\
+			\multirow{1}{*}{$S_D$} & 86 & 0 & 293 & 146 & 17,074 & 74 & 128 & 17,801 \\
 			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
 			\hline
-			Total & 112 & 0 & 380 & 176 & 28,749 & 111 & 2,418 & 31,946 \\ 
+			Total & 112 & 0 & 359 & 197 & 28,749 & 111 & 2,418 & 31,946 \\ 
 			\hline
@@
 To the best of our knowledge, this work is the first to discuss a problem of outdated code on Stack Overflow.
-Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated \cite{Xia2014}.
-Usually code clone detection is used to locate clone instances and update them to match with the original code \cite{Bellon2007}.
+Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated~\cite{Xia2014}.
+Usually code clone detection is used to locate clone instances and update them to match with the original code~\cite{Bellon2007}.
 However, for online code clones, the clones are pervasive and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts.
@@
 \subsection{RQ4: Software Licensing Violation}
-Software licensing plays an important role in software development. Violation of software licenses impacts software delivery and also leads to legal issues \cite{Sprigman2015}. 
+Software licensing plays an important role in software development. Violation of software licenses impacts software delivery and also leads to legal issues~\cite{Sprigman2015}. 
 %It is an emerging area that software engineering research community is paying attention to. For example, 
@@
 A study by An et al.~\cite{An2017} found 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code.
-%there are studies of automatic technique to identify software licensing from source code files \cite{German2010}
+%there are studies of automatic technique to identify software licensing from source code files~\cite{German2010}
 
@@
 		\hline
-		netbeans &  CDDLorGPLv2 &  & 57 & 57 \\
-		&  N/A &  & 8 & 8 \\
+		netbeans &  CDDL/GPLv2 &  & 57 & 57 \\
+		&  No license &  & 8 & 8 \\
 		&  spdxBSD3 &  & 6 & 6 \\
 		&  MPLv1.1 &  & 1 & 1 \\
-		&  unknown &  & 1 & 1 \\
+		&  Unknown &  & 1 & 1 \\
 		\hline
@@
 		eclipse-SDK & EPLv1 & 6 & 11 & 17 \\
-		& CDDLorGPLv2 & 1 & 1 & 2 \\
+		& CDDL/GPLv2 & 1 & 1 & 2 \\
 		&  Apache-2 &  & 1 & 1 \\
-		& N/A & 1 &  & 1 \\
-		& unknown &  & 1 & 1 \\
+		& No license & 1 &  & 1 \\
+		& Unknown &  & 1 & 1 \\
 		\hline
@@
 		jstock & GPLv2+ &  & 9 & 9 \\
-		& unknown &  & 1 & 1 \\
+		& Unknown &  & 1 & 1 \\
 		\hline
@@
 		hadoop & Apache-2 & 8 &  & 8 \\
-		& N/A & 1 &  & 1 \\
+		& No license & 1 &  & 1 \\
 		\hline
@@
 		\hline
-		No license & None & None &  5 & 22 & 4 \\
-		(\textit{NL}) & & & & & \\
+		No license & No license & No license &  5 & 21 & 4 \\
 		\hline
@@
 		License	& EPLv1 & EPLv1 &  1 & 1 & 0 \\
-		(\textit{CL}) & N/A & CC BY 3.0   &  0 & 0 & 5 \\
+		& Sun (proprietary) & Sun (proprietary) & 0 & 0 & 1 \\
+		& MIT-like & MIT-like & 0 & 0 & 1 \\
+		& No license & CC-NC-SA &  0 & 0 & 5 \\
+		\hline
+		\multicolumn{3}{l|}{Total} &  6 & 23 & 11 \\
+		\hline
 		\hline
 	    Incompat. & BSD3 & GPLv2+ & 0 & 1 & 0 \\
-		License	& N/A & AGPLv3/3+ & 1 & 2 & 0 \\
-		(\textit{IL}) & N/A & Apache-2 & 41 & 23 & 5 \\
-		& N/A & BSD3 & 3 & 28 & 4 \\
-		& N/A & CDDL or GPLv2 & 1 & 58 & 0 \\
-		& N/A & CDDLv1 & 0 & 0 & 1 \\
-		& N/A & EPLv1 & 7 & 10 & 0 \\
-		& N/A & GPLv2/2+/3+ & 2 & 32 & 62 \\
-		& N/A & LGPLv2/2.1+/3+ & 24 & 32 & 0 \\
-		& N/A & MPLv1.1 & 0 & 1 & 0 \\
-		& N/A & spdxBSD3 & 0 & 10 & 0 \\
-		& N/A & SPLv1 & 0 & 0 & 1 \\
-		& N/A & unknown & 0 & 3 & 3 \\
+		License	& No license & AGPLv3/3+ & 1 & 2 & 0 \\
+		& No license & Apache-2 & 41 & 23 & 5 \\
+		& No license & BSD3 & 3 & 28 & 4 \\
+		& No license & CDDL or GPLv2 & 1 & 58 & 0 \\
+		& No license & CDDLv1 & 0 & 0 & 1 \\
+		& No license & EPLv1 & 7 & 10 & 0 \\
+		& No license & GPLv2/2+/3+ & 2 & 32 & 62 \\
+		& No license & LGPLv2/2.1+/3+ & 24 & 32 & 0 \\
+		& No license & MPLv1.1 & 0 & 1 & 0 \\
+		& No license & spdxBSD3 & 0 & 10 & 0 \\
+		& No license & SPLv1 & 0 & 0 & 1 \\
+		& No license & Unknown & 0 & 3 & 3 \\
 		& spdxBSD3 & AGPLv3+ & 0 & 2 & 0 \\
-		& unknown & MIT-like & 0 & 0 & 1 \\
-		& unknown & Sun & 0 & 0 & 1 \\
-		\hline
-		\multicolumn{3}{l|}{Total} &  85 & 226 & 87 \\
+		\hline
+		\multicolumn{3}{l|}{Total} &  79 & 202 & 76 \\
 		\hline
@@
 	\includegraphics[width=\linewidth]{license_violation}
-	\caption{Summary of license matching in online code clones}
+	\caption{Summary of licensing conflicts in online code clones}
 	\label{fig:license_violation}
@@
 			\centering
-			\includegraphics[width=\linewidth]{heatmap_a-crop}
-			\caption*{(1) QS clones}\label{fig:heatmap_a}
+			\includegraphics[width=\linewidth]{sankey_license_qs}
+			\caption*{(A) QS clones}
 		\end{minipage}%
 		\hspace{5ex}
-		\begin{minipage}{0.41\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{heatmap_c-crop}
-			\caption*{(2) EX clones}\label{fig:heatmap_c}
+		\begin{minipage}{0.4\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{sankey_license_ex}
+			\caption*{(B) EX clones}
 		\end{minipage}
-	\caption{Matrix of online code clone license mapping}
+	\caption{Direction of changes in online code clone license}
+	\label{fig:sankey_license}
 \end{figure*}
@@
 In our study, we reveal another possible situation of software licensing issues caused by code cloning ``to Stack Overflow''.
-We found with evidence that 112 pieces of code had been copied from 19 Qualitas projects to Stack Overflow as examples.
+We found with evidence that 112 pieces of code had been copied from Qualitas projects to Stack Overflow as examples.
 They are also marked as accepted answers which increased their chances of being reused.
@@
 The summary of licensing information is listed in \Cref{tab:license_abc}.
-The licenses were extracted by \textbf{Ninka}, an automatic license identification tool \cite{German2010}.
+The licenses were extracted by \textbf{Ninka}, an automatic license identification tool~\cite{German2010}.
 Since Ninka worked at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of clone pairs (duplicates were ignored).
-For the ones that could not be automatically identified by Ninka and had been reported as {\small\texttt{SeeFile}} and {\small\texttt{Unknown}}, we looked at them manually.
+For the ones that could not be automatically identified by Ninka and had been reported as {\small\texttt{SeeFile}} and {\small\texttt{Unknown}}, we looked at them manually and updated if any license was found.
 The table shows license of Stack Overflow snippets and Qualitas source code.
@@
 
-\textbf{None or compatible license:} There are 85 \textit{NL} clone pairs which both clones do not have license (None vs.~None) and 13 pairs which have compatible licenses, i.e.~\textit{CL}, such as Apache2 vs.~Apache2; EPLv1 vs.~EPLv1; None vs.~CC BY 3.0.
+\textbf{No license or compatible license:} There are 31 clone pairs which do not have license on both sides and 8 pairs which have compatible licenses such as Apache license v.2; Eclipse Public License v.1 (EPLv1); No license vs.~Creative Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC BY-NC-SA 3.0).
 They are safe for being reused.
-Since source code and text on Stack Overflow posted before 1st March 2016 are protected by CC BY 3.0 (and MIT license from 1st March 2016 onwards), we can treat Stack Overflow code snippets without licensing information as having CC BY 3.0 by default.
-CC BY 3.0 license is relaxed and it only request attribution when reuse.
-
-\textbf{Incompatible license:} there are a large number of clone pairs in type \textit{IL} which do not contain licensing information after they are posted on Stack Overflow or having different license that its Qualitas clone counterpart.
-96 category-A clones are the pairs that we have evidence of being copied from Qualitas to Stack Overflow.
-64 of them do not contain licensing terms after posted and are controversial for being reused.
-396 clone pairs in category B are highly similar clones that we do not have evidence of copying.
-315 of them have incompatible licenses.
-Interestingly, there are 21 clone pairs that Stack Overflow snippets contain Sun and MIT-like license while Qualitas clones do not have any license information.
-There is also one clone pair having BSD3 license on Stack Overflow while having GPLv2+ in Qualitas source code.
-Lastly, 26 out of 31 clone pairs in category C have incompatible license.
-They are clones that have been identified to be copied from an external source.
+Since source code and text on Stack Overflow posted before 1st March 2016 are protected by CC BY-NC-SA 3.0 (and MIT license from 1st March 2016 onwards), we can treat Stack Overflow code snippets without licensing information as having CC BY-NC-SA 3.0 by default.
+CC BY-NC-SA 3.0 license is relaxed and it only request attribution when reuse.
+
+\textbf{Incompatible license:} there are 359 clone pairs which do not contain licensing information after they are posted on Stack Overflow or having different license from their Qualitas clone counterparts.
+More than half (79) of QS clone pairs have their licensing terms removed or changed after posted on Stack Overflow.
+Of 226 UD clone pairs, 202 pairs have incompatible licenses.
 Again, most of the clones in Qualitas contain license while the Stack Overflow snippets do not.
-
-\textbf{For RQ4, we observed xx code snippets on Stack Overflow that violate the license of their original software.
-Most of them do not contain licensing statements after copied to Stack Overflow.
-\FIXME{More}}
+For EX clone pairs, we searched for licensing terms of the original source code from the external sources.
+We found that 76 out of 87 EX clone pairs have incompatible license.
+%They are clones that have been identified to be copied from an external source.
+Similarly, their license were removed from Stack Overflow snippets.
+
+\Cref{fig:sankey_license} shows the direction of changes in online code clone license.
+The direction of the change is from left to right.
+The thickness of the line reflects the number of clones for that relationship.
+In \Cref{fig:sankey_license} (A), we can clearly see that most of the QS online clones have their licenses changed from having a license to ``No license'' on Stack Overflow.
+The same findings were found for EX online clones as depicted in \Cref{fig:sankey_license} (B).
+We found that most of the EX clones have their licensing information stripped of after copying to Stack Overflow.
+These clones are instead covered the default CC BY-NC-SA 3.0 license of Stack Overflow which is strongly permissive.
+These used-to-be-licensed code are dangerous for being reused because they can implicitly conflicting with the reusing software's license.
+
+\textbf{For RQ4, we found 359 code snippets on Stack Overflow that violate the license of their original software. Majority of them do not contain licensing statements after copied to Stack Overflow.}
 
 \section{Threats to Validity}
+
+\textbf{Internal validity:} 
+We could not verify all the 315,786,118 clone pairs reported by the clone detection tools in this study.
+Nevertheless, we applied several mechanism to ensure the validity to the subset of clone pairs we classified.
+First, we used the two widely-used clone detection tools, Simian and NiCad. We had tried three other clone detectors but could not add them to the study
+due to their scalability issue and susceptibility to incomplete code snippets.
+Second, we adopted Bellon's clone agreement metric~\cite{Bellon2007} to prioritise and filters clone pairs 
+for the manual classification. The agreed clone pairs that passed \textit{good} and \textit{ok} criteria had a higher chance
+to be true positive. We also applied the Bellon's clone agreement to 4 different combinations of the tools' configurations.
+For disagreed clone pairs, we applied several filters to remove spurious and uninteresting clones.
+
+The number of online clones we found are subject to the clone detectors and their configurations. 
+We mitigated the problem of clone detector's parameter sensitivity by adding another configuration, besides the default one.
+We reused the established configurations from the EvaClone study~\cite{Wang2013}.
+We also performed pairwise matching between the default and EvaClone configurations of the two clone detection tools.
+
+Our seven patterns of online code cloning may not cover all possible online cloning patterns. However, instead of 
+defining the patterns beforehand, we resorted to extract them for the data sets. We derived them
+from a manual investigation of 679 online clone pairs and adopted one pattern from the study by Kapser et al.~\cite{Kapser2003}.
+
+The 3,632 clone pairs classified manually by the first author are subject to manual judgement and human errors. 
+Although we had tried our best to be careful on searching for evidence and classifying the clones, some errors
+may still exist. We mitigated this problem by having the second author to validate the classifications with random samplings.
+The 64 classification conflicts were discussed and resolved. 
+The third author made a final judgement when no consensus could be found by the two authors.
+ %In addition, we are aware of voting mechanism
+%in Stack Overflow and plan to incorporate highest-vote answers in the future work.
+
+\textbf{External validity:} We carefully chose the data sets for our
+experiment so the findings could be generalise as much as possible. 
+We selected Stack Overflow because it is one of the most popular programming Q\&A websites available with approximately 6.3 million users.
+There are a large number of code snippets reused from the site~\cite{An2017} and there are also several studies encouraging of doing so~(e.g.~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014}).
+Nonetheless, it may not be representative to all the programming Q\&A websites.
+
+Regarding the code snippets, we downloaded the full data dump and extracted Java accepted answers. 
+Instead of analysing every post, we only focused on posts marked as accepted answers 
+since they are the most likely to being reused. This yields totally 144,075 snippets.
+Our findings are limited to these restrictions. They may not be generalised to all programming languages and all
+answers on Stack Overflow.
+
+On the other hand, we chose the curated Qualitas corpus for Java open source projects containing 111 projects \cite{QualitasCorpus}.
+The projects span over several areas of software and has been used in several empirical studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
+Although it is a curated and well-established corpus,
+it may not fully represent all Java open source software available.
+
+Lastly, two clone detection tools, Simian and NiCad, are chosen for this study 
+due to certain limitations of a few other tools. We have not tried all the tools available 
+and they might not be complete representatives of all available clone detection tools.
 
@@
 The Stack Overflow data set has been put to use in several previous studies.
-In terms of developer-assisting tools, Seahawk is an Eclipse plug-in that searches and recommends relevant code snippets from Stack Overflow \cite{Ponzanelli2013}.
+In terms of developer-assisting tools, Seahawk is an Eclipse plug-in that searches and recommends relevant code snippets from Stack Overflow~\cite{Ponzanelli2013}.
 A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} achieves the same goal but with improved algorithms.
 The code snippets on Stack Overflow are mostly examples or solutions to programming problems.
-Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases \cite{Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
-Furthermore, Treude et al.~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation \cite{Treude2016}.
+Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
+Furthermore, Treude et al.~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation~\cite{Treude2016}.
 
 Another aspect is knowledge extraction from Stack Overflow.
-Nasehi et al.~studied what makes a good code example by analysing answers from Stack Overflow \cite{Nasehi2012}.
+Nasehi et al.~studied what makes a good code example by analysing answers from Stack Overflow~\cite{Nasehi2012}.
 Similarly, Yang et al.~\cite{Yang2016} analysed Stack Overflow snippets across various programming languages and observed that code snippets in Python and Javascript are the most usable.
 Wang et al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic modelling to analyse questions and answers from Stack Overflow so that they can automatically categorise new questions.
-There are also studies trying to understand developers' behaviours on Stack Overflow, e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}, while some studies aim to improve Stack Overflow itself \cite{Diamantopoulos2015, Wang2014}.
+There are also studies trying to understand developers' behaviours on Stack Overflow, e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}, while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.
 
 \textbf{Code clone detection} is a long-standing research topic in software engineering.
-Whether clones are good or bad for software is still controversial \cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
-However, by only knowing how many code clones residing in software and how they evolve \cite{Pate2013,Mondal2011} can provide several valuable insights into the software systems.
+Whether clones are good or bad for software is still controversial~\cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
+However, by only knowing how many code clones residing in software and how they evolve~\cite{Pate2013,Mondal2011} can provide several valuable insights into the software systems.
 Besides clones, clone detection has its several applications such as software plagiarism detection~\cite{Prechelt2002},
@@
 
-Two code fragments are clones if they are similar enough according to a given definition of similarity \cite{Bellon2007}.
-Given an open interpretation of ``definition of similarity'', there are various clone detection tools and their siblings, code plagiarism detectors, invented based on plethora of different code similarity measurements \cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}.
+Two code fragments are clones if they are similar enough according to a given definition of similarity~\cite{Bellon2007}.
+Given an open interpretation of ``definition of similarity'', there are various clone detection tools and their siblings, code plagiarism detectors, invented based on plethora of different code similarity measurements~\cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}.
 Some tools
-use string comparison techniques such as Simian \cite{simian}.
-NiCad \cite{Roy2008,Cordy} also exploits Longest Common Subsequence (LCS) string similarity measure to discover clones after applying code pretty-printing using TXL \cite{Cordy2006}.
+use string comparison techniques such as Simian~\cite{simian}.
+NiCad~\cite{Roy2008,Cordy} also exploits Longest Common Subsequence (LCS) string similarity measure to discover clones after applying code pretty-printing using TXL~\cite{Cordy2006}.
 Many tools do not work on original source code directly but transform them into an
@@
 Since clone detectors are different in their detection approaches, they may behave differently and report different clones even on the same data set.
-Some researchers exploit these different behaviours of clone detectors by finding their agreement and obtain highly-confident clones \cite{Bellon2007,Wang2013}.
-Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are highly potential to be true clones than the ones reported by only a single tool \cite{Wang2013,cr2016ssbse,Funaro2010}.
-These studies also report that sensitivities of the tools' parameter settings have strong effects to the results \cite{Wang2013,cr2016ssbse}.
+Some researchers exploit these different behaviours of clone detectors by finding their agreement and obtain highly-confident clones~\cite{Bellon2007,Wang2013}.
+Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are highly potential to be true clones than the ones reported by only a single tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
+These studies also report that sensitivities of the tools' parameter settings have strong effects to the results~\cite{Wang2013,cr2016ssbse}.
 
 \textbf{Software licensing} is crucial for open source and industrial software development.
-Di Penta et al.~study an evolution of software licensing in six FOSS and found that licensing statements change over time \cite{DiPenta2010}.
+Di Penta et al.~study an evolution of software licensing in six FOSS and found that licensing statements change over time~\cite{DiPenta2010}.
 German et al.~\cite{German2009} performed an empirical study of code siblings (code clones among different systems coming from the same source) and found that licensing conflicts can occur between the clone siblings.

### 2017-02-12 cloneoverflow-latex/license_violations.m

@@ -1,5 +1,6 @@
-y = [5 1 79; 22 2 202; 4 5 78;];
-bar(y,'stacked')
+y = [5 1 79; 4 7 76; 21 2 202; ];
+%bar(y,'stacked')
+bar(y)
 
 P=findobj(gca,'type','patch');
 C=['w','k','m','g']; % make a colors list 
@@ -8,10 +9,10 @@ set(P(n),'facecolor',C(n));
 end
 
 xticks([1 2 3])
-xticklabels({'QS', 'UD', 'EX'})
+xticklabels({'QS', 'EX', 'UD'})
 %xlabel('Project','FontSize',15)
-ylabel('No. of file','FontSize',15)
-t_legend=legend('No license', 'Compatible license', 'Incompatible license');
+ylabel('No. of clones','FontSize',15)
+t_legend=legend('No license', 'Compatible license', 'Incompatible license','Location','northwest');
 set(t_legend,'FontSize',15);
 set(gca,'FontSize',15);
 %set(gca,'XTickLabelRotation',45)
@@ -20,5 +21,5 @@ box on
 h=gcf;
 set(h,'PaperPositionMode','auto');         
 set(h,'PaperOrientation','landscape');
-set(h,'Position',[50 50 800 500]);
+set(h,'Position',[50 50 500 200]);
 print('license_violation','-dpdf','-bestfit')

### 2017-02-13 cloneoverflow-latex/cloneoverflow.tex
Updated according to Jens’s comments.

@@
-%\documentclass{sig-alternate-05-2015}
-\documentclass[sigconf,review, anonymous]{acmart}
-\acmConference[ESEC/FSE 2017]{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--8 September, 2017}{Paderborn, Germany}
-
+\documentclass[sigconf]{acmart}
+
+\usepackage{booktabs} % For formal tables
 \usepackage[utf8]{inputenc}
@@
 
-\begin{document}
-
 % Copyright
-\setcopyright{acmcopyright}
+%\setcopyright{none}
+%\setcopyright{acmcopyright}
 %\setcopyright{acmlicensed}
-%\setcopyright{rightsretained}
+\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
 
-%% DOI
-%\doi{10.475/123_4}
-
-%% ISBN
-%\isbn{123-4567-24-567/08/06}
+\setcopyright{rightsretained}
+%\setcopyright{usgov}
+%\setcopyright{usgovmixed}
+%\setcopyright{cagov}
+%\setcopyright{cagovmixed}
+
+% DOI
+\acmDOI{10.475/123_4}
+
+% ISBN
+\acmISBN{123-4567-24-567/08/06}
 
 %Conference
-%\conferenceinfo{ESEC/FSE 2017}{September 4--8, 2017, Paderborn, Germany}
-
-%\acmPrice{\$15.00}
-
-%
-% --- Author Metadata here ---
-%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
-% --- End of Author Metadata ---
-
+\acmConference[ESEC/FSE 2017]{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--8 September, 2017}{Paderborn, Germany}
+\acmYear{2017}
+\copyrightyear{2017}
+
+\acmPrice{15.00}
+
+\begin{document}
 	\title{Are We Reusing Outdated and Licensed Code from Stack Overflow?}
-
-%\numberofauthors{1}
-\author{
-	\alignauthor
-	$^1$Chaiyong Ragkhitwetsagul, $^1$Matheus Paixao, $^1$Jens Krinke, $^2$Giuseppe Bianco \\
-	\affaddr{$^1$University College London, London, UK}\\
-	\affaddr{$^2$Università degli Studi del Molise, Campobasso, Italy}
+	%\titlenote{Produces the permission block, and
+	%  copyright information}
+	%\subtitle{Extended Abstract}
+	%\subtitlenote{The full version of the author's guide is available as
+	%  \texttt{acmart.pdf} document}
+
+\author{Chaiyong Ragkhitwetsagul,~Matheus Paixao,~Jens Krinke}
+\affiliation{%
+	\institution{CREST, University College London}
+	%  \streetaddress{P.O. Box 1212}
+	\city{London, UK} 
+	%  \state{Ohio} 
+	%  \postcode{43017-6221}
 }
-
-\maketitle
+%\email{{ucabagk,matheus.paixao.14,j.krinke}@ucl.ac.uk}
+
+\author{Giuseppe Bianco,~Rocco Oliveto}
+\affiliation{%
+	\institution{Università degli Studi del Molise}
+	%  \streetaddress{P.O. Box 1212}
+	\city{Campobasso, Italy} 
+	%  \state{Ohio} 
+	%  \postcode{43017-6221}
+}
 
@@
 	somewhat loosely, to the formatting guidelines for
-ACM SIG Proceedings. It is an {\em alternate} style which produces
-a {\em tighter-looking} paper and was designed in response to
-concerns expressed, by authors, over page-budgets.
-It complements the document \textit{Author's (Alternate) Guide to
-Preparing ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}.
-This source file has been written with the intention of being
-compiled under \LaTeX$2_\epsilon$\ and BibTeX.
-
-The developers have tried to include every imaginable sort
-of ``bells and whistles", such as a subtitle, footnotes on
-title, subtitle and authors, as well as in the text, and
-every optional component (e.g. Acknowledgments, Additional
-Authors, Appendices), not to mention examples of
-equations, theorems, tables and figures.
-
-To make best use of this sample document, run it through \LaTeX\
-and BibTeX, and compare this source code with the printed
-output produced by the dvi file. A compiled PDF version
-is available on the web page to help you with the
-`look and feel'.
+	ACM SIG Proceedings\footnote{This is an abstract footnote}. 
 \end{abstract}
+
+%
+% The code below should be generated by the tool at
+% http://dl.acm.org/ccs.cfm
+% Please copy and paste the code instead of the example below. 
+%
+%\begin{CCSXML}
+%<ccs2012>
+% <concept>
+%  <concept_id>10010520.10010553.10010562</concept_id>
+%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
+%  <concept_significance>500</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010575.10010755</concept_id>
+%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
+%  <concept_significance>300</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10010520.10010553.10010554</concept_id>
+%  <concept_desc>Computer systems organization~Robotics</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+% <concept>
+%  <concept_id>10003033.10003083.10003095</concept_id>
+%  <concept_desc>Networks~Network reliability</concept_desc>
+%  <concept_significance>100</concept_significance>
+% </concept>
+%</ccs2012>  
+%\end{CCSXML}
+
+\begin{CCSXML}
+	<ccs2012>
+	<concept>
+	<concept_id>10011007.10011006.10011072</concept_id>
+	<concept_desc>Software and its engineering~Software libraries and repositories</concept_desc>
+	<concept_significance>500</concept_significance>
+	</concept>
+	<concept>
+	<concept_id>10011007.10011074.10011111.10011113</concept_id>
+	<concept_desc>Software and its engineering~Software evolution</concept_desc>
+	<concept_significance>300</concept_significance>
+	</concept>
+	</ccs2012>
+\end{CCSXML}
+
+\ccsdesc[500]{Software and its engineering~Software libraries and repositories}
+\ccsdesc[300]{Software and its engineering~Software evolution}
+
+% We no longer use \terms command
+%\terms{Theory}
+
+\keywords{clone detection, Stack Overflow, outdated code, software licensing}
+
+\maketitle
 
@@
 It allows programmers to ask questions and give answers to programming problems.
-The website has found to be useful for software development~\cite{Ponzanelli2013,Ponzanelli2014,Diamantopoulos2015,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for educational purposes~\cite{Nasehi2012}.
-On Stack Overflow, each conversation contains a question and answer(s).
+The website has found to be useful for software development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for educational purposes~\cite{Nasehi2012}.
+On Stack Overflow, each conversation contains a question and a list of answer(s).
 The answers frequently contain at least one code snippet as a solution to the question asked.
-The code snippet is usually not written directly on Stack Overflow website but copied from another location.
-It can be copied and modified from the problematic code snippet in the question, copied from an answerer's own code, or borrowed from other locations including open source software (OSS) systems.
+The code snippet is usually not written directly on the Stack Overflow website but copied from another location.
+It can be copied and modified from a code snippet in the question, copied from an answerer's own code or from other locations including open source software (OSS) systems.
 The process of posting and answering questions on Stack Overflow, which involves copying and pasting source code, can be considered as code cloning.
@@
 The benefits and drawbacks of clones are still controversial.
-Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others have proofs that in some cases clones are not harmful than normal code or even beneficial~\cite{Saini2016,Kapser2006}.
+Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others suggest that in some cases clones are not harmful or even beneficial~\cite{Saini2016,Kapser2006}.
 
 Code cloning can also have side effects of violating software licenses and software vulnerabilities.
-Carelessly cloning code from one project to another project with different license may cause software licensing violation~\cite{German2009}.
-This also happens within the context of online Q\&A website such as Stack Overflow.
-An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow have potential of violating software licenses.
+Carelessly cloning code from one project to another project with a different license may cause a software licensing violation~\cite{German2009}.
+This also happens within the context of online Q\&A websites such as Stack Overflow.
+An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow potentially violate software licenses.
 Security is also among the main concerns when code is copied from online source.
-Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, gives less secure code than books and the official Android documentation~\cite{Acar2016}.
-Additionally, outdated and vulnerable third-party libraries from famous open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
-
-% INTERESTING NEWS: http://www.theverge.com/tldr/2016/5/4/11593084/dont-get-busted-copying-code-from-stack-overflow
+Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, offers less secure code than books or the official Android documentation~\cite{Acar2016}.
+Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
 
 We call code snippets that are copied from software systems to online Q\&A websites (such as Stack Overflow), and vice versa as ``online code clones'' (sometimes only ``clones'' for brevity).
-There are four ways to create online code clones: (1) code is cloned from a software project to a Q\&A website as an example; (2) code is cloned from a Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is implicitly cloned from one software project to another by having a Q\&A website as a medium; and (4) code is cloned from an external source to both a software project and a Q\&A website.
+There are four ways to create online code clones: (1) code is cloned from a software project to a Q\&A website as an example; (2) code is cloned from a Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is transferred from one software project to another via a Q\&A website; and (4) code is cloned from an external source to both a software project and a Q\&A website.
 Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.
@@
 
-In this study, we are interested in locating online code clones on Stack Overflow that are cloned from open source projects and study them on two aspects: obsoleteness and licensing issues.
+In this study, we are interested in locating online code clones on Stack Overflow that are cloned from open source projects and study them on two aspects: \textbf{outdated code and licensing issues.}
 
@@
 In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
-The snippet shows how {\small{\texttt{hadoop}}} implements {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}} class.
-The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class but it is extracted from the latest version of {\small{\texttt{hadoop}}}.
+The snippet shows how {\small{\texttt{hadoop}}} implements the {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}} class.
+The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class but it is extracted from the latest version (as of 26 September 2016) of {\small{\texttt{hadoop}}}.
 We can obviously see that they are highly similar except one line, {\small{\verb|buffer.reset(null,0,0);|}}, is added in the latest version after {\small{\verb|key2.readFields(buffer);|}}.
-The added line is intended for cleaning up the reference in {\small{\verb|buffer|}} variable.
-While this change has already been introduced into {\small{\texttt{compare}}} method in the latest version of {\small{\texttt{hadoop}}}, the code example in Stack Overflow post is still unchanged.
-This example shows that there can be inconsistencies between online code clones and its original.
-The code snippet on Stack Overflow can be outdated.
+The added line is intended for cleaning up the reference in the {\small{\verb|buffer|}} variable.
+While this change has already been introduced into the {\small{\texttt{compare}}} method in the latest version of {\small{\texttt{hadoop}}}, the code example in Stack Overflow post is still unchanged.
+This example shows that there can be inconsistencies between online code clones and their originals.
+%The code snippet on Stack Overflow can be outdated.
 %Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
@@
 
-While a lot of research has focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and effects of reusing them such as outdated code and software licensing violation.
+While a lot of research has focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation.
 
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 315,786,118 similar code snippet pairs and manually investigated 3,595 candidate clone pairs between Java code snippets obtained from Stack Overflow accepted answers and 111 Java open source projects.
+We used two clone detection tools to discover 315,786,118 similar code snippet pairs and manually investigated 3,632 candidate clone pairs between Java code snippets obtained from Stack Overflow's accepted answers and 111 Java open source projects from a curated Qualitas corpus.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 523 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate their software licenses.
-Importantly, 53 out of the 96 online code clones on Stack Overflow are outdated and questionable for being reused.
+\noindent\textbf{2.~Addressing the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 668 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate software licenses.
+In addition, 64 out of the 112 online code clones on Stack Overflow are outdated and questionable for being reused.
 
@@
 \section{Empirical Study}
-We performed an empirical study of online code clones between Stack Overflow and 109 Java open source projects to answer the following research questions: \\ 
-\textbf{RQ1 (online code clones):} \textit{To what extent  source code is cloned between Stack Overflow and open source projects?} We quantitatively measured the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem.
-\newline
-%\textbf{RQ2 (flow of online code clones):} \textit{what are the directions that source code is cloned?} If clones between the two locations exist, we would like to observe in which direction the code has been copied.
-Is it mostly from Stack Overflow to open source projects, or the other way around, or equally both?
+We performed an empirical study of online code clones between Stack Overflow and 111 Java open source projects to answer the following research questions: \\ 
+\textbf{RQ1 (online code clones):} \textit{To what extent  is source code cloned between Stack Overflow and open source projects?} We quantitatively measured the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem.
 \newline
@@
 This gave us more insights to why online code clones are created.
-%so we can differentiate and understand the motivation of cloning.
-%Clones can be copied from open source projects to Stack Overflow as examples, or vice versa.
-Furthermore, they can be cloned from a third-party location or clones containing boiler-plate code, and code stubs generated by IDE.
-\newline
 \newline
 \textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We were interested in the correctness of Stack Overflow code examples since millions of users are potentially reusing them.
-%Is there observable problems caused by clones between Stack Overflow and open source projects?
-%We are interested to investigate the problem of outdated code and software licensing conflicts caused by online code clones.
-
+\newline
 \textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We investigated whether online code clones can be legally harmful to software reusing them.
@@
 To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}.
-We processed two datasets, Stack Overflow and 111 open source projects from Qualitas corpus.
-Java code snippets were extracted from Stack Overflow posts using regular expressions.
-We prepared Java code in both datasets by removing comments and pretty-printing to increase accuracy of clone detection.
+We processed two datasets, 144,075 code snippets from Java accept answers on Stack Overflow and 111 open source projects from Qualitas corpus.
+Java code snippets were extracted from Stack Overflow posts.
+We prepared the Java code in both datasets by removing comments and pretty-printing to increase the accuracy of clone detection.
 Then, we deployed two clone detection tools, Simian~\cite{simian} and NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets.
 Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times.
-Each run was composed of the whole Stack Overflow data and single Qualitas project.
-We repeated the process until we cover 111 projects.
-
-We then converted the clone reports to General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file.
+Each run was composed of the whole Stack Overflow data and a single Qualitas project.
+We repeated the process until we covered 111 projects.
+
+We then converted the clone reports to the General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file.
 GCF provides a common format for clones which enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad.
 Moreover, using GCF, other additional clone detectors could be adopted, if needed, without any changes in the analysis.
-Simian did not provide an option to detect inter clones between two locations.
-Hence the Simian GCF clone report was pruned to contain only inter clone pairs between Stack Overflow and Qualitas projects.
+Simian did not provide an option to detect clones between two locations.
+Hence the Simian GCF clone report was pruned to contain only clone pairs between Stack Overflow and Qualitas projects.
 In this step, all intra clone pairs within either Stack Overflow or Qualitas were removed.
-NiCad provided an option to detect inter clones so no pruning is needed.
+NiCad provides an option to detect clones from two locations so no pruning is needed.
 We did not have an oracle of clones between the two data sets so we rely on a manual investigation to validate the reported clone candidates.
-However, the large amount of clone pairs hindered us from looking at all of them.
+However, the large amount of generated clone pairs hindered us from looking at all of them.
 Random sampling of clones could be done but may return mostly non-meaningful clones.
@@
 They were pairs with high confidence to be true clones since they obtained agreement from both tools.
-Then, pairs reported by Simian and NiCad that did not find agreement were \textbf{disagreed clone pairs}.
+Then, pairs reported by Simian and NiCad that did not find agreement were rejected as \textbf{disagreed clone pairs}.
 The disagreed clone pairs were clones with less confidence than the agreed ones.
-Finally, agreed and disagreed clone pairs had been looked at manually by the first and the third author.
-
-In the manual inspection process, we classified clones into seven categories according to information observed from code comments and natural text in Stack Overflow answer.
-This process took approximately a months until we successfully investigated 3,450 clone pairs.
-Clone pairs that were classified as false clones, boiler-plate code, or IDE-generated were not very interesting and were ignore in the analysis of outdated code and licensing violation.
-We compared licensing information of 523 remaining clone pairs for possibility of software licensing violations.
-Moreover, we looked forward through history of each clone from its git repository.
+Finally, agreed and disagreed clone pairs have been looked at manually by two of the authors.
+
+In the manual inspection process, we classified clones into seven categories according to information observed from code comments and natural text in the Stack Overflow answer.
+This process took approximately a month until we successfully investigated 3,632 clone pairs.
+Clone pairs that were classified as false clones, boiler-plate code, or IDE-generated are not very interesting and were ignore in the analysis of outdated code and licensing violation.
+We compared the licensing information of 668 remaining clone pairs for possibilities of software licensing violations.
+Moreover, we looked at the history starting at the date of the answers to today from its git repository.
 With this method, we discovered \textbf{outdated code}, code that changes are made to them after it had been copied to Stack Overflow.
@@
 
+We followed the experimental framework by processing the source code from the two data sets, configuring and running the clone detectors, and analysing the clones.
+We discuss each of them in details below.
+
 \subsubsection{Datasets}
 
-\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of Stack Overflow dump \footnote{https://archive.org/details/stackexchange} in January 2016.
+\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016.
 The archived dump has a size of 9 gigabytes.
@@
 	\centering
-	\caption{62 QS outdated online clone pairs. Outdated clones are caused by modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}).}
+	\caption{64 QS outdated online clone pairs. Outdated clones are caused by modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}).}
 	\label{tab:stale_code_details}

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex
Consistency checks, English checks, numbers check + improvements throughout the paper.

@@
-\documentclass[sigconf]{acmart}
+\documentclass[sigconf,review, anonymous]{acmart}
 
@@
 We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags.
-A Stack Overflow thread contains a post of question and several posts of answers.
+A Stack Overflow thread contains a post of a question and several posts of answers.
 Every answer has voting score from its users.
@@
 First, we were only interested in code snippets with at least six lines.
-Snippets which were smaller than six lines were usually spurious clones~\cite{Bellon2007}.
+Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}.
 Second, we only focused on code snippets in accepted answers.
-We chose the snippets in accept answers because they actually solved the problems in the questions and had a check mark sign on them to notify other users.
-Moreover, they were always displayed just below the questions which made them attractive to be reused than other answers.
-Each snippet was extracted from the dump using regular expressions and saved to a file using its post ID as the file's name.
+We chose the snippets in accepted answers because they actually solved the problems in the questions.
+Moreover, they are always displayed just below the questions which makes them attractive to be reused than other answers.
+Each snippet was extracted from the dump and saved to a file.
+%using its post ID as the file's name.
 If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g.
@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We finally obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
+We obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
 
@@
 It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
-The projects in the corpus represent various domains of software systems ranging from programming language to 3D and visualisation~\cite{QualitasCorpus}.
+The projects in the corpus represent various domains of software systems ranging from programming languages to visualisation~\cite{QualitasCorpus}.
 We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects.
@@
 Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study.
-This resulted in total of 111 projects analysed in the study.
+This resulted in a total of 111 projects analysed in the study.
 As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code.
@@
 There is a number of restrictions in terms of choosing clone detection tools for this study.
-First, they have to support Java.
-Second, due to nature of code snippets posted on Stack Overflow, some of them are not complete Java classes or methods.
+The main restriction is due to nature of code snippets posted on Stack Overflow, most of them are not complete Java classes or methods.
 Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable.
-Third, since the amount of code that have to be processed are in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
+Moreover, since the amount of code that has to be processed is in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
 We have tried running 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets.
-CCFinder, iClones, and DECKARD failed to report clones between 144,075 Stack Overflow code snippets and 111 Qualitas projects.
-All of them reported execution errors after running for couple of hours.
+CCFinder, iClones, and DECKARD failed with execution errors after running for couple of hours.
 Thus, we removed them from the study.
@@
 
-\textbf{Simian} is a text-based clone detector which locate clones at line-level granularity and has been used extensively in several clone studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}.
+\textbf{Simian} is a text-based clone detector that locates clones at line-level granularity and has been used extensively in several clone studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}.
 It is a command-line tool which enables us to automate the detection.
@@
 It utilises TXL~\cite{Cordy2006} for parsing and pretty-printing source code.
-It also provide code normalisation by variable renaming and abstraction.
+It also provides code normalisation by variable renaming and abstraction.
 We use a variant of NiCad called \textit{nicadcross}.
@@
 \subsubsection{Prioritise Clone Candidates Using Agreement}
-A number of clones detected in large-scale datasets can be huge.
-In our study, there are totally 266,837,480 clone pairs reported.
-It is almost infeasible for human to manually validate them all.
+The number of clones detected in large-scale datasets can be huge.
+In our study, there are in total 266,837,480 clone pairs reported.
+It is infeasible for humans to manually validate them all.
 One can do a random sampling of clones.
 However, due to a very high number of false positives, they may end up looking at most of the false clones.
-Therefore, we adopted an idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in a situation that clone oracle is missing or impossible to establish.
-Clone pairs agreed by multiple clone detection tools have higher confident to be real clones~\cite{cr2016ssbse}.
+Therefore, we adopted the idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in situations where a clone oracle is missing or impossible to establish.
+Clone pairs agreed by multiple clone detection tools have a higher confidence to be real clones~\cite{cr2016ssbse}.
 By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
-To find an agreement between two clone pairs report by two different tools, we used clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
-Two clone pairs which have large enough overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1.
+To find an agreement between two clone pairs report by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
+Two clone pairs which have a large enough number of overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1.
 A \textit{good} clone pair has stronger agreement than an \textit{ok} pair.
@@
 
-Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(p)} iff, for $p \in [0,1]$ holds 
+Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(p)} iff, for threshold $p \in [0,1]$ holds 
 %\squeezeup
@@
 
-Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266-million candidate clone pairs for manual investigation.
-\textit{good} pairs are the ones with the highest confident and ranked the first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.
+Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266 million candidate clone pairs for manual investigation.
+\textit{good} pairs are the ones with the highest confident and ranked first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.
 
@@
 We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies~\cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
-However, considering the massive size of the two datasets and search space of at least 15 Simian's and 5 NiCad's parameters, we were hindered from searching for the best configurations of the tools.
+However, considering the massive size of the two datasets and search space of at least 15 Simian and 5 NiCad parameters, we were hindered from searching for the best configurations of the tools.
 Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}).
@@
 We followed the experimental framework and detected clones between Stack Overflow and Qualitas corpus using the two selected clone detectors.
-To answer RQ1, we computed statistics of clone discovered by the tools.
+To answer RQ1, we computed statistics on clones discovered by the tools.
 To answer RQ2, we manually investigated online clone pair candidates and categorised them using our patterns of online code cloning.
 The patterns were derived from Kapser et al.~\cite{Kapser2003} augmented by common patterns found in our data set.
-For RQ3, we looked at the true positive clone pairs and check if they are still up-to-date.
-Similarly, for RQ4, we also looked at the license of each clone and observed a possibility of licensing violation.
+For RQ3, we looked at the true positive clone pairs and checked if they are still up-to-date.
+Similarly, for RQ4, we also looked at the license of each clone and checked for a possibility of licensing violation.
 
@@
 The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}.
-From \Cref{tab:raw_stats}, Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported by $S_D$ and 1,531 from $S_E$ respectively.
-$N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a larger number of 12,886 snippets  mainly due to its relaxed configurations.
-In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs of 63,635,844 and 251,449,849 respectively.
-This is expected since EvaClone configurations prefer recall so it tends to remote more clones~\cite{Wang2013}.
+Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported for $S_D$ and 1,531 for $S_E$ respectively.
+$N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a much larger number of 12,886 snippets  mainly due to its relaxed configurations.
+In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs, 63,635,844 and 251,449,849 respectively.
+This large number of clones is expected since EvaClone configurations prefer recall~\cite{Wang2013}.
+$S_D$ and $N_D$ have the average clone pairs per snippet of 62 and 455 respectively.
+On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average.
 The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79.
 Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 reported by $N_E$.
-We can see from the statistics that EvaClone tunes the tools in the way that they report smaller clones.
-The average percentage of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
-A quick manual check of Simian's clone report revealed that there were problematic 11 snippets.
+We can see from the statistics that EvaClone tunes the tools in a way that they report smaller clones.
+The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
+A quick manual check of Simian's clone report revealed that there were 11 problematic snippets.
 These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
@@
 
-As displayed in \Cref{tab:online_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} agreed clone pairs is 2,308 while \textit{ok} is 11,749.
-The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively.
+As displayed in \Cref{t_agreed_good_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729.
+%The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively.
 The total number of clone candidates is 32,039 pairs.
-The details are as follows.
-
-\begin{table}
-	\centering
-	\caption{The number of online clone pair condidates (mutually exclusive) before and after filtering.}
-	\label{tab:online_clone_pairs}
-	\small
-%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|c|c|c|c|r}
-		\hline
-		\multirow{2}{*}{Set} & \multicolumn{1}{c|}{Before} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{Cand.} \\ \cline{3-6}
-		& \multicolumn{1}{c|}{Filters} & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
-		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
-		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
-		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 229,176 & & \checkmark & \checkmark & \checkmark & 88 \\ 
-		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\hline
-		Total  & 310,803 & & & & & 31,946 \\ 
-		\hline
-		\multicolumn{7}{l}{Filters*: \textit{L}=$Line \geq 10$, \textit{S}=$Sim \geq 85\%$,} \\
-		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
-	\end{tabular} %
-%}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{The online clone classification results}
-	\label{tab:online_clone_classification_results}
-	\small
-	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r}
-		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c|}{Classification} & \multirow{2}{*}{TP} \\ \cline{3-4}
-		& & Auto & Manual & \\
-		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 & 18 \\
-		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 & 75 \\
-		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 & 525 \\
-		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 & 50 \\ 
-		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\hline
-		Total  & 31,946 & 28,314 & 3,632 & 668 \\ 
-		\hline
-	\end{tabular} %
-	%}
-\end{table}
+We explain them in more details below.
 
@@
 
-Agreed clone pairs are clone pairs that pass Bellon's good- or ok-match criteria and selected for manual investigation.
+Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria and selected for manual classification.
 Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.
@@
 
-The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs} and depicted visually in \Cref{fig:good-ok-pairs}.
+The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs}.
+%and depicted visually in \Cref{fig:good-ok-pairs}.
 There are 2,321 (2,308 unique) \textit{good} pairs consisting of 18 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,267 pairs from $S_EN_E$.
-There are 32,560 (11,749 unique) \textit{ok} pairs\footnote{This excludes the subsumed 2,308 \textit{good} pairs.
+There are 32,560 (31,729 unique) \textit{ok} pairs\footnote{This excludes the subsumed 2,308 \textit{good} pairs.
 According to the definition, \textit{ok} pairs always subsume \textit{good} pairs.} We obtained 11,467; 993; 79; and 20,021 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively.
-Between the four configuration sets, there are considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair that is agreed by all four combinations.
+Between the four configuration sets, there is considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair that is agreed by all four combinations.
 
@@
 
-The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with clones from another tool.
-The disagreement can be from misalignment of clone lines or totally dissimilar clones due to different configurations.
-Disagreed pairs from Simian also cover clone pairs in projects having NiCad's errors (1 projects for $N_D$ and 5 for $N_E$) that are automatically missing from the agreed clone pairs.
-With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and drop $S_E$ and $N_E$ due to their enormous amount of clone pairs (60 and 250 millions respectively).
-Moroever, without clone agreement, $S_E$ and $N_E$ contain a large number of false positives due to the recall preference of their EvaClone configurations.
-
-Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 229,176 pairs for $N_D$).
-We hence apply four filters: \textbf{clone size, regular expression, similarity threshold, and good/ok pairs}.
-For the clone size filter, we raise the minimum clone size to 10 line as larger clones tend to be more interesting while smaller ones tend to be false clones~\cite{Saini2016}.
-Moreover, Gabel and Su show that unique code tend to be larger than seven lines~\cite{Gabel2010}.
-The 10--line threshold is already the default configuration for NiCad, thus this filter affects Simian clones only (Simian's default configurations consider a minimum of 6 lines).~The regular expression filter captures uninteresting boiler-plate clones of \verb|hashCode()| methods and some of the obvious getters and setters using regular expressions and removes them.
-The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity threshold configuration.
-The last filter, good/ok pairs, filters the pairs that already exist in \textit{good} or \textit{ok} set to avoid duplicates.
+\begin{table}
+	\centering
+	\caption{The number of disagreed online clone pair condidates before and after filtering.}
+	\label{tab:online_clone_pairs}
+	\small
+	%	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|c|c|c|c|r}
+		\hline
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filters} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filters} \\ \cline{3-6}
+		& & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
+		\hline 
+		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
+		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
+		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
+		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
+		\multirow{1}{*}{$N_D$} & 632,855 & & \checkmark & \checkmark & \checkmark & 88 \\ 
+		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+		\hline
+		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
+		\hline
+		\multicolumn{7}{l}{Filters*: \textit{L}=clone line $\geq 10$, \textit{S}=similarity $\geq 85\%$,}  \\
+		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
+	\end{tabular} %
+	%}
+\end{table}
+
+The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement from the other tool.
+The disagreement can be from a misalignment of clone lines or totally non-overlapping clones.
+The disagreed pairs from Simian cover clone pairs in the projects with NiCad's errors (1 projects from $N_D$ and 5 from $N_E$).
+%that are automatically missing from the agreed clone pairs.
+With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs (60 and 250 millions respectively).
+Moreover, $S_E$ and $N_E$ contain a large number of false positives due to the recall preference of their EvaClone configurations.
+
+Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 632,855 pairs for $N_D$).
+We applied four filters: \textbf{clone line, regular expression, similarity threshold, and good/ok pairs}.
+For the clone line filter, we raised the minimum clone size to 10 line since larger clones are more interesting, while smaller ones tend to be false clones~\cite{Saini2016}.
+Moreover, the study of uniqueness of source code by Gabel and Su~\cite{Gabel2010} suggests that source code are unique when they are larger than seven lines.
+Since the 10--line threshold is already the default configuration for NiCad, this filter is applied to Simian only (Simian's default configurations has a minimum clone size of 6 lines).~The regular expression filter removes boiler-plate clones of \verb|hashCode()| methods and getters/setters.
+The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity configuration.
+The last filter, good/ok pairs, removes the clone pairs that have already existed in the agreed clone sets.
+
+\begin{table}
+	\centering
+	\caption{The number of online clones candidates for the classification}
+	\label{tab:online_clone_classification_results}
+	\small
+	%	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r}
+		\hline
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
+		& & Auto & Manual \\
+		\hline 
+		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 \\
+		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 \\
+		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
+		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 \\
+		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 \\ 
+		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+		\hline
+		Total  & 31,946 & 28,314 & 3,632 \\ 
+		\hline
+	\end{tabular} %
+	%}
+\end{table}
 
 As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs.
-The combination of the three filters reduce the number of $S_D$ clones to 17,801 pairs for manual investigation.
-For $N_D$, 10-line threshold is already a minimum NiCad's clone size.
+The three filters reduced the number of $S_D$ clones to 17,801 pairs.
+%For $N_D$, 10-line threshold is already a minimum NiCad's clone size.
 However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones.
-Thus, besides regular expressions and good/ok pair filters, we filtered NiCad's clones further by a stricter similarity threshold.
-We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ from 0.3 to 0.15).
-We have tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and we found that 85\% similarity provides the best balance in terms of the amount of reported clones and feasibility for manual investigation.
-Using the three filters, we reduced the size of $N_D$ clones to 88 pairs.
-
-In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs).
+Thus, besides regular expressions and good/ok pair filters,
+We filtered $N_D$ clones by raising the similarity threshold.
+We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15).
+We tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and found that 85\% similarity provided the best balance in terms of the amount of reported clones and feasibility for manual investigation.
+Using this filter along with the regular expression and the good/ok pair filter, we reduced the size of $N_D$ clones to 88 pairs.
+
+%In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs).
 Finally, there are 3,502 pairs remaining which we manually classified them.
@@
 
-\textbf{To answer RQ1, we found 31,946 clone candidates between 111 Qualitas projects and 144,075 Stack Overflow snippets.
-They are 2,308 \textit{good}, 11,749 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs.
-After classification, we found 668 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}
+\textbf{To answer RQ1, we found 51,926 clone candidates between Qualitas projects and Stack Overflow code snippets.
+They are 2,308 \textit{good}, 32,729 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs respectively.} %After classification, we found 668 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}
 
@@
 
-Besides the quantitative analysis, we are also interested in a qualitative analysis of the online clones.
-How are the clone pairs created?
-%Due to an absence of clone oracle of the two data sets, we resort to a manual investigation to classify the clone pair candidates using our 7 patterns of online code cloning.
-
-We started by a preliminary study of the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008}.
-This preliminary investigation aims to evaluate the applicability of Kapser's cloning patterns to our study.
-Using $S_D$ clone report, snippets are ranked according to (1) frequency, (2) popularity (i.e.~number of associated Qualitas projects), (3) clone size in SLOC, and (4) clone percentage compared to the snippet size.
-We selected these criteria so that we can cover clones across various aspects.
-We then picked the top 10 snippets from the 4 groups resulting in 34 unique Stack Overflow snippets chosen.
-The 34 snippets generate 697 clone pairs with Qualitas projects.
+We are interested in the analysis of the patterns of online code clones.
+We studied the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008} and performed a small study to evaluate its applicability to our study.
+Using $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet.
+We selected these four criteria so that we could cover the online clones from various aspects.
+We selected the top 10 from each ranking and obtained 34 unique Stack Overflow snippets.
+The snippets were associated with 697 clone pairs.
 Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating.
@@
 
-Nevertheless, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol as pattern BP.
-We then added 6 new patterns observed as common cloning patterns from our preliminary study.
+The benefit of the study is two-folded.
+We evaluated Kapser's cloning patterns and also observed the common cloning patterns from the 697 clone pairs.
+After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns .
 The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}.
-QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow (by having comments in source code and explanation/links in Stack Overflow post).
-Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is the opposite of QS.
-UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones but without any attribution of copying.
-They are unique enough not be boiler-plate and inheritance or interface implementation.
-ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from an external source(s).
-Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters and setters, or IDE-generated code (e.g.~GUI components).
-Pattern IN (\textbf{In}heritance/Interface) is cloning because of inheritance of the same super class or implementation of the same interface.
-They usually share similar overriding methods.
-The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents false clone pairs.
-They can be either accidentally similar clones (e.g.~similar {\small\texttt{try-catch}} statements), similar clones after code normalisation, or just false positives of the tools.
-Using the classification patterns, we can also calculate the number of true and false positives.
-We are looking for unique and meaningful clones in this study.
-Thus, we consider clone pairs classified into pattern QS, SQ, UD, and EX as true positive, and BP, IN, and AC as false positive.
+Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has an evidence to be copied from Qualitas to Stack Overflow.
+The evidence of copying can be found from comments in the source code or from the post's contents.
+Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is a cloning, with an evidence, in the opposite direction to QS.
+Pattern UD (\textbf{U}nknown \textbf{D}irection) is a cloning that creates exactly identical or highly similar clones but we could not find any attribution of copying.
+%The UD clones are also unique enough to not be a boiler-plate code.
+Pattern ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from a single or multiple external sources.
+Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components.
+Pattern IN (\textbf{In}heritance/Interface) is a cloning by inheritance of the same super class or implementation of the same interface.
+These two activities usually result in similar overriding methods.
+The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs.
+They are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements or similar code after normalisation.
+
+%With the online cloning patterns, we could calculate the number of true and false positives. %We are looking for unique and meaningful clones in this study. Thus,
 
 \subsubsection{Classification of Clone Candidates}
-
-There were 31,946 online clone pair candidates for classifications as shown in \Cref{tab:online_clone_pairs}.
-We have use regular expressions to automatically classify \texttt{equals()}, getter and setter methods  based on the method signature since they are trivial clones and not very interesting.
-As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us captured 28,314 clone pairs and classified them into pattern BP.
-There were 3,632 pairs left for manual check after the automatic classification.
-
-The first author who has been working on clone detection research for two years took the role of a main investigator performing a manual classification of all the 3,632 clone pairs.
-By consulting the cloning patterns, the main investigator manually went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair.
-A relevant and useful observation was also recorded for each clone pair.
 
@@
 
-The investigator followed the following steps to classify the clones (depicted in \Cref{fig:classification_process}).
-First, we looked at the source code to see their similarity.
-If they were accidentally similar after code normalisation or by relaxation of the clone detection tool's configurations, the pair was classified as AC.
-If they were boiler-plate code, the pair was classified as BP.
-If they implemented the same interface or inherited the same class and had similar code, the pair was classified as IN.
-If the pair was not UD, IN, or AC; we started a detailed investigation.
-The main investigator opened the Stack Overflow post using its post ID with a web browser, read through the post carefully both in natural text and source code, looked for any hints or evidence mentioning code copying.
-If an evidence(s) had been found and appeared to be a Qualitas project as reported in the clone pair, the pair was classified as QS.
-Several times questions, name of posters, tags were also considered to gain better understanding.
-If there was no evidence on Stack Overflow but on Qualitas project mentioning about copying from Stack Overflow, the pair was classified as SQ.
-If there was evidence(s) of copying, but from an external source(s) instead of Qualitas, the pair was classified as EX.
-Lastly, if there was no evidence of copying in any direction, but source code of the clone pair are almost identical or highly similar, we conservatively classified them as UD.
-
-To guarantee quality of the classification, the second author took the role of a validating investigator performing 10\% validation (363 pairs) of the clone pairs judged by the main investigator.
-After the validation, results from the two investigators were compared and 54 conflicts were found.
-The two investigators discussed and resolved 51 of them while 3 conflicts were resolved by the third author.
+The online clone classification follows the steps depicted in \Cref{fig:classification_process}.
+First, we look at a pair of clone fragments to see their similarity.
+If they are accidentally similar clones after code normalisation or false positive clones from the clone detection tools, we classify the pair into AC.
+If the two fragments are boiler-plate code, the pair is classified into BP.
+If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN.
+If the pair is not UD, IN, or AC; we start a detailed investigation.
+We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying.
+If an evidence of copying has been found from a Qualitas project, the pair is classified in QS.
+Several times questions, name of posters, and tags were also considered to gain better understanding.
+On the other hand, if the source code from Qualitas project mentioning about copying from Stack Overflow, the pair is classified into SQ.
+If there is an evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX.
+Lastly, if there is no evidence of copying in any direction but the clone fragments are highly similar, we classify them into UD.
+
+We had in total 31,946 online clone pair candidates for classifications.
+2,308 and 11,749 were \textit{good} and \textit{ok} clone pairs respectively.
+17,801 and 88 clone pairs are from $S_D$ and $N_D$ after the filtering.
+Please note that we ignored 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to their large number of clones and the very small average clone sizes of 4.79 and 5.33 lines (see \Cref{tab:raw_stats}).
+They had high possibilities to be trivial clones.
+
+Before performing manual classification, we used regular expressions to automatically classify {\small\texttt{equals()}} and the remaining getters/setters.
+As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us captured 28,314 clone pairs and classified them into pattern BP.
+
+There were 3,632 pairs left for the manual check.
+The first author who has been working on clone detection research for two years took the role of the main investigator performing a manual classification of the 3,632 clone pairs.
+By consulting the cloning patterns, the main investigator went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair.
+A relevant and useful observation was also recorded for each clone pair.
+
+To mitigate the human errors of the manual classification, the second author took the role of the validating investigator performing 10\% validation (363 pairs) of the clone pairs judged by the main investigator.
+After the validation, the classifications from the two investigators were compared and 64 conflicts were found.
+The two investigators discussed and resolved 61 of them while the 3 conflicts were resolved by involving the third author.
 The classification results are shown in \Cref{tab:classification_good_o}.
-
-\textbf{As an answer to RQ2, the classification results are explained and discussed below.}
-
-\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 110 online clone pairs with strong evidences of cloning from Qualitas projects to Stack Overflow.
+%We consider the clone pairs classified into pattern QS, SQ, UD, and EX as true positives.
+On the other hand, clones in pattern BP, IN, and AC are classified as false positives since they are trivial and not very interesting ones.
+\textbf{To answer RQ2, the classification results are explained and discussed below.}
+
+\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 110 online clone pairs with evidences of cloning from Qualitas projects to Stack Overflow.
 They include 3, 12, 86, and 9 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
-Most of them had statements in the Stack Overflow post saying that the code was ``copied'', ``modified'', ``adopted'' from a specific file or class in Qualitas.
-The most cloned projects were \texttt{hibernate} and \texttt{spring} having 20 clone pairs, followed by \texttt{eclipse} (15), and \texttt{hadoop} (12).
-The clones were mostly cloned as examples and were very similar to their original Qualitas code with limited modifications.
-
-\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find any clone pairs with strong evidences of cloning from Stack Overflow to Qualitas projects.
-
-\textbf{UD: Unknown Direction.} We found 382 online clone pairs with no evidence of cloning between Qualitas and Stack Overflow but with high code similarity.
+Most of them have a statement in the Stack Overflow post saying that the code is ``copied'' or ``modified'' from a specific file or class in Qualitas.
+The most cloned projects is {\small\texttt{hibernate}} and {\small\texttt{spring}} with 20 clone pairs, followed by {\small\texttt{eclipse}} (15 pairs), and {\small\texttt{hadoop}} (12 pairs).
+The clones are used as examples and are very similar to their original Qualitas code with limited modifications.
+
+\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find any clone pairs with an evidence of cloning from Stack Overflow to Qualitas projects.
+
+\textbf{UD: Unknown Direction.} We found 382 online clone pairs with no evidence of cloning between Qualitas and Stack Overflow but with a high code similarity.
 They include 11, 42, 294, and 35 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
-The most cloned projects in this pattern was {\small{\texttt{netbeans}}} which had 95 clone pairs.
-Most of the clones were large chunk of code involving GUI components which might also be auto-generated.
-However, we also did not have any evidence.
-The second most cloned project was {\small{\texttt{jung2}}} (62 pairs) that was a network and graph framework.
-There were several Stack Overflow snippets that were identical to code in {\small{\texttt{jung2}}}.
-The third project was {\small{\texttt{eclipse-SDK}}} (37 pairs).
-
-\textbf{EX: External Sources.} We found 178 online clone pairs with evidences of cloning from external sources to Stack Overflow.
-They include 4, 23, 145, and 6 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
-%\begin{table}[]
-%	\centering
-%	\caption{31 external clones found in Stack Overflow posts}
-%	\label{tab:ext_clones}
-%	\begin{tabular}{l|r|r}
-%		\hline
-%		Type        & FOSS & Web \\ \hline
-%		StackOverflow only     & 1    & 1   \\
-%		StackOverflow + Qualitas & 15   & 14  \\ \hline
-%	\end{tabular}
-%\end{table}
-This findings complement a study of inter clones between software projects~\cite{Svajlenko2014}.
-We show that, besides software projects, clones can also be copied over different websites on the Internet.
-There are 15 clone pairs that are originated from programming websites.
+The most cloned projects is {\small{\texttt{netbeans}}} with 95 clone pairs.
+Most of the clones are a large chunk of code handling GUI components.
+Although these GUI clones might be auto-generated by IDEs, we did not find any evidence.
+The second most cloned project is {\small{\texttt{jung2}}} (62 pairs), a network and graph framework, followed by {\small{\texttt{eclipse-SDK}}} (37 pairs).
+%There are several Stack Overflow snippets that are identical to code in {\small{\texttt{jung2}}}.
+
+\textbf{EX: External Sources.} We found 197 online clone pairs with evidences of cloning from external sources to Stack Overflow.
+They include 4, 41, 146, and 6 clone pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ respectively.
+
+This findings complement a study of clones between software projects~\cite{Svajlenko2014}.
+We found that the code cloning can also happen among different sources on the Internet just like software projects.
+There are 30 clone pairs that are originated from programming websites.
 For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html.
 Both Stack Overflow and {\small\texttt{compiere}} project source code contain attribution to the original source.
-Another example is a code of algorithm to generate graphical \textit{Perlin noise} copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/.
-This code is used in both Stack Overflow and {\small\texttt{aoi}} project with attribution.
+Another example is a code to generate graphical \textit{Perlin noise}.
+It is copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/.
+The code is used in Stack Overflow and {\small\texttt{aoi}} project with attribution.
 %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
-There were 12 pairs cloned from {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and {\small\texttt{org.bouncycastle.crypto}} project.
+There other EX clone pairs are from third-party libraries such as {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and the {\small\texttt{bouncycastle}} cryptography project.
 
 \textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs found in this study.
-Although we surly removed some of the boiler-plate code with filters before the analysis, we still observed 28,642 BP clone pairs which accounted for 89.7\% of all clone pairs we classified.
-The majority of them were {\small{\texttt{equals()}}} methods.
-
-\textbf{IN: Inheritance/interface.} There were 109 clone pairs found to be similar because they implemented the same interface or inheriting from the same class.
-An example was two implementations of {\small{\texttt{MouseListener}}} that share similar {\small\texttt{@Override}} methods of {\small\texttt{mousePressed}}, and {\small\texttt{mouseReleased}}.
-
-\textbf{AC: Accidental Clones.} 31,946 were clone pairs that were accidentally similar due to several reasons.
-Mainly, they were caused by the effects of code normalisation applied to the source code before detection.
-However, the original source code were still different enough when we manually classified them.
-Other causes include {\small\texttt{finally}} or {\small\texttt{try-catch}} clauses that were accidentally the same due to their very small sizes, or clearly non-cloned code which may somehow miss the tools' detections.
-
-%For \textit{good} pairs, 10 pairs were automatically classified by regular expressions and 2,298 pairs were manually classified.
-This resulted in 3 clone pairs in pattern QS which is found to be copied from a Qualitas project to Stack Overflow.
-Four pairs are highly similar or identical but without any evidence of copying (no comments in neither Stack Overflow post nor Qualitas source code) and are classified as pattern UD.
-Please note that we were conservative in this study when doing classification.
-Even the clone pairs were exactly or almost identical but we could not find an evidence that it was cloned in any particular direction, we classified them as UD instead of QS, SQ, or EX.
-We observed 4 pairs in pattern EX since they are copied from external sources.
-111 clone pairs are found to be pattern BP.
-Seven pairs are similar code from inheriting the same superclass or implementing the same interface, pattern IN.
-Finally, 2,172 pairs are false clones and classified into FC.
-No clones were found in pattern SQ.
-This was expected since we selected a pretty old Qualitas snapshot dated back 2013 and most of the code could be written long before that.
-
-%For \textit{ok} clone pairs, we could not feasibly investigate all 31,729 pairs manually and decided to remove $S_EN_E$ from this round of classification.
-According to the classification of \textit{good} pairs, we found that $S_EN_E$ accounted for 98.9\% of all false positive pairs in \textit{good} pairs.
-This was not a surprise since EvaClone configurations prefered recall and hence offered relaxed configurations.
-We ignored them since we were more interested in meaningful clones.
-This resulted in 11,749 \textit{ok} pairs remaining.
-11,494 clone pairs were automatically classified and 255 pairs were looked at manually.
-%We found 12, 42, 23, 11,459, 20, and 103 in QS, UD, EX, BP, IN and AC respectively. Similarly, no clone pairs were found in SQ.
+Although we have removed some of the boiler-plate code with filters before the analysis, we still observed 28,749 clone pairs.
+The BP clone pairs account for 89.7\% of all clone pairs we classified.
+The majority of them are {\small{\texttt{equals()}}}.
+
+\textbf{IN: Inheritance/interface.} There were 111 clone pairs found to be similar because they implement the same interface or inheriting from the same class.
+An example is the two implementations of {\small{\texttt{MouseListener}}} that share similar {\small\texttt{@Override}} methods of {\small\texttt{mousePressed}}, and {\small\texttt{mouseReleased}}.
+
+\textbf{AC: Accidental Clones.} There were 2,418 accidental clone pairs.
+Mainly, they are false positive clones caused by code normalisation.
+%However, the original source code were still different enough when we manually classified them.
+Other clone instances include {\small\texttt{finally}} or {\small\texttt{try-catch}} clauses that were accidentally the same due to their very small sizes, and similar {\small\texttt{switch-case}} statements.
 
@@
 %\subsubsection{Outdated Clones}
-To the best of our knowledge, this work is the first to discuss a problem of outdated code on Stack Overflow.
-Outdated code occurs when a piece of code has been copied from its origin to another location and later the original code has been updated~\cite{Xia2014}.
-Usually code clone detection is used to locate clone instances and update them to match with the original code~\cite{Bellon2007}.
-However, for online code clones, the clones are pervasive and are more difficult to detect than in a local project(s) due to its large search space and the mix of natural and programming language combined together in Stack Overflow posts.
+Outdated code occurs when a piece of code has been copied from its origin to another location and later the original has been updated~\cite{Xia2014}.
+Usually code clone detection is used to locate clone instances and update them to match with the originals~\cite{Bellon2007}.
+However, for online code clones, the clones are pervasive and more difficult to detect than software projects due to its large search space and a mix of natural and programming languages combined in the same post.
 Moreover, Stack Overflow is not a software.
-There is no test suite to run and check whether the code snippets are still working as expected.
-
-To check if our online code clones are outdated, we focused on the 112 QS clone pairs that were cloned from Qualitas to Stack Overflow (see \Cref{tab:classification_good_o}) and compared them with their latest versions.
+There is no test suite to run and check whether the validity of the code snippets.
+To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.
+
+To search for outdated online code clones, we focused on the 112 QS clone pairs that were cloned from Qualitas to Stack Overflow and compared them with their latest versions.
 We cloned the latest version of the Qualitas projects from their repositories on 26 September 2016.
-For each online clone pair, we used the file name of Qualitas clone to search for its latest version.
-Once we found the file, we located the location of the cloned snippets in the file based on method names.
-So for Simian clones that may not contain in a single method, we looked further up and down the clone region to get the method name and its nearby methods.
+For each QS online clone pair, we use the clone from Qualitas a a proxy.
+We searched for its latest version by the file name and located the cloned region in the file based on the method name.
+For Simian clones where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region.
 We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code.
-We also made sure that the changes did not come from modifications maded to Stack Overflow snippets by the posters but from the projects themselves.
-When we found inconsistent lines between the two versions, we used \texttt{git blame} command to see who modified those lines of code and noted down the details.
-
-\Cref{fig:outdated} shows the findings of outdated online clones on Stack Overflow.
+We also made sure that the changes did not come from the modifications made to the Stack Overflow snippets by the posters but from the updates in the projects themselves.
+When we found inconsistent lines between the two versions, we used {\small\texttt{git blame}} to see who modified those lines of code and noted down the timestamps and other details.
+
+\Cref{tab:stale_code_details} summarises the outdated online clones on Stack Overflow.
+The table shows information of the clones from both Stack Overflow and Qualitas side including the dates.
+We summarise the changes that make the clones outdated into three types, modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}), along with the date of change.
 We discovered 64 outdated online clone pairs out of 112 pairs.
+Some of the clone pairs overlap with each other so we group them in the same row.
 {\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}.
-An example of outdated code in {\small{texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} has already been shown in \Cref{fig:before-after}.
-We also found a few outdated code which contained heavy modifications.
-For example, the code snippet in Stack Overflow post 23520731, a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}, it had been heavily modified in the latest version (as shown in \Cref{fig:hibernate_outdated_code}).
+Besides the example of outdated code in the {\small{\texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} shown in \Cref{fig:before-after}, we also found a few outdated code which contained heavy modifications.
+For example, the code snippet in Stack Overflow post 23520731 is a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}.
+The code have been heavily modified on 5 February 2016 (as shown in \Cref{fig:hibernate_outdated_code}).
 In the 64 outdate pairs, we found 5 of them to be ``dead'' snippets.
-These snippets did not have their originals in the latest version of the projects anymore.
-For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in {\small{\texttt{spring}}}, was deleted in commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012 at 22:51:02, two years after it was posted.
+These snippets cannot find their originals in the latest version of the projects.
+For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in {\small{\texttt{spring}}}, was deleted in the commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012, two years after it was posted.
 %The latest version of Spring does not contain the file anymore.
 
-The outdated online code clones can cause problems ranging from uncompilable code (due to modifications and different API usage in the outdated code) to bug propagations.
+The outdated online code clones cause problems ranging from uncompilable code (due to modifications and different API usage in the outdated code) to introducing vulnerabilities to software~\cite{Xia2014}.
 An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers.
-Although Stack Overflow has a voting mechanism that may mitigate this outdated code issue, the check mark symbol in front of the accepted answer is still attractive enough for naive developers who are ignorant to copy and reuse the code.
+Although Stack Overflow has a voting mechanism that may mitigate this issue, the accepted answer is still attractive enough for naive developers who are ignorant to copy and reuse the code.
 
@@
 4 pairs are dead snippets.
-They do not exist any more in the latest version.
-These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
+They do not exist any more in the latest version.} %These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
 Even worse, they might also introduce bugs or vulnerabilities into their software.
@@
 %It is an emerging area that software engineering research community is paying attention to. For example, 
-One can run into licensing issue if they do not check before integrating third-party source code into their software.
-A study by An et al.~\cite{An2017} found 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code.
+One can run into a licensing issue if they integrate third-party source code into their software without checking.
+A study by An et al.~\cite{An2017} reports 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code snippets.
 %there are studies of automatic technique to identify software licensing from source code files~\cite{German2010}
@@
 	\centering
-	\caption{License matching of online clones (file-level) in QS, UD, and EX}
+	\caption{License mapping of the online clones (file-level) in QS, UD, and EX}
 	\label{tab:license_abc}
@@
 
-In our study, we reveal another possible situation of software licensing issues caused by code cloning ``to Stack Overflow''.
+In our study, we reveal another possible situation of software licensing issues caused by code cloned ``to Stack Overflow''.
 We found with evidence that 112 pieces of code had been copied from Qualitas projects to Stack Overflow as examples.
-They are also marked as accepted answers which increased their chances of being reused.
-The projects came with their respective software licenses (shown in \Cref{t:q_projects_license}).
-However, we found that the licensing information were mostly stripped from these clones after they were posted on Stack Overflow.
-The licensing terms on the top of source code are not copied because mostly a small part of the file was cloned to Stack Overflow.
-If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
-
-We analysed licensing conflicts of online clones in QS, UD, and EX set.
+Their status of accepted answers increase their chances of being reused.
+Most of the Qualitas projects came with a software license (shown in \Cref{t:q_projects_license}).
+However, we found that the licensing information were frequently missing after the code were copied to Stack Overflow.
+The licensing terms on top of source code files are not copied because usually only a small part of the file was cloned.
+%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
+
+We analysed licensing conflicts of the online clones in the QS, UD, and EX set.
 The summary of licensing information is listed in \Cref{tab:license_abc}.
 The licenses were extracted by \textbf{Ninka}, an automatic license identification tool~\cite{German2010}.
-Since Ninka worked at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of clone pairs (duplicates were ignored).
-For the ones that could not be automatically identified by Ninka and had been reported as {\small\texttt{SeeFile}} and {\small\texttt{Unknown}}, we looked at them manually and updated if any license was found.
-The table shows license of Stack Overflow snippets and Qualitas source code.
-The results were reported in groups of QS, UD, and EX.
-Overall we can see that most of the Stack Overflow snippets do not contain licensing terms while their clone counterparts in Qualitas project do.
-
-\textbf{No license or compatible license:} There are 31 clone pairs which do not have license on both sides and 8 pairs which have compatible licenses such as Apache license v.2; Eclipse Public License v.1 (EPLv1); No license vs.~Creative Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC BY-NC-SA 3.0).
-They are safe for being reused.
-Since source code and text on Stack Overflow posted before 1st March 2016 are protected by CC BY-NC-SA 3.0 (and MIT license from 1st March 2016 onwards), we can treat Stack Overflow code snippets without licensing information as having CC BY-NC-SA 3.0 by default.
-CC BY-NC-SA 3.0 license is relaxed and it only request attribution when reuse.
+Since Ninka works at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of the clone pairs (duplicates were ignored).
+For the ones that could not be automatically identified by Ninka and has been reported as {\small\texttt{SeeFile}} or {\small\texttt{Unknown}}, we looked at them manually and updated if any license was found.
+The table shows the license mapping of Stack Overflow snippets and Qualitas source code.
+The results are reported separately for the QS, UD, and EX set.
+In overall, we can see that most of the Stack Overflow snippets do not contain licensing terms while their clone counterparts in Qualitas project do.
+
+\textbf{No license or compatible license:} There are 31 clone pairs which do not have license on both sides and 8 pairs which have compatible licenses such as Apache license v.2; Eclipse Public License v.1 (EPLv1); or a pair of No license vs.~Creative Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC BY-NC-SA 3.0).
+These clones are safe for being reused.
+Since source code and text on Stack Overflow posted before 1st March 2016 are protected by CC BY-NC-SA 3.0 (and MIT license from 1st March 2016 onwards), we can treat the Stack Overflow code snippets without licensing information as having CC BY-NC-SA 3.0 by default.
+CC BY-NC-SA 3.0 license is relaxed and it only requests an attribution when reused.
 
@@
 Of 226 UD clone pairs, 202 pairs have incompatible licenses.
-Again, most of the clones in Qualitas contain license while the Stack Overflow snippets do not.
+Again, most of the clones in Qualitas contain a license while the Stack Overflow snippets do not.
 For EX clone pairs, we searched for licensing terms of the original source code from the external sources.
-We found that 76 out of 87 EX clone pairs have incompatible license.
+We found that 76 out of 87 EX clone pairs have incompatible licenses.
 %They are clones that have been identified to be copied from an external source.
-Similarly, their license were removed from Stack Overflow snippets.
+Similarly, the license statement was removed from Stack Overflow snippets.
 
@@
 We reused the established configurations from the EvaClone study~\cite{Wang2013}.
-We also performed pairwise matching between the default and EvaClone configurations of the two clone detection tools.
+We also performed a pairwise matching between the default and EvaClone configurations of the two clone detection tools.
 
@@
 
-Regarding the code snippets, we downloaded the full data dump and extracted Java accepted answers. 
-Instead of analysing every post, we only focused on posts marked as accepted answers 
+Regarding the code snippets, we downloaded a full data dump and extracted Java accepted answers. Instead of analysing every post, we only focused on posts marked as accepted answers 
 since they are the most likely to being reused. This yields totally 144,075 snippets.
-Our findings are limited to these restrictions. They may not be generalised to all programming languages and all
-answers on Stack Overflow.
-
+Our findings are limited to these restrictions.
+They may not be generalised to all programming languages and all the answers on Stack Overflow.
 On the other hand, we chose the curated Qualitas corpus for Java open source projects containing 111 projects \cite{QualitasCorpus}.
@@
 
-Lastly, two clone detection tools, Simian and NiCad, are chosen for this study 
-due to certain limitations of a few other tools. We have not tried all the tools available 
-and they might not be complete representatives of all available clone detection tools.
+Lastly, two clone detection tools, Simian and NiCad, are chosen for this study.
+We have not tried all the tools available and they might not be complete representatives of all available clone detection tools.
 
@@
 The code snippets on Stack Overflow are mostly examples or solutions to programming problems.
-Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
-Furthermore, Treude et al.~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation~\cite{Treude2016}.
-
-Another aspect is knowledge extraction from Stack Overflow.
-Nasehi et al.~studied what makes a good code example by analysing answers from Stack Overflow~\cite{Nasehi2012}.
-Similarly, Yang et al.~\cite{Yang2016} analysed Stack Overflow snippets across various programming languages and observed that code snippets in Python and Javascript are the most usable.
+Hence, several code search systems use a whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
+Furthermore, Treude et al.~\cite{Treude2016}~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation.
+
+Another research area is knowledge extraction from Stack Overflow.
+Nasehi et al.~\cite{Nasehi2012}~studied what makes a good code example by analysing answers from Stack Overflow.
+Similarly, Yang et al.~\cite{Yang2016} report the number of reusable code snippets on Stack Overflow across various programming languages.
 Wang et al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic modelling to analyse questions and answers from Stack Overflow so that they can automatically categorise new questions.
@@
 However, by only knowing how many code clones residing in software and how they evolve~\cite{Pate2013,Mondal2011} can provide several valuable insights into the software systems.
-Besides clones, clone detection has its several applications such as software plagiarism detection~\cite{Prechelt2002},
+Code clones have several applications such as software plagiarism detection~\cite{Prechelt2002},
 source code provenance~\cite{Davies2013}, and software licensing conflicts~\cite{German2009}.
@@
 use string comparison techniques such as Simian~\cite{simian}.
-NiCad~\cite{Roy2008,Cordy} also exploits Longest Common Subsequence (LCS) string similarity measure to discover clones after applying code pretty-printing using TXL~\cite{Cordy2006}.
+NiCad~\cite{Roy2008,Cordy} exploits the Longest Common Subsequence (LCS) string similarity measure after applying code pretty-printing using TXL~\cite{Cordy2006}.
 Many tools do not work on original source code directly but transform them into an
@@
 Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}.
-Our study partially adapted their patterns for our online code clone classification scheme.
-
-\textbf{Clone agreement} is useful in when clone oracle is absent.
+Our study adopted on of the patterns into our online code cloning patterns.
+
+\textbf{Clone agreement} is useful in when a clone oracle is absent.
 Since clone detectors are different in their detection approaches, they may behave differently and report different clones even on the same data set.
 Some researchers exploit these different behaviours of clone detectors by finding their agreement and obtain highly-confident clones~\cite{Bellon2007,Wang2013}.
-Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are highly potential to be true clones than the ones reported by only a single tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
-These studies also report that sensitivities of the tools' parameter settings have strong effects to the results~\cite{Wang2013,cr2016ssbse}.
+Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are more assured to be true clones than the ones reported by only a single tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
+There are studies that report sensitivities of the tools' configurations to the results~\cite{Wang2013,cr2016ssbse}.
+It has been reported that searching for an optimal configuration for every new data set is preferred.
 
@@
 \textbf{Reusing of outdated third-party source code} occurs in software development.
-Xia et al.~\cite{Xia2014} show that a large number of open source systems reuse outdated third-party libraries from famous open source projects.
-Using outdated code give detrimental effects to the software since they may introduce vulnerabilities.
-Our study discovers similar findings in the context of outdated code from Stack Overflow.
+Xia et al.~\cite{Xia2014} show that a large number of open source systems reuse outdated third-party libraries from popular open source projects.
+Using the outdated code give detrimental effects to the software since they may introduce vulnerabilities.
+Our study discovers similar findings in the context of outdated code on Stack Overflow.
 
@@
 They also observed that there are 1,219 cases of potential license violations.
-However, the authors rely on the timestamp to judge whether the code has been copied from/to Stack Overflow along with confirmations from six developers.
+The authors rely on the timestamp to judge whether the code has been copied from/to Stack Overflow along with confirmations from six developers.
 Instead of Android apps, we investigated clones between Stack Overflow and 111 open source projects.
 Our results confirm their findings that there are clones from software projects to Stack Overflow with potential licensing violations.
-In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,450 clone pairs.
-We discovered 96 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
-By comparing the clones to their latest versions in the software, we found that 58 code snippets on Stack Overflow are outdated and harmful for reuse.
+In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,632 clone pairs.
+We discovered 112 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
+By comparing the clones to their latest versions in the software, we found that 64 code snippets on Stack Overflow are outdated and harmful for reuse.
 
@@
 %ACKNOWLEDGMENTS are optional
-\section{Acknowledgments}
-This section is optional; it is a location for you
-to acknowledge grants, funding, editing assistance and
-what have you.  In the present case, for example, the
-authors would like to thank Gerald Murray of ACM for
-his help in codifying this \textit{Author's Guide}
-and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{Sankey_proj}
-	\caption{Relationships of 58 Stack Overflow clone pairs to their original projects. 55 are outdated and 3 are deleted (shown using (d) suffix).}
-	\label{fig:sankey}
-\end{figure}
+%\section{Acknowledgments}
+%This section is optional; it is a location for you
+%to acknowledge grants, funding, editing assistance and
+%what have you.  In the present case, for example, the
+%authors would like to thank Gerald Murray of ACM for
+%his help in codifying this \textit{Author's Guide}
+%and the \textbf{.cls} and \textbf{.tex} files that it describes.
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\linewidth]{Sankey_proj}
+%	\caption{Relationships of 58 Stack Overflow clone pairs to their original projects. 55 are outdated and 3 are deleted (shown using (d) suffix).}
+%	\label{fig:sankey}
+%\end{figure}
 

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex
Simple spell check.

@@
 	\centering
-	\caption{The number of disagreed online clone pair condidates before and after filtering.}
+	\caption{The number of disagreed online clone pair candidates before and after filtering.}
 	\label{tab:online_clone_pairs}
@@
 
-Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}.
+Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customisation and Exact match~\cite{Kapser2003,Kapser2008}.
 Our study adopted on of the patterns into our online code cloning patterns.

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex
Modified according to Matheus's comments/added boxplots/aded future work and conclusion.

--- 2017-02-14 cloneoverflow-latex/cloneoverflow.tex
@@
 Code cloning is an activity of reusing source code by copying and pasting.
-It normally occurs in software development and account from 7\% to 23\% in typical software systems~\cite{Bellon2007}.
+It normally occurs in software development and account from 7\% to 23\% of source code in typical software systems~\cite{Bellon2007}.
 The benefits and drawbacks of clones are still controversial.
@@
 
-Code cloning can also have side effects of violating software licenses and software vulnerabilities.
+Code cloning can also have side effects such as violating software licenses and software vulnerabilities.
 Carelessly cloning code from one project to another project with a different license may cause a software licensing violation~\cite{German2009}.
@@
 An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow potentially violate software licenses.
-Security is also among the main concerns when code is copied from online source.
+Security is also among the main concerns when code is copied from an online source.
 Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, offers less secure code than books or the official Android documentation~\cite{Acar2016}.
-Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
+
+\FIXME{Find the right location for this-->} Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
 
@@
 The snippet shows how {\small{\texttt{hadoop}}} implements the {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}} class.
-The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class but it is extracted from the latest version (as of 26 September 2016) of {\small{\texttt{hadoop}}}.
-We can obviously see that they are highly similar except one line, {\small{\verb|buffer.reset(null,0,0);|}}, is added in the latest version after {\small{\verb|key2.readFields(buffer);|}}.
+The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class, but at this time extracted from the latest version (as of 26 September 2016) of {\small{\texttt{hadoop}}}.
+We can obviously see that they are highly similar except a line containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in the latest version after {\small{\verb|key2.readFields(buffer);|}}.
 The added line is intended for cleaning up the reference in the {\small{\verb|buffer|}} variable.
 While this change has already been introduced into the {\small{\texttt{compare}}} method in the latest version of {\small{\texttt{hadoop}}}, the code example in Stack Overflow post is still unchanged.
-This example shows that there can be inconsistencies between online code clones and their originals.
+This example shows that there can be inconsistencies between online code clones and their originals leading the users of Stack Overflow to reuse outdated code.
 %The code snippet on Stack Overflow can be outdated.
@@
 
-While a lot of research has focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation.
+While research has mostly focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation.
 
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 315,786,118 similar code snippet pairs and manually investigated 3,632 candidate clone pairs between Java code snippets obtained from Stack Overflow's accepted answers and 111 Java open source projects from a curated Qualitas corpus.
+We used two clone detection tools to discover 315,786,118 similar code snippet pairs followed by a manual classification of 3,632 candidate clone pairs between Java code snippets obtained from Stack Overflow's accepted answers and 111 Java open source projects from a curated Qualitas corpus~\cite{QualitasCorpus}.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Addressing the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 668 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate software licenses.
-In addition, 64 out of the 112 online code clones on Stack Overflow are outdated and questionable for being reused.
+\noindent\textbf{2.~Investigating the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 668 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate software licenses.
+In addition, 64 out of the 112 online code clones from Qualitas to Stack Overflow are outdated and questionable for being reused.
 
@@
 \newline
-\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We were interested in the correctness of Stack Overflow code examples since millions of users are potentially reusing them.
+\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We were interested in the outdated Stack Overflow code examples since millions of users are potentially reusing them.
 \newline
@@
 Then, we deployed two clone detection tools, Simian~\cite{simian} and NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets.
-Due to scalability of Simian and NiCad, we partitioned the input and run the tools multiple times.
+Due to the scalability of Simian and NiCad, we partitioned the input and run the tools multiple times.
 Each run was composed of the whole Stack Overflow data and a single Qualitas project.
@@
 
+%enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad. Moreover, using GCF, other additional clone detectors could be adopted
 We then converted the clone reports to the General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file.
-GCF provides a common format for clones which enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad.
-Moreover, using GCF, other additional clone detectors could be adopted, if needed, without any changes in the analysis.
-Simian did not provide an option to detect clones between two locations.
+GCF provides a common format for clones which enables other clone detectors to be adopted,
+if needed, without any changes in the analysis.
+Simian did not provide an option to detect cross-project clones between two locations.
 Hence the Simian GCF clone report was pruned to contain only clone pairs between Stack Overflow and Qualitas projects.
@@
 However, the large amount of generated clone pairs hindered us from looking at all of them.
-Random sampling of clones could be done but may return mostly non-meaningful clones.
+Random sampling of clones could be employed.
+However, the risk of returning non-meaningful clones is increased.
 Instead, we selected clone pair candidates by relying on agreement of clone detectors.
@@
 They were pairs with high confidence to be true clones since they obtained agreement from both tools.
-Then, pairs reported by Simian and NiCad that did not find agreement were rejected as \textbf{disagreed clone pairs}.
+Then, pairs reported by Simian and NiCad that did not find agreement were categorised as \textbf{disagreed clone pairs}.
 The disagreed clone pairs were clones with less confidence than the agreed ones.
@@
 Moreover, we looked at the history starting at the date of the answers to today from its git repository.
-With this method, we discovered \textbf{outdated code}, code that changes are made to them after it had been copied to Stack Overflow.
+With this method, we discovered \textbf{outdated code}, i.e.~code that changes were made to them after they had been copied to Stack Overflow.
 %hence resulting in outdated clones on Stack Overflow.
@@
 We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags.
-A Stack Overflow thread contains a post of a question and several posts of answers.
-Every answer has voting score from its users.
+A Stack Overflow thread contains a post of a question and several posts of answers where every answer has voting score from its users.
 An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem.
@@
 We chose the snippets in accepted answers because they actually solved the problems in the questions.
-Moreover, they are always displayed just below the questions which makes them attractive to be reused than other answers.
+Moreover, they are always displayed just below the questions which makes them more attractive to be reused than other answers.
 Each snippet was extracted from the dump and saved to a file.
@@
 
-\textbf{Open source systems}: we selected an established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study.
+\textbf{Open source systems}: we selected the established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study.
 It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
@@
 Moreover, since the amount of code that has to be processed is in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
-We have tried running 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets.
+We have tried 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets.
 CCFinder, iClones, and DECKARD failed with execution errors after running for couple of hours.
@@
 One can do a random sampling of clones.
-However, due to a very high number of false positives, they may end up looking at most of the false clones.
+However, due to a very high number of false positives, they may end up looking mostly at the false clones.
 Therefore, we adopted the idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in situations where a clone oracle is missing or impossible to establish.
@@
 By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
-To find an agreement between two clone pairs report by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
+To find an agreement between two clone pairs reported by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
 Two clone pairs which have a large enough number of overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1.
 A \textit{good} clone pair has stronger agreement than an \textit{ok} pair.
-We follow the following definitions of good- and ok-match introduced in the original paper.
+We follow the original definitions of \textit{good}- and \textit{ok}-match introduced in Bellon's paper~\cite{Bellon2007}.
 
@@
 Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266 million candidate clone pairs for manual investigation.
-\textit{good} pairs are the ones with the highest confident and ranked first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.
+\textit{good} pairs are the ones with the highest confidence and are ranked first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.
 
@@
 To answer RQ2, we manually investigated online clone pair candidates and categorised them using our patterns of online code cloning.
-The patterns were derived from Kapser et al.~\cite{Kapser2003} augmented by common patterns found in our data set.
+The patterns were derived from Kapser et al.~\cite{Kapser2003} and augmented by common patterns found in our data set.
 For RQ3, we looked at the true positive clone pairs and checked if they are still up-to-date.
@@
 			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
-			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
+%			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
 			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
@@
 
-The clone statistics obtained from running Simian and NiCad with \textit{D} and \textit{E} configurations are presented in \Cref{tab:raw_stats}.
-Simian clones cover approximately 1\% of the 144,075 Stack Overflow snippets, 1,086 reported for $S_D$ and 1,531 for $S_E$ respectively.
-$N_D$ reports clones in 1,392 Stack Overflow code snippets, while $N_E$ reports clones in a much larger number of 12,886 snippets  mainly due to its relaxed configurations.
-In terms of number of clone pairs, $S_E$ and $N_E$ report a large number of clone pairs, 63,635,844 and 251,449,849 respectively.
-This large number of clones is expected since EvaClone configurations prefer recall~\cite{Wang2013}.
-$S_D$ and $N_D$ have the average clone pairs per snippet of 62 and 455 respectively.
+The clone statistics obtained from running Simian and NiCad are presented in \Cref{tab:raw_stats}.
+Simian with the default configuration ($S_D$) report clones in 1,086 snippets, approximately 1\% of the 144,075 Stack Overflow snippets.
+Simian with the EvaClone configuration ($S_E$) report 1,531 snippets containing clones.
+NiCad with the default configuration ($N_D$) reports clones in 1,392 Stack Overflow code snippets.
+NiCad with the EvaClone configuration ($N_E$) reports the largest number of 12,886 cloned snippets mainly due to its relaxed configurations.
+In terms of the number of clone pairs, $S_D$ reports 67,570 clone pairs while $N_D$ reports 632,855 clone pairs.
+$S_E$ and $N_E$ report a larger clone pair amount of 63,635,844 and 251,449,849 pairs respectively.
+This is expected since EvaClone configurations prefer recall~\cite{Wang2013}.
+%Using $S_D$, we found 62 clones in average originating from a single Stack Overflow snippet.
+62 and 455 respectively.
 On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average.
-The average clone size of $S_D$ is 7.72 lines which is bigger than its $S_E$ counterpart of 4.79.
-Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 reported by $N_E$.
-We can see from the statistics that EvaClone tunes the tools in a way that they report smaller clones.
+The average clone size reported by $S_D$ is 7.72 lines which is bigger than $S_E$ (4.79 lines).
+Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 lines reported by $N_E$.
+We can see from the statistics that EvaClone tunes the tools to report smaller clones.
 The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
@@
 
-As displayed in \Cref{t_agreed_good_clone_pairs}, after we applying clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729.
+As displayed in \Cref{t_agreed_good_clone_pairs}, after we applied clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729.
 %The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively.
@@
 
-Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria and selected for manual classification.
+Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria, and therefore are selected for manual classification.
 Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.
 %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \texttt{hibernate} due to clustering errors.
-$N_E$ generated renaming errors for 5 projects including \texttt{vuze}, \texttt{hibernate}, \texttt{myfaces}, \texttt{netbeans}, and \texttt{spring}.
+We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors.
+$N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and \texttt{spring}.
 We had contacted the creator of NiCad regarding the issues.
-They identified them as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
+They identified the issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
 As a result, we did not have NiCad clones from these projects in the agreed clone pairs.
@@
 We studied the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008} and performed a small study to evaluate its applicability to our study.
-Using $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet.
+Using the $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet.
 We selected these four criteria so that we could cover the online clones from various aspects.
@@
 The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}.
-Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has an evidence to be copied from Qualitas to Stack Overflow.
-The evidence of copying can be found from comments in the source code or from the post's contents.
-Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is a cloning, with an evidence, in the opposite direction to QS.
-Pattern UD (\textbf{U}nknown \textbf{D}irection) is a cloning that creates exactly identical or highly similar clones but we could not find any attribution of copying.
+Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow.
+The evidence of copying can be found in comments in the Qualitas source code or in the Stack Overflow post's contents.
+Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with an evidence, in the opposite direction to QS.
+Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones between Qualitas and Stack Overflow but where we could not find any attribution of copying.
 %The UD clones are also unique enough to not be a boiler-plate code.
-Pattern ES (\textbf{Ex}ternal Sources) is a cloning that has an evidence of copying from a single or multiple external sources.
+Pattern ES (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources.
 Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components.
-Pattern IN (\textbf{In}heritance/Interface) is a cloning by inheritance of the same super class or implementation of the same interface.
+Pattern IN (\textbf{In}heritance/Interface) is cloning by inheritance of the same super class or implementation of the same interface.
 These two activities usually result in similar overriding methods.
 The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs.
-They are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements or similar code after normalisation.
+These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements or similar code after normalisation.
 
@@
 If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN.
-If the pair is not UD, IN, or AC; we start a detailed investigation.
+If the pair is not UD, IN, or AC, we start a detailed investigation.
 We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying.
 If an evidence of copying has been found from a Qualitas project, the pair is classified in QS.
-Several times questions, name of posters, and tags were also considered to gain better understanding.
-On the other hand, if the source code from Qualitas project mentioning about copying from Stack Overflow, the pair is classified into SQ.
+In several occasions, we used extra information such as questions' contents, name of posters, and tags to gain better understanding.
+On the other hand, if the source code from Qualitas project mentions about copying from Stack Overflow, the pair is classified into SQ.
 If there is an evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX.
@@
 
-To mitigate the human errors of the manual classification, the second author took the role of the validating investigator performing 10\% validation (363 pairs) of the clone pairs judged by the main investigator.
+To mitigate the human errors of the manual classification, the second author took the role of the validating investigator, performing a validation on 10\% (363 pairs) of the clone pairs judged by the main investigator.
 After the validation, the classifications from the two investigators were compared and 64 conflicts were found.
@@
 
-\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 110 online clone pairs with evidences of cloning from Qualitas projects to Stack Overflow.
-They include 3, 12, 86, and 9 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
+\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112 online clone pairs with evidences of cloning from Qualitas projects to Stack Overflow.
+They include 3, 14, 86, and 9 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
 Most of them have a statement in the Stack Overflow post saying that the code is ``copied'' or ``modified'' from a specific file or class in Qualitas.
@@
 
-\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find any clone pairs with an evidence of cloning from Stack Overflow to Qualitas projects.
+\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find any clone pairs with evidence of cloning from Stack Overflow to Qualitas projects.
 
@@
 
-This findings complement a study of clones between software projects~\cite{Svajlenko2014}.
+These findings complement a study of clones between software projects~\cite{Svajlenko2014}.
 We found that the code cloning can also happen among different sources on the Internet just like software projects.
@@
 Usually code clone detection is used to locate clone instances and update them to match with the originals~\cite{Bellon2007}.
-However, for online code clones, the clones are pervasive and more difficult to detect than software projects due to its large search space and a mix of natural and programming languages combined in the same post.
+However, for online code clones, the clones are pervasive and more difficult to detect than in regular software projects due to its large search space and a mix of natural and programming languages combined in the same post.
 Moreover, Stack Overflow is not a software.
@@
 To search for outdated online code clones, we focused on the 112 QS clone pairs that were cloned from Qualitas to Stack Overflow and compared them with their latest versions.
-We cloned the latest version of the Qualitas projects from their repositories on 26 September 2016.
+We downloaded the latest version of the Qualitas projects from their repositories on 26 September 2016.
 For each QS online clone pair, we use the clone from Qualitas a a proxy.
@@
 An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers.
-Although Stack Overflow has a voting mechanism that may mitigate this issue, the accepted answer is still attractive enough for naive developers who are ignorant to copy and reuse the code.
+Although Stack Overflow has a voting mechanism that may mitigate this issue, the accepted answer is still attractive enough for naive developers to copy and reuse the code.
 
@@
 60 pairs differ from their newest versions by modifications applied to variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures.
-4 pairs are dead snippets.
-They do not exist any more in the latest version.} %These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
+4 pairs are dead snippets.} %They do not exist any more in the latest version.} %These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
 Even worse, they might also introduce bugs or vulnerabilities into their software.
@@
 In our study, we reveal another possible situation of software licensing issues caused by code cloned ``to Stack Overflow''.
-We found with evidence that 112 pieces of code had been copied from Qualitas projects to Stack Overflow as examples.
+We found evidence that 112 pieces of code had been copied from Qualitas projects to Stack Overflow as examples.
 Their status of accepted answers increase their chances of being reused.
-Most of the Qualitas projects came with a software license (shown in \Cref{t:q_projects_license}).
-However, we found that the licensing information were frequently missing after the code were copied to Stack Overflow.
+Even though most of the Qualitas projects came with a software license (shown in \Cref{t:q_projects_license}), we found that the licensing information were frequently missing after the code was copied to Stack Overflow.
 The licensing terms on top of source code files are not copied because usually only a small part of the file was cloned.
@@
 
-\textbf{Incompatible license:} there are 359 clone pairs which do not contain licensing information after they are posted on Stack Overflow or having different license from their Qualitas clone counterparts.
+\textbf{Incompatible license:} there are 359 clone pairs which do not contain licensing information after they are posted on Stack Overflow or contain different license from their Qualitas clone counterparts.
 More than half (79) of QS clone pairs have their licensing terms removed or changed after posted on Stack Overflow.
@@
 We found that most of the EX clones have their licensing information stripped of after copying to Stack Overflow.
-These clones are instead covered the default CC BY-NC-SA 3.0 license of Stack Overflow which is strongly permissive.
-These used-to-be-licensed code are dangerous for being reused because they can implicitly conflicting with the reusing software's license.
+These clones are instead covered by the default CC BY-NC-SA 3.0 license of Stack Overflow which is strongly permissive.
+These used-to-be-licensed code are dangerous for being reused because they can implicitly conflict with the reused software's license.
 
@@
 We could not verify all the 315,786,118 clone pairs reported by the clone detection tools in this study.
-Nevertheless, we applied several mechanism to ensure the validity to the subset of clone pairs we classified.
+Nevertheless, we applied different mechanisms to ensure the validity to the subset of clone pairs we classified.
 First, we used the two widely-used clone detection tools, Simian and NiCad. We had tried three other clone detectors but could not add them to the study
@@
 Our seven patterns of online code cloning may not cover all possible online cloning patterns. However, instead of 
-defining the patterns beforehand, we resorted to extract them for the data sets. We derived them
+defining the patterns beforehand, we resorted to extract them from the data sets. We derived them
 from a manual investigation of 679 online clone pairs and adopted one pattern from the study by Kapser et al.~\cite{Kapser2003}.
@@
 Regarding the code snippets, we downloaded a full data dump and extracted Java accepted answers. Instead of analysing every post, we only focused on posts marked as accepted answers 
-since they are the most likely to being reused. This yields totally 144,075 snippets.
+since they are the most likely to being reused. This yields a total of 144,075 snippets.
 Our findings are limited to these restrictions.
@@
 Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}.
-Our study adopted on of the patterns into our online code cloning patterns.
+Our study adopted one of the patterns into our online code cloning patterns.
 
@@
 Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are more assured to be true clones than the ones reported by only a single tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
-There are studies that report sensitivities of the tools' configurations to the results~\cite{Wang2013,cr2016ssbse}.
-It has been reported that searching for an optimal configuration for every new data set is preferred.
+There are studies that report sensitivities of the tools' configurations to the results~\cite{Wang2013,cr2016ssbse} showing that searching for an optimal configuration for every new data set is preferred.
 
 \textbf{Software licensing} is crucial for open source and industrial software development.
-Di Penta et al.~study an evolution of software licensing in six FOSS and found that licensing statements change over time~\cite{DiPenta2010}.
+Di Penta et al.~\cite{DiPenta2010}~studied the evolution of software licensing in six FOSS and found that licensing statements change over time.
 German et al.~\cite{German2009} performed an empirical study of code siblings (code clones among different systems coming from the same source) and found that licensing conflicts can occur between the clone siblings.
-Later, German et al.~\cite{German2010} created Ninka, a tool to automate identification of software license from program source code.
+Later, German et al.~\cite{German2010} created Ninka, a tool to automate the identification of software license from program source code.
 We use Ninka to analyse software license from Stack Overflow snippets and Qualitas projects.
@@
 
-The work that is closely similar to us is a study by An et al.~\cite{An2017}.
-The authors investigated clones between 399 Android apps and Stack Overflow posts.
+The work that is closely similar to us is a study by An et al.~\cite{An2017} where the authors investigated clones between 399 Android apps and Stack Overflow posts.
 They found 1,226 code snippets which were reused from 68 Android apps.
@@
 We discovered 112 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
-By comparing the clones to their latest versions in the software, we found that 64 code snippets on Stack Overflow are outdated and harmful for reuse.
+By comparing the clones to their latest versions in the software, we found that 64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
+
+\section{Future Work}
+Since this study is limited to only Java language, we are interested in expanding the study further to other popular programming languages such as C, C++, Python, and Javascript on Stack Overflow.
+The similar study of outdated code and software licensing violation can be repeated.
+It is interesting to compare the findings among different programming languages.
+Moreover, other popular software project corpora (e.g.~GitHub) can also be included to increase generalisation of the findings.
+
+We are eager to tackle the issues of outdated and license-violating online code clones with an automated tool.
+The tool should incorporate a scalable clone detection method of locate similar code from programming Q\&A websites such as Stack Overflow and online code repositories like GitHub.
+It analyses a software project under development and reports clones that are copied from Stack Overflow.
+The reported clones have traces to their origins in open source projects or websites along with their freshness (fresh/outdated/dead) so that the developer of the project can be aware of changes made to the copied code snippets.
+Lastly, the license of the original source code is also reported so the developer can make an informed decision of whether he or she will incorporate that code snippet into their own project.
 
 \section{Conclusions}
-This paragraph will end the body of this sample document.
-Remember that you might still have Acknowledgments or
-Appendices; brief samples of these
-follow.  There is still the Bibliography to deal with; and
-we will make a disclaimer about that here: with the exception
-of the reference to the \LaTeX\ book, the citations in
-this paper are to articles which have nothing to
-do with the present subject and are used as
-examples only.
-%\end{document}  % This is where a 'short' article might terminate
-
-%ACKNOWLEDGMENTS are optional
-%\section{Acknowledgments}
-%This section is optional; it is a location for you
-%to acknowledge grants, funding, editing assistance and
-%what have you.  In the present case, for example, the
-%authors would like to thank Gerald Murray of ACM for
-%his help in codifying this \textit{Author's Guide}
-%and the \textbf{.cls} and \textbf{.tex} files that it describes.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\linewidth]{Sankey_proj}
-%	\caption{Relationships of 58 Stack Overflow clone pairs to their original projects. 55 are outdated and 3 are deleted (shown using (d) suffix).}
-%	\label{fig:sankey}
-%\end{figure}
+Online code clones are clones that have been copied to Q\&A websites such as Stack Overflow.
+They are similar to clones in software projects where they can be outdated and violating software license but are much harder to detect.
+We studied the online code clones between Stack Overflow and Qualitas projects, especially 3,632 clone pairs, manually in details.
+
+Although we deployed Bellon's clone agreement and multiple filters to reduce the number of clone candidates, we still found a large number of 51,926 online clone pairs reported by two clone detectors.
+We classify 31,946 clone pairs using our seven patterns of online code cloning.
+We discovered 112 clone pairs that have been copied, with evidence, from Qualitas projects to Stack Overflow (QS), 197 clone pairs that have been copied from external sources besides Qualitas to Stack Overflow (EX), and 359 clone pairs that are highly similar but without evidence of copying (UD).
+
+A manual investigation of the 112 QS clone pairs by comparing to their latest version (as of 26 September 2017) reveals that 64 of them are outdated.
+Moreover, the study of licensing conflicts of clones in QS, EX, and UD shows that most of the clones on Stack Overflow do not contain licensing statements while their clone counterparts in Qualitas projects or external sources do.
+
+This study is among, if not the first, to address the important issues of outdated and license-violating online code clones on programming Q\&A websites using a hybrid methodology of automatic code clone detection and a manual clone investigation.
 

### 2017-02-14 cloneoverflow-latex/boxplot.R

@@ -1,0 +1,16 @@
+size_stats <- read.csv("~/Documents/CloneOverflow/cloneoverflow-latex/clone_size_stats.csv")
+View(size_stats)
+mean(size_stats["SD",1:570])
+boxplot(size_stats,ylab="clone size",outline = FALSE)
+boxplot(size_stats,ylab="clone size",outline = TRUE)
+
+
+clone_ratio_stats <- read.csv("~/Documents/CloneOverflow/cloneoverflow-latex/clone_ratio_stats.csv")
+View(clone_ratio_stats)
+boxplot(clone_ratio_stats,ylab="clone ratio (%)",outline = FALSE)
+boxplot(clone_ratio_stats,ylab="clone ratio (%)",outline = TRUE)
+
+clone_frequency_stats <- read.csv("~/Documents/CloneOverflow/cloneoverflow-latex/clone_frequency_stats.csv")
+View(clone_frequency_stats)
+boxplot(clone_frequency_stats,ylab="clone pairs per snippet",outline = FALSE)
+boxplot(clone_frequency_stats,ylab="clone pairs per snippet",outline = TRUE)

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex

@@
 
-Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customization and Exact match~\cite{Kapser2003,Kapser2008}.
-Our study adopted one of the patterns into our online code cloning patterns.
+Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customisation and Exact match~\cite{Kapser2003,Kapser2008}.
+Our study adopted on of the patterns into our online code cloning patterns.
 

### 2017-02-14 cloneoverflow-latex/cloneoverflow.tex
Added the abstract (finally!)/resized the tables/shorten table captions. Still 14 pages though ...

@@
 \begin{abstract}
-	This paper provides a sample of a \LaTeX\ document which conforms,
-	somewhat loosely, to the formatting guidelines for
-	ACM SIG Proceedings\footnote{This is an abstract footnote}. 
+	We studied online code clones on the popular programming Q\&A website, Stack Overflow, and their issues on outdated code and software licensing violation.
+Online code clones are code fragments that are copied from software projects or online sources to Stack Overflow as examples.
+They can be discovered by using code clone detectors, yet they are inherently different from normal code clones in software projects in several aspects.
+Due to an absence of checking mechanism after the code has been copied to Stack Overflow, the online code clones may suffer from being outdated and violating the original software license.
+%Moreover, we also found that majority of online code clones do not contain the license of their originals.
+	We designed the experiment incorporating several state-of-the-art tools and techniques to automatically extract, prioritise, and filter the clones.
+As a result, we discovered 51,926 non-trivial online clone candidates between 144,075 Java code snippets on Stack Overflow and 111 Java open source projects in the curated Qualitas corpus.
+The manual study of the 3,632 online clone pairs revealed that 64 clones on Stack Overflow are outdated.
+Furthermore, we found 357 Stack Overflow code snippets that do not contain software license of their originals or have conflicting licenses.
+These snippets are questionable for reuse.
+Our study is among the first to address the problem of outdated and license-violating code snippets on Stack Overflow.
 \end{abstract}
-
-%
-% The code below should be generated by the tool at
-% http://dl.acm.org/ccs.cfm
-% Please copy and paste the code instead of the example below. 
-%
-%\begin{CCSXML}
-%<ccs2012>
-% <concept>
-%  <concept_id>10010520.10010553.10010562</concept_id>
-%  <concept_desc>Computer systems organization~Embedded systems</concept_desc>
-%  <concept_significance>500</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010575.10010755</concept_id>
-%  <concept_desc>Computer systems organization~Redundancy</concept_desc>
-%  <concept_significance>300</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10010520.10010553.10010554</concept_id>
-%  <concept_desc>Computer systems organization~Robotics</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-% <concept>
-%  <concept_id>10003033.10003083.10003095</concept_id>
-%  <concept_desc>Networks~Network reliability</concept_desc>
-%  <concept_significance>100</concept_significance>
-% </concept>
-%</ccs2012>  
-%\end{CCSXML}
 
@@
 	\begin{lstlisting}
-          /* Code in Stack Overflow #22315734 */                         /* WritableComparator.java (2016-09-26) */
+          /* Code in Stack Overflow post ID 22315734 */                  /* WritableComparator.java (2016-09-26) */
           public int compare (byte[] b1,int s1,int l1,                   public int compare(byte[] b1,int s1,int l1,
@@
 	\end{lstlisting}
-	\caption{A motivating example of the same code fragments, WritableComparator.java. The one on Stack Overflow post 22315734 is outdated when compared to its latest version in Hadoop code base}
+	\caption{A motivating example of the two code fragments of {\small\texttt{WritableComparator.java}}.
+The one on the Stack Overflow post 22315734 is outdated when compared to its latest version in {\small\texttt{hadoop}} code base}
 	\label{fig:before-after}
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{exp_framework_new}
+	\includegraphics[width=\linewidth]{exp_framework_new}
 	\caption{Experimental framework}
@@
 	\small
-	\begin{tabular}{l|p{7cm}}
-		\hline 
-		Tool & Parameters \\
-		\hline
-		$S_D$ &  threshold=6, ignoreStringCase, \newline ignoreCharacterCase, ignoreModifiers \\ 
-		\hline
-		$S_E$ & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, ignoreStrings, \newline ignoreCharacters, ignoreSubtypeNames, \newline balanceSquareBrackets  \\ 
-		\hline 
-		$N_D$ & Blocks, MinLine=10, MaxLine=1000, UPI=0.30 \\
-		\hline
-		$N_E$ & Blocks, MinLine=5, MaxLine=604, UPI=0.20, \newline blind renaming, literal abstraction \\ 
+	\begin{tabular}{p{0.7cm}|p{2.4cm}|p{3.5cm}}
+		\hline 
+		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
+		\hline
+		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, \newline ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
+		\hline 
+		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=1000 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming,\newline literal abstraction \\
 		\hline
@@
 	\centering
-	\caption{Statistics of clones found between Stack Overflow and Qualitas projects using Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations \FIXME{boxplots here?}}
+	\caption{Statistics of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
 	\label{tab:raw_stats}
@@
 	\includegraphics[width=\linewidth]{good-ok_pairs-crop}
-	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) in 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
+	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
 	\label{fig:good-ok-pairs}
@@
 	\centering
-	\caption{The number of disagreed online clone pair candidates before and after filtering.}
+	\caption{Disagreed clone pairs before and after filtering.}
 	\label{tab:online_clone_pairs}
@@
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\hline
-		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
-		\hline
-		\multicolumn{7}{l}{Filters*: \textit{L}=clone line $\geq 10$, \textit{S}=similarity $\geq 85\%$,}  \\
-		\multicolumn{7}{l}{\textit{R}=regular expressions, and \textit{G}=\textit{good}/\textit{ok} pairs.} \\
+%		\hline
+%		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
+		\hline
+		\multicolumn{7}{l}{*\textit{L}=line $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{R}=reg.~expressions, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
 	\end{tabular} %
@@
 	\centering
-	\caption{The number of online clones candidates for the classification}
+	\caption{No.~of online clones candidates for the classification}
 	\label{tab:online_clone_classification_results}
@@
 	\centering
-	\caption{Seven patterns of online code cloning}
+	\caption{The seven patterns of online code cloning}
 	\label{tab:classification_scheme}
@@
 	\centering
-	\caption{Classification results of agreed and disagreed clone pairs.}
+	\caption{Classifications of online clone pairs.}
 	\label{tab:classification_good_o}
@@
 	\end{lstlisting}
-	\caption{Outdated code snippet on Stack Overflow post 23520731. This code has been copied from \texttt{SchemaUpdate.java} and its latest version in hibernate code base contains heavy modifications.}
+	\caption{Outdated code snippet on Stack Overflow post 23520731.
+This code has been copied from {\small\texttt{SchemaUpdate.java}}.
+Its latest version in {\small\texttt{hibernate}} code base contains heavy modifications.}
 	\label{fig:hibernate_outdated_code}
@@
 	\includegraphics[width=\linewidth]{license_violation}
-	\caption{Summary of licensing conflicts in online code clones}
+	\caption{Summary of online clones' licensing conflicts}
 	\label{fig:license_violation}
@@
 		\end{minipage}
-	\caption{Direction of changes in online code clone license}
+	\caption{Direction of the changes in online code clone licenses}
 	\label{fig:sankey_license}
@@
 
-\textbf{Incompatible license:} there are 359 clone pairs which do not contain licensing information after they are posted on Stack Overflow or contain different license from their Qualitas clone counterparts.
+\textbf{Incompatible license:} there are 357 clone pairs which do not contain licensing information after they are posted on Stack Overflow or contain different license from their Qualitas clone counterparts.
 More than half (79) of QS clone pairs have their licensing terms removed or changed after posted on Stack Overflow.
@@
 
-\textbf{For RQ4, we found 359 code snippets on Stack Overflow that violate the license of their original software. Majority of them do not contain licensing statements after copied to Stack Overflow.}
+\textbf{For RQ4, we found 357 code snippets on Stack Overflow that violate the license of their original software. Majority of them do not contain licensing statements after copied to Stack Overflow.}
 
@@
 
-A manual investigation of the 112 QS clone pairs by comparing to their latest version (as of 26 September 2017) reveals that 64 of them are outdated.
-Moreover, the study of licensing conflicts of clones in QS, EX, and UD shows that most of the clones on Stack Overflow do not contain licensing statements while their clone counterparts in Qualitas projects or external sources do.
+A manual investigation of the 112 QS clone pairs by comparing to their latest version (as of 26 September 2016) reveals that 64 of them are outdated.
+Moreover, the study of licensing conflicts of clones in QS, EX, and UD shows that 357 code snippets on Stack Overflow do not contain licensing statements while their clone counterparts in Qualitas projects or external sources do.
 

### 2017-02-15 cloneoverflow-latex/cloneoverflow.tex
Updated throughout the paper according to Matheus’s comments. Ready for Jens to look at.

@@
 The answers frequently contain at least one code snippet as a solution to the question asked.
-The code snippet is usually not written directly on the Stack Overflow website but copied from another location.
+We found that the code snippets are usually not written directly on the Stack Overflow website but copied from another location.
 It can be copied and modified from a code snippet in the question, copied from an answerer's own code or from other locations including open source software (OSS) systems.
-The process of posting and answering questions on Stack Overflow, which involves copying and pasting source code, can be considered as code cloning.
+The process of posting and answering questions on Stack Overflow, which involves reusing of source code, can be considered as code cloning.
 
@@
 The benefits and drawbacks of clones are still controversial.
-Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others suggest that in some cases clones are not harmful or even beneficial~\cite{Saini2016,Kapser2006}.
-
-Code cloning can also have side effects such as violating software licenses and software vulnerabilities.
+Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others suggest that clones are not harmful and can even be beneficial~\cite{Saini2016,Kapser2006}.
+
+Code cloning can also have side effects such as violating software licenses and introducing software vulnerabilities.
 Carelessly cloning code from one project to another project with a different license may cause a software licensing violation~\cite{German2009}.
@@
 We call code snippets that are copied from software systems to online Q\&A websites (such as Stack Overflow), and vice versa as ``online code clones'' (sometimes only ``clones'' for brevity).
-There are four ways to create online code clones: (1) code is cloned from a software project to a Q\&A website as an example; (2) code is cloned from a Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; (3) code is transferred from one software project to another via a Q\&A website; and (4) code is cloned from an external source to both a software project and a Q\&A website.
-Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.
+There are four ways to create online code clones: (1) code is cloned from a software project to a Q\&A website as an example; (2) code is cloned from a Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; and (3) code is transferred from one software project to another via a Q\&A website; Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.
 Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.
@@
 The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class, but at this time extracted from the latest version (as of 26 September 2016) of {\small{\texttt{hadoop}}}.
-We can obviously see that they are highly similar except a line containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in the latest version after {\small{\verb|key2.readFields(buffer);|}}.
+We can obviously see that they are highly similar except a line containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in the latest version.
 The added line is intended for cleaning up the reference in the {\small{\verb|buffer|}} variable.
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 315,786,118 similar code snippet pairs followed by a manual classification of 3,632 candidate clone pairs between Java code snippets obtained from Stack Overflow's accepted answers and 111 Java open source projects from a curated Qualitas corpus~\cite{QualitasCorpus}.
+We used two clone detection tools to discover 315,786,118 similar code snippet pairs, followed by a manual classification of 3,632 candidate clone pairs between Java code snippets obtained from Stack Overflow's accepted answers and 111 Java open source projects from a curated Qualitas corpus~\cite{QualitasCorpus}.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~Investigating the problems of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 668 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate software licenses.
+\noindent\textbf{2.~An investigation of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 668 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate software licenses.
 In addition, 64 out of the 112 online code clones from Qualitas to Stack Overflow are outdated and questionable for being reused.
@@
 \vspace{0.5ex}%
-\noindent\textbf{3.~Online code clone oracle:} The 3,632 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://to.be.disclosed.after.review} and can be used as a clone oracle.
+\noindent\textbf{3.~An online code clone oracle:} The 3,632 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://to.be.disclosed.after.review} and can be used as a clone oracle.
 
@@
 \newline
-\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We investigated whether online code clones can be legally harmful to software reusing them.
+\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We investigated whether online code clones can be legally harmful to software developers reusing them.
 
@@
 We had contacted the creator of NiCad regarding the issues.
-They identified the issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
+They identified these issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
 As a result, we did not have NiCad clones from these projects in the agreed clone pairs.
@@
 Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with an evidence, in the opposite direction to QS.
-Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones between Qualitas and Stack Overflow but where we could not find any attribution of copying.
+Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones, between Qualitas and Stack Overflow but where we could not find any attribution of copying.
 %The UD clones are also unique enough to not be a boiler-plate code.
@@
 We searched for its latest version by the file name and located the cloned region in the file based on the method name.
-For Simian clones where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region.
+For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region.
 We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code.
@@
 
-\textbf{For RQ4, we found 357 code snippets on Stack Overflow that violate the license of their original software. Majority of them do not contain licensing statements after copied to Stack Overflow.}
+\textbf{For RQ4, we found 357 code snippets on Stack Overflow that violate the license of their original software.
+The majority of them do not contain licensing statements after copied to Stack Overflow.}
 
@@
 Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customisation and Exact match~\cite{Kapser2003,Kapser2008}.
-Our study adopted on of the patterns into our online code cloning patterns.
-
-\textbf{Clone agreement} is useful in when a clone oracle is absent.
+Our study adopted one of the patterns into our online code cloning patterns.
+
+\textbf{Clone agreement} is useful when a clone oracle is absent.
 Since clone detectors are different in their detection approaches, they may behave differently and report different clones even on the same data set.
@@
 Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are more assured to be true clones than the ones reported by only a single tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
-There are studies that report sensitivities of the tools' configurations to the results~\cite{Wang2013,cr2016ssbse} showing that searching for an optimal configuration for every new data set is preferred.
+There are studies that report sensitivities of the tools' configurations to the results~\cite{Wang2013,cr2016ssbse}, showing that searching for an optimal configuration for every new data set is preferred.
 

### 2017-02-17 cloneoverflow-latex/cloneoverflow.tex
Updated the stats

@@
 			\hline
-			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
+			Snippets & 1,086 & 1,531 & 1,392 & 12,991 \\
 			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
 %			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
-			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
+			Avg.~C$_{\textrm{\textit{size}}}$ & 11.92 & 11.93 & 12.51 & 10.94 \\
+			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
 			\hline
@@
 NiCad with the default configuration ($N_D$) reports clones in 1,392 Stack Overflow code snippets.
-NiCad with the EvaClone configuration ($N_E$) reports the largest number of 12,886 cloned snippets mainly due to its relaxed configurations.
+NiCad with the EvaClone configuration ($N_E$) reports the largest number of 12,991 cloned snippets mainly due to its relaxed configurations.
 In terms of the number of clone pairs, $S_D$ reports 67,570 clone pairs while $N_D$ reports 632,855 clone pairs.
@@
 On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average.
-The average clone size reported by $S_D$ is 7.72 lines which is bigger than $S_E$ (4.79 lines).
-Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 lines reported by $N_E$.
-We can see from the statistics that EvaClone tunes the tools to report smaller clones.
-The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
+The average clone size reported by $S_D$ is 11.92 lines which comparable to $S_E$ (11.93 lines).
+$N_D$ has an average clone size of 12.51 lines which is bigger than 10.94 lines reported by $N_E$.
+%We can see from the statistics that EvaClone tunes the tools to report smaller clones.
+The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\% accordingly.
 A quick manual check of Simian's clone report revealed that there were 11 problematic snippets.

### 2017-02-17 src/eu/giuswhite/beans/SimianLog.java
Updated code to compute stats.

@@ -27,10 +27,6 @@ public class SimianLog {
         boolean thereIsStackOverflowFile = false;
         boolean thereIsSrcFile = false;
         for (LogFragment logFragment : this.fragmentList) {
-//            if (logFragment.getFilePath().contains("19051537_0.java"))
-//                System.out.println("**** YES: 19051537_0.java ****");
-//            if (logFragment.getFilePath().contains("src/apache-ant-1.8.4/src/main/org/apache/tools/bzip2/CRC.java"))
-//                System.out.println("**** YES: " + logFragment.getFilePath() + " ****");
             if (logFragment.getFilePath().contains(CommonUtils.stackoverflow_path)) {
                 thereIsStackOverflowFile = true;
             } else if (logFragment.getFilePath().contains(CommonUtils.qualitas_path)) {
@@ -50,30 +46,33 @@ public class SimianLog {
                 '}';
     }
 
-    public static List<SimianStackoverflowFragment> getSimianLogStats(List<SimianLog> simianLogs){
+    public static List<SimianStackoverflowFragment> getSimianLogStats(List<SimianLog> simianLogs) {
         HashMap<String, SimianStackoverflowFragment> result = new HashMap<>();
         HashMap<String, Integer> projectFileMap = new HashMap<>();
         int projectFileId = 0;
 
         System.out.println("Reading from simian fragments ...");
         int count = 1;
-        for(SimianLog s : simianLogs){
+
+        for (SimianLog s : simianLogs) {
             System.out.println(count + "/" + simianLogs.size());
             count++;
-            for(LogFragment lF : s.fragmentList){
-                // System.out.println("Checking fragment: " + lF.filePath);
+
+            for (LogFragment lF : s.fragmentList) {
+
                 /* Check if it exists in the result list.*/
-                if(lF.isStackoverflowFragment){
-                    if (count == 2241)
-                        System.out.println(lF.getFilePath());
+                if (lF.isStackoverflowFragment) {
                     boolean exist = false;
                     SimianStackoverflowFragment simianStackoverflowFragment = new SimianStackoverflowFragment();
+
                     if (result.containsKey(lF.filePath)) {
-                        exist = true;
+                        // exist = true;
                         simianStackoverflowFragment = result.get(lF.filePath);
-                    }
-                    /* If it is not in the list, add it */
-                    if(!exist){
+                        // even it exists, still need to update clone lines anyway
+                        simianStackoverflowFragment.setCloneLines(lF.getStart(), lF.getEnd());
[…]

### 2017-02-17 src/eu/giuswhite/beans/SimianStackoverflowFragment.java

@@ -18,11 +18,13 @@ public class SimianStackoverflowFragment {
     public int numberOfTimeIsUsed;
     public HashMap<Integer, Boolean> projectsWhereIsUsed;
     public boolean[] cloneLines;
+    public int cloneLinesCount;
     public int SLOC;
 
     public SimianStackoverflowFragment(){
         this.numberOfTimeIsUsed = 0;
         this.projectsWhereIsUsed = new HashMap<>();
+        this.cloneLinesCount = 0;
     }
 
     public SimianStackoverflowFragment(String filePath){
@@ -37,8 +39,16 @@ public class SimianStackoverflowFragment {
     }
 
     public void setCloneLines(int start, int end) {
-        for (int i=start-1; i<end-1; i++)
+        for (int i = start - 1; i < end; i++)
             cloneLines[i] = true;
+    }
+
+    public void increaseCloneLinesCount(int size) {
+        this.cloneLinesCount += size;
+    }
+
+    public int getCloneLinesCount() {
+        return this.cloneLinesCount;
     }
 
     public int getCloneLines() {

### 2017-02-17 src/eu/giuswhite/utils/CommonUtils.java

@@ -5,7 +5,7 @@ package eu.giuswhite.utils;
  */
 public class CommonUtils {
     public static final String EXTRACTED_DATA_FOLDER_PATH = "";
-    public static final String PROJECT_FOLDER_PATH = "/Users/Chaiyong/IdeasProjects/StackAnalyzer";
+    public static final String PROJECT_FOLDER_PATH = "/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer";
     public static final boolean TEST_MODE = true;
     public static int STOP_PROCESS_FLAG = 10;
     public static final String OPEN_CODE_PATTERN = "<pre><code>";

### 2017-02-17 src/eu/giuswhite/utils/CsvFileWriter.java

@@ -72,9 +72,12 @@ public class CsvFileWriter {
                 System.out.print(".");
                 // skip if they're false clones generated from simian's bug
                 if (!CommonUtils.isError(fragment.fragmentName)) {
-                    listWriter.write(fragment.fragmentName, fragment.numberOfTimeIsUsed,
-                            fragment.projectsWhereIsUsed.size(), fragment.getSLOC(), fragment.getCloneLines(),
-                            ((double) fragment.getCloneLines()) / fragment.getSLOC());
+                    listWriter.write(fragment.fragmentName,
+                            fragment.numberOfTimeIsUsed,
+                            fragment.projectsWhereIsUsed.size(),
+                            fragment.getSLOC(),
+                            (double)fragment.getCloneLinesCount()/fragment.numberOfTimeIsUsed,
+                            (double) fragment.getCloneLines() / fragment.getSLOC());
                 }
             }
         } catch (IOException e) {

### 2017-02-17 cloneoverflow-latex/cloneoverflow.tex
Fixed the stats one last time.

--- 2017-02-15 cloneoverflow-latex/cloneoverflow.tex
@@
 %			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-			Avg.~C$_{\textrm{\textit{size}}}$ & 7.72 & 4.79 & 9.84 & 5.33 \\
-			Avg.~C$_{\textrm{\textit{\%}}}$ & 29\% & 28\% & 25\% & 21\% \\
+			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
+			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
 			\hline
@@
 On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average.
-The average clone size reported by $S_D$ is 7.72 lines which is bigger than $S_E$ (4.79 lines).
-Similarly, $N_D$ has an average clone size of 9.84 lines which is bigger than 5.33 lines reported by $N_E$.
+The average clone size reported by $S_D$ is 9.11 lines which is bigger than $S_E$ (5.95 lines).
+Similarly, $N_D$ has an average clone size of 10.85 lines which is bigger than 6.28 lines reported by $N_E$.
 We can see from the statistics that EvaClone tunes the tools to report smaller clones.
-The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 29\%, 28\%, 25\%, and 21\% accordingly.
+The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\% accordingly.
 A quick manual check of Simian's clone report revealed that there were 11 problematic snippets.

### 2017-02-17 cloneoverflow-latex/cloneoverflow.tex
Updated according to Jens’s comments (haven’t worked on RQ1 though).

@@
 
-\FIXME{Find the right location for this-->} Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
+%\FIXME{Find the right location for this-->} Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
 
@@
 While research has mostly focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation.
-
-To fill this gap, this paper makes the following  primary contributions:
+This paper makes the following  primary contributions:
 
@@
 The clone statistics obtained from running Simian and NiCad are presented in \Cref{tab:raw_stats}.
-Simian with the default configuration ($S_D$) report clones in 1,086 snippets, approximately 1\% of the 144,075 Stack Overflow snippets.
-Simian with the EvaClone configuration ($S_E$) report 1,531 snippets containing clones.
+Simian with the default configuration ($S_D$) reports clones in 1,086 snippets, approximately 1\% of the 144,075 Stack Overflow snippets.
+Simian with the EvaClone configuration ($S_E$) reports 1,531 snippets containing clones.
 NiCad with the default configuration ($N_D$) reports clones in 1,392 Stack Overflow code snippets.
@@
 We can see from the statistics that EvaClone tunes the tools to report smaller clones.
-The average ratio of Stack Overflow code snippets that are cloned according to $S_D$, $S_E$, $N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\% accordingly.
+For the cloned Stack Overflow snippets, the average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\%  respectively.
 A quick manual check of Simian's clone report revealed that there were 11 problematic snippets.
@@
 Hence, their clones were removed from further analyses.
+We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors.
+$N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and \texttt{spring}.
+We have contacted the creator of NiCad regarding the issues.
+They identified these issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
 
@@
 The total number of clone candidates is 32,039 pairs.
-We explain them in more details below.
+We explain them in more detail below.
 
@@
 %The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors.
-$N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and \texttt{spring}.
-We had contacted the creator of NiCad regarding the issues.
-They identified these issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
-As a result, we did not have NiCad clones from these projects in the agreed clone pairs.
+Due to NiCad's failures, we do not have NiCad clones from five Qualitas projects in the agreed clone pairs.
 Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.
@@
 %	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r|r|r}
-		\hline
-		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Total & Unique \\
-		\hline
-		\textit{good} & 18 & 26 & 10 & 2,267 & 2,321 & 2,308 \\
-		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 32,560 & 31,729  \\
+	\begin{tabular}{l|r|r|r|r|r}
+		\hline
+		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Unique \\
+		\hline
+		\textit{good} & 18 & 26 & 10 & 2,267 & 2,308 \\
+		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 31,729  \\
 		\hline
@@
 		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filters} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filters} \\ \cline{3-6}
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-6}
 		& & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
@@
 
-The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement from the other tool.
+The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with the other tool.
 The disagreement can be from a misalignment of clone lines or totally non-overlapping clones.
@@
 For the clone line filter, we raised the minimum clone size to 10 line since larger clones are more interesting, while smaller ones tend to be false clones~\cite{Saini2016}.
-Moreover, the study of uniqueness of source code by Gabel and Su~\cite{Gabel2010} suggests that source code are unique when they are larger than seven lines.
 Since the 10--line threshold is already the default configuration for NiCad, this filter is applied to Simian only (Simian's default configurations has a minimum clone size of 6 lines).~The regular expression filter removes boiler-plate clones of \verb|hashCode()| methods and getters/setters.
@@
 The last filter, good/ok pairs, removes the clone pairs that have already existed in the agreed clone sets.
+% Moreover, the study of uniqueness of source code by Gabel and Su~\cite{Gabel2010} suggests that source code are unique when they are larger than seven lines.
 
@@
 We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15).
-We tried varying the UPI from 70\% (default), 80\%, 85\% and 90\% and found that 85\% similarity provided the best balance in terms of the amount of reported clones and feasibility for manual investigation.
+We tried varying the UPI from 70\% (default -- 632,855 pairs), 80\% (25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that 85\% similarity provided the best balance in terms of the amount of reported clones and feasibility for manual investigation.
 Using this filter along with the regular expression and the good/ok pair filter, we reduced the size of $N_D$ clones to 88 pairs.
 
-%In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which helped classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs).
+%In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which  classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs).
 Finally, there are 3,502 pairs remaining which we manually classified them.
@@
 			\hline 
-			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)).
-			\\ 
-			\hline 
-			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q).
-			\\ 
-			\hline 
-			BP & Boiler-plate or IDE auto-generated
-			\\ 
-			\hline 
-			IN & Inheritance, interface implementation 
-			\\ 
+			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
+			\hline 
+			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
+			\hline 
+			BP & Boiler-plate or IDE auto-generated \\ 
+			\hline 
+			IN & Inheritance, interface implementation  \\ 
 			\hline 
@@
 Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating.
-\textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.}
 
@@
 We evaluated Kapser's cloning patterns and also observed the common cloning patterns from the 697 clone pairs.
-After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns .
-The seven patterns include QS, SQ, UN, ES, BP, IN, and FC as presented in \Cref{tab:classification_scheme}.
-Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that has evidence to be copied from Qualitas to Stack Overflow.
+\textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.} After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns .
+The seven patterns include QS, SQ, EX, UD, BP, IN, and AC as presented in \Cref{tab:classification_scheme}.
+Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have evidence to be copied from Qualitas to Stack Overflow.
 The evidence of copying can be found in comments in the Qualitas source code or in the Stack Overflow post's contents.
-Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with an evidence, in the opposite direction to QS.
-Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates exactly identical or highly similar clones, between Qualitas and Stack Overflow but where we could not find any attribution of copying.
+Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with evidence, in the opposite direction to QS.
+Pattern EX (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources.
+Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or highly similar clones between Qualitas and Stack Overflow but where we could not find any attribution of copying.
 %The UD clones are also unique enough to not be a boiler-plate code.
-Pattern ES (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources.
 Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components.
@@
 The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs.
-These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements or similar code after normalisation.
+These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements.
 
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{classification_process}
+	\includegraphics[width=\linewidth]{classification_process}
 	\caption{Online code clone classification process}
@@
 If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN.
-If the pair is not UD, IN, or AC, we start a detailed investigation.
+If the pair is not BP, IN, or AC, we start a detailed investigation.
 We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying.
-If an evidence of copying has been found from a Qualitas project, the pair is classified in QS.
+If evidence of copying has been found from a Qualitas project, the pair is classified in QS.
 In several occasions, we used extra information such as questions' contents, name of posters, and tags to gain better understanding.
-On the other hand, if the source code from Qualitas project mentions about copying from Stack Overflow, the pair is classified into SQ.
-If there is an evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX.
+On the other hand, if the source code from the Qualitas project mentions copying from Stack Overflow, the pair is classified into SQ.
+If there is evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX.
 Lastly, if there is no evidence of copying in any direction but the clone fragments are highly similar, we classify them into UD.
@@
 Please note that we ignored 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to their large number of clones and the very small average clone sizes of 4.79 and 5.33 lines (see \Cref{tab:raw_stats}).
-They had high possibilities to be trivial clones.
+They had a high probability to be trivial clones.
 
 Before performing manual classification, we used regular expressions to automatically classify {\small\texttt{equals()}} and the remaining getters/setters.
-As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us captured 28,314 clone pairs and classified them into pattern BP.
+As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us classified and captured 28,314 clone pairs into pattern BP.
 
@@
 By consulting the cloning patterns, the main investigator went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair.
-A relevant and useful observation was also recorded for each clone pair.
+%A relevant and useful observation was also recorded for each clone pair.
 
@@
 They include 3, 14, 86, and 9 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
-Most of them have a statement in the Stack Overflow post saying that the code is ``copied'' or ``modified'' from a specific file or class in Qualitas.
-The most cloned projects is {\small\texttt{hibernate}} and {\small\texttt{spring}} with 20 clone pairs, followed by {\small\texttt{eclipse}} (15 pairs), and {\small\texttt{hadoop}} (12 pairs).
+Most of them have a statement in the Stack Overflow post saying that the code is ``copied'' or ``modified'' from a specific file or class in a Qualitas project.
+The most cloned projects are {\small\texttt{hibernate}} and {\small\texttt{spring}} with 20 clone pairs, followed by {\small\texttt{eclipse}} (15 pairs), and {\small\texttt{hadoop}} (12 pairs).
 The clones are used as examples and are very similar to their original Qualitas code with limited modifications.
@@
 \textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find any clone pairs with evidence of cloning from Stack Overflow to Qualitas projects.
+
+\textbf{EX: External Sources.} We found 197 online clone pairs with evidences of cloning from external sources to Stack Overflow.
+They include 4, 41, 146, and 6 clone pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ respectively.
+
+These findings complement a study of clones between software projects~\cite{Svajlenko2014}.
+We found that the code cloning can also happen among different sources on the Internet just like software projects.
+There are 30 clone pairs that are originated from programming websites.
+For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html.
+Both the Stack Overflow and the {\small\texttt{compiere}} project source code contain an attribution to the original source.
+Another example is a code to generate graphical \textit{Perlin noise}.
+It is copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/.
+The code is used in Stack Overflow and {\small\texttt{aoi}} project with attribution.
+%The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
+There are other EX clone pairs are from third-party libraries such as {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and the {\small\texttt{bouncycastle}} cryptography project.
 
@@
 
-\textbf{EX: External Sources.} We found 197 online clone pairs with evidences of cloning from external sources to Stack Overflow.
-They include 4, 41, 146, and 6 clone pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ respectively.
-
-These findings complement a study of clones between software projects~\cite{Svajlenko2014}.
-We found that the code cloning can also happen among different sources on the Internet just like software projects.
-There are 30 clone pairs that are originated from programming websites.
-For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html.
-Both Stack Overflow and {\small\texttt{compiere}} project source code contain attribution to the original source.
-Another example is a code to generate graphical \textit{Perlin noise}.
-It is copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/.
-The code is used in Stack Overflow and {\small\texttt{aoi}} project with attribution.
-%The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
-There other EX clone pairs are from third-party libraries such as {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and the {\small\texttt{bouncycastle}} cryptography project.
-
 \textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs found in this study.
@@
 Usually code clone detection is used to locate clone instances and update them to match with the originals~\cite{Bellon2007}.
-However, for online code clones, the clones are pervasive and more difficult to detect than in regular software projects due to its large search space and a mix of natural and programming languages combined in the same post.
-Moreover, Stack Overflow is not a software.
+However, online code clones are more difficult to detect than in regular software projects due to its large search space and a mix of natural and programming languages combined in the same post.
+%Moreover, Stack Overflow is not a software.
 There is no test suite to run and check whether the validity of the code snippets.
@@
 We searched for its latest version by the file name and located the cloned region in the file based on the method name.
-For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region.
+%For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. 
 We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code.
 We also made sure that the changes did not come from the modifications made to the Stack Overflow snippets by the posters but from the updates in the projects themselves.
-When we found inconsistent lines between the two versions, we used {\small\texttt{git blame}} to see who modified those lines of code and noted down the timestamps and other details.
-
-\Cref{tab:stale_code_details} summarises the outdated online clones on Stack Overflow.
-The table shows information of the clones from both Stack Overflow and Qualitas side including the dates.
-We summarise the changes that make the clones outdated into three types, modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}), along with the date of change.
+When we found inconsistent lines between the two versions, we used {\small\texttt{git blame}} to see who modified those lines of code and the timestamps.
+
+ %Some of the clone pairs overlap with each other so we group them in the same row. 
 We discovered 64 outdated online clone pairs out of 112 pairs.
-Some of the clone pairs overlap with each other so we group them in the same row.
-{\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}.
-Besides the example of outdated code in the {\small{\texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} shown in \Cref{fig:before-after}, we also found a few outdated code which contained heavy modifications.
+As shown in \Cref{fig:outdated}, {\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}.
+Besides the example of outdated code in the {\small{\texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} shown in \Cref{fig:before-after}, we also found a few outdated code elements which contained heavy modifications.
 For example, the code snippet in Stack Overflow post 23520731 is a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}.
-The code have been heavily modified on 5 February 2016 (as shown in \Cref{fig:hibernate_outdated_code}).
-In the 64 outdate pairs, we found 5 of them to be ``dead'' snippets.
-These snippets cannot find their originals in the latest version of the projects.
+The code has been heavily modified on 5 February 2016.
+In the 64 outdate pairs, we found 5``dead'' snippets.
+These snippets cannot be located in the latest version of the projects.
 For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in {\small{\texttt{spring}}}, was deleted in the commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012, two years after it was posted.
 %The latest version of Spring does not contain the file anymore.
+\Cref{tab:stale_code_details} shows examples of the outdated online clones on Stack Overflow.
+The table displays information of the clones from both Stack Overflow and Qualitas side including the dates.
+We summarise the changes that make the clones outdated into three types, modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}), along with the date of change.
 
@@
 
-\begin{figure*}
-	\begin{lstlisting}
-          /* Code in Stack Overflow #23520731 */             /* SchemaUpdate.java (2016-09-26) */
-          public void execute (Target target) {              public void execute(EnumSet<TargetType> targetTypes, 
-            LOG.runningHbm2ddlSchemaUpdate();                                Metadata metadata, ServiceRegistry serviceRegistry) {
-            Connection connection = null;                      if ( targetTypes.isEmpty() ) {
-            Statement stmt = null;                               LOG.debug(""Skipping SchemaExport as no targets were specified"");
-            Writer outputFileWriter = null;                      return;
-            exceptions.clear();                                }
-            try {                                              exceptions.clear();
-              DatabaseMetadata meta;                           LOG.runningHbm2ddlSchemaUpdate();
-              ...                                              ...
-	\end{lstlisting}
-	\caption{Outdated code snippet on Stack Overflow post 23520731.
+%\begin{figure*}
+%	\begin{lstlisting}
+%          /* Code in Stack Overflow #23520731 */             /* SchemaUpdate.java (2016-09-26) */
+%          public void execute (Target target) {              public void execute(EnumSet<TargetType> targetTypes, 
+%            LOG.runningHbm2ddlSchemaUpdate();                                Metadata metadata, ServiceRegistry serviceRegistry) {
+%            Connection connection = null;                      if ( targetTypes.isEmpty() ) {
+%            Statement stmt = null;                               LOG.debug(""Skipping SchemaExport as no targets were specified"");
+%            Writer outputFileWriter = null;                      return;
+%            exceptions.clear();                                }
+%            try {                                              exceptions.clear();
+%              DatabaseMetadata meta;                           LOG.runningHbm2ddlSchemaUpdate();
+%              ...                                              ...
+%	\end{lstlisting}
+%	\caption{Outdated code snippet on Stack Overflow post 23520731.
 This code has been copied from {\small\texttt{SchemaUpdate.java}}.
 Its latest version in {\small\texttt{hibernate}} code base contains heavy modifications.}
-	\label{fig:hibernate_outdated_code}
-\end{figure*}
+%	\label{fig:hibernate_outdated_code}
+%\end{figure*}
 
@@
 	\includegraphics[width=\linewidth]{freshness}
-	\caption{Freshness of 110 QS online clone pairs}
+	\caption{Status of the 112 QS online clone pairs}
 	\label{fig:outdated}
@@
 
+%\begin{table*}
+%	\centering
+%	\caption{Examples of the 6 outdated QS online clones. Outdated clones are caused by modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}).}
+%	\label{tab:stale_code_details}
+%	\small
+%	\resizebox{2\columnwidth}{!}{%
+%	\begin{tabular}{r|l|l|l|l|p{5.2cm}|r|r|l|c|l}
+%		\hline 
+%		\multirow{2}{*}{No.} & \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ \cline{2-11}
+%		& Post & Date & Project & Ver. & File & Start & End & Date & Type & Date \\
+%		\hline
+%			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
+%			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
+%			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
+%			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
+%			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{S} & 1-Mar-11 \\
+%			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{S} & 5-Jun-13 \\
+%			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{S} & 21-Jun-13 \\
+%			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
+%			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{S} & 4-Feb-13 \\
+%			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
+%			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
+%			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{S} & 25-Jun-12 \\
+%			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
+%			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
+%			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{S} & 26-Apr-13 \\
+%			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{S} & 23-Apr-13 \\
+%			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
+%			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{D} & 11-Mar-11 \\
+%			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{S} & 11-May-16 \\
+%			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{S} & 12-Apr-15 \\
+%			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{S} & 4-Jun-15 \\ 
+%			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{S} & 17-Apr-08 \\
+%			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
+%			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{S} & 16-Jan-16 \\
+%			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{S} & 29-Jun-07 \\
+%			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{S} & 2-Jun-08 \\
+%			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{S} & 22-Nov-13 \\
+%			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{R} & 13-Apr-14 \\
+%			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{S} & 13-Apr-10 \\
+%			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{S} & 29-Nov-15 \\
+%			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{S} & 12-May-15 \\
+%			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{S} & 25-Jun-16 \\
+%			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{S} & 25-May-14 \\
+%			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
+%			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{S} & 28-Oct-14 \\
+%			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{S} & 21-Nov-13 \\
+%			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
+%			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
+%			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{R} & 12-Aug-16 \\
+%			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{S} & 21-May-12 \\
+%			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{S} & 19-Mar-13 \\
+%			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{S} & 9-May-15 \\
+%			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{S} & 28-Aug-12 \\
+%			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 18-Dec-08 \\
+%			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
+%			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
+%			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerException\newline Resolver.java & 224 & 233 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
+%			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{S} & 8-Aug-11 \\
+%			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
+%			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{S} & 15-Aug-10 \\
+%			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{S} & 18-Oct-13 \\
+%			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{S} & 28-Oct-13 \\
+%			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{S} & 15-Jun-15 \\
+%			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
+%			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
+%			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{S} & 25-Sep-14 \\
+%			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{S} & 12-Sep-12 \\
+%			\hline
+%	\end{tabular} %
+%}
+%\end{table*}
+
 \begin{table*}
 	\centering
-	\caption{64 QS outdated online clone pairs. Outdated clones are caused by modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}).}
+	\caption{Examples of the outdated QS online clones}
 	\label{tab:stale_code_details}
@@
 	\resizebox{2\columnwidth}{!}{%
-	\begin{tabular}{r|l|l|l|l|p{5.2cm}|r|r|l|c|l}
-		\hline 
-		\multirow{2}{*}{No.} & \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ \cline{2-11}
-		& Post & Date & Project & Ver. & File & Start & End & Date & Type & Date \\
-		\hline
-			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
-			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
-			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
-			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
-			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{S} & 1-Mar-11 \\
-			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{S} & 5-Jun-13 \\
-			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{S} & 21-Jun-13 \\
-			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
-			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{S} & 4-Feb-13 \\
-			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
-			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
-			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{S} & 25-Jun-12 \\
-			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
-			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
-			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{S} & 26-Apr-13 \\
-			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{S} & 23-Apr-13 \\
-			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
-			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{D} & 11-Mar-11 \\
-			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{S} & 11-May-16 \\
-			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{S} & 12-Apr-15 \\
-			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{S} & 4-Jun-15 \\ 
-			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{S} & 17-Apr-08 \\
-			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
-			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{S} & 16-Jan-16 \\
-			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{S} & 29-Jun-07 \\
-			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{S} & 2-Jun-08 \\
-			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{S} & 22-Nov-13 \\
-			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{R} & 13-Apr-14 \\
-			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{S} & 13-Apr-10 \\
-			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{S} & 29-Nov-15 \\
-			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{S} & 12-May-15 \\
-			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{S} & 25-Jun-16 \\
-			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{S} & 25-May-14 \\
-			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
-			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{S} & 28-Oct-14 \\
-			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{S} & 21-Nov-13 \\
-			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
-			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
-			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{R} & 12-Aug-16 \\
-			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{S} & 21-May-12 \\
-			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{S} & 19-Mar-13 \\
-			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{S} & 9-May-15 \\
-			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{S} & 28-Aug-12 \\
-			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 18-Dec-08 \\
-			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
-			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
-			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerException\newline Resolver.java & 224 & 233 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
-			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{S} & 8-Aug-11 \\
-			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
-			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{S} & 15-Aug-10 \\
-			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{S} & 18-Oct-13 \\
-			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{S} & 28-Oct-13 \\
-			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{S} & 15-Jun-15 \\
-			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
-			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
-			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{S} & 25-Sep-14 \\
-			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{S} & 12-Sep-12 \\
-			\hline
+		\begin{tabular}{l|l|l|l|p{4.7cm}|r|r|l|c|l}
+		 \hline
+		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
+		 \hline
+		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
+		 \hline
+		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
+		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
+		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
+		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
+		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
+		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
+		 \hline 
+		 \multicolumn{10}{l}{{\footnotesize * \textit{S}=modified/added/deleted statements, \textit{D}=file deletion,  \textit{R}=method rewriting}}
 		\end{tabular} %
@@
 %It is an emerging area that software engineering research community is paying attention to. For example, 
-One can run into a licensing issue if they integrate third-party source code into their software without checking.
+One can run into a licensing issue if one integrates third-party source code into their software without checking.
 A study by An et al.~\cite{An2017} reports 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code snippets.
@@
 
-\begin{table}
-	\centering
-	\caption{Licenses of online clones (file-level) from Qualitas projects}
-	\label{t:q_projects_license}
-	%	\resizebox{\columnwidth}{!}{%
-	\small
-	\begin{tabular}{l|l|r|r|r}
-		\hline 
-		Project & License & QS & UD & Total \\
-		\hline
-		netbeans &  CDDL/GPLv2 &  & 57 & 57 \\
-		&  No license &  & 8 & 8 \\
-		&  spdxBSD3 &  & 6 & 6 \\
-		&  MPLv1.1 &  & 1 & 1 \\
-		&  Unknown &  & 1 & 1 \\
-		\hline
-		jung2 &  BSD3 & 2 & 27 & 29 \\
-		\hline
-		eclipse-SDK & EPLv1 & 6 & 11 & 17 \\
-		& CDDL/GPLv2 & 1 & 1 & 2 \\
-		&  Apache-2 &  & 1 & 1 \\
-		& No license & 1 &  & 1 \\
-		& Unknown &  & 1 & 1 \\
-		\hline
-		hibernate & LesserGPLv2.1+ & 18 & 4 & 22 \\
-		\hline
-		spring & Apache-2 & 18 & 2 & 20 \\
-		\hline
-		vuze & GPLv2 &  & 11 & 11 \\
-		\hline
-		jstock & GPLv2+ &  & 9 & 9 \\
-		& Unknown &  & 1 & 1 \\
-		\hline
-		tomcat & Apache-2 & 5 & 5 & 10 \\
-		\hline
-		hadoop & Apache-2 & 8 &  & 8 \\
-		& No license & 1 &  & 1 \\
-		\hline
-		jfreechart & LesserGPLv2.1+ & 3 & 5 & 8 \\
-		\hline
-	\end{tabular} %
-	%	}
-\end{table}
+%\begin{table}
+%	\centering
+%	\caption{Licenses of online clones (file-level) from Qualitas projects}
+%	\label{t:q_projects_license}
+%	%	\resizebox{\columnwidth}{!}{%
+%	\small
+%	\begin{tabular}{l|l|r|r|r}
+%		\hline 
+%		Project & License & QS & UD & Total \\
+%		\hline
+%		netbeans &  CDDL/GPLv2 &  & 57 & 57 \\
+%		&  No license &  & 8 & 8 \\
+%		&  spdxBSD3 &  & 6 & 6 \\
+%		&  MPLv1.1 &  & 1 & 1 \\
+%		&  Unknown &  & 1 & 1 \\
+%		\hline
+%		jung2 &  BSD3 & 2 & 27 & 29 \\
+%		\hline
+%		eclipse-SDK & EPLv1 & 6 & 11 & 17 \\
+%		& CDDL/GPLv2 & 1 & 1 & 2 \\
+%		&  Apache-2 &  & 1 & 1 \\
+%		& No license & 1 &  & 1 \\
+%		& Unknown &  & 1 & 1 \\
+%		\hline
+%		hibernate & LesserGPLv2.1+ & 18 & 4 & 22 \\
+%		\hline
+%		spring & Apache-2 & 18 & 2 & 20 \\
+%		\hline
+%		vuze & GPLv2 &  & 11 & 11 \\
+%		\hline
+%		jstock & GPLv2+ &  & 9 & 9 \\
+%		& Unknown &  & 1 & 1 \\
+%		\hline
+%		tomcat & Apache-2 & 5 & 5 & 10 \\
+%		\hline
+%		hadoop & Apache-2 & 8 &  & 8 \\
+%		& No license & 1 &  & 1 \\
+%		\hline
+%		jfreechart & LesserGPLv2.1+ & 3 & 5 & 8 \\
+%		\hline
+%	\end{tabular} %
+%	%	}
+%\end{table}
 
@@
 	\small
-%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|l|l|r|r|r}
-		\hline
-		Type & Stack Overflow & Qualitas & QS & UD & EX \\
-		\hline
-		No license & No license & No license &  5 & 21 & 4 \\
+	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|p{2cm}|l|r|r|r}
+		\hline
+		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & UD & EX \\
+%		\hline
+%		No license & No license & No license &  5 & 21 & 4 \\
 		\hline
@@
 		& MIT-like & MIT-like & 0 & 0 & 1 \\
-		& No license & CC-NC-SA &  0 & 0 & 5 \\
+		& No license & CC BY-NC-SA &  0 & 0 & 5 \\
+		& No license & No license &  5 & 21 & 4 \\
 		\hline
@@
 	\end{tabular} %
-%}
+}
 \end{table}
 
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{license_violation}
-	\caption{Summary of online clones' licensing conflicts}
-	\label{fig:license_violation}
-\end{figure}
-
-\begin{figure*}
-		\centering
-		\begin{minipage}{.4\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{sankey_license_qs}
-			\caption*{(A) QS clones}
-		\end{minipage}%
-		\hspace{5ex}
-		\begin{minipage}{0.4\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{sankey_license_ex}
-			\caption*{(B) EX clones}
-		\end{minipage}
-	\caption{Direction of the changes in online code clone licenses}
-	\label{fig:sankey_license}
-\end{figure*}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=\linewidth]{license_violation}
+%	\caption{Summary of online clones' licensing conflicts}
+%	\label{fig:license_violation}
+%\end{figure}
+
+%\begin{figure*}
+%		\centering
+%		\begin{minipage}{.4\textwidth}
+%			\centering
+%			\includegraphics[width=\linewidth]{sankey_license_qs}
+%			\caption*{(A) QS clones}
+%		\end{minipage}%
+%		\hspace{5ex}
+%		\begin{minipage}{0.4\textwidth}
+%			\centering
+%			\includegraphics[width=\linewidth]{sankey_license_ex}
+%			\caption*{(B) EX clones}
+%		\end{minipage}
+%	\caption{Direction of the changes in online code clone licenses}
+%	\label{fig:sankey_license}
+%\end{figure*}
 
@@
 Since Ninka works at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of the clone pairs (duplicates were ignored).
-For the ones that could not be automatically identified by Ninka and has been reported as {\small\texttt{SeeFile}} or {\small\texttt{Unknown}}, we looked at them manually and updated if any license was found.
+For the ones that could not be automatically identified by Ninka and have been reported as {\small\texttt{SeeFile}} or {\small\texttt{Unknown}}, we looked at them manually and updated if any license was found.
 The table shows the license mapping of Stack Overflow snippets and Qualitas source code.
 The results are reported separately for the QS, UD, and EX set.
-In overall, we can see that most of the Stack Overflow snippets do not contain licensing terms while their clone counterparts in Qualitas project do.
-
-\textbf{No license or compatible license:} There are 31 clone pairs which do not have license on both sides and 8 pairs which have compatible licenses such as Apache license v.2; Eclipse Public License v.1 (EPLv1); or a pair of No license vs.~Creative Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC BY-NC-SA 3.0).
+In overall, we can see that most of the Stack Overflow snippets do not contain licensing terms while their clone counterparts in Qualitas projects do.
+
+\textbf{Compatible license:} There are 37 pairs which have compatible licenses such as Apache license v.2; Eclipse Public License v.1 (EPLv1); or a pair of No license vs.~Creative Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC BY-NC-SA 3.0).
 These clones are safe for being reused.
@@
 Similarly, the license statement was removed from Stack Overflow snippets. 
-
-\Cref{fig:sankey_license} shows the direction of changes in online code clone license.
+%
+%\Cref{fig:sankey_license} shows the direction of changes in online code clone license.
 The direction of the change is from left to right.
@@
 Nevertheless, we applied different mechanisms to ensure the validity to the subset of clone pairs we classified.
-First, we used the two widely-used clone detection tools, Simian and NiCad. We had tried three other clone detectors but could not add them to the study
+First, we used two, instead of one, widely-used clone detection tools, Simian and NiCad. 
+We had tried three other clone detectors but could not add them to the study
 due to their scalability issue and susceptibility to incomplete code snippets.
@@
 The 3,632 clone pairs classified manually by the first author are subject to manual judgement and human errors. 
-Although we had tried our best to be careful on searching for evidence and classifying the clones, some errors
+Although we have tried our best to be careful on searching for evidence and classifying the clones, some errors
 may still exist. We mitigated this problem by having the second author to validate the classifications with random samplings.
@@
 Our findings are limited to these restrictions.
-They may not be generalised to all programming languages and all the answers on Stack Overflow.
+They may not be generalised to all programming languages and all answers on Stack Overflow.
 On the other hand, we chose the curated Qualitas corpus for Java open source projects containing 111 projects \cite{QualitasCorpus}.
@@
 
-Lastly, two clone detection tools, Simian and NiCad, are chosen for this study.
+%Lastly, two clone detection tools, Simian and NiCad, are chosen for this study.
 We have not tried all the tools available and they might not be complete representatives of all available clone detection tools.
@@
 The code snippets on Stack Overflow are mostly examples or solutions to programming problems.
-Hence, several code search systems use a whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
+Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
 Furthermore, Treude et al.~\cite{Treude2016}~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation.
@@
 Instead of Android apps, we investigated clones between Stack Overflow and 111 open source projects.
-Our results confirm their findings that there are clones from software projects to Stack Overflow with potential licensing violations.
-In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,632 clone pairs.
+Their results are similar to our findings that there are clones from software projects to Stack Overflow with potential licensing violations.
+%In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,632 clone pairs.
 We discovered 112 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
@@
 
-\section{Future Work}
-Since this study is limited to only Java language, we are interested in expanding the study further to other popular programming languages such as C, C++, Python, and Javascript on Stack Overflow.
+%\section{Future Work}
+%Since this study is limited to only Java language, we are interested in expanding the study further to other popular programming languages such as C, C++, Python, and Javascript on Stack Overflow.
 The similar study of outdated code and software licensing violation can be repeated.
@@
 Moreover, other popular software project corpora (e.g.~GitHub) can also be included to increase generalisation of the findings.
-
-We are eager to tackle the issues of outdated and license-violating online code clones with an automated tool.
+%
+%We are eager to tackle the issues of outdated and license-violating online code clones with an automated tool.
 The tool should incorporate a scalable clone detection method of locate similar code from programming Q\&A websites such as Stack Overflow and online code repositories like GitHub.

### 2017-02-17 cloneoverflow-latex/freshness.m

@@ -3,8 +3,8 @@ y = [13	6 1;
 10	5	0;
 5	7	0;
 2	5	0;
+0	6	0;
 5	0	0;
-0	4	0;
 0	4	0;
 0	3	0;
 1	2	0;
@@ -27,7 +27,7 @@ end
 
 xticks([1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19])
 xticklabels({'hibernate', 'spring', 'eclipse-SDK', 'hadoop', 'tomcat', ...
-    'log4j', 'jfreechart', 'junit', 'jgraph', 'jung2', 'poi', 'struts2', ... 
+    'junit', 'log4j', 'jfreechart', 'jgraph', 'jung2', 'poi', 'struts2', ... 
     'weka', 'aspectj', 'jasperreports', 'antlr', 'ant', 'itext', 'jgrapht'})
 %xlabel('Project','FontSize',15)
 ylabel('Clone pair','FontSize',15)

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
Added new stats for RQ1 and histograms.

@@
 	We designed the experiment incorporating several state-of-the-art tools and techniques to automatically extract, prioritise, and filter the clones.
-As a result, we discovered 51,926 non-trivial online clone candidates between 144,075 Java code snippets on Stack Overflow and 111 Java open source projects in the curated Qualitas corpus.
+As a result, we discovered 51,926 non-trivial online clone candidates between 144,064 Java code snippets on Stack Overflow and 111 Java open source projects in the curated Qualitas corpus.
 The manual study of the 3,632 online clone pairs revealed that 64 clones on Stack Overflow are outdated.
@@
 To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}.
-We processed two datasets, 144,075 code snippets from Java accept answers on Stack Overflow and 111 open source projects from Qualitas corpus.
+We processed two datasets, 144,064 code snippets from Java accept answers on Stack Overflow and 111 open source projects from Qualitas corpus.
 Java code snippets were extracted from Stack Overflow posts.
@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We obtained 144,075 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
+We obtained 144,064 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
 
@@
 		\hline
-		Stack Overflow & 144,075 & 2,347,269 \\ 
+		Stack Overflow & 144,064 & 2,346,267 \\ 
 		\hline 
@@
 	\small
-%	\resizebox{\columnwidth}{!}{%
+	\resizebox{\columnwidth}{!}{%
 		\begin{tabular}{l|r|r|r|r}
@@
 			\hline
-			Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
+			Stack Overflow Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
+			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
 			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
@@
 		\end{tabular} %
-%	}
+	}
 \end{table}
 
+\begin{figure*}
+		\centering
+		\begin{minipage}{.4\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{hist_sd}
+			\caption*{$S_D$ clones}
+		\end{minipage}%
+		\hspace{5ex}
+		\begin{minipage}{0.4\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{hist_nd}
+			\caption*{$N_D$ clones}
+		\end{minipage}
+		\\
+		\begin{minipage}{.4\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{hist_se}
+			\caption*{$S_E$ clones}
+		\end{minipage}%
+		\hspace{5ex}
+		\begin{minipage}{0.4\textwidth}
+			\centering
+			\includegraphics[width=\linewidth]{hist_ne}
+			\caption*{$N_E$ clones}
+		\end{minipage}
+	\caption{Distribution of online clones between Stack Overflow snippets and Qualitas projects}
+	\label{fig:histogram}
+\end{figure*}
+
 The clone statistics obtained from running Simian and NiCad are presented in \Cref{tab:raw_stats}.
-Simian with the default configuration ($S_D$) reports clones in 1,086 snippets, approximately 1\% of the 144,075 Stack Overflow snippets.
+Simian with the default configuration ($S_D$) reports clones in 1,086 snippets, approximately 1\% of the 144,064 Stack Overflow snippets.
 Simian with the EvaClone configuration ($S_E$) reports 1,531 snippets containing clones.
@@
 For the cloned Stack Overflow snippets, the average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\%  respectively.
-A quick manual check of Simian's clone report revealed that there were 11 problematic snippets.
+%A quick manual check of Simian's clone report revealed that there were 11 problematic snippets.
 These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
@@
 Regarding the code snippets, we downloaded a full data dump and extracted Java accepted answers. Instead of analysing every post, we only focused on posts marked as accepted answers 
-since they are the most likely to being reused. This yields a total of 144,075 snippets.
+since they are the most likely to being reused. This yields a total of 144,064 snippets.
 Our findings are limited to these restrictions.

### 2017-02-18 cloneoverflow-latex/q_histogram.m

@@ -1,0 +1,112 @@
+nd = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_df_130901_1234_fixedclonelines/qualitas_projects.csv', 1, 1);
+sd = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_simian_df_130901_1234_fixedclonelines/qualitas_projects.csv', 1, 1);
+ne = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_fse13_130901_1234_fixedclonelines/qualitas_projects.csv', 1, 1);
+se = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_simian_fse13_130901_1234_fixedclonelines/qualitas_projects.csv', 1, 1);
+
+so_sd = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_simian_df_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
+so_sd_count = so_sd(:,1);
+so_nd = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_df_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
+so_nd_count = so_nd(:,1);
+
+so_se = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_simian_fse13_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
+so_se_count = so_se(:,1);
+so_ne = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_fse13_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
+so_ne_count = so_ne(:,1);
+
+% subplot(1,2,1)
+% sosd_hist=histogram(so_sd_count,'NumBins', 60)
+% ylabel('No. of snippets','FontSize',16)
+% xlabel('No. of clone pairs','FontSize',16)
+% set(gca,'FontSize',16);
+% dim = [.19 .6 .3 .3];
+% str = 'NumBins=60, BinWidth=23';
+% annotation('textbox',dim,'String',str,'FitBoxToText','on','FontSize',15,'LineStyle','none');
+% 
+% subplot(1,2,2)
+% sdhist=histogram(sd,'NumBins', 60)
[…]

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
Updated the text in RQ1. Ready for Jens to look at.

@@
 \newline
-\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorised online clones into seven categories according to our online code cloning pattern scheme.
+\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorised online clones into seven categories according to our online code cloning patterns.
 This gave us more insights to why online code clones are created.
@@
 		\end{minipage}
-	\caption{Distribution of online clones between Stack Overflow snippets and Qualitas projects}
+	\caption{\FIXME{Useful?}~Distribution of online clones between Stack Overflow snippets and Qualitas projects}
 	\label{fig:histogram}
@@
 The clone statistics obtained from running Simian and NiCad are presented in \Cref{tab:raw_stats}.
-Simian with the default configuration ($S_D$) reports clones in 1,086 snippets, approximately 1\% of the 144,064 Stack Overflow snippets.
-Simian with the EvaClone configuration ($S_E$) reports 1,531 snippets containing clones.
-NiCad with the default configuration ($N_D$) reports clones in 1,392 Stack Overflow code snippets.
+Simian with the default configuration ($S_D$) reports clones in 1,086 snippets, approximately 1\% of the 144,064 Stack Overflow snippets, associated with 92 Qualitas projects.
+Simian with the EvaClone configuration ($S_E$) reports 1,531 snippets containing clones associated with 111 Qualitas projects.
+NiCad with the default configuration ($N_D$) reports clones between 1,392 Stack Overflow code snippets and 82 Qualitas projects.
 NiCad with the EvaClone configuration ($N_E$) reports the largest number of 12,886 cloned snippets mainly due to its relaxed configurations.
+The $N_E$ snippets are associate with 88 Qualitas projects.
+We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors.
+$N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and {\small\texttt{spring}}.
+We have contacted the creator of NiCad regarding the issues.
+They identified these issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
+\Cref{fig:histogram} illustrates the distribution of online code clones reported by $S_D$, $N_D$, $S_E$ and $N_E$ respectively.
+We can see that the distribution is right skewed.
+There are only a few Stack Overflow snippets and Qualitas projects that are outliers containing a larger number of clones compared to the others.
+
 In terms of the number of clone pairs, $S_D$ reports 67,570 clone pairs while $N_D$ reports 632,855 clone pairs.
@@
 Hence, their clones were removed from further analyses.
-We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors.
-$N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and \texttt{spring}.
-We have contacted the creator of NiCad regarding the issues.
-They identified these issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
+
+\textbf{To answer RQ1, with the four configurations of Simian and NiCad, we found online code clones in 1,086 ($S_D$), 1,531 ($S_E$), 1,392 ($N_D$) and 12,886 ($N_E$) Stack Overflow code snippets.
+They are associated with 92, 111, 82 and 88 Qualitas projects respectively.}
+
+\subsection{RQ2: Patterns of Online Code Cloning}
+
+We rely on a manual study to qualitatively investigate the patterns of online code cloning.
+To achieve this, we select a subset of the agreed clones using Bellon's criteria and a subset of the disagreed clones using clone filtering.
+We explain them in more detail below.
+
+\subsubsection{Agreed clone pairs}
 
@@
 The total number of clone candidates is 32,039 pairs.
-We explain them in more detail below.
-
-\subsubsection{Agreed clone pairs}
-
 Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria, and therefore are selected for manual classification.
@@
 
-\textbf{To answer RQ1, we found 51,926 clone candidates between Qualitas projects and Stack Overflow code snippets.
-They are 2,308 \textit{good}, 32,729 \textit{ok}, 17,801 $S_D$, and 88 $N_D$ pairs respectively.} %After classification, we found 668 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}
-
-\subsection{RQ2: Patterns of Online Code Cloning}
+%After classification, we found 668 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}
 
@@
 \end{table}
+
+\subsubsection{The Seven Patterns of Online Code Cloning}
 

### 2017-02-18 cloneoverflow-latex/q_histogram.m

@@ -13,58 +13,58 @@ so_se_count = so_se(:,1);
 so_ne = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_fse13_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
 so_ne_count = so_ne(:,1);
 
-% subplot(1,2,1)
-% sosd_hist=histogram(so_sd_count,'NumBins', 60)
-% ylabel('No. of snippets','FontSize',16)
-% xlabel('No. of clone pairs','FontSize',16)
-% set(gca,'FontSize',16);
-% dim = [.19 .6 .3 .3];
-% str = 'NumBins=60, BinWidth=23';
-% annotation('textbox',dim,'String',str,'FitBoxToText','on','FontSize',15,'LineStyle','none');
-% 
-% subplot(1,2,2)
-% sdhist=histogram(sd,'NumBins', 60)
-% ylabel('No. of projects','FontSize',16)
-% xlabel('No. of clone pairs','FontSize',16)
-% set(gca,'FontSize',16);
-% dim = [.63 .6 .3 .3];
-% str = 'NumBins=60, BinWidth=266';
-% annotation('textbox',dim,'String',str,'FitBoxToText','on','FontSize',15,'LineStyle','none');
-% 
-% h=gcf;
-% set(h,'PaperPositionMode','auto');         
-% set(h,'PaperOrientation','landscape');
-% set(h,'Position',[50 50 800 300]);
-% print('hist_sd','-dpdf','-bestfit')
-
 subplot(1,2,1)
-sond_hist=histogram(so_nd_count,'NumBins',60)
+sosd_hist=histogram(so_sd_count,'NumBins', 60)
 ylabel('No. of snippets','FontSize',16)
-xlabel('No. of clone pairs','FontSize',16)
+xlabel('SO clone pairs','FontSize',16)
 set(gca,'FontSize',16);
 dim = [.19 .6 .3 .3];
-str = 'NumBins=60, BinWidth=110';
+str = 'NumBins=60, BinWidth=23';
 annotation('textbox',dim,'String',str,'FitBoxToText','on','FontSize',15,'LineStyle','none');
 
 subplot(1,2,2)
-ndhist=histogram(nd,'NumBins', 60)
+sdhist=histogram(sd,'NumBins', 60)
 ylabel('No. of projects','FontSize',16)
[…]

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
Stopped in the middle of Section 2.

@@
 \section{Introduction}
+
 %The popularity of the Internet encourages tremendous amount of source code being shared online. 
-Stack Overflow is a popular online programming community with 6.3 million users.
-It allows programmers to ask questions and give answers to programming problems.
-The website has found to be useful for software development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for educational purposes~\cite{Nasehi2012}.
-On Stack Overflow, each conversation contains a question and a list of answer(s).
-The answers frequently contain at least one code snippet as a solution to the question asked.
-We found that the code snippets are usually not written directly on the Stack Overflow website but copied from another location.
-It can be copied and modified from a code snippet in the question, copied from an answerer's own code or from other locations including open source software (OSS) systems.
-The process of posting and answering questions on Stack Overflow, which involves reusing of source code, can be considered as code cloning.
-
-Code cloning is an activity of reusing source code by copying and pasting.
-It normally occurs in software development and account from 7\% to 23\% of source code in typical software systems~\cite{Bellon2007}.
-The benefits and drawbacks of clones are still controversial.
-Several authors state that clones lead to bug propagations and software maintenance issues~\cite{Kamiya2002}, while some others suggest that clones are not harmful and can even be beneficial~\cite{Saini2016,Kapser2006}.
-
-Code cloning can also have side effects such as violating software licenses and introducing software vulnerabilities.
-Carelessly cloning code from one project to another project with a different license may cause a software licensing violation~\cite{German2009}.
-This also happens within the context of online Q\&A websites such as Stack Overflow.
-An et al.~\cite{An2017} showed that 1,279 cloned snippets between Android apps and Stack Overflow potentially violate software licenses.
-Security is also among the main concerns when code is copied from an online source.
-Stack Overflow helps developers to solve Android programming problems more quickly than other resources while, at the same time, offers less secure code than books or the official Android documentation~\cite{Acar2016}.
+Stack Overflow is a popular online programming community with 6.3
+million users. It allows programmers to ask questions and give answers
+to programming problems. The website has found to be useful for
+software
+development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
+  Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also
+valuable for educational purposes~\cite{Nasehi2012}. On Stack
+Overflow, each conversation contains a question and a list of
+answer(s). The answers frequently contain at least one code snippet as
+a solution to the question asked. We found that the code snippets are
+usually not authored directly on the Stack Overflow website but copied
+from another location. An answer's snippet could be copied and modified
+from a code snippet in the question, copied from the answerer's own
+code or from other locations including open source software (OSS)
+systems. The process of posting and answering questions on Stack
+Overflow, which involves reusing of source code, can be considered as
+code cloning.
+
+Code cloning is an activity of reusing source code by copying and
+pasting. It normally occurs in software development and account from
+7\% to 23\% of source code in typical software
+systems~\cite{Bellon2007}. The benefits and drawbacks of clones are
+still controversial. Several authors state that clones lead to bug
+propagations and software maintenance issues~\cite{Kamiya2002}, while
+some others suggest that clones are not harmful and can even be
+beneficial~\cite{Saini2016,Kapser2006}.
+
+Code cloning can also have side effects such as violating software
+licenses or introducing software vulnerabilities. Carelessly cloning
+code from one project to another project with a different license may
+cause a software licensing violation~\cite{German2009}. This also
+happens within the context of online Q\&A websites such as Stack
+Overflow. An et al.~\cite{An2017} showed that 1,279 cloned snippets
+between Android apps and Stack Overflow potentially violate software
+licenses. Security is also among the main concerns when code is copied
+from an online source. Stack Overflow helps developers to solve
+Android programming problems more quickly than other resources while,
+at the same time, offers less secure code than books or the official
+Android documentation~\cite{Acar2016}.
 
@@
 
-We call code snippets that are copied from software systems to online Q\&A websites (such as Stack Overflow), and vice versa as ``online code clones'' (sometimes only ``clones'' for brevity).
-There are four ways to create online code clones: (1) code is cloned from a software project to a Q\&A website as an example; (2) code is cloned from a Q\&A website to a software project to obtain a functionality, perform a particular task, or fixing a bug; and (3) code is transferred from one software project to another via a Q\&A website; Online code clones can similarly lead to a problem of outdated code, bug propagation, licensing violation, and software vulnerability as classical code clones.
-Unfortunately, they are more difficult to locate and fix since the search space in online code corpora is larger and no longer confined in a local repository.
-
-In this study, we are interested in locating online code clones on Stack Overflow that are cloned from open source projects and study them on two aspects: \textbf{outdated code and licensing issues.}
+We call code snippets that are copied from software systems to online
+Q\&A websites (such as Stack Overflow), and vice versa as ``online
+code clones'' (sometimes only ``clones'' for brevity). There are two
+directions in creating online code clones: (1) code is cloned from a software
+project to a Q\&A website as an example; or (2) code is cloned from a
+Q\&A website to a software project to obtain a functionality, perform
+a particular task, or fixing a bug.
+% and (3) code is transferred from one software project to another via a Q\&A website; 
+Similar to classic clones, online code clones can lead to license
+violations, bug propagation, introduction of vulnerabilities, and
+re-use of outdated code. Unfortunately, online clones are more
+difficult to locate and fix since the search space in online code
+corpora is larger and no longer confined in a local repository.
+
+In this study, we are interested in locating online code clones on
+Stack Overflow that are cloned from open source projects and study
+them on two aspects: \textbf{outdated code and license conflicts.}
 
@@
 	\end{lstlisting}
-	\caption{A motivating example of the two code fragments of {\small\texttt{WritableComparator.java}}.
-The one on the Stack Overflow post 22315734 is outdated when compared to its latest version in {\small\texttt{hadoop}} code base}
+	\caption{A motivating example of the two code fragments of
+          {\small\texttt{WritableComparator.java}}. The one from the
+          Stack Overflow post 22315734 (left) is outdated when compared to
+          its latest version in the \textsf{hadoop} code base
+          (right).}
 	\label{fig:before-after}
@@
 
-A motivating example of outdated online code clones can be found in the a Stack Overflow post regarding how to implement {\small{\texttt{RawComparator}}} in \texttt{hadoop}\footnote{http://stackoverflow.com/questions/22262310}.
-In \Cref{fig:before-after}, the left hand side shows a code snippet embedded as a part of accepted answer to the question.
-The snippet shows how {\small{\texttt{hadoop}}} implements the {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}} class.
-The code snippet on the right hand side shows another version of the same {\small{\texttt{compare}}} method in {\small{\texttt{WritableComparator}}} class, but at this time extracted from the latest version (as of 26 September 2016) of {\small{\texttt{hadoop}}}.
-We can obviously see that they are highly similar except a line containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in the latest version.
-The added line is intended for cleaning up the reference in the {\small{\verb|buffer|}} variable.
-While this change has already been introduced into the {\small{\texttt{compare}}} method in the latest version of {\small{\texttt{hadoop}}}, the code example in Stack Overflow post is still unchanged.
-This example shows that there can be inconsistencies between online code clones and their originals leading the users of Stack Overflow to reuse outdated code.
+A motivating example of outdated online code clones can be found in an
+answer to a Stack Overflow question regarding how to implement
+{\small{\texttt{RawComparator}}} in
+\textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22262310}}.
+\Cref{fig:before-after} shows a code snippet embedded as a part of the
+accepted answer on the left. The snippet shows how \textsf{hadoop}
+implements the {\small{\texttt{compare}}} method in its
+{\small{\texttt{WritableComparator}}} class. The code snippet on the
+right shows another version of the same method, but at this time
+extracted from the latest version (as of 26 September 2016) of
+\textsf{hadoop}. We can see that they are highly similar except a line
+containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in
+the latest version. The added line is intended for cleaning up the
+reference in the {\small{\verb|buffer|}} variable. While this change
+has already been introduced into the {\small{\texttt{compare}}} method
+in the latest version of \textsf{hadoop}, the code example in Stack
+Overflow post is still unchanged. This example shows that there can be
+inconsistencies between online code clones and their originals leading
+users of Stack Overflow to reuse outdated code.
 %The code snippet on Stack Overflow can be outdated.
@@
 
-While research has mostly focused on reusing code snippets ``from Stack Overflow'' (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work has been conducted on finding the origins of code examples copied ``to Stack Overflow'' and problems of reusing them such as outdated code and software licensing violation.
-This paper makes the following  primary contributions:
+While research has mostly focused on reusing code snippets \emph{from}
+Stack Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work
+has been conducted on finding the origins of code examples copied
+\emph{to} Stack Overflow and problems of reusing them such as outdated
+code and software licensing violations. This paper makes the following
+primary contributions:
 
@@
 \noindent\textbf{1.~A manual study of online code clones:} 
-We used two clone detection tools to discover 315,786,118 similar code snippet pairs, followed by a manual classification of 3,632 candidate clone pairs between Java code snippets obtained from Stack Overflow's accepted answers and 111 Java open source projects from a curated Qualitas corpus~\cite{QualitasCorpus}.
+We used two clone detection tools to discover 315,786,118 similar code
+snippet pairs, followed by a manual classification of 3,632 candidate
+clone pairs between Java code snippets obtained from Stack Overflow's
+accepted answers and 111 Java open source projects from the curated
+Qualitas corpus~\cite{QualitasCorpus}.
 
 \vspace{0.5ex}%
-\noindent\textbf{2.~An investigation of outdated and license-violating online clones on Stack Overflow:} Our study shows that there are at least 668 clones that have been obviously copied from open source projects or external online sources to Stack Overflow as code examples which potentially violate software licenses.
-In addition, 64 out of the 112 online code clones from Qualitas to Stack Overflow are outdated and questionable for being reused.
+\noindent\textbf{2.~An investigation of outdated and license-violating
+  online clones on Stack Overflow:} Our study shows that from the
+3,632 online clones, at least 668 likely have been copied from open
+source projects or external online sources to Stack Overflow,
+potentially violating software licenses. For 112 of them, we found
+evidence that they have been copied from a specific Qualitas project
+and that 64 of them are meanwhile outdated.
+% and questionable for being reused.
 
 \vspace{0.5ex}%
-\noindent\textbf{3.~An online code clone oracle:} The 3,632 manually investigated and validated online clone pairs are available for download on the study website\footnote{https://to.be.disclosed.after.review} and can be used as a clone oracle.
+\noindent\textbf{3.~An online code clone oracle:} The 3,632 manually
+investigated and validated online clone pairs are available for
+download\footnote{https://to.be.disclosed.after.review} and can be
+used as a clone oracle.
 
 \section{Empirical Study}
-We performed an empirical study of online code clones between Stack Overflow and 111 Java open source projects to answer the following research questions: \\ 
-\textbf{RQ1 (online code clones):} \textit{To what extent  is source code cloned between Stack Overflow and open source projects?} We quantitatively measured the number of online code clones between Stack Overflow and open source projects to understand the scale of the problem.
+
+We performed an empirical study of online code clones between Stack
+Overflow and 111 Java open source projects to answer the following
+research questions: \\
+%
+\textbf{RQ1 (online code clones):} \textit{To what extent is source
+  code cloned between Stack Overflow and open source projects?} We
+quantitatively measured the number of online code clones between Stack
+Overflow and open source projects to understand the scale of the
+problem. \newline 
+%
+\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online
+  code clones occur?} We categorised online clones into seven
+categories allowing insights to why online code clones are created.
 \newline
-\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online code clones occur?} We categorised online clones into seven categories according to our online code cloning patterns.
-This gave us more insights to why online code clones are created.
-\newline
-\textbf{RQ3 (Outdated online code clones):} \textit{Are online code clones up-to-date compared to their counterparts in the original projects?} We were interested in the outdated Stack Overflow code examples since millions of users are potentially reusing them.
-\newline
-\textbf{RQ4 (Software licensing violation):} \textit{Do licensing conflicts occur between Stack Overflow clones and their originals?} We investigated whether online code clones can be legally harmful to software developers reusing them.
+%
+\textbf{RQ3 (Outdated online code clones):} \textit{Are
+  online code clones up-to-date compared to their counterparts in the
+  original projects?} We were interested in the outdated Stack
+Overflow code examples since users are potentially reusing
+them. \newline
+%
+\textbf{RQ4 (Software licensing violation):} \textit{Do
+  licensing conflicts occur between Stack Overflow clones and their
+  originals?} We investigated whether the reuse of online code clones
+can cause software developers to violate licenses.
 
@@
 \subsection{Experimental Framework}
-To answer the four research questions, we followed the experimental framework depicted in \Cref{fig:exp_framework}.
-We processed two datasets, 144,064 code snippets from Java accept answers on Stack Overflow and 111 open source projects from Qualitas corpus.
-Java code snippets were extracted from Stack Overflow posts.
-We prepared the Java code in both datasets by removing comments and pretty-printing to increase the accuracy of clone detection.
-Then, we deployed two clone detection tools, Simian~\cite{simian} and NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets.
-Due to the scalability of Simian and NiCad, we partitioned the input and run the tools multiple times.
-Each run was composed of the whole Stack Overflow data and a single Qualitas project.
-We repeated the process until we covered 111 projects.
+
+To answer the four research questions, we used the experimental
+framework depicted in \Cref{fig:exp_framework}. We processed two
+datasets, 144,064 Java code snippets from accepted answers on Stack
+Overflow and 111 open source projects from the Qualitas corpus. The
+Java code snippets were extracted from Stack Overflow posts. We
+prepared the Java code in both datasets by removing comments and
+pretty-printing to increase the accuracy of clone detection. Then, we
+deployed two clone detection tools, Simian~\cite{simian} and
+NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets.
+Due to the scalability of Simian and NiCad, we partitioned the input
+and run the tools multiple times. Each run was composed of the whole
+Stack Overflow data and a single Qualitas project. We repeated the
+process until we covered all 111 projects.
 
 %enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad. Moreover, using GCF, other additional clone detectors could be adopted
-We then converted the clone reports to the General Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF file.
-GCF provides a common format for clones which enables other clone detectors to be adopted,
-if needed, without any changes in the analysis.
-Simian did not provide an option to detect cross-project clones between two locations.
-Hence the Simian GCF clone report was pruned to contain only clone pairs between Stack Overflow and Qualitas projects.
-In this step, all intra clone pairs within either Stack Overflow or Qualitas were removed.
-NiCad provides an option to detect clones from two locations so no pruning is needed.
-We did not have an oracle of clones between the two data sets so we rely on a manual investigation to validate the reported clone candidates.
-However, the large amount of generated clone pairs hindered us from looking at all of them.
-Random sampling of clones could be employed.
-However, the risk of returning non-meaningful clones is increased.
-Instead, we selected clone pair candidates by relying on agreement of clone detectors.
-If a clone pair was similarly reported by multiple tools, we had a higher confidence that it was a real clone pair.
-To achieve this, clone pairs from the two clone detectors were pair-wise matched to find agreements using Bellon's clone overlapping criteria~\cite{Bellon2007}.
-This step generated \textbf{agreed clone pairs}.
-They were pairs with high confidence to be true clones since they obtained agreement from both tools.
-Then, pairs reported by Simian and NiCad that did not find agreement were categorised as \textbf{disagreed clone pairs}.
-The disagreed clone pairs were clones with less confidence than the agreed ones.
-Finally, agreed and disagreed clone pairs have been looked at manually by two of the authors.
-
-In the manual inspection process, we classified clones into seven categories according to information observed from code comments and natural text in the Stack Overflow answer.
-This process took approximately a month until we successfully investigated 3,632 clone pairs.
-Clone pairs that were classified as false clones, boiler-plate code, or IDE-generated are not very interesting and were ignore in the analysis of outdated code and licensing violation.
-We compared the licensing information of 668 remaining clone pairs for possibilities of software licensing violations.
-Moreover, we looked at the history starting at the date of the answers to today from its git repository.
-With this method, we discovered \textbf{outdated code}, i.e.~code that changes were made to them after they had been copied to Stack Overflow.
-%hence resulting in outdated clones on Stack Overflow.
+We then converted the clone reports to the General Clone Format
+(GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF
+file.
+% GCF provides a common format for clone reports which enables other
+% clone detectors to be adopted, if needed, without any changes in the
+% analysis.
+Simian did not provide an option to detect cross-project clones
+between two locations. Hence the Simian GCF clone report was filtered
+to contain only clone pairs between Stack Overflow and Qualitas
+projects, removing all clone pairs within either Stack Overflow or
+within Qualitas. NiCad provides an option to detect clones from two
+locations so no filtering was needed. We did not have an oracle of clones
+between the two data sets so we rely on a manual investigation to
+validate the reported clone candidates. However, the large amount of
+generated clone pairs hindered us from looking at all of them.
+% A random sampling of clones could have been employed, however, the
+% risk of returning false positives non-meaningful clones is
+% increased.
+Instead of extracting a random sample, we selected clone pair
+candidates by relying on \emph{agreement} of clone detectors. If a
+clone pair was reported by multiple tools, we had a higher
+confidence that it was a real clone pair. To achieve this, clone pairs
+from the two clone detectors were pair-wise matched to find agreements
+using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step
+generated \textbf{agreed clone
+  pairs}. They were pairs with high confidence to be true clones since
+they obtained agreement from both tools. Then, pairs reported by
+Simian and NiCad that did not find agreement were categorised as
+\textbf{disagreed clone pairs}. The disagreed clone pairs were clones
+with less confidence than the agreed ones. Finally, agreed and
+disagreed clone pairs have been looked at manually by two of the
+authors.
+
+In the manual inspection process, we classified clones into seven
+categories according to information observed from code comments and
+text in the Stack Overflow answer. This process took approximately a
+month until we successfully investigated 3,632 clone pairs. Clone
+pairs that were classified as false clones, boiler-plate code, or
+IDE-generated are not very interesting and were ignore in the analysis
+of outdated code and licensing violation. We compared the licensing
+information of the 668 remaining clone pairs for possibilities of software
+licensing violations. Moreover, we looked at the history starting at
+the date of the answers to today from its git repository. With this
+method, we discovered \textbf{outdated code}, i.e.~code that changes
+were made to them after they have been copied to Stack
+Overflow. %hence resulting in outdated clones on Stack Overflow.
 
@@
 The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow.
-Out of 112 Qualitas projects, there is one project, \texttt{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study.
+Out of 112 Qualitas projects, there is one project, \textsf{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study.
 This resulted in a total of 111 projects analysed in the study.
@@
 The $N_E$ snippets are associate with 88 Qualitas projects.
-We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in {\small\texttt{hibernate}} due to clustering errors.
-$N_E$ generated renaming errors for 5 projects including {\small\texttt{vuze}}, {\small\texttt{hibernate}}, {\small\texttt{myfaces}}, {\small\texttt{netbeans}}, and {\small\texttt{spring}}.
+We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \textsf{hibernate} due to clustering errors.
+$N_E$ generated renaming errors for 5 projects including \textsf{vuze}, \textsf{hibernate}, \textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}.
 We have contacted the creator of NiCad regarding the issues.
@@
 Most of them have a statement in the Stack Overflow post saying that the code is ``copied'' or ``modified'' from a specific file or class in a Qualitas project.
-The most cloned projects are {\small\texttt{hibernate}} and {\small\texttt{spring}} with 20 clone pairs, followed by {\small\texttt{eclipse}} (15 pairs), and {\small\texttt{hadoop}} (12 pairs).
+The most cloned projects are \textsf{hibernate} and \textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15 pairs), and \textsf{hadoop} (12 pairs).
 The clones are used as examples and are very similar to their original Qualitas code with limited modifications.
@@
 For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html.
-Both the Stack Overflow and the {\small\texttt{compiere}} project source code contain an attribution to the original source.
+Both the Stack Overflow and the \textsf{compiere} project source code contain an attribution to the original source.
 Another example is a code to generate graphical \textit{Perlin noise}.
 It is copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/.
-The code is used in Stack Overflow and {\small\texttt{aoi}} project with attribution.
+The code is used in Stack Overflow and \textsf{aoi} project with attribution.
 %The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
-There are other EX clone pairs are from third-party libraries such as {\small\texttt{zxing}}, {\small\texttt{jasper}}, {\small\texttt{java.util}}, {\small\texttt{javax.servlet}}, and the {\small\texttt{bouncycastle}} cryptography project.
+There are other EX clone pairs are from third-party libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util}, \textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography project.
 
@@
 They include 11, 42, 294, and 35 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
-The most cloned projects is {\small{\texttt{netbeans}}} with 95 clone pairs.
+The most cloned projects is \textsf{netbeans} with 95 clone pairs.
 Most of the clones are a large chunk of code handling GUI components.
 Although these GUI clones might be auto-generated by IDEs, we did not find any evidence.
-The second most cloned project is {\small{\texttt{jung2}}} (62 pairs), a network and graph framework, followed by {\small{\texttt{eclipse-SDK}}} (37 pairs).
-%There are several Stack Overflow snippets that are identical to code in {\small{\texttt{jung2}}}.
+The second most cloned project is \textsf{jung2} (62 pairs), a network and graph framework, followed by \textsf{eclipse-SDK} (37 pairs).
+%There are several Stack Overflow snippets that are identical to code in \textsf{jung2}.
 
@@
 We discovered 64 outdated online clone pairs out of 112 pairs.
-As shown in \Cref{fig:outdated}, {\small{\texttt{spring}}} and {\small{\texttt{hibernate}}} have the maximum number of 20 outdated pairs, followed by 15 from {\small{\texttt{eclipse}}}, and 12 from {\small{\texttt{hadoop}}}.
-Besides the example of outdated code in the {\small{\texttt{hadoop}}}'s {\small{\texttt{WritableComparator.java}}} shown in \Cref{fig:before-after}, we also found a few outdated code elements which contained heavy modifications.
-For example, the code snippet in Stack Overflow post 23520731 is a copy of {\small{\texttt{SchemaUpdate.java}}} in {\small{\texttt{hibernate}}}.
+As shown in \Cref{fig:outdated}, \textsf{spring} and \textsf{hibernate} have the maximum number of 20 outdated pairs, followed by 15 from \textsf{eclipse}, and 12 from \textsf{hadoop}.
+Besides the example of outdated code in the \textsf{hadoop}'s {\small{\texttt{WritableComparator.java}}} shown in \Cref{fig:before-after}, we also found a few outdated code elements which contained heavy modifications.
+For example, the code snippet in Stack Overflow post 23520731 is a copy of {\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}.
 The code has been heavily modified on 5 February 2016.
@@
 These snippets cannot be located in the latest version of the projects.
-For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in {\small{\texttt{spring}}}, was deleted in the commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012, two years after it was posted.
+For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was deleted in the commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012, two years after it was posted.
 %The latest version of Spring does not contain the file anymore.
@@
 This code has been copied from {\small\texttt{SchemaUpdate.java}}.
-Its latest version in {\small\texttt{hibernate}} code base contains heavy modifications.}
+Its latest version in \textsf{hibernate} code base contains heavy modifications.}
 %	\label{fig:hibernate_outdated_code}

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
(Section 2) merged the Experimental Framework and Experimental Setup together.

@@
 
-\subsection{Experimental Framework}
-
-To answer the four research questions, we used the experimental
-framework depicted in \Cref{fig:exp_framework}. We processed two
-datasets, 144,064 Java code snippets from accepted answers on Stack
-Overflow and 111 open source projects from the Qualitas corpus. The
-Java code snippets were extracted from Stack Overflow posts. We
-prepared the Java code in both datasets by removing comments and
-pretty-printing to increase the accuracy of clone detection. Then, we
-deployed two clone detection tools, Simian~\cite{simian} and
-NiCad~\cite{Roy2008,Cordy}, to locate clones between the two datasets.
-Due to the scalability of Simian and NiCad, we partitioned the input
-and run the tools multiple times. Each run was composed of the whole
-Stack Overflow data and a single Qualitas project. We repeated the
-process until we covered all 111 projects.
-
-%enabled us to reuse the same scripts to analyse clone reports from both Simian and NiCad. Moreover, using GCF, other additional clone detectors could be adopted
-We then converted the clone reports to the General Clone Format
-(GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF
-file.
-% GCF provides a common format for clone reports which enables other
-% clone detectors to be adopted, if needed, without any changes in the
-% analysis.
-Simian did not provide an option to detect cross-project clones
-between two locations. Hence the Simian GCF clone report was filtered
-to contain only clone pairs between Stack Overflow and Qualitas
-projects, removing all clone pairs within either Stack Overflow or
-within Qualitas. NiCad provides an option to detect clones from two
-locations so no filtering was needed. We did not have an oracle of clones
-between the two data sets so we rely on a manual investigation to
-validate the reported clone candidates. However, the large amount of
-generated clone pairs hindered us from looking at all of them.
-% A random sampling of clones could have been employed, however, the
-% risk of returning false positives non-meaningful clones is
-% increased.
-Instead of extracting a random sample, we selected clone pair
-candidates by relying on \emph{agreement} of clone detectors. If a
-clone pair was reported by multiple tools, we had a higher
-confidence that it was a real clone pair. To achieve this, clone pairs
-from the two clone detectors were pair-wise matched to find agreements
-using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step
-generated \textbf{agreed clone
-  pairs}. They were pairs with high confidence to be true clones since
-they obtained agreement from both tools. Then, pairs reported by
-Simian and NiCad that did not find agreement were categorised as
-\textbf{disagreed clone pairs}. The disagreed clone pairs were clones
-with less confidence than the agreed ones. Finally, agreed and
-disagreed clone pairs have been looked at manually by two of the
-authors.
-
-In the manual inspection process, we classified clones into seven
-categories according to information observed from code comments and
-text in the Stack Overflow answer. This process took approximately a
-month until we successfully investigated 3,632 clone pairs. Clone
-pairs that were classified as false clones, boiler-plate code, or
-IDE-generated are not very interesting and were ignore in the analysis
-of outdated code and licensing violation. We compared the licensing
-information of the 668 remaining clone pairs for possibilities of software
-licensing violations. Moreover, we looked at the history starting at
-the date of the answers to today from its git repository. With this
-method, we discovered \textbf{outdated code}, i.e.~code that changes
-were made to them after they have been copied to Stack
-Overflow. %hence resulting in outdated clones on Stack Overflow.
-
-\subsection{Experimental Setup}
-
-We followed the experimental framework by processing the source code from the two data sets, configuring and running the clone detectors, and analysing the clones.
+%\subsection{Experimental Setup}
+\vspace{1ex}
+To answer these four research questions, we perform an experiment to
+locate and study the online code clones between Stack Overflow and open source
+projects. The experimental framework is depicted in \Cref{fig:exp_framework}. 
+We discuss the experimental setup below.
+
+%\subsection{Experimental Setup}
+
+%We followed the experimental framework by processing the source code from the two data sets, configuring and running the clone detectors, and analysing the clones.
 We discuss each of them in details below.
 
-\subsubsection{Datasets}
-
-\textbf{Stack Overflow}: we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016.
+\subsection{Datasets}
+
+We reply on two data sets in this study: Java code snippets on Stack Overflow and open source projects from the Qualitas corpus.
+
+\subsubsection{Stack Overflow} we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016.
 The archived dump has a size of 9 gigabytes.
@@
 
-\subsubsection{Clone Detectors}
+\subsection{Clone Detectors}
 There is a number of restrictions in terms of choosing clone detection tools for this study.
@@
 
-\subsubsection{Prioritise Clone Candidates Using Agreement}
+%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
+%Overflow and 111 open source projects from the Qualitas corpus. 
+%The Java code snippets were extracted from Stack Overflow posts. 
+We prepared the Java code in both datasets by removing comments and
+pretty-printing to increase the accuracy of clone detection. Then, we
+deployed two clone detection tools to locate clones between the two datasets.
+Due to the scalability of Simian and NiCad, we partitioned the input
+and run the tools multiple times. Each run was composed of the whole
+Stack Overflow data and a single Qualitas project. We repeated the
+process until we covered all 111 projects.
+We then converted the clone reports to the General Clone Format
+(GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF
+file.
+Simian did not provide an option to detect cross-project clones
+between two locations. Hence the Simian GCF clone report was filtered
+to contain only clone pairs between Stack Overflow and Qualitas
+projects, removing all clone pairs within either Stack Overflow or
+within Qualitas. NiCad provides an option to detect clones from two
+locations so no filtering was needed.
+
+\subsection{Prioritise Clone Candidates Using Agreement}
 The number of clones detected in large-scale datasets can be huge.
-In our study, there are in total 266,837,480 clone pairs reported.
+In our study, there are in total 315,786,118 clone pairs reported.
 It is infeasible for humans to manually validate them all.
@@
 
-Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 266 million candidate clone pairs for manual investigation.
-\textit{good} pairs are the ones with the highest confidence and are ranked first to be looked at, followed by \textit{ok} pairs, and followed by clone pairs without agreement.
+Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 315 million candidate clone pairs for manual investigation.
+\textit{good} pairs are the ones with the highest confidence, followed by \textit{ok} pairs, and followed by clone pairs without agreement.
+We call the
+\textit{good} and \textit{ok} pairs \textbf{agreed} clone pairs and the the clone pairs reported by Simian and NiCad without agreement \textbf{disagreed} clone pairs.
 
@@
 \end{table}
+
+%\subsection{Manual Investigation}
+%We did not have an oracle of clones
+%between the two data sets so we rely on a manual investigation to
+%validate the reported clone candidates. However, the large amount of
+%generated clone pairs hindered us from looking at all of them.
+%A random sampling of clones could have been employed, however, the 
+%risk of returning false positives non-meaningful clones is increased.
+%Instead of extracting a random sample, we selected clone pair
+%candidates by relying on \emph{agreement} of clone detectors. If a
+%clone pair was reported by multiple tools, we had a higher
+%confidence that it was a real clone pair. To achieve this, clone pairs
+%from the two clone detectors were pair-wise matched to find agreements
+%using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step
+%generated 
+%\textbf{agreed clone pairs}. They were pairs with high confidence to be true clones since
+%they obtained agreement from both tools. Then, pairs reported by
+%Simian and NiCad that did not find agreement were categorised as
+%\textbf{disagreed clone pairs}. The disagreed clone pairs were clones
+%with less confidence than the agreed ones. 
+%Finally, agreed and
+%disagreed clone pairs have been looked at manually by two of the
+%authors.
+
+%In the manual inspection process, we classified clones into seven
+%categories according to information observed from code comments and
+%text in the Stack Overflow answer. This process took approximately a
+%month until we successfully investigated 3,632 clone pairs. Clone
+%pairs that were classified as false clones, boiler-plate code, or
+%IDE-generated are not very interesting and were ignore in the analysis
+%of outdated code and licensing violation. We compared the licensing
+%information of the 668 remaining clone pairs for possibilities of software
+%licensing violations. Moreover, we looked at the history starting at
+%the date of the answers to today from its git repository. With this
+%method, we discovered \textbf{outdated code}, i.e.~code that changes
+%were made to them after they have been copied to Stack
+%Overflow. 
+%hence resulting in outdated clones on Stack Overflow.
 

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
(Section 2) fixed typos.

@@
 \vspace{1ex}
-To answer these four research questions, we perform an experiment to
+To answer these four research questions, we perform an empirical study to
 locate and study the online code clones between Stack Overflow and open source
-projects. The experimental framework is depicted in \Cref{fig:exp_framework}. 
-We discuss the experimental setup below.
+projects. The experimental framework is depicted in \Cref{fig:exp_framework} and
+we discuss our experimental setup below.
 
@@
 
-We reply on two data sets in this study: Java code snippets on Stack Overflow and open source projects from the Qualitas corpus.
+We rely on two data sets in this study: Java code snippets on Stack Overflow and open source projects from the Qualitas corpus \cite{QualitasCorpus}.
 
@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We obtained 144,064 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
+We obtained 144,064 Java code snippets which contain 2,346,267 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
 

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
Commit to merge.

--- 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
@@
 
-We reply on two data sets in this study: Java code snippets on Stack Overflow and open source projects from the Qualitas corpus.
-
-\subsubsection{Stack Overflow} we extracted Java code snippets from a snapshot of a Stack Overflow dump\footnote{https://archive.org/details/stackexchange} in January 2016.
-The archived dump has a size of 9 gigabytes.
-The data dump was in XML format containing information of \textbf{Posts} (questions and answers) and supporting data such as user accounts and timestamps of the posts.
-We were interested in code snippets embedded in posts which were located between {\small\texttt{<code></code>}} tags.
-A Stack Overflow thread contains a post of a question and several posts of answers where every answer has voting score from its users.
-An answer can also be marked as \textbf{accepted answer} by the questioner if the solution fixes his/her problem.
-We collected Java code snippets using two criteria.
-First, we were only interested in code snippets with at least six lines.
-Snippets that are smaller than six lines are usually spurious clones~\cite{Bellon2007}.
-Second, we only focused on code snippets in accepted answers.
-We chose the snippets in accepted answers because they actually solved the problems in the questions.
-Moreover, they are always displayed just below the questions which makes them more attractive to be reused than other answers.
-Each snippet was extracted from the dump and saved to a file.
+We reply on two data sets in this study: Java code snippets in answers
+on Stack Overflow and open source projects from the Qualitas corpus.
+
+\subsubsection{Stack Overflow}
+
+We extracted Java code snippets from a snapshot of a Stack Overflow
+dump\footnote{\url{https://archive.org/details/stackexchange}} in
+January 2016. The archived dump has a size of 9 gigabytes. The data
+dump is in XML format containing information of \textbf{Posts}
+(questions and answers) and supporting data such as user accounts and
+timestamps of the posts. We were interested in code snippets embedded
+in posts which were located between
+{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
+thread contains a question and several answers. An answer can also be
+marked as \textbf{accepted answer} by the questioner if the solution
+fixes his/her problem. We collected Java code snippets using two
+criteria. First, we only focused on code snippets in accepted
+answers. We chose the snippets in accepted answers because they
+actually solved the problems in the questions. Moreover, they are
+always displayed just below the questions which makes them more
+likely to be reused than other answers. Second, we were only
+interested in code snippets of at least six lines. Snippets smaller
+than six lines are usually spurious clones~\cite{Bellon2007}. Each
+snippet was extracted from the dump and saved to a file.
 %using its post ID as the file's name.
@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We obtained 144,064 Java code snippets which contain 2,347,269 lines of Java source code excluding comments and blank lines\footnote{Measured by cloc: https://github.com/AlDanial/cloc}.
-
-\textbf{Open source systems}: we selected the established corpus for an empirical software engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for this study.
-It is a curated Java corpus that has been used in several software engineering studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
-The projects in the corpus represent various domains of software systems ranging from programming languages to visualisation~\cite{QualitasCorpus}.
-We selected the 20130901r release of Qualitas corpus containing 112 Java open source projects.
-This release contains projects with releases no later than 1st September 2013.
-We chose a snapshot late back in 2013 since we are interested in online code clones in the direction from open source projects to Stack Overflow.
-The 20130901r snapshot provides Java code that is at least 3 years old from the time of the experiment (January to December 2016).
-The time difference is sufficiently long for a number of code snippets to be copied onto Stack Overflow.
-Out of 112 Qualitas projects, there is one project, \textsf{jre}, that does not contain Java source code due to its licensing limitation~\cite{QualitasCorpus} so it is removed from the study.
-This resulted in a total of 111 projects analysed in the study.
-As shown in \Cref{tab:datasets}, the 111 Qualitas project have 160,937 Java files containing 19,086,883 lines of code.
-%Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.
+We obtained 144,064 Java code snippets which contain 2,347,269 lines
+of Java source code excluding comments and blank
+lines\footnote{Measured by cloc:
+  \url{https://github.com/AlDanial/cloc}}.
+
+\subsubsection{Open source systems}
+
+We selected the established corpus for an empirical software
+engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for
+this study. It is a curated Java corpus that has been used in several
+software engineering
+studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. The
+projects in the corpus represent various domains of software systems
+ranging from programming languages to
+visualisation~\cite{QualitasCorpus}. We selected the 20130901r release
+of Qualitas corpus containing 112 Java open source projects. This
+release contains projects with releases no later than 1st September
+2013. We chose a snapshot late back in 2013 since we are interested in
+online code clones in the direction from open source projects to Stack
+Overflow. The 20130901r snapshot provides Java code that is more than
+2 years older than the Stack Overflow snapshot, which is sufficiently
+long for a number of code snippets to be copied onto Stack Overflow
+and also to observe if clones become outdated. Out of 112 Qualitas
+projects, there is one project, \textsf{jre}, that does not contain
+Java source code due to its licensing limitation~\cite{QualitasCorpus}
+and is removed from the study. This resulted in a total of 111
+projects analysed in the study. As shown in \Cref{tab:datasets}, the
+111 Qualitas project have 160,937 Java files containing 19,086,883
+lines of
+code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.
 
@@
   \small
-	\begin{tabular}{l|r|r}
+  \begin{tabular}{lrr}
     \hline 
@@
     Stack Overflow & 144,064 & 2,346,267 \\ 
-		\hline 
+    %\hline 
     Qualitas &  160,937 & 19,086,883 \\ 
@@
 \subsection{Clone Detectors}
-There is a number of restrictions in terms of choosing clone detection tools for this study.
-The main restriction is due to nature of code snippets posted on Stack Overflow, most of them are not complete Java classes or methods.
-Hence, the tool must be flexible enough to process code snippets that are neither a complete block nor compilable.
-Moreover, since the amount of code that has to be processed is in a scale of millions line of code (as shown in \Cref{tab:datasets}), a clone detector must be scalable enough to successfully complete the execution and report clones in a reasonable amount of time.
-We have tried 5 state-of-the-art clone detectors including Simian~\cite{simian}, NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against Stack Overflow and Qualitas datasets.
-CCFinder, iClones, and DECKARD failed with execution errors after running for couple of hours.
-Thus, we removed them from the study.
-Simian and NiCad completed the detection with success.
-We found that both of them are also flexible enough to handle code with incomplete methods or classes.
-%So, we decided to use both of them.
+
+There are a number of restrictions in terms of choosing clone
+detection tools for this study. The main restriction is due to nature
+of code snippets posted on Stack Overflow, as most of them are
+incomplete Java classes or methods. Hence, a detector must be flexible
+enough to process code snippets that are not compilable or not
+complete blocks. Moreover, since the amount of code that has to be
+processed is in a scale of millions line of code (as shown in
+\Cref{tab:datasets}), a clone detector must be scalable enough to
+report clones in a reasonable amount of time. We have tried 5
+state-of-the-art clone detectors including Simian~\cite{simian},
+NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002},
+iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against the
+Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD
+failed with execution errors after running for couple of hours. Thus,
+we removed them from the study. Simian and NiCad are flexible enough
+to handle code with incomplete methods or classes and successfully
+completed the detection.
 

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex

@@
 
-We reply on two data sets in this study: Java code snippets in answers
-on Stack Overflow and open source projects from the Qualitas corpus.
+We rely on two data sets in this study: Java code snippets in answers
+on Stack Overflow and open source projects from the Qualitas corpus
+\cite{QualitasCorpus}.
 
@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We obtained 144,064 Java code snippets which contain 2,347,269 lines
+We obtained 144,064 Java code snippets which contain 2,347,267 lines
 of Java source code excluding comments and blank

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
Improved Section 2 and 3.1.

@@
 %\subsection{Experimental Setup}
-\vspace{1ex}
+%\vspace{1ex}
 To answer these four research questions, we perform an empirical study to
@@
 
-\subsection{Clone Detectors}
+\subsection{Clone Detection}
 
@@
 
-\textbf{Simian} is a text-based clone detector that locates clones at line-level granularity and has been used extensively in several clone studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015, Krinke2010}.
-It is a command-line tool which enables us to automate the detection.
-Furthermore, it offers normalisation of variable names and literals (strings, and numbers) which enable Simian to detect literal clones (type-1) and parameterised clones (type-2).
-\textbf{NiCad} is also a text-based clone detector which detects clones at either method- or block-level granularity.
-It can detect clones of type-1, 2 up to type-3 (clones with added/removed/relocated/changed statements) and is also used in several empirical clone studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011, Sajnani2016}.
-It utilises TXL~\cite{Cordy2006} for parsing and pretty-printing source code.
-It also provides code normalisation by variable renaming and abstraction.
-We use a variant of NiCad called \textit{nicadcross}.
-It offers the same functionalities as the original NiCad but is specialised for detecting code clones between two systems.
-NiCad is also a command-line tool which makes it suitable for automation.
+\textbf{Simian} is a text-based clone detector that locates clones at
+line-level granularity and has been used extensively in several clone
+studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
+  Krinke2010}.
+% It is a command-line tool which enables us to automate the
+% detection. 
+Furthermore, it offers normalisation of variable names and literals
+(strings and numbers) which enables Simian to detect literal clones
+(type-1) and parameterised clones (type-2). \textbf{NiCad} is also a
+text-based clone detector which detects clones at either method- or
+block-level granularity. It can detect clones of type-1, -2 up to
+type-3 (clones with added and removed statements) and has
+also been used in several empirical clone studies~\cite{Roy2008,
+  Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011,
+  Sajnani2016}. It utilises TXL~\cite{Cordy2006} for parsing and
+pretty-printing source code and provides code normalisation by
+variable renaming and abstraction. We use a variant of NiCad called
+\textit{nicadcross}. It offers the same functionalities as the
+original NiCad but is specialised for detecting code clones between
+two systems. 
+% NiCad is also a command-line tool which makes it suitable for
+% automation.
 
@@
 pretty-printing to increase the accuracy of clone detection. Then, we
-deployed two clone detection tools to locate clones between the two datasets.
-Due to the scalability of Simian and NiCad, we partitioned the input
-and run the tools multiple times. Each run was composed of the whole
-Stack Overflow data and a single Qualitas project. We repeated the
-process until we covered all 111 projects.
-We then converted the clone reports to the General Clone Format
-(GCF)~\cite{Wang2013} and combined the 111 reports into a single GCF
-file.
-Simian did not provide an option to detect cross-project clones
-between two locations. Hence the Simian GCF clone report was filtered
-to contain only clone pairs between Stack Overflow and Qualitas
-projects, removing all clone pairs within either Stack Overflow or
-within Qualitas. NiCad provides an option to detect clones from two
-locations so no filtering was needed.
-
-\subsection{Prioritise Clone Candidates Using Agreement}
-The number of clones detected in large-scale datasets can be huge.
-In our study, there are in total 315,786,118 clone pairs reported.
-It is infeasible for humans to manually validate them all.
-One can do a random sampling of clones.
-However, due to a very high number of false positives, they may end up looking mostly at the false clones.
-Therefore, we adopted the idea of \textbf{clone agreement} which has been used in clone research studies~\cite{Wang2013,Funaro2010,cr2016ssbse} in situations where a clone oracle is missing or impossible to establish.
-Clone pairs agreed by multiple clone detection tools have a higher confidence to be real clones~\cite{cr2016ssbse}.
-By using this agreement-based approach, we could reduce the number of clone candidates for manual investigation by paying more attention to the ones agreed by multiple tools.
-To find an agreement between two clone pairs reported by two different tools, we used the clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}.
-Two clone pairs which have a large enough number of overlapping clone lines can be categorised as either a good-match or an ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a confident value between 0 and 1.
-A \textit{good} clone pair has stronger agreement than an \textit{ok} pair.
-We follow the original definitions of \textit{good}- and \textit{ok}-match introduced in Bellon's paper~\cite{Bellon2007}.
-
-\vspace{0.5ex}
-Given that a clone pair \textit{CP} is formed by two clone fragments \textit{CF$_1$} and \textit{CF$_2$} with a pre-defined similarity threshold \textit{t}, i.e.~\textit{CP} = (\textit{CF$_1$}, \textit{CF$_2$}, \textit{t}), we can define \textit{overlap} and \textit{contained} value of two clone pairs as
+deployed the two clone detectors to locate clones between the two
+datasets.  We partitioned the input and ran the tools multiple
+times. Each run was composed of the entire Stack Overflow data and a
+single Qualitas project. We repeated the process until we covered all
+111 projects.  We then converted the clone reports to the General
+Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
+single GCF file.  Simian did not provide an option to detect
+cross-project clones between two locations. Hence the Simian GCF clone
+report was filtered to contain only clone pairs between Stack Overflow
+and Qualitas projects, removing all clone pairs within either Stack
+Overflow or within Qualitas. 
+% NiCad provides an option to detect clones
+% from two locations so no filtering was needed.
+
+\subsection{Filtering Clone Candidates}
+
+The number of clones detected in large-scale datasets can be huge. In
+our study, there are in total 315,786,118 clone pairs reported. It is
+infeasible for humans to manually validate them all. Instead of
+investigating a random saple, we adopted the idea of \textbf{clone
+  agreement} which has been used in clone research
+studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
+clone oracle is missing or impossible to establish. Clone pairs agreed
+by multiple clone detection tools have a higher likelihood to be real
+clones~\cite{cr2016ssbse}. By using this agreement-based approach, we
+reduced the number of clone candidates for manual investigation to the
+ones agreed by multiple tools. To find agreement between two clone
+pairs reported by two different tools, we used the clone pair matching
+metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs
+which have a large enough number of overlapping lines can be
+categorised as either a good-match or an ok-match pair (denoted as
+\textit{good} and \textit{ok} respectively) with a confidence value
+between 0 and 1. A \textit{good} clone pair has stronger agreement
+than an \textit{ok} pair. We follow the original definitions of
+\textit{good}- and \textit{ok}-match introduced in Bellon's
+paper~\cite{Bellon2007}.
+
+Given that a clone pair \textit{CP} is formed by two clone fragments
+\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} = (\textit{CF$_1$},
+\textit{CF$_2$}), we can define the \textit{overlap} and
+\textit{contained} value of two clone pairs as
 %\squeezeup
-\begin{multline}
+\begin{displaymath}
   overlap(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|}
-\end{multline}
-%\squeezeup
-\begin{multline}
-	contained(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}. 
-\end{multline}
-
-\noindent\textit{good-value} of two clone pairs is then defined as
+\end{displaymath}
+% \squeezeup
+\begin{displaymath}
+  contained(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
+\end{displaymath}
+
+\noindent%
+The \textit{good-value}  and the \textit{ok-value}  of two clone pairs are then defined as
 %\squeezeup
 \begin{align*}
-	good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2)).
+	good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2))
 \end{align*}
-
-\noindent\textit{ok-value} is defined as
-%\squeezeup
 \begin{align*}
-	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),
-	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2), \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2))).
+	ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) = min(max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1),~~ \\ contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1)),~
+	\\ max(contained(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2),~~ \\contained(\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2)))
 \end{align*}
 
-Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(p)} iff, for threshold $p \in [0,1]$ holds 
+\noindent%
+Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(t)} iff, for threshold $t \in [0,1]$ holds 
 %\squeezeup
 \begin{equation}
-good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
+good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq t.
 \end{equation}
-
-Similarly for an \textit{ok-match(p)} pair
+%
+Similarly for an \textit{ok-match(t)} pair
 %\squeezeup
 \begin{equation}
-ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq p.
+ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq t.
 \end{equation}
 
-Using this good and ok-match criteria with a predefined threshold \textit{p}, we can prune the 315 million candidate clone pairs for manual investigation.
-\textit{good} pairs are the ones with the highest confidence, followed by \textit{ok} pairs, and followed by clone pairs without agreement.
-We call the
-\textit{good} and \textit{ok} pairs \textbf{agreed} clone pairs and the the clone pairs reported by Simian and NiCad without agreement \textbf{disagreed} clone pairs.
-
-\subsection{Clone Detector's Parameter Tuning}
-We were aware of effects of configurations to clone detection results and the importance of searching for optimised configurations in empirical clone studies~\cite{Wang2014,cr2016ssbse,Ragkhitwetsagul2016,Svajlenko2014}.
-However, considering the massive size of the two datasets and search space of at least 15 Simian and 5 NiCad parameters, we were hindered from searching for the best configurations of the tools.
-Thus, we decided to configure Simian and NiCad using two established configurations: 1) the tools' default configurations chosen by the tools' creators (denoted as \textit{D}), and 2) the discovered configurations for Bellon's Java projects from \textit{EvaClone}, a study of optimising clone detectors' configurations based on clone agreement, by Wang et al.~\cite{Wang2013} (denoted by \textit{E}).
-The details of the two configurations are described in \Cref{t:param_tuning}.
-Having two clone detectors, Simian (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two chosen configurations each, we looked for Bellon's good and ok-match in four possible pair-wise combinations: $S_{D}N_{D}$, $S_{D}N_{E}$, $S_{E}N_{D}$, and $S_{E}N_{E}$.
+Using the good and ok-match criteria with a predefined threshold
+\textit{t}, we can prune the 315 million candidate clone pairs for
+manual investigation. The \textit{good} pairs are the ones with the
+highest confidence, followed by the \textit{ok} pairs, and followed by
+clone pairs without agreement. We call the \textit{good} and
+\textit{ok} pairs \textbf{agreed} clone pairs and the the clone pairs
+reported by Simian or NiCad without agreement \textbf{disagreed} clone
+pairs.
+
+\subsection{Clone Detection Parameter Tuning}
+
+We were aware of effects of configurations to clone detection results
+and the importance of searching for optimised configurations in
+empirical clone
+studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
+considering the massive size of the two datasets and the search space
+of at least 15 Simian and 5 NiCad parameters, we are unable to search
+for the best configurations of the tools. Thus, we decided to
+configure Simian and NiCad using two established configurations:
+(1)~the tools' default configurations chosen by the tools' creators
+(denoted as \textit{D}), and (2)~the discovered configurations for
+Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
+of optimising clone detectors' configurations based on clone agreement
+(denoted by \textit{E}). The details of the two configurations are
+described in \Cref{t:param_tuning}. Having two clone detectors, Simian
+(denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two
+chosen configurations (\textit{D} and \textit{E}) each, we used
+Bellon's good and ok-match for agreement in four possible pair-wise
+combinations: $S_{D}$--$N_{D}$, $S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$,
+and $S_{E}$--$N_{E}$.
 
@@
 
-We followed the experimental framework and detected clones between Stack Overflow and Qualitas corpus using the two selected clone detectors.
-To answer RQ1, we computed statistics on clones discovered by the tools.
-To answer RQ2, we manually investigated online clone pair candidates and categorised them using our patterns of online code cloning.
-The patterns were derived from Kapser et al.~\cite{Kapser2003} and augmented by common patterns found in our data set.
-For RQ3, we looked at the true positive clone pairs and checked if they are still up-to-date.
-Similarly, for RQ4, we also looked at the license of each clone and checked for a possibility of licensing violation.
+We used the experimental framework (\Cref{fig:exp_framework}) to
+detect clones between Stack Overflow and the Qualitas corpus using the
+two selected clone detectors. To answer RQ1, we computed statistics on
+discovered clones. To answer RQ2, we manually investigated online
+clone pair candidates and categorised them using patterns of online
+code cloning. The patterns were derived from Kapser et
+al.~\cite{Kapser2003} and augmented by common patterns found in our
+data set. For RQ3, we looked at the true positive clone pairs and
+checked if they have been changed since they have been
+cloned. Similarly, for RQ4, we looked at the license of each
+clone and checked for a possibility of a licensing violation.
 
@@
 
-\begin{figure*}
-		\centering
-		\begin{minipage}{.4\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{hist_sd}
-			\caption*{$S_D$ clones}
-		\end{minipage}%
-		\hspace{5ex}
-		\begin{minipage}{0.4\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{hist_nd}
-			\caption*{$N_D$ clones}
-		\end{minipage}
-		\\
-		\begin{minipage}{.4\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{hist_se}
-			\caption*{$S_E$ clones}
-		\end{minipage}%
-		\hspace{5ex}
-		\begin{minipage}{0.4\textwidth}
-			\centering
-			\includegraphics[width=\linewidth]{hist_ne}
-			\caption*{$N_E$ clones}
-		\end{minipage}
-	\caption{\FIXME{Useful?}~Distribution of online clones between Stack Overflow snippets and Qualitas projects}
-	\label{fig:histogram}
-\end{figure*}
-
-The clone statistics obtained from running Simian and NiCad are presented in \Cref{tab:raw_stats}.
-Simian with the default configuration ($S_D$) reports clones in 1,086 snippets, approximately 1\% of the 144,064 Stack Overflow snippets, associated with 92 Qualitas projects.
-Simian with the EvaClone configuration ($S_E$) reports 1,531 snippets containing clones associated with 111 Qualitas projects.
-NiCad with the default configuration ($N_D$) reports clones between 1,392 Stack Overflow code snippets and 82 Qualitas projects.
-NiCad with the EvaClone configuration ($N_E$) reports the largest number of 12,886 cloned snippets mainly due to its relaxed configurations.
-The $N_E$ snippets are associate with 88 Qualitas projects.
-We encountered NiCad failures with a few Qualitas projects.~$N_D$ could not detect clones in \textsf{hibernate} due to clustering errors.
-$N_E$ generated renaming errors for 5 projects including \textsf{vuze}, \textsf{hibernate}, \textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}.
-We have contacted the creator of NiCad regarding the issues.
-They identified these issues as problems of long file paths and TXL grammars which will be fixed in the next NiCad releases.
-\Cref{fig:histogram} illustrates the distribution of online code clones reported by $S_D$, $N_D$, $S_E$ and $N_E$ respectively.
-We can see that the distribution is right skewed.
-There are only a few Stack Overflow snippets and Qualitas projects that are outliers containing a larger number of clones compared to the others.
-
-In terms of the number of clone pairs, $S_D$ reports 67,570 clone pairs while $N_D$ reports 632,855 clone pairs.
-$S_E$ and $N_E$ report a larger clone pair amount of 63,635,844 and 251,449,849 pairs respectively.
-This is expected since EvaClone configurations prefer recall~\cite{Wang2013}.
-%Using $S_D$, we found 62 clones in average originating from a single Stack Overflow snippet.
-62 and 455 respectively.
-On the other hand, $S_E$ and $N_E$ have a much larger number of 63 and 251 million clone pairs per snippet on average.
-The average clone size reported by $S_D$ is 9.11 lines which is bigger than $S_E$ (5.95 lines).
-Similarly, $N_D$ has an average clone size of 10.85 lines which is bigger than 6.28 lines reported by $N_E$.
-We can see from the statistics that EvaClone tunes the tools to report smaller clones.
-For the cloned Stack Overflow snippets, the average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\%  respectively.
-%A quick manual check of Simian's clone report revealed that there were 11 problematic snippets.
-These 11 snippets triggered Simian to generate large clone clusters containing a huge number of false clones from array initialisation.
-Hence, their clones were removed from further analyses.
-
-\textbf{To answer RQ1, with the four configurations of Simian and NiCad, we found online code clones in 1,086 ($S_D$), 1,531 ($S_E$), 1,392 ($N_D$) and 12,886 ($N_E$) Stack Overflow code snippets.
-They are associated with 92, 111, 82 and 88 Qualitas projects respectively.}
+% \begin{figure*}
+% 		\centering
+% 		\begin{minipage}{.4\textwidth}
+% 			\centering
+% 			\includegraphics[width=\linewidth]{hist_sd}
+% 			\caption*{$S_D$ clones}
+% 		\end{minipage}%
+% 		\hspace{5ex}
+% 		\begin{minipage}{0.4\textwidth}
+% 			\centering
+% 			\includegraphics[width=\linewidth]{hist_nd}
+% 			\caption*{$N_D$ clones}
+% 		\end{minipage}
+% 		\\
+% 		\begin{minipage}{.4\textwidth}
+% 			\centering
+% 			\includegraphics[width=\linewidth]{hist_se}
+% 			\caption*{$S_E$ clones}
+% 		\end{minipage}%
+% 		\hspace{5ex}
+% 		\begin{minipage}{0.4\textwidth}
+% 			\centering
+% 			\includegraphics[width=\linewidth]{hist_ne}
+% 			\caption*{$N_E$ clones}
+% 		\end{minipage}
+% 	\caption{\FIXME{Useful?}~Distribution of online clones between Stack Overflow snippets and Qualitas projects}
+% 	\label{fig:histogram}
+% \end{figure*}
+
+The statistics on clones obtained from running Simian and NiCad are
+presented in \Cref{tab:raw_stats}. Simian in the default configuration
+($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
+144,064 Stack Overflow snippets, associated with 92 Qualitas
+projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
+snippets containing clones associated with 111 Qualitas
+projects. NiCad in the default configuration ($N_D$) reported clones
+between 1,392 Stack Overflow code snippets and 82 Qualitas
+projects. NiCad in the EvaClone configuration ($N_E$) reported the
+largest number of 12,886 cloned snippets mainly due to the more
+relaxed configuration. The $N_E$ snippets are associated with 88
+Qualitas projects. We encountered NiCad failures with a few Qualitas
+projects.~$N_D$ could not detect clones in \textsf{hibernate} due to
+clustering errors. $N_E$ generated renaming errors \FIXME{What are
+  renaming errors?}  for 5 projects including \textsf{vuze},
+\textsf{hibernate}, \textsf{myfaces}, \textsf{netbeans}, and
+\textsf{spring}. We have contacted the creator of NiCad regarding the
+issues. They identified the issues as problems in the TXL grammar and
+as problems of long file paths, and will be fixed in the next NiCad
+releases.
+
+% \Cref{fig:histogram} illustrates the distribution of online code
+% clones reported by $S_D$, $N_D$, $S_E$ and $N_E$ respectively. We can
+% see that the distribution is right skewed. There are only a few Stack
+% Overflow snippets and Qualitas projects that are outliers containing a
+% larger number of clones compared to the others.
+
+In terms of the number of clone pairs, $S_D$ reports 67,570 clone
+pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
+much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
+respectively. This is expected since EvaClone configurations prefer
+recall~\cite{Wang2013}.
+% Using $S_D$, we found 62 clones in average originating from a single
+% Stack Overflow snippet. 62 and 455 respectively. On the other hand,
+% $S_E$ and $N_E$ have a much larger number of 63 and 251 million
+% clone pairs per snippet on average.
+The average clone size reported by $S_D$ is 9.11 lines which is bigger
+than for $S_E$ (5.95 lines). Similarly, $N_D$ has an average clone
+size of 10.85 lines which is bigger than 6.28 lines reported by
+$N_E$. The drop in size is due to the EvaClone configuration with a
+smaller minimum size (\Cref{t:param_tuning}). For the cloned Stack
+Overflow snippets, the average ratio of cloned code for $S_D$, $S_E$,
+$N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\% respectively.
+% A quick manual check of Simian's clone report revealed that there
+% were 11 problematic snippets. These 11 snippets triggered Simian to
+% generate large clone clusters containing a huge number of false
+% clones from array initialisation. Hence, their clones were removed
+% from further analyses.
+
+\textbf{To answer RQ1, with the four configurations of Simian and
+  NiCad, we found online code clones in 1,086 ($S_D$), 1,531 ($S_E$),
+  1,392 ($N_D$) and 12,886 ($N_E$) Stack Overflow code snippets. They
+  are associated with 92, 111, 82 and 88 Qualitas projects
+  respectively, i.e.~most Qualitas projects share similar code with
+  Stack Overflow code snippets.}
+
+% FIXME
+% However, as it is well known that the precision of clone detectors is
+% not very good, it is clear that the above numbers may not be
+% representative for real code clones and we ...
 

### 2017-02-18 cloneoverflow-latex/cloneoverflow.tex
Restructured Section 2.
Moved patterns of online cloning to Section 2 (2.4.1)
Small change in the code example.

@@
           /* Code in Stack Overflow post ID 22315734 */                  /* WritableComparator.java (2016-09-26) */
-          public int compare (byte[] b1,int s1,int l1,                   public int compare(byte[] b1,int s1,int l1,
+          public int compare(byte[] b1,int s1,int l1,                    public int compare(byte[] b1,int s1,int l1,
                              byte[] b2,int s2,int l2) {                                     byte[] b2,int s2,int l2) {
@@
 
+\subsection{Clone Detection Parameter Tuning}
+
+We were aware of effects of configurations to clone detection results
+and the importance of searching for optimised configurations in
+empirical clone
+studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
+considering the massive size of the two datasets and the search space
+of at least 15 Simian and 5 NiCad parameters, we are unable to search
+for the best configurations of the tools. Thus, we decided to
+configure Simian and NiCad using two established configurations:
+(1)~the tools' default configurations chosen by the tools' creators
+(denoted as \textit{D}), and (2)~the discovered configurations for
+Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
+of optimising clone detectors' configurations based on clone agreement
+(denoted by \textit{E}). The details of the two configurations are
+described in \Cref{t:param_tuning}.
+
+\begin{table}
+	\centering
+	\caption{Configurations of Simian and NiCad}
+	\label{t:param_tuning}
+%	\resizebox{\columnwidth}{!}{%
+	\small
+	\begin{tabular}{p{0.7cm}|p{2.4cm}|p{3.5cm}}
+		\hline 
+		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
+		\hline
+		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, \newline ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
+		\hline 
+		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=1000 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming,\newline literal abstraction \\
+		\hline
+	\end{tabular} %
+%}
+\end{table}
+
 \subsection{Filtering Clone Candidates}
@@
 
-\subsection{Clone Detection Parameter Tuning}
-
-We were aware of effects of configurations to clone detection results
-and the importance of searching for optimised configurations in
-empirical clone
-studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
-considering the massive size of the two datasets and the search space
-of at least 15 Simian and 5 NiCad parameters, we are unable to search
-for the best configurations of the tools. Thus, we decided to
-configure Simian and NiCad using two established configurations:
-(1)~the tools' default configurations chosen by the tools' creators
-(denoted as \textit{D}), and (2)~the discovered configurations for
-Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
-of optimising clone detectors' configurations based on clone agreement
-(denoted by \textit{E}). The details of the two configurations are
-described in \Cref{t:param_tuning}. Having two clone detectors, Simian
+Having two clone detectors, Simian
 (denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two
@@
 	\centering
-	\caption{Configurations of Simian and NiCad}
-	\label{t:param_tuning}
-%	\resizebox{\columnwidth}{!}{%
-	\small
-	\begin{tabular}{p{0.7cm}|p{2.4cm}|p{3.5cm}}
-		\hline 
-		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
-		\hline
-		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, \newline ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
-		\hline 
-		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=1000 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming,\newline literal abstraction \\
+	\caption{The seven patterns of online code cloning}
+	\label{tab:classification_scheme}
+	\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{c|p{8.4cm}}
+			\hline 
+			Patt. & Descriptions \\ 
+			\hline 
+			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
+			\hline 
+			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
+			\hline 
+			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
+			\hline 
+			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
+			\hline 
+			BP & Boiler-plate or IDE auto-generated \\ 
+			\hline 
+			IN & Inheritance, interface implementation  \\ 
+			\hline 
+			AC & Accidental similarity, false clones \\ 
 			\hline 
 		\end{tabular}  %
-%}
+	}
 \end{table}
+
+\subsubsection{The Seven Patterns of Online Code Cloning}
+
+We are interested in the analysis of the patterns of online code clones.
+We studied the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008} and performed a small study to evaluate its applicability to our study.
+Using the $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet.
+We selected these four criteria so that we could cover the online clones from various aspects.
+We selected the top 10 from each ranking and obtained 34 unique Stack Overflow snippets.
+The snippets were associated with 697 clone pairs.
+Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating.
+
+The benefit of the study is two-folded.
+We evaluated Kapser's cloning patterns and also observed the common cloning patterns from the 697 clone pairs.
+\textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.} After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns .
+The seven patterns include QS, SQ, EX, UD, BP, IN, and AC as presented in \Cref{tab:classification_scheme}.
+Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have evidence to be copied from Qualitas to Stack Overflow.
+The evidence of copying can be found in comments in the Qualitas source code or in the Stack Overflow post's contents.
+Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with evidence, in the opposite direction to QS.
+Pattern EX (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources.
+Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or highly similar clones between Qualitas and Stack Overflow but where we could not find any attribution of copying.
+%The UD clones are also unique enough to not be a boiler-plate code.
+Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components.
+Pattern IN (\textbf{In}heritance/Interface) is cloning by inheritance of the same super class or implementation of the same interface.
+These two activities usually result in similar overriding methods.
+The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs.
+These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements.
+
+%With the online cloning patterns, we could calculate the number of true and false positives. %We are looking for unique and meaningful clones in this study. Thus,
+
+\subsubsection{Classification of Clone Candidates}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{classification_process}
+	\caption{Online code clone classification process}
+	\label{fig:classification_process}
+\end{figure}
+
+The online clone classification follows the steps depicted in \Cref{fig:classification_process}.
+First, we look at a pair of clone fragments to see their similarity.
+If they are accidentally similar clones after code normalisation or false positive clones from the clone detection tools, we classify the pair into AC.
+If the two fragments are boiler-plate code, the pair is classified into BP.
+If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN.
+If the pair is not BP, IN, or AC, we start a detailed investigation.
+We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying.
+If evidence of copying has been found from a Qualitas project, the pair is classified in QS.
+In several occasions, we used extra information such as questions' contents, name of posters, and tags to gain better understanding.
+On the other hand, if the source code from the Qualitas project mentions copying from Stack Overflow, the pair is classified into SQ.
+If there is evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX.
+Lastly, if there is no evidence of copying in any direction but the clone fragments are highly similar, we classify them into UD.
 
@@
 projects.~$N_D$ could not detect clones in \textsf{hibernate} due to
-clustering errors. $N_E$ generated renaming errors \FIXME{What are
-  renaming errors?}  for 5 projects including \textsf{vuze},
+clustering errors. $N_E$ generated errors during code normalisation by 
+variable renaming for 5 projects including \textsf{vuze},
 \textsf{hibernate}, \textsf{myfaces}, \textsf{netbeans}, and
@@
 
-\begin{table}
-	\centering
-	\caption{The seven patterns of online code cloning}
-	\label{tab:classification_scheme}
-	\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{c|p{8.4cm}}
-			\hline 
-			Patt. & Descriptions \\ 
-			\hline 
-			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\ 
-			\hline 
-			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\ 
-			\hline 
-			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
-			\hline 
-			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
-			\hline 
-			BP & Boiler-plate or IDE auto-generated \\ 
-			\hline 
-			IN & Inheritance, interface implementation  \\ 
-			\hline 
-			AC & Accidental similarity, false clones \\ 
-			\hline 
-		\end{tabular}  %
-	}
-\end{table}
-
-\subsubsection{The Seven Patterns of Online Code Cloning}
-
-We are interested in the analysis of the patterns of online code clones.
-We studied the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008} and performed a small study to evaluate its applicability to our study.
-Using the $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet.
-We selected these four criteria so that we could cover the online clones from various aspects.
-We selected the top 10 from each ranking and obtained 34 unique Stack Overflow snippets.
-The snippets were associated with 697 clone pairs.
-Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating.
-
-The benefit of the study is two-folded.
-We evaluated Kapser's cloning patterns and also observed the common cloning patterns from the 697 clone pairs.
-\textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.} After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns .
-The seven patterns include QS, SQ, EX, UD, BP, IN, and AC as presented in \Cref{tab:classification_scheme}.
-Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have evidence to be copied from Qualitas to Stack Overflow.
-The evidence of copying can be found in comments in the Qualitas source code or in the Stack Overflow post's contents.
-Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with evidence, in the opposite direction to QS.
-Pattern EX (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources.
-Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or highly similar clones between Qualitas and Stack Overflow but where we could not find any attribution of copying.
-%The UD clones are also unique enough to not be a boiler-plate code.
-Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components.
-Pattern IN (\textbf{In}heritance/Interface) is cloning by inheritance of the same super class or implementation of the same interface.
-These two activities usually result in similar overriding methods.
-The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs.
-These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements.
-
-%With the online cloning patterns, we could calculate the number of true and false positives. %We are looking for unique and meaningful clones in this study. Thus,
-
-\subsubsection{Classification of Clone Candidates}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{classification_process}
-	\caption{Online code clone classification process}
-	\label{fig:classification_process}
-\end{figure}
-
-The online clone classification follows the steps depicted in \Cref{fig:classification_process}.
-First, we look at a pair of clone fragments to see their similarity.
-If they are accidentally similar clones after code normalisation or false positive clones from the clone detection tools, we classify the pair into AC.
-If the two fragments are boiler-plate code, the pair is classified into BP.
-If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN.
-If the pair is not BP, IN, or AC, we start a detailed investigation.
-We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying.
-If evidence of copying has been found from a Qualitas project, the pair is classified in QS.
-In several occasions, we used extra information such as questions' contents, name of posters, and tags to gain better understanding.
-On the other hand, if the source code from the Qualitas project mentions copying from Stack Overflow, the pair is classified into SQ.
-If there is evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX.
-Lastly, if there is no evidence of copying in any direction but the clone fragments are highly similar, we classify them into UD.
-
 We had in total 31,946 online clone pair candidates for classifications.
@@
 They had a high probability to be trivial clones.
-
 Before performing manual classification, we used regular expressions to automatically classify {\small\texttt{equals()}} and the remaining getters/setters.

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Updated the diagram to reflect changes of abbreviations.
Moved much of the agreed/disagreed discussion into Section 2.
Finished Section 2 and 3.

@@
   \label{tab:datasets}
-  \small
+  %\small
   \begin{tabular}{lrr}
@@
 
-\subsection{Clone Detection Parameter Tuning}
+\subsection{Clone Detection Configuration}
 
@@
 
+We encountered NiCad failures with a few Qualitas projects.~$N_D$
+could not detect clones in \textsf{hibernate} due to clustering
+errors. $N_E$ generated errors during code normalisation for 5
+projects including \textsf{vuze}, \textsf{hibernate},
+\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
+contacted the creator of NiCad regarding the issues. They identified
+the issues as problems in the TXL grammar and as problems of long file
+paths, and will be fixed in the next NiCad releases.
+
 \begin{table}
@@
 
-The number of clones detected in large-scale datasets can be huge. In
-our study, there are in total 315,786,118 clone pairs reported. It is
+The number of online clone pairs reported by running Simian and NiCad
+are presented in \Cref{tab:raw_stats}. $S_D$ reports 67,570 clone
+pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
+much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
+respectively. This is expected since EvaClone configurations prefer
+recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
+9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
+$N_D$ has an average clone size of 10.85 lines which is bigger than
+6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
+configuration with a smaller minimum size (\Cref{t:param_tuning}).
+
+\begin{table}
+  \centering
+  \caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
+  \label{tab:orig_stats}
+  %\small
+  %\resizebox{\columnwidth}{!}{%
+    \begin{tabular}{l|r|r|r|r}
+      \hline
+      Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
+      \hline
+      Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
+      % Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
+      Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
+      \hline
+    \end{tabular} %
+  %}
+\end{table}
+
+As there are in total 315,786,118 clone pairs reported, it is
 infeasible for humans to manually validate them all. Instead of
@@
 between 0 and 1. A \textit{good} clone pair has stronger agreement
-than an \textit{ok} pair. We follow the original definitions of
-\textit{good}- and \textit{ok}-match introduced in Bellon's
-paper~\cite{Bellon2007}.
+than an \textit{ok} pair. We follow the original definitions of good-
+and ok-match introduced in Bellon's paper~\cite{Bellon2007}.
 
@@
 \noindent%
-Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$ are called a \textit{\textit{good}(t)} iff, for threshold $t \in [0,1]$ holds 
+Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$
+are called a \textit{\textit{good-match}(t)} or \textit{ok-match(t)}  iff, for threshold $t \in [0,1]$ holds 
 %\squeezeup
-\begin{equation}
-good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq t.
-\end{equation}
-%
-Similarly for an \textit{ok-match(t)} pair
-%\squeezeup
-\begin{equation}
-ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) \geq t.
-\end{equation}
-
-Using the good and ok-match criteria with a predefined threshold
+\begin{align*}
+good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t\\
+ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t
+\end{align*}
+
+Using the good- and ok-match criteria with a predefined threshold
 \textit{t}, we can prune the 315 million candidate clone pairs for
@@
 
-Having two clone detectors, Simian
-(denoted as \textit{S}) and NiCad (denoted as \textit{N}), with two
-chosen configurations (\textit{D} and \textit{E}) each, we used
-Bellon's good and ok-match for agreement in four possible pair-wise
-combinations: $S_{D}$--$N_{D}$, $S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$,
-and $S_{E}$--$N_{E}$.
+Having two clone detectors, Simian (denoted as \textit{S}) and NiCad
+(denoted as \textit{N}), with two chosen configurations (\textit{D}
+and \textit{E}) each, we used Bellon's good and ok-match for agreement
+in four possible pair-wise combinations: $S_{D}$--$N_{D}$,
+$S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$, and $S_{E}$--$N_{E}$.
+
+\subsubsection{Agreed clone pairs}
+
+As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
+agreement filtering using Bellon's criteria\footnote{Similar to the
+  original study, we selected a threshold \textit{t} of 0.7 for both
+  \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
+of \textit{good} clone pairs is 2,308 and the number of \textit{ok}
+clone pairs is 31,729, 0.1\textperthousand~of all reported clone
+pairs.  Agreed clone pairs are clone pairs that pass Bellon's
+\textit{good} or \textit{ok} criteria, and therefore are selected for
+manual classification.  Due to NiCad's failures, we do not have NiCad
+clones from five Qualitas projects in the agreed clone pairs. Simian
+clones of the same projects also disappeared from the agreed clone
+pairs since they could not be matched.
+
+\begin{table}
+  \centering
+  \caption{Distribution of the agreed clone pairs}
+  \label{t_agreed_good_clone_pairs}
+  %\small
+  %	\resizebox{\columnwidth}{!}{%
+  \begin{tabular}{l|r|r|r|r|r}
+    \hline
+    Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
+    \hline
+    \textit{good} & 18 & 26 & 10 & 2,267 & 2,308 \\
+    \textit{ok} & 11,467 & 993 & 79 & 20,021 & 31,729  \\
+    \hline
+  \end{tabular} %
+  % }
+\end{table}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{good-ok_pairs-crop}
+	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
+	\label{fig:good-ok-pairs}
+\end{figure}
+
+The distribution of \textit{good} clone pairs between the four
+combinations of \textit{D} and \textit{E} configurations are listed in
+\Cref{t_agreed_good_clone_pairs}.  There are 2,321 (2,308 unique)
+\textit{good} pairs consisting of 18 pairs from $S_D$--$N_D$, 26 pairs
+from $S_D$--$N_E$, 10 pairs from $S_E$--$N_D$, and 2,267 pairs from
+$S_E$--$N_E$. There are 32,560 (31,729 unique) \textit{ok}
+pairs\footnote{This excludes the subsumed 2,308 \textit{good}
+  pairs. According to the definition, \textit{ok} pairs always subsume
+  \textit{good} pairs.}. We obtained 11,467; 993; 79; and 20,021 pairs
+from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
+respectively. Between the four configuration sets, there is
+considerable amount of clone pairs shared between two adjacent sets
+(as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair
+that is agreed by all four combinations.
+
+\subsubsection{Disagreed clone pairs}
+
+\begin{table}
+	\centering
+	\caption{Disagreed clone pairs before and after filtering.}
+	\label{tab:online_clone_pairs}
+	%\small
+	%	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|c|c|c|c|r}
+		\hline
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-6}
+		& & \textit{L} & \textit{S} & \textit{M} & \textit{G} & \\
+		\hline 
+		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
+		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
+		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
+		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
+		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & \checkmark & 88 \\ 
+		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+%		\hline
+%		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
+		\hline
+		\multicolumn{7}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{M}=irr.~methods, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
+	\end{tabular} %
+	%}
+\end{table}
+
+The disagreed clone pairs are clone pairs that are reported by a
+single tool, either Simian or NiCad, and do not have agreement with
+the other tool. The disagreement can be from a misalignment of clone
+lines or completely non-overlapping clones. The disagreed pairs from
+Simian include clone pairs in the projects with NiCad's errors (1
+project from $N_D$ and 5 from $N_E$).  With the four configuration
+combinations, we decided to investigate only $S_D$, and $N_D$, and
+dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs
+(60 and 250 millions respectively). Moreover, $S_E$ and $N_E$ contain
+a large number of false positives due to the recall preference of
+their EvaClone configurations.
+
+Even choosing only the default configurations, the number of disagreed
+clone pair candidates is still too large for manual inspection (67,570
+for $S_D$ and 632,855 pairs for $N_D$). We applied four filters: clone
+size, irrelevant methods, similarity threshold, and good/ok pairs. For
+the \emph{clone size filter}, we raised the minimum clone size to 10 lines
+since larger clones are more interesting, while smaller ones tend to
+be false clones~\cite{Saini2016}.
+% Since the 10--line threshold is already the default configuration for
+% NiCad, this filter is applied to Simian only (Simian's default
+% configuration has a minimum clone size of 6 lines).
+The \emph{irrelevant methods filter} removes clones of
+\verb|hashCode()| methods and getters/setters which are almost always
+false clones. The third filter, \emph{similarity threshold}, applies
+only to NiCad clone pairs since Simian does not provide a similarity
+configuration. The last filter, \emph{good/ok pairs}, removes the
+clone pairs that already exist in the agreed clone sets.
+
+As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the
+results using clone size, irrelevant methods, and gook/ok pairs. The
+three filters reduced the number of $S_D$ clones to 17,801 pairs.  We
+filtered $N_D$ clones by additionally raising the similarity
+threshold. We increased NiCad's similarity threshold from 70\% to 85\%
+(by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We
+tried varying the UPI from 70\% (default, 632,855 pairs), 80\%
+(25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that
+85\% similarity provided the best balance in terms of the amount of
+reported clones and precision for small clones. Using this filter
+along with the other three filters, we reduced the number of $N_D$
+clones to 88 pairs.
+
+\subsubsection{Manual Inspection Data Set}
+
+For the manual inspection of clone pairs, we selected all
+\textit{good} pairs (2,308) and the \textit{ok} pairs for
+$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (11,749), but we ignored
+20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
+their large number of clones and the very small average clone sizes of
+5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
+probability of being trivial clones. We refer to the set of clone
+pairs as the \textit{good} set and the \textit{ok'} set.
+
+Together with the 17,801 (referred as $S_D'$ set) and 88 (referred as
+$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
+$N_D$, we ended up with a set of 31,946 online clone pair candidates
+for manual inspection.
 
@@
 	\label{tab:classification_scheme}
-	\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{c|p{8.4cm}}
-			\hline 
-			Patt. & Descriptions \\ 
+	%\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{c@{~~}p{7.35cm}}
+			\hline 
+			Patt. & Description \\ 
 			\hline 
 			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\
-			\hline 
+
 			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\
-			\hline 
+
 			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
-			\hline 
+
 			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
@@
 			BP & Boiler-plate or IDE auto-generated \\
-			\hline 
+
 			IN & Inheritance, interface implementation  \\
-			\hline 
+
 			AC & Accidental similarity, false clones \\ 
@@
 		\end{tabular}  %
-	}
+	%}
 \end{table}
 
-\subsubsection{The Seven Patterns of Online Code Cloning}
-
-We are interested in the analysis of the patterns of online code clones.
-We studied the 8 patterns of cloning from Kapser et al.~\cite{Kapser2006,Kapser2008} and performed a small study to evaluate its applicability to our study.
-Using the $S_D$ clone report, snippets are ranked according to 1) clone pair frequency, 2) popularity (i.e.~number of associated Qualitas projects), 3) clone size in SLOC, and 4) ratio of cloned code per snippet.
-We selected these four criteria so that we could cover the online clones from various aspects.
-We selected the top 10 from each ranking and obtained 34 unique Stack Overflow snippets.
-The snippets were associated with 697 clone pairs.
-Using Kapser's cloning patterns, the clone pairs were categorised into either Customisation or Templating.
-
-The benefit of the study is two-folded.
-We evaluated Kapser's cloning patterns and also observed the common cloning patterns from the 697 clone pairs.
-\textbf{Clearly Kapser's cloning patterns are too broad for our study and a more suitable and fine-grained classification scheme is needed.} After the study, we adopted one of Kapser's cloning patterns, boiler-plate code and API/library protocol, and defined 6 new cloning patterns .
-The seven patterns include QS, SQ, EX, UD, BP, IN, and AC as presented in \Cref{tab:classification_scheme}.
-Pattern QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have evidence to be copied from Qualitas to Stack Overflow.
-The evidence of copying can be found in comments in the Qualitas source code or in the Stack Overflow post's contents.
-Pattern SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with evidence, in the opposite direction to QS.
-Pattern EX (\textbf{Ex}ternal Sources) is cloning that has evidence of copying from a single or multiple external sources.
-Pattern UD (\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or highly similar clones between Qualitas and Stack Overflow but where we could not find any attribution of copying.
-%The UD clones are also unique enough to not be a boiler-plate code.
-Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones containing boiler-plate code of {\small\verb|equals()|} methods, getters/setters, or IDE-generated code such as GUI components.
-Pattern IN (\textbf{In}heritance/Interface) is cloning by inheritance of the same super class or implementation of the same interface.
-These two activities usually result in similar overriding methods.
-The last pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents accidentally similar clone pairs.
-These are mainly false positive clones from the clone detectors such as similar {\small\texttt{try-catch}} statements.
-
-%With the online cloning patterns, we could calculate the number of true and false positives. %We are looking for unique and meaningful clones in this study. Thus,
-
-\subsubsection{Classification of Clone Candidates}
+\subsection{The Seven Patterns of Online Code Cloning}
+
+As we are interested in the patterns of online code clones, we studied
+the 8 patterns of cloning from Kapser et
+al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
+evaluate its applicability to our study. Using the $S_D$ clone report,
+snippets were ranked according to (1)~clone pair frequency,
+(2)~popularity (i.e.~number of associated Qualitas projects),
+(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
+selected these four criteria so that we could cover the online clones
+from various aspects. We selected the top 10 from each ranking and
+obtained 34 unique Stack Overflow snippets. The snippets were
+associated with 697 clone pairs. Using Kapser's cloning patterns, the
+clone pairs were categorised into either Customisation or Templating.
+However, Kapser's cloning patterns are too broad for our study and a
+more suitable and fine-grained classification scheme is needed. After
+the preliminary study, we adopted one of Kapser's cloning patterns,
+\emph{boiler-plate code} and \emph{API/library protocol}, and defined
+6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
+IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
+QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
+that have evidence of being copied from a Qualitas project to Stack
+Overflow. The evidence of copying can be found in comments in the
+Qualitas source code or in the Stack Overflow post's contents. Pattern
+SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
+evidence, in the opposite direction from Stack Overflow to a Qualitas
+project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
+evidence of copying from a single or multiple external sources to
+Stack Overflow and to a Qualitas project.  Pattern UD
+(\textbf{U}nknown \textbf{D}irection) is cloning that creates
+identical or highly similar clones between Qualitas and Stack Overflow
+but where we could not find any attribution of copying.
+
+Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
+containing boiler-plate code of {\small\verb|equals()|} methods,
+getters/setters, or IDE-generated code such as GUI components. Pattern
+IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
+same super class or implementation of the same interface. These two
+activities usually result in similar overriding methods. The last
+pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents
+accidentally similar clone pairs. These are mainly false positive
+clones from the clone detectors such as similar
+{\small\texttt{try-catch}} statements.
 
@@
 
-The online clone classification follows the steps depicted in \Cref{fig:classification_process}.
-First, we look at a pair of clone fragments to see their similarity.
-If they are accidentally similar clones after code normalisation or false positive clones from the clone detection tools, we classify the pair into AC.
-If the two fragments are boiler-plate code, the pair is classified into BP.
-If they implement the same interface or inherited the same class and share similar overriding methods, the pair is classified into IN.
-If the pair is not BP, IN, or AC, we start a detailed investigation.
-We check the corresponding Stack Overflow post, read through it carefully and look for any evidence mentioning code copying.
-If evidence of copying has been found from a Qualitas project, the pair is classified in QS.
-In several occasions, we used extra information such as questions' contents, name of posters, and tags to gain better understanding.
-On the other hand, if the source code from the Qualitas project mentions copying from Stack Overflow, the pair is classified into SQ.
-If there is evidence of copying from an external source instead of Qualitas projects, the pair is classified into EX.
-Lastly, if there is no evidence of copying in any direction but the clone fragments are highly similar, we classify them into UD.
+The classification of all 31,946 online clone pairs followed the steps
+depicted in \Cref{fig:classification_process}. First, we look at a
+pair of clone fragments to see their similarity. If they are
+accidentally similar clones after code normalisation or false positive
+clones from the clone detection tools, we classify the pair into
+\textbf{AC}. If the two fragments are boiler-plate code, the pair is
+classified into \textbf{BP}. If they implement the same interface or
+inherited the same class and share similar overriding methods, the
+pair is classified into \textbf{IN}. If the pair is not \textbf{BP},
+\textbf{IN}, or \textbf{AC}, we start a detailed investigation. We
+check the corresponding Stack Overflow post, read through it carefully
+and look for any evidence mentioning code copying. If evidence of
+copying has been found from a Qualitas project, the pair is classified
+in \textbf{QS}. In several occasions, we used extra information such
+as questions' contents, name of posters, and tags to gain a better
+understanding. On the other hand, if the source code from the Qualitas
+project mentions copying from Stack Overflow, the pair is classified
+into \textbf{SQ}. If there is evidence of copying from an external
+source instead of a Qualitas projects, the pair is classified into
+\textbf{EX}. Lastly, if there is no evidence of copying in any
+direction but the clone fragments are highly similar, we classify them
+into \textbf{UD}.
 
@@
 clone pair candidates and categorised them using patterns of online
-code cloning. The patterns were derived from Kapser et
-al.~\cite{Kapser2003} and augmented by common patterns found in our
-data set. For RQ3, we looked at the true positive clone pairs and
+code cloning. For RQ3, we looked at the true positive clone pairs and
 checked if they have been changed since they have been
-cloned. Similarly, for RQ4, we looked at the license of each
-clone and checked for a possibility of a licensing violation.
+cloned. Similarly, for RQ4, we looked at the license of each clone and
+checked for a possibility of a licensing violation.
 
@@
 	\label{tab:raw_stats}
-	\small
-	\resizebox{\columnwidth}{!}{%
+	%\small
+	%\resizebox{\columnwidth}{!}{%
 		\begin{tabular}{l|r|r|r|r}
@@
 			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
-			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
+%			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
 %			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
+%			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
 			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
@@
 		\end{tabular} %
-	}
+	%}
 \end{table}
@@
 relaxed configuration. The $N_E$ snippets are associated with 88
-Qualitas projects. We encountered NiCad failures with a few Qualitas
-projects.~$N_D$ could not detect clones in \textsf{hibernate} due to
-clustering errors. $N_E$ generated errors during code normalisation by 
-variable renaming for 5 projects including \textsf{vuze},
-\textsf{hibernate}, \textsf{myfaces}, \textsf{netbeans}, and
-\textsf{spring}. We have contacted the creator of NiCad regarding the
-issues. They identified the issues as problems in the TXL grammar and
-as problems of long file paths, and will be fixed in the next NiCad
-releases.
-
-% \Cref{fig:histogram} illustrates the distribution of online code
-% clones reported by $S_D$, $N_D$, $S_E$ and $N_E$ respectively. We can
-% see that the distribution is right skewed. There are only a few Stack
-% Overflow snippets and Qualitas projects that are outliers containing a
-% larger number of clones compared to the others.
-
-In terms of the number of clone pairs, $S_D$ reports 67,570 clone
-pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
-much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
-respectively. This is expected since EvaClone configurations prefer
-recall~\cite{Wang2013}.
-% Using $S_D$, we found 62 clones in average originating from a single
-% Stack Overflow snippet. 62 and 455 respectively. On the other hand,
-% $S_E$ and $N_E$ have a much larger number of 63 and 251 million
-% clone pairs per snippet on average.
-The average clone size reported by $S_D$ is 9.11 lines which is bigger
-than for $S_E$ (5.95 lines). Similarly, $N_D$ has an average clone
-size of 10.85 lines which is bigger than 6.28 lines reported by
-$N_E$. The drop in size is due to the EvaClone configuration with a
-smaller minimum size (\Cref{t:param_tuning}). For the cloned Stack
-Overflow snippets, the average ratio of cloned code for $S_D$, $S_E$,
-$N_D$, and $N_E$ is 38\%, 50\%, 30\%, and 33\% respectively.
+Qualitas projects.  For the cloned Stack Overflow snippets, the
+average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
+38\%, 50\%, 30\%, and 33\% respectively.
 % A quick manual check of Simian's clone report revealed that there
@@
 
+However, using Bellon's criteria for matching clone pairs, only
+0.1\textperthousand~of all pairs are agreed by two tool/configuration
+combinations.
+
+\FIXME{Can you say something about the numbers only looking at the set
+  of pairs used for manual inspection?}
 % FIXME
 % However, as it is well known that the precision of clone detectors is
-% not very good, it is clear that the above numbers may not be
+c% not very good, it is clear that the above numbers may not be
 % representative for real code clones and we ...
@@
 \subsection{RQ2: Patterns of Online Code Cloning}
-
-We rely on a manual study to qualitatively investigate the patterns of online code cloning.
-To achieve this, we select a subset of the agreed clones using Bellon's criteria and a subset of the disagreed clones using clone filtering.
-We explain them in more detail below.
-
-\subsubsection{Agreed clone pairs}
-
-As displayed in \Cref{t_agreed_good_clone_pairs}, after we applied clone agreement filtering using Bellon's criteria, the number of \textit{good} clone pairs is 2,308 while the number of \textit{ok} clone pairs is 31,729.
-%The number of disagreed clone pairs ($S_D$, $N_D$) after filtering is 17,801 and 181 for Simian and NiCad respectively.
-The total number of clone candidates is 32,039 pairs.
-Agreed clone pairs are clone pairs that pass Bellon's \textit{good} or \textit{ok} criteria, and therefore are selected for manual classification.
-Similar to the original study, we select a threshold \textit{p} of 0.7 for both \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.
-%The number of projects processed by the clone detection tools are listed in \Cref{tab:projects_missing}.
-Due to NiCad's failures, we do not have NiCad clones from five Qualitas projects in the agreed clone pairs.
-Simian clones of the same projects also disappeared from the agreed clone pairs since they could not find matches.
-
-\begin{table}
-	\centering
-	\caption{Distribution of the agreed clone pairs}
-	\label{t_agreed_good_clone_pairs}
-	\small
-%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r|r}
-		\hline
-		Set & $S_DN_D$ & $S_DN_E$ & $S_EN_D$ & $S_EN_E$ & Unique \\
-		\hline
-		\textit{good} & 18 & 26 & 10 & 2,267 & 2,308 \\
-		\textit{ok} & 11,467 & 993 & 79 & 20,021 & 31,729  \\
-		\hline
-	\end{tabular} %
-%}
-\end{table}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{good-ok_pairs-crop}
-	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
-	\label{fig:good-ok-pairs}
-\end{figure}
-
-The distributions of \textit{good} clone pairs between four combinations of \textit{D} and \textit{E} configurations are listed in \Cref{t_agreed_good_clone_pairs}.
-%and depicted visually in \Cref{fig:good-ok-pairs}.
-There are 2,321 (2,308 unique) \textit{good} pairs consisting of 18 pairs from $S_DN_D$, 26 pairs from $S_DN_E$, 10 pairs from $S_EN_D$, and 2,267 pairs from $S_EN_E$.
-There are 32,560 (31,729 unique) \textit{ok} pairs\footnote{This excludes the subsumed 2,308 \textit{good} pairs.
-According to the definition, \textit{ok} pairs always subsume \textit{good} pairs.} We obtained 11,467; 993; 79; and 20,021 pairs from $S_DN_D$, $S_DN_E$, $S_EN_D$, and $S_EN_E$ respectively.
-Between the four configuration sets, there is considerable amount of clone pairs shared between two adjacent sets (as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair that is agreed by all four combinations.
-
-\subsubsection{Disagreed clone pairs}
-
-\begin{table}
-	\centering
-	\caption{Disagreed clone pairs before and after filtering.}
-	\label{tab:online_clone_pairs}
-	\small
-	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|c|c|c|c|r}
-		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-6}
-		& & \textit{L} & \textit{S} & \textit{R} & \textit{G} & \\
-		\hline 
-		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
-		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
-		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 632,855 & & \checkmark & \checkmark & \checkmark & 88 \\ 
-		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-%		\hline
-%		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
-		\hline
-		\multicolumn{7}{l}{*\textit{L}=line $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{R}=reg.~expressions, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
-	\end{tabular} %
-	%}
-\end{table}
-
-The disagreed clone pairs are clone pairs that are reported by a single tool, either Simian or NiCad, and do not have agreement with the other tool.
-The disagreement can be from a misalignment of clone lines or totally non-overlapping clones.
-The disagreed pairs from Simian cover clone pairs in the projects with NiCad's errors (1 projects from $N_D$ and 5 from $N_E$).
-%that are automatically missing from the agreed clone pairs.
-With the four configuration combinations, we decided to investigate only $S_D$, and $N_D$, and dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs (60 and 250 millions respectively).
-Moreover, $S_E$ and $N_E$ contain a large number of false positives due to the recall preference of their EvaClone configurations.
-
-Even choosing only the default configurations, the number of clone pair candidates are still very large for manual inspection (67,570 for $S_D$ and 632,855 pairs for $N_D$).
-We applied four filters: \textbf{clone line, regular expression, similarity threshold, and good/ok pairs}.
-For the clone line filter, we raised the minimum clone size to 10 line since larger clones are more interesting, while smaller ones tend to be false clones~\cite{Saini2016}.
-Since the 10--line threshold is already the default configuration for NiCad, this filter is applied to Simian only (Simian's default configurations has a minimum clone size of 6 lines).~The regular expression filter removes boiler-plate clones of \verb|hashCode()| methods and getters/setters.
-The third filter, similarity threshold, applies only to NiCad clone pairs since Simian does not provide this similarity configuration.
-The last filter, good/ok pairs, removes the clone pairs that have already existed in the agreed clone sets.
-% Moreover, the study of uniqueness of source code by Gabel and Su~\cite{Gabel2010} suggests that source code are unique when they are larger than seven lines.
 
@@
 	\label{tab:online_clone_classification_results}
-	\small
+	%\small
 	%	\resizebox{\columnwidth}{!}{%
@@
 		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 \\
-		\multirow{1}{*}{\textit{ok}} & 11,749 & 11,494 & 255 \\
+		\multirow{1}{*}{\textit{ok'}} & 11,749 & 11,494 & 255 \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 17,801 & 16,800 & 1,001 \\
-		\multirow{1}{*}{$N_D$} & 88 & 10 & 78 \\ 
+		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
+		\multirow{1}{*}{$N_D'$} & 88 & 10 & 78 \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
@@
 
-As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size, regular expressions, and gook/ok pairs.
-The three filters reduced the number of $S_D$ clones to 17,801 pairs.
-%For $N_D$, 10-line threshold is already a minimum NiCad's clone size.
-However, NiCad still reported much more clone pairs than Simian since it can detect type-3 clones.
-Thus, besides regular expressions and good/ok pair filters,
-We filtered $N_D$ clones by raising the similarity threshold.
-We increase NiCad's similarity threshold from 70\% to 85\% (by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15).
-We tried varying the UPI from 70\% (default -- 632,855 pairs), 80\% (25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that 85\% similarity provided the best balance in terms of the amount of reported clones and feasibility for manual investigation.
-Using this filter along with the regular expression and the good/ok pair filter, we reduced the size of $N_D$ clones to 88 pairs.
-
-%In our clone classification process, we used a script to automatically classify {\small\texttt{equals()}} clone pairs which  classifying 28,444 pairs out of 31,946 (more than half of the {\small\texttt{equals()}} pairs came from \textit{ok} and $S_D$ pairs).
-Finally, there are 3,502 pairs remaining which we manually classified them.
-The classification summary is shown in \Cref{tab:online_clone_classification_results}.
-
-%After classification, we found 668 non-trivial online code clones pairs between Stack Overflow and Qualitas or external sources.}
-
-We had in total 31,946 online clone pair candidates for classifications.
-2,308 and 11,749 were \textit{good} and \textit{ok} clone pairs respectively.
-17,801 and 88 clone pairs are from $S_D$ and $N_D$ after the filtering.
-Please note that we ignored 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to their large number of clones and the very small average clone sizes of 4.79 and 5.33 lines (see \Cref{tab:raw_stats}).
-They had a high probability to be trivial clones.
-Before performing manual classification, we used regular expressions to automatically classify {\small\texttt{equals()}} and the remaining getters/setters.
-As shown in \Cref{tab:online_clone_classification_results}, the automatic classifier helped us classified and captured 28,314 clone pairs into pattern BP.
-
-There were 3,632 pairs left for the manual check.
-The first author who has been working on clone detection research for two years took the role of the main investigator performing a manual classification of the 3,632 clone pairs.
-By consulting the cloning patterns, the main investigator went through each clone pair candidate, looked at the clones, and chose the most appropriate cloning pattern for the pair.
-%A relevant and useful observation was also recorded for each clone pair.
-
-To mitigate the human errors of the manual classification, the second author took the role of the validating investigator, performing a validation on 10\% (363 pairs) of the clone pairs judged by the main investigator.
-After the validation, the classifications from the two investigators were compared and 64 conflicts were found.
-The two investigators discussed and resolved 61 of them while the 3 conflicts were resolved by involving the third author.
-The classification results are shown in \Cref{tab:classification_good_o}.
-%We consider the clone pairs classified into pattern QS, SQ, UD, and EX as true positives.
-On the other hand, clones in pattern BP, IN, and AC are classified as false positives since they are trivial and not very interesting ones.
-\textbf{To answer RQ2, the classification results are explained and discussed below.}
-
-\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112 online clone pairs with evidences of cloning from Qualitas projects to Stack Overflow.
-They include 3, 14, 86, and 9 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
-Most of them have a statement in the Stack Overflow post saying that the code is ``copied'' or ``modified'' from a specific file or class in a Qualitas project.
-The most cloned projects are \textsf{hibernate} and \textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15 pairs), and \textsf{hadoop} (12 pairs).
-The clones are used as examples and are very similar to their original Qualitas code with limited modifications.
-
-\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find any clone pairs with evidence of cloning from Stack Overflow to Qualitas projects.
-
-\textbf{EX: External Sources.} We found 197 online clone pairs with evidences of cloning from external sources to Stack Overflow.
-They include 4, 41, 146, and 6 clone pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ respectively.
-
-These findings complement a study of clones between software projects~\cite{Svajlenko2014}.
-We found that the code cloning can also happen among different sources on the Internet just like software projects.
-There are 30 clone pairs that are originated from programming websites.
-For example, we found a clone of code snippet to convert numbers into words which is copied from www.rgagnon.com/javadetails/java-0426.html.
-Both the Stack Overflow and the \textsf{compiere} project source code contain an attribution to the original source.
-Another example is a code to generate graphical \textit{Perlin noise}.
-It is copied from http://mrl.nyu.edu/\textasciitilde perlin/noise/.
-The code is used in Stack Overflow and \textsf{aoi} project with attribution.
-%The original code of the 15 clone pairs do not have licensing information so these clones do not violate any license.
-There are other EX clone pairs are from third-party libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util}, \textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography project.
-
-\textbf{UD: Unknown Direction.} We found 382 online clone pairs with no evidence of cloning between Qualitas and Stack Overflow but with a high code similarity.
-They include 11, 42, 294, and 35 pairs from \textit{good}, \textit{ok}, $S_D$, and $N_D$ set respectively.
-The most cloned projects is \textsf{netbeans} with 95 clone pairs.
-Most of the clones are a large chunk of code handling GUI components.
-Although these GUI clones might be auto-generated by IDEs, we did not find any evidence.
-The second most cloned project is \textsf{jung2} (62 pairs), a network and graph framework, followed by \textsf{eclipse-SDK} (37 pairs).
-%There are several Stack Overflow snippets that are identical to code in \textsf{jung2}.
-
-\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs found in this study.
-Although we have removed some of the boiler-plate code with filters before the analysis, we still observed 28,749 clone pairs.
-The BP clone pairs account for 89.7\% of all clone pairs we classified.
-The majority of them are {\small{\texttt{equals()}}}.
-
-\textbf{IN: Inheritance/interface.} There were 111 clone pairs found to be similar because they implement the same interface or inheriting from the same class.
-An example is the two implementations of {\small{\texttt{MouseListener}}} that share similar {\small\texttt{@Override}} methods of {\small\texttt{mousePressed}}, and {\small\texttt{mouseReleased}}.
-
-\textbf{AC: Accidental Clones.} There were 2,418 accidental clone pairs.
-Mainly, they are false positive clones caused by code normalisation.
-%However, the original source code were still different enough when we manually classified them.
-Other clone instances include {\small\texttt{finally}} or {\small\texttt{try-catch}} clauses that were accidentally the same due to their very small sizes, and similar {\small\texttt{switch-case}} statements.
+\FIXME{Why equals here but not hashcode? Why isn't it the same
+  irrelevant methods filter?}
+
+We rely on a manual study to qualitatively investigate the patterns of
+online code cloning. To achieve this, we classified all 31,946
+selected clone pairs according to the process shown in
+\Cref{fig:classification_process}.  Before performing the manual
+classification, we used the irrelevant method filter to automatically
+classify {\small\texttt{equals()}} and the remaining
+getters/setters. As shown in
+\Cref{tab:online_clone_classification_results}, the automatic
+classifier helped us classified and captured 28,314 clone pairs into
+pattern \textbf{BP}.
+
+There were 3,632 pairs left for the manual check. The first author,
+who has been working on clone detection research for two years, took
+the role of the main investigator performing a manual classification
+of the 3,632 clone pairs. By consulting the cloning patterns, the main
+investigator went through each clone pair candidate, looked at the
+clones, and chose the most appropriate cloning pattern for the pair.
+
+To mitigate the human errors of the manual classification, the second
+author took the role of the validating investigator, performing a
+validation on 10\% (363 pairs) of the clone pairs judged by the main
+investigator. After the validation, the classifications from the two
+investigators were compared and 64 conflicts were found. The two
+investigators discussed and resolved 61 of them while the 3 conflicts
+were resolved by involving the third author. The classification
+results are shown in \Cref{tab:classification_good_o}.
+
+To answer RQ2, the classification results are explained and discussed
+below.
+
+\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
+online clone pairs with evidences of cloning from Qualitas projects to
+Stack Overflow. They include 3, 14, 86, and 9 pairs from the
+\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
+them have a statement in the Stack Overflow post saying that the code
+is ``copied'' or ``modified'' from a specific file or class in a
+Qualitas project. The most cloned projects are \textsf{hibernate} and
+\textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15
+pairs), and \textsf{hadoop} (12 pairs). The clones are used as
+examples and are very similar to their original Qualitas code with
+limited modifications.
+
+\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
+any clone pairs with evidence of cloning from Stack Overflow to
+Qualitas projects.
+
+\textbf{EX: External Sources.} We found 197 online clone pairs with
+evidence of cloning from external sources to Stack Overflow. They
+include 4, 41, 146, and 6 clone pairs from the \textit{good},
+\textit{ok'}, $S_D'$, and $N_D'$ set respectively.
+
+These findings complement a study of clones between software
+projects~\cite{Svajlenko2014}. We found that the code cloning can also
+happen among different sources on the Internet just like software
+projects. There are 30 clone pairs that originated from programming
+websites. For example, we found a clone of code snippet to convert
+numbers into words which is copied from
+\url{www.rgagnon.com/javadetails/java-0426.html}. Both the Stack
+Overflow and the \textsf{compiere} project source code contain an
+attribution to the original source. Another example is a code snippet
+to generate graphical \textit{Perlin noise}. It is copied from
+\url{http://mrl.nyu.edu/~perlin/noise/}. The code is used on Stack
+Overflow and in the \textsf{aoi} project with
+attribution.
+% The original code of the 15 clone pairs do not have licensing
+% information so these clones do not violate any license.
+There are other EX clone pairs which are copied from third-party
+libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util},
+\textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography
+project.
+
+\textbf{UD: Unknown Direction.} We found 382 online clone pairs with
+no evidence of cloning between Qualitas and Stack Overflow but with a
+high code similarity that suggests cloning. They include 11, 42, 294,
+and 35 pairs from the \textit{good}, \textit{ok'}, $S_D'$, and $N_D'$
+set respectively. The most cloned projects is \textsf{netbeans} with
+95 clone pairs. Most of the clones are a large chunk of code handling
+GUI components. Although these GUI clones might be auto-generated by
+IDEs, we did not find any evidence. The second most cloned project is
+\textsf{jung2} (62 pairs), a network and graph framework, followed by
+\textsf{eclipse-SDK} (37 pairs).
+% There are several Stack Overflow snippets that are identical to code
+% in \textsf{jung2}.
+
+\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate
+clone pairs found in this study. Although we have removed some of the
+boiler-plate code with filters before the analysis, we still observed
+28,749 such clone pairs. The \textbf{BP} clone pairs account for
+89.7\% of all clone pairs we classified. The majority of them are
+{\small{\texttt{equals()}}} methods.
+
+\textbf{IN: Inheritance/interface.} There were 111 clone pairs found
+to be similar because they implement the same interface or inheriting
+from the same class. An example is the two implementations of
+{\small{\texttt{MouseListener}}} that share similar
+{\small\texttt{@Override}} methods of {\small\texttt{mousePressed}},
+and {\small\texttt{mouseReleased}}.
+
+\textbf{AC: Accidental Clones.} There were 2,418 accidental clone
+pairs. Mainly, they are false positive clones caused by code
+normalisation. 
+% However, the original source code were still different enough when
+% we manually classified them.
+Other clone instances include {\small\texttt{finally}} or
+{\small\texttt{try-catch}} clauses that were accidentally the same due
+to their very small sizes, and similar {\small\texttt{switch-case}}
+statements.
 
@@
 	\centering
-	\caption{Classifications of online clone pairs.}
+	\caption{Classifications of online clone pairs. FIXME switch
+          UD and EX}
 	\label{tab:classification_good_o}
-	\small
-	\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{l|r|r|r|r|r|r|r|r}
+	%\small
+	%\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{l|rrrr|rrr|r}
 			\hline
@@
 			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
-			\multirow{1}{*}{\textit{ok}}  & 14 & 0 & 20 & 41 & 11,547 & 22 & 105 & 11,749 \\
-			\multirow{1}{*}{$S_D$} & 86 & 0 & 293 & 146 & 17,074 & 74 & 128 & 17,801 \\
-			\multirow{1}{*}{$N_D$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
+			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 20 & 41 & 11,547 & 22 & 105 & 11,749 \\
+			\multirow{1}{*}{$S_D'$} & 86 & 0 & 293 & 146 & 17,074 & 74 & 128 & 17,801 \\
+			\multirow{1}{*}{$N_D'$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
 			\hline
@@
 		\end{tabular} 
-	}
+	%}
 \end{table}
@@
 
-%\textbf{We answer RQ2 by using our patterns of online code cloning to classified 31,946 clone pairs.
-We found that a large amount of the clone pairs are boiler-plate code (28,642), clones from inheritance/interface (109), or accidental clones (2,525).
-Nevertheless, there were 670 pairs that were intentionally created.
-110 pairs had strong evidences to be cloned from Qualitas to Stack Overflow.
-382 were highly-confident clones but without evidence of cloning direction.
-178 pairs were found to be cloned from external sources outside Qualitas projects.} %We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
+\textbf{To answer RQ2, we found that a large amount of the clone pairs
+  between Stack Overflow and Qualitas projects are boiler-plate code
+  (28,642) or accidental clones (2,525) with no evidence that the code
+  has actually been copied. Nevertheless, we found 110 pairs that had
+  strong evidences to be cloned from Qualitas to Stack Overflow and
+  178 pairs were found to be cloned to Stack Overflow from external
+  sources outside Qualitas projects.} 
+%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
 
@@
 %\subsubsection{Outdated Clones}
-Outdated code occurs when a piece of code has been copied from its origin to another location and later the original has been updated~\cite{Xia2014}.
-Usually code clone detection is used to locate clone instances and update them to match with the originals~\cite{Bellon2007}.
-However, online code clones are more difficult to detect than in regular software projects due to its large search space and a mix of natural and programming languages combined in the same post.
+
+Outdated code occurs when a piece of code has been copied from its
+origin to another location and later the original has been
+updated~\cite{Xia2014}. Usually code clone detection is used to locate
+clone instances and update them to match with the
+originals~\cite{Bellon2007}. However, online code clones are more
+difficult to detect than in regular software projects due to its large
+search space and a mix of natural and programming languages combined
+in the same post.
 %Moreover, Stack Overflow is not a software.
@@
 
-To search for outdated online code clones, we focused on the 112 QS clone pairs that were cloned from Qualitas to Stack Overflow and compared them with their latest versions.
-We downloaded the latest version of the Qualitas projects from their repositories on 26 September 2016.
-For each QS online clone pair, we use the clone from Qualitas a a proxy.
-We searched for its latest version by the file name and located the cloned region in the file based on the method name.
+To search for outdated online code clones, we focused on the 112
+\textbf{QS} clone pairs that were cloned from Qualitas to Stack
+Overflow and compared them with their latest versions. We downloaded
+the latest version of the Qualitas projects from their repositories on
+26 September 2016. For each \textbf{QS} online clone pair, we used the
+clone from Qualitas a a proxy. We searched for its latest version by
+the file name and located the cloned region in the file based on the
+method name.
 %For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. 
-We then compared the Stack Overflow snippet to its latest version line-by-line to find if any change has been made to the source code.
-We also made sure that the changes did not come from the modifications made to the Stack Overflow snippets by the posters but from the updates in the projects themselves.
-When we found inconsistent lines between the two versions, we used {\small\texttt{git blame}} to see who modified those lines of code and the timestamps.
-
+We then compared the Stack Overflow snippet to its latest version
+line-by-line to find if any change has been made to the source
+code. We also made sure that the changes did not come from the
+modifications made to the Stack Overflow snippets by the posters but
+from the updates in the projects themselves. When we found
+inconsistent lines between the two versions, we used
+{\small\texttt{git blame}} to see who modified those lines of code and
+the timestamps.
+
+\FIXME{You are using the complete number of pairs in a project instead
+  of the outdated pairs!!!}
  %Some of the clone pairs overlap with each other so we group them in the same row. 
-We discovered 64 outdated online clone pairs out of 112 pairs.
-As shown in \Cref{fig:outdated}, \textsf{spring} and \textsf{hibernate} have the maximum number of 20 outdated pairs, followed by 15 from \textsf{eclipse}, and 12 from \textsf{hadoop}.
-Besides the example of outdated code in the \textsf{hadoop}'s {\small{\texttt{WritableComparator.java}}} shown in \Cref{fig:before-after}, we also found a few outdated code elements which contained heavy modifications.
-For example, the code snippet in Stack Overflow post 23520731 is a copy of {\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}.
-The code has been heavily modified on 5 February 2016.
-In the 64 outdate pairs, we found 5``dead'' snippets.
-These snippets cannot be located in the latest version of the projects.
-For example, the snippet in Stack Overflow post 3758110, a copy of {\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was deleted in the commit {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on 20th January 2012, two years after it was posted.
-%The latest version of Spring does not contain the file anymore.
-\Cref{tab:stale_code_details} shows examples of the outdated online clones on Stack Overflow.
-The table displays information of the clones from both Stack Overflow and Qualitas side including the dates.
-We summarise the changes that make the clones outdated into three types, modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}), along with the date of change.
-
-The outdated online code clones cause problems ranging from uncompilable code (due to modifications and different API usage in the outdated code) to introducing vulnerabilities to software~\cite{Xia2014}.
-An outdated code with a subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without awareness from developers.
-Although Stack Overflow has a voting mechanism that may mitigate this issue, the accepted answer is still attractive enough for naive developers to copy and reuse the code.
-
-\textbf{For RQ3, our results show that more than half (64) of QS clone pairs on Stack Overflow are outdated.
-60 pairs differ from their newest versions by modifications applied to variable names or method names, added or deleted statements, to a fully rewritten code with new method signatures.
-4 pairs are dead snippets.} %They do not exist any more in the latest version.} %These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
+We discovered 64 outdated online clone pairs out of 112 pairs. As
+shown in \Cref{fig:outdated}, \textsf{spring} and \textsf{hibernate}
+have the highest number of 20 outdated pairs, followed by 15 from
+\textsf{eclipse}, and 12 from \textsf{hadoop}. Besides the example of
+outdated code in the \textsf{hadoop}'s
+{\small{\texttt{WritableComparator.java}}} shown in
+\Cref{fig:before-after}, we also found a few outdated code elements
+which contained a large amount of modifications. For example, the code
+snippet in Stack Overflow post 23520731 is a copy of
+{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
+has been heavily modified on 5 February 2016.
+
+In the 64 outdated pairs, we found 5``dead'' snippets. These snippets
+cannot be located in the latest version of the projects. For example,
+the snippet in Stack Overflow post 3758110, a copy of
+{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
+\textsf{spring}, was deleted in the commit
+{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
+Beams on 20th January 2012, two years after it was
+posted. 
+% The latest version of Spring does not contain the file anymore.
+\Cref{tab:stale_code_details} shows examples of the outdated online
+clones on Stack Overflow. The table displays information of the clones
+from both Stack Overflow and Qualitas side including the dates. We
+summarise the changes that make the clones outdated into three types,
+modified/added/deleted statements (\textit{S}), file deletion
+(\textit{D}), and method rewriting (\textit{R}), along with the date
+of change.
+
+The outdated online code clones cause problems ranging from
+uncompilable code (due to modifications and different API usage in the
+outdated code) to introducing vulnerabilities to
+software~\cite{Xia2014}. An outdated code with a subtle change
+(e.g.~\Cref{fig:before-after}) may be copied and reused without
+awareness from developers. Although Stack Overflow has a voting
+mechanism that may mitigate this issue, the accepted answer is still
+used by naive developers who copy and reuse the outdated code.
+
+\textbf{For RQ3, our results show that more than half (64) of QS clone
+  pairs on Stack Overflow are outdated. 60 pairs differ from their
+  newest versions by modifications applied to variable names or method
+  names, added or deleted statements, to a fully rewritten code with
+  new method signatures. 4 pairs are dead
+  snippets.} 
+%They do not exist any more in the latest version.} %These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
 Even worse, they might also introduce bugs or vulnerabilities into their software.
@@
 	\label{tab:stale_code_details}
-	\small
-	\resizebox{2\columnwidth}{!}{%
+	%\small
+	%\resizebox{2\columnwidth}{!}{%
 		\begin{tabular}{l|l|l|l|p{4.7cm}|r|r|l|c|l}
@@
 		\end{tabular} %
-	}
+	%}
 \end{table*}
@@
 \subsection{RQ4: Software Licensing Violation}
-Software licensing plays an important role in software development. Violation of software licenses impacts software delivery and also leads to legal issues~\cite{Sprigman2015}. 
+
+Software licensing plays an important role in software
+development. Violation of software licenses impacts software delivery
+and also leads to legal issues~\cite{Sprigman2015}.
 %It is an emerging area that software engineering research community is paying attention to. For example, 
-One can run into a licensing issue if one integrates third-party source code into their software without checking.
-A study by An et al.~\cite{An2017} reports 1,219 cases of potential license violations between 399 Android apps and Stack Overflow code snippets.
-%there are studies of automatic technique to identify software licensing from source code files~\cite{German2010}
+One can run into a licensing issue if one integrates third-party
+source code into their software without checking. A study by An et
+al.~\cite{An2017} reports 1,219 cases of potential license violations
+between 399 Android apps and Stack Overflow code
+snippets. %there are studies of automatic technique to identify software licensing from source code files~\cite{German2010}
 
@@
 	\centering
-	\caption{License mapping of the online clones (file-level) in QS, UD, and EX}
+	\caption{License mapping of the online clones (file-level) in
+          QS, UD, and EX FIXME switch UD and EX}
 	\label{tab:license_abc}
 	\small
-	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|p{2cm}|l|r|r|r}
+	%\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|p{2cm}l|rrr}
 		\hline
@@
 		\multicolumn{3}{l|}{Total} &  6 & 23 & 11 \\
-		\hline
 		\hline
@@
 
-In our study, we reveal another possible situation of software licensing issues caused by code cloned ``to Stack Overflow''.
-We found evidence that 112 pieces of code had been copied from Qualitas projects to Stack Overflow as examples.
-Their status of accepted answers increase their chances of being reused.
-Even though most of the Qualitas projects came with a software license (shown in \Cref{t:q_projects_license}), we found that the licensing information were frequently missing after the code was copied to Stack Overflow.
-The licensing terms on top of source code files are not copied because usually only a small part of the file was cloned.
+In our study, we reveal another possible situation of software
+licensing issues caused by code cloned to Stack Overflow. We found
+evidence that 112 pieces of code have been copied from Qualitas
+projects to Stack Overflow as examples. Their status of accepted
+answers increase their chances of being reused. Even though most of
+the Qualitas projects came with a software license (shown in
+\Cref{t:q_projects_license}), we found that the licensing information
+were frequently missing after the code was copied to Stack
+Overflow. The licensing terms on top of source code files are not
+copied because usually only a small part of the file was
+cloned. 
 %If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
 
-We analysed licensing conflicts of the online clones in the QS, UD, and EX set.
-The summary of licensing information is listed in \Cref{tab:license_abc}.
-The licenses were extracted by \textbf{Ninka}, an automatic license identification tool~\cite{German2010}.
-Since Ninka works at file level, we report the findings based on Stack Overflow snippets and Qualitas source files instead of the clone pairs (duplicates were ignored).
-For the ones that could not be automatically identified by Ninka and have been reported as {\small\texttt{SeeFile}} or {\small\texttt{Unknown}}, we looked at them manually and updated if any license was found.
-The table shows the license mapping of Stack Overflow snippets and Qualitas source code.
-The results are reported separately for the QS, UD, and EX set.
-In overall, we can see that most of the Stack Overflow snippets do not contain licensing terms while their clone counterparts in Qualitas projects do.
-
-\textbf{Compatible license:} There are 37 pairs which have compatible licenses such as Apache license v.2; Eclipse Public License v.1 (EPLv1); or a pair of No license vs.~Creative Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC BY-NC-SA 3.0).
-These clones are safe for being reused.
-Since source code and text on Stack Overflow posted before 1st March 2016 are protected by CC BY-NC-SA 3.0 (and MIT license from 1st March 2016 onwards), we can treat the Stack Overflow code snippets without licensing information as having CC BY-NC-SA 3.0 by default.
-CC BY-NC-SA 3.0 license is relaxed and it only requests an attribution when reused.
-
-\textbf{Incompatible license:} there are 357 clone pairs which do not contain licensing information after they are posted on Stack Overflow or contain different license from their Qualitas clone counterparts.
-More than half (79) of QS clone pairs have their licensing terms removed or changed after posted on Stack Overflow.
-Of 226 UD clone pairs, 202 pairs have incompatible licenses.
-Again, most of the clones in Qualitas contain a license while the Stack Overflow snippets do not.
-For EX clone pairs, we searched for licensing terms of the original source code from the external sources.
-We found that 76 out of 87 EX clone pairs have incompatible licenses.
+We analysed licensing conflicts of the online clones in the
+\textbf{QS}, \textbf{EX}, and \textbf{UD} set. The summary of
+licensing information is listed in \Cref{tab:license_abc}. The
+licenses were extracted by \emph{Ninka}, an automatic license
+identification tool~\cite{German2010}. Since Ninka works at file
+level, we report the findings based on Stack Overflow snippets and
+Qualitas source files instead of the clone pairs (duplicates were
+ignored). For the ones that could not be automatically identified by
+Ninka and have been reported as {\small\texttt{SeeFile}} or
+{\small\texttt{Unknown}}, we looked at them manually to see if any
+license can be found. The table shows the license mapping of Stack
+Overflow snippets and Qualitas source code. The results are reported
+separately for the \textbf{QS}, \textbf{EX}, and \textbf{UD} set. In
+overall, we can see that most of the Stack Overflow snippets do not
+contain licensing terms while their clone counterparts in Qualitas
+projects do.
+
+\textbf{Compatible license:} There are 37 pairs which have compatible
+licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
+  License v.1 (EPLv1)}; or a pair of no license vs.~\emph{Creative
+  Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC
+  BY-NC-SA 3.0)}. These clones are safe for being reused. Since source
+code and text on Stack Overflow posted before 1st March 2016 are
+protected by \emph{CC BY-NC-SA 3.0} (and \emph{MIT} license from 1st
+March 2016 onwards), we can treat the Stack Overflow code snippets
+without licensing information as having \emph{CC BY-NC-SA 3.0} by
+default. The \emph{CC BY-NC-SA 3.0} license is relaxed and it only
+requests an attribution when reused.
+
+\textbf{Incompatible license:} there are 357 clone pairs which do not
+contain licensing information after they are posted on Stack Overflow
+or contain a different license from their Qualitas clone
+counterparts. More than half (79) of \textbf{QS} clone pairs have
+their licensing terms removed or changed when posted on Stack
+Overflow. For \textbf{EX} clone pairs, we searched for licensing terms of the
+original source code from the external sources. We found that 76 out
+of 87 EX clone pairs have incompatible licenses.
 %They are clones that have been identified to be copied from an external source.
-Similarly, the license statement was removed from Stack Overflow snippets. 
+Similarly, the license statement was removed from Stack Overflow
+snippets. Of 226 \textbf{UD} clone pairs, 202 pairs have incompatible
+licenses. Again, most of the clones in Qualitas contain a license
+while the Stack Overflow snippets do not.
 %
@@
 
-\textbf{For RQ4, we found 357 code snippets on Stack Overflow that violate the license of their original software.
-The majority of them do not contain licensing statements after copied to Stack Overflow.}
+\textbf{For RQ4, we found 357 code snippets on Stack Overflow that
+  violate the license of their original software. The majority of them
+  do not contain licensing statements after they have been copied to
+  Stack Overflow.}
 
@@
 \textbf{Internal validity:}
-We could not verify all the 315,786,118 clone pairs reported by the clone detection tools in this study.
-Nevertheless, we applied different mechanisms to ensure the validity to the subset of clone pairs we classified.
-First, we used two, instead of one, widely-used clone detection tools, Simian and NiCad. 
-We had tried three other clone detectors but could not add them to the study
-due to their scalability issue and susceptibility to incomplete code snippets.
-Second, we adopted Bellon's clone agreement metric~\cite{Bellon2007} to prioritise and filters clone pairs 
-for the manual classification. The agreed clone pairs that passed \textit{good} and \textit{ok} criteria had a higher chance
-to be true positive. We also applied the Bellon's clone agreement to 4 different combinations of the tools' configurations.
-For disagreed clone pairs, we applied several filters to remove spurious and uninteresting clones.
-
-The number of online clones we found are subject to the clone detectors and their configurations. 
-We mitigated the problem of clone detector's parameter sensitivity by adding another configuration, besides the default one.
-We reused the established configurations from the EvaClone study~\cite{Wang2013}.
-We also performed a pairwise matching between the default and EvaClone configurations of the two clone detection tools.
-
-Our seven patterns of online code cloning may not cover all possible online cloning patterns. However, instead of 
-defining the patterns beforehand, we resorted to extract them from the data sets. We derived them
-from a manual investigation of 679 online clone pairs and adopted one pattern from the study by Kapser et al.~\cite{Kapser2003}.
-
-The 3,632 clone pairs classified manually by the first author are subject to manual judgement and human errors. 
-Although we have tried our best to be careful on searching for evidence and classifying the clones, some errors
-may still exist. We mitigated this problem by having the second author to validate the classifications with random samplings.
-The 64 classification conflicts were discussed and resolved. 
-The third author made a final judgement when no consensus could be found by the two authors.
+
+We could not verify all the 315,786,118 clone pairs reported by the
+clone detection tools in this study.  Nevertheless, we applied
+different mechanisms to ensure the validity to the subset of clone
+pairs we classified.  First, we used two, instead of one, widely-used
+clone detection tools, Simian and NiCad.  We had tried three other
+clone detectors but could not add them to the study due to their
+scalability issue and susceptibility to incomplete code snippets.
+Second, we adopted Bellon's clone agreement metric~\cite{Bellon2007}
+to prioritise and filters clone pairs for the manual
+classification. The agreed clone pairs that passed \textit{good} and
+\textit{ok} criteria had a higher chance to be true positive. We also
+applied the Bellon's clone agreement to 4 different combinations of
+the tools' configurations.  For disagreed clone pairs, we applied
+several filters to remove spurious and uninteresting clones.
+
+The number of online clones we found are subject to the clone
+detectors and their configurations.  We mitigated the problem of clone
+detector's parameter sensitivity by adding another configuration,
+besides the default configuration. We reused the established
+configurations from the EvaClone study~\cite{Wang2013}.  We also
+performed a pairwise matching between the default and EvaClone
+configurations of the two clone detection tools.
+
+Our seven patterns of online code cloning may not cover all possible
+online cloning patterns. However, instead of defining the patterns
+beforehand, we resorted to extract them from the data sets. We derived
+them from a manual investigation of 679 online clone pairs and adopted
+one pattern from the study by Kapser et al.~\cite{Kapser2003}.
+
+The 3,632 clone pairs classified manually by the first author are
+subject to manual judgement and human errors.  Although we have tried
+our best to be careful on searching for evidence and classifying the
+clones, some errors may still exist. We mitigated this problem by
+having the second author to validate the classifications with a random
+sampling.  The 64 classification conflicts were discussed and
+resolved.  The third author made a final judgement when no consensus
+could be found by the two authors.
  %In addition, we are aware of voting mechanism
@@
 experiment so the findings could be generalise as much as possible.
-We selected Stack Overflow because it is one of the most popular programming Q\&A websites available with approximately 6.3 million users.
-There are a large number of code snippets reused from the site~\cite{An2017} and there are also several studies encouraging of doing so~(e.g.~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014}).
-Nonetheless, it may not be representative to all the programming Q\&A websites.
-
-Regarding the code snippets, we downloaded a full data dump and extracted Java accepted answers. Instead of analysing every post, we only focused on posts marked as accepted answers 
-since they are the most likely to being reused. This yields a total of 144,064 snippets.
-Our findings are limited to these restrictions.
-They may not be generalised to all programming languages and all answers on Stack Overflow.
-On the other hand, we chose the curated Qualitas corpus for Java open source projects containing 111 projects \cite{QualitasCorpus}.
-The projects span over several areas of software and has been used in several empirical studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}.
-Although it is a curated and well-established corpus,
-it may not fully represent all Java open source software available.
+We selected Stack Overflow because it is one of the most popular
+programming Q\&A websites available with approximately 6.3 million
+users.  There are a large number of code snippets reused from the
+site~\cite{An2017} and there are also several studies encouraging of
+doing
+so~(e.g.~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014}).
+Nonetheless, it may not be representative to all the programming Q\&A
+websites.
+
+Regarding the code snippets, we downloaded a full data dump and
+extracted Java accepted answers. Instead of analysing every post, we
+only focused on posts marked as accepted answers since they are the
+most likely ones to be reused. This yields a total of 144,064
+snippets.  Our findings are limited to these restrictions. They may
+not be generalised to all programming languages and all answers on
+Stack Overflow. On the other hand, we chose the curated Qualitas
+corpus for Java open source projects containing 111 projects
+\cite{QualitasCorpus}.  The projects span over several areas of
+software and has been used in several empirical
+studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although
+it is a curated and well-established corpus, it may not fully
+represent all Java open source software available.
 

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Worked on all the FIXMEs and fixed the confusions of the irrelevant methods filter.

@@
 		\hline 
-		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=1000 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming,\newline literal abstraction \\
+		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming,\newline literal abstraction \\
 		\hline
@@
 	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|c|c|c|c|r}
-		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{4}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-6}
-		& & \textit{L} & \textit{S} & \textit{M} & \textit{G} & \\
-		\hline 
-		%		\multirow{1}{*}{\textit{good}} & 2,308 & & & & & 2,308 \\
-		%		\multirow{1}{*}{\textit{ok}} & 11,749 & & & & & 11,749 \\
-		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & \checkmark & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & \checkmark & 88 \\ 
-		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-%		\hline
-%		Total  & 6,400,425 & \multicolumn{4}{c|}{ } & 17,169 \\ 
-		\hline
-		\multicolumn{7}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{M}=irr.~methods, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
+	\begin{tabular}{l|r|c|c|c|r}
+		\hline
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{3}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-5}
+		& & \textit{L} & \textit{S} & \textit{G} & \\
+		\hline 
+		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & 17,801 \\
+		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & 88 \\ 
+		\hline
+		\multicolumn{6}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
 	\end{tabular} %
@@
 clone pair candidates is still too large for manual inspection (67,570
-for $S_D$ and 632,855 pairs for $N_D$). We applied four filters: clone
+for $S_D$ and 632,855 pairs for $N_D$). We applied three filters: clone
 size, irrelevant methods, similarity threshold, and good/ok pairs. For
@@
 % configuration has a minimum clone size of 6 lines).
-The \emph{irrelevant methods filter} removes clones of
-\verb|hashCode()| methods and getters/setters which are almost always
-false clones. The third filter, \emph{similarity threshold}, applies
+%The \emph{irrelevant methods filter} removes clones of
+%\verb|hashCode()| methods and getters/setters which are almost always
+%false clones. 
+The second filter, \emph{similarity threshold}, applies
 only to NiCad clone pairs since Simian does not provide a similarity
@@
 As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the
-results using clone size, irrelevant methods, and gook/ok pairs. The
-three filters reduced the number of $S_D$ clones to 17,801 pairs.  We
+results using clone size and gook/ok pairs. The
+two filters reduced the number of $S_D$ clones to 17,801 pairs. We
 filtered $N_D$ clones by additionally raising the similarity
@@
 
+\FIXME{Do you think we should report at this level or in more details 
+	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}
+
 However, using Bellon's criteria for matching clone pairs, only
 0.1\textperthousand~of all pairs are agreed by two tool/configuration
-combinations.
-
-\FIXME{Can you say something about the numbers only looking at the set
-  of pairs used for manual inspection?}
+combinations. For the 2,308 \textit{good} pairs, there are 92 Stack Overflow snippets
+which are associated with 66 Qualitas projects. The 11,749 \textit{ok} 
+pairs are clones between 136 Stack Overflow snippets and 39 Qualitas 
+projects.
+
+Moreover, for the disagreed pairs, we found 17,081 clone pairs reported by $S_D$
+are clones between 471 Stack Overflow snippets and 76 Qualitas projects and 
+88 $N_D$ clone pairs are clones between 77 Stack Overflow snippets and 29
+Qualitas projects.
+
 % FIXME
 % However, as it is well known that the precision of clone detectors is
-c% not very good, it is clear that the above numbers may not be
+% not very good, it is clear that the above numbers may not be
 % representative for real code clones and we ...
@@
 
-\FIXME{Why equals here but not hashcode? Why isn't it the same
-  irrelevant methods filter?}
+%\FIXME{Why equals here but not hashcode? Why isn't it the same
+%  irrelevant methods filter?}
 
@@
 \Cref{fig:classification_process}.  Before performing the manual
-classification, we used the irrelevant method filter to automatically
-classify {\small\texttt{equals()}} and the remaining
-getters/setters. As shown in
+classification, we created and used an automatic classifier 
+to classify {\small\texttt{equals()}}, 
+{\small\texttt{hashCode()}} and getters/setters. As shown in
 \Cref{tab:online_clone_classification_results}, the automatic
@@
 	\centering
-	\caption{Classifications of online clone pairs. FIXME switch
-          UD and EX}
+	\caption{Classifications of online clone pairs.}
 	\label{tab:classification_good_o}
@@
 			\hline
-			Set & QS & SQ & UD & EX & BP & IN & AC & Total \\ 
-			\hline
-			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 11 & 4 & 111  & 7 & 2,172 & 2,308 \\
-			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 20 & 41 & 11,547 & 22 & 105 & 11,749 \\
-			\multirow{1}{*}{$S_D'$} & 86 & 0 & 293 & 146 & 17,074 & 74 & 128 & 17,801 \\
-			\multirow{1}{*}{$N_D'$} & 9  & 0 & 35 & 6 & 17 & 8 & 13 & 88 \\ 
-			\hline
-			Total & 112 & 0 & 359 & 197 & 28,749 & 111 & 2,418 & 31,946 \\ 
+			Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
+			\hline
+			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 11 & 111  & 7 & 2,172 & 2,308 \\
+			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 41 & 20 & 11,547 & 22 & 105 & 11,749 \\
+			\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
+			\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 35 & 17 & 8 & 13 & 88 \\ 
+			\hline
+			Total & 112 & 0 & 197 & 359 & 28,749 & 111 & 2,418 & 31,946 \\ 
 			\hline
@@
   (28,642) or accidental clones (2,525) with no evidence that the code
-  has actually been copied. Nevertheless, we found 110 pairs that had
+  has actually been copied. Nevertheless, we found 112 pairs that had
   strong evidences to be cloned from Qualitas to Stack Overflow and
@@
 
-\FIXME{You are using the complete number of pairs in a project instead
-  of the outdated pairs!!!}
+%\FIXME{You are using the complete number of pairs in a project instead
+%  of the outdated pairs!!!}
  %Some of the clone pairs overlap with each other so we group them in the same row. 
 We discovered 64 outdated online clone pairs out of 112 pairs. As
-shown in \Cref{fig:outdated}, \textsf{spring} and \textsf{hibernate}
-have the highest number of 20 outdated pairs, followed by 15 from
-\textsf{eclipse}, and 12 from \textsf{hadoop}. Besides the example of
+shown in \Cref{fig:outdated}, \textsf{spring}
+have the highest number of 17 outdated pairs, followed by 7 from
+\textsf{hibernate} and \textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
 outdated code in the \textsf{hadoop}'s
@@
 
-In the 64 outdated pairs, we found 5``dead'' snippets. These snippets
+In the 64 outdated pairs, we found 5 ``dead'' snippets. These snippets
 cannot be located in the latest version of the projects. For example,
@@
 	%\small
-	%\resizebox{2\columnwidth}{!}{%
-		\begin{tabular}{l|l|l|l|p{4.7cm}|r|r|l|c|l}
+	\resizebox{2.1\columnwidth}{!}{%
+		\begin{tabular}{l|l|l|l|p{5.1cm}|r|r|l|c|l}
 		 \hline
@@
 		\end{tabular} %
-	%}
+	}
 \end{table*}
@@
 	\caption{License mapping of the online clones (file-level) in
-          QS, UD, and EX FIXME switch UD and EX}
+          QS, UD, and EX}
 	\label{tab:license_abc}
@@
 		\hline
-		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & UD & EX \\
-%		\hline
-%		No license & No license & No license &  5 & 21 & 4 \\
-		\hline
-		Compatible & Apache2 & Apache2 &  0 & 1 & 0 \\
-		License	& EPLv1 & EPLv1 &  1 & 1 & 0 \\
-		& Sun (proprietary) & Sun (proprietary) & 0 & 0 & 1 \\
-		& MIT-like & MIT-like & 0 & 0 & 1 \\
-		& No license & CC BY-NC-SA &  0 & 0 & 5 \\
-		& No license & No license &  5 & 21 & 4 \\
-		\hline
-		\multicolumn{3}{l|}{Total} &  6 & 23 & 11 \\
-		\hline
-	    Incompat. & BSD3 & GPLv2+ & 0 & 1 & 0 \\
-		License	& No license & AGPLv3/3+ & 1 & 2 & 0 \\
-		& No license & Apache-2 & 41 & 23 & 5 \\
-		& No license & BSD3 & 3 & 28 & 4 \\
-		& No license & CDDL or GPLv2 & 1 & 58 & 0 \\
-		& No license & CDDLv1 & 0 & 0 & 1 \\
-		& No license & EPLv1 & 7 & 10 & 0 \\
-		& No license & GPLv2/2+/3+ & 2 & 32 & 62 \\
-		& No license & LGPLv2/2.1+/3+ & 24 & 32 & 0 \\
-		& No license & MPLv1.1 & 0 & 1 & 0 \\
-		& No license & spdxBSD3 & 0 & 10 & 0 \\
-		& No license & SPLv1 & 0 & 0 & 1 \\
+		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
+		\hline
+		Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
+		License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
+		& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
+		& MIT-like & MIT-like & 0 & 1 & 0\\
+		& No license & CC BY-NC-SA & 0 & 5 & 0 \\
+		& No license & No license & 5 & 4 & 21 \\
+		\hline
+		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
+		\hline
+	    Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
+		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
+		& No license & Apache-2 & 41 & 5 & 23 \\
+		& No license & BSD3 & 3 & 4 & 28 \\
+		& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
+		& No license & CDDLv1 & 0 & 1 & 0 \\
+		& No license & EPLv1 & 7 & 0 & 10 \\
+		& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
+		& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
+		& No license & MPLv1.1 & 0 & 0 & 1 \\
+		& No license & spdxBSD3 & 0 & 0 & 10 \\
+		& No license & SPLv1 & 0 & 1 & 0 \\
 		& No license & Unknown & 0 & 3 & 3 \\
-		& spdxBSD3 & AGPLv3+ & 0 & 2 & 0 \\
-		\hline
-		\multicolumn{3}{l|}{Total} &  79 & 202 & 76 \\
+		& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
+		\hline
+		\multicolumn{3}{l|}{Total} &  79 & 76 & 202 \\
 		\hline
@@
 answers increase their chances of being reused. Even though most of
-the Qualitas projects came with a software license (shown in
-\Cref{t:q_projects_license}), we found that the licensing information
+the Qualitas projects came with a software license, we found that the licensing information
 were frequently missing after the code was copied to Stack

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Reworked RQ1 again. Rewrote the abstract. Other small changes.

@@
 
+%\overfullrule1ex
+
 \begin{document}
@@
 \begin{abstract}
-	We studied online code clones on the popular programming Q\&A website, Stack Overflow, and their issues on outdated code and software licensing violation.
-Online code clones are code fragments that are copied from software projects or online sources to Stack Overflow as examples.
-They can be discovered by using code clone detectors, yet they are inherently different from normal code clones in software projects in several aspects.
-Due to an absence of checking mechanism after the code has been copied to Stack Overflow, the online code clones may suffer from being outdated and violating the original software license.
-%Moreover, we also found that majority of online code clones do not contain the license of their originals.
-	We designed the experiment incorporating several state-of-the-art tools and techniques to automatically extract, prioritise, and filter the clones.
-As a result, we discovered 51,926 non-trivial online clone candidates between 144,064 Java code snippets on Stack Overflow and 111 Java open source projects in the curated Qualitas corpus.
-The manual study of the 3,632 online clone pairs revealed that 64 clones on Stack Overflow are outdated.
-Furthermore, we found 357 Stack Overflow code snippets that do not contain software license of their originals or have conflicting licenses.
-These snippets are questionable for reuse.
-Our study is among the first to address the problem of outdated and license-violating code snippets on Stack Overflow.
+  % We studied online code clones on the popular programming Q\&A
+  % website, Stack Overflow, and their issues on outdated code and
+  % software licensing violations. 
+  Online code clones are code fragments that are copied from software
+  projects or online sources to Stack Overflow as examples in
+  questions and answers.
+  % They can be discovered by using code clone
+  % detectors, yet they are inherently different from normal code clones
+  % in software projects in several aspects. 
+  Due to an absence of a checking mechanism after the code has been
+  copied to Stack Overflow, online code clones may suffer from
+  becoming outdated or violating the original software license.
+  % Moreover, we also found that majority of online code clones do not
+  % contain the license of their originals.
+  We present a study incorporating several state-of-the-art tools and
+  techniques to automatically extract, prioritise, and filter
+  315,786,118 detected online clone pairs between 144,064 Java code
+  snippets on Stack Overflow and 111 Java open source projects in the
+  curated Qualitas corpus. We discovered and investigated 51,926
+  non-trivial online clone candidates. Our study revealed that 64 out
+  of 112 clones with strong evidence of copying from a Qualitas
+  project to Stack Overflow are outdated. Furthermore, we found 357
+  code snippets on Stack Overflow that violate the license of their
+  original software.
+  % These snippets are questionable for reuse.
+  Our study is among the first to address the problem of
+  outdated and license-violating code snippets on Stack Overflow.
 \end{abstract}
@@
 	                                                                       }
-	\end{lstlisting}
+	\end{lstlisting}\vspace{-2ex}
 	\caption{A motivating example of the two code fragments of
@@
 \emph{to} Stack Overflow and problems of reusing them such as outdated
-code and software licensing violations. This paper makes the following
-primary contributions:
+code and software licensing violations. This paper fills this gap and
+makes the following primary contributions:
 
@@
 \noindent%
-The \textit{good-value}  and the \textit{ok-value}  of two clone pairs are then defined as
+The \textit{good-value}  and the \textit{ok-value}  of two clone pairs are defined as
 %\squeezeup
@@
 % configuration has a minimum clone size of 6 lines).
-%The \emph{irrelevant methods filter} removes clones of
-%\verb|hashCode()| methods and getters/setters which are almost always
-%false clones. 
 The second filter, \emph{similarity threshold}, applies
@@
 	\centering
-	\includegraphics[width=\linewidth]{classification_process}
+	\includegraphics[width=0.8\linewidth]{classification_process}
 	\caption{Online code clone classification process}
@@
 
-\textbf{To answer RQ1, with the four configurations of Simian and
-  NiCad, we found online code clones in 1,086 ($S_D$), 1,531 ($S_E$),
-  1,392 ($N_D$) and 12,886 ($N_E$) Stack Overflow code snippets. They
-  are associated with 92, 111, 82 and 88 Qualitas projects
-  respectively, i.e.~most Qualitas projects share similar code with
-  Stack Overflow code snippets.}
-
-\FIXME{Do you think we should report at this level or in more details 
-	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}
+% \FIXME{Do you think we should report at this level or in more details 
+% 	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}
+% I don't think there is a need.
+
+\begin{table}
+\caption{FIXME Maybe merge with Table 7?}
+\label{tab:snippets}
+\centering
+\begin{tabular}{l|rrr}
+  & Pairs & Snippets & Projects \\
+\hline
+\textit{good} & 2,308 & 92 & 66 \\
+\textit{ok'} & 11,749 & 136 & 39 \\
+$S_D'$ & 17,081 & 471 & 76 \\
+$N_D'$ & 88 & 77 & 29 \\
+\hline
+Total & 31,946 & FIXME & FIXME
+\end{tabular}
+\end{table}
 
@@
 0.1\textperthousand~of all pairs are agreed by two tool/configuration
-combinations. For the 2,308 \textit{good} pairs, there are 92 Stack Overflow snippets
-which are associated with 66 Qualitas projects. The 11,749 \textit{ok} 
-pairs are clones between 136 Stack Overflow snippets and 39 Qualitas 
-projects.
-
-Moreover, for the disagreed pairs, we found 17,081 clone pairs reported by $S_D$
-are clones between 471 Stack Overflow snippets and 76 Qualitas projects and 
-88 $N_D$ clone pairs are clones between 77 Stack Overflow snippets and 29
-Qualitas projects.
-
-% FIXME
-% However, as it is well known that the precision of clone detectors is
-% not very good, it is clear that the above numbers may not be
-% representative for real code clones and we ...
+combinations. As shown in FIXME, for the 2,308 \textit{good} pairs,
+there are 92 Stack Overflow snippets which are associated with 66
+Qualitas projects. The 11,749 \textit{ok'} pairs are clones between
+136 Stack Overflow snippets and 39 Qualitas projects.  Moreover, for
+the disagreed pairs, we found 17,081 clone pairs reported by $S_D'$
+are clones between 471 Stack Overflow snippets and 76 Qualitas
+projects and 88 $N_D'$ clone pairs are clones between 77 Stack
+Overflow snippets and 29 Qualitas projects. In total we found that the
+manually investigated 31,946 clones pairs are clones between FIXME
+Stack Overflow snippets and FIXME Qualitas projects.
+
+\textbf{To answer RQ1, with the four configurations of Simian and
+  NiCad, we found most Qualitas projects to share similar code with
+  Stack Overflow code snippets. When onlly considering the manually
+  investigated snippets, FIXME}
+
+\FIXME{Should we have removed the AC clones right at the beginning?}
 
@@
 \end{table}
-
-%\FIXME{Why equals here but not hashcode? Why isn't it the same
-%  irrelevant methods filter?}
 
@@
 \Cref{tab:online_clone_classification_results}, the automatic
-classifier helped us classified and captured 28,314 clone pairs into
+classifier helped us to classify 28,314 clone pairs into
 pattern \textbf{BP}.
@@
 clones, and chose the most appropriate cloning pattern for the pair.
-
+%
 To mitigate the human errors of the manual classification, the second
@@
 were resolved by involving the third author. The classification
-results are shown in \Cref{tab:classification_good_o}.
-
-To answer RQ2, the classification results are explained and discussed
-below.
+results are shown in \Cref{tab:classification_good_o} and explained in
+the following.
 
@@
 
-%\FIXME{You are using the complete number of pairs in a project instead
-%  of the outdated pairs!!!}
- %Some of the clone pairs overlap with each other so we group them in the same row. 
 We discovered 64 outdated online clone pairs out of 112 pairs. As
-shown in \Cref{fig:outdated}, \textsf{spring}
-have the highest number of 17 outdated pairs, followed by 7 from
-\textsf{hibernate} and \textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
-outdated code in the \textsf{hadoop}'s
-{\small{\texttt{WritableComparator.java}}} shown in
+shown in \Cref{fig:outdated}, \textsf{spring} has the highest number
+of 17 outdated pairs, followed by 7 from \textsf{hibernate} and
+\textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
+outdated code in % \textsf{hadoop}'s
+{\small{\texttt{WritableComparator.java}}} 
+from \textsf{hadoop} shown in
 \Cref{fig:before-after}, we also found a few outdated code elements
@@
 	%\small
-	\resizebox{2.1\columnwidth}{!}{%
-		\begin{tabular}{l|l|l|l|p{5.1cm}|r|r|l|c|l}
+	%\resizebox{\textwidth}{!}{%
+		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
 		 \hline
@@
 		 \hline 
-		 \multicolumn{10}{l}{{\footnotesize * \textit{S}=modified/added/deleted statements, \textit{D}=file deletion,  \textit{R}=method rewriting}}
+		 \multicolumn{10}{l}{{\footnotesize * \textit{S}:
+                  modified/added/deleted statements, \textit{D}: file
+                  has been deleted,  \textit{R}: method has been
+                  rewritten completely}}
 		\end{tabular} %
-	}
+	%}
 \end{table*}
@@
 	\centering
-	\caption{License mapping of the online clones (file-level) in
-          QS, UD, and EX}
+	\caption{License mapping of  online clones (file-level)}
 	\label{tab:license_abc}
@@
 	%\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|p{2cm}l|rrr}
+	\begin{tabular}{l|p{1.95cm}l|rrr}
 		\hline

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Added the two totals in Table 8 and in the text. Added a few FIXMEs. Fixed a total number of clone pairs manually investigated in the abstract.

@@
   snippets on Stack Overflow and 111 Java open source projects in the
-  curated Qualitas corpus. We discovered and investigated 51,926
+  curated Qualitas corpus. We discovered and investigated 31,946
   non-trivial online clone candidates. Our study revealed that 64 out
@@
 \begin{table}
-\caption{FIXME Maybe merge with Table 7?}
+\caption{FIXME Maybe merge with Table 7? <-- You mean Table 9?}
 \label{tab:snippets}
 \centering
-\begin{tabular}{l|rrr}
-  & Pairs & Snippets & Projects \\
-\hline
-\textit{good} & 2,308 & 92 & 66 \\
-\textit{ok'} & 11,749 & 136 & 39 \\
-$S_D'$ & 17,081 & 471 & 76 \\
-$N_D'$ & 88 & 77 & 29 \\
-\hline
-Total & 31,946 & FIXME & FIXME
+\begin{tabular}{l|rrrr}
+  & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
+\hline
+\textit{good} & 2,308 & 92 & 66 & \\
+\textit{ok'} & 11,749 & 136 & 39 & \\
+$S_D'$ & 17,081 & 471 & 76 & \\
+$N_D'$ & 88 & 77 & 29 & \\
+\hline
+Total & 31,946 & 621 & 95 &
 \end{tabular}
@@
 Overflow snippets and 29 Qualitas projects. In total we found that the
-manually investigated 31,946 clones pairs are clones between FIXME
-Stack Overflow snippets and FIXME Qualitas projects.
+manually investigated 31,946 clones pairs are clones between 621
+Stack Overflow snippets and 95 Qualitas projects.
 
@@
   between Stack Overflow and Qualitas projects are boiler-plate code
-  (28,642) or accidental clones (2,525) with no evidence that the code
+  (28,642) or accidental clones (2,529) \FIXME{IN+AC here?} with no evidence that the code
   has actually been copied. Nevertheless, we found 112 pairs that had

### 2017-02-19 cloneoverflow-latex/cloneoverflow.tex
Finalised RQ1.

@@
 projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
-snippets containing clones associated with 111 Qualitas
+snippets containing clones associated with all 111 Qualitas
 projects. NiCad in the default configuration ($N_D$) reported clones
@@
 \begin{table}
-\caption{FIXME Maybe merge with Table 7? <-- You mean Table 9?}
+\caption{Investigated online clone pairs and snippets \FIXME{maybe
+    merge with tables 7 and/or 9}}
 \label{tab:snippets}
@@
 0.1\textperthousand~of all pairs are agreed by two tool/configuration
-combinations. As shown in FIXME, for the 2,308 \textit{good} pairs,
-there are 92 Stack Overflow snippets which are associated with 66
-Qualitas projects. The 11,749 \textit{ok'} pairs are clones between
-136 Stack Overflow snippets and 39 Qualitas projects.  Moreover, for
-the disagreed pairs, we found 17,081 clone pairs reported by $S_D'$
-are clones between 471 Stack Overflow snippets and 76 Qualitas
-projects and 88 $N_D'$ clone pairs are clones between 77 Stack
-Overflow snippets and 29 Qualitas projects. In total we found that the
-manually investigated 31,946 clones pairs are clones between 621
-Stack Overflow snippets and 95 Qualitas projects.
-
-\textbf{To answer RQ1, with the four configurations of Simian and
-  NiCad, we found most Qualitas projects to share similar code with
-  Stack Overflow code snippets. When onlly considering the manually
-  investigated snippets, FIXME}
-
-\FIXME{Should we have removed the AC clones right at the beginning?}
+combinations. As shown in \Cref{tab:snippets}, for the 2,308
+\textit{good} pairs, there are 92 Stack Overflow snippets which are
+associated with 66 Qualitas projects. The 11,749 \textit{ok'} pairs
+are clones between 136 Stack Overflow snippets and 39 Qualitas
+projects.  Moreover, for the disagreed pairs, we found 17,081 clone
+pairs reported by $S_D'$ are clones between 471 Stack Overflow
+snippets and 76 Qualitas projects and 88 $N_D'$ clone pairs are clones
+between 77 Stack Overflow snippets and 29 Qualitas projects. In total
+we found that the manually investigated 31,946 clones pairs are clones
+between 621 Stack Overflow snippets and 95 Qualitas projects.
+
+\textbf{To answer RQ1, we found most Qualitas projects to share
+  similar code with Stack Overflow code snippets. Depending on the
+  data set, between 82 to all 111 projects share similar code. This
+  holds even for the investigated data set where 95 projects share
+  code with Stack Overflow.}
+
+%\FIXME{Should we have removed the AC clones right at the beginning?}
 
@@
 
+%FIXME: We probably have to discuss IN clones.
+%FIXME: the numbers where 28,642 and 2,529 which I could not find elsewhere.
 \textbf{To answer RQ2, we found that a large amount of the clone pairs
   between Stack Overflow and Qualitas projects are boiler-plate code
-  (28,642) or accidental clones (2,529) \FIXME{IN+AC here?} with no evidence that the code
+  (28,749) or accidental clones (2,418) with no evidence that the code
   has actually been copied. Nevertheless, we found 112 pairs that had
   strong evidences to be cloned from Qualitas to Stack Overflow and
-  178 pairs were found to be cloned to Stack Overflow from external
+  197 pairs were found to be cloned to Stack Overflow from external
   sources outside Qualitas projects.} 
@@
 
+\FIXME{This needs rewriting}
+
 \textbf{Stack Overflow} is a gold mine for software engineering research.
@@
 \section{Conclusions}
-Online code clones are clones that have been copied to Q\&A websites such as Stack Overflow.
-They are similar to clones in software projects where they can be outdated and violating software license but are much harder to detect.
-We studied the online code clones between Stack Overflow and Qualitas projects, especially 3,632 clone pairs, manually in details.
-
-Although we deployed Bellon's clone agreement and multiple filters to reduce the number of clone candidates, we still found a large number of 51,926 online clone pairs reported by two clone detectors.
-We classify 31,946 clone pairs using our seven patterns of online code cloning.
-We discovered 112 clone pairs that have been copied, with evidence, from Qualitas projects to Stack Overflow (QS), 197 clone pairs that have been copied from external sources besides Qualitas to Stack Overflow (EX), and 359 clone pairs that are highly similar but without evidence of copying (UD).
-
-A manual investigation of the 112 QS clone pairs by comparing to their latest version (as of 26 September 2016) reveals that 64 of them are outdated.
-Moreover, the study of licensing conflicts of clones in QS, EX, and UD shows that 357 code snippets on Stack Overflow do not contain licensing statements while their clone counterparts in Qualitas projects or external sources do.
-
-This study is among, if not the first, to address the important issues of outdated and license-violating online code clones on programming Q\&A websites using a hybrid methodology of automatic code clone detection and a manual clone investigation.
+
+\FIXME{This needs rewriting}
+
+Online code clones are clones that have been copied to Q\&A websites
+such as Stack Overflow. They are similar to clones in software
+projects where they can be outdated and violating software license but
+are much harder to detect. We studied the online code clones between
+Stack Overflow and Qualitas projects, especially 3,632 clone pairs,
+manually in details.
+
+Although we deployed Bellon's clone agreement and multiple filters to
+reduce the number of clone candidates, we still found a large number
+of 51,926 online clone pairs reported by two clone detectors. We
+classify 31,946 clone pairs using our seven patterns of online code
+cloning. We discovered 112 clone pairs that have been copied, with
+evidence, from Qualitas projects to Stack Overflow (QS), 197 clone
+pairs that have been copied from external sources besides Qualitas to
+Stack Overflow (EX), and 359 clone pairs that are highly similar but
+without evidence of copying (UD).
+
+A manual investigation of the 112 QS clone pairs by comparing to their
+latest version (as of 26 September 2016) reveals that 64 of them are
+outdated. Moreover, the study of licensing conflicts of clones in QS,
+EX, and UD shows that 357 code snippets on Stack Overflow do not
+contain licensing statements while their clone counterparts in
+Qualitas projects or external sources do.
+
+This study is among, if not the first, to address the important issues
+of outdated and license-violating online code clones on programming
+Q\&A websites using a hybrid methodology of automatic code clone
+detection and a manual clone investigation.
 
@@
 % produce the bibliography for the citations in your paper.
-\bibliographystyle{abbrv}
+\bibliographystyle{ACM-Reference-Format}
 \bibliography{sigproc}

### 2017-02-20 cloneoverflow-latex/cloneoverflow.tex
Added another stats in RQ1 without the false positive (AC pairs).
Added the manually confirmed data sets.

@@
 The number of online clone pairs reported by running Simian and NiCad
-are presented in \Cref{tab:raw_stats}. $S_D$ reports 67,570 clone
+are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
 pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
@@
 
-\begin{table}
-	\centering
-	\caption{Statistics of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
-	\label{tab:raw_stats}
-	%\small
-	%\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{l|r|r|r|r}
-			\hline
-			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
-			\hline
-			Stack Overflow Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
-			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
-%			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
-%			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-%			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
-			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
-			\hline
-		\end{tabular} %
-	%}
-\end{table}
+% \begin{table}
+% 	\centering
+% 	\caption{Statistics of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
+% 	\label{tab:raw_stats}
+% 	%\small
+% 	%\resizebox{\columnwidth}{!}{%
+% 		\begin{tabular}{l|r|r|r|r}
+% 			\hline
+% 			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
+% 			\hline
+% 			Stack Overflow Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
+% 			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
+% %			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
+% %			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
+% %			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
+% 			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
+% 			\hline
+% 		\end{tabular} %
+% 	%}
+% \end{table}
 
@@
 
-The statistics on clones obtained from running Simian and NiCad are
-presented in \Cref{tab:raw_stats}. Simian in the default configuration
+The statistics on clones obtained from the different data sets are
+presented in \Cref{tab:snippets}. Simian in the default configuration
 ($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
@@
 \begin{table}
-\caption{Investigated online clone pairs and snippets \FIXME{maybe
-    merge with tables 7 and/or 9}}
+\caption{Investigated online clone pairs and corresponding snippets
+  and Qualitas projects for the different data sets}
 \label{tab:snippets}
@@
 \begin{tabular}{l|rrrr}
-  & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
-\hline
-\textit{good} & 2,308 & 92 & 66 & \\
-\textit{ok'} & 11,749 & 136 & 39 & \\
-$S_D'$ & 17,081 & 471 & 76 & \\
-$N_D'$ & 88 & 77 & 29 & \\
-\hline
-Total & 31,946 & 621 & 95 &
+  \hline 
+  Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
+  \hline 
+  \multicolumn{4}{l}{\textit{Reported Clones}} \\
+  \hline
+  $S_D$ & 67,570 & 1,086 & 92 & 38\% \\
+  $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
+  $N_D$ & 632,855& 1,392 & 82 & 30\% \\
+  $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
+  \hline
+  Total & 315,786,118 & &\\
+  \hline
+  \multicolumn{4}{l}{\textit{Filtered Data Sets}} \\
+  \hline
+  \textit{good} & 2,308 & 92 & 66 & 23\% \\
+  \textit{ok'} & 11,749 & 136 & 39 & 28\% \\
+  $S_D'$ & 17,081 & 471 & 76 & 31\% \\
+  $N_D'$ & 88 & 77 & 29 & 26\% \\
+  \hline
+  Total & 31,946 & 621 & 95 & 27\%\\
+  \hline 
+  \multicolumn{4}{l}{\textit{True Positives without AC}} \\
+  \hline 
+  $\textit{good}/\textrm{AC}$ & 136 & 47 & 25 & 23\% \\
+  $\textit{ok'}/\textrm{AC}$ & 11,644 & 125 & 34 & 28\% \\
+  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
+  $N_D'/\textrm{AC}$ & 75 & 44 & 17 & 28\% \\
+  \hline
+  Total & 29,528 & 555 & 81 & 28\% \\
+  \hline
 \end{tabular}
@@
 between 77 Stack Overflow snippets and 29 Qualitas projects. In total
-we found that the manually investigated 31,946 clones pairs are clones
-between 621 Stack Overflow snippets and 95 Qualitas projects.
+we found that the filtered data sets contains 31,946 clone pairs which
+are clones between 621 Stack Overflow snippets and 95 Qualitas
+projects. During the manual investigation, we identified 2,418 pairs
+as being accidential clones (AC), i.e.~false positives. After removing
+them, the data set still contains 29,528 clone pairs between 555 Stack
+Overflow snippets and 81 Qualitas projects.
 
@@
   similar code with Stack Overflow code snippets. Depending on the
-  data set, between 82 to all 111 projects share similar code. This
-  holds even for the investigated data set where 95 projects share
-  code with Stack Overflow.}
+  data set, between 82 to all 111 projects share similar code. The
+  filtered data set has 95 projects share code with Stack
+  Overflow. Even in the manually confirmed data set of 29,528 clone
+  pairs, a majority of 81 Qualitas projects share similar code with
+  Stack Overflow.}
 

### 2017-02-20 cloneoverflow-latex/cloneoverflow.tex
Small changes. Removed "the first study" from the abstract.

@@
   % These snippets are questionable for reuse.
-  Our study is among the first to address the problem of
-  outdated and license-violating code snippets on Stack Overflow.
+  % Our study is among the first to address the problem of
+  % outdated and license-violating code snippets on Stack Overflow.
 \end{abstract}
@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We obtained 144,064 Java code snippets which contain 2,347,267 lines
-of Java source code excluding comments and blank
+We obtained 144,064 Java code snippets containing 2,347,267
 lines\footnote{Measured by cloc:
-  \url{https://github.com/AlDanial/cloc}}.
+  \url{https://github.com/AlDanial/cloc}} of Java source code.
+% excluding comments and blank lines.
 

### 2017-02-22 cloneoverflow-latex/cloneoverflow.tex
Added missing numbers & fixed the wrong number of cloned projects in ND.
Updated all the numbers after fixing problem of ND clone path. Ready to work on Rocco's comments now.

@@
   snippets on Stack Overflow and 111 Java open source projects in the
-  curated Qualitas corpus. We discovered and investigated 31,946
+  curated Qualitas corpus. We discovered and investigated 32,533
   non-trivial online clone candidates. Our study revealed that 64 out
@@
 deployed the two clone detectors to locate clones between the two
-datasets.  We partitioned the input and ran the tools multiple
+datasets. Due to a scalability issue, we partitioned the input and ran the tools multiple
 times. Each run was composed of the entire Stack Overflow data and a
@@
   \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
-of \textit{good} clone pairs is 2,308 and the number of \textit{ok}
-clone pairs is 31,729, 0.1\textperthousand~of all reported clone
+of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
+clone pairs is 32,316, 0.1\textperthousand~of all reported clone
 pairs.  Agreed clone pairs are clone pairs that pass Bellon's
@@
     \hline
-    \textit{good} & 18 & 26 & 10 & 2,267 & 2,308 \\
-    \textit{ok} & 11,467 & 993 & 79 & 20,021 & 31,729  \\
+    \textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
+    \textit{ok} & 12,336 & 993 & 79 & 20,021 & 32,316 \\
     \hline
@@
 	\centering
-	\includegraphics[width=\linewidth]{good-ok_pairs-crop}
+	\includegraphics[width=\linewidth]{good-ok_pairs}
 	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
@@
 combinations of \textit{D} and \textit{E} configurations are listed in
-\Cref{t_agreed_good_clone_pairs}.  There are 2,321 (2,308 unique)
-\textit{good} pairs consisting of 18 pairs from $S_D$--$N_D$, 26 pairs
+\Cref{t_agreed_good_clone_pairs}.  There are 2,326 (2,313 unique)
+\textit{good} pairs consisting of 23 pairs from $S_D$--$N_D$, 26 pairs
 from $S_D$--$N_E$, 10 pairs from $S_E$--$N_D$, and 2,267 pairs from
-$S_E$--$N_E$. There are 32,560 (31,729 unique) \textit{ok}
-pairs\footnote{This excludes the subsumed 2,308 \textit{good}
+$S_E$--$N_E$. There are 33,156 (32,316 unique) \textit{ok}
+pairs\footnote{This excludes the subsumed 2,313 \textit{good}
   pairs. According to the definition, \textit{ok} pairs always subsume
-  \textit{good} pairs.}. We obtained 11,467; 993; 79; and 20,021 pairs
+  \textit{good} pairs.}. We obtained 12,336; 993; 79; and 20,021 pairs
 from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
@@
 		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & 88 \\ 
+		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & 83 \\ 
 		\hline
@@
 along with the other three filters, we reduced the number of $N_D$
-clones to 88 pairs.
+clones to 83 pairs.
 
@@
 For the manual inspection of clone pairs, we selected all
-\textit{good} pairs (2,308) and the \textit{ok} pairs for
-$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (11,749), but we ignored
+\textit{good} pairs (2,313) and the \textit{ok} pairs for
+$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (12,336), but we ignored
 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
@@
 
-Together with the 17,801 (referred as $S_D'$ set) and 88 (referred as
+Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
 $N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
-$N_D$, we ended up with a set of 31,946 online clone pair candidates
+$N_D$, we ended up with a set of 32,533 online clone pair candidates
 for manual inspection.
@@
 
-The classification of all 31,946 online clone pairs followed the steps
+The classification of all 32,533 online clone pairs followed the steps
 depicted in \Cref{fig:classification_process}. First, we look at a
@@
 projects. NiCad in the default configuration ($N_D$) reported clones
-between 1,392 Stack Overflow code snippets and 82 Qualitas
+between 1,392 Stack Overflow code snippets and 88 Qualitas
 projects. NiCad in the EvaClone configuration ($N_E$) reported the
@@
   \hline 
-  \multicolumn{4}{l}{\textit{Reported Clones}} \\
+  \multicolumn{5}{l}{\textit{Reported Clones}} \\
   \hline
@@
   $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
-  $N_D$ & 632,855& 1,392 & 82 & 30\% \\
+  $N_D$ & 632,855& 1,392 & 88 & 30\% \\
   $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
   \hline
-  Total & 315,786,118 & &\\
-  \hline
-  \multicolumn{4}{l}{\textit{Filtered Data Sets}} \\
-  \hline
-  \textit{good} & 2,308 & 92 & 66 & 23\% \\
-  \textit{ok'} & 11,749 & 136 & 39 & 28\% \\
-  $S_D'$ & 17,081 & 471 & 76 & 31\% \\
-  $N_D'$ & 88 & 77 & 29 & 26\% \\
-  \hline
-  Total & 31,946 & 621 & 95 & 27\%\\
-  \hline 
-  \multicolumn{4}{l}{\textit{True Positives without AC}} \\
-  \hline 
-  $\textit{good}/\textrm{AC}$ & 136 & 47 & 25 & 23\% \\
-  $\textit{ok'}/\textrm{AC}$ & 11,644 & 125 & 34 & 28\% \\
+  Total & 315,786,118 & 14,856 & 111 & 38\% \\
+  \hline
+  \multicolumn{5}{l}{\textit{Filtered Data Sets}} \\
+  \hline
+  \textit{good} & 2,313 & 97 & 67 & 23\% \\
+  \textit{ok'} & 12,336 & 139 & 43 & 28\% \\
+  $S_D'$ & 17,081 & 460 & 74 & 31\% \\
+  $N_D'$ & 83 & 44 & 19 & 27\% \\
+  \hline
+  Total & 32,533 & 623 & 96 & 27\%\\
+  \hline 
+  \multicolumn{5}{l}{\textit{True Positives without AC}} \\
+  \hline 
+  $\textit{good}/\textrm{AC}$ & 141 & 52 & 26 & 23\% \\
+  $\textit{ok'}/\textrm{AC}$ & 12,229 & 126 & 36 & 28\% \\
   $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
-  $N_D'/\textrm{AC}$ & 75 & 44 & 17 & 28\% \\
-  \hline
-  Total & 29,528 & 555 & 81 & 28\% \\
+  $N_D'/\textrm{AC}$ & 70 & 39 & 16 & 29\% \\
+  \hline
+  Total & 30,113 & 556 & 80 & 28\% \\
   \hline
@@
 0.1\textperthousand~of all pairs are agreed by two tool/configuration
-combinations. As shown in \Cref{tab:snippets}, for the 2,308
-\textit{good} pairs, there are 92 Stack Overflow snippets which are
-associated with 66 Qualitas projects. The 11,749 \textit{ok'} pairs
-are clones between 136 Stack Overflow snippets and 39 Qualitas
+combinations. As shown in \Cref{tab:snippets}, for the 2,313
+\textit{good} pairs, there are 97 Stack Overflow snippets which are
+associated with 67 Qualitas projects. The 12,336 \textit{ok'} pairs
+are clones between 139 Stack Overflow snippets and 43 Qualitas
 projects.  Moreover, for the disagreed pairs, we found 17,081 clone
-pairs reported by $S_D'$ are clones between 471 Stack Overflow
-snippets and 76 Qualitas projects and 88 $N_D'$ clone pairs are clones
-between 77 Stack Overflow snippets and 29 Qualitas projects. In total
-we found that the filtered data sets contains 31,946 clone pairs which
-are clones between 621 Stack Overflow snippets and 95 Qualitas
-projects. During the manual investigation, we identified 2,418 pairs
+pairs reported by $S_D'$ are clones between 460 Stack Overflow
+snippets and 74 Qualitas projects and 83 $N_D'$ clone pairs are clones
+between 44 Stack Overflow snippets and 19 Qualitas projects. In total
+we found that the filtered data sets contains 32,533 clone pairs which
+are clones between 623 Stack Overflow snippets and 96 Qualitas
+projects. During the manual investigation, we identified 2,420 pairs
 as being accidential clones (AC), i.e.~false positives. After removing
-them, the data set still contains 29,528 clone pairs between 555 Stack
-Overflow snippets and 81 Qualitas projects.
+them, the data set still contains 30,113 clone pairs between 556 Stack
+Overflow snippets and 80 Qualitas projects.
 
@@
   similar code with Stack Overflow code snippets. Depending on the
-  data set, between 82 to all 111 projects share similar code. The
-  filtered data set has 95 projects share code with Stack
-  Overflow. Even in the manually confirmed data set of 29,528 clone
-  pairs, a majority of 81 Qualitas projects share similar code with
+  data set, between 88 to all 111 projects share similar code. The
+  filtered data set has 96 projects share code with Stack
+  Overflow. Even in the manually confirmed data set of 30,113 clone
+  pairs, a majority of 80 Qualitas projects share similar code with
   Stack Overflow.}
@@
 		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,308 & 10 & 2,298 \\
-		\multirow{1}{*}{\textit{ok'}} & 11,749 & 11,494 & 255 \\
+		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
+		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
 		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
 		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
-		\multirow{1}{*}{$N_D'$} & 88 & 10 & 78 \\ 
+		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
 		\hline
-		Total  & 31,946 & 28,314 & 3,632 \\ 
+		Total  & 32,533 & 28,897 & 3,636 \\ 
 		\hline
@@
 We rely on a manual study to qualitatively investigate the patterns of
-online code cloning. To achieve this, we classified all 31,946
+online code cloning. To achieve this, we classified all 32,533
 selected clone pairs according to the process shown in
@@
 \Cref{tab:online_clone_classification_results}, the automatic
-classifier helped us to classify 28,314 clone pairs into
+classifier helped us to classify 28,897 clone pairs into
 pattern \textbf{BP}.
 
-There were 3,632 pairs left for the manual check. The first author,
+There were 3,636 pairs left for the manual check. The first author,
 who has been working on clone detection research for two years, took
 the role of the main investigator performing a manual classification
-of the 3,632 clone pairs. By consulting the cloning patterns, the main
+of the 3,636 clone pairs. By consulting the cloning patterns, the main
 investigator went through each clone pair candidate, looked at the
@@
 author took the role of the validating investigator, performing a
-validation on 10\% (363 pairs) of the clone pairs judged by the main
+validation on 10\% (364 pairs) of the clone pairs judged by the main
 investigator. After the validation, the classifications from the two
@@
 
-\textbf{EX: External Sources.} We found 197 online clone pairs with
+\textbf{EX: External Sources.} We found 200 online clone pairs with
 evidence of cloning from external sources to Stack Overflow. They
-include 4, 41, 146, and 6 clone pairs from the \textit{good},
+include 4, 44, 146, and 6 clone pairs from the \textit{good},
 \textit{ok'}, $S_D'$, and $N_D'$ set respectively.
@@
 
-\textbf{UD: Unknown Direction.} We found 382 online clone pairs with
+\textbf{UD: Unknown Direction.} We found 359 online clone pairs with
 no evidence of cloning between Qualitas and Stack Overflow but with a
-high code similarity that suggests cloning. They include 11, 42, 294,
-and 35 pairs from the \textit{good}, \textit{ok'}, $S_D'$, and $N_D'$
+high code similarity that suggests cloning. They include 15, 20, 293,
+and 31 pairs from the \textit{good}, \textit{ok'}, $S_D'$, and $N_D'$
 set respectively. The most cloned projects is \textsf{netbeans} with
-95 clone pairs. Most of the clones are a large chunk of code handling
+93 clone pairs. Most of the clones are a large chunk of code handling
 GUI components. Although these GUI clones might be auto-generated by
@@
 \textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate
-clone pairs found in this study. Although we have removed some of the
-boiler-plate code with filters before the analysis, we still observed
-28,749 such clone pairs. The \textbf{BP} clone pairs account for
-89.7\% of all clone pairs we classified. The majority of them are
+clone pairs found in this study. %Although we have removed some of the
+%boiler-plate code with filters before the analysis, we still 
+We observed 29,330 such clone pairs. The \textbf{BP} clone pairs account for
+90\% of all clone pairs we classified. The majority of them are
 {\small{\texttt{equals()}}} methods.
 
-\textbf{IN: Inheritance/interface.} There were 111 clone pairs found
+\textbf{IN: Inheritance/interface.} There were 112 clone pairs found
 to be similar because they implement the same interface or inheriting
@@
 
-\textbf{AC: Accidental Clones.} There were 2,418 accidental clone
+\textbf{AC: Accidental Clones.} There were 2,420 accidental clone
 pairs. Mainly, they are false positive clones caused by code
@@
 			\hline
-			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 11 & 111  & 7 & 2,172 & 2,308 \\
-			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 41 & 20 & 11,547 & 22 & 105 & 11,749 \\
+			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
+			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 44 & 20 & 12,128 & 23 & 107 & 12,336 \\
 			\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
-			\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 35 & 17 & 8 & 13 & 88 \\ 
-			\hline
-			Total & 112 & 0 & 197 & 359 & 28,749 & 111 & 2,418 & 31,946 \\ 
+			\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
+			\hline
+			Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
 			\hline
@@
   between Stack Overflow and Qualitas projects are boiler-plate code
-  (28,749) or accidental clones (2,418) with no evidence that the code
+  (29,330) or accidental clones (2,420) with no evidence that the code
   has actually been copied. Nevertheless, we found 112 pairs that had
   strong evidences to be cloned from Qualitas to Stack Overflow and
-  197 pairs were found to be cloned to Stack Overflow from external
+  200 pairs were found to be cloned to Stack Overflow from external
   sources outside Qualitas projects.} 
@@
 		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
-		& No license & Apache-2 & 41 & 5 & 23 \\
+		& No license & Apache-2 & 41 & 6 & 23 \\
 		& No license & BSD3 & 3 & 4 & 28 \\
@@
 		\hline
-		\multicolumn{3}{l|}{Total} &  79 & 76 & 202 \\
+		\multicolumn{3}{l|}{Total} &  79 & 77 & 202 \\
 		\hline
@@
 
-\textbf{Compatible license:} There are 37 pairs which have compatible
+\textbf{Compatible license:} There are 40 pairs which have compatible
 licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
@@
 
-\textbf{Incompatible license:} there are 357 clone pairs which do not
+\textbf{Incompatible license:} there are 358 clone pairs which do not
 contain licensing information after they are posted on Stack Overflow
@@
 Overflow. For \textbf{EX} clone pairs, we searched for licensing terms of the
-original source code from the external sources. We found that 76 out
-of 87 EX clone pairs have incompatible licenses.
+original source code from the external sources. We found that 77 out
+of 88 EX clone pairs have incompatible licenses.
 %They are clones that have been identified to be copied from an external source.
@@
 
-\textbf{For RQ4, we found 357 code snippets on Stack Overflow that
+\textbf{For RQ4, we found 358 code snippets on Stack Overflow that
   violate the license of their original software. The majority of them
@@
 of 51,926 online clone pairs reported by two clone detectors. We
-classify 31,946 clone pairs using our seven patterns of online code
+classify 32,533 clone pairs using our seven patterns of online code
 cloning. We discovered 112 clone pairs that have been copied, with

### 2017-02-23 cloneoverflow-latex/cloneoverflow.tex
Updated the experimental framework diagram. Move things around and fixed small problems (e.g. removed MIT license of Stack Overflow since it is not implemented yet).

@@
 
-\subsection{Clone Detection}
-
+To answer the four research questions, we derived three result sets; 
+\textit{Reported Clones}, \textit{Filtered Clones}, and \textit{Pattern Clones};
+and a manual investigation of online clones. 
+For the Reported Clones set, we deployed code clone detection
+to locate similar code,~i.e.~clones, between Stack Overflow and 
+Qualitas projects. The second result set, Filtered Clones, is derived from the
+Reported Clones set by filtering out trivial clones. The last result set,
+Pattern Clones, is used to define the online code cloning patterns
+for our manual classification. We show the number of clone pairs in the Reported Clones,
+Filtered Clones and Pattern Clone result set in \Cref{tab:result_sets}.
+
+\subsection{RQ1: Online Code Clones}
+
+With the Reported Clones and Filtered Clones result sets, 
+we can observe how many code snippets on
+Stack Overflow are reported as clones to/from Qualitas projects
+in two aspects: before and after removing trivial clones. 
+We explain the approach we used to create to two result sets below.
+
+\begin{table}
+	\centering
+	\caption{Clone Result Sets}
+	\label{tab:result_sets}
+	%\small
+	\begin{tabular}{lp{3cm}r}
+		\hline 
+		Result set & Description & Clone pairs \\
+		\hline
+		Reported Clones & All reported clones & 315,786,118 \\ 
+		%\hline 
+		Filtered Clones & Clones after filtering & 32,533 \\ 
+		Pattern Clones & Clones for defining online cloning patterns & 697 \\
+		\hline 
+	\end{tabular} 
+\end{table}
+
+\subsubsection{Reported Clones Result Set} 
+We use clone detection to discover online code clones. 
+%\textbf{Clone Detection and Configuration: } 
 There are a number of restrictions in terms of choosing clone
@@
 % from two locations so no filtering was needed.
-
-\subsection{Clone Detection Configuration}
+%\subsection{Clone Detection Configuration}
 
@@
 
-\subsection{Filtering Clone Candidates}
-
-The number of online clone pairs reported by running Simian and NiCad
-are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
-pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
-much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
-respectively. This is expected since EvaClone configurations prefer
-recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
-9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
-$N_D$ has an average clone size of 10.85 lines which is bigger than
-6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
-configuration with a smaller minimum size (\Cref{t:param_tuning}).
-
-\begin{table}
-  \centering
-  \caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
-  \label{tab:orig_stats}
-  %\small
-  %\resizebox{\columnwidth}{!}{%
-    \begin{tabular}{l|r|r|r|r}
-      \hline
-      Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
-      \hline
-      Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
-      % Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-      Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
-      \hline
-    \end{tabular} %
-  %}
-\end{table}
+\subsubsection{Filtered Clones Result Set}
 
@@
 
-\subsubsection{Agreed clone pairs}
-
-As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
+\textbf{Agreed clone pairs: } As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
 agreement filtering using Bellon's criteria\footnote{Similar to the
@@
 
-\subsubsection{Disagreed clone pairs}
-
 \begin{table}
@@
 
+\textbf{Disagreed clone pairs: }
 The disagreed clone pairs are clone pairs that are reported by a
@@
 
-\subsubsection{Manual Inspection Data Set}
-
-For the manual inspection of clone pairs, we selected all
-\textit{good} pairs (2,313) and the \textit{ok} pairs for
+%\subsubsection{Filtered Clones Set}
+We selected all \textit{good} pairs (2,313) and the \textit{ok} pairs for
 $S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (12,336), but we ignored
@@
 pairs as the \textit{good} set and the \textit{ok'} set.
-
 Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
@@
 
-\subsection{The Seven Patterns of Online Code Cloning}
-
+\subsection{RQ2: Patterns of Online Code Cloning}
 As we are interested in the patterns of online code clones, we studied
@@
 al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
-evaluate its applicability to our study. Using the $S_D$ clone report,
+evaluate its applicability to our study by using a small subset of the
+reported online clones.
+
+\subsubsection{Pattern Clones Result Set}
+Using the $S_D$ clone report,
 snippets were ranked according to (1)~clone pair frequency,
@@
 obtained 34 unique Stack Overflow snippets. The snippets were
-associated with 697 clone pairs. Using Kapser's cloning patterns, the
+associated with 697 clone pairs.
+
+\subsubsection{Defining Online Code Cloning Patterns}
+Using Kapser's cloning patterns and the Pattern Clones Result Set, the
 clone pairs were categorised into either Customisation or Templating.
@@
 
-The classification of all 32,533 online clone pairs followed the steps
+The classification of the filtered online clone pairs followed the steps
 depicted in \Cref{fig:classification_process}. First, we look at a
@@
 source instead of a Qualitas projects, the pair is classified into
-\textbf{EX}. Lastly, if there is no evidence of copying in any
+\textbf{EX}.
+Lastly, if there is no evidence of copying in any
 direction but the clone fragments are highly similar, we classify them
 into \textbf{UD}.
+
+The first author, who has been working on clone detection research for 
+two years, took the role of the main investigator performing a manual 
+classification of the filtered clone pairs. By consulting the cloning 
+patterns, the main investigator went through each clone pair candidate, 
+looked at the clones, and chose the most appropriate cloning pattern 
+for the pair. To mitigate the human errors of the manual classification, 
+the second author took the role of the validating investigator, performing a
+validation on 10\% of the clone pairs judged by the main
+investigator. After the validation, the classifications from the two
+investigators were compared and conflicts were discussed and resolved.
+If the two investigator cannot find a consensus, the third author is 
+involved for the final judgement.
 
@@
 
+The number of online clone pairs reported by running Simian and NiCad
+are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
+pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
+much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
+respectively. This is expected since EvaClone configurations prefer
+recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
+9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
+$N_D$ has an average clone size of 10.85 lines which is bigger than
+6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
+configuration with a smaller minimum size (\Cref{t:param_tuning}).
+
+\begin{table}
+	\centering
+	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
+	\label{tab:orig_stats}
+	%\small
+	%\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r}
+		\hline
+		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
+		\hline
+		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
+		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
+		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
+		\hline
+	\end{tabular} %
+	%}
+\end{table}
+
 The statistics on clones obtained from the different data sets are
@@
 pattern \textbf{BP}.
-
-There were 3,636 pairs left for the manual check. The first author,
-who has been working on clone detection research for two years, took
-the role of the main investigator performing a manual classification
-of the 3,636 clone pairs. By consulting the cloning patterns, the main
-investigator went through each clone pair candidate, looked at the
-clones, and chose the most appropriate cloning pattern for the pair.
 %
-To mitigate the human errors of the manual classification, the second
-author took the role of the validating investigator, performing a
-validation on 10\% (364 pairs) of the clone pairs judged by the main
-investigator. After the validation, the classifications from the two
-investigators were compared and 64 conflicts were found. The two
-investigators discussed and resolved 61 of them while the 3 conflicts
-were resolved by involving the third author. The classification
+There were 3,636 pairs left for the manual check. 
+ The classification
 results are shown in \Cref{tab:classification_good_o} and explained in
@@
 them have a statement in the Stack Overflow post saying that the code
-is ``copied'' or ``modified'' from a specific file or class in a
-Qualitas project. The most cloned projects are \textsf{hibernate} and
+is ``copied'', ``borrow'' or ``modified'' from a specific file or class in a
+Qualitas project. For example, according to the motivating example in 
+\Cref{fig:before-after}, we found evidence in the Stack Overflow 
+Post 22315734 saying that \textit{``Actually, you can learn how to compare 
+in Hadoop from WritableComparator. Here is an examle that borrows 
+some ideas from it.''}
+
+The most cloned projects are \textsf{hibernate} and
 \textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15
@@
 \textbf{EX: External Sources.} We found 200 online clone pairs with
-evidence of cloning from external sources to Stack Overflow. They
-include 4, 44, 146, and 6 clone pairs from the \textit{good},
-\textit{ok'}, $S_D'$, and $N_D'$ set respectively.
+evidence of cloning from external sources to Stack Overflow. 
+They include 4, 44, 146, and 6 clone pairs from the \textit{good},
+\textit{ok'}, $S_D'$, and $N_D'$ set respectively. All of them
+contain statements showing an external source of the cloned code.
+For example, Stack Overflow Post 9549009 contains a code comment saying \textit{``Copied 
+	shamelessly from org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator,
+	changed only the hash algorithm.''}
 
@@
   BY-NC-SA 3.0)}. These clones are safe for being reused. Since source
-code and text on Stack Overflow posted before 1st March 2016 are
-protected by \emph{CC BY-NC-SA 3.0} (and \emph{MIT} license from 1st
-March 2016 onwards), we can treat the Stack Overflow code snippets
+code and text on Stack Overflow are
+protected by \emph{CC BY-NC-SA 3.0}
+, we can treat the Stack Overflow code snippets
 without licensing information as having \emph{CC BY-NC-SA 3.0} by
@@
 
+\section{Overall Discussion}
+%What can we learn for the results?
+For example, if a developer explicitly reports in his/her code that the snippet was copied from stackoverfow, are there some benefits?
+We could notify - for instance - the developer when some new issues related to the snippet are posted on stackoverflow?
+Or could we force people posting code on SO to explicitly report licensing information?
+Or, could we implement an intelligent IDE that when pasting code from external resource checks for licensing violation?
+These of course are only some (crazy?) ideas that could be developed on the top of the results we have achieved with this study...
+
+%We discovered two issues regarding code snippets on Stack Overflow in this study: (1)  outdated online clones on Stack Overflow and (2) missing or incompatible license in Stack Overflow snippets. 
+%that there is a considerable amount of cloned code between Stack Overflow that are cloned from 111 projects in the Qualitas corpus.
+64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals.
+To mitigate the problems of outdated online clones and missing or incompatible license on Stack Overflow code snippets, we propose the following actionable items:
+
+\textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' license software projects and posted on Stack Overflow.
+Moreover, an IDE plug-in that can automatically detect pasted source code and track their origins with licensing check could also prevent the issue of license-violating Stack Overflow code snippets.
+
+\textbf{Detective measure:} A system to detect outdated source code snippets on Stack Overflow is needed.
+If a code snippet is copied from an external project with other licenses than CC BY-NC-SA, the poster has to provide the information of the project including the original file name and its online repository (if exists).
+The system can leverage clone detection tools/techniques to periodically locate and check if the cloned snippet is still up-to-date with its original.
+With such a system, the poster can be notified when the code has been updated in the original project so that he/she can update their code on Stack Overflow accordingly.
+
 \section{Threats to Validity}

### 2017-02-23 cloneoverflow-latex/cloneoverflow.tex
Lots of restructuring according to Rocco's comments. Sent to Jens before Chaiyong going to the SANER banquet.

@@
 locate and study the online code clones between Stack Overflow and open source
-projects. The experimental framework is depicted in \Cref{fig:exp_framework} and
-we discuss our experimental setup below.
+projects. We designed our study in 6 phases as depicted in \Cref{fig:exp_framework} where
+we build different data sets to answer each of our four research questions. 
+We explain our process of building the data sets in each phase separately below.
 
@@
 
-\subsection{Datasets}
+\subsection{Methodology}
+
+\subsubsection{Phase 1: Clone Identification}
 
@@
 
-\subsubsection{Stack Overflow}
-
+\textbf{Stack Overflow:} 
 We extracted Java code snippets from a snapshot of a Stack Overflow
@@
 
-\subsubsection{Open source systems}
-
+\textbf{Open source systems: }
 We selected the established corpus for an empirical software
@@
 
-To answer the four research questions, we derived three result sets; 
-\textit{Reported Clones}, \textit{Filtered Clones}, and \textit{Pattern Clones};
-and a manual investigation of online clones. 
-For the Reported Clones set, we deployed code clone detection
-to locate similar code,~i.e.~clones, between Stack Overflow and 
-Qualitas projects. The second result set, Filtered Clones, is derived from the
-Reported Clones set by filtering out trivial clones. The last result set,
-Pattern Clones, is used to define the online code cloning patterns
-for our manual classification. We show the number of clone pairs in the Reported Clones,
-Filtered Clones and Pattern Clone result set in \Cref{tab:result_sets}.
-
-\subsection{RQ1: Online Code Clones}
-
-With the Reported Clones and Filtered Clones result sets, 
-we can observe how many code snippets on
-Stack Overflow are reported as clones to/from Qualitas projects
-in two aspects: before and after removing trivial clones. 
-We explain the approach we used to create to two result sets below.
-
-\begin{table}
-	\centering
-	\caption{Clone Result Sets}
-	\label{tab:result_sets}
-	%\small
-	\begin{tabular}{lp{3cm}r}
-		\hline 
-		Result set & Description & Clone pairs \\
-		\hline
-		Reported Clones & All reported clones & 315,786,118 \\ 
-		%\hline 
-		Filtered Clones & Clones after filtering & 32,533 \\ 
-		Pattern Clones & Clones for defining online cloning patterns & 697 \\
-		\hline 
-	\end{tabular} 
-\end{table}
-
-\subsubsection{Reported Clones Result Set} 
+\textbf{Clone Detection Tools: }
 We use clone detection to discover online code clones. 
@@
 % from two locations so no filtering was needed.
-%\subsection{Clone Detection Configuration}
-
+
+\textbf{Clone Detection Configuration: }
 We were aware of effects of configurations to clone detection results
@@
 
-\subsubsection{Filtered Clones Result Set}
-
+\subsubsection{Phase 2: Clone Filtering}
 As there are in total 315,786,118 clone pairs reported, it is
@@
 $N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
-$N_D$, we ended up with a set of 32,533 online clone pair candidates
-for manual inspection.
-
-\begin{table}
-	\centering
-	\caption{The seven patterns of online code cloning}
-	\label{tab:classification_scheme}
-	%\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{c@{~~}p{7.35cm}}
-			\hline 
-			Patt. & Description \\ 
-			\hline 
-			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\
-
-			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\
-
-			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
-
-			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
-			\hline 
-			BP & Boiler-plate or IDE auto-generated \\
-
-			IN & Inheritance, interface implementation  \\
-
-			AC & Accidental similarity, false clones \\ 
-			\hline 
-		\end{tabular}  %
-	%}
-\end{table}
-
-\subsection{RQ2: Patterns of Online Code Cloning}
-As we are interested in the patterns of online code clones, we studied
-the 8 patterns of cloning from Kapser et
+$N_D$, we ended up with a set of 32,533 online clone pair candidates.
+
+Before performing the manual
+investigation, we created and used an automatic classifier 
+to classify boiler-plate code of {\small\texttt{equals()}}, 
+{\small\texttt{hashCode()}} and getters/setters 
+(depicted with a grey line in \Cref{fig:exp_framework}).
+The classifier could automatically classify 28,897 clone pairs 
+and left 3,636 clone pairs for manual investigation in phase 3 to 6.
+
+\subsubsection{Phase 3-4: Clone Validation and Classification}
+We relied on the 3,636 filtered clone pairs after automatic classification for
+manual validation and classification.
+The validation and classification of the clone pairs were done at the same time. 
+The clone validation process involves checking 
+if a clone pair is either true positive or false positive. 
+Moreover, we are also interested in the patterns of code cloning 
+so we can gain more insights into how these clones are created.
+
+For manual investigation, the first author, who has been working on clone detection research for 
+two years, took the role of the main investigator performing a manual 
+validation of the filtered clone pairs. 
+%By consulting the cloning patterns, 
+The main investigator went through each clone pair candidate, 
+looked at the clones, and decided if they are true positive or
+false positive and classified them into an appropriate pattern. 
+%the most appropriate cloning pattern for the pair. 
+To mitigate the human errors of the manual investigation, 
+the second author took the role of the validating investigator, performing a
+validation on 10\% of the clone pairs judged by the main
+investigator. After the validation, the results from the two
+investigators were compared and conflicts were discussed and resolved.
+If the two investigator cannot find a consensus, the third author is 
+involved for the final judgement.
+
+Regarding the online cloning classification patterns, 
+we studied the 8 patterns of cloning from Kapser et
 al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
-evaluate its applicability to our study by using a small subset of the
-reported online clones.
-
-\subsubsection{Pattern Clones Result Set}
-Using the $S_D$ clone report,
-snippets were ranked according to (1)~clone pair frequency,
-(2)~popularity (i.e.~number of associated Qualitas projects),
-(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
-selected these four criteria so that we could cover the online clones
-from various aspects. We selected the top 10 from each ranking and
-obtained 34 unique Stack Overflow snippets. The snippets were
-associated with 697 clone pairs.
-
-\subsubsection{Defining Online Code Cloning Patterns}
-Using Kapser's cloning patterns and the Pattern Clones Result Set, the
+evaluate its applicability to our study. 
+We have tried to classify 697 online clone pairs from
+the reported clones in phase 1 
+%Using the $S_D$ clone report,
+%snippets were ranked according to (1)~clone pair frequency,
+%(2)~popularity (i.e.~number of associated Qualitas projects),
+%(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
+%selected these four criteria so that we could cover the online clones
+%from various aspects. We selected the top 10 from each ranking and
+%obtained 34 unique Stack Overflow snippets. The snippets were
+%associated with 697 clone pairs.
+%\subsubsection{Defining Online Code Cloning Patterns}
+using Kapser's cloning patterns. We found that the
 clone pairs were categorised into either Customisation or Templating.
-However, Kapser's cloning patterns are too broad for our study and a
+Thus, Kapser's cloning patterns are too broad for our study and a
 more suitable and fine-grained classification scheme is needed. After
@@
 but where we could not find any attribution of copying.
-
 Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
@@
 
-The first author, who has been working on clone detection research for 
-two years, took the role of the main investigator performing a manual 
-classification of the filtered clone pairs. By consulting the cloning 
-patterns, the main investigator went through each clone pair candidate, 
-looked at the clones, and chose the most appropriate cloning pattern 
-for the pair. To mitigate the human errors of the manual classification, 
-the second author took the role of the validating investigator, performing a
-validation on 10\% of the clone pairs judged by the main
-investigator. After the validation, the classifications from the two
-investigators were compared and conflicts were discussed and resolved.
-If the two investigator cannot find a consensus, the third author is 
-involved for the final judgement.
+\begin{table}
+	\centering
+	\caption{The seven patterns of online code cloning}
+	\label{tab:classification_scheme}
+	%\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{c@{~~}p{7.35cm}}
+			\hline 
+			Patt. & Description \\ 
+			\hline 
+			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\
+
+			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\
+
+			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
+
+			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
+			\hline 
+			BP & Boiler-plate or IDE auto-generated \\
+
+			IN & Inheritance, interface implementation  \\
+
+			AC & Accidental similarity, false clones \\ 
+			\hline 
+		\end{tabular}  %
+	%}
+\end{table}
+
+\subsubsection{Phase 5: Outdated Clones}
+Outdated code occurs when a piece of code has been copied from its
+origin to another location and later the original has been
+updated~\cite{Xia2014}. Usually code clone detection is used to locate
+clone instances and update them to match with the
+originals~\cite{Bellon2007}. However, online code clones are more
+difficult to detect than in regular software projects due to its large
+search space and a mix of natural and programming languages combined
+in the same post.
+%Moreover, Stack Overflow is not a software.
+There is no test suite to run and check whether the validity of the code snippets.
+To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.
+
+To search for outdated online code clones, we focused on the
+\textbf{QS} clone pairs that were cloned from Qualitas to Stack
+Overflow and compared them with their latest versions. We downloaded
+the latest version of the Qualitas projects from their repositories on
+26 September 2016. For each \textbf{QS} online clone pair, we used the
+clone from Qualitas a a proxy. We searched for its latest version by
+the file name and located the cloned region in the file based on the
+method name.
+%For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. 
+We then compared the Stack Overflow snippet to its latest version
+line-by-line to find if any change has been made to the source
+code. We also made sure that the changes did not come from the
+modifications made to the Stack Overflow snippets by the posters but
+from the updates in the projects themselves. When we found
+inconsistent lines between the two versions, we used
+{\small\texttt{git blame}} to see who modified those lines of code and
+the timestamps.
+
+\subsubsection{Phase 6: Licensing Analysis}
+Software licensing plays an important role in software
+development. Violation of software licenses impacts software delivery
+and also leads to legal issues~\cite{Sprigman2015}.
+%It is an emerging area that software engineering research community is paying attention to. For example, 
+One can run into a licensing issue if one integrates third-party
+source code into their software without checking. A study by An et
+al.~\cite{An2017} reports 1,219 cases of potential license violations
+between 399 Android apps and Stack Overflow code
+snippets.
+
+We analysed licensing conflicts of the online clones in the
+\textbf{QS}, \textbf{EX}, and \textbf{UD} set. The
+licenses were extracted by \emph{Ninka}, an automatic license
+identification tool~\cite{German2010}. Since Ninka works at file
+level, we report the findings based on Stack Overflow snippets and
+Qualitas source files instead of the clone pairs (duplicates were
+ignored). For the ones that could not be automatically identified by
+Ninka and have been reported as {\small\texttt{SeeFile}} or
+{\small\texttt{Unknown}}, we looked at them manually to see if any
+license can be found. The table shows the license mapping of Stack
+Overflow snippets and Qualitas source code. The results are reported
+separately for the \textbf{QS}, \textbf{EX}, and \textbf{UD} set.
+
+%\subsection{Analysis Methods}
+We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
+to answer our four research questions. 
+To answer RQ1, we rely on the number of manually validated true positive online clone pairs
+in phase 3. We use the results of the manual classification using the
+patterns of online code cloning to answer RQ2. 
+For RQ3, we looked at the true positive clone pairs that are classified 
+as cloned from Qualitas to Stack Overflow and
+checked if they have been changed since they have been
+cloned. Similarly, for RQ4, we looked at the license of each clone in the pattern 
+QS, EX, UD and checked for a possibility of a licensing violation.
 
@@
 
-We used the experimental framework (\Cref{fig:exp_framework}) to
-detect clones between Stack Overflow and the Qualitas corpus using the
-two selected clone detectors. To answer RQ1, we computed statistics on
-discovered clones. To answer RQ2, we manually investigated online
-clone pair candidates and categorised them using patterns of online
-code cloning. For RQ3, we looked at the true positive clone pairs and
+We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
+to answer our four research questions. 
+To answer RQ1, we rely on the number of manually validated true positive online clone pairs
+in phase 3. We use the results of the manual classification by the
+seven patterns of online code cloning to answer RQ2 (phase 4). 
+For RQ3, we looked at the true positive clone pairs that are classified 
+as cloned from Qualitas to Stack Overflow and
 checked if they have been changed since they have been
-cloned. Similarly, for RQ4, we looked at the license of each clone and
-checked for a possibility of a licensing violation.
+cloned (phase 5). Similarly, for RQ4, we looked at the license of each clone in the pattern 
+QS, EX, UD and checked for a possibility of a licensing violation (phase 6).
 
 \subsection{RQ1: Online Code Clones}
+
+The number of online clone pairs reported by running Simian and NiCad
+are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
+pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
+much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
+respectively. This is expected since EvaClone configurations prefer
+recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
+9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
+$N_D$ has an average clone size of 10.85 lines which is bigger than
+6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
+configuration with a smaller minimum size (\Cref{t:param_tuning}).
+
+\begin{table}
+	\centering
+	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
+	\label{tab:orig_stats}
+	%\small
+	%\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r}
+		\hline
+		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
+		\hline
+		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
+		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
+		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
+		\hline
+	\end{tabular} %
+	%}
+\end{table}
+
+The statistics on clones obtained from the different data sets are
+presented in \Cref{tab:snippets}. Simian in the default configuration
+($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
+144,064 Stack Overflow snippets, associated with 92 Qualitas
+projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
+snippets containing clones associated with all 111 Qualitas
+projects. NiCad in the default configuration ($N_D$) reported clones
+between 1,392 Stack Overflow code snippets and 88 Qualitas
+projects. NiCad in the EvaClone configuration ($N_E$) reported the
+largest number of 12,886 cloned snippets mainly due to the more
+relaxed configuration. The $N_E$ snippets are associated with 88
+Qualitas projects.  For the cloned Stack Overflow snippets, the
+average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
+38\%, 50\%, 30\%, and 33\% respectively.
+% A quick manual check of Simian's clone report revealed that there
+% were 11 problematic snippets. These 11 snippets triggered Simian to
+% generate large clone clusters containing a huge number of false
+% clones from array initialisation. Hence, their clones were removed
+% from further analyses.
+
+% \FIXME{Do you think we should report at this level or in more details 
+% 	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}
+% I don't think there is a need.
+
+\begin{table}
+\caption{Investigated online clone pairs and corresponding snippets
+  and Qualitas projects for the different data sets}
+\label{tab:snippets}
+\centering
+\begin{tabular}{l|rrrr}
+  \hline 
+  Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
+  \hline 
+  \multicolumn{5}{l}{\textit{Reported Clones}} \\
+  \hline
+  $S_D$ & 67,570 & 1,086 & 92 & 38\% \\
+  $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
+  $N_D$ & 632,855& 1,392 & 88 & 30\% \\
+  $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
+  \hline
+  Total & 315,786,118 & 14,856 & 111 & 38\% \\
+  \hline
+  \multicolumn{5}{l}{\textit{Filtered Data Set}} \\
+  \hline
+  \textit{good} & 2,313 & 97 & 67 & 23\% \\
+  \textit{ok'} & 12,336 & 139 & 43 & 28\% \\
+  $S_D'$ & 17,081 & 460 & 74 & 31\% \\
+  $N_D'$ & 83 & 44 & 19 & 27\% \\
+  \hline
+  Total & 32,533 & 623 & 96 & 27\%\\
+  \hline 
+%  \multicolumn{5}{l}{\textit{Filtered Data Set without AC}} \\
+%  \hline 
+%  $\textit{good}/\textrm{AC}$ & 141 & 52 & 26 & 23\% \\
+%  $\textit{ok'}/\textrm{AC}$ & 12,229 & 126 & 36 & 28\% \\
+%  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
+%  $N_D'/\textrm{AC}$ & 70 & 39 & 16 & 29\% \\
+%  \hline
+%  Total & 30,113 & 556 & 80 & 28\% \\
+%  \hline
+  \multicolumn{5}{l}{\textit{True Positives in Manually Validated Clones}} \\
+  \hline 
+  $\textit{good}/\textrm{AC}$ & 131 & 51 & 24 & 22\% \\
+  $\textit{ok'}/\textrm{AC}$ & 152 & 83 & 22 & 21\% \\
+  $S_D'/\textrm{AC}$ & 873 & 337 & 60 & 35\% \\
+  $N_D'/\textrm{AC}$ & 60 & 33 & 15 & 27\% \\
+  \hline
+  Total & 1,216 & 516 & 75 & 26\% \\
+  \hline
+\end{tabular}
+\end{table}
+
+However, using Bellon's criteria for matching clone pairs, only
+0.1\textperthousand~of all pairs are agreed by two tool/configuration
+combinations. As shown in \Cref{tab:snippets}, for the 2,313
+\textit{good} pairs, there are 97 Stack Overflow snippets which are
+associated with 67 Qualitas projects. The 12,336 \textit{ok'} pairs
+are clones between 139 Stack Overflow snippets and 43 Qualitas
+projects.  Moreover, for the disagreed pairs, we found 17,081 clone
+pairs reported by $S_D'$ are clones between 460 Stack Overflow
+snippets and 74 Qualitas projects and 83 $N_D'$ clone pairs are clones
+between 44 Stack Overflow snippets and 19 Qualitas projects. In total
+we found that the filtered data sets contains 32,533 clone pairs which
+are clones between 623 Stack Overflow snippets and 96 Qualitas
+projects.
+
+During the manual investigation of 3,636 clone pairs, we identified 2,420 pairs
+as being accidential clones (AC), i.e.~false positives. After removing
+them, the data set still contains 1,216 true positive clone pairs between 516 Stack
+Overflow snippets and 75 Qualitas projects.
+
+\textbf{To answer RQ1, we found most Qualitas projects to share
+  similar code with Stack Overflow code snippets. In the manually confirmed 
+  data set of 3,636 clone pairs, we found 1,216 pairs as true positives and 
+  they account for a majority of 75 Qualitas projects and
+  516 Stack Overflow code snippets.}
+
+%\FIXME{Should we have removed the AC clones right at the beginning?}
+
+\subsection{RQ2: Patterns of Online Code Cloning}
+
+\begin{table}
+	\centering
+	\caption{No.~of online clones candidates for the classification}
+	\label{tab:online_clone_classification_results}
+	%\small
+	%	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r}
+		\hline
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
+		& & Auto & Manual \\
+		\hline 
+		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
+		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
+		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
+		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
+		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
+		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+		\hline
+		Total  & 32,533 & 28,897 & 3,636 \\ 
+		\hline
+	\end{tabular} %
+	%}
+\end{table}
+
+As shown in \Cref{tab:online_clone_classification_results}, the automatic
+classifier helped us to classify 28,897 clone pairs into
+pattern \textbf{BP}. Then, we relied on a manual study to qualitatively investigate the patterns of
+online code cloning. To achieve this, we classified all 32,533
+selected clone pairs according to the pre-defined classification process 
+(\Cref{fig:classification_process}).  
+%
+There were 3,636 pairs left for the manual check. 
+ The classification
+results are shown in \Cref{tab:classification_good_o} and explained in
+the following.
+
+\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
+online clone pairs with evidences of cloning from Qualitas projects to
+Stack Overflow. They include 3, 14, 86, and 9 pairs from the
+\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
+them have a statement in the Stack Overflow post saying that the code
+is ``copied'', ``borrow'' or ``modified'' from a specific file or class in a
+Qualitas project. For example, according to the motivating example in 
+\Cref{fig:before-after}, we found evidence in the Stack Overflow 
+Post 22315734 saying that \textit{``Actually, you can learn how to compare 
+in Hadoop from WritableComparator. Here is an examle that borrows 
+some ideas from it.''}
+
+The most cloned projects are \textsf{hibernate} and
+\textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15
+pairs), and \textsf{hadoop} (12 pairs). The clones are used as
+examples and are very similar to their original Qualitas code with
+limited modifications.
+
+\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
+any clone pairs with evidence of cloning from Stack Overflow to
+Qualitas projects.
+
+\textbf{EX: External Sources.} We found 200 online clone pairs with
+evidence of cloning from external sources to Stack Overflow. 
+They include 4, 44, 146, and 6 clone pairs from the \textit{good},
+\textit{ok'}, $S_D'$, and $N_D'$ set respectively. All of them
+contain statements showing an external source of the cloned code.
+For example, Stack Overflow Post 9549009 contains a code comment saying \textit{``Copied 
+	shamelessly from org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator,
+	changed only the hash algorithm.''}
+
+These findings complement a study of clones between software
+projects~\cite{Svajlenko2014}. We found that the code cloning can also
+happen among different sources on the Internet just like software
+projects. There are 30 clone pairs that originated from programming
+websites. For example, we found a clone of code snippet to convert
+numbers into words which is copied from
+\url{www.rgagnon.com/javadetails/java-0426.html}. Both the Stack
+Overflow and the \textsf{compiere} project source code contain an
+attribution to the original source. Another example is a code snippet
+to generate graphical \textit{Perlin noise}. It is copied from
+\url{http://mrl.nyu.edu/~perlin/noise/}. The code is used on Stack
+Overflow and in the \textsf{aoi} project with
+attribution.
+% The original code of the 15 clone pairs do not have licensing
+% information so these clones do not violate any license.
+There are other EX clone pairs which are copied from third-party
+libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util},
+\textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography
+project.
+
+\textbf{UD: Unknown Direction.} We found 359 online clone pairs with
+no evidence of cloning between Qualitas and Stack Overflow but with a
+high code similarity that suggests cloning. They include 15, 20, 293,
+and 31 pairs from the \textit{good}, \textit{ok'}, $S_D'$, and $N_D'$
+set respectively. The most cloned projects is \textsf{netbeans} with
+93 clone pairs. Most of the clones are a large chunk of code handling
+GUI components. Although these GUI clones might be auto-generated by
+IDEs, we did not find any evidence. The second most cloned project is
+\textsf{jung2} (62 pairs), a network and graph framework, followed by
+\textsf{eclipse-SDK} (37 pairs).
+% There are several Stack Overflow snippets that are identical to code
+% in \textsf{jung2}.
+
+\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate
+clone pairs found in this study. %Although we have removed some of the
+%boiler-plate code with filters before the analysis, we still 
+We observed 29,330 such clone pairs. The \textbf{BP} clone pairs account for
+90\% of all clone pairs we classified. The majority of them are
+{\small{\texttt{equals()}}} methods.
+
+\textbf{IN: Inheritance/interface.} There were 112 clone pairs found
+to be similar because they implement the same interface or inheriting
+from the same class. An example is the two implementations of
+{\small{\texttt{MouseListener}}} that share similar
+{\small\texttt{@Override}} methods of {\small\texttt{mousePressed}},
+and {\small\texttt{mouseReleased}}.
+
+\textbf{AC: Accidental Clones.} There were 2,420 accidental clone
+pairs. Mainly, they are false positive clones caused by code
+normalisation. 
+% However, the original source code were still different enough when
+% we manually classified them.
+Other clone instances include {\small\texttt{finally}} or
+{\small\texttt{try-catch}} clauses that were accidentally the same due
+to their very small sizes, and similar {\small\texttt{switch-case}}
+statements.
+
+\begin{table}
+	\centering
+	\caption{Classifications of online clone pairs.}
+	\label{tab:classification_good_o}
+	%\small
+	%\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{l|rrrr|rrr|r}
+			\hline
+			Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
+			\hline
+			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
+			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 44 & 20 & 12,128 & 23 & 107 & 12,336 \\
+			\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
+			\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
+			\hline
+			Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
+			\hline
+		\end{tabular} 
+	%}
+\end{table}
+
+%For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code.
+Our regular expressions could automatically classified 16,800 of them into BP.
+The investigator checked the 1,001 remaining pairs manually.
+As a result, we found 86 QS, 294 UD, 145 EX, 17,074 BP, 74 IN and 128 AC pairs.
+For 88 $N_D$ clone pairs, 10 of them were automatically classified into BP and 78 were manually classified.
+We found 9 QS, 35 UD, 6 EX, 17 BP, 8 IN, and 13 AC respectively.
+
+%FIXME: We probably have to discuss IN clones.
+%FIXME: the numbers where 28,642 and 2,529 which I could not find elsewhere.
+\textbf{To answer RQ2, we found that a large amount of the clone pairs
+  between Stack Overflow and Qualitas projects are boiler-plate code
+  (29,330) or accidental clones (2,420) with no evidence that the code
+  has actually been copied. Nevertheless, we found 112 pairs that had
+  strong evidences to be cloned from Qualitas to Stack Overflow and
+  200 pairs were found to be cloned to Stack Overflow from external
+  sources outside Qualitas projects.} 
+%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
+
+\subsection{RQ3: Outdated Online Code Clones}
+
+%In this study, we are interested in effects of having code clones between open source software systems and Stack Overflow.
+From the manual investigation, we found 523 true positive online clone pairs.
+With this set of true clones, we investigated further and found that there are two potential issues, outdated code and software licensing violation.
+
+%\subsubsection{Outdated Clones}
+
+We discovered 64 outdated online clone pairs out of 112 pairs. As
+shown in \Cref{fig:outdated}, \textsf{spring} has the highest number
+of 17 outdated pairs, followed by 7 from \textsf{hibernate} and
+\textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
+outdated code in % \textsf{hadoop}'s
+{\small{\texttt{WritableComparator.java}}} 
+from \textsf{hadoop} shown in
+\Cref{fig:before-after}, we also found a few outdated code elements
+which contained a large amount of modifications. For example, the code
+snippet in Stack Overflow post 23520731 is a copy of
+{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
+has been heavily modified on 5 February 2016.
+
+In the 64 outdated pairs, we found 5 ``dead'' snippets. These snippets
+cannot be located in the latest version of the projects. For example,
+the snippet in Stack Overflow post 3758110, a copy of
+{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
+\textsf{spring}, was deleted in the commit
+{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
+Beams on 20th January 2012, two years after it was
+posted. 
+% The latest version of Spring does not contain the file anymore.
+\Cref{tab:stale_code_details} shows examples of the outdated online
+clones on Stack Overflow. The table displays information of the clones
+from both Stack Overflow and Qualitas side including the dates. We
+summarise the changes that make the clones outdated into three types,
+modified/added/deleted statements (\textit{S}), file deletion
+(\textit{D}), and method rewriting (\textit{R}), along with the date
+of change.
+
+The outdated online code clones cause problems ranging from
+uncompilable code (due to modifications and different API usage in the
+outdated code) to introducing vulnerabilities to
+software~\cite{Xia2014}. An outdated code with a subtle change
+(e.g.~\Cref{fig:before-after}) may be copied and reused without
+awareness from developers. Although Stack Overflow has a voting
+mechanism that may mitigate this issue, the accepted answer is still
+used by naive developers who copy and reuse the outdated code.
+
+\textbf{For RQ3, our results show that more than half (64) of QS clone
+  pairs on Stack Overflow are outdated. 60 pairs differ from their
+  newest versions by modifications applied to variable names or method
+  names, added or deleted statements, to a fully rewritten code with
+  new method signatures. 4 pairs are dead
+  snippets.}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{freshness}
+	\caption{Status of the 112 QS online clone pairs}
+	\label{fig:outdated}
+\end{figure}
+
+\begin{table*}
+	\centering
+	\caption{Examples of the outdated QS online clones}
+	\label{tab:stale_code_details}
+	%\small
+	%\resizebox{\textwidth}{!}{%
+		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
+		 \hline
+		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
+		 \hline
+		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
+		 \hline
+		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
+		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
+		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
+		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
+		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
+		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
+		 \hline 
+		 \multicolumn{10}{l}{{\footnotesize * \textit{S}:
+                  modified/added/deleted statements, \textit{D}: file
+                  has been deleted,  \textit{R}: method has been
+                  rewritten completely}}
+		\end{tabular} %
+	%}
+\end{table*}
+
+\subsection{RQ4: Software Licensing Violation}
+
+\begin{table}[]
+	\centering
+	\caption{License mapping of  online clones (file-level)}
+	\label{tab:license_abc}
+	\small
+	%\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|p{1.95cm}l|rrr}
+		\hline
+		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
+		\hline
+		Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
+		License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
+		& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
+		& MIT-like & MIT-like & 0 & 1 & 0\\
+		& No license & CC BY-NC-SA & 0 & 5 & 0 \\
+		& No license & No license & 5 & 4 & 21 \\
+		\hline
+		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
+		\hline
+	    Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
+		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
+		& No license & Apache-2 & 41 & 6 & 23 \\
+		& No license & BSD3 & 3 & 4 & 28 \\
+		& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
+		& No license & CDDLv1 & 0 & 1 & 0 \\
+		& No license & EPLv1 & 7 & 0 & 10 \\
+		& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
+		& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
+		& No license & MPLv1.1 & 0 & 0 & 1 \\
+		& No license & spdxBSD3 & 0 & 0 & 10 \\
+		& No license & SPLv1 & 0 & 1 & 0 \\
+		& No license & Unknown & 0 & 3 & 3 \\
+		& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
+		\hline
+		\multicolumn{3}{l|}{Total} &  79 & 77 & 202 \\
+		\hline
+	\end{tabular} %
+%}
+\end{table}
+
+%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
+In our study, we reveal another possible situation of software
+licensing issues caused by code cloned to Stack Overflow. We found
+evidence that 112 pieces of code have been copied from Qualitas
+projects to Stack Overflow as examples. Their status of accepted
+answers increase their chances of being reused. Even though most of
+the Qualitas projects came with a software license, we found that the licensing information
+were frequently missing after the code was copied to Stack
+Overflow. The licensing terms on top of source code files are not
+copied because usually only a small part of the file was
+cloned. In overall, we can see that most of the Stack Overflow snippets do not
+contain licensing terms while their clone counterparts in Qualitas
+projects do. The summary of
+licensing information is listed in \Cref{tab:license_abc}.
+
+\textbf{Compatible license:} There are 40 pairs which have compatible
+licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
+  License v.1 (EPLv1)}; or a pair of no license vs.~\emph{Creative
+  Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC
+  BY-NC-SA 3.0)}. These clones are safe for being reused. Since source
+code and text on Stack Overflow are
+protected by \emph{CC BY-NC-SA 3.0}
+, we can treat the Stack Overflow code snippets
+without licensing information as having \emph{CC BY-NC-SA 3.0} by
+default. The \emph{CC BY-NC-SA 3.0} license is relaxed and it only
+requests an attribution when reused.
+
+\textbf{Incompatible license:} there are 358 clone pairs which do not
+contain licensing information after they are posted on Stack Overflow
+or contain a different license from their Qualitas clone
+counterparts. More than half (79) of \textbf{QS} clone pairs have
+their licensing terms removed or changed when posted on Stack
+Overflow. For \textbf{EX} clone pairs, we searched for licensing terms of the
+original source code from the external sources. We found that 77 out
+of 88 EX clone pairs have incompatible licenses.
+%They are clones that have been identified to be copied from an external source.
+Similarly, the license statement was removed from Stack Overflow
+snippets. Of 226 \textbf{UD} clone pairs, 202 pairs have incompatible
+licenses. Again, most of the clones in Qualitas contain a license
+while the Stack Overflow snippets do not.
+%
+%\Cref{fig:sankey_license} shows the direction of changes in online code clone license.
+The direction of the change is from left to right.
+The thickness of the line reflects the number of clones for that relationship.
+In \Cref{fig:sankey_license} (A), we can clearly see that most of the QS online clones have their licenses changed from having a license to ``No license'' on Stack Overflow.
+The same findings were found for EX online clones as depicted in \Cref{fig:sankey_license} (B).
+We found that most of the EX clones have their licensing information stripped of after copying to Stack Overflow.
+These clones are instead covered by the default CC BY-NC-SA 3.0 license of Stack Overflow which is strongly permissive.
+These used-to-be-licensed code are dangerous for being reused because they can implicitly conflict with the reused software's license.
+
+\textbf{For RQ4, we found 358 code snippets on Stack Overflow that
+  violate the license of their original software. The majority of them
+  do not contain licensing statements after they have been copied to
+  Stack Overflow.}
+
+\section{Overall Discussion}
+%What can we learn for the results?
+For example, if a developer explicitly reports in his/her code that the snippet was copied from stackoverfow, are there some benefits?
+We could notify - for instance - the developer when some new issues related to the snippet are posted on stackoverflow?
+Or could we force people posting code on SO to explicitly report licensing information?
+Or, could we implement an intelligent IDE that when pasting code from external resource checks for licensing violation?
+These of course are only some (crazy?) ideas that could be developed on the top of the results we have achieved with this study...
+
+%We discovered two issues regarding code snippets on Stack Overflow in this study: (1)  outdated online clones on Stack Overflow and (2) missing or incompatible license in Stack Overflow snippets. 
+%that there is a considerable amount of cloned code between Stack Overflow that are cloned from 111 projects in the Qualitas corpus.
+64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals.
+To mitigate the problems of outdated online clones and missing or incompatible license on Stack Overflow code snippets, we propose the following actionable items:
+
+\textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' license software projects and posted on Stack Overflow.
+Moreover, an IDE plug-in that can automatically detect pasted source code and track their origins with licensing check could also prevent the issue of license-violating Stack Overflow code snippets.
+
+\textbf{Detective measure:} A system to detect outdated source code snippets on Stack Overflow is needed.
+If a code snippet is copied from an external project with other licenses than CC BY-NC-SA, the poster has to provide the information of the project including the original file name and its online repository (if exists).
+The system can leverage clone detection tools/techniques to periodically locate and check if the cloned snippet is still up-to-date with its original.
+With such a system, the poster can be notified when the code has been updated in the original project so that he/she can update their code on Stack Overflow accordingly.
+
+\section{Threats to Validity}
+
+\textbf{Internal validity:}
+
+We could not verify all the 315,786,118 clone pairs reported by the
+clone detection tools in this study.  Nevertheless, we applied
+different mechanisms to ensure the validity to the subset of clone
+pairs we classified.  First, we used two, instead of one, widely-used
+clone detection tools, Simian and NiCad.  We had tried three other
+clone detectors but could not add them to the study due to their
+scalability issue and susceptibility to incomplete code snippets.
+Second, we adopted Bellon's clone agreement metric~\cite{Bellon2007}
+to prioritise and filters clone pairs for the manual
+classification. The agreed clone pairs that passed \textit{good} and
+\textit{ok} criteria had a higher chance to be true positive. We also
+applied the Bellon's clone agreement to 4 different combinations of
+the tools' configurations.  For disagreed clone pairs, we applied
+several filters to remove spurious and uninteresting clones.
+
+The number of online clones we found are subject to the clone
+detectors and their configurations.  We mitigated the problem of clone
+detector's parameter sensitivity by adding another configuration,
+besides the default configuration. We reused the established
+configurations from the EvaClone study~\cite{Wang2013}.  We also
+performed a pairwise matching between the default and EvaClone
+configurations of the two clone detection tools.
+
+Our seven patterns of online code cloning may not cover all possible
+online cloning patterns. However, instead of defining the patterns
+beforehand, we resorted to extract them from the data sets. We derived
+them from a manual investigation of 679 online clone pairs and adopted
+one pattern from the study by Kapser et al.~\cite{Kapser2003}.
+
+The 3,632 clone pairs classified manually by the first author are
+subject to manual judgement and human errors.  Although we have tried
+our best to be careful on searching for evidence and classifying the
+clones, some errors may still exist. We mitigated this problem by
+having the second author to validate the classifications with a random
+sampling.  The 64 classification conflicts were discussed and
+resolved.  The third author made a final judgement when no consensus
+could be found by the two authors.
+ %In addition, we are aware of voting mechanism
+%in Stack Overflow and plan to incorporate highest-vote answers in the future work.
+
+\textbf{External validity:} We carefully chose the data sets for our
+experiment so the findings could be generalise as much as possible.
+We selected Stack Overflow because it is one of the most popular
+programming Q\&A websites available with approximately 6.3 million
+users.  There are a large number of code snippets reused from the
+site~\cite{An2017} and there are also several studies encouraging of
+doing
+so~(e.g.~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014}).
+Nonetheless, it may not be representative to all the programming Q\&A
+websites.
+
+Regarding the code snippets, we downloaded a full data dump and
+extracted Java accepted answers. Instead of analysing every post, we
+only focused on posts marked as accepted answers since they are the
+most likely ones to be reused. This yields a total of 144,064
+snippets.  Our findings are limited to these restrictions. They may
+not be generalised to all programming languages and all answers on
+Stack Overflow. On the other hand, we chose the curated Qualitas
+corpus for Java open source projects containing 111 projects
+\cite{QualitasCorpus}.  The projects span over several areas of
+software and has been used in several empirical
+studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although
+it is a curated and well-established corpus, it may not fully
+represent all Java open source software available.
+
+%Lastly, two clone detection tools, Simian and NiCad, are chosen for this study.
+We have not tried all the tools available and they might not be complete representatives of all available clone detection tools.
+
+\section{Related Work}
+
+\FIXME{This needs rewriting}
+
+\textbf{Stack Overflow} is a gold mine for software engineering research.
+Its rich and developer-driven data are invaluable.
+Since posts on Stack Overflow may contain code snippets embedded within natural language text, they become a huge database for source code and code-relevant information.
+The Stack Overflow data set has been put to use in several previous studies.
+In terms of developer-assisting tools, Seahawk is an Eclipse plug-in that searches and recommends relevant code snippets from Stack Overflow~\cite{Ponzanelli2013}.
+A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} achieves the same goal but with improved algorithms.
+The code snippets on Stack Overflow are mostly examples or solutions to programming problems.
+Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
+Furthermore, Treude et al.~\cite{Treude2016}~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation.
+
+Another research area is knowledge extraction from Stack Overflow.
+Nasehi et al.~\cite{Nasehi2012}~studied what makes a good code example by analysing answers from Stack Overflow.
+Similarly, Yang et al.~\cite{Yang2016} report the number of reusable code snippets on Stack Overflow across various programming languages.
+Wang et al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic modelling to analyse questions and answers from Stack Overflow so that they can automatically categorise new questions.
+There are also studies trying to understand developers' behaviours on Stack Overflow, e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}, while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.
+
+\textbf{Code clone detection} is a long-standing research topic in software engineering.
+Whether clones are good or bad for software is still controversial~\cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
+However, by only knowing how many code clones residing in software and how they evolve~\cite{Pate2013,Mondal2011} can provide several valuable insights into the software systems.
+Code clones have several applications such as software plagiarism detection~\cite{Prechelt2002},
+source code provenance~\cite{Davies2013}, and software licensing conflicts~\cite{German2009}.
+
+Two code fragments are clones if they are similar enough according to a given definition of similarity~\cite{Bellon2007}.
+Given an open interpretation of ``definition of similarity'', there are various clone detection tools and their siblings, code plagiarism detectors, invented based on plethora of different code similarity measurements~\cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}.
+Some tools
+use string comparison techniques such as Simian~\cite{simian}.
+NiCad~\cite{Roy2008,Cordy} exploits the Longest Common Subsequence (LCS) string similarity measure after applying code pretty-printing using TXL~\cite{Cordy2006}.
+Many tools do not work on original source code directly but transform them into an
+intermediate representation such as tokens and apply similarity
+measurement on them. These tools include SourcererCC~\cite{Sajnani2016}, CCFinder~\cite{Kamiya2002},
+CP-Miner~\cite{Li2006}, iClones~\cite{Gode2009} and a few more~\cite{Burrows2007, Smith2009, Duric2012, Prechelt2002, Schleimer2003}. 
+To find more challenging clones such as clones with added/deleted/reordered statements or equivalent loop and conditional statements (i.e.~type-3 clones), structural similarity of clones is needed.
+This structural similarity can be discovered by comparing AST as found in CloneDR~\cite{Baxter1998} and Deckard~\cite{Jiang2007a} or by using program dependence
+graphs~\cite{Krinke2001,Komondoor2001}.
+
+Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customisation and Exact match~\cite{Kapser2003,Kapser2008}.
+Our study adopted one of the patterns into our online code cloning patterns.
+
+\textbf{Clone agreement} is useful when a clone oracle is absent.
+Since clone detectors are different in their detection approaches, they may behave differently and report different clones even on the same data set.
+Some researchers exploit these different behaviours of clone detectors by finding their agreement and obtain highly-confident clones~\cite{Bellon2007,Wang2013}.
+Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are more assured to be true clones than the ones reported by only a single tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
+There are studies that report sensitivities of the tools' configurations to the results~\cite{Wang2013,cr2016ssbse}, showing that searching for an optimal configuration for every new data set is preferred.
+
+\textbf{Software licensing} is crucial for open source and industrial software development.
+Di Penta et al.~\cite{DiPenta2010}~studied the evolution of software licensing in six FOSS and found that licensing statements change over time.
+German et al.~\cite{German2009} performed an empirical study of code siblings (code clones among different systems coming from the same source) and found that licensing conflicts can occur between the clone siblings.
+Later, German et al.~\cite{German2010} created Ninka, a tool to automate the identification of software license from program source code.
+We use Ninka to analyse software license from Stack Overflow snippets and Qualitas projects.
+
+\textbf{Reusing of outdated third-party source code} occurs in software development.
+Xia et al.~\cite{Xia2014} show that a large number of open source systems reuse outdated third-party libraries from popular open source projects.
+Using the outdated code give detrimental effects to the software since they may introduce vulnerabilities.
+Our study discovers similar findings in the context of outdated code on Stack Overflow.
+
+The work that is closely similar to us is a study by An et al.~\cite{An2017} where the authors investigated clones between 399 Android apps and Stack Overflow posts.
+They found 1,226 code snippets which were reused from 68 Android apps.
+They also observed that there are 1,219 cases of potential license violations.
+The authors rely on the timestamp to judge whether the code has been copied from/to Stack Overflow along with confirmations from six developers.
+Instead of Android apps, we investigated clones between Stack Overflow and 111 open source projects.
+Their results are similar to our findings that there are clones from software projects to Stack Overflow with potential licensing violations.
+%In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,632 clone pairs.
+We discovered 112 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
+By comparing the clones to their latest versions in the software, we found that 64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
+
+%\section{Future Work}
+%Since this study is limited to only Java language, we are interested in expanding the study further to other popular programming languages such as C, C++, Python, and Javascript on Stack Overflow.
+The similar study of outdated code and software licensing violation can be repeated.
+It is interesting to compare the findings among different programming languages.
+Moreover, other popular software project corpora (e.g.~GitHub) can also be included to increase generalisation of the findings.
+%
+%We are eager to tackle the issues of outdated and license-violating online code clones with an automated tool.
+The tool should incorporate a scalable clone detection method of locate similar code from programming Q\&A websites such as Stack Overflow and online code repositories like GitHub.
+It analyses a software project under development and reports clones that are copied from Stack Overflow.
+The reported clones have traces to their origins in open source projects or websites along with their freshness (fresh/outdated/dead) so that the developer of the project can be aware of changes made to the copied code snippets.
+Lastly, the license of the original source code is also reported so the developer can make an informed decision of whether he or she will incorporate that code snippet into their own project.
+
+\section{Conclusions}
+
+\FIXME{This needs rewriting}
+
+Online code clones are clones that have been copied to Q\&A websites
+such as Stack Overflow. They are similar to clones in software
+projects where they can be outdated and violating software license but
+are much harder to detect. We studied the online code clones between
+Stack Overflow and Qualitas projects, especially 3,632 clone pairs,
+manually in details.
+
+Although we deployed Bellon's clone agreement and multiple filters to
+reduce the number of clone candidates, we still found a large number
+of 51,926 online clone pairs reported by two clone detectors. We
+classify 32,533 clone pairs using our seven patterns of online code
+cloning. We discovered 112 clone pairs that have been copied, with
+evidence, from Qualitas projects to Stack Overflow (QS), 197 clone
+pairs that have been copied from external sources besides Qualitas to
+Stack Overflow (EX), and 359 clone pairs that are highly similar but
+without evidence of copying (UD).
+
+A manual investigation of the 112 QS clone pairs by comparing to their
+latest version (as of 26 September 2016) reveals that 64 of them are
+outdated. Moreover, the study of licensing conflicts of clones in QS,
+EX, and UD shows that 357 code snippets on Stack Overflow do not
+contain licensing statements while their clone counterparts in
+Qualitas projects or external sources do.
+
+This study is among, if not the first, to address the important issues
+of outdated and license-violating online code clones on programming
+Q\&A websites using a hybrid methodology of automatic code clone
+detection and a manual clone investigation.
+
+%
+% The following two commands are all you need in the
+% initial runs of your .tex file to
+% produce the bibliography for the citations in your paper.
+\bibliographystyle{ACM-Reference-Format}
+\bibliography{sigproc}
 
@@
 
-The number of online clone pairs reported by running Simian and NiCad
-are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
-pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
-much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
-respectively. This is expected since EvaClone configurations prefer
-recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
-9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
-$N_D$ has an average clone size of 10.85 lines which is bigger than
-6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
-configuration with a smaller minimum size (\Cref{t:param_tuning}).
-
-\begin{table}
-	\centering
-	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
-	\label{tab:orig_stats}
-	%\small
-	%\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r}
-		\hline
-		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
-		\hline
-		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
-		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
-		\hline
-	\end{tabular} %
-	%}
-\end{table}
-
-The statistics on clones obtained from the different data sets are
-presented in \Cref{tab:snippets}. Simian in the default configuration
-($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
-144,064 Stack Overflow snippets, associated with 92 Qualitas
-projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
-snippets containing clones associated with all 111 Qualitas
-projects. NiCad in the default configuration ($N_D$) reported clones
-between 1,392 Stack Overflow code snippets and 88 Qualitas
-projects. NiCad in the EvaClone configuration ($N_E$) reported the
-largest number of 12,886 cloned snippets mainly due to the more
-relaxed configuration. The $N_E$ snippets are associated with 88
-Qualitas projects.  For the cloned Stack Overflow snippets, the
-average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
-38\%, 50\%, 30\%, and 33\% respectively.
-% A quick manual check of Simian's clone report revealed that there
-% were 11 problematic snippets. These 11 snippets triggered Simian to
-% generate large clone clusters containing a huge number of false
-% clones from array initialisation. Hence, their clones were removed
-% from further analyses.
-
-% \FIXME{Do you think we should report at this level or in more details 
-% 	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}
-% I don't think there is a need.
-
-\begin{table}
-\caption{Investigated online clone pairs and corresponding snippets
-  and Qualitas projects for the different data sets}
-\label{tab:snippets}
-\centering
-\begin{tabular}{l|rrrr}
-  \hline 
-  Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
-  \hline 
-  \multicolumn{5}{l}{\textit{Reported Clones}} \\
-  \hline
-  $S_D$ & 67,570 & 1,086 & 92 & 38\% \\
-  $S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
-  $N_D$ & 632,855& 1,392 & 88 & 30\% \\
-  $N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
-  \hline
-  Total & 315,786,118 & 14,856 & 111 & 38\% \\
-  \hline
-  \multicolumn{5}{l}{\textit{Filtered Data Sets}} \\
-  \hline
-  \textit{good} & 2,313 & 97 & 67 & 23\% \\
-  \textit{ok'} & 12,336 & 139 & 43 & 28\% \\
-  $S_D'$ & 17,081 & 460 & 74 & 31\% \\
-  $N_D'$ & 83 & 44 & 19 & 27\% \\
-  \hline
-  Total & 32,533 & 623 & 96 & 27\%\\
-  \hline 
-  \multicolumn{5}{l}{\textit{True Positives without AC}} \\
-  \hline 
-  $\textit{good}/\textrm{AC}$ & 141 & 52 & 26 & 23\% \\
-  $\textit{ok'}/\textrm{AC}$ & 12,229 & 126 & 36 & 28\% \\
-  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
-  $N_D'/\textrm{AC}$ & 70 & 39 & 16 & 29\% \\
-  \hline
-  Total & 30,113 & 556 & 80 & 28\% \\
-  \hline
-\end{tabular}
-\end{table}
-
-However, using Bellon's criteria for matching clone pairs, only
-0.1\textperthousand~of all pairs are agreed by two tool/configuration
-combinations. As shown in \Cref{tab:snippets}, for the 2,313
-\textit{good} pairs, there are 97 Stack Overflow snippets which are
-associated with 67 Qualitas projects. The 12,336 \textit{ok'} pairs
-are clones between 139 Stack Overflow snippets and 43 Qualitas
-projects.  Moreover, for the disagreed pairs, we found 17,081 clone
-pairs reported by $S_D'$ are clones between 460 Stack Overflow
-snippets and 74 Qualitas projects and 83 $N_D'$ clone pairs are clones
-between 44 Stack Overflow snippets and 19 Qualitas projects. In total
-we found that the filtered data sets contains 32,533 clone pairs which
-are clones between 623 Stack Overflow snippets and 96 Qualitas
-projects. During the manual investigation, we identified 2,420 pairs
-as being accidential clones (AC), i.e.~false positives. After removing
-them, the data set still contains 30,113 clone pairs between 556 Stack
-Overflow snippets and 80 Qualitas projects.
-
-\textbf{To answer RQ1, we found most Qualitas projects to share
-  similar code with Stack Overflow code snippets. Depending on the
-  data set, between 88 to all 111 projects share similar code. The
-  filtered data set has 96 projects share code with Stack
-  Overflow. Even in the manually confirmed data set of 30,113 clone
-  pairs, a majority of 80 Qualitas projects share similar code with
-  Stack Overflow.}
-
-%\FIXME{Should we have removed the AC clones right at the beginning?}
-
-\subsection{RQ2: Patterns of Online Code Cloning}
-
-\begin{table}
-	\centering
-	\caption{No.~of online clones candidates for the classification}
-	\label{tab:online_clone_classification_results}
-	%\small
-	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r}
-		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
-		& & Auto & Manual \\
-		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
-		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
-		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
-		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
-		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\hline
-		Total  & 32,533 & 28,897 & 3,636 \\ 
-		\hline
-	\end{tabular} %
-	%}
-\end{table}
-
-We rely on a manual study to qualitatively investigate the patterns of
-online code cloning. To achieve this, we classified all 32,533
-selected clone pairs according to the process shown in
-\Cref{fig:classification_process}.  Before performing the manual
-classification, we created and used an automatic classifier 
-to classify {\small\texttt{equals()}}, 
-{\small\texttt{hashCode()}} and getters/setters. As shown in
-\Cref{tab:online_clone_classification_results}, the automatic
-classifier helped us to classify 28,897 clone pairs into
-pattern \textbf{BP}.
-%
-There were 3,636 pairs left for the manual check. 
- The classification
-results are shown in \Cref{tab:classification_good_o} and explained in
-the following.
-
-\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
-online clone pairs with evidences of cloning from Qualitas projects to
-Stack Overflow. They include 3, 14, 86, and 9 pairs from the
-\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
-them have a statement in the Stack Overflow post saying that the code
-is ``copied'', ``borrow'' or ``modified'' from a specific file or class in a
-Qualitas project. For example, according to the motivating example in 
-\Cref{fig:before-after}, we found evidence in the Stack Overflow 
-Post 22315734 saying that \textit{``Actually, you can learn how to compare 
-in Hadoop from WritableComparator. Here is an examle that borrows 
-some ideas from it.''}
-
-The most cloned projects are \textsf{hibernate} and
-\textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15
-pairs), and \textsf{hadoop} (12 pairs). The clones are used as
-examples and are very similar to their original Qualitas code with
-limited modifications.
-
-\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
-any clone pairs with evidence of cloning from Stack Overflow to
-Qualitas projects.
-
-\textbf{EX: External Sources.} We found 200 online clone pairs with
-evidence of cloning from external sources to Stack Overflow. 
-They include 4, 44, 146, and 6 clone pairs from the \textit{good},
-\textit{ok'}, $S_D'$, and $N_D'$ set respectively. All of them
-contain statements showing an external source of the cloned code.
-For example, Stack Overflow Post 9549009 contains a code comment saying \textit{``Copied 
-	shamelessly from org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator,
-	changed only the hash algorithm.''}
-
-These findings complement a study of clones between software
-projects~\cite{Svajlenko2014}. We found that the code cloning can also
-happen among different sources on the Internet just like software
-projects. There are 30 clone pairs that originated from programming
-websites. For example, we found a clone of code snippet to convert
-numbers into words which is copied from
-\url{www.rgagnon.com/javadetails/java-0426.html}. Both the Stack
-Overflow and the \textsf{compiere} project source code contain an
-attribution to the original source. Another example is a code snippet
-to generate graphical \textit{Perlin noise}. It is copied from
-\url{http://mrl.nyu.edu/~perlin/noise/}. The code is used on Stack
-Overflow and in the \textsf{aoi} project with
-attribution.
-% The original code of the 15 clone pairs do not have licensing
-% information so these clones do not violate any license.
-There are other EX clone pairs which are copied from third-party
-libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util},
-\textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography
-project.
-
-\textbf{UD: Unknown Direction.} We found 359 online clone pairs with
-no evidence of cloning between Qualitas and Stack Overflow but with a
-high code similarity that suggests cloning. They include 15, 20, 293,
-and 31 pairs from the \textit{good}, \textit{ok'}, $S_D'$, and $N_D'$
-set respectively. The most cloned projects is \textsf{netbeans} with
-93 clone pairs. Most of the clones are a large chunk of code handling
-GUI components. Although these GUI clones might be auto-generated by
-IDEs, we did not find any evidence. The second most cloned project is
-\textsf{jung2} (62 pairs), a network and graph framework, followed by
-\textsf{eclipse-SDK} (37 pairs).
-% There are several Stack Overflow snippets that are identical to code
-% in \textsf{jung2}.
-
-\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate
-clone pairs found in this study. %Although we have removed some of the
-%boiler-plate code with filters before the analysis, we still 
-We observed 29,330 such clone pairs. The \textbf{BP} clone pairs account for
-90\% of all clone pairs we classified. The majority of them are
-{\small{\texttt{equals()}}} methods.
-
-\textbf{IN: Inheritance/interface.} There were 112 clone pairs found
-to be similar because they implement the same interface or inheriting
-from the same class. An example is the two implementations of
-{\small{\texttt{MouseListener}}} that share similar
-{\small\texttt{@Override}} methods of {\small\texttt{mousePressed}},
-and {\small\texttt{mouseReleased}}.
-
-\textbf{AC: Accidental Clones.} There were 2,420 accidental clone
-pairs. Mainly, they are false positive clones caused by code
-normalisation. 
-% However, the original source code were still different enough when
-% we manually classified them.
-Other clone instances include {\small\texttt{finally}} or
-{\small\texttt{try-catch}} clauses that were accidentally the same due
-to their very small sizes, and similar {\small\texttt{switch-case}}
-statements.
-
-\begin{table}
-	\centering
-	\caption{Classifications of online clone pairs.}
-	\label{tab:classification_good_o}
-	%\small
-	%\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{l|rrrr|rrr|r}
-			\hline
-			Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
-			\hline
-			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
-			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 44 & 20 & 12,128 & 23 & 107 & 12,336 \\
-			\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
-			\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
-			\hline
-			Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
-			\hline
-		\end{tabular} 
-	%}
-\end{table}
-
-%For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code.
-Our regular expressions could automatically classified 16,800 of them into BP.
-The investigator checked the 1,001 remaining pairs manually.
-As a result, we found 86 QS, 294 UD, 145 EX, 17,074 BP, 74 IN and 128 AC pairs.
-For 88 $N_D$ clone pairs, 10 of them were automatically classified into BP and 78 were manually classified.
-We found 9 QS, 35 UD, 6 EX, 17 BP, 8 IN, and 13 AC respectively.
-
-%FIXME: We probably have to discuss IN clones.
-%FIXME: the numbers where 28,642 and 2,529 which I could not find elsewhere.
-\textbf{To answer RQ2, we found that a large amount of the clone pairs
-  between Stack Overflow and Qualitas projects are boiler-plate code
-  (29,330) or accidental clones (2,420) with no evidence that the code
-  has actually been copied. Nevertheless, we found 112 pairs that had
-  strong evidences to be cloned from Qualitas to Stack Overflow and
-  200 pairs were found to be cloned to Stack Overflow from external
-  sources outside Qualitas projects.} 
-%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
-
-\subsection{RQ3: Outdated Online Code Clones}
-
-%In this study, we are interested in effects of having code clones between open source software systems and Stack Overflow.
-From the manual investigation, we found 523 true positive online clone pairs.
-With this set of true clones, we investigated further and found that there are two potential issues, outdated code and software licensing violation.
-
-%\subsubsection{Outdated Clones}
-
-Outdated code occurs when a piece of code has been copied from its
-origin to another location and later the original has been
-updated~\cite{Xia2014}. Usually code clone detection is used to locate
-clone instances and update them to match with the
-originals~\cite{Bellon2007}. However, online code clones are more
-difficult to detect than in regular software projects due to its large
-search space and a mix of natural and programming languages combined
-in the same post.
-%Moreover, Stack Overflow is not a software.
-There is no test suite to run and check whether the validity of the code snippets.
-To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.
-
-To search for outdated online code clones, we focused on the 112
-\textbf{QS} clone pairs that were cloned from Qualitas to Stack
-Overflow and compared them with their latest versions. We downloaded
-the latest version of the Qualitas projects from their repositories on
-26 September 2016. For each \textbf{QS} online clone pair, we used the
-clone from Qualitas a a proxy. We searched for its latest version by
-the file name and located the cloned region in the file based on the
-method name.
-%For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. 
-We then compared the Stack Overflow snippet to its latest version
-line-by-line to find if any change has been made to the source
-code. We also made sure that the changes did not come from the
-modifications made to the Stack Overflow snippets by the posters but
-from the updates in the projects themselves. When we found
-inconsistent lines between the two versions, we used
-{\small\texttt{git blame}} to see who modified those lines of code and
-the timestamps.
-
-We discovered 64 outdated online clone pairs out of 112 pairs. As
-shown in \Cref{fig:outdated}, \textsf{spring} has the highest number
-of 17 outdated pairs, followed by 7 from \textsf{hibernate} and
-\textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
-outdated code in % \textsf{hadoop}'s
-{\small{\texttt{WritableComparator.java}}} 
-from \textsf{hadoop} shown in
-\Cref{fig:before-after}, we also found a few outdated code elements
-which contained a large amount of modifications. For example, the code
-snippet in Stack Overflow post 23520731 is a copy of
-{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
-has been heavily modified on 5 February 2016.
-
-In the 64 outdated pairs, we found 5 ``dead'' snippets. These snippets
-cannot be located in the latest version of the projects. For example,
-the snippet in Stack Overflow post 3758110, a copy of
-{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
-\textsf{spring}, was deleted in the commit
-{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
-Beams on 20th January 2012, two years after it was
-posted. 
-% The latest version of Spring does not contain the file anymore.
-\Cref{tab:stale_code_details} shows examples of the outdated online
-clones on Stack Overflow. The table displays information of the clones
-from both Stack Overflow and Qualitas side including the dates. We
-summarise the changes that make the clones outdated into three types,
-modified/added/deleted statements (\textit{S}), file deletion
-(\textit{D}), and method rewriting (\textit{R}), along with the date
-of change.
-
-The outdated online code clones cause problems ranging from
-uncompilable code (due to modifications and different API usage in the
-outdated code) to introducing vulnerabilities to
-software~\cite{Xia2014}. An outdated code with a subtle change
-(e.g.~\Cref{fig:before-after}) may be copied and reused without
-awareness from developers. Although Stack Overflow has a voting
-mechanism that may mitigate this issue, the accepted answer is still
-used by naive developers who copy and reuse the outdated code.
-
-\textbf{For RQ3, our results show that more than half (64) of QS clone
-  pairs on Stack Overflow are outdated. 60 pairs differ from their
-  newest versions by modifications applied to variable names or method
-  names, added or deleted statements, to a fully rewritten code with
-  new method signatures. 4 pairs are dead
-  snippets.} 
 %They do not exist any more in the latest version.} %These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
@@
 %\end{figure*}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{freshness}
-	\caption{Status of the 112 QS online clone pairs}
-	\label{fig:outdated}
-\end{figure}
 
@@
 
-\begin{table*}
-	\centering
-	\caption{Examples of the outdated QS online clones}
-	\label{tab:stale_code_details}
-	%\small
-	%\resizebox{\textwidth}{!}{%
-		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
-		 \hline
-		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
-		 \hline
-		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
-		 \hline
-		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
-		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
-		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
-		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
-		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
-		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
-		 \hline 
-		 \multicolumn{10}{l}{{\footnotesize * \textit{S}:
-                  modified/added/deleted statements, \textit{D}: file
-                  has been deleted,  \textit{R}: method has been
-                  rewritten completely}}
-		\end{tabular} %
-	%}
-\end{table*}
-
-\subsection{RQ4: Software Licensing Violation}
-
-Software licensing plays an important role in software
-development. Violation of software licenses impacts software delivery
-and also leads to legal issues~\cite{Sprigman2015}.
-%It is an emerging area that software engineering research community is paying attention to. For example, 
-One can run into a licensing issue if one integrates third-party
-source code into their software without checking. A study by An et
-al.~\cite{An2017} reports 1,219 cases of potential license violations
-between 399 Android apps and Stack Overflow code
-snippets. %there are studies of automatic technique to identify software licensing from source code files~\cite{German2010}
-
-%\begin{table}
-%	\centering
-%	\caption{Licenses of online clones (file-level) from Qualitas projects}
-%	\label{t:q_projects_license}
-%	%	\resizebox{\columnwidth}{!}{%
-%	\small
-%	\begin{tabular}{l|l|r|r|r}
-%		\hline 
-%		Project & License & QS & UD & Total \\
-%		\hline
-%		netbeans &  CDDL/GPLv2 &  & 57 & 57 \\
-%		&  No license &  & 8 & 8 \\
-%		&  spdxBSD3 &  & 6 & 6 \\
-%		&  MPLv1.1 &  & 1 & 1 \\
-%		&  Unknown &  & 1 & 1 \\
-%		\hline
-%		jung2 &  BSD3 & 2 & 27 & 29 \\
-%		\hline
-%		eclipse-SDK & EPLv1 & 6 & 11 & 17 \\
-%		& CDDL/GPLv2 & 1 & 1 & 2 \\
-%		&  Apache-2 &  & 1 & 1 \\
-%		& No license & 1 &  & 1 \\
-%		& Unknown &  & 1 & 1 \\
-%		\hline
-%		hibernate & LesserGPLv2.1+ & 18 & 4 & 22 \\
-%		\hline
-%		spring & Apache-2 & 18 & 2 & 20 \\
-%		\hline
-%		vuze & GPLv2 &  & 11 & 11 \\
-%		\hline
-%		jstock & GPLv2+ &  & 9 & 9 \\
-%		& Unknown &  & 1 & 1 \\
-%		\hline
-%		tomcat & Apache-2 & 5 & 5 & 10 \\
-%		\hline
-%		hadoop & Apache-2 & 8 &  & 8 \\
-%		& No license & 1 &  & 1 \\
-%		\hline
-%		jfreechart & LesserGPLv2.1+ & 3 & 5 & 8 \\
-%		\hline
-%	\end{tabular} %
-%	%	}
-%\end{table}
-
-\begin{table}[]
-	\centering
-	\caption{License mapping of  online clones (file-level)}
-	\label{tab:license_abc}
-	\small
-	%\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|p{1.95cm}l|rrr}
-		\hline
-		Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
-		\hline
-		Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
-		License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
-		& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
-		& MIT-like & MIT-like & 0 & 1 & 0\\
-		& No license & CC BY-NC-SA & 0 & 5 & 0 \\
-		& No license & No license & 5 & 4 & 21 \\
-		\hline
-		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
-		\hline
-	    Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
-		License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
-		& No license & Apache-2 & 41 & 6 & 23 \\
-		& No license & BSD3 & 3 & 4 & 28 \\
-		& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
-		& No license & CDDLv1 & 0 & 1 & 0 \\
-		& No license & EPLv1 & 7 & 0 & 10 \\
-		& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
-		& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
-		& No license & MPLv1.1 & 0 & 0 & 1 \\
-		& No license & spdxBSD3 & 0 & 0 & 10 \\
-		& No license & SPLv1 & 0 & 1 & 0 \\
-		& No license & Unknown & 0 & 3 & 3 \\
-		& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
-		\hline
-		\multicolumn{3}{l|}{Total} &  79 & 77 & 202 \\
-		\hline
-	\end{tabular} %
-%}
-\end{table}
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=\linewidth]{license_violation}
-%	\caption{Summary of online clones' licensing conflicts}
-%	\label{fig:license_violation}
-%\end{figure}
-
-%\begin{figure*}
-%		\centering
-%		\begin{minipage}{.4\textwidth}
-%			\centering
-%			\includegraphics[width=\linewidth]{sankey_license_qs}
-%			\caption*{(A) QS clones}
-%		\end{minipage}%
-%		\hspace{5ex}
-%		\begin{minipage}{0.4\textwidth}
-%			\centering
-%			\includegraphics[width=\linewidth]{sankey_license_ex}
-%			\caption*{(B) EX clones}
-%		\end{minipage}
-%	\caption{Direction of the changes in online code clone licenses}
-%	\label{fig:sankey_license}
-%\end{figure*}
-
-In our study, we reveal another possible situation of software
-licensing issues caused by code cloned to Stack Overflow. We found
-evidence that 112 pieces of code have been copied from Qualitas
-projects to Stack Overflow as examples. Their status of accepted
-answers increase their chances of being reused. Even though most of
-the Qualitas projects came with a software license, we found that the licensing information
-were frequently missing after the code was copied to Stack
-Overflow. The licensing terms on top of source code files are not
-copied because usually only a small part of the file was
-cloned. 
-%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
-
-We analysed licensing conflicts of the online clones in the
-\textbf{QS}, \textbf{EX}, and \textbf{UD} set. The summary of
-licensing information is listed in \Cref{tab:license_abc}. The
-licenses were extracted by \emph{Ninka}, an automatic license
-identification tool~\cite{German2010}. Since Ninka works at file
-level, we report the findings based on Stack Overflow snippets and
-Qualitas source files instead of the clone pairs (duplicates were
-ignored). For the ones that could not be automatically identified by
-Ninka and have been reported as {\small\texttt{SeeFile}} or
-{\small\texttt{Unknown}}, we looked at them manually to see if any
-license can be found. The table shows the license mapping of Stack
-Overflow snippets and Qualitas source code. The results are reported
-separately for the \textbf{QS}, \textbf{EX}, and \textbf{UD} set. In
-overall, we can see that most of the Stack Overflow snippets do not
-contain licensing terms while their clone counterparts in Qualitas
-projects do.
-
-\textbf{Compatible license:} There are 40 pairs which have compatible
-licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
-  License v.1 (EPLv1)}; or a pair of no license vs.~\emph{Creative
-  Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC
-  BY-NC-SA 3.0)}. These clones are safe for being reused. Since source
-code and text on Stack Overflow are
-protected by \emph{CC BY-NC-SA 3.0}
-, we can treat the Stack Overflow code snippets
-without licensing information as having \emph{CC BY-NC-SA 3.0} by
-default. The \emph{CC BY-NC-SA 3.0} license is relaxed and it only
-requests an attribution when reused.
-
-\textbf{Incompatible license:} there are 358 clone pairs which do not
-contain licensing information after they are posted on Stack Overflow
-or contain a different license from their Qualitas clone
-counterparts. More than half (79) of \textbf{QS} clone pairs have
-their licensing terms removed or changed when posted on Stack
-Overflow. For \textbf{EX} clone pairs, we searched for licensing terms of the
-original source code from the external sources. We found that 77 out
-of 88 EX clone pairs have incompatible licenses.
-%They are clones that have been identified to be copied from an external source.
-Similarly, the license statement was removed from Stack Overflow
-snippets. Of 226 \textbf{UD} clone pairs, 202 pairs have incompatible
-licenses. Again, most of the clones in Qualitas contain a license
-while the Stack Overflow snippets do not.
-%
-%\Cref{fig:sankey_license} shows the direction of changes in online code clone license.
-The direction of the change is from left to right.
-The thickness of the line reflects the number of clones for that relationship.
-In \Cref{fig:sankey_license} (A), we can clearly see that most of the QS online clones have their licenses changed from having a license to ``No license'' on Stack Overflow.
-The same findings were found for EX online clones as depicted in \Cref{fig:sankey_license} (B).
-We found that most of the EX clones have their licensing information stripped of after copying to Stack Overflow.
-These clones are instead covered by the default CC BY-NC-SA 3.0 license of Stack Overflow which is strongly permissive.
-These used-to-be-licensed code are dangerous for being reused because they can implicitly conflict with the reused software's license.
-
-\textbf{For RQ4, we found 358 code snippets on Stack Overflow that
-  violate the license of their original software. The majority of them
-  do not contain licensing statements after they have been copied to
-  Stack Overflow.}
-
-\section{Overall Discussion}
-%What can we learn for the results?
-For example, if a developer explicitly reports in his/her code that the snippet was copied from stackoverfow, are there some benefits?
-We could notify - for instance - the developer when some new issues related to the snippet are posted on stackoverflow?
-Or could we force people posting code on SO to explicitly report licensing information?
-Or, could we implement an intelligent IDE that when pasting code from external resource checks for licensing violation?
-These of course are only some (crazy?) ideas that could be developed on the top of the results we have achieved with this study...
-
-%We discovered two issues regarding code snippets on Stack Overflow in this study: (1)  outdated online clones on Stack Overflow and (2) missing or incompatible license in Stack Overflow snippets. 
-%that there is a considerable amount of cloned code between Stack Overflow that are cloned from 111 projects in the Qualitas corpus.
-64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals.
-To mitigate the problems of outdated online clones and missing or incompatible license on Stack Overflow code snippets, we propose the following actionable items:
-
-\textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' license software projects and posted on Stack Overflow.
-Moreover, an IDE plug-in that can automatically detect pasted source code and track their origins with licensing check could also prevent the issue of license-violating Stack Overflow code snippets.
-
-\textbf{Detective measure:} A system to detect outdated source code snippets on Stack Overflow is needed.
-If a code snippet is copied from an external project with other licenses than CC BY-NC-SA, the poster has to provide the information of the project including the original file name and its online repository (if exists).
-The system can leverage clone detection tools/techniques to periodically locate and check if the cloned snippet is still up-to-date with its original.
-With such a system, the poster can be notified when the code has been updated in the original project so that he/she can update their code on Stack Overflow accordingly.
-
-\section{Threats to Validity}
-
-\textbf{Internal validity:}
-
-We could not verify all the 315,786,118 clone pairs reported by the
-clone detection tools in this study.  Nevertheless, we applied
-different mechanisms to ensure the validity to the subset of clone
-pairs we classified.  First, we used two, instead of one, widely-used
-clone detection tools, Simian and NiCad.  We had tried three other
-clone detectors but could not add them to the study due to their
-scalability issue and susceptibility to incomplete code snippets.
-Second, we adopted Bellon's clone agreement metric~\cite{Bellon2007}
-to prioritise and filters clone pairs for the manual
-classification. The agreed clone pairs that passed \textit{good} and
-\textit{ok} criteria had a higher chance to be true positive. We also
-applied the Bellon's clone agreement to 4 different combinations of
-the tools' configurations.  For disagreed clone pairs, we applied
-several filters to remove spurious and uninteresting clones.
-
-The number of online clones we found are subject to the clone
-detectors and their configurations.  We mitigated the problem of clone
-detector's parameter sensitivity by adding another configuration,
-besides the default configuration. We reused the established
-configurations from the EvaClone study~\cite{Wang2013}.  We also
-performed a pairwise matching between the default and EvaClone
-configurations of the two clone detection tools.
-
-Our seven patterns of online code cloning may not cover all possible
-online cloning patterns. However, instead of defining the patterns
-beforehand, we resorted to extract them from the data sets. We derived
-them from a manual investigation of 679 online clone pairs and adopted
-one pattern from the study by Kapser et al.~\cite{Kapser2003}.
-
-The 3,632 clone pairs classified manually by the first author are
-subject to manual judgement and human errors.  Although we have tried
-our best to be careful on searching for evidence and classifying the
-clones, some errors may still exist. We mitigated this problem by
-having the second author to validate the classifications with a random
-sampling.  The 64 classification conflicts were discussed and
-resolved.  The third author made a final judgement when no consensus
-could be found by the two authors.
- %In addition, we are aware of voting mechanism
-%in Stack Overflow and plan to incorporate highest-vote answers in the future work.
-
-\textbf{External validity:} We carefully chose the data sets for our
-experiment so the findings could be generalise as much as possible.
-We selected Stack Overflow because it is one of the most popular
-programming Q\&A websites available with approximately 6.3 million
-users.  There are a large number of code snippets reused from the
-site~\cite{An2017} and there are also several studies encouraging of
-doing
-so~(e.g.~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014}).
-Nonetheless, it may not be representative to all the programming Q\&A
-websites.
-
-Regarding the code snippets, we downloaded a full data dump and
-extracted Java accepted answers. Instead of analysing every post, we
-only focused on posts marked as accepted answers since they are the
-most likely ones to be reused. This yields a total of 144,064
-snippets.  Our findings are limited to these restrictions. They may
-not be generalised to all programming languages and all answers on
-Stack Overflow. On the other hand, we chose the curated Qualitas
-corpus for Java open source projects containing 111 projects
-\cite{QualitasCorpus}.  The projects span over several areas of
-software and has been used in several empirical
-studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although
-it is a curated and well-established corpus, it may not fully
-represent all Java open source software available.
-
-%Lastly, two clone detection tools, Simian and NiCad, are chosen for this study.
-We have not tried all the tools available and they might not be complete representatives of all available clone detection tools.
-
-\section{Related Work}
-
-\FIXME{This needs rewriting}
-
-\textbf{Stack Overflow} is a gold mine for software engineering research.
-Its rich and developer-driven data are invaluable.
-Since posts on Stack Overflow may contain code snippets embedded within natural language text, they become a huge database for source code and code-relevant information.
-The Stack Overflow data set has been put to use in several previous studies.
-In terms of developer-assisting tools, Seahawk is an Eclipse plug-in that searches and recommends relevant code snippets from Stack Overflow~\cite{Ponzanelli2013}.
-A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} achieves the same goal but with improved algorithms.
-The code snippets on Stack Overflow are mostly examples or solutions to programming problems.
-Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
-Furthermore, Treude et al.~\cite{Treude2016}~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation.
-
-Another research area is knowledge extraction from Stack Overflow.
-Nasehi et al.~\cite{Nasehi2012}~studied what makes a good code example by analysing answers from Stack Overflow.
-Similarly, Yang et al.~\cite{Yang2016} report the number of reusable code snippets on Stack Overflow across various programming languages.
-Wang et al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic modelling to analyse questions and answers from Stack Overflow so that they can automatically categorise new questions.
-There are also studies trying to understand developers' behaviours on Stack Overflow, e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}, while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.
-
-\textbf{Code clone detection} is a long-standing research topic in software engineering.
-Whether clones are good or bad for software is still controversial~\cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
-However, by only knowing how many code clones residing in software and how they evolve~\cite{Pate2013,Mondal2011} can provide several valuable insights into the software systems.
-Code clones have several applications such as software plagiarism detection~\cite{Prechelt2002},
-source code provenance~\cite{Davies2013}, and software licensing conflicts~\cite{German2009}.
-
-Two code fragments are clones if they are similar enough according to a given definition of similarity~\cite{Bellon2007}.
-Given an open interpretation of ``definition of similarity'', there are various clone detection tools and their siblings, code plagiarism detectors, invented based on plethora of different code similarity measurements~\cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}.
-Some tools
-use string comparison techniques such as Simian~\cite{simian}.
-NiCad~\cite{Roy2008,Cordy} exploits the Longest Common Subsequence (LCS) string similarity measure after applying code pretty-printing using TXL~\cite{Cordy2006}.
-Many tools do not work on original source code directly but transform them into an
-intermediate representation such as tokens and apply similarity
-measurement on them. These tools include SourcererCC~\cite{Sajnani2016}, CCFinder~\cite{Kamiya2002},
-CP-Miner~\cite{Li2006}, iClones~\cite{Gode2009} and a few more~\cite{Burrows2007, Smith2009, Duric2012, Prechelt2002, Schleimer2003}. 
-To find more challenging clones such as clones with added/deleted/reordered statements or equivalent loop and conditional statements (i.e.~type-3 clones), structural similarity of clones is needed.
-This structural similarity can be discovered by comparing AST as found in CloneDR~\cite{Baxter1998} and Deckard~\cite{Jiang2007a} or by using program dependence
-graphs~\cite{Krinke2001,Komondoor2001}.
-
-Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customisation and Exact match~\cite{Kapser2003,Kapser2008}.
-Our study adopted one of the patterns into our online code cloning patterns.
-
-\textbf{Clone agreement} is useful when a clone oracle is absent.
-Since clone detectors are different in their detection approaches, they may behave differently and report different clones even on the same data set.
-Some researchers exploit these different behaviours of clone detectors by finding their agreement and obtain highly-confident clones~\cite{Bellon2007,Wang2013}.
-Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are more assured to be true clones than the ones reported by only a single tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
-There are studies that report sensitivities of the tools' configurations to the results~\cite{Wang2013,cr2016ssbse}, showing that searching for an optimal configuration for every new data set is preferred.
-
-\textbf{Software licensing} is crucial for open source and industrial software development.
-Di Penta et al.~\cite{DiPenta2010}~studied the evolution of software licensing in six FOSS and found that licensing statements change over time.
-German et al.~\cite{German2009} performed an empirical study of code siblings (code clones among different systems coming from the same source) and found that licensing conflicts can occur between the clone siblings.
-Later, German et al.~\cite{German2010} created Ninka, a tool to automate the identification of software license from program source code.
-We use Ninka to analyse software license from Stack Overflow snippets and Qualitas projects.
-
-\textbf{Reusing of outdated third-party source code} occurs in software development.
-Xia et al.~\cite{Xia2014} show that a large number of open source systems reuse outdated third-party libraries from popular open source projects.
-Using the outdated code give detrimental effects to the software since they may introduce vulnerabilities.
-Our study discovers similar findings in the context of outdated code on Stack Overflow.
-
-The work that is closely similar to us is a study by An et al.~\cite{An2017} where the authors investigated clones between 399 Android apps and Stack Overflow posts.
-They found 1,226 code snippets which were reused from 68 Android apps.
-They also observed that there are 1,219 cases of potential license violations.
-The authors rely on the timestamp to judge whether the code has been copied from/to Stack Overflow along with confirmations from six developers.
-Instead of Android apps, we investigated clones between Stack Overflow and 111 open source projects.
-Their results are similar to our findings that there are clones from software projects to Stack Overflow with potential licensing violations.
-%In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,632 clone pairs.
-We discovered 112 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
-By comparing the clones to their latest versions in the software, we found that 64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
-
-%\section{Future Work}
-%Since this study is limited to only Java language, we are interested in expanding the study further to other popular programming languages such as C, C++, Python, and Javascript on Stack Overflow.
-The similar study of outdated code and software licensing violation can be repeated.
-It is interesting to compare the findings among different programming languages.
-Moreover, other popular software project corpora (e.g.~GitHub) can also be included to increase generalisation of the findings.
-%
-%We are eager to tackle the issues of outdated and license-violating online code clones with an automated tool.
-The tool should incorporate a scalable clone detection method of locate similar code from programming Q\&A websites such as Stack Overflow and online code repositories like GitHub.
-It analyses a software project under development and reports clones that are copied from Stack Overflow.
-The reported clones have traces to their origins in open source projects or websites along with their freshness (fresh/outdated/dead) so that the developer of the project can be aware of changes made to the copied code snippets.
-Lastly, the license of the original source code is also reported so the developer can make an informed decision of whether he or she will incorporate that code snippet into their own project.
-
-\section{Conclusions}
-
-\FIXME{This needs rewriting}
-
-Online code clones are clones that have been copied to Q\&A websites
-such as Stack Overflow. They are similar to clones in software
-projects where they can be outdated and violating software license but
-are much harder to detect. We studied the online code clones between
-Stack Overflow and Qualitas projects, especially 3,632 clone pairs,
-manually in details.
-
-Although we deployed Bellon's clone agreement and multiple filters to
-reduce the number of clone candidates, we still found a large number
-of 51,926 online clone pairs reported by two clone detectors. We
-classify 32,533 clone pairs using our seven patterns of online code
-cloning. We discovered 112 clone pairs that have been copied, with
-evidence, from Qualitas projects to Stack Overflow (QS), 197 clone
-pairs that have been copied from external sources besides Qualitas to
-Stack Overflow (EX), and 359 clone pairs that are highly similar but
-without evidence of copying (UD).
-
-A manual investigation of the 112 QS clone pairs by comparing to their
-latest version (as of 26 September 2016) reveals that 64 of them are
-outdated. Moreover, the study of licensing conflicts of clones in QS,
-EX, and UD shows that 357 code snippets on Stack Overflow do not
-contain licensing statements while their clone counterparts in
-Qualitas projects or external sources do.
-
-This study is among, if not the first, to address the important issues
-of outdated and license-violating online code clones on programming
-Q\&A websites using a hybrid methodology of automatic code clone
-detection and a manual clone investigation.
-
-%
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{sigproc}
-
 \end{document}

### 2017-02-24 cloneoverflow-latex/cloneoverflow.tex
Updated Sections 1-2.

@@
 
-%\overfullrule1ex
+\overfullrule1ex
 
@@
 Overflow, each conversation contains a question and a list of
-answer(s). The answers frequently contain at least one code snippet as
+answers. The answers frequently contain at least one code snippet as
 a solution to the question asked. We found that the code snippets are
@@
 systems. The process of posting and answering questions on Stack
-Overflow, which involves reusing of source code, can be considered as
+Overflow that involves reusing of source code, can be considered as
 code cloning.
@@
 licenses. Security is also among the main concerns when code is copied
-from an online source. Stack Overflow helps developers to solve
+from an online source. For example, Stack Overflow helps developers to solve
 Android programming problems more quickly than other resources while,
@@
 We call code snippets that are copied from software systems to online
-Q\&A websites (such as Stack Overflow), and vice versa as ``online
+Q\&A websites (such as Stack Overflow) and vice versa as ``online
 code clones'' (sometimes only ``clones'' for brevity). There are two
@@
 difficult to locate and fix since the search space in online code
-corpora is larger and no longer confined in a local repository.
+corpora is larger and no longer confined to a local repository.
 
@@
 Stack Overflow that are cloned from open source projects and study
-them on two aspects: \textbf{outdated code and license conflicts.}
+them on two aspects: \textbf{outdated code} and \textbf{license conflicts.}
 
@@
 snippet pairs, followed by a manual classification of 3,632 candidate
-clone pairs between Java code snippets obtained from Stack Overflow's
+clone pairs between 144,064 Java code snippets obtained from Stack Overflow's
 accepted answers and 111 Java open source projects from the curated
@@
 locate and study the online code clones between Stack Overflow and open source
-projects. We designed our study in 6 phases as depicted in \Cref{fig:exp_framework} where
-we build different data sets to answer each of our four research questions. 
-We explain our process of building the data sets in each phase separately below.
+projects. 
+% We explain our process of building the data sets in each phase separately below.
 
@@
 
+We designed our study in 6 phases as depicted in \Cref{fig:exp_framework} where
+we build different data sets to answer each of our four research
+questions.
+
 \subsubsection{Phase 1: Clone Identification}
 
-We rely on two data sets in this study: Java code snippets in answers
+We rely on two source data sets in this study: Java code snippets in answers
 on Stack Overflow and open source projects from the Qualitas corpus
@@
 dump\footnote{\url{https://archive.org/details/stackexchange}} in
-January 2016. The archived dump has a size of 9 gigabytes. The data
-dump is in XML format containing information of \textbf{Posts}
-(questions and answers) and supporting data such as user accounts and
-timestamps of the posts. We were interested in code snippets embedded
+January 2016. 
+% The archived dump has a size of 9 gigabytes. 
+The data
+dump is in XML format containing information of posts
+(questions and answers) and 
+% supporting data such as user accounts and timestamps of the posts.
+we were interested in code snippets embedded
 in posts which were located between
@@
 \textbf{Open source systems: }
-We selected the established corpus for an empirical software
-engineering study called \textbf{Qualitas}~\cite{QualitasCorpus} for
-this study. It is a curated Java corpus that has been used in several
+We selected the established \textbf{Qualitas} corpus~\cite{QualitasCorpus} 
+for this study. It is a curated Java corpus that has been used in several
 software engineering
@@
 ranging from programming languages to
-visualisation~\cite{QualitasCorpus}. We selected the 20130901r release
-of Qualitas corpus containing 112 Java open source projects. This
+visualisation. We selected the 20130901r release
+of the Qualitas corpus containing 112 Java open source projects. This
 release contains projects with releases no later than 1st September
@@
 pretty-printing to increase the accuracy of clone detection. Then, we
-deployed the two clone detectors to locate clones between the two
-datasets. Due to a scalability issue, we partitioned the input and ran the tools multiple
+deployed the two detectors to locate clones between the two
+datasets. For scalability reasons, we % partitioned the input and 
+ran the tools multiple
 times. Each run was composed of the entire Stack Overflow data and a
 single Qualitas project. We repeated the process until we covered all
-111 projects.  We then converted the clone reports to the General
-Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
-single GCF file.  Simian did not provide an option to detect
-cross-project clones between two locations. Hence the Simian GCF clone
+111 projects.  
+% We then converted the clone reports to the General
+% Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
+% single GCF file.  
+Simian did not provide an option to detect
+cross-project clones between two locations. Hence the Simian clone
 report was filtered to contain only clone pairs between Stack Overflow
@@
   \small
-	\begin{tabular}{p{0.7cm}|p{2.4cm}|p{3.5cm}}
+  \begin{tabular}{p{0.7cm}|p{2.4cm}p{3.8cm}}
     \hline 
@@
     \hline
-		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, \newline ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
-		\hline 
-		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming,\newline literal abstraction \\
+    Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
+    \hline 
+    NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming, literal abstraction \\
     \hline
@@
 clone pairs without agreement. We call the \textit{good} and
-\textit{ok} pairs \textbf{agreed} clone pairs and the the clone pairs
+\textit{ok} pairs \textbf{agreed} clone pairs and the clone pairs
 reported by Simian or NiCad without agreement \textbf{disagreed} clone
@@
 for $S_D$ and 632,855 pairs for $N_D$). We applied three filters: clone
-size, irrelevant methods, similarity threshold, and good/ok pairs. For
+size, similarity threshold, and good/ok pairs. For
 the \emph{clone size filter}, we raised the minimum clone size to 10 lines
@@
 (by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We
-tried varying the UPI from 70\% (default, 632,855 pairs), 80\%
+tried varying the threshold from 70\% (default, 632,855 pairs), 80\%
 (25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that
@@
 The classifier could automatically classify 28,897 clone pairs 
-and left 3,636 clone pairs for manual investigation in phase 3 to 6.
+and left 3,636 clone pairs for manual investigation in phases 3 to 6.
 
 \subsubsection{Phase 3-4: Clone Validation and Classification}
-We relied on the 3,636 filtered clone pairs after automatic classification for
+We used the 3,636 filtered clone pairs after automatic classification for
 manual validation and classification.
-The validation and classification of the clone pairs were done at the same time. 
+The validation and classification of the pairs was done at the same time. 
 The clone validation process involves checking 
-if a clone pair is either true positive or false positive. 
+if a clone pair is a true positive or a false positive. 
 Moreover, we are also interested in the patterns of code cloning 
@@
 The main investigator went through each clone pair candidate, 
-looked at the clones, and decided if they are true positive or
+looked at the clones, and decided if they are a true positive or a
 false positive and classified them into an appropriate pattern. 
 %the most appropriate cloning pattern for the pair. 
-To mitigate the human errors of the manual investigation, 
+To mitigate the human error of the manual investigation, 
 the second author took the role of the validating investigator, performing a
@@
 investigators were compared and conflicts were discussed and resolved.
-If the two investigator cannot find a consensus, the third author is 
+If the two investigator could not find a consensus, the third author was 
 involved for the final judgement.
@@
 26 September 2016. For each \textbf{QS} online clone pair, we used the
-clone from Qualitas a a proxy. We searched for its latest version by
+clone from Qualitas as a proxy. We searched for its latest version by
 the file name and located the cloned region in the file based on the
@@
 {\small\texttt{Unknown}}, we looked at them manually to see if any
-license can be found. The table shows the license mapping of Stack
-Overflow snippets and Qualitas source code. The results are reported
-separately for the \textbf{QS}, \textbf{EX}, and \textbf{UD} set.
+license can be found.
+
+% The table shows the license mapping of Stack Overflow snippets and
+% Qualitas source code. The results are reported separately for the
+% \textbf{QS}, \textbf{EX}, and \textbf{UD} set.
 
 %\subsection{Analysis Methods}
-We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
-to answer our four research questions. 
-To answer RQ1, we rely on the number of manually validated true positive online clone pairs
-in phase 3. We use the results of the manual classification using the
-patterns of online code cloning to answer RQ2. 
-For RQ3, we looked at the true positive clone pairs that are classified 
-as cloned from Qualitas to Stack Overflow and
-checked if they have been changed since they have been
-cloned. Similarly, for RQ4, we looked at the license of each clone in the pattern 
-QS, EX, UD and checked for a possibility of a licensing violation.
+
+% We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
+% to answer our four research questions. 
+% To answer RQ1, we rely on the number of manually validated true positive online clone pairs
+% in phase 3. We use the results of the manual classification using the
+% patterns of online code cloning to answer RQ2. 
+% For RQ3, we looked at the true positive clone pairs that are classified 
+% as cloned from Qualitas to Stack Overflow and
+% checked if they have been changed since they have been
+% cloned. Similarly, for RQ4, we looked at the license of each clone in the pattern 
+% QS, EX, UD and checked for a possibility of a licensing violation.
 

### 2017-02-24 cloneoverflow-latex/cloneoverflow.tex
Down to 10 pages of text!

@@
 
-\overfullrule1ex
+%\overfullrule1ex
 
@@
 
+\begin{table}
+  \centering
+  \caption{Configurations of Simian and NiCad}
+  \label{t:param_tuning}
+  %	\resizebox{\columnwidth}{!}{%
+  \small
+  \begin{tabular}{p{0.7cm}|p{2.4cm}p{3.8cm}}
+    \hline 
+    Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
+    \hline
+    Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
+    \hline 
+    NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming, literal abstraction \\
+    \hline
+  \end{tabular} %
+%}
+\end{table}
+
 \textbf{Clone Detection Configuration: }
-We were aware of effects of configurations to clone detection results
+We are aware of effects of configurations to clone detection results
 and the importance of searching for optimised configurations in
@@
 of optimising clone detectors' configurations based on clone agreement
-(denoted by \textit{E}). The details of the two configurations are
-described in \Cref{t:param_tuning}.
+(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
 
@@
 
+The number of online clone pairs reported % by running Simian and NiCad
+are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
+pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
+much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
+respectively. This is expected since EvaClone configurations prefer
+recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
+9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
+$N_D$ has an average clone size of 10.85 lines which is bigger than
+6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
+configuration with a smaller minimum size (\Cref{t:param_tuning}).
+
 \begin{table}
 	\centering
-  \caption{Configurations of Simian and NiCad}
-  \label{t:param_tuning}
-  %	\resizebox{\columnwidth}{!}{%
-  \small
-  \begin{tabular}{p{0.7cm}|p{2.4cm}p{3.8cm}}
-    \hline 
-    Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
-    \hline
-    Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
-    \hline 
-    NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming, literal abstraction \\
+	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
+	\label{tab:orig_stats}
+	%\small
+	%\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r|r}
+		\hline
+		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
+		\hline
+		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
+		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
+		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
 		\hline
@@
 agreement filtering using Bellon's criteria\footnote{Similar to the
-  original study, we selected a threshold \textit{t} of 0.7 for both
+  original study, we selected a threshold of 0.7 for
   \textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
@@
 	\centering
-	\includegraphics[width=\linewidth]{good-ok_pairs}
+	\includegraphics[width=0.9\linewidth]{good-ok_pairs}
 	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
@@
 pairs\footnote{This excludes the subsumed 2,313 \textit{good}
-  pairs. According to the definition, \textit{ok} pairs always subsume
+  pairs because \textit{ok} pairs subsume
   \textit{good} pairs.}. We obtained 12,336; 993; 79; and 20,021 pairs
@@
 evaluate its applicability to our study. 
-We have tried to classify 697 online clone pairs from
+We tried to classify 697 online clone pairs from
 the reported clones in phase 1 
@@
 %\subsubsection{Defining Online Code Cloning Patterns}
-using Kapser's cloning patterns. We found that the
-clone pairs were categorised into either Customisation or Templating.
-Thus, Kapser's cloning patterns are too broad for our study and a
+using Kapser's cloning patterns. We found that 
+% the
+% clone pairs were categorised into either Customisation or Templating.
+% Thus, 
+Kapser's patterns are too broad for our study and a
 more suitable and fine-grained classification scheme is needed. After
 the preliminary study, we adopted one of Kapser's cloning patterns,
-\emph{boiler-plate code} and \emph{API/library protocol}, and defined
+\emph{boiler-plate code}, and defined
 6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{classification_process}
+	\includegraphics[width=0.8\linewidth]{classification_process}\vspace{-1ex}
 	\caption{Online code clone classification process}
@@
 	%\resizebox{\columnwidth}{!}{%
+        \small\vspace{-1ex}
 		\begin{tabular}{c@{~~}p{7.35cm}}
@@
 
-The number of online clone pairs reported by running Simian and NiCad
-are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
-pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
-much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
-respectively. This is expected since EvaClone configurations prefer
-recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
-9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
-$N_D$ has an average clone size of 10.85 lines which is bigger than
-6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
-configuration with a smaller minimum size (\Cref{t:param_tuning}).
-
-\begin{table}
-	\centering
-	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
-	\label{tab:orig_stats}
-	%\small
-	%\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r}
-		\hline
-		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
-		\hline
-		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
-		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
-		\hline
-	\end{tabular} %
-	%}
-\end{table}
-
 The statistics on clones obtained from the different data sets are
@@
 as being accidential clones (AC), i.e.~false positives. After removing
-them, the data set still contains 1,216 true positive clone pairs between 516 Stack
+them, the set still contains 1,216 true positive clone pairs between 516 Stack
 Overflow snippets and 75 Qualitas projects.
@@
 them have a statement in the Stack Overflow post saying that the code
-is ``copied'', ``borrow'' or ``modified'' from a specific file or class in a
+is ``copied'', ``borrowed'' or ``modified'' from a specific file or class in a
 Qualitas project. For example, according to the motivating example in 
@@
 \textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
-any clone pairs with evidence of cloning from Stack Overflow to
-Qualitas projects.
+any pairs with evidence of cloning from Stack Overflow to Qualitas
+projects. This is very likely due to the age of the Qualitas corpus.
 
 \textbf{EX: External Sources.} We found 200 online clone pairs with
-evidence of cloning from external sources to Stack Overflow. 
-They include 4, 44, 146, and 6 clone pairs from the \textit{good},
-\textit{ok'}, $S_D'$, and $N_D'$ set respectively. All of them
-contain statements showing an external source of the cloned code.
-For example, Stack Overflow Post 9549009 contains a code comment saying \textit{``Copied 
-	shamelessly from org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator,
-	changed only the hash algorithm.''}
+evidence of cloning from external sources to Stack Overflow.  They
+include 4, 44, 146, and 6 pairs from the \textit{good}, \textit{ok'},
+$S_D'$, and $N_D'$ set respectively. All of them contain statements
+giving an external source of the cloned code.  For example, Stack
+Overflow Post 9549009 contains a code comment saying \textit{``Copied
+  shamelessly from
+  org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''}.
 
 These findings complement a study of clones between software
-projects~\cite{Svajlenko2014}. We found that the code cloning can also
+projects~\cite{Svajlenko2014}. We found that cloning can also
 happen among different sources on the Internet just like software
 projects. There are 30 clone pairs that originated from programming
-websites. For example, we found a clone of code snippet to convert
+websites. For example, we found a clone of a snippet to convert
 numbers into words which is copied from
 \url{www.rgagnon.com/javadetails/java-0426.html}. Both the Stack
-Overflow and the \textsf{compiere} project source code contain an
-attribution to the original source. Another example is a code snippet
+Overflow and the \textsf{compiere} project code contain an
+attribution to the original source. Another example is a snippet
 to generate graphical \textit{Perlin noise}. It is copied from
-\url{http://mrl.nyu.edu/~perlin/noise/}. The code is used on Stack
+\url{http://mrl.nyu.edu/~perlin/noise/} and is used on Stack
 Overflow and in the \textsf{aoi} project with
@@
 % information so these clones do not violate any license.
-There are other EX clone pairs which are copied from third-party
+There are other EX pairs which are copied from third-party
 libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util},
@@
   names, added or deleted statements, to a fully rewritten code with
-  new method signatures. 4 pairs are dead
+  new method signatures. 4~pairs are dead
   snippets.}
@@
 	\label{tab:stale_code_details}
-	%\small
+	\small
 	%\resizebox{\textwidth}{!}{%
@@
 	\label{tab:license_abc}
-	\small
+	\footnotesize
 	%\resizebox{\columnwidth}{!}{%
@@
 \textbf{Internal validity:} 
-
+%
 We could not verify all the 315,786,118 clone pairs reported by the
@@
 different mechanisms to ensure the validity to the subset of clone
-pairs we classified.  First, we used two, instead of one, widely-used
-clone detection tools, Simian and NiCad.  We had tried three other
+pairs we classified.  First, we used two widely-used
+clone detection tools, Simian and NiCad.  We tried three other
 clone detectors but could not add them to the study due to their
-scalability issue and susceptibility to incomplete code snippets.
-Second, we adopted Bellon's clone agreement metric~\cite{Bellon2007}
+scalability issues and susceptibility to incomplete code snippets.
+Second, we adopted Bellon's agreement metric~\cite{Bellon2007}
 to prioritise and filters clone pairs for the manual
 classification. The agreed clone pairs that passed \textit{good} and
-\textit{ok} criteria had a higher chance to be true positive. We also
-applied the Bellon's clone agreement to 4 different combinations of
-the tools' configurations.  For disagreed clone pairs, we applied
-several filters to remove spurious and uninteresting clones.
-
-The number of online clones we found are subject to the clone
-detectors and their configurations.  We mitigated the problem of clone
-detector's parameter sensitivity by adding another configuration,
-besides the default configuration. We reused the established
-configurations from the EvaClone study~\cite{Wang2013}.  We also
-performed a pairwise matching between the default and EvaClone
-configurations of the two clone detection tools.
+\textit{ok} criteria had a higher chance to be true positive. 
+% We also
+% applied the Bellon's clone agreement to 4 different combinations of
+% the tools' configurations.  For disagreed clone pairs, we applied
+% several filters to remove spurious and uninteresting clones.
+
+% The number of online clones we found are subject to the clone
+% detectors and their configurations.  
+We mitigated the problem of clone
+detector's parameter sensitivity by adding another established
+configuration from the EvaClone study~\cite{Wang2013}.
+
+% We also
+% performed a pairwise matching between the default and EvaClone
+% configurations of the two clone detection tools.
 
@@
 having the second author to validate the classifications with a random
-sampling.  The 64 classification conflicts were discussed and
-resolved.  The third author made a final judgement when no consensus
+sampling. 
+% The 64 classification conflicts were discussed and
+% resolved.  
+The third author made a final judgement when no consensus
 could be found by the two authors.
@@
 Regarding the code snippets, we downloaded a full data dump and
-extracted Java accepted answers. Instead of analysing every post, we
-only focused on posts marked as accepted answers since they are the
-most likely ones to be reused. This yields a total of 144,064
-snippets.  Our findings are limited to these restrictions. They may
+extracted Java accepted answers
+% Instead of analysing every post, we
+only focused on posts marked as accepted answers 
+since they are the
+most likely ones to be reused. 
+% This yields a total of 144,064 snippets.  
+Our findings are limited to these restrictions. They may
 not be generalised to all programming languages and all answers on
-Stack Overflow. On the other hand, we chose the curated Qualitas
+Stack Overflow. We chose the curated Qualitas
 corpus for Java open source projects containing 111 projects
@@
 
-\FIXME{This needs rewriting}
-
-\textbf{Stack Overflow} is a gold mine for software engineering research.
-Its rich and developer-driven data are invaluable.
-Since posts on Stack Overflow may contain code snippets embedded within natural language text, they become a huge database for source code and code-relevant information.
-The Stack Overflow data set has been put to use in several previous studies.
-In terms of developer-assisting tools, Seahawk is an Eclipse plug-in that searches and recommends relevant code snippets from Stack Overflow~\cite{Ponzanelli2013}.
-A follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014} achieves the same goal but with improved algorithms.
-The code snippets on Stack Overflow are mostly examples or solutions to programming problems.
-Hence, several code search systems use whole or partial data from Stack Overflow as their code search databases~\cite{Keivanloo2014,Park2014, Stolee2014,Subramanian2013,Diamantopoulos2015}.
-Furthermore, Treude et al.~\cite{Treude2016}~use machine learning techniques to extract insight sentences from Stack Overflow and use them to improve API documentation.
-
-Another research area is knowledge extraction from Stack Overflow.
-Nasehi et al.~\cite{Nasehi2012}~studied what makes a good code example by analysing answers from Stack Overflow.
-Similarly, Yang et al.~\cite{Yang2016} report the number of reusable code snippets on Stack Overflow across various programming languages.
-Wang et al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic modelling to analyse questions and answers from Stack Overflow so that they can automatically categorise new questions.
-There are also studies trying to understand developers' behaviours on Stack Overflow, e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}, while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.
-
-\textbf{Code clone detection} is a long-standing research topic in software engineering.
-Whether clones are good or bad for software is still controversial~\cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
-However, by only knowing how many code clones residing in software and how they evolve~\cite{Pate2013,Mondal2011} can provide several valuable insights into the software systems.
-Code clones have several applications such as software plagiarism detection~\cite{Prechelt2002},
-source code provenance~\cite{Davies2013}, and software licensing conflicts~\cite{German2009}.
-
-Two code fragments are clones if they are similar enough according to a given definition of similarity~\cite{Bellon2007}.
-Given an open interpretation of ``definition of similarity'', there are various clone detection tools and their siblings, code plagiarism detectors, invented based on plethora of different code similarity measurements~\cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}.
-Some tools
-use string comparison techniques such as Simian~\cite{simian}.
-NiCad~\cite{Roy2008,Cordy} exploits the Longest Common Subsequence (LCS) string similarity measure after applying code pretty-printing using TXL~\cite{Cordy2006}.
+\textbf{Stack Overflow} is a gold mine for software engineering
+research and
+% Its rich and developer-driven data are invaluable. Since
+% posts on Stack Overflow may contain code snippets embedded within
+% natural language text, they become a huge database for source code and
+% code-relevant information. 
+%The Stack Overflow data set 
+has been put to
+use in several previous studies. In terms of developer-assisting
+tools, Seahawk is an Eclipse plug-in that searches and recommends
+relevant code snippets from Stack Overflow~\cite{Ponzanelli2013}. A
+follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014}
+achieves the same goal but with improved algorithms. The code snippets
+on Stack Overflow are mostly examples or solutions to programming
+problems. Hence, several code search systems use whole or partial data
+from Stack Overflow as their code search
+databases~\cite{Keivanloo2014,Park2014,
+  Stolee2014,Subramanian2013,Diamantopoulos2015}. Furthermore, Treude
+et al.~\cite{Treude2016}~use machine learning techniques to extract
+insight sentences from Stack Overflow and use them to improve API
+documentation.
+
+Another research area is knowledge extraction from Stack
+Overflow. Nasehi et al.~\cite{Nasehi2012}~studied what makes a good
+code example by analysing answers from Stack Overflow. Similarly, Yang
+et al.~\cite{Yang2016} report the number of reusable code snippets on
+Stack Overflow across various programming languages. Wang et
+al.~\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation
+(LDA) topic modelling to analyse questions and answers from Stack
+Overflow so that they can automatically categorise new
+questions. There are also studies trying to understand developers'
+behaviours on Stack Overflow,
+e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
+% , while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.
+
+\textbf{Code clone detection} is a long-standing research topic in
+software engineering. Whether clones are good or bad for software is
+still
+controversial~\cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
+% However, by only knowing how many code clones residing in software
+% and how they evolve~\cite{Pate2013,Mondal2011} can provide several
+% valuable insights into the software systems.
+Code clones have several
+applications such as software plagiarism
+detection~\cite{Prechelt2002}, source code
+provenance~\cite{Davies2013}, and software licensing
+conflicts~\cite{German2009}.
+
+Two code fragments are clones if they are similar enough according to
+a given definition of similarity~\cite{Bellon2007}. Given an open
+interpretation of ``definition of similarity'', there are various
+clone detection tools and their siblings, code plagiarism detectors,
+invented based on plethora of different code similarity
+measurements~\cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}. 
+% Some tools use string comparison techniques such as Simian~\cite{simian}. 
+% NiCad~\cite{Roy2008,Cordy} exploits the Longest Common Subsequence
+% (LCS) string similarity measure after applying code pretty-printing
+% using TXL~\cite{Cordy2006}. 
 Many tools do not work on original source code directly but transform them into an
@@
 
-\textbf{Clone agreement} is useful when a clone oracle is absent.
-Since clone detectors are different in their detection approaches, they may behave differently and report different clones even on the same data set.
-Some researchers exploit these different behaviours of clone detectors by finding their agreement and obtain highly-confident clones~\cite{Bellon2007,Wang2013}.
-Using the same data set, clone pairs that are agreed by several tools (or several code similarity measurement techniques) are more assured to be true clones than the ones reported by only a single tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
-There are studies that report sensitivities of the tools' configurations to the results~\cite{Wang2013,cr2016ssbse}, showing that searching for an optimal configuration for every new data set is preferred.
+\textbf{Clone agreement} is useful when a clone oracle is
+absent. Since clone detectors are different in their detection
+approaches, they may behave differently and report different clones
+even on the same data set. Some researchers exploit these different
+behaviours of clone detectors by finding their agreement and obtain
+highly-confident clones~\cite{Bellon2007,Wang2013}. Using the same
+data set, clone pairs that are agreed by several tools (or several
+code similarity measurement techniques) are more assured to be true
+clones than the ones reported by only a single
+tool~\cite{Wang2013,cr2016ssbse,Funaro2010}. 
+% There are studies that report sensitivities of the tools'
+% configurations to the results~\cite{Wang2013,cr2016ssbse}, showing
+% that searching for an optimal configuration for every new data set
+% is preferred.
 

### 2017-02-24 cloneoverflow-latex/cloneoverflow.tex
Fixing simple typos and errors pointed after FSE lunch review.

@@
 %\textbf{Clone Detection and Configuration: } 
-There are a number of restrictions in terms of choosing clone
+There are a number of restrictions in terms of choosing the clone
 detection tools for this study. The main restriction is due to nature
@@
 infeasible for humans to manually validate them all. Instead of
-investigating a random saple, we adopted the idea of \textbf{clone
+investigating a random sample, we adopted the idea of \textbf{clone
   agreement} which has been used in clone research
@@
 highest confidence, followed by the \textit{ok} pairs, and followed by
-clone pairs without agreement. We call the \textit{good} and
-\textit{ok} pairs \textbf{agreed} clone pairs and the clone pairs
+clone pairs without agreement. We call the \textit{good}- and
+\textit{ok}- pairs \textbf{agreed} clone pairs and the clone pairs
 reported by Simian or NiCad without agreement \textbf{disagreed} clone
@@
 (denoted as \textit{N}), with two chosen configurations (\textit{D}
-and \textit{E}) each, we used Bellon's good and ok-match for agreement
+and \textit{E}) each, we used Bellon's good- and ok-match for agreement
 in four possible pair-wise combinations: $S_{D}$--$N_{D}$,
-$S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$, and $S_{E}$--$N_{E}$.
+$S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$, and $S_{E}$--$N_{E}$, as shown in \Cref{t:param_tuning}.
 
@@
 For RQ3, we looked at the true positive clone pairs that are classified 
-as cloned from Qualitas to Stack Overflow and
+as clones from Qualitas to Stack Overflow and
 checked if they have been changed since they have been
@@
 to prioritise and filters clone pairs for the manual
-classification. The agreed clone pairs that passed \textit{good} and
-\textit{ok} criteria had a higher chance to be true positive. 
+classification. The agreed clone pairs that passed \textit{good}- and
+\textit{ok}- criteria had a higher chance to be true positive. 
 % We also

### 2017-02-25 cloneoverflow-latex/cloneoverflow.tex
Changes to the example code, and to the explanation of the runs.

@@
 \usepackage{tikz}
+\usepackage[normalem]{ulem}
 
@@
 
-\lstset{language=Java,tabsize=2,basicstyle=\ttfamily\scriptsize}
+\lstset{language=Java,
+  tabsize=2,
+  basicstyle=\ttfamily\footnotesize,
+  moredelim=[is][\dotuline]{@}{@},
+  mathescape=true
+}
 
@@
 \newcolumntype{"}{@{\hskip\tabcolsep\vrule width 1pt\hskip\tabcolsep}}
-
-\lstdefinestyle{base}{
-	language=C,
-	emptylines=1,
-	breaklines=true,
-	basicstyle=\ttfamily\color{black},
-	moredelim=**[is][\color{red}]{@}{@},
-}
 
@@
   /* Code in Stack Overflow post ID 22315734 */              /* WritableComparator.java (2016-09-26) */
-          public int compare(byte[] b1,int s1,int l1,                    public int compare(byte[] b1,int s1,int l1,
-                             byte[] b2,int s2,int l2) {                                     byte[] b2,int s2,int l2) {
+  public int compare(byte[] b1,int s1,int l1, ...) {         public int compare(byte[] b1,int s1,int l1, ...) {
     try {                                                      try {
@@
       key2.readFields(buffer);                                   key2.readFields(buffer);
-            } catch (IOException e) {                                        buffer.reset(null,0,0); /* clean up reference */
+    } catch (IOException e) {                                    $$@buffer.reset(null,0,0); /* clean up reference */@
       throw new RuntimeException(e);                           } catch (IOException e) {
@@
 release contains projects with releases no later than 1st September
-2013. We chose a snapshot late back in 2013 since we are interested in
+2013. We intentionally chose an old corpus from 2013 since we are interested in
 online code clones in the direction from open source projects to Stack
@@
 We prepared the Java code in both datasets by removing comments and
-pretty-printing to increase the accuracy of clone detection. Then, we
+pretty-printing to increase the clone detection accuracy. Then, we
 deployed the two detectors to locate clones between the two
-datasets. For scalability reasons, we % partitioned the input and 
-ran the tools multiple
-times. Each run was composed of the entire Stack Overflow data and a
-single Qualitas project. We repeated the process until we covered all
-111 projects.  
+datasets.  For each Qualitas project, we ran the tools on the
+project's code and the entire Stack Overflow data.
+% For scalability reasons, we partitioned the input and ran the tools
+% multiple times. Each run was composed of the entire Stack Overflow
+% data and a single Qualitas project. We repeated the process until we
+% covered all 111 projects.
 % We then converted the clone reports to the General
@@
 % single GCF file.  
-Simian did not provide an option to detect
-cross-project clones between two locations. Hence the Simian clone
-report was filtered to contain only clone pairs between Stack Overflow
-and Qualitas projects, removing all clone pairs within either Stack
-Overflow or within Qualitas. 
+Simian did not provide an option to detect cross-project
+clones. % between two locations.
+Hence the Simian clone report was filtered to contain only clone pairs
+between Stack Overflow and Qualitas projects, removing all clone pairs
+within either Stack Overflow or within Qualitas.
 % NiCad provides an option to detect clones
@@
 	\label{tab:license_abc}
-	\footnotesize
+	\small
 	%\resizebox{\columnwidth}{!}{%

### 2017-02-25 cloneoverflow-latex/cloneoverflow.tex
Added footnote about overlap = Jaccard
Revised by working on comments from FSE lunch, corrected the old numbers, and fixed references.

@@
 %The popularity of the Internet encourages tremendous amount of source code being shared online. 
-Stack Overflow is a popular online programming community with 6.3
-million users. It allows programmers to ask questions and give answers
+Stack Overflow is a popular online programming community with 6.8
+million users\footnote{Statistics as of 25 February 2017 from \url{http://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
 to programming problems. The website has found to be useful for
@@
 We used two clone detection tools to discover 315,786,118 similar code
-snippet pairs, followed by a manual classification of 3,632 candidate
+snippet pairs, followed by a manual classification of 3,636 candidate
 clone pairs between 144,064 Java code snippets obtained from Stack Overflow's
@@
   online clones on Stack Overflow:} Our study shows that from the
-3,632 online clones, at least 668 likely have been copied from open
+3,636 online clones, at least 671 likely have been copied from open
 source projects or external online sources to Stack Overflow,
@@
 \vspace{0.5ex}%
-\noindent\textbf{3.~An online code clone oracle:} The 3,632 manually
+\noindent\textbf{3.~An online code clone oracle:} The 3,636 manually
 investigated and validated online clone pairs are available for
@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We obtained 144,064 Java code snippets containing 2,347,267
+We obtained 144,064 Java code snippets containing 2,346,267
 lines\footnote{Measured by cloc:
@@
 (denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
+In total, we have four configurations: Simian with the default
+configuration ($S_D$), Simian with EvaClone configuration ($S_E$), 
+NiCad with the default configurations ($N_D$)
+and NiCad with EvaClone configuration ($N_E$).
 
@@
 \textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} = (\textit{CF$_1$},
-\textit{CF$_2$}), we can define the \textit{overlap} and
+\textit{CF$_2$}), we can define the \textit{overlap}\footnote{The overlap value can be considered as Jaccard similarity.} and
 \textit{contained} value of two clone pairs as
@@
 in four possible pair-wise combinations: $S_{D}$--$N_{D}$,
-$S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$, and $S_{E}$--$N_{E}$, as shown in \Cref{t:param_tuning}.
+$S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$, and $S_{E}$--$N_{E}$. %as shown in \Cref{t:param_tuning}.
 
@@
 We selected all \textit{good} pairs (2,313) and the \textit{ok} pairs for
-$S_D$--$N_D$, $S_E$--$N_D$, and $S_D$--$N_E$ (12,336), but we ignored
+$S_D$--$N_D$ (12,336), $S_E$--$N_D$ (993), and $S_D$--$N_E$ (79), but we ignored
 20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
@@
 Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
-$N_D'$ set) clone pairs after filtering clone pairs from $S_D$ and
-$N_D$, we ended up with a set of 32,533 online clone pair candidates.
+$N_D'$ set) clone pairs after filtering, we ended up with a set of 32,533 online clone pair candidates.
 
@@
 The validation and classification of the pairs was done at the same time. 
-The clone validation process involves checking 
+The clone validation process (phase 3 in \Cref{fig:exp_framework}) involves checking 
 if a clone pair is a true positive or a false positive. 
-Moreover, we are also interested in the patterns of code cloning 
-so we can gain more insights into how these clones are created.
+Moreover, we are also interested in 
+the patterns of code cloning so we can gain more insights into 
+how these clones are created (phase 4 in \Cref{fig:exp_framework}).
 
@@
 two years, took the role of the main investigator performing a manual 
-validation of the filtered clone pairs. 
+validation and classification of the filtered clone pairs. 
 %By consulting the cloning patterns, 
@@
 the second author took the role of the validating investigator, performing a
-validation on 10\% of the clone pairs judged by the main
+validation on 10\% (364 pairs) of the clone pairs judged by the main
 investigator. After the validation, the results from the two
-investigators were compared and conflicts were discussed and resolved.
-If the two investigator could not find a consensus, the third author was 
-involved for the final judgement.
+investigators were compared and 61 conflicts were discussed and resolved.
+There were 3 conflicts that the two investigators could not find a consensus 
+and the third author was involved for the final judgement.
 
@@
 as clones from Qualitas to Stack Overflow and
-checked if they have been changed since they have been
-cloned (phase 5). Similarly, for RQ4, we looked at the license of each clone in the pattern 
-QS, EX, UD and checked for a possibility of a licensing violation (phase 6).
+checked if they have been changed after cloning (phase 5). Similarly, for RQ4, we looked at the license of each clone in the pattern 
+QS, EX, UD and checked for a possibility of licensing violation (phase 6).
 
@@
   similar code with Stack Overflow code snippets. In the manually confirmed 
-  data set of 3,636 clone pairs, we found 1,216 pairs as true positives and 
-  they account for a majority of 75 Qualitas projects and
+  data set of 3,636 clone pairs, we found 1,216 pairs as true positives which 
+  account for 75 Qualitas projects and
   516 Stack Overflow code snippets.}
@@
 classifier helped us to classify 28,897 clone pairs into
-pattern \textbf{BP}. Then, we relied on a manual study to qualitatively investigate the patterns of
-online code cloning. To achieve this, we classified all 32,533
-selected clone pairs according to the pre-defined classification process 
-(\Cref{fig:classification_process}).  
+pattern \textbf{BP}. Then, we relied on a manual classification
+% to qualitatively investigate the patterns of
+%online code cloning 
+on the remaining 3,636 pairs by following the classification process
+in \Cref{fig:classification_process}. 
+%To achieve this, we classified all 32,533
+%selected clone pairs according to the classification process 
+%in \Cref{fig:classification_process}.  
 %
-There were 3,636 pairs left for the manual check. 
- The classification
-results are shown in \Cref{tab:classification_good_o} and explained in
-the following.
+%There were 3,636 pairs left for the manual check. 
+The classification results are shown in \Cref{tab:classification_good_o} 
+and explained in the following.
 
@@
 projects. This is very likely due to the age of the Qualitas corpus.
+However, with a newer data set, one can find online clones in
+this direction as shown in another study~\cite{An2017}.
 
 \textbf{EX: External Sources.} We found 200 online clone pairs with
-evidence of cloning from external sources to Stack Overflow.  They
-include 4, 44, 146, and 6 pairs from the \textit{good}, \textit{ok'},
+evidence of cloning from external sources to Stack Overflow and to Qualitas.  
+They include 4, 44, 146, and 6 pairs from the \textit{good}, \textit{ok'},
 $S_D'$, and $N_D'$ set respectively. All of them contain statements
@@
 (\textit{D}), and method rewriting (\textit{R}), along with the date
-of change.
+of change. The complete set of 64 outdated online clones can be found
+from the study website.
 
@@
 64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals.
-To mitigate the problems of outdated online clones and missing or incompatible license on Stack Overflow code snippets, we propose the following actionable items:
-
-\textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' license software projects and posted on Stack Overflow.
-Moreover, an IDE plug-in that can automatically detect pasted source code and track their origins with licensing check could also prevent the issue of license-violating Stack Overflow code snippets.
+Our study discovers links from code in open source projects to code snippets on Stack Overflow using clone detection techniques.
+These links enable us to discover outdate code and licensing problems.
+The links can be exploited further to mitigate the problems of reusing outdated online clones and incompatible license on Stack Overflow code snippets.
+We propose the following actionable items:
+
+\textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' licensed software projects to Stack Overflow.
+Moreover, an IDE plug-in that can automatically detect pasted source code and follow the link to Stack Overflow and then to the original open source projects, could also prevent the issue of license violation.
 
 \textbf{Detective measure:} A system to detect outdated source code snippets on Stack Overflow is needed.
-If a code snippet is copied from an external project with other licenses than CC BY-NC-SA, the poster has to provide the information of the project including the original file name and its online repository (if exists).
-The system can leverage clone detection tools/techniques to periodically locate and check if the cloned snippet is still up-to-date with its original.
+The system can leverage the online clone detection techniques in this study to periodically check if the cloned snippets are still up-to-date with their originals.
+%Moreover, Stack Overflow posters have to provide the information of the project including the original file name and its online repository (if exists).
 With such a system, the poster can be notified when the code has been updated in the original project so that he/she can update their code on Stack Overflow accordingly.
+On the other hand, with a crowdsourcing solution using an IDE plug-in, developers can also report the corrected version of outdated code back to the original Stack Overflow threads when they reuse outdated code and makes corrections to them.
 
@@
 \textit{ok}- criteria had a higher chance to be true positive. 
+Nevertheless, we might still suffers from false negatives, i.e.~online 
+code clones that are not reported by the tools or filtered 
+out by the automatic classifier before the manual investigation.
 % We also
@@
 
-The 3,632 clone pairs classified manually by the first author are
+The 3,636 clone pairs classified manually by the first author are
 subject to manual judgement and human errors.  Although we have tried
@@
 The third author made a final judgement when no consensus
-could be found by the two authors.
+could be found by the two authors. This validation process
+can be even improved by employing an external investigator. 
  %In addition, we are aware of voting mechanism
@@
 We selected Stack Overflow because it is one of the most popular
-programming Q\&A websites available with approximately 6.3 million
+programming Q\&A websites available with approximately 6.8 million
 users.  There are a large number of code snippets reused from the
@@
 % Instead of analysing every post, we
-only focused on posts marked as accepted answers 
+%only focused on posts marked as accepted answers 
 since they are the
@@
 % using TXL~\cite{Cordy2006}. 
-Many tools do not work on original source code directly but transform them into an
-intermediate representation such as tokens and apply similarity
-measurement on them. These tools include SourcererCC~\cite{Sajnani2016}, CCFinder~\cite{Kamiya2002},
-CP-Miner~\cite{Li2006}, iClones~\cite{Gode2009} and a few more~\cite{Burrows2007, Smith2009, Duric2012, Prechelt2002, Schleimer2003}. 
-To find more challenging clones such as clones with added/deleted/reordered statements or equivalent loop and conditional statements (i.e.~type-3 clones), structural similarity of clones is needed.
-This structural similarity can be discovered by comparing AST as found in CloneDR~\cite{Baxter1998} and Deckard~\cite{Jiang2007a} or by using program dependence
+Many tools do not work on original source code directly but detect clones
+at an intermediate representation such as tokens ~\cite{Sajnani2016,Kamiya2002,Li2006,Gode2009,Burrows2007, Smith2009, Duric2012, Prechelt2002, Schleimer2003}, AST~\cite{Baxter1998,Jiang2007a} or program dependence
 graphs~\cite{Krinke2001,Komondoor2001}.
 
-Kapser et al.~studied clones in Linux file systems and create 11 patterns of code cloning based on four groups: Forking, Templating, Customisation and Exact match~\cite{Kapser2003,Kapser2008}.
+\textbf{Cloning patterns} is initially defined 
+by Kapser et al.~\cite{Kapser2003,Kapser2008} by studying clones in 
+Linux file systems and deriving 11 patterns of code cloning. 
 Our study adopted one of the patterns into our online code cloning patterns.
@@
 \textbf{Clone agreement} is useful when a clone oracle is
-absent. Since clone detectors are different in their detection
-approaches, they may behave differently and report different clones
-even on the same data set. Some researchers exploit these different
-behaviours of clone detectors by finding their agreement and obtain
-highly-confident clones~\cite{Bellon2007,Wang2013}. Using the same
-data set, clone pairs that are agreed by several tools (or several
-code similarity measurement techniques) are more assured to be true
+absent. %Since clone detectors are different in their detection
+%approaches, they may behave differently and report different clones
+%even on the same data set. 
+By exploiting the different behaviours of clone detectors,
+one can look for their agreement and obtain
+highly-confident clones~\cite{Bellon2007,Wang2013}. %Using the same
+%data set, 
+Clone pairs that are agreed by multiple tools are more assured to be true
 clones than the ones reported by only a single
@@
 
-\textbf{Software licensing} is crucial for open source and industrial software development.
-Di Penta et al.~\cite{DiPenta2010}~studied the evolution of software licensing in six FOSS and found that licensing statements change over time.
-German et al.~\cite{German2009} performed an empirical study of code siblings (code clones among different systems coming from the same source) and found that licensing conflicts can occur between the clone siblings.
-Later, German et al.~\cite{German2010} created Ninka, a tool to automate the identification of software license from program source code.
-We use Ninka to analyse software license from Stack Overflow snippets and Qualitas projects.
-
-\textbf{Reusing of outdated third-party source code} occurs in software development.
-Xia et al.~\cite{Xia2014} show that a large number of open source systems reuse outdated third-party libraries from popular open source projects.
-Using the outdated code give detrimental effects to the software since they may introduce vulnerabilities.
-Our study discovers similar findings in the context of outdated code on Stack Overflow.
-
-The work that is closely similar to us is a study by An et al.~\cite{An2017} where the authors investigated clones between 399 Android apps and Stack Overflow posts.
+\textbf{Software licensing} is crucial for open source and 
+industrial software development. Di Penta et al.~\cite{DiPenta2010}
+studied the evolution of software licensing in open source 
+software and found that licensing statements change over 
+time. German et al.~\cite{German2009} found that licensing 
+conflicts occur between the clone siblings (clones among 
+different systems that come from the same source). Later, 
+German et al.~\cite{German2010} created an automated tool 
+for software license identification, Ninka. 
+%We use Ninka to analyse software license from Stack 
+Overflow snippets and Qualitas projects.
+
+\textbf{Reusing of outdated third-party source code} occurs 
+in software development. Xia et al.~\cite{Xia2014} show that 
+a large number of open source systems reuse outdated third-party 
+libraries from popular open source projects. Using the outdated 
+code give detrimental effects to the software since they may 
+introduce vulnerabilities. Our study discovers similar findings 
+in the context of outdated code on Stack Overflow.
+
+The work that is closely similar to us is a study by 
+An et al.~\cite{An2017} where the authors investigated 
+clones between 399 Android apps and Stack Overflow posts. 
 They found 1,226 code snippets which were reused from 68 Android apps. 
-They also observed that there are 1,219 cases of potential license violations.
-The authors rely on the timestamp to judge whether the code has been copied from/to Stack Overflow along with confirmations from six developers.
-Instead of Android apps, we investigated clones between Stack Overflow and 111 open source projects.
-Their results are similar to our findings that there are clones from software projects to Stack Overflow with potential licensing violations.
-%In our work, we defined seven patterns of online code cloning and performed a large-scale manual check of 3,632 clone pairs.
-We discovered 112 clone pairs with strong evidences, based on natural text in comments and post contents, that they were copied from Qualitas to Stack Overflow.
-By comparing the clones to their latest versions in the software, we found that 64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
+They also observed that there are 1,219 cases of potential 
+license violations. The authors rely on the timestamp to 
+judge whether the code has been copied from/to Stack Overflow 
+along with confirmations from six developers. Instead of Android apps, 
+we investigated clones between Stack Overflow and 111 open 
+source projects. Their results are similar to our findings that 
+there exist clones from software projects to Stack Overflow with 
+potential licensing violations. 
+%In our work, we defined seven patterns of online code cloning and 
+%performed a large-scale manual check of 3,632 clone pairs. 
+%We discovered 112 clone pairs with strong evidences, 
+%based on natural text in comments and post contents, that they 
+%were copied from Qualitas to Stack Overflow. By comparing the 
+%clones to their latest versions in the software, we found that 
+%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
 
@@
 Online code clones are clones that have been copied to Q\&A websites
-such as Stack Overflow. They are similar to clones in software
+such as Stack Overflow. They are similar to classical clones in software
 projects where they can be outdated and violating software license but
-are much harder to detect. We studied the online code clones between
-Stack Overflow and Qualitas projects, especially 3,632 clone pairs,
-manually in details.
-
-Although we deployed Bellon's clone agreement and multiple filters to
-reduce the number of clone candidates, we still found a large number
-of 51,926 online clone pairs reported by two clone detectors. We
-classify 32,533 clone pairs using our seven patterns of online code
-cloning. We discovered 112 clone pairs that have been copied, with
-evidence, from Qualitas projects to Stack Overflow (QS), 197 clone
+are much harder to detect. We classified 32,533 clone pairs using our seven patterns of online code
+cloning and discovered 112 clone pairs that have been copied, with
+evidence, from Qualitas projects to Stack Overflow, 197 clone
 pairs that have been copied from external sources besides Qualitas to
-Stack Overflow (EX), and 359 clone pairs that are highly similar but
-without evidence of copying (UD).
-
-A manual investigation of the 112 QS clone pairs by comparing to their
-latest version (as of 26 September 2016) reveals that 64 of them are
-outdated. Moreover, the study of licensing conflicts of clones in QS,
-EX, and UD shows that 357 code snippets on Stack Overflow do not
-contain licensing statements while their clone counterparts in
-Qualitas projects or external sources do.
+Stack Overflow, and 359 clone pairs that are highly similar but
+without evidence of copying.
+
+We performed a detailed analysis of the online
+clone pairs on two aspects: outdated code and
+licensing violation. The investigation of the 112 clone pairs from Qualitas
+to Stack Overflow reveals that 64 of them are outdated. 
+Moreover, we found 358 code snippets on Stack Overflow that violate
+the license of their original software.
 

### 2017-02-25 cloneoverflow-latex/cloneoverflow.tex
Checked the last change.

@@
 In total, we have four configurations: Simian with the default
-configuration ($S_D$), Simian with EvaClone configuration ($S_E$), 
-NiCad with the default configurations ($N_D$)
-and NiCad with EvaClone configuration ($N_E$).
+configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
+NiCad with the default configuration ($N_D$)
+and NiCad with the EvaClone configuration ($N_E$).
 
@@
 investigators were compared and 61 conflicts were discussed and resolved.
-There were 3 conflicts that the two investigators could not find a consensus 
+There were 3 conflicts where the two investigators could not find a consensus 
 and the third author was involved for the final judgement.
@@
 any pairs with evidence of cloning from Stack Overflow to Qualitas
-projects. This is very likely due to the age of the Qualitas corpus.
-However, with a newer data set, one can find online clones in
-this direction as shown in another study~\cite{An2017}.
+projects. This is very likely due to the age of the Qualitas corpus as
+another study~\cite{An2017} showed the presence of clones from Stack
+Overflow in newer open source data sets.
 
@@
 64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals.
-Our study discovers links from code in open source projects to code snippets on Stack Overflow using clone detection techniques.
-These links enable us to discover outdate code and licensing problems.
-The links can be exploited further to mitigate the problems of reusing outdated online clones and incompatible license on Stack Overflow code snippets.
-We propose the following actionable items:
+Our study discovers links from code in open source projects to code
+snippets on Stack Overflow using clone detection techniques. These
+links enable us to discover outdated code and licensing problems. The
+links can be exploited further to mitigate the problems of reusing
+outdated online clones and incompatible license on Stack Overflow code
+snippets. We propose the following actionable items:
 
@@
 
-\textbf{Detective measure:} A system to detect outdated source code snippets on Stack Overflow is needed.
-The system can leverage the online clone detection techniques in this study to periodically check if the cloned snippets are still up-to-date with their originals.
-%Moreover, Stack Overflow posters have to provide the information of the project including the original file name and its online repository (if exists).
-With such a system, the poster can be notified when the code has been updated in the original project so that he/she can update their code on Stack Overflow accordingly.
-On the other hand, with a crowdsourcing solution using an IDE plug-in, developers can also report the corrected version of outdated code back to the original Stack Overflow threads when they reuse outdated code and makes corrections to them.
+\textbf{Detective measure:} A system to detect outdated source code
+snippets on Stack Overflow is needed. The system can leverage the
+online clone detection techniques in this study to periodically check
+if the cloned snippets are still up-to-date with their
+originals. %Moreover, Stack Overflow posters have to provide the information of the project including the original file name and its online repository (if exists).
+With such a system, the poster can be notified when the code has been
+updated in the original project so that he/she can update their code
+on Stack Overflow accordingly. On the other hand, with a crowdsourcing
+solution using an IDE plug-in, developers can also report the
+corrected version of outdated code back to the original Stack Overflow
+threads when they reuse outdated code and make corrections to them.
 
@@
 Nevertheless, we might still suffers from false negatives, i.e.~online 
-code clones that are not reported by the tools or filtered 
+code clones that are not reported by the tools or are filtered 
 out by the automatic classifier before the manual investigation.
@@
 \section{Conclusions}
-
-\FIXME{This needs rewriting}
 

### 2017-02-25 cloneoverflow-latex/cloneoverflow.tex
New title.
Rewrote the conclusions.

@@
 \begin{document}
-	\title{Are We Reusing Outdated and Licensed Code from Stack Overflow?}
+	\title{Outdated and License-Violating Code on Stack Overflow}
 	%\titlenote{Produces the permission block, and
@@
 Online code clones are clones that have been copied to Q\&A websites
-such as Stack Overflow. They are similar to classical clones in software
-projects where they can be outdated and violating software license but
-are much harder to detect. We classified 32,533 clone pairs using our seven patterns of online code
-cloning and discovered 112 clone pairs that have been copied, with
-evidence, from Qualitas projects to Stack Overflow, 197 clone
-pairs that have been copied from external sources besides Qualitas to
-Stack Overflow, and 359 clone pairs that are highly similar but
-without evidence of copying.
-
-We performed a detailed analysis of the online
-clone pairs on two aspects: outdated code and
-licensing violation. The investigation of the 112 clone pairs from Qualitas
-to Stack Overflow reveals that 64 of them are outdated. 
-Moreover, we found 358 code snippets on Stack Overflow that violate
-the license of their original software.
+such as Stack Overflow. 
+% They are similar to classical clones in software
+% projects where they can be outdated and violating software license but
+% are much harder to detect. 
+We classified 32,533 clone pairs using seven patterns of online code
+cloning.  After automatically removing boiler-plate clones, we
+manually investigated 3,636 clone pairs. In the 1,216 manually
+confirmed clone pairs, we discovered 112 clone pairs that have been
+copied, with evidence, from Qualitas projects to Stack Overflow, 197
+clone pairs that have been copied from external sources besides
+Qualitas to Stack Overflow, and 359 clone pairs that are highly
+similar but without evidence of copying.
+
+We performed a detailed analysis of the online clone pairs on two
+aspects: outdated code and licensing violation. The investigation of
+the 112 clone pairs copied, with evidence, from Qualitas to Stack
+Overflow reveals that 64 of them are outdated.  Moreover, we found 358
+code snippets on Stack Overflow that violate the license of their
+original software.
 

### 2017-02-25 cloneoverflow-latex/cloneoverflow.tex
Back under 10 pages!

@@
 Q\&A websites (such as Stack Overflow) and vice versa as ``online
-code clones'' (sometimes only ``clones'' for brevity). There are two
+code clones''. There are two
 directions in creating online code clones: (1) code is cloned from a software
@@
 violations, bug propagation, introduction of vulnerabilities, and
-re-use of outdated code. Unfortunately, online clones are more
+re-use of outdated code. Unfortunately, online clones are 
 difficult to locate and fix since the search space in online code
@@
 in the latest version of \textsf{hadoop}, the code example in Stack
-Overflow post is still unchanged. This example shows that there can be
-inconsistencies between online code clones and their originals leading
-users of Stack Overflow to reuse outdated code.
+Overflow post is still unchanged. This example shows that
+inconsistencies between online code clones and their originals can
+lead users of Stack Overflow to reuse outdated code.
 %The code snippet on Stack Overflow can be outdated.
@@
 projects. 
-% We explain our process of building the data sets in each phase separately below.
-
-%\subsection{Experimental Setup}
-
-%We followed the experimental framework by processing the source code from the two data sets, configuring and running the clone detectors, and analysing the clones.
-We discuss each of them in details below.
-
-\subsection{Methodology}
-
+%
+%\subsection{Methodology}
+%
 We designed our study in 6 phases as depicted in \Cref{fig:exp_framework} where
@@
 
-\subsubsection{Phase 1: Clone Identification}
+\subsection{Phase 1: Clone Identification}
 
@@
 
-\subsubsection{Phase 2: Clone Filtering}
+\subsection{Phase 2: Clone Filtering}
 As there are in total 315,786,118 clone pairs reported, it is
@@
 
-%\subsubsection{Filtered Clones Set}
+%\subsection{Filtered Clones Set}
 We selected all \textit{good} pairs (2,313) and the \textit{ok} pairs for
@@
 
-\subsubsection{Phase 3-4: Clone Validation and Classification}
+\subsection{Phase 3-4: Validation and Classification}
 We used the 3,636 filtered clone pairs after automatic classification for
@@
 %associated with 697 clone pairs.
-%\subsubsection{Defining Online Code Cloning Patterns}
+%\subsection{Defining Online Code Cloning Patterns}
 using Kapser's cloning patterns. We found that 
@@
 
-\subsubsection{Phase 5: Outdated Clones}
+\subsection{Phase 5: Outdated Clones}
 Outdated code occurs when a piece of code has been copied from its
@@
 
-\subsubsection{Phase 6: Licensing Analysis}
+\subsection{Phase 6: Licensing Analysis}
 Software licensing plays an important role in software
@@
 
-\textbf{EX: External Sources.} We found 200 online clone pairs with
+\textbf{EX: External Sources.} We found 200 clone pairs with
 evidence of cloning from external sources to Stack Overflow and to Qualitas.  
@@
 no evidence of cloning between Qualitas and Stack Overflow but with a
-high code similarity that suggests cloning. They include 15, 20, 293,
-and 31 pairs from the \textit{good}, \textit{ok'}, $S_D'$, and $N_D'$
-set respectively. The most cloned projects is \textsf{netbeans} with
+high code similarity that suggests cloning. 
+% They include 15, 20, 293, and 31 pairs from the \textit{good},
+% \textit{ok'}, $S_D'$, and $N_D'$ set respectively.
+The most cloned projects is \textsf{netbeans} with
 93 clone pairs. Most of the clones are a large chunk of code handling
@@
 	\centering
-	\includegraphics[width=\linewidth]{freshness}
+	\includegraphics[width=\linewidth]{freshness}\vspace{-1ex}
 	\caption{Status of the 112 QS online clone pairs}
@@
 answers increase their chances of being reused. Even though most of
-the Qualitas projects came with a software license, we found that the licensing information
+the Qualitas projects came with a software license, we found that the license information
 were frequently missing after the code was copied to Stack
@@
 snippets. Of 226 \textbf{UD} clone pairs, 202 pairs have incompatible
-licenses. Again, most of the clones in Qualitas contain a license
+licenses. Again, most clones in Qualitas contain a license
 while the Stack Overflow snippets do not.

### 2017-02-26 cloneoverflow-latex/cloneoverflow.tex
Added medians of SO snippets and Qualitas (also updated the other numbers since I just found cloc option to not skip duplicated files).

@@
 Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We obtained 144,064 Java code snippets containing 2,346,267
+We obtained 144,064 Java code snippets containing 2,332,940
 lines\footnote{Measured by cloc:
   \url{https://github.com/AlDanial/cloc}} of Java source code.
+Median of the snippet size is 10.
 % excluding comments and blank lines.
@@
 projects analysed in the study. As shown in \Cref{tab:datasets}, the
-111 Qualitas project have 160,937 Java files containing 19,086,883
-lines of
-code. %Details of the 109 Qualitas projects and their licenses are listed in Table \ref{t:new_and_old}.
+111 Qualitas project have 166,709 Java files containing 19,614,083
+lines of code. Median of the project size is 60,667 lines of code.
 
@@
   %\small
-  \begin{tabular}{lrr}
-    \hline 
-    Dataset & No. of files & SLOC \\
-    \hline
-    Stack Overflow & 144,064 & 2,346,267 \\ 
+  \begin{tabular}{lrrr}
+    \hline 
+    Dataset & No. of files & SLOC & Median \\
+    \hline
+    Stack Overflow & 144,064 & 2,332,940 & 10 \\ 
     %\hline 
-    Qualitas &  160,937 & 19,086,883 \\ 
+    Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
     \hline 

### 2017-02-26 cloneoverflow-latex/cloneoverflow.tex
Checked the latest changes and corrected the bibliography.

@@
 extracted from the latest version (as of 26 September 2016) of
-\textsf{hadoop}. We can see that they are highly similar except a line
+\textsf{hadoop}. We can see that they both are highly similar except a line
 containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in
@@
   \url{https://github.com/AlDanial/cloc}} of Java source code.
-Median of the snippet size is 10.
+The median of the snippet size is 10.
 % excluding comments and blank lines.
@@
 111 Qualitas project have 166,709 Java files containing 19,614,083
-lines of code. Median of the project size is 60,667 lines of code.
+lines of code. The median project size is 60,667 lines of code.
 

### 2017-02-26 cloneoverflow-latex/cloneoverflow.tex
Updated the experimental framework to clearly show outputs of phase 5 & 6, a minor revision of typos and errors from previous revisions. Still in 10 pages!

@@
 
-Regarding the online cloning classification patterns, 
-we studied the 8 patterns of cloning from Kapser et
+\textbf{The online cloning classification patterns:} 
+We studied the 8 patterns of cloning from Kapser et
 al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
@@
 
-			EX & Cloned from an external source (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
+			EX & Cloned from an external source \textit{X} (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
 
@@
 %boiler-plate code with filters before the analysis, we still 
-We observed 29,330 such clone pairs. The \textbf{BP} clone pairs account for
+We observed 29,330 such clone pairs. The BP clone pairs account for
 90\% of all clone pairs we classified. The majority of them are
@@
 time. German et al.~\cite{German2009} found that licensing 
-conflicts occur between the clone siblings (clones among 
-different systems that come from the same source). Later, 
+conflicts occur between the clone siblings, i.e.~clones among 
+different systems that come from the same source. Later, 
 German et al.~\cite{German2010} created an automated tool 
-for software license identification, Ninka. 
+for software license identification, Ninka, which is used
+in our online clone license analysis. 
 %We use Ninka to analyse software license from Stack 
-Overflow snippets and Qualitas projects.
+%Overflow snippets and Qualitas projects.
 

### 2017-02-27 cloneoverflow-latex/cloneoverflow.tex
Small changes to the abstract.

@@
   We present a study incorporating several state-of-the-art tools and
-  techniques to automatically extract, prioritise, and filter
-  315,786,118 detected online clone pairs between 144,064 Java code
-  snippets on Stack Overflow and 111 Java open source projects in the
-  curated Qualitas corpus. We discovered and investigated 32,533
-  non-trivial online clone candidates. Our study revealed that 64 out
-  of 112 clones with strong evidence of copying from a Qualitas
-  project to Stack Overflow are outdated. Furthermore, we found 357
-  code snippets on Stack Overflow that violate the license of their
-  original software.
+  techniques to automatically extract, prioritise, and filter detected
+  online clone pairs between 144,064 Java code snippets on Stack
+  Overflow and 111 Java open source projects in the curated Qualitas
+  corpus. We discovered and analysed 32,533 non-trivial online clone
+  candidates. Our investigation of 3,636 manually confirmed clone
+  pairs revealed strong evidence that 112 clones have been copied from
+  a Qualitas project to Stack Overflow.  We found 64 of them (57\%) 
+  to be outdated and potentially harmful for reuse.  Furthermore, we
+  found 357 code snippets on Stack Overflow that violate the license
+  of their original software.
   % These snippets are questionable for reuse.
@@
   200 pairs were found to be cloned to Stack Overflow from external
-  sources outside Qualitas projects.} 
+  sources.} 
 %We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
@@
 scalability issues and susceptibility to incomplete code snippets.
+We mitigated the problem of clone
+detector's parameter sensitivity by adding another established
+configuration from the EvaClone study~\cite{Wang2013}. 
 Second, we adopted Bellon's agreement metric~\cite{Bellon2007}
@@
 % detectors and their configurations.
-We mitigated the problem of clone
-detector's parameter sensitivity by adding another established
-configuration from the EvaClone study~\cite{Wang2013}.
 
@@
 
-The 3,636 clone pairs classified manually by the first author are
-subject to manual judgement and human errors.  Although we have tried
+The 3,636 clone pairs classified by the first author are
+subject to manual judgement and human errors.  Although we tried
 our best to be careful on searching for evidence and classifying the
@@
 code give detrimental effects to the software since they may 
-introduce vulnerabilities. Our study discovers similar findings 
-in the context of outdated code on Stack Overflow.
+introduce vulnerabilities. Our study similarily finds
+% on % the context of 
+outdated code on Stack Overflow.
 

### 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
Incorporated Rocco's changes.

@@
 \affiliation{%
-	\institution{Università degli Studi del Molise}
+	\institution{University of Molise}
 	%  \streetaddress{P.O. Box 1212}
-	\city{Campobasso, Italy} 
+	\city{Pesche (IS), Italy} 
 	%  \state{Ohio} 
@@
 
-\keywords{clone detection, Stack Overflow, outdated code, software licensing}
+\keywords{Clone Detection, Stack Overflow, Outdated Code, Software Licensing}
 
@@
 Stack Overflow is a popular online programming community with 6.8
-million users\footnote{Statistics as of 25 February 2017 from \url{http://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
+million users\footnote{Statistics as of February 25, 2017 from \url{http://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
 to programming problems. The website has found to be useful for
@@
 usually not authored directly on the Stack Overflow website but copied
-from another location. An answer's snippet could be copied and modified
+from another location. A snippet in an answer could be copied and modified
 from a code snippet in the question, copied from the answerer's own
@@
 \textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22262310}}.
-\Cref{fig:before-after} shows a code snippet embedded as a part of the
-accepted answer on the left. The snippet shows how \textsf{hadoop}
+\Cref{fig:before-after} shows---on the left---a code snippet embedded as a part of the
+accepted answer. The snippet shows how \textsf{hadoop}
 implements the {\small{\texttt{compare}}} method in its
@@
 right shows another version of the same method, but at this time
-extracted from the latest version (as of 26 September 2016) of
+extracted from the latest version (as of September 26, 2016) of
 \textsf{hadoop}. We can see that they both are highly similar except a line
@@
 While research has mostly focused on reusing code snippets \emph{from}
-Stack Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less work
-has been conducted on finding the origins of code examples copied
+Stack Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less studies
+have been conducted on finding the origins of code examples copied
 \emph{to} Stack Overflow and problems of reusing them such as outdated
@@
 makes the following primary contributions:
-
-\vspace{0.5ex}%
-\noindent\textbf{1.~A manual study of online code clones:} 
+\begin{enumerate}
+\item \textbf{A manual study of online code clones:} 
 We used two clone detection tools to discover 315,786,118 similar code
@@
 Qualitas corpus~\cite{QualitasCorpus}.
-
-\vspace{0.5ex}%
-\noindent\textbf{2.~An investigation of outdated and license-violating
+\item \textbf{An investigation of outdated and license-violating
   online clones on Stack Overflow:} Our study shows that from the
@@
 % and questionable for being reused.
-
-\vspace{0.5ex}%
-\noindent\textbf{3.~An online code clone oracle:} The 3,636 manually
+\item \textbf{An online code clone oracle:} The 3,636 manually
 investigated and validated online clone pairs are available for
@@
 used as a clone oracle.
+\end{enumerate}
 
@@
 Overflow and 111 Java open source projects to answer the following
-research questions: \\
-%
-\textbf{RQ1 (online code clones):} \textit{To what extent is source
+research questions:
+\begin{itemize}
+\item \textbf{RQ1 (Online code clones):} \textit{To what extent is source
   code cloned between Stack Overflow and open source projects?} We
@@
 Overflow and open source projects to understand the scale of the
-problem. \newline 
-%
-\textbf{RQ2 (Patterns of online code clones):} \textit{Why do online
+problem. 
+\item \textbf{RQ2 (Patterns of online code clones):} \textit{Why do online
   code clones occur?} We categorised online clones into seven
 categories allowing insights to why online code clones are created.
-\newline
-%
-\textbf{RQ3 (Outdated online code clones):} \textit{Are
+\item \textbf{RQ3 (Outdated online code clones):} \textit{Are
   online code clones up-to-date compared to their counterparts in the
@@
 Overflow code examples since users are potentially reusing
-them. \newline
-%
-\textbf{RQ4 (Software licensing violation):} \textit{Do
+them. 
+\item \textbf{RQ4 (Software licensing violation):} \textit{Do
   licensing conflicts occur between Stack Overflow clones and their
@@
 can cause software developers to violate licenses.
+\end{itemize}
 
@@
 \textbf{Open source systems: }
-We selected the established \textbf{Qualitas} corpus~\cite{QualitasCorpus} 
-for this study. It is a curated Java corpus that has been used in several
+We selected the established \textbf{Qualitas} corpus~\cite{QualitasCorpus}. It is a curated Java corpus that has been used in several
 software engineering
@@
 ranging from programming languages to
-visualisation. We selected the 20130901r release
+visualisation. We selected the release 20130901r
 of the Qualitas corpus containing 112 Java open source projects. This
@@
 Java source code due to its licensing limitation~\cite{QualitasCorpus}
-and is removed from the study. This resulted in a total of 111
-projects analysed in the study. As shown in \Cref{tab:datasets}, the
-111 Qualitas project have 166,709 Java files containing 19,614,083
-lines of code. The median project size is 60,667 lines of code.
+and is removed from the study. This resulted in 111
+projects analysed in the study, for a total of 166,709 Java files containing 19,614,083
+lines of code (see \Cref{tab:datasets}). The median project size is 60,667 lines of code.
 
@@
   Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011,
-  Sajnani2016}. It utilises TXL~\cite{Cordy2006} for parsing and
+  Sajnani2016}. NiCad utilises TXL~\cite{Cordy2006} for parsing and
 pretty-printing source code and provides code normalisation by
@@
 	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|c|c|c|r}
-		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{3}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-5}
-		& & \textit{L} & \textit{S} & \textit{G} & \\
-		\hline 
-		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & \checkmark & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & \checkmark & 83 \\ 
-		\hline
-		\multicolumn{6}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$, \textit{G}=\textit{good}/\textit{ok} pairs.}  \\
+	\begin{tabular}{l|r|c|c|r}
+		\hline
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-4}
+		& & \textit{L} & \textit{S} & \\ 
+		\hline 
+		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & 17,801 \\
+		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & 83 \\ 
+		\hline
+		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
 	\end{tabular} %
@@
 clone pair candidates is still too large for manual inspection (67,570
-for $S_D$ and 632,855 pairs for $N_D$). We applied three filters: clone
-size, similarity threshold, and good/ok pairs. For
-the \emph{clone size filter}, we raised the minimum clone size to 10 lines
+for $S_D$ and 632,855 pairs for $N_D$). We applied two filters: clone
+size and similarity threshold. %, and good/ok pairs. 
+For the \emph{clone size filter}, we raised the minimum clone size to 10 lines
 since larger clones are more interesting, while smaller ones tend to
@@
 only to NiCad clone pairs since Simian does not provide a similarity
-configuration. The last filter, \emph{good/ok pairs}, removes the
-clone pairs that already exist in the agreed clone sets.
-
-As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the
-results using clone size and gook/ok pairs. The
-two filters reduced the number of $S_D$ clones to 17,801 pairs. We
+configuration. 
+%The last filter, \emph{good/ok pairs}, removes the clone pairs that already exist in the agreed clone sets.
+%As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and gook/ok pairs.
+
+The two filters reduced the number of $S_D$ clones to 17,801 pairs. We
 filtered $N_D$ clones by additionally raising the similarity
@@
 
+\textbf{Selection of clones: }
 %\subsection{Filtered Clones Set}
@@
 
-For manual investigation, the first author, who has been working on clone detection research for 
+\textbf{Manual investigation:} 
+The first author, who has been working on clone detection research for 
 two years, took the role of the main investigator performing a manual 
@@
 investigators were compared and 61 conflicts were discussed and resolved.
-There were 3 conflicts where the two investigators could not find a consensus 
+There were three conflicts where the two investigators could not find a consensus 
 and the third author was involved for the final judgement.
 
+\begin{table}
+	\centering
+	\caption{The seven patterns of online code cloning}
+	\label{tab:classification_scheme}
+	%\resizebox{\columnwidth}{!}{%
+        \small\vspace{-1ex}
+		\begin{tabular}{c@{~~}p{7.35cm}}
+			\hline 
+			Patt. & Description \\ 
+			\hline 
+			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\
+
+			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\
+
+			EX & Cloned from an external source \textit{X} (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
+
+			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
+			\hline 
+			BP & Boiler-plate or IDE auto-generated \\
+
+			IN & Inheritance, interface implementation  \\
+
+			AC & Accidental similarity, false clones \\ 
+			\hline 
+		\end{tabular}  %
+	%}
+\end{table}
+
 \textbf{The online cloning classification patterns:} 
-We studied the 8 patterns of cloning from Kapser et
+We studied the eight patterns of cloning from Kapser et
 al.~\cite{Kapser2006,Kapser2008} and performed a preliminary study to
@@
 more suitable and fine-grained classification scheme is needed. After
-the preliminary study, we adopted one of Kapser's cloning patterns,
+a preliminary study, we adopted one of Kapser's cloning patterns,
 \emph{boiler-plate code}, and defined
-6 new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
+six new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
 IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
@@
 
-\begin{table}
-	\centering
-	\caption{The seven patterns of online code cloning}
-	\label{tab:classification_scheme}
-	%\resizebox{\columnwidth}{!}{%
-        \small\vspace{-1ex}
-		\begin{tabular}{c@{~~}p{7.35cm}}
-			\hline 
-			Patt. & Description \\ 
-			\hline 
-			QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\
-
-			SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\
-
-			EX & Cloned from an external source \textit{X} (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
-
-			UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
-			\hline 
-			BP & Boiler-plate or IDE auto-generated \\
-
-			IN & Inheritance, interface implementation  \\
-
-			AC & Accidental similarity, false clones \\ 
-			\hline 
-		\end{tabular}  %
-	%}
-\end{table}
-
 \subsection{Phase 5: Outdated Clones}
@@
 the latest version of the Qualitas projects from their repositories on
-26 September 2016. For each \textbf{QS} online clone pair, we used the
+September 26, 2016. For each \textbf{QS} online clone pair, we used the
 clone from Qualitas as a proxy. We searched for its latest version by
@@
 
-\begin{table}
-	\centering
-	\caption{No.~of online clones candidates for the classification}
-	\label{tab:online_clone_classification_results}
-	%\small
-	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r}
-		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
-		& & Auto & Manual \\
-		\hline 
-		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
-		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
-		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
-		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
-		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\hline
-		Total  & 32,533 & 28,897 & 3,636 \\ 
-		\hline
-	\end{tabular} %
-	%}
-\end{table}
-
 As shown in \Cref{tab:online_clone_classification_results}, the automatic
@@
 
+\begin{table}
+	\centering
+	\caption{No.~of online clones candidates for the classification}
+	\label{tab:online_clone_classification_results}
+	%\small
+	%	\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{l|r|r|r}
+		\hline
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
+		& & Auto & Manual \\
+		\hline 
+		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
+		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
+		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
+		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
+		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
+		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+		\hline
+		Total  & 32,533 & 28,897 & 3,636 \\ 
+		\hline
+	\end{tabular} %
+	%}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Classifications of online clone pairs.}
+	\label{tab:classification_good_o}
+	%\small
+	%\resizebox{\columnwidth}{!}{%
+		\begin{tabular}{l|rrrr|rrr|r}
+			\hline
+			Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
+			\hline
+			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
+			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 44 & 20 & 12,128 & 23 & 107 & 12,336 \\
+			\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
+			\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
+			\hline
+			Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
+			\hline
+		\end{tabular} 
+	%}
+\end{table}
+
 \textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
-online clone pairs with evidences of cloning from Qualitas projects to
+online clone pairs with evidences of cloning from 19 Qualitas projects to
 Stack Overflow. They include 3, 14, 86, and 9 pairs from the
@@
   org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''}.
+
+\begin{table*}
+	\centering
+	\caption{Examples of the outdated QS online clones}
+	\label{tab:stale_code_details}
+	\resizebox{0.9\linewidth}{!}{
+		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
+		 \hline
+		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
+		 \hline
+		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
+		 \hline
+		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
+		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
+		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
+		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
+		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
+		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
+		 \hline 
+		 \multicolumn{10}{l}{{\footnotesize * \textit{S}:
+                  modified/added/deleted statements, \textit{D}: file
+                  has been deleted,  \textit{R}: method has been
+                  rewritten completely}}
+		\end{tabular} %
+	}
+\end{table*}
 
@@
 
-\begin{table}
-	\centering
-	\caption{Classifications of online clone pairs.}
-	\label{tab:classification_good_o}
-	%\small
-	%\resizebox{\columnwidth}{!}{%
-		\begin{tabular}{l|rrrr|rrr|r}
-			\hline
-			Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
-			\hline
-			\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
-			\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 44 & 20 & 12,128 & 23 & 107 & 12,336 \\
-			\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
-			\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
-			\hline
-			Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
-			\hline
-		\end{tabular} 
-	%}
-\end{table}
-
 %For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code.
@@
 \textbf{To answer RQ2, we found that a large amount of the clone pairs
-  between Stack Overflow and Qualitas projects are boiler-plate code
+  between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
   (29,330) or accidental clones (2,420) with no evidence that the code
-  has actually been copied. Nevertheless, we found 112 pairs that had
-  strong evidences to be cloned from Qualitas to Stack Overflow and
+  has actually been copied. Nevertheless, we found 112 pairs with
+  strong evidences to be cloned from 19 Qualitas projects to Stack Overflow and
   200 pairs were found to be cloned to Stack Overflow from external
@@
 {\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
-has been heavily modified on 5 February 2016.
+has been heavily modified on February 5, 2016.
 
@@
 {\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
-Beams on 20th January 2012, two years after it was
+Beams on January 20, 2012, two years after it was
 posted.
+
 % The latest version of Spring does not contain the file anymore.
@@
 	\centering
-	\includegraphics[width=\linewidth]{freshness}\vspace{-1ex}
+	\includegraphics[width=0.9\linewidth]{freshness}
 	\caption{Status of the 112 QS online clone pairs}
@@
 \end{figure}
-
-\begin{table*}
-	\centering
-	\caption{Examples of the outdated QS online clones}
-	\label{tab:stale_code_details}
-	\small
-	%\resizebox{\textwidth}{!}{%
-		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
-		 \hline
-		 \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
-		 \hline
-		 Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
-		 \hline
-		 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
-		 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
-		 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
-		 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
-		 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
-		 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
-		 \hline 
-		 \multicolumn{10}{l}{{\footnotesize * \textit{S}:
-                  modified/added/deleted statements, \textit{D}: file
-                  has been deleted,  \textit{R}: method has been
-                  rewritten completely}}
-		\end{tabular} %
-	%}
-\end{table*}
 
@@
 	\label{tab:license_abc}
-	\small
-	%\resizebox{\columnwidth}{!}{%
+	%\small
+	\resizebox{0.95\linewidth}{!}{
 	\begin{tabular}{l|p{1.95cm}l|rrr}
@@
 		\hline
-	\end{tabular} %
-%}
+	\end{tabular} 
+}
 \end{table}
@@
 
-\section{Overall Discussion}
+\subsection{Overall Discussion}
 %What can we learn for the results?
@@
 snippets. We propose the following actionable items:
-
-\textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' licensed software projects to Stack Overflow.
+\begin{itemize}
+\item \textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' licensed software projects to Stack Overflow.
 Moreover, an IDE plug-in that can automatically detect pasted source code and follow the link to Stack Overflow and then to the original open source projects, could also prevent the issue of license violation.
-
-\textbf{Detective measure:} A system to detect outdated source code
+\item \textbf{Detective measure:} A system to detect outdated source code
 snippets on Stack Overflow is needed. The system can leverage the
@@
 threads when they reuse outdated code and make corrections to them.
+\end{itemize}
+The implementation and the evaluation of the above actionable items is part of the agenda of our future work.
 

### 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
Modified the paper according to Rocco's comments.

@@
 
-Given that a clone pair \textit{CP} is formed by two clone fragments
-\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} = (\textit{CF$_1$},
-\textit{CF$_2$}), we can define the \textit{overlap}\footnote{The overlap value can be considered as Jaccard similarity.} and
-\textit{contained} value of two clone pairs as
+We define the \textit{overlap}\footnote{The overlap value can be considered as Jaccard similarity.} and
+\textit{contained} value of two clone fragments (\textit{CF}) as
 %\squeezeup
 \begin{displaymath}
-  overlap(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|}
+  overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|}
 \end{displaymath}
@@
 \begin{displaymath}
-  contained(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
+  contained(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1)|}
 \end{displaymath}
@@
 \noindent%
-The \textit{good-value}  and the \textit{ok-value}  of two clone pairs are defined as
+Given that a clone pair \textit{CP} is formed by two clone fragments
+\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} = (\textit{CF$_1$},
+\textit{CF$_2$}), the \textit{good-value}  and the \textit{ok-value}  of two clone pairs are defined as
 %\squeezeup
@@
 Even choosing only the default configurations, the number of disagreed
-clone pair candidates is still too large for manual inspection (67,570
-for $S_D$ and 632,855 pairs for $N_D$). We applied two filters: clone
+clone pair candidates is still too large for manual inspection.
+%(67,570 for $S_D$ and 632,855 pairs for $N_D$). 
+We applied two filters: clone
 size and similarity threshold. %, and good/ok pairs. 

### 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
Fixed the number of disagreed clone candidates.

@@
 		\hline 
-		\multirow{1}{*}{$S_D$} & 67,570 & \checkmark & & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 632,855 & \checkmark & \checkmark & 83 \\ 
+		\multirow{1}{*}{$S_D$} & 55,274 & \checkmark & & 17,801 \\
+		\multirow{1}{*}{$N_D$} & 620,680 & \checkmark & \checkmark & 83 \\ 
 		\hline
@@
 Even choosing only the default configurations, the number of disagreed
-clone pair candidates is still too large for manual inspection.
-%(67,570 for $S_D$ and 632,855 pairs for $N_D$). 
+clone pair candidates is still too large for manual inspection
+(as shown in \Cref{tab:online_clone_pairs}). 
 We applied two filters: clone

### 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
Fixed formatting of Table 11.
Last changes.

@@
 While research has mostly focused on reusing code snippets \emph{from}
-Stack Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), less studies
+Stack Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), fewer studies
 have been conducted on finding the origins of code examples copied
@@
 research questions:
-\begin{itemize}
-\item \textbf{RQ1 (Online code clones):} \textit{To what extent is source
+\begin{description}
+\item[RQ1 (Online code clones):] \textit{To what extent is source
   code cloned between Stack Overflow and open source projects?} We
@@
 problem. 
-\item \textbf{RQ2 (Patterns of online code clones):} \textit{Why do online
+\item[RQ2 (Patterns of online code clones):] \textit{Why do online
   code clones occur?} We categorised online clones into seven
 categories allowing insights to why online code clones are created.
-\item \textbf{RQ3 (Outdated online code clones):} \textit{Are
+\item[RQ3 (Outdated online code clones):] \textit{Are
   online code clones up-to-date compared to their counterparts in the
@@
 them. 
-\item \textbf{RQ4 (Software licensing violation):} \textit{Do
+\item[RQ4 (Software licensing violation):] \textit{Do
   licensing conflicts occur between Stack Overflow clones and their
@@
 can cause software developers to violate licenses.
-\end{itemize}
+\end{description}
 
@@
 between 0 and 1. A \textit{good} clone pair has stronger agreement
-than an \textit{ok} pair. We follow the original definitions of good-
-and ok-match introduced in Bellon's paper~\cite{Bellon2007}.
-
-We define the \textit{overlap}\footnote{The overlap value can be considered as Jaccard similarity.} and
-\textit{contained} value of two clone fragments (\textit{CF}) as
+than an \textit{ok} pair. We follow Bellon's original definitions of
+good- and ok-match~\cite{Bellon2007}, which are based on how much two
+clone fragments \textit{CF} overlap\footnote{The overlap value can be
+  considered as Jaccard similarity.}  and how much of them is
+contained in each other:
 %\squeezeup
@@
 \end{displaymath}
-
 \noindent%
-Given that a clone pair \textit{CP} is formed by two clone fragments
-\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} = (\textit{CF$_1$},
-\textit{CF$_2$}), the \textit{good-value}  and the \textit{ok-value}  of two clone pairs are defined as
+A clone pair \textit{CP} is formed by two clone fragments
+\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} =
+(\textit{CF$_1$}, \textit{CF$_2$}), and the \textit{good-value} and
+the \textit{ok-value} of two clone pairs are defined as
+
 %\squeezeup
@@
   \centering
+  \vspace{3.5ex}
   \includegraphics[width=0.9\linewidth]{good-ok_pairs}
@@
 	%\small
-	\resizebox{0.95\linewidth}{!}{
-	\begin{tabular}{l|p{1.95cm}l|rrr}
+	\resizebox{\linewidth}{!}{
+	\begin{tabular}{l|p{2.2cm}l|rrr}
 		\hline

### 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
Modified the URL to point to the answer directly instead of question. Avoid confusion of the ID shown in footnote and the motivating example.
Corrected the number of ok SDND pairs!
Last-minute typo fixes.

@@
 {\small{\texttt{RawComparator}}} in
-\textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22262310}}.
+\textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
 \Cref{fig:before-after} shows---on the left---a code snippet embedded as a part of the
@@
     \textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
-    \textit{ok} & 12,336 & 993 & 79 & 20,021 & 32,316 \\
+    \textit{ok} & 12,063 & 993 & 79 & 20,021 & 32,316 \\
     \hline
@@
   pairs because \textit{ok} pairs subsume
-  \textit{good} pairs.}. We obtained 12,336; 993; 79; and 20,021 pairs
+  \textit{good} pairs.}. We obtained 12,063; 993; 79; and 20,021 pairs
 from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
@@
 source code into their software without checking. A study by An et
-al.~\cite{An2017} reports 1,219 cases of potential license violations
+al.~\cite{An2017} reports 1,279 cases of potential license violations
 between 399 Android apps and Stack Overflow code
@@
 
-\textbf{For RQ3, our results show that more than half (64) of QS clone
+\textbf{For RQ3, our results show that 57\% (64) of QS clone
   pairs on Stack Overflow are outdated. 60 pairs differ from their
@@
 They found 1,226 code snippets which were reused from 68 Android apps. 
-They also observed that there are 1,219 cases of potential 
+They also observed that there are 1,279 cases of potential 
 license violations. The authors rely on the timestamp to 

### 2017-05-02 cloneoverflow-latex/rebuttal/rebuttal.txt
Added a rebuttal draft and a small program to calculate the number of snippets per Qualitas clone.

REVIEWER 1

Question 1: 
This study is motivated by [1, 2]. An et al. [2] found that 62 active Android projects contains 232 exact copies of snippets on Stack Overflow (SO) with confirmation from the developers. 60 apps have license violations between the copied snippets and project's license. 126 snippets are found to potentially migrate from one app to another via SO posts, i.e. 'code laundering'. Acar et al. [1] found that SO is often chosen by programmers when solving tasks. They examined 139 SO threads used by the participants in four Android security-related tasks and found that only 17% of them contain secure snippets. The same security-related problems are discovered in a random sampling of 200,000 apps from Google Play (e.g. 98.9% implement insecure hostname verifier similarly to the SO examples).

Question 2:
The motivation still holds. It is known that clone detection tools report a lot of false/trivial clones. We focus on the important ones. The number of 32,533 analysed clone pairs are the ones that are not trivial clones according to the clone agreement and clone filtering process for feasibility of a manual study. However, they are not the 'total' number of clones between SO and Qualitas.

Question 3:
No. We cannot expect the same results from a different pair of evaluators. Classifications of clones by human are known to be very subjective. However, we expect similar results with a higher number of evaluators.

Question 4:
Although the code is provided as minimum working examples, it is known that the code is used as-is and causing problems in active projects [1,2]. Active maintenance and support provided by SO can mitigate such problems

REVIEWER 2

Question 1:
We are not aware of any curated set of software that includes non-open source projects. We focused on open source projects to allow replication of our study.

Question 2:
See Table 11: 79 (QS) and 77 (EX) pairs (snippets) violate the license but acknowledge the source, 202 (UD) pairs violate the license and have no acknowledgement.

REVIEWER 3

Question 1:
Disagreed clone pairs are also clones, they just have lower confidence to be true clones. By only inspecting agreed clones, one would miss several true clones due to the tools' differences [61].

Question 3:
We consider them as two clone pairs. From 32,533 online clone pair candidates, there are 4,018 distinct Qualitas clones (file + start + end lines) and, on average, each of them forms a clone pair with 7.6 distinct Stack Overflow snippets.

Question 4:
The automatic classification of boiler plate code is done first (Figure 2). The manual investigation (Figure 4) only classifies boiler plate clones that have been missed by the automatic classification. During the manual investigation, the classification of accidental clones is easier than the boiler plate classification, thus it comes second.

Question 5:
See Table 7: for the manual confirmed pairs, 516/144,064 of snippets with on average 26% of the snippets' code. And for the reported pairs, 14,856/144,064 with an average of 38%. Note that it is restricted to only 111 Qualitas projects and one can expect a large number of clones to other projects.

### 2017-05-02 SnippetCounter/src/main/java/Main.java

@@ -1,0 +1,149 @@
+import java.io.*;
+import java.util.*;
+
+/**
+ * Created by Chaiyong on 5/2/17.
+ */
+public class Main {
+    public static void main(String[] args) {
+        File file = new File("clones.csv");
+        HashMap<String, HashSet<String>> cloneMap = new HashMap<String ,HashSet<String>>();
+        HashMap<String, HashSet<String>> cloneMapNoLine = new HashMap<String ,HashSet<String>>();
+
+        HashSet<String> snippets;
+        HashSet<String> snippetsNoLine;
+
+        HashSet<String> qualitasClones = new HashSet<String>();
+        int count = 0;
+        // copied from
+        // http://stackoverflow.com/questions/5868369/how-to-read-a-large-text-file-line-by-line-using-java
+        try {
+            BufferedReader br = new BufferedReader(new FileReader(file));
+            String line;
+
+            while ((line = br.readLine()) != null) {
+                if (line.contains(",")) {
+                    count++;
+                    String[] lineSplit = line.split(",");
+
+                    String qClone = "";
+                    String soClone = "";
+
+                    if (lineSplit.length >= 11) {
+                         qClone = lineSplit[3] + "$"
+                                + lineSplit[4] + "$"
+                                + lineSplit[5] + "$"
+                                + lineSplit[9] + "$"
+                                + lineSplit[10] + "$"
+                                + lineSplit[11];
+                         soClone = lineSplit[0] + "$"
+                                 + lineSplit[1] + "$"
+                                 + lineSplit[2] + "$"
+                                 + lineSplit[6] + "$"
+                                 + lineSplit[7] + "$"
+                                 + lineSplit[8];
+                    } else {
+                        qClone = lineSplit[3] + "$"
+                                + lineSplit[4] + "$"
+                                + lineSplit[5];
+                        soClone = lineSplit[0] + "$"
+                                + lineSplit[1] + "$"
+                                + lineSplit[2];
+                    }
+
+                    if (cloneMap.get(qClone) == null) {
+                        snippets = new HashSet<String>();
+                        snippetsNoLine = new HashSet<String>();
+
+                        snippets.add(soClone);
+                        snippetsNoLine.add(lineSplit[0]);
+                    } else {
+                        snippets = cloneMap.get(qClone);
+                        snippetsNoLine = cloneMapNoLine.get(qClone);
+
[…]

### 2017-05-03 SnippetCounter/src/main/java/Main.java
Updated code to count the number of SO snippets per Qualitas file.

@@ -6,14 +6,14 @@ import java.util.*;
  */
 public class Main {
     public static void main(String[] args) {
-        File file = new File("clones.csv");
+//        File file = new File("clones.csv");
+        File file = new File("clones_qs_ex_ud.csv");
         HashMap<String, HashSet<String>> cloneMap = new HashMap<String ,HashSet<String>>();
         HashMap<String, HashSet<String>> cloneMapNoLine = new HashMap<String ,HashSet<String>>();
 
         HashSet<String> snippets;
         HashSet<String> snippetsNoLine;
 
-        HashSet<String> qualitasClones = new HashSet<String>();
         int count = 0;
         // copied from
         // http://stackoverflow.com/questions/5868369/how-to-read-a-large-text-file-line-by-line-using-java
@@ -27,118 +27,88 @@ public class Main {
                     String[] lineSplit = line.split(",");
 
                     String qClone = "";
+                    String qCloneNoLine = "";
                     String soClone = "";
+                    String soCloneNoLine = "";
 
                     if (lineSplit.length >= 11) {
-                         qClone = lineSplit[3] + "$"
+                        qClone = lineSplit[3] + "$"
                                 + lineSplit[4] + "$"
                                 + lineSplit[5] + "$"
                                 + lineSplit[9] + "$"
                                 + lineSplit[10] + "$"
                                 + lineSplit[11];
-                         soClone = lineSplit[0] + "$"
-                                 + lineSplit[1] + "$"
-                                 + lineSplit[2] + "$"
-                                 + lineSplit[6] + "$"
-                                 + lineSplit[7] + "$"
-                                 + lineSplit[8];
+                        soClone = lineSplit[0] + "$"
+                                + lineSplit[1] + "$"
+                                + lineSplit[2] + "$"
+                                + lineSplit[6] + "$"
+                                + lineSplit[7] + "$"
+                                + lineSplit[8];
                     } else {
                         qClone = lineSplit[3] + "$"
                                 + lineSplit[4] + "$"
                                 + lineSplit[5];
+
                         soClone = lineSplit[0] + "$"
                                 + lineSplit[1] + "$"
                                 + lineSplit[2];
                     }
+                    qCloneNoLine = lineSplit[3];
+                    soCloneNoLine = lineSplit[0];
 
                     if (cloneMap.get(qClone) == null) {
[…]

### 2017-08-12 SCCTokenizer/file_concatenator.py
added scripts from summit and modified the tokenizer a little more

@@ -38,6 +38,7 @@ def createFileId(file):
 
     file_id_list.append(file)
     fileid = file_id_list.index(file)
+    writefile("so-headers.txt", str(fileid) + "," + file + "\n", "a", False)
 
     return fileid
 
@@ -46,14 +47,14 @@ def saveFileId():
     global file_id_list
     # print file_id_list
     try:
-        os.remove("fileidmap.txt")
+        os.remove("so-headers.txt")
     except Exception as e:
-        print "couldn't remove fileidmap.txt file."
+        print "couldn't remove so-headers.txt file."
 
     for index, file in enumerate(file_id_list):
-        writefile("fileidmap.txt", str(index) + "," + file + "\n", "a", False)
+        writefile("so-headers.txt", str(index) + "," + file + "\n", "a", False)
 
-    print "saved fileidmap.txt."
+    print "saved so-headers.txt."
 
 
 def writefile(filename, fcontent, mode, isprint):
@@ -82,23 +83,35 @@ def main():
     except Exception as e:
         print "No so.txt file ..."
 
+    # remove file_id_list
+    try:
+        os.remove("so-headers.txt")
+    except Exception as e:
+        print "couldn't remove so-headers.txt file."
+
     # get list of Java files
     javafiles = get_file_list(sys.argv[1], "*.java");
+
+    print "files: ", len(javafiles)
     # start method extraction
     for index, jfile in enumerate(javafiles):
-        sys.stdout.write(str(index) + ": " + jfile)
-        sys.stdout.flush()
-        methods = get_methods(jfile)
-        print ":", len(methods), "methods."
-        for i, method in enumerate(methods):
-            method_parts = method.split("@@UCL@@")
-            writefile("so.txt", "===@@@UCI===\n", "a", False)
-            id = createFileId(jfile + "," + method_parts[0].strip())
-            writefile("so.txt", str(id) + "\n", "a", False)
-            writefile("so.txt", str(i) + "\n", "a", False)
-            writefile("so.txt", method_parts[1].strip() + "\n", "a", False)
-
-    saveFileId()
+        try:
+            sys.stdout.write(str(index) + ": " + jfile)
+            sys.stdout.flush()
+            methods = get_methods(jfile)
+            print ":", len(methods), "methods."
+            for i, method in enumerate(methods):
+                # print method
+                method_parts = method.split("@@UCL@@")
+                writefile("so.txt", "===@@@UCI===\n", "a", False)
[…]

### 2017-08-12 SCCTokenizer/tokenizer_stackoverflow.py

@@ -16,12 +16,13 @@ comment_inline_pattern = comment_inline + '.*?$'
 comment_open_tag = "/\\*"
 comment_close_tag = "\\*/"
 comment_open_close_pattern = comment_open_tag + '.*?' + comment_close_tag
-proj_id_flag = "2"
+# proj_id_flag = "2"
 
 FILE_blocks_stats_file = 'so-stats.stats'
 FILE_blocks_tokens_file = 'so-tokens.tokens'
 
 block_count = 0
+
 
 def tokenize_python_blocks(block_string):
     # This function will return ((blocks_tokens,blocks_stats), block_parsing_times)
@@ -38,7 +39,7 @@ def tokenize_python_blocks(block_string):
 
     h_time = dt.datetime.now()
     m = hashlib.md5()
-    m.update(block_string.encode("utf-8"))
+    # m.update(block_string.encode("utf-8"))
     block_hash = m.hexdigest()
     hash_time = (dt.datetime.now() - h_time).microseconds
     
@@ -101,7 +102,8 @@ def tokenize_python_blocks(block_string):
 
     return ((block_tokens, block_stats), [se_time, token_time, hash_time, re_time])
 
-def process_contents(proj_id, method_id, block_string, FILE_tokens_file, FILE_stats_file, logging):
+
+def process_contents(post_id, method_id, block_string, FILE_tokens_file, FILE_stats_file, logging):
 	
     (block_data, block_parsing_times) = tokenize_python_blocks(block_string)
     ww_time = dt.datetime.now()
@@ -114,13 +116,14 @@ def process_contents(proj_id, method_id, block_string, FILE_tokens_file, FILE_st
     (tokens_count_total,tokens_count_unique,token_hash,tokens) = blocks_tokens
 
     # Adjust the blocks stats written to the files, file stats start with a letter 'b'
-    FILE_stats_file.write(','.join([proj_id, block_id, '\"'+block_hash+'\"', method_id, str(block_LOC)]) + '\n')
-    FILE_tokens_file.write(','.join([proj_id, block_id, str(tokens_count_total),str(tokens_count_unique), method_id, token_hash+tokens]) + '\n')
+    # FILE_stats_file.write(','.join([post_id, block_id, '\"' + block_hash + '\"', method_id, str(block_LOC)]) + '\n')
[…]

### 2017-08-12 scripts/cp_stackoverflow.sh

@@ -1,0 +1,488 @@
+cp stackoverflow_orig/22315734_0.java temp/
+cp stackoverflow_orig/16928749_0.java temp/
+cp stackoverflow_orig/22315734_0.java temp/
+cp stackoverflow_orig/2513183_0.java temp/
+cp stackoverflow_orig/2513183_0.java temp/
+cp stackoverflow_orig/2513183_0.java temp/
+cp stackoverflow_orig/2513183_0.java temp/
+cp stackoverflow_orig/6722760_1.java temp/
+cp stackoverflow_orig/6722760_1.java temp/
+cp stackoverflow_orig/6722760_1.java temp/
+cp stackoverflow_orig/6722760_1.java temp/
+cp stackoverflow_orig/6722760_1.java temp/
+cp stackoverflow_orig/18833798_0.java temp/
+cp stackoverflow_orig/5708120_0.java temp/
+cp stackoverflow_orig/5708120_0.java temp/
+cp stackoverflow_orig/5708120_0.java temp/
+cp stackoverflow_orig/5708120_0.java temp/
+cp stackoverflow_orig/10274267_0.java temp/
+cp stackoverflow_orig/10289462_0.java temp/
+cp stackoverflow_orig/10737817_0.java temp/
+cp stackoverflow_orig/10774468_0.java temp/
+cp stackoverflow_orig/10774468_0.java temp/
+cp stackoverflow_orig/10777586_0.java temp/
+cp stackoverflow_orig/10924700_0.java temp/
+cp stackoverflow_orig/11187462_0.java temp/
+cp stackoverflow_orig/11861598_0.java temp/
+cp stackoverflow_orig/12106623_0.java temp/
+cp stackoverflow_orig/12593810_0.java temp/
+cp stackoverflow_orig/12936580_0.java temp/
+cp stackoverflow_orig/14019840_0.java temp/
+cp stackoverflow_orig/14330686_0.java temp/
+cp stackoverflow_orig/14582029_0.java temp/
+cp stackoverflow_orig/14845581_1.java temp/
+cp stackoverflow_orig/14940863_0.java temp/
+cp stackoverflow_orig/15168494_0.java temp/
+cp stackoverflow_orig/15633427_0.java temp/
+cp stackoverflow_orig/15889119_0.java temp/
+cp stackoverflow_orig/16058183_0.java temp/
+cp stackoverflow_orig/16180910_0.java temp/
[…]

### 2017-08-12 scripts/extract.sh

@@ -1,0 +1,22 @@
+while read line           
+do
+	foldername=`echo $line | cut -d'.' -f1`
+	echo $foldername 
+	mkdir $foldername
+        cp ../compressed_src/$line $foldername 
+	cd $foldername
+
+        if [ ${line: -4} == ".jar" ]
+        then
+            mv $line `echo $line | sed 's/\(.*\.\)jar/\1zip/'`
+            unzip $line
+        elif [ ${line: -4} == ".zip" ]
+            then
+            unzip $line 
+        elif [ ${line: -3} == ".gz" ]
+            then
+            tar -zxvf $line
+        fi
+	rm *.zip *.jar *.gz	
+  	cd ..      
+done < $1

### 2017-08-12 scripts/format.sh

@@ -1,0 +1,1 @@
+for i in ./* ; do cd $i ; ../../scripts/format.sh ; cd .. ; done

### 2017-08-12 scripts/format_all.sh

@@ -1,0 +1,19 @@
+#!/bin/sh
+
+for i in *; do
+    cd $i
+    for j in `find . -type f -name *.java`; do
+	echo "*** ASTYLE $i/$j"
+	/scratch0/NOT_BACKED_UP/crest/gbianco/tools/astyle --style=java -p -P -d -H -U -xd -j "$j"
+	mv "$j" "$j~"
+	echo "*** UNCOMMENT $j"
+        /scratch0/NOT_BACKED_UP/crest/gbianco/tools/uncomment-java < "$j~"| sed -e '/^[ \t\r]*$/d' > "$j"
+	if [ -f $j ]; then
+	    rm "$j~" 
+	fi
+	if [ -f "$j.orig" ]; then
+	    rm "$j.orig"
+	fi	
+    done
+    cd ..
+done

### 2017-08-12 scripts/format_project.sh

@@ -1,0 +1,6 @@
+while read line           
+do
+	cd $line
+	../../scripts/format_all.sh
+  	cd ..      
+done < $1

### 2017-08-12 scripts/gcf.sh

@@ -1,0 +1,9 @@
+DIR=$1
+TOOL=$2
+PREFIX=$3
+GCF=../tools/gcfFileConverter-0.4.jar
+
+for i in $DIR/*.txt; do
+	echo $i
+	java -jar $GCF $TOOL $PREFIX $i
+done   

### 2017-08-12 scripts/iclones.sh

@@ -1,0 +1,18 @@
+FILES=/scratch0/NOT_BACKED_UP/crest/gbianco/QualitasCorpus-20130901r/projects
+RAM_PROJECT_FOLDER=/dev/shm/cragkhit
+SRC_ICLONES_FOLDER=/dev/shm/cragkhit/src
+
+while read i; do    
+    printf "*** Processing: $FILES/$i ***\n"
+    if [ ! -d $SRC_ICLONES_FOLDER ]; then
+        mkdir $SRC_ICLONES_FOLDER
+    fi
+    cp -r $FILES/$i $SRC_ICLONES_FOLDER/
+    for compressed in $SRC_ICLONES_FOLDER/*
+    do
+        BASENAME="$(basename $compressed)"
+        java -jar /scratch0/NOT_BACKED_UP/crest/gbianco/tools/iclones-0.2/jar/iclones.jar -minblock 10 -minclone 50 -input "/dev/shm/cragkhit" > "${RAM_PROJECT_FOLDER}"/iclones_results/"${BASENAME}".txt
+    done
+    rm -rf $SRC_ICLONES_FOLDER
+    printf "Done\n"
+done <$1

### 2017-08-12 scripts/license_check.sh

@@ -1,0 +1,1 @@
+for i in `cat $1`; do ./tools/ninka-1.3/ninka.pl $i; done

### 2017-08-12 scripts/nicad.sh

@@ -1,0 +1,18 @@
+FILES=/scratch0/NOT_BACKED_UP/crest/gbianco/QualitasCorpus-20130901r/projects
+RAM_PROJECT_FOLDER=/dev/shm/cragkhit
+SRC_NICAD_FOLDER=/dev/shm/cragkhit/src
+
+while read i; do    
+    printf "*** Processing: $FILES/$i ***\n"
+    if [ ! -d $SRC_NICAD_FOLDER ]; then
+        mkdir $SRC_NICAD_FOLDER
+    fi
+    cp -r $FILES/$i $SRC_NICAD_FOLDER/
+    for compressed in $SRC_NICAD_FOLDER/*
+    do
+        BASENAME="$(basename $compressed)"
+        java -jar /scratch0/NOT_BACKED_UP/crest/gbianco/tools/iclones-0.2/jar/iclones.jar -minblock 10 -minclone 50 -input "/dev/shm/cragkhit" > "${RAM_PROJECT_FOLDER}"/iclones_results/"${BASENAME}".txt
+    done
+    rm -rf $SRC_NICAD_FOLDER
+    printf "Done\n"
+done <$1

### 2017-08-12 scripts/simian.sh

@@ -1,0 +1,28 @@
+FILES=$2
+RAM_PROJECT_FOLDER=/dev/shm/cragkhit
+SRC_SIMIAN_FOLDER=/dev/shm/cragkhit/src
+SETTING=$3
+
+echo "Reading from $1, analysing $2 using settings $3"
+
+while read i; do    
+    printf "*** Processing: $FILES/$i ***\n"
+    if [ ! -d $SRC_SIMIAN_FOLDER ]; then
+        mkdir $SRC_SIMIAN_FOLDER
+    fi
+    if [ ! -d ${RAM_PROJECT_FOLDER}/simian_results ]; then
+        mkdir ${RAM_PROJECT_FOLDER}/simian_results
+    fi
+    cp -r $FILES/$i $SRC_SIMIAN_FOLDER/
+    for compressed in $SRC_SIMIAN_FOLDER/*
+    do
+        BASENAME="$(basename $compressed)"
+	if [ $3 = "default" ]; then
+        	java -jar -Xmx1024m /home/cragkhit/Documents/CloneOverflow/tools/simian/bin/simian-2.3.35.jar "/dev/shm/cragkhit/**/*.java" > "${RAM_PROJECT_FOLDER}"/simian_results/"${BASENAME}".txt
+        elif [ $3 = "fse13" ]; then
+		java -jar -Xmx1024m /home/cragkhit/Documents/CloneOverflow/tools/simian/bin/simian-2.3.35.jar -threshold=5 -ignoreCurlyBraces+ -ignoreIdentifiers+ -ignoreIdentifierCase+ -ignoreStrings+ -ignoreCharacters+ -ignoreSubtypeNames+ -balanceSquareBrackets+ "/dev/shm/cragkhit/**/*.java" > "${RAM_PROJECT_FOLDER}"/simian_results/"${BASENAME}".txt
+	fi
+    done
+    rm -rf $SRC_SIMIAN_FOLDER
+    printf "Done\n"
+done <$1

### 2017-08-12 SCCTokenizer/file_concatenator.py
A few changes:
- Renamed Ethical Waiver form folder
- Fixed the way of generating tokens.

@@ -5,6 +5,7 @@ import datetime as dt
 
 
 file_id_list = []
+starting_id = 0
 
 
 def get_methods(file):
@@ -36,9 +37,9 @@ def get_file_list(home_dir, filter):
 
 def createFileId(file):
     global file_id_list
-
+    global starting_id
     file_id_list.append(file)
-    fileid = file_id_list.index(file)
+    fileid = file_id_list.index(file) + starting_id
     writefile("so-headers.txt", str(fileid) + "," + file + "\n", "a", False)
 
     return fileid
@@ -92,6 +93,11 @@ def main():
 
     # get list of Java files
     javafiles = get_file_list(sys.argv[1], "*.java");
+
+    # get the starting id, if not, start at 0
+    global starting_id
+    if len(sys.argv) == 3:
+        starting_id = int(sys.argv[2])
 
     print "files: ", len(javafiles)
     

### 2017-08-12 SCCTokenizer/tokenizer_stackoverflow.py

@@ -117,7 +117,9 @@ def process_contents(post_id, method_id, block_string, FILE_tokens_file, FILE_st
 
     # Adjust the blocks stats written to the files, file stats start with a letter 'b'
     # FILE_stats_file.write(','.join([post_id, block_id, '\"' + block_hash + '\"', method_id, str(block_LOC)]) + '\n')
-    FILE_tokens_file.write(','.join([post_id, block_id, str(tokens_count_total), str(tokens_count_unique), method_id, token_hash + tokens]) + '\n')
+    # FILE_tokens_file.write(','.join([post_id, block_id, str(tokens_count_total), str(tokens_count_unique), method_id, token_hash + tokens]) + '\n')
+    FILE_tokens_file.write(','.join(
+        [post_id, method_id + tokens]) + '\n')
     w_time = (dt.datetime.now() - ww_time).microseconds
 
     logging.info('Successfully ran process_contents ' + post_id)
@@ -147,6 +149,8 @@ def process_so_file(FILE_tokens_file, FILE_stats_file):
                 except Exception as e:
                     logging.warning("%s cannot be pasred by so text parser" % item)
                     logging.warning(e)
+
+
 def main():
 
     # logging setting    

### 2017-08-13 cloverflow-tse/cloverflow.tex
Added TSE-formatted paper.

--- 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
@@
-\documentclass[sigconf,review, anonymous]{acmart}
+\documentclass[10pt,journal,compsoc]{IEEEtran}
+
+% *** CITATION PACKAGES ***
+%
+\ifCLASSOPTIONcompsoc
+  % IEEE Computer Society needs nocompress option
+  % requires cite.sty v4.0 or later (November 2003)
+  \usepackage[nocompress]{cite}
+\else
+  % normal IEEE
+  \usepackage{cite}
+\fi
 
@@
 \usepackage[T1]{fontenc}
+\usepackage{url}
 \usepackage{graphicx}
@@
 \usepackage[normalem]{ulem}
+\usepackage{amsmath}
+\usepackage{amsfonts}
 
@@
 
-% Copyright
-%\setcopyright{none}
-%\setcopyright{acmcopyright}
-%\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-\setcopyright{rightsretained}
-%\setcopyright{usgov}
-%\setcopyright{usgovmixed}
-%\setcopyright{cagov}
-%\setcopyright{cagovmixed}
-
-% DOI
-\acmDOI{10.475/123_4}
-
-% ISBN
-\acmISBN{123-4567-24-567/08/06}
-
-%Conference
-\acmConference[ESEC/FSE 2017]{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--8 September, 2017}{Paderborn, Germany}
-\acmYear{2017}
-\copyrightyear{2017}
-
-\acmPrice{15.00}
-
-%\overfullrule1ex
+% correct bad hyphenation here
+%\hyphenation{op-tical net-works semi-conduc-tor}
 
 \begin{document}
+
 \title{Outdated and License-Violating Code on Stack Overflow}
-	%\titlenote{Produces the permission block, and
-	%  copyright information}
-	%\subtitle{Extended Abstract}
-	%\subtitlenote{The full version of the author's guide is available as
-	%  \texttt{acmart.pdf} document}
-
-\author{Chaiyong Ragkhitwetsagul,~Matheus Paixao,~Jens Krinke}
-\affiliation{%
-	\institution{CREST, University College London}
-	%  \streetaddress{P.O. Box 1212}
-	\city{London, UK} 
-	%  \state{Ohio} 
-	%  \postcode{43017-6221}
-}
-%\email{{ucabagk,matheus.paixao.14,j.krinke}@ucl.ac.uk}
-
-\author{Giuseppe Bianco,~Rocco Oliveto}
-\affiliation{%
-	\institution{University of Molise}
-	%  \streetaddress{P.O. Box 1212}
-	\city{Pesche (IS), Italy} 
-	%  \state{Ohio} 
-	%  \postcode{43017-6221}
-}
-
+
+\author{Chaiyong Ragkhitwetsagul,~Matheus Paixao,~Jens Krinke,~Giuseppe Bianco,~Rocco Oliveto}
+
+% The paper headers
+\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
+{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+% The only time the second header will appear is for the odd numbered pages
+% after the title page when using the twoside option.
+% 
+% *** Note that you probably will NOT want to include the author's ***
+% *** name in the headers of peer review papers.                   ***
+% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
+% you desire.
+
+% The publisher's ID mark at the bottom of the page is less important with
+% Computer Society journal papers as those publications place the marks
+% outside of the main text columns and, therefore, unlike regular IEEE
+% journals, the available text space is not reduced by their presence.
+% If you want to put a publisher's ID mark on the page you can do it like
+% this:
+%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
+% or like this to get the Computer Society new two part style.
+%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
+%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
+% Remember, if you use this you must call \IEEEpubidadjcol in the second
+% column for its text to clear the IEEEpubid mark (Computer Society jorunal
+% papers don't need this extra clearance.)
+
+% for Computer Society papers, we must declare the abstract and index terms
+% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
+% command as these need to go into the title area created by \maketitle.
+% As a general rule, do not put math, special symbols or citations
+% in the abstract or keywords.
+\IEEEtitleabstractindextext{%
 \begin{abstract}
@@
 
-\begin{CCSXML}
-	<ccs2012>
-	<concept>
-	<concept_id>10011007.10011006.10011072</concept_id>
-	<concept_desc>Software and its engineering~Software libraries and repositories</concept_desc>
-	<concept_significance>500</concept_significance>
-	</concept>
-	<concept>
-	<concept_id>10011007.10011074.10011111.10011113</concept_id>
-	<concept_desc>Software and its engineering~Software evolution</concept_desc>
-	<concept_significance>300</concept_significance>
-	</concept>
-	</ccs2012>
-\end{CCSXML}
-
-\ccsdesc[500]{Software and its engineering~Software libraries and repositories}
-\ccsdesc[300]{Software and its engineering~Software evolution}
-
-% We no longer use \terms command
-%\terms{Theory}
-
-\keywords{Clone Detection, Stack Overflow, Outdated Code, Software Licensing}
-
+% Note that keywords are not normally used for peerreview papers.
+\begin{IEEEkeywords}
+Clone Detection, Stack Overflow, Outdated Code, Software Licensing
+\end{IEEEkeywords}}
+
+% make the title area
 \maketitle
 
-\section{Introduction}
+% To allow for easy dual compilation without having to reenter the
+% abstract/keywords data, the \IEEEtitleabstractindextext text will
+% not be used in maketitle, but will appear (i.e., to be "transported")
+% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
+% or transmag modes are not selected <OR> if conference mode is selected 
+% - because all conference papers position the abstract like regular
+% papers do.
+\IEEEdisplaynontitleabstractindextext
+% \IEEEdisplaynontitleabstractindextext has no effect when using
+% compsoc or transmag under a non-conference mode.
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
+
+\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
 
@@
 Android documentation~\cite{Acar2016}.
-
-%\FIXME{Find the right location for this-->} Additionally, outdated and vulnerable third-party libraries from well-known open source projects are cloned into in a large number of open source systems~\cite{Xia2014}.
 
@@
 research questions:
-\begin{description}
-\item[RQ1 (Online code clones):] \textit{To what extent is source
+\begin{itemize}
+	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
 		code cloned between Stack Overflow and open source projects?} We
@@
 	problem. 
-\item[RQ2 (Patterns of online code clones):] \textit{Why do online
+	\item \textbf{RQ2 (Patterns of online code clones): }\textit{Why do online
 		code clones occur?} We categorised online clones into seven
 	categories allowing insights to why online code clones are created.
-\item[RQ3 (Outdated online code clones):] \textit{Are
+	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
 		online code clones up-to-date compared to their counterparts in the
@@
 	them. 
-\item[RQ4 (Software licensing violation):] \textit{Do
+	\item \textbf{RQ4 (Software licensing violation): }\textit{Do
 		licensing conflicts occur between Stack Overflow clones and their
@@
 	can cause software developers to violate licenses.
-\end{description}
+	\item \textbf{RQ5 (Developers' awareness): }\textit{Do Stack Overflow
+		users aware of the outdated code and licensing problem when
+		they answer a question on Stack Overflow?} 
+	We surveyed 600 high reputation Stack Overflow users to study their
+	awareness of the issues.
+\end{itemize}
 
@@
 	\begin{tabular}{lrrr}
-    \hline 
+		\toprule
 		Dataset & No. of files & SLOC & Median \\
-    \hline
+		\midrule
 		Stack Overflow & 144,064 & 2,332,940 & 10 \\ 
-    %\hline 
 		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
-    \hline 
+		\bottomrule
 	\end{tabular} 
@@
 
-\textbf{Simian} is a text-based clone detector that locates clones at
-line-level granularity and has been used extensively in several clone
+\textbf{Simian} is a text-based clone detector that locates clones at line-level
+granularity and has been used extensively in several clone
 studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
-  Krinke2010}.
-% It is a command-line tool which enables us to automate the
-% detection. 
-Furthermore, it offers normalisation of variable names and literals
-(strings and numbers) which enables Simian to detect literal clones
-(type-1) and parameterised clones (type-2). \textbf{NiCad} is also a
-text-based clone detector which detects clones at either method- or
-block-level granularity. It can detect clones of type-1, -2 up to
-type-3 (clones with added and removed statements) and has
-also been used in several empirical clone studies~\cite{Roy2008,
-  Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011,
+	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
+(strings and numbers) which enables Simian to detect literal clones (type-1) and
+parameterised clones (type-2). \textbf{NiCad} is also a text-based clone
+detector which detects clones at either method- or block-level granularity. It
+can detect clones of type-1, -2 up to type-3 (clones with added and removed
+statements) and has also been used in several empirical clone
+studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011,
 	Sajnani2016}. NiCad utilises TXL~\cite{Cordy2006} for parsing and
-pretty-printing source code and provides code normalisation by
-variable renaming and abstraction. We use a variant of NiCad called
-\textit{nicadcross}. It offers the same functionalities as the
-original NiCad but is specialised for detecting code clones between
-two systems. 
-% NiCad is also a command-line tool which makes it suitable for
-% automation.
-
-%We processed two datasets, 144,064 Java code snippets from accepted answers on Stack
-%Overflow and 111 open source projects from the Qualitas corpus. 
-%The Java code snippets were extracted from Stack Overflow posts. 
+pretty-printing source code and provides code normalisation by variable renaming
+and abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers
+the same functionalities as the original NiCad but is specialised for detecting
+code clones between two systems.
+
 We prepared the Java code in both datasets by removing comments and
-pretty-printing to increase the clone detection accuracy. Then, we
-deployed the two detectors to locate clones between the two
-datasets.  For each Qualitas project, we ran the tools on the
-project's code and the entire Stack Overflow data.
-% For scalability reasons, we partitioned the input and ran the tools
-% multiple times. Each run was composed of the entire Stack Overflow
-% data and a single Qualitas project. We repeated the process until we
-% covered all 111 projects.
-% We then converted the clone reports to the General
-% Clone Format (GCF)~\cite{Wang2013} and combined the 111 reports into a
-% single GCF file.  
-Simian did not provide an option to detect cross-project
-clones. % between two locations.
-Hence the Simian clone report was filtered to contain only clone pairs
-between Stack Overflow and Qualitas projects, removing all clone pairs
-within either Stack Overflow or within Qualitas.
-% NiCad provides an option to detect clones
-% from two locations so no filtering was needed.
+pretty-printing to increase the clone detection accuracy. Then, we deployed the
+two detectors to locate clones between the two datasets.  For each Qualitas
+project, we ran the tools on the project's code and the entire Stack Overflow
+data. Simian did not provide an option to detect cross-project clones. Hence the
+Simian clone report was filtered to contain only clone pairs between Stack
+Overflow and Qualitas projects, removing all clone pairs within either Stack
+Overflow or within Qualitas.
 
@@
 	\label{t:param_tuning}
-  %	\resizebox{\columnwidth}{!}{%
+%		\resizebox{\columnwidth}{!}{
 	\small
-  \begin{tabular}{p{0.7cm}|p{2.4cm}p{3.8cm}}
-    \hline 
+	\begin{tabular}{p{0.8cm}|p{2.5cm}p{3.8cm}}
+		\toprule
 		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
-    \hline
+		\midrule
 		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
-    \hline 
+		\bottomrule
 		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming, literal abstraction \\
@@
 	\end{tabular} %
-%}
+%	}
 \end{table}
@@
 	\begin{tabular}{l|r|r|r|r}
-		\hline
+		\toprule
 		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
-		\hline
+		\midrule
 		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
@@
 		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
-		\hline
+		\bottomrule
 	\end{tabular} %
@@
 of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
-clone pairs is 32,316, 0.1\textperthousand~of all reported clone
+clone pairs is 32,316, 0.1\%~of all reported clone
 pairs.  Agreed clone pairs are clone pairs that pass Bellon's
@@
 	\begin{tabular}{l|r|r|r|r|r}
-    \hline
+		\toprule
 		Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
-    \hline
+		\midrule
 		\textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
 		\textit{ok} & 12,063 & 993 & 79 & 20,021 & 32,316 \\
-    \hline
+		\bottomrule
 	\end{tabular} %
@@
 	\begin{tabular}{l|r|c|c|r}
-		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cline{3-4}
+		\toprule
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cmidrule{3-4}
 		& & \textit{L} & \textit{S} & \\ 
-		\hline 
+		\midrule 
 		\multirow{1}{*}{$S_D$} & 55,274 & \checkmark & & 17,801 \\
 		\multirow{1}{*}{$N_D$} & 620,680 & \checkmark & \checkmark & 83 \\ 
-		\hline
+		\bottomrule
 		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
@@
 	%\resizebox{\columnwidth}{!}{%
-        \small\vspace{-1ex}
 	\begin{tabular}{c@{~~}p{7.35cm}}
-			\hline 
+		\toprule
 		Patt. & Description \\ 
-			\hline 
+		\midrule
 		QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\
@@
 		AC & Accidental similarity, false clones \\ 
-			\hline 
+		\bottomrule 
 	\end{tabular}  %
@@
 	\centering
-	\includegraphics[width=0.8\linewidth]{classification_process}\vspace{-1ex}
+	\includegraphics[width=\linewidth]{classification_process}\vspace{-1ex}
 	\caption{Online code clone classification process}
@@
 The classification of the filtered online clone pairs followed the steps
-depicted in \Cref{fig:classification_process}. First, we look at a
-pair of clone fragments to see their similarity. If they are
-accidentally similar clones after code normalisation or false positive
-clones from the clone detection tools, we classify the pair into
-\textbf{AC}. If the two fragments are boiler-plate code, the pair is
-classified into \textbf{BP}. If they implement the same interface or
-inherited the same class and share similar overriding methods, the
-pair is classified into \textbf{IN}. If the pair is not \textbf{BP},
-\textbf{IN}, or \textbf{AC}, we start a detailed investigation. We
-check the corresponding Stack Overflow post, read through it carefully
-and look for any evidence mentioning code copying. If evidence of
-copying has been found from a Qualitas project, the pair is classified
-in \textbf{QS}. In several occasions, we used extra information such
-as questions' contents, name of posters, and tags to gain a better
-understanding. On the other hand, if the source code from the Qualitas
-project mentions copying from Stack Overflow, the pair is classified
-into \textbf{SQ}. If there is evidence of copying from an external
-source instead of a Qualitas projects, the pair is classified into
-\textbf{EX}.
-Lastly, if there is no evidence of copying in any
-direction but the clone fragments are highly similar, we classify them
-into \textbf{UD}.
-
-\subsection{Phase 5: Outdated Clones}
-Outdated code occurs when a piece of code has been copied from its
-origin to another location and later the original has been
-updated~\cite{Xia2014}. Usually code clone detection is used to locate
-clone instances and update them to match with the
-originals~\cite{Bellon2007}. However, online code clones are more
-difficult to detect than in regular software projects due to its large
-search space and a mix of natural and programming languages combined
-in the same post.
-%Moreover, Stack Overflow is not a software.
-There is no test suite to run and check whether the validity of the code snippets.
-To the best of our knowledge, this work is the first to address the problem of outdated code on Stack Overflow.
-
-To search for outdated online code clones, we focused on the
-\textbf{QS} clone pairs that were cloned from Qualitas to Stack
-Overflow and compared them with their latest versions. We downloaded
-the latest version of the Qualitas projects from their repositories on
-September 26, 2016. For each \textbf{QS} online clone pair, we used the
-clone from Qualitas as a proxy. We searched for its latest version by
-the file name and located the cloned region in the file based on the
-method name.
-%For Simian clones, where clones may span across several methods, we scanned upwards until we find a method name ahead of the clone region. 
-We then compared the Stack Overflow snippet to its latest version
-line-by-line to find if any change has been made to the source
-code. We also made sure that the changes did not come from the
-modifications made to the Stack Overflow snippets by the posters but
-from the updates in the projects themselves. When we found
-inconsistent lines between the two versions, we used
-{\small\texttt{git blame}} to see who modified those lines of code and
-the timestamps.
-
-\subsection{Phase 6: Licensing Analysis}
-Software licensing plays an important role in software
-development. Violation of software licenses impacts software delivery
-and also leads to legal issues~\cite{Sprigman2015}.
-%It is an emerging area that software engineering research community is paying attention to. For example, 
-One can run into a licensing issue if one integrates third-party
-source code into their software without checking. A study by An et
-al.~\cite{An2017} reports 1,279 cases of potential license violations
-between 399 Android apps and Stack Overflow code
-snippets.
-
-We analysed licensing conflicts of the online clones in the
-\textbf{QS}, \textbf{EX}, and \textbf{UD} set. The
-licenses were extracted by \emph{Ninka}, an automatic license
-identification tool~\cite{German2010}. Since Ninka works at file
-level, we report the findings based on Stack Overflow snippets and
-Qualitas source files instead of the clone pairs (duplicates were
-ignored). For the ones that could not be automatically identified by
-Ninka and have been reported as {\small\texttt{SeeFile}} or
-{\small\texttt{Unknown}}, we looked at them manually to see if any
-license can be found.
-
-% The table shows the license mapping of Stack Overflow snippets and
-% Qualitas source code. The results are reported separately for the
-% \textbf{QS}, \textbf{EX}, and \textbf{UD} set.
-
-%\subsection{Analysis Methods}
-
-% We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
-% to answer our four research questions. 
-% To answer RQ1, we rely on the number of manually validated true positive online clone pairs
-% in phase 3. We use the results of the manual classification using the
-% patterns of online code cloning to answer RQ2. 
-% For RQ3, we looked at the true positive clone pairs that are classified 
-% as cloned from Qualitas to Stack Overflow and
-% checked if they have been changed since they have been
-% cloned. Similarly, for RQ4, we looked at the license of each clone in the pattern 
-% QS, EX, UD and checked for a possibility of a licensing violation.
-
-%\subsection{Manual Investigation}
-%We did not have an oracle of clones
-%between the two data sets so we rely on a manual investigation to
-%validate the reported clone candidates. However, the large amount of
-%generated clone pairs hindered us from looking at all of them.
-%A random sampling of clones could have been employed, however, the 
-%risk of returning false positives non-meaningful clones is increased.
-%Instead of extracting a random sample, we selected clone pair
-%candidates by relying on \emph{agreement} of clone detectors. If a
-%clone pair was reported by multiple tools, we had a higher
-%confidence that it was a real clone pair. To achieve this, clone pairs
-%from the two clone detectors were pair-wise matched to find agreements
-%using Bellon's clone overlapping criteria~\cite{Bellon2007}. This step
-%generated 
-%\textbf{agreed clone pairs}. They were pairs with high confidence to be true clones since
-%they obtained agreement from both tools. Then, pairs reported by
-%Simian and NiCad that did not find agreement were categorised as
-%\textbf{disagreed clone pairs}. The disagreed clone pairs were clones
-%with less confidence than the agreed ones. 
-%Finally, agreed and
-%disagreed clone pairs have been looked at manually by two of the
-%authors.
-
-%In the manual inspection process, we classified clones into seven
-%categories according to information observed from code comments and
-%text in the Stack Overflow answer. This process took approximately a
-%month until we successfully investigated 3,632 clone pairs. Clone
-%pairs that were classified as false clones, boiler-plate code, or
-%IDE-generated are not very interesting and were ignore in the analysis
-%of outdated code and licensing violation. We compared the licensing
-%information of the 668 remaining clone pairs for possibilities of software
-%licensing violations. Moreover, we looked at the history starting at
-%the date of the answers to today from its git repository. With this
-%method, we discovered \textbf{outdated code}, i.e.~code that changes
-%were made to them after they have been copied to Stack
-%Overflow. 
-%hence resulting in outdated clones on Stack Overflow.
+depicted in \Cref{fig:classification_process}. First, we look at a pair of clone
+fragments to see their similarity. If they are accidentally similar clones after
+code normalisation or false positive clones from the clone detection tools, we
+classify the pair into \textbf{AC}. If the two fragments are boiler-plate code,
+the pair is classified into \textbf{BP}. If they implement the same interface or
+inherited the same class and share similar overriding methods, the pair is
+classified into \textbf{IN}. If the pair is not \textbf{BP}, \textbf{IN}, or
+\textbf{AC}, we start a detailed investigation. We check the corresponding Stack
+Overflow post, read through it carefully and look for any evidence mentioning
+code copying. If evidence of copying has been found from a Qualitas project, the
+pair is classified in \textbf{QS}. In several occasions, we used extra
+information such as questions' contents, name of posters, and tags to gain a
+better understanding. On the other hand, if the source code from the Qualitas
+project mentions copying from Stack Overflow, the pair is classified into
+\textbf{SQ}. If there is evidence of copying from an external source instead of
+a Qualitas projects, the pair is classified into \textbf{EX}. Lastly, if there
+is no evidence of copying in any direction but the clone fragments are highly
+similar, we classify them into \textbf{UD}.
+
+\subsection{Phase 5: Outdated Clones} Outdated code occurs when a piece of code
+has been copied from its origin to another location and later the original has
+been updated~\cite{Xia2014}. Usually code clone detection is used to locate
+clone instances and update them to match with the originals~\cite{Bellon2007}.
+However, online code clones are more difficult to detect than in regular
+software projects due to its large search space and a mix of natural and
+programming languages combined in the same post.
+
+To search for outdated online code clones, we focused on the \textbf{QS} clone
+pairs that were cloned from Qualitas to Stack Overflow and compared them with
+their latest versions. We downloaded the latest version of the Qualitas projects
+from their repositories on September 26, 2016. For each \textbf{QS} online clone
+pair, we used the clone from Qualitas as a proxy. We searched for its latest
+version by the file name and located the cloned region in the file based on the
+method name. We then compared the Stack Overflow snippet to its latest version
+line-by-line to find if any change has been made to the source code. We also
+made sure that the changes did not come from the modifications made to the Stack
+Overflow snippets by the posters but from the updates in the projects
+themselves. When we found inconsistent lines between the two versions, we used
+{\small\texttt{git blame}} to see who modified those lines of code and the
+timestamps.
+
+\subsection{Phase 6: Licensing Analysis} Software licensing plays an important
+role in software development. Violation of software licenses impacts software
+delivery and also leads to legal issues~\cite{Sprigman2015}. 
+One can run into a licensing issue if one integrates third-party source code
+into their software without checking. A study by An et al.~\cite{An2017} reports
+1,279 cases of potential license violations between 399 Android apps and Stack
+Overflow code snippets.
+
+We analysed licensing conflicts of the online clones in the \textbf{QS},
+\textbf{EX}, and \textbf{UD} set. The licenses were extracted by \emph{Ninka},
+an automatic license identification tool~\cite{German2010}. Since Ninka works at
+file level, we report the findings based on Stack Overflow snippets and Qualitas
+source files instead of the clone pairs (duplicates were ignored). For the ones
+that could not be automatically identified by Ninka and have been reported as
+{\small\texttt{SeeFile}} or {\small\texttt{Unknown}}, we looked at them manually
+to see if any license can be found.
+
+\subsection{Stack Overflow Developers' Survey} We support our findings of
+outdated and license-violating code snippets on Stack Overflow by asking Stack
+Overflow users to take an online survey. The survey was used for assessing awareness of
+the developers on the two issues of outdated code and licensing-violating code
+snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
+Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
+anonymous and the participants could decide to leave at any time. It contained
+11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
+open-ended question for additional comments. The first two questions were
+mandatory while the other 9 questions were shown to the participants based on
+their previous answers. The full survey can be found in our \FIXME{technical
+	report/website?} ~\footnote{Stack Overflow Answerers' Survey:
+	\url{http://www.cs.ucl.ac.uk/staff/C.Ragkhitwetsagul/files/so_survey.pdf}}.
+
+\begin{table}
+	\centering
+	\caption{The two groups of Stack Overflow users invited to take the survey}
+	\label{tab:survey_target}
+	\begin{tabular}{lrrrr}
+		\toprule
+		Target group & Reputation & Sent emails & Answers & Rate \\
+		\midrule
+		Group 1 & 963,731--7,674 & 300 & 112 & 37\% \\
+		Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We selected the participants for our survey based on the users' reputations. On
+Stack Overflow, a user's reputation reflects how much the community trust the
+user. A user earns reputations when he or she receives up votes for good
+questions and useful answers. Accepted answers receive more reputation score
+than questions, and regular answers\footnote{Stack Overflow
+	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
+Overflow reputation is an indicator of user's skills and their involvement in
+asking and answering questions on the site. We call Stack Overflow users who
+have high reputations ``Stack Overflow answerers.''
+
+The participants were invited to take the survey via email addresses on their
+public Stack Overflow and GitHub profiles. We selected the answerers who had highly
+ranked all-time reputations\footnote{Stack Overflow Users (data as of 25 July
+	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}} and
+separated them into two groups (see \Cref{tab:survey_target}) so that we can
+compare the results or observe similar patterns between them. 
+The first group had reputation from 963,731 (the
+highest) to 7,674, and the second group had reputation from 7,636 to 6,999 which
+we sent out 300 and 307 emails (excluding undelivered ones) respectively. The
+survey was open for participation for a month, from 25 July 2017 to 25 August
+2017, before we collected and analysed the responses.
 
@@
 	\begin{tabular}{l|rrrr}
-  \hline 
+		\toprule 
 		Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
-  \hline 
+		\midrule 
 		\multicolumn{5}{l}{\textit{Reported Clones}} \\
-  \hline
+		\midrule
 		$S_D$ & 67,570 & 1,086 & 92 & 38\% \\
@@
 		$N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
-  \hline
+		\midrule
 		Total & 315,786,118 & 14,856 & 111 & 38\% \\
-  \hline
+		\midrule
 		\multicolumn{5}{l}{\textit{Filtered Data Set}} \\
-  \hline
+		\midrule
 		\textit{good} & 2,313 & 97 & 67 & 23\% \\
@@
 		$N_D'$ & 83 & 44 & 19 & 27\% \\
-  \hline
+		\midrule
 		Total & 32,533 & 623 & 96 & 27\%\\
-  \hline 
+		\midrule 
 		%  \multicolumn{5}{l}{\textit{Filtered Data Set without AC}} \\
@@
 		\multicolumn{5}{l}{\textit{True Positives in Manually Validated Clones}} \\
-  \hline 
+		\midrule 
 		$\textit{good}/\textrm{AC}$ & 131 & 51 & 24 & 22\% \\
@@
 		$N_D'/\textrm{AC}$ & 60 & 33 & 15 & 27\% \\
-  \hline
+		\midrule
 		Total & 1,216 & 516 & 75 & 26\% \\
-  \hline
+		\bottomrule
 	\end{tabular}
@@
 However, using Bellon's criteria for matching clone pairs, only
-0.1\textperthousand~of all pairs are agreed by two tool/configuration
+0.1\%~of all pairs are agreed by two tool/configuration
 combinations. As shown in \Cref{tab:snippets}, for the 2,313
@@
 	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r}
-		\hline
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ \cline{3-4}
+	\begin{tabular}{lrrr}
+		\toprule
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ %\cmidrule{3-4}
 		& & Auto & Manual \\
-		\hline 
+		\midrule 
 		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
@@
 		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\hline
+		\midrule
 		Total  & 32,533 & 28,897 & 3,636 \\ 
-		\hline
+		\bottomrule
 	\end{tabular} %
@@
 	\begin{tabular}{l|rrrr|rrr|r}
-			\hline
+		\toprule
 		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
-			\hline
+		\midrule
 		\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
@@
 		\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
-			\hline
+		\midrule
 		Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
-			\hline
+		\bottomrule
 	\end{tabular} 
@@
 	\label{tab:stale_code_details}
-	\resizebox{0.9\linewidth}{!}{
+	\resizebox{\linewidth}{!}{
 		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
-		 \hline
+			\toprule
 			\multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
-		 \hline
+			\midrule
 			Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
-		 \hline
+			\midrule
 			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
@@
 			3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
-		 \hline 
+			\bottomrule 
 			\multicolumn{10}{l}{{\footnotesize * \textit{S}:
@@
 	\resizebox{\linewidth}{!}{
-	\begin{tabular}{l|p{2.2cm}l|rrr}
-		\hline
+		\begin{tabular}{lp{2.2cm}lrrr}
+			\toprule
 			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
-		\hline
+			\midrule
 			Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
@@
 			& No license & No license & 5 & 4 & 21 \\
-		\hline
-		\multicolumn{3}{l|}{Total} & 6 & 11 & 23 \\
-		\hline
+			\midrule
+			\multicolumn{3}{l}{Total} & 6 & 11 & 23 \\
+			\midrule
 			Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
@@
 			& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
-		\hline
-		\multicolumn{3}{l|}{Total} &  79 & 77 & 202 \\
-		\hline
+			\midrule
+			\multicolumn{3}{l}{Total} &  79 & 77 & 202 \\
+			\bottomrule
 		\end{tabular} 
@@
 	Stack Overflow.}
+
+\subsection{RQ5: Stack Overflow Answerers' Awareness}
+
+We received 112 answers (37\% response rate) from the first group and 85 answers
+(28\% response rate) from the second group of Stack Overflow answerers. The response
+rate from both groups were high considered other online survey in software
+engineering that received approximately 14--20\%~\FIXME{double-check the
+	citation again for the magic numbers.}\cite{Punter2003}.
+We only present a summary of the survey answers in this paper. The full analysis
+is available as a technical report \FIXME{Ok?}.
+
+\begin{figure}
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{survey_exp_1-crop}
+		\caption{Group 1}
+		\label{fig:survey_group1_exp}
+	\end{subfigure}%
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=.82\linewidth]{survey_exp_2-crop}
+		\caption{Group 2}
+		\label{fig:survey_group2_exp}
+	\end{subfigure}
+	\caption{Experience of the Stack Overflow users}
+	\label{fig:survey_exp}
+\end{figure}
+
+\subsubsection{Answerers' Experience}
+The majority of users in both groups are experienced developers 
+with more than 10 years of experience or between 5 to 10 years 
+as depicted in \Cref{fig:survey_exp}. They are active users and
+regularly answer questions on Stack Overflow.
+Eighty one and sixty percent of users from Group 1 and Group 2 
+answer questions at least once a week.
+
+\begin{figure*}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{survey_snippet_source_1}
+		\caption{Group 1}
+		\label{fig:survey_snippet_source_1}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{survey_snippet_source_2}
+		\caption{Group 2}
+		\label{fig:survey_snippet_source_2}
+	\end{subfigure}
+	\caption{Sources of code snippets in Stack Overflow answers}
+	\label{fig:survey_snippet_source}
+\end{figure*}
+
+\subsubsection{Code Snippets in Answers} 
+A large amount of 91 (81\%) and 58
+(68\%) users in both group include code snippets in more than sixty percent of
+their answers. \Cref{fig:survey_snippet_source} explains where are these code
+snippets from. Stack Overflow answerers mostly write new code from scratch 
+or modify from the code snippets in question for each answer, while 
+fewer numbers are from other sources including their personal projects, 
+their company projects, open source projects. We found 27 answerers in both Group 1
+and Group 2 occasionally to very frequently copy code from open source projects.
+
+\begin{figure}
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{survey_license_1}
+		\caption{Group 1}
+		\label{fig:survey_license_1}
+	\end{subfigure}%
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{survey_license_2}
+		\caption{Group 2}
+		\label{fig:survey_license_2}
+	\end{subfigure}
+	\caption{Do you usually include a software license in your code snippets on Stack Overflow?}
+	\label{fig:survey_license}
+\end{figure}
+
+\subsubsection{Outdated Code Snippets}
+
+\subsubsection{License of Code Snippets} 
+More than half of the answerers in both groups (63.1\% and 61.9\% respectively)
+are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0
+Unported (CC BY-SA 3.0) to content in the posts, including code snippets, while
+the rest of 36.9\% and 38.1\% are not. Nevertheless, we found that almost all 
+of them do not include license statement in their code snippets (as depicted in
+\Cref{fig:survey_license}) due to several reasons. First, some answerers posted
+only their own code or code that was adapted from the question, hence
+ they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
+company or open source projects that they knew were permitted to be publicly distributed.
+Third, some answerers believe that code snippets in their answers are too small 
+to claim any intellectual property on them and fall under fair use.
+
+\begin{figure}
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{survey_license_check_1}
+		\caption{Group 1}
+		\label{fig:survey_license_check_1}
+	\end{subfigure}%
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{survey_license_check_2}
+		\caption{Group 2}
+		\label{fig:survey_license_check_2}
+	\end{subfigure}
+	\caption{How frequently did you check the software license of the code snippets you copy to Stack Overflow if they conflict with Stack Overflow's CC BY-SA 3.0 license?}
+	\label{fig:survey_license_check}
+\end{figure}
+
+We asked the answerers how frequently they checked for a conflict between software license of the code snippets they copied to Stack Overflow and Stack Overflow's CC BY-SA 3.0.
+As shown in \Cref{fig:survey_license_check}, approximately sixty nine percent of answerers from both groups did not perform the checking.
+Nonetheless, they are about 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.
 
@@
 
+% use section* for acknowledgment
+\ifCLASSOPTIONcompsoc
+  % The Computer Society usually uses the plural form
+  \section*{Acknowledgments}
+\else
+  % regular IEEE prefers the singular form
+  \section*{Acknowledgment}
+\fi
+
+The authors would like to thank...
+
+\bibliographystyle{plain}
+\bibliography{sigproc}
+
+% biography section
 % 
-% The following two commands are all you need in the
-% initial runs of your .tex file to
-% produce the bibliography for the citations in your paper.
-\bibliographystyle{ACM-Reference-Format}
-\bibliography{sigproc}
-
-% \begin{table}
-% 	\centering
-% 	\caption{Statistics of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
-% 	\label{tab:raw_stats}
-% 	%\small
-% 	%\resizebox{\columnwidth}{!}{%
-% 		\begin{tabular}{l|r|r|r|r}
-% 			\hline
-% 			Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
-% 			\hline
-% 			Stack Overflow Snippets & 1,086 & 1,531 & 1,392 & 12,886 \\
-% 			No. of Qualitas projects & 92 & 111 & 82 & 88 \\
-% %			Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
-% %			Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-% %			Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
-% 			Avg.~C$_{\textrm{\textit{\%}}}$ & 38\% & 50\% & 30\% & 33\% \\
-% 			\hline
-% 		\end{tabular} %
-% 	%}
-% \end{table}
-
-% \begin{figure*}
-% 		\centering
-% 		\begin{minipage}{.4\textwidth}
-% 			\centering
-% 			\includegraphics[width=\linewidth]{hist_sd}
-% 			\caption*{$S_D$ clones}
-% 		\end{minipage}%
-% 		\hspace{5ex}
-% 		\begin{minipage}{0.4\textwidth}
-% 			\centering
-% 			\includegraphics[width=\linewidth]{hist_nd}
-% 			\caption*{$N_D$ clones}
-% 		\end{minipage}
-% 		\\
-% 		\begin{minipage}{.4\textwidth}
-% 			\centering
-% 			\includegraphics[width=\linewidth]{hist_se}
-% 			\caption*{$S_E$ clones}
-% 		\end{minipage}%
-% 		\hspace{5ex}
-% 		\begin{minipage}{0.4\textwidth}
-% 			\centering
-% 			\includegraphics[width=\linewidth]{hist_ne}
-% 			\caption*{$N_E$ clones}
-% 		\end{minipage}
-% 	\caption{\FIXME{Useful?}~Distribution of online clones between Stack Overflow snippets and Qualitas projects}
-% 	\label{fig:histogram}
-% \end{figure*}
-
-%They do not exist any more in the latest version.} %These outdated Stack Overflow online clone snippets are questionable for reuse.} %These changes did not reflect They might later find out that the copied code does not work any more due to different API versions.
-Even worse, they might also introduce bugs or vulnerabilities into their software.
-}
-%Usually when developers reuse a code snippet from a Stack Overflow post and find that it does not work nor compatible with their environment.
-They can cast a down vote to that answer resulting in low votes for the answer (which might be outdated).
-However, if the answer is marked as accepted by the person who asks the question, the check mark symbol attached to the answer is still attractive to naive developers who are ignorant.
-
-%\begin{figure*}
-%	\begin{lstlisting}
-%          /* Code in Stack Overflow #23520731 */             /* SchemaUpdate.java (2016-09-26) */
-%          public void execute (Target target) {              public void execute(EnumSet<TargetType> targetTypes, 
-%            LOG.runningHbm2ddlSchemaUpdate();                                Metadata metadata, ServiceRegistry serviceRegistry) {
-%            Connection connection = null;                      if ( targetTypes.isEmpty() ) {
-%            Statement stmt = null;                               LOG.debug(""Skipping SchemaExport as no targets were specified"");
-%            Writer outputFileWriter = null;                      return;
-%            exceptions.clear();                                }
-%            try {                                              exceptions.clear();
-%              DatabaseMetadata meta;                           LOG.runningHbm2ddlSchemaUpdate();
-%              ...                                              ...
-%	\end{lstlisting}
-%	\caption{Outdated code snippet on Stack Overflow post 23520731.
-This code has been copied from {\small\texttt{SchemaUpdate.java}}.
-Its latest version in \textsf{hibernate} code base contains heavy modifications.}
-%	\label{fig:hibernate_outdated_code}
-%\end{figure*}
-
-%\begin{table*}
-%	\centering
-%	\caption{Examples of the 6 outdated QS online clones. Outdated clones are caused by modified/added/deleted statements (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}).}
-%	\label{tab:stale_code_details}
-%	\small
-%	\resizebox{2\columnwidth}{!}{%
-%	\begin{tabular}{r|l|l|l|l|p{5.2cm}|r|r|l|c|l}
-%		\hline 
-%		\multirow{2}{*}{No.} & \multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ \cline{2-11}
-%		& Post & Date & Project & Ver. & File & Start & End & Date & Type & Date \\
-%		\hline
-%			1 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjtools/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
-%			2 & 18303692 & 18-Aug-13 & aspectj & 1.6.9  & aspectjweaver/../Agent.java & 7 & 18 & 5-Mar-08 & \textit{S} & 8-Sep-15 \\
-%			3 & 2513183 & 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
-%			4 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 117 & 126 & 5-Jun-13 & \textit{S} & 17-Mar-15 \\
-%			5 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 143 & 165 & 5-Jun-13 & \textit{S} & 1-Mar-11 \\
-%			6 & 2513183	& 25-Mar-10 & eclipse-SDK & 4.3 & GenerateToStringAction.java & 178 & 187 & 5-Jun-13 & \textit{S} & 5-Jun-13 \\
-%			7 & 11861598 & 8-Aug-12 & eclipse-SDK & 4.3 & WizardDialog.java & 377 & 394 & 1-May-13 & \textit{S} & 21-Jun-13 \\
-%			8 & 22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
-%			9 & 801987 & 29-Apr-09 & hadoop & 1.0.0 & StringUtils.java & 40 & 56 & 15-Dec-11 & \textit{S} & 4-Feb-13 \\
-%			10 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 275 & 287 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
-%			11 & 21702608 & 11-Feb-14 & hadoop & 1.0.0 & DBCountPageView.java & 289 & 309 & 15-Dec-11 & \textit{S} & 12-Jun-11 \\
-%			12 & 14845581 & 13-Feb-13 & hadoop & 1.0.0 & JobSubmissionFiles.java & 46 & 55 & 15-Dec-11 & \textit{S} & 25-Jun-12 \\
-%			13 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapred/../LineRecordReader.java & 47 & 60 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
-%			14 & 16180910 & 24-Apr-13 & hadoop & 1.0.0 & mapreduce/../LineRecordReader.java & 41 & 54 & 15-Dec-11 & \textit{R} & 25-Jul-11 \\
-%			15 & 15168494 & 24-Feb-14 & hibernate & 4.2.2 & ConnectionProviderInitiator.java & 65 & 93 & 22-May-13 & \textit{S} & 26-Apr-13 \\
-%			16 & 24924255 & 24-Jul-14 & hibernate & 4.2.2 & Example.java & 224 & 243 & 22-May-13 & \textit{S} & 23-Apr-13 \\
-%			17 & 23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
-%			18 & 8257554 & 26-Nov-11 & hibernate & 4.2.2 & SettingsFactory.java & 244 & 255 & 22-May-13 & \textit{D} & 11-Mar-11 \\
-%			19 & 23967852 & 31-Apr-14 & hibernate & 4.2.2 & SQLServer2005LimitHandler.java & 43 & 61 & 22-May-13 & \textit{S} & 11-May-16 \\
-%			20 & 19298607 & 10-Oct-13 & hibernate & 4.2.2 & Oracle9iDialect.java & 23 & 32 & 22-May-13 & \textit{S} & 12-Apr-15 \\
-%			21 & 10031897 & 5-Apr-12 & hibernate & 4.2.2 & AliasToBeanResultTransformer.java & 44 & 61 & 22-May-13 & \textit{S} & 4-Jun-15 \\ 
-%			22 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 982 & 998 & 31-May-10 & \textit{S} & 17-Apr-08 \\
-%			23 & 8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
-%			24 & 12936580 & 17-Oct-12 & jfreechart & 1.0.13 & AbstractXYItemRenderer.java & 532 & 569 & 20-Apr-09 & \textit{S} & 16-Jan-16 \\
-%			25 & 16058183 & 17-Apr-13 & jfreechart & 1.0.13 & KeyToGroupMap.java & 18 & 30 & 20-Apr-09 & \textit{S} & 29-Jun-07 \\
-%			26 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 502 & 520 & 20-Apr-09 & \textit{S} & 2-Jun-08 \\
-%			27 & 21998949 & 24-Feb-14 & jfreechart & 1.0.13 & SpiderWebPlot.java & 522 & 536 & 20-Apr-09 & \textit{S} & 22-Nov-13 \\
-%			28 & 6722760 & 17-Jul-11 & jgraph & 5.13.0.0 & HelloWorld.java (3 overlaps)  & 14 & 37 & 25-Sep-09 & \textit{R} & 13-Apr-14 \\
-%			31 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 106 & 117 & 20-Jun-08 & \textit{S} & 13-Apr-10 \\
-%			32 & 6025026 & 17-Jul-11 & jung2 & 2\_0\_1  & ShortestPathDemo.java & 158 & 172 & 20-Jun-08 & \textit{S} & 29-Nov-15 \\
-%			33 & 23586872 & 31-May-14 & junit & 4.11 & Assert.java & 33 & 52 & 11-Oct-12 & \textit{S} & 12-May-15 \\
-%			34 & 7504040 & 29-Sep-11 & junit & 4.11 & ExternalResource.java (3 overlaps) & 4 & 23 & 11-Oct-12 & \textit{S} & 25-Jun-16 \\
-%			37 & 8802082 & 10-Jan-12 & junit & 4.11 & ExpectException.java (2 overlaps) & 11 & 29 & 11-Oct-12 & \textit{S} & 25-May-14 \\
-%			39 & 12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
-%			40 & 20913543 & 6-Jan-14 & spring & 3.0.5  & AutowireUtils.java & 32 & 42 & 20-Oct-10 & \textit{S} & 28-Oct-14 \\
-%			41 & 18623736 & 4-Sep-13 & spring & 3.0.5  & CustomCollectionEditor.java & 33 & 71 & 20-Oct-10 & \textit{S} & 21-Nov-13 \\
-%			42 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 169 & 185 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
-%			43 & 22865824 & 4-Apr-14 & spring & 3.0.5  & JavaMailSenderImpl.java & 186 & 197 & 20-Oct-10 & \textit{S} & 6-Oct-14 \\
-%			44 & 20421869 & 6-Dec-13 & spring & 3.0.5  & ClassPathScanningCandidateComponent\newline Provider.java (2 overlaps) & 85 & 133 & 20-Oct-10 & \textit{R} & 12-Aug-16 \\
-%			46 & 3751463 & 20-Sep-10 & spring & 3.0.5  & ScheduledTasksBeanDefinitionParser.java & 42 & 52 & 20-Oct-10 & \textit{S} & 21-May-12 \\
-%			47 & 6149818 & 27-May-11 & spring & 3.0.5  & DefaultPropertiesPersister.java & 69 & 80 & 20-Oct-10 & \textit{S} & 19-Mar-13 \\
-%			48 & 10952561 & 8-Jun-12 & spring & 3.0.5  & HibernateTemplate.java & 761 & 769 & 20-Oct-10 & \textit{S} & 9-May-15 \\
-%			49 & 10952561 & 8-Jun-12 & spring & 3.0.5  & Jaxb2Marshaller.java & 253 & 269 & 20-Oct-10 & \textit{S} & 28-Aug-12 \\
-%			50 & 20996373 & 8-Jan-14 & spring & 3.0.5  & test/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 18-Dec-08 \\
-%			51 & 20996373 & 8-Jan-14 & spring & 3.0.5  & web/../DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
-%			52 & 20996373 & 8-Jan-14 & spring & 3.0.5  & servlet/../ DelegatingServletInputStream.java & 6 & 20 & 20-Oct-10 & \textit{S} & 15-Jul-16 \\
-%			53 & 5660519 & 15-Apr-11 & spring & 3.0.5 & AnnotationMethodHandlerException\newline Resolver.java & 224 & 233 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
-%			54 & 4781746 & 24-Jan-11 & spring & 3.0.5  & DispatcherServlet.java & 91 & 103 & 20-Oct-10 & \textit{S} & 8-Aug-11 \\
-%			55 & 3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
-%			56 & 9003314 & 25-Jan-12 & spring & 3.0.5  & WebDataBinder.java & 95 & 108 & 20-Oct-10 & \textit{S} & 15-Aug-10 \\
-%			57 & 14019840 & 24-Dec-12 & struts2 & 2.2.1  & DefaultActionMapper.java & 128 & 144 & 17-Jul-10 & \textit{S} & 18-Oct-13 \\
-%			58 & 15131432 & 28-Feb-13 & struts2 & 2.2.1  & FreemarkerManager.java & 163 & 177 & 17-Jul-10 & \textit{S} & 28-Oct-13 \\
-%			59 & 15110171 & 27-Feb-13 & struts2 & 2.2.1  & StringLengthFieldValidator.java & 25 & 42 & 17-Jul-10 & \textit{S} & 15-Jun-15 \\
-%			60 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & BasicAuthenticator.java (2 overlaps) & 25 & 73 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
-%			62 & 21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
-%			63 & 24404964 & 25-Jun-14 & tomcat & 7.0.2  & CoyoteAdapter.java & 543 & 553 & 4-Aug-10 & \textit{S} & 25-Sep-14 \\
-%			64 & 10289462 & 23-Apr-12 & tomcat & 7.0.2  & JspRuntimeLibrary.java & 252 & 296 & 4-Aug-10 & \textit{S} & 12-Sep-12 \\
-%			\hline
-%	\end{tabular} %
-%}
-%\end{table*}
-
+% If you have an EPS/PDF photo (graphicx package needed) extra braces are
+% needed around the contents of the optional argument to biography to prevent
+% the LaTeX parser from getting confused when it sees the complicated
+% \includegraphics command within an optional argument. (You could create
+% your own custom macro containing the \includegraphics command to make things
+% simpler here.)
+%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
+% or if you just want to reserve a space for a photo:
+
+\begin{IEEEbiography}{Michael Shell}
+Biography text here.
+\end{IEEEbiography}
+
+% if you will not have a photo at all:
+\begin{IEEEbiographynophoto}{John Doe}
+Biography text here.
+\end{IEEEbiographynophoto}
+
+% insert where needed to balance the two columns on the last page with
+% biographies
+%\newpage
+
+\begin{IEEEbiographynophoto}{Jane Doe}
+Biography text here.
+\end{IEEEbiographynophoto}
+
+% You can push biographies down or up by placing
+% a \vfill before or after them. The appropriate
+% use of \vfill depends on what kind of text is
+% on the last page and whether or not the columns
+% are being equalized.
+
+%\vfill
+
+% Can be used to pull up biographies so that the bottom of the last one
+% is flush with the other column.
+%\enlargethispage{-5in}
+
+% that's all folks
 \end{document}

### 2017-08-13 cloverflow-tse/freshness.m

@@ -1,0 +1,44 @@
+y = [13	6 1;
+3	15	2;
+10	5	0;
+5	7	0;
+2	5	0;
+0	6	0;
+5	0	0;
+0	4	0;
+0	3	0;
+1	2	0;
+2	1	0;
+0	3	0;
+3	0	0;
+0	2	0;
+0	1	1;
+1	0	0;
+1	0	0;
+1	0	0;
+1	0	0];
+bar(y,'stacked')
+
+P=findobj(gca,'type','patch');
+C=['w','k','m','g']; % make a colors list 
+for n=1:length(P) 
+set(P(n),'facecolor',C(n));
+end
+
+xticks([1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19])
+xticklabels({'hibernate', 'spring', 'eclipse-SDK', 'hadoop', 'tomcat', ...
+    'junit', 'log4j', 'jfreechart', 'jgraph', 'jung2', 'poi', 'struts2', ... 
+    'weka', 'aspectj', 'jasperreports', 'antlr', 'ant', 'itext', 'jgrapht'})
+%xlabel('Project','FontSize',15)
+ylabel('Clone pair','FontSize',15)
+t_legend=legend('Fresh', 'Outdated', 'Dead');
+set(t_legend,'FontSize',15);
+set(gca,'FontSize',15);
+set(gca,'XTickLabelRotation',45)
+box on
+
+h=gcf;
+set(h,'PaperPositionMode','auto');         
+set(h,'PaperOrientation','landscape');
+set(h,'Position',[50 50 1200 500]);
+print('freshness','-dpdf','-bestfit')

### 2017-08-13 cloverflow-tse/license_violations.m

@@ -1,0 +1,25 @@
+y = [5 1 79; 4 7 76; 21 2 202; ];
+%bar(y,'stacked')
+bar(y)
+
+P=findobj(gca,'type','patch');
+C=['w','k','m','g']; % make a colors list 
+for n=1:length(P) 
+set(P(n),'facecolor',C(n));
+end
+
+xticks([1 2 3])
+xticklabels({'QS', 'EX', 'UD'})
+%xlabel('Project','FontSize',15)
+ylabel('No. of clones','FontSize',15)
+t_legend=legend('No license', 'Compatible license', 'Incompatible license','Location','northwest');
+set(t_legend,'FontSize',15);
+set(gca,'FontSize',15);
+%set(gca,'XTickLabelRotation',45)
+box on
+
+h=gcf;
+set(h,'PaperPositionMode','auto');         
+set(h,'PaperOrientation','landscape');
+set(h,'Position',[50 50 500 200]);
+print('license_violation','-dpdf','-bestfit')

### 2017-08-13 cloverflow-tse/piechart.m

@@ -1,0 +1,2 @@
+X = [0 1 13 32 66];
+pie(X)

### 2017-08-13 cloverflow-tse/q_histogram.m

@@ -1,0 +1,112 @@
+nd = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_df_130901_1234_fixedclonelines/qualitas_projects.csv', 1, 1);
+sd = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_simian_df_130901_1234_fixedclonelines/qualitas_projects.csv', 1, 1);
+ne = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_fse13_130901_1234_fixedclonelines/qualitas_projects.csv', 1, 1);
+se = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_simian_fse13_130901_1234_fixedclonelines/qualitas_projects.csv', 1, 1);
+
+so_sd = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_simian_df_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
+so_sd_count = so_sd(:,1);
+so_nd = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_df_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
+so_nd_count = so_nd(:,1);
+
+so_se = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_simian_fse13_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
+so_se_count = so_se(:,1);
+so_ne = csvread('/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer/stats_nicad_fse13_130901_1234_fixedclonelines/fragment_stats.csv', 1, 1);
+so_ne_count = so_ne(:,1);
+
+subplot(1,2,1)
+sosd_hist=histogram(so_sd_count,'NumBins', 60)
+ylabel('No. of snippets','FontSize',16)
+xlabel('SO clone pairs','FontSize',16)
+set(gca,'FontSize',16);
+dim = [.19 .6 .3 .3];
+str = 'NumBins=60, BinWidth=23';
+annotation('textbox',dim,'String',str,'FitBoxToText','on','FontSize',15,'LineStyle','none');
+
+subplot(1,2,2)
+sdhist=histogram(sd,'NumBins', 60)
+ylabel('No. of projects','FontSize',16)
[…]

### 2017-08-13 cloverflow-tse/stacked_bar_outdated_clones.m

@@ -1,0 +1,25 @@
+%fresh =     (1, 4, 0, 7, 5, 11, 0, 0, 0, 1, 0, 0, 0, 2, 3, 0, 3, 0)
+%outdated =  (0, 0, 2, 5, 9, 4,  2, 4, 4, 0, 2, 2, 3, 1, 9, 1, 0, 7)
+%deleted =   (0, 0, 0, 0, 0, 1,  0, 0, 0, 0, 0, 0, 0, 0, 2, 0, 0, 0)
+%other =     (0, 0, 0, 0, 0, 0,  0, 0, 1, 0, 0, 0, 0, 0, 0, 0, 0, 0)
+y = [1 0 0 0; 4 0 0 0; 0 2 0 0; 7 5 0 0; 5 9 0 0; 11 4 1 0; 0 2 0 0; 0 4 0 0; 0 4 0 1; 1 0 0 0; 0 2 0 0; 0 2 0 0; 0 3 0 0; 2 1 0 0; 3 9 2 0; 0 1 0 0; 3 0 0 0; 0 7 0 0];
+
+bar_handle = bar(y,'stacked');
+
+set(bar_handle(1),'FaceColor',[0 0.6 0]);
+set(bar_handle(2),'FaceColor','yellow');
+set(bar_handle(3),'FaceColor','red');
+set(bar_handle(4),'FaceColor','blue');
+
+ylabel('Amount','FontSize',18);
+xticks([1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,18]);
+xticklabels({'ant', 'log4j', 'aspectj', 'eclipse', 'hadoop', 'hibernate','jasperreports', 'jfreechart', 'jgraph', 'jgrapht','jstock','jung','junit','poi','spring','struts','tomcat','weka'});
+xtickangle(45);
+
+set(gca,'fontsize',18);
+grid on
+l = cell(1,4);
+l{1}='Fresh'; l{2}='Outdated'; l{3}='Deleted'; l{4}='Not found';
+legend(bar_handle,l,'fontsize',18);
+
+%print('outdated','-dpdf','-bestfit')

### 2017-08-13 cloverflow-tse/survey_snippet_source.m

@@ -1,0 +1,21 @@
+group1 = [14 20 19 10 14 7; 3 5 9 0 14 53; 
+    5 6 16 13 16 28; 36 38 7 1 1 1; 
+    24 28 16 5 4 7; 1 2 14 6 17 44];
+
+group2 = [13 20 30 19 18 11; 1 5 12 14 13 66; 
+    4 8 15 17 28 39; 66 32 10 1 2 0; 
+    42 26 18 10 11 4; 2 4 23 8 20 54];
+
+bar_handle = bar(group1,'grouped');
+ylim([0 70])
+ylabel('Amount','FontSize',16);
+xticklabels({'Personal projects', 'Company projects', 'Open source projects', 'Write from scratch', 'Modify from questions', 'Others'});
+xtickangle(30);
+set(gca,'fontsize',16);
+grid on
+
+l = cell(1,6);
+l{1}='Very frequently'; l{2}='Frequently'; l{3}='Occasionally'; l{4}='Rarely'; l{5}='Very rarely'; l{6}='Never';
+legend(bar_handle,l,'Location','Northwest','fontsize',12);
+
+% print('survey_snippet_source','-dpdf','-bestfit')

### 2017-08-13 MethodExtractor/files/20000593_0.java
Updated the SCC tokenizer to generate -1 as parentId.

@@ -1,4 +1,3 @@
-1,23@@UCL@@
 public void testStaticInit() throws Exception {
     try {
         new BadInitClass().doSomething();

### 2017-08-13 MethodExtractor/src/main/java/crest/MethodParser.java

@@ -91,7 +91,6 @@ public class MethodParser {
             StringBuilder content = new StringBuilder();
             int numberOfLines = 0;
             /* example from here: https://www.leveluplunch.com/java/examples/count-number-of-lines-in-text-file/ */
-            File file = new File("c:/temp/data.txt");
             FileReader fr = new FileReader(FILE_PATH);
             BufferedReader br = new BufferedReader(fr);
             String line;

### 2017-08-13 SCCTokenizer/file_concatenator.py

@@ -5,7 +5,8 @@ import datetime as dt
 
 
 file_id_list = []
-starting_id = 0
+starting_postid = 0
+starting_blockid = 0
 
 
 def get_methods(file):
@@ -37,9 +38,9 @@ def get_file_list(home_dir, filter):
 
 def createFileId(file):
     global file_id_list
-    global starting_id
+    global starting_blockid
     file_id_list.append(file)
-    fileid = file_id_list.index(file) + starting_id
+    fileid = file_id_list.index(file) + starting_blockid
     writefile("so-headers.txt", str(fileid) + "," + file + "\n", "a", False)
 
     return fileid
@@ -95,9 +96,13 @@ def main():
     javafiles = get_file_list(sys.argv[1], "*.java");
 
     # get the starting id, if not, start at 0
-    global starting_id
-    if len(sys.argv) == 3:
-        starting_id = int(sys.argv[2])
+    global starting_blockid
+    global starting_postid
+
+    starting_blockid = int(sys.argv[2])
+
+    # if len(sys.argv) == 4:
+        # starting_postid = int(sys.argv[2])
 
     print "files: ", len(javafiles)
     
@@ -113,11 +118,17 @@ def main():
             for i, method in enumerate(methods):
                 # print method
                 method_parts = method.split("@@UCL@@")
-                writefile("so.txt", "===@@@UCI===\n", "a", False)
-                id = createFileId(jfile + "," + method_parts[0].strip())
-                writefile("so.txt", str(index) + "\n", "a", False)
-                writefile("so.txt", str(id) + "\n", "a", False)
-                writefile("so.txt", method_parts[1].strip() + "\n", "a", False)
+                lines = len(method_parts[1].strip().split("\n"))
+
+                # filter for only the one with more than 10 lines
+                if lines >= 10:
+                    writefile("so.txt", "===@@@UCI===\n", "a", False)
+                    id = createFileId(jfile + "," + method_parts[0].strip())
+                    # writefile("so.txt", str(index + starting_postid) + "\n", "a", False)
+                    # -1 means we don't care about parentId
+                    writefile("so.txt", "-1\n", "a", False)
+                    writefile("so.txt", str(id) + "\n", "a", False)
+                    writefile("so.txt", method_parts[1].strip() + "\n", "a", False)
         except Exception as e:
             writefile("errors.txt", "error processing " + jfile + ".\n", "a", False)
             traceback.print_exc(file=sys.stdout)

### 2017-08-13 SCCTokenizer/tokenizer_stackoverflow.py

@@ -143,7 +143,7 @@ def process_so_file(FILE_tokens_file, FILE_stats_file):
                     post_id = lines[0]
                     method_id = lines[1]
                     snippet = "\n".join(lines[2:])
-                    process_contents(post_id, method_id, snippet, FILE_tokens_file, FILE_stats_file, logging)
+                    process_contents(post_id, method_id, snippet.decode('UTF-8'), FILE_tokens_file, FILE_stats_file, logging)
                     block_count += 1
                     
                 except Exception as e:

### 2017-08-14 cloverflow-tse/cloverflow.tex
Latest update to the paper.

@@
 % The paper headers
-\markboth{Journal of \LaTeX\ Class Files,~Vol.~14, No.~8, August~2015}%
-{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for Computer Society Journals}
+\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, August~2017}%
+{Ragkhitwetsagul \MakeLowercase{\textit{et al.}}: Outdated and License-Violating Code on Stack Overflow}
 % The only time the second header will appear is for the odd numbered pages
@@
 We extracted Java code snippets from a snapshot of a Stack Overflow
-dump\footnote{\url{https://archive.org/details/stackexchange}} in
-January 2016. 
+dump\footnote{\url{https://archive.org/details/stackexchange}} in January 2016.
 % The archived dump has a size of 9 gigabytes.
-The data
-dump is in XML format containing information of posts
-(questions and answers) and 
-% supporting data such as user accounts and timestamps of the posts.
-we were interested in code snippets embedded
-in posts which were located between
-{\small\texttt{<code>}...\texttt{</code>}} tags. A Stack Overflow
-thread contains a question and several answers. An answer can also be
-marked as \textbf{accepted answer} by the questioner if the solution
-fixes his/her problem. We collected Java code snippets using two
-criteria. First, we only focused on code snippets in accepted
-answers. We chose the snippets in accepted answers because they
-actually solved the problems in the questions. Moreover, they are
-always displayed just below the questions which makes them more
-likely to be reused than other answers. Second, we were only
-interested in code snippets of at least six lines. Snippets smaller
-than six lines are usually spurious clones~\cite{Bellon2007}. Each
-snippet was extracted from the dump and saved to a file.
-%using its post ID as the file's name.
-If an accepted answer had more than one code snippet, we appended an indexing number, starting from zero, after the post ID (e.g.
-45051109\_0, and 45051109\_1.).
-Lastly, we added {\small\texttt{.java}} extension to the file's names so that clone detectors could recognise them.
-We obtained 144,064 Java code snippets containing 2,332,940
-lines\footnote{Measured by cloc:
-	\url{https://github.com/AlDanial/cloc}} of Java source code.
-The median of the snippet size is 10.
-% excluding comments and blank lines.
+The data dump is in XML format containing information of posts (questions and
+answers) and we were interested in code snippets embedded in posts which were
+located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
+Overflow thread contains a question and several answers. An answer can also be
+marked as \textbf{accepted answer} by the questioner if the solution fixes
+his/her problem. We collected Java code snippets using two criteria. First, we
+only focused on code snippets in accepted answers. We chose the snippets in
+accepted answers because they actually solved the problems in the questions.
+Moreover, they are always displayed just below the questions which makes them
+more likely to be reused than other answers. Second, we were only interested in
+code snippets of at least ten lines. Although the minimum clone size of six
+lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006},
+snippets of at least ten lines are usually more interesting since most of
+boiler-plate code of \texttt{equal} or \texttt{hashCode} methods are removed.
+Each snippet was extracted from the dump and saved to a file. Moreover, we
+filtered out irrelevant code snippets that were part of the accepted answers
+but were not written in Java by using regular expressions and manual checking.
+~\FIXME{should I mention I use PMD CPD to help here? More confusing?}.
+Finally we obtained
+72,365 Java code snippets containing 1,840,581 lines\footnote{Measured by cloc:
+	\url{https://github.com/AlDanial/cloc}} of Java source code. The median of the
+snippet size is 10.
 
@@
 		\midrule
-		Stack Overflow & 144,064 & 2,332,940 & 10 \\ 
+		Stack Overflow & 72,365 & 1,840,581 & 10 \\ 
 		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
@@
 
-\textbf{Clone Detection Tools: }
-We use clone detection to discover online code clones. 
-%\textbf{Clone Detection and Configuration: } 
-There are a number of restrictions in terms of choosing the clone
-detection tools for this study. The main restriction is due to nature
-of code snippets posted on Stack Overflow, as most of them are
-incomplete Java classes or methods. Hence, a detector must be flexible
-enough to process code snippets that are not compilable or not
-complete blocks. Moreover, since the amount of code that has to be
-processed is in a scale of millions line of code (as shown in
-\Cref{tab:datasets}), a clone detector must be scalable enough to
-report clones in a reasonable amount of time. We have tried 5
-state-of-the-art clone detectors including Simian~\cite{simian},
-NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002},
-iClones~\cite{Gode2009}, and DECKARD~\cite{Jiang2007a} against the
-Stack Overflow and Qualitas datasets. CCFinder, iClones, and DECKARD
-failed with execution errors after running for couple of hours. Thus,
-we removed them from the study. Simian and NiCad are flexible enough
-to handle code with incomplete methods or classes and successfully
-completed the detection.
+\textbf{Clone Detection Tools: } We use clone detection to discover online code
+clones. %\textbf{Clone Detection and Configuration: }
+There are a number of restrictions in terms of choosing the clone detection
+tools for this study. The main restriction is due to nature of code snippets
+posted on Stack Overflow, as most of them are incomplete Java classes or
+methods. Hence, a detector must be flexible enough to process code snippets that
+are not compilable or not complete blocks. Moreover, since the amount of code
+that has to be processed is in a scale of millions line of code (as shown in
+\Cref{tab:datasets}), a clone detector must be scalable enough to report clones
+in a reasonable amount of time. We have tried 7 state-of-the-art clone detectors
+including Simian~\cite{simian}, SourcererCC~\cite{Sajnani2016},
+NiCad~\cite{Cordy,Roy2008}, CCFinder~\cite{Kamiya2002}, iClones~\cite{Gode2009},
+DECKARD~\cite{Jiang2007a}, and PMD-CPD~\cite{pmd-cpd} against the Stack Overflow
+and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
+while PMD CPD failed to complete the execution. Although Simian, SourcererCC,
+CCFinder, iClones, and DECKARD could successfully report clones, we decided to
+choose Simian and SourcererCC due to their fast detection speed.
 
@@
 (strings and numbers) which enables Simian to detect literal clones (type-1) and
-parameterised clones (type-2). \textbf{NiCad} is also a text-based clone
-detector which detects clones at either method- or block-level granularity. It
+parameterised clones (type-2). \textbf{SourcererCC} is a token-based clone
+detector which detects clones at either function- or block-level granularity. It
 can detect clones of type-1, -2 up to type-3 (clones with added and removed
-statements) and has also been used in several empirical clone
-studies~\cite{Roy2008, Ragkhitwetsagul2016, Svajlenko2014, Wang2013, Mondal2011,
-	Sajnani2016}. NiCad utilises TXL~\cite{Cordy2006} for parsing and
-pretty-printing source code and provides code normalisation by variable renaming
-and abstraction. We use a variant of NiCad called \textit{nicadcross}. It offers
-the same functionalities as the original NiCad but is specialised for detecting
-code clones between two systems.
+statements) and offer scalability against large code
+corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Due to incomplete code blocks and
+functions normally found in Stack Overflow snippets, the built-in Java tokeniser
+could not parse more than half of all snippets. SourcererCC provides an option
+to plug in a customised tokeniser, so we developed a special Java tokeniser with
+assistance from the tool's creator. Another benefit of SourcererCC is its
+indexing and search processing allows us to detect code clones between two
+systems.
 
@@
 	\centering
-	\caption{Configurations of Simian and NiCad}
+	\caption{Configurations of Simian and SourcererCC}
 	\label{t:param_tuning}
@@
 	\small
-	\begin{tabular}{p{0.8cm}|p{2.5cm}p{3.8cm}}
+	\begin{tabular}{lp{5cm}}
 		\toprule
-		Tool & Default (\textit{D}) & EvaClone (\textit{E}) \\
+		Tool & Configurations \\
 		\midrule
-		Simian\newline (\textit{S}) &  threshold=6,\newline ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers & threshold=5, ignoreIdentifiers, \newline ignoreIdentifierCase, \newline ignoreStrings, ignoreCharacters,\newline ignoreSubtypeNames, \newline balanceSquareBrackets \\
+		Simian~(\textit{S}) &  Threshold=10, ignoreStringCase, \newline ignoreCharacterCase, \newline ignoreModifiers \\ 
+		\midrule
+		SourcererCC~(\textit{SCC}) & Functions, Minimum clone size=10, \newline Similarity=80\% \\
 		\bottomrule
-		NiCad\newline (\textit{N}) & Blocks, UPI=0.30,\newline MinLine=10,\newline MaxLine=2500 & Blocks, UPI=0.20, \newline MinLine=5, MaxLine=604, \newline blind renaming, literal abstraction \\
-		\hline
 	\end{tabular} %
@@
 	\centering
-	\caption{Number of online clones reported by Simian (\textit{S}) and NiCad (\textit{N}) with default (\textit{D}) and EvaClone (\textit{E}) configurations}
+	\caption{Number of online clones reported by Simian and SourcererCC}
 	\label{tab:orig_stats}
@@
 	%\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r}
+	\begin{tabular}{lrr}
 		\toprule
-		Stats & \multicolumn{1}{c|}{$S_D$} & \multicolumn{1}{c|}{$S_E$} & \multicolumn{1}{c|}{$N_D$} & \multicolumn{1}{c}{$N_E$} \\
+		Stats & \multicolumn{1}{c}{Simian} & \multicolumn{1}{c}{SourcererCC} \\
 		\midrule
-		Total C$_{\textrm{\textit{pairs}}}$ & 67,570 & 63,635,844 & 632,855 & 251,449,849 \\
-		% Avg.~C$_{\textrm{\textit{pairs}}}$ & 62 & 41,565 & 455 & 19,356 \\
-		Avg.~C$_{\textrm{\textit{size}}}$ & 9.11 & 5.95 & 10.85 & 6.28 \\
+		Total clone pairs & 721 & 1,678 \\
+		Average clone size & 16.61 & 17.86 \\
 		\bottomrule
@@
 
-\subsection{Phase 2: Clone Filtering}
+\subsection{Phase 2: Clone Merging}
 As there are in total 315,786,118 clone pairs reported, it is
@@
 	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|r|r|r|r}
+	\begin{tabular}{lrrrrr}
 		\toprule
@@
 	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|r|c|c|r}
+	\begin{tabular}{lrccr}
 		\toprule
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c|}{Filters*} & \multirow{2}{*}{After Filtering} \\ \cmidrule{3-4}
+		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c}{Filters*} & \multirow{2}{*}{After Filtering} \\ %\cmidrule{3-4}
 		& & \textit{L} & \textit{S} & \\ 
@@
 		UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
-		\hline 
+		\midrule
 		BP & Boiler-plate or IDE auto-generated \\
@@
 	\centering
-	\includegraphics[width=\linewidth]{classification_process}\vspace{-1ex}
+	\includegraphics[width=0.9\linewidth]{classification_process}\vspace{-1ex}
 	\caption{Online code clone classification process}
@@
 their previous answers. The full survey can be found in our \FIXME{technical
-	report/website?} ~\footnote{Stack Overflow Answerers' Survey:
+	report/website?} ~\footnote{Survey--Stack Overflow Answerers:
 	\url{http://www.cs.ucl.ac.uk/staff/C.Ragkhitwetsagul/files/so_survey.pdf}}.
@@
 	\caption{Investigated online clone pairs and corresponding snippets
-		and Qualitas projects for the different data sets}
+		and Qualitas projects}
 	\label{tab:snippets}
 	\centering
-	\begin{tabular}{l|rrrr}
+	\begin{tabular}{rrrr}
 		\toprule
-		Data Set & Pairs & Snippets & Projects & Avg.~C$_{\textrm{\textit{\%}}}$ \\
+		Pairs & Snippets & Projects & Avg.~cloned ratio \\
 		\midrule
-		\multicolumn{5}{l}{\textit{Reported Clones}} \\
-		\midrule
-		$S_D$ & 67,570 & 1,086 & 92 & 38\% \\
-		$S_E$ & 63,635,844 & 1,531 & 111 & 50\% \\
-		$N_D$ & 632,855& 1,392 & 88 & 30\% \\
-		$N_E$ & 251,449,849& 12,886 & 88 & 33\% \\
-		\midrule
-		Total & 315,786,118 & 14,856 & 111 & 38\% \\
-		\midrule
-		\multicolumn{5}{l}{\textit{Filtered Data Set}} \\
-		\midrule
-		\textit{good} & 2,313 & 97 & 67 & 23\% \\
-		\textit{ok'} & 12,336 & 139 & 43 & 28\% \\
-		$S_D'$ & 17,081 & 460 & 74 & 31\% \\
-		$N_D'$ & 83 & 44 & 19 & 27\% \\
-		\midrule
-		Total & 32,533 & 623 & 96 & 27\%\\
-		\midrule 
-		%  \multicolumn{5}{l}{\textit{Filtered Data Set without AC}} \\
-		%  \hline 
-		%  $\textit{good}/\textrm{AC}$ & 141 & 52 & 26 & 23\% \\
-		%  $\textit{ok'}/\textrm{AC}$ & 12,229 & 126 & 36 & 28\% \\
-		%  $S_D'/\textrm{AC}$ & 17,673 & 448 & 72 & 31\% \\
-		%  $N_D'/\textrm{AC}$ & 70 & 39 & 16 & 29\% \\
-		%  \hline
-		%  Total & 30,113 & 556 & 80 & 28\% \\
-		%  \hline
-		\multicolumn{5}{l}{\textit{True Positives in Manually Validated Clones}} \\
-		\midrule 
-		$\textit{good}/\textrm{AC}$ & 131 & 51 & 24 & 22\% \\
-		$\textit{ok'}/\textrm{AC}$ & 152 & 83 & 22 & 21\% \\
-		$S_D'/\textrm{AC}$ & 873 & 337 & 60 & 35\% \\
-		$N_D'/\textrm{AC}$ & 60 & 33 & 15 & 27\% \\
-		\midrule
-		Total & 1,216 & 516 & 75 & 26\% \\
+		2,304 & 460 & 77 & ??\% \\ % <-- for avg. cloned ratio, use scripts in ~/Downloads/stackoverflow/scripts/checking
 		\bottomrule
@@
 
-\begin{table}
-	\centering
-	\caption{No.~of online clones candidates for the classification}
-	\label{tab:online_clone_classification_results}
-	%\small
-	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{lrrr}
-		\toprule
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ %\cmidrule{3-4}
-		& & Auto & Manual \\
-		\midrule 
-		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
-		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
-		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
-		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
-		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-		\midrule
-		Total  & 32,533 & 28,897 & 3,636 \\ 
-		\bottomrule
-	\end{tabular} %
-	%}
-\end{table}
+%\begin{table}
+%	\centering
+%	\caption{No.~of online clones candidates for the classification}
+%	\label{tab:online_clone_classification_results}
+%	%\small
+%	%	\resizebox{\columnwidth}{!}{%
+%	\begin{tabular}{lrrr}
+%		\toprule
+%		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ %\cmidrule{3-4}
+%		& & Auto & Manual \\
+%		\midrule 
+%		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
+%		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
+%		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
+%		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
+%		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
+%		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
+%		\midrule
+%		Total  & 32,533 & 28,897 & 3,636 \\ 
+%		\bottomrule
+%	\end{tabular} %
+%	%}
+%\end{table}
 
@@
 	%\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{l|rrrr|rrr|r}
+	\begin{tabular}{lrrrrrrrr}
 		\toprule
@@
 		\centering
-		\includegraphics[width=.8\linewidth]{survey_exp_1-crop}
+		\includegraphics[width=.6\linewidth]{survey_exp_1-crop}
 		\caption{Group 1}
@@
 		\centering
-		\includegraphics[width=.82\linewidth]{survey_exp_2-crop}
+		\includegraphics[width=.62\linewidth]{survey_exp_2-crop}
 		\caption{Group 2}
@@
 		\centering
-		\includegraphics[width=\linewidth]{survey_snippet_source_1}
+		\includegraphics[width=.8\linewidth]{survey_snippet_source_1}
 		\caption{Group 1}
@@
 		\centering
-		\includegraphics[width=\linewidth]{survey_snippet_source_2}
+		\includegraphics[width=.8\linewidth]{survey_snippet_source_2}
 		\caption{Group 2}
@@
 		\centering
-		\includegraphics[width=.8\linewidth]{survey_license_1}
+		\includegraphics[width=.6\linewidth]{survey_license_1}
 		\caption{Group 1}
@@
 		\centering
-		\includegraphics[width=.8\linewidth]{survey_license_2}
+		\includegraphics[width=.6\linewidth]{survey_license_2}
 		\caption{Group 2}
@@
 	\end{subfigure}
-	\caption{Do you usually include a software license in your code snippets on Stack Overflow?}
+	\caption{Software license in Stack Overflow code snippets.}
 	\label{fig:survey_license}
@@
 \subsubsection{Outdated Code Snippets}
+
+We found that 63.1\% of Stack Overflow answerers in Group 1 have been notified of
+outdated code in their answers (see \Cref{fig:survey_outdated}). The ratio drops to 47.6\% in
+Group 2. Thus, at least roughly half of the top answerers on Stack Overflow
+are aware of their outdated code in some of their answers.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=.8\linewidth]{survey_outdated}
+	\caption{Percentage of answerers who are notified of outdated code in their Stack Overflow answers.}
+	\label{fig:survey_outdated}
+\end{figure}%
+
+We then asked the participants to have been notified of their outdated code
+(80 and 48 participants from Group 1 and 2 respectively) a
+follow-up questions ``how frequently did you fix your outdated code on Stack
+Overflow?''. The answers, depicted in \Cref{fig:survey_outdated_fix}, show that
+more than half of them frequently fix the outdated code snippets. However, there
+are 18.8\% of the answerers in both groups who rarely or never fix their code.
+
+\begin{figure}
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{survey_outdated_fix_1}
+		\caption{Group 1}
+		\label{fig:survey_outdated_fix_1}
+	\end{subfigure}%
+	\begin{subfigure}{.25\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{survey_outdated_fix_2}
+		\caption{Group 2}
+		\label{fig:survey_outdated_fix_2}
+	\end{subfigure}
+	\caption{Frequency of the answerers fixing their outdated code.}
+	\label{fig:survey_outdated_fix}
+\end{figure}
+
+The answers support our findings of outdated online code clones. Although most
+of the Stack Overflow answerers know that their code are outdated, the code may
+still not be fixed.
 
@@
 of them do not include license statement in their code snippets (as depicted in
-\Cref{fig:survey_license}) due to several reasons. First, some answerers posted
-only their own code or code that was adapted from the question, hence
+\Cref{fig:survey_license}) due to several reasons. First, some answerers chose to 
+post only their own code or code that was adapted from the question, hence
  they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
@@
 Third, some answerers believe that code snippets in their answers are too small 
-to claim any intellectual property on them and fall under fair use.
+to claim any intellectual property on them and fall under fair use~\cite{fairuse}.
+
+While nobody explicitly includes a software license in their snippets,
+many users include a statement on their profile page that states all their
+answers are under a certain license. For example, \textit{All code posted by me on
+Stack Overflow should be considered public domain without copyright. For
+countries where public domain is not applicable, I hereby grant everyone the
+right to modify, use and redistribute any code posted by me on Stack Overflow
+for any purpose. It is provided "as-is" without warranty of any kind.}  Many
+users either declare their snippets to be public domain, or they grant
+additional licenses, e.g. Apache 2.0 or MIT/Expat.
 
@@
 	\end{subfigure}
-	\caption{How frequently did you check the software license of the code snippets you copy to Stack Overflow if they conflict with Stack Overflow's CC BY-SA 3.0 license?}
+	\caption{Frequency of the answerers checking license of their code snippets against Stack Overflow's CC BY-SA 3.0.}
 	\label{fig:survey_license_check}
@@
 
-We asked the answerers how frequently they checked for a conflict between software license of the code snippets they copied to Stack Overflow and Stack Overflow's CC BY-SA 3.0.
-As shown in \Cref{fig:survey_license_check}, approximately sixty nine percent of answerers from both groups did not perform the checking.
+We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0.
+As shown in \Cref{fig:survey_license_check}, approximately 69\% of answerers from both groups did not perform the checking.
 Nonetheless, they are about 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.
+
+\subsubsection{Open Comments} 
+We also invited the participants to give any comments regarding answering Stack Overflow with code snippets. These are some interesting comments we received.
+
+Comment 1: ``The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software "professionals" that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.
+A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about.
+Think php/mysql tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}).
+They're also full of toxic code snippets.''
+
+Comment 2: ``When I copy code it's usually short enough to be considered "fair use" but I am not a lawyer or copyright expert so some guidance from SO would be helpful.
+I'd also like the ability to flag/review questions that violate these guidelines.''
+
+Comment 3: ``My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.''
+
+Comment 4: ``The main problem for me/us is outdated code, esp.
+as old answers have high google rank so that is what people see first, then try and fail.
+Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.''
+
+Comment 5: ``Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).''
 

### 2017-08-15 FirebaseDBConnector/DLClonesFromDB.py
Removed the clone classification tool (along with it python db connector) out to its own repo.

@@ -1,72 +1,0 @@
-import firebase_admin
-from firebase_admin import credentials
-from firebase_admin import db
-import os
-
-
-def write_file(filename, fcontent, mode, isprint):
-    """
-    Write the string content to a file
-    copied from
-    http://www.pythonforbeginners.com/files/reading-and-writing-files-in-python
-    :param filename: name of the file
-    :param fcontent: string content to put into the file
-    :param mode: writing mode, 'w' overwrite every time, 'a' append to an existing file
-    :return: N/A
-    """
-    # try:
-    file = open(filename, mode)
-    file.write(fcontent)
-    file.close()
-
-    if isprint:
-        print "saved:" + filename
-
-
-def delete_file(filename):
-    """ delete the file and recreate it
-    :param filename: the name of file
-    :return: True = succeeded, False = failed
-    """
-    try:
-        os.remove(filename)
-    except OSError:
-        return False
-
-    return True
-
-
-def main():
-    file_name = "classifications.csv"
-    # Fetch the service account key JSON file contents
-    cred = credentials.Certificate('cloverflow-firebase-adminsdk.json')
-
-    # Initialize the app with a service account, granting admin privileges
-    firebase_admin.initialize_app(cred, {
-        'databaseURL': 'https://cloverflow-4dd16.firebaseio.com/'
-    })
-
-    # Get a database reference to our clone pairs.
-    ref = db.reference('clones/pairs')
-    # download all clone pairs
-    clones = ref.get()
-    print "total clone pairs: ", len(clones)
-    delete_file(file_name)
-    # write to a csv file
-    for clone in clones:
-        content = clone["file1"] + "," + \
-                  str(clone["start1"]) + "," + \
-                  str(clone["end1"]) + "," + \
-                  clone["file2"] + "," + \
-                  str(clone["start2"]) + "," + \
-                  str(clone["end2"]) + "," + \
-                  clone["classification"] + ",\"" + \
-                  clone["notes"] + "\"\n"
-
-        write_file(file_name, content, "a", True)
-
-        print clone['file1'] + " (" + str(clone['start1']) + "," + str(clone['end1']) + ") : " + \
-              clone['file2'] + " (" + str(clone['start2']) + "," + str(clone['end2']) + ")"
-
-
-main()

### 2017-08-15 FirebaseDBConnector/ULClonesToDB.py

@@ -1,75 +1,0 @@
-import firebase_admin
-from firebase_admin import credentials
-from firebase_admin import db
-import csv
-
-# Fetch the service account key JSON file contents
-cred = credentials.Certificate('cloverflow-firebase-adminsdk.json')
-
-# Initialize the app with a service account, granting admin privileges
-firebase_admin.initialize_app(cred, {
-    'databaseURL': 'https://cloverflow-4dd16.firebaseio.com/'
-})
-
-# Get a database reference to our blog.
-ref = db.reference('clones/')
-# print(ref.get())
-
-pairs_ref = ref.child('pairs')
-
-filename = '/Users/Chaiyong/IdeasProjects/StackoverflowChecker/indv_simian_df_130901_pt1+2+3+4_firebase.csv'
-bigdict = {}
-count = 0
-rowcount = 0
-
-with open(filename) as csvfile:
-    readCSV = csv.reader(csvfile, delimiter=',')
-
-    # count how many record we have
-    for row in readCSV:
-        rowcount += 1
-
-with open(filename) as csvfile:
-    readCSV = csv.reader(csvfile, delimiter=',')
-
-    for row in readCSV:
-        # if count > 199:
-        #     break
-        # print(row)
-        codefile1 = open('/Users/Chaiyong/Downloads/stackoverflow/stackoverflow_formatted/' + row[0],'r')
-        code1 = codefile1.read()
-
-        codefile2 = open('/Users/Chaiyong/Downloads/stackoverflow/QualitasCorpus-20130901r/projects_130901r_pt1+2+3/' + row[3], 'r')
-        code2 = codefile2.read()
-
-        codefile2orig = open(
-            '/Users/Chaiyong/Downloads/stackoverflow/QualitasCorpus-20130901r/projects_orig_130901/' + row[3],
-            'r')
-        code2orig = codefile2orig.read()
-        # code2orig = ""
-
-        bigdict.update({
-                count: {
-                    'file1': row[0],
-                    'start1': int(row[1]),
-                    'end1': int(row[2]),
-                    'code1': code1,
-                    'code1orig': code1,
-                    'file2': row[3],
-                    'start2': int(row[4]),
-                    'end2': int(row[5]),
-                    'code2': code2,
-                    'code2orig': code2orig,
-                    'classification': '',
-                    'notes': '',
-                    # 'total': 200
-                    'total': rowcount
-
-                }
-            })
-        count += 1
-
[…]

### 2017-08-15 mcloneinvest/src/App.js

@@ -1,210 +1,0 @@
-import React, { Component } from 'react';
-import './App.css';
-import fire from './fire';
-import Form from './Form';
-import Code from './Code';
-import _ from 'lodash';
-
-class App extends Component {
-
-  constructor(props) {
-    super(props);
-    this.state = {
-      snapshot: [],
-      pageoffset: 0,
-      showorig: false,
-      scrollTop: 100
-    }; // <- set up react state
-
-    // normal variable
-    this.pagesize = 20;
-    this.page = 0;
-    this.currentid = 0;
-    this.total = 0;
-
-    this.decreaseId = this.decreaseId.bind(this);
-    this.increaseId = this.increaseId.bind(this);
-    this.handleFileIdChange = this.handleFileIdChange.bind(this);
-    this.showOriginalCode = this.showOriginalCode.bind(this);
-    this.showFormattedCode = this.showFormattedCode.bind(this);
-    this.queryDB = this.queryDB.bind(this);
-    this.previousSet = this.previousSet.bind(this);
-    this.nextSet = this.nextSet.bind(this);
-  }
-
-  componentWillMount(){
-    this.queryDB();
-    document.title = "Cloverflow: Manual Clone Classification Tool";
-  }
-
-  queryDB() {
-    /* Create reference to messages in Firebase Database */
-    let clonesRef = fire.database().ref('clones/pairs')
-                        .orderByKey()
-                        .startAt(this.page * this.pagesize + '')
-                        .endAt((this.page * this.pagesize + this.pagesize - 1) + '');
-
-    clonesRef.once("value", snapshot => {
-      this.setState({snapshot: Object.values(snapshot.val())});
-    });
-  }
-
-  decreaseId(event) {
-    if (this.currentid > 0) {
-      if (this.currentid > this.page * this.pagesize) {
-        this.currentid--;
-        this.setState({pageoffset: this.state.pageoffset - 1});
-      } else {
-        this.previousSetSelectLast();
-      }
-    }
-    this.showFormattedCode();
-  }
-
-  increaseId(event) {
-    if (this.currentid < this.maxid - 1) {
-      this.currentid++;
-      this.setState({pageoffset: parseInt(this.state.pageoffset, 10) + 1});
-    } else if (this.currentid === this.maxid - 1 && this.currentid < this.total - 1) {
-      this.nextSet();
-    }
-    this.showFormattedCode();
-  }
-
-  previousSetSelectLast(event) {
[…]

### 2017-08-15 mcloneinvest/src/Form.js

@@ -1,149 +1,0 @@
-import React, { Component } from 'react';
-import fire from './fire';
-
-class Form extends Component {
-
-  constructor(props) {
-    super(props);
-
-    this.state = {
-      classifications: [],
-      selectedOption: 'QS',
-      notes: 'Any notes?',
-      currentid: this.props.currentid
-    }; // <- set up react state
-
-    this.changeSelection = false;
-
-    this.onPatternChanged = this.onPatternChanged.bind(this);
-    this.submitForm = this.submitForm.bind(this);
-    this.handleTextAreaChange = this.handleTextAreaChange.bind(this);
-  }
-
-  componentWillReceiveProps(nextProps) {
-    // alert(nextProps.currentid);
-    // alert(nextProps.data["classification"] + "," + nextProps.data["notes"]); // set the classification
-    this.setState({selectedOption: nextProps.data["classification"]});
-    this.setState({notes: nextProps.data["notes"]});
-  }
-
-  componentWillMount(props) {
-    // alert(this.props.data["classification"] + ", " + this.props.data["notes"]);
-    this.setState({selectedOption: this.props.data["classification"]});
-    this.setState({notes: this.props.data["notes"]});
-  }
-
-  onPatternChanged(event) {
-    this.setState({selectedOption: event.target.value});
-    this.changeSelection = true;
-  }
-
-  handleTextAreaChange(event) {
-    this.setState({notes: event.target.value});
-    this.changeSelection = true;
-  }
-
-  submitForm(event) {
-    var id = this.props.currentid;
-    /* Create reference to messages in Firebase Database */
-    let clonesRef = fire.database().ref('clones/pairs').child(id);
-    var classification = this.state.selectedOption;
-    var notes = this.state.notes;
-    clonesRef.update({
-                    'classification': classification,
-                    'notes': notes
-                });
-
-    this.changeSelection = false;
-    alert("Updated");
-  }
-
-  render() {
-    // alert(this.props.data["classification"]);
-    // if (!this.changeSelection) {
-    //   this.setState({selectedOption: this.props.data["classification"]});
-    //   this.setState({notes: this.props.data["notes"]});
-    // }
-    return (
-      <div id="form_container">
-        <div className="row">
-          <div className="col-sm-12">
-            <form>
-              <div className="container">
-                <div className="radio">
-                  <label>
-                    <input type="radio" value="QS"
-                      checked={this.state.selectedOption === 'QS'}
-                      onChange={this.onPatternChanged}  />
-                    QS
[…]

### 2017-08-15 cloverflow-tse/cloverflow.tex
Latest update to the paper.

@@
 and Qualitas datasets. NiCad failed to parse 44,960 Stack Overflow snippets
-while PMD CPD failed to complete the execution. Although Simian, SourcererCC,
-CCFinder, iClones, and DECKARD could successfully report clones, we decided to
-choose Simian and SourcererCC due to their fast detection speed.
+while PMD CPD failed to complete the execution due to lexical errors. iClones
+could complete its execution but skipped 367 snippets due to malformed blocks in
+Stack Overflow data set. Although Simian, SourcererCC, CCFinder, and DECKARD
+could successfully report clones, we decided to choose only Simian and
+SourcererCC due to their fast detection speed.
 
@@
 statements) and offer scalability against large code
-corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Due to incomplete code blocks and
-functions normally found in Stack Overflow snippets, the built-in Java tokeniser
-could not parse more than half of all snippets. SourcererCC provides an option
-to plug in a customised tokeniser, so we developed a special Java tokeniser with
-assistance from the tool's creator. Another benefit of SourcererCC is its
-indexing and search processing allows us to detect code clones between two
+corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Another benefit of SourcererCC is
+its indexing and search processing allows us to detect code clones between two
 systems.
@@
 project, we ran the tools on the project's code and the entire Stack Overflow
-data. Simian did not provide an option to detect cross-project clones. Hence the
+data. Due to incomplete code blocks and functions
+normally found in Stack Overflow snippets, the built-in SourcererCC's Java
+tokeniser could not parse 45,903 snippets, more than half of them. Nevertheless,
+the tool provides an option to plug in a customised tokeniser, so we developed a
+special Java tokeniser with assistance from the tool's creator. The customised
+tokeniser successfully processed all Stack Overflow snippets.
+Simian did not provide an option to detect cross-project clones. Hence the
 Simian clone report was filtered to contain only clone pairs between Stack
@@
 %		\resizebox{\columnwidth}{!}{
-	\small
+%	\small
 	\begin{tabular}{lp{5cm}}
@@
 
-\textbf{Clone Detection Configuration: }
-We are aware of effects of configurations to clone detection results
-and the importance of searching for optimised configurations in
-empirical clone
+\textbf{Clone Detection Configuration: } We are aware of effects of
+configurations to clone detection results and the importance of searching for
+optimised configurations in empirical clone
 studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
-considering the massive size of the two datasets and the search space
-of at least 15 Simian and 5 NiCad parameters, we are unable to search
-for the best configurations of the tools. Thus, we decided to
-configure Simian and NiCad using two established configurations:
-(1)~the tools' default configurations chosen by the tools' creators
-(denoted as \textit{D}), and (2)~the discovered configurations for
-Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
-of optimising clone detectors' configurations based on clone agreement
-(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
-In total, we have four configurations: Simian with the default
-configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
-NiCad with the default configuration ($N_D$)
-and NiCad with the EvaClone configuration ($N_E$).
-
-We encountered NiCad failures with a few Qualitas projects.~$N_D$
-could not detect clones in \textsf{hibernate} due to clustering
-errors. $N_E$ generated errors during code normalisation for 5
-projects including \textsf{vuze}, \textsf{hibernate},
-\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
-contacted the creator of NiCad regarding the issues. They identified
-the issues as problems in the TXL grammar and as problems of long file
-paths, and will be fixed in the next NiCad releases.
+considering the massive size of the two datasets and the search space of at
+least 15 Simian and 3 SourcererCC parameters, we are unable to search for the
+best configurations of the tools. Thus, we decided to configure Simian and
+SourcererCC based on their established default configurations chosen by the
+tools' creators. All variable renaming are disabled to decrease a number of
+false positives since we aim for finding clones that are copied from open source
+projects with minimal modifications. The two clone detectors complement each
+other by having Simian detecting literal copies of code snippets and SourcererCC
+detecting clones with added/deleted statments. We made sure that they 
+detected only non-trivial clones by increasing the minimum clone size to ten
+lines.
+%(denoted as \textit{D}), and (2)~the discovered configurations for
+%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
+%of optimising clone detectors' configurations based on clone agreement
+%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
+%In total, we have four configurations: Simian with the default
+%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
+%NiCad with the default configuration ($N_D$)
+%and NiCad with the EvaClone configuration ($N_E$).
+
+%We encountered NiCad failures with a few Qualitas projects.~$N_D$
+%could not detect clones in \textsf{hibernate} due to clustering
+%errors. $N_E$ generated errors during code normalisation for 5
+%projects including \textsf{vuze}, \textsf{hibernate},
+%\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
+%contacted the creator of NiCad regarding the issues. They identified
+%the issues as problems in the TXL grammar and as problems of long file
+%paths, and will be fixed in the next NiCad releases.
 
 The number of online clone pairs reported % by running Simian and NiCad
-are presented in \Cref{tab:orig_stats}. $S_D$ reports 67,570 clone
-pairs while $N_D$ reports 632,855 clone pairs. $S_E$ and $N_E$ report
-much larger numbers of clone pairs, 63,635,844 and 251,449,849 pairs
-respectively. This is expected since EvaClone configurations prefer
-recall~\cite{Wang2013}.  The average clone size reported by $S_D$ is
-9.11 lines which is bigger than for $S_E$ (5.95 lines). Similarly,
-$N_D$ has an average clone size of 10.85 lines which is bigger than
-6.28 lines reported by $N_E$. The drop in size is due to the EvaClone
-configuration with a smaller minimum size (\Cref{t:param_tuning}).
+are presented in \Cref{tab:orig_stats}. Simian reports 721 clone
+pairs while SourcererCC reports 1,678 clone pairs. 
+SourcererCC reports more clones due to its capability of detecting
+type-1 to type-3 clones while Simian only detects type-1 and type-2 clones.
+The average clone size reported by Simian is
+16.61 lines which is slightly smaller than SourcererCC (17.86 lines).
 
@@
 		\toprule
-		Stats & \multicolumn{1}{c}{Simian} & \multicolumn{1}{c}{SourcererCC} \\
+		Stats & \multicolumn{1}{c}{Total clone pairs} & \multicolumn{1}{c}{Average clone size} \\
 		\midrule
-		Total clone pairs & 721 & 1,678 \\
-		Average clone size & 16.61 & 17.86 \\
+		Simian & 721 & 16.61 \\
+		SourcererCC & 1,678 & 17.86 \\
 		\bottomrule

### 2017-08-21 cloverflow_technical_report/cloverflow_survey_rn.tex
Added technical report updates.

\RequirePackage{fix-cm}
%
\documentclass{svjour3}                     % onecolumn (standard format)
% To have symmetric margin (only for research note)
\setlength{\textwidth}{\dimexpr\pdfpagewidth-2in}% Equal left/right margins
%\documentclass[smallcondensed]{svjour3}     % onecolumn (ditto)
%\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%

\usepackage{uclrn}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[round]{natbib} 
%\setcitestyle{aysep={}}

\newcommand\fscore{\operatorname{F-score}}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{listings}
\usepackage{float}
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{makecell}
\usepackage{algorithm}
%\usepackage{cleveref}
\usepackage{algpseudocode}
\usepackage{pifont}
%\usepackage{cite}
\usepackage{verbatim}
\usepackage{url}
%\usepackage{microtype}
\usepackage{caption}
\usepackage{booktabs} % For formal tables
\usepackage{subcaption}
\usepackage[misc,geometry]{ifsym} 
\usepackage{etoolbox}
\usepackage[colorlinks=true,allcolors=blue]{hyperref}

\captionsetup{compatibility=false}

\rnnumber{17/xx}
%\usepackage[table]{xcolor}% http://ctan.org/pkg/xcolor
%\newtheorem{definition}{Definition}

\lstset{language=Java,tabsize=2,basicstyle=\ttfamily\scriptsize}

\newcommand\FIXME[1]{\textbf{FIXME: #1}}

\begin{document}

\title{Awareness of Stack Overflow Users to\\ Outdated and License-violating Code:\\ The Online Survey}
%\subtitle{Do you have a subtitle?\\ If so, write it here}

\titlerunning{SO Developers awareness: Outdated and License-violating Code}        % if too long for running head

\author{Chaiyong~Ragkhitwetsagul, Jens~Krinke, Mathues~Paixao,~Giuseppe Bianco, Rocco~Oliveto}

%\authorrunning{Short form of author list} % if too long for running head

\institute{Chaiyong Ragkhitwetsagul~(\Letter), Jens Krinke \at
              Computer Science Department., University College London, UK \\
              Tel.: +44 (0)20 7679,  Fax: +44 (0)20 7387 1397\\
              \email{\{ucabagk, j.krinke\}@ucl.ac.uk}           %  \\
%             \emph{Present address:} of F. Author  %  if needed}
}

\date{\today}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
ABSTRACT GOES HERE
\end{abstract}

\section{Introduction}

Outdated third-party code and software licensing conflicts are ramifications by
reusing source code by copying and pasting (i.e.~code cloning). \cite{Xia2014}
show that a large number of open source systems reuse outdated third-party
libraries from popular open source projects. Using the outdated code give
detrimental effects to the software since they may introduce vulnerabilities. On
the other hand, \cite{German2009} found conflicts in software license between
the clones among different systems that come from the same source,~i.e.~clone
siblings.

The Internet encourages fast and easy way of sharing and copying code.
Developers nowadays do not only copy code from local software projects, but also
from online sources such as programming Q\&A website and online code
repositories. Stack Overflow is one of the most popular programming Q\&A
websites in the word. It has 7.6 million users, 14 million questions, 23 million
answers\footnote{Data as of 21 August 2017
	from~\url{https://stackexchange.com/sites}}, and more than 50 million developers
visiting each month\footnote{Data as of 21 August 2017 from:
	\url{https://stackoverflow.com}}. Nevertheless, several code snippets on Stack
Overflow are found to be problematic. Many code snippets provided as solutions
are workarounds and occasionally contains defects or vulnerabilities.
\cite{Acar2016} performed a user study and found that Stack Overflow helps
developers to solve Android programming problems quicker than other resources
while, at the same time, offers less secure code than books or the official
Android documentation. Only 17\% of the Stack Overflow discussion threads the
participant visited during the study contain secure code snippets. They also
found that similar piece of API call copied from Stack Overflow by participants
in their study existed in a random sample of 200,000 Android apps from Google
Play. \cite{An2017} showed that 1,279 cloned snippets between 399 Android apps
and Stack Overflow potentially violate software licenses.

We are interested in studying the issues of outdated code and software license
violation cause by code snippets on Stack Overflow. Asking and answering
questions on Stack Overflow usually involve copying and pasting source code
snippets, either in a question or an answer. However, the copied snippets are
not regularly checked and occasionally not up-to-date with their originals. Some
snippets are copied from an open source system with stricter software license
than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Before
this study, we performed an preliminary study using code clone detection tools
to locate cloned code snippets in accepted answers. We found that many snippets
were copied from open source projects. Some cloned snippets are outdated and
possibly violating the original software license. In either case, these snippets
are potentially harmful for reuse. To accompany the findings and to gain
insights into the cause of this problem, we resort to a qualitative study using
an online survey of Stack Overflow developers who 1) answer programming
questions with code snippets and 2) reuse code snippets from Stack Overflow
answers.

In this paper, we use the term ``answerers'' to refer to Stack Overflow users
who have high reputation, specifically the users with reputation from 963,731
(highest)  to 6,999. The answerers gain their reputation from answering
questions and receiving votes from other users. The reputation reflects trust
they gain from other users and their activeness in answering questions. We ask
the answerers the origins of source code snippets in their answers  and assess
their awareness of outdated and licensed code. We use the term ``visitors'' the
refer to developers, who may or may not have a Stack Overflow account but visit
Stack Overflow when facing programming problems. They copy example code snippets
that are relevant to their problems and reused them in their software. 
We ask Stack Overflow visitors, who copied code snippets from
Stack Overflow, about their experience of outdated or license-violating code.

\section{Research Questions}
In this study, we would like to answer the following
research questions:

\begin{enumerate}
	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{where are the code snippets in Stack Overflow answers from?}
	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{are Stack Overflow answerers aware of outdated code in their answers?}
	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to software licensing conflicts):} \textit{are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}
	\item \textbf{RQ4 (Awareness of Stack Overflow visitors to outdated code):} \textit{are Stack Overflow visitors aware of outdated code on Stack Overflow?}
	\item \textbf{RQ5 (Awareness of Stack Overflow visitors to software licensing conflicts):} \textit{are Stack Overflow visitors aware of of software licensing conflicts caused by reusing code snippets from Stack Overflow?}
\end{enumerate}

\section{Research Methodology}
The study is performed using online surveys. We designed the surveys using
Google Forms by following the principles of survey research
by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. We created two versions of the
survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. The
surveys are completely anonymous and the participants could decide to leave at
any time. They do not collect any sensitive personal information from the
participants and were approved for an ethical waiver by the designated ethics
officer in the Computer Science Department at UCL.  The complete versions of
both surveys can be found in the Appendix A and B.

\begin{table}
	\centering
	\caption{The Stack Overflow answerer taken the surveys}
	\label{tab:answerers}
	\begin{tabular}{lrrrr}
		\toprule
		Target group & Reputation & Sent emails & Answers & Rate \\
		\midrule
		Answerer Group 1 & 963,731--7,674 & 300 & 113 & 38\% \\
		Answerer Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
		\midrule
		Total & -- & 607 & 198 & 33\% \\
		\bottomrule
	\end{tabular}
\end{table}

\subsection{The Answerer Survey}
The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
questions, 3 yes/no questions, and one open-ended question for additional
comments. The first two questions were mandatory while the other 9 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, experience of
answering Stack Overflow questions, sources of the Stack Overflow snippets,
concerns of copying code snippets to Stack Overflow, problems from code 
snippets on Stack Overflow, fixing outdated code, and additional feedbacks.

We selected the participants for our answerer survey based on their Stack Overflow reputation. On
Stack Overflow, a user's reputation reflects how much the community trust the
user. A user earns reputation when he or she receives up votes for good
questions and useful answers. Accepted answers receive more reputation score
than questions, and regular answers\footnote{Stack Overflow
	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
Overflow reputation is an indicator of user's skills and their involvement in
asking and answering questions on the site.

The participants were invited to take the survey via email addresses publicly available on their
public Stack Overflow and GitHub profiles. We selected the answerers based on
all-time reputation ranking\footnote{Stack Overflow Users (data as of 25 July
	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}} and
separated them into two groups (see Table~\ref{tab:answerers}) so that we can
compare the results or observe similar patterns between them. 
The first group had reputation from 963,731 (the
highest) to 7,674, and the second group had reputation from 7,636 to 6,999 which
we sent out 300 and 307 emails (excluding undelivered ones) respectively. The
survey was open for participation for a month, from 25 July 2017 to 25 August
2017, before we collected and analysed the responses.

\subsection{The Visitor Survey}

The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
questions. The first four questions were mandatory while the other 12 questions
were shown to the participants based on their previous answers. The survey collects
information of the participant's software development experience, importance of
Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
Stack Overflow snippets, licensing of code on Stack Overflow, and additional
feedbacks.

\begin{table}
	\centering
	\caption{The Stack Overflow visitors taken the survey}
	\label{tab:visitors}
	\begin{tabular}{lr}
		\toprule
		Invitation channels & Answers \\
		\midrule
		Chaiyong's Facebook post & 47 \\
		Blognone.com & 32 \\
		University of Molise & 6 \\
		comp.lang.java.programmer & 3 \\
		Software Engineering Facebook page & 1 \\
		\midrule
		Total & 89 \\
		\bottomrule
	\end{tabular}
\end{table}

The participants for this survey were invited to take the survey via five
channels. The first channel is via the first author's Facebook post where the
first author invited friends who are software developers and have experience of
copying code snippets from Stack Overflow to take the survey. The second channel
is a popular Thai technology news and media community called blognone.com which
attracts a high number of software developers. The first author posted an
invitation to the visitor survey in a discussion forum. The third channel
collects answers from University of Molise which is the third author's
workplace. The last two channels are from a comp.lang.java.programmer Google
groups and Software Engineering Facebook page. The survey was open for
participation for a month, from 25 July 2017 to 25 August 2017, before we
collected and analysed the responses. The number of participants taken the
survey are shown in Table~\ref{tab:visitors}.

\section{Results and Discussions}

\subsection{Answerer Survey}
We received 113 answers (38\% response rate) from the first group and 85 answers
(28\% response rate) from the second group of Stack Overflow answerers. The response
rate from both groups were high considered other online survey in software
engineering that received approximately 14--20\%~\FIXME{double-check the
	citation again for the magic numbers.}~\citep{Punter2003}.

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.5\linewidth]{survey_exp_1-crop}
		\caption{Group 1}
		\label{fig:survey_group1_exp}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=0.5\linewidth]{survey_exp_2-crop}
		\caption{Group 2}
		\label{fig:survey_group2_exp}
	\end{subfigure}
	\caption{Experience of the Stack Overflow answerers}
	\label{fig:survey_exp}
\end{figure}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How long have you been working on developing software?}
	}%
}
\vspace{0.5cm}

The majority of users in both groups are experienced developers 
with more than 10 years of experience or between 5 to 10 years 
as depicted in Figure~\ref{fig:survey_exp}. They are active users and
regularly answer questions on Stack Overflow.
Eighty one and sixty percent of users from Group 1 and Group 2 
answer questions at least once a week.

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently do or did you answer questions on Stack Overflow?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently do or did you include code snippets in your answers on Stack Overflow?}
	}%
}
\vspace{0.5cm}

\subsection{RQ1: Where are the code snippets in Stack Overflow answers from?}

To answer this research question, we ask the participants this question:

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Where did the code snippets in your answers come from?}
	}%
}
\vspace{0.5cm}

From the answers, a large amount of 91 (81\%) and 58
(68\%) answerers in both group include code snippets in more than sixty percent of
their answers. Figure~\ref{fig:survey_snippet_source} explains where are these code
snippets from. Stack Overflow answerers mostly write new code from scratch 
or modify from the code snippets in question for each answer, while 
fewer numbers are from other sources including their personal projects, 
their company projects, open source projects. We found 27 answerers in both Group 1
and Group 2 occasionally to very frequently copy code from open source projects.

\begin{figure*}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{survey_snippet_source_1}
		\caption{Group 1}
		\label{fig:survey_snippet_source_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{survey_snippet_source_2}
		\caption{Group 2}
		\label{fig:survey_snippet_source_2}
	\end{subfigure}
	\caption{Sources of code snippets in Stack Overflow answers}
	\label{fig:survey_snippet_source}
\end{figure*}

\begin{figure}
	\begin{subfigure}{5\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_license_1}
		\caption{Group 1}
		\label{fig:survey_license_1}
	\end{subfigure}%
	\begin{subfigure}{.25\textwidth}
		\centering
		\includegraphics[width=.6\linewidth]{survey_license_2}
		\caption{Group 2}
		\label{fig:survey_license_2}
	\end{subfigure}
	\caption{Software license in Stack Overflow code snippets.}
	\label{fig:survey_license}
\end{figure}

\subsection{RQ2: Are Stack Overflow answerers aware of outdated code in their answers?}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{Outdated code occurs when code snippets in your answers are no longer up-to-date with the latest version of the software you copied the code from. Have you ever been notified of outdated code in your Stack Overflow answers?}
	}%
}
\vspace{0.5cm}

We found that 63.1\% of Stack Overflow answerers in Group 1 have been notified of
outdated code in their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 47.6\% in
Group 2. Thus, at least roughly half of the top answerers on Stack Overflow
are aware of their outdated code in some of their answers.

\begin{figure}
	\centering
	\includegraphics[width=.5\linewidth]{survey_outdated}
	\caption{Percentage of answerers who are notified of outdated code in their Stack Overflow answers.}
	\label{fig:survey_outdated}
\end{figure}%

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently were you notified of outdated or deprecated code in your Stack
			Overflow answers?}
	}%
}
\vspace{0.5cm}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{How frequently did you fix your outdated code on Stack Overflow?}
	}%
}
\vspace{0.5cm}

We then asked the participants to have been notified of their outdated code
(80 and 48 participants from Group 1 and 2 respectively) a
follow-up questions ``how frequently did you fix your outdated code on Stack
Overflow?''. The answers, depicted in Figure~\ref{fig:survey_outdated_fix}, show that
more than half of them frequently fix the outdated code snippets. However, there
are 18.8\% of the answerers in both groups who rarely or never fix their code.

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{survey_outdated_fix_1}
		\caption{Group 1}
		\label{fig:survey_outdated_fix_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.9\linewidth]{survey_outdated_fix_2}
		\caption{Group 2}
		\label{fig:survey_outdated_fix_2}
	\end{subfigure}
	\caption{Frequency of the answerers fixing their outdated code.}
	\label{fig:survey_outdated_fix}
\end{figure}

\subsection{RQ2: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{Were you aware, at the time of copying the code, that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets?}
	}%
}
\vspace{0.5cm}

More than half of the answerers in both groups (63.1\% and 61.9\% respectively)
are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0
Unported (CC BY-SA 3.0) to content in the posts, including code snippets, while
the rest of 36.9\% and 38.1\% are not. Nevertheless, we found that almost all 
of them do not include license statement in their code snippets (as depicted in
Figure~\ref{fig:survey_license}) due to several reasons. First, some answerers chose to 
post only their own code or code that was adapted from the question, hence
they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
company or open source projects that they knew were permitted to be publicly distributed.
Third, some answerers believe that code snippets in their answers are too small 
to claim any intellectual property on them and fall under fair use~\citep{fairuse}.

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Do you usually include a software license in your code snippets on Stack Overflow?}
	}%
}
\vspace{0.5cm}

While nobody explicitly includes a software license in their snippets,
many users include a statement on their profile page that states all their
answers are under a certain license. For example, \textit{All code posted by me on
	Stack Overflow should be considered public domain without copyright. For
	countries where public domain is not applicable, I hereby grant everyone the
	right to modify, use and redistribute any code posted by me on Stack Overflow
	for any purpose. It is provided "as-is" without warranty of any kind.}  Many
users either declare their snippets to be public domain, or they grant
additional licenses, e.g. Apache 2.0 or MIT/Expat.

\begin{figure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.85\linewidth]{survey_license_check_1}
		\caption{Group 1}
		\label{fig:survey_license_check_1}
	\end{subfigure}%
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=.85\linewidth]{survey_license_check_2}
		\caption{Group 2}
		\label{fig:survey_license_check_2}
	\end{subfigure}
	\caption{Frequency of the answerers checking license of their code snippets against Stack Overflow's CC BY-SA 3.0.}
	\label{fig:survey_license_check}
\end{figure}

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][1cm]{0.98\textwidth}{%
		\textit{How frequently did you check the software license of the code snippets you copy to Stack Overflow if they conflict with Stack Overflow's CC BY-SA 3.0 license? }
	}%
}
\vspace{0.5cm}

We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0. As shown in Figure~\ref{fig:survey_license_check}, approximately 69\% of answerers from both groups did not perform the checking. Nonetheless, they are about 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.

\vspace{0.5cm}
\noindent\fbox{%
	\parbox[c][0.5cm]{0.98\textwidth}{%
		\textit{Do you have any other concerns regarding answering Stack Overflow with code snippets?}
	}%
}
\vspace{0.5cm}

We also invited the participants to give any comments regarding answering Stack Overflow with code snippets. These are some interesting comments we received.

Comment 1: ``The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software "professionals" that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.  A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about. Think php/mysql tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}). They're also full of toxic code snippets.''

Comment 2: ``When I copy code it's usually short enough to be considered "fair use" but I am not a lawyer or copyright expert so some guidance from SO would be helpful. I'd also like the ability to flag/review questions that violate these guidelines.''

Comment 3: ``My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.''

Comment 4: ``The main problem for me/us is outdated code, esp. as old answers have high google rank so that is what people see first, then try and fail. Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.''

Comment 5: ``Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).''

\subsubsection{Visitors' Experience}

\section{Related Work}

\subsection{Stack Overflow}

Stack Overflow is a gold mine for software engineering research and has been put
to use in several previous studies. In terms of developer-assisting tools,
Seahawk is an Eclipse plug-in that searches and recommends relevant code
snippets from Stack Overflow~\citep{Ponzanelli2013}. A follow up work, Prompter,
by Ponzanelli et al.~\citep{Ponzanelli2014} achieves the same goal but with
improved algorithms. The code snippets on Stack Overflow are mostly examples or
solutions to programming problems. Hence, several code search systems use whole
or partial data from Stack Overflow as their code search
databases~\citep{Keivanloo2014,Park2014,
	Stolee2014,Subramanian2013,Diamantopoulos2015}. Furthermore, Treude et
al.~\cite{Treude2016}~use machine learning techniques to extract insight
sentences from Stack Overflow and use them to improve API documentation.

Another research area is knowledge extraction from Stack Overflow.
\cite{Nasehi2012}~studied what makes a good code example by analysing answers
from Stack Overflow. Similarly, \cite{Yang2016} report the number of reusable
code snippets on Stack Overflow across various programming languages.
\cite{Wang2013_StackOverflow} use Latent Dirichlet Allocation (LDA) topic
modelling to analyse questions and answers from Stack Overflow so that they can
automatically categorise new questions. There are also studies trying to
understand developers' behaviours on Stack Overflow, e.g.~A study by
\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
\cite{Yang2017} analysed 909k non-fork Python projects on Github and 1.9
million python code snippets on Stack Overflow and found thousands of 
code blocks that are copied from Stack Overflow to GitHub.

\subsection{Software Licensing}
Software licensing is crucial for open source and industrial software
development. Di Penta et al.~\cite{DiPenta2010} studied the evolution of
software licensing in open source software and found that licensing statements
change over time. \cite{German2009} found that licensing conflicts occur between
the clone siblings, i.e.~clones among different systems that come from the same
source. Later, \cite{German2010} created an automated tool for software license
identification, Ninka. \cite{An2017} detected clones between 399 Android apps
and Stack Overflow Java code snippets. They found that  that 1,279 cloned
snippets potentially violate software licenses. Our study gives insights into
the software licensing of Stack Overflow code snippets. We study the licensing
awareness of developers when they copy and paste code to/from Stack Overflow.

\subsection{Reusing of outdated third-party source code} 
Outdated code occurs in software development. Xia et al.~\cite{Xia2014} discover
that there are code reused from popular open source projects in a large number
of open source systems. More importantly, some of the reused code are outdated
which affect quality and security of the software. Our study focuses on a
similar problem but on the context of Stack Overflow.

\section{Conclusions}

%\bibliographystyle{abbrv}
%\bibliographystyle{plainnat}
\bibliographystyle{spbasic}
\bibliography{sigproc}

\clearpage
\section{Appendix}
\appendix
\section{Stack Overflow Answerer Survey}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.8\linewidth]{answerer-1}
	\label{fig:answerer-1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{answerer-2}
	\label{fig:answerer-2}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{answerer-3}
	\label{fig:answerer-3}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{answerer-4}
	\label{fig:answerer-4}
\end{figure}

\section{Stack Overflow Visitor Survey}
\begin{figure}[H]
	\centering
	\includegraphics[width=0.85\linewidth]{visitor-1}
	\label{fig:visitor-1}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{visitor-2}
	\label{fig:visitor-2}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{visitor-3}
	\label{fig:visitor-3}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{visitor-4}
	\label{fig:visitor-4}
\end{figure}

\end{document}
% end of file template.tex

### 2017-08-22 cloverflow_technical_report/cloverflow_survey_rn.tex
Continued working on the technical report.

@@
 
-\subsection{Answerer Survey}
+\subsection{Answerer Responses}
 We received 113 answers (38\% response rate) from the first group and 85 answers
@@
 
+\subsubsection*{General Information}
+%General information of the answerers' experience and frequency of answering 
+%questions on Stack Overflow with code snippets as discussed below.
+
+%\subsubsection*{Q1: How long have you been working on developing software?}
+
 \begin{figure}
@@
 		\centering
-		\includegraphics[width=0.5\linewidth]{survey_exp_1-crop}
+		\includegraphics[width=0.8\linewidth]{survey_exp_1}
 		\caption{Group 1}
@@
 		\centering
-		\includegraphics[width=0.5\linewidth]{survey_exp_2-crop}
+		\includegraphics[width=0.8\linewidth]{survey_exp_2}
 		\caption{Group 2}
@@
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How long have you been working on developing software?}
-	}%
-}
-\vspace{0.5cm}
-
 The majority of users in both groups are experienced developers 
 with more than 10 years of experience or between 5 to 10 years 
-as depicted in Figure~\ref{fig:survey_exp}. They are active users and
-regularly answer questions on Stack Overflow.
-Eighty one and sixty percent of users from Group 1 and Group 2 
-answer questions at least once a week.
+as depicted in Figure~\ref{fig:survey_exp}.
+There are 59\% of the answerers in Group 1 that have more than 10 year of software development experience, while a slightly less percentage of 50\% in Group 2.
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How frequently do or did you answer questions on Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
+The participants are active users and regularly answer questions on Stack Overflow (see Figure~\ref{fig:survey_answer_frequency}).
+Ninety two (81\%) and fifty one (61\%) of answerers from Group 1 and Group 2  answer questions at least once a week.
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How frequently do or did you include code snippets in your answers on Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
+More than half of the answerers very frequently (81--100\% of the time) or frequently (61--80\% of the time) include code snippets in their answers.
+To break down into two groups as depicted in Figure~\ref{fig:survey_answer_frequency_with_code},
+Group 1 very frequently (48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise, Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).
 
-\subsection{RQ1: Where are the code snippets in Stack Overflow answers from?}
+%\subsubsection*{How frequently do or did you answer questions on Stack Overflow?}
 
-To answer this research question, we ask the participants this question:
+\begin{figure}
+		\centering
+		\includegraphics[width=0.8\linewidth]{survey_answer_frequency}
+		\caption{Frequency of answering questions}
+		\label{fig:survey_answer_frequency}
+\end{figure}
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Where did the code snippets in your answers come from?}
-	}%
-}
-\vspace{0.5cm}
+%\subsubsection*{How frequently do or did you include code snippets in your answers on Stack Overflow?}
 
-From the answers, a large amount of 91 (81\%) and 58
-(68\%) answerers in both group include code snippets in more than sixty percent of
-their answers. Figure~\ref{fig:survey_snippet_source} explains where are these code
-snippets from. Stack Overflow answerers mostly write new code from scratch 
-or modify from the code snippets in question for each answer, while 
-fewer numbers are from other sources including their personal projects, 
-their company projects, open source projects. We found 27 answerers in both Group 1
-and Group 2 occasionally to very frequently copy code from open source projects.
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=\linewidth]{survey_answer_frequency_with_code_1}
+		\caption{Group 1}
+		\label{fig:survey_answer_frequency_with_code_1}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=0.9\linewidth]{survey_answer_frequency_with_code_2}
+		\caption{Group 2}
+		\label{fig:survey_answer_frequency_with_code_2}
+	\end{subfigure}
+	\caption{Frequency of answering questions with code snippet(s)}
+	\label{fig:survey_answer_frequency_with_code}
+\end{figure}
+
+\subsubsection*{RQ1: Where are the code snippets in Stack Overflow answers from?}
+
+To answer this research question, we ask the participants of the original
+sources for their code examples. We provided six options (allowing more than one answer)
+including \textit{I copied them from my own personal projects}, \textit{I copied
+	them from my company's projects}, \textit{I copied them from open source
+	projects}, \textit{I wrote the new code from scratch}, \textit{I copied the code
+	from the question and modify it for the answer}, and \textit{Others}. From the
+answers (Figure~\ref{fig:survey_snippet_source}), Stack Overflow answerers
+in Group 1 mainly write new code from scratch (112) or copy from the code snippets in question
+and modify it for the answer (108), followed by from their personal
+projects (101), open source projects (73), other sources (57), and company projects (46). 
+For Group 2, the most selected option is also writing code from scratch (83), followed by copying
+from personal projects and modifying from the question (77), copying from open source projects (56),
+copying from other sources (40), and copying from company projects (31).
 
@@
 
-\begin{figure}
-	\begin{subfigure}{5\textwidth}
-		\centering
-		\includegraphics[width=.6\linewidth]{survey_license_1}
-		\caption{Group 1}
-		\label{fig:survey_license_1}
-	\end{subfigure}%
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.6\linewidth]{survey_license_2}
-		\caption{Group 2}
-		\label{fig:survey_license_2}
-	\end{subfigure}
-	\caption{Software license in Stack Overflow code snippets.}
-	\label{fig:survey_license}
-\end{figure}
-
-\subsection{RQ2: Are Stack Overflow answerers aware of outdated code in their answers?}
-
 \vspace{0.5cm}
 \noindent\fbox{%
-	\parbox[c][1cm]{0.98\textwidth}{%
-		\textit{Outdated code occurs when code snippets in your answers are no longer up-to-date with the latest version of the software you copied the code from.
-Have you ever been notified of outdated code in your Stack Overflow answers?}
+	\parbox[c][1.5cm]{0.98\textwidth}{%
+		\textit{For research question 1, we found almost every answerer writes the new code from scratch or modifies from the code in question most of the time.
+Other less popular choices include copying code from their personal projects, and open source projects.
+Company projects are the least popular choice.}
 	}%
@@
 
-We found that 63.1\% of Stack Overflow answerers in Group 1 have been notified of
-outdated code in their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 47.6\% in
-Group 2. Thus, at least roughly half of the top answerers on Stack Overflow
-are aware of their outdated code in some of their answers.
+\subsection{RQ2: Are Stack Overflow answerers aware of outdated code in their answers?}
+
+Roughly half of the top answerers on Stack Overflow
+are aware of outdated code in their answers. We found that 72.3\% of Stack Overflow answerers in Group 1 have been notified of
+outdated code in at least one of their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 57.1\% in
+Group 2.
 
@@
 	\label{fig:survey_outdated}
-\end{figure}%
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How frequently were you notified of outdated or deprecated code in your Stack
-			Overflow answers?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How frequently did you fix your outdated code on Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
-
-We then asked the participants to have been notified of their outdated code
-(80 and 48 participants from Group 1 and 2 respectively) a
-follow-up questions ``how frequently did you fix your outdated code on Stack
-Overflow?''. The answers, depicted in Figure~\ref{fig:survey_outdated_fix}, show that
-more than half of them frequently fix the outdated code snippets. However, there
-are 18.8\% of the answerers in both groups who rarely or never fix their code.
+\end{figure}
 
@@
 		\centering
-		\includegraphics[width=.9\linewidth]{survey_outdated_fix_1}
+		\includegraphics[width=.8\linewidth]{survey_outdated_fix_1}
 		\caption{Group 1}
@@
 		\centering
-		\includegraphics[width=.9\linewidth]{survey_outdated_fix_2}
+		\includegraphics[width=.8\linewidth]{survey_outdated_fix_2}
 		\caption{Group 2}
@@
 
-\subsection{RQ2: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}
+We then asked the participants who have been notified of their outdated code
+(81 and 48 participants from Group 1 and 2 respectively) a
+follow-up questions \textit{``how frequently did you fix your outdated code on Stack
+Overflow?''} The answers, depicted in Figure~\ref{fig:survey_outdated_fix}, show that
+more than half of them frequently fix the outdated code snippets. However, there
+are 19.8\% and 18.8\% of the answerers in Groups 1 and 2 who rarely or never fix their code.
 
@@
 \noindent\fbox{%
-	\parbox[c][1cm]{0.98\textwidth}{%
-		\textit{Were you aware, at the time of copying the code, that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets?}
+	\parbox[c][1.2cm]{0.98\textwidth}{%
+		\textit{For research question 2, we found that the majority of Stack Overflow answerers are aware of outdated code in their answers and fixed them.
+Nonetheless, there are approximately 19\% of the answerers who rarely or never fix their outdated code.}
 	}%
@@
 
-More than half of the answerers in both groups (63.1\% and 61.9\% respectively)
-are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0
-Unported (CC BY-SA 3.0) to content in the posts, including code snippets, while
-the rest of 36.9\% and 38.1\% are not. Nevertheless, we found that almost all 
-of them do not include license statement in their code snippets (as depicted in
-Figure~\ref{fig:survey_license}) due to several reasons. First, some answerers chose to 
-post only their own code or code that was adapted from the question, hence
-they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
-company or open source projects that they knew were permitted to be publicly distributed.
-Third, some answerers believe that code snippets in their answers are too small 
-to claim any intellectual property on them and fall under fair use~\citep{fairuse}.
+\subsubsection*{RQ2: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Do you usually include a software license in your code snippets on Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
+As shown in Figure~\ref{fig:survey_license_known}, more than half of the
+answerers in both groups (63.4\% and 61.9\% respectively) are aware that Stack
+Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA
+3.0) to content in the posts, including code snippets, while the rest of 36.6\%
+and 38.1\% are not.
+
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.4\linewidth]{survey_license_known_1}
+		\caption{Group 1}
+		\label{fig:survey_license_known_1}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.4\linewidth]{survey_license_known_2}
+		\caption{Group 2}
+		\label{fig:survey_license_known_2}
+	\end{subfigure}
+	\caption{Awareness of answerers to Stack Overflow CC BY-SA 3.0 license}
+	\label{fig:survey_license_known}
+\end{figure}
+
+In addition, we found that almost all of the answerers in both groups (98\% and
+99\% respectively) do not include license statement in their code snippets
+(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
+gave more information regarding this question in the open comment question and
+we summarised them into three groups as follows. First, some answerers chose to post only their
+own code or code that was adapted from the question. They are hence
+automatically subjected to CC BY-SA 3.0. Second, they copied code from company
+or open source projects that they knew were permitted to be publicly
+distributed. Third, some answerers believe that code snippets in their answers
+are too small to claim any intellectual property on them and fall under fair
+use~\citep{fairuse}.
+
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.4\linewidth]{survey_license_1}
+		\caption{Group 1}
+		\label{fig:survey_license_1}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.4\linewidth]{survey_license_2}
+		\caption{Group 2}
+		\label{fig:survey_license_2}
+	\end{subfigure}
+	\caption{Software license in Stack Overflow code snippets.}
+	\label{fig:survey_license}
+\end{figure}
 
@@
 		\centering
-		\includegraphics[width=.85\linewidth]{survey_license_check_1}
+		\includegraphics[width=.75\linewidth]{survey_license_check_1}
 		\caption{Group 1}
@@
 		\centering
-		\includegraphics[width=.85\linewidth]{survey_license_check_2}
+		\includegraphics[width=.75\linewidth]{survey_license_check_2}
 		\caption{Group 2}
@@
 \subsubsection{Visitors' Experience}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{How long have you been working on developing software?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{When you had a problem with your programming tasks, please rank in which order did you search for help (1 for the first, and 5 for the last, without a tie)?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{How frequently do or did you copy source code snippets from Stack Overflow?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{Why did you copy and reuse code snippets from Stack Overflow?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{Have you ever found any problems from reusing Stack Overflow code snippets?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{How frequently did you find problems from reusing Stack Overflow code snippets?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{What were the problems?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{How frequently did you report the problems back to the Stack Overflow discussion threads?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{How did you report the problems?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{Were you aware, at the time of copying the code, that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{How often did you give attribution (adding a link to a Stack Overflow question/answer) as required by CC BY-SA 3.0 in the code where you used the snippet?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{Have you ever checked if the Stack Overflow code snippet originated from a different source (e.g. an open source project) with an incompatible license to your project?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{How often did you check for licensing conflicts of code snippets from Stack Overflow and your project(s) before using them?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{How frequently did you have legal problems by copying code snippets from Stack Overflow?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{Could you please briefly explain what are the legal problems that you faced by copying code snippets from Stack Overflow?}
+	}%
+}
+\vspace{0.5cm}
+
+\vspace{0.5cm}
+\noindent\fbox{%
+	\parbox[c][0.5cm]{0.98\textwidth}{%
+		\textit{Did you have any other problems from using code snippets from Stack Overflow?}
+	}%
+}
+\vspace{0.5cm}
 

### 2017-08-22 cloverflow_technical_report/cloverflow_survey_rn.tex
Small fix.

@@
 
-In addition, we found that almost all of the answerers in both groups (98\% and
+In addition, we found that almost every answerer in both groups (98\% and
 99\% respectively) do not include license statement in their code snippets

### 2017-08-22 cloverflow-tse/survey_snippet_source.m
Updated the number in stacked bar chart.

@@ -1,13 +1,19 @@
-group1 = [14 20 19 10 14 7; 3 5 9 0 14 53; 
-    5 6 16 13 16 28; 36 38 7 1 1 1; 
-    24 28 16 5 4 7; 1 2 14 6 17 44];
+group1 = [13 20 30 20 18; 
+    1 5 12 15 13; 
+    4 8 15 18 28; 
+    67 32 10 1 2; 
+    42 26 19 10 11; 
+    2 4 23 8 20];
 
-group2 = [13 20 30 19 18 11; 1 5 12 14 13 66; 
-    4 8 15 17 28 39; 66 32 10 1 2 0; 
-    42 26 18 10 11 4; 2 4 23 8 20 54];
+group2 = [14 20 19 10 14; 
+    3 5 9 0 14; 
+    5 6 16 13 16; 
+    36 38 7 1 1; 
+    24 28 16 5 4; 
+    1 2 14 6 17];
 
-bar_handle = bar(group1,'grouped');
-ylim([0 70])
+bar_handle = bar(group2,'stacked');
+ylim([0 120])
 ylabel('Amount','FontSize',16);
 xticklabels({'Personal projects', 'Company projects', 'Open source projects', 'Write from scratch', 'Modify from questions', 'Others'});
 xtickangle(30);
@@ -16,6 +22,6 @@ grid on
 
 l = cell(1,6);
 l{1}='Very frequently'; l{2}='Frequently'; l{3}='Occasionally'; l{4}='Rarely'; l{5}='Very rarely'; l{6}='Never';
-legend(bar_handle,l,'Location','Northwest','fontsize',12);
+legend(bar_handle,l,'Location','Northeast','fontsize',12);
 
 % print('survey_snippet_source','-dpdf','-bestfit')

### 2017-08-23 cloverflow_technical_report/cloverflow_survey_rn.tex
Another update to the technical report.

@@
 \usepackage{verbatim}
+\usepackage{enumitem}
 \usepackage{url}
@@
 
-\author{Chaiyong~Ragkhitwetsagul, Jens~Krinke, Mathues~Paixao,~Giuseppe Bianco, Rocco~Oliveto}
+\author{Chaiyong~Ragkhitwetsagul, Jens~Krinke}
 
@@
 \begin{enumerate}
-	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{where are the code snippets in Stack Overflow answers from?}
-	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{are Stack Overflow answerers aware of outdated code in their answers?}
-	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to software licensing conflicts):} \textit{are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}
-	\item \textbf{RQ4 (Awareness of Stack Overflow visitors to outdated code):} \textit{are Stack Overflow visitors aware of outdated code on Stack Overflow?}
-	\item \textbf{RQ5 (Awareness of Stack Overflow visitors to software licensing conflicts):} \textit{are Stack Overflow visitors aware of of software licensing conflicts caused by reusing code snippets from Stack Overflow?}
+	\item \textbf{RQ1 (Sources of Stack Overflow Answer Snippets):} \textit{Where are the code snippets in Stack Overflow answers from?}
+	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
+	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
+%	\item \textbf{RQ4(Awareness of Stack Overflow visitors to outdated code):} \textit{Are Stack Overflow visitors aware of outdated code on Stack Overflow?}
+%	\item \textbf{RQ5 (Awareness of Stack Overflow visitors to software licensing conflicts):} \textit{Are Stack Overflow visitors aware of of software licensing conflicts caused by reusing code snippets from Stack Overflow?}
 \end{enumerate}
@@
 \section{Research Methodology}
-The study is performed using online surveys. We designed the surveys using
+The study is performed using an online survey. We designed the survey using
 Google Forms by following the principles of survey research
-by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. We created two versions of the
-survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. The
-surveys are completely anonymous and the participants could decide to leave at
-any time. They do not collect any sensitive personal information from the
+by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. 
+%We created two versions of the
+%survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. 
+The survey is completely anonymous and the participants could decide to leave at
+any time. It does not collect any sensitive personal information from the
 participants and were approved for an ethical waiver by the designated ethics
-officer in the Computer Science Department at UCL.  The complete versions of
-both surveys can be found in the Appendix A and B.
+officer in the Computer Science Department at UCL.  The complete version of
+the survey can be found in the Appendix~\ref{appendixA}.
+
+\subsection{The Survey Design}
+The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
+questions, 3 yes/no questions, and one open-ended question for additional
+comments. The first two questions were mandatory while the other 9 questions
+were shown to the participants based on their previous answers. The survey collects
+information of the participant's software development experience, experience of
+answering Stack Overflow questions, sources of the Stack Overflow snippets,
+concerns of copying code snippets to Stack Overflow, problems from code 
+snippets on Stack Overflow, fixing outdated code, and additional feedbacks.
+
+\subsection{Participants}
 
@@
 \end{table}
-
-\subsection{The Answerer Survey}
-The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
-questions, 3 yes/no questions, and one open-ended question for additional
-comments. The first two questions were mandatory while the other 9 questions
-were shown to the participants based on their previous answers. The survey collects
-information of the participant's software development experience, experience of
-answering Stack Overflow questions, sources of the Stack Overflow snippets,
-concerns of copying code snippets to Stack Overflow, problems from code 
-snippets on Stack Overflow, fixing outdated code, and additional feedbacks.
 
@@
 
-\subsection{The Visitor Survey}
-
-The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
-questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
-questions. The first four questions were mandatory while the other 12 questions
-were shown to the participants based on their previous answers. The survey collects
-information of the participant's software development experience, importance of
-Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
-Stack Overflow snippets, licensing of code on Stack Overflow, and additional
-feedbacks.
-
-\begin{table}
-	\centering
-	\caption{The Stack Overflow visitors taken the survey}
-	\label{tab:visitors}
-	\begin{tabular}{lr}
-		\toprule
-		Invitation channels & Answers \\
-		\midrule
-		Chaiyong's Facebook post & 47 \\
-		Blognone.com & 32 \\
-		University of Molise & 6 \\
-		comp.lang.java.programmer & 3 \\
-		Software Engineering Facebook page & 1 \\
-		\midrule
-		Total & 89 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-The participants for this survey were invited to take the survey via five
-channels. The first channel is via the first author's Facebook post where the
-first author invited friends who are software developers and have experience of
-copying code snippets from Stack Overflow to take the survey. The second channel
-is a popular Thai technology news and media community called blognone.com which
-attracts a high number of software developers. The first author posted an
-invitation to the visitor survey in a discussion forum. The third channel
-collects answers from University of Molise which is the third author's
-workplace. The last two channels are from a comp.lang.java.programmer Google
-groups and Software Engineering Facebook page. The survey was open for
-participation for a month, from 25 July 2017 to 25 August 2017, before we
-collected and analysed the responses. The number of participants taken the
-survey are shown in Table~\ref{tab:visitors}.
+%\subsection{The Visitor Survey}
+%
+%The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
+%questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
+%questions. The first four questions were mandatory while the other 12 questions
+%were shown to the participants based on their previous answers. The survey collects
+%information of the participant's software development experience, importance of
+%Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
+%Stack Overflow snippets, licensing of code on Stack Overflow, and additional
+%feedbacks.
+%
+%\begin{table}
+%	\centering
+%	\caption{The Stack Overflow visitors taken the survey}
+%	\label{tab:visitors}
+%	\begin{tabular}{lr}
+%		\toprule
+%		Invitation channels & Answers \\
+%		\midrule
+%		Chaiyong's Facebook post & 47 \\
+%		Blognone.com & 32 \\
+%		University of Molise & 6 \\
+%		comp.lang.java.programmer & 3 \\
+%		Software Engineering Facebook page & 1 \\
+%		\midrule
+%		Total & 89 \\
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
+%
+%The participants for this survey were invited to take the survey via five
+%channels. The first channel is via the first author's Facebook post where the
+%first author invited friends who are software developers and have experience of
+%copying code snippets from Stack Overflow to take the survey. The second channel
+%is a popular Thai technology news and media community called blognone.com which
+%attracts a high number of software developers. The first author posted an
+%invitation to the visitor survey in a discussion forum. The third channel
+%collects answers from University of Molise which is the third author's
+%workplace. The last two channels are from a comp.lang.java.programmer Google
+%groups and Software Engineering Facebook page. The survey was open for
+%participation for a month, from 25 July 2017 to 25 August 2017, before we
+%collected and analysed the responses. The number of participants taken the
+%survey are shown in Table~\ref{tab:visitors}.
 
@@
 
-\subsection{Answerer Responses}
+%\subsection{Answerer Responses}
 We received 113 answers (38\% response rate) from the first group and 85 answers
@@
 	\parbox[c][1.5cm]{0.98\textwidth}{%
-		\textit{For research question 1, we found almost every answerer writes the new code from scratch or modifies from the code in question most of the time.
+		\textit{For RQ 1, we found almost every answerer writes the new code from scratch or modifies from the code in question most of the time.
 Other less popular choices include copying code from their personal projects, and open source projects.
@@
 
-\subsection{RQ2: Are Stack Overflow answerers aware of outdated code in their answers?}
+\subsubsection*{RQ2: Are Stack Overflow answerers aware of outdated code in their answers?}
 
@@
 	\parbox[c][1.2cm]{0.98\textwidth}{%
-		\textit{For research question 2, we found that the majority of Stack Overflow answerers are aware of outdated code in their answers and fixed them.
+		\textit{For RQ 2, we found that the majority of Stack Overflow answerers are aware of outdated code in their answers and fixed them.
 Nonetheless, there are approximately 19\% of the answerers who rarely or never fix their outdated code.}
@@
 
-\subsubsection*{RQ2: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}
+\subsubsection*{RQ3: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}
 
@@
 
+We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0.
+As shown in Figure~\ref{fig:survey_license_check}, 67.9\% -- 69\% of answerers from both groups did not perform the checking.
+There are only approximately 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.
+
 \vspace{0.5cm}
 \noindent\fbox{%
-	\parbox[c][1cm]{0.98\textwidth}{%
-		\textit{How frequently did you check the software license of the code snippets you copy to Stack Overflow if they conflict with Stack Overflow's CC BY-SA 3.0 license? }
+	\parbox[c][1.5cm]{0.98\textwidth}{%
+		\textit{For RQ3, approximately 60\% of answerers are aware of CC BY-SA 3.0 license enforced by Stack Overflow.
+However, 98--99\% of the answerers do not include software license in their Stack Overflow snippets nor check for licensing conflicts when they copy code snippets to Stack Overflow answers.}
 	}%
@@
 
-We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0.
-As shown in Figure~\ref{fig:survey_license_check}, approximately 69\% of answerers from both groups did not perform the checking.
-Nonetheless, they are about 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.
+In addition, we invited the answerers to give comments regarding their concerns when answering Stack Overflow (SO) with code snippets.
+Some interesting comments are selected and discussed belwo.
+The full set of answers can be found in the Appendix~\ref{appendixC}.
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Do you have any other concerns regarding answering Stack Overflow with code snippets?}
-	}%
-}
-\vspace{0.5cm}
+\begin{itemize}[label={}]
+	\itemsep1em
+	\item Comment 1: The answerer addresses a concern of reusing the code snippet without understanding.
+Moreover, he or she discusses a ramification of low-quality snippets or outdated code containing security issues.
 
-We also invited the participants to give any comments regarding answering Stack Overflow with code snippets. These are some interesting comments we received.
+	\begin{quote}\textit{The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software ``professionals'' that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.
+A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about.
+Think PHP/MySQL tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}).
+They're also full of toxic code snippets.}\end{quote}
 
-Comment 1: ``The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software "professionals" that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.
-A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about.
-Think php/mysql tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}).
-They're also full of toxic code snippets.''
+	\item Comment 2: The answerer suggests that a guidance from Stack Overflow regarding software license will be beneficial.
 
-Comment 2: ``When I copy code it's usually short enough to be considered "fair use" but I am not a lawyer or copyright expert so some guidance from SO would be helpful.
-I'd also like the ability to flag/review questions that violate these guidelines.''
+	\begin{quote}\textit{When I copy code it's usually short enough to be considered ``fair use'' but I am not a lawyer or copyright expert so some guidance from SO would be helpful.
+I'd also like the ability to flag/review questions that violate these guidelines.}\end{quote}
 
-Comment 3: ``My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.''
+	\item Comment 3: The answerer addresses a concern of code understanding.
 
-Comment 4: ``The main problem for me/us is outdated code, esp.
-as old answers have high google rank so that is what people see first, then try and fail.
-Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.''
+	\begin{quote}\textit{My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.}\end{quote}
 
-Comment 5: ``Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).''
+	\item Comment 4: The answerer discusses a problem from outdated code and his/her solution.
 
-\subsubsection{Visitors' Experience}
+	\begin{quote}\textit{The main problem for me/us is outdated code, esp.
+as old answers have high Google rank so that is what people see first, then try and fail.
+Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.}\end{quote}
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How long have you been working on developing software?}
-	}%
-}
-\vspace{0.5cm}
+	\item Comment 5: The answerers gives insights into the quality of the Stack Overflow code snippets.
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{When you had a problem with your programming tasks, please rank in which order did you search for help (1 for the first, and 5 for the last, without a tie)?}
-	}%
-}
-\vspace{0.5cm}
+	\begin{quote}\textit{Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).}\end{quote}
+\end{itemize}
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How frequently do or did you copy source code snippets from Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Why did you copy and reuse code snippets from Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Have you ever found any problems from reusing Stack Overflow code snippets?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How frequently did you find problems from reusing Stack Overflow code snippets?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{What were the problems?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How frequently did you report the problems back to the Stack Overflow discussion threads?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How did you report the problems?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Were you aware, at the time of copying the code, that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How often did you give attribution (adding a link to a Stack Overflow question/answer) as required by CC BY-SA 3.0 in the code where you used the snippet?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Have you ever checked if the Stack Overflow code snippet originated from a different source (e.g. an open source project) with an incompatible license to your project?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How often did you check for licensing conflicts of code snippets from Stack Overflow and your project(s) before using them?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{How frequently did you have legal problems by copying code snippets from Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Could you please briefly explain what are the legal problems that you faced by copying code snippets from Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
-
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][0.5cm]{0.98\textwidth}{%
-		\textit{Did you have any other problems from using code snippets from Stack Overflow?}
-	}%
-}
-\vspace{0.5cm}
+%\subsection{Visitor Responses}
+%
+%To answer RQ4 and RQ5, we ask Stack Overflow visitors about their experiences of outdated code and their awareness to software license of Stack Overflow code snippets.
+We received 89 answers from 5 groups of Stack Overflow visitors.
+The combined results and discussions are presented below.
+%
+%\subsubsection*{RQ4: Are Stack Overflow visitors aware of outdated code on Stack Overflow?}
+%
+%We asked the visitors whether they have any problem from reusing Stack Overflow code snippets and how often did the problems occur. 
+%
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=.5\linewidth]{survey_v_problems}
+%	\caption{Number of visitors who experienced a problem from reusing Stack Overflow code snippets.}
+%	\label{fig:survey_v_problems}
+%\end{figure}
+%
+%
+%\vspace{0.5cm}
+%\noindent\fbox{%
+%	\parbox[c][0.5cm]{0.98\textwidth}{%
+%		\textit{For RQ4, }
+%	}%
+%}
+%\vspace{0.5cm}
+%
+%\subsubsection*{RQ5: Are Stack Overflow visitors aware of software licensing of code snippets from Stack Overflow?}
+%
+%\vspace{0.5cm}
+%\noindent\fbox{%
+%	\parbox[c][0.5cm]{0.98\textwidth}{%
+%		\textit{For RQ5, }
+%	}%
+%}
+%\vspace{0.5cm}
 
@@
 \section{Appendix}
+
+This appendix contains additional materials of the Stack Overflow answerer survey questions, the visitor survey questions, and the complete set of open comments from the Stack Overflow answerers.
+
+\clearpage
+
 \appendix
-\section{Stack Overflow Answerer Survey}
+\section{Stack Overflow Answerer Survey}\label{appendixA}
 \begin{figure}[H]
@@
 
-\section{Stack Overflow Visitor Survey}
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.85\linewidth]{visitor-1}
-	\label{fig:visitor-1}
-\end{figure}
+%\section{Stack Overflow Visitor Survey}\label{appendixB}
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.85\linewidth]{visitor-1}
+%	\label{fig:visitor-1}
+%\end{figure}
+%
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.9\linewidth]{visitor-2}
+%	\label{fig:visitor-2}
+%\end{figure}
+%
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.9\linewidth]{visitor-3}
+%	\label{fig:visitor-3}
+%\end{figure}
+%
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.9\linewidth]{visitor-4}
+%	\label{fig:visitor-4}
+%\end{figure}
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.9\linewidth]{visitor-2}
-	\label{fig:visitor-2}
-\end{figure}
+\section{Open Comments from Stack Overflow Answerers}\label{appendixC}
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.9\linewidth]{visitor-3}
-	\label{fig:visitor-3}
-\end{figure}
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.9\linewidth]{visitor-4}
-	\label{fig:visitor-4}
-\end{figure}
+\begin{enumerate}
+	\itemsep1em
+	\item Sometimes you have to post code from official documentation, like in case of C\#, code form MSDN is posted in the answer with added explanation.
+	\item Snippets on SO are usually for demonstrating a technique and therefore age well. If otherwise, I usually made them a gist, codebin or jsfiddle.
+	\item The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software ``professionals'' that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.
+	\item A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about.
+Think PHP/MySQL tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}).
+They're also full of toxic code snippets.
+	\item Just to say: the reason that I very rarely check the license status is that the code I am posting is almost always my own or adapted from the question, or imported from an open source project that I have worked on and already know the license terms, or from my own company code that I can 100\% say it is OK to post in public because I know our policies.
+	\item No. Code snippets are short and small enough that no IP can be in them.
+	\item The point of snippets are that they are trivial.
+I mostly write from scratch or copy-\&-fix a snippet from the question.
+Most are illustrative or incomplete --- they aren't of any value at all in isolation.
+They rarely take more than a few minutes to write, and it's usually harder to explain what they're doing in plain English.
+Where something is large enough to worth the effort of licensing then it's far too big for a snippet.
+In those cases I create a GitHub project (with a license) and link to it.
+I'd be wary of increased IP controls --- I doubt there is value they could add to snippets, but they could create significant barriers to contributors, which would hurt the site.
+	\item I always try to see what kind of person is asking the question.
+If it is a student, I don't want to just hand out the answer; they will learn nothing from that.
+If, on the other hand, it's somebody looking for best practices or a clever trick, I'm not too worried about giving out the solution.
+In this case, chances are much higher that the person asking the question will go ``Ahh, yes, of course!'' and understand the question, whereas some students are more likely to mindlessly copy-paste the answer.
+	\item However, it is also a competitive site, so if your answer requires too much work to incorporate, it won't get accepted or upvoted.
+As a result, some people---I'm guilty of this myself, I'm sure---will hand out an answer willy-nilly that might solve the problem at hand, but in the long run be a disservice to the person asking.
+	\item But I digress: My point is that it's sometimes better to describe a solution rather than just hand off a code snippet.
+However, since your project seems to pertain to copyright issues, I suppose that's not relevant to you.
+	\item I'm not sure it's possible to include a license in your questions/answers.
+I'm not sure what the legal ramifications would be if you tried it, since you already agreed to S.O.'s terms.
+This is a very interesting question and I look forward to hearing the results of your research.
+	\item I think it's important to realise the code snippets are designed to be very small, useful to illustrate concepts (10 lines or less).
+When you consider licensing laws of such a small amount of code, while technically may be violating a licence, in practice it would be nearly impossible to enforce such a claim.
+	\item SO code snippets are great but there is lot to improve .
+It's hard to edit and see output in so but website like jsfiddle , jsbin provide nice interface where code editing and output is easy to do.
+	\item Outer thing is in so lot of code snippets doesn't work because some users don't add libraries like angular, jquery.
+I think it's better if we can identify and ask user to auto inject relevant libraries.
+	\item Code snippets are usually just a few lines of code so it will be hard to enforce any copyright claims except when it is a method used for something company-specific (such as generating encryption keys).
+Regardless, since most of the code I write is specifically to answer a given question and having full knowledge of the license system used by Stack Overflow, it is entirely unimportant to concern myself with licensing the code provided.
+Also, code from MSDN documentation which I sometimes adapt and modify for answers are already in the public domain so it makes no sense re-licensing it.
+	\item On the matter of deprecation, I almost entirely use .NET which has got different versions of the framework.
+Therefore, code deprecation is not often a problem since what is deprecated on one version of the framework may be the only way of solving a given problem on an older version of the framework.
+I may also have to add that questions I tend to answer are about how to solve general coding problems so they are not usually subject to deprecation.
+	\item I think you're forgetting the fact that as a community, we want to share knowledge.
+Patents, copyright issues and so on --- it's all just annoying.
+We're there to have fun and to share knowledge with people.
+	\item In the early days, the internet used to be full of free-for-all stuff without any licenses.
+Because of that, it was a fantastic tool to share knowledge and information on a vast scale.
+The remnant of this, open source, couldn't have existed without this!
+	\item Personally, I believe this ``intellectual property'' drive of the last decade is completely overrated.
+If you make something \textbf{substantial}, it's fine to be able to claim some ownership --- but on snippets?
+It's like patenting the stuff you make in your free time in your shed...
+it doesn't make sense and just adds to the pile of legal bullshit imho.
+	\item No. I only put code on there that I have the right to (code I created or have permission to share). Adding the code is not an issue for me.
+	\item When I copy code it's usually short enough to be considered ``fair use'' but I am not a lawyer or copyright expert so some guidance from SO would be helpful.
+I'd also like the ability to flag/review questions that violate these guidelines.
+	\item The snippets are all small enough that I reckon they fall under fair use.
+	\item I always try and attribute the code I take from other places.
+I feel pointing back to the origin should be sufficient in terms of giving credit where it's due.
+Open source is about the sharing of ideas so that others can build on them.
+Education is a primary use case of open source in my opinion.
+	\item My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.
+	\item This survey may be inapplicable to me because I never copy code from existing projects.
+	\item Stack Overflow did an effort to apply a MIT license to all code snippets, while keeping CC-SA for the text content. Too bad they didn't succeed with it, as it would have solved many issues.
+	\item The main problem for me/us is outdated code, esp.
+as old answers have high Google rank so that is what people see first, then try and fail.
+Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.
+	\item I've got no issues with code snippets on Stack Overflow, I think they are great. Any one using them should pay attention to details such as the date of the answer etc.
+	\item SO's license is not clearly explained when one registers or starts to answer questions.
+	\item No, most copied code snippets are so trivial that licensing them would be nearly impossible. It's also mostly modified version, where only some patterns are used.
+	\item Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).
+	\item I think most example and explanatory snippets don't need a code-specific license.
+The CC license provides just fine.
+The examples either aren't copyrightable in the first place, or merely used as starting point (not used exactly as-is, not very different from reading an ``All rights reserved'' education book when learning programming, and ``using'' it in your career every day going forward).
+In addition, there is also the attitude of authors.
+Where I might care about attribution for distribution of my answer, the code within my answer is always Public Domain for me, meaning, I would never defend it.
+(I used to state that on my profile as well, but not in every post.)
+	\item Correctness and even syntax are often in doubt if I haven't had time to test the snippet end-to-end under the OP's conditions/environment.
+	\item It will be awesome if it becomes simple git repositories like github's gist.
+	\item Note that although I was not specifically of SO's licensing terms, I did have an in mind what those terms were likely to be.
+I have always made sure that there should be no reason that I should not share the code that I included in my replies.
+	\item It's an ESSENTIAL part of the site, it would NEVER work without such pieces of code.
+Also, given the snippets are very small in 99.99\% of cases, legal aspects of this are inherently and pretty much always overlooked by the users.
+\end{enumerate}
 

### 2017-08-28 cloverflow_technical_report/cloverflow_survey_rn.tex
Latest update of the technical report.

@@
 the answerers the origins of source code snippets in their answers  and assess
-their awareness of outdated and licensed code. We use the term ``visitors'' the
-refer to developers, who may or may not have a Stack Overflow account but visit
-Stack Overflow when facing programming problems. They copy example code snippets
-that are relevant to their problems and reused them in their software. 
-We ask Stack Overflow visitors, who copied code snippets from
-Stack Overflow, about their experience of outdated or license-violating code.
+their awareness of outdated and licensed code. 
+%We use the term ``visitors'' the
+%refer to developers, who may or may not have a Stack Overflow account but visit
+%Stack Overflow when facing programming problems. They copy example code snippets
+%that are relevant to their problems and reused them in their software. 
+%We ask Stack Overflow visitors, who copied code snippets from
+%Stack Overflow, about their experience of outdated or license-violating code.
 
@@
 
+We present our online survey results of Stack Overflow answerers in terms of their awareness to outdated code snippets and their software license.
+
 %\bibliographystyle{abbrv}

### 2017-09-13 cloverflow_technical_report/cloverflow_survey_rn.tex
Latest update to RN.

--- 2017-08-23 cloverflow_technical_report/cloverflow_survey_rn.tex
@@
 
-Outdated third-party code and software licensing conflicts are ramifications by
-reusing source code by copying and pasting (i.e.~code cloning). \cite{Xia2014}
-show that a large number of open source systems reuse outdated third-party
-libraries from popular open source projects. Using the outdated code give
-detrimental effects to the software since they may introduce vulnerabilities. On
-the other hand, \cite{German2009} found conflicts in software license between
-the clones among different systems that come from the same source,~i.e.~clone
-siblings.
+%This study is interested in the problem of outdated code and software licensing
+%violations caused by code cloning on Internet-based question and answer
+%websites. 
+Recent research shows that outdated third-party code and software
+licensing conflicts are ramifications by reusing source code by copying and
+pasting (i.e.~code cloning). \cite{Xia2014} report that a large number of open
+source systems reuse outdated third-party libraries from popular open source
+projects. Using the outdated code give detrimental effects to the software since
+they may introduce vulnerabilities. On the other hand, \cite{German2009} found
+that code cloning leads to conflicts in software license among different
+systems.
 
-The Internet encourages fast and easy way of sharing and copying code.
-Developers nowadays do not only copy code from local software projects, but also
-from online sources such as programming Q\&A website and online code
-repositories. Stack Overflow is one of the most popular programming Q\&A
-websites in the word. It has 7.6 million users, 14 million questions, 23 million
-answers\footnote{Data as of 21 August 2017
+The Internet encourages fast and easy code cloning by sharing and copying code
+to and from online sources. Developers nowadays do not only clone code from local
+software projects, but also from online sources such as programming Q\&A website
+and online code repositories~\FIXME{Add citation}. Stack Overflow is one of the most popular
+programming Q\&A websites in the word. It has 7.6 million users, 14 million
+questions, 23 million answers\footnote{Data as of 21 August 2017
 	from~\url{https://stackexchange.com/sites}}, and more than 50 million developers
@@
 
-We are interested in studying the issues of outdated code and software license
-violation cause by code snippets on Stack Overflow. Asking and answering
+\textbf{We are interested in studying the issues of outdated code and software license
+violation cause by code snippets on Stack Overflow.} Asking and answering
 questions on Stack Overflow usually involve copying and pasting source code
@@
 snippets are copied from an open source system with stricter software license
-than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Before
-this study, we performed an preliminary study using code clone detection tools
+than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior to
+this study, we performed an empirical study using code clone detection tools
 to locate cloned code snippets in accepted answers. We found that many snippets
@@
 possibly violating the original software license. In either case, these snippets
-are potentially harmful for reuse. To accompany the findings and to gain
-insights into the cause of this problem, we resort to a qualitative study using
+are potentially harmful for reuse. To accompany the findings and gain
+insights into the cause of the problems, we resort to a qualitative study using
 an online survey of Stack Overflow developers who 1) answer programming
@@
 the answerers the origins of source code snippets in their answers  and assess
-their awareness of outdated and licensed code. We use the term ``visitors'' the
+their awareness of outdated and licensed code. 
+We use the term ``visitors'' the
 refer to developers, who may or may not have a Stack Overflow account but visit
@@
 \section{Research Questions}
-In this study, we would like to answer the following
-research questions:
+In this study, we would like to answer seven research questions listed below. The first three questions will be
+answered by the Stack Overflow answerer survey, while the last three questions will be answered by the
+Stack Overflow visitor survey.
 
@@
 	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
-%	\item \textbf{RQ4(Awareness of Stack Overflow visitors to outdated code):} \textit{Are Stack Overflow visitors aware of outdated code on Stack Overflow?}
-%	\item \textbf{RQ5 (Awareness of Stack Overflow visitors to software licensing conflicts):} \textit{Are Stack Overflow visitors aware of of software licensing conflicts caused by reusing code snippets from Stack Overflow?}
+	\item \textbf{RQ4 (Importance of Stack Overflow to developers):} \textit{Why developers choose to find programming solutions on Stack Overflow?}
+	\item \textbf{RQ5 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
+	\item \textbf{RQ6 (Awareness of Stack Overflow visitors to CC BY-SA 3.0 license):} \textit{Are Stack Overflow visitors aware of the the CC BY-SA 3.0 license enforced by Stack Overflow?}
+	\item \textbf{RQ7 (Software licensing issues from Stack Overflow code snippets):} \textit{How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
 \end{enumerate}
@@
 by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. 
-%We created two versions of the
-%survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. 
-The survey is completely anonymous and the participants could decide to leave at
+We created two versions of the
+survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. 
+The surveys are completely anonymous and the participants could decide to leave at
 any time. It does not collect any sensitive personal information from the
@@
 officer in the Computer Science Department at UCL.  The complete version of
-the survey can be found in the Appendix~\ref{appendixA}.
+the surveys can be found in the Appendix~\ref{appendixA}.
 
-\subsection{The Survey Design}
+\subsection{The Answerer Survey}
 The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
@@
 
-\subsection{Participants}
-
 \begin{table}
@@
 		\midrule
-		Answerer Group 1 & 963,731--7,674 & 300 & 113 & 38\% \\
+		Answerer Group 1 & 963,731--7,674 & 300 & 117 & 39\% \\
 		Answerer Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
 		\midrule
-		Total & -- & 607 & 198 & 33\% \\
+		Total & -- & 607 & 202 & 33\% \\
 		\bottomrule
@@
 
-%\subsection{The Visitor Survey}
-%
-%The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
-%questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
-%questions. The first four questions were mandatory while the other 12 questions
-%were shown to the participants based on their previous answers. The survey collects
-%information of the participant's software development experience, importance of
-%Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
-%Stack Overflow snippets, licensing of code on Stack Overflow, and additional
-%feedbacks.
-%
-%\begin{table}
-%	\centering
-%	\caption{The Stack Overflow visitors taken the survey}
-%	\label{tab:visitors}
-%	\begin{tabular}{lr}
-%		\toprule
-%		Invitation channels & Answers \\
-%		\midrule
-%		Chaiyong's Facebook post & 47 \\
-%		Blognone.com & 32 \\
-%		University of Molise & 6 \\
-%		comp.lang.java.programmer & 3 \\
-%		Software Engineering Facebook page & 1 \\
-%		\midrule
-%		Total & 89 \\
-%		\bottomrule
-%	\end{tabular}
-%\end{table}
-%
-%The participants for this survey were invited to take the survey via five
-%channels. The first channel is via the first author's Facebook post where the
-%first author invited friends who are software developers and have experience of
-%copying code snippets from Stack Overflow to take the survey. The second channel
-%is a popular Thai technology news and media community called blognone.com which
-%attracts a high number of software developers. The first author posted an
-%invitation to the visitor survey in a discussion forum. The third channel
-%collects answers from University of Molise which is the third author's
-%workplace. The last two channels are from a comp.lang.java.programmer Google
-%groups and Software Engineering Facebook page. The survey was open for
-%participation for a month, from 25 July 2017 to 25 August 2017, before we
-%collected and analysed the responses. The number of participants taken the
-%survey are shown in Table~\ref{tab:visitors}.
+\subsection{The Visitor Survey}
+
+The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
+questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
+questions. The first four questions were mandatory while the other 12 questions
+were shown to the participants based on their previous answers. The survey collects
+information of the participant's software development experience, importance of
+Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
+Stack Overflow snippets, licensing of code on Stack Overflow, and additional
+feedbacks.
+
+\begin{table}
+	\centering
+	\caption{The Stack Overflow visitors taken the survey}
+	\label{tab:visitors}
+	\begin{tabular}{lr}
+		\toprule
+		Invitation channels & Answers \\
+		\midrule
+		Social media (Facebook posts) & 47 \\
+		Blognone.com & 32 \\
+		University of Molise & 6 \\
+		comp.lang.java.programmer & 3 \\
+		Software Engineering Facebook page & 1 \\
+		\midrule
+		Total & 89 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+The participants for this survey were invited to take the survey via five
+channels. The first channel is via the first author's Facebook post where the
+first author invited friends who are software developers and have experience of
+copying code snippets from Stack Overflow to take the survey. The second channel
+is a popular Thai technology news and media community called blognone.com which
+attracts a high number of software developers. The first author posted an
+invitation to the visitor survey in a discussion forum. The third channel
+collects answers from University of Molise which is the third author's
+workplace. The last two channels are from a comp.lang.java.programmer Google
+groups and Software Engineering Facebook page. The survey was open for
+participation for a month, from 25 July 2017 to 25 August 2017, before we
+collected and analysed the responses. The number of participants taken the
+survey are shown in Table~\ref{tab:visitors}.
 
@@
 
-%\subsection{Answerer Responses}
-We received 113 answers (38\% response rate) from the first group and 85 answers
+\subsection{Answerer Responses}
+We received 117 answers (39\% response rate) from the first group and 85 answers
 (28\% response rate) from the second group of Stack Overflow answerers. The response
@@
 
-The majority of users in both groups are experienced developers 
-with more than 10 years of experience or between 5 to 10 years 
-as depicted in Figure~\ref{fig:survey_exp}.
-There are 59\% of the answerers in Group 1 that have more than 10 year of software development experience, while a slightly less percentage of 50\% in Group 2.
+The majority of users in both groups are experienced developers with more than
+10 years of experience or between 5 to 10 years as depicted in
+Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 that
+have more than 10 year of software development experience, while a slightly less
+percentage of 50\% in Group 2.
 
-The participants are active users and regularly answer questions on Stack Overflow (see Figure~\ref{fig:survey_answer_frequency}).
-Ninety two (81\%) and fifty one (61\%) of answerers from Group 1 and Group 2  answer questions at least once a week.
-
-More than half of the answerers very frequently (81--100\% of the time) or frequently (61--80\% of the time) include code snippets in their answers.
-To break down into two groups as depicted in Figure~\ref{fig:survey_answer_frequency_with_code},
-Group 1 very frequently (48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise, Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).
+The participants are active users and regularly answer questions on Stack
+Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty two (82\%) and
+sixty (60\%) of answerers from Group 1 and Group 2  answer questions at
+least once a week.
+More than half of the answerers very frequently (81--100\% of the time) or
+frequently (61--80\% of the time) include code snippets in their answers. To
+break down into two groups as depicted in
+Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
+(48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
+Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).
 
@@
 
-To answer this research question, we ask the participants of the original
-sources for their code examples. We provided six options (allowing more than one answer)
+To answer this research question, we ask the participants for original
+sources of their code examples. We provided six options (allowing more than one answer)
 including \textit{I copied them from my own personal projects}, \textit{I copied
@@
 	projects}, \textit{I wrote the new code from scratch}, \textit{I copied the code
-	from the question and modify it for the answer}, and \textit{Others}. From the
-answers (Figure~\ref{fig:survey_snippet_source}), Stack Overflow answerers
-in Group 1 mainly write new code from scratch (112) or copy from the code snippets in question
-and modify it for the answer (108), followed by from their personal
-projects (101), open source projects (73), other sources (57), and company projects (46). 
-For Group 2, the most selected option is also writing code from scratch (83), followed by copying
+	from the question and modify it for the answer}, and \textit{Others}. The
+answers are shown in Figure~\ref{fig:survey_snippet_source}. Participants
+in Group 1 mainly write new code from scratch (116) or copy from the code snippets in question
+and modify it for the answer (112), followed by from their personal
+projects (105), open source projects (77), other sources (59), and company projects (48). 
+For Group 2, the main source is also writing code from scratch (83), followed by copying
 from personal projects and modifying from the question (77), copying from open source projects (56),
@@
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][1.5cm]{0.98\textwidth}{%
-		\textit{For RQ 1, we found almost every answerer writes the new code from scratch or modifies from the code in question most of the time.
-Other less popular choices include copying code from their personal projects, and open source projects.
-Company projects are the least popular choice.}
-	}%
+\vspace{0.5cm} \noindent\fbox{%
+	\parbox[c][2cm]{0.98\textwidth}{%
+		\textit{For RQ 1, we found that answering questions by writing the new code from
+			scratch is the most popular choice for Stack Overflow answerers followed by modifying from the code in question, or copying from personal projects. Other less
+			popular choices include copying code from open
+			source projects and from other sources. Copying code from company projects are the least popular choice.} }%
 }
@@
 
-Roughly half of the top answerers on Stack Overflow
-are aware of outdated code in their answers. We found that 72.3\% of Stack Overflow answerers in Group 1 have been notified of
+Half of the top answerers on Stack Overflow
+are aware of outdated code in their answers. We found that 71.6\% of Stack Overflow answerers in Group 1 have been notified of
 outdated code in at least one of their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 57.1\% in
@@
 
-\vspace{0.5cm}
-\noindent\fbox{%
-	\parbox[c][1.2cm]{0.98\textwidth}{%
-		\textit{For RQ 2, we found that the majority of Stack Overflow answerers are aware of outdated code in their answers and fixed them.
-Nonetheless, there are approximately 19\% of the answerers who rarely or never fix their outdated code.}
-	}%
+\vspace{0.5cm} \noindent\fbox{%
+	\parbox[c][1cm]{0.98\textwidth}{%
+		\textit{For RQ 2, Stack Overflow answerers are aware of outdated code in their
+			answers. Nonetheless, there are approximately 19\% of the answerers who rarely
+			or never fix their outdated code.} }%
 }
@@
 
-\subsubsection*{RQ3: Are Stack Overflow answerers aware of software licensing conflicts caused by code snippets in their answers?}
+\subsubsection*{RQ3: Are Stack Overflow answerers aware of software licensing
+	conflicts caused by code snippets in their answers?}
 
 As shown in Figure~\ref{fig:survey_license_known}, more than half of the
-answerers in both groups (63.4\% and 61.9\% respectively) are aware that Stack
+answerers in both groups (62.1\% and 61.9\% respectively) are aware that Stack
 Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA
-3.0) to content in the posts, including code snippets, while the rest of 36.6\%
+3.0) to content in the posts, including code snippets, while the rest of 37.9\%
 and 38.1\% are not.
@@
 
-In addition, we found that almost every answerer in both groups (98\% and
-99\% respectively) do not include license statement in their code snippets
-(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
-gave more information regarding this question in the open comment question and
-we summarised them into three groups as follows. First, some answerers chose to post only their
-own code or code that was adapted from the question. They are hence
-automatically subjected to CC BY-SA 3.0. Second, they copied code from company
-or open source projects that they knew were permitted to be publicly
-distributed. Third, some answerers believe that code snippets in their answers
-are too small to claim any intellectual property on them and fall under fair
+Almost every answerer in both groups (98\% and 99\% respectively) does not
+include license statement in their code snippets (numbers are shown in
+Figure~\ref{fig:survey_license}). Some of the participants explain the reason in
+the open comment question which we summarised into three groups as follows.
+First, they choose to post only their own code or code that is adapted from the
+question. The code is automatically subjected to Stack Overflow's CC BY-SA 3.0.
+Second, they copy code from company or open source projects that they know are
+permitted to be publicly distributed. Hence, no license statement is required.
+Third, some answerers believe that code snippets in their answers are too small
+to claim any intellectual property on them and fall under fair
 use~\citep{fairuse}.
@@
 
-We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0.
-As shown in Figure~\ref{fig:survey_license_check}, 67.9\% -- 69\% of answerers from both groups did not perform the checking.
-There are only approximately 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.
+We asked the answerers a follow-up question of how frequently they checked for a
+conflict between software license of the code snippets they copied to their
+answers and Stack Overflow's CC BY-SA 3.0. As shown in
+Figure~\ref{fig:survey_license_check}, 69\% of answerers from both groups did
+not perform the checking. There are only approximately 10\% of the answerers who
+frequently checks for licensing conflicts when they copy code snippets to Stack
+Overflow.
 
-\vspace{0.5cm}
-\noindent\fbox{%
+\vspace{0.5cm} \noindent\fbox{%
 	\parbox[c][1.5cm]{0.98\textwidth}{%
-		\textit{For RQ3, approximately 60\% of answerers are aware of CC BY-SA 3.0 license enforced by Stack Overflow.
-However, 98--99\% of the answerers do not include software license in their Stack Overflow snippets nor check for licensing conflicts when they copy code snippets to Stack Overflow answers.}
+		\textit{For RQ3, approximately 60\% of answerers are aware of CC BY-SA 3.0
+			license enforced by Stack Overflow. However, 98--99\% of the answerers do not
+			include software license in their Stack Overflow snippets nor check for
+			licensing conflicts when they copy code snippets to Stack Overflow answers.}
 	}%
-}
-\vspace{0.5cm}
+} \vspace{0.5cm}
 
-In addition, we invited the answerers to give comments regarding their concerns when answering Stack Overflow (SO) with code snippets.
-Some interesting comments are selected and discussed belwo.
-The full set of answers can be found in the Appendix~\ref{appendixC}.
+In addition, we invited the answerers to give comments regarding their concerns
+when answering Stack Overflow (SO) with code snippets. Some interesting comments
+are selected and discussed below. The full set of answers can be found in the
+Appendix~\ref{appendixC}.
 
-\begin{itemize}[label={}]
-	\itemsep1em
-	\item Comment 1: The answerer addresses a concern of reusing the code snippet without understanding.
-Moreover, he or she discusses a ramification of low-quality snippets or outdated code containing security issues.
+\begin{itemize}[label={}] \itemsep1em \item Comment 1: The answerer addresses a
+	concern of programmers reusing his/her code snippets without understanding them.
+	Moreover, he or she discusses a ramification of low-quality snippets or outdated
+	code containing security issues on Stack Overflow.
 
-	\begin{quote}\textit{The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software ``professionals'' that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.
-A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about.
-Think PHP/MySQL tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}).
-They're also full of toxic code snippets.}\end{quote}
+	\begin{quote}\textit{The real issue is less about the amount the code snippets
+			on SO than it is about the staggeringly high number of software
+			``professionals'' that mindlessly use them without understanding what they're
+			copying, and the only slightly less high number of would-be professionals that
+			post snippets with built-in security issues.  A related topic is beginners who
+			post (at times dangerously) misleading tutorials online on topics they actually
+			know very little about. Think PHP/MySQL tutorials written 10+ years after
+			\texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that
+			got posted the other day on HackerNew
+			(\url{https://news.ycombinator.com/item?id=14846506}). They're also full of
+			toxic code snippets.}\end{quote}
 
-	\item Comment 2: The answerer suggests that a guidance from Stack Overflow regarding software license will be beneficial.
+	\item Comment 2: The answerer suggests that a guidance from Stack Overflow
+	regarding software license of code snippets will be beneficial.
 
-	\begin{quote}\textit{When I copy code it's usually short enough to be considered ``fair use'' but I am not a lawyer or copyright expert so some guidance from SO would be helpful.
-I'd also like the ability to flag/review questions that violate these guidelines.}\end{quote}
+	\begin{quote}\textit{When I copy code it's usually short enough to be
+			considered ``fair use'' but I am not a lawyer or copyright expert so some
+			guidance from SO would be helpful. I'd also like the ability to flag/review
+			questions that violate these guidelines.}\end{quote}
 
-	\item Comment 3: The answerer addresses a concern of code understanding.
+	\item Comment 3: Similar to comment 1, the answerer addresses a concern of
+reusing Stack Overflow code snippets without understanding.
 
-	\begin{quote}\textit{My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.}\end{quote}
+	\begin{quote}\textit{My only concern, albeit minor, is that I know people
+			blindly copy my code without even understanding what the code does.}\end{quote}
 
-	\item Comment 4: The answerer discusses a problem from outdated code and his/her solution.
+	\item Comment 4: The answerer discusses a problem from outdated Stack Overflow code snippets and
+	his/her solution.
 
-	\begin{quote}\textit{The main problem for me/us is outdated code, esp.
-as old answers have high Google rank so that is what people see first, then try and fail.
-Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.}\end{quote}
+	\begin{quote}\textit{The main problem for me/us is outdated code, esp. as old
+			answers have high Google rank so that is what people see first, then try and
+			fail. Thats why we're moving more and more of those examples to knowledge base
+			and docs and rather link to those.}\end{quote}
 
-	\item Comment 5: The answerers gives insights into the quality of the Stack Overflow code snippets.
+	\item Comment 5: The answerers gives insights into the quality of the Stack
+	Overflow code snippets.
 
-	\begin{quote}\textit{Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).}\end{quote}
-\end{itemize}
+	\begin{quote}\textit{Lot of the answers are from hobbyist so the quality is
+			poor. Usually they are hacks or workarounds (even MY best answer on SO is a
+			workaround).}\end{quote} \end{itemize}
 
-%\subsection{Visitor Responses}
-%
-%To answer RQ4 and RQ5, we ask Stack Overflow visitors about their experiences of outdated code and their awareness to software license of Stack Overflow code snippets.
-We received 89 answers from 5 groups of Stack Overflow visitors.
-The combined results and discussions are presented below.
-%
-%\subsubsection*{RQ4: Are Stack Overflow visitors aware of outdated code on Stack Overflow?}
-%
-%We asked the visitors whether they have any problem from reusing Stack Overflow code snippets and how often did the problems occur. 
-%
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=.5\linewidth]{survey_v_problems}
-%	\caption{Number of visitors who experienced a problem from reusing Stack Overflow code snippets.}
-%	\label{fig:survey_v_problems}
-%\end{figure}
-%
-%
-%\vspace{0.5cm}
-%\noindent\fbox{%
-%	\parbox[c][0.5cm]{0.98\textwidth}{%
-%		\textit{For RQ4, }
-%	}%
-%}
-%\vspace{0.5cm}
-%
-%\subsubsection*{RQ5: Are Stack Overflow visitors aware of software licensing of code snippets from Stack Overflow?}
-%
-%\vspace{0.5cm}
-%\noindent\fbox{%
-%	\parbox[c][0.5cm]{0.98\textwidth}{%
-%		\textit{For RQ5, }
-%	}%
-%}
-%\vspace{0.5cm}
+\subsection{Visitor Responses}
+
+To answer RQ4 and RQ5, we ask Stack Overflow visitors about their experiences of
+outdated code and their awareness to software license of Stack Overflow code
+snippets. We received 89 answers from 5 groups of Stack Overflow visitors. The
+combined results and discussions are presented below.
+
+\subsubsection*{General Information}
+
+\begin{figure}
+		\centering
+		\includegraphics[width=0.5\linewidth]{survey_visitor_exp}
+		\caption{Experience of the Stack Overflow visitors}
+		\label{fig:survey_visitor_exp}
+\end{figure}
+
+As illustrated in Figure~\ref{fig:survey_visitor_exp}, 24 (27\%) and 21 (24\%)
+of the participants in Stack Overflow visitor survey have over 10 years and 5-10
+years of experience respectively. There are 19 participants (21\%) who have 3-5
+years, 18 (20\%) who have 1-2 years, and 7 (8\%) participants who have less than a
+year of programming experience.
+
+\subsubsection*{RQ4: Why developers choose to find programming solutions on Stack Overflow?}
+
+Similar to a study by~\cite{Acar2016}, we asked the participants to rank five options, without a tie, they will choose to
+find programming solutions. The given five options include books, official documentations, Stack Overflow,
+online repositories (e.g. GitHub), and others. The results are displayed in Figure~\ref{fig:survey_visitor_rankings-crop}.
+We found that 47 out of 89 participants rank Stack Overflow as the 1st option to search for programming solutions, followed
+by official documentation (33), online repositories (6), other resources (5), and books (1).
+
+\begin{figure} \centering
+	\includegraphics[width=.5\linewidth]{survey_visitor_rankings-crop} 
+	\caption{Rankings of the resources developers use to solve programming problems}
+	\label{fig:survey_visitor_rankings-crop} 
+\end{figure}
+
+We then shift the focus to only Stack Overflow. We ask the participants how frequently they reuse code snippets from answers on Stack Overflow.
+According to the answers (see Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we found that 57 (64\%) participants actively reusing
+code snippets from Stack Overflow. Eight participants (9\%) copy Stack Overflow
+code everyday, 22 (25\%) do copying 3-6 times a week, 27 (30\%) do copying once or twice a week. There are 2 participants (2\%) who never
+copy code from Stack Overflow.
+
+\begin{figure} \centering
+	\includegraphics[width=.5\linewidth]{survey_visitor_frequency_so_copy} 
+	\caption{Frequency of copying code from Stack Overflow}
+	\label{fig:survey_visitor_frequency_so_copy-crop} 
+\end{figure}
+
+To understand why the participants choose to copy code snippets from Stack
+Overflow, we asked them to rate four reasons in Likert's scale (Strongly agree,
+Agree, Undecided, Disagree, Strongly disagree). The four reasons include
+\textit{They are easy to find by searching the web}, \textit{They solve problems
+	similar to my problems with minimal changes}, \textit{The context of questions
+	and answers helped me understand the code snippets better}, \textit{The voting
+	mechanism and accepted answers helped filtering good code from bad code}. The
+answers are depicted in Figure~\ref{fig:survey_visitor_why_copy_so}. More than 80\% of the
+participants agree with all the four reasons.
+
+\begin{figure} \centering
+	\includegraphics[width=0.6\linewidth]{survey_visitor_why_copy_so} 
+	\caption{Why did you copy and reuse code snippets from Stack Overflow?}
+	\label{fig:survey_visitor_why_copy_so} 
+\end{figure}
+
+\vspace{0.5cm} \noindent\fbox{%
+	\parbox[c][1.5cm]{0.98\textwidth}{%
+		\textit{For RQ4, Stack Overflow is ranked higher than official documentations, online repositories, and book as the resource to look for programming solutions. 
+		Developers rely on Stack Overflow answers because they are easy to search for on the web. Moreover, 64\% of the participants reuse code snippets from
+	Stack Overflow at least once a week.}
+	}%
+} \vspace{0.5cm}
+
+\subsubsection*{RQ5: What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
+
+We asked the visitors whether they have any problem from reusing Stack Overflow
+code snippets and how often did the problems occur.  Fifty seven (out of eighty seven) participants (see Figure~\ref{fig:survey_v_problems})
+experienced a problem from reusing Stack Overflow snippets. Among the 57, there are 2 participants who found problems in more than 80\%
+of the reused code snippets. Eight and sixteen faced problems from at least sixty and forty percent of the reused snippets.
+
+%We did not specifically point out the problem 
+%of outdated code but include it as one of the answers.
+
+\begin{figure} \centering
+	\includegraphics[width=.4\linewidth]{survey_v_problems} 
+	\caption{Number of visitors who experienced a problem from reusing Stack Overflow code snippets and the frequency.}
+	\label{fig:survey_v_problems} 
+\end{figure}
+
+The problems from reusing Stack Overflow code snippets (illustrated in
+Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions,the code
+claims to solve the problem in the question while it does not,  (20 out of 57
+$\approx$ 35\%); outdated solutions, i.e.~the code may work with the some older
+versions of the library or API, but not the one they are using, (39 out of 57
+$\approx$ 68\%); mismatched solutions, i.e.~the code solves the problem in the
+question but it is not exactly the right solution for their problem, (40 out of
+57 $\approx$ 70\%); and buggy code (1 out of 57 $\approx$ 2\%). Stack Overflow
+visitors rarely report the problems back to the discussion threads (as can be
+seen in Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32
+participants who encounter problems of Stack Overflow snippets, 18 of them
+(56\%) never report the problems. As shown in
+Figure~\ref{fig:survey_visitor_how_report_problems}, the 14 participants who
+reported the problems did so by writing a comment (10), down-voting the answer
+(8), contacted the answerer (2), and posting the new and correct answer (2).
+
+\begin{figure} \centering
+	\includegraphics[width=.5\linewidth]{survey_visitor_problems} 
+	\caption{Problems from reusing Stack Overflow code snippets}
+	\label{fig:survey_visitor_problems} 
+\end{figure}
+
+\begin{figure} \centering
+	\includegraphics[width=.4\linewidth]{survey_visitor_freq_report_problems} 
+	\caption{Frequency of Stack Overflow visitors reporting the problems back to Stack Overflow discussion threads}
+	\label{fig:survey_visitor_freq_report_problems} 
+\end{figure}
+
+\begin{figure} \centering
+	\includegraphics[width=.5\linewidth]{survey_visitor_how_report_problems} 
+	\caption{Options that Stack Overflow visitors choose to report the problems from Stack Overflow snippets}
+	\label{fig:survey_visitor_how_report_problems} 
+\end{figure}
+
+\vspace{0.5cm} \noindent\fbox{%
+	\parbox[c][2cm]{0.98\textwidth}{%
+		\textit{For RQ5, our survey results show that 57 out of 87 Stack Overflow
+	visitors find a problem from reusing Stack Overflow code snippets. Ten
+	participants experience the problems on more 80\% of the copied snippets and
+	sixteen participants face the problems on 40--60\% of the reused code. The
+	mostly found problem is a mismatched solution (40), followed by outdated
+	solution (39), incorrect solution (20), and buggy code (1). Fifty-six percent
+	of the participants never report the problems back to Stack Overflow.}}%
+} \vspace{0.5cm}
+
+\subsubsection*{RQ6: Are Stack Overflow visitors aware of the the CC BY-SA 3.0 license enforced by Stack Overflow?}
+
+As depicted in Figure~\ref{fig:survey_visitor_cc_by-sa}, 74 out of 87 (85\%)
+Stack Overflow visitors are not aware, at the time of copying the code, that
+Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC
+BY-SA 3.0) to content in the posts, including code snippets. As a consequence,
+62\% of the visitors never give an attribution, which is required by CC BY-SA
+3.0, to a Stack Overflow post they copied the code from (the complete statistics
+can be found from Figure~\ref{fig:survey_visitor_attribution-sa}).
+
+\begin{figure} \centering
+	\includegraphics[width=.4\linewidth]{survey_visitor_cc_by_sa} 
+	\caption{Awareness of Stack Overflow visitor to CC BY-SA 3.0 license}
+	\label{fig:survey_visitor_cc_by-sa} 
+\end{figure}
+
+\begin{figure} \centering
+	\includegraphics[width=.4\linewidth]{survey_visitor_attribution} 
+	\caption{Attributions to Stack Overflow when reusing code snippets}
+	\label{fig:survey_visitor_attribution-sa} 
+\end{figure}
+
+\vspace{0.5cm} \noindent\fbox{%
+	\parbox[c][1cm]{0.98\textwidth}{%
+		\textit{For RQ6, 85\% of the participants are not aware of Stack Overflow CC
+	BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
+	they copied the code snippets from.}}%
+} \vspace{0.5cm}
+
+\subsubsection*{RQ7: How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
+
+Figure~\ref{fig:survey_visitor_original_license} shows that 79\% (69) Stack
+Overflow visitors who adopted code from Stack Overflow never check if the code
+snippet originated from a different source (e.g. an open source project) with an
+incompatible license to their projects.
+
+Sixty-six percent of the participants never
+check for licensing conflicts at all when reusing Stack Overflow code (see Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly,
+possibly due to their fairly small size of code which might fall under fair use,
+only 9\% of the participants experience legal issues by reusing code snippets on
+Stack Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}).
+
+\begin{figure} \centering
+	\includegraphics[width=.4\linewidth]{survey_visitor_original_license} 
+	\caption{Checking for the original license of Stack Overflow code snippets}
+	\label{fig:survey_visitor_original_license} 
+\end{figure}
+
+\begin{figure} \centering
+	\includegraphics[width=.4\linewidth]{survey_visitor_licensing_conflict_check} 
+	\caption{Checking for licensing conflicts from reusing Stack Overflow snippets}
+	\label{fig:survey_visitor_licensing_conflict_check} 
+\end{figure}
+
+\begin{figure} \centering
+	\includegraphics[width=.4\linewidth]{survey_visitor_legal_issue} 
+	\caption{Legal issues found from reusing Stack Overflow code snippets}
+	\label{fig:survey_visitor_legal_issue} 
+\end{figure}
+
+\vspace{0.5cm} \noindent\fbox{%
+	\parbox[c][1cm]{0.98\textwidth}{%
+		\textit{For RQ7, we found that 66\% of the visitors never check for software
+	licensing conflicts between Stack Overflow code snippets and their projects.
+	However, only 9\% of the participants encountered legal issues.}}%
+} \vspace{0.5cm}
+
+\section{Threats to Validity}
 
@@
 
+We present the results from online surveys of Stack Overflow answerers and
+visitors regarding their awareness and experience of answering and reusing code
+snippets on Stack Overflow. We are interested in cloned code in Stack Overflow
+answers. Two online surveys have been performed to find out \textit{where} are the code
+snippets in Stack Overflow answers from and \textit{how} developers, in terms of both
+Stack Overflow answerers and visitors, handle potential problem of outdated code
+and software licensing conflicts.
+
+From the answerer's responses, we discovered that code in Stack Overflow answers are usually written from
+scratch to answer a question. Nonetheless, there are some code snippets that are
+copied from the answerers' personal, open source, or company projects.
+
+Outdated code on Stack Overflow occurs when the code snippet in an answer is
+copied from another location and is no longer up-to-date. The results show that
+although the answerers are aware of outdated code in their answers, 19\% of them
+rarely or never fix the code.
+
+Regarding the software license, approximately 60\% of the answerers are aware
+of Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
+license in their answers nor check for licensing conflicts when they copy code from
+another location and paste in the answer.
+
+From the visitor's responses, Stack Overflow is ranked the highest as the resource to
+solve programming tasks because it is easy to be found by search engines. More than
+half of them (64\%) reuse code from Stack Overflow at least once a week. Sixty-seven percent of the visitors
+find a problem from reusing Stack Overflow snippets ranging from a mismatched solution,
+outdated solution, incorrect solution, and buggy code. However, 56\% of the participants never
+report the problems back to Stack Overflow.
+
+Eighty-five percent of the visitors are not aware of Stack Overflow's CC BY-SA 3.0 and 62\% never
+give attributions to Stack Overflow posts that they copied the code from. Moreover, 66\% of them
+never check for licensing conflicts while reusing Stack Overflow code snippets in their software
+projects.
+
 %\bibliographystyle{abbrv}
@@
 
-%\section{Stack Overflow Visitor Survey}\label{appendixB}
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.85\linewidth]{visitor-1}
-%	\label{fig:visitor-1}
-%\end{figure}
-%
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{visitor-2}
-%	\label{fig:visitor-2}
-%\end{figure}
-%
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{visitor-3}
-%	\label{fig:visitor-3}
-%\end{figure}
-%
-%\begin{figure}[H]
-%	\centering
-%	\includegraphics[width=0.9\linewidth]{visitor-4}
-%	\label{fig:visitor-4}
-%\end{figure}
+\section{Stack Overflow Visitor Survey}\label{appendixB}
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.85\linewidth]{visitor-1}
+	\label{fig:visitor-1}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.9\linewidth]{visitor-2}
+	\label{fig:visitor-2}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.9\linewidth]{visitor-3}
+	\label{fig:visitor-3}
+\end{figure}
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.9\linewidth]{visitor-4}
+	\label{fig:visitor-4}
+\end{figure}
 

### 2017-09-13 cloverflow-tse/survey_snippet_source.m

@@ -1,18 +1,18 @@
-group1 = [13 20 30 20 18; 
-    1 5 12 15 13; 
-    4 8 15 18 28; 
-    67 32 10 1 2; 
-    42 26 19 10 11; 
-    2 4 23 8 20];
+answerers1 = [14 22 31 20 18; 
+    1 5 12 16 14; 
+    4 8 15 20 30; 
+    70 33 10 1 2; 
+    42 28 19 10 13; 
+    2 5 24 8 20];
 
-group2 = [14 20 19 10 14; 
+answerers2 = [14 20 19 10 14; 
     3 5 9 0 14; 
     5 6 16 13 16; 
     36 38 7 1 1; 
     24 28 16 5 4; 
     1 2 14 6 17];
 
-bar_handle = bar(group2,'stacked');
+bar_handle = bar(answerers2,'stacked');
 ylim([0 120])
 ylabel('Amount','FontSize',16);
 xticklabels({'Personal projects', 'Company projects', 'Open source projects', 'Write from scratch', 'Modify from questions', 'Others'});
@@ -24,4 +24,4 @@ l = cell(1,6);
 l{1}='Very frequently'; l{2}='Frequently'; l{3}='Occasionally'; l{4}='Rarely'; l{5}='Very rarely'; l{6}='Never';
 legend(bar_handle,l,'Location','Northeast','fontsize',12);
 
-% print('survey_snippet_source','-dpdf','-bestfit')
+print('survey_snippet_source', '-bestfit', '-dpdf')

### 2017-09-13 cloverflow-tse/survey_visitor_ranking.m

@@ -1,0 +1,19 @@
+rankings = [1 7 6 32 43; 
+    33 31 18 4 3; 
+    47 32 6 3 1; 
+    6 21 44 11 7; 
+    5 8 14 26 36];
+
+bar_handle = bar(rankings,'grouped');
+% ylim([0 120])
+ylabel('Amount','FontSize',16);
+xticklabels({'Books', 'Official documentations', 'Stack Overflow', 'Online repos', 'Others'});
+xtickangle(30);
+set(gca,'fontsize',16);
+grid on
+
+l = cell(1,5);
+l{1}='1st'; l{2}='2nd'; l{3}='3rd'; l{4}='4th'; l{5}='5th';
+legend(bar_handle,l,'Location','Northeast','fontsize',12,'Orientation','horizontal');
+
+% print('survey_snippet_source', '-bestfit', '-dpdf')

### 2017-09-13 cloverflow-tse/survey_visitor_why_copy_so.m

@@ -1,0 +1,21 @@
+rankings = [48 32 0 3 3; 
+    30 44 5 6 1; 
+    38 36 11 2 0; 
+    29 40 11 5 1];
+
+bar_handle = bar(rankings,'grouped');
+% ylim([0 120])
+ylabel('Amount','FontSize',16);
+xticklabels({'Easy to find', 
+    'Solve similar problems', 
+    'Helpful context', 
+    'Voting and accepted answers'});
+xtickangle(30);
+set(gca,'fontsize',16);
+grid on
+
+l = cell(1,5);
+l{1}='Strongly agree'; l{2}='Agree'; l{3}='Undecided'; l{4}='Disagree'; l{5}='Strongly disagree';
+legend(bar_handle,l,'Location','northoutside','fontsize',12,'Orientation','horizontal');
+
+% print('survey_snippet_source', '-bestfit', '-dpdf')

### 2017-09-13 cloverflow-tse/survey_visitor_why_copy_so_yes_no.m

@@ -1,0 +1,21 @@
+rankings = [80 0 6; 
+    74 5 7; 
+    74 11 2; 
+    69 11 6];
+
+bar_handle = bar(rankings,'grouped');
+% ylim([0 120])
+ylabel('Amount','FontSize',16);
+xticklabels({'Easy to find', 
+    'Solve similar problems', 
+    'Helpful context', 
+    'Voting and accepted answers'});
+xtickangle(30);
+set(gca,'fontsize',16);
+grid on
+
+l = cell(1,3);
+l{1}='Agree'; l{2}='Undecided'; l{3}='Disagree';
+legend(bar_handle,l,'Location','northoutside','fontsize',12,'Orientation','horizontal');
+
+% print('survey_snippet_source', '-bestfit', '-dpdf')

### 2017-09-14 cloverflow_technical_report/cloverflow_survey_rn.tex
Latest update of the RN.

@@
 
-\title{Awareness of Stack Overflow Users to\\ Outdated and License-violating Code:\\ The Online Survey}
+\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ The Online Survey}
 %\subtitle{Do you have a subtitle?\\ If so, write it here}
@@
 %websites.
-Recent research shows that outdated third-party code and software
-licensing conflicts are ramifications by reusing source code by copying and
-pasting (i.e.~code cloning). \cite{Xia2014} report that a large number of open
-source systems reuse outdated third-party libraries from popular open source
-projects. Using the outdated code give detrimental effects to the software since
-they may introduce vulnerabilities. On the other hand, \cite{German2009} found
-that code cloning leads to conflicts in software license among different
-systems.
-
-The Internet encourages fast and easy code cloning by sharing and copying code
-to and from online sources. Developers nowadays do not only clone code from local
-software projects, but also from online sources such as programming Q\&A website
-and online code repositories~\FIXME{Add citation}. Stack Overflow is one of the most popular
-programming Q\&A websites in the word. It has 7.6 million users, 14 million
-questions, 23 million answers\footnote{Data as of 21 August 2017
-	from~\url{https://stackexchange.com/sites}}, and more than 50 million developers
-visiting each month\footnote{Data as of 21 August 2017 from:
-	\url{https://stackoverflow.com}}. Nevertheless, several code snippets on Stack
-Overflow are found to be problematic. Many code snippets provided as solutions
-are workarounds and occasionally contains defects or vulnerabilities.
-\cite{Acar2016} performed a user study and found that Stack Overflow helps
-developers to solve Android programming problems quicker than other resources
-while, at the same time, offers less secure code than books or the official
-Android documentation. Only 17\% of the Stack Overflow discussion threads the
-participant visited during the study contain secure code snippets. They also
-found that similar piece of API call copied from Stack Overflow by participants
-in their study existed in a random sample of 200,000 Android apps from Google
-Play. \cite{An2017} showed that 1,279 cloned snippets between 399 Android apps
-and Stack Overflow potentially violate software licenses.
-
-\textbf{We are interested in studying the issues of outdated code and software license
-violation cause by code snippets on Stack Overflow.} Asking and answering
-questions on Stack Overflow usually involve copying and pasting source code
-snippets, either in a question or an answer. However, the copied snippets are
-not regularly checked and occasionally not up-to-date with their originals. Some
-snippets are copied from an open source system with stricter software license
-than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior to
-this study, we performed an empirical study using code clone detection tools
-to locate cloned code snippets in accepted answers. We found that many snippets
-were copied from open source projects. Some cloned snippets are outdated and
-possibly violating the original software license. In either case, these snippets
-are potentially harmful for reuse. To accompany the findings and gain
-insights into the cause of the problems, we resort to a qualitative study using
-an online survey of Stack Overflow developers who 1) answer programming
-questions with code snippets and 2) reuse code snippets from Stack Overflow
-answers.
+Recent research shows that outdated third-party code and software licensing
+conflicts are ramifications by code cloning, i.e.~reusing source code by copying
+and pasting. \cite{Xia2014} report that a large number of open source systems
+reuse outdated third-party libraries from popular open source projects. Using
+the outdated code give detrimental effects to the software since they may
+introduce vulnerabilities. On the other hand, \cite{German2009} found that code
+cloning leads to conflicts in software license among different systems.
+
+The Internet encourages fast and easy code cloning by sharing and copying the
+code to and from online sources. Developers nowadays do not only clone code from
+local software projects, but also from online sources such as programming Q\&A
+website and online code
+repositories~\citep{Acar2016,Abdalkareem2017,An2017,Yang2017}. Stack Overflow is
+one of the most popular programming Q\&A websites in the world. It has 7.6
+million users, 14 million questions, 23 million answers\footnote{Data as of 21
+	August 2017 from~\url{https://stackexchange.com/sites}}, and more than 50
+million developers visiting each month\footnote{Data as of 21 August 2017 from:
+	\url{https://stackoverflow.com}}. Some code snippets on Stack Overflow are found
+to be problematic. \cite{Acar2016} discovered that many code snippets provided
+as solutions on Stack Overflow are workarounds and occasionally contains defects
+or vulnerabilities. They performed a user study and found that although Stack
+Overflow helps developers to solve Android programming problems quicker than
+other resources, at the same time, offers less secure code than books or the
+official Android documentation. Only 17\% of the Stack Overflow discussion
+threads the participant visited during the study contain secure code snippets.
+They also found a similar piece of an API call copied from Stack Overflow by
+participants in their study occurring in a random sample of 200,000 Android apps
+from Google Play. In addition, \cite{An2017} investigated clones between 399
+Android apps and Stack Overflow posts. They found 1,226 code snippets which were
+reused from 68 Android apps. They also observed that there are 1,279 cases of
+potential license violations.
+
+Asking and answering questions on Stack Overflow involves including source code
+snippets, either in a question or an answer or both. While many answers contain
+snippets that are written from scratch, there are several answers containing
+code snippets copied from other sources. The copied snippets on Stack Overflow
+is a snapshot of the code at the time of copying. They are less frequently
+updated than in normal software projects and might not be up-to-date with their
+originals, which are further modified due to bug fixing or feature improvements.
+In addition, Some snippets are copied from software systems with stricter
+license than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA
+3.0). Prior to this study, we performed a quantitative empirical study using
+code clone detection tools to locate cloned code snippets in accepted answers.
+We found that many snippets were copied from open source projects. Some cloned
+snippets are outdated (or obsolete) and some possibly violate the original software license.
+These snippets are potentially harmful to reuse. To accompany the findings and
+gain insights into the cause of the problems, we resort to a qualitative study
+using an online survey of Stack Overflow developers who 1) regularly answer
+programming questions with code snippets and 2) reuse code snippets from Stack
+Overflow. \textbf{The study aims to understand the developers' awareness and
+	experience to the issues of outdated and license-violating code on Stack
+	Overflow.}
 
 In this paper, we use the term ``answerers'' to refer to Stack Overflow users
-who have high reputation, specifically the users with reputation from 963,731
-(highest)  to 6,999. The answerers gain their reputation from answering
-questions and receiving votes from other users. The reputation reflects trust
-they gain from other users and their activeness in answering questions. We ask
-the answerers the origins of source code snippets in their answers  and assess
-their awareness of outdated and licensed code. 
-We use the term ``visitors'' the
-refer to developers, who may or may not have a Stack Overflow account but visit
-Stack Overflow when facing programming problems. They copy example code snippets
-that are relevant to their problems and reused them in their software. 
-We ask Stack Overflow visitors, who copied code snippets from
-Stack Overflow, about their experience of outdated or license-violating code.
+who actively answer questions, which is measured by their reputation. The
+answerers gain a reputation from giving a helpful answer to a question and
+receiving votes from other users. The reputation reflects trust they gain from
+other users and also the quality of their answers. We ask the answerers the
+origins of source code snippets in their answers, assess their awareness of
+outdated and licensed code, and understand how they handle the issues.
+
+We use the term ``visitors'' the refer to developers, who may or may not have a
+Stack Overflow account but visit Stack Overflow when they encounter programming
+problems. They copy code snippet(s) in a solution that is relevant to their
+problem and reused them with or without a modification. We ask the visitors
+about their experience of reusing source code from Stack Overflow and the problems
+they faced including code obsolescence and software license.
 
 \section{Research Questions}
-In this study, we would like to answer seven research questions listed below. The first three questions will be
-answered by the Stack Overflow answerer survey, while the last three questions will be answered by the
+In this study, we would like to answer six research questions. The first three questions will be
+answered by the Stack Overflow answerer survey, while the other three questions will be answered by the
 Stack Overflow visitor survey.
@@
 	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
-	\item \textbf{RQ4 (Importance of Stack Overflow to developers):} \textit{Why developers choose to find programming solutions on Stack Overflow?}
-	\item \textbf{RQ5 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
-	\item \textbf{RQ6 (Awareness of Stack Overflow visitors to CC BY-SA 3.0 license):} \textit{Are Stack Overflow visitors aware of the the CC BY-SA 3.0 license enforced by Stack Overflow?}
-	\item \textbf{RQ7 (Software licensing issues from Stack Overflow code snippets):} \textit{How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
+	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
+	\item \textbf{RQ5 (Software licensing issues from Stack Overflow code snippets):}\textit{How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
 \end{enumerate}
@@
 \section{Research Methodology}
-The study is performed using an online survey. We designed the survey using
+The study is conducted using online surveys. We designed the surveys using
 Google Forms by following the principles of survey research
-by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. 
-We created two versions of the
-survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. 
-The surveys are completely anonymous and the participants could decide to leave at
-any time. It does not collect any sensitive personal information from the
-participants and were approved for an ethical waiver by the designated ethics
-officer in the Computer Science Department at UCL.  The complete version of
-the surveys can be found in the Appendix~\ref{appendixA}.
+by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. We created two versions of the
+survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. Both
+surveys are completely anonymous and the participants could decide to leave at
+any time. They do not collect any sensitive personal information from the
+participants and are approved for an ethical waiver by the designated ethics
+officer in the Computer Science Department at University College London (UCL). 
+The complete version of the surveys can be found in 
+Appendix~\ref{appendixA}.
 
@@
 questions, 3 yes/no questions, and one open-ended question for additional
-comments. The first two questions were mandatory while the other 9 questions
-were shown to the participants based on their previous answers. The survey collects
-information of the participant's software development experience, experience of
-answering Stack Overflow questions, sources of the Stack Overflow snippets,
-concerns of copying code snippets to Stack Overflow, problems from code 
-snippets on Stack Overflow, fixing outdated code, and additional feedbacks.
+comments. The first two questions are mandatory while the other 9 questions will
+be shown to the participants based on their previous answers. The survey
+collects information of the participant's software development experience, the
+experience of answering Stack Overflow questions, sources of the Stack Overflow
+snippets, awareness of outdated code in their answers, concerns regarding
+license when they copy code snippets to Stack Overflow, and additional feedbacks.
 
@@
 
-We selected the participants for our answerer survey based on their Stack Overflow reputation. On
-Stack Overflow, a user's reputation reflects how much the community trust the
-user. A user earns reputation when he or she receives up votes for good
-questions and useful answers. Accepted answers receive more reputation score
-than questions, and regular answers\footnote{Stack Overflow
+We selected the participants for our answerer survey based on their Stack
+Overflow reputations. On Stack Overflow, a user's reputation reflects how much
+the community trusts the user. A user earns reputation when he or she receives
+up votes for good questions and useful answers. Accepted answers receive more
+reputation score than questions and regular answers\footnote{Stack Overflow
 	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
@@
 
-The participants were invited to take the survey via email addresses publicly available on their
-public Stack Overflow and GitHub profiles. We selected the answerers based on
-all-time reputation ranking\footnote{Stack Overflow Users (data as of 25 July
-	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}} and
-separated them into two groups (see Table~\ref{tab:answerers}) so that we can
-compare the results or observe similar patterns between them. 
-The first group had reputation from 963,731 (the
-highest) to 7,674, and the second group had reputation from 7,636 to 6,999 which
-we sent out 300 and 307 emails (excluding undelivered ones) respectively. The
-survey was open for participation for a month, from 25 July 2017 to 25 August
-2017, before we collected and analysed the responses.
+The participants were invited to take the survey via email addresses publicly
+available on their Stack Overflow and GitHub profiles. We selected the answerers
+based on their all-time reputation ranking\footnote{Stack Overflow Users (data as of
+	25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}
+and separated them into two groups (see Table~\ref{tab:answerers}) so that we
+can compare the results or observe similar patterns between them. The first
+group had reputation from 963,731 (the highest) to 7,674, and the second group
+had reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
+(excluding undelivered ones) respectively. The survey was open for participation
+for a month, from 25 July 2017 to 25 August 2017, before we collected and
+analysed the responses.ponses.
 
@@
 
-The Stack Overflow visitor survey is consisted of 16 questions: 9 Likert's scale
+The Stack Overflow visitor survey consists of 16 questions: 9 Likert's scale
 questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
@@
 were shown to the participants based on their previous answers. The survey collects
-information of the participant's software development experience, importance of
+information of the participant's software development experience, the importance of
 Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
@@
 invitation to the visitor survey in a discussion forum. The third channel
-collects answers from University of Molise which is the third author's
+collects answers from the University of Molise which is the third author's
 workplace. The last two channels are from a comp.lang.java.programmer Google
@@
 collected and analysed the responses. The number of participants taken the
-survey are shown in Table~\ref{tab:visitors}.
+survey is shown in Table~\ref{tab:visitors}.
 
@@
 (28\% response rate) from the second group of Stack Overflow answerers. The response
-rate from both groups were high considered other online survey in software
+rate from both groups was high considered other online survey in software
 engineering that received approximately 14--20\%~\FIXME{double-check the
@@
 Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 that
-have more than 10 year of software development experience, while a slightly less
+have more than 10 years of software development experience, while a slightly less
 percentage of 50\% in Group 2.
@@
 The participants are active users and regularly answer questions on Stack
-Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty two (82\%) and
+Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty-two (82\%) and
 sixty (60\%) of answerers from Group 1 and Group 2  answer questions at
@@
 
-To answer this research question, we ask the participants for original
-sources of their code examples. We provided six options (allowing more than one answer)
+To answer this research question, we ask the participants for original sources
+of their code examples. We provided six options (allowing more than one answer)
 including \textit{I copied them from my own personal projects}, \textit{I copied
@@
 	from the question and modify it for the answer}, and \textit{Others}. The
-answers are shown in Figure~\ref{fig:survey_snippet_source}. Participants
-in Group 1 mainly write new code from scratch (116) or copy from the code snippets in question
-and modify it for the answer (112), followed by from their personal
-projects (105), open source projects (77), other sources (59), and company projects (48). 
-For Group 2, the main source is also writing code from scratch (83), followed by copying
-from personal projects and modifying from the question (77), copying from open source projects (56),
-copying from other sources (40), and copying from company projects (31).
+answers are shown in Figure~\ref{fig:survey_snippet_source}. Participants in
+Group 1 mainly write new code from scratch (116) or copy from the code snippets
+in question and modify it for the answer (112), followed by from their personal
+projects (105), open source projects (77), other sources (59), and company
+projects (48). For Group 2, the main source is also writing code from scratch
+(83), followed by copying from personal projects and modifying from the question
+(77), copying from open source projects (56), copying from other sources (40),
+and copying from company projects (31).
 
@@
 	\parbox[c][2cm]{0.98\textwidth}{%
-		\textit{For RQ 1, we found that answering questions by writing the new code from
-			scratch is the most popular choice for Stack Overflow answerers followed by modifying from the code in question, or copying from personal projects. Other less
-			popular choices include copying code from open
-			source projects and from other sources. Copying code from company projects are the least popular choice.} }%
+        \textit{For RQ 1, we found that answering questions by writing the new
+	code from scratch is the most popular choice for Stack Overflow
+	answerers followed by modifying the code in question or copying from
+	personal projects. Other less popular choices include copying code from
+	open source projects and from other sources. Copying code from company
+	projects are the least popular choice.} }%
 }
@@
 question. The code is automatically subjected to Stack Overflow's CC BY-SA 3.0.
-Second, they copy code from company or open source projects that they know are
+Second, they copy the code from company or open source projects that they know are
 permitted to be publicly distributed. Hence, no license statement is required.
@@
 
-Similar to a study by~\cite{Acar2016}, we asked the participants to rank five options, without a tie, they will choose to
-find programming solutions. The given five options include books, official documentations, Stack Overflow,
-online repositories (e.g. GitHub), and others. The results are displayed in Figure~\ref{fig:survey_visitor_rankings-crop}.
-We found that 47 out of 89 participants rank Stack Overflow as the 1st option to search for programming solutions, followed
-by official documentation (33), online repositories (6), other resources (5), and books (1).
+Similar to a study by~\cite{Acar2016}, we asked the participants to rank five
+options, without a tie, they will choose to find programming solutions. The
+given five options include books, official documentations, Stack Overflow,
+online repositories (e.g. GitHub), and others. The results are displayed in
+Figure~\ref{fig:survey_visitor_rankings-crop}. We found that 47 out of 89
+participants rank Stack Overflow as the 1st option to search for programming
+solutions, followed by official documentation (33), online repositories (6),
+other resources (5), and books (1).
 
@@
 
-We then shift the focus to only Stack Overflow. We ask the participants how frequently they reuse code snippets from answers on Stack Overflow.
-According to the answers (see Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we found that 57 (64\%) participants actively reusing
-code snippets from Stack Overflow. Eight participants (9\%) copy Stack Overflow
-code everyday, 22 (25\%) do copying 3-6 times a week, 27 (30\%) do copying once or twice a week. There are 2 participants (2\%) who never
-copy code from Stack Overflow.
+We then shift the focus to only Stack Overflow. We ask the participants how
+frequently they reuse code snippets from answers on Stack Overflow. According to
+the answers (see Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we
+found that 57 (64\%) participants actively reusing code snippets from Stack
+Overflow. Eight participants (9\%) copy Stack Overflow code every day, 22 (25\%)
+do copying 3-6 times a week, 27 (30\%) do copying once or twice a week. There
+are 2 participants (2\%) who never copy the code from Stack Overflow.
 
@@
 	and answers helped me understand the code snippets better}, \textit{The voting
-	mechanism and accepted answers helped filtering good code from bad code}. The
+	mechanism and accepted answers helped to filter good code from bad code}. The
 answers are depicted in Figure~\ref{fig:survey_visitor_why_copy_so}. More than 80\% of the
@@
 	\parbox[c][1.5cm]{0.98\textwidth}{%
-		\textit{For RQ4, Stack Overflow is ranked higher than official documentations, online repositories, and book as the resource to look for programming solutions. 
-		Developers rely on Stack Overflow answers because they are easy to search for on the web. Moreover, 64\% of the participants reuse code snippets from
-	Stack Overflow at least once a week.}
+		\textit{For RQ4, Stack Overflow is ranked higher than official documentations,
+	online repositories, and book as the resource to look for programming
+	solutions. Developers rely on Stack Overflow answers because they are easy to
+	search for on the web. Moreover, 64\% of the participants reuse code snippets
+	from Stack Overflow at least once a week.}
 	}%
@@
 
-\subsubsection*{RQ5: What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
+\subsubsection*{RQ5: What are the problems Stack Overflow visitors experiencing
+	from reusing code snippets on Stack Overflow?}
 
 We asked the visitors whether they have any problem from reusing Stack Overflow
-code snippets and how often did the problems occur.  Fifty seven (out of eighty seven) participants (see Figure~\ref{fig:survey_v_problems})
-experienced a problem from reusing Stack Overflow snippets. Among the 57, there are 2 participants who found problems in more than 80\%
-of the reused code snippets. Eight and sixteen faced problems from at least sixty and forty percent of the reused snippets.
+code snippets and how often did the problems occur.  Fifty seven (out of eighty
+seven) participants (see Figure~\ref{fig:survey_v_problems}) experienced a
+problem from reusing Stack Overflow snippets. Among the 57, there are 2
+participants who found problems in more than 80\% of the reused code snippets.
+Eight and sixteen faced problems from at least sixty and forty percent of the
+reused snippets.
 
@@
 
-\subsubsection*{RQ6: Are Stack Overflow visitors aware of the the CC BY-SA 3.0 license enforced by Stack Overflow?}
+\subsubsection*{RQ6: Are Stack Overflow visitors aware of the the CC BY-SA 3.0
+	license enforced by Stack Overflow?}
 
@@
 
-\subsubsection*{RQ7: How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
+\subsubsection*{RQ7: How often do Stack Overflow visitors check for software
+	licensing issues from code snippets on Stack Overflow?}
 
@@
 
-Sixty-six percent of the participants never
-check for licensing conflicts at all when reusing Stack Overflow code (see Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly,
-possibly due to their fairly small size of code which might fall under fair use,
-only 9\% of the participants experience legal issues by reusing code snippets on
-Stack Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}).
+Sixty-six percent of the participants never check for licensing conflicts at all
+when reusing Stack Overflow code (see
+Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, possibly due
+to their fairly small size of code which might fall under fair use, only 9\% of
+the participants experience legal issues by reusing code snippets on Stack
+Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}).
 
@@
 Seahawk is an Eclipse plug-in that searches and recommends relevant code
-snippets from Stack Overflow~\citep{Ponzanelli2013}. A follow up work, Prompter,
+snippets from Stack Overflow~\citep{Ponzanelli2013}. A follow-up work, Prompter,
 by Ponzanelli et al.~\citep{Ponzanelli2014} achieves the same goal but with
@@
 \cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
-\cite{Yang2017} analysed 909k non-fork Python projects on Github and 1.9
-million python code snippets on Stack Overflow and found thousands of 
-code blocks that are copied from Stack Overflow to GitHub.
-
-\subsection{Software Licensing}
-Software licensing is crucial for open source and industrial software
-development. Di Penta et al.~\cite{DiPenta2010} studied the evolution of
-software licensing in open source software and found that licensing statements
-change over time. \cite{German2009} found that licensing conflicts occur between
-the clone siblings, i.e.~clones among different systems that come from the same
-source. Later, \cite{German2010} created an automated tool for software license
-identification, Ninka. \cite{An2017} detected clones between 399 Android apps
-and Stack Overflow Java code snippets. They found that  that 1,279 cloned
-snippets potentially violate software licenses. Our study gives insights into
-the software licensing of Stack Overflow code snippets. We study the licensing
-awareness of developers when they copy and paste code to/from Stack Overflow.
-
-\subsection{Reusing of outdated third-party source code} 
-Outdated code occurs in software development. Xia et al.~\cite{Xia2014} discover
-that there are code reused from popular open source projects in a large number
-of open source systems. More importantly, some of the reused code are outdated
-which affect quality and security of the software. Our study focuses on a
-similar problem but on the context of Stack Overflow.
+\cite{Yang2017} analysed 909k non-fork Python projects on Github and 1.9 million
+python code snippets on Stack Overflow and found thousands of code blocks that
+are copied from Stack Overflow to GitHub.
+
+\subsection{Software Licensing} Software licensing is crucial for open source
+and industrial software development. Di Penta et al.~\cite{DiPenta2010} studied
+the evolution of software licensing in open source software and found that
+licensing statements change over time. \cite{German2009} found that licensing
+conflicts occur between the clone siblings, i.e.~clones among different systems
+that come from the same source. Later, \cite{German2010} created an automated
+tool for software license identification, Ninka. \cite{An2017} detected clones
+between 399 Android apps and Stack Overflow Java code snippets. They found  that
+1,279 cloned snippets potentially violate software licenses. Our study gives
+insights into the software licensing of Stack Overflow code snippets. We study
+the licensing awareness of developers when they copy and paste code to/from
+Stack Overflow.
+
+\subsection{Reusing of outdated third-party source code} Outdated code occurs in
+software development. Xia et al.~\cite{Xia2014} discover that there is code
+reused from popular open source projects in a large number of open source
+systems. More importantly, some of the reused code is outdated which affect
+quality and security of the software. Our study focuses on a similar problem but
+on the context of Stack Overflow.
 
@@
 snippets on Stack Overflow. We are interested in cloned code in Stack Overflow
-answers. Two online surveys have been performed to find out \textit{where} are the code
-snippets in Stack Overflow answers from and \textit{how} developers, in terms of both
-Stack Overflow answerers and visitors, handle potential problem of outdated code
-and software licensing conflicts.
-
-From the answerer's responses, we discovered that code in Stack Overflow answers are usually written from
-scratch to answer a question. Nonetheless, there are some code snippets that are
-copied from the answerers' personal, open source, or company projects.
-
-Outdated code on Stack Overflow occurs when the code snippet in an answer is
+answers. Two online surveys have been performed to find out \textit{where} are
+the code snippets in Stack Overflow answers from and \textit{how} developers, in
+terms of both Stack Overflow answerers and visitors, handle potential problem of
+outdated code and software licensing conflicts.
+
+From the answerer's responses, we discovered that code in Stack Overflow answers
+is usually written from scratch to answer a question. Nonetheless, there are
+some code snippets that are copied from the answerers' personal, open source, or
+company projects.
+
+The outdated code on Stack Overflow occurs when the code snippet in an answer is
 copied from another location and is no longer up-to-date. The results show that
@@
 
-Regarding the software license, approximately 60\% of the answerers are aware
-of Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
-license in their answers nor check for licensing conflicts when they copy code from
-another location and paste in the answer.
-
-From the visitor's responses, Stack Overflow is ranked the highest as the resource to
-solve programming tasks because it is easy to be found by search engines. More than
-half of them (64\%) reuse code from Stack Overflow at least once a week. Sixty-seven percent of the visitors
-find a problem from reusing Stack Overflow snippets ranging from a mismatched solution,
-outdated solution, incorrect solution, and buggy code. However, 56\% of the participants never
+Regarding the software license, approximately 60\% of the answerers are aware of
+Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
+the license in their answers nor check for licensing conflicts when they copy
+the code from another location and paste in the answer.
+
+From the visitor's responses, Stack Overflow is ranked the highest as the
+resource to solve programming tasks because it is easy to be found by search
+engines. More than half of them (64\%) reuse code from Stack Overflow at least
+once a week. Sixty-seven percent of the visitors find a problem from reusing
+Stack Overflow snippets ranging from a mismatched solution, outdated solution,
+incorrect solution, and buggy code. However, 56\% of the participants never
 report the problems back to Stack Overflow.
 
-Eighty-five percent of the visitors are not aware of Stack Overflow's CC BY-SA 3.0 and 62\% never
-give attributions to Stack Overflow posts that they copied the code from. Moreover, 66\% of them
-never check for licensing conflicts while reusing Stack Overflow code snippets in their software
-projects.
+Eighty-five percent of the visitors are not aware of Stack Overflow's CC BY-SA
+3.0 and 62\% never give attributions to Stack Overflow posts that they copied
+the code from. Moreover, 66\% of them never check for licensing conflicts while
+reusing Stack Overflow code snippets in their software projects.
 

### 2017-09-15 cloverflow_technical_report/cloverflow_survey_rn.tex
Technical report revision#1.

@@
 Overflow. \textbf{The study aims to understand the developers' awareness and
-	experience to the issues of outdated and license-violating code on Stack
+	experience to outdated code and code licensing on Stack
 	Overflow.}
@@
 
-\section{Research Questions}
-In this study, we would like to answer six research questions. The first three questions will be
-answered by the Stack Overflow answerer survey, while the other three questions will be answered by the
-Stack Overflow visitor survey.
+\section{Research Methodology}
+We followed the principles of survey research by~\cite{Pfleeger2001}
+and~\cite{Kitchenham2002} by setting specific and measurable objective, 
+designing and scheduling the survey, selecting participants, analysing the data, and reporting the results.
+We now discuss each of them in detail.
+
+\subsection{Survey Objective}
+The main objective of the survey is to understand the developers' awareness and
+experience to outdated code and code licensing on Stack Overflow. It can break
+down into the following six research questions.
 
@@
 
-\section{Research Methodology}
-The study is conducted using online surveys. We designed the surveys using
-Google Forms by following the principles of survey research
-by~\cite{Pfleeger2001} and~\cite{Kitchenham2002}. We created two versions of the
+The first three questions will be answered by
+the Stack Overflow answerer survey, while the other three questions will be
+answered by the Stack Overflow visitor survey.
+
+\subsection{Survey Design and Schedule}
+The study is conducted using unsupervised online surveys. We designed the surveys using
+Google Forms. We created two versions of the
 survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. Both
@@
 
-\subsection{The Answerer Survey}
-The Stack Overflow answerer survey contains 11 questions: 7 Likert's scale
-questions, 3 yes/no questions, and one open-ended question for additional
+\subsubsection{The answerer survey} 
+The survey contains 11 questions: 7 Likert's
+scale questions, 3 yes/no questions, and one open-ended question for additional
 comments. The first two questions are mandatory while the other 9 questions will
@@
 snippets, awareness of outdated code in their answers, concerns regarding
-license when they copy code snippets to Stack Overflow, and additional feedbacks.
+license when they copy code snippets to Stack Overflow, and additional
+feedbacks. The survey was open for participation for 50 days, from 25 July 2017
+to 12 September 2017, before we collected and analysed the responses.
+
+\subsubsection{The visitor survey} 
+The survey consists of 16 questions: 9 Likert's
+scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
+open-ended questions. The first four questions are mandatory while the other 12
+questions will be shown to the participants based on their previous answers. The
+survey collects information of the participant's software development
+experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
+snippets, problems from Stack Overflow snippets, licensing of code on Stack
+Overflow, and additional feedbacks. The survey was open for participation for 50
+days, from 25 July 2017 to 12 September 2017, before we collected and analysed
+the responses.
+
+\subsection{Participant Selection}
+
+\subsubsection{The answerer survey} 
+We selected the participants for our answerer survey based on their Stack
+Overflow reputations. On Stack Overflow, a user's reputation reflects how much
+the community trusts the user. A user earns reputation when he or she receives
+up votes for good questions and useful answers. Accepted answers receive more
+reputation score than questions and regular answers\footnote{Stack Overflow
+	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
+Overflow reputation is an indicator of user's skills and their involvement in
+asking and answering questions on the site.
 
@@
 
-We selected the participants for our answerer survey based on their Stack
-Overflow reputations. On Stack Overflow, a user's reputation reflects how much
-the community trusts the user. A user earns reputation when he or she receives
-up votes for good questions and useful answers. Accepted answers receive more
-reputation score than questions and regular answers\footnote{Stack Overflow
-	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
-Overflow reputation is an indicator of user's skills and their involvement in
-asking and answering questions on the site.
-
 The participants were invited to take the survey via email addresses publicly
@@
 had reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
-(excluding undelivered ones) respectively. The survey was open for participation
-for a month, from 25 July 2017 to 25 August 2017, before we collected and
-analysed the responses.ponses.
-
-\subsection{The Visitor Survey}
-
-The Stack Overflow visitor survey consists of 16 questions: 9 Likert's scale
-questions, 3 yes/no questions, 2 multiple-choice questions, and 2 open-ended
-questions. The first four questions were mandatory while the other 12 questions
-were shown to the participants based on their previous answers. The survey collects
-information of the participant's software development experience, the importance of
-Stack Overflow, reasons for reusing Stack Overflow snippets, problems from
-Stack Overflow snippets, licensing of code on Stack Overflow, and additional
-feedbacks.
+(excluding undelivered ones) respectively.
+
+\subsubsection{The visitor survey} 
+We adopted non-probability convenient sampling to invite participants for this
+survey. Participation in the survey requires experience of
+visiting Stack Overflow for solving programming tasks at least once. The
+participants were invited to take the survey via five channels. The first
+channel is via the first author's social media post (Facebook) where the he
+invited friends who are software developers and have experience of copying code
+snippets from Stack Overflow to take the survey. The second channel is a popular
+technology news and media community in Thailand called \textsf{blognone.com} which
+attracts a high number of Thai software developers. The first author posted an
+invitation to the visitor survey in a discussion forum mentioning the
+requirements to take the survey. The third channel collects answers from the
+University of Molise from help of an external researcher. The last two
+channels are from a \textsf{comp.lang.java.programmer} Google groups and Software
+Engineering Facebook page. The number of participants taken the survey is shown in
+Table~\ref{tab:visitors}.
 
@@
 		\toprule
-		Invitation channels & Answers \\
+		Group & Answers \\
 		\midrule
@@
 
-The participants for this survey were invited to take the survey via five
-channels. The first channel is via the first author's Facebook post where the
-first author invited friends who are software developers and have experience of
-copying code snippets from Stack Overflow to take the survey. The second channel
-is a popular Thai technology news and media community called blognone.com which
-attracts a high number of software developers. The first author posted an
-invitation to the visitor survey in a discussion forum. The third channel
-collects answers from the University of Molise which is the third author's
-workplace. The last two channels are from a comp.lang.java.programmer Google
-groups and Software Engineering Facebook page. The survey was open for
-participation for a month, from 25 July 2017 to 25 August 2017, before we
-collected and analysed the responses. The number of participants taken the
-survey is shown in Table~\ref{tab:visitors}.
+\subsection{Data Analysis}
+Google Forms provide a helpful summary of responses to the online surveys. We
+relied on the summary from Google Forms when analysing the answers from the
+answerer survey. For the visitor survey, since we created a copy of the survey for each
+group of the participants, we downloaded the responses in comma-separated values
+(CSV) files and merged the results before the analysis.
 
 \section{Results and Discussions}
-
-\subsection{Answerer Responses}
+We collected and analysed the results after we closed the surveys on 12
+September 2017. We now discuss the results separately for the answerer and the
+visitor survey.
+
+\subsection{The answerer survey}
 We received 117 answers (39\% response rate) from the first group and 85 answers
@@
 
-\subsubsection*{General Information}
+\subsubsection{General Information}
 %General information of the answerers' experience and frequency of answering 
@@
 \section{Threats to Validity}
+
+\subsection{Internal Validity}
+We targeted the participants for the answerer survey based on their Stack Overflow
+reputation instead of random sampling. This is because reflects the developers
+involvement in asking and answering questions on the site. Thus, our findings
+capture awareness and experience of experienced Stack Overflow developers. Moreover,
+due to a large number of users on Stack Overflow, we could invite only 607
+highly-ranked developers to participate in the study.
+
+We selected the participants for the visitor survey based on convenient sampling which
+could suffer from bias and outliers.
+
+\subsection{External Validity} 
+While the reputation is a good proxy to reflect the amount of answers the
+developers have given, it might not cover all kinds of answerers on Stack
+Overflow. The answerers who have lower-reputation than 6,999 were not invited to
+our study and their awareness and experience may differ from our findings.
+
+At least 39\% of the participants in the visitor survey are from
+\textsf{blognone.com} which is based in Thailand. Due to working culture,
+answers from this group of developers may only represent software developers in
+Thailand. We alleviate this concern by inviting participants from other groups,
+e.g.~University of Molise in Italy, comp.lang.java.programmer, and Software
+Engineering Facebook group.
 

### 2017-09-16 cloverflow_technical_report/cloverflow_survey_rn.tex
Latest update on the technical report.

@@
 	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
+	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
 	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
@@
 We collected and analysed the results after we closed the surveys on 12
-September 2017. We now discuss the results separately for the answerer and the
-visitor survey.
+September 2017. We now discuss the results from the answerer and
+visitor survey separately.
 
@@
 Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 that
-have more than 10 years of software development experience, while a slightly less
-percentage of 50\% in Group 2.
+have more than 10 years of software development experience, while a slightly
+less percentage of 50\% in Group 2.
 
@@
 Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty-two (82\%) and
-sixty (60\%) of answerers from Group 1 and Group 2  answer questions at
-least once a week.
-More than half of the answerers very frequently (81--100\% of the time) or
-frequently (61--80\% of the time) include code snippets in their answers. To
-break down into two groups as depicted in
+sixty (60\%) of answerers from Group 1 and Group 2  answer questions at least
+once a week. More than half of the answerers very frequently (81--100\% of the
+time) or frequently (61--80\% of the time) include code snippets in their
+answers. To break down into two groups as depicted in
 Figure~\ref{fig:survey_answer_frequency_with_code}, Group 1 very frequently
 (48.7\%) and frequently (27.4\%) provide code examples when answering. Likewise,
-Group 2 does the same (very frequently for 32.1\% and frequently for 36.9\%).
+Group 2 follow the same trend (very frequently for 32.1\% and frequently for
+36.9\%). Interestingly, there is one participant who never include code snippet
+in his/her answer thus the results after this question are from 116 participants.
 
@@
 
-To answer this research question, we ask the participants for original sources
-of their code examples. We provided six options (allowing more than one answer)
-including \textit{I copied them from my own personal projects}, \textit{I copied
-	them from my company's projects}, \textit{I copied them from open source
-	projects}, \textit{I wrote the new code from scratch}, \textit{I copied the code
-	from the question and modify it for the answer}, and \textit{Others}. The
-answers are shown in Figure~\ref{fig:survey_snippet_source}. Participants in
-Group 1 mainly write new code from scratch (116) or copy from the code snippets
-in question and modify it for the answer (112), followed by from their personal
-projects (105), open source projects (77), other sources (59), and company
-projects (48). For Group 2, the main source is also writing code from scratch
-(83), followed by copying from personal projects and modifying from the question
-(77), copying from open source projects (56), copying from other sources (40),
-and copying from company projects (31).
+To answer this research question, we asked the participants for the original
+source of their code examples. We provided six options (allowing more than one
+answer) including \textit{I copied them from my own personal projects},
+\textit{I copied them from my company's projects}, \textit{I copied them from
+	open source projects}, \textit{I wrote the new code from scratch}, \textit{I
+	copied the code from the question and modify it for the answer}, and
+\textit{Others}. The answers are shown in
+Figure~\ref{fig:survey_snippet_source}. Participants in Group 1 mainly write new
+code from scratch (116) or copy from the code snippets in question and modify it
+for the answer (112), followed by from their personal projects (105), open
+source projects (77), other sources (59), and company projects (48). For Group
+2, the main source is also writing code from scratch (83), followed by copying
+from personal projects and modifying from the question (77), copying from open
+source projects (56), copying from other sources (40), and copying from company
+projects (31). There are 133 answerers out of total 607 from two groups who have cloned
+code snippets from open source projects into their answers at least once. We are interested
+in this type of clones and will investigate further in the later RQs.
 
@@
 
-Half of the top answerers on Stack Overflow
-are aware of outdated code in their answers. We found that 71.6\% of Stack Overflow answerers in Group 1 have been notified of
-outdated code in at least one of their answers (see Figure~\ref{fig:survey_outdated}). The ratio drops to 57.1\% in
-Group 2.
+Half of the top answerers on Stack Overflow are aware of outdated code in their
+answers. As visualised in Figure~\ref{fig:survey_outdated}, 83 participants (71.6\%)
+of Stack Overflow answerers in Group 1 have been notified of outdated code in at
+least one of their answers. The ratio drops to 48 participants (57.1\%) in Group 2.
 
@@
 
-We then asked the participants who have been notified of their outdated code
-(81 and 48 participants from Group 1 and 2 respectively) a
-follow-up questions \textit{``how frequently did you fix your outdated code on Stack
-Overflow?''} The answers, depicted in Figure~\ref{fig:survey_outdated_fix}, show that
-more than half of them frequently fix the outdated code snippets. However, there
-are 19.8\% and 18.8\% of the answerers in Groups 1 and 2 who rarely or never fix their code.
+We then asked the participants who have been notified of their outdated code (83
+and 48 participants from Group 1 and 2 respectively) a follow-up questions
+\textit{``how frequently did you fix your outdated code on Stack Overflow?''}
+The answers, depicted in Figure~\ref{fig:survey_outdated_fix}, show that more
+than half of them frequently fix the outdated code snippets. However, there are
+17 (19.8\%) and 9 (18.8\%) participants in Groups 1 and 2 who rarely, very
+rarely or never fix their code.
+
+Regarding this issue of outdated code, one participant expresses their concern
+in the open comment question: \textit{``The main problem for me/us is outdated
+	code, esp. as old answers have high Google rank so that is what people see
+	first, then try and fail. Thats why we're moving more and more of those examples
+	to knowledge base and docs and rather link to those.''} On the other hand,
+another participant does not  worry about his/her outdated code and how he
+or she handles them: \textit{``On
+	the matter of deprecation, I almost entirely use .NET which has got different
+	versions of the framework. Therefore, code deprecation is not often a problem
+	since what is deprecated on one version of the framework may be the only way of
+	solving a given problem on an older version of the framework. I may also have to
+	add that questions I tend to answer are about how to solve general coding
+	problems so they are not usually subject to deprecation.''}
 
@@
 As shown in Figure~\ref{fig:survey_license_known}, more than half of the
-answerers in both groups (62.1\% and 61.9\% respectively) are aware that Stack
+answerers in both groups, 72 (62.1\%) and 53 (62.3\%) respectively, are aware that Stack
 Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC BY-SA
-3.0) to content in the posts, including code snippets, while the rest of 37.9\%
-and 38.1\% are not.
+3.0) to content in the posts, including code snippets, while the rest of 44 (37.9\%)
+and 32 (37.6\%) are not.
 
@@
 
-Almost every answerer in both groups (98\% and 99\% respectively) does not
-include license statement in their code snippets (numbers are shown in
-Figure~\ref{fig:survey_license}). Some of the participants explain the reason in
-the open comment question which we summarised into three groups as follows.
-First, they choose to post only their own code or code that is adapted from the
-question. The code is automatically subjected to Stack Overflow's CC BY-SA 3.0.
-Second, they copy the code from company or open source projects that they know are
-permitted to be publicly distributed. Hence, no license statement is required.
-Third, some answerers believe that code snippets in their answers are too small
-to claim any intellectual property on them and fall under fair
-use~\citep{fairuse}.
+Almost every answerer in both groups, 114 out of 116 (98\%) and 84 out of 85
+(99\%) respectively, does not include license statement in their code snippets
+(numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
+explain the reason in the open comment question which we summarised into three
+groups as follows. First, they choose to post only their own code or code that
+is adapted from the question. The code is automatically subjected to Stack
+Overflow's CC BY-SA 3.0 without any explicit licensing statement. Second, they
+copy the code from company or open source projects that they know are permitted
+to be publicly distributed. Hence, no license statement is required. Third, some
+answerers believe that code snippets in their answers are too small to claim any
+intellectual property on them and fall under fair use~\citep{fairuse}.
 
@@
 
-While nobody explicitly includes a software license in their snippets,
-many users include a statement on their profile page that states all their
+While almost nobody explicitly includes a software license in their snippets,
+many participants include a statement on their profile page that all their
 answers are under a certain license. For example, \textit{All code posted by me on
@@
 	for any purpose. It is provided "as-is" without warranty of any kind.}  Many
-users either declare their snippets to be public domain, or they grant
+participants either declare their snippets to be public domain, or they grant
 additional licenses, e.g. Apache 2.0 or MIT/Expat.
@@
 answers and Stack Overflow's CC BY-SA 3.0. As shown in
-Figure~\ref{fig:survey_license_check}, 69\% of answerers from both groups did
-not perform the checking. There are only approximately 10\% of the answerers who
-frequently checks for licensing conflicts when they copy code snippets to Stack
-Overflow.
+Figure~\ref{fig:survey_license_check}, 80 (69\%) and 58 (69\%) answerers from
+group 1 and group 2 did not perform the checking. There are only approximately
+10\% of the answerers who frequently checks for licensing conflicts when they
+copy code snippets to Stack Overflow.
 
@@
 	\parbox[c][1.5cm]{0.98\textwidth}{%
-		\textit{For RQ3, approximately 60\% of answerers are aware of CC BY-SA 3.0
-			license enforced by Stack Overflow. However, 98--99\% of the answerers do not
-			include software license in their Stack Overflow snippets nor check for
-			licensing conflicts when they copy code snippets to Stack Overflow answers.}
-	}%
+		\textit{For RQ3, approximately 62\% of our participants are aware of CC BY-SA
+			3.0 license enforced by Stack Overflow. However, 98--99\% of the answerers
+			never include software license in their Stack Overflow snippets. Sixty-nine
+			percent never check for licensing conflicts when they copy code snippets to
+			Stack Overflow answers.} }%
 } \vspace{0.5cm}
 
-In addition, we invited the answerers to give comments regarding their concerns
-when answering Stack Overflow (SO) with code snippets. Some interesting comments
-are selected and discussed below. The full set of answers can be found in the
-Appendix~\ref{appendixC}.
+To acquire additional insights, we invited every answerers for
+further comments regarding their concerns of answering Stack Overflow (SO)
+with code snippets. Some interesting comments are selected and discussed below.
+The full set of answers can be found in the Appendix~\ref{appendixC}.
 
@@
 
-	\item Comment 4: The answerer discusses a problem from outdated Stack Overflow code snippets and
+	\item Comment 4: As shown in RQ2, the answerer discusses a problem from outdated Stack Overflow code snippets and
 	his/her solution.
@@
 
-To answer RQ4 and RQ5, we ask Stack Overflow visitors about their experiences of
-outdated code and their awareness to software license of Stack Overflow code
-snippets. We received 89 answers from 5 groups of Stack Overflow visitors. The
-combined results and discussions are presented below.
+To answer RQ4 and RQ5, we used another online survey, the visitor survey, to ask
+Stack Overflow visitors about their experiences of obsolete code and their
+awareness to software license of Stack Overflow code snippets. We received 89
+answers from 5 groups of Stack Overflow visitors. We combined the results and
+present them as a single group below.
 
@@
 		\centering
-		\includegraphics[width=0.5\linewidth]{survey_visitor_exp}
+		\includegraphics[width=0.4\linewidth]{survey_visitor_exp}
 		\caption{Experience of the Stack Overflow visitors}
@@
 
-\subsubsection*{RQ4: Why developers choose to find programming solutions on Stack Overflow?}
-
-Similar to a study by~\cite{Acar2016}, we asked the participants to rank five
-options, without a tie, they will choose to find programming solutions. The
-given five options include books, official documentations, Stack Overflow,
-online repositories (e.g. GitHub), and others. The results are displayed in
-Figure~\ref{fig:survey_visitor_rankings-crop}. We found that 47 out of 89
-participants rank Stack Overflow as the 1st option to search for programming
-solutions, followed by official documentation (33), online repositories (6),
-other resources (5), and books (1).
+\subsubsection*{RQ4: Where do the developers search for programming solutions?}
+
+We asked the participants to rank five options, without a tie, they will choose
+to find programming solutions. The given five options include books, official
+documentations, Stack Overflow, online repositories (e.g. GitHub), and others.
+The results are displayed in Figure~\ref{fig:survey_visitor_rankings-crop}. We
+found that 47 out of 89 participants rank Stack Overflow as the 1st option to
+search for programming solutions, followed by official documentation (33),
+online repositories (6), other resources (5), and books (1).
 
@@
 
-We then shift the focus to only Stack Overflow. We ask the participants how
-frequently they reuse code snippets from answers on Stack Overflow. According to
-the answers (see Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we
-found that 57 (64\%) participants actively reusing code snippets from Stack
-Overflow. Eight participants (9\%) copy Stack Overflow code every day, 22 (25\%)
-do copying 3-6 times a week, 27 (30\%) do copying once or twice a week. There
-are 2 participants (2\%) who never copy the code from Stack Overflow.
+Since Stack Overflow is among the first research to solve programming tasks, we
+ask the participants how frequently they reuse code snippets from answers on
+Stack Overflow. According to the results (see
+Figure~\ref{fig:survey_visitor_frequency_so_copy-crop}), we found that 57 (64\%)
+participants actively reusing code snippets from Stack Overflow. Eight
+participants (9\%) copy Stack Overflow code every day, 22 (25\%) do copying 3-6
+times a week, 27 (30\%) do copying once or twice a week. There are 2
+participants (2\%) who never copy the code from Stack Overflow.
 
@@
 	mechanism and accepted answers helped to filter good code from bad code}. The
-answers are depicted in Figure~\ref{fig:survey_visitor_why_copy_so}. More than 80\% of the
-participants agree with all the four reasons.
+answers are depicted in Figure~\ref{fig:survey_visitor_why_copy_so}. More than
+80\% of the participants agree with all the four reasons. We observed only two
+``disagree'' and zero ``Strongly disagree'' answer for ``Helpful context'', the
+lowest disagreement among the four reasons. This means most of them agree that
+the context of questions and answers on Stack Overflow help them understand the
+code snippet better.
 
@@
 \vspace{0.5cm} \noindent\fbox{%
-	\parbox[c][1.5cm]{0.98\textwidth}{%
+	\parbox[c][2cm]{0.98\textwidth}{%
 		\textit{For RQ4, Stack Overflow is ranked higher than official documentations,
@@
 	search for on the web. Moreover, 64\% of the participants reuse code snippets
-	from Stack Overflow at least once a week.}
+	from Stack Overflow at least once a week. The copy code from Stack Overflow
+    because they can be found easily from search engine, solve similar problems to
+    their problems, provide helpful context, and offer voting and accepted answers.}
 	}%

### 2017-09-18 cloverflow_technical_report/cloverflow_survey_rn.tex
The first complete draft of the research note from the Stack Overflow surveys.

@@
 \begin{abstract}
-ABSTRACT GOES HERE
+We performed two online surveys of Stack Overflow answerers and visitors to
+assess their awareness to outdated code and software license in Stack Overflow
+answerers. The answerer survey targets 607 Stack Overflow users with high
+reputation and receives a high response rate of 33\%. While most of the code
+snippets in the answers are written from scratch, there are code snippets that
+are cloned from the questions, personal or company projects, and also open
+source projects. Stack Overflow answerers are aware that some of their snippets
+are outdated. However, 19\% of the participants report that they rarely or never
+fix the code. At least 98\% of the answerers never include software license in
+their snippets and 69\% never check for licensing conflicts with Stack
+Overflow's CC BY-SA 3.0 if they copy the code from other sources to Stack
+Overflow answers. The visitor survey uses convenient sampling and receives 89
+responses. We found that 66\% of the participants experience a problem from
+cloning and reusing Stack Overflow snippets. Fifty-six percent of the visitors
+never report the problems back to Stack Overflow. Lastly, 85\% of the
+participants are not aware of CC BY-SA 3.0 license and 62\% never give
+attributions to Stack Overflow posts or answers they copied the code from.
+Moreover, 66\% of the participants do not check for licensing conflicts between
+the cloned Stack Overflow code and their software. We suggest Stack Overflow to
+raise an awareness of their users, both the answerers and the visitors, to the
+problem of code obsolescence and licensing.
 \end{abstract}
@@
 experience to outdated code and code licensing on Stack Overflow. It can break
-down into the following six research questions.
+down into the following five research questions.
 
@@
 	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
-	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
+%	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
 	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
-	\item \textbf{RQ5 (Software licensing issues from Stack Overflow code snippets):}\textit{How often do Stack Overflow visitors check for software licensing issues from code snippets on Stack Overflow?}
+	\item \textbf{RQ5 (Software license of Stack Overflow code snippets):}\textit{Are Stack Overflow visitors aware of code licensing on Stack Overflow}
 \end{enumerate}
@@
 The first three questions will be answered by
-the Stack Overflow answerer survey, while the other three questions will be
+the Stack Overflow answerer survey, while the other two questions will be
 answered by the Stack Overflow visitor survey.
@@
 requirements to take the survey. The third channel collects answers from the
-University of Molise from help of an external researcher. The last two
+University of Molise from the help of an external researcher. The last two
 channels are from a \textsf{comp.lang.java.programmer} Google groups and Software
@@
 
-\subsubsection*{RQ4: Where do the developers search for programming solutions?}
+\subsubsection*{Where do the developers search for programming solutions?}
 
@@
 
-\vspace{0.5cm} \noindent\fbox{%
-	\parbox[c][2cm]{0.98\textwidth}{%
-		\textit{For RQ4, Stack Overflow is ranked higher than official documentations,
-	online repositories, and book as the resource to look for programming
-	solutions. Developers rely on Stack Overflow answers because they are easy to
-	search for on the web. Moreover, 64\% of the participants reuse code snippets
-	from Stack Overflow at least once a week. The copy code from Stack Overflow
-    because they can be found easily from search engine, solve similar problems to
-    their problems, provide helpful context, and offer voting and accepted answers.}
-	}%
-} \vspace{0.5cm}
-
-\subsubsection*{RQ5: What are the problems Stack Overflow visitors experiencing
+To sum up, Stack Overflow is ranked higher than official documentations, online
+repositories, and book as the resource to look for programming solutions.
+Developers rely on Stack Overflow answers because they are easy to search for on
+the web. Moreover, 64\% of the participants reuse code snippets from Stack
+Overflow at least once a week. The copy code from Stack Overflow because they
+can be found easily from search engine, solve similar problems to their
+problems, provide helpful context, and offer voting and accepted answers.
+
+\subsubsection*{RQ4: What are the problems Stack Overflow visitors experiencing
 	from reusing code snippets on Stack Overflow?}
@@
 The problems from reusing Stack Overflow code snippets (illustrated in
-Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions,the code
-claims to solve the problem in the question while it does not,  (20 out of 57
-$\approx$ 35\%); outdated solutions, i.e.~the code may work with the some older
-versions of the library or API, but not the one they are using, (39 out of 57
-$\approx$ 68\%); mismatched solutions, i.e.~the code solves the problem in the
-question but it is not exactly the right solution for their problem, (40 out of
-57 $\approx$ 70\%); and buggy code (1 out of 57 $\approx$ 2\%). Stack Overflow
-visitors rarely report the problems back to the discussion threads (as can be
-seen in Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32
-participants who encounter problems of Stack Overflow snippets, 18 of them
-(56\%) never report the problems. As shown in
-Figure~\ref{fig:survey_visitor_how_report_problems}, the 14 participants who
-reported the problems did so by writing a comment (10), down-voting the answer
-(8), contacted the answerer (2), and posting the new and correct answer (2).
+Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions, i.e.~the
+code claims to solve the problem in the question while it does not,  (28 out of
+57 $\approx$ 49\% participants reported this); outdated solutions, i.e.~the code
+may work with the some older versions of the library or API, but not the one
+they are using, (39 out of 57 $\approx$ 68\% participants reported this);
+mismatched solutions, i.e.~the code solves the problem in the question but it is
+not exactly the right solution for their problem, (40 out of 57 $\approx$ 70\%
+participants reported this); and buggy code (1 out of 57 $\approx$ 2\%
+participants reported this).
+
+Stack Overflow visitors rarely report the problems back to the discussion
+threads (as can be seen in
+Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32 participants
+who encounter problems of Stack Overflow snippets, 18 of them (56\%) never
+report the problems. Fourteen participants who reported the problems
+did so by writing a comment (10), down-voting the answer (8), contacted the
+answerer (2), and posting the new and correct answer (2), as shown in
+Figure~\ref{fig:survey_visitor_how_report_problems}.
 
@@
 \vspace{0.5cm} \noindent\fbox{%
-	\parbox[c][2cm]{0.98\textwidth}{%
-		\textit{For RQ5, our survey results show that 57 out of 87 Stack Overflow
+	\parbox[c][2.2cm]{0.98\textwidth}{%
+		\textit{For RQ4, our survey results show that 57 out of 87 Stack Overflow
 			visitors find a problem from reusing Stack Overflow code snippets. Ten
-			participants experience the problems on more 80\% of the copied snippets and
-			sixteen participants face the problems on 40--60\% of the reused code. The
-			mostly found problem is a mismatched solution (40), followed by outdated
-			solution (39), incorrect solution (20), and buggy code (1). Fifty-six percent
+			participants experience the problems from more than 80\% of the copied snippets and
+			sixteen participants face the problems from 40--60\% of the reused code. The
+			problems ranked by frequency include mismatched solutions (40), outdated
+			solutions (39), incorrect solutions (28), and buggy code (1). Fifty-six percent
 			of the participants never report the problems back to Stack Overflow.}}%
@@
 
-\subsubsection*{RQ6: Are Stack Overflow visitors aware of the the CC BY-SA 3.0
-	license enforced by Stack Overflow?}
+\subsubsection*{RQ5: Are Stack Overflow visitors aware of code licensing on Stack Overflow?}
 
@@
 Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0 Unported (CC
-BY-SA 3.0) to content in the posts, including code snippets. As a consequence,
+BY-SA 3.0) to content in the posts, including code snippets. As a consequence
 62\% of the visitors never give an attribution, which is required by CC BY-SA
@@
 
-\vspace{0.5cm} \noindent\fbox{%
-	\parbox[c][1cm]{0.98\textwidth}{%
-		\textit{For RQ6, 85\% of the participants are not aware of Stack Overflow CC
-	BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
-	they copied the code snippets from.}}%
-} \vspace{0.5cm}
-
-\subsubsection*{RQ7: How often do Stack Overflow visitors check for software
-	licensing issues from code snippets on Stack Overflow?}
-
-Figure~\ref{fig:survey_visitor_original_license} shows that 79\% (69) Stack
-Overflow visitors who adopted code from Stack Overflow never check if the code
-snippet originated from a different source (e.g. an open source project) with an
-incompatible license to their projects.
-
-Sixty-six percent of the participants never check for licensing conflicts at all
+%\subsubsection*{RQ7: How often do Stack Overflow visitors check for software
+%	licensing issues from code snippets on Stack Overflow?}
+
+Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow
+never check if the code snippet originated from a different source (e.g. an open
+source project) with an incompatible license to their projects (see
+Figure~\ref{fig:survey_visitor_original_license}).
+
+Fifty seven participants (66\%) never check for licensing conflicts at all
 when reusing Stack Overflow code (see
@@
 the participants experience legal issues by reusing code snippets on Stack
-Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}).
+Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}). Nonetheless, as we designed the
+survey to be anonymous, it is not possible to contact them for further details
+on the legal issues they found.
 
@@
 \vspace{0.5cm} \noindent\fbox{%
-	\parbox[c][1cm]{0.98\textwidth}{%
-		\textit{For RQ7, we found that 66\% of the visitors never check for software
+	\parbox[c][1.7cm]{0.98\textwidth}{%
+		\textit{For RQ5, 85\% of the participants are not aware of Stack Overflow CC
+			BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts
+			they copied the code snippets from. We found that 66\% of the visitors never check for software
 	licensing conflicts between Stack Overflow code snippets and their projects.
@@
 \subsection{Internal Validity}
-We targeted the participants for the answerer survey based on their Stack Overflow
-reputation instead of random sampling. This is because reflects the developers
-involvement in asking and answering questions on the site. Thus, our findings
-capture awareness and experience of experienced Stack Overflow developers. Moreover,
-due to a large number of users on Stack Overflow, we could invite only 607
-highly-ranked developers to participate in the study.
-
-We selected the participants for the visitor survey based on convenient sampling which
-could suffer from bias and outliers.
+Due to a large number of users on Stack Overflow, we could invite only 607
+developers to participate in the answerer survey. If all the developers are
+invited, which is almost impossible considering 7.6 million users on Stack
+Overflow, the results may be different. Nevertheless, we mitigate this threat to
+internal validity by selecting the participants based on their Stack Overflow
+reputation. This targeted selection of the participants makes sure that we
+invite developers who have been actively involved in asking and answering
+questions on the site for a long period of time, and refrain from inviting new
+users who merely answer a question or two. The highest reputation user invited
+to our survey answered 33,933 questions and the lowest reputation user in our
+survey answered 116 questions.
+
+We selected the participants for the visitor survey based on convenient sampling
+which could suffer from bias and outliers. We mitigate the threat by inviting
+different groups of participants ranging from the author's social media,
+technology news and media community, software engineering community (on
+Facebook), Java programmer discussion thread (com.lang.java.programmer), and
+from University of Molise.
 
@@
 While the reputation is a good proxy to reflect the amount of answers the
-developers have given, it might not cover all kinds of answerers on Stack
-Overflow. The answerers who have lower-reputation than 6,999 were not invited to
-our study and their awareness and experience may differ from our findings.
-
-At least 39\% of the participants in the visitor survey are from
-\textsf{blognone.com} which is based in Thailand. Due to working culture,
-answers from this group of developers may only represent software developers in
-Thailand. We alleviate this concern by inviting participants from other groups,
-e.g.~University of Molise in Italy, comp.lang.java.programmer, and Software
-Engineering Facebook group.
+developers have given, it might not cover all kinds of answerers and their
+experience on Stack Overflow. The answerers who have lower-reputation than 6,999
+were not invited to our study and their awareness and experience may differ from
+our findings. Hence, our findings may not be generalised to all Stack Overflow
+answerers.
+
+At least 39\% of the participants in the visitor survey are from Thailand
+(\textsf{blognone.com} and some of the first author's contacts). Due to working
+culture, answers from this group of developers may only represent software
+developers in Thailand. Similarly our findings from the visitor survey may not
+be generalised to all Stack Overflow visitors. We alleviate this concern by
+inviting participants from other groups, e.g.~University of Molise in Italy,
+comp.lang.java.programmer, and Software Engineering Facebook group.
 
@@
 visitors regarding their awareness and experience of answering and reusing code
-snippets on Stack Overflow. We are interested in cloned code in Stack Overflow
+snippets on Stack Overflow. We are interested in cloned snippets in Stack Overflow
 answers. Two online surveys have been performed to find out \textit{where} are
@@
 is usually written from scratch to answer a question. Nonetheless, there are
-some code snippets that are copied from the answerers' personal, open source, or
-company projects.
+some code snippets that are copied from the answerer personal or company projects,
+and open source software.
 
@@
 although the answerers are aware of outdated code in their answers, 19\% of them
-rarely or never fix the code.
-
-Regarding the software license, approximately 60\% of the answerers are aware of
+rarely or never fix the code. One answerer express a concern of having
+outdated code in his/her popular answer (by having high Google rank) being used 
+by many other developers.
+
+Approximately 60\% of the answerers are aware of
 Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
 the license in their answers nor check for licensing conflicts when they copy
-the code from another location and paste in the answer.
+the code from another location and paste in the answer. Some developers believe
+the code are too small and fall under fair use policy while others state the license
+of their code in their profile pages instead.
 

### 2017-09-24 cloverflow_technical_report/cloverflow_survey_rn.tex
Latest update. Added a missing results (answerer survey).

@@
 assess their awareness to outdated code and software license in Stack Overflow
-answerers. The answerer survey targets 607 Stack Overflow users with high
-reputation and receives a high response rate of 33\%. While most of the code
-snippets in the answers are written from scratch, there are code snippets that
-are cloned from the questions, personal or company projects, and also open
-source projects. Stack Overflow answerers are aware that some of their snippets
-are outdated. However, 19\% of the participants report that they rarely or never
-fix the code. At least 98\% of the answerers never include software license in
-their snippets and 69\% never check for licensing conflicts with Stack
-Overflow's CC BY-SA 3.0 if they copy the code from other sources to Stack
-Overflow answers. The visitor survey uses convenient sampling and receives 89
-responses. We found that 66\% of the participants experience a problem from
+answerers. The answerer survey targets 607 highly reputable Stack Overflow users
+and receives an impressive response rate of 33\%. Our findings are as follows.
+Although most of the code snippets in the answers are written from scratch,
+there are code snippets cloned from the questions, personal or company projects,
+and from open source projects. Stack Overflow answerers are aware that some of
+their snippets are outdated. However, 19\% of the participants report that they
+rarely or never fix the code. At least 98\% of the answerers never include
+software license in their snippets and 69\% never check for licensing conflicts
+with Stack Overflow's CC BY-SA 3.0 if they copy the code from other sources to
+Stack Overflow answers. The visitor survey uses convenient sampling and receives
+89 responses. We found that 66\% of the participants experience a problem from
 cloning and reusing Stack Overflow snippets. Fifty-six percent of the visitors
-never report the problems back to Stack Overflow. Lastly, 85\% of the
-participants are not aware of CC BY-SA 3.0 license and 62\% never give
-attributions to Stack Overflow posts or answers they copied the code from.
+never report the problems back to Stack Overflow. Eighty-five percent of the
+participants are not aware of CC BY-SA 3.0 license, and sixty-two percent never
+give attributions to Stack Overflow posts or answers they copied the code from.
 Moreover, 66\% of the participants do not check for licensing conflicts between
-the cloned Stack Overflow code and their software. We suggest Stack Overflow to
-raise an awareness of their users, both the answerers and the visitors, to the
-problem of code obsolescence and licensing.
+the copied Stack Overflow code and their software. With these findings, we
+suggest Stack Overflow raise an awareness of their users, both the answerers and
+the visitors, to the problem of outdated and license-violating code snippets.
 \end{abstract}
@@
 originals, which are further modified due to bug fixing or feature improvements.
-In addition, Some snippets are copied from software systems with stricter
-license than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA
-3.0). Prior to this study, we performed a quantitative empirical study using
-code clone detection tools to locate cloned code snippets in accepted answers.
-We found that many snippets were copied from open source projects. Some cloned
-snippets are outdated (or obsolete) and some possibly violate the original software license.
-These snippets are potentially harmful to reuse. To accompany the findings and
-gain insights into the cause of the problems, we resort to a qualitative study
-using an online survey of Stack Overflow developers who 1) regularly answer
-programming questions with code snippets and 2) reuse code snippets from Stack
-Overflow. \textbf{The study aims to understand the developers' awareness and
-	experience to outdated code and code licensing on Stack
-	Overflow.}
+Besides, Some snippets are copied from software systems with stricter license
+than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior
+to this study, we performed a quantitative empirical study using code clone
+detection tools to locate cloned code snippets in accepted answers. We found
+that many snippets were copied from open source projects. Some cloned snippets
+are outdated (or obsolete) and some possibly violate the original software
+license. These snippets are potentially harmful to reuse. To accompany the
+findings and gain insights into the cause of the problems, we resort to a
+qualitative study using an online survey of Stack Overflow developers who 1)
+regularly answer programming questions with code snippets and 2) reuse code
+snippets from Stack Overflow. \textbf{The study aims to understand the
+	developers' awareness and experience to outdated code and code licensing on
+	Stack Overflow.}
 
@@
 problem and reused them with or without a modification. We ask the visitors
-about their experience of reusing source code from Stack Overflow and the problems
-they faced including code obsolescence and software license.
+about their experience of reusing source code from Stack Overflow and the
+problems they faced including code obsolescence and software license.
 
@@
 and~\cite{Kitchenham2002} by setting specific and measurable objective,
-designing and scheduling the survey, selecting participants, analysing the data, and reporting the results.
-We now discuss each of them in detail.
+designing and scheduling the survey, selecting participants, analysing the data,
+and reporting the results. We now discuss each of them in detail.
 
@@
 	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
-	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
+	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing conflicts):} \textit{Are Stack Overflow answerers aware of software licensing
+		conflicts caused by code snippets in their answers?}
 %	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
@@
 be shown to the participants based on their previous answers. The survey
-collects information of the participant's software development experience, the
+collects information about the participant's software development experience, the
 experience of answering Stack Overflow questions, sources of the Stack Overflow
@@
 questions will be shown to the participants based on their previous answers. The
-survey collects information of the participant's software development
+survey collects information about the participant's software development
 experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
@@
 the community trusts the user. A user earns reputation when he or she receives
-up votes for good questions and useful answers. Accepted answers receive more
+upvotes for good questions and useful answers. Accepted answers receive more
 reputation score than questions and regular answers\footnote{Stack Overflow
@@
 can compare the results or observe similar patterns between them. The first
-group had reputation from 963,731 (the highest) to 7,674, and the second group
-had reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
+group had a reputation from 963,731 (the highest) to 7,674, and the second group
+had a reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
 (excluding undelivered ones) respectively.
@@
 We adopted non-probability convenient sampling to invite participants for this
-survey. Participation in the survey requires experience of
-visiting Stack Overflow for solving programming tasks at least once. The
-participants were invited to take the survey via five channels. The first
-channel is via the first author's social media post (Facebook) where the he
-invited friends who are software developers and have experience of copying code
-snippets from Stack Overflow to take the survey. The second channel is a popular
-technology news and media community in Thailand called \textsf{blognone.com} which
-attracts a high number of Thai software developers. The first author posted an
-invitation to the visitor survey in a discussion forum mentioning the
-requirements to take the survey. The third channel collects answers from the
-University of Molise from the help of an external researcher. The last two
-channels are from a \textsf{comp.lang.java.programmer} Google groups and Software
-Engineering Facebook page. The number of participants taken the survey is shown in
+survey. Participation in the survey requires experience of visiting Stack
+Overflow for solving programming tasks at least once. The participants were
+invited to take the survey via five channels. The first channel is via the first
+author's social media post (Facebook) inviting software developers who have
+experience of copying code snippets from Stack Overflow to take the survey. The
+second channel is a popular technology news and media community in Thailand
+called \textsf{blognone.com} which attracts a high number of Thai software
+developers. The first author posted an invitation to the visitor survey in a
+discussion forum mentioning the requirements to take the survey. The third
+channel collects answers from the University of Molise from the help of an
+external researcher. The last two channels are from a
+\textsf{comp.lang.java.programmer} Google groups and Software Engineering
+Facebook page. The number of participants taken the survey is shown in
 Table~\ref{tab:visitors}.
@@
 Group 2 follow the same trend (very frequently for 32.1\% and frequently for
-36.9\%). Interestingly, there is one participant who never include code snippet
-in his/her answer thus the results after this question are from 116 participants.
+36.9\%). Interestingly, there is one participant who never includes code snippet
+in his/her answer thus the results after this question is from 116 participants.
 
@@
 		\centering
-		\includegraphics[width=0.9\linewidth]{survey_answer_frequency_with_code_2}
+		\includegraphics[width=\linewidth]{survey_answer_frequency_with_code_2}
 		\caption{Group 2}
@@
 Half of the top answerers on Stack Overflow are aware of outdated code in their
-answers. As visualised in Figure~\ref{fig:survey_outdated}, 83 participants (71.6\%)
-of Stack Overflow answerers in Group 1 have been notified of outdated code in at
-least one of their answers. The ratio drops to 48 participants (57.1\%) in Group 2.
+answers. Seventy-one participants (61.2\%) of Stack Overflow answerers in Group
+1 have been notified of outdated code in at least one of their answers. The
+ratio drops to forty participants (47.1\%) in Group 2. We asked a follow up
+question regarding the frequency of being notified of outdated code in their
+answers. We found that only 0.5\% and 5.2\% of the answerers in Group 1
+frequently or occasionally been notified. The answerers in Group 2 have very
+frequently and occasionally been notified for 2.4\% and 3.5\% respectively.
+Please note that we found inconsistencies between the answers of these two
+questions. The percentage of participants who ``Never'' been notified of
+outdated code in their Stack Overflow answers are 38.8\% and 52.9\% for Group 1
+and Group 2 respectively. However, the answers for frequency of being notified
+equal to ``Never'' decrease to 28.4\% and 43.5\% for Group 1 and 2 respectively
+(see
+Figure~\ref{fig:survey_outdated}~and~Figure~\ref{fig:survey_outdated_freq}).
 
@@
 	\label{fig:survey_outdated}
+\end{figure}
+
+\begin{figure}
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{survey_outdated_freq_1}
+		\caption{Group 1}
+		\label{fig:survey_outdated_freq_1}
+	\end{subfigure}%
+	\begin{subfigure}{.5\textwidth}
+		\centering
+		\includegraphics[width=.8\linewidth]{survey_outdated_freq_2}
+		\caption{Group 2}
+		\label{fig:survey_outdated_freq_2}
+	\end{subfigure}
+	\caption{Frequency of being notified of outdated code in the answerers' answers.}
+	\label{fig:survey_outdated_freq}
 \end{figure}
@@
 internal validity by selecting the participants based on their Stack Overflow
-reputation. This targeted selection of the participants makes sure that we
+reputation. This targeted participant selection ensures that we
 invite developers who have been actively involved in asking and answering
@@
 visitors regarding their awareness and experience of answering and reusing code
-snippets on Stack Overflow. We are interested in cloned snippets in Stack Overflow
-answers. Two online surveys have been performed to find out \textit{where} are
-the code snippets in Stack Overflow answers from and \textit{how} developers, in
-terms of both Stack Overflow answerers and visitors, handle potential problem of
-outdated code and software licensing conflicts.
-
-From the answerer's responses, we discovered that code in Stack Overflow answers
+snippets on Stack Overflow. We are particularly interested in cloned code
+snippets in Stack Overflow answers. Thus, the two online surveys are performed to
+find out the \textit{origin} of code snippets in Stack Overflow answers and
+\textit{awareness} of Stack Overflow developers, both answerers and visitors,
+to the problem of outdated and license-violating code.
+
+From the answerer's responses, we discover that code in Stack Overflow answers
 is usually written from scratch to answer a question. Nonetheless, there are
-some code snippets that are copied from the answerer personal or company projects,
-and open source software.
-
-The outdated code on Stack Overflow occurs when the code snippet in an answer is
+some code snippets that are copied from the answerer personal or company
+projects, and open source software.
+
+Outdated code on Stack Overflow occurs when a code snippet is
 copied from another location and is no longer up-to-date. The results show that
 although the answerers are aware of outdated code in their answers, 19\% of them
-rarely or never fix the code. One answerer express a concern of having
-outdated code in his/her popular answer (by having high Google rank) being used 
+rarely or never fix the code. One answerer expresses a concern of having
+an outdated code in his/her popular answer reused
 by many other developers.
 
-Approximately 60\% of the answerers are aware of
-Stack Overflow CC BY-SA 3.0. Ninety-eight to ninety-nine percent do not include
-the license in their answers nor check for licensing conflicts when they copy
-the code from another location and paste in the answer. Some developers believe
-the code are too small and fall under fair use policy while others state the license
-of their code in their profile pages instead.
-
-From the visitor's responses, Stack Overflow is ranked the highest as the
-resource to solve programming tasks because it is easy to be found by search
-engines. More than half of them (64\%) reuse code from Stack Overflow at least
-once a week. Sixty-seven percent of the visitors find a problem from reusing
-Stack Overflow snippets ranging from a mismatched solution, outdated solution,
-incorrect solution, and buggy code. However, 56\% of the participants never
-report the problems back to Stack Overflow.
+Approximately 60\% of the answerers are aware of Stack Overflow CC BY-SA 3.0
+license applied to code on Stack Overflow. Ninety-eight to ninety-nine percent
+does not include license in their answers nor check for licensing conflicts when
+they copy the code from another location to their answer. Some developers
+believe the code is too small and fall under fair use policy. Many answerers
+mention the license of their code in their profile page instead.
+
+From the visitor's responses, Stack Overflow is ranked the highest as a resource
+to solve programming tasks. They agree that Stack Overflow answers are easy to
+find by search engines. More than half of them (64\%) reuse code from Stack
+Overflow at least once a week. Sixty-seven percent of the visitors find a
+problem from reusing Stack Overflow snippets ranging from a mismatched solution,
+outdated solution, incorrect solution, and buggy code. However, 56\% of the
+participants never report the problems back to Stack Overflow.
 
 Eighty-five percent of the visitors are not aware of Stack Overflow's CC BY-SA
-3.0 and 62\% never give attributions to Stack Overflow posts that they copied
-the code from. Moreover, 66\% of them never check for licensing conflicts while
+3.0 and sixty-two percent never give attributions to Stack Overflow posts that they copied
+the code from. Moreover, sixty-six percent never check for licensing conflicts while
 reusing Stack Overflow code snippets in their software projects.
+
+With these findings, we
+suggest Stack Overflow raise an awareness of their users, both the answerers and
+the visitors, to the problem of outdated and license-violating code snippets.
 
@@
 
-This appendix contains additional materials of the Stack Overflow answerer survey questions, the visitor survey questions, and the complete set of open comments from the Stack Overflow answerers.
+This appendix contains additional materials of the Stack Overflow answerer
+survey questions, the visitor survey questions, and the complete set of open
+comments from the Stack Overflow answerers.
 

### 2017-09-25 EmailExtractor/MailController.py
Removed emails

@@ -1,63 +1,0 @@
-import smtplib
-import getpass
-from email.mime.text import MIMEText
-
-mailTitle = "Outdated and license-violating code snippets on Stack Overflow" # Mail title
-
-me= 'ucabagk@ucl.ac.uk' # Change with your UCL email address with alias
-uclAccount = ""
-password = ""
-
-
-def init():
-    global uclAccount
-    global password
-    uclAccount = raw_input("Enter your ucl email id (not alias): ")
-    password = getpass.getpass("Please enter your password: ")
-
-
-def sendMail(recipient):
-    global uclAccount
-    global password
-    if (uclAccount == ""):
-        init()
-
-    mailContent = '''
-Dear Developer, 
-
-Since you are one of the top answerers on Stack Overflow, we hope you can help us with a not-for-profit study.
-
-We are researchers in the Software Systems Engineering Group at University College London, UK. We are studying problems caused by outdated and license-violating code snippets on Stack Overflow. 
-
-We have designed a survey to understand these problems and would be grateful if you would complete it:
-
-https://docs.google.com/forms/d/e/1FAIpQLSfagOcgFYYqt0vMLZOoacGQ55SeZyhF1g5MTinTBoD23FRktQ/viewform?usp=sf_link
-
-The survey is completely anonymous and has 11 questions and should only take about 3-5 minutes to complete. 
-
-The survey results will be used only for academic research purposes and we plan to release the results to Stack Overflow and in the form of academic papers and presentations.
-
-Your email address has been extracted from Stack Overflow and GitHub websites and it will not be saved or distributed to other parties.
-
-This research project has been approved by the designated ethics officer in the Computer Science Department at UCL.
-
-Thank you,
-Chaiyong Ragkhitwetsagul, Jens Krinke
-CREST, Dept. of Computer Science
-University College London
-www.cs.ucl.ac.uk/staff/C.Ragkhitwetsagul
-    '''
-    MSG_TEMPLATE="\r\n".join([
-        "From: %s"%me,
-        "To: %s"%recipient,
-        "Subject: %s"%mailTitle,
-        "",
-        mailContent])
-
-    msg = MSG_TEMPLATE
-    server = smtplib.SMTP('smtp.office365.com', 587)
-    server.starttls()
-    server.login(str(uclAccount), str(password))
-    server.sendmail(me, recipient, msg)
-    server.quit()
-

### 2017-09-25 EmailExtractor/SendMail.py

@@ -1,67 +1,0 @@
-import MailController #https://gitlab.cs.ucl.ac.uk/snippets/1
-import random
-import time
-import csv
-import traceback
-import sys
-
-
-def writefile(filename, fcontent, mode):
-    """
-    Write the string content to a file
-    copied from
-    http://www.pythonforbeginners.com/files/reading-and-writing-files-in-python
-    :param filename: name of the file
-    :param fcontent: string content to put into the file
-    :param mode: writing mode, 'w' overwrite every time, 'a' append to an existing file
-    :return: N/A
-    """
-    try:
-        file = open(filename, mode)
-        file.write(fcontent)
-        file.close()
-    except Exception as e:
-        traceback.print_exc(file=sys.stdout)
-
-
-def read_csv(file):
-    """
-    Read csv file for email addresses
-    :param file: a csv file
-    :return: list of email addresses
-    """
-    recipients = []
-    with open(file) as csvfile:
-        readCSV = csv.reader(csvfile, delimiter=',')
-
-        for row in readCSV:
-            # skip the page header
-            if len(row) >= 3:
-                # only keep unique emails
-                if not row[0].startswith('page') \
-                        and row[2] not in recipients\
-                        and 'users.noreply.github.com' not in row[2]:
-                    recipients.append(row[2])
-
-    return recipients
-
-
-def main():
-
-    batch_no = 9
-    recipients = read_csv('emails' + batch_no + '.csv')
-    writefile('email_errors.txt', 'Batch: ' + str(batch_no) + '... sending emails to ' + str(len(recipients)) + ' developers.', 'a')
-    # print recipients
-
-    for recipient in recipients:
-        try:
-            MailController.sendMail(recipient)
-            time.sleep(random.randint(1, 3))
-        except Exception as e:
-            error_msg = time.strftime("%H:%M:%S") + ": " + recipient + ": " + str(e) + "\n"
-            writefile('email_errors.txt', error_msg, 'a')
-
-        print('Sent to :' + recipient)
-
-
-main()

### 2017-09-25 EmailExtractor/main.py

@@ -1,132 +1,0 @@
-import urllib2
-import sys, traceback
-import json
-import time
-
-
-def writefile(filename, fcontent, mode):
-    """
-    Write the string content to a file
-    copied from
-    http://www.pythonforbeginners.com/files/reading-and-writing-files-in-python
-    :param filename: name of the file
-    :param fcontent: string content to put into the file
-    :param mode: writing mode, 'w' overwrite every time, 'a' append to an existing file
-    :return: N/A
-    """
-    try:
-        file = open(filename, mode)
-        file.write(fcontent.encode('utf-8', 'ignore'))
-        file.close()
-    except Exception as e:
-        print '-' * 60
-        traceback.print_exc(file=sys.stdout)
-        print '-' * 60
-
-
-def find_email(json, emailstr):
-    email = None
-    for node in json:
-        try:
-            email = node['payload']['commits'][0]['author']['email']
-            return email
-        except Exception as e:
-            continue
-
-    return email
-
-
-reload(sys)
-sys.setdefaultencoding("ISO-8859-1")
-
-for pageno in range(int(sys.argv[1]),1000):
-
-    try:
-        print_buffer = ''
-        print 'page' + str(pageno) + ','
-        print_buffer += 'page' + str(pageno) + ',' + '\n'
-
-        response = urllib2.urlopen('https://stackoverflow.com/users?page=' + str(pageno) + '&tab=reputation&filter=all')
-        html = response.read()
-        lines = html.split('\n')
-
-
-        for index, line in enumerate(lines):
-
-            if '<a href="/users/' in line and '<div class=\"gravatar' in line:
-
-                parts = line.split('"')
-                response2 = urllib2.urlopen('https://stackoverflow.com/' + parts[1])
-                html2 = response2.read()
-                # print html2
-                lines2 = html2.split('\n')
-
-                for index, line2 in enumerate(lines2):
-
-                    # Here re.findall() returns a list of all the found email strings
-                    # emails = re.findall(r'[\w\.-]+@[\w\.-]+', line2)
-                    #
-                    # for email in emails:
-                    #     # do something with each found email string
-                    #     print email
-
-                    if 'email' in line2.lower() or 'e-mail' in line2.lower():
-
-                        # found email on Stack Overflow profile!
-                        print parts[1] + ',' + 'https://stackoverflow.com/' + parts[1] + ',' + line2
[…]

### 2017-09-25 EmailExtractor/temp.py

@@ -1,10 +1,0 @@
-import urllib2
-import json
-
-
-response = urllib2.urlopen('https://api.github.com/users/JoergWMittag')
-html = response.read()
-json_data = json.loads(html)
-
-print json_data
-print json_data['email']

### 2017-10-06 cloneoverflow-fse17/rebuttal/rebuttal.txt
Renamed old paper to "cloverflow-fse17".

--- 2017-05-02 cloneoverflow-latex/rebuttal/rebuttal.txt
@@
+We would like to thank the reviewers for their helpful comments. Please find below the answers.
+
 REVIEWER 1
@@
 Question 1: 
-This study is motivated by [1, 2].
-An et al.
-[2] found that 62 active Android projects contains 232 exact copies of snippets on Stack Overflow (SO) with confirmation from the developers.
-60 apps have license violations between the copied snippets and project's license.
-126 snippets are found to potentially migrate from one app to another via SO posts, i.e.
-'code laundering'.
+Previous studies have found serious problems in code copied from Stack Overflow (SO): An et al.
+[2] found 62 active Android projects to contain 232 exact copies of snippets on SO (confirmed by developers) and 60 apps violate the original license.
+126 snippets were found to potentially migrate from one app to another via SO posts (`code laundering’).
 Acar et al.
-[1] found that SO is often chosen by programmers when solving tasks.
-They examined 139 SO threads used by the participants in four Android security-related tasks and found that only 17% of them contain secure snippets.
-The same security-related problems are discovered in a random sampling of 200,000 apps from Google Play (e.g.
+[1] examined 139 SO threads used by the participants in four Android security-related tasks and found that 83% of them contain insecure snippets.
+The same security-related problems are discovered in a random sampling of 200,000 apps (e.g.
 98.9% implement insecure hostname verifier similarly to the SO examples).
@@
 Question 2:
-The motivation still holds.
 It is known that clone detection tools report a lot of false/trivial clones.
 We focus on the important ones.
-The number of 32,533 analysed clone pairs are the ones that are not trivial clones according to the clone agreement and clone filtering process for feasibility of a manual study.
+The number of 32,533 analysed clone pairs are not trivial clones according to the clone agreement and clone filtering process (making the manual study feasible).
 However, they are not the 'total' number of clones between SO and Qualitas.
+Moreover, one can expect a large number of clones to other projects not in Qualitas.
 
 Question 3:
-No.
-We cannot expect the same results from a different pair of evaluators.
-Classifications of clones by human are known to be very subjective.
-However, we expect similar results with a higher number of evaluators.
+Classifications of clones by humans are known to be very subjective. However, we expect similar results with different evaluators or a higher number of evaluators.
 
@@
 Although the code is provided as minimum working examples, it is known that the code is used as-is and causing problems in active projects [1,2].
-Active maintenance and support provided by SO can mitigate such problems
+Active maintenance and support provided by SO could mitigate such problems.
 
@@
 Question 2:
-See Table 11: 79 (QS) and 77 (EX) pairs (snippets) violate the license but acknowledge the source, 202 (UD) pairs violate the license and have no acknowledgement.
+See Table 11: 79 (QS) and 77 (EX) pairs (snippets) violate the license but acknowledge the source, 202 (UD) pairs violate licenses and have no acknowledgement.
 
@@
 Question 3:
-We consider them as two clone pairs.
-From 32,533 online clone pair candidates, there are 4,018 distinct Qualitas clones (file + start + end lines) and, on average, each of them forms a clone pair with 7.6 distinct Stack Overflow snippets.
+We consider them as two clone pairs. In the set of 671 QS+EX+UD clones pairs, a clone in Qualitas is appearing, on average, in 1.2 SO answers.
 

### 2017-10-06 cloneoverflow-fse17/cloneoverflow_fse17.tex
Renamed old paper to "cloverflow-fse17".

--- 2017-02-28 cloneoverflow-latex/cloneoverflow.tex
@@
 % Copyright
-%\setcopyright{none}
+\setcopyright{none}
 %\setcopyright{acmcopyright}
 %\setcopyright{acmlicensed}
-\setcopyright{rightsretained}
+%\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
 
-\setcopyright{rightsretained}
+%\setcopyright{rightsretained}
 %\setcopyright{usgov}
@@
 % DOI
-\acmDOI{10.475/123_4}
+%\acmDOI{10.475/123_4}
 
 % ISBN
-\acmISBN{123-4567-24-567/08/06}
+%\acmISBN{123-4567-24-567/08/06}
 
 %Conference
-\acmConference[ESEC/FSE 2017]{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--8 September, 2017}{Paderborn, Germany}
-\acmYear{2017}
-\copyrightyear{2017}
-
-\acmPrice{15.00}
-
-%\overfullrule1ex
+%\acmConference[ESEC/FSE 2017]{11th Joint Meeting of the European Software Engineering Conference and the ACM SIGSOFT Symposium on the Foundations of Software Engineering}{4--8 September, 2017}{Paderborn, Germany}
+%\acmYear{2017}
+%\copyrightyear{2017}
+
+%\acmPrice{15.00}
+
+\overfullrule1ex
 
 \begin{document}
-	\title{Outdated and License-Violating Code on Stack Overflow}
+	\title{Toxic Code Snippets on Stack Overflow}
 	%\titlenote{Produces the permission block, and
@@
   % software licensing violations. 
-  Online code clones are code fragments that are copied from software
+ \FIXME{Outdated.~Revise this last}~ Online code clones are code fragments that are copied from software
   projects or online sources to Stack Overflow as examples in

### 2017-10-06 cloverflow-tse/cloverflow.tex
Added technical report updates.
Added latest results to the TSE draft.

@@
 
-\newcommand\FIXME[1]{\textbf{FIXME: #1}}
+\newcommand\FIXME[1]{{\color{red}\textbf{FIXME: #1}}}
 
@@
 % software licensing violations. 
-Online code clones are code fragments that are copied from software
+\FIXME{Outdated.~Revise the last.}~Online code clones are code fragments that are copied from software
 projects or online sources to Stack Overflow as examples in
@@
 %The popularity of the Internet encourages tremendous amount of source code being shared online. 
-Stack Overflow is a popular online programming community with 6.8
-million users\footnote{Statistics as of February 25, 2017 from \url{http://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
+Stack Overflow is a popular online programming community with 7.6
+million users, 14 million questions, and 23 million answers\footnote{Data as of 21
+	August 2017 from~\url{https://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
 to programming problems. The website has found to be useful for
@@
 
-In this study, we are interested in locating online code clones on
-Stack Overflow that are cloned from open source projects and study
-them on two aspects: \textbf{outdated code} and \textbf{license conflicts.}
+The findings from our online survey of Stack Overflow answerers show that code
+reusing activity occurs on Stack Overflow, just like in software. Stack Overflow
+answerers occasionally clone code from other locations, such as their personal
+projects, company projects, and open source projects, to Stack Overflow answers
+as a solution or to complement their answer~\FIXME{put a precise number here}.
+One participants says
+
+\begin{quote}\textit{The real issue is less about the amount the code snippets
+		on SO than it is about the staggeringly high number of software
+		``professionals'' that mindlessly use them without understanding what they're
+		copying, and the only slightly less high number of would-be professionals that
+		post snippets with built-in security issues.  A related topic is beginners who
+		post (at times dangerously) misleading tutorials online on topics they actually
+		know very little about. Think PHP/MySQL tutorials written 10+ years after
+		\texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that
+		got posted the other day on HackerNew
+		(\url{https://news.ycombinator.com/item?id=14846506}). They're also full of
+		toxic code snippets.}\end{quote}
+
+With the same analogy, in this study we are interested in mining Stack Overflow
+posts, detecting online code clones, and revealing \textbf{toxic code snippets},
+which means code snippets that are harmful for reuse.
+Stack Overflow snippets can become toxic because they are outdated and violating
+their original software license. Outdated code snippets can be harmful since
+they may contain defects. Moreover, licensed code snippets that are cloned from
+open source software projects to Stack Overflow without their respective license
+can lead to legal issues if being reused.
 
@@
 	\begin{lstlisting}
-/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2016-09-26) */
+/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2017-10-03) */
 public int compare(byte[] b1,int s1,int l1, ...) {    public int compare(byte[] b1,int s1,int l1, ...) {
@@
 
-A motivating example of outdated online code clones can be found in an
+We would like to motivate the readers to the problem of toxic code snippets
+on Stack Overflow by giving two examples.
+
+The first motivating example of outdated online code clones can be found in an
 answer to a Stack Overflow question regarding how to implement
@@
 \textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
-\Cref{fig:before-after} shows---on the left---a code snippet embedded as a part of the
-accepted answer. The snippet shows how \textsf{hadoop}
-implements the {\small{\texttt{compare}}} method in its
-{\small{\texttt{WritableComparator}}} class. The code snippet on the
-right shows another version of the same method, but at this time
-extracted from the latest version (as of September 26, 2016) of
+\Cref{fig:before-after} shows---on the left---a code snippet embedded as a part
+of the accepted answer. The snippet shows how \textsf{hadoop} implements the
+{\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}}
+class. The code snippet on the right shows another version of the same method,
+but at this time extracted from the latest version (as of October 3, 2017) of
 \textsf{hadoop}. We can see that they both are highly similar except a line
-containing {\small{\verb|buffer.reset(null,0,0);|}} which was added in
-the latest version. The added line is intended for cleaning up the
-reference in the {\small{\verb|buffer|}} variable. While this change
-has already been introduced into the {\small{\texttt{compare}}} method
-in the latest version of \textsf{hadoop}, the code example in Stack
-Overflow post is still unchanged. This example shows that
-inconsistencies between online code clones and their originals can
-lead users of Stack Overflow to reuse outdated code.
+containing {\small{\verb|buffer.reset(null,0,0);|}} which was added on November
+21, 2014. The added line is intended for cleaning up the reference in the
+{\small{\verb|buffer|}} variable and avoid excess heap usage
+(HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
+While this change has already been introduced into the
+{\small{\texttt{compare}}} method for several years, the code example in Stack
+Overflow post is still unchanged. 
+%This example shows that inconsistencies
+%between online code clones and their originals can lead users of Stack Overflow
+%to reuse outdated code. 
+In addition, although the original code snippet of
+WritableComparator.java in Hadoop is subject to Apache license version 2.0, the
+cloned code on Stack Overflow contains only a {\small{\texttt{compare}}}
+method and misses its license statement on top of the file. There are two
+potential issues for this. First, the code snippet may look like it is under
+Stack Overflow's CC BY-SA 3.0 instead of its original Apache license. Second, if
+the code snippet is copied and incorporated into another software project with
+conflicting license, a legal issue may arise.
+
+\begin{figure*}
+	\begin{lstlisting}
+/* Code in Stack Overflow post ID 801987 */             /* StringUtils.java (2017-10-03) */
+public static String humanReadableInt(long number) {    public static String humanReadableInt(long number) {
+  long absNumber = Math.abs(number);                      return TraditionalBinaryPrefix.long2String(number,"",1);
+  double result = number;                               }
+  String suffix = "";
+  if (absNumber < 1024) {
+  } else if (absNumber < 1024 * 1024) {
+    result = number / 1024.0;
+    suffix = "k";
+  } else if (absNumber < 1024 * 1024 * 1024) {
+    result = number / (1024.0 * 1024);
+    suffix = "m";
+  } else {
+    result = number / (1024.0 * 1024 * 1024);
+    suffix = "g";
+  }
+  return oneDecimal.format(result) + suffix;
+}
+	\end{lstlisting}\vspace{-2ex}
+	\caption{A motivating example of the two code fragments of
+		{\small\texttt{StringUtils.java}}. The one from the
+		Stack Overflow post 801987 (left) is outdated when compared to
+		its latest version in the \textsf{hadoop} code base
+		(right). The outdated code has race conditions.}
+	\label{fig:before-after_2}
+\end{figure*}
+
+The second motivating example of outdated online code clones with more
+disrupting changes than the first one  can be found in an answer to a Stack
+Overflow question regarding how to format files sizes in a human readable form.
+\Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
+task from {\small{\texttt{StringUtils}}} class in \textsf{hadoop}. The code snippet on the
+right shows another version of the same method, but at this time extracted from
+the latest version of \textsf{hadoop}. We can see that
+they both are totally different. The {\small{\texttt{humanReadableInt}}} method is
+rewritten on February 5, 2013 to solve an issue of a race condition
+(HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
+
+This two toxic code snippet has been posted on March 11, 2014 and April 9, 2009
+respectively. They have already been viewed 259 and 2,886 times as the time of
+writing this paper (October 3, 2017). Our calculation finds that there will be a
+new viewer of the first toxic snippet in approximately every 5 days while the
+second toxic snippet will be viewed almost every single day. Moreover, a
+quick web search shows that the same {\small{\texttt{humanReadableInt}}}
+method already reside in approximately 500 projects on GitHub. Considering the popularity of Stack
+Overflow, which has more than 50 million developers visiting each
+month\footnote{Data as of 21 August 2017 from: \url{https://stackoverflow.com}},
+one toxic code snippets on Stack Overflow can spread and grow to hundred or
+thousand copies within only a year or two.
+
 %The code snippet on Stack Overflow can be outdated.
@@
 
-While research has mostly focused on reusing code snippets \emph{from}
-Stack Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), fewer studies
-have been conducted on finding the origins of code examples copied
-\emph{to} Stack Overflow and problems of reusing them such as outdated
-code and software licensing violations. This paper fills this gap and
-makes the following primary contributions:
+While research has mostly focused on reusing code snippets \emph{from} Stack
+Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), fewer studies have been
+conducted on finding the origins of code examples copied \emph{to} Stack
+Overflow and the awareness of Stack Overflow developers in doing so. Finding the
+origins of code examples gives insights to the problems of toxic code snippets
+including outdated code and software licensing violations. It is probably more
+important than studying the effects of reusing Stack Overflow code snippets
+because it tackles the root cause of the problem. Moreover, this paper lays a
+foundation to possibility of having an automatic technique to detect and report
+such problems to developers in the future.
+
+This paper fills this gap and makes the following primary contributions:
+
 \begin{enumerate} 
-	\item \textbf{A manual study of online code clones:} 
-	We used two clone detection tools to discover 315,786,118 similar code
-	snippet pairs, followed by a manual classification of 3,636 candidate
-	clone pairs between 144,064 Java code snippets obtained from Stack Overflow's
-	accepted answers and 111 Java open source projects from the curated
-	Qualitas corpus~\cite{QualitasCorpus}.
-	\item \textbf{An investigation of outdated and license-violating
-		online clones on Stack Overflow:} Our study shows that from the
-	3,636 online clones, at least 671 likely have been copied from open
-	source projects or external online sources to Stack Overflow,
-	potentially violating software licenses. For 112 of them, we found
-	evidence that they have been copied from a specific Qualitas project
-	and that 64 of them are meanwhile outdated.
+	\item \textbf{A manual study of online code clones:} We used
+	two clone detection tools to discover 315,786,118 similar code snippet pairs,
+	followed by a manual classification of 3,636 candidate clone pairs between
+	144,064 Java code snippets obtained from Stack Overflow's accepted answers and
+	111 Java open source projects from the curated Qualitas
+	corpus~\cite{QualitasCorpus}.
+
+	\item \textbf{An investigation of outdated and
+		license-violating online clones on Stack Overflow:} Our study shows that from
+	the 3,636 online clones, at least 671 likely have been copied from open source
+	projects or external online sources to Stack Overflow, potentially violating
+	software licenses. For 112 of them, we found evidence that they have been copied
+	from a specific Qualitas project and that 64 of them are meanwhile outdated. %
 	% and questionable for being reused.
-	\item \textbf{An online code clone oracle:} The 3,636 manually
-	investigated and validated online clone pairs are available for
-	download\footnote{https://to.be.disclosed.after.review} and can be
-	used as a clone oracle.
-\end{enumerate}
+
+	\item \textbf{Awareness of Stack Overflow answerers to
+	toxic code snippets:} We performed an online survey and collected answers from
+	202 highly-ranked Stack Overflow developers. We found that there are~\FIXME{add
+	the number here}\% of code snippets cloned from open source projects to Stack
+	Overflow answers. While Stack Overflow answerers are aware of their outdated
+	code snippets, 19\% of the participants report that they rarely or never fix
+	the code. At least 98\% of the answerers never include software license in
+	their snippets and 69\% never check for licensing conflicts with Stack
+	Overflow's CC BY-SA 3.0 if they copy the code from other sources to Stack
+	Overflow answers.
+
+	\item \textbf{An online code
+		clone oracle:} The 2,302 manually investigated and validated online clone pairs
+	are available for download\footnote{https://to.be.disclosed.after.review} and
+	can be used as a clone oracle. \end{enumerate}
 
@@
 		they answer a question on Stack Overflow?} 
-	We surveyed 600 high reputation Stack Overflow users to study their
+	We surveyed 607 high reputation Stack Overflow users to study their
 	awareness of the issues.
@@
 %\vspace{1ex}
-To answer these four research questions, we perform an empirical study to
+To answer these five research questions, we perform an empirical study to
 locate and study the online code clones between Stack Overflow and open source
@@
 but were not written in Java by using regular expressions and manual checking.
-~\FIXME{should I mention I use PMD CPD to help here? More confusing?}.
+~\FIXME{@Jens, should I mention I use PMD CPD to help here? More confusing?}.
 Finally we obtained
@@
 		\midrule
-		Stack Overflow & 72,365 & 1,840,581 & 10 \\ 
+		Stack Overflow & 72,365 & 1,840,581 & ?? \\ 
 		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
@@
 could complete its execution but skipped 367 snippets due to malformed blocks in
-Stack Overflow data set. Although Simian, SourcererCC, CCFinder, and DECKARD
+Stack Overflow data set. CCFinder reported 8 errors while processing the two data set. 
+Although Simian, SourcererCC, and DECKARD
 could successfully report clones, we decided to choose only Simian and
@@
 \subsection{Phase 2: Clone Merging}
-As there are in total 315,786,118 clone pairs reported, it is
-infeasible for humans to manually validate them all. Instead of
-investigating a random sample, we adopted the idea of \textbf{clone
-	agreement} which has been used in clone research
-studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
-clone oracle is missing or impossible to establish. Clone pairs agreed
-by multiple clone detection tools have a higher likelihood to be real
-clones~\cite{cr2016ssbse}. By using this agreement-based approach, we
-reduced the number of clone candidates for manual investigation to the
-ones agreed by multiple tools. To find agreement between two clone
-pairs reported by two different tools, we used the clone pair matching
-metric proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs
-which have a large enough number of overlapping lines can be
-categorised as either a good-match or an ok-match pair (denoted as
-\textit{good} and \textit{ok} respectively) with a confidence value
-between 0 and 1. A \textit{good} clone pair has stronger agreement
-than an \textit{ok} pair. We follow Bellon's original definitions of
-good- and ok-match~\cite{Bellon2007}, which are based on how much two
-clone fragments \textit{CF} overlap\footnote{The overlap value can be
-	considered as Jaccard similarity.}  and how much of them is
-contained in each other:
+As there are in total 315,786,118 clone pairs reported, it is infeasible for
+humans to manually validate them all. Instead of investigating a random sample,
+we adopted the idea of \textbf{clone agreement} which has been used in clone
+research studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
+clone oracle is missing or impossible to establish. Clone pairs agreed by
+multiple clone detection tools have a higher likelihood to be real
+clones~\cite{cr2016ssbse}. By using this agreement-based approach, we reduced
+the number of clone candidates for manual investigation and avoid a threat to
+internal validity of double counting the same clone pair twice by merging the
+ones agreed by the two tools. To find agreement between two clone pairs
+reported by two different tools, we used the clone pair matching metric proposed
+by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large enough
+number of overlapping lines can be categorised as either a good-match or an
+ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a
+confidence value between 0 and 1. Although good-match has stronger
+agreement than ok-match, we choose ok-match as our clone merging method because 
+it does not take clone size into account which suit our results of clones from
+two tools, Simian, SourcererCC, with two different detection methods, 
+line-based and method-based.
+
+\ We follow Bellon's original definitions of ok-match~\cite{Bellon2007}, which are based on how much two clone
+fragments \textit{CF} is contained in each other:
+
 %\squeezeup
-\begin{displaymath}
-overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|} 
-\end{displaymath}
+%\begin{displaymath}
+%overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|}
+%\end{displaymath}
 % \squeezeup
@@
 \textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} =
-(\textit{CF$_1$}, \textit{CF$_2$}), and the \textit{good-value} and
-the \textit{ok-value} of two clone pairs are defined as
+(\textit{CF$_1$}, \textit{CF$_2$})
+%, and the \textit{good-value} and
+and the \textit{ok-value} of two clone pairs are defined as
 
 %\squeezeup
-\begin{align*}
-good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2))
-\end{align*}
+%\begin{align*}
+%good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2))
+%\end{align*}
 \begin{align*}
@@
 Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$
-are called a \textit{\textit{good-match}(t)} or \textit{ok-match(t)}  iff, for threshold $t \in [0,1]$ holds 
+are called an \textit{ok-match(t)}  iff, for threshold $t \in [0,1]$ holds 
 %\squeezeup
 \begin{align*}
-good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t\\
+%good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t\\
 ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t
@@
 
-Using the good- and ok-match criteria with a predefined threshold
-\textit{t}, we can prune the 315 million candidate clone pairs for
-manual investigation. The \textit{good} pairs are the ones with the
-highest confidence, followed by the \textit{ok} pairs, and followed by
-clone pairs without agreement. We call the \textit{good}- and
-\textit{ok}- pairs \textbf{agreed} clone pairs and the clone pairs
-reported by Simian or NiCad without agreement \textbf{disagreed} clone
-pairs.
-
-Having two clone detectors, Simian (denoted as \textit{S}) and NiCad
-(denoted as \textit{N}), with two chosen configurations (\textit{D}
-and \textit{E}) each, we used Bellon's good- and ok-match for agreement
-in four possible pair-wise combinations: $S_{D}$--$N_{D}$,
-$S_{D}$--$N_{E}$, $S_{E}$--$N_{D}$, and $S_{E}$--$N_{E}$. %as shown in \Cref{t:param_tuning}.
-
-\textbf{Agreed clone pairs: } As shown in \Cref{t_agreed_good_clone_pairs}, after we applied clone
-agreement filtering using Bellon's criteria\footnote{Similar to the
-	original study, we selected a threshold of 0.7 for
-	\textit{good} and \textit{ok} pairs~\cite{Bellon2007}.}, the number
-of \textit{good} clone pairs is 2,313 and the number of \textit{ok}
-clone pairs is 32,316, 0.1\%~of all reported clone
-pairs.  Agreed clone pairs are clone pairs that pass Bellon's
-\textit{good} or \textit{ok} criteria, and therefore are selected for
-manual classification.  Due to NiCad's failures, we do not have NiCad
-clones from five Qualitas projects in the agreed clone pairs. Simian
-clones of the same projects also disappeared from the agreed clone
-pairs since they could not be matched.
-
-\begin{table}
-	\centering
-	\caption{Distribution of the agreed clone pairs}
-	\label{t_agreed_good_clone_pairs}
-	%\small
-	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{lrrrrr}
-		\toprule
-		Set & $S_D$--$N_D$ & $S_D$--$N_E$ & $S_E$--$N_D$ & $S_E$--$N_E$ & Unique \\
-		\midrule
-		\textit{good} & 23 & 26 & 10 & 2,267 & 2,313 \\
-		\textit{ok} & 12,063 & 993 & 79 & 20,021 & 32,316 \\
-		\bottomrule
-	\end{tabular} %
-	% }
-\end{table}
+Using the ok-match criteria with a predefined threshold \textit{t} of 0.7
+similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
+Simian and 1,678 clone pairs from SourcererCC into a single set of 2,302 online
+clone pairs. There are 97 common clone pairs between the two clone sets 
+as depicted in~\Cref{fig:clonemerging}.
 
@@
 	\centering
-	\vspace{3.5ex}
-	\includegraphics[width=0.9\linewidth]{good-ok_pairs}
-	\caption{Distribution of \textit{good} (top) and \textit{ok} pairs (bottom) reported by the 4 configurations of Simian and NiCad. The shaded areas are overlapping pairs.}
-	\label{fig:good-ok-pairs}
+	\includegraphics[width=0.8\linewidth]{clone_merging}
+	\caption{The result from clone merging using Bellon's ok-match criterion}
+	\label{fig:clonemerging}
 \end{figure}
 
-The distribution of \textit{good} clone pairs between the four
-combinations of \textit{D} and \textit{E} configurations are listed in
-\Cref{t_agreed_good_clone_pairs}.  There are 2,326 (2,313 unique)
-\textit{good} pairs consisting of 23 pairs from $S_D$--$N_D$, 26 pairs
-from $S_D$--$N_E$, 10 pairs from $S_E$--$N_D$, and 2,267 pairs from
-$S_E$--$N_E$. There are 33,156 (32,316 unique) \textit{ok}
-pairs\footnote{This excludes the subsumed 2,313 \textit{good}
-	pairs because \textit{ok} pairs subsume
-	\textit{good} pairs.}. We obtained 12,063; 993; 79; and 20,021 pairs
-from $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, and $S_E$--$N_E$
-respectively. Between the four configuration sets, there is
-considerable amount of clone pairs shared between two adjacent sets
-(as depicted in \Cref{fig:good-ok-pairs}), but there is no clone pair
-that is agreed by all four combinations.
-
-\begin{table}
-	\centering
-	\caption{Disagreed clone pairs before and after filtering.}
-	\label{tab:online_clone_pairs}
-	%\small
-	%	\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{lrccr}
-		\toprule
-		\multirow{2}{*}{Set} & \multirow{2}{*}{Before Filtering} & \multicolumn{2}{c}{Filters*} & \multirow{2}{*}{After Filtering} \\ %\cmidrule{3-4}
-		& & \textit{L} & \textit{S} & \\ 
-		\midrule 
-		\multirow{1}{*}{$S_D$} & 55,274 & \checkmark & & 17,801 \\
-		\multirow{1}{*}{$N_D$} & 620,680 & \checkmark & \checkmark & 83 \\ 
-		\bottomrule
-		\multicolumn{5}{l}{*\textit{L}=size $\geq 10$, \textit{S}=sim $\geq 85\%$.}  \\
-	\end{tabular} %
-	%}
-\end{table}
-
-\textbf{Disagreed clone pairs: }
-The disagreed clone pairs are clone pairs that are reported by a
-single tool, either Simian or NiCad, and do not have agreement with
-the other tool. The disagreement can be from a misalignment of clone
-lines or completely non-overlapping clones. The disagreed pairs from
-Simian include clone pairs in the projects with NiCad's errors (1
-project from $N_D$ and 5 from $N_E$).  With the four configuration
-combinations, we decided to investigate only $S_D$, and $N_D$, and
-dropped $S_E$ and $N_E$ due to their enormous amount of clone pairs
-(60 and 250 millions respectively). Moreover, $S_E$ and $N_E$ contain
-a large number of false positives due to the recall preference of
-their EvaClone configurations.
-
-Even choosing only the default configurations, the number of disagreed
-clone pair candidates is still too large for manual inspection
-(as shown in \Cref{tab:online_clone_pairs}). 
-We applied two filters: clone
-size and similarity threshold. %, and good/ok pairs. 
-For the \emph{clone size filter}, we raised the minimum clone size to 10 lines
-since larger clones are more interesting, while smaller ones tend to
-be false clones~\cite{Saini2016}.
-% Since the 10--line threshold is already the default configuration for
-% NiCad, this filter is applied to Simian only (Simian's default
-% configuration has a minimum clone size of 6 lines).
-The second filter, \emph{similarity threshold}, applies
-only to NiCad clone pairs since Simian does not provide a similarity
-configuration. 
-%The last filter, \emph{good/ok pairs}, removes the clone pairs that already exist in the agreed clone sets.
-%As shown in \Cref{tab:online_clone_pairs}, for $S_D$ we filtered the results using clone size and gook/ok pairs.
-
-The two filters reduced the number of $S_D$ clones to 17,801 pairs. We
-filtered $N_D$ clones by additionally raising the similarity
-threshold. We increased NiCad's similarity threshold from 70\% to 85\%
-(by adjusting NiCad's $\mathrm{UPI}$ parameter from 0.3 to 0.15). We
-tried varying the threshold from 70\% (default, 632,855 pairs), 80\%
-(25,003 pairs), 85\% (185 pairs) and 90\% (83 pairs) and found that
-85\% similarity provided the best balance in terms of the amount of
-reported clones and precision for small clones. Using this filter
-along with the other three filters, we reduced the number of $N_D$
-clones to 83 pairs.
-
-\textbf{Selection of clones: }
-%\subsection{Filtered Clones Set}
-We selected all \textit{good} pairs (2,313) and the \textit{ok} pairs for
-$S_D$--$N_D$ (12,336), $S_E$--$N_D$ (993), and $S_D$--$N_E$ (79), but we ignored
-20,021 $S_EN_E$ \textit{ok} clone pairs in the classification due to
-their large number of clones and the very small average clone sizes of
-5.95 and 6.28 lines (see \Cref{tab:orig_stats}), leading to a high
-probability of being trivial clones. We refer to the set of clone
-pairs as the \textit{good} set and the \textit{ok'} set.
-Together with the 17,801 (referred as $S_D'$ set) and 83 (referred as
-$N_D'$ set) clone pairs after filtering, we ended up with a set of 32,533 online clone pair candidates.
-
-Before performing the manual
-investigation, we created and used an automatic classifier 
-to classify boiler-plate code of {\small\texttt{equals()}}, 
-{\small\texttt{hashCode()}} and getters/setters 
-(depicted with a grey line in \Cref{fig:exp_framework}).
-The classifier could automatically classify 28,897 clone pairs 
-and left 3,636 clone pairs for manual investigation in phases 3 to 6.
-
 \subsection{Phase 3-4: Validation and Classification}
-We used the 3,636 filtered clone pairs after automatic classification for
+We used the 2,302 merged clone pairsfor
 manual validation and classification.
@@
 \textbf{Manual investigation:} 
-The first author, who has been working on clone detection research for 
-two years, took the role of the main investigator performing a manual 
-validation and classification of the filtered clone pairs. 
-%By consulting the cloning patterns, 
-The main investigator went through each clone pair candidate, 
-looked at the clones, and decided if they are a true positive or a
-false positive and classified them into an appropriate pattern. 
-%the most appropriate cloning pattern for the pair. 
-To mitigate the human error of the manual investigation, 
-the second author took the role of the validating investigator, performing a
-validation on 10\% (364 pairs) of the clone pairs judged by the main
-investigator. After the validation, the results from the two
-investigators were compared and 61 conflicts were discussed and resolved.
-There were three conflicts where the two investigators could not find a consensus 
-and the third author was involved for the final judgement.
+To mitigate the human error, we deployed two persons in the manual clone
+investigation process. The first author, who is a research student working on
+clone detection research for three years, and the third author, who is a
+software engineering research student who is familiar with code clones, took the
+role of the investigators performing a manual validation and classification of
+the merged clone pairs. The two investigators separately went through each clone
+pair candidate, looked at the clones, and decided if they are a true positive or
+a false positive and classified them into an appropriate pattern. After the
+validation, the results from the two investigators were compared and 607 (26\%)
+conflicts were discussed and resolved. There are 145 conflicts caused by
+one investigator being more careful than the other and finding evidence of 
+copying while the other could not. They result in a better classification
+to a stronger one, i.e.~from UD to QS or EX. 
+%There were three conflicts where the two
+%investigators could not find a consensus and the third author was involved for
+%the final judgement.
+
+% No. of conflicts = 37 (ok) + 352 (simian) + 218 (SCC)
+% 33 pairs are changed from MP.UD --> CR.EX,QS
+% 112 pairs are changed from CR.UD --> MP.EX,QS
 
@@
 Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
-containing boiler-plate code of {\small\verb|equals()|} methods,
-getters/setters, or IDE-generated code such as GUI components. Pattern
+containing boiler-plate (according to our definition of boiler-plate 
+code in \Cref{tab:boiler-plate_code} which is more specific to Java
+than the definition in Kapser's~\cite{Kapser2008}).
+%of {\small\verb|equals()|} methods,
+%getters/setters, well-known code patterns such as deleting a file
+%or implementing a {\small{\texttt{toString}} method,
+% or IDE-generated code such as GUI components. 
+ Pattern
 IN (\textbf{In}heritance/Interface) is cloning by inheritance of the
@@
 {\small\texttt{try-catch}} statements.
+
+\begin{table}
+	\centering
+	\caption{The definition of boiler-plate code}
+	\label{tab:boiler-plate_code}
+	\begin{tabular}{lp{5.5cm}}
+		\toprule
+		Type & Description \\ 
+		\midrule
+		\textbf{API constraints} & Similar code fragments are created because of a constraint by an API. For example, reading and writing to database using JDBC, reading and writing a file in Java. \\
+		\midrule
+		\textbf{Templating} & An optimised or stable code fragment is reused multiple times. This also includes auto-generated code by IDE. \\
+		\midrule
+		\textbf{Design patterns} & Java design patterns suggest a way of implementing similar pieces of code.
+For example, getters, setters, {\small\texttt{equals}}, {\small\texttt{hashCode}}, and {\small\texttt{toString}} method.
+\\
+		\bottomrule 
+	\end{tabular}  %
+	%}
+\end{table}
 
@@
 their latest versions. We downloaded the latest version of the Qualitas projects
-from their repositories on September 26, 2016. For each \textbf{QS} online clone
+from their repositories on October 3, 2017. For each \textbf{QS} online clone
 pair, we used the clone from Qualitas as a proxy. We searched for its latest
 version by the file name and located the cloned region in the file based on the
-method name. We then compared the Stack Overflow snippet to its latest version
-line-by-line to find if any change has been made to the source code. We also
-made sure that the changes did not come from the modifications made to the Stack
-Overflow snippets by the posters but from the updates in the projects
-themselves. When we found inconsistent lines between the two versions, we used
-{\small\texttt{git blame}} to see who modified those lines of code and the
-timestamps.
+method name or specific code statements. We then compared the Stack Overflow
+snippet to its latest version line-by-line to find if any change has been made
+to the source code. We also made sure that the changes did not come from the
+modifications made to the Stack Overflow snippets by the posters but from the
+updates in the projects themselves. When we found inconsistent lines between the
+two versions, we used {\small\texttt{git blame}} to see who modified those lines
+of code and the timestamps. We also collected IDs of issue tracking information
+if the code change is linked to an automatic issue tracking system, such as Jira.
 
@@
 we sent out 300 and 307 emails (excluding undelivered ones) respectively. The
-survey was open for participation for a month, from 25 July 2017 to 25 August
+survey was open for participation for two months, from 25 August 2017 to 25 August
 2017, before we collected and analysed the responses.
@@
 
-The statistics on clones obtained from the different data sets are
-presented in \Cref{tab:snippets}. Simian in the default configuration
-($S_D$) reported clones in 1,086 snippets, approximately 1\% of the
-144,064 Stack Overflow snippets, associated with 92 Qualitas
-projects. Simian in the EvaClone configuration ($S_E$) reported 1,531
-snippets containing clones associated with all 111 Qualitas
-projects. NiCad in the default configuration ($N_D$) reported clones
-between 1,392 Stack Overflow code snippets and 88 Qualitas
-projects. NiCad in the EvaClone configuration ($N_E$) reported the
-largest number of 12,886 cloned snippets mainly due to the more
-relaxed configuration. The $N_E$ snippets are associated with 88
-Qualitas projects.  For the cloned Stack Overflow snippets, the
-average ratio of cloned code for $S_D$, $S_E$, $N_D$, and $N_E$ is
-38\%, 50\%, 30\%, and 33\% respectively.
+The statistics on clones obtained from the merged clone data set are
+presented in \Cref{tab:snippets}. Simian and SourcererCC
+reported clones in 560 snippets, approximately 1\% of the
+72,365 Stack Overflow snippets, associated with 59 Qualitas
+projects. For the cloned Stack Overflow snippets, the
+average ratio of cloned code is 54.22\%.
 % A quick manual check of Simian's clone report revealed that there
@@
 	\centering
-	\begin{tabular}{rrrr}
+	\begin{tabular}{p{2.2cm}rrrr}
 		\toprule
-		Pairs & Snippets & Projects & Avg.~cloned ratio \\
+		Set & Pairs & Snippets & Projects & Cloned ratio \\
 		\midrule
-		2,304 & 460 & 77 & ??\% \\ % <-- for avg. cloned ratio, use scripts in ~/Downloads/stackoverflow/scripts/checking
+		Reported clones & 2,302 & 590 & 63 & 53.10\% \\ 
+		\midrule
+		TP from manual validation & 2,076 & 560 & 59 & 54.22\% \\ % <-- for avg. cloned ratio, use scripts in ~/Downloads/stackoverflow/scripts/checking
 		\bottomrule
@@
 
-However, using Bellon's criteria for matching clone pairs, only
-0.1\%~of all pairs are agreed by two tool/configuration
-combinations. As shown in \Cref{tab:snippets}, for the 2,313
-\textit{good} pairs, there are 97 Stack Overflow snippets which are
-associated with 67 Qualitas projects. The 12,336 \textit{ok'} pairs
-are clones between 139 Stack Overflow snippets and 43 Qualitas
-projects.  Moreover, for the disagreed pairs, we found 17,081 clone
-pairs reported by $S_D'$ are clones between 460 Stack Overflow
-snippets and 74 Qualitas projects and 83 $N_D'$ clone pairs are clones
-between 44 Stack Overflow snippets and 19 Qualitas projects. In total
-we found that the filtered data sets contains 32,533 clone pairs which
-are clones between 623 Stack Overflow snippets and 96 Qualitas
-projects.
-
 During the manual investigation of 3,636 clone pairs, we identified 2,420 pairs
-as being accidential clones (AC), i.e.~false positives. After removing
+as being accidental clones (AC), i.e.~false positives. After removing
 them, the set still contains 1,216 true positive clone pairs between 516 Stack
@@
 
-\begin{table}
+\begin{table*}
 	\centering
@@
 	%\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{lrrrrrrrr}
+	\begin{tabular}{rrrrrrrr}
 		\toprule
-		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
+		QS & SQ & EX & UD & BP & IN & AC & Total \\ 
 		\midrule
-		\multirow{1}{*}{\textit{good}}  & 3 & 0 & 4 & 15 & 111  & 8 & 2,172 & 2,313 \\
-		\multirow{1}{*}{\textit{ok'}}  & 14 & 0 & 44 & 20 & 12,128 & 23 & 107 & 12,336 \\
-		\multirow{1}{*}{$S_D'$} & 86 & 0 & 146 & 293 & 17,074 & 74 & 128 & 17,801 \\
-		\multirow{1}{*}{$N_D'$} & 9  & 0  & 6 & 31 & 17 & 7 & 13 & 83 \\ 
-		\midrule
-		Total & 112 & 0 & 200 & 359 & 29,330 & 112 & 2,420 & 32,533 \\ 
+		239 (149) & 1 (1) & 208 (119) & 107 (65) & 1,505 (217) & 16 (9) & 226 (53) & 2,302 (560) \\
 		\bottomrule
@@
 	%}
-\end{table}
+\end{table*}
 

### 2017-10-09 cloverflow-tse/cloverflow.tex
Latest update on RQ1, 2, and 3.

@@
 mandatory while the other 9 questions were shown to the participants based on
-their previous answers. The full survey can be found in our \FIXME{technical
-	report/website?} ~\footnote{Survey--Stack Overflow Answerers:
-	\url{http://www.cs.ucl.ac.uk/staff/C.Ragkhitwetsagul/files/so_survey.pdf}}.
+their previous answers. The full survey can be found in our research note~
+\FIXME{add URL to the RN}.
 
@@
 presented in \Cref{tab:snippets}. Simian and SourcererCC
-reported clones in 560 snippets, approximately 1\% of the
+reported clones in 460 snippets, approximately 0.6\% of the
 72,365 Stack Overflow snippets, associated with 59 Qualitas
 projects. For the cloned Stack Overflow snippets, the
-average ratio of cloned code is 54.22\%.
+average ratio of cloned code is 53.10\%.
 % A quick manual check of Simian's clone report revealed that there
@@
 		\midrule
-		Reported clones & 2,302 & 590 & 63 & 53.10\% \\ 
-		\midrule
-		TP from manual validation & 2,076 & 560 & 59 & 54.22\% \\ % <-- for avg. cloned ratio, use scripts in ~/Downloads/stackoverflow/scripts/checking
+		Reported clones & 2,302 & 460 & 59 & 53.10\% \\ 
+		\midrule
+		TP from manual validation & 2,076 & 449 & 59 & 54.22\% \\ 
 		\bottomrule
@@
 
-During the manual investigation of 3,636 clone pairs, we identified 2,420 pairs
+During the manual investigation of 2,302 clone pairs, we identified 226 pairs
 as being accidental clones (AC), i.e.~false positives. After removing
-them, the set still contains 1,216 true positive clone pairs between 516 Stack
-Overflow snippets and 75 Qualitas projects.
-
-\textbf{To answer RQ1, we found most Qualitas projects to share
+them, the set still contains 2,076 true positive clone pairs between 449 Stack
+Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
+true positive clone pairs is 54.22\%.
+
+\textbf{To answer RQ1, we found more than half of Qualitas projects to share
 	similar code with Stack Overflow code snippets. In the manually confirmed 
-	data set of 3,636 clone pairs, we found 1,216 pairs as true positives which 
-	account for 75 Qualitas projects and
-	516 Stack Overflow code snippets.}
-
-%\FIXME{Should we have removed the AC clones right at the beginning?}
+	data set of 2,302 clone pairs, we found 2,076 pairs as true positives which 
+	account for 59 Qualitas projects and
+	449 Stack Overflow code snippets.}
 
@@
 
-As shown in \Cref{tab:online_clone_classification_results}, the automatic
-classifier helped us to classify 28,897 clone pairs into
-pattern \textbf{BP}. Then, we relied on a manual classification
-% to qualitatively investigate the patterns of
-%online code cloning 
-on the remaining 3,636 pairs by following the classification process
+We performed a manual classification
+of the 2,302 merged clone pairs by following the classification process
 in \Cref{fig:classification_process}. 
-%To achieve this, we classified all 32,533
-%selected clone pairs according to the classification process 
-%in \Cref{fig:classification_process}.  
-%
-%There were 3,636 pairs left for the manual check. 
 The classification results are shown in \Cref{tab:classification_good_o} 
 and explained in the following.
-
-%\begin{table}
-%	\centering
-%	\caption{No.~of online clones candidates for the classification}
-%	\label{tab:online_clone_classification_results}
-%	%\small
-%	%	\resizebox{\columnwidth}{!}{%
-%	\begin{tabular}{lrrr}
-%		\toprule
-%		\multirow{2}{*}{Set} & \multirow{2}{*}{Candidates} & \multicolumn{2}{c}{Classification} \\ %\cmidrule{3-4}
-%		& & Auto & Manual \\
-%		\midrule 
-%		\multirow{1}{*}{\textit{good}} & 2,313 & 10 & 2,303 \\
-%		\multirow{1}{*}{\textit{ok'}} & 12,336 & 12,077 & 259 \\
-%		%\multirow{1}{*}{\textit{agreed clone pairs}}      & 29,099 \\
-%		\multirow{1}{*}{$S_D'$} & 17,801 & 16,800 & 1,001 \\
-%		\multirow{1}{*}{$N_D'$} & 83 & 10 & 73 \\ 
-%		%\multirow{1}{*}{\textit{disagreed clone pairs}}    & 1,039 \\
-%		\midrule
-%		Total  & 32,533 & 28,897 & 3,636 \\ 
-%		\bottomrule
-%	\end{tabular} %
-%	%}
-%\end{table}
 
@@
 	%\resizebox{\columnwidth}{!}{%
-	\begin{tabular}{rrrrrrrr}
+	\begin{tabular}{lrrrrrrrr}
 		\toprule
-		QS & SQ & EX & UD & BP & IN & AC & Total \\ 
-		\midrule
-		239 (149) & 1 (1) & 208 (119) & 107 (65) & 1,505 (217) & 16 (9) & 226 (53) & 2,302 (560) \\
+		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
+		\midrule
+		Before consolidation & 248 & 1 & 199 & 107 & 1,505 & 16 & 226 & 2,302 \\
+		After consolidation & 154 & 1 & 111 & 65 & 217 & 9 & 53 & 560 \\
 		\bottomrule
@@
 
-\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 112
-online clone pairs with evidences of cloning from 19 Qualitas projects to
-Stack Overflow. They include 3, 14, 86, and 9 pairs from the
-\textit{good}, \textit{ok'}, $S_D'$, and $N_D'$ set respectively. Most of
-them have a statement in the Stack Overflow post saying that the code
-is ``copied'', ``borrowed'' or ``modified'' from a specific file or class in a
-Qualitas project. For example, according to the motivating example in 
-\Cref{fig:before-after}, we found evidence in the Stack Overflow 
-Post 22315734 saying that \textit{``Actually, you can learn how to compare 
-	in Hadoop from WritableComparator. Here is an examle that borrows 
-	some ideas from it.''}
-
-The most cloned projects are \textsf{hibernate} and
-\textsf{spring} with 20 clone pairs, followed by \textsf{eclipse} (15
-pairs), and \textsf{hadoop} (12 pairs). The clones are used as
-examples and are very similar to their original Qualitas code with
-limited modifications.
-
-\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We did not find
-any pairs with evidence of cloning from Stack Overflow to Qualitas
-projects. This is very likely due to the age of the Qualitas corpus as
-another study~\cite{An2017} showed the presence of clones from Stack
-Overflow in newer open source data sets.
-
-\textbf{EX: External Sources.} We found 200 clone pairs with
-evidence of cloning from external sources to Stack Overflow and to Qualitas.  
-They include 4, 44, 146, and 6 pairs from the \textit{good}, \textit{ok'},
-$S_D'$, and $N_D'$ set respectively. All of them contain statements
-giving an external source of the cloned code.  For example, Stack
-Overflow Post 9549009 contains a code comment saying \textit{``Copied
-	shamelessly from
-	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''}.
+\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 248 online clone
+pairs with evidences of cloning from Qualitas projects to Stack Overflow.
+However, we observed that, in some cases, a cloned code snippet on Stack
+Overflow matched with more than one code snippet in Qualitas projects. This is
+because there were also code cloning inside Qualitas projects themselves. To
+avoid double counting of such online clones, we consolidated clone pairs having
+the same Stack Overflow snippet, starting line, and ending line into a single
+clone pair. We finally obtained 154 QS pairs having unique Stack Overflow code
+snippets and associated with 23 Qualitas projects listed in
+\Cref{tab:qs_qualitas_projects}. The most cloned projects are \textsf{hibernate}
+and \textsf{spring} with 24 clone pairs, followed by \textsf{eclipse} (21
+pairs), \textsf{jung2} (19 pairs), \textsf{spring} (17 pairs), and
+\textsf{jfreechart} (13 pairs). The clones are used as examples and are very
+similar to their original Qualitas code with limited modifications. Most of them
+have a statement in the Stack Overflow post saying that the code is ``copied'',
+``borrowed'' or ``modified'' from a specific file or class in a Qualitas
+project. For example, according to the motivating example in
+\Cref{fig:before-after}, we found evidence in the Stack Overflow Post 22315734
+saying that \textit{``Actually, you can learn how to compare in Hadoop from
+	WritableComparator. Here is an examle that borrows some ideas from it.''}
+
+\begin{table}
+	\centering
+	\caption{Qualitas projects associated with QS and UD online clone pairs}
+	\label{tab:qs_qualitas_projects}
+	%\small
+	%\resizebox{\columnwidth}{!}{%
+	\begin{tabular}{lrlr}
+		\toprule
+		\multicolumn{2}{c}{QS} & \multicolumn{2}{c}{UD} \\
+		\midrule
+		Project & Pairs & Project & Pairs\\
+		\midrule
+		hibernate & 24 & netbeans & 11 \\
+		eclipse & 21 & eclipse & 8 \\
+		jung2 & 19 & jstock & 5 \\
+		spring & 17 & compiere & 5 \\
+		jfreechart & 13 & ireport & 4 \\
+		hadoop & 10 & jmeter & 4 \\
+		log4j & 8 & jung2 & 3 \\
+		tomcat & 8 & jhotdraw & 3 \\
+		struts & 5 & c-jdbc & 3 \\
+		lucene & 4 & log4j & 3 \\
+		weka & 4 & wct & 2 \\
+		junit & 3 & hibernate & 2 \\
+		poi & 3 & tomcat & 2 \\
+		compiere & 2 & spring & 1 \\
+		jasperreports & 2 & rssowl & 1 \\
+		jboss & 2 & mvnforum & 1 \\
+		jgraph & 2 & jfreechart & 1 \\
+		jstock & 2 & jboss & 1 \\
+		antlr & 1 & hadoop & 1 \\
+		itext & 1 & geotools & 1 \\
+		jgrapht & 1 & freemind & 1 \\
+		ant & 1 & findbugs & 1 \\
+		c-jdbc & 1 & cayenne & 1 \\
+		\bottomrule
+	\end{tabular} 
+	%}
+\end{table}
+
+\textbf{SQ: Stack Overflow $\rightarrow$ Qualitas.} We found one pair with
+evidence of cloning from Stack Overflow post ID 698283 to
+{\small\texttt{POIUtils.java}} in \textsf{jstock} project. The user
+\textsf{yccheok} who asked the question in Stack Overflow is the author of
+\textsf{jstock}. The question is about determining the right method to call
+among 7 overloading methods of {\small\texttt{setCellValue}} during runtime. We
+could not find evidence of copying or attribution to Stack Overflow in
+\textsf{jstock}. However, considering that the 25 lines of code of
+{\small\texttt{findMethodToInvoke}} method depicted in \Cref{fig:jstock_code} in Stack
+Overflow is identical to the code in \textsf{jstock} including comments, it is almost certain that
+the two code snippets form a clone pair. In addition, Stack Overflow answer was
+posted on March 30, 2009, while the code in {\small\texttt{POIUtils}} class in
+\textsf{jstock} was committed to GitHub on the next day of March 31, 2009.
+
+\begin{figure}
+	\begin{lstlisting}
+private Method findMethodToInvoke(Object test) {
+  Method method = parameterTypeMap.get(test.getClass());
+  if (method != null) {
+    return method;
+  }
+
+  // Look for superclasses
+  Class<?> x = test.getClass().getSuperclass();
+  while (x != null && x != Object.class) {
+    method = parameterTypeMap.get(x);
+    if (method != null) {
+      return method;
+    }
+    x = x.getSuperclass();
+  }
+
+  // Look for interfaces
+  for (Class<?> i : test.getClass().getInterfaces()) {
+    method = parameterTypeMap.get(i);
+    if (method != null) {
+      return method;
+    }
+  }
+  return null;
+}
+	\end{lstlisting}\vspace{-2ex}
+	\caption{The {\small\texttt{findMethodToInvoke}} that is found to be copied from Stack Overflow post 698283 to {\small\texttt{POIUtils}} class.}
+	\label{fig:jstock_code}
+\end{figure}
+
+We did not find other online clones besides the one mentioned above. 
+This very low number of SQ clone pair is very likely due to the age of the
+Qualitas corpus as another study~\cite{An2017} showed the presence of clones
+from Stack Overflow in newer open source data sets. This is expected and
+comes from our experimental design since
+we are more interested in a cloning direction from Qualitas to Stack Overflow.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{ex_sources}
+	\caption{Original sources of EX clone pairs}
+	\label{fig:ex_sources}
+\end{figure}
+
+\textbf{EX: External Sources.} We found 199 clone pairs with evidence of cloning
+from external sources to Stack Overflow. After getting rid of duplicated SO
+snippets due to multiple intra-clone instances in Qualitas, we obtained 111 EX
+pairs. Fifty pairs provide evidences of copying to both Stack
+Overflow and Qualitas while the rest (61) only provides evidence of copying to
+Stack Overflow. All of them contain statements giving an external source of the
+cloned code which fall into six groups as displayed in \Cref{fig:ex_sources}. 
+We discovered that 63 EX online clone pairs are copied from source code of classes or 
+methods in Java SDK, 18 pairs are from websites, 15 pairs are from open source systems,
+11 pairs are from Java official documentations from Sun Microsystems or Oracle,
+3 pairs are from books, and 1 pair is from a company project.
+For example, Stack Overflow Post
+9549009 contains a code comment saying \textit{``Copied shamelessly from
+	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
+open source project. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
+class with a license statement showing that it is developed by a private company
+called \textsf{Sapient}. Post 12879764 has a text saying \textit{``Code modified
+	and cleaned from the original at Filthy Rich Clients.''} which is a book for
+developing animated and graphical effects for desktop Java applications. Another
+example is a copy of code from a website in post 15260207. The text surrounding
+source code reads ``\textit{I basically stole this from the web and modified it
+	slightly... You can see the original post here
+	(\url{http://www.java2s.com/Code/Java/Swing-JFC/DragListDemo.htm}).}''.
+Interestingly, the code is actually a copy from Sun Microsystems.
 
@@
 These findings complement a study of clones between software
-projects~\cite{Svajlenko2014}. We found that cloning can also
-happen among different sources on the Internet just like software
-projects. There are 30 clone pairs that originated from programming
-websites. For example, we found a clone of a snippet to convert
-numbers into words which is copied from
-\url{www.rgagnon.com/javadetails/java-0426.html}. Both the Stack
-Overflow and the \textsf{compiere} project code contain an
-attribution to the original source. Another example is a snippet
-to generate graphical \textit{Perlin noise}. It is copied from
-\url{http://mrl.nyu.edu/~perlin/noise/} and is used on Stack
-Overflow and in the \textsf{aoi} project with
-attribution.
-% The original code of the 15 clone pairs do not have licensing
-% information so these clones do not violate any license.
-There are other EX pairs which are copied from third-party
-libraries such as \textsf{zxing}, \textsf{jasper}, \textsf{java.util},
-\textsf{javax.servlet}, and the \textsf{bouncycastle} cryptography
-project.
-
-\textbf{UD: Unknown Direction.} We found 359 online clone pairs with
-no evidence of cloning between Qualitas and Stack Overflow but with a
-high code similarity that suggests cloning. 
-% They include 15, 20, 293, and 31 pairs from the \textit{good},
-% \textit{ok'}, $S_D'$, and $N_D'$ set respectively.
-The most cloned projects is \textsf{netbeans} with
-93 clone pairs. Most of the clones are a large chunk of code handling
-GUI components. Although these GUI clones might be auto-generated by
-IDEs, we did not find any evidence. The second most cloned project is
-\textsf{jung2} (62 pairs), a network and graph framework, followed by
-\textsf{eclipse-SDK} (37 pairs).
-% There are several Stack Overflow snippets that are identical to code
-% in \textsf{jung2}.
-
-\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate
-clone pairs found in this study. %Although we have removed some of the
-%boiler-plate code with filters before the analysis, we still 
-We observed 29,330 such clone pairs. The BP clone pairs account for
-90\% of all clone pairs we classified. The majority of them are
-{\small{\texttt{equals()}}} methods.
-
-\textbf{IN: Inheritance/interface.} There were 112 clone pairs found
-to be similar because they implement the same interface or inheriting
-from the same class. An example is the two implementations of
-{\small{\texttt{MouseListener}}} that share similar
-{\small\texttt{@Override}} methods of {\small\texttt{mousePressed}},
-and {\small\texttt{mouseReleased}}.
-
-\textbf{AC: Accidental Clones.} There were 2,420 accidental clone
-pairs. Mainly, they are false positive clones caused by code
-normalisation. 
-% However, the original source code were still different enough when
-% we manually classified them.
-Other clone instances include {\small\texttt{finally}} or
+projects~\cite{Svajlenko2014}. We found that cloning can also happen among
+different sources on the Internet just like software projects. The are 18 clone
+pairs that originated from programming websites including \url{www.java2s.com}
+and \url{exampledepot.com}. Moreover, there is one snippet which comes from a
+research website. We found that a snippet to generate graphical \textit{Perlin
+	noise} is copied from NYU Media Research Lab
+(\url{http://mrl.nyu.edu/~perlin/noise/}) website and is used on Stack Overflow
+and in the \textsf{aoi} project with attribution. There are other EX pairs which
+are copied from open source libraries or Java SDK such as \textsf{Mozilla
+	Rhino}, \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}, and
+the \textsf{bouncycastle} cryptography project.
+
+\textbf{UD: Unknown Direction.} We found 107 online clone pairs, reduced to 65
+pairs after consolidating the clones, with no evidence of cloning between Qualitas
+and Stack Overflow but with a high code similarity that suggests cloning. 
+The most cloned projects is \textsf{netbeans} with 11 clone pairs. Most of the
+clones are a large chunk of code handling GUI components. Although these GUI
+clones might be auto-generated by IDEs, we did not find any evidence. The second
+most cloned project is \textsf{eclipse} (8 pairs), followed by \textsf{jstock},
+a free stock market software, and \textsf{compiere}, a software and customer
+relationship management (CRM) system, (5 pairs).
+
+\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs
+found in this study. We observed 1,505 such clone pairs and 217 after
+consolidation. The BP clone pairs account for 65\% of all clone pairs we
+classified. The majority of them are {\small{\texttt{equals()}}} methods.
+
+\textbf{IN: Inheritance/interface.} There were 16 clone pairs, 9 pairs after
+consolidation, found to be similar because they implement the same interface or
+inheriting from the same class. An example is the two implementations of a
+custom data type which implements {\small\texttt{UserType}}. They share similar
+{\small\texttt{@Override}} methods of {\small\texttt{deepCopy}},
+{\small\texttt{isMutable}}, {\small\texttt{assemble}},
+{\small\texttt{disassemble}}, and {\small\texttt{replace}}.
+
+\textbf{AC: Accidental Clones.} There were 226 accidental clone
+pairs, 53 after consolidation. Mainly, they are false positive clones caused by code
+normalisation and false type-3 clones from SourcererCC. 
+Examples of the AC clone instances include {\small\texttt{finally}} or
 {\small\texttt{try-catch}} clauses that were accidentally the same due
@@
 
-%For 17,801 $S_D$ clone pairs, they contained a large volume of boiler-plate code.
-Our regular expressions could automatically classified 16,800 of them into BP.
-The investigator checked the 1,001 remaining pairs manually.
-As a result, we found 86 QS, 294 UD, 145 EX, 17,074 BP, 74 IN and 128 AC pairs.
-For 88 $N_D$ clone pairs, 10 of them were automatically classified into BP and 78 were manually classified.
-We found 9 QS, 35 UD, 6 EX, 17 BP, 8 IN, and 13 AC respectively.
-
-%FIXME: We probably have to discuss IN clones.
-%FIXME: the numbers where 28,642 and 2,529 which I could not find elsewhere.
-\textbf{To answer RQ2, we found that a large amount of the clone pairs
+\textbf{To answer RQ2, we found 154 pairs with
+	strong evidences to be cloned from 23 Qualitas projects to Stack Overflow, 1 pair
+	was cloned from Stack Overflow to Qualitas, and
+	111 pairs were found to be cloned to Stack Overflow from external
+	sources. However, the largest amount of the clone pairs
 	between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
-	(29,330) or accidental clones (2,420) with no evidence that the code
-	has actually been copied. Nevertheless, we found 112 pairs with
-	strong evidences to be cloned from 19 Qualitas projects to Stack Overflow and
-	200 pairs were found to be cloned to Stack Overflow from external
-	sources.} 
-%We did not find any clone pairs in the direction from Stack Overflow to Qualitas.}
+	(217), followed by 65 clone pairs with no evidence that the code has actually been copied,
+	and 16 pairs of clones due to implementing the same interface or inheriting the same class.}
 
@@
 
-%In this study, we are interested in effects of having code clones between open source software systems and Stack Overflow.
-From the manual investigation, we found 523 true positive online clone pairs.
-With this set of true clones, we investigated further and found that there are two potential issues, outdated code and software licensing violation.
-
-%\subsubsection{Outdated Clones}
-
-We discovered 64 outdated online clone pairs out of 112 pairs. As
-shown in \Cref{fig:outdated}, \textsf{spring} has the highest number
-of 17 outdated pairs, followed by 7 from \textsf{hibernate} and
-\textsf{hadoop}, and 6 from \textsf{junit}. Besides the example of
-outdated code in % \textsf{hadoop}'s
-{\small{\texttt{WritableComparator.java}}} 
-from \textsf{hadoop} shown in
-\Cref{fig:before-after}, we also found a few outdated code elements
-which contained a large amount of modifications. For example, the code
-snippet in Stack Overflow post 23520731 is a copy of
-{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code
-has been heavily modified on February 5, 2016.
-
-In the 64 outdated pairs, we found 5 ``dead'' snippets. These snippets
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.8\linewidth]{outdated}
+	\caption{Outdated QS online clone pairs group by projects}
+	\label{fig:outdated}
+\end{figure*}
+
+We discovered 101 outdated online clone pairs out of 154 pairs. As shown in
+\Cref{fig:outdated}, \textsf{hibernate} has the highest number of 19 outdated
+pairs, followed by 14 from \textsf{spring}, 13 from \textsf{eclipse}, and 9 from
+\textsf{hadoop}. Besides the two examples of outdated code in % \textsf{hadoop}'s
+{\small{\texttt{WritableComparator.java}}} and
+{\small{\texttt{StringUtils.java}}} from \textsf{hadoop} shown in
+\Cref{fig:before-after} and \Cref{fig:before-after_2}, we also found a few
+outdated code elements which contained a large amount of modifications. For
+example, the code snippet in Stack Overflow post 23520731 is a copy of
+{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code has been
+heavily modified on February 5, 2016.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.7\linewidth]{mod_types}
+	\caption{Six code modification found in the latest versions of the outdated clone pairs}
+	\label{fig:mod_types}
+\end{figure}
+
+We analysed code modifications which made Stack Overflow code outdated by going
+though commits and git blame information. The summary of six code modification
+types found in the 101 outdated online clone pairs are displayed in
+\Cref{fig:mod_types} including statement addition, statement modification,
+statement removal, method rewriting, API change (changing in method signature),
+and file deletion. We occasionally found multiple code modifications applied to
+one clone pair at the same time but at a different location. The most often
+code changes found is statement modification (49 occurrences), followed by statement
+addition (29 occurrences), statement removal (18 occurrences), changing of method
+signature, i.e.~API change (16 occurrences), and method rewriting (15 occurrences).
+Moreover, in the 101 outdated pairs, we found 15 ``dead'' snippets. These snippets
 cannot be located in the latest version of the projects. For example,
@@
 	snippets.}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{freshness}
-	\caption{Status of the 112 QS online clone pairs}
-	\label{fig:outdated}
-\end{figure}
 

### 2017-10-09 cloverflow-tse/ex_sources.m

@@ -1,0 +1,18 @@
+y = [63 18 15 11 3 1];
+bar(y)
+
+%xticks([1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19])
+xticklabels({'JDK', 'Web', 'OSS', 'Official docs', 'Book', 'Company'})
+%xlabel('Project','FontSize',15)
+ylabel('Clone pairs','FontSize',15)
+%t_legend=legend('Fresh', 'Outdated', 'Dead');
+%set(t_legend,'FontSize',15);
+set(gca,'FontSize',15);
+set(gca,'XTickLabelRotation',45)
+box on
+
+h=gcf;
+set(h,'PaperPositionMode','auto');         
+set(h,'PaperOrientation','landscape');
+set(h,'Position',[50 50 500 300]);
+print('ex_sources','-dpdf','-bestfit')

### 2017-10-10 cloverflow-tse/cloverflow.tex
Finished RQ 3.

@@
 	\resizebox{\linewidth}{!}{
-		\begin{tabular}{cc|lcp{5.15cm}@{}rrc|c@{}c}
+		\begin{tabular}{cc|lcp{4cm}@{}rrc|lc@{}c}
 			\toprule
-			\multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{2}{c}{Changes} \\ 
-			\midrule
-			Post & Date & Project & Ver. & File & Start & End & Date & Type$^*$ & Date \\
-			\midrule
-			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & \textit{S} & 20-Nov-14 \\
-			23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & \textit{S} & 5-Feb-16 \\
-			21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & \textit{R} & 4-Aug-16 \\
-			12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 18 & 28 & 7-Dec-09 & \textit{R} & 26-Jun-13 \\
-			8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & \textit{D} & 20-May-11 \\
-			3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotationHandlerMapping.java & 78 & 92 & 20-Oct-10 & \textit{D} & 20-Jan-12 \\
+			\multicolumn{2}{c|}{Stack Overflow} & \multicolumn{6}{c|}{Qualitas} & \multicolumn{3}{c}{Changes} \\ 
+			\midrule
+			Post & Date & Project & Ver. & File & Start & End & Date & Issue ID & Type$^*$ & Date \\
+			\midrule
+			2513183 & 25-Mar-10 & eclipse & 4.3 & GenerateToStringAction.java & 113 & 166 & & Bug 439874 & \textit{S} & 17-Mar-15 \\
+			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & HADOOP-11323 & \textit{S} & 20-Nov-14 \\
+			23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & HHH-10458 & \textit{S} & 5-Feb-16 \\
+			18232672 & 14-Aug-13 & log4j & 1.2.16 & SMTPAppender.java & 207 & 228 & & Bug 44644 & \textit{R} & 18-Oct-08 \\ 
+			17697173 & 17-Jul-13 & lucene & 4.3.0 & SlowSynonymFilterFactory.java & 38 & 52 & & LUCENE-4095 & \textit{D} & 31-May-12 \\
+			21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & BZ 59823 &\textit{R} & 4-Aug-16 \\
+			12593810 & 26-Sep-12 & poi & 3.6 & WorkbookFactory.java & 49 & 60 & 7-Dec-09 & 57593 & \textit{R} & 30-Apr-15 \\
+			8037824 & 7-Nov-11 & jasperreports & 3.7.4 & JRVerifier.java & 1221 & 1240 & 31-May-10 & N/A & \textit{D} & 20-May-11 \\
+			3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotation\newline HandlerMapping.java & 78 & 92 & 20-Oct-10 & SPR-14129 & \textit{D} & 20-Jan-12 \\
+			14019840 & 24-Dec-12 & struts & 2.2.1 & DefaultActionMapper.java & 273 & 288 & & WW-4225 & \textit{S} & 18-Oct-13 \\
 			\bottomrule 
@@
 
-\begin{figure}
-	\centering
-	\includegraphics[width=0.7\linewidth]{mod_types}
-	\caption{Six code modification found in the latest versions of the outdated clone pairs}
-	\label{fig:mod_types}
-\end{figure}
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.7\linewidth]{mod_types}
+%	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
+%	\label{fig:mod_types}
+%\end{figure}
+
+\begin{table}
+	\centering
+	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
+	\label{tab:mod_types}
+		\begin{tabular}{lr}
+			\toprule
+			Modification & Occurrences \\
+			\midrule
+			Statement modification & 49 \\
+			Statement addition & 29 \\
+			Statement removal & 18 \\
+			Method signature change & 16 \\
+			Method rewriting & 15 \\
+			File deletion & 15 \\
+			\bottomrule 
+		\end{tabular}
+\end{table}
 
@@
 types found in the 101 outdated online clone pairs are displayed in
-\Cref{fig:mod_types} including statement addition, statement modification,
+\Cref{tab:mod_types} including statement addition, statement modification,
 statement removal, method rewriting, API change (changing in method signature),
 and file deletion. We occasionally found multiple code modifications applied to
-one clone pair at the same time but at a different location. The most often
-code changes found is statement modification (49 occurrences), followed by statement
-addition (29 occurrences), statement removal (18 occurrences), changing of method
-signature, i.e.~API change (16 occurrences), and method rewriting (15 occurrences).
-Moreover, in the 101 outdated pairs, we found 15 ``dead'' snippets. These snippets
-cannot be located in the latest version of the projects. For example,
-the snippet in Stack Overflow post 3758110, a copy of
-{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in
-\textsf{spring}, was deleted in the commit
-{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris
-Beams on January 20, 2012, two years after it was
-posted.
-
-% The latest version of Spring does not contain the file anymore.
-\Cref{tab:stale_code_details} shows examples of the outdated online
-clones on Stack Overflow. The table displays information of the clones
-from both Stack Overflow and Qualitas side including the dates. We
-summarise the changes that make the clones outdated into three types,
-modified/added/deleted statements (\textit{S}), file deletion
-(\textit{D}), and method rewriting (\textit{R}), along with the date
-of change. The complete set of 64 outdated online clones can be found
-from the study website.
-
-The outdated online code clones cause problems ranging from
-uncompilable code (due to modifications and different API usage in the
-outdated code) to introducing vulnerabilities to
-software~\cite{Xia2014}. An outdated code with a subtle change
-(e.g.~\Cref{fig:before-after}) may be copied and reused without
-awareness from developers. Although Stack Overflow has a voting
-mechanism that may mitigate this issue, the accepted answer is still
-used by naive developers who copy and reuse the outdated code.
-
-\textbf{For RQ3, our results show that 57\% (64) of QS clone
-	pairs on Stack Overflow are outdated. 60 pairs differ from their
-	newest versions by modifications applied to variable names or method
-	names, added or deleted statements, to a fully rewritten code with
-	new method signatures. 4~pairs are dead
-	snippets.}
+one clone pair at the same time but at a different location. The most often code
+changes found is statement modification (49 occurrences), followed by statement
+addition (29 occurrences), statement removal (18 occurrences), changing of
+method signature, i.e.~API change (16 occurrences), and method rewriting (15
+occurrences). Moreover, in the 101 outdated pairs, we found 15 ``dead''
+snippets. These snippets cannot be located in the latest version of the
+projects. For example, the snippet in Stack Overflow post 3758110, a copy of
+{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was
+deleted in the commit
+{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on
+January 20, 2012, two years after it was posted.
+
+Moreover, using the information in git commit messages, we can associate each
+change to its respective issues in an issue tracking system, such as Bugzilla or
+Jira. We found that in 58 cases, the cloned code snippets on Stack Overflow were
+changed because of a request in the issue tracking system. Since issue tracking
+systems are also used, besides bug reports, for feature request and feature
+enhancements, having an issue tracking ID can reflect that the change is important
+and not only a superficial fix such as code formatting.
+
+\Cref{tab:stale_code_details} shows examples of the outdated online clones on
+Stack Overflow. The table displays information of the clones from both Stack
+Overflow and Qualitas side including the dates. We summarise the changes that
+make the clones outdated into three types, modified/added/deleted statements
+(\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}),
+along with the issue tracking number and the date of change. The complete set of
+101 outdated online clones can be found from the study website.
+
+The outdated online code clones cause problems ranging from uncompilable code
+(due to modifications and different API usage in the outdated code) to
+introducing vulnerabilities to software~\cite{Xia2014}. An outdated code with a
+subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without
+awareness from developers. Moreover, an outdated code with a defect
+(e.g.~a race condition problem in \Cref{fig:before-after_2}) is harmful to be reused. Although Stack
+Overflow has a voting mechanism that may mitigate this issue, the accepted
+answer is still used by naive developers who copy and reuse the outdated code.
+
+\textbf{For RQ3, our results show that 66\% (101) of QS clone pairs on Stack
+	Overflow are outdated. 127 pairs differ from their newest versions by
+	modifications applied to variable names or method names, added or deleted
+	statements, to a fully rewritten code with new method signatures. 15~pairs are
+	dead snippets.}
 

### 2017-10-10 cloverflow-tse/cloverflow.tex
Last update before flying.

@@
 			\midrule
-			Compatible & Apache2 & Apache2 &  0 & 0  & 1\\
-			License	& EPLv1 & EPLv1 &  1 & 0 & 1\\
-			& Sun (proprietary) & Sun (proprietary) & 0 & 1 & 0\\
-			& MIT-like & MIT-like & 0 & 1 & 0\\
-			& No license & CC BY-NC-SA & 0 & 5 & 0 \\
-			& No license & No license & 5 & 4 & 21 \\
-			\midrule
-			\multicolumn{3}{l}{Total} & 6 & 11 & 23 \\
-			\midrule
-			Incompat. & BSD3 & GPLv2+ & 0 & 0 & 1 \\
-			License	& No license & AGPLv3/3+ & 1 & 0 & 2 \\
-			& No license & Apache-2 & 41 & 6 & 23 \\
-			& No license & BSD3 & 3 & 4 & 28 \\
-			& No license & CDDL or GPLv2 & 1 & 0 & 58 \\
-			& No license & CDDLv1 & 0 & 1 & 0 \\
-			& No license & EPLv1 & 7 & 0 & 10 \\
-			& No license & GPLv2/2+/3+ & 2 & 62 & 32 \\
-			& No license & LGPLv2/2.1+/3+ & 24 & 0 & 32 \\
-			& No license & MPLv1.1 & 0 & 0 & 1 \\
-			& No license & spdxBSD3 & 0 & 0 & 10 \\
-			& No license & SPLv1 & 0 & 1 & 0 \\
-			& No license & Unknown & 0 & 3 & 3 \\
-			& spdxBSD3 & AGPLv3+ & 0 & 0 & 2 \\
-			\midrule
-			\multicolumn{3}{l}{Total} &  79 & 77 & 202 \\
+			Compatible & No license & No license & 28 & & \\
+			\midrule
+			\multicolumn{3}{l}{Total} & 28 & & \\
+			\midrule
+			Incompat. & No license & Apache-2 & 55 & & \\
+			          & No license & BSD-3 & 1 & & \\
+			          & No license & CDDLorGPLv2 & 1 & & \\
+			          & No license & EPLv1 & 19 & & \\
+			          & No license & GPLv2+/3+ & 6 & & \\
+			          & No license & LesserGPLv2.1+/3+ & 20 & & \\
+			          & No license & Unknown & 24 & & \\
+			\midrule
+			\multicolumn{3}{l}{Total} & 154 & & \\
 			\bottomrule
@@
 %If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
-In our study, we reveal another possible situation of software
-licensing issues caused by code cloned to Stack Overflow. We found
-evidence that 112 pieces of code have been copied from Qualitas
-projects to Stack Overflow as examples. Their status of accepted
-answers increase their chances of being reused. Even though most of
-the Qualitas projects came with a software license, we found that the license information
-were frequently missing after the code was copied to Stack
-Overflow. The licensing terms on top of source code files are not
-copied because usually only a small part of the file was
-cloned. In overall, we can see that most of the Stack Overflow snippets do not
-contain licensing terms while their clone counterparts in Qualitas
-projects do. The summary of
+In our study, we reveal another type of toxic code snippets which is software
+licensing issues caused by code cloned to Stack Overflow. We found evidence that
+154 pieces of code have been copied from Qualitas projects to Stack Overflow as
+examples. Their status of accepted answers increase their chances of being
+reused. Even though most of the Qualitas projects came with a software license,
+we found that the license information were frequently missing after the code was
+copied to Stack Overflow. The licensing terms on top of source code files are
+not copied because usually only a small part of the file was cloned. In overall,
+we can see that most of the Stack Overflow snippets do not contain licensing
+terms while their clone counterparts in Qualitas projects do. The summary of
 licensing information is listed in \Cref{tab:license_abc}.

### 2017-10-12 cloverflow-tse/cloverflow.tex
Latest update.

@@
 
-\subsection{Phase 2: Clone Merging}
-As there are in total 315,786,118 clone pairs reported, it is infeasible for
-humans to manually validate them all. Instead of investigating a random sample,
-we adopted the idea of \textbf{clone agreement} which has been used in clone
-research studies~\cite{Funaro2010, Wang2013,cr2016ssbse} in situations where a
-clone oracle is missing or impossible to establish. Clone pairs agreed by
-multiple clone detection tools have a higher likelihood to be real
-clones~\cite{cr2016ssbse}. By using this agreement-based approach, we reduced
-the number of clone candidates for manual investigation and avoid a threat to
-internal validity of double counting the same clone pair twice by merging the
-ones agreed by the two tools. To find agreement between two clone pairs
-reported by two different tools, we used the clone pair matching metric proposed
-by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large enough
-number of overlapping lines can be categorised as either a good-match or an
-ok-match pair (denoted as \textit{good} and \textit{ok} respectively) with a
-confidence value between 0 and 1. Although good-match has stronger
-agreement than ok-match, we choose ok-match as our clone merging method because 
-it does not take clone size into account which suit our results of clones from
-two tools, Simian, SourcererCC, with two different detection methods, 
-line-based and method-based.
+\subsection{Phase 2: Clone Merging} As there are in total 315,786,118 clone
+pairs reported, it is infeasible for humans to manually validate them all.
+Instead of investigating a random sample, we adopted the idea of \textbf{clone
+	agreement} which has been used in clone research studies~\cite{Funaro2010,
+	Wang2013,cr2016ssbse} in situations where a clone oracle is missing or
+impossible to establish. Clone pairs agreed by multiple clone detection tools
+have a higher likelihood to be real clones~\cite{cr2016ssbse}. By using this
+agreement-based approach, we reduced the number of clone candidates for manual
+investigation and avoid a threat to internal validity of double counting the
+same clone pair twice by merging the ones agreed by the two tools. To find
+agreement between two clone pairs reported by two different tools, we used the
+clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two
+clone pairs which have a large enough number of overlapping lines can be
+categorised as either a good-match or an ok-match pair (denoted as \textit{good}
+and \textit{ok} respectively) with a confidence value between 0 and 1. Although
+good-match has stronger agreement than ok-match, we choose ok-match as our clone
+merging method because it does not take clone size into account. Clone containment suits our
+online code clones from two tools, Simian (line-level) and SourcererCC
+(method-level), better because Simian's clone fragments  are sometimes smaller or bigger than
+a method while SourcererCC's clone fragments are always confined to a method boundary.
 
@@
 potential licensing violations. 
+\FIXME{Add a discussion of Abdalkareem et al.~\cite{Abdalkareem2017}}
 %In our work, we defined seven patterns of online code cloning and 

### 2017-10-12 cloverflow-tse/cloverflow.tex
Fixed the number of QS and outdated clone pairs.

--- 2017-10-10 cloverflow-tse/cloverflow.tex
@@
 		\midrule
-		TP from manual validation & 2,076 & 449 & 59 & 54.22\% \\ 
+		TP from manual validation & 2,076 & 443 & 59 & 53.89\% \\ 
 		\bottomrule
@@
 as being accidental clones (AC), i.e.~false positives. After removing
-them, the set still contains 2,076 true positive clone pairs between 449 Stack
+them, the set still contains 2,076 true positive clone pairs between 443 Stack
 Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
-true positive clone pairs is 54.22\%.
+true positive clone pairs is 53.89\%.
 
@@
 	account for 59 Qualitas projects and
-	449 Stack Overflow code snippets.}
+	443 Stack Overflow code snippets.}
 
@@
 			\midrule
-			Statement modification & 49 \\
-			Statement addition & 29 \\
+			Statement modification & 50 \\
+			Statement addition & 28 \\
 			Statement removal & 18 \\

### 2017-10-12 cloverflow-tse/cloverflow.tex
Latest changes.

@@
 
-\title{Outdated and License-Violating Code on Stack Overflow}
-
-\author{Chaiyong Ragkhitwetsagul,~Matheus Paixao,~Jens Krinke,~Giuseppe Bianco,~Rocco Oliveto}
+\title{Toxic code snippets on Stack Overflow}
+
+\author{Chaiyong Ragkhitwetsagul,~Jens Krinke,~Matheus Paixao,~Giuseppe Bianco,~Rocco Oliveto}
 
@@
 as a solution or to complement their answer~\FIXME{put a precise number here}.
-One participants says
-
-\begin{quote}\textit{The real issue is less about the amount the code snippets
+One participants says:
+
+\begin{quote}\textit{``The real issue is less about the amount the code snippets
 		on SO than it is about the staggeringly high number of software
@@
 		(\url{https://news.ycombinator.com/item?id=14846506}). They're also full of
-		toxic code snippets.}\end{quote}
+		toxic code snippets.''}\end{quote}
 
@@
 			\midrule
-			Compatible & No license & No license & 28 & & \\
-			\midrule
-			\multicolumn{3}{l}{Total} & 28 & & \\
-			\midrule
-			Incompat. & No license & Apache-2 & 55 & & \\
-			          & No license & BSD-3 & 1 & & \\
-			          & No license & CDDLorGPLv2 & 1 & & \\
-			          & No license & EPLv1 & 19 & & \\
-			          & No license & GPLv2+/3+ & 6 & & \\
-			          & No license & LesserGPLv2.1+/3+ & 20 & & \\
-			          & No license & Unknown & 24 & & \\
-			\midrule
-			\multicolumn{3}{l}{Total} & 154 & & \\
+			Compatible & Apache-2 & Apache-2 & 1 & & \\
+								  & EPLv1 & EPLv1 & 2 & & \\
+								  & No license & No license	& 20 & & \\
+			\midrule
+			\multicolumn{3}{l}{Total} & 23 & & \\
+			\midrule
+			Incompat. & No license & EPLv1	& 10 & & \\
+								& No license & GPLv2/2+/3+	& 7 & & \\
+								& No license & AGPLv3 & 1 & & \\
+								& No license & Apache-2 & 46 & & \\
+								& No license & BSD/BSD3	& 4 & & \\
+								& No license & LesserGPL/v2.1+/v3+ & 17 & & \\
+								& spdxBSD3 & LesserGPLv2.1+	& 1 & & \\
+			\midrule
+			\multicolumn{3}{l}{Total} & 86 & & \\
 			\bottomrule
@@
 
-%If developers copy and reuse these licensed pieces of code in their projects, conflicts may happen without their realisation.
+%If developers copy and reuse these licensed pieces of code in their projects,
+% conflicts may happen without their realisation.
 In our study, we reveal another type of toxic code snippets which is software
@@
 we can see that most of the Stack Overflow snippets do not contain licensing
-terms while their clone counterparts in Qualitas projects do. The summary of
+terms while their clone counterparts in Qualitas projects do. 
+Pleaste note that the
+results here are analysed at file level, not clone fragment, thus there are some
+clone pairs that share the same result and we combine them into a single pair.
+The summary of
 licensing information is listed in \Cref{tab:license_abc}.

### 2017-10-14 cloverflow-tse/cloverflow.tex
Completed the whole paper (RQ1 - RQ5).

@@
 	can cause software developers to violate licenses.
-	\item \textbf{RQ5 (Developers' awareness): }\textit{Do Stack Overflow
-		users aware of the outdated code and licensing problem when
+	\item \textbf{RQ5 (Stack Overflow answerers' awareness): }
+		\subitem \textit{RQ5.1 Do Stack Overflow
+		answerers aware of the outdated code when
 		they answer a question on Stack Overflow?} 
+		\subitem \textit{RQ5.2 Do Stack Overflow
+			answerers aware of licensing conflicts when
+			they answer a question on Stack Overflow?}
+
 	We surveyed 607 high reputation Stack Overflow users to study their
-	awareness of the issues.
+	awareness of the two issues.
 \end{itemize}
@@
 
-\begin{table}
-	\centering
-	\caption{The two groups of Stack Overflow users invited to take the survey}
-	\label{tab:survey_target}
-	\begin{tabular}{lrrrr}
-		\toprule
-		Target group & Reputation & Sent emails & Answers & Rate \\
-		\midrule
-		Group 1 & 963,731--7,674 & 300 & 112 & 37\% \\
-		Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
 We selected the participants for our survey based on the users' reputations. On
@@
 ranked all-time reputations\footnote{Stack Overflow Users (data as of 25 July
-	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}} and
-separated them into two groups (see \Cref{tab:survey_target}) so that we can
-compare the results or observe similar patterns between them. 
-The first group had reputation from 963,731 (the
-highest) to 7,674, and the second group had reputation from 7,636 to 6,999 which
-we sent out 300 and 307 emails (excluding undelivered ones) respectively. The
-survey was open for participation for two months, from 25 August 2017 to 25 August
+	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}.
+They had a reputation from 963,731 (the
+highest) to 6,999 which
+we sent out 607 emails (excluding undelivered ones) respectively. The
+survey was open for participation for two months, from 25 July to 25 September
 2017, before we collected and analysed the responses.
@@
 \subsection{RQ1: Online Code Clones} 
+\vspace{0.25cm}
+\textit{To what extent is source
+	code cloned between Stack Overflow and open source projects?}
+\vspace{0.25cm}
 
@@
 \subsection{RQ2: Patterns of Online Code Cloning}
+\vspace{0.25cm}
+\textit{Why do online code clones occur?}
+\vspace{0.25cm}
 
@@
 			\midrule
-			2513183 & 25-Mar-10 & eclipse & 4.3 & GenerateToStringAction.java & 113 & 166 & & Bug 439874 & \textit{S} & 17-Mar-15 \\
+			2513183 & 25-Mar-10 & eclipse & 4.3 & GenerateToStringAction.java & 113 & 166 & 5-Jun-13 & Bug 439874 & \textit{S} & 17-Mar-15 \\
 			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & HADOOP-11323 & \textit{S} & 20-Nov-14 \\
 			23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & HHH-10458 & \textit{S} & 5-Feb-16 \\
-			18232672 & 14-Aug-13 & log4j & 1.2.16 & SMTPAppender.java & 207 & 228 & & Bug 44644 & \textit{R} & 18-Oct-08 \\ 
-			17697173 & 17-Jul-13 & lucene & 4.3.0 & SlowSynonymFilterFactory.java & 38 & 52 & & LUCENE-4095 & \textit{D} & 31-May-12 \\
+			18232672 & 14-Aug-13 & log4j & 1.2.16 & SMTPAppender.java & 207 & 228 & 31-Mar-10 & Bug 44644 & \textit{R} & 18-Oct-08 \\ 
+			17697173 & 17-Jul-13 & lucene & 4.3.0 & SlowSynonymFilterFactory.java & 38 & 52 & 6-Apr-13 & LUCENE-4095 & \textit{D} & 31-May-12 \\
 			21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & BZ 59823 &\textit{R} & 4-Aug-16 \\
@@
 			3758110 & 21-Sep-10 & spring & 3.0.5  & DefaultAnnotation\newline HandlerMapping.java & 78 & 92 & 20-Oct-10 & SPR-14129 & \textit{D} & 20-Jan-12 \\
-			14019840 & 24-Dec-12 & struts & 2.2.1 & DefaultActionMapper.java & 273 & 288 & & WW-4225 & \textit{S} & 18-Oct-13 \\
+			14019840 & 24-Dec-12 & struts & 2.2.1 & DefaultActionMapper.java & 273 & 288 & 17-Jul-10 & WW-4225 & \textit{S} & 18-Oct-13 \\
 			\bottomrule 
@@
 \subsection{RQ3: Outdated Online Code Clones}
+\vspace{0.25cm}
+\textit{Are online code clones up-to-date compared to their counterparts in the original projects?}
+\vspace{0.25cm}
 
@@
 \subsection{RQ4: Software Licensing Violation}
-
-\begin{table}[]
+\vspace{0.25cm}
+\textit{Do
+	licensing conflicts occur between Stack Overflow clones and their
+	originals?}
+\vspace{0.25cm}
+
+\begin{table}
 	\centering
@@
 	\resizebox{\linewidth}{!}{
-		\begin{tabular}{lp{2.2cm}lrrr}
+		\begin{tabular}{lp{2.5cm}p{2.5cm}rrr}
 			\toprule
@@
 			\midrule
-			Compatible & Apache-2 & Apache-2 & 1 & & \\
-								  & EPLv1 & EPLv1 & 2 & & \\
-								  & No license & No license	& 20 & & \\
-			\midrule
-			\multicolumn{3}{l}{Total} & 23 & & \\
-			\midrule
-			Incompat. & No license & EPLv1	& 10 & & \\
-								& No license & GPLv2/2+/3+	& 7 & & \\
-								& No license & AGPLv3 & 1 & & \\
-								& No license & Apache-2 & 46 & & \\
-								& No license & BSD/BSD3	& 4 & & \\
-								& No license & LesserGPL/v2.1+/v3+ & 17 & & \\
-								& spdxBSD3 & LesserGPLv2.1+	& 1 & & \\
-			\midrule
-			\multicolumn{3}{l}{Total} & 86 & & \\
+			Compatible 
+			& Apache-2 & Apache-2 & 1 & & \\ 
+			& EPLv1 & EPLv1 & 2 & & 1 \\ 
+			& Proprietary & Proprietary & & 2 & \\ 
+			& Sun Microsystems & Sun Microsystems & & 3 & \\ 
+			& No license & No license & 20 & 9 & 2 \\ 
+			& CC BY-SA 3.0 & No license & & 1 & \\
+			\midrule
+			\multicolumn{3}{l}{Total} & 23 & 15 & 3 \\
+			\midrule
+			Incompat. 
+			& No license & AGPLv3/3+ & 1 & & 4 \\
+			& No license & Apache-2 & 46 & 14 & 12 \\  
+			& No license & BSD/BSD3 & 4 & & 1 \\ 
+			& No license & CDDL or GPLv2 & & & 6 \\ 
+			& No license & EPLv1 & 10 & & 6 \\
+			& No license & GPL/v2/2+/3+ & 8 & 48 & 7 \\ 
+			& No license & LesserGPL/v2.1+/3+ & 16 & & 9 \\ 			
+			& No license & MPLv1.1 & & & 1 \\ 
+			& No license & Oracle & & 3 \\ 
+			& No license & Proprietary & & 1 & 2 \\ 
+			& No license & Sun Microsystems & & 1 & 2 \\ 
+			& No license & Unknown & & 11 & \\
+			& New BSD3 & LesserGPLv2.1+ & 1 & & \\ 
+			\midrule
+			\multicolumn{3}{l}{Total} & 86 & 78 & 50 \\
 			\bottomrule
@@
 154 pieces of code have been copied from Qualitas projects to Stack Overflow as
-examples. Their status of accepted answers increase their chances of being
-reused. Even though most of the Qualitas projects came with a software license,
-we found that the license information were frequently missing after the code was
-copied to Stack Overflow. The licensing terms on top of source code files are
-not copied because usually only a small part of the file was cloned. In overall,
-we can see that most of the Stack Overflow snippets do not contain licensing
-terms while their clone counterparts in Qualitas projects do. 
-Pleaste note that the
-results here are analysed at file level, not clone fragment, thus there are some
-clone pairs that share the same result and we combine them into a single pair.
-The summary of
-licensing information is listed in \Cref{tab:license_abc}.
-
-\textbf{Compatible license:} There are 40 pairs which have compatible
+examples. Another 111 pieces of code are cloned from external sources. Their
+status of accepted answers increase their chances of being reused. Even though
+most of the Qualitas projects came with a software license, we found that the
+license information were frequently missing after the code was copied to Stack
+Overflow. The licensing terms on top of source code files are not copied because
+usually only a small part of the file was cloned. In overall, we can see that
+most of the Stack Overflow snippets do not contain licensing terms while their
+clone counterparts in Qualitas projects and external sources do. Since licensing
+statement resides on top of a file, the results here are analysed at file level,
+not clone fragment, and clone pairs from the same file are merged. 
+The summary of licensing information is listed in
+\Cref{tab:license_abc}.
+
+\textbf{Compatible license:} There are 41 pairs which have compatible
 licenses such as \emph{Apache license v.2}; \emph{Eclipse Public
-	License v.1 (EPLv1)}; or a pair of no license vs.~\emph{Creative
+	License v.1 (EPLv1)}; or a pair of \emph{Creative
 	Common Attribution-NonCommercial-ShareAlike 3.0 Unported (CC
-	BY-NC-SA 3.0)}. These clones are safe for being reused. Since source
+	BY-NC-SA 3.0)} vs.~no license. These clones are safe for being reused. Since source
 code and text on Stack Overflow are
@@
 
-\textbf{Incompatible license:} there are 358 clone pairs which do not
-contain licensing information after they are posted on Stack Overflow
-or contain a different license from their Qualitas clone
-counterparts. More than half (79) of \textbf{QS} clone pairs have
-their licensing terms removed or changed when posted on Stack
-Overflow. For \textbf{EX} clone pairs, we searched for licensing terms of the
-original source code from the external sources. We found that 77 out
-of 88 EX clone pairs have incompatible licenses.
-%They are clones that have been identified to be copied from an external source.
-Similarly, the license statement was removed from Stack Overflow
-snippets. Of 226 \textbf{UD} clone pairs, 202 pairs have incompatible
-licenses. Again, most clones in Qualitas contain a license
-while the Stack Overflow snippets do not.
+\textbf{Incompatible license:} there are 214 clone pairs which do not contain
+licensing information after they are posted on Stack Overflow or contain a
+different license from their Qualitas clone counterparts. Almost all (85) of
+\textbf{QS} clone pairs have their licensing terms removed or changed when
+posted on Stack Overflow. One QS clone pair posted by a JFreeChart developer
+changes its license from Lesser GPL v2.1+ to New BSD 3-clause. The JFreeChart
+developer may intentionally change the license to be more suitable for Stack
+Overflow since New BSD 3-clause license allows reuse without requiring the same
+license in the distributing software or statement of changes.
+
+For \textbf{EX}
+clone pairs, we searched for licensing terms of the original source code from
+the external sources. We found that 78 out of 93 EX clone pairs have
+incompatible licenses. %They are clones that have been identified to be copied
+% from an external source.
+Similarly, the license statement was removed from Stack Overflow snippets.
+
+Of 53 \textbf{UD} clone pairs, 50 pairs have incompatible licenses. Again, most
+clones in Qualitas contain a license while the Stack Overflow snippets do not.
 %
-%\Cref{fig:sankey_license} shows the direction of changes in online code clone license.
-The direction of the change is from left to right.
-The thickness of the line reflects the number of clones for that relationship.
-In \Cref{fig:sankey_license} (A), we can clearly see that most of the QS online clones have their licenses changed from having a license to ``No license'' on Stack Overflow.
-The same findings were found for EX online clones as depicted in \Cref{fig:sankey_license} (B).
-We found that most of the EX clones have their licensing information stripped of after copying to Stack Overflow.
-These clones are instead covered by the default CC BY-NC-SA 3.0 license of Stack Overflow which is strongly permissive.
-These used-to-be-licensed code are dangerous for being reused because they can implicitly conflict with the reused software's license.
-
-\textbf{For RQ4, we found 358 code snippets on Stack Overflow that
+%\Cref{fig:sankey_license} shows the direction of changes in online code clone
+% license. The direction of the change is from left to right. The thickness of
+% the line reflects the number of clones for that relationship. In
+% \Cref{fig:sankey_license} (A), we can clearly see that most of the QS online
+% clones have their licenses changed from having a license to ``No license'' on
+% Stack Overflow. The same findings were found for EX online clones as depicted
+% in \Cref{fig:sankey_license} (B). We found that most of the EX clones have
+% their licensing information stripped of after copying to Stack Overflow. These
+% clones are instead covered by the default CC BY-NC-SA 3.0 license of Stack
+% Overflow which is strongly permissive. These used-to-be-licensed code are
+% dangerous for being reused because they can implicitly conflict with the
+% reused software's license.
+
+\textbf{For RQ4, we found 214 code snippets on Stack Overflow that
 	violate the license of their original software. The majority of them
@@
 
-We received 112 answers (37\% response rate) from the first group and 85 answers
-(28\% response rate) from the second group of Stack Overflow answerers. The response
-rate from both groups were high considered other online survey in software
-engineering that received approximately 14--20\%~\FIXME{double-check the
-	citation again for the magic numbers.}\cite{Punter2003}.
-We only present a summary of the survey answers in this paper. The full analysis
-is available as a technical report \FIXME{Ok?}.
+\begin{table}
+	\centering
+	\caption{Stack Overflow answerers taken the survey}
+	\label{tab:survey_target}
+	\begin{tabular}{rrrr}
+		\toprule
+		Reputation & Sent emails & Answers & Rate \\
+		\midrule
+		963,731--6,999 & 607 & 201 & 33\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We received 201 answers (33\% response rate) from 607 emails we sent to the
+Stack Overflow answerers. The response rate was high
+considered other online survey in software engineering that received
+approximately 14--20\%~\FIXME{double-check the citation again for the magic
+	numbers.}\cite{Punter2003}.
+We only present a summary of the survey answers in
+this paper and the full analysis is available as a technical report \FIXME{add URL}.
+
+\subsubsection{General Information}
+As shown in \Cref{tab:survey_exp}, majority of the answerers are experienced
+developers with more than 10 years of experience (55.4\%) or between 5 to 10
+years (28.7\%). They are active users and regularly answer questions. 49
+participants answer questions on Stack Overflow every day.
+
+\begin{table}
+	\centering
+	\caption{Experience of Stack Overflow answerers}
+	\label{tab:survey_exp}
+	\begin{tabular}{lrr}
+		\toprule
+		Experience & Amount & Percent \\
+		\midrule
+		Less than a year & 1 & 0.5\% \\
+		1 -- 2 years & 1 & 0.5\% \\
+		3 -- 5 years & 30 & 14.9\% \\
+		5 -- 10 years & 58 & 28.9\% \\
+		More than 10 years	& 111 & 55.2\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\subsubsection{Code Snippets in Answers}
+
+\begin{table}
+	\centering
+	\caption{Frequency of including code snippets in answers}
+	\label{tab:survey_code_snippet_frequency}
+	\begin{tabular}{lrr}
+		\toprule
+		Include code snippets & Amount & Percent \\
+		\midrule
+		Very Frequently (81--100\% of the time)	& 84 & 42\% \\
+		Frequently (61--80\% of the time) &	63 & 31\% \\
+		Occasionally (41--60\% of the time) & 40 & 20\% \\
+		Rarely (21--40\% of the time) & 11 & 6\% \\
+		Very Rarely (1--20\% of the time) & 2 & 1\% \\
+		Never (0\% of the time) & 1 & 1\% \\
+		\midrule
+		Total & 201 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+84 and 63 answerers include code snippets in more than 80\% and 60\% of
+their answers respectively. Interestingly, there is one answerer who never
+include code snippet in his/her answers.
 
 \begin{figure}
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.6\linewidth]{survey_exp_1-crop}
-		\caption{Group 1}
-		\label{fig:survey_group1_exp}
-	\end{subfigure}%
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.62\linewidth]{survey_exp_2-crop}
-		\caption{Group 2}
-		\label{fig:survey_group2_exp}
-	\end{subfigure}
-	\caption{Experience of the Stack Overflow users}
-	\label{fig:survey_exp}
+	\centering
+	\includegraphics[width=0.9\linewidth]{survey_snippet_source}
+	\caption{The sources of code snippets in Stack Overflow answers}
+	\label{fig:survey_snippet_source}
 \end{figure}
 
-\subsubsection{Answerers' Experience}
-The majority of users in both groups are experienced developers 
-with more than 10 years of experience or between 5 to 10 years 
-as depicted in \Cref{fig:survey_exp}. They are active users and
-regularly answer questions on Stack Overflow.
-Eighty one and sixty percent of users from Group 1 and Group 2 
-answer questions at least once a week.
-
-\begin{figure*}
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=.8\linewidth]{survey_snippet_source_1}
-		\caption{Group 1}
-		\label{fig:survey_snippet_source_1}
-	\end{subfigure}%
-	\begin{subfigure}{.5\textwidth}
-		\centering
-		\includegraphics[width=.8\linewidth]{survey_snippet_source_2}
-		\caption{Group 2}
-		\label{fig:survey_snippet_source_2}
-	\end{subfigure}
-	\caption{Sources of code snippets in Stack Overflow answers}
-	\label{fig:survey_snippet_source}
-\end{figure*}
-
-\subsubsection{Code Snippets in Answers} 
-A large amount of 91 (81\%) and 58
-(68\%) users in both group include code snippets in more than sixty percent of
-their answers. \Cref{fig:survey_snippet_source} explains where are these code
-snippets from. Stack Overflow answerers mostly write new code from scratch 
-or modify from the code snippets in question for each answer, while 
-fewer numbers are from other sources including their personal projects, 
-their company projects, open source projects. We found 27 answerers in both Group 1
-and Group 2 occasionally to very frequently copy code from open source projects.
-
-\begin{figure}
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.6\linewidth]{survey_license_1}
-		\caption{Group 1}
-		\label{fig:survey_license_1}
-	\end{subfigure}%
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=.6\linewidth]{survey_license_2}
-		\caption{Group 2}
-		\label{fig:survey_license_2}
-	\end{subfigure}
-	\caption{Software license in Stack Overflow code snippets.}
-	\label{fig:survey_license}
-\end{figure}
+We asked the participants for the origins of code snippets in their answers. We
+provided six locations (allow multiple selection) including the answerer's
+personal projects, the answerer's company projects, open source projects,
+writing the code from scratch, copying and modifying the code from the question,
+and others (e.g.~code that are copied from other questions or answers on Stack
+Overflow) and asked them to rate how often they copied the code from these
+locations. The results are shown in \Cref{fig:survey_snippet_source}. Looking at
+Very Frequently section, we can see that the answerers mainly write new code
+from scratch (71) or modify from the code snippets in question for each answer
+(56), while fewer numbers are from other sources including their personal
+projects (42), their company projects (10), and open source projects (14).
+Although copying from open source projects is not the most popular choice, the answerers
+still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
+participants who frequently, occasionally, and rarely copied code snippets from open
+source projects.
 
 \subsubsection{Outdated Code Snippets} 
-
-We found that 63.1\% of Stack Overflow answerers in Group 1 have been notified of
-outdated code in their answers (see \Cref{fig:survey_outdated}). The ratio drops to 47.6\% in
-Group 2. Thus, at least roughly half of the top answerers on Stack Overflow
-are aware of their outdated code in some of their answers.
-
-\begin{figure}
-	\centering
-	\includegraphics[width=.8\linewidth]{survey_outdated}
-	\caption{Percentage of answerers who are notified of outdated code in their Stack Overflow answers.}
-	\label{fig:survey_outdated}
-\end{figure}%
-
-We then asked the participants to have been notified of their outdated code
-(80 and 48 participants from Group 1 and 2 respectively) a
+\vspace{0.25cm}
+\textit{Do Stack Overflow
+	answerers aware of the outdated code when
+	they answer a question on Stack Overflow?} 
+\vspace{0.25cm}
+
+We asked the answerers if they have ever been notified about outdated code in
+their answers. 111 participants selected \textit{Yes} while the other 89 participants
+selected \textit{No}. However, we found inconsistent results when we asked a follow up
+question on the frequency of being notified. As displayed in
+\Cref{tab:survey_code_snippet_outdated}, the number of participants who has
+\textit{Never} been notified about outdated code snippets in their answers drops
+from 89 to 69.
+
+\begin{table}
+	\centering
+	\caption{Awareness to outdated code snippets in answers}
+	\label{tab:survey_code_snippet_outdated}
+	\begin{tabular}{lrr}
+		\toprule
+		Notified of outdated code & Amount & Percent \\
+		\midrule
+		Very frequently (81--100\% of my answers) & 2 & 1\% \\
+		Frequently (61--80\% of my answers) & 1 & 0.5\% \\
+		Occasionally (41--60\% of my answers) & 9 & 4.5\% \\
+		Rarely (21--40\% of my answers) & 16 & 8\% \\
+		Very rarely (1--20\% of my answers) & 103 & 51.5\% \\
+		Never (0\% of my answers) & 69 & 34.5\% \\
+		\midrule
+		Total & 200 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We found that although the answerer have been notified of
+outdated code in their answers, 51.5\% occurs very rarely (only 1--20\% of the answers). 
+Only 3 participants reported that they were notified in more than 60\% of their answers.
+
+\begin{table}
+	\centering
+	\caption{Fixing of outdated code snippets in answers}
+	\label{tab:survey_code_snippet_outdated_fix}
+	\begin{tabular}{lrr}
+		\toprule
+		Fixing of outdated code & Amount & Percent \\
+		\midrule
+		Very frequently (81--100\% of the cases) & 48 & 36.6\% \\
+		Frequently (61--80\% of the cases) & 27 & 20.6\% \\
+		Occasionally (41--60\% of the cases) & 30 & 22.9\% \\
+		Rarely (21--40\% of the cases) & 11 & 8.4\% \\
+		Very rarely (1--20\% of the cases) & 8 & 6.1\% \\
+		Never (0\% of the cases) & 7 & 5.3\% \\
+		\midrule
+		Total & 131 & 100.0\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We then asked 131 participants to have been notified of their outdated code a
 follow-up questions ``how frequently did you fix your outdated code on Stack
-Overflow?''. The answers, depicted in \Cref{fig:survey_outdated_fix}, show that
-more than half of them frequently fix the outdated code snippets. However, there
-are 18.8\% of the answerers in both groups who rarely or never fix their code.
-
-\begin{figure}
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{survey_outdated_fix_1}
-		\caption{Group 1}
-		\label{fig:survey_outdated_fix_1}
-	\end{subfigure}%
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{survey_outdated_fix_2}
-		\caption{Group 2}
-		\label{fig:survey_outdated_fix_2}
-	\end{subfigure}
-	\caption{Frequency of the answerers fixing their outdated code.}
-	\label{fig:survey_outdated_fix}
-\end{figure}
-
-The answers support our findings of outdated online code clones. Although most
-of the Stack Overflow answerers know that their code are outdated, the code may
-still not be fixed.
+Overflow?''. The answers, depicted in
+\Cref{tab:survey_code_snippet_outdated_fix}, show that more than half of them
+(57.2\%) very frequently or frequently fix the outdated code snippets. However,
+there are 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
+their outdated code.
+
+\textbf{To answer RQ 5.1, although most of the Stack Overflow answerers are aware that their code
+can be outdated. 51.5\% of the answerers were very rarely notified while 35.5\% never been notified of
+outdated code in the answers. 19.8\% of them rarely fix the outdated code or left them unfixed.}
+
+The responses from the answerers support our findings of outdated online code
+clones. In addition, this
+results only reflect experienced answerers who accumulate the reputation for a
+long time. Due to the voting mechanism of Stack Overflow, high reputation users
+usually provide quality answers and earn up votes from other users. They must be
+very careful when posting code snippets in the answer to avoid problems and, in
+the end, getting down votes. It is also interesting to compare the findings to
+Stack Overflow answerers who are newer and have lower reputation. However, we
+leave it as the future work.
 
 \subsubsection{License of Code Snippets} 
-More than half of the answerers in both groups (63.1\% and 61.9\% respectively)
-are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike 3.0
-Unported (CC BY-SA 3.0) to content in the posts, including code snippets, while
-the rest of 36.9\% and 38.1\% are not. Nevertheless, we found that almost all 
-of them do not include license statement in their code snippets (as depicted in
-\Cref{fig:survey_license}) due to several reasons. First, some answerers chose to 
-post only their own code or code that was adapted from the question, hence
+\vspace{0.25cm}
+\textit{Do Stack Overflow
+	answerers aware of the outdated code when
+	they answer a question on Stack Overflow?} 
+\vspace{0.25cm}
+
+\begin{table}
+	\centering
+	\caption{Inclusion of software license in answer}
+	\label{tab:survey_license_include}
+	\begin{tabular}{lr}
+		\toprule
+		Include license? & Amount \\
+		\midrule
+		No. & 197 \\
+		Yes, in code comment &	1 \\
+		Yes, in text surrounding the code & 2 \\
+		\midrule
+		Total & 200 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+More than half of the 200 answerers who include code snippets in their answers,
+124 are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike
+3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets,
+while the rest (76) are not. Nevertheless, we found that almost all of them (197) do
+not include license statement in their code snippets (as presented in
+\Cref{tab:survey_license_include}) due to several reasons. First, some answerers chose
+to post only their own code or code that was adapted from the question, hence
 they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
-company or open source projects that they knew were permitted to be publicly distributed.
-Third, some answerers believe that code snippets in their answers are too small 
-to claim any intellectual property on them and fall under fair use~\cite{fairuse}.
+company or open source projects that they knew were permitted to be publicly
+distributed. Third, some answerers believe that code snippets in their answers
+are too small to claim any intellectual property on them and fall under fair
+use~\cite{fairuse}.
 
@@
 many users include a statement on their profile page that states all their
-answers are under a certain license. For example, \textit{All code posted by me on
+answers are under a certain license. For example, a Stack Overflow includes 
+the following text in his/her profile page.
+
+\begin{quotation}
+\textit{All code posted by me on
 	Stack Overflow should be considered public domain without copyright. For
@@
 	right to modify, use and redistribute any code posted by me on Stack Overflow
-for any purpose. It is provided "as-is" without warranty of any kind.}  Many
-users either declare their snippets to be public domain, or they grant
+	for any purpose. It is provided ``as-is'' without warranty of any kind.}
+\end{quotation}
+
+Many users either declare their snippets to be public domain, or they grant
 additional licenses, e.g. Apache 2.0 or MIT/Expat.
 
-\begin{figure}
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{survey_license_check_1}
-		\caption{Group 1}
-		\label{fig:survey_license_check_1}
-	\end{subfigure}%
-	\begin{subfigure}{.25\textwidth}
-		\centering
-		\includegraphics[width=\linewidth]{survey_license_check_2}
-		\caption{Group 2}
-		\label{fig:survey_license_check_2}
-	\end{subfigure}
-	\caption{Frequency of the answerers checking license of their code snippets against Stack Overflow's CC BY-SA 3.0.}
-	\label{fig:survey_license_check}
-\end{figure}
-
-We asked the answerers a follow-up question of how frequently they checked for a conflict between software license of the code snippets they copied to their answers and Stack Overflow's CC BY-SA 3.0.
-As shown in \Cref{fig:survey_license_check}, approximately 69\% of answerers from both groups did not perform the checking.
-Nonetheless, they are about 10\% of the answerers who frequently checks for licensing conflicts when they copy code snippets to Stack Overflow.
-
-\subsubsection{Open Comments} 
-We also invited the participants to give any comments regarding answering Stack Overflow with code snippets. These are some interesting comments we received.
-
-Comment 1: ``The real issue is less about the amount the code snippets on SO than it is about the staggeringly high number of software "professionals" that mindlessly use them without understanding what they're copying, and the only slightly less high number of would-be professionals that post snippets with built-in security issues.
-A related topic is beginners who post (at times dangerously) misleading tutorials online on topics they actually know very little about.
-Think php/mysql tutorials written 10+ years after \texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that got posted the other day on HackerNew (\url{https://news.ycombinator.com/item?id=14846506}).
-They're also full of toxic code snippets.''
-
-Comment 2: ``When I copy code it's usually short enough to be considered "fair use" but I am not a lawyer or copyright expert so some guidance from SO would be helpful.
-I'd also like the ability to flag/review questions that violate these guidelines.''
-
-Comment 3: ``My only concern, albeit minor, is that I know people blindly copy my code without even understanding what the code does.''
-
-Comment 4: ``The main problem for me/us is outdated code, esp.
-as old answers have high google rank so that is what people see first, then try and fail.
-Thats why we're moving more and more of those examples to knowledge base and docs and rather link to those.''
-
-Comment 5: ``Lot of the answers are from hobbyist so the quality is poor. Usually they are hacks or workarounds (even MY best answer on SO is a workaround).''
-
-\subsection{Overall Discussion}
-%What can we learn for the results?
-For example, if a developer explicitly reports in his/her code that the snippet was copied from stackoverfow, are there some benefits?
-We could notify - for instance - the developer when some new issues related to the snippet are posted on stackoverflow?
-Or could we force people posting code on SO to explicitly report licensing information?
-Or, could we implement an intelligent IDE that when pasting code from external resource checks for licensing violation?
-These of course are only some (crazy?) ideas that could be developed on the top of the results we have achieved with this study...
-
-%We discovered two issues regarding code snippets on Stack Overflow in this study: (1)  outdated online clones on Stack Overflow and (2) missing or incompatible license in Stack Overflow snippets. 
-%that there is a considerable amount of cloned code between Stack Overflow that are cloned from 111 projects in the Qualitas corpus.
-64 clone pairs are outdated and 358 snippets have incompatible software licenses to their originals.
-Our study discovers links from code in open source projects to code
-snippets on Stack Overflow using clone detection techniques. These
-links enable us to discover outdated code and licensing problems. The
-links can be exploited further to mitigate the problems of reusing
-outdated online clones and incompatible license on Stack Overflow code
-snippets. We propose the following actionable items:
+\begin{table}
+	\centering
+	\caption{Checking for licensing conflicts with CC BY-SA 3.0}
+	\label{tab:survey_license_check}
+	\begin{tabular}{lrr}
+		\toprule
+		Check license conflicts? & Amount & Percent \\
+		\midrule
+		Very Frequently (81--100\% of the time)	& 14 & 7\% \\
+		Frequently (61--80\% of the time) & 7 & 3.5\% \\
+		Occasionally (41--60\% of the time) & 10 & 5\% \\
+		Rarely (21--40\% of the time) & 16 & 8\% \\
+		Very rarely (1--20\% of the time) & 15 & 7.5\% \\
+		Never (0\% of the time) & 138 & 69\% \\
+		\midrule
+		Total & 200 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We asked the answerers a follow-up question of how frequently they checked for a
+conflict between software license of the code snippets they copied to their
+answers and Stack Overflow's CC BY-SA 3.0. As shown in
+\Cref{tab:survey_license_check}, approximately 69\% of answerers did not perform
+the checking. Nonetheless, they are about 10.5\% of the answerers who very
+frequently or frequently checks for licensing conflicts when they copy code
+snippets to Stack Overflow.
+
+\textbf{To answer RQ 5.2, 124 answerers out of 200 (62\%) are aware of Stack Overflow's
+CC BY-SA 3.0 license applied to code snippets in questions and answers. However,
+only 3 answerers explicitly include software license in their answers. Some 
+answerers choose to include the license in their profile page instead. 69\% of the
+answerers never check for licensing conflicts between their copied code snippets
+and Stack Overflow's CC BY-SA 3.0.}
+
+Similar to outdated code, the responses from the answerers support our findings
+of licensing conflicts in online code clones and possibly explain why most of
+the clones copied from open source projects and external sources do not include
+their original software license.
+
+\subsubsection{Open Comments} We also invited the participants to give a
+free-form comment regarding their concerns of answering Stack Overflow with code
+snippets. Besides the one we present earlier in the introduction, these are
+interesting comments we received.
+
+\begin{enumerate}
+	\item \textit{``When I copy code it's usually short enough to be considered "fair
+		use" but I am not a lawyer or copyright expert so some guidance from SO would be
+		helpful. I'd also like the ability to flag/review questions that violate these
+		guidelines.''}
+	\item \textit{``My only concern, albeit minor, is that I know people blindly copy
+		my code without even understanding what the code does.''}
+	\item \textit{``The main problem for me/us is outdated code, esp. as old answers
+		have high google rank so that is what people see first, then try and fail. Thats
+		why we're moving more and more of those examples to knowledge base and docs and
+		rather link to those.''}
+	\item \textit{``Lot of the answers are from hobbyist so the quality is poor.
+		Usually they are hacks or workarounds (even MY best answer on SO is a
+		workaround).''}
+\end{enumerate}
+
+\subsection{Overall Discussion} %What can we learn for the results? For example,
+% if a developer explicitly reports in his/her code that the snippet was copied
+% from stackoverfow, are there some benefits? We could notify - for instance -
+% the developer when some new issues related to the snippet are posted on
+% stackoverflow? Or could we force people posting code on SO to explicitly
+% report licensing information? Or, could we implement an intelligent IDE that
+% when pasting code from external resource checks for licensing violation? These
+% of course are only some (crazy?) ideas that could be developed on the top of
+% the results we have achieved with this study...
+
+%We discovered two issues regarding code snippets on Stack Overflow in this
+% study: (1)  outdated online clones on Stack Overflow and (2) missing or
+% incompatible license in Stack Overflow snippets.
+%that there is a considerable amount of cloned code between Stack Overflow that
+% are cloned from 111 projects in the Qualitas corpus. 64 clone pairs are
+% outdated and 358 snippets have incompatible software licenses to their
+% originals.
+Our study discovers links from code in open source projects to code snippets on
+Stack Overflow using clone detection techniques. These links enable us to
+discover toxic code snippets with outdated code or licensing problems. 
+The links can be exploited further to mitigate the problems of reusing outdated online clones and
+incompatible license on Stack Overflow code snippets. We propose the following
+actionable items:
+
 \begin{itemize} 
-	\item \textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution when source code snippets have been copied ``from'' licensed software projects to Stack Overflow.
-Moreover, an IDE plug-in that can automatically detect pasted source code and follow the link to Stack Overflow and then to the original open source projects, could also prevent the issue of license violation.
-	\item \textbf{Detective measure:} A system to detect outdated source code
-	snippets on Stack Overflow is needed. The system can leverage the
-	online clone detection techniques in this study to periodically check
-	if the cloned snippets are still up-to-date with their
-	originals. %Moreover, Stack Overflow posters have to provide the information of the project including the original file name and its online repository (if exists).
-	With such a system, the poster can be notified when the code has been
-	updated in the original project so that he/she can update their code
-	on Stack Overflow accordingly. On the other hand, with a crowdsourcing
-	solution using an IDE plug-in, developers can also report the
-	corrected version of outdated code back to the original Stack Overflow
-	threads when they reuse outdated code and make corrections to them.
+	\item \textbf{Preventive measure:} We
+	encourage Stack Overflow to enforce attribution when source code snippets have
+	been copied ``from'' licensed software projects to Stack Overflow. Moreover, an
+	IDE plug-in that can automatically detect pasted source code and follow the link
+	to Stack Overflow and then to the original open source projects, could also
+	prevent the issue of license violation. 
+	\item \textbf{Detective measure:} A
+	system to detect outdated source code snippets on Stack Overflow is needed. The
+	system can leverage the online clone detection techniques in this study to
+	periodically check if the cloned snippets are still up-to-date with their
+	originals. %Moreover, Stack Overflow posters have to provide the information of
+	% the project including the original file name and its online repository (if
+	% exists).
+	With such a system, the poster can be notified when the code has been updated
+	in the original project so that he/she can update their code on Stack Overflow
+	accordingly. On the other hand, with a crowdsourcing solution using an IDE
+	plug-in, developers can also report the corrected version of outdated code back
+	to the original Stack Overflow threads when they reuse outdated code and make
+	corrections to them. 
 \end{itemize}
-The implementation and the evaluation of the above actionable items is part of the agenda of our future work.
+
+The implementation and the evaluation of the
+above actionable items is part of the agenda of our future work.
 
@@
 \textbf{Internal validity:} 
-%
-We could not verify all the 315,786,118 clone pairs reported by the
-clone detection tools in this study.  Nevertheless, we applied
-different mechanisms to ensure the validity to the subset of clone
+We applied
+different mechanisms to ensure the validity of the clone
 pairs we classified.  First, we used two widely-used
-clone detection tools, Simian and NiCad.  We tried three other
+clone detection tools, Simian and SourcererCC.  We tried five other
 clone detectors but could not add them to the study due to their
 scalability issues and susceptibility to incomplete code snippets.
-We mitigated the problem of clone
-detector's parameter sensitivity by adding another established
-configuration from the EvaClone study~\cite{Wang2013}. 
-Second, we adopted Bellon's agreement metric~\cite{Bellon2007}
-to prioritise and filters clone pairs for the manual
-classification. The agreed clone pairs that passed \textit{good}- and
-\textit{ok}- criteria had a higher chance to be true positive. 
+We adopted Bellon's agreement metric~\cite{Bellon2007}
+to merge clone pairs for the manual
+classification and avoid double counting of the same clone pairs. 
 Nevertheless, we might still suffers from false negatives, i.e.~online 
 code clones that are not reported by the tools or are filtered 
-out by the automatic classifier before the manual investigation.
+out by the size (less than 10 lines) within the clone detection process.
 % We also
@@
 
-Our seven patterns of online code cloning may not cover all possible
-online cloning patterns. However, instead of defining the patterns
-beforehand, we resorted to extract them from the data sets. We derived
-them from a manual investigation of 679 online clone pairs and adopted
-one pattern from the study by Kapser et al.~\cite{Kapser2003}.
-
-The 3,636 clone pairs classified by the first author are
-subject to manual judgement and human errors.  Although we tried
-our best to be careful on searching for evidence and classifying the
-clones, some errors may still exist. We mitigated this problem by
-having the second author to validate the classifications with a random
-sampling. 
-% The 64 classification conflicts were discussed and
-% resolved.  
-The third author made a final judgement when no consensus
-could be found by the two authors. This validation process
-can be even improved by employing an external investigator. 
-%In addition, we are aware of voting mechanism
-%in Stack Overflow and plan to incorporate highest-vote answers in the future work.
+Our seven patterns of online code cloning may not cover all possible online
+cloning patterns. However, instead of defining the patterns beforehand, we
+resorted to extract them from the data sets. We derived them from a manual
+investigation of 679 online clone pairs and adopted one pattern from the study
+by Kapser et al.~\cite{Kapser2003}.
+
+The 2,302 clone pairs classified by the first and the third author are subject
+to manual judgement and human errors.  Although we tried our best to be careful
+on searching for evidence and classifying the clones, some errors may still
+exist. We mitigated this problem by having two investigators to cross check the
+classifications and found 145 cases that lead to better classification results.
+This validation process can be even improved by employing an external
+investigator.
+
+In addition, we are aware of voting mechanism in Stack Overflow and plan to
+incorporate highest-vote answers in the future work.
 
@@
 We selected Stack Overflow because it is one of the most popular
-programming Q\&A websites available with approximately 6.8 million
+programming Q\&A websites available with approximately 7.6 million
 users. There are a large number of code snippets reused from the
@@
 % are much harder to detect. 
-We classified 32,533 clone pairs using seven patterns of online code
-cloning.  After automatically removing boiler-plate clones, we
-manually investigated 3,636 clone pairs. In the 1,216 manually
-confirmed clone pairs, we discovered 112 clone pairs that have been
-copied, with evidence, from Qualitas projects to Stack Overflow, 197
+We classified 2,302 clone pairs using seven patterns of online code
+cloning. We discovered 154 clone pairs that have been
+copied, with evidence, from Qualitas projects to Stack Overflow, 111
 clone pairs that have been copied from external sources besides
-Qualitas to Stack Overflow, and 359 clone pairs that are highly
+Qualitas to Stack Overflow, and 65 clone pairs that are highly
 similar but without evidence of copying.
@@
 aspects: outdated code and licensing violation. The investigation of
-the 112 clone pairs copied, with evidence, from Qualitas to Stack
-Overflow reveals that 64 of them are outdated.  Moreover, we found 358
+the 154 clone pairs copied, with evidence, from Qualitas to Stack
+Overflow reveals that 101 of them are outdated.  Moreover, we found 214
 code snippets on Stack Overflow that violate the license of their
@@
 
-This study is among, if not the first, to address the important issues
-of outdated and license-violating online code clones on programming
-Q\&A websites using a hybrid methodology of automatic code clone
+The online survey of 201 high-reputation Stack Overflow developers (i.e.~answerers)
+show that although the developers are aware of outdated code in their answers,
+19.8\% of them rarely or never fix the outdated code. In addition, 62\% of the participants
+are aware of Stack Overflow CC BY-SA 3.0 license applied to code snippets on the website.
+Only 3 answerers include the original license in their answers. 69\% of the answerers
+never check for licensing conflicts between the original code and CC BY-SA 3.0 
+enforced by Stack Overflow.
+
+This study is among, if not the first, to address the important issues of toxic
+code snippets, including outdated and license-violating online code clones, on
+programming Q\&A websites using a hybrid methodology of automatic code clone
 detection and a manual clone investigation.
@@
 
-The authors would like to thank...
+The authors would like to thank Prof.~Cristina Lopes and Di Yang
+from University of California, Irvine
+for their help in running SourcererCC clone detector and implementing
+a custom tokeniser for Stack Overflow snippets.
 

### 2017-10-15 cloverflow-tse/cloverflow.tex
Added median SLOC of SO snippet.
Revised through out the whole paper.

@@
 % The paper headers
-\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, August~2017}%
+\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, Month~2017}%
 {Ragkhitwetsagul \MakeLowercase{\textit{et al.}}: Outdated and License-Violating Code on Stack Overflow}
@@
 
-The findings from our online survey of Stack Overflow answerers show that code
-reusing activity occurs on Stack Overflow, just like in software. Stack Overflow
-answerers occasionally clone code from other locations, such as their personal
-projects, company projects, and open source projects, to Stack Overflow answers
-as a solution or to complement their answer~\FIXME{put a precise number here}.
-One participants says:
-
-\begin{quote}\textit{``The real issue is less about the amount the code snippets
+Our survey of Stack Overflow answerers shows that online code cloning occurs on
+Stack Overflow. Stack Overflow answerers frequently
+clone code from other locations, such as their personal projects, company
+projects, and open source projects, to Stack Overflow answers as a solution or
+to complement their answer. The code cloning activity on Stack Overflow
+is obviously beneficial considered the popularity of Stack Overflow and its
+influence on software development~\FIXME{find citations}. On the other hand,
+there is also a downside caused by low quality, defective, and harmful code
+snippets that are reused without an awareness by millions of users.
+
+One participants in our survey expresses his/her concerns about this:
+
+\begin{quote}
+	\textit{``The real issue is less about the amount the code snippets
 	on SO than it is about the staggeringly high number of software
@@
 	(\url{https://news.ycombinator.com/item?id=14846506}). They're also full of
-		toxic code snippets.''}\end{quote}
-
-With the same analogy, in this study we are interested in mining Stack Overflow
-posts, detecting online code clones, and revealing \textbf{toxic code snippets},
-which means code snippets that are harmful for reuse.
-Stack Overflow snippets can become toxic because they are outdated and violating
-their original software license. Outdated code snippets can be harmful since
-they may contain defects. Moreover, licensed code snippets that are cloned from
-open source software projects to Stack Overflow without their respective license
-can lead to legal issues if being reused.
+	toxic code snippets.''}
+\end{quote}
+
+Using the same analogy, in this study, we are interested in mining Stack
+Overflow posts, detecting online code clones, and analysing the clones to reveal
+``toxic code snippets''.
+
+Toxic code snippets mean code snippets that are harmful for reuse and, in
+several cases, are caused by online code cloning. Stack Overflow code snippets
+cloned from open source software or online sources can become toxic when they
+are (1) outdated or (2) violating their original software license. Outdated code
+can be harmful since they are not up-to-date with their originals and may
+contain defects. Code snippets from open source projects usually fall under a
+specific software license , e.g.~GNU General Public License (GPL). If they are
+cloned to Stack Overflow answers without the license and flow to other projects
+with conflicting license, legal issues may occur.
 
@@
 	\end{lstlisting}\vspace{-2ex}
-	\caption{A motivating example of the two code fragments of
+	\caption{An example of the two code fragments of
 		{\small\texttt{WritableComparator.java}}. The one from the
@@
 		its latest version in the \textsf{hadoop} code base
-		(right).}
+		(right). Its Apache v.2.0 license is also missing.}
 	\label{fig:before-after}
@@
 
-We would like to motivate the readers to the problem of toxic code snippets
-on Stack Overflow by giving two examples.
-
-The first motivating example of outdated online code clones can be found in an
+We would like to motivate the readers by giving two examples of toxic
+cod snippets.
+The first example is outdated and license-violating online code clones in an
 answer to a Stack Overflow question regarding how to implement
@@
 {\small{\verb|buffer|}} variable and avoid excess heap usage
-(HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
+(issue no.~HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
 While this change has already been introduced into the
@@
 %to reuse outdated code. 
-In addition, although the original code snippet of
-WritableComparator.java in Hadoop is subject to Apache license version 2.0, the
-cloned code on Stack Overflow contains only a {\small{\texttt{compare}}}
-method and misses its license statement on top of the file. There are two
-potential issues for this. First, the code snippet may look like it is under
-Stack Overflow's CC BY-SA 3.0 instead of its original Apache license. Second, if
-the code snippet is copied and incorporated into another software project with
-conflicting license, a legal issue may arise.
+In addition, the original code snippet of
+{\small\texttt{WritableComparator}} class in Hadoop is distributed with Apache license
+version 2.0 while its cloned instance on Stack Overflow contains only the
+{\small{\texttt{compare}}} method and ignores its license statement on top of the
+file. There are two potential issues for this. First, the code snippet may appear to be 
+under Stack Overflow's CC BY-SA 3.0 instead of its original Apache
+license. Second, if the code snippet is copied and incorporated into another
+software project with a conflicting license, a legal issue may arise.
 
@@
 	\end{lstlisting}\vspace{-2ex}
-	\caption{A motivating example of the two code fragments of
+	\caption{An example of the two code fragments of
 		{\small\texttt{StringUtils.java}}. The one from the
@@
 		its latest version in the \textsf{hadoop} code base
-		(right). The outdated code has race conditions.}
+		(right). The toxic code snippet is outdated code, has race conditions, and does not contain its
+		original Apache v.2.0 license.}
 	\label{fig:before-after_2}
@@
 rewritten on February 5, 2013 to solve an issue of a race condition
-(HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
-
-This two toxic code snippet has been posted on March 11, 2014 and April 9, 2009
-respectively. They have already been viewed 259 and 2,886 times as the time of
-writing this paper (October 3, 2017). Our calculation finds that there will be a
-new viewer of the first toxic snippet in approximately every 5 days while the
-second toxic snippet will be viewed almost every single day. Moreover, a
-quick web search shows that the same {\small{\texttt{humanReadableInt}}}
-method already reside in approximately 500 projects on GitHub. Considering the popularity of Stack
-Overflow, which has more than 50 million developers visiting each
-month\footnote{Data as of 21 August 2017 from: \url{https://stackoverflow.com}},
-one toxic code snippets on Stack Overflow can spread and grow to hundred or
-thousand copies within only a year or two.
+(issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
+The missing of Apache v.2.0 license also similarly occurs after posted on 
+Stack Overflow.
+
+The two toxic code snippet in our examples has been posted on March 11, 2014 and
+April 9, 2009 respectively. They have already been viewed 259 and 2,886 times as
+the time of writing this paper (October 3, 2017). Our calculation finds that
+there will be a new viewer of the first toxic snippet in approximately every 5
+days compared to almost every day for the second one. A quick web search shows
+that the defective {\small{\texttt{humanReadableInt}}} method in the second
+example already appears in approximately 500 projects on GitHub. Considering the
+popularity of Stack Overflow, which has more than 50 million developers visiting
+each month\footnote{Data as of 21 August 2017 from:
+	\url{https://stackoverflow.com}}, one toxic code snippets on Stack Overflow can
+spread and grow to hundred or thousand copies within only a year or two.
 
@@
 Overflow and the awareness of Stack Overflow developers in doing so. Finding the
-origins of code examples gives insights to the problems of toxic code snippets
-including outdated code and software licensing violations. It is probably more
+origins of code examples reveals the problem of toxic code snippets
+caused by outdated code and software licensing violations. It is probably more
 important than studying the effects of reusing Stack Overflow code snippets
-because it tackles the root cause of the problem. Moreover, this paper lays a
-foundation to possibility of having an automatic technique to detect and report
-such problems to developers in the future.
-
-This paper fills this gap and makes the following primary contributions:
+because it gives insights to the root cause of the problem and lays a
+foundation to an automatic technique to detect and report
+toxic code snippets on Stack Overflow to developers in the future.
+
+This paper makes the following primary contributions:
 
@@
 	\item \textbf{A manual study of online code clones:} We used
-	two clone detection tools to discover 315,786,118 similar code snippet pairs,
-	followed by a manual classification of 3,636 candidate clone pairs between
-	144,064 Java code snippets obtained from Stack Overflow's accepted answers and
+	two clone detection tools to discover 2,302 similar code snippet pairs between
+	72,365 Java code snippets obtained from Stack Overflow's accepted answers and
 	111 Java open source projects from the curated Qualitas
-	corpus~\cite{QualitasCorpus}.
-
-	\item \textbf{An investigation of outdated and
-		license-violating online clones on Stack Overflow:} Our study shows that from
-	the 3,636 online clones, at least 671 likely have been copied from open source
+	corpus~\cite{QualitasCorpus}. We manually
+	classified all of them.
+
+	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
+	the 2,302 online clones, at least 330 likely have been copied from open source
 	projects or external online sources to Stack Overflow, potentially violating
-	software licenses. For 112 of them, we found evidence that they have been copied
-	from a specific Qualitas project and that 64 of them are meanwhile outdated. %
+	software licenses. For 154 of them, we found evidence that they have been copied
+	from a specific Qualitas project and that 101 of them are meanwhile outdated. %
 	% and questionable for being reused.
 
-	\item \textbf{Awareness of Stack Overflow answerers to
-	toxic code snippets:} We performed an online survey and collected answers from
-	202 highly-ranked Stack Overflow developers. We found that there are~\FIXME{add
-	the number here}\% of code snippets cloned from open source projects to Stack
-	Overflow answers. While Stack Overflow answerers are aware of their outdated
-	code snippets, 19\% of the participants report that they rarely or never fix
-	the code. At least 98\% of the answerers never include software license in
-	their snippets and 69\% never check for licensing conflicts with Stack
-	Overflow's CC BY-SA 3.0 if they copy the code from other sources to Stack
-	Overflow answers.
+	\item \textbf{Awareness of Stack Overflow answerers to toxic code snippets:} We
+	performed an online survey and collected answers from 201 highly-ranked Stack
+	Overflow developers. We found that they cloned code snippets from open source
+	projects to Stack Overflow answers. While Stack Overflow answerers are aware of
+	their outdated code snippets, 19\% of the participants rarely
+	or never fix the code. 99\% of the answerers never include software
+	license in their snippets and 69\% never check for licensing conflicts between the
+	cloned code snippets and Stack Overflow's CC BY-SA 3.0.
 
@@
 		clone oracle:} The 2,302 manually investigated and validated online clone pairs
-	are available for download\footnote{https://to.be.disclosed.after.review} and
+	are available for download\footnote{\FIXME{ADD THIS URL}} and
 	can be used as a clone oracle. \end{enumerate}
@@
 	\item \textbf{RQ5 (Stack Overflow answerers' awareness): }
-		\subitem \textit{RQ5.1 Do Stack Overflow
+
+	\textit{1) Do Stack Overflow
 		answerers aware of the outdated code when
 		they answer a question on Stack Overflow?}
-		\subitem \textit{RQ5.2 Do Stack Overflow
+
+	\textit{2) Do Stack Overflow
 			answerers aware of licensing conflicts when
@@
 We designed our study in 6 phases as depicted in \Cref{fig:exp_framework} where
-we build different data sets to answer each of our four research
+we build different data sets to answer each of our five research
 questions.
@@
 accepted answers because they actually solved the problems in the questions.
-Moreover, they are always displayed just below the questions which makes them
+Moreover, they are usually displayed just below the questions which makes them
 more likely to be reused than other answers. Second, we were only interested in
@@
 snippets of at least ten lines are usually more interesting since most of
-boiler-plate code of \texttt{equal} or \texttt{hashCode} methods are removed.
+boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode} methods are removed.
 Each snippet was extracted from the dump and saved to a file. Moreover, we
@@
 	\url{https://github.com/AlDanial/cloc}} of Java source code. The median of the
-snippet size is 10.
+snippet size is 17.
 
@@
 		\midrule
-		Stack Overflow & 72,365 & 1,840,581 & ?? \\ 
+		Stack Overflow & 72,365 & 1,840,581 & 17 \\ 
 		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
@@
 could complete its execution but skipped 367 snippets due to malformed blocks in
-Stack Overflow data set. CCFinder reported 8 errors while processing the two data set. 
+Stack Overflow data sets. CCFinder reported 8 errors while processing the two data set. 
 Although Simian, SourcererCC, and DECKARD
@@
 corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Another benefit of SourcererCC is
-its indexing and search processing allows us to detect code clones between two
-systems.
+its flexibility of detecting code clones between two systems.
 
@@
 the tool provides an option to plug in a customised tokeniser, so we developed a
-special Java tokeniser with assistance from the tool's creator. The customised
+special Java tokeniser with assistance from the tool's creators. The customised
 tokeniser successfully processed all Stack Overflow snippets.
@@
 projects with minimal modifications. The two clone detectors complement each
-other by having Simian detecting literal copies of code snippets and SourcererCC
-detecting clones with added/deleted statments. We made sure that they 
+other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
+detecting clones with renaming and added/deleted statments (type-2, type-3). We made sure that they 
 detected only non-trivial clones by increasing the minimum clone size to ten
@@
 SourcererCC reports more clones due to its capability of detecting
-type-1 to type-3 clones while Simian only detects type-1 and type-2 clones.
+clones of type-1 to type-3 while Simian only detects type-1 clones.
 The average clone size reported by Simian is
@@
 
-\subsection{Phase 2: Clone Merging} As there are in total 315,786,118 clone
-pairs reported, it is infeasible for humans to manually validate them all.
-Instead of investigating a random sample, we adopted the idea of \textbf{clone
-	agreement} which has been used in clone research studies~\cite{Funaro2010,
-	Wang2013,cr2016ssbse} in situations where a clone oracle is missing or
-impossible to establish. Clone pairs agreed by multiple clone detection tools
-have a higher likelihood to be real clones~\cite{cr2016ssbse}. By using this
-agreement-based approach, we reduced the number of clone candidates for manual
-investigation and avoid a threat to internal validity of double counting the
-same clone pair twice by merging the ones agreed by the two tools. To find
-agreement between two clone pairs reported by two different tools, we used the
-clone pair matching metric proposed by Bellon et al.~\cite{Bellon2007}. Two
-clone pairs which have a large enough number of overlapping lines can be
-categorised as either a good-match or an ok-match pair (denoted as \textit{good}
-and \textit{ok} respectively) with a confidence value between 0 and 1. Although
-good-match has stronger agreement than ok-match, we choose ok-match as our clone
-merging method because it does not take clone size into account. Clone containment suits our
-online code clones from two tools, Simian (line-level) and SourcererCC
-(method-level), better because Simian's clone fragments  are sometimes smaller or bigger than
-a method while SourcererCC's clone fragments are always confined to a method boundary.
+\subsection{Phase 2: Clone Merging} Clones from the two detectors can be
+duplicated. To avoid double-counting of the same clone pair, we adopted the idea
+of \textbf{clone agreement} which has been used in clone research
+studies~\cite{Funaro2010, Wang2013,cr2016ssbse} to merge clones from two data
+sets. Clone pairs agreed by both clone detection tools have a high
+likelihood to be duplicate and must be merged. 
+%By using this agreement-based
+%approach, we reduced the number of clone candidates for manual investigation and
+%avoid a threat to internal validity of double counting the same clone pair twice
+%by merging the ones agreed by the two tools. 
+To find agreement between two clone
+pairs reported by two different tools, we used the clone pair matching metric
+proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large
+enough number of overlapping lines can be categorised as either a good-match or
+an ok-match pair with a
+confidence value between 0 and 1. Although good-match has stronger agreement
+than ok-match, we choose the ok-match criterion as our clone merging method
+because it depends on clone containment and does
+not take clone size into account. Clone containment suits our online code clones
+from two tools, Simian (line-level) and SourcererCC (method-level), better
+because Simian's clone fragments can be smaller or bigger than a method
+while SourcererCC's clone fragments are always confined to a method boundary.
 
@@
 
-Using the ok-match criteria with a predefined threshold \textit{t} of 0.7
+Using the ok-match criterion with a predefined threshold \textit{t} of 0.7
 similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
@@
 \subsection{Phase 3-4: Validation and Classification}
-We used the 2,302 merged clone pairsfor
+We used the 2,302 merged clone pairs for
 manual validation and classification.
@@
 clone detection research for three years, and the third author, who is a
-software engineering research student who is familiar with code clones, took the
+software engineering research student and familiar with code clones, took the
 role of the investigators performing a manual validation and classification of
@@
 conflicts were discussed and resolved. There are 145 conflicts caused by
-one investigator being more careful than the other and finding evidence of 
-copying while the other could not. They result in a better classification
-to a stronger one, i.e.~from UD to QS or EX. 
+one investigator being more careful than the other and able to find evidence of 
+copying while the other could not. They result in a better classification,
+ i.e.~from UD to QS or EX. 
 %There were three conflicts where the two
@@
 % Thus, 
-Kapser's patterns are too broad for our study and a
-more suitable and fine-grained classification scheme is needed. After
-a preliminary study, we adopted one of Kapser's cloning patterns,
-\emph{boiler-plate code}, and defined
-six new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP,
-IN, and AC as presented in \Cref{tab:classification_scheme}. Pattern
-QS (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones
-that have evidence of being copied from a Qualitas project to Stack
-Overflow. The evidence of copying can be found in comments in the
-Qualitas source code or in the Stack Overflow post's contents. Pattern
-SQ (\textbf{S}tack Overflow to \textbf{Q}ualitas) is cloning, with
-evidence, in the opposite direction from Stack Overflow to a Qualitas
-project. Pattern EX (\textbf{Ex}ternal Sources) is cloning that has
-evidence of copying from a single or multiple external sources to
-Stack Overflow and to a Qualitas project.  Pattern UD
-(\textbf{U}nknown \textbf{D}irection) is cloning that creates
-identical or highly similar clones between Qualitas and Stack Overflow
-but where we could not find any attribution of copying.
-Pattern BP (\textbf{B}oiler-\textbf{P}late) represents clones
-containing boiler-plate (according to our definition of boiler-plate 
-code in \Cref{tab:boiler-plate_code} which is more specific to Java
-than the definition in Kapser's~\cite{Kapser2008}).
+Kapser's patterns are too broad for our study and a more suitable and
+fine-grained classification scheme is needed. After a preliminary study, we
+adopted one of Kapser's cloning patterns, \emph{boiler-plate code}, and defined
+six new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP, IN, and
+AC as presented in \Cref{tab:classification_scheme}. Pattern QS
+(\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have
+evidence of being copied from a Qualitas project to Stack Overflow. The evidence
+of copying can be found in comments in the Qualitas source code or in the Stack
+Overflow post's contents. Pattern SQ (\textbf{S}tack Overflow to
+\textbf{Q}ualitas) is cloning, with evidence, in the opposite direction from
+Stack Overflow to a Qualitas project. Pattern EX (\textbf{Ex}ternal Sources) is
+cloning that has evidence of copying from a single or multiple external sources
+to Stack Overflow, and possibly also to a Qualitas project.  Pattern UD
+(\textbf{U}nknown \textbf{D}irection) is cloning that creates identical or
+highly similar clones between Qualitas and Stack Overflow but where we could not
+find any attribution of copying. Pattern BP (\textbf{B}oiler-\textbf{P}late)
+represents clones containing boiler-plate. We define three cases of boiler-plate
+code and use in our classification as shown in \Cref{tab:boiler-plate_code}. Our
+definition is specific to Java and more suitable to our study than the general
+definition in Kapser's~\cite{Kapser2008}.
 %of {\small\verb|equals()|} methods,
@@
 of code and the timestamps. We also collected IDs of issue tracking information
-if the code change is linked to an automatic issue tracking system, such as Jira.
+if the code change is linked to an automatic issue tracking system, such as Jira
+or BugZilla.
 
@@
 {\small\texttt{SeeFile}} or {\small\texttt{Unknown}}, we looked at them manually
-to see if any license can be found.
+to see if any license can be found. For EX clone pairs that are cloned from
+external sources such as JDK or websites. We manually searched for the license
+of the original code.
 
 \subsection{Stack Overflow Developers' Survey} We support our findings of
-outdated and license-violating code snippets on Stack Overflow by asking Stack
+toxic code snippets on Stack Overflow by asking Stack
 Overflow users to take an online survey. The survey was used for assessing awareness of
-the developers on the two issues of outdated code and licensing-violating code
+the developers on the two issues of outdated code and license-violating code
 snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
@@
 
-We selected the participants for our survey based on the users' reputations. On
-Stack Overflow, a user's reputation reflects how much the community trust the
-user. A user earns reputations when he or she receives up votes for good
-questions and useful answers. Accepted answers receive more reputation score
-than questions, and regular answers\footnote{Stack Overflow
+We selected the participants for our survey based on their Stack Overflow
+reputation. On Stack Overflow, a user's reputation reflects how much the
+community trust them. A user earns reputations when he or she receives up votes
+for good questions and useful answers. Accepted answers receive more reputation
+score than questions, and regular answers\footnote{Stack Overflow
 Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
 Overflow reputation is an indicator of user's skills and their involvement in
-asking and answering questions on the site. We call Stack Overflow users who
-have high reputations ``Stack Overflow answerers.''
-
-The participants were invited to take the survey via email addresses on their
-public Stack Overflow and GitHub profiles. We selected the answerers who had highly
-ranked all-time reputations\footnote{Stack Overflow Users (data as of 25 July
-	2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}.
-They had a reputation from 963,731 (the
-highest) to 6,999 which
-we sent out 607 emails (excluding undelivered ones) respectively. The
-survey was open for participation for two months, from 25 July to 25 September
-2017, before we collected and analysed the responses.
+asking and answering questions on the site. In this study, we call Stack
+Overflow users who have high reputation ``Stack Overflow answerers.''
+
+The participants were invited to take the survey via email addresses available
+on their public Stack Overflow and GitHub profiles. We selected the answerers
+based on the all-time reputation ranking\footnote{Stack Overflow Users (data as
+of 25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}. The
+invited participants had a reputation from 963,731 (the highest) to 6,999 which
+we sent out 607 emails (excluding undelivered ones) respectively. The survey was
+open for participation for two months, from 25 July to 25 September 2017, before
+we collected and analysed the responses.
 
@@
 
-We followed the 6 phases in the experimental framework (\Cref{fig:exp_framework})
-to answer our four research questions. 
-To answer RQ1, we rely on the number of manually validated true positive online clone pairs
-in phase 3. We use the results of the manual classification by the
-seven patterns of online code cloning to answer RQ2 (phase 4). 
-For RQ3, we looked at the true positive clone pairs that are classified 
-as clones from Qualitas to Stack Overflow and
-checked if they have been changed after cloning (phase 5). Similarly, for RQ4, we looked at the license of each clone in the pattern 
-QS, EX, UD and checked for a possibility of licensing violation (phase 6).
+We followed the 6 phases in the experimental framework
+(\Cref{fig:exp_framework}) to answer our four research questions. To answer RQ1,
+we rely on the number of manually validated true positive online clone pairs in
+phase 3. We use the results of the manual classification by the seven patterns
+of online code cloning to answer RQ2 (phase 4). For RQ3, we looked at the true
+positive clone pairs that are classified as clones from Qualitas to Stack
+Overflow and checked if they have been changed after cloning (phase 5).
+Similarly, for RQ4, we looked at the license of each clone in the pattern QS,
+EX, UD and checked for a possibility of licensing violation (phase 6). We use
+the online survey to answer RQ5.
 
@@
 The statistics on clones obtained from the merged clone data set are
-presented in \Cref{tab:snippets}. Simian and SourcererCC
+presented in~\Cref{tab:snippets}. Simian and SourcererCC
 reported clones in 460 snippets, approximately 0.6\% of the
@@
 average ratio of cloned code is 53.10\%.
-% A quick manual check of Simian's clone report revealed that there
-% were 11 problematic snippets. These 11 snippets triggered Simian to
-% generate large clone clusters containing a huge number of false
-% clones from array initialisation. Hence, their clones were removed
-% from further analyses.
-
-% \FIXME{Do you think we should report at this level or in more details 
-% 	into $S_D$--$N_D$, $S_D$--$N_E$, $S_E$--$N_D$, $S_E$--$N_E$??}
-% I don't think there is a need.
 
@@
 However, we observed that, in some cases, a cloned code snippet on Stack
-Overflow matched with more than one code snippet in Qualitas projects. This is
-because there were also code cloning inside Qualitas projects themselves. To
-avoid double counting of such online clones, we consolidated clone pairs having
-the same Stack Overflow snippet, starting line, and ending line into a single
-clone pair. We finally obtained 154 QS pairs having unique Stack Overflow code
-snippets and associated with 23 Qualitas projects listed in
-\Cref{tab:qs_qualitas_projects}. The most cloned projects are \textsf{hibernate}
-and \textsf{spring} with 24 clone pairs, followed by \textsf{eclipse} (21
-pairs), \textsf{jung2} (19 pairs), \textsf{spring} (17 pairs), and
-\textsf{jfreechart} (13 pairs). The clones are used as examples and are very
-similar to their original Qualitas code with limited modifications. Most of them
-have a statement in the Stack Overflow post saying that the code is ``copied'',
-``borrowed'' or ``modified'' from a specific file or class in a Qualitas
-project. For example, according to the motivating example in
-\Cref{fig:before-after}, we found evidence in the Stack Overflow Post 22315734
-saying that \textit{``Actually, you can learn how to compare in Hadoop from
-	WritableComparator. Here is an examle that borrows some ideas from it.''}
+Overflow matched with more than one code snippet in Qualitas projects because of
+code cloning inside Qualitas projects themselves. To avoid double counting of
+such online clones, we consolidated multiple clone pairs having the same Stack
+Overflow snippet, starting line, and ending line into a single clone pair. We
+finally obtained 154 QS pairs having unique Stack Overflow code snippets and
+associated with 23 Qualitas projects listed in \Cref{tab:qs_qualitas_projects}.
+The most cloned projects are \textsf{hibernate} and \textsf{spring} with 24
+clone pairs, followed by \textsf{eclipse} (21 pairs), \textsf{jung2} (19 pairs),
+\textsf{spring} (17 pairs), and \textsf{jfreechart} (13 pairs). The clones are
+used as examples and are very similar to their original Qualitas code with
+limited modifications. Most of them have a statement in the Stack Overflow post
+saying that the code is ``copied'', ``borrowed'' or ``modified'' from a specific
+file or class in a Qualitas project. For example, according to the motivating
+example in \Cref{fig:before-after}, we found evidence in the Stack Overflow Post
+22315734 saying that \textit{``Actually, you can learn how to compare in Hadoop
+from WritableComparator. Here is an examle that borrows some ideas from it.''}
 
@@
 {\small\texttt{POIUtils.java}} in \textsf{jstock} project. The user
-\textsf{yccheok} who asked the question in Stack Overflow is the author of
+ who asked the question on Stack Overflow is an author of
 \textsf{jstock}. The question is about determining the right method to call
@@
 {\small\texttt{findMethodToInvoke}} method depicted in \Cref{fig:jstock_code} in Stack
-Overflow is identical to the code in \textsf{jstock} including comments, it is almost certain that
+Overflow is very similar to the code in \textsf{jstock} including comments, it is almost certain that
 the two code snippets form a clone pair. In addition, Stack Overflow answer was
@@
 	\end{lstlisting}\vspace{-2ex}
-	\caption{The {\small\texttt{findMethodToInvoke}} that is found to be copied from Stack Overflow post 698283 to {\small\texttt{POIUtils}} class.}
+	\caption{The {\small\texttt{findMethodToInvoke}} that is found to be copied from Stack Overflow post 698283 to {\small\texttt{POIUtils}} class in \textsf{jstock}.}
 	\label{fig:jstock_code}
@@
 pairs. Fifty pairs provide evidences of copying to both Stack
-Overflow and Qualitas while the rest (61) only provides evidence of copying to
-Stack Overflow. All of them contain statements giving an external source of the
+Overflow and Qualitas while the rest (61) provides evidence of copying to
+Stack Overflow only. All of them contain statements giving an external source of the
 cloned code which fall into six groups as displayed in \Cref{fig:ex_sources}. 
@@
 	noise} is copied from NYU Media Research Lab
-(\url{http://mrl.nyu.edu/~perlin/noise/}) website and is used on Stack Overflow
-and in the \textsf{aoi} project with attribution. There are other EX pairs which
+(\url{http://mrl.nyu.edu/~perlin/noise/}) website and is used in both Stack Overflow
+answer and the \textsf{aoi} project with attribution. There are other EX pairs which
 are copied from open source libraries or Java SDK such as \textsf{Mozilla
@@
 most cloned project is \textsf{eclipse} (8 pairs), followed by \textsf{jstock},
-a free stock market software, and \textsf{compiere}, a software and customer
+a free stock market software, and \textsf{compiere}, a customer
 relationship management (CRM) system, (5 pairs).
@@
 \textsf{hadoop}. Besides the two examples of outdated code in % \textsf{hadoop}'s
-{\small{\texttt{WritableComparator.java}}} and
-{\small{\texttt{StringUtils.java}}} from \textsf{hadoop} shown in
+{\small{\texttt{WritableComparator}}} and
+{\small{\texttt{StringUtils}}} class from \textsf{hadoop} shown in
 \Cref{fig:before-after} and \Cref{fig:before-after_2}, we also found a few
@@
 We analysed code modifications which made Stack Overflow code outdated by going
-though commits and git blame information. The summary of six code modification
-types found in the 101 outdated online clone pairs are displayed in
+though commits and git blame information. The of six code modification
+types found in the 101 outdated online clone pairs are summarised in
 \Cref{tab:mod_types} including statement addition, statement modification,
@@
 one clone pair at the same time but at a different location. The most often code
-changes found is statement modification (49 occurrences), followed by statement
-addition (29 occurrences), statement removal (18 occurrences), changing of
+changes found is statement modification (50 occurrences), followed by statement
+addition (28 occurrences), statement removal (18 occurrences), changing of
 method signature, i.e.~API change (16 occurrences), and method rewriting (15
@@
 along with the issue tracking number and the date of change. The complete set of
-101 outdated online clones can be found from the study website.
+101 outdated online clones can be found on the study website.
 
@@
 subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without
-awareness from developers. Moreover, an outdated code with a defect
-(e.g.~a race condition problem in \Cref{fig:before-after_2}) is harmful to be reused. Although Stack
-Overflow has a voting mechanism that may mitigate this issue, the accepted
-answer is still used by naive developers who copy and reuse the outdated code.
+awareness from developers. Moreover, an outdated code with a defect (e.g.~a race
+condition problem in \Cref{fig:before-after_2}) is clearly harmful to be reused.
+Although Stack Overflow has a voting mechanism that may mitigate this issue, the
+accepted answer is still used by naive developers who copy and reuse the
+outdated code.
 
 \textbf{For RQ3, our results show that 66\% (101) of QS clone pairs on Stack
-	Overflow are outdated. 127 pairs differ from their newest versions by
+	Overflow are outdated. 86 pairs differ from their newest versions by
 	modifications applied to variable names or method names, added or deleted
@@
 	\resizebox{\linewidth}{!}{
-		\begin{tabular}{lp{2.5cm}p{2.5cm}rrr}
+		\begin{tabular}{lp{2.3cm}p{2.3cm}rrr}
 			\toprule
@@
 			& No license & EPLv1 & 10 & & 6 \\
-			& No license & GPL/v2/2+/3+ & 8 & 48 & 7 \\ 
-			& No license & LesserGPL/v2.1+/3+ & 16 & & 9 \\ 			
+			& No license & GPLv2+/3+ & 8 & 48 & 7 \\ 
+			& No license & LesserGPLv2.1+/3+ & 16 & & 9 \\ 			
 			& No license & MPLv1.1 & & & 1 \\ 
@@
 In our study, we reveal another type of toxic code snippets which is software
-licensing issues caused by code cloned to Stack Overflow. We found evidence that
+licensing issues caused by code cloning to Stack Overflow. We found evidence that
 154 pieces of code have been copied from Qualitas projects to Stack Overflow as
@@
 posted on Stack Overflow. One QS clone pair posted by a JFreeChart developer
-changes its license from Lesser GPL v2.1+ to New BSD 3-clause. The JFreeChart
-developer may intentionally change the license to be more suitable for Stack
+changes its license from Lesser GPL v2.1+ to New BSD 3-clause. The
+developer may intentionally change the license to be more suitable to Stack
 Overflow since New BSD 3-clause license allows reuse without requiring the same
@@
 
-We asked the participants for the origins of code snippets in their answers. We
-provided six locations (allow multiple selection) including the answerer's
-personal projects, the answerer's company projects, open source projects,
-writing the code from scratch, copying and modifying the code from the question,
-and others (e.g.~code that are copied from other questions or answers on Stack
-Overflow) and asked them to rate how often they copied the code from these
-locations. The results are shown in \Cref{fig:survey_snippet_source}. Looking at
-Very Frequently section, we can see that the answerers mainly write new code
-from scratch (71) or modify from the code snippets in question for each answer
-(56), while fewer numbers are from other sources including their personal
-projects (42), their company projects (10), and open source projects (14).
-Although copying from open source projects is not the most popular choice, the answerers
+We asked the remaining 200 participants for the origins of code snippets in
+their answers. We provided six locations including the answerer's personal
+projects, the answerer's company projects, open source projects, writing the
+code from scratch, copying and modifying the code from the question, and others
+(e.g.~code that are copied from other questions or answers on Stack Overflow)
+and we asked them to rate how often they copied the code from these locations. The
+results are shown in \Cref{fig:survey_snippet_source}. Looking at Very
+Frequently section, we can see that the answerers mainly write new code from
+scratch (71) or modify from the code snippets in question for each answer (56),
+while fewer numbers are from other sources including their personal projects
+(42), their company projects (10), and open source projects (14). Although
+copying from open source projects is not the most popular choice, the answerers
 still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
-participants who frequently, occasionally, and rarely copied code snippets from open
-source projects.
+participants who frequently, occasionally, and rarely copied code snippets from
+open source projects.
 
@@
 	\centering
-	\caption{Awareness to outdated code snippets in answers}
+	\caption{Notifications of outdated code snippets in answers}
 	\label{tab:survey_code_snippet_outdated}
@@
 We then asked 131 participants to have been notified of their outdated code a
-follow-up questions ``how frequently did you fix your outdated code on Stack
-Overflow?''. The answers, depicted in
+follow-up questions \textit{``how frequently did you fix your outdated code on Stack
+Overflow?''}. The answers, depicted in
 \Cref{tab:survey_code_snippet_outdated_fix}, show that more than half of them
 (57.2\%) very frequently or frequently fix the outdated code snippets. However,
-there are 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
+there are totally 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
 their outdated code.
@@
 can be outdated. 51.5\% of the answerers were very rarely notified while 35.5\% never been notified of
-outdated code in the answers. 19.8\% of them rarely fix the outdated code or left them unfixed.}
+outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.}
 
 The responses from the answerers support our findings of outdated online code
-clones. In addition, this
-results only reflect experienced answerers who accumulate the reputation for a
+clones in RQ3. The low percentage of outdated code notifications
+reflect the experience of high reputation answerers who accumulate the reputation for a
 long time. Due to the voting mechanism of Stack Overflow, high reputation users
-usually provide quality answers and earn up votes from other users. They must be
-very careful when posting code snippets in the answer to avoid problems and, in
-the end, getting down votes. It is also interesting to compare the findings to
+usually provide high quality answers to earn up votes from other users. They are
+careful when posting code snippets in the answer to avoid problems and, vice versa, 
+getting down votes. It is also interesting to compare the findings to
 Stack Overflow answerers who are newer and have lower reputation. However, we
@@
 
-More than half of the 200 answerers who include code snippets in their answers,
-124 are aware that Stack Overflow apply Creative Commons Attribution-ShareAlike
-3.0 Unported (CC BY-SA 3.0) to content in the posts, including code snippets,
-while the rest (76) are not. Nevertheless, we found that almost all of them (197) do
-not include license statement in their code snippets (as presented in
-\Cref{tab:survey_license_include}) due to several reasons. First, some answerers chose
-to post only their own code or code that was adapted from the question, hence
-they are automatically subjected to CC BY-SA 3.0. Second, they copied code from
-company or open source projects that they knew were permitted to be publicly
-distributed. Third, some answerers believe that code snippets in their answers
-are too small to claim any intellectual property on them and fall under fair
-use~\cite{fairuse}.
+Among the 200 answerers who include code snippets in their answers, 124
+answerers are aware that Stack Overflow apply Creative Commons
+Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts,
+including code snippets, while the rest (76) are not. Nevertheless, as shown in
+\Cref{tab:survey_license_include}, almost all of them (197) reported that they
+did not include license statement in their code snippets due to several reasons.
+First, some answerers chose to post only their own code or code that was adapted
+from the question, hence they are automatically subjected to CC BY-SA 3.0.
+Second, they copied code from company or open source projects that they knew
+were permitted to be publicly distributed. Third, some answerers believe that
+code snippets in their answers are too small to claim any intellectual property
+on them and fall under fair use~\cite{fairuse}.
 
 While nobody explicitly includes a software license in their snippets,
-many users include a statement on their profile page that states all their
-answers are under a certain license. For example, a Stack Overflow includes 
+many users include a statement on their profile page that all their
+answers are under a certain license. For example, a Stack Overflow user includes 
 the following text in his/her profile page.
@@
 \Cref{tab:survey_license_check}, approximately 69\% of answerers did not perform
-the checking. Nonetheless, they are about 10.5\% of the answerers who very
+the checking. Nonetheless, there are about 10.5\% of the answerers who very
 frequently or frequently checks for licensing conflicts when they copy code
@@
 Similar to outdated code, the responses from the answerers support our findings
-of licensing conflicts in online code clones and possibly explain why most of
+of licensing conflicts in online code clones in RQ4 and possibly explain why most of
 the clones copied from open source projects and external sources do not include
@@
 	\item \textit{``When I copy code it's usually short enough to be considered "fair
-		use" but I am not a lawyer or copyright expert so some guidance from SO would be
+		use" but I am not a lawyer or copyright expert so some guidance from Stack Overflow would be
 		helpful. I'd also like the ability to flag/review questions that violate these
@@
 	\item \textit{``Lot of the answers are from hobbyist so the quality is poor.
-		Usually they are hacks or workarounds (even MY best answer on SO is a
+		Usually they are hacks or workarounds (even MY best answer on Stack Overflow is a
 		workaround).''}
@@
 
-In addition, we are aware of voting mechanism in Stack Overflow and plan to
-incorporate highest-vote answers in the future work.
+%In addition, we are aware of voting mechanism in Stack Overflow and plan to
+%incorporate highest-vote answers in the future work.
 

### 2017-10-16 cloverflow-tse/cloverflow.tex
Changes at the office.

--- 2017-10-12 cloverflow-tse/cloverflow.tex
@@
 
-		EX & Cloned from an external source \textit{X} (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q). \\
+		EX & Cloned from an external source \textit{X} (X $\rightarrow$ S). \\
 
@@
 
-\textbf{EX: External Sources.} We found 199 clone pairs with evidence of cloning
-from external sources to Stack Overflow. After getting rid of duplicated SO
-snippets due to multiple intra-clone instances in Qualitas, we obtained 111 EX
-pairs. Fifty pairs provide evidences of copying to both Stack
-Overflow and Qualitas while the rest (61) only provides evidence of copying to
-Stack Overflow. All of them contain statements giving an external source of the
-cloned code which fall into six groups as displayed in \Cref{fig:ex_sources}. 
-We discovered that 63 EX online clone pairs are copied from source code of classes or 
-methods in Java SDK, 18 pairs are from websites, 15 pairs are from open source systems,
-11 pairs are from Java official documentations from Sun Microsystems or Oracle,
-3 pairs are from books, and 1 pair is from a company project.
-For example, Stack Overflow Post
-9549009 contains a code comment saying \textit{``Copied shamelessly from
+\textbf{EX: External Sources.} We found 199 clone pairs from external sources to
+Stack Overflow. After consolidating duplicated SO snippets due to multiple
+intra-clone instances in Qualitas, we obtained 111 EX pairs. We found evidence
+of copying from an external source to Stack Overflow, but not in Qualitas, in 61 pairs. 
+A stronger evidence of copying from an external source to both Stack
+Overflow and Qualitas is available in the other 50 pairs. Each of them contains
+statement(s) pointing to the original external location of the cloned code. Our
+analysis shows that the external sources fall into six groups as displayed in
+\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
+from source code of Java SDK, 18 pairs from websites, 15 pairs from open
+source systems, 11 pairs from Java official documentations from Sun
+Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
+project. For example, Stack Overflow Post 9549009 contains a code comment saying
+\textit{``Copied shamelessly from
 	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
@@
 			\midrule
-			2513183 & 25-Mar-10 & eclipse & 4.3 & GenerateToStringAction.java & 113 & 166 & & Bug 439874 & \textit{S} & 17-Mar-15 \\
+			2513183 & 25-Mar-10 & eclipse & 4.3 & GenerateToStringAction.java & 113 & 166 & 25-Jun-13 & Bug 439874 & \textit{S} & 17-Mar-15 \\
 			22315734 & 11-Mar-14 & hadoop & 1.0.0 & WritableComparator.java & 44 & 54 & 25-Aug-11 & HADOOP-11323 & \textit{S} & 20-Nov-14 \\
 			23520731 & 7-May-14 & hibernate & 4.2.2 & SchemaUpdate.java & 115 & 168 & 22-May-13 & HHH-10458 & \textit{S} & 5-Feb-16 \\
-			18232672 & 14-Aug-13 & log4j & 1.2.16 & SMTPAppender.java & 207 & 228 & & Bug 44644 & \textit{R} & 18-Oct-08 \\ 
-			17697173 & 17-Jul-13 & lucene & 4.3.0 & SlowSynonymFilterFactory.java & 38 & 52 & & LUCENE-4095 & \textit{D} & 31-May-12 \\
+			18232672 & 14-Aug-13 & log4j & 1.2.16 & SMTPAppender.java & 207 & 228 & 31-Mar-10 & Bug 44644 & \textit{R} & 18-Oct-08 \\ 
+			17697173 & 17-Jul-13 & lucene & 4.3.0 & SlowSynonymFilterFactory.java & 38 & 52 & 6-Apr-13 & LUCENE-4095 & \textit{D} & 31-May-12 \\
 			21734562 & 12-Feb-14 & tomcat & 7.0.2  & FormAuthenticator.java & 51 & 61 & 4-Aug-10 & BZ 59823 &\textit{R} & 4-Aug-16 \\

### 2017-10-16 cloverflow-tse/cloverflow.tex

--- 2017-10-15 cloverflow-tse/cloverflow.tex
@@
 
-\textbf{EX: External Sources.} We found 199 clone pairs with evidence of cloning
-from external sources to Stack Overflow. After getting rid of duplicated SO
-snippets due to multiple intra-clone instances in Qualitas, we obtained 111 EX
-pairs. Fifty pairs provide evidences of copying to both Stack
-Overflow and Qualitas while the rest (61) provides evidence of copying to
-Stack Overflow only. All of them contain statements giving an external source of the
-cloned code which fall into six groups as displayed in \Cref{fig:ex_sources}. 
-We discovered that 63 EX online clone pairs are copied from source code of classes or 
-methods in Java SDK, 18 pairs are from websites, 15 pairs are from open source systems,
-11 pairs are from Java official documentations from Sun Microsystems or Oracle,
-3 pairs are from books, and 1 pair is from a company project.
-For example, Stack Overflow Post
-9549009 contains a code comment saying \textit{``Copied shamelessly from
+\textbf{EX: External Sources.} We found 199 clone pairs from external sources to
+Stack Overflow. After consolidating duplicated SO snippets due to multiple
+intra-clone instances in Qualitas, we obtained 111 EX pairs. We found evidence
+of copying from an external source to Stack Overflow, but not in Qualitas, in 61 pairs. 
+A stronger evidence of copying from an external source to both Stack
+Overflow and Qualitas is available in the other 50 pairs. Each of them contains
+statement(s) pointing to the original external location of the cloned code. Our
+analysis shows that the external sources fall into six groups as displayed in
+\Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
+from source code of Java SDK, 18 pairs from websites, 15 pairs from open
+source systems, 11 pairs from Java official documentations from Sun
+Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
+project. For example, Stack Overflow Post 9549009 contains a code comment saying
+\textit{``Copied shamelessly from
 	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an

### 2017-10-18 cloverflow-tse/cloverflow.tex
Incorporated Matheus's comments/changes.

@@
 systems. The process of posting and answering questions on Stack
-Overflow that involves reusing of source code, can be considered as
+Overflow that involves the reuse of source code can be considered
 code cloning.
@@
 
-We call code snippets that are copied from software systems to online
-Q\&A websites (such as Stack Overflow) and vice versa as ``online
-code clones''. There are two
-directions in creating online code clones: (1) code is cloned from a software
-project to a Q\&A website as an example; or (2) code is cloned from a
-Q\&A website to a software project to obtain a functionality, perform
-a particular task, or fixing a bug.
-% and (3) code is transferred from one software project to another via a Q\&A website; 
-Similar to classic clones, online code clones can lead to license
-violations, bug propagation, introduction of vulnerabilities, and
-re-use of outdated code. Unfortunately, online clones are 
-difficult to locate and fix since the search space in online code
-corpora is larger and no longer confined to a local repository.
+We call code snippets that are copied from software systems to online Q\&A
+websites (such as Stack Overflow) and vice versa as ``online code clones''.
+There are two directions in creating online code clones: (1) code is cloned from
+a software project to a Q\&A website as an example; or (2) code is cloned from a
+Q\&A website to a software project to obtain a functionality, perform a
+particular task, or fixing a bug. % and (3) code is transferred from one
+% software project to another via a Q\&A website;
+Similar to classic code clones, i.e.~clones between software systems, online code clones
+can lead to license violations, bug propagation, introduction of
+vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
+difficult to locate and fix since the search space in online code corpora is
+larger and no longer confined to a local repository.
 
@@
 clone code from other locations, such as their personal projects, company
-projects, and open source projects, to Stack Overflow answers as a solution or
-to complement their answer. The code cloning activity on Stack Overflow
+projects, and open source projects, to Stack Overflow as a solution or
+a complement to a solution. The code cloning activity on Stack Overflow
 is obviously beneficial considered the popularity of Stack Overflow and its
@@
 
-One participants in our survey expresses his/her concerns about this:
+One participant in our survey expresses his/her concerns about this:
 
@@
 specific software license , e.g.~GNU General Public License (GPL). If they are
-cloned to Stack Overflow answers without the license and flow to other projects
+cloned to Stack Overflow answers without the license, and then flow to other projects
 with conflicting license, legal issues may occur.
@@
 	\begin{lstlisting}
-/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2017-10-03) */
+/* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2014-11-21) */
 public int compare(byte[] b1,int s1,int l1, ...) {    public int compare(byte[] b1,int s1,int l1, ...) {
@@
 	\begin{lstlisting}
-/* Code in Stack Overflow post ID 801987 */             /* StringUtils.java (2017-10-03) */
+/* Code in Stack Overflow post ID 801987 */             /* StringUtils.java (2013-02-05) */
 public static String humanReadableInt(long number) {    public static String humanReadableInt(long number) {
@@
 \Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
-task from {\small{\texttt{StringUtils}}} class in \textsf{hadoop}. The code snippet on the
+task from the {\small{\texttt{StringUtils}}} class in \textsf{hadoop}. The code snippet on the
 right shows another version of the same method, but at this time extracted from
 the latest version of \textsf{hadoop}. We can see that
-they both are totally different. The {\small{\texttt{humanReadableInt}}} method is
+they are totally different. The {\small{\texttt{humanReadableInt}}} method is
 rewritten on February 5, 2013 to solve an issue of a race condition
 (issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
-The missing of Apache v.2.0 license also similarly occurs after posted on 
+The absence of Apache v.2.0 license also occurs after the snippet is posted on 
 Stack Overflow.
 
-The two toxic code snippet in our examples has been posted on March 11, 2014 and
+The two toxic code snippet in our examples have been posted on March 11, 2014 and
 April 9, 2009 respectively. They have already been viewed 259 and 2,886 times as
@@
 	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
-	the 2,302 online clones, at least 330 likely have been copied from open source
+	the 2,302 online clones, at least 330 have been copied from open source
 	projects or external online sources to Stack Overflow, potentially violating
 	software licenses. For 154 of them, we found evidence that they have been copied
-	from a specific Qualitas project and that 101 of them are meanwhile outdated. %
+	from a specific open source project and that 101 of them are outdated. %
 	% and questionable for being reused.
@@
 	performed an online survey and collected answers from 201 highly-ranked Stack
-	Overflow developers. We found that they cloned code snippets from open source
+	Overflow users. We found that they cloned code snippets from open source
 	projects to Stack Overflow answers. While Stack Overflow answerers are aware of
@@
 	them. 
-	\item \textbf{RQ4 (Software licensing violation): }\textit{Do
+	\item \textbf{RQ4 (Software licensing violation): }\textit{How often do
 		licensing conflicts occur between Stack Overflow clones and their
@@
 
-	\textit{1) Do Stack Overflow
+	\textit{1) How often are Stack Overflow
 		answerers aware of the outdated code when
@@
 
-	\textit{2) Do Stack Overflow
+	\textit{2) How often are Stack Overflow
 			answerers aware of licensing conflicts when
@@
 
-We rely on two source data sets in this study: Java code snippets in answers
+We rely on two source code data sets in this study: Java code snippets in answers
 on Stack Overflow and open source projects from the Qualitas corpus
-\cite{QualitasCorpus}.
+\cite{QualitasCorpus}, as detailed next.
 
@@
 % The archived dump has a size of 9 gigabytes.
-The data dump is in XML format containing information of posts (questions and
-answers) and we were interested in code snippets embedded in posts which were
+The data dump is in XML, and it contains information of posts (questions and
+answers). We were interested in code snippets embedded in posts which were
 located between {\small\texttt{<code>}...\texttt{</code>}} tags. A Stack
 Overflow thread contains a question and several answers. An answer can also be
-marked as \textbf{accepted answer} by the questioner if the solution fixes
+marked as an \textbf{accepted answer} by the questioner if the solution fixes
 his/her problem. We collected Java code snippets using two criteria. First, we
@@
 lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006},
-snippets of at least ten lines are usually more interesting since most of
-boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode} methods are removed.
+we empirically found that snippets of six lines contain a large number of
+boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode} methods,
+which are not interesting for the study.
 Each snippet was extracted from the dump and saved to a file. Moreover, we
@@
 72,365 Java code snippets containing 1,840,581 lines\footnote{Measured by cloc:
-	\url{https://github.com/AlDanial/cloc}} of Java source code. The median of the
-snippet size is 17.
+	\url{https://github.com/AlDanial/cloc}} of Java source code. The median size of the
+snippet is 17 lines.
 
@@
 There are a number of restrictions in terms of choosing the clone detection
-tools for this study. The main restriction is due to nature of code snippets
+tools for this study. The main restriction is due to the nature of code snippets
 posted on Stack Overflow, as most of them are incomplete Java classes or
@@
 (strings and numbers) which enables Simian to detect literal clones (type-1) and
-parameterised clones (type-2). \textbf{SourcererCC} is a token-based clone
+parameterised clones (type-2)~\cite{Bellon2007}. \textbf{SourcererCC} is a token-based clone
 detector which detects clones at either function- or block-level granularity. It
@@
 statements) and offer scalability against large code
-corpus~\cite{Sajnani2016,Saini2016,Yang2017}. Another benefit of SourcererCC is
-its flexibility of detecting code clones between two systems.
+corpus~\cite{Sajnani2016,Saini2016,Yang2017}.
 
@@
 tokeniser successfully processed all Stack Overflow snippets.
+
 Simian did not provide an option to detect cross-project clones. Hence the
@@
 Overflow or within Qualitas. 
+SourcererCC can detect cross-project clones between two systems so we did
+not filter the clones.
 
@@
 	\caption{Configurations of Simian and SourcererCC}
-	\label{t:param_tuning}
+	\label{tab:clone_config}
 %		\resizebox{\columnwidth}{!}{
@@
 SourcererCC based on their established default configurations chosen by the
-tools' creators. All variable renaming are disabled to decrease a number of
+tools' creators as depicted in \Cref{tab:clone_config}. All variable renaming are disabled to decrease the number of
 false positives since we aim for finding clones that are copied from open source
@@
 pairs reported by two different tools, we used the clone pair matching metric
-proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs which have a large
+proposed by Bellon et al.~\cite{Bellon2007}. Two clone pairs that have a large
 enough number of overlapping lines can be categorised as either a good-match or
@@
 \ We follow Bellon's original definitions of ok-match~\cite{Bellon2007}, which are based on how much two clone
-fragments \textit{CF} is contained in each other:
+fragments \textit{CF} are contained in each other:
 
@@
 associated with 23 Qualitas projects listed in \Cref{tab:qs_qualitas_projects}.
-The most cloned projects are \textsf{hibernate} and \textsf{spring} with 24
+The most cloned projects is \textsf{hibernate} with 24
 clone pairs, followed by \textsf{eclipse} (21 pairs), \textsf{jung2} (19 pairs),
@@
 Overflow is very similar to the code in \textsf{jstock} including comments, it is almost certain that
-the two code snippets form a clone pair. In addition, Stack Overflow answer was
+the two code snippets form a clone pair. In addition, the Stack Overflow answer was
 posted on March 30, 2009, while the code in {\small\texttt{POIUtils}} class in
@@
 
-We did not find other online clones besides the one mentioned above. 
 This very low number of SQ clone pair is very likely due to the age of the
@@
 \Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
-from source code of Java SDK, 18 pairs from websites, 15 pairs from open
-source systems, 11 pairs from Java official documentations from Sun
+from source code of Java SDK (e.g.~\textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
+18 pairs from websites, 15 pairs from open
+source systems not in Qualitas (e.g.~\textsf{Mozilla
+	Rhino}), 11 pairs from Java official documentations from Sun
 Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
@@
 	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
-open source project. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
+open source project not included in the Qualitas corpus. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
 class with a license statement showing that it is developed by a private company
@@
 Interestingly, the code is actually a copy from Sun Microsystems.
+
+These findings complement a study of clones between software
+projects~\cite{Svajlenko2014}. We found that cloning can also happen among
+different sources on the Internet just like software projects. The are 18 clone
+pairs that originated from programming websites including \url{www.java2s.com}
+and \url{exampledepot.com}. Moreover, there is one snippet which comes from a
+research website. We found that a snippet to generate graphical \textit{Perlin
+	noise} is copied from NYU Media Research Lab
+(\url{http://mrl.nyu.edu/~perlin/noise/}) website and is used in both Stack Overflow
+answer and the \textsf{aoi} project with attribution.
+
+%There are other EX pairs which
+%are copied from open source libraries or Java SDK such as \textsf{Mozilla
+%	Rhino}, \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}, and
+%the \textsf{bouncycastle} cryptography project.
+
+\textbf{UD: Unknown Direction.} We found 107 online clone pairs, reduced to 65
+pairs after consolidating the clones, with no evidence of cloning between Qualitas
+and Stack Overflow but with a high code similarity that suggests cloning. 
+The most cloned projects is \textsf{netbeans} with 11 clone pairs. Most of the
+clones are a large chunk of code handling GUI components. Although these GUI
+clones might be auto-generated by IDEs, we did not find any evidence. The second
+most cloned project is \textsf{eclipse} (8 pairs), followed by \textsf{jstock},
+a free stock market software, and \textsf{compiere}, a customer
+relationship management (CRM) system, (5 pairs).
+
+\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs
+found in this study. We observed 1,505 such clone pairs and 217 after
+consolidation. The BP clone pairs account for 65\% of all clone pairs we
+classified. The majority of them are {\small{\texttt{equals()}}} methods.
+
+\textbf{IN: Inheritance/interface.} There were 16 clone pairs, 9 pairs after
+consolidation, found to be similar because they implement the same interface or
+inheriting from the same class. An example is the two implementations of a
+custom data type which implements {\small\texttt{UserType}}. They share similar
+{\small\texttt{@Override}} methods of {\small\texttt{deepCopy}},
+{\small\texttt{isMutable}}, {\small\texttt{assemble}},
+{\small\texttt{disassemble}}, and {\small\texttt{replace}}.
+
+\textbf{AC: Accidental Clones.} There were 226 accidental clone
+pairs, 53 after consolidation. Mainly, they are false positive clones caused by code
+normalisation and false type-3 clones from SourcererCC. 
+Examples of the AC clone instances include {\small\texttt{finally}} or
+{\small\texttt{try-catch}} clauses that were accidentally the same due
+to their very small sizes, and similar {\small\texttt{switch-case}}
+statements.
+
+\textbf{To answer RQ2, we found 154 pairs with
+	strong evidences to be cloned from 23 Qualitas projects to Stack Overflow, 1 pair
+	was cloned from Stack Overflow to Qualitas, and
+	111 pairs were found to be cloned to Stack Overflow from external
+	sources. However, the largest amount of the clone pairs
+	between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
+	(217), followed by 65 clone pairs with no evidence that the code has actually been copied,
+	and 16 pairs of clones due to implementing the same interface or inheriting the same class.}
+
+\subsection{RQ3: Outdated Online Code Clones}
+\vspace{0.25cm}
+\textit{Are online code clones up-to-date compared to their counterparts in the original projects?}
+\vspace{0.25cm}
+
+\begin{figure*}
+	\centering
+	\includegraphics[width=0.8\linewidth]{outdated}
+	\caption{Outdated QS online clone pairs group by projects}
+	\label{fig:outdated}
+\end{figure*}
+
+We discovered 101 outdated online clone pairs out of 154 pairs. As shown in
+\Cref{fig:outdated}, \textsf{hibernate} has the highest number of 19 outdated
+pairs, followed by 14 from \textsf{spring}, 13 from \textsf{eclipse}, and 9 from
+\textsf{hadoop}. Besides the two examples of outdated code in % \textsf{hadoop}'s
+{\small{\texttt{WritableComparator}}} and
+{\small{\texttt{StringUtils}}} class from \textsf{hadoop} shown in
+\Cref{fig:before-after} and \Cref{fig:before-after_2}, we also found a few
+outdated code elements which contained a large amount of modifications. For
+example, the code snippet in Stack Overflow post 23520731 is a copy of
+{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code has been
+heavily modified on February 5, 2016.
+
+%\begin{figure}
+%	\centering
+%	\includegraphics[width=0.7\linewidth]{mod_types}
+%	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
+%	\label{fig:mod_types}
+%\end{figure}
+
+\begin{table}
+	\centering
+	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
+	\label{tab:mod_types}
+		\begin{tabular}{lr}
+			\toprule
+			Modification & Occurrences \\
+			\midrule
+			Statement modification & 50 \\
+			Statement addition & 28 \\
+			Statement removal & 18 \\
+			Method signature change & 16 \\
+			Method rewriting & 15 \\
+			File deletion & 15 \\
+			\bottomrule 
+		\end{tabular}
+\end{table}
+
+We analysed code modifications which made Stack Overflow code outdated by going
+though commits and git blame information. The six code modification
+types found in the 101 outdated online clone pairs are summarised in
+\Cref{tab:mod_types}. They include statement addition, statement modification,
+statement removal, method rewriting, API change (changing in method signature),
+and file deletion. We occasionally found multiple code modifications applied to
+one clone pair at the same time but at a different location. The most often code
+change found is statement modification (50 occurrences), followed by statement
+addition (28 occurrences), statement removal (18 occurrences), change of
+method signature, i.e.~API change (16 occurrences), and method rewriting (15
+occurrences). Moreover, in the 101 outdated pairs, we found 15 ``dead''
+snippets. These snippets cannot be located in the latest version of the
+projects. For example, the snippet in Stack Overflow post 3758110, a copy of
+{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was
+deleted in the commit
+{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on
+January 20, 2012, two years after it was posted.
 
@@
 
-These findings complement a study of clones between software
-projects~\cite{Svajlenko2014}. We found that cloning can also happen among
-different sources on the Internet just like software projects. The are 18 clone
-pairs that originated from programming websites including \url{www.java2s.com}
-and \url{exampledepot.com}. Moreover, there is one snippet which comes from a
-research website. We found that a snippet to generate graphical \textit{Perlin
-	noise} is copied from NYU Media Research Lab
-(\url{http://mrl.nyu.edu/~perlin/noise/}) website and is used in both Stack Overflow
-answer and the \textsf{aoi} project with attribution. There are other EX pairs which
-are copied from open source libraries or Java SDK such as \textsf{Mozilla
-	Rhino}, \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}, and
-the \textsf{bouncycastle} cryptography project.
-
-\textbf{UD: Unknown Direction.} We found 107 online clone pairs, reduced to 65
-pairs after consolidating the clones, with no evidence of cloning between Qualitas
-and Stack Overflow but with a high code similarity that suggests cloning. 
-The most cloned projects is \textsf{netbeans} with 11 clone pairs. Most of the
-clones are a large chunk of code handling GUI components. Although these GUI
-clones might be auto-generated by IDEs, we did not find any evidence. The second
-most cloned project is \textsf{eclipse} (8 pairs), followed by \textsf{jstock},
-a free stock market software, and \textsf{compiere}, a customer
-relationship management (CRM) system, (5 pairs).
-
-\textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs
-found in this study. We observed 1,505 such clone pairs and 217 after
-consolidation. The BP clone pairs account for 65\% of all clone pairs we
-classified. The majority of them are {\small{\texttt{equals()}}} methods.
-
-\textbf{IN: Inheritance/interface.} There were 16 clone pairs, 9 pairs after
-consolidation, found to be similar because they implement the same interface or
-inheriting from the same class. An example is the two implementations of a
-custom data type which implements {\small\texttt{UserType}}. They share similar
-{\small\texttt{@Override}} methods of {\small\texttt{deepCopy}},
-{\small\texttt{isMutable}}, {\small\texttt{assemble}},
-{\small\texttt{disassemble}}, and {\small\texttt{replace}}.
-
-\textbf{AC: Accidental Clones.} There were 226 accidental clone
-pairs, 53 after consolidation. Mainly, they are false positive clones caused by code
-normalisation and false type-3 clones from SourcererCC. 
-Examples of the AC clone instances include {\small\texttt{finally}} or
-{\small\texttt{try-catch}} clauses that were accidentally the same due
-to their very small sizes, and similar {\small\texttt{switch-case}}
-statements.
-
-\textbf{To answer RQ2, we found 154 pairs with
-	strong evidences to be cloned from 23 Qualitas projects to Stack Overflow, 1 pair
-	was cloned from Stack Overflow to Qualitas, and
-	111 pairs were found to be cloned to Stack Overflow from external
-	sources. However, the largest amount of the clone pairs
-	between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
-	(217), followed by 65 clone pairs with no evidence that the code has actually been copied,
-	and 16 pairs of clones due to implementing the same interface or inheriting the same class.}
-
-\subsection{RQ3: Outdated Online Code Clones}
-\vspace{0.25cm}
-\textit{Are online code clones up-to-date compared to their counterparts in the original projects?}
-\vspace{0.25cm}
-
-\begin{figure*}
-	\centering
-	\includegraphics[width=0.8\linewidth]{outdated}
-	\caption{Outdated QS online clone pairs group by projects}
-	\label{fig:outdated}
-\end{figure*}
-
-We discovered 101 outdated online clone pairs out of 154 pairs. As shown in
-\Cref{fig:outdated}, \textsf{hibernate} has the highest number of 19 outdated
-pairs, followed by 14 from \textsf{spring}, 13 from \textsf{eclipse}, and 9 from
-\textsf{hadoop}. Besides the two examples of outdated code in % \textsf{hadoop}'s
-{\small{\texttt{WritableComparator}}} and
-{\small{\texttt{StringUtils}}} class from \textsf{hadoop} shown in
-\Cref{fig:before-after} and \Cref{fig:before-after_2}, we also found a few
-outdated code elements which contained a large amount of modifications. For
-example, the code snippet in Stack Overflow post 23520731 is a copy of
-{\small{\texttt{SchemaUpdate.java}}} in \textsf{hibernate}. The code has been
-heavily modified on February 5, 2016.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.7\linewidth]{mod_types}
-%	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
-%	\label{fig:mod_types}
-%\end{figure}
-
-\begin{table}
-	\centering
-	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
-	\label{tab:mod_types}
-		\begin{tabular}{lr}
-			\toprule
-			Modification & Occurrences \\
-			\midrule
-			Statement modification & 50 \\
-			Statement addition & 28 \\
-			Statement removal & 18 \\
-			Method signature change & 16 \\
-			Method rewriting & 15 \\
-			File deletion & 15 \\
-			\bottomrule 
-		\end{tabular}
-\end{table}
-
-We analysed code modifications which made Stack Overflow code outdated by going
-though commits and git blame information. The of six code modification
-types found in the 101 outdated online clone pairs are summarised in
-\Cref{tab:mod_types} including statement addition, statement modification,
-statement removal, method rewriting, API change (changing in method signature),
-and file deletion. We occasionally found multiple code modifications applied to
-one clone pair at the same time but at a different location. The most often code
-changes found is statement modification (50 occurrences), followed by statement
-addition (28 occurrences), statement removal (18 occurrences), changing of
-method signature, i.e.~API change (16 occurrences), and method rewriting (15
-occurrences). Moreover, in the 101 outdated pairs, we found 15 ``dead''
-snippets. These snippets cannot be located in the latest version of the
-projects. For example, the snippet in Stack Overflow post 3758110, a copy of
-{\small{\texttt{DefaultAnnotationHandlerMapping.java}}} in \textsf{spring}, was
-deleted in the commit
-{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on
-January 20, 2012, two years after it was posted.
-
 Moreover, using the information in git commit messages, we can associate each
@@
 (due to modifications and different API usage in the outdated code) to
-introducing vulnerabilities to software~\cite{Xia2014}. An outdated code with a
+the introduction of vulnerabilities to the software~\cite{Xia2014}. An outdated code with a
 subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without
@@
 \subsubsection{General Information}
-As shown in \Cref{tab:survey_exp}, majority of the answerers are experienced
+As shown in \Cref{tab:survey_exp}, the majority of the answerers are experienced
 developers with more than 10 years of experience (55.4\%) or between 5 to 10
@@
 \vspace{0.25cm}
-\textit{Do Stack Overflow
+\textit{How often are Stack Overflow
 	answerers aware of the outdated code when
@@
 
-We then asked 131 participants to have been notified of their outdated code a
-follow-up questions \textit{``how frequently did you fix your outdated code on Stack
+We then asked 131 participants who have been notified of their outdated code a
+follow-up question \textit{``how frequently did you fix your outdated code on Stack
 Overflow?''}. The answers, depicted in
@@
 \textbf{To answer RQ 5.1, although most of the Stack Overflow answerers are aware that their code
-can be outdated. 51.5\% of the answerers were very rarely notified while 35.5\% never been notified of
+can be outdated. 51.5\% of the answerers were very rarely notified while 35.5\% have never been notified of
 outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.}
@@
 \vspace{0.25cm}
-\textit{Do Stack Overflow
-	answerers aware of the outdated code when
+\textit{How often are Stack Overflow
+	answerers aware of licensing conflicts when
 	they answer a question on Stack Overflow?} 

### 2017-10-19 cloverflow_technical_report/cloverflow_survey_rn.tex
Completed the whole paper (RQ1 - RQ5).
Updated the number of Group 2 in technical report due to removing one participant.

@@
 snippets, problems from Stack Overflow snippets, licensing of code on Stack
-Overflow, and additional feedbacks. The survey was open for participation for 50
-days, from 25 July 2017 to 12 September 2017, before we collected and analysed
+Overflow, and additional feedbacks. The survey was open for participation for 2 months, 
+from 25 July 2017 to 25 September 2017, before we collected and analysed
 the responses.
@@
 		Answerer Group 1 & 963,731--7,674 & 300 & 117 & 39\% \\
-		Answerer Group 2 & 7,636--6,999 & 307 & 85 & 28\% \\
+		Answerer Group 2 & 7,636--6,999 & 307 & 84 & 27\% \\
 		\midrule
-		Total & -- & 607 & 202 & 33\% \\
+		Total & -- & 607 & 201 & 33\% \\
 		\bottomrule
@@
 \subsection{The answerer survey}
-We received 117 answers (39\% response rate) from the first group and 85 answers
-(28\% response rate) from the second group of Stack Overflow answerers. The response
+We received 117 answers (39\% response rate) from the first group and 84 answers
+(27\% response rate) from the second group of Stack Overflow answerers. The response
 rate from both groups was high considered other online survey in software
@@
 10 years of experience or between 5 to 10 years as depicted in
-Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 that
-have more than 10 years of software development experience, while a slightly
-less percentage of 50\% in Group 2.
+Figure~\ref{fig:survey_exp}. There are 59\% of the answerers in Group 1 
+and 50\% of the answerers in Group 2 that
+have more than 10 years of software development experience.
 
@@
 Overflow (see Figure~\ref{fig:survey_answer_frequency}). Eighty-two (82\%) and
-sixty (60\%) of answerers from Group 1 and Group 2  answer questions at least
+sixty (61\%) of answerers from Group 1 and Group 2  answer questions at least
 once a week. More than half of the answerers very frequently (81--100\% of the

### 2017-10-19 cloverflow-tse/cloverflow.tex
Finalise the draft to be ready for Jens to look at.

@@
 \begin{abstract}
-% We studied online code clones on the popular programming Q\&A
-% website, Stack Overflow, and their issues on outdated code and
-% software licensing violations. 
-\FIXME{Outdated.~Revise the last.}~Online code clones are code fragments that are copied from software
-projects or online sources to Stack Overflow as examples in
-questions and answers.
-% They can be discovered by using code clone
-% detectors, yet they are inherently different from normal code clones
-% in software projects in several aspects. 
-Due to an absence of a checking mechanism after the code has been
-copied to Stack Overflow, online code clones may suffer from
-becoming outdated or violating the original software license.
-% Moreover, we also found that majority of online code clones do not
-% contain the license of their originals.
-We present a study incorporating several state-of-the-art tools and
-techniques to automatically extract, prioritise, and filter detected
-online clone pairs between 144,064 Java code snippets on Stack
-Overflow and 111 Java open source projects in the curated Qualitas
-corpus. We discovered and analysed 32,533 non-trivial online clone
-candidates. Our investigation of 3,636 manually confirmed clone
-pairs revealed strong evidence that 112 clones have been copied from
-a Qualitas project to Stack Overflow.  We found 64 of them (57\%) 
-to be outdated and potentially harmful for reuse.  Furthermore, we
-found 357 code snippets on Stack Overflow that violate the license
-of their original software.
-% These snippets are questionable for reuse.
-% Our study is among the first to address the problem of
-% outdated and license-violating code snippets on Stack Overflow.
+Online code clones are code fragments that are copied from software projects or
+online sources to Stack Overflow as examples in questions and answers. % They
+Due to an absence of a checking mechanism after the code has been copied to
+Stack Overflow, they can become toxic code snippets, i.e.~ they suffer from
+being outdated or violating the original software license. We present a study
+incorporating several state-of-the-art tools and techniques to automatically
+extract and filter detected online clone pairs between 72,365 Java code snippets
+on Stack Overflow and 111 Java open source projects in the curated Qualitas
+corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
+Our investigation of the online clone pairs revealed strong evidence that 154
+clones have been copied from a Qualitas project to Stack Overflow.  We found 101
+of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
+we found 214 code snippets on Stack Overflow that violate the license of their
+original software. We surveyed 201 high-reputation Stack Overflow answerers
+(33\% response rate) and found that 69 of them have never been notified of
+outdated code in the answers and 26 of them rarely or never fix the outdated
+code. Only 3 answerers explicitly include software license in their answers and
+138 answerers never check for licensing conflicts between their copied code
+snippets and Stack Overflow's CC BY-SA 3.0.
 \end{abstract}
@@
 is obviously beneficial considered the popularity of Stack Overflow and its
-influence on software development~\FIXME{find citations}. On the other hand,
+influence on software development~\cite{Ponzanelli2013,Ponzanelli2014,Park2014}. On the other hand,
 there is also a downside caused by low quality, defective, and harmful code
@@
 		its latest version in the \textsf{hadoop} code base
-		(right). Its Apache v.2.0 license is also missing.}
+		(right). Its Apache v.2.0 license is also missing.~\FIXME{@Jens Could you please make the underline clearer?}}
 	\label{fig:before-after}
@@
 
-\textbf{Stack Overflow:} 
-We extracted Java code snippets from a snapshot of a Stack Overflow
-dump\footnote{\url{https://archive.org/details/stackexchange}} in January 2016.
-% The archived dump has a size of 9 gigabytes.
+\textbf{Stack Overflow:} We extracted Java code snippets from a snapshot of a
+Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
+January 2016. % The archived dump has a size of 9 gigabytes.
 The data dump is in XML, and it contains information of posts (questions and
@@
 code snippets of at least ten lines. Although the minimum clone size of six
-lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006},
-we empirically found that snippets of six lines contain a large number of
-boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode} methods,
-which are not interesting for the study.
-Each snippet was extracted from the dump and saved to a file. Moreover, we
-filtered out irrelevant code snippets that were part of the accepted answers
-but were not written in Java by using regular expressions and manual checking.
-~\FIXME{@Jens, should I mention I use PMD CPD to help here? More confusing?}.
-Finally we obtained
-72,365 Java code snippets containing 1,840,581 lines\footnote{Measured by cloc:
-	\url{https://github.com/AlDanial/cloc}} of Java source code. The median size of the
-snippet is 17 lines.
+lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
+empirically found that snippets of six lines contain a large number of
+boiler-plate code of getters/setters, \texttt{equal} or \texttt{hashCode}
+methods, which are not interesting for the study. Each snippet was extracted
+from the dump and saved to a file. Moreover, we filtered out irrelevant code
+snippets that were part of the accepted answers but were not written in Java by
+using regular expressions and manual checking. ~\FIXME{@Jens, should I mention I
+	use PMD CPD to help filtering SO code snippets here? Will it be too confusing?}.
+Finally we obtained 72,365 Java code snippets containing 1,840,581
+lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
+source code. The median size of the snippet is 17 lines.
 
@@
 copying while the other could not. They result in a better classification,
- i.e.~from UD to QS or EX. 
+ i.e.~from UD to QS or EX.~\FIXME{@Jens Is it better to just report \% of conflicts
+ between TP vs.~FP classifications (e.g. only from QS, SQ, EX, UD, BP, IN <--> AC)?
+Because 26\% does not come from a wrong validation, it's mostly just a different classification.}
 %There were three conflicts where the two

### 2017-10-20 cloverflow-tse/cloverflow.tex
Small changes to FIXMEs and adding one more related work by Abdalkareem et al.

@@
 their previous answers. The full survey can be found in our research note~
-\FIXME{add URL to the RN}.
+\cite{Ragkhitwetsagul_RN2017}~\FIXME{Fix the RN bibtex}.
 
@@
 We only present a summary of the survey answers in
-this paper and the full analysis is available as a technical report \FIXME{add URL}.
+this paper and the full analysis is available as a technical report~\cite{Ragkhitwetsagul_RN2017}.
 
@@
 
-The work that is closely similar to us is a study by 
-An et al.~\cite{An2017} where the authors investigated 
-clones between 399 Android apps and Stack Overflow posts. 
-They found 1,226 code snippets which were reused from 68 Android apps. 
-They also observed that there are 1,279 cases of potential 
-license violations. The authors rely on the timestamp to 
-judge whether the code has been copied from/to Stack Overflow 
-along with confirmations from six developers. Instead of Android apps, 
-we investigated clones between Stack Overflow and 111 open 
-source projects. Their results are similar to our findings that 
-there exist clones from software projects to Stack Overflow with 
-potential licensing violations. 
-\FIXME{Add a discussion of Abdalkareem et al.~\cite{Abdalkareem2017}}
+The work that are closely similar to us are studies by An et al.~\cite{An2017}
+and Abdalkareem et al.~\cite{Abdalkareem2017}. An et al.~investigated clones
+between 399 Android apps and Stack Overflow posts. They found 1,226 code
+snippets which were reused from 68 Android apps. They also observed that there
+are 1,279 cases of potential license violations. The authors rely on the
+timestamp to judge whether the code has been copied from/to Stack Overflow along
+with confirmations from six developers. Instead of Android apps, we investigated
+clones between Stack Overflow and 111 open source projects. Their results are
+similar to our findings that there exist clones from software projects to Stack
+Overflow with potential licensing violations. Abdalkareem et
+al.~\cite{Abdalkareem2017} detected clones between Stack Overflow posts and
+android apps from F-Droid repository and used timestamp to determine direction
+of copying. They found 22 apps containing code cloned from Stack Overflow. They
+reported that cloned code are commonly used for enhancing existing code. Their
+analysis shows that the cloned code from Stack Overflow have negative effects to
+quality of the apps. The median percentage of bug fixing commits after adding
+Stack Overflow code (19.09\%) is higher than before adding the code (5.96\%)
+with statistical significance.
 %In our work, we defined seven patterns of online code cloning and 

### 2017-10-22 cloverflow-tse/cloverflow.tex
Checked the paper, corrected issues and added a few FIXMEs.

@@
 	basicstyle=\ttfamily\footnotesize,
-	moredelim=[is][\dotuline]{@}{@},
 	mathescape=true
@@
 original software. We surveyed 201 high-reputation Stack Overflow answerers
-(33\% response rate) and found that 69 of them have never been notified of
-outdated code in the answers and 26 of them rarely or never fix the outdated
+(33\% response rate) and found that 69 of them (FIXME\%) have never been notified of
+outdated code in the answers and 26 of them (FIXME\%) rarely or never fix the outdated
 code. Only 3 answerers explicitly include software license in their answers and
-138 answerers never check for licensing conflicts between their copied code
+138 answerers (FIXME\%) never check for licensing conflicts between their copied code
 snippets and Stack Overflow's CC BY-SA 3.0.
@@
 code or from other locations including open source software (OSS)
-systems. The process of posting and answering questions on Stack
-Overflow that involves the reuse of source code can be considered
+systems.
+
+The process of posting and answering questions on Stack
+Overflow that involves the reuse (copying) of source code can be considered
 code cloning.
-
 Code cloning is an activity of reusing source code by copying and
@@
 cloned from open source software or online sources can become toxic when they
-are (1) outdated or (2) violating their original software license. Outdated code
+are (1) outdated or (2) violating their original software
+license. Outdated code snippets
 can be harmful since they are not up-to-date with their originals and may
@@
 cloned to Stack Overflow answers without the license, and then flow to other projects
-with conflicting license, legal issues may occur.
+with conflicting licenses, legal issues may occur.
 
 \begin{figure*}
-	\begin{lstlisting}
+  \fboxsep0pt
+	\begin{lstlisting}[escapechar=&]
 /* Code in Stack Overflow post ID 22315734 */         /* WritableComparator.java (2014-11-21) */
@@
     key2.readFields(buffer);                              key2.readFields(buffer);
-  } catch (IOException e) {                               $$@buffer.reset(null,0,0); /* clean up reference */@
+  } catch (IOException e) {                               &\framebox{buffer.reset(null,0,0); \textit{/* clean up reference */}}&
     throw new RuntimeException(e);                      } catch (IOException e) {
@@
 		Stack Overflow post 22315734 (left) is outdated when compared to
-		its latest version in the \textsf{hadoop} code base
-		(right). Its Apache v.2.0 license is also missing.~\FIXME{@Jens Could you please make the underline clearer?}}
+		its latest version in the \textsf{Hadoop} code base
+		(right). Its Apache v.2.0 license is also missing.}
 	\label{fig:before-after}
@@
 {\small{\texttt{RawComparator}}} in
-\textsf{hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
+\textsf{Hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
 \Cref{fig:before-after} shows---on the left---a code snippet embedded as a part
-of the accepted answer. The snippet shows how \textsf{hadoop} implements the
+of the accepted answer. The snippet shows how \textsf{Hadoop} implements the
 {\small{\texttt{compare}}} method in its {\small{\texttt{WritableComparator}}}
@@
 but at this time extracted from the latest version (as of October 3, 2017) of
-\textsf{hadoop}. We can see that they both are highly similar except a line
+\textsf{Hadoop}. We can see that they both are highly similar except a line
 containing {\small{\verb|buffer.reset(null,0,0);|}} which was added on November
@@
 While this change has already been introduced into the
-{\small{\texttt{compare}}} method for several years, the code example in Stack
+{\small{\texttt{compare}}} method several years ago, the code example in Stack
 Overflow post is still unchanged. 
@@
 		Stack Overflow post 801987 (left) is outdated when compared to
-		its latest version in the \textsf{hadoop} code base
+		its latest version in the \textsf{Hadoop} code base
 		(right). The toxic code snippet is outdated code, has race conditions, and does not contain its
@@
 \Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
-task from the {\small{\texttt{StringUtils}}} class in \textsf{hadoop}. The code snippet on the
+task from the {\small{\texttt{StringUtils}}} class in \textsf{Hadoop}. The code snippet on the
 right shows another version of the same method, but at this time extracted from
-the latest version of \textsf{hadoop}. We can see that
+the latest version of \textsf{Hadoop}. We can see that
 they are totally different. The {\small{\texttt{humanReadableInt}}} method is
@@
 (issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
-The absence of Apache v.2.0 license also occurs after the snippet is posted on 
+\FIXME{I don't understand the following:} The absence of Apache v.2.0 license also occurs after the snippet is posted on 
 Stack Overflow.
@@
 The two toxic code snippet in our examples have been posted on March 11, 2014 and
-April 9, 2009 respectively. They have already been viewed 259 and 2,886 times as
+April 9, 2009 respectively. They have already been viewed 259 and 2,886 times at
 the time of writing this paper (October 3, 2017). Our calculation finds that
-there will be a new viewer of the first toxic snippet in approximately every 5
+there will be a new viewer of the first toxic snippet approximately every 5
 days compared to almost every day for the second one. A quick web search shows
@@
 	software licenses. For 154 of them, we found evidence that they have been copied
-	from a specific open source project and that 101 of them are outdated. %
+	from a specific open source project. 101 of them we found to be outdated. %
 	% and questionable for being reused.
@@
 	their outdated code snippets, 19\% of the participants rarely
-	or never fix the code. 99\% of the answerers never include software
+	or never fix the code. 99\% of the answerers never include a software
 	license in their snippets and 69\% never check for licensing conflicts between the
@@
 snippets that were part of the accepted answers but were not written in Java by
-using regular expressions and manual checking. ~\FIXME{@Jens, should I mention I
-	use PMD CPD to help filtering SO code snippets here? Will it be too confusing?}.
+using regular expressions and manual checking.
 Finally we obtained 72,365 Java code snippets containing 1,840,581
 lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
-source code. The median size of the snippet is 17 lines.
+source code. The median size of the snippets is 17 lines.
 
@@
 		\toprule
-		Dataset & No. of files & SLOC & Median \\
+		Data set & No. of files & SLOC & Median \\
 		\midrule
@@
 could complete its execution but skipped 367 snippets due to malformed blocks in
-Stack Overflow data sets. CCFinder reported 8 errors while processing the two data set. 
+Stack Overflow data sets. CCFinder reported 8 errors while processing the two data sets. 
 Although Simian, SourcererCC, and DECKARD
 could successfully report clones, we decided to choose only Simian and
-SourcererCC due to their fast detection speed.
+SourcererCC due to their fast detection speed. Moreover, Simian and
+SourcererCC complement each other as SourcererCC's clone fragments are
+always confined to method boundaries while Simian's fragments are not.
 
@@
 granularity and has been used extensively in several clone
-studies~\cite{Ragkhitwetsagul2016, Wang2013, Mondal2011, Cheung2015,
+studies~\cite{Ragkhitwetsagul2016, emse, Wang2013, Mondal2011, Cheung2015,
 	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
@@
 optimised configurations in empirical clone
-studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016}. However,
+studies~\cite{Svajlenko2014,Wang2014,cr2016ssbse,Ragkhitwetsagul2016, emse}. However,
 considering the massive size of the two datasets and the search space of at
@@
 SourcererCC based on their established default configurations chosen by the
-tools' creators as depicted in \Cref{tab:clone_config}. All variable renaming are disabled to decrease the number of
+tools' creators as depicted in \Cref{tab:clone_config}. 
+\FIXME{Something is not right: First it says that variable renaming is
+  disabled, and later it is said that SourcererCC uses renaming.}
+All variable renaming are disabled to decrease the number of
 false positives since we aim for finding clones that are copied from open source
@@
 other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
-detecting clones with renaming and added/deleted statments (type-2, type-3). We made sure that they 
+detecting clones with renaming and added/deleted statements (type-2, type-3). We made sure that they 
 detected only non-trivial clones by increasing the minimum clone size to ten
@@
 
-\ We follow Bellon's original definitions of ok-match~\cite{Bellon2007}, which are based on how much two clone
+We follow Bellon's original definitions of ok-match~\cite{Bellon2007}, which are based on how much two clone
 fragments \textit{CF} are contained in each other:
@@
 %, and the \textit{good-value} and
-and the \textit{ok-value} of two clone pairs are defined as
+and the \textit{ok-value} of two clone pairs is defined as
 
@@
 Simian and 1,678 clone pairs from SourcererCC into a single set of 2,302 online
-clone pairs. There are 97 common clone pairs between the two clone sets 
-as depicted in~\Cref{fig:clonemerging}.
+clone pairs. There are only 97 common clone pairs between the two clone sets 
+as depicted in~\Cref{fig:clonemerging}.  The low number of common
+clone pairs is due to SourcererCC reporting clones with method
+boundaries while Simian is purely line-based.
 
@@
 copying while the other could not. They result in a better classification,
- i.e.~from UD to QS or EX.~\FIXME{@Jens Is it better to just report \% of conflicts
- between TP vs.~FP classifications (e.g. only from QS, SQ, EX, UD, BP, IN <--> AC)?
-Because 26\% does not come from a wrong validation, it's mostly just a different classification.}
+ i.e.~from UD to QS or EX.~\FIXME{Report \% of conflicts
+ between TP vs.~FP classifications first, and then about evidence.}
 %There were three conflicts where the two
@@
 
-		UD & Cloned from each other or from an external source \textit{X} outside the project (unknown) (S $\leftrightarrow$ Q $\vee$ (X $\rightarrow$ S $\wedge$ X $\rightarrow$ Q)). \\ 
+		UD & Cloned from each other or from an external source
+                     \textit{X} outside the project (unknown)\\
 		\midrule
@@
 to see if any license can be found. For EX clone pairs that are cloned from
-external sources such as JDK or websites. We manually searched for the license
+external sources such as JDK or websites, we manually searched for the license
 of the original code.
@@
 mandatory while the other 9 questions were shown to the participants based on
-their previous answers. The full survey can be found in our research note~
-\cite{Ragkhitwetsagul_RN2017}~\FIXME{Fix the RN bibtex}.
+their previous answers. The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}~\FIXME{Fix the RN bibtex}.
 
@@
 of 25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}. The
-invited participants had a reputation from 963,731 (the highest) to 6,999 which
-we sent out 607 emails (excluding undelivered ones) respectively. The survey was
+invited participants had a reputation from 963,731 (the highest) to 6,999 and
+we sent out 607 emails (excluding undelivered ones, e.g.\ due to
+illegal email addresses). The survey was
 open for participation for two months, from 25 July to 25 September 2017, before
@@
 projects. For the cloned Stack Overflow snippets, the
-average ratio of cloned code is 53.10\%.
+average ratio of cloned code is 53.10\% (i.e.\ the number of cloned
+lines of the cloned Stack Overflow snippet).
 
@@
 
-\textbf{To answer RQ1, we found more than half of Qualitas projects to share
+\textbf{To answer RQ1, we found more than half (53\%) of Qualitas projects to share
 	similar code with Stack Overflow code snippets. In the manually confirmed 
@@
 \textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 248 online clone
-pairs with evidences of cloning from Qualitas projects to Stack Overflow.
+pairs with evidence of cloning from Qualitas projects to Stack Overflow.
 However, we observed that, in some cases, a cloned code snippet on Stack
@@
 Overflow snippet, starting line, and ending line into a single clone pair. We
-finally obtained 154 QS pairs having unique Stack Overflow code snippets and
+finally obtained 154 QS pairs (\Cref{tab:classification_good_o}) having unique Stack Overflow code snippets and
 associated with 23 Qualitas projects listed in \Cref{tab:qs_qualitas_projects}.
-The most cloned projects is \textsf{hibernate} with 24
+The most cloned project is \textsf{hibernate} with 24
 clone pairs, followed by \textsf{eclipse} (21 pairs), \textsf{jung2} (19 pairs),
@@
 comes from our experimental design since
-we are more interested in a cloning direction from Qualitas to Stack Overflow.
+we are more interested in cloning from Qualitas to Stack Overflow.
 
@@
 Stack Overflow. After consolidating duplicated SO snippets due to multiple
-intra-clone instances in Qualitas, we obtained 111 EX pairs. We found evidence
-of copying from an external source to Stack Overflow, but not in Qualitas, in 61 pairs. 
-A stronger evidence of copying from an external source to both Stack
-Overflow and Qualitas is available in the other 50 pairs. Each of them contains
-statement(s) pointing to the original external location of the cloned code. Our
+intra-clone instances in Qualitas, we obtained 111 EX pairs. We found
+evidence of copying from an external source to both Stack
+Overflow and Qualitas in 50 pairs. Each of the pairs contains
+statement(s) pointing to the original external location of the cloned
+code in Qualitas and Stack Overflow. In addition, we found evidence
+of copying from an external source to Stack Overflow, but not in
+Qualitas, in 61 pairs. 
+Our
 analysis shows that the external sources fall into six groups as displayed in
@@
 and Stack Overflow but with a high code similarity that suggests cloning. 
-The most cloned projects is \textsf{netbeans} with 11 clone pairs. Most of the
+The most cloned project is \textsf{netbeans} with 11 clone pairs. Most of the
 clones are a large chunk of code handling GUI components. Although these GUI
 clones might be auto-generated by IDEs, we did not find any evidence. The second
-most cloned project is \textsf{eclipse} (8 pairs), followed by \textsf{jstock},
+most cloned project is \textsf{eclipse} (8 pairs), followed by
+\textsf{jstock}  (5 pairs),
 a free stock market software, and \textsf{compiere}, a customer
-relationship management (CRM) system, (5 pairs).
+relationship management (CRM) system.
 
@@
 	\centering
-	\caption{License mapping of online clones (file-level)}
+	\caption{License mapping of online clones (file-level)
+          \FIXME{Change order of columns, Qualitas before SO}}
 	\label{tab:license_abc}
@@
 posted on Stack Overflow. One QS clone pair posted by a JFreeChart developer
-changes its license from Lesser GPL v2.1+ to New BSD 3-clause. The
-developer may intentionally change the license to be more suitable to Stack
+changed its license from Lesser GPL v2.1+ to New BSD 3-clause. The
+developer may intentionally changed the license to be more suitable to Stack
 Overflow since New BSD 3-clause license allows reuse without requiring the same
@@
 \textbf{For RQ4, we found 214 code snippets on Stack Overflow that
-	violate the license of their original software. The majority of them
+	could violate the license of their original software. The majority of them
 	do not contain licensing statements after they have been copied to
-	Stack Overflow.}
+	Stack Overflow. For 164 of them, we were able to identify,
+        with evidence, where the code snippet has been copied from.}
+
+Note that the code snippets could violate the license, but do
+not necessarily do so. In the example where the JFreeChart
+developer copied his own code, she or he was free to change the
+license. The same may have occurred with any of the 214 code
+snippets.
 
@@
 We received 201 answers (33\% response rate) from 607 emails we sent to the
-Stack Overflow answerers. The response rate was high
-considered other online survey in software engineering that received
-approximately 14--20\%~\FIXME{double-check the citation again for the magic
-	numbers.}\cite{Punter2003}.
+Stack Overflow answerers. The response rate was high considering other
+online surveys in software engineering~\cite{Punter2003}. 
 We only present a summary of the survey answers in
@@
 years (28.7\%). They are active users and regularly answer questions. 49
-participants answer questions on Stack Overflow every day.
+participants (FIXME\%) answer questions on Stack Overflow every day.
 
@@
 their answers respectively. Interestingly, there is one answerer who never
-include code snippet in his/her answers.
+include code snippet in his/her answers (\Cref{tab:survey_code_snippet_frequency}).
 
@@
 and we asked them to rate how often they copied the code from these locations. The
-results are shown in \Cref{fig:survey_snippet_source}. Looking at Very
+results are shown in \Cref{fig:survey_snippet_source}. Looking at the Very
 Frequently section, we can see that the answerers mainly write new code from
-scratch (71) or modify from the code snippets in question for each answer (56),
+scratch (71) or copy and modify the code snippets from the question for each answer (56),
 while fewer numbers are from other sources including their personal projects
@@
 We found that although the answerer have been notified of
-outdated code in their answers, 51.5\% occurs very rarely (only 1--20\% of the answers). 
+outdated code in their answers, for 51.5\% of them such notifications occur very rarely (only 1--20\% of the answers). 
 Only 3 participants reported that they were notified in more than 60\% of their answers.
@@
 (57.2\%) very frequently or frequently fix the outdated code snippets. However,
-there are totally 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
+there are 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
 their outdated code.
@@
 careful when posting code snippets in the answer to avoid problems and, vice versa, 
-getting down votes. It is also interesting to compare the findings to
+getting down votes. It would be interesting to compare the findings to
 Stack Overflow answerers who are newer and have lower reputation. However, we
-leave it as the future work.
+leave it to future work.
 
@@
 the checking. Nonetheless, there are about 10.5\% of the answerers who very
-frequently or frequently checks for licensing conflicts when they copy code
+frequently or frequently check for licensing conflicts when they copy code
 snippets to Stack Overflow.
@@
 \end{enumerate}
+
+The comments highlight that Stack Overflow users are unsure about the
+legal implications of copying code, that code is copied without
+understanding it, and that the quality of code on Stack Overflow is
+often low.
 
@@
 classification and avoid double counting of the same clone pairs. 
-Nevertheless, we might still suffers from false negatives, i.e.~online 
+Nevertheless, our study might still suffer from false negatives, i.e.~online 
 code clones that are not reported by the tools or are filtered 
@@
 invented based on plethora of different code similarity
-measurements~\cite{Roy2008, Ragkhitwetsagul2016,Svajlenko2014}. 
+measurements~\cite{Roy2008, Ragkhitwetsagul2016,emse,Svajlenko2014}. 
 % Some tools use string comparison techniques such as Simian~\cite{simian}. 
@@
 code give detrimental effects to the software since they may 
-introduce vulnerabilities. Our study similarily finds
+introduce vulnerabilities. Our study similarly finds
 % on % the context of 
@@
 al.~\cite{Abdalkareem2017} detected clones between Stack Overflow posts and
-android apps from F-Droid repository and used timestamp to determine direction
+Android apps from the F-Droid repository and used timestamps to
+determine the direction
 of copying. They found 22 apps containing code cloned from Stack Overflow. They
-reported that cloned code are commonly used for enhancing existing code. Their
+reported that cloned code is commonly used for enhancing existing code. Their
 analysis shows that the cloned code from Stack Overflow have negative effects to

### 2017-10-22 cloverflow-tse/cloverflow.tex
Fixed most of the FIXMEs.

@@
 original software. We surveyed 201 high-reputation Stack Overflow answerers
-(33\% response rate) and found that 69 of them (FIXME\%) have never been notified of
-outdated code in the answers and 26 of them (FIXME\%) rarely or never fix the outdated
+(33\% response rate) and found that 69 of them (34.5\%) have never been notified of
+outdated code in the answers and 26 of them (19.8\%) rarely or never fix the outdated
 code. Only 3 answerers explicitly include software license in their answers and
-138 answerers (FIXME\%) never check for licensing conflicts between their copied code
+138 answerers (69\%) never check for licensing conflicts between their copied code
 snippets and Stack Overflow's CC BY-SA 3.0.
@@
 (issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
-\FIXME{I don't understand the following:} The absence of Apache v.2.0 license also occurs after the snippet is posted on 
-Stack Overflow.
+Similar to the first example, the clone code snippet on Stack Overflow does not 
+include its original Apache v.2.0 license.
+%\FIXME{I don't understand the following:} The absence of Apache v.2.0 license also occurs after the snippet is posted on 
+%Stack Overflow.
 
@@
 tools' creators as depicted in \Cref{tab:clone_config}. 
-\FIXME{Something is not right: First it says that variable renaming is
-  disabled, and later it is said that SourcererCC uses renaming.}
-All variable renaming are disabled to decrease the number of
-false positives since we aim for finding clones that are copied from open source
-projects with minimal modifications. The two clone detectors complement each
+%\FIXME{Something is not right: First it says that variable renaming is
+%  disabled, and later it is said that SourcererCC uses renaming.}
+%All variable renaming are disabled to decrease the number of
+%false positives since we aim for finding clones that are copied from open source
+%projects with minimal modifications. 
+The two clone detectors complement each
 other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
@@
 a false positive and classified them into an appropriate pattern. After the
-validation, the results from the two investigators were compared and 607 (26\%)
-conflicts were discussed and resolved. There are 145 conflicts caused by
+validation, the results from the two investigators were compared. 
+%and 607 (26\%)
+%conflicts were discussed and resolved. 
+There are 338 (15\%) conflicts between 
+true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC). The other 270 pairs (12\%) are 
+conflicts in the classification of
+the true clone pairs. Among these pairs, 145 conflicts were caused by
 one investigator being more careful than the other and able to find evidence of 
 copying while the other could not. They result in a better classification,
- i.e.~from UD to QS or EX.~\FIXME{Report \% of conflicts
- between TP vs.~FP classifications first, and then about evidence.}
+ i.e.~from UD to QS or EX.
+%~\FIXME{Report \% of conflicts
+% between TP vs.~FP classifications first, and then about evidence.}
 %There were three conflicts where the two
@@
 
-		SQ &Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\
-
-		EX & Cloned from an external source \textit{X} (X $\rightarrow$ S). \\
+		SQ & Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\
+
+		EX & Cloned from an external source \textit{X} to Stack Overflow\newline (X $\rightarrow$ S). \\
 
@@
 	\centering
-	\caption{License mapping of online clones (file-level)
-          \FIXME{Change order of columns, Qualitas before SO}}
+	\caption{License mapping of online clones (file-level)}
 	\label{tab:license_abc}
@@
 			\toprule
-			Type & Stack Overflow\newline (CC BY-NC-SA) & Qualitas & QS & EX & UD \\
+			Type & Qualitas & Stack Overflow\newline (CC BY-NC-SA)& QS & EX & UD \\
 			\midrule
@@
 			& No license & No license & 20 & 9 & 2 \\ 
-			& CC BY-SA 3.0 & No license & & 1 & \\
+			& No license & CC BY-SA 3.0 & & 1 & \\
 			\midrule
@@
 			Incompat. 
-			& No license & AGPLv3/3+ & 1 & & 4 \\
-			& No license & Apache-2 & 46 & 14 & 12 \\  
-			& No license & BSD/BSD3 & 4 & & 1 \\ 
-			& No license & CDDL or GPLv2 & & & 6 \\ 
-			& No license & EPLv1 & 10 & & 6 \\
-			& No license & GPLv2+/3+ & 8 & 48 & 7 \\ 
-			& No license & LesserGPLv2.1+/3+ & 16 & & 9 \\ 			
-			& No license & MPLv1.1 & & & 1 \\ 
-			& No license & Oracle & & 3 \\ 
-			& No license & Proprietary & & 1 & 2 \\ 
-			& No license & Sun Microsystems & & 1 & 2 \\ 
-			& No license & Unknown & & 11 & \\
-			& New BSD3 & LesserGPLv2.1+ & 1 & & \\ 
+			& AGPLv3/3+ & No license & 1 & & 4 \\
+			& Apache-2 & No license & 46 & 14 & 12 \\  
+			& BSD/BSD3 & No license & 4 & & 1 \\ 
+			& CDDL or GPLv2 & No license & & & 6 \\ 
+			& EPLv1 & No license & 10 & & 6 \\
+			& GPLv2+/3+ & No license & 8 & 48 & 7 \\ 
+			& LesserGPLv2.1+/3+ & No license & 16 & & 9 \\ 			
+			& MPLv1.1 & No license & & & 1 \\ 
+			& Oracle & No license & & 3 \\ 
+			& Proprietary & No license & & 1 & 2 \\ 
+			& Sun Microsystems & No license & & 1 & 2 \\ 
+			& Unknown & No license & & 11 & \\
+			& LesserGPLv2.1+ & New BSD3 & 1 & & \\ 
 			\midrule
@@
 years (28.7\%). They are active users and regularly answer questions. 49
-participants (FIXME\%) answer questions on Stack Overflow every day.
+participants (24\%) answer questions on Stack Overflow every day.
 

### 2017-10-23 cloverflow-tse/cloverflow.tex
Further improvements.

@@
 Due to an absence of a checking mechanism after the code has been copied to
-Stack Overflow, they can become toxic code snippets, i.e.~ they suffer from
+Stack Overflow, they can become toxic code snippets, i.e.~they suffer from
 being outdated or violating the original software license. We present a study
@@
 original software. We surveyed 201 high-reputation Stack Overflow answerers
-(33\% response rate) and found that 69 of them (34.5\%) have never been notified of
-outdated code in the answers and 26 of them (19.8\%) rarely or never fix the outdated
-code. Only 3 answerers explicitly include software license in their answers and
+(33\% response rate) and found that 131 of the answerers (65\%) have ever been notified of
+outdated code in the answers and 26 of them (20\%) rarely or never fix the outdated
+code. Only 3 answerers explicitly include software licenses in their answers and
 138 answerers (69\%) never check for licensing conflicts between their copied code
@@
 include its original Apache v.2.0 license.
-%\FIXME{I don't understand the following:} The absence of Apache v.2.0 license also occurs after the snippet is posted on 
-%Stack Overflow.
 
@@
 tools' creators as depicted in \Cref{tab:clone_config}. 
-%\FIXME{Something is not right: First it says that variable renaming is
-%  disabled, and later it is said that SourcererCC uses renaming.}
-%All variable renaming are disabled to decrease the number of
-%false positives since we aim for finding clones that are copied from open source
-%projects with minimal modifications. 
 The two clone detectors complement each
@@
 %conflicts were discussed and resolved. 
-There are 338 (15\%) conflicts between 
-true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC). The other 270 pairs (12\%) are 
+There were 338 (15\%) conflicts between 
+true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC) \FIXME{How have
+  they been resolved?}. 
+Another 270 pairs (12\%) were
 conflicts in the classification of
@@
 one investigator being more careful than the other and able to find evidence of 
-copying while the other could not. They result in a better classification,
+copying while the other could not. Resolving the conflicts lead to a better classification,
  i.e.~from UD to QS or EX.
-%~\FIXME{Report \% of conflicts
-% between TP vs.~FP classifications first, and then about evidence.}
 %There were three conflicts where the two
@@
 		\midrule
-		QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S). \\
-
-		SQ & Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q). \\
-
-		EX & Cloned from an external source \textit{X} to Stack Overflow\newline (X $\rightarrow$ S). \\
+		QS & Cloned from Qualitas project to Stack Overflow (Q $\rightarrow$ S) \\
+
+		SQ & Cloned from Stack Overflow to Qualitas project (S $\rightarrow$ Q) \\
+
+		EX & Cloned from an external source to Stack Overflow (X $\rightarrow$ S) \\
 
 		UD & Cloned from each other or from an external source
-                     \textit{X} outside the project (unknown)\\
+                     outside the project (unknown)\\
 		\midrule
@@
 
-\begin{IEEEbiography}{Michael Shell}
-Biography text here.
-\end{IEEEbiography}
-
-% if you will not have a photo at all:
-\begin{IEEEbiographynophoto}{John Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
-
-% insert where needed to balance the two columns on the last page with
-% biographies
-%\newpage
-
-\begin{IEEEbiographynophoto}{Jane Doe}
-Biography text here.
-\end{IEEEbiographynophoto}
+% \begin{IEEEbiographynophoto}{Chaiyong Ragkhitwetsagul}
+% Biography text here.
+% \end{IEEEbiographynophoto}
+
+% % if you will not have a photo at all:
+% \begin{IEEEbiographynophoto}{Jens Krinke}
+% Biography text here.
+% \end{IEEEbiographynophoto}
+
+% \begin{IEEEbiographynophoto}{Matheus Paixao}
+% Biography text here.
+% \end{IEEEbiographynophoto}
+
+% \begin{IEEEbiographynophoto}{Giuseppe Bianco}
+% Biography text here.
+% \end{IEEEbiographynophoto}
+
+% % insert where needed to balance the two columns on the last page with
+% % biographies
+% %\newpage
+
+% \begin{IEEEbiographynophoto}{Rocco Oliveto}
+% Biography text here.
+% \end{IEEEbiographynophoto}
 

### 2017-10-23 cloverflow-tse/cloverflow.tex
Fixed the new FIXME (version to send to Nassim).

@@
 There were 338 (15\%) conflicts between 
-true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC) \FIXME{How have
-  they been resolved?}. 
+true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC).
+The investigators looked at each conflicting pair together and
+discussed until a consensus was made. 
 Another 270 pairs (12\%) were
@@
 the true clone pairs. Among these pairs, 145 conflicts were caused by
-one investigator being more careful than the other and able to find evidence of 
-copying while the other could not. Resolving the conflicts lead to a better classification,
+one investigator being more careful than the other and being able to find evidence of 
+copying while the other could not. Thus, resolving the conflicts lead to a better classification,
  i.e.~from UD to QS or EX.

### 2017-10-24 cloverflow-tse/piechart.m
Clean up.

@@ -1,2 +1,0 @@
-X = [0 1 13 32 66];
-pie(X)

### 2017-10-29 cloverflow-tse/cloverflow.tex
Fixed a small typo.

@@
 		clone oracle:} The 2,302 manually investigated and validated online clone pairs
-	are available for download\footnote{\FIXME{ADD THIS URL}} and
+	are available for download\footnote{https://ucl-crest.github.io/cloverflow-web} and
 	can be used as a clone oracle. \end{enumerate}
@@
 		\toprule
-		Stats & \multicolumn{1}{c}{Total clone pairs} & \multicolumn{1}{c}{Average clone size} \\
+		Tool & \multicolumn{1}{c}{Total clone pairs} & \multicolumn{1}{c}{Average clone size} \\
 		\midrule

### 2017-11-01 cloverflow_technical_report/cloverflow_survey_rn.tex
Improved the paper a little bit. Added some FIXMEs.

@@
 
-\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ The Online Survey}
+\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ An Online Survey}
 %\subtitle{Do you have a subtitle?\\ If so, write it here}
@@
 
+\FIXME{Should Rocco be added as an author?}
+
+\FIXME{Check all occurrences of violating.}
+
+\FIXME{Merge changes to the bib file from the TSE version.}
+
 \begin{abstract}
 We performed two online surveys of Stack Overflow answerers and visitors to
-assess their awareness to outdated code and software license in Stack Overflow
-answerers. The answerer survey targets 607 highly reputable Stack Overflow users
-and receives an impressive response rate of 33\%. Our findings are as follows.
+assess their awareness to outdated code and software licenses in Stack Overflow
+answerers. The answerer survey targeted 607 highly reputed Stack Overflow users
+and received a high response rate of 33\%. Our findings are as follows.
 Although most of the code snippets in the answers are written from scratch,
-there are code snippets cloned from the questions, personal or company projects,
-and from open source projects. Stack Overflow answerers are aware that some of
+there are code snippets cloned from the corresponding questions, from personal or company projects,
+or from open source projects. Stack Overflow answerers are aware that some of
 their snippets are outdated. However, 19\% of the participants report that they
-rarely or never fix the code. At least 98\% of the answerers never include
-software license in their snippets and 69\% never check for licensing conflicts
+rarely or never fix their outdated code. At least 98\% of the answerers never include
+software licenses in their snippets and 69\% never check for licensing conflicts
 with Stack Overflow's CC BY-SA 3.0 if they copy the code from other sources to
-Stack Overflow answers. The visitor survey uses convenient sampling and receives
-89 responses. We found that 66\% of the participants experience a problem from
+Stack Overflow answers. The visitor survey uses convenient sampling and received
+89 responses. We found that 66\% of the participants experienced a problem from
 cloning and reusing Stack Overflow snippets. Fifty-six percent of the visitors
-never report the problems back to Stack Overflow. Eighty-five percent of the
-participants are not aware of CC BY-SA 3.0 license, and sixty-two percent never
+never reported the problems back to the Stack Overflow post. Eighty-five percent of the
+participants are not aware that StackOverflow applies the CC BY-SA 3.0 license, and sixty-two percent never
 give attributions to Stack Overflow posts or answers they copied the code from.
@@
 the copied Stack Overflow code and their software. With these findings, we
-suggest Stack Overflow raise an awareness of their users, both the answerers and
-the visitors, to the problem of outdated and license-violating code snippets.
+suggest Stack Overflow raise awareness of their users, both answerers and
+visitors, to the problem of outdated and license-violating code snippets.
 \end{abstract}
@@
 introduce vulnerabilities. On the other hand, \cite{German2009} found that code
-cloning leads to conflicts in software license among different systems.
+cloning leads to software license conflicts among different systems.
 
@@
 to be problematic. \cite{Acar2016} discovered that many code snippets provided
-as solutions on Stack Overflow are workarounds and occasionally contains defects
+as solutions on Stack Overflow are workarounds and occasionally contain defects
 or vulnerabilities. They performed a user study and found that although Stack
@@
 official Android documentation. Only 17\% of the Stack Overflow discussion
-threads the participant visited during the study contain secure code snippets.
+threads the participant visited during the study contained secure code snippets.
 They also found a similar piece of an API call copied from Stack Overflow by
@@
 from Google Play. In addition, \cite{An2017} investigated clones between 399
-Android apps and Stack Overflow posts. They found 1,226 code snippets which were
+Android apps and Stack Overflow posts. They found 1,226 code snippets that were
 reused from 68 Android apps. They also observed that there are 1,279 cases of
@@
 code snippets copied from other sources. The copied snippets on Stack Overflow
-is a snapshot of the code at the time of copying. They are less frequently
+are snapshots of the code at the time of copying. They are less frequently
 updated than in normal software projects and might not be up-to-date with their
 originals, which are further modified due to bug fixing or feature improvements.
-Besides, Some snippets are copied from software systems with stricter license
+Besides, some snippets are copied from software systems with stricter licenses
 than Stack Overflow's Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0). Prior
@@
 The main objective of the survey is to understand the developers' awareness and
-experience to outdated code and code licensing on Stack Overflow. It can break
-down into the following five research questions.
+experience to outdated code and code licensing on Stack Overflow. It addresses
+the following five research questions.
 
@@
 	\item \textbf{RQ4 (Problems from Stack Overflow code snippets):} \textit{What are the problems Stack Overflow visitors experiencing from reusing code snippets on Stack Overflow?}
-	\item \textbf{RQ5 (Software license of Stack Overflow code snippets):}\textit{Are Stack Overflow visitors aware of code licensing on Stack Overflow}
+	\item \textbf{RQ5 (Software license of Stack Overflow code
+            snippets):} \textit{Are Stack Overflow visitors aware of code licensing on Stack Overflow?}
 \end{enumerate}
@@
 Google Forms. We created two versions of the
-survey: \textbf{the answerer survey}, and, \textbf{the visitor survey}. Both
+survey: \textbf{the answerer survey} and \textbf{the visitor survey}. Both
 surveys are completely anonymous and the participants could decide to leave at
@@
 license when they copy code snippets to Stack Overflow, and additional
-feedbacks. The survey was open for participation for 50 days, from 25 July 2017
+feedback. The survey was open for participation for 50 days, from 25 July 2017
 to 12 September 2017, before we collected and analysed the responses.
@@
 snippets, problems from Stack Overflow snippets, licensing of code on Stack
-Overflow, and additional feedbacks. The survey was open for participation for 2 months, 
+Overflow, and additional feedback. The survey was open for participation for 2 months, 
 from 25 July 2017 to 25 September 2017, before we collected and analysed
@@
 the community trusts the user. A user earns reputation when he or she receives
-upvotes for good questions and useful answers. Accepted answers receive more
+upvotes for good questions and useful answers. \FIXME{I don't
+  understand the sentence:} Accepted answers receive more
 reputation score than questions and regular answers\footnote{Stack Overflow
@@
 group had a reputation from 963,731 (the highest) to 7,674, and the second group
-had a reputation from 7,636 to 6,999 which we sent out 300 and 307 emails
-(excluding undelivered ones) respectively.
+had a reputation from 7,636 to 6,999. We sent out 300 and 307 emails
+(excluding undelivered ones) to the two groups respectively.
 
@@
 discussion forum mentioning the requirements to take the survey. The third
-channel collects answers from the University of Molise from the help of an
-external researcher. The last two channels are from a
-\textsf{comp.lang.java.programmer} Google groups and Software Engineering
+channel collected answers from the University of Molise with the help of an
+external researcher. The last two channels are the
+\textsf{comp.lang.java.programmer} group and the Software Engineering
 Facebook page. The number of participants taken the survey is shown in
@@
 (27\% response rate) from the second group of Stack Overflow answerers. The response
-rate from both groups was high considered other online survey in software
-engineering that received approximately 14--20\%~\FIXME{double-check the
-	citation again for the magic numbers.}~\citep{Punter2003}.
+rate from both groups was high considering other online surveys in software
+engineering~\citep{Punter2003}.
 
@@
 Group 2 follow the same trend (very frequently for 32.1\% and frequently for
-36.9\%). Interestingly, there is one participant who never includes code snippet
-in his/her answer thus the results after this question is from 116 participants.
+36.9\%). Interestingly, there is one participant in the first group who never includes code snippet
+in his/her answer thus the results after this question is from 116
+participants of the first group.
 
@@
 answers. We found that only 0.5\% and 5.2\% of the answerers in Group 1
-frequently or occasionally been notified. The answerers in Group 2 have very
+are frequently or occasionally been notified. The answerers in Group 2 have very
 frequently and occasionally been notified for 2.4\% and 3.5\% respectively.
 Please note that we found inconsistencies between the answers of these two
-questions. The percentage of participants who ``Never'' been notified of
+questions. The percentage of participants who have ``Never'' been notified of
 outdated code in their Stack Overflow answers are 38.8\% and 52.9\% for Group 1
-and Group 2 respectively. However, the answers for frequency of being notified
+and Group 2 respectively. However, the answers for the frequency of being notified
 equal to ``Never'' decrease to 28.4\% and 43.5\% for Group 1 and 2 respectively
@@
 
-Regarding this issue of outdated code, one participant expresses their concern
+Regarding the issue of outdated code, one participant expresses their concern
 in the open comment question: \textit{``The main problem for me/us is outdated
@@
 			answers. Nonetheless, there are approximately 19\% of the answerers who rarely
-			or never fix their outdated code.} }%
+			or never fix their outdated code for which
+                        they have been notified.} }%
 }
@@
 Almost every answerer in both groups, 114 out of 116 (98\%) and 84 out of 85
-(99\%) respectively, does not include license statement in their code snippets
+(99\%) respectively, do not include license statement in their code snippets
 (numbers are shown in Figure~\ref{fig:survey_license}). Some of the participants
@@
 Since Stack Overflow is among the first research to solve programming tasks, we
-ask the participants how frequently they reuse code snippets from answers on
+asked the participants how frequently they reuse code snippets from answers on
 Stack Overflow. According to the results (see
@@
 times a week, 27 (30\%) do copying once or twice a week. There are 2
-participants (2\%) who never copy the code from Stack Overflow.
+participants (2\%) who never copy code from Stack Overflow.
 
@@
 
-To sum up, Stack Overflow is ranked higher than official documentations, online
-repositories, and book as the resource to look for programming solutions.
+To sum up, Stack Overflow is ranked higher than official documentation, online
+repositories, and books as the resource to look for programming solutions.
 Developers rely on Stack Overflow answers because they are easy to search for on
@@
 
-We asked the visitors whether they have any problem from reusing Stack Overflow
+We asked the visitors whether they have had any problem from reusing Stack Overflow
 code snippets and how often did the problems occur.  Fifty seven (out of eighty
@@
 Figure~\ref{fig:survey_visitor_problems}) include incorrect solutions, i.e.~the
-code claims to solve the problem in the question while it does not,  (28 out of
+code claims to solve the problem in the question while it does not  (28 out of
 57 $\approx$ 49\% participants reported this); outdated solutions, i.e.~the code
 may work with the some older versions of the library or API, but not the one
-they are using, (39 out of 57 $\approx$ 68\% participants reported this);
+they are using (39 out of 57 $\approx$ 68\% participants reported this);
 mismatched solutions, i.e.~the code solves the problem in the question but it is
-not exactly the right solution for their problem, (40 out of 57 $\approx$ 70\%
+not exactly the right solution for their problem (40 out of 57 $\approx$ 70\%
 participants reported this); and buggy code (1 out of 57 $\approx$ 2\%
@@
 did so by writing a comment (10), down-voting the answer (8), contacted the
-answerer (2), and posting the new and correct answer (2), as shown in
-Figure~\ref{fig:survey_visitor_how_report_problems}.
+answerer (2), and posting the new and correct answer (2) (shown in
+Figure~\ref{fig:survey_visitor_how_report_problems}).
 
@@
 		\textit{For RQ4, our survey results show that 57 out of 87 Stack Overflow
-			visitors find a problem from reusing Stack Overflow code snippets. Ten
-			participants experience the problems from more than 80\% of the copied snippets and
-			sixteen participants face the problems from 40--60\% of the reused code. The
+			visitors encountered a problem from reusing Stack Overflow code snippets. Ten
+			participants experienced problems for more than 80\% of the copied snippets and
+			sixteen participants faced problems for 40--60\% of the reused code. The
 			problems ranked by frequency include mismatched solutions (40), outdated
@@
 when reusing Stack Overflow code (see
-Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, possibly due
-to their fairly small size of code which might fall under fair use, only 9\% of
-the participants experience legal issues by reusing code snippets on Stack
-Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}). Nonetheless, as we designed the
-survey to be anonymous, it is not possible to contact them for further details
-on the legal issues they found.
+Figure~\ref{fig:survey_visitor_licensing_conflict_check}). Lastly, 9\% of
+the participants experienced legal issues by reusing code snippets on Stack
+Overflow (see Figure~\ref{fig:survey_visitor_legal_issue}). We did not
+expect that any participant encountered legal issues as we are not
+aware of such cases being reported in the literature. It would
+be interesting to followup on the kind of legal issues that have been
+encountered, however, as we designed the
+survey to be anonymous, it was not possible to contact the participants for further details.
 
@@
 	licensing conflicts between Stack Overflow code snippets and their projects.
-	However, only 9\% of the participants encountered legal issues.}}%
+	9\% of the participants encountered legal issues.}}%
 } \vspace{0.5cm}
 
+\FIXME{Add an overall discussion.}
+
 \section{Threats to Validity}
@@
 \subsection{Internal Validity}
-Due to a large number of users on Stack Overflow, we could invite only 607
+We only invited 607
 developers to participate in the answerer survey. If all the developers are
@@
 \cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
-\cite{Yang2017} analysed 909k non-fork Python projects on Github and 1.9 million
+\cite{Yang2017} analysed 909k non-fork Python projects on GitHub and 1.9 million
 python code snippets on Stack Overflow and found thousands of code blocks that
@@
 is usually written from scratch to answer a question. Nonetheless, there are
-some code snippets that are copied from the answerer personal or company
-projects, and open source software.
+some code snippets that are copied from the answerer's personal or company
+projects, or from open source software.
 
@@
 rarely or never fix the code. One answerer expresses a concern of having
-an outdated code in his/her popular answer reused
+outdated code in his/her popular answer reused
 by many other developers.
 
-Approximately 60\% of the answerers are aware of Stack Overflow CC BY-SA 3.0
-license applied to code on Stack Overflow. Ninety-eight to ninety-nine percent
-does not include license in their answers nor check for licensing conflicts when
+Approximately 60\% of the answerers are aware that Stack Overflow
+applies the CC BY-SA 3.0
+license to code on Stack Overflow. Ninety-eight to ninety-nine percent
+do not include a license in their answers nor check for licensing conflicts when
 they copy the code from another location to their answer. Some developers
@@
 the code from. Moreover, sixty-six percent never check for licensing conflicts while
-reusing Stack Overflow code snippets in their software projects.
+reusing Stack Overflow code snippets in their software
+projects. Unexpectedly, 9\%
+of the participants encountered legal issues.
 

### 2017-11-03 cloverflow_technical_report/cloverflow_survey_rn.tex
Solved the FIXMEs. Still working on the overall discussion.

@@
 
-\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ An Online Survey}
+\title{Awareness and Experience of Developers to\\ Outdated and License-incompatible Code on Stack Overflow:\\ An Online Survey}
 %\subtitle{Do you have a subtitle?\\ If so, write it here}
 
-\titlerunning{SO Developers awareness: Outdated and License-violating Code}        % if too long for running head
-
-\author{Chaiyong~Ragkhitwetsagul, Jens~Krinke}
+\titlerunning{SO Developers awareness: Outdated and License-incompatible Code}        % if too long for running head
+
+\author{Chaiyong~Ragkhitwetsagul, Jens~Krinke, Rocco~Oliveto}
 
@@
 
-\FIXME{Should Rocco be added as an author?}
-
-\FIXME{Check all occurrences of violating.}
+%\FIXME{Should Rocco be added as an author?}
+
+%\FIXME{Check all occurrences of violating.}
 
@@
 rarely or never fix their outdated code. At least 98\% of the answerers never include
-software licenses in their snippets and 69\% never check for licensing conflicts
+software licenses in their snippets and 69\% never check for licensing compatibility
 with Stack Overflow's CC BY-SA 3.0 if they copy the code from other sources to
@@
 give attributions to Stack Overflow posts or answers they copied the code from.
-Moreover, 66\% of the participants do not check for licensing conflicts between
+Moreover, 66\% of the participants do not check for licensing compatibility between
 the copied Stack Overflow code and their software. With these findings, we
 suggest Stack Overflow raise awareness of their users, both answerers and
-visitors, to the problem of outdated and license-violating code snippets.
+visitors, to the problem of outdated and license-incompatible code snippets.
 \end{abstract}
@@
 Recent research shows that outdated third-party code and software licensing
-conflicts are ramifications by code cloning, i.e.~reusing source code by copying
+incompatibility are ramifications by code cloning, i.e.~reusing source code by copying
 and pasting. \cite{Xia2014} report that a large number of open source systems
@@
 introduce vulnerabilities. On the other hand, \cite{German2009} found that code
-cloning leads to software license conflicts among different systems.
+cloning leads to software license incompatibility among different systems.
 
@@
 that many snippets were copied from open source projects. Some cloned snippets
-are outdated (or obsolete) and some possibly violate the original software
+are outdated (or obsolete) and some possibly incompatible with the original software
 license. These snippets are potentially harmful to reuse. To accompany the
@@
 	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
-	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing conflicts):} \textit{Are Stack Overflow answerers aware of software licensing
-		conflicts caused by code snippets in their answers?}
+	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing compatibility):} \textit{Are Stack Overflow answerers aware of software licensing
+		incompatibility caused by code snippets in their answers?}
 %	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
@@
 the community trusts the user. A user earns reputation when he or she receives
-upvotes for good questions and useful answers. \FIXME{I don't
-  understand the sentence:} Accepted answers receive more
-reputation score than questions and regular answers\footnote{Stack Overflow
-	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
+upvotes for good questions and useful answers. \FIXME{I don't understand the
+	sentence. @Jens Ok now?:} For example, they gain reputation when they receives a vote up for
+their question (+5), a vote up for their answer (+10), or a marking as accepted answer (+15)\footnote{Stack
+	Overflow Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
 Overflow reputation is an indicator of user's skills and their involvement in
@@
 \subsubsection*{RQ3: Are Stack Overflow answerers aware of software licensing
-	conflicts caused by code snippets in their answers?}
+	incompatibility caused by code snippets in their answers?}
 
@@
 
-We asked the answerers a follow-up question of how frequently they checked for a
-conflict between software license of the code snippets they copied to their
+We asked the answerers a follow-up question of how frequently they checked for compatibility between software license of the code snippets they copied to their
 answers and Stack Overflow's CC BY-SA 3.0. As shown in
@@
 group 1 and group 2 did not perform the checking. There are only approximately
-10\% of the answerers who frequently checks for licensing conflicts when they
+10\% of the answerers who frequently checks for licensing compatibility when they
 copy code snippets to Stack Overflow.
@@
 			never include software license in their Stack Overflow snippets. Sixty-nine
-			percent never check for licensing conflicts when they copy code snippets to
+			percent never check for licensing compatibility when they copy code snippets to
 			Stack Overflow answers.} }%
@@
 
-Fifty seven participants (66\%) never check for licensing conflicts at all
+Fifty seven participants (66\%) never check for licensing compatibility at all
 when reusing Stack Overflow code (see
@@
 	\includegraphics[width=.4\linewidth]{survey_visitor_licensing_conflict_check} 
-	\caption{Checking for licensing conflicts from reusing Stack Overflow snippets}
+	\caption{Checking for licensing compatibility from reusing Stack Overflow snippets}
 	\label{fig:survey_visitor_licensing_conflict_check} 
@@
 			they copied the code snippets from. We found that 66\% of the visitors never check for software
-	licensing conflicts between Stack Overflow code snippets and their projects.
+	licensing compatibility between Stack Overflow code snippets and their projects.
 	9\% of the participants encountered legal issues.}}%
@@
 
-\FIXME{Add an overall discussion.}
+%\FIXME{Add an overall discussion.}
+
+\subsection{Overall Discussion}
+
+\subsubsection{Stack Overflow Answerers}
+By separating the answerers into two groups, we are able to compare the answers and
+observe similarities or differences in their answers according to their reputation. In summary, we found the
+following.
+
+The sources of code snippets in Stack Overflow answers are similar in both
+groups. The answerers mainly write the code snippets from scratch aiming to
+answer the question. Considering the frequencies of copying from each source,
+i.e.~personal projects, company projects, open source projects, writing from
+scartch, modifying from the questions, and others, they also follow the same
+proportion for both group.
+
+The answerers in Group 1 have larger percentage (61.2\%) of being notified about
+outdated code in their answers than Group 2 (47.1\%). Nevertheless, since
+Group-1 answerers have higher reputation than Group-2 answerers, they
+potentially have given more answers on Stack Overflow than Group 2. The higher amount of
+answers may increase the chance of the code being outdated. Nevertheless, while the number of being notified of
+outdated code is lower, the percentage of the answerers in Group 2 who very
+frequently fixed their outdated code are higher than of Group 1.
+
+Regarding software license, the answerers in both groups show the same level of
+awareness to Stack Overflow CC BY-SA 3.0 license (62.1\% and 62.3\%). Similarly,
+the answerers in both groups neither include software license in their code
+snippets (98\% and 99\%) nor check of license compatibility between their
+code snippet's and Stack Overflow CC BY-SA 3.0 (69\%).
+
+\subsubsection{Stack Overflow Visitors}
 
@@
 licensing statements change over time. \cite{German2009} found that licensing
-conflicts occur between the clone siblings, i.e.~clones among different systems
+incompatibility occur between the clone siblings, i.e.~clones among different systems
 that come from the same source. Later, \cite{German2010} created an automated
@@
 \textit{awareness} of Stack Overflow developers, both answerers and visitors,
-to the problem of outdated and license-violating code.
+to the problem of outdated and license-incompatible code.
 
@@
 license to code on Stack Overflow. Ninety-eight to ninety-nine percent
-do not include a license in their answers nor check for licensing conflicts when
+do not include a license in their answers nor check for licensing compatibility when
 they copy the code from another location to their answer. Some developers
@@
 3.0 and sixty-two percent never give attributions to Stack Overflow posts that they copied
-the code from. Moreover, sixty-six percent never check for licensing conflicts while
+the code from. Moreover, sixty-six percent never check for licensing compatibility while
 reusing Stack Overflow code snippets in their software
@@
 suggest Stack Overflow raise an awareness of their users, both the answerers and
-the visitors, to the problem of outdated and license-violating code snippets.
+the visitors, to the problem of outdated and license-incompatible code snippets.
 

### 2017-11-04 cloverflow_technical_report/cloverflow_survey_rn.tex
Completed the overall discussion and added Baltes et al. study to the Related Work.

@@
 upvotes for good questions and useful answers. \FIXME{I don't understand the
-	sentence. @Jens Ok now?:} For example, they gain reputation when they receives a vote up for
-their question (+5), a vote up for their answer (+10), or a marking as accepted answer (+15)\footnote{Stack
+	sentence. @Jens Ok now?:} For example, they gain reputation when they receives an upvote for
+their question (+5), an upvote for their answer (+10), or a marking as accepted answer (+15)\footnote{Stack
 	Overflow Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
@@
 discussion forum mentioning the requirements to take the survey. The third
-channel collected answers from the University of Molise with the help of an
-external researcher. The last two channels are the
+channel collected answers from the University of Molise in Italy, where the third author
+works. The last two channels are the
 \textsf{comp.lang.java.programmer} group and the Software Engineering
@@
 We asked the visitors whether they have had any problem from reusing Stack Overflow
-code snippets and how often did the problems occur.  Fifty seven (out of eighty
-seven) participants (see Figure~\ref{fig:survey_v_problems}) experienced a
-problem from reusing Stack Overflow snippets. Among the 57, there are 2
+code snippets and how often did the problems occur.  Fifty seven out of eighty
+seven participants (66\%) experienced a
+problem from reusing Stack Overflow snippets (see Figure~\ref{fig:survey_v_problems}). Among the 57, there are 2
 participants who found problems in more than 80\% of the reused code snippets.
@@
 
-\subsubsection{Stack Overflow Answerers}
-By separating the answerers into two groups, we are able to compare the answers and
-observe similarities or differences in their answers according to their reputation. In summary, we found the
-following.
-
-The sources of code snippets in Stack Overflow answers are similar in both
-groups. The answerers mainly write the code snippets from scratch aiming to
-answer the question. Considering the frequencies of copying from each source,
-i.e.~personal projects, company projects, open source projects, writing from
-scartch, modifying from the questions, and others, they also follow the same
-proportion for both group.
-
-The answerers in Group 1 have larger percentage (61.2\%) of being notified about
-outdated code in their answers than Group 2 (47.1\%). Nevertheless, since
-Group-1 answerers have higher reputation than Group-2 answerers, they
-potentially have given more answers on Stack Overflow than Group 2. The higher amount of
-answers may increase the chance of the code being outdated. Nevertheless, while the number of being notified of
-outdated code is lower, the percentage of the answerers in Group 2 who very
-frequently fixed their outdated code are higher than of Group 1.
-
-Regarding software license, the answerers in both groups show the same level of
-awareness to Stack Overflow CC BY-SA 3.0 license (62.1\% and 62.3\%). Similarly,
-the answerers in both groups neither include software license in their code
-snippets (98\% and 99\%) nor check of license compatibility between their
-code snippet's and Stack Overflow CC BY-SA 3.0 (69\%).
+By separating the answerers into two groups according to their reputation, we
+observed some similarities and differences in their responses. The sources of
+code snippets in Stack Overflow answers are similar in both groups. The
+answerers mainly write the code snippets from scratch aiming to answer the
+question. The frequencies of copying from each source, i.e.~personal projects,
+company projects, open source projects, writing from scratch, modifying from the
+questions, and others, also follow the same proportions for both group.
+
+The main difference we found is responses regarding outdated code. The answerers
+in Group 1 have a more substantial percentage (61.2\%) of being notified about
+the outdated code in their answers than Group 2 (47.1\%). This may be caused by
+the amount of their Stack Overflow answers. Since Group-1 answerers have a
+higher reputation than Group-2 answerers, they possibly have given more answers
+on Stack Overflow. The higher amount of answers hence increase the chance of the
+code being outdated. Interestingly, although the percentage of outdated code
+notifications in Group 2 is lower, the percentage of the answerers who very
+frequently fixed their outdated code is higher than of Group 1.
+
+Regarding software license, the responses from the two groups agree with each
+other. The answerers in both groups show the same level of awareness to Stack
+Overflow CC BY-SA 3.0 license (62.1\% and 62.3\%). Similarly, the answerers in
+both groups neither include software license in their code snippets (98\% and
+99\%) nor check of license compatibility between their code snippet's and Stack
+Overflow CC BY-SA 3.0 (69\%).
+
+The visitors survey confirms the findings from the previous studies that Stack
+Overflow code snippets can be problematic~\citep{Acar2016,An2017}. Sixty-six
+percent of the visitors experienced a problem from reusing Stack Overflow code
+snippets ranging from incorrect solutions, outdated solutions, mismatched
+solutions, to buggy code. Although they are aware of the problems, half of them
+(56\%) never reports back to the Stack Overflow discussions. On the other hand,
+the visitors rarely give attributions to Stack Overflow when they reuse code
+snippets from the website, similar to the findings reported
+by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
+license, and more than half of them never check for license compatibility when
+reusing Stack Overflow code snippets. We also found that 9\% of the participants
+encountered legal issues by copying code from Stack Overflow. To the best of our
+knowledge, a study of legal problems from reusing Stack Overflow code snippets
+has never been done before and will be our future work.
 
@@
 python code snippets on Stack Overflow and found thousands of code blocks that
-are copied from Stack Overflow to GitHub.
+are copied from Stack Overflow to GitHub. \cite{Baltes2017} discovered that two
+third of the clones from 10 most frequently referenced Java code snippets on Stack
+Overflow do not contain attributions.
 

### 2017-11-05 cloverflow-tse/cloverflow.tex
Added Baltest et al. to Related Work.

@@
 The work that are closely similar to us are studies by An et al.~\cite{An2017}
-and Abdalkareem et al.~\cite{Abdalkareem2017}. An et al.~investigated clones
+Abdalkareem et al.~\cite{Abdalkareem2017}, and Baltest et al.~\cite{Baltes2017}. 
+An et al.~investigated clones
 between 399 Android apps and Stack Overflow posts. They found 1,226 code
@@
 with statistical significance.
+Baltes et al.~\cite{Baltes2017} discovered that two
+third of the clones from 10 most frequently referenced Java code snippets on Stack
+Overflow do not contain attributions.
 %In our work, we defined seven patterns of online code cloning and 

### 2017-11-07 cloverflow-tse/cloverflow.tex
Small fixes to the TSE paper:
1) address the threat to validity of selecting only accepted answers.
2) modify RQ2 to "how" question instead of "why".

@@
 	problem. 
-	\item \textbf{RQ2 (Patterns of online code clones): }\textit{Why do online
+	\item \textbf{RQ2 (Patterns of online code clones): }\textit{How do online
 		code clones occur?} We categorised online clones into seven
-	categories allowing insights to why online code clones are created.
+	categories allowing insights to how online code clones are created.
 	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
@@
 \vspace{0.25cm}
-\textit{Why do online code clones occur?}
+\textit{How do online code clones occur?}
 \vspace{0.25cm}
@@
 \textbf{Internal validity:} 
-We applied
-different mechanisms to ensure the validity of the clone
-pairs we classified.  First, we used two widely-used
-clone detection tools, Simian and SourcererCC.  We tried five other
-clone detectors but could not add them to the study due to their
-scalability issues and susceptibility to incomplete code snippets.
-We adopted Bellon's agreement metric~\cite{Bellon2007}
-to merge clone pairs for the manual
-classification and avoid double counting of the same clone pairs. 
-Nevertheless, our study might still suffer from false negatives, i.e.~online 
-code clones that are not reported by the tools or are filtered 
-out by the size (less than 10 lines) within the clone detection process.
+We applied different mechanisms to ensure the validity of the clone pairs we
+classified.  First, we used two widely-used clone detection tools, Simian and
+SourcererCC.  We tried five other clone detectors but could not add them to the
+study due to their scalability issues and susceptibility to incomplete code
+snippets. We adopted Bellon's agreement metric~\cite{Bellon2007} to merge clone
+pairs for the manual classification and avoid double counting of the same clone
+pairs. Nevertheless, our study might still suffer from false negatives,
+i.e.~online code clones that are not reported by the tools or are filtered out
+by the size (less than 10 lines) within the clone detection process. We selected
+Stack Overflow accepted answers in this study to focus on code snippets that
+solve problems in the question and are often showed on top of the answer list.
+While most of the time they are also the highest voted answers, there is some
+time that they are not. We plan to incorporate the highest voted answers in the
+future work.
 % We also

### 2017-11-07 cloverflow_technical_report/cloverflow_survey_rn.tex
Fixed the last FIXME.

@@
 
-\FIXME{Merge changes to the bib file from the TSE version.}
+%\FIXME{Merge changes to the bib file from the TSE version.}
 
@@
 the community trusts the user. A user earns reputation when he or she receives
-upvotes for good questions and useful answers. \FIXME{I don't understand the
-	sentence. @Jens Ok now?:} For example, they gain reputation when they receives an upvote for
-their question (+5), an upvote for their answer (+10), or a marking as accepted answer (+15)\footnote{Stack
+upvotes for good questions and useful answers. For example, they gain reputation when they receive an upvote for
+their question (+5) or their answer (+10), or when their answer is accepted (+15)\footnote{Stack
 	Overflow Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack

### 2017-11-07 cloverflow-tse/cloverflow.tex
Checked occurences of violations.

--- 2017-10-29 cloverflow-tse/cloverflow.tex
@@
 
-\title{Toxic code snippets on Stack Overflow}
+\title{Toxic Code Snippets on Stack Overflow}
 
@@
 \markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, Month~2017}%
-{Ragkhitwetsagul \MakeLowercase{\textit{et al.}}: Outdated and License-Violating Code on Stack Overflow}
+{Ragkhitwetsagul \MakeLowercase{\textit{et al.}}: Toxic Code Snippets on Stack Overflow}
 % The only time the second header will appear is for the odd numbered pages
@@
 of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
-we found 214 code snippets on Stack Overflow that violate the license of their
+we found 214 code snippets on Stack Overflow that could potentially violate the license of their
 original software. We surveyed 201 high-reputation Stack Overflow answerers
@@
 code from one project to another project with a different license may
-cause a software licensing violation~\cite{German2009}. This also
+cause a software license violation~\cite{German2009}. This also
 happens within the context of online Q\&A websites such as Stack
@@
 cod snippets.
-The first example is outdated and license-violating online code clones in an
+The first example is an outdated and potentially license-violating online code clone in an
 answer to a Stack Overflow question regarding how to implement
@@
 	\item \textbf{RQ4 (Software licensing violation): }\textit{How often do
-		licensing conflicts occur between Stack Overflow clones and their
+		license conflicts occur between Stack Overflow clones and their
 		originals?} We investigated whether the reuse of online code clones
@@
 Similarly, for RQ4, we looked at the license of each clone in the pattern QS,
-EX, UD and checked for a possibility of licensing violation (phase 6). We use
+EX, UD and checked for a possibility of license violation (phase 6). We use
 the online survey to answer RQ5.
@@
 
-\subsection{RQ4: Software Licensing Violation}
+\subsection{RQ4: Software Licensing Violations}
 \vspace{0.25cm}
@@
 \textbf{For RQ4, we found 214 code snippets on Stack Overflow that
-	could violate the license of their original software. The majority of them
+	could potentially violate the license of their original software. The majority of them
 	do not contain licensing statements after they have been copied to
@@
 
-Note that the code snippets could violate the license, but do
+Note that the code snippets could potentially violate the license, but do
 not necessarily do so. In the example where the JFreeChart
@@
 \textbf{Internal validity:} 
-We applied
-different mechanisms to ensure the validity of the clone
-pairs we classified.  First, we used two widely-used
-clone detection tools, Simian and SourcererCC.  We tried five other
-clone detectors but could not add them to the study due to their
-scalability issues and susceptibility to incomplete code snippets.
-We adopted Bellon's agreement metric~\cite{Bellon2007}
-to merge clone pairs for the manual
-classification and avoid double counting of the same clone pairs. 
-Nevertheless, our study might still suffer from false negatives, i.e.~online 
-code clones that are not reported by the tools or are filtered 
-out by the size (less than 10 lines) within the clone detection process.
+We applied different mechanisms to ensure the validity of the clone pairs we
+classified.  First, we used two widely-used clone detection tools, Simian and
+SourcererCC.  We tried five other clone detectors but could not add them to the
+study due to their scalability issues and susceptibility to incomplete code
+snippets. We adopted Bellon's agreement metric~\cite{Bellon2007} to merge clone
+pairs for the manual classification and avoid double counting of the same clone
+pairs. Nevertheless, our study might still suffer from false negatives,
+i.e.~online code clones that are not reported by the tools or are filtered out
+by the size (less than 10 lines) within the clone detection process. We selected
+accepted answers on Stack Overflow in this study to focus on code snippets that
+solve the question's problem and are often showed on top of the answer list.
+While most of the time they are also the highest voted answers, some
+times they are not. We plan to incorporate the highest voted answers in 
+future work.
 % We also
@@
 
-The work that are closely similar to us are studies by An et al.~\cite{An2017}
-and Abdalkareem et al.~\cite{Abdalkareem2017}. An et al.~investigated clones
+Work similar to ours are studies by An et al.~\cite{An2017}
+Abdalkareem et al.~\cite{Abdalkareem2017}, and Baltes et al.~\cite{Baltes2017}. 
+An et al.~investigated clones
 between 399 Android apps and Stack Overflow posts. They found 1,226 code
@@
 with statistical significance.
+Baltes et al.~\cite{Baltes2017} discovered that two
+thirds of the clones from the 10 most frequently referenced Java code snippets on Stack
+Overflow do not contain attributions.
 %In our work, we defined seven patterns of online code cloning and 
@@
 We performed a detailed analysis of the online clone pairs on two
-aspects: outdated code and licensing violation. The investigation of
+aspects: outdated code and potential license violation. The investigation of
 the 154 clone pairs copied, with evidence, from Qualitas to Stack
 Overflow reveals that 101 of them are outdated.  Moreover, we found 214
-code snippets on Stack Overflow that violate the license of their
+code snippets on Stack Overflow that could potentially violate the license of their
 original software.

### 2017-11-07 cloverflow-tse/cloverflow.tex
Layout improvements.

@@
 websites (such as Stack Overflow) and vice versa as ``online code clones''.
-There are two directions in creating online code clones: (1) code is cloned from
-a software project to a Q\&A website as an example; or (2) code is cloned from a
+There are two directions in creating online code clones: (1)~code is cloned from
+a software project to a Q\&A website as an example; or (2)~code is cloned from a
 Q\&A website to a software project to obtain a functionality, perform a
-particular task, or fixing a bug. % and (3) code is transferred from one
+particular task, or fixing a bug. % and (3)~code is transferred from one
 % software project to another via a Q\&A website;
@@
 cloned from open source software or online sources can become toxic when they
-are (1) outdated or (2) violating their original software
+are (1)~outdated or (2)~violating their original software
 license. Outdated code snippets
@@
 contain defects. Code snippets from open source projects usually fall under a
-specific software license , e.g.~GNU General Public License (GPL). If they are
+specific software license , e.g.\ GNU General Public License (GPL). If they are
 cloned to Stack Overflow answers without the license, and then flow to other projects
@@
 
-	\textit{1) How often are Stack Overflow
+	\textit{1)~How often are Stack Overflow
 		answerers aware of the outdated code when
@@
 \Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
-from source code of Java SDK (e.g.~\textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
+from source code of Java SDK (e.g.\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
 18 pairs from websites, 15 pairs from open
-source systems not in Qualitas (e.g.~\textsf{Mozilla
+source systems not in Qualitas (e.g.\ \textsf{Mozilla
 	Rhino}), 11 pairs from Java official documentations from Sun
@@
 the introduction of vulnerabilities to the software~\cite{Xia2014}. An outdated code with a
-subtle change (e.g.~\Cref{fig:before-after}) may be copied and reused without
-awareness from developers. Moreover, an outdated code with a defect (e.g.~a race
+subtle change (e.g.\ \Cref{fig:before-after}) may be copied and reused without
+awareness from developers. Moreover, an outdated code with a defect (e.g.\ a race
 condition problem in \Cref{fig:before-after_2}) is clearly harmful to be reused.
@@
 code from scratch, copying and modifying the code from the question, and others
-(e.g.~code that are copied from other questions or answers on Stack Overflow)
+(e.g.\ code that are copied from other questions or answers on Stack Overflow)
 and we asked them to rate how often they copied the code from these locations. The
@@
 Many users either declare their snippets to be public domain, or they grant
-additional licenses, e.g. Apache 2.0 or MIT/Expat.
+additional licenses, e.g.\ Apache 2.0 or MIT/Expat.
 
@@
 %We discovered two issues regarding code snippets on Stack Overflow in this
-% study: (1)  outdated online clones on Stack Overflow and (2) missing or
+% study: (1)~outdated online clones on Stack Overflow and (2)~missing or
 % incompatible license in Stack Overflow snippets.
@@
 It is interesting to compare the findings among different programming languages.
-Moreover, other popular software project corpora (e.g.~GitHub) can also be included to increase generalisation of the findings.
+Moreover, other popular software project corpora (e.g.\ GitHub) can also be included to increase generalisation of the findings.
 %

### 2017-11-07 cloverflow_technical_report/cloverflow_survey_rn.tex
Some corrections.

@@
 are copied from Stack Overflow to GitHub. \cite{Baltes2017} discovered that two
-third of the clones from 10 most frequently referenced Java code snippets on Stack
+thirds of the clones from the 10 most frequently referenced Java code snippets on Stack
 Overflow do not contain attributions.

### 2017-11-07 cloverflow_technical_report/cloverflow_survey_rn.tex
Reverted the RN back to use violations

@@
 
-\title{Awareness and Experience of Developers to\\ Outdated and License-incompatible Code on Stack Overflow:\\ An Online Survey}
+\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ An Online Survey}
 %\subtitle{Do you have a subtitle?\\ If so, write it here}
 
-\titlerunning{SO Developers awareness: Outdated and License-incompatible Code}        % if too long for running head
+\titlerunning{SO Developers awareness: Outdated and License-violating Code}        % if too long for running head
 
@@
 rarely or never fix their outdated code. At least 98\% of the answerers never include
-software licenses in their snippets and 69\% never check for licensing compatibility
+software licenses in their snippets and 69\% never check for licensing conflicts
 with Stack Overflow's CC BY-SA 3.0 if they copy the code from other sources to
@@
 give attributions to Stack Overflow posts or answers they copied the code from.
-Moreover, 66\% of the participants do not check for licensing compatibility between
+Moreover, 66\% of the participants do not check for licensing conflicts between
 the copied Stack Overflow code and their software. With these findings, we
 suggest Stack Overflow raise awareness of their users, both answerers and
-visitors, to the problem of outdated and license-incompatible code snippets.
+visitors, to the problem of outdated and license-violating code snippets.
 \end{abstract}
@@
 Recent research shows that outdated third-party code and software licensing
-incompatibility are ramifications by code cloning, i.e.~reusing source code by copying
+conflicts are ramifications by code cloning, i.e.~reusing source code by copying
 and pasting. \cite{Xia2014} report that a large number of open source systems
@@
 introduce vulnerabilities. On the other hand, \cite{German2009} found that code
-cloning leads to software license incompatibility among different systems.
+cloning leads to software license conflicts among different systems.
 
@@
 that many snippets were copied from open source projects. Some cloned snippets
-are outdated (or obsolete) and some possibly incompatible with the original software
+are outdated (or obsolete) and some possibly violate the original software
 license. These snippets are potentially harmful to reuse. To accompany the
@@
 
+We use the term ``license-violating code snippets'' or ``code with licensing conflicts''
+interchangeably to refer to Stack Overflow cloned code snippets that \textit{potentially} violate the
+original license by not including the original license statement in the cloned snippets and
+adopt the Stack Overflow CC BY-SA 3.0 license instead.
+
 \section{Research Methodology}
@@
 	\item \textbf{RQ2 (Awareness of Stack Overflow answerers to outdated code):} \textit{Are Stack Overflow answerers aware of outdated code in their answers?}
-	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing compatibility):} \textit{Are Stack Overflow answerers aware of software licensing
-		incompatibility caused by code snippets in their answers?}
+	\item \textbf{RQ3 (Awareness of Stack Overflow answerers to licensing violations):} \textit{Are Stack Overflow answerers aware of software licensing
+		violations caused by code snippets in their answers?}
 %	\item \textbf{RQ4 (Search for Coding Solutions):} \textit{Where do the developers search for programming solutions?}
@@
 \subsubsection*{RQ3: Are Stack Overflow answerers aware of software licensing
-	incompatibility caused by code snippets in their answers?}
+	violations caused by code snippets in their answers?}
 
@@
 
-We asked the answerers a follow-up question of how frequently they checked for compatibility between software license of the code snippets they copied to their
+We asked the answerers a follow-up question of how frequently they checked for
+conflicts between software license of the code snippets they copied to their
 answers and Stack Overflow's CC BY-SA 3.0. As shown in
@@
 group 1 and group 2 did not perform the checking. There are only approximately
-10\% of the answerers who frequently checks for licensing compatibility when they
+10\% of the answerers who frequently checks for licensing conflicts when they
 copy code snippets to Stack Overflow.
@@
 			never include software license in their Stack Overflow snippets. Sixty-nine
-			percent never check for licensing compatibility when they copy code snippets to
+			percent never check for licensing conflicts when they copy code snippets to
 			Stack Overflow answers.} }%
@@
 
-Fifty seven participants (66\%) never check for licensing compatibility at all
+Fifty seven participants (66\%) never check for licensing conflicts at all
 when reusing Stack Overflow code (see
@@
 	\includegraphics[width=.4\linewidth]{survey_visitor_licensing_conflict_check} 
-	\caption{Checking for licensing compatibility from reusing Stack Overflow snippets}
+	\caption{Checking for licensing conflicts from reusing Stack Overflow snippets}
 	\label{fig:survey_visitor_licensing_conflict_check} 
@@
 			they copied the code snippets from. We found that 66\% of the visitors never check for software
-	licensing compatibility between Stack Overflow code snippets and their projects.
+	licensing conflicts between Stack Overflow code snippets and their projects.
 	9\% of the participants encountered legal issues.}}%
@@
 both groups neither include software license in their code snippets (98\% and
-99\%) nor check of license compatibility between their code snippet's and Stack
+99\%) nor check of licensing conflicts between their code snippet's and Stack
 Overflow CC BY-SA 3.0 (69\%).
@@
 \textit{awareness} of Stack Overflow developers, both answerers and visitors,
-to the problem of outdated and license-incompatible code.
+to the problem of outdated and license-violating code.
 
@@
 license to code on Stack Overflow. Ninety-eight to ninety-nine percent
-do not include a license in their answers nor check for licensing compatibility when
+do not include a license in their answers nor check for licensing conflicts when
 they copy the code from another location to their answer. Some developers
@@
 3.0 and sixty-two percent never give attributions to Stack Overflow posts that they copied
-the code from. Moreover, sixty-six percent never check for licensing compatibility while
+the code from. Moreover, sixty-six percent never check for licensing conflicts while
 reusing Stack Overflow code snippets in their software
@@
 suggest Stack Overflow raise an awareness of their users, both the answerers and
-the visitors, to the problem of outdated and license-incompatible code snippets.
+the visitors, to the problem of outdated and license-violating code snippets.
 

### 2017-11-07 cloverflow_technical_report/cloverflow_survey_rn.tex
Final fixes.

@@
 %
-\smartqed  % flush right qed marks, e.g. at end of proof
+\smartqed
 %
@@
 
+\fancyhead[L]{Outdated and License-Violating Code on Stack Overflow}	
+%\fancyhead[R]{Ragkhitwetsagul, Krinke, Oliveto}
+
 \lstset{language=Java,tabsize=2,basicstyle=\ttfamily\scriptsize}
@@
 
-\title{Awareness and Experience of Developers to\\ Outdated and License-violating Code on Stack Overflow:\\ An Online Survey}
+\title{Awareness and Experience of Developers to\\ Outdated and License-Violating Code on Stack Overflow:\\ An Online Survey}
 %\subtitle{Do you have a subtitle?\\ If so, write it here}
 
-\titlerunning{SO Developers awareness: Outdated and License-violating Code}        % if too long for running head
+\titlerunning{Awareness and Experience of Developers to Outdated and License-Violating Code on Stack Overflow}        % if too long for running head
 
@@
 participants either declare their snippets to be public domain, or they grant
-additional licenses, e.g. Apache 2.0 or MIT/Expat.
+additional licenses, e.g.\ Apache 2.0 or MIT/Expat.
 
@@
 to find programming solutions. The given five options include books, official
-documentations, Stack Overflow, online repositories (e.g. GitHub), and others.
+documentations, Stack Overflow, online repositories (e.g.\ GitHub), and others.
 The results are displayed in Figure~\ref{fig:survey_visitor_rankings-crop}. We
@@
 Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow
-never check if the code snippet originated from a different source (e.g. an open
+never check if the code snippet originated from a different source (e.g.\ an open
 source project) with an incompatible license to their projects (see
@@
 I mostly write from scratch or copy-\&-fix a snippet from the question.
-Most are illustrative or incomplete --- they aren't of any value at all in isolation.
+Most are illustrative or incomplete -- they aren't of any value at all in isolation.
 They rarely take more than a few minutes to write, and it's usually harder to explain what they're doing in plain English.
@@
 In those cases I create a GitHub project (with a license) and link to it.
-I'd be wary of increased IP controls --- I doubt there is value they could add to snippets, but they could create significant barriers to contributors, which would hurt the site.
+I'd be wary of increased IP controls -- I doubt there is value they could add to snippets, but they could create significant barriers to contributors, which would hurt the site.
 	\item I always try to see what kind of person is asking the question.
@@
 	\item I think you're forgetting the fact that as a community, we want to share knowledge.
-Patents, copyright issues and so on --- it's all just annoying.
+Patents, copyright issues and so on -- it's all just annoying.
 We're there to have fun and to share knowledge with people.
@@
 	\item Personally, I believe this ``intellectual property'' drive of the last decade is completely overrated.
-If you make something \textbf{substantial}, it's fine to be able to claim some ownership --- but on snippets?
+If you make something \textbf{substantial}, it's fine to be able to claim some ownership -- but on snippets?
 It's like patenting the stuff you make in your free time in your shed...

### 2017-11-09 cloverflow-tse/cloverflow.tex
Added the percentage of accepted answers which are also the highest voted ones.
Added statistics of agreement between accepted answers and highest voted answers in Section 2.1.

@@
 Moreover, they are usually displayed just below the questions which makes them
-more likely to be reused than other answers. Second, we were only interested in
+more likely to be reused than other answers. Moreover, we found that in our data set
+of Java answers, 86\% of the accepted answers are, at the same time, the highest voted
+answers. Thus, they are well accepted by the Stack Overflow community.
+Second, we were only interested in
 code snippets of at least ten lines. Although the minimum clone size of six
@@
 solve the question's problem and are often showed on top of the answer list.
-While most of the time they are also the highest voted answers, some
-times they are not. We plan to incorporate the highest voted answers in 
-future work.
+We investigated the 72,365 Stack Overflow code snippets used in our study and
+found that 62,245 of them (86\%) are also the highest voted answers.
+%While most of the time they are also the highest voted answers, some
+%times they are not. 
+We plan to incorporate the highest voted answers in future work.
 % We also

### 2017-11-13 cloverflow-tse/cloverflow.tex
Incorporated Rocco's changes.

@@
 we found 214 code snippets on Stack Overflow that could potentially violate the license of their
-original software. We surveyed 201 high-reputation Stack Overflow answerers
+original software. To better understand the phenomenon, we also surveyed 201 high-reputation Stack Overflow answerers
 (33\% response rate) and found that 131 of the answerers (65\%) have ever been notified of
@@
 Android documentation~\cite{Acar2016}.
-
-We call code snippets that are copied from software systems to online Q\&A
-websites (such as Stack Overflow) and vice versa as ``online code clones''.
-There are two directions in creating online code clones: (1)~code is cloned from
-a software project to a Q\&A website as an example; or (2)~code is cloned from a
-Q\&A website to a software project to obtain a functionality, perform a
-particular task, or fixing a bug. % and (3)~code is transferred from one
-% software project to another via a Q\&A website;
-Similar to classic code clones, i.e.~clones between software systems, online code clones
-can lead to license violations, bug propagation, introduction of
-vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
-difficult to locate and fix since the search space in online code corpora is
-larger and no longer confined to a local repository.
-
-Our survey of Stack Overflow answerers shows that online code cloning occurs on
-Stack Overflow. Stack Overflow answerers frequently
-clone code from other locations, such as their personal projects, company
-projects, and open source projects, to Stack Overflow as a solution or
-a complement to a solution. The code cloning activity on Stack Overflow
-is obviously beneficial considered the popularity of Stack Overflow and its
-influence on software development~\cite{Ponzanelli2013,Ponzanelli2014,Park2014}. On the other hand,
-there is also a downside caused by low quality, defective, and harmful code
-snippets that are reused without an awareness by millions of users.
-
-One participant in our survey expresses his/her concerns about this:
-
-\begin{quote}
-	\textit{``The real issue is less about the amount the code snippets
-	on SO than it is about the staggeringly high number of software
-	``professionals'' that mindlessly use them without understanding what they're
-	copying, and the only slightly less high number of would-be professionals that
-	post snippets with built-in security issues.  A related topic is beginners who
-	post (at times dangerously) misleading tutorials online on topics they actually
-	know very little about. Think PHP/MySQL tutorials written 10+ years after
-	\texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that
-	got posted the other day on HackerNew
-	(\url{https://news.ycombinator.com/item?id=14846506}). They're also full of
-	toxic code snippets.''}
-\end{quote}
-
-Using the same analogy, in this study, we are interested in mining Stack
-Overflow posts, detecting online code clones, and analysing the clones to reveal
-``toxic code snippets''.
-
-Toxic code snippets mean code snippets that are harmful for reuse and, in
-several cases, are caused by online code cloning. Stack Overflow code snippets
-cloned from open source software or online sources can become toxic when they
-are (1)~outdated or (2)~violating their original software
-license. Outdated code snippets
-can be harmful since they are not up-to-date with their originals and may
-contain defects. Code snippets from open source projects usually fall under a
-specific software license , e.g.\ GNU General Public License (GPL). If they are
-cloned to Stack Overflow answers without the license, and then flow to other projects
-with conflicting licenses, legal issues may occur.
 
@@
 
+We call code snippets that are copied from software systems to online Q\&A
+websites (such as Stack Overflow) and vice versa as ``online code clones''.
+There are two directions in creating online code clones: (1)~code is cloned from
+a software project to a Q\&A website as an example; or (2)~code is cloned from a
+Q\&A website to a software project to obtain a functionality, perform a
+particular task, or fixing a bug. % and (3)~code is transferred from one
+% software project to another via a Q\&A website;
+Similar to classic code clones, i.e.~clones between software systems, online code clones
+can lead to license violations, bug propagation, introduction of
+vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
+difficult to locate and fix since the search space in online code corpora is
+larger and no longer confined to a local repository.
+
+To have a deeper insight on online code clones, we surveyed 201 high-reputation Stack Overflow answerers. The results of such a survey show that online code cloning occurs on
+Stack Overflow. Stack Overflow answerers frequently
+clone code from other locations, such as their personal projects, company
+projects, and open source projects, to Stack Overflow as a solution or
+a complement to a solution. The code cloning activity on Stack Overflow
+is obviously beneficial considered the popularity of Stack Overflow and its
+influence on software development~\cite{Ponzanelli2013,Ponzanelli2014,Park2014}. On the other hand,
+there is also a downside caused by low quality, defective, and harmful code
+snippets that are reused without an awareness by millions of users.
+
+One participant in our survey expresses his/her concerns about this:
+
+\begin{quote}
+	\textit{``The real issue is less about the amount the code snippets
+	on SO than it is about the staggeringly high number of software
+	``professionals'' that mindlessly use them without understanding what they're
+	copying, and the only slightly less high number of would-be professionals that
+	post snippets with built-in security issues.  A related topic is beginners who
+	post (at times dangerously) misleading tutorials online on topics they actually
+	know very little about. Think PHP/MySQL tutorials written 10+ years after
+	\texttt{mysql\_*} functions were obsolete, or the recent regex tutorial that
+	got posted the other day on HackerNew
+	(\url{https://news.ycombinator.com/item?id=14846506}). They're also full of
+	toxic code snippets.''}
+\end{quote}
+
+Using the same analogy, in this study, we are interested in mining Stack
+Overflow posts, detecting online code clones, and analysing the clones to reveal
+``toxic code snippets''.
+
+Toxic code snippets mean code snippets that are harmful for reuse and, in
+several cases, are caused by online code cloning. Stack Overflow code snippets
+cloned from open source software or online sources can become toxic when they
+are (1)~outdated or (2)~violating their original software
+license. Outdated code snippets
+can be harmful since they are not up-to-date with their originals and may
+contain defects. Code snippets from open source projects usually fall under a
+specific software license, e.g.\ GNU General Public License (GPL). If they are
+cloned to Stack Overflow answers without the license, and then flow to other projects
+with conflicting licenses, legal issues may occur.
+
 We would like to motivate the readers by giving two examples of toxic
-cod snippets.
+code snippets.
 The first example is an outdated and potentially license-violating online code clone in an
@@
 
-The two toxic code snippet in our examples have been posted on March 11, 2014 and
+The two toxic code snippets in our examples have been posted on March 11, 2014 and
 April 9, 2009 respectively. They have already been viewed 259 and 2,886 times at
@@
 each month\footnote{Data as of 21 August 2017 from:
-	\url{https://stackoverflow.com}}, one toxic code snippets on Stack Overflow can
+	\url{https://stackoverflow.com}}, one toxic code snippet on Stack Overflow can
 spread and grow to hundred or thousand copies within only a year or two.
@@
 Moreover, they are usually displayed just below the questions which makes them
-more likely to be reused than other answers. Moreover, we found that in our data set
-of Java answers, 86\% of the accepted answers are, at the same time, the highest voted
-answers. Thus, they are well accepted by the Stack Overflow community.
-Second, we were only interested in
+more likely to be reused than other answers. Second, we were only interested in
 code snippets of at least ten lines. Although the minimum clone size of six
@@
 fragments \textit{CF} are contained in each other:
-
 %\squeezeup
@@
 and the \textit{ok-value} of two clone pairs is defined as
-
 %\squeezeup
@@
 \textbf{Manual investigation:} 
-To mitigate the human error, we deployed two persons in the manual clone
+To mitigate the human error, we deployed two people in the manual clone
 investigation process. The first author, who is a research student working on
@@
 \textbf{To answer RQ 5.1, although most of the Stack Overflow answerers are aware that their code
-can be outdated. 51.5\% of the answerers were very rarely notified while 35.5\% have never been notified of
+can be outdated, 51.5\% of the answerers were very rarely notified and 35.5\% have never been notified of
 outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.}
@@
 \begin{quotation}
-\textit{All code posted by me on
+\noindent \textit{All code posted by me on
 	Stack Overflow should be considered public domain without copyright. For

### 2017-11-13 cloverflow-tse/cloverflow.tex
Corrected the numbers from Figure 9.

@@
 Frequently section, we can see that the answerers mainly write new code from
-scratch (71) or copy and modify the code snippets from the question for each answer (56),
+scratch (106) or copy and modify the code snippets from the question for each answer (66),
 while fewer numbers are from other sources including their personal projects
-(42), their company projects (10), and open source projects (14). Although
+(28), their company projects (4), and open source projects (9). Although
 copying from open source projects is not the most popular choice, the answerers

### 2017-11-13 cloverflow-tse/cloverflow.tex
Formatting, small fixes, and modifying the abstract to fit with 200-word TSE limit.

@@
 Online code clones are code fragments that are copied from software projects or
-online sources to Stack Overflow as examples in questions and answers. % They
-Due to an absence of a checking mechanism after the code has been copied to
-Stack Overflow, they can become toxic code snippets, i.e.~they suffer from
-being outdated or violating the original software license. We present a study
-incorporating several state-of-the-art tools and techniques to automatically
-extract and filter detected online clone pairs between 72,365 Java code snippets
-on Stack Overflow and 111 Java open source projects in the curated Qualitas
-corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
-Our investigation of the online clone pairs revealed strong evidence that 154
-clones have been copied from a Qualitas project to Stack Overflow.  We found 101
-of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
-we found 214 code snippets on Stack Overflow that could potentially violate the license of their
-original software. To better understand the phenomenon, we also surveyed 201 high-reputation Stack Overflow answerers
-(33\% response rate) and found that 131 of the answerers (65\%) have ever been notified of
-outdated code in the answers and 26 of them (20\%) rarely or never fix the outdated
-code. Only 3 answerers explicitly include software licenses in their answers and
-138 answerers (69\%) never check for licensing conflicts between their copied code
-snippets and Stack Overflow's CC BY-SA 3.0.
+online sources to Stack Overflow as examples. Due to an absence of a checking
+mechanism after the code has been copied to Stack Overflow, they can become
+toxic code snippets, i.e. they suffer from being outdated or violating the
+original software license. We present a study incorporating state-of-the-art
+tools and techniques to automatically extract and filter online clone pairs
+between 72,365 Java code snippets on Stack Overflow and 111 open source projects
+in the curated Qualitas corpus. We analysed 2,302 non-trivial online clone
+candidates. Our investigation revealed strong evidence that 154 clones have been
+copied from a Qualitas project to Stack Overflow. We found 101 of them (66\%) to
+be outdated and potentially harmful for reuse. Furthermore, we found 214 code
+snippets that could potentially violate the license of their original software.
+The survey of 201 high-reputation Stack Overflow answerers (33\% response rate)
+showed that 131 participants (65\%) have ever been notified of outdated code and
+26 of them (20\%) rarely or never fix the code. 138 answerers (69\%) never check
+for licensing conflicts between their copied code snippets and Stack Overflow's
+CC BY-SA 3.0.
+
+%Online code clones are code fragments that are copied from software projects or
+%online sources to Stack Overflow as examples in questions and answers. % They
+%Due to an absence of a checking mechanism after the code has been copied to
+%Stack Overflow, they can become toxic code snippets, i.e.~they suffer from
+%being outdated or violating the original software license. We present a study
+%incorporating several state-of-the-art tools and techniques to automatically
+%extract and filter detected online clone pairs between 72,365 Java code snippets
+%on Stack Overflow and 111 Java open source projects in the curated Qualitas
+%corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
+%Our investigation of the online clone pairs revealed strong evidence that 154
+%clones have been copied from a Qualitas project to Stack Overflow.  We found 101
+%of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
+%we found 214 code snippets on Stack Overflow that could potentially violate the license of their
+%original software. To better understand the phenomenon, we also surveyed 201 high-reputation Stack Overflow answerers
+%(33\% response rate) and found that 131 of the answerers (65\%) have ever been notified of
+%outdated code in the answers and 26 of them (20\%) rarely or never fix the outdated
+%code. Only 3 answerers explicitly include software licenses in their answers and
+%138 answerers (69\%) never check for licensing conflicts between their copied code
+%snippets and Stack Overflow's CC BY-SA 3.0.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-Clone Detection, Stack Overflow, Outdated Code, Software Licensing
+Code Clone Detection, Stack Overflow, Outdated Code, Software Licensing
 \end{IEEEkeywords}}
@@
 
-%The popularity of the Internet encourages tremendous amount of source code being shared online. 
-Stack Overflow is a popular online programming community with 7.6
-million users, 14 million questions, and 23 million answers\footnote{Data as of 21
-	August 2017 from~\url{https://stackexchange.com/sites}}. It allows programmers to ask questions and give answers
-to programming problems. The website has found to be useful for
-software
+%The popularity of the Internet encourages tremendous amount of source code
+% being shared online.
+Stack Overflow is a popular online programming community with 7.6 million users,
+14 million questions, and 23 million answers\footnote{Data as of 21 August 2017
+	from~\url{https://stackexchange.com/sites}}. It allows programmers to ask
+questions and give answers to programming problems. The website has found to be
+useful for software
 development~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014,
-	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also
-valuable for educational purposes~\cite{Nasehi2012}. On Stack
-Overflow, each conversation contains a question and a list of
-answers. The answers frequently contain at least one code snippet as
-a solution to the question asked. We found that the code snippets are
-usually not authored directly on the Stack Overflow website but copied
-from another location. A snippet in an answer could be copied and modified
-from a code snippet in the question, copied from the answerer's own
-code or from other locations including open source software (OSS)
-systems.
-
-The process of posting and answering questions on Stack
-Overflow that involves the reuse (copying) of source code can be considered
-code cloning.
-Code cloning is an activity of reusing source code by copying and
-pasting. It normally occurs in software development and account from
-7\% to 23\% of source code in typical software
-systems~\cite{Bellon2007}. The benefits and drawbacks of clones are
-still controversial. Several authors state that clones lead to bug
-propagations and software maintenance issues~\cite{Kamiya2002}, while
-some others suggest that clones are not harmful and can even be
+	Stolee2014,Subramanian2013,Diamantopoulos2015,Treude2016} and also valuable for
+educational purposes~\cite{Nasehi2012}. On Stack Overflow, each conversation
+contains a question and a list of answers. The answers frequently contain at
+least one code snippet as a solution to the question asked. We found that the
+code snippets are usually not authored directly on the Stack Overflow website
+but copied from another location. A snippet in an answer could be copied and
+modified from a code snippet in the question, copied from the answerer's own
+code or from other locations including open source software (OSS) systems.
+
+The process of posting and answering questions on Stack Overflow that involves
+the reuse (copying) of source code can be considered code cloning. Code cloning
+is an activity of reusing source code by copying and pasting. It normally occurs
+in software development and account from 7\% to 23\% of source code in typical
+software systems~\cite{Bellon2007}. The benefits and drawbacks of clones are
+still controversial. Several authors state that clones lead to bug propagations
+and software maintenance issues~\cite{Kamiya2002}, while some others suggest
+that clones are not harmful and can even be
 beneficial~\cite{Saini2016,Kapser2006}.
 
-Code cloning can also have side effects such as violating software
-licenses or introducing software vulnerabilities. Carelessly cloning
-code from one project to another project with a different license may
-cause a software license violation~\cite{German2009}. This also
-happens within the context of online Q\&A websites such as Stack
-Overflow. An et al.~\cite{An2017} showed that 1,279 cloned snippets
-between Android apps and Stack Overflow potentially violate software
-licenses. Security is also among the main concerns when code is copied
+Code cloning can also have side effects such as violating software licenses or
+introducing software vulnerabilities. Carelessly cloning code from one project
+to another project with a different license may cause a software license
+violation~\cite{German2009}. This also happens within the context of online Q\&A
+websites such as Stack Overflow. An et al.~\cite{An2017} showed that 1,279
+cloned snippets between Android apps and Stack Overflow potentially violate
+software licenses. Security is also among the main concerns when code is copied
 from an online source. For example, Stack Overflow helps developers to solve
-Android programming problems more quickly than other resources while,
-at the same time, offers less secure code than books or the official
-Android documentation~\cite{Acar2016}.
+Android programming problems more quickly than other resources while, at the
+same time, offers less secure code than books or the official Android
+documentation~\cite{Acar2016}.
 
@@
 % software project to another via a Q\&A website;
-Similar to classic code clones, i.e.~clones between software systems, online code clones
-can lead to license violations, bug propagation, introduction of
+Similar to classic code clones, i.e.~clones between software systems, online
+code clones can lead to license violations, bug propagation, introduction of
 vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
@@
 
-To have a deeper insight on online code clones, we surveyed 201 high-reputation Stack Overflow answerers. The results of such a survey show that online code cloning occurs on
-Stack Overflow. Stack Overflow answerers frequently
-clone code from other locations, such as their personal projects, company
-projects, and open source projects, to Stack Overflow as a solution or
-a complement to a solution. The code cloning activity on Stack Overflow
-is obviously beneficial considered the popularity of Stack Overflow and its
-influence on software development~\cite{Ponzanelli2013,Ponzanelli2014,Park2014}. On the other hand,
+To have a deeper insight on online code clones, we surveyed 201 high-reputation
+Stack Overflow answerers. The results of such a survey show that online code
+cloning occurs on Stack Overflow. Stack Overflow answerers frequently clone code
+from other locations, such as their personal projects, company projects, and
+open source projects, to Stack Overflow as a solution or a complement to a
+solution. The code cloning activity on Stack Overflow is obviously beneficial
+considered the popularity of Stack Overflow and its influence on software
+development~\cite{Ponzanelli2013,Ponzanelli2014,Park2014}. On the other hand,
 there is also a downside caused by low quality, defective, and harmful code
@@
 
-We would like to motivate the readers by giving two examples of toxic
-code snippets.
-The first example is an outdated and potentially license-violating online code clone in an
-answer to a Stack Overflow question regarding how to implement
-{\small{\texttt{RawComparator}}} in
+We would like to motivate the readers by giving two examples of toxic code
+snippets. The first example is an outdated and potentially license-violating
+online code clone in an answer to a Stack Overflow question regarding how to
+implement {\small{\texttt{RawComparator}}} in
 \textsf{Hadoop}\footnote{\url{http://stackoverflow.com/questions/22315734}}.
@@
 21, 2014. The added line is intended for cleaning up the reference in the
-{\small{\verb|buffer|}} variable and avoid excess heap usage
-(issue no.~HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
+{\small{\verb|buffer|}} variable and avoid excess heap usage (issue
+no.~HADOOP-11323\footnote{https://issues.apache.org/jira/browse/HADOOP-11323}).
 While this change has already been introduced into the
 {\small{\texttt{compare}}} method several years ago, the code example in Stack
-Overflow post is still unchanged. 
-%This example shows that inconsistencies
+Overflow post is still unchanged. %This example shows that inconsistencies
 %between online code clones and their originals can lead users of Stack Overflow
 %to reuse outdated code.
-In addition, the original code snippet of
-{\small\texttt{WritableComparator}} class in Hadoop is distributed with Apache license
-version 2.0 while its cloned instance on Stack Overflow contains only the
-{\small{\texttt{compare}}} method and ignores its license statement on top of the
-file. There are two potential issues for this. First, the code snippet may appear to be 
-under Stack Overflow's CC BY-SA 3.0 instead of its original Apache
-license. Second, if the code snippet is copied and incorporated into another
-software project with a conflicting license, a legal issue may arise.
+In addition, the original code snippet of {\small\texttt{WritableComparator}}
+class in Hadoop is distributed with Apache license version 2.0 while its cloned
+instance on Stack Overflow contains only the {\small{\texttt{compare}}} method
+and ignores its license statement on top of the file. There are two potential
+issues for this. First, the code snippet may appear to be under Stack Overflow's
+CC BY-SA 3.0 instead of its original Apache license. Second, if the code snippet
+is copied and incorporated into another software project with a conflicting
+license, a legal issue may arise.
 
@@
 		its latest version in the \textsf{Hadoop} code base
-		(right). The toxic code snippet is outdated code, has race conditions, and does not contain its
-		original Apache v.2.0 license.}
+		(right). The toxic code snippet is outdated code and has race conditions.}
 	\label{fig:before-after_2}
@@
 (issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
-Similar to the first example, the clone code snippet on Stack Overflow does not 
-include its original Apache v.2.0 license.
+%Similar to the first example, the clone code snippet on Stack Overflow does not 
+%include its original Apache v.2.0 license.
 
@@
 mandatory while the other 9 questions were shown to the participants based on
-their previous answers. The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}~\FIXME{Fix the RN bibtex}.
+their previous answers. The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
 
@@
 consolidation, found to be similar because they implement the same interface or
-inheriting from the same class. An example is the two implementations of a
+inherit from the same class. An example is the two implementations of a
 custom data type which implements {\small\texttt{UserType}}. They share similar
@@
 
-\begin{table}
-	\centering
-	\caption{Stack Overflow answerers taken the survey}
-	\label{tab:survey_target}
-	\begin{tabular}{rrrr}
-		\toprule
-		Reputation & Sent emails & Answers & Rate \\
-		\midrule
-		963,731--6,999 & 607 & 201 & 33\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
+%\begin{table}
+%	\centering
+%	\caption{Stack Overflow answerers taken the survey}
+%	\label{tab:survey_target}
+%	\begin{tabular}{rrrr}
+%		\toprule
+%		Reputation & Sent emails & Answers & Rate \\
+%		\midrule
+%		963,731--6,999 & 607 & 201 & 33\% \\
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
 
@@
 We only present a summary of the survey answers in
-this paper and the full analysis is available as a technical report~\cite{Ragkhitwetsagul_RN2017}.
+this paper and the full analysis is available as a research note~\cite{Ragkhitwetsagul_RN2017}.
 
@@
 As shown in \Cref{tab:survey_exp}, the majority of the answerers are experienced
-developers with more than 10 years of experience (55.4\%) or between 5 to 10
-years (28.7\%). They are active users and regularly answer questions. 49
+developers with more than 10 years of experience (55.2\%) or between 5 to 10
+years (28.9\%). They are active users and regularly answer questions. 49
 participants (24\%) answer questions on Stack Overflow every day.
@@
 
-Work similar to ours are studies by An et al.~\cite{An2017}
+Work similar to ours are studies by An et al.~\cite{An2017},
 Abdalkareem et al.~\cite{Abdalkareem2017}, and Baltes et al.~\cite{Baltes2017}. 

### 2017-11-13 cloverflow-tse/cloverflow.tex
Prepared for the photos and biographies.

@@
 
-% \begin{IEEEbiographynophoto}{Chaiyong Ragkhitwetsagul}
-% Biography text here.
-% \end{IEEEbiographynophoto}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
+is working toward the PhD degree in computer science at University College London, where he is part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
+He is supervised by Jens Krinke and David Clark.
+His research interests include code search, code clone detection, software plagiarism, search-based software engineering, and mining software repository.
+\end{IEEEbiography}
+\vspace{-1cm}
 
 % % if you will not have a photo at all:
-% \begin{IEEEbiographynophoto}{Jens Krinke}
-% Biography text here.
-% \end{IEEEbiographynophoto}
-
-% \begin{IEEEbiographynophoto}{Matheus Paixao}
-% Biography text here.
-% \end{IEEEbiographynophoto}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.jpg}}]{Jens Krinke}
+is Senior Lecturer in the Software Systems Engineering
+Group at the University College London, where he is Director of CREST,
+the Centre for Research on Evolution, Search, and Testing.  His main
+focus is software analysis for software engineering purposes. His
+current research interests include software
+similarity, modern code review, and mutation testing.  He is well known for his work on
+program slicing and clone detection.
+\end{IEEEbiography}
+\vspace{-1cm}
+
+\begin{IEEEbiography}{Matheus Paixao}
+Biography text here.
+\end{IEEEbiography}
+\vspace{-1cm}
+
+\begin{IEEEbiography}{Giuseppe Bianco}
+	Biography text here.
+\end{IEEEbiography}
+\vspace{-0.5cm}
+
+\begin{IEEEbiography}{Rocco Oliveto}
+	Biography text here.
+\end{IEEEbiography}
+\vfill
 

### 2017-11-14 cloverflow-tse/cloverflow.tex
Fixed the abstract.

@@
 mechanism after the code has been copied to Stack Overflow, they can become
-toxic code snippets, i.e. they suffer from being outdated or violating the
+toxic code snippets, i.e.~they suffer from being outdated or violating the
 original software license. We present a study incorporating state-of-the-art
@@
 snippets that could potentially violate the license of their original software.
-The survey of 201 high-reputation Stack Overflow answerers (33\% response rate)
+A survey of 201 high-reputation Stack Overflow answerers (33\% response rate)
 showed that 131 participants (65\%) have ever been notified of outdated code and

### 2017-11-14 cloverflow-tse/cloverflow.tex
Updated Rocco and Matheus's bio.

--- 2017-11-13 cloverflow-tse/cloverflow.tex
@@
 is working toward the PhD degree in computer science at University College London, where he is part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
-He is supervised by Jens Krinke and David Clark.
+He is supervised by Dr.~Jens Krinke and Dr.~David Clark.
 His research interests include code search, code clone detection, software plagiarism, search-based software engineering, and mining software repository.
@@
 
-\begin{IEEEbiography}{Matheus Paixao}
-Biography text here.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
+is currently a PhD candidate in the computer science department at University College London, where he is part of the CREST centre.~He is supervised by Dr.~Jens Krinke, Prof.~Mark Harman, Dr.~Emmanuel Letier and Dr.~Yuanyuan Zhang.
+His research interests include software architecture, search based software engineering, technical debt, empirical software engineering and modern code review.
 \end{IEEEbiography}
@@
 
-\begin{IEEEbiography}{Rocco Oliveto}
-	Biography text here.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{rocco.png}}]{Rocco Oliveto}
+is Associate Professor at University of Molise (Italy), where he is also the Director of the Computer Science Bachelor and Master programs and the Director of the Software and Knowledge Engineering Lab (STAKE Lab).
+He co-authored over 100 papers on topics related to software traceability, software maintenance and evolution, search-based software engineering, and empirical software engineering.
+His activities span various international software engineering research communities.
+He has served as organizing and program committee member of several international conferences in the field of software engineering.
+He was program co-chair of ICPC 2015, TEFSE 2009 and 2015, SCAM 2014, WCRE 2012, and 2013.
+He is general chair for SANER 2018 that will be held in Campobasso from March 20, 2018 to March 23, 2018.
+He is also one of the co-founders and CEO of DataSound, a spin-off of the University of Molise aiming at efficiently exploiting the priceless heritage that can be extracted from big data analysis via machine learning.
+More info at \url{https://dibt.unimol.it/staff/oliveto}.
 \end{IEEEbiography}

### 2017-11-14 cloverflow-tse/cloverflow.tex
Added my own version of Giuseppe's bio.

@@
 
-\begin{IEEEbiography}{Giuseppe Bianco}
-	Biography text here.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{giuseppe.png}}]{Giuseppe Bianco}
+receives his bachelor degree in Computer Science from University of Molise (Italy) under supervision of  Dr.~Rocco Oliveto.
+He was an Erasmus exchange student at CREST centre, University College London, UK, for three months and was supervised by Dr.~Jens Krinke.~He is now a project manager at Corsi.it.
 \end{IEEEbiography}

### 2017-11-14 cloverflow-tse/cloverflow.tex
Update to bios.

--- 2017-11-14 cloverflow-tse/cloverflow.tex
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
-is working toward the PhD degree in computer science at University College London, where he is part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
+is working toward the PhD degree in Computer Science at University College London, where he is part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
 He is supervised by Dr.~Jens Krinke and Dr.~David Clark.
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
-is currently a PhD candidate in the computer science department at University College London, where he is part of the CREST centre.~He is supervised by Dr.~Jens Krinke, Prof.~Mark Harman, Dr.~Emmanuel Letier and Dr.~Yuanyuan Zhang.
+is currently a PhD candidate in the Computer Science Department at University College London, where he is part of the CREST centre.~He is supervised by Dr.~Jens Krinke, Prof.~Mark Harman, Dr.~Emmanuel Letier and Dr.~Yuanyuan Zhang.
 His research interests include software architecture, search based software engineering, technical debt, empirical software engineering and modern code review.
@@
 
-\begin{IEEEbiography}{Giuseppe Bianco}
-	Biography text here.
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{giuseppe.png}}]{Giuseppe Bianco}
+  received his bachelor degree in Computer Science from the University
+  of Molise (Italy) under the supervision of Dr.~Rocco Oliveto. As
+  part of an Erasmus+ traineeship, he spent three month at the
+  CREST centre, University College London, UK, under the supervision
+  of Dr.~Jens Krinke.~He is now a project manager at Corsi.it.
 \end{IEEEbiography}

### 2018-02-14 cloverflow-tse/cover_letter/cover_letter.tex
Prepared the cover letter for TSE resubmission.

% Copyright Javier Sánchez-Monedero.
% Please report bugs and suggestions to (jsanchezm at uco.es)
%
% This document is released under a Creative Commons Licence 
% CC-BY-SA (http://creativecommons.org/licenses/by-sa/3.0/) 
%
% BASIC INSTRUCTIONS: 
% 1. Load and set up proper language packages
% 2. Complete the paper data commands
% 3. Use commands \rcomment and \newtext as shown in the example

\documentclass[a4paper,twoside,10pt]{reviewresponse}

% 1. Load and set up proper language packages
%\usepackage[utf8x]{inputenc}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[latin9]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{natbib}

% 2. Complete the paper data
\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul,~Jens Krinke,~Matheus Paixao,~Giuseppe Bianco,~Rocco Oliveto}
\newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
\newcommand{\myEmail}{{chaiyong.ragkhitwetsagul.14,j.krinke,matheus.paixao.14}@ucl.ac.uk, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
%\newcommand{\mySecEmail}{}
\newcommand{\myTitle}{Cover Letter for the Reviewers of the Paper \\ ``Toxic Code Snippets on Stack Overflow''}
\newcommand{\myShortTitle}{Cover Letter}
\newcommand{\myJournal}{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING}
\newcommand{\myDept}{University College London (UK), University of Molise (Italy)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage[linktoc=all]{hyperref}
\usepackage[linktoc=all,bookmarks,bookmarksopen=true,bookmarksnumbered=true]{hyperref}

\hypersetup{
pdfauthor = {\myAuthorsShort},
pdftitle = {\myTitle},
pdfsubject = {\myJournal\xspace},
colorlinks = true,
linkcolor=blue,          % color of internal links
citecolor=black!70!green,        % color of links to bibliography
filecolor=magenta,      % color of file links
urlcolor=black           % color of external links
}

\begin{document}

\thispagestyle{plain}

\begin{center}
 {\LARGE\myTitle} \vspace{0.3cm} \\
 {\large\myJournal} \vspace{0.3cm} \\
 \today \vspace{0.3cm} \\
 \myAuthors \\
 \url{\myEmail} \\
 %\url{\mySecEmail} 
 \vspace{0.3cm} 
 \myDept \vspace{1cm}
\end{center}

%\tableofcontents

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software Engineering. 
This is a re-submission of the previous submission no.~TSE-2017-11-0335 and we would like to thank the anonymous Reviewers for taking their time to carefully read our paper. With their useful and constructive reviews, we substantially improved the work by adding the following improvements:

\textbf{1. A study of toxic code snippets on GitHub:}~To provide an evidence that toxic code snippets are actually reused in software projects and strengthen the motivation, we performed a large-scale analysis of clones between toxic code snippets found on Stack Overflow and GitHub projects.

\textbf{2. Analysis of tools' parameter settings:}~We mitigated the threats to validity due to parameter settings of the clone detection tools and the clone merging technique by performing a comparison of different tools' parameter settings.

\textbf{3. Revisions to the overall discussion:}~???

We also tried our best to address all the comments from the reviewers. Each particular comment led to an improvement on this submission as presented in the following discussions.

\clearpage

\section{Reviewer 1}

\rcomment{
Regarding this statement: ``It is probably more important than studying the effects of reusing Stack Overflow code snippets because it gives insights to the root cause of the problem and lays a foundation to an automatic technique to detect and report toxic code snippets on Stack Overflow to developers in the future.''

While~\cite{An2017} do suggest that copying from Stack Overflow to software projects occurs (and results in license violations), they do not establish that code snippets from Stack Overflow ``go viral'' and end up distributed widely across (open or closed source) software projects. Moreover, while the quote on the first page implies that developers often ``mindlessly'' reuse code snippets from Stack Overflow, to the best of my knowledge, this claim is conventional wisdom but not empirically validated. So, it seems to me that the primary interest in toxic code snippets is that may cause widespread harm, but I am missing the evidence that they do so in practice. Even assuming that code snippets from Stack Overflow are distributed mindlessly and widely, I wonder how many code snippets on Stack Overflow are toxic, the extent to which they are reused without modification (or with only minor adaptation), what kinds of projects they end up in (i.e., a popular project from Microsoft or Apache vs. a hobby project by a single developer vs. a student solution to an assignment), and ultimately, how much damage can we expect them to cause. In the end, I agree that it is better to detect and report toxic code snippets than to not do so, but I am not sure how big of a problem is solved by doing so. As such, I disagree that it is ``probably more important'' to find the toxic code snippets than to understand their effects. Instead, I think that understanding their effects (on software projects rather than on the quality of the Stack Overflow platform) is necessary to appreciate the value in finding them.
}

We would like to thank for the comments.~We agree with the concern of real evidence that code snippets on Stack Overflow ...

\rcomment{
	I think that the survey evidence is compelling. But I am missing the awareness of Stack Overflow questioners or information-seekers to toxic code snippets. I wonder: how skeptical are developers when considering code snippets on Stack Overflow, how often do developers use code snippets directly, and how often do developers use clues such as ``A quick google search returned me this from Appache hadoop project. Copying from there:'' to seek out the latest version of the information provided in the answer. The survey responses described in Section 3.5.3 suggest that there are questioners/information-seekers that are aware of toxic code snippets (as they are reporting them to the answerers), and there is evidence that the Stack Overflow community is aware of the need to retire outdated information and of the many concerns related to software licensing, as these issues are discussed on meta.stackoverflow.com. So, again, I wonder about the impact of toxic code snippets on actual software projects.
}

\rcomment{
	The ``Overall Discussion'' section is not commensurate with the quality and breadth of the empirical study. The proposed preventative measure is actually two measures: a policy change and an IDE plugin. While an IDE plugin would provide early detection (and possible prevention) of license violations, the exact mechanics are not clear based on the description. Further, companies (and perhaps major open source projects?) use auditing platforms/services to detect such violations. Regarding the detective measure, I do not think that the paper establishes that a system to detect outdated code snippets on Stack Overflow is needed (but rather it establishes that outdated code snippets exist on Stack Overflow). Further, not all outdated code snippets are bad. For instance, a code snippet may show a solution using an older version of an API, and that older version may still be used in production. So, the definition of outdated would need to be a bit more nuanced to be used in an automated system for flagging or updating old Stack Overflow posts.
}

\rcomment{
Other Comments

\begin{itemize}
	\item While ``Toxic Code Snippets'' is a catchy phrase for the title, I think that online code clones are the dominant topic.
	\item The introduction states that the erroneous code snippet in post 22262310 has been viewed 259 as of the writing of the paper. But I note that while the question was posted on Mar 7, 14 the answer was posted on Mar 11, 14. I also note that the question has a score of -1. So, I wonder (a) whether the view count is for the answer (i.e., the code snippet) or the post (which existed for a few days before the answer appeared), (b) how many people viewed the question before it was answered, and (c) if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.
	\item FYI, since this paper was authored, a Stack Overflow user has posted a comment in response to the answer for post 22262310. The comment highlights the missing line and refers to the relevant HADOOP issue report. Interestingly, the gap between the issue report being resolved (Nov 20, 14) and the comment appearing on Stack Overflow (Oct 31, 17) is nearly three years. I wonder how many views occurred during this gap and whether the addition of the comment mitigates the toxicity of the code snippet.
	\item Table 1 has a median column. Median of what?
	\item Section 2.1 states that comments were removed before clone detection, but as stated later in the paper, comments can provide clues regarding provenance. Can the manual inspection of comments to find evidence of copying be automated as part of the clone detection process?
	\item Typo: ``how much the community trust them'' --> ``how much the community trusts them''
\end{itemize}
}

\section{Reviewer 2}

\rcomment{
\textbf{The definition of toxic code snippets:} I understand that the authors are trying to put a new spin or name to the phenomena they study, but the definition the authors provide is, in my opinion, not sufficient. For example, their definition is ``toxic code snippets mean code snippets that are harmful for reuse and, \textbf{in several cases}, are caused by online...''. A definition should be clear - saying in several cases - means that in several other cases (1- your several cases) it is not harmful. So, I ask the authors to refine and clarify this definition, because as it stands now, this definition is confusing (at best). Given that your entire paper is about toxic code snippets, you can appreciate why this is important.
}

We appreciate the comments.

\rcomment{
	\textbf{RQs need to be better linked:} First, I can see a clear motivation for RQs 1-3, however, RQs 4 and 5 seem to be tagged on. I did not see a clear transition of why RQs 4 and 5 would follow RQs 1-3. This can be an easy fix, but it is an important one since it makes your paper seem less cohesive.

	\vspace{1ex}
	\textit{Issues related to RQs}

	Since we are talking about the RQs, this might be a good chance to discuss some of my other concerns with specific RQs.

	\begin{itemize}
		\item RQ3.~I believe that the answer to this question is expected and perhaps the way that the authors answered this question is incorrect. If I use some code from SO that was posted in 2014, then I expect that it is outdated. Also, SO does not allow people to update their posts, so why would I expect the snippets to not be outdated, hence, I feel that your question is incorrect. Another issue that might impact the answer to this RQ is the fact that your Qualitas dataset is older than that of SO, so your setup encourages the finding of outdated snippets. What I think would be a better approach is to look if there are other answers (maybe not the accepted one) that are newer. For me, if I see an old accepted answer or a newer post with an upvoted answer, I will probably go for the newer post. This was never considered by the authors.
		\item In section 2.4, you consider a change to the code in the Q project to be evidence that the snippet is outdated. How do you control for changes that are simply due to evolution? For example, what if I refactor the code and change the variable names of the snippet.
	\end{itemize}
}

\rcomment{
	\textbf{Data used:} why is the SO data from Jan. 2016? This dump is now 2 years old! I can see why you used an older version of the Qualitas dataset, but I cannot understand why you would want to use an old version of the SO data. Please explain. 
}

\rcomment{
	\textbf{Arbitrary use of parameter:} On page 4, you use snippets of at least 10 lines. Why 10, why not 15? Given that this is a journal paper, you have the space to examine the impact of your parameters (at least in brief) on your results. What I would like the authors to do is to actually examine the impact of such parameters on your work in a discussion section. A similar concern exists on page 5, where t=0.7 is chosen. Sure, it worked in another context, but did they show that a 0.7 threshold is OK to use for SO snippets? I think you can also vary this t value and examine its impact.
}

\rcomment{
	\textbf{Question about clone patterns:} Table 4 lists all the clone patterns you considered. First, I have a major concern about the two most interesting patterns Q->S and S->Q. Especially in the case of S->Q, how can you be sure that this code actually came from SO? It could have come from any other project or from SO or another forum. Also, for Q->S, how can you be sure these snippets came from the Q projects? This is somewhat of a major concern since the rest of your paper is built on this. I would like to see a clear explanation of how we can be sure about this.

	\vspace{1ex}
	Now, you can say that we see code that is similar in Q and S or S and Q, but you can (almost) never say that this code comes from SO or from Q (to SO). This puts your toxic code idea into question and makes me take the results of RQs 1 and 2 with a grain of salt.

	\vspace{1ex}
	In fact, in the answer of RQ1, you explicitly say ``...share similar code with SO ...'', but throughout the paper, you present the work as if the code came from SO -> Q or vice versa.

	\vspace{1ex}
	And given the types of clones you find (e.g., BP code), this can really come from anywhere (and more likely to come from things like tutorials or IDEs). Then, you report that 65\% of the closes are BP. AC is also not a clone really since even in your Table 4 you said AC is false clones - how can an Accidental *clone* be a false clone? If something is false, then it is not a clone.
}

\rcomment{
I feel that the strongest part of the paper is the survey section. I really enjoyed the findings and think that the community can learn something from the outcomes of the survey (especially section 3.5.5). However, I did find the question in section 3.5.3 to be unfair somehow since there is really no mechanism in SO to notify anyone who used a code snippet. In fact, no one even knows who used a code snippet from SO.
}

\rcomment{
Perhaps minor, but this issue really did not sit well with me, in the introduction, you say in RQ5 that you survey 607 participants, but later it turns out that only 201 responded. To me, this is somewhat misleading and does not sit well. I strongly encourage the authors to refactor such `marketing' statements.
}

\clearpage

\section{Reviewer 3}

\rcomment{
There is also no discussion if partial updates to the outdate code clones where posted in the same Q\&A threat (e.g., addressed by somebody else who just mentioned the necessary modifications or provided a link to the updated code fragment).  It would also have been interesting to know how old the Q\&As (clones) were, since the Qualitas code base is 4 years older then the StackOverflow snapshot. Not sure why you selected 2013 and not 2014 or 2012.
Average and mean time/date of the clone postings on stackoverflow would be interesting to see the distribution of the clone age (simple boxplot would do).
}

We are grateful for the insightful comment.

\rcomment{
I do believe the survey results from the StackOverflow contributors actually provides more meaningful insights then then the clone detection itself, since the responses by the contributors actually help explaining some of the results. The authors should provide further analysis and interpretation of the survey results.
}

\rcomment{
Overall discussion is very weak. While the authors went through a lengthy and detailed study of code clones published on StackOverflow and the survey of StackOverflow contributors, the paper lacks really a take home message. At the end there is no real evidence that either code clones are really toxic or bad (are they actually causing problems ? due to the use of clones. Just because a code fragment is outdated does not mean it is necessarily bad or causes any problems. What is the actual take home message from your study? Should we stop reusing code from StackOverflow? I do believe there is a need to dig deeper in the observed data and draw some real conclusions on how the observed results can benefit both the StackOverflow community and the source code community.
}

\vspace{1cm}

Finally, we would like to thank the reviewers again for the comments.
We believe this new submission has been considerably improved from the previous version due to the insightful reviews and discussions.

% Uncomment in case references are needed
%\bibliographystyle{plain}
\bibliographystyle{spbasic}
\bibliography{bib}

\end{document}

### 2018-02-18 SCCTokenizer/tokenizer_stackoverflow.py
Make the script support Python 3.6.

@@ -165,21 +165,12 @@ def main():
     with open(FILE_blocks_tokens_file, 'w') as FILE_tokens_file, \
          open(FILE_blocks_stats_file, 'w') as FILE_stats_file:
         
-        print "starting"
+        print("starting")
         process_so_file(FILE_tokens_file, FILE_stats_file)
 
     p_elapsed = dt.datetime.now() - p_start
     logging.info('All done in %s' % p_elapsed)
-    print 'All %s blocks done in %s' % (block_count, p_elapsed)
+    print('All %s blocks done in %s' % (block_count, p_elapsed))
 
 
 main()
-
-
-	
-
-
-
-
-
-

### 2018-02-18 SOSnippetFilter/main.py
Added a script to filter non-Java Stack Overflow snippets.

@@ -1,0 +1,46 @@
+import subprocess as sp
+import os
+
+
+def writefile(filename, fcontent, mode, isprint):
+    """
+    Write the string content to a file
+    copied from
+    http://www.pythonforbeginners.com/files/reading-and-writing-files-in-python
+    :param filename: name of the file
+    :param fcontent: string content to put into the file
+    :param mode: writing mode, 'w' overwrite every time, 'a' append to an existing file
+    :return: N/A
+    """
+    # try:
+    file = open(filename, mode)
+    file.write(fcontent)
+    file.close()
+
+    if isprint:
+        print "saved:" + filename
+
+
+with open("log.txt", "r") as f:
+    all_snippets = f.read().split("\n")
+    for snippet in all_snippets:
+        with open("/Users/Chaiyong/Downloads/stackoverflow/" + snippet, "r") as sofile:
+            tmp = sp.call('clear', shell=True)
+            print snippet
+            code = sofile.read()
+            print "----------"
+            print code
+            print "----------"
+            selection = raw_input("Should I move it? (y/n)")
+            if selection.lower() == "y":
+                print "Moving: " + "/Users/Chaiyong/Downloads/stackoverflow/" + snippet + " to " + \
+                      "/Users/Chaiyong/Downloads/stackoverflow/filtered_so_snippets/pmdcpd/"\
+                      + snippet.replace("stackoverflow_formatted/","")
+                writefile("/Users/Chaiyong/Downloads/stackoverflow/filtered_so_snippets/pmdcpd/movedfiles.txt",
+                          "/Users/Chaiyong/Downloads/stackoverflow/" + snippet + "," + \
+                      "/Users/Chaiyong/Downloads/stackoverflow/filtered_so_snippets/pmdcpd/"\
+                      + snippet.replace("stackoverflow_formatted/",""), "a", False)
+                os.rename("/Users/Chaiyong/Downloads/stackoverflow/" + snippet,
+                          "/Users/Chaiyong/Downloads/stackoverflow/filtered_so_snippets/pmdcpd/"
+                          + snippet.replace("stackoverflow_formatted/",""))
+

### 2018-02-18 src/eu/giuswhite/LineCounter.java
Cleaned up the repo. Removed outdated Giuseppe's tool since it's already moved to another separated repo. The repo is now having the papers, related documents, and the other tools used for the experiments.

@@ -1,147 +1,0 @@
-package eu.giuswhite;
-
-import eu.giuswhite.utils.CommonUtils;
-
-import java.io.*;
-import java.util.ArrayList;
-import java.util.HashMap;
-import java.util.List;
-import java.util.Map;
-
-/**
- * Created by GiusWhite on 01/02/2016.
- */
-public class LineCounter {
-
-    public static LineCounter instance = null;
-    public Map<String, Integer> topSmallestCode = new HashMap<>();
-    public Map<String, Integer> topBiggestCode = new HashMap<>();
-
-    protected LineCounter() {
-    }
-
-    public static LineCounter getInstance() {
-        if (instance == null) {
-            instance = new LineCounter();
-        }
-        return instance;
-    }
-
-    public int countLines(String filename) throws IOException {
-        InputStream is = new BufferedInputStream(new FileInputStream(filename));
-        try {
-            byte[] c = new byte[1024];
-            int count = 0;
-            int readChars = 0;
-            boolean empty = true;
-            while ((readChars = is.read(c)) != -1) {
-                empty = false;
-                for (int i = 0; i < readChars; ++i) {
-                    if (c[i] == '\n') {
-                        ++count;
-                    }
-                }
-            }
-            return (count == 0 && !empty) ? 1 : count;
-        } finally {
-            is.close();
-        }
-    }
-
-    public Map getMapOfLinesStat(String folderPath) {
-        Map<Integer, Integer> lineStatMap = new HashMap<>();
-        File dir = new File(folderPath);
-        List<String> allFilesInFolder = new ArrayList<>();
-        this.getDirectoryContents(dir, allFilesInFolder);
-        for (String file : allFilesInFolder) {
-            try {
-                int numberOfLines = this.countLines(file);
-                ParserManager.TOTAL_LINE_NUMBER = ParserManager.TOTAL_LINE_NUMBER + numberOfLines;
-                this.manageTopFile(file, numberOfLines);
-                if (lineStatMap.containsKey(numberOfLines)) {
-                    lineStatMap.put(numberOfLines, lineStatMap.get(numberOfLines) + 1);
-                } else {
-                    lineStatMap.put(numberOfLines, 1);
-                }
-                System.out.println("DONE: " + file);
-            } catch (IOException e) {
-                e.printStackTrace();
-            }
-        }
-        return lineStatMap;
-    }
-
-    private void getDirectoryContents(File dir, List<String> filesName) {
-        File[] files = dir.listFiles();
[…]

### 2018-02-18 src/eu/giuswhite/Main.java

@@ -1,123 +1,0 @@
-package eu.giuswhite;
-
-import eu.giuswhite.utils.CommonUtils;
-import eu.giuswhite.utils.CsvFileWriter;
-import org.apache.commons.cli.*;
-import java.io.File;
-import java.util.Map;
-
-public class Main {
-    private static Options options = new Options();
-    private static String fileDir;
-    private static String mode;
-    private static String TOOL="simian";
-    private static String SETTING="df";
-
-    public static void main(String[] args) {
-        processCommandLine(args);
-
-        if (mode.equals("p")) {
-            ParserManager.getInstance().stackoverflowParser();
-            Map map = LineCounter.getInstance().getMapOfLinesStat(CommonUtils.PROJECT_FOLDER_PATH + "/data_four_split/0/");
-            Map smallest = LineCounter.getInstance().getTopSmallestFile();
-            Map biggest = LineCounter.getInstance().getTopBiggestFile();
-//            CsvFileWriter.sortHashMapByKey("first_half_stats", CommonUtils.CODE_LINES_STAT_CSV_HEADER, map);
-            CsvFileWriter.sortHashMapByKey(map);
-            CsvFileWriter.writeHashMapToCsv("Post ID, # of lines", smallest, "first_half_5_smallest_code");
-            CsvFileWriter.writeHashMapToCsv("Post ID, # of lines", biggest, "first_half_5_sbiggest_code");
-            /*
-            Map map = new HashMap<>();
-            BufferedReader br = new BufferedReader(new InputStreamReader(System.in));
-            try {
-                System.out.println("Path of projects folder:");
-                String path = br.readLine();
-                System.out.println("Destination path:");
-                String destinatioPath = br.readLine();
-                System.out.println("Result file name:");
-                String resultFileName = br.readLine();
-                FileManager.getDirectoryContents(new File(path), map);
-                map = FileManager.randomizeMap(map);
-                CsvFileWriter.writeHashMapToCsv(destinatioPath, "File Name, File Path", map, resultFileName);
-
-            } catch (IOException e) {
-                e.printStackTrace();
-            }
-            */
-        }
-
-        else if (mode.equals("f")) { // filter
-            String gcfDir = fileDir;
-            File f = new File(gcfDir);
-            if (f.exists() && f.isDirectory()) {
-                ParserManager.getInstance().simianLogsFilterParser(gcfDir, TOOL, SETTING);
-            } else {
[…]

### 2018-02-18 src/eu/giuswhite/ParserManager.java

@@ -1,138 +1,0 @@
-package eu.giuswhite;
-
-import eu.giuswhite.beans.SimianLog;
-import eu.giuswhite.beans.SimianStackoverflowFragment;
-import eu.giuswhite.comparators.SimianLogComparator;
-import eu.giuswhite.exceptions.SaxTerminatorException;
-import eu.giuswhite.handlers.ParserHandler;
-import eu.giuswhite.handlers.SimianLogsFilterHandler;
-import eu.giuswhite.handlers.UsefulSimianFragmentHandler;
-import eu.giuswhite.utils.CommonUtils;
-import eu.giuswhite.utils.CsvFileWriter;
-import eu.giuswhite.utils.FileManager;
-import eu.giuswhite.utils.XmlFileWriter;
-import org.xml.sax.SAXException;
-import org.xml.sax.helpers.DefaultHandler;
-
-import javax.xml.parsers.ParserConfigurationException;
-import javax.xml.parsers.SAXParser;
-import javax.xml.parsers.SAXParserFactory;
-import java.io.File;
-import java.io.IOException;
-import java.util.ArrayList;
-import java.util.Comparator;
-import java.util.List;
-
-/**
- * Created by GiusWhite on 20/01/2016.
- */
-public class ParserManager {
-    public static final String FILE_PATH = "./data/Posts.xml";
-
-    private static ParserManager instance = null;
-
-    private SAXParser saxParser;
-    private DefaultHandler handler;
-
-    public static int NUMBER_OF_POSTS = 0;
-    public static int NUMBER_OF_QUESTIONS = 0;
-    public static int NUMBER_OF_ANSWERS = 0;
-    public static int NUMBER_OF_JAVA_QUESTIONS = 0;
-    public static int NUMBER_OF_JAVA_ANSWERS = 0;
-    public static int NUMBER_OF_JAVA_QUESTIONS_WITH_ANSWERS = 0;
-    public static int NUMBER_OF_QUESTIONS_WITH_ANSWERS = 0;
-    public static int TOTAL_LINE_NUMBER = 0;
-
-    protected ParserManager() {
-        try {
-            SAXParserFactory saxParserFactory = SAXParserFactory.newInstance();
-            this.saxParser = saxParserFactory.newSAXParser();
-        } catch (ParserConfigurationException | SAXException e) {
-            e.printStackTrace();
-        }
-    }
-
-    public static ParserManager getInstance() {
-        if (instance == null) {
[…]

### 2018-02-18 src/eu/giuswhite/SimianLogFilter.java

@@ -1,22 +1,0 @@
-package eu.giuswhite;
-
-/**
- * Created by GiusWhite on 15/03/2016.
- */
-public class SimianLogFilter {
-    private String smianLogsPath;
-    public SimianLogFilter() {
-    }
-
-    public void setSmianLogsPath(String smianLogsPath) {
-        this.smianLogsPath = smianLogsPath;
-    }
-
-    public void filterLog(String logPath){
-
-    }
-
-    public void filterLogs(){
-
-    }
-}

### 2018-02-18 src/eu/giuswhite/beans/SimianLog.java

@@ -1,241 +1,0 @@
-package eu.giuswhite.beans;
-
-import eu.giuswhite.comparators.SimianLogComparator;
-import eu.giuswhite.utils.CommonUtils;
-
-import java.io.IOException;
-import java.util.*;
-
-/**
- * Created by GiusWhite on 15/03/2016.
- */
-public class SimianLog {
-    public int id;
-    public List<LogFragment> fragmentList;
-
-    public SimianLog() {
-        this.fragmentList = new ArrayList<>();
-    }
-
-    public LogFragment getEmptyFragment() {
-        this.fragmentList.add(new LogFragment());
-        return this.fragmentList.get(this.fragmentList.size() - 1);
-    }
-
-    public boolean isUseful() {
-        boolean result = false;
-        boolean thereIsStackOverflowFile = false;
-        boolean thereIsSrcFile = false;
-        for (LogFragment logFragment : this.fragmentList) {
-            if (logFragment.getFilePath().contains(CommonUtils.stackoverflow_path)) {
-                thereIsStackOverflowFile = true;
-            } else if (logFragment.getFilePath().contains(CommonUtils.qualitas_path)) {
-                thereIsSrcFile = true;
-            }
-        }
-        result = thereIsSrcFile && thereIsStackOverflowFile;
-
-        return result;
-    }
-
-    @Override
-    public String toString() {
-        return "SimianLog{" +
-                "id=" + id +
-                ", fragmentList=" + fragmentList +
-                '}';
-    }
-
-    public static List<SimianStackoverflowFragment> getSimianLogStats(List<SimianLog> simianLogs) {
-        HashMap<String, SimianStackoverflowFragment> result = new HashMap<>();
-        HashMap<String, Integer> projectFileMap = new HashMap<>();
-        int projectFileId = 0;
-
-        System.out.println("Reading from simian fragments ...");
-        int count = 1;
-
-        for (SimianLog s : simianLogs) {
-            System.out.println(count + "/" + simianLogs.size());
-            count++;
-
-            for (LogFragment lF : s.fragmentList) {
-
-                /* Check if it exists in the result list.*/
-                if (lF.isStackoverflowFragment) {
-                    boolean exist = false;
-                    SimianStackoverflowFragment simianStackoverflowFragment = new SimianStackoverflowFragment();
-
-                    if (result.containsKey(lF.filePath)) {
-                        // exist = true;
-                        simianStackoverflowFragment = result.get(lF.filePath);
[…]

### 2018-02-18 src/eu/giuswhite/beans/SimianStackoverflowFragment.java

@@ -1,94 +1,0 @@
-package eu.giuswhite.beans;
-
-import eu.giuswhite.utils.CommonUtils;
-
-import java.io.BufferedInputStream;
-import java.io.FileInputStream;
-import java.io.IOException;
-import java.io.InputStream;
-import java.util.ArrayList;
-import java.util.HashMap;
-import java.util.List;
-
-/**
- * Created by GiusWhite on 22/03/2016.
- */
-public class SimianStackoverflowFragment {
-    public String fragmentName;
-    public int numberOfTimeIsUsed;
-    public HashMap<Integer, Boolean> projectsWhereIsUsed;
-    public boolean[] cloneLines;
-    public int cloneLinesCount;
-    public int SLOC;
-
-    public SimianStackoverflowFragment(){
-        this.numberOfTimeIsUsed = 0;
-        this.projectsWhereIsUsed = new HashMap<>();
-        this.cloneLinesCount = 0;
-    }
-
-    public SimianStackoverflowFragment(String filePath){
-        this.numberOfTimeIsUsed = 0;
-        this.projectsWhereIsUsed = new HashMap<>();
-        try {
-            this.setSLOC(filePath);
-        } catch (IOException e) {
-            System.err.println("Error: cannot read the file.");
-            e.printStackTrace();
-        }
-    }
-
-    public void setCloneLines(int start, int end) {
-        for (int i = start - 1; i < end; i++)
-            cloneLines[i] = true;
-    }
-
-    public void increaseCloneLinesCount(int size) {
-        this.cloneLinesCount += size;
-    }
-
-    public int getCloneLinesCount() {
-        return this.cloneLinesCount;
-    }
-
-    public int getCloneLines() {
-        int count = 0;
-        for (boolean isCloned: cloneLines) {
-            if (isCloned)
-                count++;
-        }
-        return count;
-    }
-
-    public void setSLOC(String filePath) throws IOException {
-        SLOC = countLines(CommonUtils.SF_FRAG_LOCATION + "/" + filePath);
-        // initiate the clone line array as well
-        cloneLines = new boolean[SLOC];
-    }
-
-    public int getSLOC() {
-        return SLOC;
-    }
-
-    /*** Copied from http://stackoverflow.com/questions/453018/number-of-lines-in-a-file-in-java **/
-    public static int countLines(String filename) throws IOException {
-        InputStream is = new BufferedInputStream(new FileInputStream(filename));
-        try {
-            byte[] c = new byte[1024];
-            int count = 0;
-            int readChars = 0;
[…]

### 2018-02-18 src/eu/giuswhite/comparators/SimianLogComparator.java

@@ -1,34 +1,0 @@
-package eu.giuswhite.comparators;
-
-import eu.giuswhite.beans.SimianStackoverflowFragment;
-
-import java.util.Comparator;
-
-/**
- * Created by GiusWhite on 25/03/2016.
- */
-public class SimianLogComparator implements Comparator<SimianStackoverflowFragment> {
-
-    public static int USAGE = 1;
-    public static int PROJECTS = 0;
-    private int sortBy;
-
-    public SimianLogComparator(int sortBy){
-        this.sortBy = sortBy;
-    }
-
-    @Override
-    public int compare(SimianStackoverflowFragment o1, SimianStackoverflowFragment o2) {
-        if(this.sortBy == USAGE){
-            return compare(o1.numberOfTimeIsUsed, o2.numberOfTimeIsUsed);
-        } else {
-            return compare(o1.projectsWhereIsUsed.size(), o2.projectsWhereIsUsed.size());
-        }
-    }
-
-    private static int compare(int a, int b) {
-        return a < b ? -1
-                : a > b ? 1
-                : 0;
-    }
-}

### 2018-02-18 src/eu/giuswhite/handlers/ParserHandler.java

@@ -1,104 +1,0 @@
-package eu.giuswhite.handlers;
-
-import eu.giuswhite.LineCounter;
-import eu.giuswhite.ParserManager;
-import eu.giuswhite.beans.StackOverflowPost;
-import eu.giuswhite.exceptions.SaxTerminatorException;
-import eu.giuswhite.utils.CommonUtils;
-import eu.giuswhite.utils.FileManager;
-import org.xml.sax.Attributes;
-import org.xml.sax.SAXException;
-import org.xml.sax.helpers.DefaultHandler;
-
-import java.util.ArrayList;
-import java.util.List;
-
-/**
- * Created by GiusWhite on 20/01/2016.
- */
-public class ParserHandler extends DefaultHandler {
-    private StackOverflowPost stackOverflowPost = new StackOverflowPost();
-    private List<String> javaAnswersId = new ArrayList<>();
-    private ParserManager parserManager = ParserManager.getInstance();
-
-
-    @Override
-    public void startDocument() throws SAXException {
-        super.startDocument();
-    }
-
-    @Override
-    public void endDocument() throws SAXException {
-        super.endDocument();
-    }
-
-    @Override
-    public void startElement(String uri, String localName, String qName, Attributes attributes) throws SAXException {
-        //Crea elemento StackOverflowPost
-        if (qName.equals("row")) {
-            stackOverflowPost.setId(Integer.parseInt(attributes.getValue("Id")));
-            stackOverflowPost.setPostType(Integer.parseInt(attributes.getValue("PostTypeId")));
-            stackOverflowPost.setTags(attributes.getValue("Tags"));
-            String acceptedAnswerId = attributes.getValue("AcceptedAnswerId");
-            if (acceptedAnswerId != null) {
-                stackOverflowPost.setAcceptedAnswerId(Integer.parseInt(attributes.getValue("AcceptedAnswerId")));
-            } else {
-                stackOverflowPost.setAcceptedAnswerId(-1);
-            }
-            stackOverflowPost.setBody(attributes.getValue("Body"));
-        }
-    }
-
-    @Override
-    public void endElement(String uri, String localName, String qName) throws SAXException {
-        //this.getAllAnswers();
-        this.getOnlyJavaQuestions();
-        ParserManager.NUMBER_OF_POSTS++;
-        if (CommonUtils.TEST_MODE) {
[…]

### 2018-02-18 src/eu/giuswhite/handlers/SimianLogsFilterHandler.java

@@ -1,101 +1,0 @@
-package eu.giuswhite.handlers;
-
-import eu.giuswhite.beans.SimianLog;
-import org.xml.sax.Attributes;
-import org.xml.sax.SAXException;
-import org.xml.sax.helpers.DefaultHandler;
-
-import java.util.List;
-
-/**
- * Created by GiusWhite on 15/03/2016.
- */
-public class SimianLogsFilterHandler extends DefaultHandler {
-    private List<SimianLog> usefulSimianLog;
-    private SimianLog simianLog;
-    private SimianLog.LogFragment logFragment;
-    private boolean id;
-    private boolean file;
-    private boolean start;
-    private boolean end;
-
-    public SimianLogsFilterHandler(List<SimianLog> list) {
-        super();
-        this.usefulSimianLog = list;
-    }
-
-    @Override
-    public void startDocument() throws SAXException {
-        super.startDocument();
-    }
-
-    @Override
-    public void endDocument() throws SAXException {
-        super.endDocument();
-    }
-
-    @Override
-    public void startElement(String uri, String localName, String qName, Attributes attributes) throws SAXException {
-        if (qName.equals("CloneClass")) {
-            this.simianLog = new SimianLog();
-        }
-        if (qName.equals("ID")) {
-            this.id = true;
-            this.file = false;
-            this.end = false;
-            this.start = false;
-        }
-        if (qName.equals("Fragment")) {
-            this.logFragment = this.simianLog.getEmptyFragment();
-        }
-        if (qName.equals("File")) {
-            this.id = false;
-            this.file = true;
-            this.end = false;
-            this.start = false;
-        }
-        if (qName.equals("End")) {
-            this.id = false;
-            this.file = false;
-            this.end = true;
-            this.start = false;
-        }
-        if (qName.equals("Start")) {
-            this.id = false;
-            this.file = false;
-            this.end = false;
-            this.start = true;
-        }
-    }
-
-    @Override
-    public void characters(char[] ch, int start, int length) throws SAXException {
-        String value = new String(ch, start, length).trim();
-        if (value.length() == 0) {
-            return; // ignore white space
-        }
-        if (this.id) {
-            this.simianLog.id = Integer.parseInt(value);
-        }
-        if (this.file) {
-            this.logFragment.setFilePath(value);
-        }
-        if (this.start) {
-            this.logFragment.setStart(Integer.parseInt(value));
-        }
-        if (this.end) {
[…]

### 2018-02-18 src/eu/giuswhite/handlers/UsefulSimianFragmentHandler.java

@@ -1,105 +1,0 @@
-package eu.giuswhite.handlers;
-
-import eu.giuswhite.ParserManager;
-import eu.giuswhite.beans.SimianLog;
-import eu.giuswhite.beans.SimianStackoverflowFragment;
-import eu.giuswhite.exceptions.SaxTerminatorException;
-import eu.giuswhite.utils.CommonUtils;
-import org.xml.sax.Attributes;
-import org.xml.sax.SAXException;
-import org.xml.sax.helpers.DefaultHandler;
-
-import java.util.ArrayList;
-import java.util.List;
-
-/**
- * Created by GiusWhite on 21/03/2016.
- */
-public class UsefulSimianFragmentHandler extends DefaultHandler {
-    public List<SimianLog> simianLogs;
-
-    public UsefulSimianFragmentHandler() {
-        this.simianLogs = new ArrayList<>();
-    }
-
-    public UsefulSimianFragmentHandler(List<SimianLog> simianLogs) {
-        this.simianLogs = simianLogs;
-    }
-
-
-    @Override
-    public void startDocument() throws SAXException {
-        super.startDocument();
-    }
-
-    @Override
-    public void endDocument() throws SAXException {
-        super.endDocument();
-    }
-
-    @Override
-    public void characters(char[] ch, int start, int length) throws SAXException {
-        super.characters(ch, start, length);
-    }
-
-    @Override
-    public void startElement(String uri, String localName, String qName, Attributes attributes) throws SAXException {
-        this.createSimianLog(qName, attributes);
-    }
-
-    @Override
-    public void endElement(String uri, String localName, String qName) throws SAXException {
-        if (CommonUtils.TEST_MODE) {
-            if (ParserManager.NUMBER_OF_POSTS >= CommonUtils.STOP_PROCESS_FLAG) {
-                throw new SaxTerminatorException();
-            }
-        }
-    }
-    /*
-    private void getFragmentStats(String qName, Attributes attributes) {
-        SimianStackoverflowFragment actualFragment = new SimianStackoverflowFragment();
-        if (qName.equals("FRAGMENT_LOG")) {
-            String filePath = attributes.getValue("filePath");
-            if (filePath.contains("extracted_data_full")) {
-                String[] parts = filePath.split("/");
-                String fragmentName = parts[parts.length - 1];
-                boolean exixt = false;
-                for (SimianStackoverflowFragment fragment : this.stackoverflowFragments) {
-                    if (fragment.fragmentName.equals(fragmentName)) {
-                        exixt = true;
[…]

### 2018-02-18 src/eu/giuswhite/utils/CommonUtils.java

@@ -1,31 +1,0 @@
-package eu.giuswhite.utils;
-
-/**
- * Created by GiusWhite on 21/01/2016.
- */
-public class CommonUtils {
-    public static final String EXTRACTED_DATA_FOLDER_PATH = "";
-    public static final String PROJECT_FOLDER_PATH = "/Users/Chaiyong/IdeasProjects/StackOverflowAnalyzer";
-    public static final boolean TEST_MODE = true;
-    public static int STOP_PROCESS_FLAG = 10;
-    public static final String OPEN_CODE_PATTERN = "<pre><code>";
-    public static final String CLOSED_CODE_PATTERN = "</code></pre>";
-    public static final String CODE_LINES_STAT_CSV_HEADER = "# of lines, # of posts";
-    public static final String stackoverflow_path = "stackoverflow_formatted/";
-    public static final String SF_FRAG_LOCATION = "/Users/Chaiyong/Documents/stackoverflow/stackoverflow_formatted";
-    public static final String qualitas_path = "src/";
-
-    public static boolean isError(String fragId) {
-        // check for 11 fragments generating Simian's sliding error clones.
-        if (fragId.contains("16327677_0.java") || fragId.contains("25018225_0.java")
-                || fragId.contains("21535828_0.java") || fragId.contains("22041769_1.java")
-                || fragId.contains("12124636_0.java") || fragId.contains("21655588_0.java")
-                || fragId.contains("5066587_0.java") || fragId.contains("19051537_0.java")
-                || fragId.contains("18877151_0.java") || fragId.contains("3215448_0.java")
-                || fragId.contains("25703453_0.java")) {
-            System.out.println("Found error fragment " + fragId + ": skipping ... ");
-            return true;
-        } else
-            return false;
-    }
-}

### 2018-02-18 src/eu/giuswhite/utils/CsvFileWriter.java

@@ -1,90 +1,0 @@
-package eu.giuswhite.utils;
-
-import eu.giuswhite.beans.SimianStackoverflowFragment;
-import org.supercsv.io.CsvListWriter;
-import org.supercsv.io.ICsvListWriter;
-import org.supercsv.prefs.CsvPreference;
-
-import java.io.IOException;
-import java.io.StringWriter;
-import java.util.*;
-
-/**
- * Created by GiusWhite on 01/02/2016.
- */
-public class CsvFileWriter {
-
-    public static void writeHashMapToCsv(String header, Map<Object, Object> map, String filename) {
-        StringWriter output = new StringWriter();
-        try (ICsvListWriter listWriter = new CsvListWriter(output,
-                CsvPreference.STANDARD_PREFERENCE)) {
-            for (Map.Entry<Object, Object> entry : map.entrySet()) {
-                listWriter.write(entry.getKey(), entry.getValue());
-            }
-        } catch (IOException e) {
-            e.printStackTrace();
-        }
-        String result = header + "\n" + output.toString();
-        FileManager.getInstance().createAndWriteFile(CommonUtils.PROJECT_FOLDER_PATH + "/stats", filename + ".csv", result, false);
-    }
-
-    public static void writeHashMapToCsv(String destinationPath, String header, Map<?, ?> map, String filename) {
-        StringWriter output = new StringWriter();
-        try (ICsvListWriter listWriter = new CsvListWriter(output,
-                CsvPreference.STANDARD_PREFERENCE)) {
-            for (Map.Entry<?, ?> entry : map.entrySet()) {
-                listWriter.write(entry.getKey(), entry.getValue());
-            }
-        } catch (IOException e) {
-            e.printStackTrace();
-        }
-        String result = header + "\n" + output.toString();
-        FileManager.getInstance().createAndWriteFile(destinationPath, filename + ".csv", result, false);
-    }
-
-    public static Map<Object, Object> sortHashMapByKey(Map<Object, Object> unsortedMap) {
-        return new TreeMap<>(unsortedMap);
-    }
-
-    public static <K, V extends Comparable<? super V>> Map<K, V>
-    sortByValue(Map<K, V> map) {
-        List<Map.Entry<K, V>> list =
-                new LinkedList<Map.Entry<K, V>>(map.entrySet());
-        Collections.sort(list, new Comparator<Map.Entry<K, V>>() {
[…]

### 2018-02-18 src/eu/giuswhite/utils/FileManager.java

@@ -1,146 +1,0 @@
-package eu.giuswhite.utils;
-
-import org.apache.commons.io.FileUtils;
-
-import java.io.*;
-import java.nio.file.Files;
-import java.nio.file.Paths;
-import java.util.*;
-
-/**
- * Created by GiusWhite on 21/01/2016.
- */
-public class FileManager {
-    private static FileManager instance = null;
-
-    protected FileManager() {
-    }
-
-    public static FileManager getInstance() {
-        if (instance == null) {
-            instance = new FileManager();
-        }
-        return instance;
-    }
-
-    public void createAndWriteFile(String path, String fileName, String body, boolean reformatCode) {
-        System.out.println("\nWriting to " + path + "/" + fileName);
-        File file = new File(path + "/" + fileName);
-        try {
-            if (!Files.exists(Paths.get(path))) {
-                File f = new File(path);
-                f.mkdir();
-            }
-            if (!file.exists()) {
-                file.createNewFile();
-            }
-            FileWriter fileWriter = new FileWriter(file.getAbsoluteFile());
-            BufferedWriter bufferedWriter = new BufferedWriter(fileWriter);
-            if (!reformatCode) {
-                this.writeFormattedBody(body, bufferedWriter);
-            } else {
-                String[] formattedBodyStrings = this.splitBody(body);
-                this.writeFormattedString(formattedBodyStrings, bufferedWriter);
-            }
-            bufferedWriter.close();
-        } catch (IOException e) {
-            e.printStackTrace();
-        }
-    }
-
-    private String[] splitBody(String inlineCode) {
-        String[] result = inlineCode.split("<br>");
-        return result;
-    }
-
-    private void writeFormattedString(String[] inlineCode, BufferedWriter bufferedWriter) throws IOException {
-        for (String s : inlineCode) {
-            bufferedWriter.write(s);
-            bufferedWriter.newLine();
-        }
-    }
-
-    public void writeFormattedBody(String inlineCode, BufferedWriter bufferedWriter) throws IOException {
-        bufferedWriter.write(inlineCode);
-    }
-
-    public static void splitFolderContent(String folderPath, String newFolderPath, int numberOfSubGroup) {
-        if (!Files.exists(Paths.get(newFolderPath))) {
-            File f = new File(newFolderPath);
-            f.mkdir();
-        }
-        int counter = 0;
-        List<String> folderContent = new ArrayList<>();
-        File file = new File(folderPath);
-        FileManager.getDirectoryContents(file, folderContent);
-        try {
[…]

### 2018-02-18 src/eu/giuswhite/utils/XmlFileWriter.java

@@ -1,59 +1,0 @@
-package eu.giuswhite.utils;
-
-import eu.giuswhite.beans.SimianLog;
-import org.jdom2.Document;
-import org.jdom2.Element;
-import org.jdom2.output.Format;
-import org.jdom2.output.XMLOutputter;
-
-import java.io.File;
-import java.io.FileWriter;
-import java.io.IOException;
-import java.util.List;
-
-
-/**
- * Created by GiusWhite on 16/03/2016.
- */
-public class XmlFileWriter {
-
-    public static void writeSimianUsefulFragmentsToXml(String filename, List<SimianLog> content) {
-        try {
-            Document doc = new Document();
-            Element root = new Element("FRAGMENTS");
-            for (SimianLog simianLog : content) {
-                Element sL = new Element("SIMIAN_LOG");
-                sL.setAttribute("ID", String.valueOf(simianLog.id));
-                boolean foundErrorFrag = false;
-                for (SimianLog.LogFragment logFragment : simianLog.fragmentList) {
-                    // TODO: have to check this list of error fragments everytime before running!
-                    // check if the fragment is in the error list, skip it
-                     if (! CommonUtils.isError(logFragment.filePath)) {
-                        Element lF = new Element("FRAGMENT_LOG");
-                        lF.setAttribute("filePath", logFragment.filePath);
-                        lF.setAttribute("start", String.valueOf(logFragment.start));
-                        lF.setAttribute("end", String.valueOf(logFragment.end));
-                        sL.addContent(lF);
-                      }
-                     // else {
-                        // found error pairs, skip the whole cluster
-                         foundErrorFrag = true;
-                     //}
-                }
-
-                // if (!foundErrorFrag)
-
-                // has at least one S-Q clone pair
-                if (sL.getContentSize()>1)
-                    root.addContent(sL);
-            }
-
-            doc.setRootElement(root);
-            XMLOutputter outter = new XMLOutputter();
-            outter.setFormat(Format.getPrettyFormat());
-            outter.output(doc, new FileWriter(new File(filename + ".xml")));
-        } catch (IOException e) {
-            e.printStackTrace();
-        }
-    }
-}

### 2018-02-21 programs/GCFtoCSV/main.py
Added a new program to convert GCF to CSV

@@ -1,0 +1,38 @@
+import xml.etree.ElementTree
+import sys
+
+
+
+def writefile(filename, fcontent, mode, isprint):
+    """
+    Write the string content to a file
+    copied from
+    http://www.pythonforbeginners.com/files/reading-and-writing-files-in-python
+    :param filename: name of the file
+    :param fcontent: string content to put into the file
+    :param mode: writing mode, 'w' overwrite every time, 'a' append to an existing file
+    :return: N/A
+    """
+    # try:
+    file = open(filename, mode)
+    file.write(fcontent)
+    file.close()
+
+    if isprint:
+        print("saved:" + filename)
+
+
+def main():
+    scc_clones = xml.etree.ElementTree.parse(sys.argv[1])
+    clones = scc_clones.findall('CloneClass')
+    output = ''
+    num_pairs = len(clones)
+    for idx, clone in enumerate(clones):
+        pair = clone.findall('Clone')
+        output += pair[0][0][0].text + ',' + pair[0][0][1].text + ',' + pair[0][0][2].text + ','
+        output += pair[1][0][0].text + ',' + pair[1][0][1].text + ',' + pair[1][0][2].text + '\n'
+
+    print('processed:', num_pairs + 1, 'files')
+    writefile(sys.argv[1].replace('.xml', '.csv'), output, 'w', True)
+
+main()

### 2018-02-21 programs/SCCTokenizer/file_concatenator_with_clone_filter.py
SCCTokenizer: added usage and outdated clone snippet filter.

@@ -36,6 +36,14 @@ def get_file_list(home_dir, filter):
     return all_files
 
 
+def get_outdated_clones(clone_list):
+    with open(clone_list, 'r') as f:
+        lines = f.readlines()
+    # remove '\n' at the end
+    lines = [line.strip() for line in lines]
+    return lines
+
+
 def createFileId(file):
     global file_id_list
     global starting_blockid
@@ -83,7 +91,8 @@ def main():
 
     if len(sys.argv) == 1:
         print '-' * 60
-        print 'Usage: python file_concatenator.py <location of SO snippets> <starting ID>'
+        print 'Usage: python file_concatenator.py <location of SO snippets> <starting ID> <outdated clone list> <basepath>'
+        print 'Note: outdated clone list looks like this ... <SO ID>,<Start line>,<End line>'
         print '-' * 60
         exit()
 
@@ -105,15 +114,13 @@ def main():
     # get the starting id, if not, start at 0
     global starting_blockid
     global starting_postid
-
     starting_blockid = int(sys.argv[2])
+    outdated_clones = get_outdated_clones(sys.argv[3])
 
-    # if len(sys.argv) == 4:
-        # starting_postid = int(sys.argv[2])
-
+    basepath = sys.argv[4]
     print "files: ", len(javafiles)
-    
     p_start = dt.datetime.now()
+    found_clones = 0
 
     # start method extraction
     for index, jfile in enumerate(javafiles):
@@ -127,18 +134,36 @@ def main():
                 method_parts = method.split("@@UCL@@")
                 lines = len(method_parts[1].strip().split("\n"))
 
+                # location[0] = starting line, location[1] = ending line
+                location = method_parts[0].strip().split(',')
+                clone = jfile.replace(basepath, '') + ',' + method_parts[0].strip()
+                print clone
+
                 # filter for only the one with more than 10 lines
                 if lines >= 10:
-                    writefile("so.txt", "===@@@UCI===\n", "a", False)
-                    id = createFileId(jfile + "," + method_parts[0].strip())
-                    # writefile("so.txt", str(index + starting_postid) + "\n", "a", False)
-                    # -1 means we don't care about parentId
-                    writefile("so.txt", "-1\n", "a", False)
-                    writefile("so.txt", str(id) + "\n", "a", False)
-                    writefile("so.txt", method_parts[1].strip() + "\n", "a", False)
+                    clone_add1 = jfile.replace(basepath, '') + ',' + location[0] + ',' + str(int(location[1]) + 1)
[…]

### 2018-05-09 cloverflow-tse/cover_letter/cover_letter.tex
Updated the cover letter.

@@
 
+\newcommand\FIXME[1]{{\color{red}\textbf{FIXME: #1}}}
+
 \begin{document}
@@
 This is a re-submission of the previous submission no.~TSE-2017-11-0335 and we would like to thank the anonymous Reviewers for taking their time to carefully read our paper.
-With their useful and constructive reviews, we substantially improved the work by adding the following improvements:
+With their useful and constructive reviews, we substantially improved the work by adding three major improvements as listed below to our previous submission and minor improvements as discussed later in this letter:
 
 \textbf{1.
-A study of toxic code snippets on GitHub:}~To provide an evidence that toxic code snippets are actually reused in software projects and strengthen the motivation, we performed a large-scale analysis of clones between toxic code snippets found on Stack Overflow and GitHub projects.
+A study of toxic code snippets on GitHub:}~To provide an evidence that toxic code snippets are actually reused in software projects and strengthen the motivation, we performed a large-scale analysis of clones between toxic code snippets on Stack Overflow and xxx,xxx GitHub projects.
 
@@
 \rcomment{
-Regarding this statement: ``It is probably more important than studying the effects of reusing Stack Overflow code snippets because it gives insights to the root cause of the problem and lays a foundation to an automatic technique to detect and report toxic code snippets on Stack Overflow to developers in the future.''
+Regarding this statement: \textit{``It is probably more important than studying the effects of reusing Stack Overflow code snippets because it gives insights to the root cause of the problem and lays a foundation to an automatic technique to detect and report toxic code snippets on Stack Overflow to developers in the future.''}
 
-While~\cite{An2017} do suggest that copying from Stack Overflow to software projects occurs (and results in license violations), they do not establish that code snippets from Stack Overflow ``go viral'' and end up distributed widely across (open or closed source) software projects.
-Moreover, while the quote on the first page implies that developers often ``mindlessly'' reuse code snippets from Stack Overflow, to the best of my knowledge, this claim is conventional wisdom but not empirically validated.
+While~\cite{An2017} do suggest that copying from Stack Overflow to software projects occurs (and results in license violations), they do not establish that code snippets from Stack Overflow \textit{``go viral''} and end up distributed widely across (open or closed source) software projects.
+Moreover, while the quote on the first page implies that developers often \textit{``mindlessly''} reuse code snippets from Stack Overflow, to the best of my knowledge, this claim is conventional wisdom but not empirically validated.
 So, it seems to me that the primary interest in toxic code snippets is that may cause widespread harm, but I am missing the evidence that they do so in practice.
@@
 In the end, I agree that it is better to detect and report toxic code snippets than to not do so, but I am not sure how big of a problem is solved by doing so.
-As such, I disagree that it is ``probably more important'' to find the toxic code snippets than to understand their effects.
+As such, I disagree that it is \textit{``probably more important''} to find the toxic code snippets than to understand their effects.
 Instead, I think that understanding their effects (on software projects rather than on the quality of the Stack Overflow platform) is necessary to appreciate the value in finding them.
@@
 
-We would like to thank for the comments.~We agree with the concern of real evidence that code snippets on Stack Overflow ...
+We would like to thank the reviewer for the comments.~We agree with the suggestion and we made the following changes to the paper:
+
+\begin{enumerate}
+	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects.
+Hence, we have performed a study of code clone detection between our reported outdated code fragments on Stack Overflow and 131,307 most starred GitHub projects.
+We found that there are xxx clone instances of xxx outdated Stack Overflow code snippets appearing in xx GitHub projects.
+Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks).
+Unfortunately, due to the lack of evidence, we could not explain how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects.
+It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.
+
+	Nevertheless, we decided to report the developers of the two projects regarding the issue.
+We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers of the projects by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop.
+The issue has been fixed in deeplearning4j.
+The developers of deeplearning4j agreed that the method was problematic and they decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base.
+On the other hand, the bug report in Apache Hive is still unfixed.
+	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub.
+However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information.
+Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets because ...
+developers in the future.}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets because ...
+developers in the future.}''.
+\end{enumerate}
 
@@
 But I am missing the awareness of Stack Overflow questioners or information-seekers to toxic code snippets.
-I wonder: how skeptical are developers when considering code snippets on Stack Overflow, how often do developers use code snippets directly, and how often do developers use clues such as ``A quick google search returned me this from Appache hadoop project.
-Copying from there:'' to seek out the latest version of the information provided in the answer.
+I wonder: how skeptical are developers when considering code snippets on Stack Overflow, how often do developers use code snippets directly, and how often do developers use clues such as \textit{``A quick google search returned me this from Appache hadoop project.
+Copying from there:''} to seek out the latest version of the information provided in the answer.
 The survey responses described in Section 3.5.3 suggest that there are questioners/information-seekers that are aware of toxic code snippets (as they are reporting them to the answerers), and there is evidence that the Stack Overflow community is aware of the need to retire outdated information and of the many concerns related to software licensing, as these issues are discussed on meta.stackoverflow.com.
@@
 
+We partially address this comment in the previous answer by performing an empirical study of code cloning between Stack Overflow toxic code snippets and GitHub projects.
+Furthermore, we also improved the paper on the aspect of the awareness of information-seekers to toxic code snippets on Stack Overflow by including the results from another survey of Stack Overflow visitors (i.e.~information seekers).
+This survey of the Stack Overflow visitors was performed during the same time as the Stack Overflow answerers (25 July 2017 to 25 September 2017).
+We did not include the results in the previous version of the paper due to a smaller sample size compared to the answerers survey.
+However, we did find some interesting results and we discussed only the key findings in~Section \ref{#}.
+We copied the text below.
+
+\textbf{Stack Overflow visitors' survey}
+
+We adopted non-probability convenient sampling to invite participants for this survey.
+Participation in the survey requires experience of visiting Stack Overflow for solving programming tasks at least once.
+The participants were invited to take the survey via various channels: social media post (Facebook), Thailand's popular technology news and media community in Thailand called \texttt{blognone.com}, the University of Molise in Italy where the third author works, \texttt{comp.lang.java.programmer} group and the Software Engineering Facebook page.
+We received answers from 89 participants.
+Two participants never copy code from Stack Overflow so we analysed the answers of the remaining 87 participants.
+The key findings are as follows.
+
+Stack Overflow is ranked higher than official documentation, online repositories, and books as the resource to look for programming solutions.
+Developers rely on Stack Overflow answers because they are easy to search for on the web.
+Moreover, 64\% of the participants reuse code snippets from Stack Overflow at least once a week.
+They copy code from Stack Overflow because they can be found easily from search engine, solve similar problems to their problems, provide helpful context, and offer voting and accepted answers.
+The results show that 57 out of 87 Stack Overflow visitors encountered a problem from reusing Stack Overflow code snippets.
+Ten participants experienced problems for more than 80\% of the copied snippets and sixteen participants faced problems for 40--60\% of the reused code.
+The problems ranked by frequency include mismatched solutions (40), outdated solutions (39), incorrect solutions (28), and buggy code (1).
+Fifty-six percent of the participants never report the problems back to Stack Overflow.
+In addition, 85\% of the participants are not aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts they copied the code snippets from.
+We found that 66\% of the visitors never check for software licensing conflicts between Stack Overflow code snippets and their projects.
+Interestingly, 9\% of the participants encountered legal issues.
+Unfortunately, due to the anonymity of the survey, we could not investigate further regarding the legal issues that the participants faced from using Stack Overflow code snippets.
+
 \rcomment{
-	The ``Overall Discussion'' section is not commensurate with the quality and breadth of the empirical study.
+	The \textbf{Overall Discussion} section is not commensurate with the quality and breadth of the empirical study.
 The proposed preventative measure is actually two measures: a policy change and an IDE plugin.
@@
 
+Thanks for the suggestion.~We rewrote the Overall Discussion section to be more precise and practical as discussed below.
+
+Using the updated definition of outdated code, we foresee the implementation of the IDE plugin using a combination of scalable code clone detection~\citep{Sajnani2016} or clone search techniques~\citep{Kim2018} and automated software licensing detection~\citep{German2010}.
+In this study, we performed the check using a set of code clone detectors (Simian and SourcererCC) and software licensing detector (Ninka) but we had to operate the tools manually.
+Using the knowledge obtained from this study, we plan to build an automated and scalable clone search with licensing detection.
+With the proposed solution, we can use the tool to create a database of code snippets on Stack Overflow and allow the users to search for clones and check their licenses.
+The clone search tool can offer a service via REST API and integrated into the IDE plugin.
+Every time a new code fragment is pasted into the IDE, the plugin performs the check by calling the clone search tool service and report the finding to the developers in real time.
+
+In addition, we also performed a small survey of software auditing platforms/services including:~\FIXME{Blackduck OpenHub, foo, and bar} and found that, while they check for code copied from open source projects and analyse their license compatibility, none of them offers the checking for cloned code from Stack Overflow.
+So, our proposed service will be useful as an add-on check for code copying from Stack Overflow and their license implications.
+
+For the detective measure, while checking if the copied code snippets on Stack Overflow are still up-to-date with the latest version of their originals can possibly be done automatically, it is a challenging task to automate the process of establishing the origin of code clones.
+As shown in this study, we still relied on manual validation to read the post, understand the context, and use multiple hints with human judgement (comments in the code, natural text in the question and answers, date/time of the posts) to conclude that the code snippets are actually copied from Qualitas to Stack Overflow.
+Thus, one viable solution for now is encouraging the Stack Overflow developers to always include the origin of the copied code snippet in the post so that this link is always established at the posting time.
+Even better, Stack Overflow can provide an optional form to fill in when an answerer post an answer if he or she copies code from other software projects.
+The form should include the origin of the code snippet and its original license.
+
 \rcomment{
 Other Comments
+While ``Toxic Code Snippets'' is a catchy phrase for the title, I think that online code clones are the dominant topic.}
 
-\begin{itemize}
-	\item While ``Toxic Code Snippets'' is a catchy phrase for the title, I think that online code clones are the dominant topic.
-	\item The introduction states that the erroneous code snippet in post 22262310 has been viewed 259 as of the writing of the paper.
+You are right.
+We mainly study the online code clones and established their existence.
+However, we coined the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning.
+We updated the Introduction to be clearer on this point~\FIXME{to do}.
+%Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.
+
+\rcomment{
+	The introduction states that the erroneous code snippet in post 22262310 has been viewed 259 as of the writing of the paper.
 But I note that while the question was posted on Mar 7, 14 the answer was posted on Mar 11, 14.
 I also note that the question has a score of -1.
-So, I wonder (a) whether the view count is for the answer (i.e., the code snippet) or the post (which existed for a few days before the answer appeared), (b) how many people viewed the question before it was answered, and (c) if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.
-	\item FYI, since this paper was authored, a Stack Overflow user has posted a comment in response to the answer for post 22262310.
+So, I wonder (a) whether the view count is for the answer (i.e., the code snippet) or the post (which existed for a few days before the answer appeared), (b) how many people viewed the question before it was answered, and (c) if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.}
+
+That is a fair point and we would like to analyse the statistics as you suggested.
+Unfortunately, for our experiment, we extracted only the code snippets from the Stack Overflow dumps but not other information.
+They are the only available data of the January 2016 snapshot we currently have.
+We checked and found that the latest available Stack Overflow dump already contains different data than the one we used in our study since it is now more than 2 years newer, and will result in incorrect statistics and inconsistent results.
+Nevertheless, we have modified the text in the Introduction to include your concern ...
+\FIXME{do this}.
+
+\rcomment{
+	FYI, since this paper was authored, a Stack Overflow user has posted a comment in response to the answer for post 22262310.
 The comment highlights the missing line and refers to the relevant HADOOP issue report.
@@
 I wonder how many views occurred during this gap and whether the addition of the comment mitigates the toxicity of the code snippet.
+}
+
+Thank you for the detailed checking of the Stack Overflow post.
+Interestingly, this is surprising to us as well.
+The comment in the post 22262310 by Joseph K on 31 October 2017 that highlights the missing line in HADOOP \texttt{compare} method is actually from a student in our class.
+His name is Joseph Kalash and he is a master student in Machine Learning MsC program at UCL Computer Science department \footnote{Joseph's CV can be found here: \url{https://jkala.sh/cv}}.
+We assigned a preprint of this paper to students in the COMPGS11 -- Research Seminar in Software Engineering course and had a discussion about the paper on Thu 2 November 2017.
+Joseph, who was an active Stack Overflow member, was one of the students in the class and he actively participated in the discussion.
+It seemed like he had seen the Hadoop's toxic code snippet in the paper and decided to post a comment to warn other users.
+
+Nevertheless, since this is a very interesting suggestion.
+We also performed an investigation of the 101 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet.
+We include the result of this investigation in the RQ regarding outdated code (RQ?).
+We found that, out of 101 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment).
+Thus, there is about 6\% of outdated answers that were notified by the Stack Overflow users based on our analysed data.
+We added this discussion in the RQ\FIXME{?}.
+
+\rcomment{
+\begin{enumerate}
 	\item Table 1 has a median column. Median of what?
@@
 	\item Typo: ``how much the community trust them'' --> ``how much the community trusts them''
-\end{itemize}
+\end{enumerate}
 }
+
+\begin{enumerate}
+	\item For the Stack Overflow data set, the value represents the median size of Stack Overflow code snippets.
+For the Qualitas data set, the value represents the median of number of lines of code in each project.
+Since they are confusing as you pointed out, we decided to remove them from the table and only discuss the numbers in the text.
+	\item That is a good idea. We included this discussion in the future work.
+	\item Thanks. This has been fixed.
+\end{enumerate}
 
@@
 
-We appreciate the comments.
+We appreciate the comments. We have refined our definition of toxic code snippets in the paper to:
+
+\FIXME{Is this ok?}~``Toxic code snippets mean cloned code snippets that
+are harmful for reuse due to (1) being outdated and containing bugs or (2) violating their original software license. They are two ramifications of code cloning
+including bug propagation~\citep{Bellon2007}
+and software license violations~\citep{An2017}.
+Toxic code snippets can occur in software projects or programming Q\&A websites, such
+as Stack Overflow.
+This study focuses on toxic code snippets that occur on Stack Overflow and how they occur.''
 
@@
 This can be an easy fix, but it is an important one since it makes your paper seem less cohesive.
+}
 
-	\vspace{1ex}
+Regarding RQ4 (Software licensing violation), it needs to follow RQ 1--2 because the license violation needs evidence of cloning direction.
+To put it another way, we could tell that the code snippets on Stack Overflow may have incompatible licenses to their originals after we confirmed that (1) the Stack Overflow code snippets were actually clones of Qualitas projects and (2) the direction of cloning was from Qualitas to Stack Overflow, which both are addressed in RQ1 and RQ2.
+Nevertheless, RQ4 does not need to follow RQ3 (Outdated online code clones) because they are independent of each other.
+
+Regarding RQ5 (the Stack Overflow answerer survey), that is a good point.
+Since RQ5 actually supports the motivation of our experiment by showing that code copying from software projects to Stack Overflow actually occurs and showing that some of the answerers are not aware of outdated code and software license incompatibility.
+We moved them to RQ1 instead and reorganised the paper to discuss the survey results as a support for our experiment of online code clone detection and toxic code snippet identification.
+The findings in RQ2--5 will support the survey results by showing that the issues actually occur on Stack Overflow.
+
+\rcomment{
 	\textit{Issues related to RQs}
@@
 
-	\begin{itemize}
-		\item RQ3.~I believe that the answer to this question is expected and perhaps the way that the authors answered this question is incorrect.
+	RQ3.~I believe that the answer to this question is expected and perhaps the way that the authors answered this question is incorrect.
 If I use some code from SO that was posted in 2014, then I expect that it is outdated.
@@
 This was never considered by the authors.
-		\item In section 2.4, you consider a change to the code in the Q project to be evidence that the snippet is outdated.
+}
+
+Stack Overflow allows its users to edit their own posts, i.e.~questions/answers~\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts~\footnote{https://stackoverflow.com/help/privileges/edit}.
+Thus, if the code snippet in an answer is outdated and has an issue, the answerer or other high-reputation users can update the answer to be up-to-date or to warn other users that the code is already outdated and may contain problems.
+We found some discussions regarding this concern on Metaexchange as well so the Stack Overflow community is also considering this option~\footnote{Discussion about outdated answer: https://meta.stackexchange.com/questions/131495/how-to-handle-outdated-answers and https://meta.stackexchange.com/questions/180864/editing-outdated-source-code-in-an-answer}.
+We included this discussion in the paper.
+
+Based on your suggestion of looking at other newer or higher-voted answers, we performed an investigation of all the answers in 101 posts containing outdated code snippets as accepted answers.
+We discussed the findings in the relevant RQ.
+\FIXME{Add the findings.}
+
+\rcomment{
+	In section 2.4, you consider a change to the code in the Q project to be evidence that the snippet is outdated.
 How do you control for changes that are simply due to evolution?
 For example, what if I refactor the code and change the variable names of the snippet.
-	\end{itemize}
 }
+
+Good point.
+Although we grouped the code modifications that make Stack Overflow snippets outdated into 6 categories as shown in Table 9, we did not investigate the motivation of the changes such as code refactoring or variable renaming.
+We have performed the check as you suggested by checking the commit message of each change that make the code outdated and included the findings in RQ?.
+\FIXME{Add the findings.}
 
@@
 
+We used the Stack Overflow data dump of January 2016 since it was the latest dump when we started our experiment.
+Nonetheless, we finally completed the whole experiment, the result analysis, and the survey two years later.
+That is why the dump is 2 years old.
+
+Fortunately, we could use this opportunity to study the evolution of the toxic code snippets on Stack Overflow.
+We manually investigated the outdated and license incompatible code snippets that we discovered to see if they are still the same or not.
+The check was performed on 6 May 2018, approximately 2 years after the snapshot was created.
+Moreover, we also checked if there is any comment regarding the outdated code or the license of the snippets from other Stack Overflow users.
+For the 101 outdated answers, we found that one answer was deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue.
+For the xxx license-incompatible answers, \FIXME{add the results}.
+We included this discussion in RQ\FIXME{?} and RQ\FIXME{?}.
+
 \rcomment{
@@
 Given that this is a journal paper, you have the space to examine the impact of your parameters (at least in brief) on your results.
-What I would like the authors to do is to actually examine the impact of such parameters on your work in a discussion section.
+What I would like the authors to do is to actually examine the impact of such parameters on your work in a discussion section.}
+
+That is a fair point.
+The reason we chose the clone size of at least 10 lines is as follows.
+The minimum clone size of 10 lines is considered a standard setting for clone detection in large-scale data sets to avoid trivial clones (e.g.
+\texttt{equals}, \texttt{hashCode}, or getter and setter methods) in the analysis or the manual investigation phase~\citep{Sajnani2016}.
+Choosing this size threshold larger than 10 could possibly remove some non-trivial clones from the analysis, i.e.~create more false negatives.
+On the other hand, decreasing the threshold to be lower than 10 lines will result in a larger number of clone candidate pairs to look at and a higher chance of getting false positives.
+Moreover, the large number of clone pairs will hinders the full manual validation of the clones and force us to rely on sampling of clone pairs.
+We performed a small analysis to confirm this.
+
+Regarding increasing the minimum clone size to more than 10 lines (e.g.
+15 lines), we added an analysis of the clone size as shown in Figure 6.
+We found that the distribution of true clones; QS, SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines.
+Increasing the threshold to be higher than 10 would remove some of the trivial BP and IN clone pairs which are not interesting for this study.
+However, it will also remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.
+
+Regarding decreasing the minimum clone size to be less than 10 lines, we reran the two clone detection tools (Simian and SourcererCC) again using a minimum clone size of 6 lines, another well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
+Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs using Bellon's ok-match threshold $t=0.5$.
+With this large amount of clone candidate pairs, it is not feasible to manually confirm all of the clones and we must rely on sampling.
+This will result in weaker findings and weaker conclusion.
+Thus, we decide to retain the minimum clone size of 10 lines to keep the balance between the number of non-trivial clone pairs and the feasibility of manual clone investigation.
+
+We have modified the paper to include this discussion.
+
+\rcomment{
  A similar concern exists on page 5, where t=0.7 is chosen.
@@
 }
+
+We selected the Bellon's ok-match threshold of 0.7 because it is a standard value in clone benchmarking \citep{Bellon2007} and also used in other study of clones, e.g.~\cite{Sajnani2016}.
+Nevertheless, we agree that varying the threshold ($t$) value is beneficial to the validity of the findings so we did an analysis by choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
+As shown in the our paper, by setting $t=0.7$ according to Bellon's study, we found 97 ok-match pairs reported.
+On the other hand, setting $t$ to 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
+Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually checked all the 111 reported pairs.
+We found one false positive pair and 110 true positive pairs.
+By raising the $t$ to 0.3 and 0.5, we got rid of the false positive pair and still retained all the 110 true positive pairs.
+All the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a subset of $t=0.5$.
+However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates in the final merged clone set.
+
+With this analysis, we can see that setting the threshold $t$ to 0.1 is too relaxed and results in having false positive ok-match pairs, while setting the $t$ to 0.7 or 0.9 is too strict and generates some false negative pairs.
+Thus, we decided to select the $t$ value at 0.5.
+This reduces the number of merged clone pairs to 2,290 pairs.
+All other numbers which derive from this merged clone pairs have been updated accordingly.
 
@@
 	In fact, in the answer of RQ1, you explicitly say ``...share similar code with SO ...'', but throughout the paper, you present the work as if the code came from SO -> Q or vice versa.
+}
 
-	\vspace{1ex}
+For the QS clone pairs, we \textbf{manually confirmed with evidence} that the Stack Overflow code snippets were actually copied from Qualitas projects.
+This was done by the two authors reading the Stack Overflow answers containing the QS code snippets and looked for evidence such as explanation in the text or the code comments and made their decision.
+The two authors also compared their results and discussed until a consensus was made.
+Similarly, the same process was applied for the SQ clone pair.
+%For the SQ pair we discovered, we found
+%evidence of cloning from Stack Overflow post ID 698283 to
+%{\small\texttt{POIUtils.java}} in \textsf{jstock} project. The user
+%who asked the question on Stack Overflow is an author of
+%\textsf{jstock}. The question is about determining the right method to call
+%among 7 overloading methods of {\small\texttt{setCellValue}} during runtime. We
+%could not find evidence of copying or attribution to Stack Overflow in
+%\textsf{jstock}. However, considering that the 25 lines of code of
+%{\small\texttt{findMethodToInvoke}} method depicted in Figure 7 in Stack
+%Overflow is very similar to the code in \textsf{jstock} including comments, it is almost certain that
+%the two code snippets form a clone pair. In addition, the Stack Overflow answer was
+%posted on March 30, 2009, while the code in {\small\texttt{POIUtils}} class in
+%\textsf{jstock} was committed to GitHub on the next day of March 31, 2009.
+In case of a doubt or not enough evidence, we always categorised the clone pairs into UD (unknown direction) instead.
+
+To emphasise this point, we also modified the answer of the RQ to be clearer. It now says ``\FIXME{...}''.
+
+\rcomment{
 	And given the types of clones you find (e.g., BP code), this can really come from anywhere (and more likely to come from things like tutorials or IDEs).
@@
 }
+
+You are correct regarding the BP clone pairs.
+They can really come from anywhere (we did find that some of the BP clone pairs were auto-generated code by NetBeans) and that is why we did not draw any conclusion about them.
+Moreover, thank you for pointing out the inappropriate naming for AC. We now renamed them from AC to NC (i.e.~Not Clones).
 
@@
 
+%Our apologies if the writing in section 3.5.3 confuses you. 
+The research question (section 3.5.3) is actually about notifying the answerers that their answers are already outdated, not notifying the users of the outdated code snippets.
+This notification to the answerer can be done by posting comments for that answer on Stack Overflow.
+For example, the answerer of the Stack Overflow question no.~10924648 posted a comment on his own answer saying that the answer is specifically for Spring 3.1.
+Moroever, another user posted a comment on the answer of the post no.~801935 that the code snippet is not of high quality and suggested an alternative in another post.
+
 \rcomment{
@@
 
-\clearpage
+You are right. We fixed the text in the RQ to say that we surveyed 201 participants.
 
@@
 We are grateful for the insightful comment.
+We performed another manual check of the outdated clones as you suggested and the findings are discussed in Section X.
+We selected the 2013 snapshot of Qualitas data since it is the latest and the most complete snapshot (i.e.~having the highest number of Java projects) provided by the data set author.
+
+Regarding the age of cloned code on Stack Overflow, we did the analysis and added a boxplot as you suggested in RQ X. We found that ... \FIXME{add the discussion}.
 
@@
 }
+
+We expanded the analysis of the survey results \FIXME{Where?
+and How?} and now moved them to RQ1 to better link with the motivation.
+We also added results of another survey, the Stack Overflow visitor survey, to understand the awareness of the developers who copied code snippets from Stack Overflow regarding outdated and license-incompatible code.
 
@@
 
+We have performed an additional experiment to search for occurrences of outdated code snippets in open source GitHub projects. The findings show \FIXME{...}
+
 \vspace{1cm}
 
+\section{Conclusion}
 Finally, we would like to thank the reviewers again for the comments.
-We believe this new submission has been considerably improved from the previous version due to the insightful reviews and discussions.
+We have addressed every concern that has been pointed out by the reviewers which result in inclusion of a Stack Overflow visitors' survey, an analysis of toxic code snippets in GitHub projects, analysis of different tools' and technique's parameters, the definition of toxic code snippets, and the improvements in writing.
+We believe this new submission has been considerably improved from the previous version due to the insightful reviews and discussions and we are looking forward to the new reviews.
 
@@
 \bibliographystyle{spbasic}
-\bibliography{bib}
+\bibliography{references}
 

### 2018-05-09 cloverflow-tse/cloverflow.tex
Fixed a small typo.
Added boxplots and table of clone size
Updated the boxplots and stats.
Updated the data after changing Bellon's ok-match threshold to 0.5. Now there are 2,289 clone pairs. Other stats are now updated to reflect the change.

@@
 
-	We surveyed 607 high reputation Stack Overflow users to study their
+	We surveyed 201 high reputation Stack Overflow users to study their
 	awareness of the two issues.
@@
 reputation. On Stack Overflow, a user's reputation reflects how much the
-community trust them. A user earns reputations when he or she receives up votes
+community trusts them. A user earns reputations when he or she receives up votes
 for good questions and useful answers. Accepted answers receive more reputation
@@
 		\midrule
-		Reported clones & 2,302 & 460 & 59 & 53.10\% \\ 
-		\midrule
-		TP from manual validation & 2,076 & 443 & 59 & 53.89\% \\ 
+		Reported clones & 2,289 & 460 & 59 & 53.28\% \\ 
+		\midrule
+		TP from manual validation & 2,063 & 443 & 59 & 54.09\% \\ 
 		\bottomrule
@@
 		\midrule
-		Before consolidation & 248 & 1 & 199 & 107 & 1,505 & 16 & 226 & 2,302 \\
-		After consolidation & 154 & 1 & 111 & 65 & 217 & 9 & 53 & 560 \\
+		Before consolidation & 247 & 1 & 197 & 107 & 1,495 & 16 & 226 & 2,289 \\
+		After consolidation & 153 & 1 & 109 & 65 & 216 & 9 & 53 & 606 \\
 		\bottomrule
@@
 \end{table*}
+
+\begin{table}
+	\centering
+	\caption{Statistics of clone sizes}
+	\label{tab:clone_stats}
+	\begin{tabular}{lrrrr}
+		\toprule
+		Clones & Min & Max & Mean & Median \\
+		\midrule
+		QS & 10 & 135 & 18.6 & 14 \\
+		SQ & 21 & 21 & 21.0 & 21 \\
+		UD & 10 & 104 & 18.1 & 14 \\
+		EX & 10 & 48 & 16.7 & 14 \\
+		BP & 10 & 55 & 19.9 & 21 \\
+		IN & 11 & 22 & 13.8 & 13.0 \\
+		\bottomrule
+	\end{tabular} 
+\end{table}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{boxplot_clone_size}
+	\caption{Size of online code clones.}
+	\label{fig:boxplotclonesize}
+\end{figure}
 
@@
 22315734 saying that \textit{``Actually, you can learn how to compare in Hadoop
-from WritableComparator. Here is an examle that borrows some ideas from it.''}
+from WritableComparator. Here is an example that borrows some ideas from it.''}
 
@@
 		\midrule
-		hibernate & 24 & netbeans & 11 \\
+		hibernate & 23 & netbeans & 11 \\
 		eclipse & 21 & eclipse & 8 \\
@@
 		hadoop & 10 & jmeter & 4 \\
-		log4j & 8 & jung2 & 3 \\
-		tomcat & 8 & jhotdraw & 3 \\
-		struts & 5 & c-jdbc & 3 \\
-		lucene & 4 & log4j & 3 \\
-		weka & 4 & wct & 2 \\
-		junit & 3 & hibernate & 2 \\
-		poi & 3 & tomcat & 2 \\
-		compiere & 2 & spring & 1 \\
-		jasperreports & 2 & rssowl & 1 \\
+		tomcat & 8 & jung2 & 3 \\
+		log4j & 8 & jhotdraw & 3 \\
+		struts2 & 5 & c-jdbc & 3 \\
+		weka & 4 & log4j & 3 \\
+		lucene & 4 & wct & 2 \\
+		poi & 3 & hibernate & 2 \\
+		junit & 3 & tomcat & 2 \\
+		jstock & 2 & spring & 1 \\
+		jgraph & 2 & rssowl & 1 \\
 		jboss & 2 & mvnforum & 1 \\
-		jgraph & 2 & jfreechart & 1 \\
-		jstock & 2 & jboss & 1 \\
-		antlr & 1 & hadoop & 1 \\
+		jasperreports & 2 & jfreechart & 1 \\
+		compiere & 2 & jboss & 1 \\
+		jgrapht & 1 & hadoop & 1 \\
 		itext & 1 & geotools & 1 \\
-		jgrapht & 1 & freemind & 1 \\
+		c-jdbc & 1 & freemind & 1 \\
 		ant & 1 & findbugs & 1 \\
-		c-jdbc & 1 & cayenne & 1 \\
+		antlr4 & 1 & cayenne & 1 \\
 		\bottomrule
@@
 
-\textbf{EX: External Sources.} We found 199 clone pairs from external sources to
+\textbf{EX: External Sources.} We found 197 clone pairs from external sources to
 Stack Overflow. After consolidating duplicated SO snippets due to multiple
-intra-clone instances in Qualitas, we obtained 111 EX pairs. We found
+intra-clone instances in Qualitas, we obtained 109 EX pairs. We found
 evidence of copying from an external source to both Stack
-Overflow and Qualitas in 50 pairs. Each of the pairs contains
+Overflow and Qualitas in 49 pairs. Each of the pairs contains
 statement(s) pointing to the original external location of the cloned
@@
 of copying from an external source to Stack Overflow, but not in
-Qualitas, in 61 pairs. 
+Qualitas, in 60 pairs. 
 Our
@@
 from source code of Java SDK (e.g.\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
-18 pairs from websites, 15 pairs from open
+18 pairs from websites, 14 pairs from open
 source systems not in Qualitas (e.g.\ \textsf{Mozilla
-	Rhino}), 11 pairs from Java official documentations from Sun
+	Rhino}), 10 pairs from Java official documentations from Sun
 Microsystems or Oracle, 3 pairs from books, and 1 pair from a company

### 2018-05-09 cloverflow-tse/ex_sources.m

@@ -1,4 +1,4 @@
-y = [63 18 15 11 3 1];
+y = [63 18 14 10 3 1];
 bar(y)
 
 %xticks([1 2 3 4 5 6 7 8 9 10 11 12 13 14 15 16 17 18 19])

### 2018-05-09 cloverflow-tse/cover_letter/cover_letter.tex
Updated the outdated vs. GitHub results and updated the software license auditing survey results.

@@
 	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects.
-Hence, we have performed a study of code clone detection between our reported outdated code fragments on Stack Overflow and 131,307 most starred GitHub projects.
-We found that there are xxx clone instances of xxx outdated Stack Overflow code snippets appearing in xx GitHub projects.
+Hence, we have performed a study of code clone detection between our reported outdated code fragments on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star.
+We selected SourcererCC with 80\% similarity for this experiment and detected clones between the 101 outdated code snippets and the retrieved GitHub data set.
+We relied on SourcererCC because it could scale to a large-scale data set, while Simian could not.
+We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them.
+Out of the 102 cloned snippets, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly matched (they contained additional code modifications made by the projects' developers).
+Lastly, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
+
+	Among the exact-copy of 47 outdated cloned snippets, there were only two cloned snippets that gave attributions to Stack Overflow.
+However, the attributions pointed to different posts that the ones we found the outdated code, but containing the same code in the answers.
+The other 32 cloned snippets were very likely to be a file-level clone from its original projects based on their license header and the Javadoc comments.
+Lastly, the remaining 13 cloned snippets did not have any hints or evidence of copying.
 	Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks).
-Unfortunately, due to the lack of evidence, we could not explain how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects.
+Due to the lack of evidence, we could not conclude how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects.
 It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.
-
 	Nevertheless, we decided to report the developers of the two projects regarding the issue.
@@
 
-We adopted non-probability convenient sampling to invite participants for this survey.
-Participation in the survey requires experience of visiting Stack Overflow for solving programming tasks at least once.
-The participants were invited to take the survey via various channels: social media post (Facebook), Thailand's popular technology news and media community in Thailand called \texttt{blognone.com}, the University of Molise in Italy where the third author works, \texttt{comp.lang.java.programmer} group and the Software Engineering Facebook page.
-We received answers from 89 participants.
-Two participants never copy code from Stack Overflow so we analysed the answers of the remaining 87 participants.
-The key findings are as follows.
+tho
+Thailand's popular technology news and media community in Thailand called
+\texttt{blognone.com}, the University of Molise in Italy where the third author
+works, \texttt{comp.lang.java.programmer} group and the Software Engineering
+Facebook page. We received answers from 89 participants. Two participants never
+copy code from Stack Overflow so we analysed the answers of the remaining 87
+participants. The key findings are as follows.
 
-Stack Overflow is ranked higher than official documentation, online repositories, and books as the resource to look for programming solutions.
-Developers rely on Stack Overflow answers because they are easy to search for on the web.
-Moreover, 64\% of the participants reuse code snippets from Stack Overflow at least once a week.
-They copy code from Stack Overflow because they can be found easily from search engine, solve similar problems to their problems, provide helpful context, and offer voting and accepted answers.
-The results show that 57 out of 87 Stack Overflow visitors encountered a problem from reusing Stack Overflow code snippets.
-Ten participants experienced problems for more than 80\% of the copied snippets and sixteen participants faced problems for 40--60\% of the reused code.
-The problems ranked by frequency include mismatched solutions (40), outdated solutions (39), incorrect solutions (28), and buggy code (1).
-Fifty-six percent of the participants never report the problems back to Stack Overflow.
-In addition, 85\% of the participants are not aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to the Stack Overflow posts they copied the code snippets from.
-We found that 66\% of the visitors never check for software licensing conflicts between Stack Overflow code snippets and their projects.
-Interestingly, 9\% of the participants encountered legal issues.
-Unfortunately, due to the anonymity of the survey, we could not investigate further regarding the legal issues that the participants faced from using Stack Overflow code snippets.
+Stack Overflow is ranked higher than official documentation, online
+repositories, and books as the resource to look for programming solutions.
+Developers rely on Stack Overflow answers because they are easy to search for on
+the web. Moreover, 64\% of the participants reuse code snippets from Stack
+Overflow at least once a week. They copy code from Stack Overflow because they
+can be found easily from search engine, solve similar problems to their
+problems, provide helpful context, and offer voting and accepted answers. The
+results show that 57 out of 87 Stack Overflow visitors encountered a problem
+from reusing Stack Overflow code snippets. Ten participants experienced problems
+for more than 80\% of the copied snippets and sixteen participants faced
+problems for 40--60\% of the reused code. The problems ranked by frequency
+include mismatched solutions (40), outdated solutions (39), incorrect solutions
+(28), and buggy code (1). Fifty-six percent of the participants never report the
+problems back to Stack Overflow. In addition, 85\% of the participants are not
+aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to
+the Stack Overflow posts they copied the code snippets from. We found that 66\%
+of the visitors never check for software licensing conflicts between Stack
+Overflow code snippets and their projects. Interestingly, 9\% of the
+participants encountered legal issues. Unfortunately, due to the anonymity of
+the survey, we could not investigate further regarding the legal issues that the
+participants faced from using Stack Overflow code snippets.
+
+The visitors survey confirms the findings from the previous studies that Stack
+Overflow code snippets can be problematic~\citep{Zhang2018,Acar2016,An2017}. Sixty-six
+percent of the visitors experienced a problem from reusing Stack Overflow code
+snippets ranging from incorrect solutions, outdated solutions, mismatched
+solutions, to buggy code. Although they are aware of the problems, half of them
+(56\%) never reports back to the Stack Overflow discussions. On the other hand,
+the visitors rarely give attributions to Stack Overflow when they reuse code
+snippets from the website, similar to the findings reported
+by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
+license, and more than half of them never check for license compatibility when
+reusing Stack Overflow code snippets. We also found that 9\% of the participants
+encountered legal issues by copying code from Stack Overflow. To the best of our
+knowledge, a study of legal problems from reusing Stack Overflow code snippets
+has never been done before and will be our future work.
 
@@
 
-In addition, we also performed a small survey of software auditing platforms/services including:~\FIXME{Blackduck OpenHub, foo, and bar} and found that, while they check for code copied from open source projects and analyse their license compatibility, none of them offers the checking for cloned code from Stack Overflow.
-So, our proposed service will be useful as an add-on check for code copying from Stack Overflow and their license implications.
+In addition, we also performed a study of two open source software auditing platforms/services:~BlackDuck Software\footnote{https://www.blackducksoftware.com} and nexB\footnote{https://www.nexb.com}.
+For BlackDuck Software, we found from their report~\citep{CORSI2017} that while they check for code copied from open source projects including GitHub and Stack Overflow and analyse their license compatibility with their customer software, the BlackDuck auditing system will treat the code snippets on Stack Overflow as having ``unknown'' license because it does not know the original license of Stack Overflow code snippets.
+For nexB, their product does not mention checking of reused source code from Stack Overflow.
+So, our proposed service, which can offer more precise licensing information of Stack Overflow code snippets, will be useful as an add-on license check for code copying from Stack Overflow.
 
@@
 We mainly study the online code clones and established their existence.
-However, we coined the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning.
-We updated the Introduction to be clearer on this point~\FIXME{to do}.
+However, we used the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning.
+Moreover, the term code cloning is not well known outside the code cloning community, so we decided not to use the term in the title.
+
+We also updated the Introduction to state that the dominant topic is about online code clones~\FIXME{to do}.
 %Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.
@@
 
-We expanded the analysis of the survey results \FIXME{Where?
-and How?} and now moved them to RQ1 to better link with the motivation.
-We also added results of another survey, the Stack Overflow visitor survey, to understand the awareness of the developers who copied code snippets from Stack Overflow regarding outdated and license-incompatible code.
+We moved them to RQ1 to better link with the motivation.
+We also expanded the findings to include another survey, the Stack Overflow visitor survey, in order to understand the awareness of the developers on both sides: the answerers and the visitors (i.e.~information seekers).
+We asked the visitors their experience regarding outdated and license-incompatible code caused by copying and reusing code snippets from Stack Overflow.
 

### 2018-05-14 cloverflow-tse/cloverflow.tex
Start restructuring the paper.

@@
 \usepackage{amsfonts}
+\usepackage{framed}
 
@@
 }
+
+\newenvironment{boxquote}{\vspace{-1ex}\setlength{\FrameSep}{1\fboxsep}\begin{framed}\setlength{\parskip}{0.5\baselineskip}\setlength{\parindent}{0pt}}{\end{framed}}
 
@@
 between 72,365 Java code snippets on Stack Overflow and 111 open source projects
-in the curated Qualitas corpus. We analysed 2,302 non-trivial online clone
+in the curated Qualitas corpus. We analysed 2,289 non-trivial online clone
 candidates. Our investigation revealed strong evidence that 154 clones have been
@@
 %on Stack Overflow and 111 Java open source projects in the curated Qualitas
-%corpus. We discovered and analysed 2,302 non-trivial online clone candidates.
+%corpus. We discovered and analysed 2,289 non-trivial online clone candidates.
 %Our investigation of the online clone pairs revealed strong evidence that 154
@@
 \begin{enumerate}
-	\item \textbf{A manual study of online code clones:} We used
-	two clone detection tools to discover 2,302 similar code snippet pairs between
+
+	\item \textbf{Awareness of Stack Overflow answerers and visitors to toxic code
+	snippets:} We performed an online survey and collected answers from 201
+highly-ranked Stack Overflow users. We found that they cloned code snippets
+from open source projects to Stack Overflow answers. While Stack Overflow
+answerers are aware of their outdated code snippets, 19\% of the participants
+rarely or never fix the code. 99\% of the answerers never include a software
+license in their snippets and 69\% never check for licensing conflicts between
+the cloned code snippets and Stack Overflow's CC BY-SA 3.0. On the other hand, we also
+surveyed 87 Stack Overflow visitors (i.e.~information seekers) on their
+experiences to toxic code snippets on Stack Overflow. Sixty-six percent of the
+visitors experienced a problem from reusing Stack Overflow code snippets. The
+visitors are generally not aware of the CC BY-SA 3.0 license, and more than
+half of them never check for license compatibility when reusing Stack Overflow
+code snippets.
+
+	\item \textbf{A manual study of online code clones:} 
+	To confirm the results in the surveys, we used
+	two clone detection tools to discover 2,289 similar code snippet pairs between
 	72,365 Java code snippets obtained from Stack Overflow's accepted answers and
@@
 	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
-	the 2,302 online clones, at least 330 have been copied from open source
+	the 2,289 online clones, at least 330 have been copied from open source
 	projects or external online sources to Stack Overflow, potentially violating
-	software licenses. For 154 of them, we found evidence that they have been copied
-	from a specific open source project. 101 of them we found to be outdated. %
+	software licenses. For 153 of them, we found evidence that they have been copied
+	from a specific open source project. 100 of them we found to be outdated. %
 	% and questionable for being reused.
 
-	\item \textbf{Awareness of Stack Overflow answerers to toxic code snippets:} We
-	performed an online survey and collected answers from 201 highly-ranked Stack
-	Overflow users. We found that they cloned code snippets from open source
-	projects to Stack Overflow answers. While Stack Overflow answerers are aware of
-	their outdated code snippets, 19\% of the participants rarely
-	or never fix the code. 99\% of the answerers never include a software
-	license in their snippets and 69\% never check for licensing conflicts between the
-	cloned code snippets and Stack Overflow's CC BY-SA 3.0.
-
 	\item \textbf{An online code
-		clone oracle:} The 2,302 manually investigated and validated online clone pairs
+		clone oracle:} The 2,289 manually investigated and validated online clone pairs
 	are available for download\footnote{https://ucl-crest.github.io/cloverflow-web} and
@@
 \begin{itemize}
-	\item \textbf{RQ1 (Online code clones): }\textit{To what extent is source
+
+	\item \textbf{RQ1 (Stack Overflow answerers' and visitors' awareness to toxic code snippets): }
+
+	\textit{1)~How often are Stack Overflow
+		answerers aware of the outdated code and licensing conflicts when
+		they answer a question on Stack Overflow?}
+
+	\textit{2) How often are Stack Overflow
+		visitors experience the outdated code and licensing conflicts when
+		they copy an answer from Stack Overflow?}
+
+	We surveyed 201 high-reputation Stack Overflow answerers and 87 Stack Overflow visitors to study their
+	awareness of the two issues.
+
+	\item \textbf{RQ2 (Online code clones): }\textit{To what extent is source
 		code cloned between Stack Overflow and open source projects?} We
@@
 	problem.
-	\item \textbf{RQ2 (Patterns of online code clones): }\textit{How do online
+
+	\item \textbf{RQ3 (Patterns of online code clones): }\textit{How do online
 		code clones occur?} We categorised online clones into seven
 	categories allowing insights to how online code clones are created.
-	\item \textbf{RQ3 (Outdated online code clones): }\textit{Are
+
+	\item \textbf{RQ4 (Outdated online code clones): }\textit{Are
 		online code clones up-to-date compared to their counterparts in the
@@
 	them.
-	\item \textbf{RQ4 (Software licensing violation): }\textit{How often do
+
+	\item \textbf{RQ5 (Software licensing violation): }\textit{How often do
 		license conflicts occur between Stack Overflow clones and their
@@
 	can cause software developers to violate licenses.
-	\item \textbf{RQ5 (Stack Overflow answerers' awareness): }
-
-	\textit{1)~How often are Stack Overflow
-		answerers aware of the outdated code when
-		they answer a question on Stack Overflow?}
-
-	\textit{2) How often are Stack Overflow
-			answerers aware of licensing conflicts when
-			they answer a question on Stack Overflow?}
-
-	We surveyed 201 high reputation Stack Overflow users to study their
-	awareness of the two issues.
 \end{itemize}
@@
 %\vspace{1ex}
-To answer these five research questions, we perform an empirical study to
-locate and study the online code clones between Stack Overflow and open source
-projects. 
-%
-%\subsection{Methodology}
-%
-We designed our study in 6 phases as depicted in \Cref{fig:exp_framework} where
-we build different data sets to answer each of our five research
-questions.
-
-\subsection{Phase 1: Clone Identification}
+To answer these five research questions, we perform two surveys and an empirical study to
+understand the developers' awareness of toxic code snippets on Stack Overflow and to
+empirically study the online code clones between Stack Overflow and open source
+projects and their toxicity.
+
+\subsection{Stack Overflow Developers' Survey} We support our motivation of
+toxic code snippets on Stack Overflow and answer RQ1 by asking Stack
+Overflow users to take an online survey. The survey was used for assessing awareness of
+the developers on the two issues of outdated code and license-violating code
+snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
+Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
+anonymous and the participants could decide to leave at any time. 
+We created two versions of the survey: \textbf{the answerer survey} and \textbf{the visitor survey}.
+The answerer survey targeted the developers who were experienced Stack Overflow users
+and were highly active in answering questions. On the other hand, the visitor survey
+targeted the developers who searched for solutions and reused code from Stack Overflow answers.
+
+\textbf{The answerer survey:} the survey contained
+11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
+open-ended question for additional comments. The first two questions were
+mandatory while the other 9 questions were shown to the participants based on
+their previous answers. The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
+We selected the participants for the answerer survey based on their Stack Overflow
+reputation. On Stack Overflow, a user's reputation reflects how much the
+community trusts them. A user earns reputations when he or she receives up votes
+for good questions and useful answers. Accepted answers receive more reputation
+score than questions, and regular answers\footnote{Stack Overflow
+	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
+Overflow reputation is an indicator of user's skills and their involvement in
+asking and answering questions on the site. In this study, we call Stack
+Overflow users who have high reputation ``Stack Overflow answerers.''
+The participants were invited to take the survey via email addresses available
+on their public Stack Overflow and GitHub profiles. We selected the answerers
+based on the all-time reputation ranking\footnote{Stack Overflow Users (data as
+	of 25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}. The
+invited participants had a reputation from 963,731 (the highest) to 6,999 and
+we sent out 607 emails (excluding undelivered ones, e.g.\ due to
+illegal email addresses). 
+The survey was
+open for participation for two months, from 25 July to 25 September 2017, before
+we collected and analysed the responses.
+
+\textbf{The visitors' survey}
+The survey consists of 16 questions: 9 Likert's
+scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
+open-ended questions. 
+The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
+The first four questions are mandatory while the other 12
+questions will be shown to the participants based on their previous answers. 
+The survey collects information about the participant's software development
+experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
+snippets, problems from Stack Overflow snippets, licensing of code on Stack
+Overflow, and additional feedback. 
+We adopted non-probability convenient sampling to invite participants for this
+survey. Participation in the survey requires experience of visiting Stack
+Overflow for solving programming tasks at least once. The participants were
+invited to take the survey via five channels: social media post (Facebook),
+\textsf{blognone.com}, a popular technology news and media community in Thailand, the University of Molise in Italy where the third author
+works, \texttt{comp.lang.java.programmer} group and the Software Engineering
+Facebook page. We received answers from 89 participants. Two participants never
+copy code from Stack Overflow so we analysed the answers of the remaining 87
+participants.
+The survey was open for participation for 2 months, 
+from 25 July 2017 to 25 September 2017, before we collected and analysed
+the responses.
+
+\subsection{Empirical Study of Online Code Clones}
+We support the motivation and the findings in the surveys by performing
+an empirical study of online code clones between Stack Overflow
+answers and 111 Java open source projects.
+We designed the study in 6 phases as depicted in \Cref{fig:exp_framework} where
+we build different data sets to answer RQ2 -- RQ5.
+
+\subsubsection{Phase 1: Clone Identification}
 
@@
 
-\subsection{Phase 2: Clone Merging} Clones from the two detectors can be
+\subsubsection{Phase 2: Clone Merging} Clones from the two detectors can be
 duplicated. To avoid double-counting of the same clone pair, we adopted the idea
@@
 similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
-Simian and 1,678 clone pairs from SourcererCC into a single set of 2,302 online
+Simian and 1,678 clone pairs from SourcererCC into a single set of 2,289 online
 clone pairs. There are only 97 common clone pairs between the two clone sets 
@@
 
-\subsection{Phase 3-4: Validation and Classification}
-We used the 2,302 merged clone pairs for
+\subsubsection{Phase 3-4: Validation and Classification}
+We used the 2,289 merged clone pairs for
 manual validation and classification.
@@
 
-\subsection{Phase 5: Outdated Clones} Outdated code occurs when a piece of code
+\subsubsection{Phase 5: Outdated Clones} Outdated code occurs when a piece of code
 has been copied from its origin to another location and later the original has
@@
 
-\subsection{Phase 6: Licensing Analysis} Software licensing plays an important
+\subsubsection{Phase 6: Licensing Analysis} Software licensing plays an important
 role in software development. Violation of software licenses impacts software
@@
 
-\subsection{Stack Overflow Developers' Survey} We support our findings of
-toxic code snippets on Stack Overflow by asking Stack
-Overflow users to take an online survey. The survey was used for assessing awareness of
-the developers on the two issues of outdated code and license-violating code
-snippets. We designed the survey using Google Forms by following the guidelines by Pfleeger and
-Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
-anonymous and the participants could decide to leave at any time. It contained
-11 questions. There were 7 Likert's scale questions, 3 yes/no questions, and one
-open-ended question for additional comments. The first two questions were
-mandatory while the other 9 questions were shown to the participants based on
-their previous answers. The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
-
-We selected the participants for our survey based on their Stack Overflow
-reputation. On Stack Overflow, a user's reputation reflects how much the
-community trusts them. A user earns reputations when he or she receives up votes
-for good questions and useful answers. Accepted answers receive more reputation
-score than questions, and regular answers\footnote{Stack Overflow
-Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
-Overflow reputation is an indicator of user's skills and their involvement in
-asking and answering questions on the site. In this study, we call Stack
-Overflow users who have high reputation ``Stack Overflow answerers.''
-
-The participants were invited to take the survey via email addresses available
-on their public Stack Overflow and GitHub profiles. We selected the answerers
-based on the all-time reputation ranking\footnote{Stack Overflow Users (data as
-of 25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}. The
-invited participants had a reputation from 963,731 (the highest) to 6,999 and
-we sent out 607 emails (excluding undelivered ones, e.g.\ due to
-illegal email addresses). The survey was
-open for participation for two months, from 25 July to 25 September 2017, before
-we collected and analysed the responses.
-
 \section{Results and Discussion}
 
-We followed the 6 phases in the experimental framework
-(\Cref{fig:exp_framework}) to answer our four research questions. To answer RQ1,
+We use the two online surveys of Stack Overflow answerers and visitors to answer RQ1
+and follow the 6 phases in the experimental framework
+(\Cref{fig:exp_framework}) to answer the other four research questions. To answer RQ2,
 we rely on the number of manually validated true positive online clone pairs in
 phase 3. We use the results of the manual classification by the seven patterns
-of online code cloning to answer RQ2 (phase 4). For RQ3, we looked at the true
+of online code cloning to answer RQ3 (phase 4). For RQ4, we looked at the true
 positive clone pairs that are classified as clones from Qualitas to Stack
 Overflow and checked if they have been changed after cloning (phase 5).
-Similarly, for RQ4, we looked at the license of each clone in the pattern QS,
-EX, UD and checked for a possibility of license violation (phase 6). We use
-the online survey to answer RQ5.
-
-\subsection{RQ1: Online Code Clones} 
+Similarly, for RQ5, we looked at the license of each clone in the pattern QS,
+EX, UD and checked for a possibility of license violation (phase 6).
+
+\subsection{RQ1: Stack Overflow Answerers' and Visitors' Awareness}
+
+%\begin{table}
+%	\centering
+%	\caption{Stack Overflow answerers taken the survey}
+%	\label{tab:survey_target}
+%	\begin{tabular}{rrrr}
+%		\toprule
+%		Reputation & Sent emails & Answers & Rate \\
+%		\midrule
+%		963,731--6,999 & 607 & 201 & 33\% \\
+%		\bottomrule
+%	\end{tabular}
+%\end{table}
+
+\subsubsection{The Answerer Survey}
+
+We received 201 answers (33\% response rate) from 607 emails we sent to the
+Stack Overflow answerers. The response rate was high considering other
+online surveys in software engineering~\cite{Punter2003}. 
+We only present a summary of the survey answers in
+this paper and the full analysis is available as a research note~\cite{Ragkhitwetsagul_RN2017}.
+
+\textbf{General Information:} As shown in \Cref{tab:survey_exp}, the majority of the answerers are experienced
+developers with more than 10 years of experience (55.2\%) or between 5 to 10
+years (28.9\%). They are active users and regularly answer questions. 49
+participants (24\%) answer questions on Stack Overflow every day.
+
+\begin{table}
+	\centering
+	\caption{Experience of Stack Overflow answerers}
+	\label{tab:survey_exp}
+	\begin{tabular}{lrr}
+		\toprule
+		Experience & Amount & Percent \\
+		\midrule
+		Less than a year & 1 & 0.5\% \\
+		1 -- 2 years & 1 & 0.5\% \\
+		3 -- 5 years & 30 & 14.9\% \\
+		5 -- 10 years & 58 & 28.9\% \\
+		More than 10 years	& 111 & 55.2\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Frequency of including code snippets in answers}
+	\label{tab:survey_code_snippet_frequency}
+	\begin{tabular}{lrr}
+		\toprule
+		Include code snippets & Amount & Percent \\
+		\midrule
+		Very Frequently (81--100\% of the time)	& 84 & 42\% \\
+		Frequently (61--80\% of the time) &	63 & 31\% \\
+		Occasionally (41--60\% of the time) & 40 & 20\% \\
+		Rarely (21--40\% of the time) & 11 & 6\% \\
+		Very Rarely (1--20\% of the time) & 2 & 1\% \\
+		Never (0\% of the time) & 1 & 1\% \\
+		\midrule
+		Total & 201 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\textbf{Code Snippets in Answers:}
+84 and 63 answerers include code snippets in more than 80\% and 60\% of
+their answers respectively. Interestingly, there is one answerer who never
+include code snippet in his/her answers (\Cref{tab:survey_code_snippet_frequency}).
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{survey_snippet_source}
+	\caption{The sources of code snippets in Stack Overflow answers}
+	\label{fig:survey_snippet_source}
+\end{figure}
+
+We asked the remaining 200 participants for the origins of code snippets in
+their answers. We provided six locations including the answerer's personal
+projects, the answerer's company projects, open source projects, writing the
+code from scratch, copying and modifying the code from the question, and others
+(e.g.\ code that are copied from other questions or answers on Stack Overflow)
+and we asked them to rate how often they copied the code from these locations. The
+results are shown in \Cref{fig:survey_snippet_source}. Looking at the Very
+Frequently section, we can see that the answerers mainly write new code from
+scratch (106) or copy and modify the code snippets from the question for each answer (66),
+while fewer numbers are from other sources including their personal projects
+(28), their company projects (4), and open source projects (9). Although
+copying from open source projects is not the most popular choice, the answerers
+still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
+participants who frequently, occasionally, and rarely copied code snippets from
+open source projects.
+
+\vspace{0.25cm}
+\textit{RQ 1.1 How often are Stack Overflow
+	answerers aware of the outdated code and 
+	licensing conflicts when
+	they answer a question on Stack Overflow?} 
+\vspace{0.25cm}
+
+\textbf{Outdated Code Snippets:} We asked the answerers if they have ever been notified about outdated code in
+their answers. 111 participants selected \textit{Yes} while the other 89 participants
+selected \textit{No}. However, we found inconsistent results when we asked a follow up
+question on the frequency of being notified. As displayed in
+\Cref{tab:survey_code_snippet_outdated}, the number of participants who has
+\textit{Never} been notified about outdated code snippets in their answers drops
+from 89 to 69.
+
+\begin{table}
+	\centering
+	\caption{Notifications of outdated code snippets in answers}
+	\label{tab:survey_code_snippet_outdated}
+	\begin{tabular}{lrr}
+		\toprule
+		Notified of outdated code & Amount & Percent \\
+		\midrule
+		Very frequently (81--100\% of my answers) & 2 & 1\% \\
+		Frequently (61--80\% of my answers) & 1 & 0.5\% \\
+		Occasionally (41--60\% of my answers) & 9 & 4.5\% \\
+		Rarely (21--40\% of my answers) & 16 & 8\% \\
+		Very rarely (1--20\% of my answers) & 103 & 51.5\% \\
+		Never (0\% of my answers) & 69 & 34.5\% \\
+		\midrule
+		Total & 200 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We found that although the answerer have been notified of
+outdated code in their answers, for 51.5\% of them such notifications occur very rarely (only 1--20\% of the answers). 
+Only 3 participants reported that they were notified in more than 60\% of their answers.
+
+\begin{table}
+	\centering
+	\caption{Fixing of outdated code snippets in answers}
+	\label{tab:survey_code_snippet_outdated_fix}
+	\begin{tabular}{lrr}
+		\toprule
+		Fixing of outdated code & Amount & Percent \\
+		\midrule
+		Very frequently (81--100\% of the cases) & 48 & 36.6\% \\
+		Frequently (61--80\% of the cases) & 27 & 20.6\% \\
+		Occasionally (41--60\% of the cases) & 30 & 22.9\% \\
+		Rarely (21--40\% of the cases) & 11 & 8.4\% \\
+		Very rarely (1--20\% of the cases) & 8 & 6.1\% \\
+		Never (0\% of the cases) & 7 & 5.3\% \\
+		\midrule
+		Total & 131 & 100.0\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We then asked 131 participants who have been notified of their outdated code a
+follow-up question \textit{``how frequently did you fix your outdated code on Stack
+	Overflow?''}. The answers, depicted in
+\Cref{tab:survey_code_snippet_outdated_fix}, show that more than half of them
+(57.2\%) very frequently or frequently fix the outdated code snippets. However,
+there are 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
+their outdated code.
+
+The responses from the answerers support our findings of outdated online code
+clones in RQ3. The low percentage of outdated code notifications
+reflect the experience of high reputation answerers who accumulate the reputation for a
+long time. Due to the voting mechanism of Stack Overflow, high reputation users
+usually provide high quality answers to earn up votes from other users. They are
+careful when posting code snippets in the answer to avoid problems and, vice versa, 
+getting down votes. It would be interesting to compare the findings to
+Stack Overflow answerers who are newer and have lower reputation. However, we
+leave it to future work.
+
+%\vspace{0.25cm}
+%\textit{How often are Stack Overflow
+%	answerers aware of licensing conflicts when
+%	they answer a question on Stack Overflow?} 
+%\vspace{0.25cm}
+
+\begin{table}
+	\centering
+	\caption{Inclusion of software license in answer}
+	\label{tab:survey_license_include}
+	\begin{tabular}{lr}
+		\toprule
+		Include license? & Amount \\
+		\midrule
+		No. & 197 \\
+		Yes, in code comment &	1 \\
+		Yes, in text surrounding the code & 2 \\
+		\midrule
+		Total & 200 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\textbf{License of Code Snippets:} Among the 200 answerers who include code snippets in their answers, 124
+answerers are aware that Stack Overflow apply Creative Commons
+Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts,
+including code snippets, while the rest (76) are not. Nevertheless, as shown in
+\Cref{tab:survey_license_include}, almost all of them (197) reported that they
+did not include license statement in their code snippets due to several reasons.
+First, some answerers chose to post only their own code or code that was adapted
+from the question, hence they are automatically subjected to CC BY-SA 3.0.
+Second, they copied code from company or open source projects that they knew
+were permitted to be publicly distributed. Third, some answerers believe that
+code snippets in their answers are too small to claim any intellectual property
+on them and fall under fair use~\cite{fairuse}.
+
+While nobody explicitly includes a software license in their snippets,
+many users include a statement on their profile page that all their
+answers are under a certain license. For example, a Stack Overflow user includes 
+the following text in his/her profile page.
+
+\begin{quotation}
+	\noindent \textit{All code posted by me on
+		Stack Overflow should be considered public domain without copyright. For
+		countries where public domain is not applicable, I hereby grant everyone the
+		right to modify, use and redistribute any code posted by me on Stack Overflow
+		for any purpose. It is provided ``as-is'' without warranty of any kind.}
+\end{quotation}
+
+Many users either declare their snippets to be public domain, or they grant
+additional licenses, e.g.\ Apache 2.0 or MIT/Expat.
+
+\begin{table}
+	\centering
+	\caption{Checking for licensing conflicts with CC BY-SA 3.0}
+	\label{tab:survey_license_check}
+	\begin{tabular}{lrr}
+		\toprule
+		Check license conflicts? & Amount & Percent \\
+		\midrule
+		Very Frequently (81--100\% of the time)	& 14 & 7\% \\
+		Frequently (61--80\% of the time) & 7 & 3.5\% \\
+		Occasionally (41--60\% of the time) & 10 & 5\% \\
+		Rarely (21--40\% of the time) & 16 & 8\% \\
+		Very rarely (1--20\% of the time) & 15 & 7.5\% \\
+		Never (0\% of the time) & 138 & 69\% \\
+		\midrule
+		Total & 200 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+We asked the answerers a follow-up question of how frequently they checked for a
+conflict between software license of the code snippets they copied to their
+answers and Stack Overflow's CC BY-SA 3.0. As shown in
+\Cref{tab:survey_license_check}, approximately 69\% of answerers did not perform
+the checking. Nonetheless, there are about 10.5\% of the answerers who very
+frequently or frequently check for licensing conflicts when they copy code
+snippets to Stack Overflow.
+
+Similar to outdated code, the responses from the answerers support our findings
+of licensing conflicts in online code clones in RQ4 and possibly explain why most of
+the clones copied from open source projects and external sources do not include
+their original software license.
+
+\begin{boxquote}
+	To answer RQ 5.1, regarding outdated code, although most of the Stack Overflow answerers are aware that their code
+	can be outdated, 51.5\% of the answerers were very rarely notified and 35.5\% have never been notified of
+	outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.
+
+	For licensing conflicts, 124 answerers out of 200 (62\%) are aware of Stack Overflow's
+	CC BY-SA 3.0 license applied to code snippets in questions and answers. However,
+	only 3 answerers explicitly include software license in their answers. Some 
+	answerers choose to include the license in their profile page instead. 69\% of the
+	answerers never check for licensing conflicts between their copied code snippets
+	and Stack Overflow's CC BY-SA 3.0.
+\end{boxquote}
+
+\textbf{Open Comments:} We also invited the participants to give a
+free-form comment regarding their concerns of answering Stack Overflow with code
+snippets. Besides the one we present earlier in the introduction, these are
+interesting comments we received.
+
+\begin{enumerate}
+	\item \textit{``When I copy code it's usually short enough to be considered "fair
+		use" but I am not a lawyer or copyright expert so some guidance from Stack Overflow would be
+		helpful. I'd also like the ability to flag/review questions that violate these
+		guidelines.''}
+	\item \textit{``My only concern, albeit minor, is that I know people blindly copy
+		my code without even understanding what the code does.''}
+	\item \textit{``The main problem for me/us is outdated code, esp. as old answers
+		have high google rank so that is what people see first, then try and fail. Thats
+		why we're moving more and more of those examples to knowledge base and docs and
+		rather link to those.''}
+	\item \textit{``Lot of the answers are from hobbyist so the quality is poor.
+		Usually they are hacks or workarounds (even MY best answer on Stack Overflow is a
+		workaround).''}
+\end{enumerate}
+
+The comments highlight that Stack Overflow users are unsure about the
+legal implications of copying code, that code is copied without
+understanding it, and that the quality of code on Stack Overflow is
+often low.
+
+\subsection{RQ2: Online Code Clones} 
 \vspace{0.25cm}
@@
 
-During the manual investigation of 2,302 clone pairs, we identified 226 pairs
+During the manual investigation of 2,289 clone pairs, we identified 226 pairs
 as being accidental clones (AC), i.e.~false positives. After removing
@@
 
-\textbf{To answer RQ1, we found more than half (53\%) of Qualitas projects to share
+\begin{boxquote}
+	To answer RQ2, we found more than half (53\%) of Qualitas projects to share
 	similar code with Stack Overflow code snippets. In the manually confirmed 
-	data set of 2,302 clone pairs, we found 2,076 pairs as true positives which 
+	data set of 2,289 clone pairs, we found 2,076 pairs as true positives which 
 	account for 59 Qualitas projects and
-	443 Stack Overflow code snippets.}
-
-\subsection{RQ2: Patterns of Online Code Cloning}
+	443 Stack Overflow code snippets.
+\end{boxquote}
+
+\subsection{RQ3: Patterns of Online Code Cloning}
 \vspace{0.25cm}
@@
 We performed a manual classification
-of the 2,302 merged clone pairs by following the classification process
+of the 2,289 merged clone pairs by following the classification process
 in \Cref{fig:classification_process}. 
@@
 
-\textbf{To answer RQ2, we found 154 pairs with
+\begin{boxquote}
+To answer RQ3, we found 154 pairs with
 strong evidences to be cloned from 23 Qualitas projects to Stack Overflow, 1 pair
@@
 (217), followed by 65 clone pairs with no evidence that the code has actually been copied,
-	and 16 pairs of clones due to implementing the same interface or inheriting the same class.}
-
-\subsection{RQ3: Outdated Online Code Clones}
+and 16 pairs of clones due to implementing the same interface or inheriting the same class.
+\end{boxquote}
+
+\subsection{RQ4: Outdated Online Code Clones}
 \vspace{0.25cm}
@@
 
-We discovered 101 outdated online clone pairs out of 154 pairs. As shown in
+We discovered 100 outdated online clone pairs out of 153 pairs. As shown in
 \Cref{fig:outdated}, \textsf{hibernate} has the highest number of 19 outdated
@@
 			Method rewriting & 15 \\
-			File deletion & 15 \\
+			File deletion & 14 \\
 			\bottomrule 
@@
 
-\textbf{For RQ3, our results show that 66\% (101) of QS clone pairs on Stack
+\begin{boxquote}
+For RQ4, our results show that 66\% (101) of QS clone pairs on Stack
 Overflow are outdated. 86 pairs differ from their newest versions by
@@
 statements, to a fully rewritten code with new method signatures. 15~pairs are
-	dead snippets.}
-
-\subsection{RQ4: Software Licensing Violations}
+dead snippets.
+\end{boxquote}
+
+\subsection{RQ5: Software Licensing Violations}
 \vspace{0.25cm}
@@
 
-\textbf{For RQ4, we found 214 code snippets on Stack Overflow that
+\begin{boxquote}
+For RQ5, we found 214 code snippets on Stack Overflow that
 could potentially violate the license of their original software. The majority of them
@@
 Stack Overflow. For 164 of them, we were able to identify,
-        with evidence, where the code snippet has been copied from.}
+with evidence, where the code snippet has been copied from.
+\end{boxquote}
 
@@
 snippets.
-
-\subsection{RQ5: Stack Overflow Answerers' Awareness}
-
-%\begin{table}
-%	\centering
-%	\caption{Stack Overflow answerers taken the survey}
-%	\label{tab:survey_target}
-%	\begin{tabular}{rrrr}
-%		\toprule
-%		Reputation & Sent emails & Answers & Rate \\
-%		\midrule
-%		963,731--6,999 & 607 & 201 & 33\% \\
-%		\bottomrule
-%	\end{tabular}
-%\end{table}
-
-We received 201 answers (33\% response rate) from 607 emails we sent to the
-Stack Overflow answerers. The response rate was high considering other
-online surveys in software engineering~\cite{Punter2003}. 
-We only present a summary of the survey answers in
-this paper and the full analysis is available as a research note~\cite{Ragkhitwetsagul_RN2017}.
-
-\subsubsection{General Information}
-As shown in \Cref{tab:survey_exp}, the majority of the answerers are experienced
-developers with more than 10 years of experience (55.2\%) or between 5 to 10
-years (28.9\%). They are active users and regularly answer questions. 49
-participants (24\%) answer questions on Stack Overflow every day.
-
-\begin{table}
-	\centering
-	\caption{Experience of Stack Overflow answerers}
-	\label{tab:survey_exp}
-	\begin{tabular}{lrr}
-		\toprule
-		Experience & Amount & Percent \\
-		\midrule
-		Less than a year & 1 & 0.5\% \\
-		1 -- 2 years & 1 & 0.5\% \\
-		3 -- 5 years & 30 & 14.9\% \\
-		5 -- 10 years & 58 & 28.9\% \\
-		More than 10 years	& 111 & 55.2\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\subsubsection{Code Snippets in Answers}
-
-\begin{table}
-	\centering
-	\caption{Frequency of including code snippets in answers}
-	\label{tab:survey_code_snippet_frequency}
-	\begin{tabular}{lrr}
-		\toprule
-		Include code snippets & Amount & Percent \\
-		\midrule
-		Very Frequently (81--100\% of the time)	& 84 & 42\% \\
-		Frequently (61--80\% of the time) &	63 & 31\% \\
-		Occasionally (41--60\% of the time) & 40 & 20\% \\
-		Rarely (21--40\% of the time) & 11 & 6\% \\
-		Very Rarely (1--20\% of the time) & 2 & 1\% \\
-		Never (0\% of the time) & 1 & 1\% \\
-		\midrule
-		Total & 201 & 100\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-84 and 63 answerers include code snippets in more than 80\% and 60\% of
-their answers respectively. Interestingly, there is one answerer who never
-include code snippet in his/her answers (\Cref{tab:survey_code_snippet_frequency}).
-
-\begin{figure}
-	\centering
-	\includegraphics[width=0.9\linewidth]{survey_snippet_source}
-	\caption{The sources of code snippets in Stack Overflow answers}
-	\label{fig:survey_snippet_source}
-\end{figure}
-
-We asked the remaining 200 participants for the origins of code snippets in
-their answers. We provided six locations including the answerer's personal
-projects, the answerer's company projects, open source projects, writing the
-code from scratch, copying and modifying the code from the question, and others
-(e.g.\ code that are copied from other questions or answers on Stack Overflow)
-and we asked them to rate how often they copied the code from these locations. The
-results are shown in \Cref{fig:survey_snippet_source}. Looking at the Very
-Frequently section, we can see that the answerers mainly write new code from
-scratch (106) or copy and modify the code snippets from the question for each answer (66),
-while fewer numbers are from other sources including their personal projects
-(28), their company projects (4), and open source projects (9). Although
-copying from open source projects is not the most popular choice, the answerers
-still rely on them sometimes. As shown in the figure, there are 14, 31, and 33
-participants who frequently, occasionally, and rarely copied code snippets from
-open source projects.
-
-\subsubsection{Outdated Code Snippets} 
-\vspace{0.25cm}
-\textit{How often are Stack Overflow
-	answerers aware of the outdated code when
-	they answer a question on Stack Overflow?} 
-\vspace{0.25cm}
-
-We asked the answerers if they have ever been notified about outdated code in
-their answers. 111 participants selected \textit{Yes} while the other 89 participants
-selected \textit{No}. However, we found inconsistent results when we asked a follow up
-question on the frequency of being notified. As displayed in
-\Cref{tab:survey_code_snippet_outdated}, the number of participants who has
-\textit{Never} been notified about outdated code snippets in their answers drops
-from 89 to 69.
-
-\begin{table}
-	\centering
-	\caption{Notifications of outdated code snippets in answers}
-	\label{tab:survey_code_snippet_outdated}
-	\begin{tabular}{lrr}
-		\toprule
-		Notified of outdated code & Amount & Percent \\
-		\midrule
-		Very frequently (81--100\% of my answers) & 2 & 1\% \\
-		Frequently (61--80\% of my answers) & 1 & 0.5\% \\
-		Occasionally (41--60\% of my answers) & 9 & 4.5\% \\
-		Rarely (21--40\% of my answers) & 16 & 8\% \\
-		Very rarely (1--20\% of my answers) & 103 & 51.5\% \\
-		Never (0\% of my answers) & 69 & 34.5\% \\
-		\midrule
-		Total & 200 & 100\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-We found that although the answerer have been notified of
-outdated code in their answers, for 51.5\% of them such notifications occur very rarely (only 1--20\% of the answers). 
-Only 3 participants reported that they were notified in more than 60\% of their answers.
-
-\begin{table}
-	\centering
-	\caption{Fixing of outdated code snippets in answers}
-	\label{tab:survey_code_snippet_outdated_fix}
-	\begin{tabular}{lrr}
-		\toprule
-		Fixing of outdated code & Amount & Percent \\
-		\midrule
-		Very frequently (81--100\% of the cases) & 48 & 36.6\% \\
-		Frequently (61--80\% of the cases) & 27 & 20.6\% \\
-		Occasionally (41--60\% of the cases) & 30 & 22.9\% \\
-		Rarely (21--40\% of the cases) & 11 & 8.4\% \\
-		Very rarely (1--20\% of the cases) & 8 & 6.1\% \\
-		Never (0\% of the cases) & 7 & 5.3\% \\
-		\midrule
-		Total & 131 & 100.0\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-We then asked 131 participants who have been notified of their outdated code a
-follow-up question \textit{``how frequently did you fix your outdated code on Stack
-Overflow?''}. The answers, depicted in
-\Cref{tab:survey_code_snippet_outdated_fix}, show that more than half of them
-(57.2\%) very frequently or frequently fix the outdated code snippets. However,
-there are 19.8\% of the answerers in both groups who rarely, very rarely, or never fix 
-their outdated code.
-
-\textbf{To answer RQ 5.1, although most of the Stack Overflow answerers are aware that their code
-can be outdated, 51.5\% of the answerers were very rarely notified and 35.5\% have never been notified of
-outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.}
-
-The responses from the answerers support our findings of outdated online code
-clones in RQ3. The low percentage of outdated code notifications
-reflect the experience of high reputation answerers who accumulate the reputation for a
-long time. Due to the voting mechanism of Stack Overflow, high reputation users
-usually provide high quality answers to earn up votes from other users. They are
-careful when posting code snippets in the answer to avoid problems and, vice versa, 
-getting down votes. It would be interesting to compare the findings to
-Stack Overflow answerers who are newer and have lower reputation. However, we
-leave it to future work.
-
-\subsubsection{License of Code Snippets} 
-\vspace{0.25cm}
-\textit{How often are Stack Overflow
-	answerers aware of licensing conflicts when
-	they answer a question on Stack Overflow?} 
-\vspace{0.25cm}
-
-\begin{table}
-	\centering
-	\caption{Inclusion of software license in answer}
-	\label{tab:survey_license_include}
-	\begin{tabular}{lr}
-		\toprule
-		Include license? & Amount \\
-		\midrule
-		No. & 197 \\
-		Yes, in code comment &	1 \\
-		Yes, in text surrounding the code & 2 \\
-		\midrule
-		Total & 200 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-Among the 200 answerers who include code snippets in their answers, 124
-answerers are aware that Stack Overflow apply Creative Commons
-Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts,
-including code snippets, while the rest (76) are not. Nevertheless, as shown in
-\Cref{tab:survey_license_include}, almost all of them (197) reported that they
-did not include license statement in their code snippets due to several reasons.
-First, some answerers chose to post only their own code or code that was adapted
-from the question, hence they are automatically subjected to CC BY-SA 3.0.
-Second, they copied code from company or open source projects that they knew
-were permitted to be publicly distributed. Third, some answerers believe that
-code snippets in their answers are too small to claim any intellectual property
-on them and fall under fair use~\cite{fairuse}.
-
-While nobody explicitly includes a software license in their snippets,
-many users include a statement on their profile page that all their
-answers are under a certain license. For example, a Stack Overflow user includes 
-the following text in his/her profile page.
-
-\begin{quotation}
-\noindent \textit{All code posted by me on
-	Stack Overflow should be considered public domain without copyright. For
-	countries where public domain is not applicable, I hereby grant everyone the
-	right to modify, use and redistribute any code posted by me on Stack Overflow
-	for any purpose. It is provided ``as-is'' without warranty of any kind.}
-\end{quotation}
-
-Many users either declare their snippets to be public domain, or they grant
-additional licenses, e.g.\ Apache 2.0 or MIT/Expat.
-
-\begin{table}
-	\centering
-	\caption{Checking for licensing conflicts with CC BY-SA 3.0}
-	\label{tab:survey_license_check}
-	\begin{tabular}{lrr}
-		\toprule
-		Check license conflicts? & Amount & Percent \\
-		\midrule
-		Very Frequently (81--100\% of the time)	& 14 & 7\% \\
-		Frequently (61--80\% of the time) & 7 & 3.5\% \\
-		Occasionally (41--60\% of the time) & 10 & 5\% \\
-		Rarely (21--40\% of the time) & 16 & 8\% \\
-		Very rarely (1--20\% of the time) & 15 & 7.5\% \\
-		Never (0\% of the time) & 138 & 69\% \\
-		\midrule
-		Total & 200 & 100\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-We asked the answerers a follow-up question of how frequently they checked for a
-conflict between software license of the code snippets they copied to their
-answers and Stack Overflow's CC BY-SA 3.0. As shown in
-\Cref{tab:survey_license_check}, approximately 69\% of answerers did not perform
-the checking. Nonetheless, there are about 10.5\% of the answerers who very
-frequently or frequently check for licensing conflicts when they copy code
-snippets to Stack Overflow.
-
-\textbf{To answer RQ 5.2, 124 answerers out of 200 (62\%) are aware of Stack Overflow's
-CC BY-SA 3.0 license applied to code snippets in questions and answers. However,
-only 3 answerers explicitly include software license in their answers. Some 
-answerers choose to include the license in their profile page instead. 69\% of the
-answerers never check for licensing conflicts between their copied code snippets
-and Stack Overflow's CC BY-SA 3.0.}
-
-Similar to outdated code, the responses from the answerers support our findings
-of licensing conflicts in online code clones in RQ4 and possibly explain why most of
-the clones copied from open source projects and external sources do not include
-their original software license.
-
-\subsubsection{Open Comments} We also invited the participants to give a
-free-form comment regarding their concerns of answering Stack Overflow with code
-snippets. Besides the one we present earlier in the introduction, these are
-interesting comments we received.
-
-\begin{enumerate}
-	\item \textit{``When I copy code it's usually short enough to be considered "fair
-		use" but I am not a lawyer or copyright expert so some guidance from Stack Overflow would be
-		helpful. I'd also like the ability to flag/review questions that violate these
-		guidelines.''}
-	\item \textit{``My only concern, albeit minor, is that I know people blindly copy
-		my code without even understanding what the code does.''}
-	\item \textit{``The main problem for me/us is outdated code, esp. as old answers
-		have high google rank so that is what people see first, then try and fail. Thats
-		why we're moving more and more of those examples to knowledge base and docs and
-		rather link to those.''}
-	\item \textit{``Lot of the answers are from hobbyist so the quality is poor.
-		Usually they are hacks or workarounds (even MY best answer on Stack Overflow is a
-		workaround).''}
-\end{enumerate}
-
-The comments highlight that Stack Overflow users are unsure about the
-legal implications of copying code, that code is copied without
-understanding it, and that the quality of code on Stack Overflow is
-often low.
 
@@
 
-The 2,302 clone pairs classified by the first and the third author are subject
+The 2,289 clone pairs classified by the first and the third author are subject
 to manual judgement and human errors.  Although we tried our best to be careful
@@
 % are much harder to detect. 
-We classified 2,302 clone pairs using seven patterns of online code
+We classified 2,289 clone pairs using seven patterns of online code
 cloning. We discovered 154 clone pairs that have been

### 2018-05-14 cloverflow-tse/cover_letter/cover_letter.tex
Start restructuring the paper.

@@
 \usepackage{natbib}
+\usepackage{booktabs} % For formal tables
 
@@
 	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects.
-Hence, we have performed a study of code clone detection between our reported outdated code fragments on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star.
-We selected SourcererCC with 80\% similarity for this experiment and detected clones between the 101 outdated code snippets and the retrieved GitHub data set.
-We relied on SourcererCC because it could scale to a large-scale data set, while Simian could not.
+Hence, we have performed a study of code clone detection between our reported outdated code snippets on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star.
+We selected SourcererCC with 80\% similarity for this experiment because it could scale to a large-scale data set, while Simian could not.
 We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them.
-Out of the 102 cloned snippets, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly matched (they contained additional code modifications made by the projects' developers).
+Out of the 102 cloned snippets, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).
 Lastly, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
@@
 	Among the exact-copy of 47 outdated cloned snippets, there were only two cloned snippets that gave attributions to Stack Overflow.
-However, the attributions pointed to different posts that the ones we found the outdated code, but containing the same code in the answers.
-The other 32 cloned snippets were very likely to be a file-level clone from its original projects based on their license header and the Javadoc comments.
+However, the attributions pointed to different posts than the ones we found, but containing the same code in the answers.
+The other 32 cloned snippets were very likely to be a file-level clone from its respective original project (e.g.
+JFreeChart, JUnit, Log4J, Hadoop) based on their license header and the Javadoc comments.
 Lastly, the remaining 13 cloned snippets did not have any hints or evidence of copying.
@@
 However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information.
-Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets because ...
-developers in the future.}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets because ...
-developers in the future.}''.
+Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
 \end{enumerate}
@@
 Furthermore, we also improved the paper on the aspect of the awareness of information-seekers to toxic code snippets on Stack Overflow by including the results from another survey of Stack Overflow visitors (i.e.~information seekers).
-This survey of the Stack Overflow visitors was performed during the same time as the Stack Overflow answerers (25 July 2017 to 25 September 2017).
+This survey of the Stack Overflow visitors was performed during the same time as the Stack Overflow answerers (25 July 2017 to 25 September 2017) and the full results are reported in our technical report~\citep{Ragkhitwetsagul_RN2017}.
 We did not include the results in the previous version of the paper due to a smaller sample size compared to the answerers survey.
-However, we did find some interesting results and we discussed only the key findings in~Section \ref{#}.
+However, we did find some interesting results so we have included them into this version and discussed the key findings in~RQ1 \ref{#}.
 We copied the text below.
@@
 
-tho
+We adopted non-probability convenient sampling to invite participants for this
+survey. Participation in the survey requires experience of visiting Stack
+Overflow for solving programming tasks at least once. The participants were
+invited to take the survey via various channels: social media post (Facebook),
 Thailand's popular technology news and media community in Thailand called
@@
 For the detective measure, while checking if the copied code snippets on Stack Overflow are still up-to-date with the latest version of their originals can possibly be done automatically, it is a challenging task to automate the process of establishing the origin of code clones.
-As shown in this study, we still relied on manual validation to read the post, understand the context, and use multiple hints with human judgement (comments in the code, natural text in the question and answers, date/time of the posts) to conclude that the code snippets are actually copied from Qualitas to Stack Overflow.
+As shown in this study, we still relied on manual validation to read the post, understand the context, and use multiple hints based on human judgement (comments in the code, natural text in the question and answers, date/time of the posts) to conclude that the code snippets are actually copied from Qualitas to Stack Overflow.
 Thus, one viable solution for now is encouraging the Stack Overflow developers to always include the origin of the copied code snippet in the post so that this link is always established at the posting time.
 Even better, Stack Overflow can provide an optional form to fill in when an answerer post an answer if he or she copies code from other software projects.
-The form should include the origin of the code snippet and its original license.
+The form should include the origin of the code snippet (possibly as a GitHub url) and its original license.
+Using this manually established links at posting time, we can then automate the process of checking for outdated code.
 
@@
 However, we used the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning.
-Moreover, the term code cloning is not well known outside the code cloning community, so we decided not to use the term in the title.
+Moreover, the term code cloning is not well known outside the code cloning community.
+Code clones are called differently in each research community or in practice, such as duplicated code, copy-and-paste code, code reuse, software similarity or software redundancy.
+So, we decided not to use the term in the title.
 
@@
 We include the result of this investigation in the RQ regarding outdated code (RQ?).
-We found that, out of 101 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment).
+We found that, out of 100 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment).
 Thus, there is about 6\% of outdated answers that were notified by the Stack Overflow users based on our analysed data.
+None of the 6 answers change their outdated code, but the comments themselves may help to warn other Stack Overflow users.
 We added this discussion in the RQ\FIXME{?}.
@@
 
-We appreciate the comments. We have refined our definition of toxic code snippets in the paper to:
+We appreciate the comments.
+We have refined our definition of toxic code snippets in the paper by adapting from Israel Gat's definition~\citep{toxiccode} which links toxic code to technical debt, i.e.~``a metaphor reflecting technical compromises that can yield short-term benefit but may hurt the long-term health of a software system''~\citep{Li2015}.
+The new definition of toxic doe snippets are as follows.
 
-\FIXME{Is this ok?}~``Toxic code snippets mean cloned code snippets that
-are harmful for reuse due to (1) being outdated and containing bugs or (2) violating their original software license. They are two ramifications of code cloning
-including bug propagation~\citep{Bellon2007}
-and software license violations~\citep{An2017}.
-Toxic code snippets can occur in software projects or programming Q\&A websites, such
-as Stack Overflow.
-This study focuses on toxic code snippets that occur on Stack Overflow and how they occur.''
+``Toxic code snippets mean code snippets that, after incorporating into software,
+the cost of paying back the technical debt exceeds the value it generates in the long run.'' 
+Stack Overflow code snippets
+cloned from open source software or online sources can become toxic when they
+are (1)~outdated or (2)~violating their original software
+license. Outdated code snippets
+can be harmful since they are not up-to-date with their originals and may
+contain defects. Code snippets from open source projects usually fall under a
+specific software license, e.g.\ GNU General Public License (GPL). If they are
+cloned to Stack Overflow answers without the license, and then flow to other projects
+with conflicting licenses, legal issues may occur.
 
@@
 
-Based on your suggestion of looking at other newer or higher-voted answers, we performed an investigation of all the answers in 101 posts containing outdated code snippets as accepted answers.
-We discussed the findings in the relevant RQ.
-\FIXME{Add the findings.}
+Based on your suggestion of looking at other newer or higher-voted answers, we performed an investigation of all the answers in 100 posts containing outdated code snippets as accepted answers.
+We found that there were 34 posts which contains newer answers.
+Regarding the number of votes, there were 5 posts which contained other answers with a higher number of votes than the outdated answer.
+Ninety-nine out of the one hundred outdated code were still marked as accepted answers.
+This discussion of the findings is added to the the RQ\FIXME{?}.
 
@@
 Although we grouped the code modifications that make Stack Overflow snippets outdated into 6 categories as shown in Table 9, we did not investigate the motivation of the changes such as code refactoring or variable renaming.
-We have performed the check as you suggested by checking the commit message of each change that make the code outdated and included the findings in RQ?.
-\FIXME{Add the findings.}
+We have performed the check as you suggested by checking the commit message of each change that make the code outdated.
+The findings are discussed below and are included in the RQ\FIXME{?}.
+
+We looked through the commit history of 100 outdated code snippets and summarised the reasons of code updates.
+We carefully read the commit messages and/or used the bug IDs in the commit messages to obtain more information from the bug report systems.
+We summarised the reasons of code changes into 6 groups as shown in the table below.
+
+\begin{table}
+	\centering
+	\begin{tabular}{llr}
+		\toprule
+		Reason & Detail & Amount \\
+		\midrule
+		Enhancement & Add features or update existing features & 64 \\
+		Deprecation & Delete dead or deprecated code & 15 \\
+		Bug & Fix bugs & 10 \\
+		Refactoring & Refactor code for better design & 6 \\
+		Coding style & Update code to conform to a style guideline & 3 \\
+		Data change & Change code due to changing of the data & 2 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Reasons of code changes in 100 outdated code snippets}
+\end{table}
+
+The majority of the changes are due to code enhancement.
+There are 64 changes for software enhancement, such as adding a new features or improving existing code to support a newer version of the language or APIs.
+Fifteen changes are for removal of dead or deprecated code such as SQL connection code in Hibernate.
+Ten changes are made to fix bugs in the software (e.g.~array reference, race condition, wrong field access, \texttt{NullPointerException}).
+There are 6 changes for code refactoring, 3 changes for updating coding styles using an automated tool or manually, and 2 changes that are caused by the change of data format.
 
@@
 Moreover, we also checked if there is any comment regarding the outdated code or the license of the snippets from other Stack Overflow users.
-For the 101 outdated answers, we found that one answer was deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue.
-For the xxx license-incompatible answers, \FIXME{add the results}.
-We included this discussion in RQ\FIXME{?} and RQ\FIXME{?}.
+From the 100 outdated answers, we found that four answers were deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue.
+We included this discussion in RQ\FIXME{?}.
 

### 2018-05-14 cloverflow-tse/cover_letter/cover_letter.tex
Updated several sections in the cover letter.

@@
 \usepackage{natbib}
+\usepackage{float}
 \usepackage{booktabs} % For formal tables
@@
 	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects.
-Hence, we have performed a study of code clone detection between our reported outdated code snippets on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star.
+Hence, we have performed a study of code clone detection between our 100 reported outdated code snippets on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star.
 We selected SourcererCC with 80\% similarity for this experiment because it could scale to a large-scale data set, while Simian could not.
 We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them.
-Out of the 102 cloned snippets, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).
-Lastly, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
+As shown in Table~\ref{tab:outdated_github}, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
+For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).
+
+	\begin{table}[H]
+		\centering
+		\caption{Clones of the 100 Stack Overflow outdated code snippets in 131,703 GitHub projects}
+		\label{tab:outdated_github}
+		\begin{tabular}{lr}
+			\toprule
+			Clones & Amount \\
+			\midrule
+			\textit{Found in Qualitas GitHub repos} & 13 \\
+			\midrule
+			\textit{Found in other project repos} & \\
+			Exact copy & 47 \\
+			Non-exact copy & 32 \\
+			\midrule
+			Total & 102 \\
+			\bottomrule
+		\end{tabular}
+	\end{table}
 
@@
 Lastly, the remaining 13 cloned snippets did not have any hints or evidence of copying.
+
 	Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks).
@@
 Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
+	We also updated the Overall Discussion section to reflect the findings that there is only a few toxic outdated code that are found in open source projects on GitHub.
+Moreover, the direction of copying is also unclear.
+The clones could come from Stack Overflow, the original project repositories, or other places.
 \end{enumerate}
@@
 We did not include the results in the previous version of the paper due to a smaller sample size compared to the answerers survey.
-However, we did find some interesting results so we have included them into this version and discussed the key findings in~RQ1 \ref{#}.
-We copied the text below.
+However, we did find some interesting results so we have included them into this version and discussed the key findings in~RQ1.
+The summary of the visitor survey is as follows.
 
@@
 
+The survey consists of 16 questions: 9 Likert's
+scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
+open-ended questions. 
+The full survey can be found in our research note~\citep{Ragkhitwetsagul_RN2017}.
+The first four questions are mandatory while the other 12
+questions will be shown to the participants based on their previous answers. 
+The survey collects information about the participant's software development
+experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
+snippets, problems from Stack Overflow snippets, licensing of code on Stack
+Overflow, and additional feedback. 
 We adopted non-probability convenient sampling to invite participants for this
@@
 Overflow for solving programming tasks at least once. The participants were
-invited to take the survey via various channels: social media post (Facebook),
-Thailand's popular technology news and media community in Thailand called
-\texttt{blognone.com}, the University of Molise in Italy where the third author
+invited to take the survey via five channels: social media post (Facebook),
+\textsf{blognone.com}, a popular technology news and media community in Thailand, the University of Molise in Italy where the third author
 works, \texttt{comp.lang.java.programmer} group and the Software Engineering
-Facebook page. We received answers from 89 participants. Two participants never
+Facebook page. 
+The survey was open for participation for 2 months, 
+from 25 July 2017 to 25 September 2017, before we collected and analysed
+the responses.
+
+We received answers from 89 participants. 
+Two participants never
 copy code from Stack Overflow so we analysed the answers of the remaining 87
-participants. The key findings are as follows.
+participants.
 
+\textbf{General Information: }
+Twenty four (27\%) and twenty one (24\%) participants have over 10 years and 5--10
+years of experience respectively. There are 19 participants (21\%) who have 3--5
+years, 18 (20\%) who have 1-2 years, and 7 (8\%) participants who have less than a
+year of programming experience.
+
+\textbf{Choice for programming solutions: }
 Stack Overflow is ranked higher than official documentation, online
@@
 can be found easily from search engine, solve similar problems to their
-problems, provide helpful context, and offer voting and accepted answers. The
-results show that 57 out of 87 Stack Overflow visitors encountered a problem
-from reusing Stack Overflow code snippets. Ten participants experienced problems
-for more than 80\% of the copied snippets and sixteen participants faced
-problems for 40--60\% of the reused code. The problems ranked by frequency
+problems, provide helpful context, and offer voting and accepted answers.
+
+\vspace{0.25cm}
+\textit{Do Stack Overflow
+	visitors experience outdated code and check for licensing conflicts when
+	they copy and reuse answer from Stack Overflow?}
+\vspace{0.25cm}
+
+\begin{table}
+	\centering
+	\caption{Problems from Stack Overflow code snippets}
+	\label{tab:visitor_survey_code_problems}
+	\begin{tabular}{lr}
+		\toprule
+		Problem & Amount \\
+		\midrule
+		Mismatched solutions & 40 \\
+		Outdated solutions & 39 \\
+		Incorrect solutions	& 28 \\
+		Buggy code & 1 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Frequency of reporting the problems to Stack Overflow posts}
+	\label{tab:visitor_survey_report_problem}
+	\begin{tabular}{lrr}
+		\toprule
+		Report? & Amount & Percent \\
+		\midrule
+		Very Frequently (81--100\% of the time)	& 1 & 1.8\% \\
+		Frequently (61--80\% of the time) & 1 & 1.8\% \\
+		Occasionally (41--60\% of problematic snippets) & 3 & 5.3\% \\
+		Rarely (21--40\% of problematic snippets) & 8 & 14.0\% \\
+		Very rarely (1--20\% of problematic snippets) & 8 & 14.0\% \\
+		Never (0\% of problematic snippets) & 36 & 63.2\% \\
+		\midrule
+		Total & 57 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+The survey results show that 57 out of 87 Stack Overflow visitors encountered a
+problem from reusing Stack Overflow code snippets. Ten participants experienced
+problems for more than 80\% of the copied snippets and sixteen participants
+faced problems for 40--60\% of the reused code. As shown in Table~\ref{tab:visitor_survey_code_problems}, 
+the problems ranked by frequency
 include mismatched solutions (40), outdated solutions (39), incorrect solutions
-(28), and buggy code (1). Fifty-six percent of the participants never report the
-problems back to Stack Overflow. In addition, 85\% of the participants are not
+(28), and buggy code (1). Sixty-three percent of the participants never report
+the problems back to Stack Overflow (Table~\ref{tab:visitor_survey_report_problem}). 
+The ways of reporting the problems
+(22 answers) included down-voting the answer containing the problematic code
+snippet (8), writing a comment saying that the code has problems (10),
+contacting the answerers regarding the problems directly (2), and posting a
+better snippet as new answer on same topic (2).
+
+\begin{table}
+	\centering
+	\caption{Check for licensing conflicts before using Stack Overflow snippets}
+	\label{tab:visitor_survey_license_check}
+	\begin{tabular}{lrr}
+		\toprule
+		License check? & Amount & Percent \\
+		\midrule
+		Very frequently (81--100\% of the time) & 0 & 0.0\% \\
+		Frequently (61--80\% of the time) & 7 & 8.1\%
+\\
+		Occasionally (41--60\% of the time) & 6 & 6.9\%
+\\
+		Rarely (21--40\% of the time) & 6 & 6.9\% \\
+		Very rarely (1--20\% of the time) & 11 & 12.6\% \\
+		Never (0\% of the time)	& 57 & 65.5\% \\
+		\midrule
+		Total & 87 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+In addition, 74 out of the 87 (85\%) participants are not
 aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to
-the Stack Overflow posts they copied the code snippets from. We found that 66\%
+the Stack Overflow posts they copied the code snippets from. 
+As shown in Table~\ref{tab:visitor_survey_license_check}, we found that 66\%
 of the visitors never check for software licensing conflicts between Stack
@@
 license, and more than half of them never check for license compatibility when
-reusing Stack Overflow code snippets. We also found that 9\% of the participants
+reusing Stack Overflow code snippets. 
+Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
+check if the code snippet originated from a different source (e.g. an open source project) 
+with an incompatible license to their projects.
+Moreover, we also found that 9\% of the participants
 encountered legal issues by copying code from Stack Overflow. To the best of our
@@
 has never been done before and will be our future work.
+
+\textit{To answer RQ 1.2, Stack Overflow visitors experienced several issues from Stack
+Overflow answers including outdated code. The majority of them are not aware of
+CC BY-SA 3.0 license enforced by Stack Overflow and never check for license
+conflicts when reusing code snippets.}
 
@@
 
-Thanks for the suggestion.~We rewrote the Overall Discussion section to be more precise and practical as discussed below.
+Thanks for the suggestion.~We rewrote the Overall Discussion section to reflect yours and Reviewer 3's comments. The changes include:
 
-Using the updated definition of outdated code, we foresee the implementation of the IDE plugin using a combination of scalable code clone detection~\citep{Sajnani2016} or clone search techniques~\citep{Kim2018} and automated software licensing detection~\citep{German2010}.
+\begin{enumerate}
+	\item We added a discussion of toxicity of outdated and license-incompatible clones on Stack Overflow.
+Although we found some harmful outdated clones, we could not find evidence that they are widely reused in open source projects on GitHub.
+\end{enumerate}
+
+We empirically show from the surveys and the clone detection experiment that online code clones occur on Stack Overflow and the clones may become toxic due to outdated code and software license incompatibility.
+Nevertheless, we found only a small amount of toxic outdated code snippets in open source projects on GitHub.
+Besides 12 buggy and outdated code snippets found in 12 projects, the rest were non-harmful clones of the outdated code.
+Although other studies show that Stack Overflow code snippets may contain security vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we found in this study that the damage caused by reusing outdated code on Stack Overflow is not high.
+
+On the other hand, the missing of licensing statement of online code clones on Stack Overflow can be more harmful than outdated code.
+As shown in our study and also in the study by \cite{An2017}, some online clones on Stack Overflow are originally licensed under more restrictive license than Stack Overflow's CC BY-SA 3.0.
+If these missing-license online clones are reused in a software with incompatible license, the software owner may face legal issues.
+The software auditing service such as Black Duck Software or nexB, which can effectively check for license compliance of code copied from open source projects, cannot check for the original license of the code snippets on Stack Overflow.
+Although Stack Overflow answerers participated in our survey believe that most of the code snippets on Stack Overflow are too small to claim for copyright and they fall under fair-use, there is still a risk due to different legal system in each country.
+For example, Germany legal system does not have a concept of fair use or the number of minimum lines of code to be consider trivial, i.e.~de minimis, is also different from case to case or from country to country.
+
+We foresee the implementation of the IDE plugin using a combination of scalable code clone detection~\citep{Sajnani2016} or clone search techniques~\citep{Kim2018} and automated software licensing detection~\citep{German2010}.
 In this study, we performed the check using a set of code clone detectors (Simian and SourcererCC) and software licensing detector (Ninka) but we had to operate the tools manually.
@@
 Nevertheless, since this is a very interesting suggestion.
-We also performed an investigation of the 101 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet.
+We also performed an investigation of the 100 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet.
 We include the result of this investigation in the RQ regarding outdated code (RQ?).
@@
 
-Regarding the age of cloned code on Stack Overflow, we did the analysis and added a boxplot as you suggested in RQ X. We found that ... \FIXME{add the discussion}.
+Regarding the age of cloned code on Stack Overflow, we did an analysis of clone ages on the QS clone pairs since we successfully manually confirmed the direction of cloning.
+Moreover, we could searched for the date that the cloned version of the QS project appeared, which was not possible for UD, EX, BP, and IN clone pairs.
+We calculated the clone ages by counting the number of month difference from the dates of each Qualitas project to the date the answers were posted on Stack Overflow.
+We drew a boxplot as you suggested and included the discussion of the statistics in RQ4.
+We found that the minimum, maximum, median, and average clone ages were 0, 64, 26.5 and 26 months respectively (also summarised in the table below).
+
+\begin{table}[H]
+	\centering
+\begin{tabular}{lrrrr}
+	\toprule
+	Pattern & Min & Max & Avg. & Median \\
+	\midrule
+	QS & 0 & 64 & 26.5 & 26.0 \\
+	\bottomrule
+\end{tabular}
+\end{table}
+
+From the data, we observed that the it took around 2 years for the clones from Qualitas projects to appear on Stack Overflow answers.
+Some of the clones appeared on Stack Overflow almost at the same time as the original, while the oldest clones took around 5 years.
 
@@
 
-We have performed an additional experiment to search for occurrences of outdated code snippets in open source GitHub projects. The findings show \FIXME{...}
+That is a good point. We relied on the two new analyses to include discussion about toxicity of outdated code in the Overall Discussion.
+
+First, from the answer to Reviewer 2, we analysed the intent behind the changes that made the code outdated and found that only 10 and 15 out of 100 cases were bug fixing and dead code.
+Besides that, the code were outdated because of evolution in the software (adding or enhancing features, refactoring, changing coding style, and data change).
+
+Second, as previously discussed in the answer to Reviewer 1, we have performed an additional experiment to search for occurrences of the 100 outdated code snippets in 130,703 open source GitHub projects and found 102 occurrences of the outdated code.
+47 were exact copy of the outdated versions, of which 12 were buggy.
+However, we could not establish evidence that the outdated code were cloned from Stack Overflow or somewhere else.
+We have reported the problem of race condition in two clone snippets found in deeplearning4j and Apache Hive to the developers.
+
+To summarise, we empirically show from the surveys and the clone detection experiment that online code clones occur on Stack Overflow and the clones may become toxic due to outdated code and software license incompatibility.
+Nevertheless, we found only a small amount of toxic outdated code snippets in open source projects on GitHub.
+Besides 12 buggy and outdated code snippets found in 12 projects, the rest were non-harmful clones of the outdated code.
+Although other studies show that Stack Overflow code snippets may contain security vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we found in this study that the damage caused by reusing outdated code on Stack Overflow is not high.
+
+On the other hand, the missing of licensing statement of online code clones on Stack Overflow can be more harmful.
+As shown in our study and also in the study by \cite{An2017}, some online clones on Stack Overflow are originally licensed under more restrictive license than Stack Overflow's CC BY-SA 3.0.
+If these missing-license online clones are reused in a software with incompatible license, the software owner may face legal issues.
+The software auditing service such as Black Duck Software or nexB, which can effectively check for license compliance of code copied from open source projects, cannot check for the original license of the code snippets on Stack Overflow.
+Although Stack Overflow answerers participated in our survey believe that most of the code snippets on Stack Overflow are too small to claim for copyright and they fall under fair-use, there is still a risk due to different legal system in each country.
+For example, Germany legal system does not have a concept of fair use or the number of minimum lines of code to be consider trivial, i.e.~de minimis, is also different from case to case or from country to country.
 

### 2018-05-14 cloverflow-tse/cloverflow.tex
Added QS clone ages and improved several sections in the paper.

@@
 works, \texttt{comp.lang.java.programmer} group and the Software Engineering
-Facebook page. We received answers from 89 participants. Two participants never
-copy code from Stack Overflow so we analysed the answers of the remaining 87
-participants.
+Facebook page. 
 The survey was open for participation for 2 months, 
@@
 \vspace{0.25cm}
-\textit{RQ 1.1 How often are Stack Overflow
+\textit{How often are Stack Overflow
 	answerers aware of the outdated code and 
@@
 \begin{boxquote}
-	To answer RQ 5.1, regarding outdated code, although most of the Stack Overflow answerers are aware that their code
+	To answer RQ 1.1, regarding outdated code, although most of the Stack Overflow answerers are aware that their code
 	can be outdated, 51.5\% of the answerers were very rarely notified and 35.5\% have never been notified of
@@
 
+\subsubsection{The Visitor Survey}
+
+We received answers from 89 participants. 
+Two participants never
+copy code from Stack Overflow so we analysed the answers of the remaining 87
+participants.
+
+\textbf{General Information: }
+Twenty four (27\%) and twenty one (24\%) participants have over 10 years and 5--10
+years of experience respectively. There are 19 participants (21\%) who have 3--5
+years, 18 (20\%) who have 1-2 years, and 7 (8\%) participants who have less than a
+year of programming experience.
+
+\textbf{Choice for programming solutions: }
+Stack Overflow is ranked higher than official documentation, online
+repositories, and books as the resource to look for programming solutions.
+Developers rely on Stack Overflow answers because they are easy to search for on
+the web. Moreover, 64\% of the participants reuse code snippets from Stack
+Overflow at least once a week. They copy code from Stack Overflow because they
+can be found easily from search engine, solve similar problems to their
+problems, provide helpful context, and offer voting and accepted answers.
+
+\vspace{0.25cm}
+\textit{Do Stack Overflow
+	visitors experience outdated code and check for licensing conflicts when
+	they copy and reuse answer from Stack Overflow?}
+\vspace{0.25cm}
+
+\begin{table}
+	\centering
+	\caption{Problems from Stack Overflow code snippets}
+	\label{tab:visitor_survey_code_problems}
+	\begin{tabular}{lr}
+		\toprule
+		Problem & Amount \\
+		\midrule
+		Mismatched solutions & 40 \\
+		Outdated solutions & 39 \\
+		Incorrect solutions	& 28 \\
+		Buggy code & 1 \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+\begin{table}
+	\centering
+	\caption{Frequency of reporting the problems to Stack Overflow posts}
+	\label{tab:visitor_survey_report_problem}
+	\begin{tabular}{lrr}
+		\toprule
+		Report? & Amount & Percent \\
+		\midrule
+		Very Frequently (81--100\% of the time)	& 1 & 1.8\% \\
+		Frequently (61--80\% of the time) & 1 & 1.8\% \\
+		Occasionally (41--60\% of problematic snippets) & 3 & 5.3\% \\
+		Rarely (21--40\% of problematic snippets) & 8 & 14.0\% \\
+		Very rarely (1--20\% of problematic snippets) & 8 & 14.0\% \\
+		Never (0\% of problematic snippets) & 36 & 63.2\% \\
+		\midrule
+		Total & 57 & 100\% \\
+		\bottomrule
+	\end{tabular}
+\end{table}
+
+The survey results show that 57 out of 87 Stack Overflow visitors encountered a
+problem from reusing Stack Overflow code snippets. Ten participants experienced
+problems for more than 80\% of the copied snippets and sixteen participants
+faced problems for 40--60\% of the reused code. As shown in~\Cref{tab:visitor_survey_code_problems}, 
+the problems ranked by frequency
+include mismatched solutions (40), outdated solutions (39), incorrect solutions
+(28), and buggy code (1). Sixty-three percent of the participants never report
+the problems back to Stack Overflow (\Cref{tab:visitor_survey_report_problem}). 
+The ways of reporting the problems
+(22 answers) included down-voting the answer containing the problematic code
+snippet (8), writing a comment saying that the code has problems (10),
+contacting the answerers regarding the problems directly (2), and posting a
+better snippet as new answer on same topic (2).
+
+\begin{table}
+	\centering
+	\caption{Check for licensing conflicts before using Stack Overflow snippets}
+	\label{tab:visitor_survey_license_check}
+	\begin{tabular}{lrr}
+		\toprule
+		License check? & Amount & Percent \\
+		\midrule
+		Very frequently (81--100\% of the time) & 0 & 0.0\% \\
+		Frequently (61--80\% of the time) & 7 & 8.1\%
+\\
+		Occasionally (41--60\% of the time) & 6 & 6.9\%
+\\
+		Rarely (21--40\% of the time) & 6 & 6.9\% \\
+		Very rarely (1--20\% of the time) & 11 & 12.6\% \\
+		Never (0\% of the time)	& 57 & 65.5\% \\
+		\midrule
+		Total & 87 & 100\% \\
+\bottomrule
+\end{tabular}
+\end{table}
+
+In addition, 74 out of the 87 (85\%) participants are not
+aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to
+the Stack Overflow posts they copied the code snippets from. 
+As shown in \Cref{tab:visitor_survey_license_check}, we found that 66\%
+of the visitors never check for software licensing conflicts between Stack
+Overflow code snippets and their projects. Interestingly, 9\% of the
+participants encountered legal issues. Unfortunately, due to the anonymity of
+the survey, we could not investigate further regarding the legal issues that the
+participants faced from using Stack Overflow code snippets.
+
+The visitors survey confirms the findings from the previous studies that Stack
+Overflow code snippets can be problematic~\cite{Zhang2018,Acar2016,An2017,Fischer2017}. Sixty-six
+percent of the visitors experienced a problem from reusing Stack Overflow code
+snippets ranging from incorrect solutions, outdated solutions, mismatched
+solutions, to buggy code. Although they are aware of the problems, half of them
+(56\%) never reports back to the Stack Overflow discussions. On the other hand,
+the visitors rarely give attributions to Stack Overflow when they reuse code
+snippets from the website, similar to the findings reported
+by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
+license, and more than half of them never check for license compatibility when
+reusing Stack Overflow code snippets. 
+Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
+check if the code snippet originated from a different source (e.g. an open source project) 
+with an incompatible license to their projects.
+Moreover, we also found that 9\% of the participants
+encountered legal issues by copying code from Stack Overflow. To the best of our
+knowledge, a study of legal problems from reusing Stack Overflow code snippets
+has never been done before and will be our future work.
+
+\begin{boxquote}
+	To answer RQ 1.2, Stack Overflow visitors experienced several issues from Stack
+Overflow answers including outdated code. The majority of them are not aware of
+CC BY-SA 3.0 license enforced by Stack Overflow and never check for license
+conflicts when reusing code snippets.
+\end{boxquote}
+
 \subsection{RQ2: Online Code Clones} 
@@
 	\label{fig:boxplotclonesize}
+\end{figure}
+
+\begin{figure}
+	\centering
+	\includegraphics[width=\linewidth]{boxplot_clone_age}
+	\caption{Age of online code clones.}
+	\label{fig:boxplotcloneage}
 \end{figure}
@@
 
+To check occurrences of our Stack Overflow outdated code snippets in software projects, 
+we
+
 \begin{boxquote}
@@
 % originals.
+
+This study empirically show from the surveys and the clone detection experiment that
+online code clones occur on Stack Overflow and the clones may become toxic due
+to outdated code and software license incompatibility. The findings lead to the
+insight about toxicity of online code clones and two actionable items
+we are proposing to the Stack Overflow community.
+
+\subsubsection{Toxicity of outdated and license-incompatible clones}
+We found only a small amount of toxic outdated code snippets in open source projects on
+GitHub. Besides 12 buggy and outdated code snippets found in 12 projects, the
+rest were non-harmful clones of the outdated code. Although other studies show
+that Stack Overflow code snippets may contain security
+vulnerabilities~\cite{Acar2016,Fischer2017} or API misuse~\cite{Zhang2018}, we
+found in this study that the damage caused by reusing outdated code on Stack
+Overflow is not high.
+
+On the other hand, the missing of licensing statement of online code clones on
+Stack Overflow can cause more damage than outdated code. As shown in our study and
+also in the study by An et al. \cite{An2017}, some online clones on Stack Overflow are
+originally licensed under more restrictive license than Stack Overflow's CC
+BY-SA 3.0. If these missing-license online clones are reused in a software with
+incompatible license, the software owner may face legal issues. The software
+auditing service such as Black Duck Software or nexB, which can effectively
+check for license compliance of code copied from open source projects, cannot
+check for the original license of the cloned code snippets on Stack Overflow. Although
+Stack Overflow answerers participated in our survey believe that most of the
+code snippets on Stack Overflow are too small to claim for copyright and they
+fall under fair-use, there is still a risk due to different legal system in each
+country. For example, Germany legal system does not have a concept of fair use~\cite{?}
+or the number of minimum lines of code to be consider trivial, i.e.~de minimis,
+is also different from case to case or from country to country~\cite{?}.
+
+\subsubsection{Actionable Items}
 Our study discovers links from code in open source projects to code snippets on
@@
 
-\begin{itemize} 
-	\item \textbf{Preventive measure:} We
-	encourage Stack Overflow to enforce attribution when source code snippets have
-	been copied ``from'' licensed software projects to Stack Overflow. Moreover, an
-	IDE plug-in that can automatically detect pasted source code and follow the link
-	to Stack Overflow and then to the original open source projects, could also
-	prevent the issue of license violation. 
-	\item \textbf{Detective measure:} A
-	system to detect outdated source code snippets on Stack Overflow is needed. The
+\textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution
+when source code snippets have been copied ``from'' licensed software projects
+to Stack Overflow. Moreover, an IDE plug-in that can automatically detect pasted
+source code and follow the link to Stack Overflow and then to the original open
+source projects, could also prevent the issue of license violation. We foresee
+the implementation of the IDE plugin using a combination of scalable code clone
+detection~\cite{Sajnani2016} or clone search techniques~\cite{Kim2018} and
+automated software licensing detection~\cite{German2010}. In this study, we
+performed the check using a set of code clone detectors (Simian and SourcererCC)
+and software licensing detector (Ninka) but we had to operate the tools
+manually. Using the knowledge obtained from this study, we plan to build an
+automated and scalable clone search with licensing detection. With the proposed
+solution, we can use the tool to create a database of code snippets on Stack
+Overflow and allow the users to search for clones and check their licenses. The
+clone search tool can offer a service via REST API and integrated into the IDE
+plugin. Every time a new code fragment is pasted into the IDE, the plugin
+performs the check by calling the clone search tool service and report the
+finding to the developers in real time.
+
+In addition, we also performed a study of two open source software auditing
+platforms/services:~BlackDuck
+Software\footnote{https://www.blackducksoftware.com} and
+nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from their
+report~\cite{CORSI2017} that while they check for code copied from open source
+projects including GitHub and Stack Overflow and analyse their license
+compatibility with their customer software, the BlackDuck auditing system will
+treat the code snippets on Stack Overflow as having ``unknown'' license because
+it does not know the original license of Stack Overflow code snippets. For nexB,
+their product does not mention checking of reused source code from Stack
+Overflow. So, our proposed service, which can offer more precise licensing
+information of Stack Overflow code snippets, will be useful as an add-on license
+check for code copying from Stack Overflow.
+
+\textbf{Detective measure:} A
+system to detect outdated source code snippets on Stack Overflow may be needed. The
 system can leverage the online clone detection techniques in this study to
 periodically check if the cloned snippets are still up-to-date with their
-	originals. %Moreover, Stack Overflow posters have to provide the information of
-	% the project including the original file name and its online repository (if
-	% exists).
+originals.
+
+While checking if the copied code snippets on Stack Overflow are still up-to-date with the latest version of their originals can possibly be done automatically, it is a challenging task to automate the process of establishing the origin of code clones.
+As shown in this study, we still relied on manual validation to read the post, understand the context, and use multiple hints based on human judgement (comments in the code, natural text in the question and answers, date/time of the posts) to conclude that the code snippets are actually copied from Qualitas to Stack Overflow.
+Thus, one viable solution for now is encouraging the Stack Overflow developers to always include the origin of the copied code snippet in the post so that this link is always established at the posting time.
+Even better, Stack Overflow can provide an optional form to fill in when an answerer post an answer if he or she copies code from other software projects.
+The form should include the origin of the code snippet (possibly as a GitHub url) and its original license.
+Using this manually established links at posting time, we can then automate the process of checking for outdated code.
+
 With such a system, the poster can be notified when the code has been updated
@@
 corrections to them.
-\end{itemize}
 

### 2018-05-14 cloverflow_technical_report/cloverflow_survey_rn.tex
Removed unwanted subsection (RN).
Added the RN number.
Fixed a wrong stat in the technical repot.

@@
 
-\rnnumber{17/xx}
+\rnnumber{17/10}
 %\usepackage[table]{xcolor}% http://ctan.org/pkg/xcolor
@@
 
-\subsection{Visitor Responses}
+\subsection{The visitor survey}
 
@@
 threads (as can be seen in
-Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 32 participants
-who encounter problems of Stack Overflow snippets, 18 of them (56\%) never
+Figure~\ref{fig:survey_visitor_freq_report_problems}). Among the 57 participants
+who encounter problems of Stack Overflow snippets, 36 of them (63.2\%) never
 report the problems. Fourteen participants who reported the problems
@@
 			problems ranked by frequency include mismatched solutions (40), outdated
-			solutions (39), incorrect solutions (28), and buggy code (1). Fifty-six percent
+			solutions (39), incorrect solutions (28), and buggy code (1). Sixty-three percent
 			of the participants never report the problems back to Stack Overflow.}}%
@@
 
-\subsubsection{Stack Overflow Visitors}
+%\subsubsection{Stack Overflow Visitors}
 

### 2018-05-15 cloverflow-tse/cloverflow.tex
Latest update with many improvements.

@@
 \begin{boxquote}
-	To answer RQ2, we found more than half (53\%) of Qualitas projects to share
-	similar code with Stack Overflow code snippets. In the manually confirmed 
-	data set of 2,289 clone pairs, we found 2,076 pairs as true positives which 
-	account for 59 Qualitas projects and
-	443 Stack Overflow code snippets.
+	To answer RQ2, we found 2,076 manually confirmed clone pairs between 443 Stack Overflow code snippets
+	and 59 Qualitas proejcts. 
+	%After the manual confirmation, 2,076 pairs as true positives, i.e.~
+	%they are manually confirmed as clones, which 
+	%account for 59 Qualitas projects and
+	%443 Stack Overflow code snippets.
 \end{boxquote}
@@
 
+\begin{table}
+\centering
+\label{tab:license_github}
+\caption{Clones of the 214 missing-license code snippets in 131,703 GitHub projects}
+\begin{tabular}{lrr}
+	\toprule
+	No. of stars & Qualitas & Other Projects \\
+	\midrule
+	29,540 to 10 stars & 71 & 1,836 \\
+	9 to 5 stars & 0 & 739 \\
+	4 to 1 stars & 19 & 4,541 \\
+	\midrule
+	Total & 90 & 7,116 \\
+	\bottomrule
+\end{tabular}
+\end{table}
+
 %If developers copy and reuse these licensed pieces of code in their projects,

### 2018-05-15 cloverflow-tse/cover_letter/cover_letter.tex
Latest update with many improvements.

@@
 \usepackage{float}
+\usepackage{multirow}
 \usepackage{booktabs} % For formal tables
@@
 %\begin{abstract}
-This paper is a journal-first submission to Transactions on Software Engineering. 
-This is a re-submission of the previous submission no.~TSE-2017-11-0335 and we would like to thank the anonymous Reviewers for taking their time to carefully read our paper.
-With their useful and constructive reviews, we substantially improved the work by adding three major improvements as listed below to our previous submission and minor improvements as discussed later in this letter:
+This paper is a journal-first submission to Transactions on Software
+Engineering. This is a re-submission of the previous submission
+no.~TSE-2017-11-0335 and we would like to thank the anonymous Reviewers for
+taking their time to carefully read our paper. With their useful and
+constructive reviews, we substantially improved the work by adding three major
+improvements as listed below to our previous submission and minor improvements
+as discussed later in this letter:
 
-\textbf{1.
-A study of toxic code snippets on GitHub:}~To provide an evidence that toxic code snippets are actually reused in software projects and strengthen the motivation, we performed a large-scale analysis of clones between toxic code snippets on Stack Overflow and xxx,xxx GitHub projects.
+\textbf{1. A study of toxic code snippets on GitHub:}~To provide an evidence
+that toxic code snippets are actually reused in software projects and strengthen
+the motivation, we performed a large-scale analysis of clones between the
+discovered 100 outdated code snippets on Stack Overflow and 130,703 GitHub
+projects using a clone detection tool and a manual validation.
 
-\textbf{2.
-Analysis of tools' parameter settings:}~We mitigated the threats to validity due to parameter settings of the clone detection tools and the clone merging technique by performing a comparison of different tools' parameter settings.
+\textbf{2. Analysis of tools' parameter settings:}~We mitigated the threats to
+validity due to parameter settings of the clone detection tools and the clone
+merging technique by performing a comparison of different tools' parameter
+settings.
 
-\textbf{3. Revisions to the overall discussion:}~???
+\textbf{3. Extended analysis of online code clones:}~We performed more analyses
+on the 2,289 online code clones and 100 outdated code snippets. For example,
+we analysed the size and age of the clones, and summarised the six intents that
+made the clones outdated.
 
-We also tried our best to address all the comments from the reviewers. Each particular comment led to an improvement on this submission as presented in the following discussions.
+\textbf{4. Revisions to the overall discussion:}~We substantially expanded the
+overall discussion to include (1) a discussion of toxicity of outdated and
+license-incompatible clones on Stack Overflow, and (2) more detailed discussion
+of how to implement the tools or approaches proposed in the preventive and
+detective measures.
+
+We also tried our best to address all the comments from the reviewers. Every
+comment led to an improvement(s) on this submission and we discuss them in order as shown in the
+next sections.
 
@@
 We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them.
-As shown in Table~\ref{tab:outdated_github}, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
+As shown in the table below, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
 For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).
@@
 		\centering
-		\caption{Clones of the 100 Stack Overflow outdated code snippets in 131,703 GitHub projects}
+%		\caption{Clones of the 100 Stack Overflow outdated code snippets in 131,703 GitHub projects}
 		\label{tab:outdated_github}
@@
 			\textit{Found in other project repos} & \\
-			Exact copy & 47 \\
+			Exact copy (outdated) & 47 \\
 			Non-exact copy & 32 \\
@@
 On the other hand, the bug report in Apache Hive is still unfixed.
+
+	\item The same study has been done for another type of toxic code snippets on Stack Overflow, license-incompatible code snippets.
+We detected clones between the 214 code snippets without their original license (86 QS, 78 EX and 50 UD)  and 130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
+	Then, we used the Ninka tool to automatically identify software license from the 7,207 code snippets.
+	Opposite to the outdated clones, we discovered many more clones of 7,207 candidate pairs. There were 90 pairs from 10 Qualitas projects on GitHub and 7,117 pairs from 
+	2,427 other projects. From the Table \ref{tab:license_github} shown below, the clones were found from highly-starred projects (29,465 to 10 stars) to 1-star projects.
+
+	\begin{table}[H]
+		\centering
+		\label{tab:license_github}
+		\begin{tabular}{l|rr|rrr}
+			\toprule
+			\multirow{2}{*}{No. of stars} & \multicolumn{2}{c|}{Qualitas} & \multicolumn{3}{c}{Other Projects} \\ \cmidrule{2-6}
+			& Projects & Clone Pairs & Projects & Clone Pairs & Same license \\
+			\midrule
+			29,540 to 10 stars & 8 & 71 & 406 & 1,837 & 193 \\
+			9 to 5 stars & 0 & 0 & 275 & 739 & 110 \\
+			4 to 1 stars & 2 & 24 & 1,746 & 4,536 & 692 \\
+			\midrule
+			Total & 10 & 95 & 2,427 & 7,112 & 995 \\
+			\bottomrule
+		\end{tabular}
+		\caption{Clones of the 214 Stack Overflow missing-license code snippets in 131,703 GitHub projects}
+	\end{table}
+
 	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub.
@@
 	We also updated the Overall Discussion section to reflect the findings that there is only a few toxic outdated code that are found in open source projects on GitHub.
-Moreover, the direction of copying is also unclear.
+%Moreover, the direction of copying is also unclear.
 The clones could come from Stack Overflow, the original project repositories, or other places.
@@
 However, we did find some interesting results so we have included them into this version and discussed the key findings in~RQ1.
-The summary of the visitor survey is as follows.
+The brief summary of the visitor survey is as follows.
 
@@
 
-The survey consists of 16 questions: 9 Likert's
-scale questions, 3 yes/no questions, 2 multiple-choice questions, and 2
-open-ended questions. 
-The full survey can be found in our research note~\citep{Ragkhitwetsagul_RN2017}.
-The first four questions are mandatory while the other 12
-questions will be shown to the participants based on their previous answers. 
-The survey collects information about the participant's software development
-experience, the importance of Stack Overflow, reasons for reusing Stack Overflow
-snippets, problems from Stack Overflow snippets, licensing of code on Stack
-Overflow, and additional feedback. 
-We adopted non-probability convenient sampling to invite participants for this
-survey. Participation in the survey requires experience of visiting Stack
-Overflow for solving programming tasks at least once. The participants were
-invited to take the survey via five channels: social media post (Facebook),
-\textsf{blognone.com}, a popular technology news and media community in Thailand, the University of Molise in Italy where the third author
-works, \texttt{comp.lang.java.programmer} group and the Software Engineering
+We surveyed 87 Stack Overflow visitors (visit the site and reuse code from Stack Overflow at least once) via five channels: social media post (Facebook),
+\textsf{blognone.com}, a popular technology news and media community in Thailand, the University of Molise in Italy where the third author works, \texttt{comp.lang.java.programmer} group and the Software Engineering
 Facebook page.
-The survey was open for participation for 2 months, 
-from 25 July 2017 to 25 September 2017, before we collected and analysed
-the responses.
-
-We received answers from 89 participants. 
-Two participants never
-copy code from Stack Overflow so we analysed the answers of the remaining 87
-participants.
-
-\textbf{General Information: }
-Twenty four (27\%) and twenty one (24\%) participants have over 10 years and 5--10
-years of experience respectively. There are 19 participants (21\%) who have 3--5
-years, 18 (20\%) who have 1-2 years, and 7 (8\%) participants who have less than a
-year of programming experience.
-
-\textbf{Choice for programming solutions: }
-Stack Overflow is ranked higher than official documentation, online
-repositories, and books as the resource to look for programming solutions.
-Developers rely on Stack Overflow answers because they are easy to search for on
-the web. Moreover, 64\% of the participants reuse code snippets from Stack
-Overflow at least once a week. They copy code from Stack Overflow because they
-can be found easily from search engine, solve similar problems to their
-problems, provide helpful context, and offer voting and accepted answers.
-
-\vspace{0.25cm}
-\textit{Do Stack Overflow
-	visitors experience outdated code and check for licensing conflicts when
-	they copy and reuse answer from Stack Overflow?}
-\vspace{0.25cm}
-
-\begin{table}
-	\centering
-	\caption{Problems from Stack Overflow code snippets}
-	\label{tab:visitor_survey_code_problems}
-	\begin{tabular}{lr}
-		\toprule
-		Problem & Amount \\
-		\midrule
-		Mismatched solutions & 40 \\
-		Outdated solutions & 39 \\
-		Incorrect solutions	& 28 \\
-		Buggy code & 1 \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-\begin{table}
-	\centering
-	\caption{Frequency of reporting the problems to Stack Overflow posts}
-	\label{tab:visitor_survey_report_problem}
-	\begin{tabular}{lrr}
-		\toprule
-		Report? & Amount & Percent \\
-		\midrule
-		Very Frequently (81--100\% of the time)	& 1 & 1.8\% \\
-		Frequently (61--80\% of the time) & 1 & 1.8\% \\
-		Occasionally (41--60\% of problematic snippets) & 3 & 5.3\% \\
-		Rarely (21--40\% of problematic snippets) & 8 & 14.0\% \\
-		Very rarely (1--20\% of problematic snippets) & 8 & 14.0\% \\
-		Never (0\% of problematic snippets) & 36 & 63.2\% \\
-		\midrule
-		Total & 57 & 100\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-The survey results show that 57 out of 87 Stack Overflow visitors encountered a
-problem from reusing Stack Overflow code snippets. Ten participants experienced
-problems for more than 80\% of the copied snippets and sixteen participants
-faced problems for 40--60\% of the reused code. As shown in Table~\ref{tab:visitor_survey_code_problems}, 
-the problems ranked by frequency
-include mismatched solutions (40), outdated solutions (39), incorrect solutions
-(28), and buggy code (1). Sixty-three percent of the participants never report
-the problems back to Stack Overflow (Table~\ref{tab:visitor_survey_report_problem}). 
-The ways of reporting the problems
-(22 answers) included down-voting the answer containing the problematic code
-snippet (8), writing a comment saying that the code has problems (10),
-contacting the answerers regarding the problems directly (2), and posting a
-better snippet as new answer on same topic (2).
-
-\begin{table}
-	\centering
-	\caption{Check for licensing conflicts before using Stack Overflow snippets}
-	\label{tab:visitor_survey_license_check}
-	\begin{tabular}{lrr}
-		\toprule
-		License check? & Amount & Percent \\
-		\midrule
-		Very frequently (81--100\% of the time) & 0 & 0.0\% \\
-		Frequently (61--80\% of the time) & 7 & 8.1\%
-\\
-		Occasionally (41--60\% of the time) & 6 & 6.9\%
-\\
-		Rarely (21--40\% of the time) & 6 & 6.9\% \\
-		Very rarely (1--20\% of the time) & 11 & 12.6\% \\
-		Never (0\% of the time)	& 57 & 65.5\% \\
-		\midrule
-		Total & 87 & 100\% \\
-		\bottomrule
-	\end{tabular}
-\end{table}
-
-In addition, 74 out of the 87 (85\%) participants are not
-aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to
-the Stack Overflow posts they copied the code snippets from. 
-As shown in Table~\ref{tab:visitor_survey_license_check}, we found that 66\%
-of the visitors never check for software licensing conflicts between Stack
-Overflow code snippets and their projects. Interestingly, 9\% of the
-participants encountered legal issues. Unfortunately, due to the anonymity of
-the survey, we could not investigate further regarding the legal issues that the
-participants faced from using Stack Overflow code snippets.
 
@@
 
-\textit{To answer RQ 1.2, Stack Overflow visitors experienced several issues from Stack
-Overflow answers including outdated code. The majority of them are not aware of
-CC BY-SA 3.0 license enforced by Stack Overflow and never check for license
-conflicts when reusing code snippets.}
+The full detail can be found in the RQ1 result section in the paper.
 
@@
 Although we found some harmful outdated clones, we could not find evidence that they are widely reused in open source projects on GitHub.
+Thus, outdated code snippets may not be so harmful to reuse.
+On the other hand, the problem of license incompatibility caused by missing original license in Stack Overflow code snippets can cause more damage than outdated code.
+Different legal system and different interpretation of fair-use concept and de minimis (i.e.~the minimal lines of code allowed to be copied without violating copyright) in each country can result in a legal case in one country becoming illegal in another country.
+
+	\item We performed a study of two open source software auditing
+	platforms/services:~BlackDuck
+	Software\footnote{https://www.blackducksoftware.com} and
+	nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from their
+	report~\cite{CORSI2017} that while they check for code copied from open source
+	projects including GitHub and Stack Overflow and analyse their license
+	compatibility with their customer software, the BlackDuck auditing system will
+	treat the code snippets on Stack Overflow as having ``unknown'' license because
+	it does not know the original license of Stack Overflow code snippets. For nexB,
+	their product does not mention checking of reused source code from Stack
+	Overflow. So, our proposed service, which can offer more precise licensing
+	information of Stack Overflow code snippets, will be useful as an add-on license
+	check for code copying from Stack Overflow. We include this in the Overall Discussion.
+
+	\item We improved the Actionable Items to be more precise about the mechanics on how to automate the process of finding online code clones, detecting outdated code, and finding license-incompatible code snippets.
 \end{enumerate}
-
-We empirically show from the surveys and the clone detection experiment that online code clones occur on Stack Overflow and the clones may become toxic due to outdated code and software license incompatibility.
-Nevertheless, we found only a small amount of toxic outdated code snippets in open source projects on GitHub.
-Besides 12 buggy and outdated code snippets found in 12 projects, the rest were non-harmful clones of the outdated code.
-Although other studies show that Stack Overflow code snippets may contain security vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we found in this study that the damage caused by reusing outdated code on Stack Overflow is not high.
-
-On the other hand, the missing of licensing statement of online code clones on Stack Overflow can be more harmful than outdated code.
-As shown in our study and also in the study by \cite{An2017}, some online clones on Stack Overflow are originally licensed under more restrictive license than Stack Overflow's CC BY-SA 3.0.
-If these missing-license online clones are reused in a software with incompatible license, the software owner may face legal issues.
-The software auditing service such as Black Duck Software or nexB, which can effectively check for license compliance of code copied from open source projects, cannot check for the original license of the code snippets on Stack Overflow.
-Although Stack Overflow answerers participated in our survey believe that most of the code snippets on Stack Overflow are too small to claim for copyright and they fall under fair-use, there is still a risk due to different legal system in each country.
-For example, Germany legal system does not have a concept of fair use or the number of minimum lines of code to be consider trivial, i.e.~de minimis, is also different from case to case or from country to country.
-
-We foresee the implementation of the IDE plugin using a combination of scalable code clone detection~\citep{Sajnani2016} or clone search techniques~\citep{Kim2018} and automated software licensing detection~\citep{German2010}.
-In this study, we performed the check using a set of code clone detectors (Simian and SourcererCC) and software licensing detector (Ninka) but we had to operate the tools manually.
-Using the knowledge obtained from this study, we plan to build an automated and scalable clone search with licensing detection.
-With the proposed solution, we can use the tool to create a database of code snippets on Stack Overflow and allow the users to search for clones and check their licenses.
-The clone search tool can offer a service via REST API and integrated into the IDE plugin.
-Every time a new code fragment is pasted into the IDE, the plugin performs the check by calling the clone search tool service and report the finding to the developers in real time.
-
-In addition, we also performed a study of two open source software auditing platforms/services:~BlackDuck Software\footnote{https://www.blackducksoftware.com} and nexB\footnote{https://www.nexb.com}.
-For BlackDuck Software, we found from their report~\citep{CORSI2017} that while they check for code copied from open source projects including GitHub and Stack Overflow and analyse their license compatibility with their customer software, the BlackDuck auditing system will treat the code snippets on Stack Overflow as having ``unknown'' license because it does not know the original license of Stack Overflow code snippets.
-For nexB, their product does not mention checking of reused source code from Stack Overflow.
-So, our proposed service, which can offer more precise licensing information of Stack Overflow code snippets, will be useful as an add-on license check for code copying from Stack Overflow.
-
-For the detective measure, while checking if the copied code snippets on Stack Overflow are still up-to-date with the latest version of their originals can possibly be done automatically, it is a challenging task to automate the process of establishing the origin of code clones.
-As shown in this study, we still relied on manual validation to read the post, understand the context, and use multiple hints based on human judgement (comments in the code, natural text in the question and answers, date/time of the posts) to conclude that the code snippets are actually copied from Qualitas to Stack Overflow.
-Thus, one viable solution for now is encouraging the Stack Overflow developers to always include the origin of the copied code snippet in the post so that this link is always established at the posting time.
-Even better, Stack Overflow can provide an optional form to fill in when an answerer post an answer if he or she copies code from other software projects.
-The form should include the origin of the code snippet (possibly as a GitHub url) and its original license.
-Using this manually established links at posting time, we can then automate the process of checking for outdated code.
 
@@
 
-We also updated the Introduction to state that the dominant topic is about online code clones~\FIXME{to do}.
+We also updated the Introduction to state that the dominant topic is about online code clones~\FIXME{do it}.
 %Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.
@@
 Nevertheless, we have modified the text in the Introduction to include your concern ...
-\FIXME{do this}.
+\FIXME{do it}.
 
@@
 None of the 6 answers change their outdated code, but the comments themselves may help to warn other Stack Overflow users.
-We added this discussion in the RQ\FIXME{?}.
+We added this discussion in the RQ4 \FIXME{do it}.
 
@@
 Ninety-nine out of the one hundred outdated code were still marked as accepted answers.
-This discussion of the findings is added to the the RQ\FIXME{?}.
+This discussion of the findings is added to the the RQ4 \FIXME{do it}.
 
@@
 We have performed the check as you suggested by checking the commit message of each change that make the code outdated.
-The findings are discussed below and are included in the RQ\FIXME{?}.
+The findings are discussed below and are included in the RQ4 \FIXME{do it}.
 
@@
 From the 100 outdated answers, we found that four answers were deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue.
-We included this discussion in RQ\FIXME{?}.
+We included this discussion in RQ4 \FIXME{do it}.
 
@@
 
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.5\linewidth]{../boxplot_clone_size}
+	\caption{Size of online code clones.}
+	\label{fig:boxplotclonesize}
+\end{figure}
+
 Regarding increasing the minimum clone size to more than 10 lines (e.g.
-15 lines), we added an analysis of the clone size as shown in Figure 6.
+15 lines), we added an analysis of the clone size as shown in Figure \ref{fig:boxplotclonesize}.
 We found that the distribution of true clones; QS, SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines.
@@
 
-We have modified the paper to include this discussion.
+We have modified the paper to include this discussion in RQ2 \FIXME{do it}.
 
@@
 
-To emphasise this point, we also modified the answer of the RQ to be clearer. It now says ``\FIXME{...}''.
+To emphasise this point, we also modified the answer of the RQ2 to be clearer.
+It now says \textit{``To answer RQ2, we found 2,076 manually confirmed clone pairs between 443 Stack Overflow code snippets
+and 59 Qualitas proejcts.''.}
 
@@
 Moroever, another user posted a comment on the answer of the post no.~801935 that the code snippet is not of high quality and suggested an alternative in another post.
+We extended this discussion in RQ4 \FIXME{do it}.
 
@@
 We are grateful for the insightful comment.
-We performed another manual check of the outdated clones as you suggested and the findings are discussed in Section X.
 We selected the 2013 snapshot of Qualitas data since it is the latest and the most complete snapshot (i.e.~having the highest number of Java projects) provided by the data set author.
 
-Regarding the age of cloned code on Stack Overflow, we did an analysis of clone ages on the QS clone pairs since we successfully manually confirmed the direction of cloning.
+Regarding the age of cloned code on Stack Overflow, we did an analysis of clone ages as you suggested.
+We only chose the QS clone pairs since we could manually confirmed the direction of cloning.
 Moreover, we could searched for the date that the cloned version of the QS project appeared, which was not possible for UD, EX, BP, and IN clone pairs.
@@
 	\centering
-\begin{tabular}{lrrrr}
+\begin{tabular}{lrrrrr}
 	\toprule
-	Pattern & Min & Max & Avg. & Median \\
+	\multirow{2}{*}{Clone pattern} & \multirow{2}{*}{Amount} & \multicolumn{4}{c}{Age of clones (months)} \\ \cmidrule{3-6}
+	& & Min & Max & Avg. & Median \\
 	\midrule
-	QS & 0 & 64 & 26.5 & 26.0 \\
+	QS & 153 & 0 & 64 & 26.5 & 26.0 \\
 	\bottomrule
@@
 
-From the data, we observed that the it took around 2 years for the clones from Qualitas projects to appear on Stack Overflow answers.
+From the data, we observed that, on average, it took around 2 years for the clones from Qualitas projects to appear on Stack Overflow answers.
 Some of the clones appeared on Stack Overflow almost at the same time as the original, while the oldest clones took around 5 years.
@@
 We asked the visitors their experience regarding outdated and license-incompatible code caused by copying and reusing code snippets from Stack Overflow.
+The findings are incorporated into RQ1.
 
@@
 
-That is a good point. We relied on the two new analyses to include discussion about toxicity of outdated code in the Overall Discussion.
+That is a good point. We relied on the two new analyses and added a new discussion about toxicity of outdated code in the Overall Discussion.
 
@@
 
+We also updated the Actionable Items section to reflect Reviewer 1's comment.
+
 \vspace{1cm}
@@
 \section{Conclusion}
-Finally, we would like to thank the reviewers again for the comments.
-We have addressed every concern that has been pointed out by the reviewers which result in inclusion of a Stack Overflow visitors' survey, an analysis of toxic code snippets in GitHub projects, analysis of different tools' and technique's parameters, the definition of toxic code snippets, and the improvements in writing.
+We would like to thank the reviewers again for their comments.
+We have tried our best to address every concern that has been pointed out by the reviewers.
+This result in inclusion of a Stack Overflow visitors' survey, an analysis of toxic code snippets in GitHub projects, analysis of different tools' and technique's parameters, a more detailed analysis of online code clones, the updated definition of toxic code snippets, the improved overall discussion section, and other minor improvements throughout the paper.
 We believe this new submission has been considerably improved from the previous version due to the insightful reviews and discussions and we are looking forward to the new reviews.

### 2018-05-16 cloverflow-tse/cloverflow.tex
Improved the paper based on the responses in the cover letter.

@@
 larger and no longer confined to a local repository.
+Although this activity of online code cloning is well-known, there is only a few
+empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
+the on finding the origins of the clones.
+We tackle this challenge of establishing existence of online code clones and
+investigate how they occur in this study.
 
@@
 The two toxic code snippets in our examples have been posted on March 11, 2014 and
-April 9, 2009 respectively. They have already been viewed 259 and 2,886 times at
+April 9, 2009 respectively. They have already been viewed 259 and 2,886 times\footnote{The number of views
+is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
+because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).} 
+at
 the time of writing this paper (October 3, 2017). Our calculation finds that
@@
 origins of code examples reveals the problem of toxic code snippets
-caused by outdated code and software licensing violations. It is probably more
-important than studying the effects of reusing Stack Overflow code snippets
+caused by outdated code and software licensing violations. It is equally
+important to studying the effects of reusing Stack Overflow code snippets
 because it gives insights to the root cause of the problem and lays a
@@
 	snippets:} We performed an online survey and collected answers from 201
-highly-ranked Stack Overflow users. We found that they cloned code snippets
+highly-ranked Stack Overflow users and 87 Stack Overflow visitors. 
+We found that the answerers cloned code snippets
 from open source projects to Stack Overflow answers. While Stack Overflow
@@
 rarely or never fix the code. 99\% of the answerers never include a software
-license in their snippets and 69\% never check for licensing conflicts between
-the cloned code snippets and Stack Overflow's CC BY-SA 3.0. On the other hand, we also
-surveyed 87 Stack Overflow visitors (i.e.~information seekers) on their
-experiences to toxic code snippets on Stack Overflow. Sixty-six percent of the
-visitors experienced a problem from reusing Stack Overflow code snippets. The
-visitors are generally not aware of the CC BY-SA 3.0 license, and more than
+license in their snippets and 69\% never check for licensing conflicts.
+On the other hand, 66\% of the
+Stack Overflow visitors experienced a problem from reusing Stack Overflow code snippets. 
+They are generally not aware of the CC BY-SA 3.0 license, and more than
 half of them never check for license compatibility when reusing Stack Overflow
@@
 other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
-detecting clones with renaming and added/deleted statements (type-2, type-3). We made sure that they 
-detected only non-trivial clones by increasing the minimum clone size to ten
-lines.
+detecting clones with renaming and added/deleted statements (type-2, type-3).
+
+Nevertheless, we have tried varying the minimum clone lines of 6, 10, and larger
+than 10 for the two clone detection tools. The minimum clone size of 10 lines is
+considered a standard setting for clone detection in large-scale data sets to
+avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
+setter methods) in the analysis or the manual investigation
+phase~\cite{Sajnani2016}. Choosing this size threshold larger than 10 could
+possibly remove some non-trivial clones from the analysis, i.e.~create more
+false negatives. On the other hand, decreasing the threshold to be lower than 10
+lines will result in a larger number of clone candidate pairs to look at and a
+higher chance of getting false positives. It is known that lowering the number
+of minimum clone lines is harmful to precision. Moreover, the large number of
+clone pairs will hinders the full manual validation of the clones and force us
+to rely on sampling of clone pairs. We performed an analysis to confirm this. We
+started by running the tools with minimum clone size of 10 lines and performing
+the manual clone confirmation. Then, we compared the number of true clone pairs
+detected if we increase or decrease the size.
+
+\begin{figure}[H] \centering
+	\includegraphics[width=0.8\linewidth]{boxplot_clone_size} 
+	\caption{Size of online code clones.} 
+	\label{fig:boxplotclonesize}
+\end{figure}
+
+Regarding increasing the minimum clone size to more than 10 lines (e.g. 15
+lines), the result is as shown in
+\Cref{fig:boxplotclonesize}. We found that the distribution of true clones; QS,
+SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines. Increasing
+the threshold to be higher than 10 would remove some of the trivial BP and IN
+clone pairs which are not interesting for this study. However, it will also
+remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.
+
+Regarding decreasing the minimum clone size to be less than 10 lines, we reran
+the two clone detection tools again using a minimum
+clone size of 6 lines, another well-accepted minimum clone size in clone
+benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
+SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
+With this large amount of clone
+candidate pairs, it is not feasible to manually confirm all of the clones and we
+must rely on sampling. This will result in weaker findings and
+weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
+to keep the balance between the number of non-trivial clone pairs and the
+feasibility of manual clone investigation.
+%We made sure that they 
+%detected only non-trivial clones by increasing the minimum clone size to ten
+%lines.
 %(denoted as \textit{D}), and (2)~the discovered configurations for
@@
 
-Using the ok-match criterion with a predefined threshold \textit{t} of 0.7
+The threshold \textit{t} is crucial for the ok-match because it affects the number
+of merged clone pairs. Setting a high \textit{t} value will result in a few ok-match clone pairs
+and duplicates of the same clone pairs (which are supposed to be merged) may appear in the merged
+clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
+pairs and some non-duplicate clone pairs may be accidentally merged by only
+a few matching lines.
+In order to get an optimal $t$ value, we did an analysis by choosing
+five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
+By setting $t=0.7$ according to Bellon's study, we
+found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3,
+0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
+Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually
+checked all the 111 reported pairs. We found one false positive pair and 110
+true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false
+positive pair and still retained all the 110 true positive pairs. All the clone
+pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
+subset of $t=0.5$. However, since there is a fewer true positive pairs reported
+(i.e.~generating false negatives), we ended up leaving some duplicates of the 
+same clones in the final merged clone set.
+With this analysis, we can see that setting the threshold $t$ to 0.1 is too
+relaxed and results in having false positive ok-match pairs, while setting the
+$t$ to 0.7 or 0.9 is too strict and generates some false negative pairs. Thus,
+we decided to select the $t$ value at 0.5.
+
+Using the ok-match criterion with the threshold \textit{t} of 0.5
 similar to Bellon's study~\cite{Bellon2007}, we merge 721 clone pairs from
 Simian and 1,678 clone pairs from SourcererCC into a single set of 2,289 online
-clone pairs. There are only 97 common clone pairs between the two clone sets 
+clone pairs. There are only 110 common clone pairs between the two clone sets 
 as depicted in~\Cref{fig:clonemerging}.  The low number of common
@@
 
-We found that although the answerer have been notified of
-outdated code in their answers, for 51.5\% of them such notifications occur very rarely (only 1--20\% of the answers). 
-Only 3 participants reported that they were notified in more than 60\% of their answers.
+We found that although the answerer have been notified of outdated code in their
+answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
+of the answers). Only 3 participants reported that they were notified in more
+than 60\% of their answers. This notification to the answerer can be done by
+posting comments for that answer on Stack Overflow. For example, the answerer of
+the Stack Overflow question no.~10924648 posted a comment on his own answer
+saying that the answer is specifically for Spring 3.1. Moroever, another user
+posted a comment on the answer of the post no.~801935 that the code snippet is
+not of high quality and suggested an alternative in another post.
 
@@
 
-During the manual investigation of 2,289 clone pairs, we identified 226 pairs
+Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
 as being accidental clones (AC), i.e.~false positives. After removing
@@
 
-\begin{table}
-	\centering
-	\caption{Statistics of clone sizes}
-	\label{tab:clone_stats}
-	\begin{tabular}{lrrrr}
-		\toprule
-		Clones & Min & Max & Mean & Median \\
-		\midrule
-		QS & 10 & 135 & 18.6 & 14 \\
-		SQ & 21 & 21 & 21.0 & 21 \\
-		UD & 10 & 104 & 18.1 & 14 \\
-		EX & 10 & 48 & 16.7 & 14 \\
-		BP & 10 & 55 & 19.9 & 21 \\
-		IN & 11 & 22 & 13.8 & 13.0 \\
-		\bottomrule
-	\end{tabular} 
-\end{table}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{boxplot_clone_size}
-	\caption{Size of online code clones.}
-	\label{fig:boxplotclonesize}
-\end{figure}
-
-\begin{figure}
-	\centering
-	\includegraphics[width=\linewidth]{boxplot_clone_age}
-	\caption{Age of online code clones.}
-	\label{fig:boxplotcloneage}
-\end{figure}
+%\begin{table}
+%	\centering
+%	\caption{Statistics of clone sizes}
+%	\label{tab:clone_stats}
+%	\begin{tabular}{lrrrr}
+%		\toprule
+%		Clones & Min & Max & Mean & Median \\
+%		\midrule
+%		QS & 10 & 135 & 18.6 & 14 \\
+%		SQ & 21 & 21 & 21.0 & 21 \\
+%		UD & 10 & 104 & 18.1 & 14 \\
+%		EX & 10 & 48 & 16.7 & 14 \\
+%		BP & 10 & 55 & 19.9 & 21 \\
+%		IN & 11 & 22 & 13.8 & 13.0 \\
+%		\bottomrule
+%	\end{tabular} 
+%\end{table}
 
@@
 \end{table}
+
+We did an analysis of the time it took for the clone to appear from Qualitas
+projects to Stack Overflow. The clone ages were calculated by counting the
+number of month difference from the dates of each Qualitas project to the date
+the answers were posted on Stack Overflow as shown in~\ref{fig:boxplotcloneage}.
+We found that, on average, it took the clones around 2 years since they appeared
+in Qualitas projects to appear on Stack Overflow answers. Some of the clones
+appeared on Stack Overflow almost at the same time as the original, while the
+oldest clones took around 5 years.
+
+\begin{figure}
+	\centering
+	\includegraphics[width=0.9\linewidth]{boxplot_clone_age}
+	\caption{Age of QS online code clones.}
+	\label{fig:boxplotcloneage}
+\end{figure}
 
@@
 
+We performed a detailed investigation of the 100 outdated answers on Stack
+Overflow two years after the snapshot we have (6 May 2018) 
+on three aspects: newer or higher-voted answers and comments. We found
+that there were 34 posts which contains newer answers. Regarding the number of
+votes, there were 5 questions which contained answers with a higher number of
+votes than the outdated answer. However, 99 of the 100 outdated answers were still
+marked as accepted answers. For the comments, we check if there is any comment
+to mitigate or point out the toxicity of the outdated code snippets. We found
+that, out of 100 answers, there were 6 answers that had a comment saying the
+code in the answer is outdated or containing issues, such as \textit{``spring
+	3.1 stuff''}, \textit{``...tried this but having connect exception --
+	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
+	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no.
+HADOOP-11323)''} or \textit{``..
+I do not have experience
+	with new versions of hibernate for a long time. But previously without clean you
+	could receive some unexpected results. So I suggest to try different approaches
+	or even check latest documentation''}. None of the 6 answers change their
+outdated code, but the comments themselves may help to warn other Stack Overflow
+users.
+
 To check occurrences of our Stack Overflow outdated code snippets in software projects, 

### 2018-05-16 cloverflow-tse/cover_letter/cover_letter.tex
Improved the paper based on the responses in the cover letter.

@@
 Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
-	We also updated the Overall Discussion section to reflect the findings that there is only a few toxic outdated code that are found in open source projects on GitHub.
+	We also updated the Overall Discussion section to reflect the findings that (1) there is only a small number of toxic code snippets from outdated code that are found in GitHub projects, (2) there is a large number of toxic code snippets from missing license that are found in GitHub projects.
 %Moreover, the direction of copying is also unclear.
@@
 
-We also updated the Introduction to state that the dominant topic is about online code clones~\FIXME{do it}.
+We also updated the Introduction to state that the dominant topic is about online code clones as follows.
+
+``Although this activity of online code cloning is well-known, there is only a few
+empirical studies on the topic~\citep{An2017,Abdalkareem2017,Baltes2017}, especially
+the on finding the origins of the clones.
+We tackle this challenge of establishing existence of online code clones and
+investigate how they occur in this study.''
 %Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.
@@
 That is a fair point and we would like to analyse the statistics as you suggested. 
-Unfortunately, for our experiment, we extracted only the code snippets from the Stack Overflow dumps but not other information.
+For (a), the number of views
+is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
+because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).
+For (b), unfortunately, for our experiment we extracted only the code snippets from the Stack Overflow dumps but not other information.
 They are the only available data of the January 2016 snapshot we currently have.
 We checked and found that the latest available Stack Overflow dump already contains different data than the one we used in our study since it is now more than 2 years newer, and will result in incorrect statistics and inconsistent results.
-Nevertheless, we have modified the text in the Introduction to include your concern ...
-\FIXME{do it}.
+For (c), that is a really interesting idea. However, it is out of the scope of this study and would involve an extensive analysis of the data so we plan to do it in the future work.
+
+ Nevertheless, we have added a footnote to the text in the Introduction to clarify point (a).
 
@@
 We also performed an investigation of the 100 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet.
-We include the result of this investigation in the RQ regarding outdated code (RQ?).
+We include the result of this investigation in the RQ4.
 We found that, out of 100 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment).
@@
 None of the 6 answers change their outdated code, but the comments themselves may help to warn other Stack Overflow users.
-We added this discussion in the RQ4 \FIXME{do it}.
+We added this discussion in the RQ4.
 
@@
 From the 100 outdated answers, we found that four answers were deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue.
-We included this discussion in RQ4 \FIXME{do it}.
+We included this discussion in RQ4.
 
@@
 
-That is a fair point.
-The reason we chose the clone size of at least 10 lines is as follows.
+That is a fair point. The reason we chose the clone size of at least 10 lines is as follows.
+
 The minimum clone size of 10 lines is considered a standard setting for clone detection in large-scale data sets to avoid trivial clones (e.g.
@@
 With this large amount of clone candidate pairs, it is not feasible to manually confirm all of the clones and we must rely on sampling.
+Moreover, it is known that lowering the number of minimum clone lines is harmful to precision.
 This will result in weaker findings and weaker conclusion.
@@
 
-We have modified the paper to include this discussion in RQ2 \FIXME{do it}.
+We have modified the paper to include this discussion in RQ2.
 
@@
 On the other hand, setting $t$ to 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
+an analysis by choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
+As shown in the our paper, by setting $t=0.7$ according to Bellon's study, we found 97 ok-match pairs reported.
+On the other hand, setting $t$ to 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
+Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually checked all the 111 reported pairs.
+We found one false positive pair and 110 true positive pairs.
+By raising the $t$ to 0.3 and 0.5, we got rid of the false positive pair and still retained all the 110 true positive pairs.
+All the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a subset of $t=0.5$.
+However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates in the final merged clone set.
+
+With this analysis, we can see that setting the threshold $t$ to 0.1 is too relaxed and results in having false positive ok-match pairs, while setting the $t$ to 0.7 or 0.9 is too strict and generates some false negative pairs.
+Thus, we decided to select the $t$ value at 0.5.
+This reduces the number of merged clone pairs to 2,290 pairs.
+All other numbers which derive from this merged clone pairs have been updated accordingly.
 Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually checked all the 111 reported pairs.
@@
 Moroever, another user posted a comment on the answer of the post no.~801935 that the code snippet is not of high quality and suggested an alternative in another post.
-We extended this discussion in RQ4 \FIXME{do it}.
+We extended this discussion in Section 3.1.1 (RQ1).
 
@@
 We drew a boxplot as you suggested and included the discussion of the statistics in RQ4.
-We found that the minimum, maximum, median, and average clone ages were 0, 64, 26.5 and 26 months respectively (also summarised in the table below).
+We found that the minimum, maximum, median, and average clone ages were 0, 64, 26.5 and 26 months respectively.
+%(also summarised in the table below).
 
-\begin{table}[H]
-	\centering
-\begin{tabular}{lrrrrr}
-	\toprule
-	\multirow{2}{*}{Clone pattern} & \multirow{2}{*}{Amount} & \multicolumn{4}{c}{Age of clones (months)} \\ \cmidrule{3-6}
-	& & Min & Max & Avg. & Median \\
-	\midrule
-	QS & 153 & 0 & 64 & 26.5 & 26.0 \\
-	\bottomrule
-\end{tabular}
-\end{table}
+%\begin{table}[H]
+%	\centering
+%\begin{tabular}{lrrrrr}
+%	\toprule
+%	\multirow{2}{*}{Clone pattern} & \multirow{2}{*}{Amount} & \multicolumn{4}{c}{Age of clones (months)} \\ \cmidrule{3-6}
+%	& & Min & Max & Avg. & Median \\
+%	\midrule
+%	QS & 153 & 0 & 64 & 26.5 & 26.0 \\
+%	\bottomrule
+%\end{tabular}
+%\end{table}
 

### 2018-05-16 programs/SOTokenPreparator/main.py
Added a tool to rewrite SourcererCC token files.

@@ -1,0 +1,58 @@
+def write_file(filename, fcontent, mode, isprint):
+    """
+    Write the string content to a file
+    copied from
+    http://www.pythonforbeginners.com/files/reading-and-writing-files-in-python
+    :param filename: name of the file
+    :param fcontent: string content to put into the file
+    :param mode: writing mode, 'w' overwrite every time, 'a' append to an existing file
+    :return: N/A
+    """
+    # try:
+    file = open(filename, mode)
+    file.write(fcontent)
+    file.close()
+
+    if isprint:
+        print("saved:" + filename)
+
+
+def modify_token_file(file):
+    starting_id = 4000000
+    fname = file
+    with open(fname) as f:
+        content = f.readlines()
+    for c in content:
+        split = c.split('@#@')
+        loc = split[0]
+        token = split[1]
+        locsplit = loc.split(',')
+        first = locsplit[0]
+        second = locsplit[1]
+        # print(first, second)
+        new_id = int(second) + starting_id
+        write_file(file.replace('.', '-new.'), '-1,' + str(new_id) + '@#@' + token, 'a', False)
+
+
+def modify_header_file(file):
+    starting_id = 4000000
+    fname = file
+    with open(fname) as f:
+        content = f.readlines()
+    for c in content:
+        split = c.split(',')
+        print(split)
+        loc = int(split.pop(0))
+        pathc = ",".join(split)
+        print(loc, pathc)
+        write_file(file.replace('.', '-new.'), str(loc + starting_id) + ',' + pathc, 'a', False)
+
+
+def main():
+    modify_token_file('so-license-tokens.file')
+    modify_header_file('so-license-headers.file')
+
+
+main()
+
+

### 2018-05-16 programs/SOTokenPreparator/random_selection.py

@@ -1,0 +1,39 @@
+import random
+
+
+def write_file(filename, fcontent, mode, isprint):
+    """
+    Write the string content to a file
+    copied from
+    http://www.pythonforbeginners.com/files/reading-and-writing-files-in-python
+    :param filename: name of the file
+    :param fcontent: string content to put into the file
+    :param mode: writing mode, 'w' overwrite every time, 'a' append to an existing file
+    :return: N/A
+    """
+    # try:
+    file = open(filename, mode)
+    file.write(fcontent)
+    file.close()
+
+    if isprint:
+        print("saved:" + filename)
+
+
+def random_select(file, amount):
+    random.seed(13)
+    with open(file) as f:
+        clones = f.readlines()
+    for i in range(0, amount):
+        # print(i, random.choice(clones), end='')
+        write_file('license-github-random.csv', random.choice(clones), 'a', False)
+
+
+def main():
+    write_file('license-github-random.csv', 'github,ghstart,ghend,so,sostart,soend,solicense,ghlicense\n', 'a', False)
+    random_select(
+        '/Users/Chaiyong/Documents/phd/2017/CloneOverflow/experiment/results/license-github/combined.csv',
+        400)
+
+
+main()

### 2018-05-18 cloverflow-tse/cloverflow.tex
Continued revising the TSE paper.

@@
 
-Toxic code snippets mean code snippets that are harmful for reuse and, in
-several cases, are caused by online code cloning. Stack Overflow code snippets
+``Toxic code snippets mean code snippets that, after incorporating into software,
+the cost of paying back the technical debt exceeds the value it generates in the long run.'' 
+Stack Overflow code snippets
 cloned from open source software or online sources can become toxic when they
-are (1)~outdated or (2)~violating their original software
-license. Outdated code snippets
-can be harmful since they are not up-to-date with their originals and may
+are (1)~outdated, (2)~violating their original software
+license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
+We chose to study toxic code snippets caused by outdated code and license-violating code snippets in
+this study as the two problems are still under explored compared to code smells~\cite{Tufano2015} or vulnerabilities~\cite{Acar2016,Fischer2017}.
+Outdated code snippets can be harmful since they are not up-to-date with their originals and may
 contain defects. Code snippets from open source projects usually fall under a
@@
 	%\small
-	\begin{tabular}{lrrr}
+	\begin{tabular}{lrr}
 		\toprule
-		Data set & No. of files & SLOC & Median \\
-		\midrule
-		Stack Overflow & 72,365 & 1,840,581 & 17 \\ 
-		Qualitas &  166,709 & 19,614,083 & 60,667 \\ 
+		Data set & No. of files & SLOC \\
+		\midrule
+		Stack Overflow & 72,365 & 1,840,581 \\ 
+		Qualitas &  166,709 & 19,614,083 \\ 
 		\bottomrule
@@
 two versions, we used {\small\texttt{git blame}} to see who modified those lines
-of code and the timestamps. We also collected IDs of issue tracking information
+of code and the timestamps. We also read commit messages and investigated the issue tracking information
 if the code change is linked to an automatic issue tracking system, such as Jira
-or BugZilla.
+or BugZilla to gain insights into the intent behind the change.
+
+Lastly, we searched for the outdated code snippets in 130,703 GitHub projects to
+see how widespread is the outdated code in the wild. We mined GitHub
+based on the number of stars the projects received, which indicated their popularity. We relied on
+GitHub API to query the project metadata before cloning them.
+Since GitHub API returned only top 1,000 projects at a time for each query, we formulated the
+query to retrieve most starred projects based on their sizes.
+The project size range started from 1KB to 2MB with 1KB step size and the last query is
+for all the remaining projects that were larger than 2MB.
+With this method, we retrieved the top 1,000 most starred projects for each project size. 
+As a result, we cloned 130,703 GitHub projects ranging from 29,465 stars to 1 star.
+A clone detection was then performed between the outdated code snippets and the GitHub
+projects. We selected SourcererCC with 80\% similarity for this task because it
+could scale to a large-scale data set, while Simian could not. Finally, we analysed
+the clone reports and manually checked the clones.
 
@@
 check if the code snippet originated from a different source (e.g. an open source project) 
-with an incompatible license to their projects.
+and if they had an incompatible license to their projects.
 Moreover, we also found that 9\% of the participants
@@
 systems are also used, besides bug reports, for feature request and feature
-enhancements, having an issue tracking ID can reflect that the change is important
-and not only a superficial fix such as code formatting.
+enhancements, having an issue tracking ID can reflect that most of the changes are important
+and not only a superficial fix such as code formatting. The intent behind
+the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
+Enhancement are the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
+by code deprecation (15\%). There were 10 outdated code snippets (10\%) due to bug fixing.
+The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
+data format change (2\%).
+Not all outdated code are toxic. However, the 10 buggy and outdated code snippets 
+we found are toxic and are harmful for reuse.
+
+\begin{table}
+	\centering
+	\begin{tabular}{llr}
+		\toprule
+		Intent & Detail & Amount \\
+		\midrule
+		Enhancement & Add or update existing features & 64 \\
+		Deprecation & Delete dead/deprecated code & 15 \\
+		Bug & Fix bugs & 10 \\
+		Refactoring & Refactor code for better design & 6 \\
+		Coding style & Update to a new style guideline & 3 \\
+		Data change & Changes in data format & 2 \\
+		\bottomrule
+	\end{tabular}
+	\label{tab:intent_outdated}
+	\caption{Intents of code changes in 100 outdated code snippets}
+\end{table}
 
@@
 along with the issue tracking number and the date of change. The complete set of
-101 outdated online clones can be found on the study website.
-
-The outdated online code clones cause problems ranging from uncompilable code
-(due to modifications and different API usage in the outdated code) to
-the introduction of vulnerabilities to the software~\cite{Xia2014}. An outdated code with a
-subtle change (e.g.\ \Cref{fig:before-after}) may be copied and reused without
-awareness from developers. Moreover, an outdated code with a defect (e.g.\ a race
-condition problem in \Cref{fig:before-after_2}) is clearly harmful to be reused.
-Although Stack Overflow has a voting mechanism that may mitigate this issue, the
-accepted answer is still used by naive developers who copy and reuse the
-outdated code.
+100 outdated online clones can be found on the study website.
 
@@
 
-To check occurrences of our Stack Overflow outdated code snippets in software projects, 
-we
+\begin{table}[H]
+\centering
+\label{tab:outdated_github}
+\begin{tabular}{lr}
+	\toprule
+	Clones & Amount \\
+	\midrule
+	\textit{Found in Qualitas GitHub repos} & 13 \\
+	\midrule
+	\textit{Found in other project repos} & \\
+	Exact copy (outdated) & 47 \\
+	Non-exact copy & 32 \\
+	\midrule
+	Total & 102 \\
+	\bottomrule
+\end{tabular}
+	\caption{Clones of the 100 Stack Overflow outdated code snippets in 131,703 GitHub projects}
+\end{table}
+
+Then, we performed the check for clones of the 100 outdated code snippets in 130,703 GitHub projects.
+We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all
+of them. As shown in \Cref{tab:outdated_github}, out of the 102 cloned snippets, there were
+13 cloned snippets that matched with themselves because some of the Qualitas
+projects also appear on GitHub. For other projects besides the Qualitas
+projects, there were 47 cloned snippets that were exactly the same as the
+outdated code snippets and 42 cloned snippets that were not exactly the same
+(e.g.~they contained additional code modifications made by the projects'
+developers or they were copied from another source with a slightly different
+code).
+
+Among the exact-copy of 47 outdated cloned snippets, there were only two cloned
+snippets that gave attributions to Stack Overflow. However, the attributions
+pointed to different posts than the ones we found, but containing the same code
+in the answers. The other 32 cloned snippets were very likely to be a file-level
+clone from its respective original project (e.g. JFreeChart, JUnit, Log4J,
+Hadoop) based on their license header and the Javadoc comments. Lastly, the
+remaining 13 cloned snippets did not have any hints or evidence of copying.
+Twelve of them were toxic because they were the old versions that still contained bugs.
+
+Interestingly, we discovered that the buggy version of the
+\texttt{humanReadableInt()} method from Hadoop appears in two popular Java
+projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
+stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
+this method, which is exactly the same as the toxic code snippet we found on
+Stack Overflow, appears in the two projects. It is possible that the developers
+retrieved them from Stack Overflow, other websites, or from Hadoop code base
+directly. Nevertheless, we decided to report the developers of the two projects
+regarding the issue. We created a bug report for each project (deeplearning4j
+\#4694\footnote{deeplearning4j bug report:
+	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
+HIVE-18929\footnote{Apache Hive bug report: \url{
+		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
+developers of the projects by describing the problem of race condition in the
+outdated version of \texttt{humanReadableInt()} method and proposed a fix by
+using the newest version of the method in Hadoop. The issue has been fixed in
+deeplearning4j. The developers of deeplearning4j agreed that the method was
+problematic and they decided to implement their own fix due to a concern of a
+potential software licensing conflict caused by copying the fix directly from
+Hadoop code base. On the other hand, the bug report in Apache Hive is still
+unfixed.
+
+The outdated online code clones cause problems ranging from uncompilable code
+(due to modifications and different API usage in the outdated code) to
+the introduction of vulnerabilities to the software~\cite{Xia2014}. An outdated code with a
+subtle change (e.g.\ \Cref{fig:before-after}) may be copied and reused without
+awareness from developers. Moreover, an outdated code with a defect (e.g.\ a race
+condition problem in \Cref{fig:before-after_2}) is clearly harmful to be reused.
+Stack Overflow has a voting mechanism that may mitigate this issue, the
+accepted answer is still used by naive developers who copy and reuse the
+outdated code.
+Although we did not find strong evidence of the outdated code snippets
+being cloned to GitHub projects, it would still be useful if Stack Overflow
+implements a flagging of outdated answers.
 
@@
 statements, to a fully rewritten code with new method signatures. 15~pairs are
-dead snippets.
+dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
+without evidence of copying. Two of them contains a race condition and
+are found in popular projects: deeplearning4j and Apache Hive.
 \end{boxquote}
@@
 	}
-\end{table}
-
-\begin{table}
-\centering
-\label{tab:license_github}
-\caption{Clones of the 214 missing-license code snippets in 131,703 GitHub projects}
-\begin{tabular}{lrr}
-	\toprule
-	No. of stars & Qualitas & Other Projects \\
-	\midrule
-	29,540 to 10 stars & 71 & 1,836 \\
-	9 to 5 stars & 0 & 739 \\
-	4 to 1 stars & 19 & 4,541 \\
-	\midrule
-	Total & 90 & 7,116 \\
-	\bottomrule
-\end{tabular}
 \end{table}
@@
 
+The same GitHub study has been done for license-incompatible code snippets. 
+We detected clones between the 214
+code snippets without their original license (86 QS, 78 EX and 50 UD)  and
+130,703 GitHub projects using SourcererCC with 80\% similarity threshold. Then,
+we used the Ninka tool to automatically identify software license from the 7,207
+code snippets. Opposite to the outdated clones, we discovered many more clones
+of 7,207 candidate pairs. There were 90 pairs from 10 Qualitas projects on
+GitHub and 7,117 pairs from 2,427 other projects. From
+\Cref{tab:license_github}, the clones were found from highly-starred
+projects (29,465 to 10 stars) to 1-star projects.
+We found 12 code snippets with attributions to Stack Overflow questions/answers and
+6 of them were the answers we found as clones from Qualitas or external sources.
+Five code snippets did not have license while the originals had Apache-2, GPLv2,
+or EPLv1 license. One snippets had AGPLv3 license while the original had Apache-2 license.
+Only 995 code snippets in GitHub projects that have the same license
+as the originals in Qualitas.
+
+\begin{table}
+	\centering
+	\label{tab:license_github}
+	\begin{tabular}{lrrrrr}
+		\toprule
+		\multirow{2}{*}{No. of stars} & \multicolumn{2}{c}{Qualitas} & \multicolumn{3}{c}{Other Projects} \\ \cmidrule{2-6}
+		& Projects & Pairs & Projects & Pairs & Same license \\
+		\midrule
+		29,540--10 & 8 & 71 & 406 & 1,837 & 193 \\
+		9--5 & 0 & 0 & 275 & 739 & 110 \\
+		4--1 & 2 & 24 & 1,746 & 4,536 & 692 \\
+		\midrule
+		Total & 10 & 95 & 2,427 & 7,112 & 995 \\
+		\bottomrule
+	\end{tabular}
+	\caption{Clones of the 214 Stack Overflow missing-license code snippets in 131,703 GitHub projects}
+\end{table}
+
 \begin{boxquote}
@@
 with evidence, where the code snippet has been copied from.
+We found 7,117 of the 214 license-incompatible code snippets
+in 130,703 GitHub projects.
 \end{boxquote}
@@
 fall under fair-use, there is still a risk due to different legal system in each
-country. For example, Germany legal system does not have a concept of fair use~\cite{?}
+country. For example, Germany legal system does not have a concept of fair use
 or the number of minimum lines of code to be consider trivial, i.e.~de minimis,
-is also different from case to case or from country to country~\cite{?}.
+is also different from case to case or from country to country.
 
@@
 actionable items:
+
+\textbf{Automated cloning direction detection:} 
+As shown in this study, we still relied on manual
+validation to read the post, understand the context, and use multiple hints
+based on human judgement (comments in the code, natural text in the question and
+answers, date/time of the posts) to conclude that the code snippets are actually
+copied from Qualitas to Stack Overflow. We call for more research in
+automation of code cloning direction detection. From our experience in this
+paper, we found that code comments and accompanied natural text
+on Stack Overflow were good source of information to decide the direction of
+code copying. Thus, by using code clone detection to locate clone candidates
+and then applying information retrieval techniques, e.g. cosine similarity with tf-idf, 
+we can rank the clone candidates based on the similarity of their project names (or classes) to the text in 
+comments or natural text surrounding the clones in Stack Overflow posts.
+For example, the Stack Overflow answer containing the text \textit{``Actually, you can learn how to compare in \textbf{Hadoop}
+from \textbf{WritableComparator}. Here is an example that borrows some ideas from it.''}
+must be ranked very high among the list of clone candidates of a code snippet
+from Hadoop since it contains two terms of the project name (Hadoop) and a class name (WritableComparator)
+in it.
+This technique will dramatically reduce the manual validation effort to establish
+the direction of cloning. The technique can also be used on Stack Overflow to 
+flag that an answer has high chance of copying from open source projects.
 
@@
 
-While checking if the copied code snippets on Stack Overflow are still up-to-date with the latest version of their originals can possibly be done automatically, it is a challenging task to automate the process of establishing the origin of code clones.
-As shown in this study, we still relied on manual validation to read the post, understand the context, and use multiple hints based on human judgement (comments in the code, natural text in the question and answers, date/time of the posts) to conclude that the code snippets are actually copied from Qualitas to Stack Overflow.
-Thus, one viable solution for now is encouraging the Stack Overflow developers to always include the origin of the copied code snippet in the post so that this link is always established at the posting time.
-Even better, Stack Overflow can provide an optional form to fill in when an answerer post an answer if he or she copies code from other software projects.
-The form should include the origin of the code snippet (possibly as a GitHub url) and its original license.
-Using this manually established links at posting time, we can then automate the process of checking for outdated code.
-
-With such a system, the poster can be notified when the code has been updated
-in the original project so that he/she can update their code on Stack Overflow
+While checking if the copied code snippets on Stack Overflow are still
+up-to-date with the latest version of their originals can possibly be done
+automatically, it is a challenging task to automate the process of establishing
+the origin of code clones. Since automatically establishing code cloning
+is still an open challenge, one viable solution for now is
+encouraging the Stack Overflow developers to always include the origin of the
+copied code snippet in the post so that this link is always established at the
+posting time. Even better, Stack Overflow can provide an optional form to fill
+in when an answerer post an answer if he or she copies code from other software
+projects. The form should include the origin of the code snippet (possibly as a
+GitHub url) and its original license. Using this manually established links at
+posting time, we can then automate the process of checking for outdated code.
+
+With such a system, the poster can be notified when the code has been updated in
+the original project so that he/she can update their code on Stack Overflow
 accordingly. On the other hand, with a crowdsourcing solution using an IDE
@@
 
-The implementation and the evaluation of the
-above actionable items is part of the agenda of our future work.
+%The implementation and the evaluation of the
+%above actionable items is part of the agenda of our future work.
 

### 2018-05-18 cloverflow-tse/cover_letter/cover_letter.tex
Continued revising the TSE paper.

@@
 the motivation, we performed a large-scale analysis of clones between the
-discovered 100 outdated code snippets on Stack Overflow and 130,703 GitHub
-projects using a clone detection tool and a manual validation.
+discovered online code clones, 100 outdated and 214 license-incompatible code snippets, 
+on Stack Overflow and 130,703 GitHub projects using a clone detection tool followed by manual validation.
 
-\textbf{2. Analysis of tools' parameter settings:}~We mitigated the threats to
+\textbf{2. Analysis of the tools' parameter settings:}~We mitigated the threats to
 validity due to parameter settings of the clone detection tools and the clone
-merging technique by performing a comparison of different tools' parameter
-settings.
+merging technique by exploring different tools' parameter values.
 
-\textbf{3. Extended analysis of online code clones:}~We performed more analyses
+\textbf{3. Extended analysis of online code clones:}~We performed an extended analyses
 on the 2,289 online code clones and 100 outdated code snippets. For example,
@@
 overall discussion to include (1) a discussion of toxicity of outdated and
-license-incompatible clones on Stack Overflow, and (2) more detailed discussion
+license-incompatible clones on Stack Overflow and their implications, and (2) more detailed discussion
 of how to implement the tools or approaches proposed in the preventive and
-detective measures.
+detective measures, and (3) a suggestion for automation of code cloning direction detection.
 
@@
 \begin{enumerate}
-	\item We understand the concern of finding real evidence to support that code snippets on Stack Overflow do appear in software projects.
-Hence, we have performed a study of code clone detection between our 100 reported outdated code snippets on Stack Overflow and 131,703 GitHub projects ranging from 29,465 stars to 1 star.
+	\item We understand the concern of finding real evidence to support the claim that code snippets on Stack Overflow do appear in open- or closed-source software projects.
+Hence, we have performed a study of code clone detection between our 100 reported outdated code snippets on Stack Overflow and 131,703 GitHub projects.
 We selected SourcererCC with 80\% similarity for this experiment because it could scale to a large-scale data set, while Simian could not.
 We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them.
-As shown in the table below, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
+As shown in Table~\ref{tab:outdated_github} below, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
 For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).
@@
 		\centering
-%		\caption{Clones of the 100 Stack Overflow outdated code snippets in 131,703 GitHub projects}
-		\label{tab:outdated_github}
 		\begin{tabular}{lr}
@@
 		\end{tabular}
+		\label{tab:outdated_github}
+		\caption{Clones of the 100 Stack Overflow outdated code snippets in 131,703 GitHub projects}
 	\end{table}
@@
 Lastly, the remaining 13 cloned snippets did not have any hints or evidence of copying.
+	Twelve of them were toxic because they were the old versions that still contained bugs.
 
@@
 It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.
-	Nevertheless, we decided to report the developers of the two projects regarding the issue.
-We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers of the projects by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop.
+	Nevertheless, we reported the developers of the two projects regarding the issue.
+We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop.
 The issue has been fixed in deeplearning4j.
-The developers of deeplearning4j agreed that the method was problematic and they decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base.
+The developers of deeplearning4j agreed that the method was problematic and decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base.
 On the other hand, the bug report in Apache Hive is still unfixed.
@@
 	\item The same study has been done for another type of toxic code snippets on Stack Overflow, license-incompatible code snippets. 
-We detected clones between the 214 code snippets without their original license (86 QS, 78 EX and 50 UD)  and 130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
-	Then, we used the Ninka tool to automatically identify software license from the 7,207 code snippets.
-	Opposite to the outdated clones, we discovered many more clones of 7,207 candidate pairs. There were 90 pairs from 10 Qualitas projects on GitHub and 7,117 pairs from 
-	2,427 other projects. From the Table \ref{tab:license_github} shown below, the clones were found from highly-starred projects (29,465 to 10 stars) to 1-star projects.
+	We detected clones between the 214
+	code snippets without their original license (86 QS, 78 EX and 50 UD)  and
+	130,703 GitHub projects using SourcererCC with 80\% similarity threshold. 
+	Opposite to the outdated clones, we discovered many more clones
+	of 7,207 candidate pairs.
+	Then, we used the Ninka tool to automatically identify software license from the 7,207
+	code snippets.  There were 90 pairs from 10 Qualitas projects on
+	GitHub and 7,117 pairs from 2,427 other projects. From
+	Table \ref{tab:license_github} below, the clones were found from highly-starred
+	projects (29,465 to 10 stars) to 1-star projects.
+	We found 12 code snippets with attributions to Stack Overflow questions/answers and
+	6 of them were the answers we found as clones from Qualitas or external sources.
+	Five code snippets did not have license while the originals had Apache-2, GPLv2,
+	or EPLv1 license. One snippets had AGPLv3 license while the original had Apache-2 license.
+	Only 995 code snippets in GitHub projects that have the same license
+	as the originals in Qualitas.
 
@@
 		\centering
-		\label{tab:license_github}
 		\begin{tabular}{l|rr|rrr}
@@
 		\end{tabular}
+		\label{tab:license_github}
 		\caption{Clones of the 214 Stack Overflow missing-license code snippets in 131,703 GitHub projects}
@@
 Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
-	We also updated the Overall Discussion section to reflect the findings that (1) there is only a small number of toxic code snippets from outdated code that are found in GitHub projects, (2) there is a large number of toxic code snippets from missing license that are found in GitHub projects.
+	We also updated the Overall Discussion section to reflect the findings that (1) there is only a small number of toxic code snippets from outdated code that are found in GitHub projects, (2) there is a large number of toxic code snippets caused by missing license that are found in GitHub projects.
 %Moreover, the direction of copying is also unclear.
@@
 We surveyed 87 Stack Overflow visitors (visit the site and reuse code from Stack Overflow at least once) via five channels: social media post (Facebook),
-\textsf{blognone.com}, a popular technology news and media community in Thailand, the University of Molise in Italy where the third author works, \texttt{comp.lang.java.programmer} group and the Software Engineering
+\textsf{blognone.com}, a popular IT community and discussion forum in Thailand, the University of Molise in Italy where the third author works, \texttt{comp.lang.java.programmer} group and the Software Engineering
 Facebook page.
@@
 Although we found some harmful outdated clones, we could not find evidence that they are widely reused in open source projects on GitHub.
-Thus, outdated code snippets may not be so harmful to reuse.
+Therefore, the damage is not high since there is only a few outdated code snippets that are harmful for reuse.
 On the other hand, the problem of license incompatibility caused by missing original license in Stack Overflow code snippets can cause more damage than outdated code.
-Different legal system and different interpretation of fair-use concept and de minimis (i.e.~the minimal lines of code allowed to be copied without violating copyright) in each country can result in a legal case in one country becoming illegal in another country.
+Different legal system and different interpretation of fair-use concept and de minimis (i.e.~the minimal lines of code allowed to be copied without violating copyright) in each country can make a reuse of these code snippets becoming illegal.
 
-	\item We performed a study of two open source software auditing
+	\item We improved the Actionable Items to be more precise about the mechanics on how to automate the process of finding online code clones, detecting outdated code, and finding license-incompatible code snippets.
+
+	\item To address your point about auditing platforms/services, 
+	we performed a study of two open source software auditing
 	platforms/services:~BlackDuck
@@
 	their product does not mention checking of reused source code from Stack
-	Overflow. So, our proposed service, which can offer more precise licensing
+	Overflow. So, our proposed preventive measure, which can offer more precise licensing
 	information of Stack Overflow code snippets, will be useful as an add-on license
 	check for code copying from Stack Overflow. We include this in the Overall Discussion.
-
-	\item We improved the Actionable Items to be more precise about the mechanics on how to automate the process of finding online code clones, detecting outdated code, and finding license-incompatible code snippets.
 \end{enumerate}
@@
 That is a fair point and we would like to analyse the statistics as you suggested. 
-For (a), the number of views
+To answer your question in (a), the number of views
 is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
@@
 We checked and found that the latest available Stack Overflow dump already contains different data than the one we used in our study since it is now more than 2 years newer, and will result in incorrect statistics and inconsistent results.
-For (c), that is a really interesting idea. However, it is out of the scope of this study and would involve an extensive analysis of the data so we plan to do it in the future work.
+For (c), that is a really interesting idea. However, it is out of the scope of this study and would involve an extensive analysis of the data so we may investigate it in the future work.
 
@@
 Since they are confusing as you pointed out, we decided to remove them from the table and only discuss the numbers in the text.
-	\item That is a good idea. We included this discussion in the future work.
+	\item This is actually a great insight!
+We expanded the idea further and came up with a suggestion for an automated technique to facilitate human investigator on finding provenance and included it in a section called Automated cloning direction detection in the Overall Discussion.
 	\item Thanks. This has been fixed.
@@
 cloned from open source software or online sources can become toxic when they
-are (1)~outdated or (2)~violating their original software
-license. Outdated code snippets
-can be harmful since they are not up-to-date with their originals and may
+are (1)~outdated, (2)~violating their original software
+license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
+We chose to study toxic code snippets caused by outdated code and license-violating code snippets in
+this study as the two problems are still under explored compared to code smells~\citep{Tufano2015} or vulnerabilities~\citep{Acar2016,Fischer2017}.
+Outdated code snippets can be harmful since they are not up-to-date with their originals and may
 contain defects. Code snippets from open source projects usually fall under a
@@
 Ninety-nine out of the one hundred outdated code were still marked as accepted answers.
-This discussion of the findings is added to the the RQ4 \FIXME{do it}.
+This discussion of the findings is added to the the RQ4.
 
@@
 We have performed the check as you suggested by checking the commit message of each change that make the code outdated.
-The findings are discussed below and are included in the RQ4 \FIXME{do it}.
+The findings are discussed below and are included in the RQ4.
 
@@
 We calculated the clone ages by counting the number of month difference from the dates of each Qualitas project to the date the answers were posted on Stack Overflow.
-We drew a boxplot as you suggested and included the discussion of the statistics in RQ4.
+
+\begin{figure}[H]
+	\centering
+	\includegraphics[width=0.7\linewidth]{../boxplot_clone_age}
+	\caption{Age of QS cloned snippets}
+	\label{fig:boxplotcloneage}
+\end{figure}
+
+We drew a boxplot as you suggested (shown above) and included the discussion of the statistics in RQ4.
 We found that the minimum, maximum, median, and average clone ages were 0, 64, 26.5 and 26 months respectively.
-%(also summarised in the table below).
-
-%\begin{table}[H]
-%	\centering
-%\begin{tabular}{lrrrrr}
-%	\toprule
-%	\multirow{2}{*}{Clone pattern} & \multirow{2}{*}{Amount} & \multicolumn{4}{c}{Age of clones (months)} \\ \cmidrule{3-6}
-%	& & Min & Max & Avg. & Median \\
-%	\midrule
-%	QS & 153 & 0 & 64 & 26.5 & 26.0 \\
-%	\bottomrule
-%\end{tabular}
-%\end{table}
-
-From the data, we observed that, on average, it took around 2 years for the clones from Qualitas projects to appear on Stack Overflow answers.
+We observed that, on average, it took around 2 years for the clones from Qualitas projects to appear on Stack Overflow answers.
 Some of the clones appeared on Stack Overflow almost at the same time as the original, while the oldest clones took around 5 years.

### 2018-05-18 cloverflow-tse/cloverflow.tex
Revised until 2.2.1.

@@
 larger and no longer confined to a local repository.
-Although this activity of online code cloning is well-known, there is only a few
-empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
-the on finding the origins of the clones.
-We tackle this challenge of establishing existence of online code clones and
-investigate how they occur in this study.
 
@@
 there is also a downside caused by low quality, defective, and harmful code
-snippets that are reused without an awareness by millions of users.
+snippets that are reused without an awareness by millions of users~\cite{Zhang2018,Acar2016,Fischer2017}.
 
@@
 
-Using the same analogy, in this study, we are interested in mining Stack
-Overflow posts, detecting online code clones, and analysing the clones to reveal
+Although this activity of online code cloning is well-known, there is only a few
+empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
+on finding the origins of the clones on Q\&A websites.
+In this study, we tackle this challenge of establishing existence of online code 
+clones on Stack Overflow, investigate how they occur, and study the potential
+effects to software reusing them.
+%Using the same analogy, in this study, we are interested in 
+Therefore, we mine Stack Overflow posts, detected online code clones, and analysed the clones to reveal
 ``toxic code snippets''.
 
-``Toxic code snippets mean code snippets that, after incorporating into software,
-the cost of paying back the technical debt exceeds the value it generates in the long run.'' 
+Toxic code snippets mean code snippets that, after incorporating into software,
+the cost of paying back the technical debt exceeds the value it generates in the long run.
 Stack Overflow code snippets
@@
 license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
-We chose to study toxic code snippets caused by outdated code and license-violating code snippets in
-this study as the two problems are still under explored compared to code smells~\cite{Tufano2015} or vulnerabilities~\cite{Acar2016,Fischer2017}.
+In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
+as these two problems are still under explored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
 Outdated code snippets can be harmful since they are not up-to-date with their originals and may
@@
 there will be a new viewer of the first toxic snippet approximately every 5
-days compared to almost every day for the second one. A quick web search shows
-that the defective {\small{\texttt{humanReadableInt}}} method in the second
-example already appears in approximately 500 projects on GitHub. Considering the
-popularity of Stack Overflow, which has more than 50 million developers visiting
+days compared to almost every day for the second one. 
+%A quick web search shows
+%that the defective {\small{\texttt{humanReadableInt}}} method in the second
+%example already appears in approximately 500 projects on GitHub. 
+Considering the popularity of Stack Overflow, which has more than 50 million developers visiting
 each month\footnote{Data as of 21 August 2017 from:
@@
 On the other hand, 66\% of the
-Stack Overflow visitors experienced a problem from reusing Stack Overflow code snippets. 
+Stack Overflow visitors experienced problems from reusing Stack Overflow code snippets, including outdated code. 
 They are generally not aware of the CC BY-SA 3.0 license, and more than
@@
 	\item \textbf{A manual study of online code clones:} 
-	To confirm the results in the surveys, we used
+	To empirically confirm the findings from the surveys, we used
 	two clone detection tools to discover 2,289 similar code snippet pairs between
@@
 	\item \textbf{An investigation of toxic code snippets on Stack Overflow:} Our study shows that from
-	the 2,289 online clones, at least 330 have been copied from open source
+	the 2,289 online clones, at least 328 have been copied from open source
 	projects or external online sources to Stack Overflow, potentially violating
@@
 
-	\textit{2) How often are Stack Overflow
+	\textit{2) How often do Stack Overflow
 		visitors experience the outdated code and licensing conflicts when
-		they copy an answer from Stack Overflow?}
+		they reuse code in an answer from Stack Overflow?}
 
@@
 The answerer survey targeted the developers who were experienced Stack Overflow users
-and were highly active in answering questions. On the other hand, the visitor survey
+and were highly active in answering questions. The visitor survey
 targeted the developers who searched for solutions and reused code from Stack Overflow answers.
@@
 open-ended questions. 
-The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
 The first four questions are mandatory while the other 12
@@
 Overflow, and additional feedback. 
+The full survey can be found in our research note~\cite{Ragkhitwetsagul_RN2017}.
 We adopted non-probability convenient sampling to invite participants for this
@@
 Facebook page. 
-The survey was open for participation for 2 months, 
-from 25 July 2017 to 25 September 2017, before we collected and analysed
-the responses.
+The survey was open for participation for 2 months 
+from 25 July 2017 to 25 September 2017.
 
@@
 We designed the study in 6 phases as depicted in \Cref{fig:exp_framework} where
-we build different data sets to answer RQ2 -- RQ5.
+we build different data sets to answer RQ2 to RQ5.
 
@@
 
-Nevertheless, we have tried varying the minimum clone lines of 6, 10, and larger
-than 10 for the two clone detection tools. The minimum clone size of 10 lines is
-considered a standard setting for clone detection in large-scale data sets to
-avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
-setter methods) in the analysis or the manual investigation
-phase~\cite{Sajnani2016}. Choosing this size threshold larger than 10 could
-possibly remove some non-trivial clones from the analysis, i.e.~create more
-false negatives. On the other hand, decreasing the threshold to be lower than 10
-lines will result in a larger number of clone candidate pairs to look at and a
-higher chance of getting false positives. It is known that lowering the number
-of minimum clone lines is harmful to precision. Moreover, the large number of
-clone pairs will hinders the full manual validation of the clones and force us
-to rely on sampling of clone pairs. We performed an analysis to confirm this. We
-started by running the tools with minimum clone size of 10 lines and performing
-the manual clone confirmation. Then, we compared the number of true clone pairs
-detected if we increase or decrease the size.
-
-\begin{figure}[H] \centering
-	\includegraphics[width=0.8\linewidth]{boxplot_clone_size} 
-	\caption{Size of online code clones.} 
-	\label{fig:boxplotclonesize}
-\end{figure}
-
-Regarding increasing the minimum clone size to more than 10 lines (e.g. 15
-lines), the result is as shown in
-\Cref{fig:boxplotclonesize}. We found that the distribution of true clones; QS,
-SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines. Increasing
-the threshold to be higher than 10 would remove some of the trivial BP and IN
-clone pairs which are not interesting for this study. However, it will also
-remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.
-
-Regarding decreasing the minimum clone size to be less than 10 lines, we reran
-the two clone detection tools again using a minimum
-clone size of 6 lines, another well-accepted minimum clone size in clone
+Nevertheless, we investigated a crucial parameter setting for clone detection: the minimum clone size threshold.
+Choosing a large clone size threshold can reduce the number of false clones reported,
+while at the same time creates some false negatives, i.e.~missing some of the true clones.
+On the other hand, setting a low threshold results in a larger number of clone
+candidate pairs to look at and a higher chance of getting false positives.
+It is known that lowering the number of minimum clone lines is harmful to precision.
+Moreover, the large number of clone pairs will hinders the full manual
+validation of the clones and one needs to rely on sampling of clone pairs.
+We started our investigation by using a minimum clone
+size of 6 lines, a well-accepted minimum clone size in clone
 benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
-SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
-With this large amount of clone
-candidate pairs, it is not feasible to manually confirm all of the clones and we
-must rely on sampling. This will result in weaker findings and
-weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
-to keep the balance between the number of non-trivial clone pairs and the
-feasibility of manual clone investigation.
+SourcererCC reported 7,752 clone candidate pairs. We randomly sampled 382 pairs
+from the merged set of 74,148 clone pairs and the first author investigated them. This was
+a statistical significant sample with a 95\% confidence level and $\pm 5\%$ confidence interval.
+We found 322 trivial clone pairs including \texttt{equals}, \texttt{hashCode}, or getters/setters;
+26 non clone pairs, and 34 non-trivial clone pairs.
+We then increased the minimum clone size to 10 lines, another well-established 
+minimum clone size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from Simian and
+1,678 clone pairs from SourcererCC. We randomly sampled and manually checked the same amount of 382 pairs
+from the merged set of 2,289 clone pairs.
+We found 251 trivial clone pairs, 40 non-clone pairs, and 91 non-trivial clone pairs.
+
+The findings from the two samples show that selecting the minimum of 6 lines generated
+a large number of clones (74,148 pairs) with more trivial clone pairs, which we were not interesting for this study, 
+and fewer non-trivial pairs compared to the minimum of 10 lines.
+%To put it another way, lowering the number of clone lines is harmful to precision.
+Moreover, the amount of 2,289 clone pairs using minimum of 10 clone lines 
+was feasible for manual investigation in the next phase.
+Increasing the minimum clone size further will result in a smaller clone subset
+but may also remove some of the true clone pairs (generating false negatives).
+Thus, we selected the minimum clone size of 10 lines for both Simian and SourcererCC.
+
+%The minimum clone size of 10 lines is
+%considered a standard setting for clone detection in large-scale data sets to
+%avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
+%setter methods) in the analysis or the manual investigation phase~\cite{Sajnani2016}.  
+%We
+% performed an analysis to confirm this.
+%\begin{figure} 
+%	\centering
+%	\includegraphics[width=\linewidth]{boxplot_clone_size_combined} 
+%	\caption{Size of online code clones.} 
+%	\label{fig:boxplotclonesize}
+%\end{figure}
+
+%The result is as shown in
+%\Cref{fig:boxplotclonesize}. We found that the distribution of the manually
+%confirmed true clones 
+%mainly cover the size from about 10 to 20 lines. Increasing
+%the threshold to be higher than 10 would remove some of the
+%true clone pairs.
+%
+%Regarding decreasing the minimum clone size to be less than 10 lines, we reran
+%the two clone detection tools again using a minimum
+%clone size of 6 lines, another well-accepted minimum clone size in clone
+%benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
+%SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
+%With this large amount of clone
+%candidate pairs, it is not feasible to manually confirm all of the clones and we
+%must rely on sampling. This will result in weaker findings and
+%weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
+%to keep the balance between the number of non-trivial clone pairs and the
+%feasibility of manual clone investigation.
 %We made sure that they 
@@
 There were 338 (15\%) conflicts between 
-true and false clones (QS, SQ, EX, UD, BP, IN vs.~AC).
+true and false clones (QS, SQ, EX, UD, BP, IN vs.~NC).
 The investigators looked at each conflicting pair together and
@@
 
-		AC & Accidental similarity, false clones \\ 
+		NC & Not clones \\ 
 		\bottomrule 
@@
 six new cloning patterns. The seven patterns include QS, SQ, EX, UD, BP, IN, and
-AC as presented in \Cref{tab:classification_scheme}. Pattern QS
+NC as presented in \Cref{tab:classification_scheme}. Pattern QS
 (\textbf{Q}ualitas to \textbf{S}tack Overflow) represents clones that have
@@
 activities usually result in similar overriding methods. The last
-pattern, AC (\textbf{A}ccidental \textbf{C}lones), represents
-accidentally similar clone pairs. These are mainly false positive
+pattern, NC (\textbf{N}ot \textbf{C}lones), represents
+false clone pairs. These are mainly false positive
 clones from the clone detectors such as similar
@@
 code normalisation or false positive clones from the clone detection tools, we
-classify the pair into \textbf{AC}. If the two fragments are boiler-plate code,
+classify the pair into \textbf{NC}. If the two fragments are boiler-plate code,
 the pair is classified into \textbf{BP}. If they implement the same interface or
@@
 classified into \textbf{IN}. If the pair is not \textbf{BP}, \textbf{IN}, or
-\textbf{AC}, we start a detailed investigation. We check the corresponding Stack
+\textbf{NC}, we start a detailed investigation. We check the corresponding Stack
 Overflow post, read through it carefully and look for any evidence mentioning
@@
 than 60\% of their answers. This notification to the answerer can be done by
-posting comments for that answer on Stack Overflow. For example, the answerer of
+posting comments below the answer on Stack Overflow. For example, the answerer of
 the Stack Overflow question no.~10924648 posted a comment on his own answer
@@
 \vspace{0.25cm}
-\textit{Do Stack Overflow
-	visitors experience outdated code and check for licensing conflicts when
-	they copy and reuse answer from Stack Overflow?}
+\textit{How often do Stack Overflow
+	visitors experience the outdated code and licensing conflicts when
+	they reuse code in an answer from Stack Overflow?}
 \vspace{0.25cm}
@@
 Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
-as being accidental clones (AC), i.e.~false positives. After removing
+as being accidental clones (NC), i.e.~false positives. After removing
 them, the set still contains 2,076 true positive clone pairs between 443 Stack
@@
 		\toprule
-		Set & QS & SQ & EX & UD & BP & IN & AC & Total \\ 
+		Set & QS & SQ & EX & UD & BP & IN & NC & Total \\ 
 		\midrule
@@
 
-\textbf{AC: Accidental Clones.} There were 226 accidental clone
+\textbf{NC: Not Clones.} There were 226 non-clone
 pairs, 53 after consolidation. Mainly, they are false positive clones caused by code
 normalisation and false type-3 clones from SourcererCC. 
-Examples of the AC clone instances include {\small\texttt{finally}} or
+Examples of the NC clone instances include {\small\texttt{finally}} or
 {\small\texttt{try-catch}} clauses that were accidentally the same due
@@
 insight about toxicity of online code clones and two actionable items
-we are proposing to the Stack Overflow community.
+we are proposing to the software engineering research and the Stack Overflow community.
 
@@
 country. For example, Germany legal system does not have a concept of fair use
-or the number of minimum lines of code to be consider trivial, i.e.~de minimis,
-is also different from case to case or from country to country.
+or the number of minimum lines of code to be consider copying, i.e.~de minimis,
+is also differently interpreted from case to case or from country to country.
 

### 2018-05-18 cloverflow-tse/cover_letter/cover_letter.tex
Revised until 2.2.1.

@@
 We chose to study toxic code snippets caused by outdated code and license-violating code snippets in
-this study as the two problems are still under explored compared to code smells~\citep{Tufano2015} or vulnerabilities~\citep{Acar2016,Fischer2017}.
+this study since these two problems are still under explored compared to code smells~\citep{Tufano2015} or vulnerabilities~\citep{Acar2016,Fischer2017}.
 Outdated code snippets can be harmful since they are not up-to-date with their originals and may
@@
 Since RQ5 actually supports the motivation of our experiment by showing that code copying from software projects to Stack Overflow actually occurs and showing that some of the answerers are not aware of outdated code and software license incompatibility.
-We moved them to RQ1 instead and reorganised the paper to discuss the survey results as a support for our experiment of online code clone detection and toxic code snippet identification.
-The findings in RQ2--5 will support the survey results by showing that the issues actually occur on Stack Overflow.
+We moved them to RQ1 instead and reorganised the paper to discuss the survey results as an incentive for our experiment of online code clone detection and toxic code snippet identification.
+The findings in RQ2--5 will confirm the survey results by showing that the issues actually occur on Stack Overflow.
 
@@
 
-\begin{table}
+\begin{table}[H]
 	\centering
@@
 		\toprule
-		Reason & Detail & Amount \\
+		Intent & Detail & Amount \\
 		\midrule
-		Enhancement & Add features or update existing features & 64 \\
-		Deprecation & Delete dead or deprecated code & 15 \\
+		Enhancement & Add or update existing features & 64 \\
+		Deprecation & Delete dead/deprecated code & 15 \\
 		Bug & Fix bugs & 10 \\
 		Refactoring & Refactor code for better design & 6 \\
-		Coding style & Update code to conform to a style guideline & 3 \\
-		Data change & Change code due to changing of the data & 2 \\
+		Coding style & Update to a new style guideline & 3 \\
+		Data change & Changes in data format & 2 \\
 		\bottomrule
 	\end{tabular}
-	\caption{Reasons of code changes in 100 outdated code snippets}
+	\label{tab:intent_outdated}
+	\caption{Intents of code changes in 100 outdated code snippets}
 \end{table}
 
-The majority of the changes are due to code enhancement.
-There are 64 changes for software enhancement, such as adding a new features or improving existing code to support a newer version of the language or APIs.
-Fifteen changes are for removal of dead or deprecated code such as SQL connection code in Hibernate.
+The majority, 64, of the changes are due to code enhancement, such as adding a new features or improving existing code to support a newer version of the language or APIs.
+Fifteen changes are for removal of dead or deprecated code such as SQL connection code example in Hibernate.
 Ten changes are made to fix bugs in the software (e.g.~array reference, race condition, wrong field access, \texttt{NullPointerException}).
@@
 Fortunately, we could use this opportunity to study the evolution of the toxic code snippets on Stack Overflow.
-We manually investigated the outdated and license incompatible code snippets that we discovered to see if they are still the same or not.
+We manually investigated the outdated and license incompatible code snippets that we discovered to see whether they are still the same.
 The check was performed on 6 May 2018, approximately 2 years after the snapshot was created.
@@
 
-We selected the Bellon's ok-match threshold of 0.7 because it is a standard value in clone benchmarking \citep{Bellon2007} and also used in other study of clones, e.g.~\cite{Sajnani2016}.
+We selected the Bellon's ok-match threshold of 0.7 because it is a standard value in clone benchmarking \citep{Bellon2007} and also used in other studies of clones, e.g.~\cite{Sajnani2016}.
 Nevertheless, we agree that varying the threshold ($t$) value is beneficial to the validity of the findings so we did an analysis by choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
-As shown in the our paper, by setting $t=0.7$ according to Bellon's study, we found 97 ok-match pairs reported.
-On the other hand, setting $t$ to 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
-an analysis by choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
 As shown in the our paper, by setting $t=0.7$ according to Bellon's study, we found 97 ok-match pairs reported.
@@
 All the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a subset of $t=0.5$.
-However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates in the final merged clone set.
+However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates of the same clone pairs (that were supposed to be merged) in the final merged clone set.
 
@@
 Thus, we decided to select the $t$ value at 0.5.
-This reduces the number of merged clone pairs to 2,290 pairs.
-All other numbers which derive from this merged clone pairs have been updated accordingly.
-Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually checked all the 111 reported pairs.
-We found one false positive pair and 110 true positive pairs.
-By raising the $t$ to 0.3 and 0.5, we got rid of the false positive pair and still retained all the 110 true positive pairs.
-All the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a subset of $t=0.5$.
-However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates in the final merged clone set.
-
-With this analysis, we can see that setting the threshold $t$ to 0.1 is too relaxed and results in having false positive ok-match pairs, while setting the $t$ to 0.7 or 0.9 is too strict and generates some false negative pairs.
-Thus, we decided to select the $t$ value at 0.5.
-This reduces the number of merged clone pairs to 2,290 pairs.
+This reduces the number of merged clone pairs to 2,289 pairs.
 All other numbers which derive from this merged clone pairs have been updated accordingly.
@@
 
-For the QS clone pairs, we \textbf{manually confirmed with evidence} that the Stack Overflow code snippets were actually copied from Qualitas projects.
+For the QS clone pairs, as explained in Section 2.2.3 (The online cloning classification patterns) and Section 3.3 (RQ3: Patterns of Online Code Cloning), we \textbf{manually confirmed with evidence} that the Stack Overflow code snippets were actually copied from Qualitas projects.
 This was done by the two authors reading the Stack Overflow answers containing the QS code snippets and looked for evidence such as explanation in the text or the code comments and made their decision.
@@
 %\textsf{jstock} was committed to GitHub on the next day of March 31, 2009.
-In case of a doubt or not enough evidence, we always categorised the clone pairs into UD (unknown direction) instead.
+In case of a doubt or not enough cloning evidence and the clone pairs did not fit into EX, BP and IN, we always categorised the clone pairs into UD (unknown direction) instead.
 
@@
 You are correct regarding the BP clone pairs.
-They can really come from anywhere (we did find that some of the BP clone pairs were auto-generated code by NetBeans) and that is why we did not draw any conclusion about them.
+They can really come from anywhere (we did find that some of the BP clone pairs were auto-generated code by NetBeans).
+Therefore, we did not draw any conclusion about them in the paper.
 Moreover, thank you for pointing out the inappropriate naming for AC. We now renamed them from AC to NC (i.e.~Not Clones).
@@
 Moroever, another user posted a comment on the answer of the post no.~801935 that the code snippet is not of high quality and suggested an alternative in another post.
-We extended this discussion in Section 3.1.1 (RQ1).
+We extended this explanation in Section 3.1.1 (RQ1).
 
@@
 We only chose the QS clone pairs since we could manually confirmed the direction of cloning.
-Moreover, we could searched for the date that the cloned version of the QS project appeared, which was not possible for UD, EX, BP, and IN clone pairs.
+Moreover, we knew the date that the original version of the QS clones appeared in Qualitas projects (we used the version release date), which was not possible for UD, EX, BP, and IN clone pairs.
 We calculated the clone ages by counting the number of month difference from the dates of each Qualitas project to the date the answers were posted on Stack Overflow.
@@
 While the authors went through a lengthy and detailed study of code clones published on StackOverflow and the survey of StackOverflow contributors, the paper lacks really a take home message.
-At the end there is no real evidence that either code clones are really toxic or bad (are they actually causing problems ?
+At the end there is no real evidence that either code clones are really toxic or bad (are they actually causing problems?
 due to the use of clones.
@@
 
-First, from the answer to Reviewer 2, we analysed the intent behind the changes that made the code outdated and found that only 10 and 15 out of 100 cases were bug fixing and dead code.
+First, from the answer to Reviewer 2, we analysed the intent behind the changes that made the code outdated and found that only 10 out of 100 cases were bug fixes.
 Besides that, the code were outdated because of evolution in the software (adding or enhancing features, refactoring, changing coding style, and data change).
+Thus, outdated code can sometimes become toxic, but not always.
 
@@
 To summarise, we empirically show from the surveys and the clone detection experiment that online code clones occur on Stack Overflow and the clones may become toxic due to outdated code and software license incompatibility.
-Nevertheless, we found only a small amount of toxic outdated code snippets in open source projects on GitHub.
-Besides 12 buggy and outdated code snippets found in 12 projects, the rest were non-harmful clones of the outdated code.
+For outdated code, we found only a small amount of clones.
 Although other studies show that Stack Overflow code snippets may contain security vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we found in this study that the damage caused by reusing outdated code on Stack Overflow is not high.
-
 On the other hand, the missing of licensing statement of online code clones on Stack Overflow can be more harmful.

### 2018-05-19 cloverflow-tse/cloverflow.tex
Revised until Section 3.4.

@@
 
-Nevertheless, we investigated a crucial parameter setting for clone detection: the minimum clone size threshold.
-Choosing a large clone size threshold can reduce the number of false clones reported,
-while at the same time creates some false negatives, i.e.~missing some of the true clones.
-On the other hand, setting a low threshold results in a larger number of clone
-candidate pairs to look at and a higher chance of getting false positives.
-It is known that lowering the number of minimum clone lines is harmful to precision.
-Moreover, the large number of clone pairs will hinders the full manual
-validation of the clones and one needs to rely on sampling of clone pairs.
-We started our investigation by using a minimum clone
-size of 6 lines, a well-accepted minimum clone size in clone
-benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
-SourcererCC reported 7,752 clone candidate pairs. We randomly sampled 382 pairs
-from the merged set of 74,148 clone pairs and the first author investigated them. This was
-a statistical significant sample with a 95\% confidence level and $\pm 5\%$ confidence interval.
-We found 322 trivial clone pairs including \texttt{equals}, \texttt{hashCode}, or getters/setters;
-26 non clone pairs, and 34 non-trivial clone pairs.
-We then increased the minimum clone size to 10 lines, another well-established 
-minimum clone size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from Simian and
-1,678 clone pairs from SourcererCC. We randomly sampled and manually checked the same amount of 382 pairs
-from the merged set of 2,289 clone pairs.
-We found 251 trivial clone pairs, 40 non-clone pairs, and 91 non-trivial clone pairs.
-
-The findings from the two samples show that selecting the minimum of 6 lines generated
-a large number of clones (74,148 pairs) with more trivial clone pairs, which we were not interesting for this study, 
-and fewer non-trivial pairs compared to the minimum of 10 lines.
-%To put it another way, lowering the number of clone lines is harmful to precision.
-Moreover, the amount of 2,289 clone pairs using minimum of 10 clone lines 
-was feasible for manual investigation in the next phase.
-Increasing the minimum clone size further will result in a smaller clone subset
-but may also remove some of the true clone pairs (generating false negatives).
-Thus, we selected the minimum clone size of 10 lines for both Simian and SourcererCC.
-
+Nevertheless, we investigated a crucial parameter setting for clone detection: 
+the minimum clone size threshold.
+Choosing a large threshold value can reduce the number of trivial clones
+(e.g. \texttt{equals}, \texttt{hashCode}, or getter and setter methods) and
+false clones in the analysis or the manual investigation
+phase~\cite{Sajnani2016}, while at the same time may create some false negatives,
+i.e.~increasing precision. On the other hand, setting a low threshold
+results in a larger number of clone candidate pairs to look at, i.e.~increasing recall, 
+and a higher chance of getting false positives. 
+%It is known that lowering the threshold value 
+%is harmful to precision. 
+Moreover, the large number of clone
+pairs will hinders the full manual validation of the clones.
+% and one needs to
+%rely on sampling of clone pairs. 
+Three threshold values, six, ten, and fifteen lines, were chosen for our
+investigation. We started our investigation by using a threshold value of six
+lines, a well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}.
+Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
+clone candidate pairs. We randomly sampled 382 pairs from the two sets for
+manual check. This sample amount was a statistical significant sample with a
+95\% confidence level and $\pm 5\%$ confidence interval. The first author
+investigated the sampled clone pairs and classified them into three groups:
+non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
+setter methods), and non-trivial clones. The manual check found 26 non-clone
+pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we increased the
+threshold to ten lines, another well-established minimum clone size for
+large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
+Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and manually
+checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
+clone pairs and 102 non-trivial clone pairs. Then, we increased the threshold
+further to fifteen lines and retrieved 196 clone pairs from Simian and 1,230
+clone pairs from SourcererCC. The manual check of the 382 randomly sampled pairs
+reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial clone
+pairs.
+
+The findings from the three threshold values show that selecting the minimum clone size 
+of ten lines was preferred over six and fifteen lines. First, it generated 
+a fewer number of clone pairs than using six lines, which made the manual clone
+investigation feasible. Second, it preserved the highest number of non-trivial clone
+pairs.
+%
 %The minimum clone size of 10 lines is
@@
 %\end{figure}
-
+%
 %The result is as shown in
@@
 %and NiCad with the EvaClone configuration ($N_E$).
-
+%
 %We encountered NiCad failures with a few Qualitas projects.~$N_D$
@@
 %paths, and will be fixed in the next NiCad releases.
-
-The number of online clone pairs reported % by running Simian and NiCad
+%
+The number of online clone pairs reported using the minimum clone size of 10 lines
 are presented in \Cref{tab:orig_stats}. Simian reports 721 clone
 pairs while SourcererCC reports 1,678 clone pairs. 
-SourcererCC reports more clones due to its capability of detecting
-clones of type-1 to type-3 while Simian only detects type-1 clones.
+%SourcererCC reports more clones due to its capability of detecting
+%clones of type-1 to type-3 while Simian only detects type-1 clones.
 The average clone size reported by Simian is
@@
 relaxed and results in having false positive ok-match pairs, while setting the
-$t$ to 0.7 or 0.9 is too strict and generates some false negative pairs. Thus,
+$t$ to 0.7 or 0.9 is too strict. Thus,
 we decided to select the $t$ value at 0.5.
@@
 Simian and 1,678 clone pairs from SourcererCC into a single set of 2,289 online
-clone pairs. There are only 110 common clone pairs between the two clone sets 
+clone pairs. There are 110 common clone pairs between the two clone sets 
 as depicted in~\Cref{fig:clonemerging}.  The low number of common
@@
 We used the 2,289 merged clone pairs for
-manual validation and classification.
+manual validation and online clone classification.
 The validation and classification of the pairs was done at the same time. 
@@
 \vspace{0.25cm}
-\textit{How often are Stack Overflow
+\textit{RQ1.1 How often are Stack Overflow
 	answerers aware of the outdated code and 
@@
 the Stack Overflow question no.~10924648 posted a comment on his own answer
-saying that the answer is specifically for Spring 3.1. Moroever, another user
+saying that the answer is specifically for Spring 3.1 and another user
 posted a comment on the answer of the post no.~801935 that the code snippet is
 not of high quality and suggested an alternative in another post.
+The low percentage of outdated code notifications
+reflect the experience of high reputation answerers who accumulate the reputation for a
+long time. Due to the voting mechanism of Stack Overflow, high reputation users
+usually provide high quality answers to earn up votes from other users. They are
+careful when posting code snippets in the answer to avoid problems and, vice versa, 
+getting down votes. It would be interesting to compare the findings to
+Stack Overflow answerers who are newer and have lower reputation. However, we
+leave it to future work.
 
@@
 their outdated code.
-
-The responses from the answerers support our findings of outdated online code
-clones in RQ3. The low percentage of outdated code notifications
-reflect the experience of high reputation answerers who accumulate the reputation for a
-long time. Due to the voting mechanism of Stack Overflow, high reputation users
-usually provide high quality answers to earn up votes from other users. They are
-careful when posting code snippets in the answer to avoid problems and, vice versa, 
-getting down votes. It would be interesting to compare the findings to
-Stack Overflow answerers who are newer and have lower reputation. However, we
-leave it to future work.
+%
+%The responses from the answerers support our findings of outdated online code
+%clones in RQ3.
 
@@
 
-Similar to outdated code, the responses from the answerers support our findings
-of licensing conflicts in online code clones in RQ4 and possibly explain why most of
-the clones copied from open source projects and external sources do not include
-their original software license.
+%Similar to outdated code, the responses from the answerers support our findings
+%of licensing conflicts in online code clones in RQ4 and possibly explain why most of
+%the clones copied from open source projects and external sources do not include
+%their original software license.
 
 \begin{boxquote}
-	To answer RQ 1.1, regarding outdated code, although most of the Stack Overflow answerers are aware that their code
-	can be outdated, 51.5\% of the answerers were very rarely notified and 35.5\% have never been notified of
-	outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.
-
-	For licensing conflicts, 124 answerers out of 200 (62\%) are aware of Stack Overflow's
-	CC BY-SA 3.0 license applied to code snippets in questions and answers. However,
-	only 3 answerers explicitly include software license in their answers. Some 
-	answerers choose to include the license in their profile page instead. 69\% of the
+	To answer RQ 1.1, although most of the Stack Overflow answerers are aware that their code
+	can be outdated, half of the answerers were very rarely notified of
+	outdated code in the answers. After being notified, some of them rarely or never fix the outdated code.
+	More than half of the answerers are aware of Stack Overflow's
+	CC BY-SA 3.0 license. Only 3 answerers explicitly include software license in their answers
+	while some of them choose to include the license in their profile page instead. More than half of the
 	answerers never check for licensing conflicts between their copied code snippets
@@
 can be found easily from search engine, solve similar problems to their
-problems, provide helpful context, and offer voting and accepted answers.
+problems, provide helpful context, and offer voting mechanism and accepted answers.
 
 \vspace{0.25cm}
-\textit{How often do Stack Overflow
+\textit{RQ1.2 How often do Stack Overflow
 	visitors experience the outdated code and licensing conflicts when
@@
 Overflow code snippets and their projects. Interestingly, 9\% of the
-participants encountered legal issues. Unfortunately, due to the anonymity of
+participants encountered legal issues. Due to the anonymity of
 the survey, we could not investigate further regarding the legal issues that the
 participants faced from using Stack Overflow code snippets.
-
-The visitors survey confirms the findings from the previous studies that Stack
-Overflow code snippets can be problematic~\cite{Zhang2018,Acar2016,An2017,Fischer2017}. Sixty-six
-percent of the visitors experienced a problem from reusing Stack Overflow code
-snippets ranging from incorrect solutions, outdated solutions, mismatched
-solutions, to buggy code. Although they are aware of the problems, half of them
-(56\%) never reports back to the Stack Overflow discussions. On the other hand,
-the visitors rarely give attributions to Stack Overflow when they reuse code
-snippets from the website, similar to the findings reported
-by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
-license, and more than half of them never check for license compatibility when
-reusing Stack Overflow code snippets. 
-Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
-check if the code snippet originated from a different source (e.g. an open source project) 
-and if they had an incompatible license to their projects.
-Moreover, we also found that 9\% of the participants
-encountered legal issues by copying code from Stack Overflow. To the best of our
+To the best of our
 knowledge, a study of legal problems from reusing Stack Overflow code snippets
 has never been done before and will be our future work.
+
+%The visitors survey confirms the findings from the previous studies that Stack
+%Overflow code snippets can be problematic~\cite{Zhang2018,Acar2016,An2017,Fischer2017}. 
+%Sixty-six
+%percent of the visitors experienced a problem from reusing Stack Overflow code
+%snippets ranging from incorrect solutions, outdated solutions, mismatched
+%solutions, to buggy code. Although they are aware of the problems, half of them
+%(56\%) never reports back to the Stack Overflow discussions. On the other hand,
+%the visitors rarely give attributions to Stack Overflow when they reuse code
+%snippets from the website, similar to the findings reported
+%by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
+%license, and more than half of them never check for license compatibility when
+%reusing Stack Overflow code snippets. 
+%Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
+%check if the code snippet originated from a different source (e.g. an open source project) 
+%and if they had an incompatible license to their projects.
+%Moreover, we also found that 9\% of the participants
+%encountered legal issues by copying code from Stack Overflow.
 
@@
 projects. For the cloned Stack Overflow snippets, the
-average ratio of cloned code is 53.10\% (i.e.\ the number of cloned
+average ratio of cloned code is 53.28\% (i.e.\ the number of cloned
 lines of the cloned Stack Overflow snippet).
@@
 as being accidental clones (NC), i.e.~false positives. After removing
-them, the set still contains 2,076 true positive clone pairs between 443 Stack
+them, the set still contains 2,063 true positive clone pairs between 443 Stack
 Overflow snippets and 59 Qualitas projects. The average cloned ratio for the
-true positive clone pairs is 53.89\%.
+true positive clone pairs is 54.09\%.
 
 \begin{boxquote}
-	To answer RQ2, we found 2,076 manually confirmed clone pairs between 443 Stack Overflow code snippets
+	To answer RQ2, we found 2,063 manually confirmed clone pairs between 443 Stack Overflow code snippets
 	and 59 Qualitas proejcts. 
@@
 
-\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 248 online clone
+\textbf{QS: Qualitas $\rightarrow$ Stack Overflow.} We found 247 online clone
 pairs with evidence of cloning from Qualitas projects to Stack Overflow.
@@
 Overflow snippet, starting line, and ending line into a single clone pair. We
-finally obtained 154 QS pairs (\Cref{tab:classification_good_o}) having unique Stack Overflow code snippets and
+finally obtained 153 QS pairs (\Cref{tab:classification_good_o}) having unique Stack Overflow code snippets and
 associated with 23 Qualitas projects listed in \Cref{tab:qs_qualitas_projects}.
-The most cloned project is \textsf{hibernate} with 24
+The most cloned project is \textsf{hibernate} with 23
 clone pairs, followed by \textsf{eclipse} (21 pairs), \textsf{jung2} (19 pairs),
@@
 \textbf{BP: Boiler-Plate.} There were a large amount of boiler-plate clone pairs
-found in this study. We observed 1,505 such clone pairs and 217 after
+found in this study. We observed 1,495 such clone pairs and 216 after
 consolidation. The BP clone pairs account for 65\% of all clone pairs we
@@
 \begin{boxquote}
-To answer RQ3, we found 154 pairs with
+To answer RQ3, we found 153 pairs with
 strong evidences to be cloned from 23 Qualitas projects to Stack Overflow, 1 pair
 was cloned from Stack Overflow to Qualitas, and
-111 pairs were found to be cloned to Stack Overflow from external
+109 pairs were found to be cloned to Stack Overflow from external
 sources. However, the largest amount of the clone pairs
 between Stack Overflow and Qualitas projects are \linebreak boiler-plate code
-(217), followed by 65 clone pairs with no evidence that the code has actually been copied,
-and 16 pairs of clones due to implementing the same interface or inheriting the same class.
+(216), followed by 65 clone pairs with no evidence that the code has actually been copied,
+and 9 pairs of clones due to implementing the same interface or inheriting the same class.
 \end{boxquote}
@@
 though commits and git blame information. The six code modification
-types found in the 101 outdated online clone pairs are summarised in
+types found in the 100 outdated online clone pairs are summarised in
 \Cref{tab:mod_types}. They include statement addition, statement modification,
@@
 Enhancement are the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
-by code deprecation (15\%). There were 10 outdated code snippets (10\%) due to bug fixing.
+by code deprecation (15\%). There were 10 outdated code snippets (10\%) caused by bug fixing.
 The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 

### 2018-05-19 cloverflow-tse/cover_letter/cover_letter.tex
Revised until Section 3.4.

@@
 
-That is a fair point. The reason we chose the clone size of at least 10 lines is as follows.
+That is a fair point.
+The reason we chose the clone size of at least 10 lines is because it is considered a standard setting for clone detection in large-scale data sets to avoid trivial clones (e.g.
+\texttt{equals}, \texttt{hashCode}, or getter and setter methods) in the analysis or the manual investigation phase~\citep{Sajnani2016}.
 
-The minimum clone size of 10 lines is considered a standard setting for clone detection in large-scale data sets to avoid trivial clones (e.g.
-\texttt{equals}, \texttt{hashCode}, or getter and setter methods) in the analysis or the manual investigation phase~\citep{Sajnani2016}.
-Choosing this size threshold larger than 10 could possibly remove some non-trivial clones from the analysis, i.e.~create more false negatives.
-On the other hand, decreasing the threshold to be lower than 10 lines will result in a larger number of clone candidate pairs to look at and a higher chance of getting false positives.
+%Choosing this size threshold larger than 10 could possibly remove some non-trivial clones from the analysis, i.e.~create more false negatives.
+%On the other hand, decreasing the threshold to be lower than 10 lines will result in a larger number of clone candidate pairs to look at and a higher chance of getting false positives.
 Moreover, the large number of clone pairs will hinders the full manual validation of the clones and force us to rely on sampling of clone pairs.
 We performed a small analysis to confirm this.
-
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.5\linewidth]{../boxplot_clone_size}
-	\caption{Size of online code clones.}
-	\label{fig:boxplotclonesize}
-\end{figure}
-
-Regarding increasing the minimum clone size to more than 10 lines (e.g.
+%
+%\begin{figure}[H]
+%	\centering
+%	\includegraphics[width=0.5\linewidth]{../boxplot_clone_size}
+%	\caption{Size of online code clones.}
+%	\label{fig:boxplotclonesize}
+%\end{figure}
+%
+%Regarding increasing the minimum clone size to more than 10 lines (e.g.
 15 lines), we added an analysis of the clone size as shown in Figure \ref{fig:boxplotclonesize}.
@@
 However, it will also remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.
-
-Regarding decreasing the minimum clone size to be less than 10 lines, we reran the two clone detection tools (Simian and SourcererCC) again using a minimum clone size of 6 lines, another well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
+%
+%Regarding decreasing the minimum clone size to be less than 10 lines, we reran the two clone detection tools (Simian and SourcererCC) again using a minimum clone size of 6 lines, another well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
 Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs using Bellon's ok-match threshold $t=0.5$.
@@
 
-We have modified the paper to include this discussion in RQ2.
+To measure the impact of this minimum clone size threshold on the clone results, 
+we performed an investigation of three different threshold values: six, ten, and fifteen lines. 
+We started the investigation by using a minimum clone size of six lines, a
+well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}. Simian
+reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone
+candidate pairs. We randomly sampled 382 pairs from the two sets and the first
+author investigated them. This was a statistical significant sample with a 95\%
+confidence level and $\pm 5\%$ confidence interval. We found 26 non-clone pairs;
+322 trivial clone pairs including \texttt{equals}, \texttt{hashCode}, or
+getters/setters; and 34 non-trivial clone pairs. Next, we increased the minimum
+clone size to ten lines, another well-established minimum clone size for
+large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
+Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and manually
+checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
+clone pairs and 102 non-trivial clone pairs. Then, we increased the minimum
+clone size further to fifteen lines and retrieved 196 clone pairs from Simian
+and 1,230 clone pairs from SourcererCC. The manual check of the 382 randomly
+sampled pairs reveal zero non-clone pairs, 298 trivial clone pairs and 83
+non-trivial clone pairs.
+
+The findings from the three samples show that selecting the minimum of ten lines
+was a sweet spot and was preferred over six and fifteen lines. First, it generated 
+a fewer number of clone pairs than using six lines, which made the manual clone
+investigation feasible. Second, it preserved the highest number of non-trivial clone
+pairs.
+
+We have modified the paper to include this discussion at the end of Section 2.2.1.
 

### 2018-05-20 cloverflow-tse/cloverflow.tex
The complete draft of the cover letter and the TSE paper.

@@
 toxic code snippets, i.e.~they suffer from being outdated or violating the
-original software license. We present a study incorporating state-of-the-art
-tools and techniques to automatically extract and filter online clone pairs
-between 72,365 Java code snippets on Stack Overflow and 111 open source projects
-in the curated Qualitas corpus. We analysed 2,289 non-trivial online clone
-candidates. Our investigation revealed strong evidence that 154 clones have been
-copied from a Qualitas project to Stack Overflow. We found 101 of them (66\%) to
-be outdated and potentially harmful for reuse. Furthermore, we found 214 code
-snippets that could potentially violate the license of their original software.
-A survey of 201 high-reputation Stack Overflow answerers (33\% response rate)
-showed that 131 participants (65\%) have ever been notified of outdated code and
-26 of them (20\%) rarely or never fix the code. 138 answerers (69\%) never check
-for licensing conflicts between their copied code snippets and Stack Overflow's
-CC BY-SA 3.0.
+original software license. We present a study of online code clones on Stack
+Overflow and their toxicity by incorporating two developer surveys and a
+large-scale code clone detection. A survey of 201 high-reputation Stack Overflow
+answerers (33\% response rate) showed that 131 participants (65\%) have ever
+been notified of outdated code and 26 of them (20\%) rarely or never fix the
+code. 138 answerers (69\%) never check for licensing conflicts between their
+copied code snippets and Stack Overflow's CC BY-SA 3.0. A survey of 87 Stack
+Overflow visitors shows that they experienced several issues from Stack Overflow
+answers: mismatched solutions, outdated solutions, incorrect solutions, and buggy code. 
+85\% of them are not aware of CC BY-SA 3.0
+license enforced by Stack Overflow and 66\% never check for license conflicts
+when reusing code snippets. Our clone detection found online clone pairs between
+72,365 Java code snippets on Stack Overflow and 111 open source projects in the
+curated Qualitas corpus. We analysed 2,289 non-trivial online clone candidates.
+Our investigation revealed strong evidence that 153 clones have been copied from
+a Qualitas project to Stack Overflow. We found 100 of them (66\%) to be outdated
+and potentially harmful for reuse. Furthermore, we found 214 code snippets that
+could potentially violate the license of their original software and appear 7,112
+times in 2,427 GitHub projects.
 
@@
 as these two problems are still under explored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
+Moreover, Stack Overflow users also express their concerns about these two problems
+as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
+	Stack Overflow: meta.stackexchange.com/questions/131495, 
+	meta.stackexchange.com/questions/11705/, meta.stackexchange.com/questions/12527,
+	meta.stackexchange.com/questions/25956, meta.stackoverflow.com/questions/321291.}
+	 on \textsf{meta.stackexchange.com} about outdated
+answers and license of code on Stack Overflow.
 Outdated code snippets can be harmful since they are not up-to-date with their originals and may
@@
 \subsection{Empirical Study of Online Code Clones}
-We support the motivation and the findings in the surveys by performing
+We support the motivation and confirm the findings in the surveys by performing
 an empirical study of online code clones between Stack Overflow
@@
 pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
-subset of $t=0.5$. However, since there is a fewer true positive pairs reported
-(i.e.~generating false negatives), we ended up leaving some duplicates of the 
-same clones in the final merged clone set.
+subset of $t=0.5$. However, since there is a fewer merged clone pairs, 
+we ended up leaving some duplicates of the same clones in the final merged clone set.
 With this analysis, we can see that setting the threshold $t$ to 0.1 is too
@@
 A clone detection was then performed between the outdated code snippets and the GitHub
-projects. We selected SourcererCC with 80\% similarity for this task because it
-could scale to a large-scale data set, while Simian could not. Finally, we analysed
+projects. We selected SourcererCC with with the same settings (see \Cref{tab:clone_config}) 
+for this task because it could scale to a large-scale data set, while Simian could not. Finally, we analysed
 the clone reports and manually checked the clones.
@@
 external sources such as JDK or websites, we manually searched for the license
-of the original code.
+of the original code. Lastly, we searched for occurrences of the license-conflicting
+online clones in GitHub projects using the same method as in the outdated clones.
 
@@
 \vspace{0.25cm}
-\textit{RQ1.1 How often are Stack Overflow
+\textit{RQ 1.1 How often are Stack Overflow
 	answerers aware of the outdated code and 
@@
 of the answers). Only 3 participants reported that they were notified in more
-than 60\% of their answers. This notification to the answerer can be done by
-posting comments below the answer on Stack Overflow. For example, the answerer of
-the Stack Overflow question no.~10924648 posted a comment on his own answer
-saying that the answer is specifically for Spring 3.1 and another user
-posted a comment on the answer of the post no.~801935 that the code snippet is
-not of high quality and suggested an alternative in another post.
+than 60\% of their answers. This notification to the answerer can be done 
+via several means, such as contacting the author directly, 
+writing a comment saying that the answer is
+already outdated, down-voting the answer or posting a newer answer.
 The low percentage of outdated code notifications
@@
 	To answer RQ 1.1, although most of the Stack Overflow answerers are aware that their code
-	can be outdated, half of the answerers were very rarely notified of
-	outdated code in the answers. After being notified, some of them rarely or never fix the outdated code.
-	More than half of the answerers are aware of Stack Overflow's
-	CC BY-SA 3.0 license. Only 3 answerers explicitly include software license in their answers
-	while some of them choose to include the license in their profile page instead. More than half of the
+	can be outdated, 51.5\% of the answerers were very rarely notified and 35.5\% have never been notified of
+	outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.
+	124 answerers out of 200 (62\%) are aware of Stack Overflow's
+	CC BY-SA 3.0 license applied to code snippets in questions and answers. However,
+	only 3 answerers explicitly include software license in their answers. Some 
+	answerers choose to include the license in their profile page instead. 69\% of the
 	answerers never check for licensing conflicts between their copied code snippets
 	and Stack Overflow's CC BY-SA 3.0.
+%	To answer RQ 1.1, although most of the Stack Overflow answerers are aware that their code
+%	can be outdated, half of the answerers were very rarely notified of
+%	outdated code in the answers. After being notified, some of them rarely or never fix the outdated code.
+%	More than half of the answerers are aware of Stack Overflow's
+%	CC BY-SA 3.0 license. Only 3 answerers explicitly include software license in their answers
+%	while some of them choose to include the license in their profile page instead. More than half of the
+%	answerers never check for licensing conflicts between their copied code snippets
+%	and Stack Overflow's CC BY-SA 3.0.
 \end{boxquote}
@@
 \vspace{0.25cm}
-\textit{RQ1.2 How often do Stack Overflow
+\textit{RQ 1.2 How often do Stack Overflow
 	visitors experience the outdated code and licensing conflicts when
@@
 	To answer RQ 1.2, Stack Overflow visitors experienced several issues from Stack
-Overflow answers including outdated code. The majority of them are not aware of
-CC BY-SA 3.0 license enforced by Stack Overflow and never check for license
+Overflow answers including outdated code. 85\% of them are not aware of
+CC BY-SA 3.0 license enforced by Stack Overflow and 66\% never check for license
 conflicts when reusing code snippets.
@@
 on three aspects: newer or higher-voted answers and comments. We found
-that there were 34 posts which contains newer answers. Regarding the number of
-votes, there were 5 questions which contained answers with a higher number of
-votes than the outdated answer. However, 99 of the 100 outdated answers were still
+that there were 34 posts which contains newer answers and 5 posts which contained answers with a higher number of
+votes than the outdated answers. However, 99 of the 100 outdated answers were still
 marked as accepted answers. For the comments, we check if there is any comment
@@
 	could receive some unexpected results. So I suggest to try different approaches
-	or even check latest documentation''}. None of the 6 answers change their
-outdated code, but the comments themselves may help to warn other Stack Overflow
+	or even check latest documentation''}. The 6 outdated code snippets were still
+not fixed, but the comments themselves may help to warn other Stack Overflow
 users.
@@
 
-Then, we performed the check for clones of the 100 outdated code snippets in 130,703 GitHub projects.
+Then, we performed code clone detection between the 100 outdated code snippets and 130,703 GitHub projects.
 We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all
@@
 projects also appear on GitHub. For other projects besides the Qualitas
-projects, there were 47 cloned snippets that were exactly the same as the
-outdated code snippets and 42 cloned snippets that were not exactly the same
+projects, there were 32 cloned snippets that were not exactly the same
 (e.g.~they contained additional code modifications made by the projects'
-developers or they were copied from another source with a slightly different
-code).
-
-Among the exact-copy of 47 outdated cloned snippets, there were only two cloned
-snippets that gave attributions to Stack Overflow. However, the attributions
+developers or they were copied from another source with a slightly different code).
+There were 47 cloned snippets that were exactly the same as the
+outdated code snippets, which of 12 were buggy.
+Two cloned snippets gave attributions to Stack Overflow. The attributions
 pointed to different posts than the ones we found, but containing the same code
-in the answers. The other 32 cloned snippets were very likely to be a file-level
+in the answers. 32 cloned snippets were very likely to be a file-level
 clone from its respective original project (e.g. JFreeChart, JUnit, Log4J,
-Hadoop) based on their license header and the Javadoc comments. Lastly, the
-remaining 13 cloned snippets did not have any hints or evidence of copying.
-Twelve of them were toxic because they were the old versions that still contained bugs.
+Hadoop) based on their license header and the Javadoc comments. 
+13 cloned snippets did not have any hints or evidence of copying.
 
 Interestingly, we discovered that the buggy version of the
-\texttt{humanReadableInt()} method from Hadoop appears in two popular Java
+\texttt{humanReadableInt()} method from Hadoop appeared in two popular Java
 projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
@@
 deeplearning4j. The developers of deeplearning4j agreed that the method was
-problematic and they decided to implement their own fix due to a concern of a
+problematic and decided to implement their own fix due to a concern of a
 potential software licensing conflict caused by copying the fix directly from
-Hadoop code base. On the other hand, the bug report in Apache Hive is still
+Hadoop code base. The bug report in Apache Hive is still
 unfixed.
 
-The outdated online code clones cause problems ranging from uncompilable code
-(due to modifications and different API usage in the outdated code) to
-the introduction of vulnerabilities to the software~\cite{Xia2014}. An outdated code with a
-subtle change (e.g.\ \Cref{fig:before-after}) may be copied and reused without
-awareness from developers. Moreover, an outdated code with a defect (e.g.\ a race
-condition problem in \Cref{fig:before-after_2}) is clearly harmful to be reused.
-Stack Overflow has a voting mechanism that may mitigate this issue, the
-accepted answer is still used by naive developers who copy and reuse the
-outdated code.
-Although we did not find strong evidence of the outdated code snippets
-being cloned to GitHub projects, it would still be useful if Stack Overflow
-implements a flagging of outdated answers.
+Although we did not find strong evidence of the outdated code snippets in GitHub
+projects, it would still be useful if Stack Overflow implements a flagging of
+outdated answers. The outdated online code clones cause problems ranging from
+uncompilable code (due to modifications and different API usage in the outdated
+code) to the introduction of vulnerabilities to the software~\cite{Xia2014}. An
+outdated code with a subtle change (e.g.\ \Cref{fig:before-after}) may be copied
+and reused without awareness from developers. Moreover, an outdated code with a
+defect (e.g.\ a race condition problem in \Cref{fig:before-after_2}) is clearly
+harmful to be reused. Although Stack Overflow has a voting mechanism that may
+mitigate this issue, the accepted answer may still be used by naive developers
+who copy and reuse the outdated code.
 
@@
 dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
-without evidence of copying. Two of them contains a race condition and
+without evidence of copying. Twelve were buggy. Two of them contains a race condition and
 are found in popular projects: deeplearning4j and Apache Hive.
@@
 licensing issues caused by code cloning to Stack Overflow. We found evidence that
-154 pieces of code have been copied from Qualitas projects to Stack Overflow as
-examples. Another 111 pieces of code are cloned from external sources. Their
+153 pieces of code have been copied from Qualitas projects to Stack Overflow as
+examples. Another 109 pieces of code are cloned from external sources. Their
 status of accepted answers increase their chances of being reused. Even though
@@
 We detected clones between the 214
-code snippets without their original license (86 QS, 78 EX and 50 UD)  and
-130,703 GitHub projects using SourcererCC with 80\% similarity threshold. Then,
-we used the Ninka tool to automatically identify software license from the 7,207
-code snippets. Opposite to the outdated clones, we discovered many more clones
-of 7,207 candidate pairs. There were 90 pairs from 10 Qualitas projects on
-GitHub and 7,117 pairs from 2,427 other projects. From
-\Cref{tab:license_github}, the clones were found from highly-starred
+code snippets with their original license missing (86 QS, 78 EX and 50 UD)  and
+130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
+Opposite to the outdated clones, we discovered a large number
+of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects on
+GitHub and 7,112 pairs from 2,427 other projects. From
+\Cref{tab:license_github}, the clones were found in highly-starred
 projects (29,465 to 10 stars) to 1-star projects.
 We found 12 code snippets with attributions to Stack Overflow questions/answers and
-6 of them were the answers we found as clones from Qualitas or external sources.
+6 of them refer to one of our QS or EX clone pairs.
+We used the Ninka tool to automatically identify software license of the 7,207 cloned
+code snippets. 
 Five code snippets did not have license while the originals had Apache-2, GPLv2,
@@
 \end{table}
+
+Note that the code snippets could potentially violate the license, but do
+not necessarily do so. In the example where the JFreeChart
+developer copied his own code, she or he was free to change the
+license. The same may have occurred with any of the 214 code
+snippets.
 
@@
 	with evidence, where the code snippet has been copied from.
-We found 7,117 of the 214 license-incompatible code snippets
-in 130,703 GitHub projects.
+	We found occurrences of 7,112 clones of the 214 license-incompatible code snippets
+	in 2,427 GitHub projects.
 \end{boxquote}
-
-Note that the code snippets could potentially violate the license, but do
-not necessarily do so. In the example where the JFreeChart
-developer copied his own code, she or he was free to change the
-license. The same may have occurred with any of the 214 code
-snippets.
 
@@
 to outdated code and software license incompatibility. The findings lead to the
-insight about toxicity of online code clones and two actionable items
-we are proposing to the software engineering research and the Stack Overflow community.
+insight about toxicity of online code clones and we proposed three actionable items
+to the software engineering research and the Stack Overflow community.
 
@@
 rest were non-harmful clones of the outdated code. Although other studies show
-that Stack Overflow code snippets may contain security
+that Stack Overflow code snippets may become toxic by containing security
 vulnerabilities~\cite{Acar2016,Fischer2017} or API misuse~\cite{Zhang2018}, we
-found in this study that the damage caused by reusing outdated code on Stack
+found in this study that the damage caused by outdated code on Stack
 Overflow is not high.
@@
 fall under fair-use, there is still a risk due to different legal system in each
-country. For example, Germany legal system does not have a concept of fair use
-or the number of minimum lines of code to be consider copying, i.e.~de minimis,
+country. For example, Germany legal system does not have a concept of fair use.
+In addition, the number of minimum lines of code to be consider copying, i.e.~de minimis,
 is also differently interpreted from case to case or from country to country.
@@
 answers, date/time of the posts) to conclude that the code snippets are actually
-copied from Qualitas to Stack Overflow. We call for more research in
+copied from Qualitas to Stack Overflow. This is a burdensome and time-consuming process. We call for more research in
 automation of code cloning direction detection. From our experience in this
@@
 automatically, it is a challenging task to automate the process of establishing
-the origin of code clones. Since automatically establishing code cloning
+the direction of code cloning as previously discussed. 
+Since automatically establishing code cloning direction
 is still an open challenge, one viable solution for now is
@@
 pairs for the manual classification and avoid double counting of the same clone
-pairs. Nevertheless, our study might still suffer from false negatives,
+pairs. We studied the impact of choosing different thresholds for Bellon's clone agreement and the minimum clone
+size of the two clone detectors and selected the optimal values.
+Nevertheless, our study might still suffer from false negatives,
 i.e.~online code clones that are not reported by the tools or are filtered out
@@
 
-Regarding the code snippets, we downloaded a full data dump and
-extracted Java accepted answers
-% Instead of analysing every post, we
-%only focused on posts marked as accepted answers 
-since they are the
-most likely ones to be reused. 
-% This yields a total of 144,064 snippets.  
-Our findings are limited to these restrictions. They may
-not be generalised to all programming languages and all answers on
-Stack Overflow. We chose the curated Qualitas
-corpus for Java open source projects containing 111 projects
-\cite{QualitasCorpus}.  The projects span over several areas of
-software and has been used in several empirical
-studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although
-it is a curated and well-established corpus, it may not fully
-represent all Java open source software available.
-
-%Lastly, two clone detection tools, Simian and NiCad, are chosen for this study.
-We have not tried all the tools available and they might not be complete representatives of all available clone detection tools.
+Regarding the code snippets, we downloaded a full data dump and extracted Java
+accepted answers since they are the most likely ones to be reused. Our findings
+are limited to these restrictions. They may not be generalised to all
+programming languages and all answers on Stack Overflow. We chose the curated
+Qualitas corpus for Java open source projects containing 111 projects
+\cite{QualitasCorpus}.  The projects span over several areas of software and has
+been used in several empirical
+studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although it
+is a curated and well-established corpus, it may not fully represent all Java
+open source software available. Lastly, we selected 130,703 GitHub Java projects
+based on the number of stars they obtained to represent their popularity. They
+might not represent all Java projects on GitHub and the number of clone pairs
+found may differ from other project selection criteria.
 

### 2018-05-20 cloverflow-tse/cover_letter/cover_letter.tex
The complete draft of the cover letter and the TSE paper.

@@
 we performed an investigation of three different threshold values: six, ten, and fifteen lines. 
-We started the investigation by using a minimum clone size of six lines, a
-well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}. Simian
-reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone
-candidate pairs. We randomly sampled 382 pairs from the two sets and the first
-author investigated them. This was a statistical significant sample with a 95\%
-confidence level and $\pm 5\%$ confidence interval. We found 26 non-clone pairs;
-322 trivial clone pairs including \texttt{equals}, \texttt{hashCode}, or
-getters/setters; and 34 non-trivial clone pairs. Next, we increased the minimum
-clone size to ten lines, another well-established minimum clone size for
+We started our investigation by using a threshold value of six
+lines, a well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}.
+Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
+clone candidate pairs. We randomly sampled 382 pairs from the two sets for
+manual check. This sample amount was a statistical significant sample with a
+95\% confidence level and $\pm 5\%$ confidence interval. The first author
+investigated the sampled clone pairs and classified them into three groups:
+non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
+setter methods), and non-trivial clones. The manual check found 26 non-clone
+pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we increased the
+threshold to ten lines, another well-established minimum clone size for
 large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
@@
 checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
-clone pairs and 102 non-trivial clone pairs. Then, we increased the minimum
-clone size further to fifteen lines and retrieved 196 clone pairs from Simian
-and 1,230 clone pairs from SourcererCC. The manual check of the 382 randomly
-sampled pairs reveal zero non-clone pairs, 298 trivial clone pairs and 83
-non-trivial clone pairs.
+clone pairs and 102 non-trivial clone pairs. Then, we increased the threshold
+further to fifteen lines and retrieved 196 clone pairs from Simian and 1,230
+clone pairs from SourcererCC. The manual check of the 382 randomly sampled pairs
+reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial clone
+pairs.
 
-The findings from the three samples show that selecting the minimum of ten lines
-was a sweet spot and was preferred over six and fifteen lines. First, it generated 
+The findings from the three threshold values show that selecting the minimum clone size 
+of ten lines was preferred over six and fifteen lines. First, it generated 
 a fewer number of clone pairs than using six lines, which made the manual clone

### 2018-05-24 cloverflow-tse/cover_letter/cover_letter.tex
Incorporated Jens's comments on the cover letter.

@@
 Engineering. This is a re-submission of the previous submission
-no.~TSE-2017-11-0335 and we would like to thank the anonymous Reviewers for
+no.~TSE-2017-11-0335 and we would like to thank the anonymous reviewers for
 taking their time to carefully read our paper. With their useful and
-constructive reviews, we substantially improved the work by adding three major
+constructive reviews, we substantially improved the work by adding five major
 improvements as listed below to our previous submission and minor improvements
-as discussed later in this letter:
+as discussed later in this letter.
 
-\textbf{1. A study of toxic code snippets on GitHub:}~To provide an evidence
-that toxic code snippets are actually reused in software projects and strengthen
+\textbf{1.~A Stack Overflow Visitor survey}~To understand the effects of toxic
+code snippets on Stack Overflow to information seekers who look for coding
+solutions on Stack Overflow, we performed another survey of 87 Stack Overflow
+visitors. The survey shows that the visitors experienced several problems from
+reusing Stack Overflow code snippets including outdated code. They are 85\% of
+them that are not aware of CC BY-SA 3.0 license enforced by Stack Overflow and
+66\% never check for license conflicts when reusing code snippets.
+
+\textbf{2.~A study of toxic code snippets on GitHub:}~To provide evidence that
+toxic code snippets are actually reused in software projects and to strengthen
 the motivation, we performed a large-scale analysis of clones between the
-discovered online code clones, 100 outdated and 214 license-incompatible code snippets, 
-on Stack Overflow and 130,703 GitHub projects using a clone detection tool followed by manual validation.
+discovered online code clones (100 outdated and 214 license-incompatible code
+snippets) and 130,703 GitHub projects using a clone detection tool followed by
+manual validation.
 
-\textbf{2. Analysis of the tools' parameter settings:}~We mitigated the threats to
-validity due to parameter settings of the clone detection tools and the clone
-merging technique by exploring different tools' parameter values.
+\textbf{3.~An analysis of the tools' parameter settings:}~We mitigated the
+threats to validity due to parameter settings of the clone detection tools and
+the clone merging technique by exploring different tools' parameter values. We
+discovered that using the minimum clone size threshold of 10 lines gave the
+highest number of non-trivial clone pairs and using the Bellon's ok-match
+threshold of 0.5 gave the highest clone merging precision. We updated the
+results in the paper to reflect the findings.
 
-\textbf{3. Extended analysis of online code clones:}~We performed an extended analyses
-on the 2,289 online code clones and 100 outdated code snippets. For example,
-we analysed the size and age of the clones, and summarised the six intents that
-made the clones outdated.
+\textbf{4.~An extended analysis of outdated code clones:}~We performed an
+extended analysis on the 100 outdated code snippets. For example, we analysed
+age of the clones; studied effects of comments, newer answers, higher-voted
+answers on the outdated answers; and summarised the six intents that made the
+clones outdated. We found that, on average, the code is cloned to Stack Overflow
+2 years after it appears in Qualitas projects, and comments/newer or
+higher-voted answers did not strongly affect the outdated answers (99\% are
+still marked as accepted). Lastly, we discovered that the code are outdated
+because of code enhancement (65\%), followed by code deprecation (15\%), but
+fixing (10\%), code refactoring (6\%), changing coding style (3\%), and data
+format change (2\%).
 
-\textbf{4. Revisions to the overall discussion:}~We substantially expanded the
+\textbf{5.~Revisions to the overall discussion:}~We substantially expanded the
 overall discussion to include (1) a discussion of toxicity of outdated and
-license-incompatible clones on Stack Overflow and their implications, and (2) more detailed discussion
-of how to implement the tools or approaches proposed in the preventive and
-detective measures, and (3) a suggestion for automation of code cloning direction detection.
+license-incompatible clones on Stack Overflow and their implications, and (2)
+more detailed discussion of how to implement the tools or approaches proposed
+for preventive and detective measures, and (3) a suggestion for automation of
+code cloning direction detection.
 
 We also tried our best to address all the comments from the reviewers. Every
-comment led to an improvement(s) on this submission and we discuss them in order as shown in the
-next sections.
+comment led to an improvement on this submission and we discuss them in order as
+shown in the next sections.
+
+Lastly, we would also like to ask the reviewers to comment on how to address the
+newly established page limits of IEEE TSE that was enforced after our previous
+submission. After incorporating the suggestions from the reviewers and
+rewriting, our paper is now extended to 22 pages. Are there any elements that
+could or should be removed, or should a split into two separate papers be
+considered?
 
@@
 As shown in Table~\ref{tab:outdated_github} below, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
-For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippets and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).
+For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippet and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).
 
@@
 
-	Among the exact-copy of 47 outdated cloned snippets, there were only two cloned snippets that gave attributions to Stack Overflow.
-However, the attributions pointed to different posts than the ones we found, but containing the same code in the answers.
-The other 32 cloned snippets were very likely to be a file-level clone from its respective original project (e.g.
-JFreeChart, JUnit, Log4J, Hadoop) based on their license header and the Javadoc comments.
-Lastly, the remaining 13 cloned snippets did not have any hints or evidence of copying.
-	Twelve of them were toxic because they were the old versions that still contained bugs.
+	Among the exact-copy of 47 outdated cloned snippets, there were only two cloned
+snippets that gave attributions to Stack Overflow. However, the attributions
+pointed to different posts than the ones we found, but containing the same code
+in the answers. The other 32 cloned snippets were very likely to be a
+file-level clone from its respective original project (e.g. JFreeChart, JUnit,
+Log4J, Hadoop) based on their license header and the Javadoc comments. Lastly,
+the remaining 13 cloned snippets did not have any hints or evidence of copying.
+Twelve of them were toxic because they were the old versions that still
+contained bugs.
 
-	Interestingly, we discovered that the buggy version of the \texttt{humanReadableInt()} method from Hadoop appears in two popular Java projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854 stars and 1,946 forks).
-Due to the lack of evidence, we could not conclude how this method, which is exactly the same as the toxic code snippet we found on Stack Overflow, appear in the two projects.
-It is possible that the developers retrieved them from Stack Overflow, other websites, or from Hadoop code base directly.
-	Nevertheless, we reported the developers of the two projects regarding the issue.
-We created a bug report for each project (deeplearning4j \#4694\footnote{deeplearning4j bug report: \url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and HIVE-18929\footnote{Apache Hive bug report: \url{ https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the developers by describing the problem of race condition in the outdated version of \texttt{humanReadableInt()} method and proposed a fix by using the newest version of the method in Hadoop.
-The issue has been fixed in deeplearning4j.
-The developers of deeplearning4j agreed that the method was problematic and decided to implement their own fix due to a concern of a potential software licensing conflict caused by copying the fix directly from Hadoop code base.
-On the other hand, the bug report in Apache Hive is still unfixed.
+Interestingly, we discovered that the buggy version of the
+\texttt{humanReadableInt()} method from Hadoop appears in two popular Java
+projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
+stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
+this method, which is exactly the same as the toxic code snippet we found on
+Stack Overflow, appear in the two projects. It is possible that the developers
+retrieved them from Stack Overflow, other websites, or from Hadoop code base
+directly. Nevertheless, we reported them to the developers of the two projects
+regarding the issue. We created a bug report for each project (deeplearning4j
+\#4694\footnote{deeplearning4j bug report:
+	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
+HIVE-18929\footnote{Apache Hive bug report: \url{
+		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
+developers by describing the problem of race condition in the outdated version
+of the \texttt{humanReadableInt()} method and proposed a fix by using the
+newest version of the method in Hadoop. The issue has been fixed in
+deeplearning4j. The developers of deeplearning4j agreed that the method was
+problematic and decided to implement their own fix due to a concern of a
+potential software licensing conflict caused by copying the fix directly from
+the Hadoop code base. On the other hand, the bug report in Apache Hive is still
+open.
 
-	\item The same study has been done for another type of toxic code snippets on Stack Overflow, license-incompatible code snippets. 
-	We detected clones between the 214
-	code snippets without their original license (86 QS, 78 EX and 50 UD)  and
-	130,703 GitHub projects using SourcererCC with 80\% similarity threshold. 
-	Opposite to the outdated clones, we discovered many more clones
-	of 7,207 candidate pairs.
-	Then, we used the Ninka tool to automatically identify software license from the 7,207
-	code snippets.  There were 90 pairs from 10 Qualitas projects on
-	GitHub and 7,117 pairs from 2,427 other projects. From
-	Table \ref{tab:license_github} below, the clones were found from highly-starred
-	projects (29,465 to 10 stars) to 1-star projects.
-	We found 12 code snippets with attributions to Stack Overflow questions/answers and
-	6 of them were the answers we found as clones from Qualitas or external sources.
-	Five code snippets did not have license while the originals had Apache-2, GPLv2,
-	or EPLv1 license. One snippets had AGPLv3 license while the original had Apache-2 license.
-	Only 995 code snippets in GitHub projects that have the same license
+	\item The same study has been done for another type of toxic code snippets on
+Stack Overflow, license-incompatible code snippets. We detected clones between
+the 214 code snippets without their original license (86 QS, 78 EX and 50 UD) 
+and 130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
+In contrast to the outdated clones, we discovered many more clones of 7,207
+candidate pairs. 
+There were 95 pairs from 10
+Qualitas projects hosted on GitHub and 7,112 pairs from 2,427 other projects.
+Then, we used the Ninka tool to automatically identify
+software licenses from the reported cloned snippets. Shown in
+Table \ref{tab:license_github} below, the clones were found in highly-starred
+projects (29,465 to 10 stars) to 1-star projects. We found 12 code snippets
+with attributions to Stack Overflow questions/answers and 6 of them were the
+answers we found as clones from Qualitas or external sources. Five code
+snippets did not have a license while the originals had the Apache-2, GPLv2, or EPLv1
+license. One snippets had the AGPLv3 license while the original had the Apache-2
+license. Only 995 code snippets in GitHub projects have the same license
 as the originals in Qualitas.
@@
 
-	\item With the finding above, we show that the clones of Stack Overflow toxic code fragments do occur in several open source software projects on GitHub.
-However, we could not establish a strong evidence that the toxic code snippets were originated from Stack Overflow due to lack of supporting information.
-Hence, we softened our claim by changing the statement ``\textit{It is probably more important than studying the effects of reusing Stack Overflow code snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the effects of reusing Stack Overflow code snippets ...}''.
-	We also updated the Overall Discussion section to reflect the findings that (1) there is only a small number of toxic code snippets from outdated code that are found in GitHub projects, (2) there is a large number of toxic code snippets caused by missing license that are found in GitHub projects.
-%Moreover, the direction of copying is also unclear.
-The clones could come from Stack Overflow, the original project repositories, or other places.
+	\item With the finding above, we show that clones of toxic Stack Overflow 
+code fragments do occur in several open source software projects on GitHub.
+However, we could not establish strong evidence that the toxic code snippets
+were originated from Stack Overflow due to lack of supporting information.
+Hence, we softened our claim by changing the statement ``\textit{It is probably
+	more important than studying the effects of reusing Stack Overflow code
+	snippets ...}'' to ```\textit{It is \textbf{equally} important to studying the
+	effects of reusing Stack Overflow code snippets ...}''. We also updated the
+Overall Discussion section to reflect the findings that (1) there is only a
+small number of toxic code snippets from outdated code that are found in GitHub
+projects, (2) there is a large number of toxic code snippets caused by missing
+license that are found in GitHub projects. %Moreover, the direction of copying
+% is also unclear. The clones could come from Stack Overflow, the original
+% project repositories, or other places.
 \end{enumerate}
@@
 \rcomment{
-	I think that the survey evidence is compelling.
-But I am missing the awareness of Stack Overflow questioners or information-seekers to toxic code snippets.
-I wonder: how skeptical are developers when considering code snippets on Stack Overflow, how often do developers use code snippets directly, and how often do developers use clues such as \textit{``A quick google search returned me this from Appache hadoop project.
-Copying from there:''} to seek out the latest version of the information provided in the answer.
-The survey responses described in Section 3.5.3 suggest that there are questioners/information-seekers that are aware of toxic code snippets (as they are reporting them to the answerers), and there is evidence that the Stack Overflow community is aware of the need to retire outdated information and of the many concerns related to software licensing, as these issues are discussed on meta.stackoverflow.com.
-So, again, I wonder about the impact of toxic code snippets on actual software projects.
+	I think that the survey evidence is compelling. But I am missing the awareness
+of Stack Overflow questioners or information-seekers to toxic code snippets. I
+wonder: how skeptical are developers when considering code snippets on Stack
+Overflow, how often do developers use code snippets directly, and how often do
+developers use clues such as \textit{``A quick google search returned me this
+	from Appache hadoop project. Copying from there:''} to seek out the latest
+version of the information provided in the answer. The survey responses
+described in Section 3.5.3 suggest that there are
+questioners/information-seekers that are aware of toxic code snippets (as they
+are reporting them to the answerers), and there is evidence that the Stack
+Overflow community is aware of the need to retire outdated information and of
+the many concerns related to software licensing, as these issues are discussed
+on meta.stackoverflow.com. So, again, I wonder about the impact of toxic code
+snippets on actual software projects.
 }
 
-We partially address this comment in the previous answer by performing an empirical study of code cloning between Stack Overflow toxic code snippets and GitHub projects.
-Furthermore, we also improved the paper on the aspect of the awareness of information-seekers to toxic code snippets on Stack Overflow by including the results from another survey of Stack Overflow visitors (i.e.~information seekers).
-This survey of the Stack Overflow visitors was performed during the same time as the Stack Overflow answerers (25 July 2017 to 25 September 2017) and the full results are reported in our technical report~\citep{Ragkhitwetsagul_RN2017}.
-We did not include the results in the previous version of the paper due to a smaller sample size compared to the answerers survey.
-However, we did find some interesting results so we have included them into this version and discussed the key findings in~RQ1.
-The brief summary of the visitor survey is as follows.
+We partially address this comment in the previous answer by performing an
+empirical study of code cloning between toxic Stack Overflow code snippets and
+GitHub projects. Furthermore, we also improved the paper on the aspect of the
+awareness of information-seekers to toxic code snippets on Stack Overflow by
+including the results from another survey of Stack Overflow visitors
+(i.e.~information seekers). This survey of the Stack Overflow visitors was
+performed during the same time as the Stack Overflow answerers (25 July 2017 to
+25 September 2017) and the full results are reported in our technical
+report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the
+previous version of the paper due to a smaller sample size compared to the
+answerers survey. However, we did find some interesting results so we have
+included them into this version and discussed the key findings in~RQ1. The brief
+summary of the visitor survey is as follows.
 
@@
 
-We surveyed 87 Stack Overflow visitors (visit the site and reuse code from Stack Overflow at least once) via five channels: social media post (Facebook),
-\textsf{blognone.com}, a popular IT community and discussion forum in Thailand, the University of Molise in Italy where the third author works, \texttt{comp.lang.java.programmer} group and the Software Engineering
-Facebook page.
+We surveyed 87 Stack Overflow visitors (visited the site and reused code from Stack
+Overflow at least once) via five channels: social media post (Facebook),
+\textsf{blognone.com} (a popular IT community and discussion forum in Thailand),
+the University of Molise in Italy where the third author works, the
+\texttt{comp.lang.java.programmer} group and the Software Engineering Facebook
+page.
 
@@
 solutions, to buggy code. Although they are aware of the problems, half of them
-(56\%) never reports back to the Stack Overflow discussions. On the other hand,
+(56\%) never report back to the Stack Overflow discussions. On the other hand,
 the visitors rarely give attributions to Stack Overflow when they reuse code
@@
 Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
-check if the code snippet originated from a different source (e.g. an open source project) 
+check if the code snippet originated from a different source (e.g.~an open source project) 
 and if they had an incompatible license to their projects.
@@
 
-\rcomment{
-	The \textbf{Overall Discussion} section is not commensurate with the quality and breadth of the empirical study.
-The proposed preventative measure is actually two measures: a policy change and an IDE plugin.
-While an IDE plugin would provide early detection (and possible prevention) of license violations, the exact mechanics are not clear based on the description.
-Further, companies (and perhaps major open source projects?) use auditing platforms/services to detect such violations.
-Regarding the detective measure, I do not think that the paper establishes that a system to detect outdated code snippets on Stack Overflow is needed (but rather it establishes that outdated code snippets exist on Stack Overflow).
-Further, not all outdated code snippets are bad.
-For instance, a code snippet may show a solution using an older version of an API, and that older version may still be used in production.
-So, the definition of outdated would need to be a bit more nuanced to be used in an automated system for flagging or updating old Stack Overflow posts.
-}
+\rcomment{ The \textbf{Overall Discussion} section is not commensurate with the
+	quality and breadth of the empirical study. The proposed preventative measure is
+	actually two measures: a policy change and an IDE plugin. While an IDE plugin
+	would provide early detection (and possible prevention) of license violations,
+	the exact mechanics are not clear based on the description. Further, companies
+	(and perhaps major open source projects?) use auditing platforms/services to
+	detect such violations. Regarding the detective measure, I do not think that the
+	paper establishes that a system to detect outdated code snippets on Stack
+	Overflow is needed (but rather it establishes that outdated code snippets exist
+	on Stack Overflow). Further, not all outdated code snippets are bad. For
+	instance, a code snippet may show a solution using an older version of an API,
+	and that older version may still be used in production. So, the definition of
+	outdated would need to be a bit more nuanced to be used in an automated system
+	for flagging or updating old Stack Overflow posts. }
 
-Thanks for the suggestion.~We rewrote the Overall Discussion section to reflect yours and Reviewer 3's comments. The changes include:
+Thanks for the suggestion.~We rewrote the Overall Discussion section to reflect
+yours and Reviewer 3's comments. The changes include:
 
-\begin{enumerate}
-	\item We added a discussion of toxicity of outdated and license-incompatible clones on Stack Overflow.
-Although we found some harmful outdated clones, we could not find evidence that they are widely reused in open source projects on GitHub.
-Therefore, the damage is not high since there is only a few outdated code snippets that are harmful for reuse.
-On the other hand, the problem of license incompatibility caused by missing original license in Stack Overflow code snippets can cause more damage than outdated code.
-Different legal system and different interpretation of fair-use concept and de minimis (i.e.~the minimal lines of code allowed to be copied without violating copyright) in each country can make a reuse of these code snippets becoming illegal.
+\begin{enumerate} \item We added a discussion of toxicity of outdated and
+	license-incompatible clones on Stack Overflow. Although we found some harmful
+	outdated clones, we could not find evidence that they are widely reused in open
+	source projects on GitHub. Therefore, the damage is not high since there are only
+	a few outdated code snippets that are harmful for reuse. On the other hand, the
+	problem of license incompatibility caused by missing original licenses in Stack
+	Overflow code snippets can cause more damage than outdated code. Different legal
+	system and different interpretation of fair-use concept and de minimis (i.e.~the
+	minimal lines of code allowed to be copied without violating copyright) in each
+	country can make a reuse of these code snippets legally problematic.
 
-	\item We improved the Actionable Items to be more precise about the mechanics on how to automate the process of finding online code clones, detecting outdated code, and finding license-incompatible code snippets.
+	\item We improved the Actionable Items to be more precise about the mechanics
+	on how to automate the process of finding online code clones, detecting
+	outdated code, and finding license-incompatible code snippets.
 
-	\item To address your point about auditing platforms/services, 
-	we performed a study of two open source software auditing
-	platforms/services:~BlackDuck
+	\item To address your point about auditing platforms/services, we performed a
+	study of two open source software auditing platforms/services:~BlackDuck
 	Software\footnote{https://www.blackducksoftware.com} and
-	nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from their
-	report~\cite{CORSI2017} that while they check for code copied from open source
-	projects including GitHub and Stack Overflow and analyse their license
+	nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from
+	their report~\cite{CORSI2017} that while they check for code copied from open
+	source projects including GitHub and Stack Overflow and analyse their license
 	compatibility with their customer software, the BlackDuck auditing system will
-	treat the code snippets on Stack Overflow as having ``unknown'' license because
-	it does not know the original license of Stack Overflow code snippets. For nexB,
-	their product does not mention checking of reused source code from Stack
-	Overflow. So, our proposed preventive measure, which can offer more precise licensing
-	information of Stack Overflow code snippets, will be useful as an add-on license
-	check for code copying from Stack Overflow. We include this in the Overall Discussion.
-\end{enumerate}
+	treat the code snippets on Stack Overflow as having an ``unknown'' license because
+	it does not know the original license of Stack Overflow code snippets. For
+	nexB, their product does not mention checking of reused source code from Stack
+	Overflow. So, our proposed preventive measure, which can offer more precise
+	licensing information of Stack Overflow code snippets, will be useful as an
+	add-on license check for code copying from Stack Overflow. We include this in
+	the Overall Discussion. \end{enumerate}
 
-\rcomment{
-Other Comments
-While ``Toxic Code Snippets'' is a catchy phrase for the title, I think that online code clones are the dominant topic.}
+\rcomment{ Other Comments While ``Toxic Code Snippets'' is a catchy phrase for
+	the title, I think that online code clones are the dominant topic.}
 
-You are right.
-We mainly study the online code clones and established their existence.
-However, we used the term ``toxic code snippets'' in order to emphasise the possible ramifications from online code cloning.
-Moreover, the term code cloning is not well known outside the code cloning community.
-Code clones are called differently in each research community or in practice, such as duplicated code, copy-and-paste code, code reuse, software similarity or software redundancy.
-So, we decided not to use the term in the title.
+You are right. We mainly study online code clones and established their
+existence. However, we used the term ``toxic code snippets'' in order to
+emphasise the possible ramifications from online code cloning. Moreover, the
+term code cloning is not well known outside the code cloning community. Code
+clones are called differently in each research community or in practice, such as
+duplicated code, copy-and-paste code, code reuse, software similarity or
+software redundancy. So, we decided not to use the term in the title.
 
-We also updated the Introduction to state that the dominant topic is about online code clones as follows.
+We also updated the Introduction to state that the dominant topic is about
+online code clones as follows.
 
-``Although this activity of online code cloning is well-known, there is only a few
-empirical studies on the topic~\citep{An2017,Abdalkareem2017,Baltes2017}, especially
-the on finding the origins of the clones.
-We tackle this challenge of establishing existence of online code clones and
-investigate how they occur in this study.''
-%Considering your suggestion and another suggestion by Reviewer 2 that the definition of ``toxic code snippets'' is vague, we also tightened the definition of toxic code snippets to be more precise.
+``Although this activity of online code cloning is well-known, there are only a
+few empirical studies on the topic~\citep{An2017,Abdalkareem2017,Baltes2017},
+especially on finding the origins of the clones. We tackle this challenge of
+establishing existence of online code clones and investigate how they occur in
+this study.'' %Considering your suggestion and another suggestion by Reviewer 2
+% that the definition of ``toxic code snippets'' is vague, we also tightened the
+% definition of toxic code snippets to be more precise.
 
-\rcomment{
-	The introduction states that the erroneous code snippet in post 22262310 has been viewed 259 as of the writing of the paper.
-But I note that while the question was posted on Mar 7, 14 the answer was posted on Mar 11, 14.
-I also note that the question has a score of -1.
-So, I wonder (a) whether the view count is for the answer (i.e., the code snippet) or the post (which existed for a few days before the answer appeared), (b) how many people viewed the question before it was answered, and (c) if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.}
+\rcomment{ The introduction states that the erroneous code snippet in post
+	22262310 has been viewed 259 as of the writing of the paper. But I note that
+	while the question was posted on Mar 7, 14 the answer was posted on Mar 11, 14.
+	I also note that the question has a score of -1. So, I wonder (a) whether the
+	view count is for the answer (i.e., the code snippet) or the post (which existed
+	for a few days before the answer appeared), (b) how many people viewed the
+	question before it was answered, and (c) if the negative score for the question
+	impacts both the number of views and the trust that people place in the answer
+	to a down-voted question.}
 
-That is a fair point and we would like to analyse the statistics as you suggested. 
-To answer your question in (a), the number of views
-is for the whole Stack Overflow post but we use it as a proxy of the number of views the accepted answer receives
-because the question and the answer of the two motivation examples have a short gap of posting time (within the same day and four days after).
-For (b), unfortunately, for our experiment we extracted only the code snippets from the Stack Overflow dumps but not other information.
-They are the only available data of the January 2016 snapshot we currently have.
-We checked and found that the latest available Stack Overflow dump already contains different data than the one we used in our study since it is now more than 2 years newer, and will result in incorrect statistics and inconsistent results.
-For (c), that is a really interesting idea. However, it is out of the scope of this study and would involve an extensive analysis of the data so we may investigate it in the future work.
+That is a fair point and we would like to analyse the statistics as you
+suggested. To answer your question (a), the number of views is for the whole
+Stack Overflow post but we use it as a proxy of the number of views the accepted
+answer receives because the question and the answer of the two motivation
+examples have a short gap of posting time (within the same day and four days
+after). For (b), unfortunately, for our experiment we extracted only the code
+snippets from the Stack Overflow dumps but not other information. They are the
+only available data of the January 2016 snapshot we currently have. We checked
+and found that the latest available Stack Overflow dump already contains
+different data than the one we used in our study since it is more than 2
+years newer, and will result in incorrect statistics and inconsistent results.
+For (c), that is a really interesting idea. However, it is out of the scope of
+this study and would involve an extensive analysis of the data so we may
+investigate it in the future work.
 
- Nevertheless, we have added a footnote to the text in the Introduction to clarify point (a).
+Nevertheless, we have added a footnote to the text in the Introduction to
+clarify point (a).
 
-\rcomment{
-	FYI, since this paper was authored, a Stack Overflow user has posted a comment in response to the answer for post 22262310.
-The comment highlights the missing line and refers to the relevant HADOOP issue report.
-Interestingly, the gap between the issue report being resolved (Nov 20, 14) and the comment appearing on Stack Overflow (Oct 31, 17) is nearly three years.
-I wonder how many views occurred during this gap and whether the addition of the comment mitigates the toxicity of the code snippet.
-}
+\rcomment{ FYI, since this paper was authored, a Stack Overflow user has posted
+	a comment in response to the answer for post 22262310. The comment highlights
+	the missing line and refers to the relevant HADOOP issue report. Interestingly,
+	the gap between the issue report being resolved (Nov 20, 14) and the comment
+	appearing on Stack Overflow (Oct 31, 17) is nearly three years. I wonder how
+	many views occurred during this gap and whether the addition of the comment
+	mitigates the toxicity of the code snippet. }
 
-Thank you for the detailed checking of the Stack Overflow post.
-Interestingly, this is surprising to us as well.
-The comment in the post 22262310 by Joseph K on 31 October 2017 that highlights the missing line in HADOOP \texttt{compare} method is actually from a student in our class.
-His name is Joseph Kalash and he is a master student in Machine Learning MsC program at UCL Computer Science department \footnote{Joseph's CV can be found here: \url{https://jkala.sh/cv}}.
-We assigned a preprint of this paper to students in the COMPGS11 -- Research Seminar in Software Engineering course and had a discussion about the paper on Thu 2 November 2017.
-Joseph, who was an active Stack Overflow member, was one of the students in the class and he actively participated in the discussion.
-It seemed like he had seen the Hadoop's toxic code snippet in the paper and decided to post a comment to warn other users.
+Thank you for the detailed checking of the Stack Overflow post. Interestingly,
+this is surprising to us as well. The comment in the post 22262310 by Joseph K
+on 31 October 2017 that highlights the missing line in HADOOP \texttt{compare}
+method is actually from a student in our class. His name is Joseph Kalash and he
+is a master student in Machine Learning MsC program at UCL Computer Science
+department\footnote{Joseph's CV can be found here: \url{https://jkala.sh/cv}}.
+We assigned a preprint of this paper to students in the COMPGS11 -- Research
+Seminar in Software Engineering course and had a discussion about the paper on
+Thu 2 November 2017. Joseph, who was an active Stack Overflow member, was one of
+the students in the class and he actively participated in the discussion. It
+seems that he had seen the Hadoop's toxic code snippet in the paper and decided
+to post a comment to warn other users.
 
-Nevertheless, since this is a very interesting suggestion.
-We also performed an investigation of the 100 answers of our reported outdated code snippets on Stack Overflow on 6 May 2018 to see if there is any comment to mitigate or point out the toxicity of the code snippet.
-We include the result of this investigation in the RQ4.
-We found that, out of 100 answers containing outdated code snippets, there were 6 answers that had a comment saying the code in the answer is outdated or containing issues (including Joseph's comment).
-Thus, there is about 6\% of outdated answers that were notified by the Stack Overflow users based on our analysed data.
-None of the 6 answers change their outdated code, but the comments themselves may help to warn other Stack Overflow users.
-We added this discussion in the RQ4.
+Nevertheless, since this is a very interesting suggestion, we also performed an
+investigation of the 100 answers of our reported outdated code snippets on Stack
+Overflow on 6 May 2018 to see if there is any comment to mitigate or point out
+the toxicity of the code snippet. We include the result of this investigation in
+RQ4. We found that out of 100 answers containing outdated code snippets,
+there were 6 answers that had a comment saying the code in the answer is
+outdated or contains issues (including Joseph's comment). Thus, there are about
+6\% of outdated answers that were notified by the Stack Overflow users based on
+our analysed data. None of the 6 answers change their outdated code, but the
+comments themselves may help to warn other Stack Overflow users. We added this
+discussion to RQ4.
 
-\rcomment{
-\begin{enumerate}
-	\item Table 1 has a median column. Median of what?
-	\item Section 2.1 states that comments were removed before clone detection, but as stated later in the paper, comments can provide clues regarding provenance.
-Can the manual inspection of comments to find evidence of copying be automated as part of the clone detection process?
-	\item Typo: ``how much the community trust them'' --> ``how much the community trusts them''
-\end{enumerate}
-}
+\rcomment{ \begin{enumerate} \item Table 1 has a median column. Median of what?
+		\item Section 2.1 states that comments were removed before clone detection, but
+		as stated later in the paper, comments can provide clues regarding provenance.
+		Can the manual inspection of comments to find evidence of copying be automated
+		as part of the clone detection process? \item Typo: ``how much the community
+		trust them'' --> ``how much the community trusts them'' \end{enumerate} }
 
-\begin{enumerate}
-	\item For the Stack Overflow data set, the value represents the median size of Stack Overflow code snippets.
-For the Qualitas data set, the value represents the median of number of lines of code in each project.
-Since they are confusing as you pointed out, we decided to remove them from the table and only discuss the numbers in the text.
-	\item This is actually a great insight!
-We expanded the idea further and came up with a suggestion for an automated technique to facilitate human investigator on finding provenance and included it in a section called Automated cloning direction detection in the Overall Discussion.
-	\item Thanks. This has been fixed.
-\end{enumerate}
+\begin{enumerate} \item For the Stack Overflow data set, the value represents
+	the median size of Stack Overflow code snippets. For the Qualitas data set, the
+	value represents the median of number of lines of code in each project. Since
+	they are confusing as you pointed out, we decided to remove them from the table
+	and only discuss the numbers in the text. \item This is actually a great
+	insight! We expanded the idea further and came up with a suggestion for an
+	automated technique to facilitate human investigator on finding provenance and
+	included it in a section called Automated cloning direction detection in the
+	Overall Discussion. \item Thanks. This has been fixed. \end{enumerate}
 
@@
 
-\rcomment{
-\textbf{The definition of toxic code snippets:} I understand that the authors are trying to put a new spin or name to the phenomena they study, but the definition the authors provide is, in my opinion, not sufficient.
-For example, their definition is ``toxic code snippets mean code snippets that are harmful for reuse and, \textbf{in several cases}, are caused by online...''.
-A definition should be clear - saying in several cases - means that in several other cases (1- your several cases) it is not harmful.
-So, I ask the authors to refine and clarify this definition, because as it stands now, this definition is confusing (at best).
-Given that your entire paper is about toxic code snippets, you can appreciate why this is important.
-}
+\rcomment{ \textbf{The definition of toxic code snippets:} I understand that the
+	authors are trying to put a new spin or name to the phenomena they study, but
+	the definition the authors provide is, in my opinion, not sufficient. For
+	example, their definition is ``toxic code snippets mean code snippets that are
+	harmful for reuse and, \textbf{in several cases}, are caused by online...''. A
+	definition should be clear - saying in several cases - means that in several
+	other cases (1- your several cases) it is not harmful. So, I ask the authors to
+	refine and clarify this definition, because as it stands now, this definition is
+	confusing (at best). Given that your entire paper is about toxic code snippets,
+	you can appreciate why this is important. }
 
-We appreciate the comments.
-We have refined our definition of toxic code snippets in the paper by adapting from Israel Gat's definition~\citep{toxiccode} which links toxic code to technical debt, i.e.~``a metaphor reflecting technical compromises that can yield short-term benefit but may hurt the long-term health of a software system''~\citep{Li2015}.
-The new definition of toxic doe snippets are as follows.
+We appreciate the comments. We have refined our definition of toxic code
+snippets in the paper by adapting Israel Gat's definition~\citep{toxiccode}
+which links toxic code to technical debt, i.e.~``a metaphor reflecting technical
+compromises that can yield short-term benefit but may hurt the long-term health
+of a software system''~\citep{Li2015}. The new definition of toxic doe snippets
+are as follows.
 
-``Toxic code snippets mean code snippets that, after incorporating into software,
-the cost of paying back the technical debt exceeds the value it generates in the long run.'' 
-Stack Overflow code snippets
-cloned from open source software or online sources can become toxic when they
-are (1)~outdated, (2)~violating their original software
-license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
-We chose to study toxic code snippets caused by outdated code and license-violating code snippets in
-this study since these two problems are still under explored compared to code smells~\citep{Tufano2015} or vulnerabilities~\citep{Acar2016,Fischer2017}.
-Outdated code snippets can be harmful since they are not up-to-date with their originals and may
-contain defects. Code snippets from open source projects usually fall under a
-specific software license, e.g.\ GNU General Public License (GPL). If they are
-cloned to Stack Overflow answers without the license, and then flow to other projects
-with conflicting licenses, legal issues may occur.
+``Toxic code snippets mean code snippets that, after incorporating into
+software, the cost of paying back the technical debt exceeds the value it
+generates in the long run.'' Stack Overflow code snippets cloned from open
+source software or online sources can become toxic when they are (1)~outdated,
+(2)~violating their original software license, (3) exhibiting code smells, or
+(4) having security vulnerabilities. We chose to study toxic code snippets
+caused by outdated code and license-violating code snippets in this study since
+these two problems are still under explored compared to code
+smells~\citep{Tufano2015} or vulnerabilities~\citep{Acar2016,Fischer2017}.
+Outdated code snippets can be harmful since they are not up-to-date with their
+originals and may contain defects. Code snippets from open source projects
+usually fall under a specific software license, e.g.\ GNU General Public License
+(GPL). If they are cloned to Stack Overflow answers without the license, and
+then flow to other projects with conflicting licenses, legal issues may occur.
 
-\rcomment{
-	\textbf{RQs need to be better linked:} First, I can see a clear motivation for RQs 1-3, however, RQs 4 and 5 seem to be tagged on.
-I did not see a clear transition of why RQs 4 and 5 would follow RQs 1-3.
-This can be an easy fix, but it is an important one since it makes your paper seem less cohesive.
-}
+\rcomment{ \textbf{RQs need to be better linked:} First, I can see a clear
+	motivation for RQs 1-3, however, RQs 4 and 5 seem to be tagged on. I did not see
+	a clear transition of why RQs 4 and 5 would follow RQs 1-3. This can be an easy
+	fix, but it is an important one since it makes your paper seem less cohesive. }
 
-Regarding RQ4 (Software licensing violation), it needs to follow RQ 1--2 because the license violation needs evidence of cloning direction.
-To put it another way, we could tell that the code snippets on Stack Overflow may have incompatible licenses to their originals after we confirmed that (1) the Stack Overflow code snippets were actually clones of Qualitas projects and (2) the direction of cloning was from Qualitas to Stack Overflow, which both are addressed in RQ1 and RQ2.
-Nevertheless, RQ4 does not need to follow RQ3 (Outdated online code clones) because they are independent of each other.
+Regarding RQ4 (Software licensing violation), it needs to follow RQ 1--2 because
+the license violation needs evidence of cloning direction. To put it another
+way, we could tell that the code snippets on Stack Overflow may have
+incompatible licenses to their originals after we confirmed that (1) the Stack
+Overflow code snippets were actually clones of Qualitas projects and (2) the
+direction of cloning was from Qualitas to Stack Overflow, which both are
+addressed in RQ1 and RQ2. Nevertheless, RQ4 does not need to follow RQ3
+(Outdated online code clones) because they are independent of each other.
 
-Regarding RQ5 (the Stack Overflow answerer survey), that is a good point.
-Since RQ5 actually supports the motivation of our experiment by showing that code copying from software projects to Stack Overflow actually occurs and showing that some of the answerers are not aware of outdated code and software license incompatibility.
-We moved them to RQ1 instead and reorganised the paper to discuss the survey results as an incentive for our experiment of online code clone detection and toxic code snippet identification.
-The findings in RQ2--5 will confirm the survey results by showing that the issues actually occur on Stack Overflow.
+Regarding RQ5 (the Stack Overflow answerer survey), that is a good point. Since
+RQ5 actually supports the motivation of our experiment by showing that code
+copying from software projects to Stack Overflow actually occurs and showing
+that some of the answerers are not aware of outdated code and software license
+incompatibility. We moved them to RQ1 instead and reorganised the paper to
+discuss the survey results as an incentive for our experiment of online code
+clone detection and toxic code snippet identification. The findings in RQ2--5
+will confirm the survey results by showing that the issues actually occur on
+Stack Overflow.
 
-\rcomment{
-	\textit{Issues related to RQs}
+\rcomment{ \textit{Issues related to RQs}
 
-	Since we are talking about the RQs, this might be a good chance to discuss some of my other concerns with specific RQs.
+	Since we are talking about the RQs, this might be a good chance to discuss some
+	of my other concerns with specific RQs.
 
-	RQ3.~I believe that the answer to this question is expected and perhaps the way that the authors answered this question is incorrect.
-If I use some code from SO that was posted in 2014, then I expect that it is outdated.
-Also, SO does not allow people to update their posts, so why would I expect the snippets to not be outdated, hence, I feel that your question is incorrect.
-Another issue that might impact the answer to this RQ is the fact that your Qualitas dataset is older than that of SO, so your setup encourages the finding of outdated snippets.
-What I think would be a better approach is to look if there are other answers (maybe not the accepted one) that are newer.
-For me, if I see an old accepted answer or a newer post with an upvoted answer, I will probably go for the newer post.
-This was never considered by the authors.
-}
+	RQ3.~I believe that the answer to this question is expected and perhaps the way
+	that the authors answered this question is incorrect. If I use some code from
+	SO that was posted in 2014, then I expect that it is outdated. Also, SO does
+	not allow people to update their posts, so why would I expect the snippets to
+	not be outdated, hence, I feel that your question is incorrect. Another issue
+	that might impact the answer to this RQ is the fact that your Qualitas dataset
+	is older than that of SO, so your setup encourages the finding of outdated
+	snippets. What I think would be a better approach is to look if there are other
+	answers (maybe not the accepted one) that are newer. For me, if I see an old
+	accepted answer or a newer post with an upvoted answer, I will probably go for
+	the newer post. This was never considered by the authors. }
 
-Stack Overflow allows its users to edit their own posts, i.e.~questions/answers~\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts~\footnote{https://stackoverflow.com/help/privileges/edit}.
+Stack Overflow allows its users to edit their own posts,
+i.e.~questions/answers\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts\footnote{https://stackoverflow.com/help/privileges/edit}.
 Thus, if the code snippet in an answer is outdated and has an issue, the answerer or other high-reputation users can update the answer to be up-to-date or to warn other users that the code is already outdated and may contain problems.
-We found some discussions regarding this concern on Metaexchange as well so the Stack Overflow community is also considering this option~\footnote{Discussion about outdated answer: https://meta.stackexchange.com/questions/131495/how-to-handle-outdated-answers and https://meta.stackexchange.com/questions/180864/editing-outdated-source-code-in-an-answer}.
+We found some discussions regarding this concern on Metaexchange as well so the Stack Overflow community is also considering this option\footnote{Discussion about outdated answer: https://meta.stackexchange.com/questions/131495/how-to-handle-outdated-answers and https://meta.stackexchange.com/questions/180864/editing-outdated-source-code-in-an-answer}.
 We included this discussion in the paper.
 
-Based on your suggestion of looking at other newer or higher-voted answers, we performed an investigation of all the answers in 100 posts containing outdated code snippets as accepted answers.
-We found that there were 34 posts which contains newer answers.
-Regarding the number of votes, there were 5 posts which contained other answers with a higher number of votes than the outdated answer.
-Ninety-nine out of the one hundred outdated code were still marked as accepted answers.
-This discussion of the findings is added to the the RQ4.
+Based on your suggestion of looking at other newer or higher-voted answers, we
+performed an investigation of all the answers in 100 posts containing outdated
+code snippets as accepted answers. We found that there were 34 posts which
+contains newer answers. Regarding the number of votes, there were 5 posts which
+contained other answers with a higher number of votes than the outdated answer.
+Ninety-nine out of the one hundred outdated code snippets were still marked as accepted
+answers. This discussion of the findings is added to RQ4.
 
-\rcomment{
-	In section 2.4, you consider a change to the code in the Q project to be evidence that the snippet is outdated.
-How do you control for changes that are simply due to evolution?
-For example, what if I refactor the code and change the variable names of the snippet.
-}
+\rcomment{ In section 2.4, you consider a change to the code in the Q project to
+	be evidence that the snippet is outdated. How do you control for changes that
+	are simply due to evolution? For example, what if I refactor the code and change
+	the variable names of the snippet. }
 
-Good point.
-Although we grouped the code modifications that make Stack Overflow snippets outdated into 6 categories as shown in Table 9, we did not investigate the motivation of the changes such as code refactoring or variable renaming.
-We have performed the check as you suggested by checking the commit message of each change that make the code outdated.
-The findings are discussed below and are included in the RQ4.
+Good point. Although we grouped the code modifications that make Stack Overflow
+snippets outdated into 6 categories as shown in Table 9, we did not investigate
+the motivation of the changes such as code refactoring or variable renaming. We
+have performed the check as you suggested by checking the commit message of each
+change that make the code outdated. The findings are discussed below and are
+included in RQ4.
 
-We looked through the commit history of 100 outdated code snippets and summarised the reasons of code updates.
-We carefully read the commit messages and/or used the bug IDs in the commit messages to obtain more information from the bug report systems.
-We summarised the reasons of code changes into 6 groups as shown in the table below.
+We looked through the commit history of 100 outdated code snippets and
+summarised the reasons of code updates. We carefully read the commit messages
+and/or used the bug IDs in the commit messages to obtain more information from
+the bug report systems. We summarised the reasons of code changes into 6 groups
+as shown in the table below.
 
@@
 
-The majority, 64, of the changes are due to code enhancement, such as adding a new features or improving existing code to support a newer version of the language or APIs.
-Fifteen changes are for removal of dead or deprecated code such as SQL connection code example in Hibernate.
-Ten changes are made to fix bugs in the software (e.g.~array reference, race condition, wrong field access, \texttt{NullPointerException}).
-There are 6 changes for code refactoring, 3 changes for updating coding styles using an automated tool or manually, and 2 changes that are caused by the change of data format.
+The majority (64) of the changes are due to code enhancement, such as adding a
+new features or improving existing code to support a newer version of the
+language or APIs. Fifteen changes are for removal of dead or deprecated code
+such as the SQL connection code example in Hibernate. Ten changes are made to
+fix bugs in the software (e.g.~array reference, race condition, wrong field
+access, \texttt{NullPointerException}). There are 6 changes for code
+refactoring, 3 changes for updating coding styles using an automated tool or
+manually, and 2 changes that are caused by the change of data format.
 
-\rcomment{
-	\textbf{Data used:} why is the SO data from Jan.
-2016?
-This dump is now 2 years old!
-I can see why you used an older version of the Qualitas dataset, but I cannot understand why you would want to use an old version of the SO data.
-Please explain.
-}
+\rcomment{ \textbf{Data used:} why is the SO data from Jan. 2016? This dump is
+	now 2 years old! I can see why you used an older version of the Qualitas
+	dataset, but I cannot understand why you would want to use an old version of the
+	SO data. Please explain. }
 
-We used the Stack Overflow data dump of January 2016 since it was the latest dump when we started our experiment.
-Nonetheless, we finally completed the whole experiment, the result analysis, and the survey two years later.
-That is why the dump is 2 years old.
+We used the Stack Overflow data dump of January 2016 since it was the latest
+dump when we started our experiment. We completed the whole
+experiment, the result analysis, and the survey two years later. That is why the
+dump is 2 years old.
 
-Fortunately, we could use this opportunity to study the evolution of the toxic code snippets on Stack Overflow.
-We manually investigated the outdated and license incompatible code snippets that we discovered to see whether they are still the same.
-The check was performed on 6 May 2018, approximately 2 years after the snapshot was created.
-Moreover, we also checked if there is any comment regarding the outdated code or the license of the snippets from other Stack Overflow users.
-From the 100 outdated answers, we found that four answers were deleted and six answers contained a comment mentioning either the code is intended for a specific version of the software/API or complaining that the code is not working or having an issue.
-We included this discussion in RQ4.
+Fortunately, we could use this opportunity to study the evolution of the toxic
+code snippets on Stack Overflow. We manually investigated the outdated and
+license incompatible code snippets that we discovered to see whether they are
+still the same. The check was performed on 6 May 2018, approximately 2 years
+after the snapshot was created. Moreover, we also checked if there is any
+comment regarding the outdated code or the license of the snippets from other
+Stack Overflow users. From the 100 outdated answers, we found that four answers
+were deleted and six answers contained a comment mentioning either the code is
+intended for a specific version of the software/API or complaining that the code
+is not working or having an issue. We included this discussion in RQ4.
 
-\rcomment{
-	\textbf{Arbitrary use of parameter:} On page 4, you use snippets of at least 10 lines.
-Why 10, why not 15?
-Given that this is a journal paper, you have the space to examine the impact of your parameters (at least in brief) on your results.
-What I would like the authors to do is to actually examine the impact of such parameters on your work in a discussion section.}
+\rcomment{ \textbf{Arbitrary use of parameter:} On page 4, you use snippets of
+	at least 10 lines. Why 10, why not 15? Given that this is a journal paper, you
+	have the space to examine the impact of your parameters (at least in brief) on
+	your results. What I would like the authors to do is to actually examine the
+	impact of such parameters on your work in a discussion section.}
 
-That is a fair point.
-The reason we chose the clone size of at least 10 lines is because it is considered a standard setting for clone detection in large-scale data sets to avoid trivial clones (e.g.
-\texttt{equals}, \texttt{hashCode}, or getter and setter methods) in the analysis or the manual investigation phase~\citep{Sajnani2016}.
+That is a fair point. The reason we chose the clone size of at least 10 lines is
+because it is considered a standard setting for clone detection in large-scale
+data sets to avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or
+getter and setter methods) in the analysis or the manual investigation
+phase~\citep{Sajnani2016}.
 
-%Choosing this size threshold larger than 10 could possibly remove some non-trivial clones from the analysis, i.e.~create more false negatives.
-%On the other hand, decreasing the threshold to be lower than 10 lines will result in a larger number of clone candidate pairs to look at and a higher chance of getting false positives.
-Moreover, the large number of clone pairs will hinders the full manual validation of the clones and force us to rely on sampling of clone pairs.
-We performed a small analysis to confirm this.
+%Choosing this size threshold larger than 10 could possibly remove some
+% non-trivial clones from the analysis, i.e.~create more false negatives.
+%On the other hand, decreasing the threshold to be lower than 10 lines will
+% result in a larger number of clone candidate pairs to look at and a higher
+% chance of getting false positives. Moreover, the large number of clone pairs
+% will hinders the full manual validation of the clones and force us to rely on
+% sampling of clone pairs. We performed a small analysis to confirm this.
 %
@@
 %
-%Regarding increasing the minimum clone size to more than 10 lines (e.g.
-15 lines), we added an analysis of the clone size as shown in Figure \ref{fig:boxplotclonesize}.
-We found that the distribution of true clones; QS, SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines.
-Increasing the threshold to be higher than 10 would remove some of the trivial BP and IN clone pairs which are not interesting for this study.
-However, it will also remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.
+%Regarding increasing the minimum clone size to more than 10 lines (e.g. 15
+% lines), we added an analysis of the clone size as shown in Figure
+% \ref{fig:boxplotclonesize}. We found that the distribution of true clones; QS,
+% SQ, UD, EX, BP, IN; mainly cover the size from about 10 to 20 lines.
+% Increasing the threshold to be higher than 10 would remove some of the trivial
+% BP and IN clone pairs which are not interesting for this study. However, it
+% will also remove some of the true non-trivial clone pairs in QS, SQ, UD, and EX.
 %
-%Regarding decreasing the minimum clone size to be less than 10 lines, we reran the two clone detection tools (Simian and SourcererCC) again using a minimum clone size of 6 lines, another well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
-Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs using Bellon's ok-match threshold $t=0.5$.
-With this large amount of clone candidate pairs, it is not feasible to manually confirm all of the clones and we must rely on sampling.
-Moreover, it is known that lowering the number of minimum clone lines is harmful to precision.
-This will result in weaker findings and weaker conclusion.
-Thus, we decide to retain the minimum clone size of 10 lines to keep the balance between the number of non-trivial clone pairs and the feasibility of manual clone investigation.
+%Regarding decreasing the minimum clone size to be less than 10 lines, we reran
+% the two clone detection tools (Simian and SourcererCC) again using a minimum
+% clone size of 6 lines, another well-accepted minimum clone size in clone
+% benchmark~\citep{Bellon2007}. Simian reported 67,172 clone candidate pairs and
+% SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs
+% using Bellon's ok-match threshold $t=0.5$. With this large amount of clone
+% candidate pairs, it is not feasible to manually confirm all of the clones and
+% we must rely on sampling. Moreover, it is known that lowering the number of
+% minimum clone lines is harmful to precision. This will result in weaker
+% findings and weaker conclusion. Thus, we decide to retain the minimum clone
+% size of 10 lines to keep the balance between the number of non-trivial clone
+% pairs and the feasibility of manual clone investigation.
 
 To measure the impact of this minimum clone size threshold on the clone results,
-we performed an investigation of three different threshold values: six, ten, and fifteen lines. 
-We started our investigation by using a threshold value of six
-lines, a well-accepted minimum clone size in clone benchmark~\cite{Bellon2007}.
+we performed an investigation of three different threshold values: six, ten, and
+fifteen lines. We started our investigation by using a threshold value of six
+lines, a well-accepted minimum clone size in clone benchmark~\citep{Bellon2007}.
 Simian reported 67,172 clone candidate pairs and SourcererCC reported 7,752
 clone candidate pairs. We randomly sampled 382 pairs from the two sets for
-manual check. This sample amount was a statistical significant sample with a
+manual check. This sample number was a statistical significant sample with a
 95\% confidence level and $\pm 5\%$ confidence interval. The first author
@@
 setter methods), and non-trivial clones. The manual check found 26 non-clone
-pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we increased the
-threshold to ten lines, another well-established minimum clone size for
-large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs from
-Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and manually
-checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
-clone pairs and 102 non-trivial clone pairs. Then, we increased the threshold
-further to fifteen lines and retrieved 196 clone pairs from Simian and 1,230
-clone pairs from SourcererCC. The manual check of the 382 randomly sampled pairs
-reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial clone
-pairs.
+pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we
+increased the threshold to ten lines, another well-established minimum clone
+size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs
+from Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and
+manually checked the same amount of 382 pairs and found 27 non-clone pairs, 253
+trivial clone pairs and 102 non-trivial clone pairs. Then, we increased the
+threshold further to fifteen lines and retrieved 196 clone pairs from Simian and
+1,230 clone pairs from SourcererCC. The manual check of the 382 randomly sampled
+pairs reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial
+clone pairs.
 
-The findings from the three threshold values show that selecting the minimum clone size 
-of ten lines was preferred over six and fifteen lines. First, it generated 
-a fewer number of clone pairs than using six lines, which made the manual clone
-investigation feasible. Second, it preserved the highest number of non-trivial clone
-pairs.
+The findings from the three threshold values show that selecting the minimum
+clone size of ten lines was preferred over six and fifteen lines. First, it
+generated a fewer number of clone pairs than using six lines, which made the
+manual clone investigation feasible. Second, it preserved the highest number of
+non-trivial clone pairs.
 
-We have modified the paper to include this discussion at the end of Section 2.2.1.
+We have modified the paper to include this discussion at the end of Section
+2.2.1.
 
-\rcomment{
- A similar concern exists on page 5, where t=0.7 is chosen.
-Sure, it worked in another context, but did they show that a 0.7 threshold is OK to use for SO snippets?
-I think you can also vary this t value and examine its impact.
+\rcomment{ A similar concern exists on page 5, where t=0.7 is chosen. Sure, it
+	worked in another context, but did they show that a 0.7 threshold is OK to use
+	for SO snippets? I think you can also vary this t value and examine its impact.
 }
 
-We selected the Bellon's ok-match threshold of 0.7 because it is a standard value in clone benchmarking \citep{Bellon2007} and also used in other studies of clones, e.g.~\cite{Sajnani2016}.
-Nevertheless, we agree that varying the threshold ($t$) value is beneficial to the validity of the findings so we did an analysis by choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
-As shown in the our paper, by setting $t=0.7$ according to Bellon's study, we found 97 ok-match pairs reported.
-On the other hand, setting $t$ to 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
-Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually checked all the 111 reported pairs.
-We found one false positive pair and 110 true positive pairs.
-By raising the $t$ to 0.3 and 0.5, we got rid of the false positive pair and still retained all the 110 true positive pairs.
-All the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a subset of $t=0.5$.
-However, since there is a fewer true positive pairs reported (i.e.~generating false negatives), we ended up leaving some duplicates of the same clone pairs (that were supposed to be merged) in the final merged clone set.
+We selected Bellon's ok-match threshold of 0.7 because it is a standard value in
+clone benchmarking \citep{Bellon2007} and also used in other studies of clones,
+e.g.~\cite{Sajnani2016}. Nevertheless, we agree that varying the threshold ($t$)
+value is beneficial to the validity of the findings so we did an analysis by
+choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone
+candidates. As shown in the our paper, by setting $t=0.7$ according to Bellon's
+study, we found 97 ok-match pairs reported. On the other hand, setting $t$ to
+0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs
+respectively. Since the clone pairs of $t=0.1$ was the superset of other sets, 
+we manually checked all the 111 reported pairs. We found one false positive pair
+and 110 true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of
+the false positive pair and still retained all the 110 true positive pairs. All
+the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to
+being a subset of $t=0.5$. However, since there is a fewer true positive pairs
+reported (i.e.~generating false negatives), we ended up leaving some duplicates
+of the same clone pairs (that were supposed to be merged) in the final merged
+clone set.
 
-With this analysis, we can see that setting the threshold $t$ to 0.1 is too relaxed and results in having false positive ok-match pairs, while setting the $t$ to 0.7 or 0.9 is too strict and generates some false negative pairs.
-Thus, we decided to select the $t$ value at 0.5.
-This reduces the number of merged clone pairs to 2,289 pairs.
-All other numbers which derive from this merged clone pairs have been updated accordingly.
+With this analysis, we can see that setting the threshold $t$ to 0.1 is too
+relaxed and results in having false positive ok-match pairs, while setting the
+$t$ to 0.7 or 0.9 is too strict and generates some false negative pairs. Thus,
+we decided to select the $t$ value at 0.5. This reduces the number of merged
+clone pairs to 2,289 pairs. All other numbers which derive from this merged
+clone pairs have been updated accordingly.
 
-\rcomment{
-	\textbf{Question about clone patterns:} Table 4 lists all the clone patterns you considered.
-First, I have a major concern about the two most interesting patterns Q->S and S->Q.
-Especially in the case of S->Q, how can you be sure that this code actually came from SO?
-It could have come from any other project or from SO or another forum.
-Also, for Q->S, how can you be sure these snippets came from the Q projects?
-This is somewhat of a major concern since the rest of your paper is built on this.
-I would like to see a clear explanation of how we can be sure about this.
+\rcomment{ \textbf{Question about clone patterns:} Table 4 lists all the clone
+	patterns you considered. First, I have a major concern about the two most
+	interesting patterns Q->S and S->Q. Especially in the case of S->Q, how can you
+	be sure that this code actually came from SO? It could have come from any other
+	project or from SO or another forum. Also, for Q->S, how can you be sure these
+	snippets came from the Q projects? This is somewhat of a major concern since the
+	rest of your paper is built on this. I would like to see a clear explanation of
+	how we can be sure about this.
 
-	\vspace{1ex}
-	Now, you can say that we see code that is similar in Q and S or S and Q, but you can (almost) never say that this code comes from SO or from Q (to SO).
-This puts your toxic code idea into question and makes me take the results of RQs 1 and 2 with a grain of salt.
+	\vspace{1ex} Now, you can say that we see code that is similar in Q and S or S
+	and Q, but you can (almost) never say that this code comes from SO or from Q
+	(to SO). This puts your toxic code idea into question and makes me take the
+	results of RQs 1 and 2 with a grain of salt.
 
-	\vspace{1ex}
-	In fact, in the answer of RQ1, you explicitly say ``...share similar code with SO ...'', but throughout the paper, you present the work as if the code came from SO -> Q or vice versa.
-}
+	\vspace{1ex} In fact, in the answer of RQ1, you explicitly say ``...share
+	similar code with SO ...'', but throughout the paper, you present the work as
+	if the code came from SO -> Q or vice versa. }
 
-For the QS clone pairs, as explained in Section 2.2.3 (The online cloning classification patterns) and Section 3.3 (RQ3: Patterns of Online Code Cloning), we \textbf{manually confirmed with evidence} that the Stack Overflow code snippets were actually copied from Qualitas projects.
-This was done by the two authors reading the Stack Overflow answers containing the QS code snippets and looked for evidence such as explanation in the text or the code comments and made their decision.
-The two authors also compared their results and discussed until a consensus was made.
-Similarly, the same process was applied for the SQ clone pair.
-%For the SQ pair we discovered, we found
+For the QS clone pairs, as explained in Section 2.2.3 (The online cloning
+classification patterns) and Section 3.3 (RQ3: Patterns of Online Code Cloning),
+we \textbf{manually confirmed with evidence} that the Stack Overflow code
+snippets were actually copied from Qualitas projects. This was done by the two
+authors reading the Stack Overflow answers containing the QS code snippets and
+looked for evidence such as explanation in the text or the code comments and
+made their decision. The two authors also compared their results and discussed
+until a consensus was made. Similarly, the same process was applied for the SQ
+clone pair. %For the SQ pair we discovered, we found
 %evidence of cloning from Stack Overflow post ID 698283 to
@@
 %{\small\texttt{findMethodToInvoke}} method depicted in Figure 7 in Stack
-%Overflow is very similar to the code in \textsf{jstock} including comments, it is almost certain that
-%the two code snippets form a clone pair. In addition, the Stack Overflow answer was
+%Overflow is very similar to the code in \textsf{jstock} including comments, it
+% is almost certain that
+%the two code snippets form a clone pair. In addition, the Stack Overflow answer
+% was
 %posted on March 30, 2009, while the code in {\small\texttt{POIUtils}} class in
 %\textsf{jstock} was committed to GitHub on the next day of March 31, 2009.
-In case of a doubt or not enough cloning evidence and the clone pairs did not fit into EX, BP and IN, we always categorised the clone pairs into UD (unknown direction) instead.
+In case of a doubt or not enough cloning evidence and the clone pairs did not
+fit into EX, BP and IN, we always categorised the clone pairs into UD (unknown
+direction) instead.
 
 To emphasise this point, we also modified the answer of the RQ2 to be clearer.
-It now says \textit{``To answer RQ2, we found 2,076 manually confirmed clone pairs between 443 Stack Overflow code snippets
-and 59 Qualitas proejcts.''.}
+It now says \textit{``To answer RQ2, we found 2,076 manually confirmed clone
+	pairs between 443 Stack Overflow code snippets and 59 Qualitas proejcts.''.}
 
-\rcomment{
-	And given the types of clones you find (e.g., BP code), this can really come from anywhere (and more likely to come from things like tutorials or IDEs).
-Then, you report that 65\% of the closes are BP.
-AC is also not a clone really since even in your Table 4 you said AC is false clones - how can an Accidental *clone* be a false clone?
-If something is false, then it is not a clone.
-}
+\rcomment{ And given the types of clones you find (e.g., BP code), this can
+	really come from anywhere (and more likely to come from things like tutorials or
+	IDEs). Then, you report that 65\% of the closes are BP. AC is also not a clone
+	really since even in your Table 4 you said AC is false clones - how can an
+	Accidental *clone* be a false clone? If something is false, then it is not a
+	clone. }
 
-You are correct regarding the BP clone pairs.
-They can really come from anywhere (we did find that some of the BP clone pairs were auto-generated code by NetBeans).
-Therefore, we did not draw any conclusion about them in the paper.
-Moreover, thank you for pointing out the inappropriate naming for AC. We now renamed them from AC to NC (i.e.~Not Clones).
+You are correct regarding the BP clone pairs. They can really come from anywhere
+(we did find that some of the BP clone pairs were auto-generated code by
+NetBeans). Therefore, we did not draw any conclusion about them in the paper.
+Moreover, thank you for pointing out the inappropriate naming for AC. We now
+renamed them from AC to NC (i.e.~Not Clones).
 
-\rcomment{
-I feel that the strongest part of the paper is the survey section.
-I really enjoyed the findings and think that the community can learn something from the outcomes of the survey (especially section 3.5.5).
-However, I did find the question in section 3.5.3 to be unfair somehow since there is really no mechanism in SO to notify anyone who used a code snippet.
-In fact, no one even knows who used a code snippet from SO.
-}
+\rcomment{ I feel that the strongest part of the paper is the survey section. I
+	really enjoyed the findings and think that the community can learn something
+	from the outcomes of the survey (especially section 3.5.5). However, I did find
+	the question in section 3.5.3 to be unfair somehow since there is really no
+	mechanism in SO to notify anyone who used a code snippet. In fact, no one even
+	knows who used a code snippet from SO. }
 
 %Our apologies if the writing in section 3.5.3 confuses you.
-The research question (section 3.5.3) is actually about notifying the answerers that their answers are already outdated, not notifying the users of the outdated code snippets.
-This notification to the answerer can be done by posting comments for that answer on Stack Overflow.
-For example, the answerer of the Stack Overflow question no.~10924648 posted a comment on his own answer saying that the answer is specifically for Spring 3.1.
-Moroever, another user posted a comment on the answer of the post no.~801935 that the code snippet is not of high quality and suggested an alternative in another post.
-We extended this explanation in Section 3.1.1 (RQ1).
+The research question (section 3.5.3) is actually about notifying the answerers
+that their answers are already outdated, not notifying the users of the outdated
+code snippets. This notification to the answerer can be done by posting comments
+for that answer on Stack Overflow. For example, the answerer of the Stack
+Overflow question no.~10924648 posted a comment on his own answer saying that
+the answer is specifically for Spring 3.1. Moroever, another user posted a
+comment on the answer of the post no.~801935 that the code snippet is not of
+high quality and suggested an alternative in another post. We extended this
+explanation in Section 3.1.1 (RQ1).
 
-\rcomment{
-Perhaps minor, but this issue really did not sit well with me, in the introduction, you say in RQ5 that you survey 607 participants, but later it turns out that only 201 responded.
-To me, this is somewhat misleading and does not sit well.
-I strongly encourage the authors to refactor such `marketing' statements.
-}
+\rcomment{ Perhaps minor, but this issue really did not sit well with me, in the
+	introduction, you say in RQ5 that you survey 607 participants, but later it
+	turns out that only 201 responded. To me, this is somewhat misleading and does
+	not sit well. I strongly encourage the authors to refactor such `marketing'
+	statements. }
 
-You are right. We fixed the text in the RQ to say that we surveyed 201 participants.
+You are right. We fixed the text in the RQ to say that we surveyed 201
+participants.
 
@@
 
-\rcomment{
-There is also no discussion if partial updates to the outdate code clones where posted in the same Q\&A threat (e.g., addressed by somebody else who just mentioned the necessary modifications or provided a link to the updated code fragment).
-It would also have been interesting to know how old the Q\&As (clones) were, since the Qualitas code base is 4 years older then the StackOverflow snapshot.
-Not sure why you selected 2013 and not 2014 or 2012.
-Average and mean time/date of the clone postings on stackoverflow would be interesting to see the distribution of the clone age (simple boxplot would do).
+\rcomment{ There is also no discussion if partial updates to the outdate code
+	clones where posted in the same Q\&A threat (e.g., addressed by somebody else
+	who just mentioned the necessary modifications or provided a link to the updated
+	code fragment).  It would also have been interesting to know how old the Q\&As
+	(clones) were, since the Qualitas code base is 4 years older then the
+	StackOverflow snapshot. Not sure why you selected 2013 and not 2014 or 2012.
+	Average and mean time/date of the clone postings on stackoverflow would be
+	interesting to see the distribution of the clone age (simple boxplot would do).
 }
 
-We are grateful for the insightful comment.
-We selected the 2013 snapshot of Qualitas data since it is the latest and the most complete snapshot (i.e.~having the highest number of Java projects) provided by the data set author.
+We are grateful for the insightful comment. We selected the 2013 snapshot of
+Qualitas data since it is the latest and the most complete snapshot (i.e.~having
+the highest number of Java projects) provided by the data set author.
 
-Regarding the age of cloned code on Stack Overflow, we did an analysis of clone ages as you suggested.
-We only chose the QS clone pairs since we could manually confirmed the direction of cloning.
-Moreover, we knew the date that the original version of the QS clones appeared in Qualitas projects (we used the version release date), which was not possible for UD, EX, BP, and IN clone pairs.
-We calculated the clone ages by counting the number of month difference from the dates of each Qualitas project to the date the answers were posted on Stack Overflow.
+Regarding the age of cloned code on Stack Overflow, we did an analysis of clone
+ages as you suggested. We only chose the QS clone pairs since we could manually
+confirmed the direction of cloning. Moreover, we knew the date that the original
+version of the QS clones appeared in Qualitas projects (we used the version
+release date), which was not possible for UD, EX, BP, and IN clone pairs. We
+calculated the clone ages by counting the number of months between the date of
+each Qualitas project and the date the answer was posted on Stack Overflow.
 
-\begin{figure}[H]
-	\centering
-	\includegraphics[width=0.7\linewidth]{../boxplot_clone_age}
-	\caption{Age of QS cloned snippets}
-	\label{fig:boxplotcloneage}
-\end{figure}
+\begin{figure}[H] \centering
+	\includegraphics[width=0.7\linewidth]{../boxplot_clone_age} \caption{Age of QS
+		cloned snippets} \label{fig:boxplotcloneage} \end{figure}
 
-We drew a boxplot as you suggested (shown above) and included the discussion of the statistics in RQ4.
-We found that the minimum, maximum, median, and average clone ages were 0, 64, 26.5 and 26 months respectively.
-We observed that, on average, it took around 2 years for the clones from Qualitas projects to appear on Stack Overflow answers.
-Some of the clones appeared on Stack Overflow almost at the same time as the original, while the oldest clones took around 5 years.
+We drew a boxplot as you suggested (shown above) and included the discussion of
+the statistics in RQ4. We found that the minimum, maximum, median, and average
+clone ages were 0, 64, 26.5 and 26 months respectively. We observed that, on
+average, it took around 2 years for the clones from Qualitas projects to appear
+on Stack Overflow answers. Some of the clones appeared on Stack Overflow almost
+at the same time as the original, while the oldest clones took around 5 years.
 
-\rcomment{
-I do believe the survey results from the StackOverflow contributors actually provides more meaningful insights then then the clone detection itself, since the responses by the contributors actually help explaining some of the results.
-The authors should provide further analysis and interpretation of the survey results.
-}
+\rcomment{ I do believe the survey results from the StackOverflow contributors
+	actually provides more meaningful insights then then the clone detection itself,
+	since the responses by the contributors actually help explaining some of the
+	results. The authors should provide further analysis and interpretation of the
+	survey results. }
 
-We moved them to RQ1 to better link with the motivation.
-We also expanded the findings to include another survey, the Stack Overflow visitor survey, in order to understand the awareness of the developers on both sides: the answerers and the visitors (i.e.~information seekers).
-We asked the visitors their experience regarding outdated and license-incompatible code caused by copying and reusing code snippets from Stack Overflow.
-The findings are incorporated into RQ1.
+We moved them to RQ1 to better link with the motivation. We also expanded the
+findings to include another survey, the Stack Overflow visitor survey, in order
+to understand the awareness of the developers on both sides: the answerers and
+the visitors (i.e.~information seekers). We asked the visitors their experience
+regarding outdated and license-incompatible code caused by copying and reusing
+code snippets from Stack Overflow. The findings are incorporated into RQ1.
 
-\rcomment{
-Overall discussion is very weak.
-While the authors went through a lengthy and detailed study of code clones published on StackOverflow and the survey of StackOverflow contributors, the paper lacks really a take home message.
-At the end there is no real evidence that either code clones are really toxic or bad (are they actually causing problems?
-due to the use of clones.
-Just because a code fragment is outdated does not mean it is necessarily bad or causes any problems.
-What is the actual take home message from your study?
-Should we stop reusing code from StackOverflow?
-I do believe there is a need to dig deeper in the observed data and draw some real conclusions on how the observed results can benefit both the StackOverflow community and the source code community.
-}
+\rcomment{ Overall discussion is very weak. While the authors went through a
+	lengthy and detailed study of code clones published on StackOverflow and the
+	survey of StackOverflow contributors, the paper lacks really a take home
+	message. At the end there is no real evidence that either code clones are really
+	toxic or bad (are they actually causing problems? due to the use of clones. Just
+	because a code fragment is outdated does not mean it is necessarily bad or
+	causes any problems. What is the actual take home message from your study?
+	Should we stop reusing code from StackOverflow? I do believe there is a need to
+	dig deeper in the observed data and draw some real conclusions on how the
+	observed results can benefit both the StackOverflow community and the source
+	code community. }
 
@@
 First, from the answer to Reviewer 2, we analysed the intent behind the changes that made the code outdated and found that only 10 out of 100 cases were bug fixes.
-Besides that, the code were outdated because of evolution in the software (adding or enhancing features, refactoring, changing coding style, and data change).
+Besides that, the code snippets were outdated because of evolution in the software (adding or enhancing features, refactoring, changing coding style, and data change).
 Thus, outdated code can sometimes become toxic, but not always.
 
-Second, as previously discussed in the answer to Reviewer 1, we have performed an additional experiment to search for occurrences of the 100 outdated code snippets in 130,703 open source GitHub projects and found 102 occurrences of the outdated code.
+Second, as previously discussed in the answer to Reviewer 1, we have performed an additional experiment to search for occurrences of the 100 outdated code snippets in 130,703 open source GitHub projects and found 102 clones of 30 outdated code snippets.
 47 were exact copy of the outdated versions, of which 12 were buggy.
-However, we could not establish evidence that the outdated code were cloned from Stack Overflow or somewhere else.
+However, we could not establish evidence that the outdated code snippets were cloned from Stack Overflow or somewhere else.
 We have reported the problem of race condition in two clone snippets found in deeplearning4j and Apache Hive to the developers.
@@
 To summarise, we empirically show from the surveys and the clone detection experiment that online code clones occur on Stack Overflow and the clones may become toxic due to outdated code and software license incompatibility.
-For outdated code, we found only a small amount of clones.
+For outdated code, we found only a small number of clones.
 Although other studies show that Stack Overflow code snippets may contain security vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we found in this study that the damage caused by reusing outdated code on Stack Overflow is not high.
-On the other hand, the missing of licensing statement of online code clones on Stack Overflow can be more harmful.
+On the other hand, the missing licensing statements of online code clones on Stack Overflow can be more harmful.
 As shown in our study and also in the study by \cite{An2017}, some online clones on Stack Overflow are originally licensed under more restrictive license than Stack Overflow's CC BY-SA 3.0.
-If these missing-license online clones are reused in a software with incompatible license, the software owner may face legal issues.
-The software auditing service such as Black Duck Software or nexB, which can effectively check for license compliance of code copied from open source projects, cannot check for the original license of the code snippets on Stack Overflow.
-Although Stack Overflow answerers participated in our survey believe that most of the code snippets on Stack Overflow are too small to claim for copyright and they fall under fair-use, there is still a risk due to different legal system in each country.
-For example, Germany legal system does not have a concept of fair use or the number of minimum lines of code to be consider trivial, i.e.~de minimis, is also different from case to case or from country to country.
+If these missing-license online clones are reused in a software with an incompatible license, the software owner may face legal issues.
+Software auditing services such as Black Duck Software or nexB, which can effectively check for license compliance of code copied from open source projects, do not check for the original license of the code snippets on Stack Overflow.
+Although the Stack Overflow answerers who participated in our survey believe that most of the code snippets on Stack Overflow are too small to claim for copyright and they fall under fair-use, there is still a risk due to different legal systems in each country.
+For example, Germany's legal system does not have a concept of fair use or the number of minimum lines of code to be considered trivial, i.e.~de minimis, is also different from case to case or from country to country.
 

### 2018-05-24 cloverflow-tse/cover_letter/cover_letter.tex
After the Grammarly check.

@@
 no.~TSE-2017-11-0335 and we would like to thank the anonymous reviewers for
-taking their time to carefully read our paper. With their useful and
+taking their time to read our paper carefully. With their useful and
 constructive reviews, we substantially improved the work by adding five major
@@
 \textbf{1.~A Stack Overflow Visitor survey}~To understand the effects of toxic
-code snippets on Stack Overflow to information seekers who look for coding
+code snippets to information seekers who look for coding
 solutions on Stack Overflow, we performed another survey of 87 Stack Overflow
@@
 \textbf{4.~An extended analysis of outdated code clones:}~We performed an
-extended analysis on the 100 outdated code snippets. For example, we analysed
-age of the clones; studied effects of comments, newer answers, higher-voted
-answers on the outdated answers; and summarised the six intents that made the
-clones outdated. We found that, on average, the code is cloned to Stack Overflow
-2 years after it appears in Qualitas projects, and comments/newer or
+extended analysis of the 100 outdated code snippets. For example, we analysed
+the age of the clones; studied effects of comments, newer answers, higher-voted
+answers on the outdated answers; and summarised six intents that made the
+clones outdated. We found that, on average, the outdated code snippets were cloned to Stack Overflow
+2 years after it appeared in Qualitas projects, and comments/newer or
 higher-voted answers did not strongly affect the outdated answers (99\% are
-still marked as accepted). Lastly, we discovered that the code are outdated
+still marked as accepted). Lastly, we discovered that the code snippets are outdated
 because of code enhancement (65\%), followed by code deprecation (15\%), but
@@
 
+\clearpage
 We also tried our best to address all the comments from the reviewers. Every
-comment led to an improvement on this submission and we discuss them in order as
+comment led to an improvement on this submission, and we discuss them in order as
 shown in the next sections.
@@
 
-\rcomment{
-Regarding this statement: \textit{``It is probably more important than studying the effects of reusing Stack Overflow code snippets because it gives insights to the root cause of the problem and lays a foundation to an automatic technique to detect and report toxic code snippets on Stack Overflow to developers in the future.''}
+\rcomment{ Regarding this statement: \textit{``It is probably more important
+		than studying the effects of reusing Stack Overflow code snippets because it
+		gives insights to the root cause of the problem and lays a foundation to an
+		automatic technique to detect and report toxic code snippets on Stack Overflow
+		to developers in the future.''}
 
-While~\cite{An2017} do suggest that copying from Stack Overflow to software projects occurs (and results in license violations), they do not establish that code snippets from Stack Overflow \textit{``go viral''} and end up distributed widely across (open or closed source) software projects.
-Moreover, while the quote on the first page implies that developers often \textit{``mindlessly''} reuse code snippets from Stack Overflow, to the best of my knowledge, this claim is conventional wisdom but not empirically validated.
-So, it seems to me that the primary interest in toxic code snippets is that may cause widespread harm, but I am missing the evidence that they do so in practice.
-Even assuming that code snippets from Stack Overflow are distributed mindlessly and widely, I wonder how many code snippets on Stack Overflow are toxic, the extent to which they are reused without modification (or with only minor adaptation), what kinds of projects they end up in (i.e., a popular project from Microsoft or Apache vs.
-a hobby project by a single developer vs.
-a student solution to an assignment), and ultimately, how much damage can we expect them to cause.
-In the end, I agree that it is better to detect and report toxic code snippets than to not do so, but I am not sure how big of a problem is solved by doing so.
-As such, I disagree that it is \textit{``probably more important''} to find the toxic code snippets than to understand their effects.
-Instead, I think that understanding their effects (on software projects rather than on the quality of the Stack Overflow platform) is necessary to appreciate the value in finding them.
-}
+	While~\cite{An2017} do suggest that copying from Stack Overflow to software
+	projects occurs (and results in license violations), they do not establish that
+	code snippets from Stack Overflow \textit{``go viral''} and end up distributed
+	widely across (open or closed source) software projects. Moreover, while the
+	quote on the first page implies that developers often \textit{``mindlessly''}
+	reuse code snippets from Stack Overflow, to the best of my knowledge, this claim
+	is conventional wisdom but not empirically validated. So, it seems to me that
+	the primary interest in toxic code snippets is that may cause widespread harm,
+	but I am missing the evidence that they do so in practice. Even assuming that
+	code snippets from Stack Overflow are distributed mindlessly and widely, I
+	wonder how many code snippets on Stack Overflow are toxic, the extent to which
+	they are reused without modification (or with only minor adaptation), what kinds
+	of projects they end up in (i.e., a popular project from Microsoft or Apache vs.
+	a hobby project by a single developer vs. a student solution to an assignment),
+	and ultimately, how much damage can we expect them to cause. In the end, I agree
+	that it is better to detect and report toxic code snippets than to not do so,
+	but I am not sure how big of a problem is solved by doing so. As such, I
+	disagree that it is \textit{``probably more important''} to find the toxic code
+	snippets than to understand their effects. Instead, I think that understanding
+	their effects (on software projects rather than on the quality of the Stack
+	Overflow platform) is necessary to appreciate the value in finding them. }
 
-We would like to thank the reviewer for the comments.~We agree with the suggestion and we made the following changes to the paper:
+We would like to thank the reviewer for the comments.~We agree with the
+suggestion, and we made the following changes to the paper:
 
-\begin{enumerate}
-	\item We understand the concern of finding real evidence to support the claim that code snippets on Stack Overflow do appear in open- or closed-source software projects.
-Hence, we have performed a study of code clone detection between our 100 reported outdated code snippets on Stack Overflow and 131,703 GitHub projects.
-We selected SourcererCC with 80\% similarity for this experiment because it could scale to a large-scale data set, while Simian could not.
-We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all of them.
-As shown in Table~\ref{tab:outdated_github} below, out of the 102 cloned snippets, there were 13 cloned snippets that matched with themselves because some of the Qualitas projects also appear on GitHub.
-For other projects besides the Qualitas projects, there were 47 cloned snippets that were exactly the same as the outdated code snippet and 42 cloned snippets that were not exactly the same (e.g.~they contained additional code modifications made by the projects' developers or they were copied from another source with a slightly different code).
+\begin{enumerate} \item We understand the concern of finding real evidence to
+	support the claim that code snippets on Stack Overflow do appear in open- or
+	closed-source software projects. Hence, we have performed a study of code clone
+	detection between our 100 reported outdated code snippets on Stack Overflow and
+	131,703 GitHub projects. We selected SourcererCC with 80\% similarity for this
+	experiment because it could scale to a large-scale data set, while Simian could
+	not. We found 102 cloned candidates appearing in 68 GitHub projects and manually
+	investigated all of them. As shown in Table~\ref{tab:outdated_github} below, out
+	of the 102 cloned snippets, 13 cloned snippets matched with
+	themselves because some of the Qualitas projects also appear on GitHub. For
+	other projects besides the Qualitas projects, 47 cloned snippets
+	were exactly the same as the outdated code snippet and 42 cloned snippets that
+	were not the same (e.g.,~they contained additional code modifications
+	made by the projects' developers, or they were copied from another source with a
+	slightly different code).
 
@@
 snippets that gave attributions to Stack Overflow. However, the attributions
-pointed to different posts than the ones we found, but containing the same code
+pointed to different posts than the ones we found but containing the same code
 in the answers. The other 32 cloned snippets were very likely to be a
-file-level clone from its respective original project (e.g. JFreeChart, JUnit,
+file-level clone from its respective original project (e.g.,~JFreeChart, JUnit,
 Log4J, Hadoop) based on their license header and the Javadoc comments. Lastly,
@@
 Stack Overflow, license-incompatible code snippets. We detected clones between
-the 214 code snippets without their original license (86 QS, 78 EX and 50 UD) 
+the 214 code snippets without their original license (86 QS, 78 EX, and 50 UD) 
 and 130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
@@
 Qualitas projects hosted on GitHub and 7,112 pairs from 2,427 other projects.
-Then, we used the Ninka tool to automatically identify
-software licenses from the reported cloned snippets. Shown in
+Then, we used the Ninka tool to identify
+software licenses from the reported cloned snippets automatically. Shown in
 Table \ref{tab:license_github} below, the clones were found in highly-starred
@@
 snippets did not have a license while the originals had the Apache-2, GPLv2, or EPLv1
-license. One snippets had the AGPLv3 license while the original had the Apache-2
+license. One snippet had the AGPLv3 license while the original had the Apache-2
 license. Only 995 code snippets in GitHub projects have the same license
@@
 small number of toxic code snippets from outdated code that are found in GitHub
-projects, (2) there is a large number of toxic code snippets caused by missing
+projects, (2) there is a large number of toxic code snippets caused by a missing
 license that are found in GitHub projects. %Moreover, the direction of copying
@@
 including the results from another survey of Stack Overflow visitors
-(i.e.~information seekers). This survey of the Stack Overflow visitors was
+(i.e.,~information seekers). This survey of the Stack Overflow visitors was
 performed during the same time as the Stack Overflow answerers (25 July 2017 to
-25 September 2017) and the full results are reported in our technical
+25 September 2017), and the full results are reported in our technical
 report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the
 previous version of the paper due to a smaller sample size compared to the
-answerers survey. However, we did find some interesting results so we have
-included them into this version and discussed the key findings in~RQ1. The brief
+answerers' survey. However, we did find some interesting results, so we have
+included them in this version and discussed the key findings in~RQ1. The brief
 summary of the visitor survey is as follows.
@@
 
-The visitors survey confirms the findings from the previous studies that Stack
+The visitors' survey confirms the findings from the previous studies that Stack
 Overflow code snippets can be problematic~\citep{Zhang2018,Acar2016,An2017}. Sixty-six
@@
 Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
-check if the code snippet originated from a different source (e.g.~an open source project) 
+check if the code snippet originated from a different source (e.g.,~an open source project) 
 and if they had an incompatible license to their projects.
@@
 	source projects on GitHub. Therefore, the damage is not high since there are only
-	a few outdated code snippets that are harmful for reuse. On the other hand, the
+	a few outdated code snippets that are harmful to reuse. On the other hand, the
 	problem of license incompatibility caused by missing original licenses in Stack
 	Overflow code snippets can cause more damage than outdated code. Different legal
-	system and different interpretation of fair-use concept and de minimis (i.e.~the
+	system and different interpretation of fair-use concept and de minimis (i.e.,~the
 	minimal lines of code allowed to be copied without violating copyright) in each
-	country can make a reuse of these code snippets legally problematic.
+	country can make reuse of these code snippets legally problematic.
 
@@
 You are right. We mainly study online code clones and established their
-existence. However, we used the term ``toxic code snippets'' in order to
+existence. However, we used the term ``toxic code snippets'' to
 emphasise the possible ramifications from online code cloning. Moreover, the
 term code cloning is not well known outside the code cloning community. Code
-clones are called differently in each research community or in practice, such as
+clones are called differently in each research community or practice, such as
 duplicated code, copy-and-paste code, code reuse, software similarity or
@@
 especially on finding the origins of the clones. We tackle this challenge of
-establishing existence of online code clones and investigate how they occur in
+establishing the existence of online code clones and investigate how they occur in
 this study.'' %Considering your suggestion and another suggestion by Reviewer 2
@@
 
-That is a fair point and we would like to analyse the statistics as you
+That is a fair point, and we would like to analyse the statistics as you
 suggested. To answer your question (a), the number of views is for the whole
@@
 For (c), that is a really interesting idea. However, it is out of the scope of
-this study and would involve an extensive analysis of the data so we may
+this study and would involve extensive analysis of the data so we may
 investigate it in the future work.
@@
 Nevertheless, we have added a footnote to the text in the Introduction to
-clarify point (a).
+clarify the point (a).
 
@@
 on 31 October 2017 that highlights the missing line in HADOOP \texttt{compare}
-method is actually from a student in our class. His name is Joseph Kalash and he
+method is actually from a student in our class. His name is Joseph Kalash, and he
 is a master student in Machine Learning MsC program at UCL Computer Science
@@
 RQ4. We found that out of 100 answers containing outdated code snippets,
-there were 6 answers that had a comment saying the code in the answer is
+6 answers had a comment saying the code in the answer is
 outdated or contains issues (including Joseph's comment). Thus, there are about
@@
 
-\rcomment{ \begin{enumerate} \item Table 1 has a median column. Median of what?
+\rcomment{ \begin{enumerate} 
+		\item Table 1 has a median column. Median of what?
 		\item Section 2.1 states that comments were removed before clone detection, but
@@
 		Can the manual inspection of comments to find evidence of copying be automated
-		as part of the clone detection process? \item Typo: ``how much the community
+		as part of the clone detection process? 
+		\item Typo: ``how much the community
 		trust them'' --> ``how much the community trusts them'' \end{enumerate} }
 
-\begin{enumerate} \item For the Stack Overflow data set, the value represents
+\begin{enumerate} 
+	\item For the Stack Overflow data set, the value represents
 	the median size of Stack Overflow code snippets. For the Qualitas data set, the
-	value represents the median of number of lines of code in each project. Since
+	value represents the median of the number of lines of code in each project. Since
 	they are confusing as you pointed out, we decided to remove them from the table
-	and only discuss the numbers in the text. \item This is actually a great
-	insight! We expanded the idea further and came up with a suggestion for an
+	and only discuss the numbers in the text. 
+	\item This is a great insight! We expanded the idea further and came up with a suggestion for an
 	automated technique to facilitate human investigator on finding provenance and
 	included it in a section called Automated cloning direction detection in the
-	Overall Discussion. \item Thanks. This has been fixed. \end{enumerate}
+	Overall Discussion. 
+	\item Thanks. This has been fixed. \end{enumerate}
 
@@
 	example, their definition is ``toxic code snippets mean code snippets that are
-	harmful for reuse and, \textbf{in several cases}, are caused by online...''. A
+	harmful to reuse and, \textbf{in several cases}, are caused by online...''. A
 	definition should be clear - saying in several cases - means that in several
@@
 of a software system''~\citep{Li2015}. The new definition of toxic doe snippets
-are as follows.
+is as follows.
 
@@
 caused by outdated code and license-violating code snippets in this study since
-these two problems are still under explored compared to code
+these two problems are still underexplored compared to code
 smells~\citep{Tufano2015} or vulnerabilities~\citep{Acar2016,Fischer2017}.
@@
 originals and may contain defects. Code snippets from open source projects
-usually fall under a specific software license, e.g.\ GNU General Public License
+usually fall under a specific software license, e.g.,\ GNU General Public License
 (GPL). If they are cloned to Stack Overflow answers without the license, and
@@
 Regarding RQ5 (the Stack Overflow answerer survey), that is a good point. Since
-RQ5 actually supports the motivation of our experiment by showing that code
-copying from software projects to Stack Overflow actually occurs and showing
+RQ5 supports the motivation of our experiment by showing that code
+copying from software projects to Stack Overflow occurs and showing
 that some of the answerers are not aware of outdated code and software license
@@
 Stack Overflow allows its users to edit their own posts,
-i.e.~questions/answers\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts\footnote{https://stackoverflow.com/help/privileges/edit}.
+i.e.,~questions/answers\footnote{https://meta.stackoverflow.com/questions/315915/i-am-not-allowed-to-edit-my-own-question}, or other user's posts\footnote{https://stackoverflow.com/help/privileges/edit}.
 Thus, if the code snippet in an answer is outdated and has an issue, the answerer or other high-reputation users can update the answer to be up-to-date or to warn other users that the code is already outdated and may contain problems.
@@
 code snippets as accepted answers. We found that there were 34 posts which
-contains newer answers. Regarding the number of votes, there were 5 posts which
+contain newer answers. Regarding the number of votes, there were 5 posts which
 contained other answers with a higher number of votes than the outdated answer.
@@
 have performed the check as you suggested by checking the commit message of each
-change that make the code outdated. The findings are discussed below and are
+change that makes the code outdated. The findings are discussed below and are
 included in RQ4.
@@
 We looked through the commit history of 100 outdated code snippets and
-summarised the reasons of code updates. We carefully read the commit messages
+summarised the reasons for code updates. We carefully read the commit messages
 and/or used the bug IDs in the commit messages to obtain more information from
-the bug report systems. We summarised the reasons of code changes into 6 groups
+the bug report systems. We summarised the reasons for code changes into 6 groups
 as shown in the table below.
@@
 		Coding style & Update to a new style guideline & 3 \\
-		Data change & Changes in data format & 2 \\
+		Data change & Changes in the data format & 2 \\
 		\bottomrule
@@
 
-The majority (64) of the changes are due to code enhancement, such as adding a
+The majority (64) of the changes are due to code enhancement, such as adding
 new features or improving existing code to support a newer version of the
@@
 such as the SQL connection code example in Hibernate. Ten changes are made to
-fix bugs in the software (e.g.~array reference, race condition, wrong field
+fix bugs in the software (e.g.,~array reference, race condition, wrong field
 access, \texttt{NullPointerException}). There are 6 changes for code
@@
 because it is considered a standard setting for clone detection in large-scale
-data sets to avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or
+data sets to avoid trivial clones (e.g., \texttt{equals}, \texttt{hashCode}, or
 getter and setter methods) in the analysis or the manual investigation
@@
 clone candidate pairs. We randomly sampled 382 pairs from the two sets for
-manual check. This sample number was a statistical significant sample with a
+a manual check. This sample number was a statistically significant sample with a
 95\% confidence level and $\pm 5\%$ confidence interval. The first author
@@
 setter methods), and non-trivial clones. The manual check found 26 non-clone
-pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we
+pairs; 322 trivial clone pairs, and 34 non-trivial clone pairs. Next, we
 increased the threshold to ten lines, another well-established minimum clone
@@
 manually checked the same amount of 382 pairs and found 27 non-clone pairs, 253
-trivial clone pairs and 102 non-trivial clone pairs. Then, we increased the
+trivial clone pairs, and 102 non-trivial clone pairs. Then, we increased the
 threshold further to fifteen lines and retrieved 196 clone pairs from Simian and
 1,230 clone pairs from SourcererCC. The manual check of the 382 randomly sampled
-pairs reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial
+pairs revealed zero non-clone pairs, 298 trivial clone pairs, and 83 non-trivial
 clone pairs.
@@
 clone benchmarking \citep{Bellon2007} and also used in other studies of clones,
-e.g.~\cite{Sajnani2016}. Nevertheless, we agree that varying the threshold ($t$)
-value is beneficial to the validity of the findings so we did an analysis by
+e.g.,~\cite{Sajnani2016}. Nevertheless, we agree that varying the threshold ($t$)
+value is beneficial to the validity of the findings, so we did an analysis by
 choosing five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone
-candidates. As shown in the our paper, by setting $t=0.7$ according to Bellon's
+candidates. As shown in our paper, by setting $t=0.7$ according to Bellon's
 study, we found 97 ok-match pairs reported. On the other hand, setting $t$ to
 0.1, 0.3, 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs
-respectively. Since the clone pairs of $t=0.1$ was the superset of other sets, 
+respectively. Since the clone pairs of $t=0.1$ were the superset of other sets, 
 we manually checked all the 111 reported pairs. We found one false positive pair
@@
 the clone pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to
-being a subset of $t=0.5$. However, since there is a fewer true positive pairs
-reported (i.e.~generating false negatives), we ended up leaving some duplicates
+being a subset of $t=0.5$. However, since there were fewer true positive pairs
+reported (i.e.,~generating false negatives), we ended up leaving some duplicates
 of the same clone pairs (that were supposed to be merged) in the final merged
@@
 With this analysis, we can see that setting the threshold $t$ to 0.1 is too
-relaxed and results in having false positive ok-match pairs, while setting the
+relaxed and results in having false positive ok-match pairs while setting the
 $t$ to 0.7 or 0.9 is too strict and generates some false negative pairs. Thus,
@@
 made their decision. The two authors also compared their results and discussed
-until a consensus was made. Similarly, the same process was applied for the SQ
+until a consensus was made. Similarly, the same process was applied to the SQ
 clone pair. %For the SQ pair we discovered, we found
@@
 It now says \textit{``To answer RQ2, we found 2,076 manually confirmed clone
-	pairs between 443 Stack Overflow code snippets and 59 Qualitas proejcts.''.}
+	pairs between 443 Stack Overflow code snippets and 59 Qualitas projects.''.}
 
@@
 Moreover, thank you for pointing out the inappropriate naming for AC. We now
-renamed them from AC to NC (i.e.~Not Clones).
+renamed them from AC to NC (i.e.,~Not Clones).
 
@@
 Overflow question no.~10924648 posted a comment on his own answer saying that
-the answer is specifically for Spring 3.1. Moroever, another user posted a
-comment on the answer of the post no.~801935 that the code snippet is not of
+the answer is specifically for Spring 3.1. Moreover, another user posted a
+comment on the answer to the post no.~801935 that the code snippet is not of
 high quality and suggested an alternative in another post. We extended this
@@
 We are grateful for the insightful comment. We selected the 2013 snapshot of
-Qualitas data since it is the latest and the most complete snapshot (i.e.~having
+Qualitas data since it is the latest and the most complete snapshot (i.e.,~having
 the highest number of Java projects) provided by the data set author.
@@
 ages as you suggested. We only chose the QS clone pairs since we could manually
-confirmed the direction of cloning. Moreover, we knew the date that the original
+confirm the direction of cloning. Moreover, we knew the date that the original
 version of the QS clones appeared in Qualitas projects (we used the version
@@
 \rcomment{ I do believe the survey results from the StackOverflow contributors
-	actually provides more meaningful insights then then the clone detection itself,
+	actually provides more meaningful insights than the clone detection itself,
 	since the responses by the contributors actually help explaining some of the
@@
 We moved them to RQ1 to better link with the motivation. We also expanded the
-findings to include another survey, the Stack Overflow visitor survey, in order
+findings to include another survey, the Stack Overflow visitor survey,
 to understand the awareness of the developers on both sides: the answerers and
-the visitors (i.e.~information seekers). We asked the visitors their experience
+the visitors (i.e.,~information seekers). We asked the visitors their experience
 regarding outdated and license-incompatible code caused by copying and reusing
@@
 
-That is a good point. We relied on the two new analyses and added a new discussion about toxicity of outdated code in the Overall Discussion.
+That is a good point. We relied on the two new analyses and added a new
+discussion about the toxicity of outdated code in the Overall Discussion.
 
-First, from the answer to Reviewer 2, we analysed the intent behind the changes that made the code outdated and found that only 10 out of 100 cases were bug fixes.
-Besides that, the code snippets were outdated because of evolution in the software (adding or enhancing features, refactoring, changing coding style, and data change).
-Thus, outdated code can sometimes become toxic, but not always.
+First, from the answer to Reviewer 2, we analysed the intent behind the changes
+that made the code outdated and found that only 10 out of 100 cases were bug
+fixes. Besides that, the code snippets were outdated because of evolution in the
+software (adding or enhancing features, refactoring, changing coding style, and
+data change). Thus, outdated code can sometimes become toxic, but not always.
 
-Second, as previously discussed in the answer to Reviewer 1, we have performed an additional experiment to search for occurrences of the 100 outdated code snippets in 130,703 open source GitHub projects and found 102 clones of 30 outdated code snippets.
-47 were exact copy of the outdated versions, of which 12 were buggy.
-However, we could not establish evidence that the outdated code snippets were cloned from Stack Overflow or somewhere else.
-We have reported the problem of race condition in two clone snippets found in deeplearning4j and Apache Hive to the developers.
+Second, as previously discussed in answer to Reviewer 1, we have performed
+an additional experiment to search for occurrences of the 100 outdated code
+snippets in 130,703 open source GitHub projects and found 102 clones of 30
+outdated code snippets. 47 were an exact copy of the outdated versions, of which 12
+were buggy. However, we could not establish evidence that the outdated code
+snippets were cloned from Stack Overflow or somewhere else. We have reported the
+problem of race condition in two clone snippets found in deeplearning4j and
+Apache Hive to the developers.
 
-To summarise, we empirically show from the surveys and the clone detection experiment that online code clones occur on Stack Overflow and the clones may become toxic due to outdated code and software license incompatibility.
-For outdated code, we found only a small number of clones.
-Although other studies show that Stack Overflow code snippets may contain security vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we found in this study that the damage caused by reusing outdated code on Stack Overflow is not high.
-On the other hand, the missing licensing statements of online code clones on Stack Overflow can be more harmful.
-As shown in our study and also in the study by \cite{An2017}, some online clones on Stack Overflow are originally licensed under more restrictive license than Stack Overflow's CC BY-SA 3.0.
-If these missing-license online clones are reused in a software with an incompatible license, the software owner may face legal issues.
-Software auditing services such as Black Duck Software or nexB, which can effectively check for license compliance of code copied from open source projects, do not check for the original license of the code snippets on Stack Overflow.
-Although the Stack Overflow answerers who participated in our survey believe that most of the code snippets on Stack Overflow are too small to claim for copyright and they fall under fair-use, there is still a risk due to different legal systems in each country.
-For example, Germany's legal system does not have a concept of fair use or the number of minimum lines of code to be considered trivial, i.e.~de minimis, is also different from case to case or from country to country.
+To summarise, we empirically show from the surveys and the clone detection
+experiment that online code clones occur on Stack Overflow and the clones may
+become toxic due to outdated code and software license incompatibility. For
+outdated code, we found only a small number of clones. Although other studies
+show that Stack Overflow code snippets may contain security
+vulnerabilities~\citep{Acar2016,Fischer2017} or API misuse~\citep{Zhang2018}, we
+found in this study that the damage caused by reusing outdated code on Stack
+Overflow is not high. On the other hand, the missing licensing statements of
+online code clones on Stack Overflow can be more harmful. As shown in our study
+and also in the study by \cite{An2017}, some online clones on Stack Overflow are
+originally licensed under more restrictive license than Stack Overflow's CC
+BY-SA 3.0. If these missing-license online clones are reused in software with
+an incompatible license, the software owner may face legal issues. Software
+auditing services such as Black Duck Software or nexB, which can effectively
+check for license compliance of code copied from open source projects, do not
+check for the original license of the code snippets on Stack Overflow. Although
+the Stack Overflow answerers who participated in our survey believe that most of
+the code snippets on Stack Overflow are too small to claim for copyright and
+they fall under fair-use, there is still a risk due to different legal systems
+in each country. For example, Germany's legal system does not have a concept of
+fair use or the number of minimum lines of code to be considered trivial,
+i.e.,~de minimis, is also different from case to case or from country to country.
 

### 2018-05-24 cloverflow-tse/cover_letter/cover_letter.tex
Further changes to the cover letter.

@@
 extended analysis of the 100 outdated code snippets. For example, we analysed
-the age of the clones; studied effects of comments, newer answers, higher-voted
+the age of the clones; studied the effects of comments, newer answers, and higher-voted
 answers on the outdated answers; and summarised six intents that made the
@@
 \clearpage
-We also tried our best to address all the comments from the reviewers. Every
+We tried our best to address all the comments from the reviewers. Every
 comment led to an improvement on this submission, and we discuss them in order as
@@
 Lastly, we would also like to ask the reviewers to comment on how to address the
-newly established page limits of IEEE TSE that was enforced after our previous
-submission. After incorporating the suggestions from the reviewers and
+newly established page limits of IEEE TSE that was enforced on 18 February 2018, after our previous
+submission (15 November 2017). After incorporating the suggestions from the reviewers and
 rewriting, our paper is now extended to 22 pages. Are there any elements that
@@
 	other projects besides the Qualitas projects, 47 cloned snippets
-	were exactly the same as the outdated code snippet and 42 cloned snippets that
+	were the same as the outdated code snippet, and 42 cloned snippets
 	were not the same (e.g.,~they contained additional code modifications
@@
 pointed to different posts than the ones we found but containing the same code
-in the answers. The other 32 cloned snippets were very likely to be a
+in the answers (the answers were not marked as accepted so they were not included in our experiment). 
+The other 32 cloned snippets were very likely to be a
 file-level clone from its respective original project (e.g.,~JFreeChart, JUnit,
@@
 performed during the same time as the Stack Overflow answerers (25 July 2017 to
-25 September 2017), and the full results are reported in our technical
-report~\citep{Ragkhitwetsagul_RN2017}. We did not include the results in the
+25 September 2017), and the full results are reported in our research note~\citep{Ragkhitwetsagul_RN2017}. 
+We did not include the results in the
 previous version of the paper due to a smaller sample size compared to the
@@
 	on how to automate the process of finding online code clones, detecting
-	outdated code, and finding license-incompatible code snippets.
+	outdated code, and finding license-incompatible code snippets as the means
+	to mitigate the problems from toxic code snippets.
 
@@
 
-\rcomment{ Other Comments While ``Toxic Code Snippets'' is a catchy phrase for
+\rcomment{ Other Comments:\newline While ``Toxic Code Snippets'' is a catchy phrase for
 	the title, I think that online code clones are the dominant topic.}
@@
 Overflow code snippets were actually clones of Qualitas projects and (2) the
-direction of cloning was from Qualitas to Stack Overflow, which both are
+direction of cloning was from Qualitas to Stack Overflow, which are both
 addressed in RQ1 and RQ2. Nevertheless, RQ4 does not need to follow RQ3
@@
 increased the threshold to ten lines, another well-established minimum clone
-size for large-scale data sets~\cite{Sajnani2016}, and retrieved 721 clone pairs
+size for large-scale data sets~\citep{Sajnani2016}, and retrieved 721 clone pairs
 from Simian and 1,678 clone pairs from SourcererCC. We randomly sampled and
@@
 non-trivial clone pairs.
-
 We have modified the paper to include this discussion at the end of Section
@@
 in each country. For example, Germany's legal system does not have a concept of
-fair use or the number of minimum lines of code to be considered trivial,
+fair use. The number of minimum lines of code to be considered trivial,
 i.e.,~de minimis, is also different from case to case or from country to country.
-
-We also updated the Actionable Items section to reflect Reviewer 1's comment.
+Lastly, we also updated the Actionable Items section to reflect Reviewer 1's comment.
 
@@
 This result in inclusion of a Stack Overflow visitors' survey, an analysis of toxic code snippets in GitHub projects, analysis of different tools' and technique's parameters, a more detailed analysis of online code clones, the updated definition of toxic code snippets, the improved overall discussion section, and other minor improvements throughout the paper.
-We believe this new submission has been considerably improved from the previous version due to the insightful reviews and discussions and we are looking forward to the new reviews.
+We believe this new submission has been considerably improved from the previous version due to the insightful reviews and discussions. We are looking forward to the new reviews.
 

### 2018-05-24 cloverflow-tse/cloverflow.tex
After the Grammarly check.
Fixed e.g. (to e.g.,) and i.e. (to i.e.,) as suggested by Grammarly.

@@
 contain defects. Code snippets from open source projects usually fall under a
-specific software license, e.g.\ GNU General Public License (GPL). If they are
+specific software license, e.g.,\ GNU General Public License (GPL). If they are
 cloned to Stack Overflow answers without the license, and then flow to other projects
@@
 While research has mostly focused on reusing code snippets \emph{from} Stack
-Overflow (e.g.~\cite{Keivanloo2014,An2017,Yang2016}), fewer studies have been
+Overflow (e.g.,~\cite{Keivanloo2014,An2017,Yang2016}), fewer studies have been
 conducted on finding the origins of code examples copied \emph{to} Stack
@@
 invited participants had a reputation from 963,731 (the highest) to 6,999 and
-we sent out 607 emails (excluding undelivered ones, e.g.\ due to
+we sent out 607 emails (excluding undelivered ones, e.g.,\ due to
 illegal email addresses). 
@@
 invited to take the survey via five channels: social media post (Facebook),
-\textsf{blognone.com}, a popular technology news and media community in Thailand, the University of Molise in Italy where the third author
-works, \texttt{comp.lang.java.programmer} group and the Software Engineering
+\textsf{blognone.com} (a popular technology news and media community in Thailand), 
+the University of Molise in Italy where the third author
+works, the \texttt{comp.lang.java.programmer} group and the Software Engineering
 Facebook page. 
@@
 	\label{tab:clone_config}
-%		\resizebox{\columnwidth}{!}{
-%	\small
 	\begin{tabular}{lp{5cm}}
@@
 		\bottomrule
-	\end{tabular} %
-%	}
+	\end{tabular}
 \end{table}
@@
 Choosing a large threshold value can reduce the number of trivial clones
-(e.g. \texttt{equals}, \texttt{hashCode}, or getter and setter methods) and
+(e.g.,~\texttt{equals}, \texttt{hashCode}, or getter and setter methods) and
 false clones in the analysis or the manual investigation
 phase~\cite{Sajnani2016}, while at the same time may create some false negatives,
-i.e.~increasing precision. On the other hand, setting a low threshold
-results in a larger number of clone candidate pairs to look at, i.e.~increasing recall, 
+i.e.,~increasing precision. On the other hand, setting a low threshold
+results in a larger number of clone candidate pairs to look at, i.e.,~increasing recall, 
 and a higher chance of getting false positives. 
@@
 %considered a standard setting for clone detection in large-scale data sets to
-%avoid trivial clones (e.g. \texttt{equals}, \texttt{hashCode}, or getter and
+%avoid trivial clones (e.g.,~\texttt{equals}, \texttt{hashCode}, or getter and
 %setter methods) in the analysis or the manual investigation phase~\cite{Sajnani2016}.  
@@
 A clone pair \textit{CP} is formed by two clone fragments
-\textit{CF$_1$} and \textit{CF$_2$}, i.e.~\textit{CP} =
+\textit{CF$_1$} and \textit{CF$_2$}, i.e.,~\textit{CP} =
 (\textit{CF$_1$}, \textit{CF$_2$})
@@
 copying while the other could not. Thus, resolving the conflicts lead to a better classification,
- i.e.~from UD to QS or EX.
+ i.e.,~from UD to QS or EX.
 %There were three conflicts where the two
@@
 %snippets were ranked according to (1)~clone pair frequency,
-%(2)~popularity (i.e.~number of associated Qualitas projects),
+%(2)~popularity (i.e.,~number of associated Qualitas projects),
 %(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
@@
 code from scratch, copying and modifying the code from the question, and others
-(e.g.\ code that are copied from other questions or answers on Stack Overflow)
+(e.g.,\ code that are copied from other questions or answers on Stack Overflow)
 and we asked them to rate how often they copied the code from these locations. The
@@
 Many users either declare their snippets to be public domain, or they grant
-additional licenses, e.g.\ Apache 2.0 or MIT/Expat.
+additional licenses, e.g.,\ Apache 2.0 or MIT/Expat.
 
@@
 %Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
-%check if the code snippet originated from a different source (e.g. an open source project) 
+%check if the code snippet originated from a different source (e.g.,~an open source project) 
 %and if they had an incompatible license to their projects.
@@
 projects. For the cloned Stack Overflow snippets, the
-average ratio of cloned code is 53.28\% (i.e.\ the number of cloned
+average ratio of cloned code is 53.28\% (i.e.,\ the number of cloned
 lines of the cloned Stack Overflow snippet).
@@
 Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
-as being accidental clones (NC), i.e.~false positives. After removing
+as being accidental clones (NC), i.e.,~false positives. After removing
 them, the set still contains 2,063 true positive clone pairs between 443 Stack
@@
 	and 59 Qualitas proejcts. 
-	%After the manual confirmation, 2,076 pairs as true positives, i.e.~
+	%After the manual confirmation, 2,076 pairs as true positives, i.e.,~
 	%they are manually confirmed as clones, which 
@@
 \Cref{fig:ex_sources}. There are 63 EX online clone pairs copied
-from source code of Java SDK (e.g.\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
+from source code of Java SDK (e.g.,\ \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}), 
 18 pairs from websites, 14 pairs from open
-source systems not in Qualitas (e.g.\ \textsf{Mozilla
+source systems not in Qualitas (e.g.,\ \textsf{Mozilla
 	Rhino}), 10 pairs from Java official documentations from Sun
@@
 addition (28 occurrences), statement removal (18 occurrences), change of
-method signature, i.e.~API change (16 occurrences), and method rewriting (15
+method signature, i.e.,~API change (16 occurrences), and method rewriting (15
 occurrences). Moreover, in the 101 outdated pairs, we found 15 ``dead''
@@
 
-\begin{table}[H]
+\begin{table}
 \centering
@@
 projects, there were 32 cloned snippets that were not exactly the same
-(e.g.~they contained additional code modifications made by the projects'
+(e.g.,~they contained additional code modifications made by the projects'
 developers or they were copied from another source with a slightly different code).
@@
 in the answers. 32 cloned snippets were very likely to be a file-level
-clone from its respective original project (e.g. JFreeChart, JUnit, Log4J,
+clone from its respective original project (e.g.,~JFreeChart, JUnit, Log4J,
 Hadoop) based on their license header and the Javadoc comments. 
@@
 retrieved them from Stack Overflow, other websites, or from Hadoop code base
-directly. Nevertheless, we decided to report the developers of the two projects
+directly. Nevertheless, we reported them to the developers of the two projects
 regarding the issue. We created a bug report for each project (deeplearning4j
@@
 developers of the projects by describing the problem of race condition in the
-outdated version of \texttt{humanReadableInt()} method and proposed a fix by
+outdated version of the \texttt{humanReadableInt()} method and proposed a fix by
 using the newest version of the method in Hadoop. The issue has been fixed in
@@
 potential software licensing conflict caused by copying the fix directly from
-Hadoop code base. The bug report in Apache Hive is still
-unfixed.
+the Hadoop code base. The bug report in Apache Hive is still open.
 
@@
 code) to the introduction of vulnerabilities to the software~\cite{Xia2014}. An
-outdated code with a subtle change (e.g.\ \Cref{fig:before-after}) may be copied
+outdated code with a subtle change (e.g.,\ \Cref{fig:before-after}) may be copied
 and reused without awareness from developers. Moreover, an outdated code with a
-defect (e.g.\ a race condition problem in \Cref{fig:before-after_2}) is clearly
+defect (e.g.,\ a race condition problem in \Cref{fig:before-after_2}) is clearly
 harmful to be reused. Although Stack Overflow has a voting mechanism that may
@@
 Opposite to the outdated clones, we discovered a large number
-of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects on
-GitHub and 7,112 pairs from 2,427 other projects. From
+of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects hosted on
+GitHub and 7,112 pairs from 2,427 other projects. Shown in
 \Cref{tab:license_github}, the clones were found in highly-starred
@@
 6 of them refer to one of our QS or EX clone pairs.
-We used the Ninka tool to automatically identify software license of the 7,207 cloned
-code snippets. 
-Five code snippets did not have license while the originals had Apache-2, GPLv2,
-or EPLv1 license. One snippets had AGPLv3 license while the original had Apache-2 license.
-Only 995 code snippets in GitHub projects that have the same license
+We used the Ninka tool to identify software licenses of the 7,207 cloned
+code snippets automatically. 
+Five code snippets did not have a license while the originals had the Apache-2, GPLv2,
+or EPLv1 license. One snippets had the AGPLv3 license while the original had the Apache-2 license.
+Only 995 code snippets in GitHub projects have the same license
 as the originals in Qualitas.
@@
 country. For example, Germany legal system does not have a concept of fair use.
-In addition, the number of minimum lines of code to be consider copying, i.e.~de minimis,
+In addition, the number of minimum lines of code to be consider copying, i.e.,~de minimis,
 is also differently interpreted from case to case or from country to country.
@@
 code copying. Thus, by using code clone detection to locate clone candidates
-and then applying information retrieval techniques, e.g. cosine similarity with tf-idf, 
+and then applying information retrieval techniques, e.g.,~cosine similarity with tf-idf, 
 we can rank the clone candidates based on the similarity of their project names (or classes) to the text in 
@@
 Nevertheless, our study might still suffer from false negatives,
-i.e.~online code clones that are not reported by the tools or are filtered out
+i.e.,~online code clones that are not reported by the tools or are filtered out
 by the size (less than 10 lines) within the clone detection process. We selected
@@
 doing
-so~(e.g.~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014}).
+so~(e.g.,~\cite{Ponzanelli2013,Ponzanelli2014,Keivanloo2014,Park2014}).
 Nonetheless, it may not be representative to all the programming Q\&A
@@
 behaviours on Stack Overflow,
-e.g.~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
+e.g.,~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
 % , while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.
@@
 time. German et al.~\cite{German2009} found that licensing 
-conflicts occur between the clone siblings, i.e.~clones among 
+conflicts occur between the clone siblings, i.e.,~clones among 
 different systems that come from the same source. Later, 
@@
 It is interesting to compare the findings among different programming languages.
-Moreover, other popular software project corpora (e.g.\ GitHub) can also be included to increase generalisation of the findings.
+Moreover, other popular software project corpora (e.g.,\ GitHub) can also be included to increase generalisation of the findings.
 %
@@
 
-The online survey of 201 high-reputation Stack Overflow developers (i.e.~answerers)
+The online survey of 201 high-reputation Stack Overflow developers (i.e.,~answerers)
 show that although the developers are aware of outdated code in their answers,

### 2018-05-24 cloverflow-tse/cloverflow.tex
Adopted the changes from the cover letter.

@@
 
-Although this activity of online code cloning is well-known, there is only a few
+Although this activity of online code cloning is well-known, there are only a few
 empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
@@
 clone candidate pairs. We randomly sampled 382 pairs from the two sets for
-manual check. This sample amount was a statistical significant sample with a
+manual check. This sample number was a statistical significant sample with a
 95\% confidence level and $\pm 5\%$ confidence interval. The first author
@@
 projects to Stack Overflow. The clone ages were calculated by counting the
-number of month difference from the dates of each Qualitas project to the date
-the answers were posted on Stack Overflow as shown in~\ref{fig:boxplotcloneage}.
+number of months between the date of each Qualitas project and the date the answer
+was posted on Stack Overflow as shown in~\ref{fig:boxplotcloneage}.
 We found that, on average, it took the clones around 2 years since they appeared
@@
 Then, we performed code clone detection between the 100 outdated code snippets and 130,703 GitHub projects.
-We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all
+We found 102 cloned candidates, which were associated with 30 outdated code snippets, 
+appearing in 68 GitHub projects and manually investigated all
 of them. As shown in \Cref{tab:outdated_github}, out of the 102 cloned snippets, there were
@@
 \subsubsection{Toxicity of outdated and license-incompatible clones}
-We found only a small amount of toxic outdated code snippets in open source projects on
+We found only a small number of toxic outdated code snippets in open source projects on
 GitHub. Besides 12 buggy and outdated code snippets found in 12 projects, the
@@
 
-On the other hand, the missing of licensing statement of online code clones on
+On the other hand, the missing licensing statements of online code clones on
 Stack Overflow can cause more damage than outdated code. As shown in our study and
@@
 BY-SA 3.0. If these missing-license online clones are reused in a software with
-incompatible license, the software owner may face legal issues. The software
-auditing service such as Black Duck Software or nexB, which can effectively
-check for license compliance of code copied from open source projects, cannot
+an incompatible license, the software owner may face legal issues. Software
+auditing services such as Black Duck Software or nexB, which can effectively
+check for license compliance of code copied from open source projects, do not
 check for the original license of the cloned code snippets on Stack Overflow. Although
-Stack Overflow answerers participated in our survey believe that most of the
+the Stack Overflow answerers who participated in our survey believe that most of the
 code snippets on Stack Overflow are too small to claim for copyright and they
-fall under fair-use, there is still a risk due to different legal system in each
-country. For example, Germany legal system does not have a concept of fair use.
+fall under fair-use, there is still a risk due to different legal systems in each
+country. For example, Germany's legal system does not have a concept of fair use.
 In addition, the number of minimum lines of code to be consider copying, i.e.,~de minimis,
@@
 compatibility with their customer software, the BlackDuck auditing system will
-treat the code snippets on Stack Overflow as having ``unknown'' license because
+treat the code snippets on Stack Overflow as having an ``unknown'' license because
 it does not know the original license of Stack Overflow code snippets. For nexB,

### 2018-05-24 cloverflow-tse/cloverflow.tex
Passed a Grammarly check.

@@
 mechanism after the code has been copied to Stack Overflow, they can become
-toxic code snippets, i.e.~they suffer from being outdated or violating the
+toxic code snippets, i.e.,~they suffer from being outdated or violating the
 original software license. We present a study of online code clones on Stack
@@
 85\% of them are not aware of CC BY-SA 3.0
-license enforced by Stack Overflow and 66\% never check for license conflicts
+license enforced by Stack Overflow, and 66\% never check for license conflicts
 when reusing code snippets. Our clone detection found online clone pairs between
@@
 cloned snippets between Android apps and Stack Overflow potentially violate
-software licenses. Security is also among the main concerns when code is copied
+software licenses. Security is also among the main concerns when the code is copied
 from an online source. For example, Stack Overflow helps developers to solve
@@
 We call code snippets that are copied from software systems to online Q\&A
-websites (such as Stack Overflow) and vice versa as ``online code clones''.
+websites (such as Stack Overflow) and vice versa as ``online code clones.''
 There are two directions in creating online code clones: (1)~code is cloned from
@@
 % software project to another via a Q\&A website;
-Similar to classic code clones, i.e.~clones between software systems, online
-code clones can lead to license violations, bug propagation, introduction of
+Similar to classic code clones, i.e.,~clones between software systems, online
+code clones can lead to license violations, bug propagation, an introduction of
 vulnerabilities, and re-use of outdated code. Unfortunately, online clones are
@@
 
-To have a deeper insight on online code clones, we surveyed 201 high-reputation
+To have a deeper insight into online code clones, we surveyed 201 high-reputation
 Stack Overflow answerers. The results of such a survey show that online code
@@
 there is also a downside caused by low quality, defective, and harmful code
-snippets that are reused without an awareness by millions of users~\cite{Zhang2018,Acar2016,Fischer2017}.
+snippets that are reused without awareness by millions of users~\cite{Zhang2018,Acar2016,Fischer2017}.
 
@@
 on finding the origins of the clones on Q\&A websites.
-In this study, we tackle this challenge of establishing existence of online code 
+In this study, we tackle this challenge of establishing the existence of online code 
 clones on Stack Overflow, investigate how they occur, and study the potential
@@
 Therefore, we mine Stack Overflow posts, detected online code clones, and analysed the clones to reveal
-``toxic code snippets''.
+``toxic code snippets.''
 
@@
 In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
-as these two problems are still under explored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
+as these two problems are still underexplored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
 Moreover, Stack Overflow users also express their concerns about these two problems
@@
 disrupting changes than the first one  can be found in an answer to a Stack
-Overflow question regarding how to format files sizes in a human readable form.
+Overflow question regarding how to format files sizes in a human-readable form.
 \Cref{fig:before-after_2} shows---on the left---a code snippet to perform the
@@
 the latest version of \textsf{Hadoop}. We can see that
-they are totally different. The {\small{\texttt{humanReadableInt}}} method is
+they are entirely different. The {\small{\texttt{humanReadableInt}}} method is
 rewritten on February 5, 2013 to solve an issue of a race condition
@@
 important to studying the effects of reusing Stack Overflow code snippets
-because it gives insights to the root cause of the problem and lays a
+because it gives insights into the root cause of the problem and lays a
 foundation to an automatic technique to detect and report
@@
 		code clones occur?} We categorised online clones into seven
-	categories allowing insights to how online code clones are created.
+	categories allowing insights into how online code clones are created.
 
@@
 	\includegraphics[width=\linewidth]{exp_framework_new}
-	\caption{Experimental framework}
+	\caption{The Experimental framework}
 	\label{fig:exp_framework}
@@
 Kitchenham~\cite{Pfleeger2001,Kitchenham2002}. The survey was completely
-anonymous and the participants could decide to leave at any time. 
+anonymous, and the participants could decide to leave at any time. 
 We created two versions of the survey: \textbf{the answerer survey} and \textbf{the visitor survey}.
@@
 reputation. On Stack Overflow, a user's reputation reflects how much the
-community trusts them. A user earns reputations when he or she receives up votes
+community trusts them. A user earns reputations when he or she receives upvotes
 for good questions and useful answers. Accepted answers receive more reputation
-score than questions, and regular answers\footnote{Stack Overflow
+score than questions and regular answers\footnote{Stack Overflow
 	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
@@
 asking and answering questions on the site. In this study, we call Stack
-Overflow users who have high reputation ``Stack Overflow answerers.''
+Overflow users who have a high reputation ``Stack Overflow answerers.''
 The participants were invited to take the survey via email addresses available
@@
 	of 25 July 2017):~\url{https://stackoverflow.com/users?tab=Reputation&filter=all}}. The
-invited participants had a reputation from 963,731 (the highest) to 6,999 and
+invited participants had a reputation from 963,731 (the highest) to 6,999, and
 we sent out 607 emails (excluding undelivered ones, e.g.,\ due to
@@
 code snippets of at least ten lines. Although the minimum clone size of six
-lines are usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
+lines is usual in clone detection~\cite{Bellon2007,Wang2013,Koschke2006}, we
 empirically found that snippets of six lines contain a large number of
@@
 using regular expressions and manual checking.
-Finally we obtained 72,365 Java code snippets containing 1,840,581
+Finally, we obtained 72,365 Java code snippets containing 1,840,581
 lines\footnote{Measured by cloc: \url{https://github.com/AlDanial/cloc}} of Java
@@
 data. Due to incomplete code blocks and functions
-normally found in Stack Overflow snippets, the built-in SourcererCC's Java
+typically found in Stack Overflow snippets, the built-in SourcererCC's Java
 tokeniser could not parse 45,903 snippets, more than half of them. Nevertheless,
@@
 Overflow and Qualitas projects, removing all clone pairs within either Stack
-Overflow or within Qualitas. 
-SourcererCC can detect cross-project clones between two systems so we did
+Overflow or Qualitas. 
+SourcererCC can detect cross-project clones between two systems, so we did
 not filter the clones.
@@
 tools' creators as depicted in \Cref{tab:clone_config}. 
-The two clone detectors complement each
+The two clone detectors complemented each
 other by having Simian detecting literal copies of code snippets (type-1) and SourcererCC
@@
 Moreover, the large number of clone
-pairs will hinders the full manual validation of the clones.
+pairs will hinder the full manual validation of the clones.
 % and one needs to
@@
 checked the same amount of 382 pairs and found 27 non-clone pairs, 253 trivial
-clone pairs and 102 non-trivial clone pairs. Then, we increased the threshold
+clone pairs, and 102 non-trivial clone pairs. Then, we increased the threshold
 further to fifteen lines and retrieved 196 clone pairs from Simian and 1,230
 clone pairs from SourcererCC. The manual check of the 382 randomly sampled pairs
-reveal zero non-clone pairs, 298 trivial clone pairs and 83 non-trivial clone
+revealed zero non-clone pairs, 298 trivial clone pairs, and 83 non-trivial clone
 pairs.
@@
 an ok-match pair with a
-confidence value between 0 and 1. Although good-match has stronger agreement
+confidence value between 0 and 1. Although good-match has a stronger agreement
 than ok-match, we choose the ok-match criterion as our clone merging method
@@
 clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
-pairs and some non-duplicate clone pairs may be accidentally merged by only
+pairs, and some non-duplicate clone pairs may be accidentally merged by only
 a few matching lines.
@@
 0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
-Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually
+Since the clone pairs of $t=0.1$ were the superset of other sets,  we manually
 checked all the 111 reported pairs. We found one false positive pair and 110
@@
 pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
-subset of $t=0.5$. However, since there is a fewer merged clone pairs, 
+subset of $t=0.5$. However, since there were fewer merged clone pairs, 
 we ended up leaving some duplicates of the same clones in the final merged clone set.
@@
 manual validation and online clone classification.
-The validation and classification of the pairs was done at the same time. 
+The validation and classification of the pairs were done at the same time. 
 The clone validation process (phase 3 in \Cref{fig:exp_framework}) involves checking 
@@
 pair is classified in \textbf{QS}. In several occasions, we used extra
-information such as questions' contents, name of posters, and tags to gain a
+information such as the questions' contents, the name of posters, and the tags to gain a
 better understanding. On the other hand, if the source code from the Qualitas
@@
 \textbf{SQ}. If there is evidence of copying from an external source instead of
-a Qualitas projects, the pair is classified into \textbf{EX}. Lastly, if there
+a Qualitas project, the pair is classified as \textbf{EX}. Lastly, if there
 is no evidence of copying in any direction but the clone fragments are highly
@@
 \subsubsection{Phase 5: Outdated Clones} Outdated code occurs when a piece of code
-has been copied from its origin to another location and later the original has
-been updated~\cite{Xia2014}. Usually code clone detection is used to locate
+has been copied from its origin to another location, and later the original has
+been updated~\cite{Xia2014}. Usually, code clone detection is used to locate
 clone instances and update them to match with the originals~\cite{Bellon2007}.
@@
 query to retrieve most starred projects based on their sizes.
-The project size range started from 1KB to 2MB with 1KB step size and the last query is
+The project size range started from 1KB to 2MB with 1KB step size, and the last query is
 for all the remaining projects that were larger than 2MB.
@@
 A clone detection was then performed between the outdated code snippets and the GitHub
-projects. We selected SourcererCC with with the same settings (see \Cref{tab:clone_config}) 
+projects. We selected SourcererCC with the same settings (see \Cref{tab:clone_config}) 
 for this task because it could scale to a large-scale data set, while Simian could not. Finally, we analysed
@@
 an automatic license identification tool~\cite{German2010}. Since Ninka works at
-file level, we report the findings based on Stack Overflow snippets and Qualitas
+a file level, we report the findings based on Stack Overflow snippets and Qualitas
 source files instead of the clone pairs (duplicates were ignored). For the ones
@@
 We only present a summary of the survey answers in
-this paper and the full analysis is available as a research note~\cite{Ragkhitwetsagul_RN2017}.
+this paper, and the full analysis is available as a research note~\cite{Ragkhitwetsagul_RN2017}.
 
@@
 their answers. 111 participants selected \textit{Yes} while the other 89 participants
-selected \textit{No}. However, we found inconsistent results when we asked a follow up
+selected \textit{No}. However, we found inconsistent results when we asked a follow-up
 question on the frequency of being notified. As displayed in
-\Cref{tab:survey_code_snippet_outdated}, the number of participants who has
+\Cref{tab:survey_code_snippet_outdated}, the number of participants who have
 \textit{Never} been notified about outdated code snippets in their answers drops
@@
 
-We found that although the answerer have been notified of outdated code in their
+We found that although the answerers have been notified of outdated code in their
 answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
@@
 long time. Due to the voting mechanism of Stack Overflow, high reputation users
-usually provide high quality answers to earn up votes from other users. They are
+usually provide high-quality answers to earn upvotes from other users. They are
 careful when posting code snippets in the answer to avoid problems and, vice versa, 
-getting down votes. It would be interesting to compare the findings to
-Stack Overflow answerers who are newer and have lower reputation. However, we
+getting downvotes. It would be interesting to compare the findings to
+Stack Overflow answerers who are newer and have a lower reputation. However, we
 leave it to future work.
@@
 
-\textbf{License of Code Snippets:} Among the 200 answerers who include code snippets in their answers, 124
-answerers are aware that Stack Overflow apply Creative Commons
+\textbf{The License of Code Snippets:} Among the 200 answerers who include code snippets in their answers, 124
+answerers are aware that Stack Overflow applies Creative Commons
 Attribution-ShareAlike 3.0 Unported (CC BY-SA 3.0) to content in the posts,
@@
 First, some answerers chose to post only their own code or code that was adapted
-from the question, hence they are automatically subjected to CC BY-SA 3.0.
-Second, they copied code from company or open source projects that they knew
+from the question; hence they are automatically subjected to CC BY-SA 3.0.
+Second, they copied the code from company or open source projects that they knew
 were permitted to be publicly distributed. Third, some answerers believe that
@@
 many users include a statement on their profile page that all their
-answers are under a certain license. For example, a Stack Overflow user includes 
+answers are under a specific license. For example, a Stack Overflow user includes 
 the following text in his/her profile page.
@@
 \textbf{Open Comments:} We also invited the participants to give a
-free-form comment regarding their concerns of answering Stack Overflow with code
+free-form comment regarding their concerns about answering Stack Overflow with code
 snippets. Besides the one we present earlier in the introduction, these are
@@
 Two participants never
-copy code from Stack Overflow so we analysed the answers of the remaining 87
+copy code from Stack Overflow, so we analysed the answers of the remaining 87
 participants.
@@
 \textbf{General Information: }
-Twenty four (27\%) and twenty one (24\%) participants have over 10 years and 5--10
+Twenty-four (27\%) and twenty-one (24\%) participants have over 10 years and 5--10
 years of experience respectively. There are 19 participants (21\%) who have 3--5
@@
 
-\textbf{Choice for programming solutions: }
+\textbf{The Choice for programming solutions: }
 Stack Overflow is ranked higher than official documentation, online
@@
 Overflow at least once a week. They copy code from Stack Overflow because they
-can be found easily from search engine, solve similar problems to their
+can be found easily from a search engine, solve similar problems to their
 problems, provide helpful context, and offer voting mechanism and accepted answers.
@@
 problem from reusing Stack Overflow code snippets. Ten participants experienced
-problems for more than 80\% of the copied snippets and sixteen participants
+problems for more than 80\% of the copied snippets, and sixteen participants
 faced problems for 40--60\% of the reused code. As shown in~\Cref{tab:visitor_survey_code_problems}, 
@@
 In addition, 74 out of the 87 (85\%) participants are not
-aware of Stack Overflow CC BY-SA 3.0 license and 62\% never give attributions to
+aware of Stack Overflow CC BY-SA 3.0 license, and 62\% never give attributions to
 the Stack Overflow posts they copied the code snippets from. 
@@
 limited modifications. Most of them have a statement in the Stack Overflow post
-saying that the code is ``copied'', ``borrowed'' or ``modified'' from a specific
+saying that the code is ``copied,'' ``borrowed'' or ``modified'' from a specific
 file or class in a Qualitas project. For example, according to the motivating
@@
 
-We did an analysis of the time it took for the clone to appear from Qualitas
+We analysed the time it took for the clone to appear from Qualitas
 projects to Stack Overflow. The clone ages were calculated by counting the
@@
 statement(s) pointing to the original external location of the cloned
-code in Qualitas and Stack Overflow. In addition, we found evidence
+code in Qualitas and Stack Overflow. Besides, we found evidence
 of copying from an external source to Stack Overflow, but not in
@@
 source systems not in Qualitas (e.g.,\ \textsf{Mozilla
-	Rhino}), 10 pairs from Java official documentations from Sun
+	Rhino}), 10 pairs from Java official documentation from Sun
 Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
@@
 developing animated and graphical effects for desktop Java applications. Another
-example is a copy of code from a website in post 15260207. The text surrounding
+example is a copy of the code from a website in post 15260207. The text surrounding
 source code reads ``\textit{I basically stole this from the web and modified it
@@
 projects~\cite{Svajlenko2014}. We found that cloning can also happen among
-different sources on the Internet just like software projects. The are 18 clone
+different sources on the Internet just like software projects. There are 18 clone
 pairs that originated from programming websites including \url{www.java2s.com}
@@
 {\small\texttt{try-catch}} clauses that were accidentally the same due
-to their very small sizes, and similar {\small\texttt{switch-case}}
+to their tiny sizes, and similar {\small\texttt{switch-case}}
 statements.
@@
 \Cref{fig:before-after} and \Cref{fig:before-after_2}, we also found a few
-outdated code elements which contained a large amount of modifications. For
+outdated code elements which contained a large number of modifications. For
 example, the code snippet in Stack Overflow post 23520731 is a copy of
@@
 We analysed code modifications which made Stack Overflow code outdated by going
-though commits and git blame information. The six code modification
+through commits and git blame information. The six code modification
 types found in the 100 outdated online clone pairs are summarised in
@@
 the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
-Enhancement are the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
+Enhancement is the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
 by code deprecation (15\%). There were 10 outdated code snippets (10\%) caused by bug fixing.
@@
 data format change (2\%).
-Not all outdated code are toxic. However, the 10 buggy and outdated code snippets 
-we found are toxic and are harmful for reuse.
+Not all outdated code is toxic. However, the 10 buggy and outdated code snippets 
+we found are toxic and are harmful to reuse.
 
@@
 \Cref{tab:stale_code_details} shows examples of the outdated online clones on
-Stack Overflow. The table displays information of the clones from both Stack
+Stack Overflow. The table displays information about the clones from both Stack
 Overflow and Qualitas side including the dates. We summarise the changes that
@@
 (\textit{S}), file deletion (\textit{D}), and method rewriting (\textit{R}),
-along with the issue tracking number and the date of change. The complete set of
+along with the issue tracking number and the date of the change. The complete set of
 100 outdated online clones can be found on the study website.
@@
 on three aspects: newer or higher-voted answers and comments. We found
-that there were 34 posts which contains newer answers and 5 posts which contained answers with a higher number of
+that there were 34 posts which contained newer answers and 5 posts which contained answers with a higher number of
 votes than the outdated answers. However, 99 of the 100 outdated answers were still
@@
 to mitigate or point out the toxicity of the outdated code snippets. We found
-that, out of 100 answers, there were 6 answers that had a comment saying the
+that, out of 100 answers, 6 answers had a comment saying the
 code in the answer is outdated or containing issues, such as \textit{``spring
@@
 appearing in 68 GitHub projects and manually investigated all
-of them. As shown in \Cref{tab:outdated_github}, out of the 102 cloned snippets, there were
-13 cloned snippets that matched with themselves because some of the Qualitas
+of them. As shown in \Cref{tab:outdated_github}, out of the 102 cloned snippets,
+13 cloned snippets matched with themselves because some of the Qualitas
 projects also appear on GitHub. For other projects besides the Qualitas
-projects, there were 32 cloned snippets that were not exactly the same
+projects, 32 cloned snippets were not exactly the same
 (e.g.,~they contained additional code modifications made by the projects'
-developers or they were copied from another source with a slightly different code).
-There were 47 cloned snippets that were exactly the same as the
+developers, or they were copied from another source with a slightly different code).
+47 cloned snippets were the same as the
 outdated code snippets, which of 12 were buggy.
 Two cloned snippets gave attributions to Stack Overflow. The attributions
-pointed to different posts than the ones we found, but containing the same code
-in the answers. 32 cloned snippets were very likely to be a file-level
+pointed to different posts than the ones we found but containing the same code
+in the answers\footnote{The answers were not marked as accepted so they were not 
+included in our experiment.}. 32 cloned snippets were very likely to be a file-level
 clone from its respective original project (e.g.,~JFreeChart, JUnit, Log4J,
@@
 stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
-this method, which is exactly the same as the toxic code snippet we found on
+this method, which is the same as the toxic code snippet we found on
 Stack Overflow, appears in the two projects. It is possible that the developers
@@
 examples. Another 109 pieces of code are cloned from external sources. Their
-status of accepted answers increase their chances of being reused. Even though
+status of accepted answers increases their chances of being reused. Even though
 most of the Qualitas projects came with a software license, we found that the
-license information were frequently missing after the code was copied to Stack
+license information was frequently missing after the code was copied to Stack
 Overflow. The licensing terms on top of source code files are not copied because
@@
 clone counterparts in Qualitas projects and external sources do. Since licensing
-statement resides on top of a file, the results here are analysed at file level,
+statement resides on top of a file, the results here are analysed at a file level,
 not clone fragment, and clone pairs from the same file are merged. 
@@
 code and text on Stack Overflow are
-protected by \emph{CC BY-NC-SA 3.0}
-, we can treat the Stack Overflow code snippets
+protected by \emph{CC BY-NC-SA 3.0}, we can treat the Stack Overflow code snippets
 without licensing information as having \emph{CC BY-NC-SA 3.0} by
-default. The \emph{CC BY-NC-SA 3.0} license is relaxed and it only
+default. The \emph{CC BY-NC-SA 3.0} license is relaxed, and it only
 requests an attribution when reused.
@@
 We detected clones between the 214
-code snippets with their original license missing (86 QS, 78 EX and 50 UD)  and
+code snippets with their original license missing (86 QS, 78 EX, and 50 UD)  and
 130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
@@
 Five code snippets did not have a license while the originals had the Apache-2, GPLv2,
-or EPLv1 license. One snippets had the AGPLv3 license while the original had the Apache-2 license.
+or EPLv1 license. One snippet had the AGPLv3 license while the original had the Apache-2 license.
 Only 995 code snippets in GitHub projects have the same license
@@
 
-This study empirically show from the surveys and the clone detection experiment that
+This study empirically shows from the surveys and the clone detection experiment that
 online code clones occur on Stack Overflow and the clones may become toxic due
 to outdated code and software license incompatibility. The findings lead to the
-insight about toxicity of online code clones and we proposed three actionable items
+insight about the toxicity of online code clones, and we proposed three actionable items
 to the software engineering research and the Stack Overflow community.
@@
 also in the study by An et al. \cite{An2017}, some online clones on Stack Overflow are
-originally licensed under more restrictive license than Stack Overflow's CC
-BY-SA 3.0. If these missing-license online clones are reused in a software with
+initially licensed under more restrictive license than Stack Overflow's CC
+BY-SA 3.0. If these missing-license online clones are reused in software with
 an incompatible license, the software owner may face legal issues. Software
@@
 country. For example, Germany's legal system does not have a concept of fair use.
-In addition, the number of minimum lines of code to be consider copying, i.e.,~de minimis,
+Besides, the number of minimum lines of code to be considered copying, i.e.,~de minimis,
 is also differently interpreted from case to case or from country to country.
@@
 paper, we found that code comments and accompanied natural text
-on Stack Overflow were good source of information to decide the direction of
+on Stack Overflow were a good source of information to decide the direction of
 code copying. Thus, by using code clone detection to locate clone candidates
@@
 the direction of cloning. The technique can also be used on Stack Overflow to 
-flag that an answer has high chance of copying from open source projects.
+flag that an answer has a high chance of copying from open source projects.
 
@@
 source code and follow the link to Stack Overflow and then to the original open
-source projects, could also prevent the issue of license violation. We foresee
+source projects could also prevent the issue of license violation. We foresee
 the implementation of the IDE plugin using a combination of scalable code clone
@@
 performed the check using a set of code clone detectors (Simian and SourcererCC)
-and software licensing detector (Ninka) but we had to operate the tools
+and software licensing detector (Ninka), but we had to operate the tools
 manually. Using the knowledge obtained from this study, we plan to build an
@@
 
-In addition, we also performed a study of two open source software auditing
+Also, we also performed a study of two open source software auditing
 platforms/services:~BlackDuck
@@
 Since automatically establishing code cloning direction
-is still an open challenge, one viable solution for now is
+is still an open challenge, one viable solution, for now, is
 encouraging the Stack Overflow developers to always include the origin of the
@@
 posting time. Even better, Stack Overflow can provide an optional form to fill
-in when an answerer post an answer if he or she copies code from other software
+in when an answerer post an answer if he or she copies the code from other software
 projects. The form should include the origin of the code snippet (possibly as a
-GitHub url) and its original license. Using this manually established links at
-posting time, we can then automate the process of checking for outdated code.
+GitHub URL) and its original license. Using this manually established links at
+posting time, we can then automate the process of checking for an outdated code.
 
@@
 accepted answers on Stack Overflow in this study to focus on code snippets that
-solve the question's problem and are often showed on top of the answer list.
+solve the question's problem and are often shown on top of the answer list.
 We investigated the 72,365 Stack Overflow code snippets used in our study and
@@
 cloning patterns. However, instead of defining the patterns beforehand, we
-resorted to extract them from the data sets. We derived them from a manual
+resorted to extracting them from the data sets. We derived them from a manual
 investigation of 679 online clone pairs and adopted one pattern from the study
@@
 \textbf{External validity:} We carefully chose the data sets for our
-experiment so the findings could be generalise as much as possible.
+experiment so the findings could be generalised as much as possible.
 We selected Stack Overflow because it is one of the most popular
@@
 users. There are a large number of code snippets reused from the
-site~\cite{An2017} and there are also several studies encouraging of
+site~\cite{An2017}, and there are also several studies encouraging of
 doing
@@
 Qualitas corpus for Java open source projects containing 111 projects
-\cite{QualitasCorpus}.  The projects span over several areas of software and has
+\cite{QualitasCorpus}.  The projects span several areas of software and have
 been used in several empirical
@@
 based on the number of stars they obtained to represent their popularity. They
-might not represent all Java projects on GitHub and the number of clone pairs
+might not represent all Java projects on GitHub, and the number of clone pairs
 found may differ from other project selection criteria.
@@
 has been put to
-use in several previous studies. In terms of developer-assisting
+use in several previous studies. Regarding developer-assisting
 tools, Seahawk is an Eclipse plug-in that searches and recommends
 relevant code snippets from Stack Overflow~\cite{Ponzanelli2013}. A
-follow up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014}
+follow-up work, Prompter, by Ponzanelli et al.~\cite{Ponzanelli2014}
 achieves the same goal but with improved algorithms. The code snippets
@@
 a given definition of similarity~\cite{Bellon2007}. Given an open
-interpretation of ``definition of similarity'', there are various
+interpretation of ``definition of similarity,'' there are various
 clone detection tools and their siblings, code plagiarism detectors,
-invented based on plethora of different code similarity
+invented based on a plethora of different code similarity
 measurements~\cite{Roy2008, Ragkhitwetsagul2016,emse,Svajlenko2014}. 
@@
 
-\textbf{Cloning patterns} is initially defined 
+\textbf{Cloning patterns} are initially defined 
 by Kapser et al.~\cite{Kapser2003,Kapser2008} by studying clones in 
@@
 code give detrimental effects to the software since they may 
-introduce vulnerabilities. Our study similarly finds
+introduce vulnerabilities. Our study similarly finds the
 % on % the context of 
@@
 reported that cloned code is commonly used for enhancing existing code. Their
-analysis shows that the cloned code from Stack Overflow have negative effects to
+analysis shows that the cloned code from Stack Overflow has detrimental effects on
 quality of the apps. The median percentage of bug fixing commits after adding
@@
 with statistical significance.
-Baltes et al.~\cite{Baltes2017} discovered that two
-thirds of the clones from the 10 most frequently referenced Java code snippets on Stack
+Baltes et al.~\cite{Baltes2017} discovered that two-thirds of the clones 
+from the 10 most frequently referenced Java code snippets on Stack
 Overflow do not contain attributions.
@@
 The online survey of 201 high-reputation Stack Overflow developers (i.e.,~answerers)
-show that although the developers are aware of outdated code in their answers,
+shows that although the developers are aware of outdated code in their answers,
 19.8\% of them rarely or never fix the outdated code. In addition, 62\% of the participants

### 2018-05-24 cloverflow-tse/cloverflow.tex
Another round of revision on the TSE paper.

@@
 	software licenses. For 153 of them, we found evidence that they have been copied
-	from a specific open source project. 100 of them we found to be outdated. %
+	from a specific open source project. 100 of them were found to be outdated. %
 	% and questionable for being reused.
@@
 empirically study the online code clones between Stack Overflow and open source
-projects and their toxicity.
+projects, and their toxicity.
 
@@
 the University of Molise in Italy where the third author
-works, the \texttt{comp.lang.java.programmer} group and the Software Engineering
+works, the \texttt{comp.lang.java.programmer} group, and the Software Engineering
 Facebook page. 
@@
 January 2016. % The archived dump has a size of 9 gigabytes.
-The data dump is in XML, and it contains information of posts (questions and
+The data dump is in XML, and it contains information about posts (questions and
 answers). We were interested in code snippets embedded in posts which were
@@
 false clones in the analysis or the manual investigation
-phase~\cite{Sajnani2016}, while at the same time may create some false negatives,
-i.e.,~increasing precision. On the other hand, setting a low threshold
+phase~\cite{Sajnani2016}, i.e.,~increasing precision. 
+Nonetheless, it may create some false negatives. 
+On the other hand, setting a low threshold
 results in a larger number of clone candidate pairs to look at, i.e.,~increasing recall, 
@@
 Moreover, the large number of clone
-pairs will hinder the full manual validation of the clones.
+pairs hinders a full manual validation of the clones.
 % and one needs to
@@
 setter methods), and non-trivial clones. The manual check found 26 non-clone
-pairs; 322 trivial clone pairs and 34 non-trivial clone pairs. Next, we increased the
+pairs, 322 trivial clone pairs, and 34 non-trivial clone pairs. Next, we increased the
 threshold to ten lines, another well-established minimum clone size for
@@
 In order to get an optimal $t$ value, we did an analysis by choosing
-five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
+five $t$ values of 0.1, 0.3, 0.5, 0.7, 0.9 and studied the merged clone candidates.
 By setting $t=0.7$ according to Bellon's study, we
@@
 than 60\% of their answers. This notification to the answerer can be done 
-via several means, such as contacting the author directly, 
+via several means, such as contacting the author directly or 
 writing a comment saying that the answer is
-already outdated, down-voting the answer or posting a newer answer.
+already outdated.
 The low percentage of outdated code notifications
 reflect the experience of high reputation answerers who accumulate the reputation for a
-long time. Due to the voting mechanism of Stack Overflow, high reputation users
+long time. Due to the voting mechanism of Stack Overflow, high-reputation users
 usually provide high-quality answers to earn upvotes from other users. They are
@@
 
-We received answers from 89 participants. 
-Two participants never
-copy code from Stack Overflow, so we analysed the answers of the remaining 87
-participants.
+We received answers from 89 participants. Two participants never copy code from
+Stack Overflow, so we analysed the answers of the remaining 87 participants. We
+only present a summary of the survey answers in this paper, and the full
+analysis is available as a research note~\cite{Ragkhitwetsagul_RN2017}.
 
@@
 number of months between the date of each Qualitas project and the date the answer
-was posted on Stack Overflow as shown in~\ref{fig:boxplotcloneage}.
+was posted on Stack Overflow as shown in~\Cref{fig:boxplotcloneage}.
 We found that, on average, it took the clones around 2 years since they appeared
@@
 source systems not in Qualitas (e.g.,\ \textsf{Mozilla
-	Rhino}), 10 pairs from Java official documentation from Sun
+	Rhino}), 10 pairs from Java official documentation by Sun
 Microsystems or Oracle, 3 pairs from books, and 1 pair from a company
@@
 The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
-data format change (2\%).
+the data format change (2\%).
 Not all outdated code is toxic. However, the 10 buggy and outdated code snippets 
@@
 We performed a detailed investigation of the 100 outdated answers on Stack
-Overflow two years after the snapshot we have (6 May 2018) 
-on three aspects: newer or higher-voted answers and comments. We found
-that there were 34 posts which contained newer answers and 5 posts which contained answers with a higher number of
+Overflow, on 6 May 2018, approximately two years after the snapshot we analysed was created
+to look for any changes, warnings, or mitigations made to the outdated code snippets.
+We investigated the answers on three aspects: newer answers, higher-voted answers, and comments on the
+outdated answers. We found
+34 posts which contained newer answers and 5 posts which contained answers with a higher number of
 votes than the outdated answers. However, 99 of the 100 outdated answers were still
@@
 	or even check latest documentation''}. The 6 outdated code snippets were still
-not fixed, but the comments themselves may help to warn other Stack Overflow
+not fixed, but the comments themselves may help to warn some of the Stack Overflow
 users.
@@
 appearing in 68 GitHub projects and manually investigated all
-of them. As shown in \Cref{tab:outdated_github}, out of the 102 cloned snippets,
+of them. Out of the 102 cloned snippets,
 13 cloned snippets matched with themselves because some of the Qualitas
@@
 dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
-without evidence of copying. Twelve were buggy. Two of them contains a race condition and
-are found in popular projects: deeplearning4j and Apache Hive.
+without evidence of copying, which of 12 were buggy. A toxic 
+code snippet with a race condition was found in two popular projects: deeplearning4j and Apache Hive.
 \end{boxquote}
@@
 of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects hosted on
-GitHub and 7,112 pairs from 2,427 other projects. Shown in
+GitHub and 7,112 pairs from 2,427 other projects. As shown in
 \Cref{tab:license_github}, the clones were found in highly-starred
@@
 6 of them refer to one of our QS or EX clone pairs.
-We used the Ninka tool to identify software licenses of the 7,207 cloned
+We used the Ninka tool to identify software licenses of the 7,112 cloned
 code snippets automatically. 
@@
 	\centering
-	\label{tab:license_github}
 	\begin{tabular}{lrrrrr}
@@
 	\caption{Clones of the 214 Stack Overflow missing-license code snippets in 131,703 GitHub projects}
+	\label{tab:license_github}
 \end{table}
@@
 \subsubsection{Toxicity of outdated and license-incompatible clones}
-We found only a small number of toxic outdated code snippets in open source projects on
+The insights from our study of toxic code snippets on Stack Overflow are as follows:
+
+\textbf{Outdated clones are not harmful:} We found only a small number of toxic outdated code snippets in open source projects on
 GitHub. Besides 12 buggy and outdated code snippets found in 12 projects, the
@@
 
-On the other hand, the missing licensing statements of online code clones on
+\textbf{License-incompatible clones can be harmful:} The missing licensing statements of online code clones on
 Stack Overflow can cause more damage than outdated code. As shown in our study and
@@
 answers, date/time of the posts) to conclude that the code snippets are actually
-copied from Qualitas to Stack Overflow. This is a burdensome and time-consuming process. We call for more research in
+copied from Qualitas or external sources to Stack Overflow. 
+This is a burdensome and time-consuming process. We call for more research in
 automation of code cloning direction detection. From our experience in this
 paper, we found that code comments and accompanied natural text
-on Stack Overflow were a good source of information to decide the direction of
+on Stack Overflow were a great source of information to decide the direction of
 code copying. Thus, by using code clone detection to locate clone candidates
@@
 \textbf{Preventive measure:} We encourage Stack Overflow to enforce attribution
-when source code snippets have been copied ``from'' licensed software projects
+when source code snippets have been copied \textit{from} licensed software projects
 to Stack Overflow. Moreover, an IDE plug-in that can automatically detect pasted
@@
 Work similar to ours are studies by An et al.~\cite{An2017},
-Abdalkareem et al.~\cite{Abdalkareem2017}, and Baltes et al.~\cite{Baltes2017}. 
+Abdalkareem et al.~\cite{Abdalkareem2017}, Baltes et al.~\cite{Baltes2017},
+and~Zhang et al.~\cite{Zhang2018}. 
 An et al.~investigated clones
@@
 Overflow do not contain attributions.
+Zhang et al.~\cite{Zhang2018} study quality of code snippets on
+Stack Overflow.
+They show that 31\% of the analysed Stack Overflow posts
+contain potential API usage violations and could lead to program
+crashes or resource leaks.
+%Our study presents another findings that the Stack Overflow code snippets
+%can be problematic due to being outdated or violating the original
+%licenses.
 %In our work, we defined seven patterns of online code cloning and 
@@
 % are much harder to detect. 
-We classified 2,289 clone pairs using seven patterns of online code
-cloning. We discovered 154 clone pairs that have been
-copied, with evidence, from Qualitas projects to Stack Overflow, 111
-clone pairs that have been copied from external sources besides
-Qualitas to Stack Overflow, and 65 clone pairs that are highly
+We classified 2,289 clone pairs using seven patterns of online code cloning. We
+discovered 153 clone pairs that have been copied, with evidence, from Qualitas
+projects to Stack Overflow, 109 clone pairs that have been copied from external
+sources besides Qualitas to Stack Overflow, and 65 clone pairs that are highly
 similar but without evidence of copying.
 
-We performed a detailed analysis of the online clone pairs on two
-aspects: outdated code and potential license violation. The investigation of
-the 154 clone pairs copied, with evidence, from Qualitas to Stack
-Overflow reveals that 101 of them are outdated.  Moreover, we found 214
-code snippets on Stack Overflow that could potentially violate the license of their
-original software.
-
-The online survey of 201 high-reputation Stack Overflow developers (i.e.,~answerers)
-shows that although the developers are aware of outdated code in their answers,
-19.8\% of them rarely or never fix the outdated code. In addition, 62\% of the participants
-are aware of Stack Overflow CC BY-SA 3.0 license applied to code snippets on the website.
-Only 3 answerers include the original license in their answers. 69\% of the answerers
-never check for licensing conflicts between the original code and CC BY-SA 3.0 
-enforced by Stack Overflow.
+The online survey of 201 high-reputation Stack Overflow developers
+(i.e.,~answerers) shows that although the developers are aware of outdated code
+in their answers, 19.8\% of them rarely or never fix the outdated code. In
+addition, 62\% of the participants are aware of Stack Overflow CC BY-SA 3.0
+license applied to code snippets on the website. Only 3 answerers include the
+original license in their answers. 69\% of the answerers never check for
+licensing conflicts between the original code and CC BY-SA 3.0 enforced by Stack
+Overflow. Another survey of 87 Stack Overflow visitors shows that Stack Overflow
+code snippets have several issues, including outdated code. 85\% of them are not
+aware of CC BY-SA 3.0 license enforced by Stack Overflow and 66\% never check
+for license conflicts when reusing code snippets.
+
+We support the surveys' findings by performing a detailed analysis of toxic code
+snippets on Stack Overflow. We investigated the online clone pairs on two
+aspects: outdated code and potential license violation. The investigation of the
+153 clone pairs copied, with evidence, from Qualitas to Stack Overflow reveals
+that 100 of them are outdated. Twelve outdated clone pairs are buggy and toxic
+to reuse. Our large-scale clone detection between the outdated code snippets 
+and 130,703 GitHub projects finds 102 candidates of the outdated code being
+used in the wild.
+ Moreover, we found 214 code snippets on Stack Overflow that could
+potentially violate the license of their original software, and they
+occur in 7,112 projects on GitHub.
 

### 2018-06-19 cloverflow-arxiv/cloverflow.tex
Created a version for arxiv.

--- 2018-05-24 cloverflow-tse/cloverflow.tex
@@
-\documentclass[10pt,journal,compsoc]{IEEEtran}
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
+\documentclass[10pt,journal]{IEEEtran}
+
 \usepackage{cite}
-\fi
-
-\usepackage{booktabs} % For formal tables
-\usepackage[utf8]{inputenc}
+\usepackage{booktabs} \usepackage[utf8]{inputenc}
 \usepackage[english]{babel}
@@
 \usepackage{multirow}
-%\usepackage[table]{xcolor}
 \usepackage{float}
@@
 \usepackage{ragged2e}
-\usepackage{cleveref}
 \usepackage{subcaption}
@@
 \usepackage{framed}
+\usepackage{cleveref}
+\usepackage{newtxtext}
+\usepackage{newtxmath}
 
@@
 	basicstyle=\ttfamily\footnotesize,
-	mathescape=true
+        basewidth=0.56em,
+	mathescape=true,
+        fontadjust
 }
@@
 
-\newcommand{\squeezeup}{\vspace{-0.5mm}}
-
 \usepackage{etoolbox}
-\makeatletter
-\patchcmd{\@makecaption}
-{\scshape}
-{}
-{}
-{}
-\makeatother
 
@@
 
-\newcommand\FIXME[1]{{\color{red}\textbf{FIXME: #1}}}
-
-% correct bad hyphenation here
-%\hyphenation{op-tical net-works semi-conduc-tor}
+\overfullrule5pt
 
@@
 
-\author{Chaiyong Ragkhitwetsagul,~Jens Krinke,~Matheus Paixao,~Giuseppe Bianco,~Rocco Oliveto}
-
-% The paper headers
-\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, Month~2017}%
-{Ragkhitwetsagul \MakeLowercase{\textit{et al.}}: Toxic Code Snippets on Stack Overflow}
-% The only time the second header will appear is for the odd numbered pages
-% after the title page when using the twoside option.
-% 
-% *** Note that you probably will NOT want to include the author's ***
-% *** name in the headers of peer review papers.                   ***
-% You can use \ifCLASSOPTIONpeerreview for conditional compilation here if
-% you desire.
-
-% The publisher's ID mark at the bottom of the page is less important with
-% Computer Society journal papers as those publications place the marks
-% outside of the main text columns and, therefore, unlike regular IEEE
-% journals, the available text space is not reduced by their presence.
-% If you want to put a publisher's ID mark on the page you can do it like
-% this:
-%\IEEEpubid{0000--0000/00\$00.00~\copyright~2015 IEEE}
-% or like this to get the Computer Society new two part style.
-%\IEEEpubid{\makebox[\columnwidth]{\hfill 0000--0000/00/\$00.00~\copyright~2015 IEEE}%
-%\hspace{\columnsep}\makebox[\columnwidth]{Published by the IEEE Computer Society\hfill}}
-% Remember, if you use this you must call \IEEEpubidadjcol in the second
-% column for its text to clear the IEEEpubid mark (Computer Society jorunal
-% papers don't need this extra clearance.)
-
-% for Computer Society papers, we must declare the abstract and index terms
-% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
-% command as these need to go into the title area created by \maketitle.
-% As a general rule, do not put math, special symbols or citations
-% in the abstract or keywords.
-\IEEEtitleabstractindextext{%
+\author{
+  \IEEEauthorblockN{Chaiyong Ragkhitwetsagul\IEEEauthorrefmark{1},
+    Jens Krinke\IEEEauthorrefmark{1}, Matheus
+    Paixao\IEEEauthorrefmark{1},
+    Giuseppe Bianco\IEEEauthorrefmark{2},
+    Rocco Oliveto\IEEEauthorrefmark{2}}\\
+  \IEEEauthorblockA{\IEEEauthorrefmark{1}University College London,
+    London, UK}\\
+  \IEEEauthorblockA{\IEEEauthorrefmark{2}University of Molise,
+    Campobasso, Italy}
+}
+
+\maketitle
+
 \begin{abstract}
@@
 times in 2,427 GitHub projects.
-
-%Online code clones are code fragments that are copied from software projects or
-%online sources to Stack Overflow as examples in questions and answers. % They
-%Due to an absence of a checking mechanism after the code has been copied to
-%Stack Overflow, they can become toxic code snippets, i.e.~they suffer from
-%being outdated or violating the original software license. We present a study
-%incorporating several state-of-the-art tools and techniques to automatically
-%extract and filter detected online clone pairs between 72,365 Java code snippets
-%on Stack Overflow and 111 Java open source projects in the curated Qualitas
-%corpus. We discovered and analysed 2,289 non-trivial online clone candidates.
-%Our investigation of the online clone pairs revealed strong evidence that 154
-%clones have been copied from a Qualitas project to Stack Overflow.  We found 101
-%of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
-%we found 214 code snippets on Stack Overflow that could potentially violate the license of their
-%original software. To better understand the phenomenon, we also surveyed 201 high-reputation Stack Overflow answerers
-%(33\% response rate) and found that 131 of the answerers (65\%) have ever been notified of
-%outdated code in the answers and 26 of them (20\%) rarely or never fix the outdated
-%code. Only 3 answerers explicitly include software licenses in their answers and
-%138 answerers (69\%) never check for licensing conflicts between their copied code
-%snippets and Stack Overflow's CC BY-SA 3.0.
 \end{abstract}
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Code Clone Detection, Stack Overflow, Outdated Code, Software Licensing
-\end{IEEEkeywords}}
-
-% make the title area
-\maketitle
-
-% To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEtitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
-% or transmag modes are not selected <OR> if conference mode is selected 
-% - because all conference papers position the abstract like regular
-% papers do.
-\IEEEdisplaynontitleabstractindextext
-% \IEEEdisplaynontitleabstractindextext has no effect when using
-% compsoc or transmag under a non-conference mode.
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
-
-%The popularity of the Internet encourages tremendous amount of source code
-% being shared online.
+\section{Introduction}\label{sec:introduction}
+
 Stack Overflow is a popular online programming community with 7.6 million users,
@@
 Q\&A website to a software project to obtain a functionality, perform a
-particular task, or fixing a bug. % and (3)~code is transferred from one
-% software project to another via a Q\&A website;
-Similar to classic code clones, i.e.,~clones between software systems, online
+particular task, or fixing a bug. Similar to classic code clones, i.e.,~clones between software systems, online
 code clones can lead to license violations, bug propagation, an introduction of
@@
 effects to software reusing them.
-%Using the same analogy, in this study, we are interested in 
 Therefore, we mine Stack Overflow posts, detected online code clones, and analysed the clones to reveal
@@
 as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
-	Stack Overflow: meta.stackexchange.com/questions/131495, 
-	meta.stackexchange.com/questions/11705/, meta.stackexchange.com/questions/12527,
-	meta.stackexchange.com/questions/25956, meta.stackoverflow.com/questions/321291.}
+  Stack Overflow:\\
+  meta.stackexchange.com/questions/131495, .../11705, .../12527,
+	.../25956,\\ .../321291.}
 	 on \textsf{meta.stackexchange.com} about outdated
@@
 {\small{\texttt{compare}}} method several years ago, the code example in Stack
-Overflow post is still unchanged. %This example shows that inconsistencies
-%between online code clones and their originals can lead users of Stack Overflow
-%to reuse outdated code.
-In addition, the original code snippet of {\small\texttt{WritableComparator}}
+Overflow post is still unchanged. In addition, the original code snippet of {\small\texttt{WritableComparator}}
 class in Hadoop is distributed with Apache license version 2.0 while its cloned
@@
 (issue no.~HADOOP-9252\footnote{https://issues.apache.org/jira/browse/HADOOP-9252}).
-%Similar to the first example, the clone code snippet on Stack Overflow does not 
-%include its original Apache v.2.0 license.
 
@@
 days compared to almost every day for the second one. 
-%A quick web search shows
-%that the defective {\small{\texttt{humanReadableInt}}} method in the second
-%example already appears in approximately 500 projects on GitHub. 
 Considering the popularity of Stack Overflow, which has more than 50 million developers visiting
@@
 spread and grow to hundred or thousand copies within only a year or two.
-
-%The code snippet on Stack Overflow can be outdated.
-%Since reusing source code from Stack Overflow is considered a common practice nowadays, the scale of online code cloning is more than intra or inter project clone in a local code bases.
-%This is an emerging and challenging problem.
-Since studies in this area are still limited, we aim to gain more insight of the problem in this study.
-%We are interested to gain more insights of online code clone in this study.
 
@@
 	software licenses. For 153 of them, we found evidence that they have been copied
-	from a specific open source project. 100 of them were found to be outdated. %
-	% and questionable for being reused.
+	from a specific open source project. 100 of them were found to be outdated.
 
@@
 
-%\subsection{Experimental Setup}
-%\vspace{1ex}
 To answer these five research questions, we perform two surveys and an empirical study to
@@
 for good questions and useful answers. Accepted answers receive more reputation
-score than questions and regular answers\footnote{Stack Overflow
-	Reputation:~\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
+score than questions and regular answers\footnote{\url{https://stackoverflow.com/help/whats-reputation}}. Thus, Stack
 Overflow reputation is an indicator of user's skills and their involvement in
@@
 Stack Overflow dump\footnote{\url{https://archive.org/details/stackexchange}} in
-January 2016. % The archived dump has a size of 9 gigabytes.
-The data dump is in XML, and it contains information about posts (questions and
+January 2016. The data dump is in XML, and it contains information about posts (questions and
 answers). We were interested in code snippets embedded in posts which were
@@
 	\label{tab:datasets}
-	%\small
 	\begin{tabular}{lrr}
@@
 \textbf{Clone Detection Tools: } We use clone detection to discover online code
-clones. %\textbf{Clone Detection and Configuration: }
-There are a number of restrictions in terms of choosing the clone detection
+clones. There are a number of restrictions in terms of choosing the clone detection
 tools for this study. The main restriction is due to the nature of code snippets
@@
 and a higher chance of getting false positives. 
-%It is known that lowering the threshold value 
-%is harmful to precision. 
 Moreover, the large number of clone
 pairs hinders a full manual validation of the clones.
-% and one needs to
-%rely on sampling of clone pairs. 
 Three threshold values, six, ten, and fifteen lines, were chosen for our
@@
 pairs.
-%
-%The minimum clone size of 10 lines is
-%considered a standard setting for clone detection in large-scale data sets to
-%avoid trivial clones (e.g.,~\texttt{equals}, \texttt{hashCode}, or getter and
-%setter methods) in the analysis or the manual investigation phase~\cite{Sajnani2016}.  
-%We
-% performed an analysis to confirm this.
-%\begin{figure} 
-%	\centering
-%	\includegraphics[width=\linewidth]{boxplot_clone_size_combined} 
-%	\caption{Size of online code clones.} 
-%	\label{fig:boxplotclonesize}
-%\end{figure}
-%
-%The result is as shown in
-%\Cref{fig:boxplotclonesize}. We found that the distribution of the manually
-%confirmed true clones 
-%mainly cover the size from about 10 to 20 lines. Increasing
-%the threshold to be higher than 10 would remove some of the
-%true clone pairs.
-%
-%Regarding decreasing the minimum clone size to be less than 10 lines, we reran
-%the two clone detection tools again using a minimum
-%clone size of 6 lines, another well-accepted minimum clone size in clone
-%benchmark~\cite{Bellon2007}. Simian reported 67,172 clone candidate pairs and
-%SourcererCC reported 7,752 clone candidate pairs with 776 common clone pairs. 
-%With this large amount of clone
-%candidate pairs, it is not feasible to manually confirm all of the clones and we
-%must rely on sampling. This will result in weaker findings and
-%weaker conclusion. Thus, we decide pick the minimum clone size of 10 lines
-%to keep the balance between the number of non-trivial clone pairs and the
-%feasibility of manual clone investigation.
-%We made sure that they 
-%detected only non-trivial clones by increasing the minimum clone size to ten
-%lines.
-%(denoted as \textit{D}), and (2)~the discovered configurations for
-%Bellon's Java projects from \textit{EvaClone}~\cite{Wang2013}, a study
-%of optimising clone detectors' configurations based on clone agreement
-%(denoted by \textit{E}). \Cref{t:param_tuning} shows the two configurations.
-%In total, we have four configurations: Simian with the default
-%configuration ($S_D$), Simian with the EvaClone configuration ($S_E$), 
-%NiCad with the default configuration ($N_D$)
-%and NiCad with the EvaClone configuration ($N_E$).
-%
-%We encountered NiCad failures with a few Qualitas projects.~$N_D$
-%could not detect clones in \textsf{hibernate} due to clustering
-%errors. $N_E$ generated errors during code normalisation for 5
-%projects including \textsf{vuze}, \textsf{hibernate},
-%\textsf{myfaces}, \textsf{netbeans}, and \textsf{spring}. We have
-%contacted the creator of NiCad regarding the issues. They identified
-%the issues as problems in the TXL grammar and as problems of long file
-%paths, and will be fixed in the next NiCad releases.
-%
 The number of online clone pairs reported using the minimum clone size of 10 lines
@@
 pairs while SourcererCC reports 1,678 clone pairs. 
-%SourcererCC reports more clones due to its capability of detecting
-%clones of type-1 to type-3 while Simian only detects type-1 clones.
 The average clone size reported by Simian is
@@
 	\label{tab:orig_stats}
-	%\small
-	%\resizebox{\columnwidth}{!}{%
 	\begin{tabular}{lrr}
@@
 		\bottomrule
-	\end{tabular} %
-	%}
-\end{table}
+	\end{tabular} \end{table}
 
@@
 likelihood to be duplicate and must be merged. 
-%By using this agreement-based
-%approach, we reduced the number of clone candidates for manual investigation and
-%avoid a threat to internal validity of double counting the same clone pair twice
-%by merging the ones agreed by the two tools. 
 To find agreement between two clone
@@
 fragments \textit{CF} are contained in each other:
-%\squeezeup
-%\begin{displaymath}
-%overlap(\textrm{\textit{CF}}_1, \textrm{\textit{CF}}_2) = \frac{|lines(\textrm{\textit{CF}}_1) \cap lines(\textrm{\textit{CF}}_2)|}{|lines(\textrm{\textit{CF}}_1) \cup lines(\textrm{\textit{CF}}_2)|}
-%\end{displaymath}
-% \squeezeup
 \begin{displaymath}
@@
 \end{displaymath}
-\noindent%
+\noindent
 A clone pair \textit{CP} is formed by two clone fragments
@@
 (\textit{CF$_1$}, \textit{CF$_2$})
-%, and the \textit{good-value} and
 and the \textit{ok-value} of two clone pairs is defined as
-%\squeezeup
-%\begin{align*}
-%good(\textrm{\textit{CP}}_1, \textrm{\textit{CP}}_2) = min(overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_1,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_1), \\ overlap(\textrm{\textit{CP}}_1.\textrm{\textit{CF}}_2,\textrm{\textit{CP}}_2.\textrm{\textit{CF}}_2))
-%\end{align*}
 \begin{align*}
@@
 
-\noindent%
+\noindent
 Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$
 are called an \textit{ok-match(t)}  iff, for threshold $t \in [0,1]$ holds 
-%\squeezeup
 \begin{align*}
-%good(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t\\
 ok(\textrm{\textit{CP}}_1,\textrm{\textit{CP}}_2) & \geq t
@@
 validation, the results from the two investigators were compared. 
-%and 607 (26\%)
-%conflicts were discussed and resolved. 
 There were 338 (15\%) conflicts between 
@@
  i.e.,~from UD to QS or EX.
-%There were three conflicts where the two
-%investigators could not find a consensus and the third author was involved for
-%the final judgement.
-
-% No. of conflicts = 37 (ok) + 352 (simian) + 218 (SCC)
-% 33 pairs are changed from MP.UD --> CR.EX,QS
-% 112 pairs are changed from CR.UD --> MP.EX,QS
 
@@
 	\label{tab:classification_scheme}
-	%\resizebox{\columnwidth}{!}{%
 	\begin{tabular}{c@{~~}p{7.35cm}}
@@
 		\bottomrule 
-	\end{tabular}  %
-	%}
-\end{table}
+	\end{tabular}  \end{table}
 
@@
 the reported clones in phase 1 
-%Using the $S_D$ clone report,
-%snippets were ranked according to (1)~clone pair frequency,
-%(2)~popularity (i.e.,~number of associated Qualitas projects),
-%(3)~clone size in SLOC, and (4)~ratio of cloned code per snippet. We
-%selected these four criteria so that we could cover the online clones
-%from various aspects. We selected the top 10 from each ranking and
-%obtained 34 unique Stack Overflow snippets. The snippets were
-%associated with 697 clone pairs.
-%\subsection{Defining Online Code Cloning Patterns}
 using Kapser's cloning patterns. We found that 
-% the
-% clone pairs were categorised into either Customisation or Templating.
-% Thus, 
 Kapser's patterns are too broad for our study and a more suitable and
@@
 definition in Kapser's~\cite{Kapser2008}.
-%of {\small\verb|equals()|} methods,
-%getters/setters, well-known code patterns such as deleting a file
-%or implementing a {\small{\texttt{toString}} method,
-% or IDE-generated code such as GUI components. 
  Pattern
@@
 
-%\begin{table}
-%	\centering
-%	\caption{Stack Overflow answerers taken the survey}
-%	\label{tab:survey_target}
-%	\begin{tabular}{rrrr}
-%		\toprule
-%		Reputation & Sent emails & Answers & Rate \\
-%		\midrule
-%		963,731--6,999 & 607 & 201 & 33\% \\
-%		\bottomrule
-%	\end{tabular}
-%\end{table}
-
 \subsubsection{The Answerer Survey}
@@
 their outdated code.
-%
-%The responses from the answerers support our findings of outdated online code
-%clones in RQ3.
-
-%\vspace{0.25cm}
-%\textit{How often are Stack Overflow
-%	answerers aware of licensing conflicts when
-%	they answer a question on Stack Overflow?} 
-%\vspace{0.25cm}
 
@@
 
-%Similar to outdated code, the responses from the answerers support our findings
-%of licensing conflicts in online code clones in RQ4 and possibly explain why most of
-%the clones copied from open source projects and external sources do not include
-%their original software license.
-
 \begin{boxquote}
@@
 	and Stack Overflow's CC BY-SA 3.0.
-%	To answer RQ 1.1, although most of the Stack Overflow answerers are aware that their code
-%	can be outdated, half of the answerers were very rarely notified of
-%	outdated code in the answers. After being notified, some of them rarely or never fix the outdated code.
-%	More than half of the answerers are aware of Stack Overflow's
-%	CC BY-SA 3.0 license. Only 3 answerers explicitly include software license in their answers
-%	while some of them choose to include the license in their profile page instead. More than half of the
-%	answerers never check for licensing conflicts between their copied code snippets
-%	and Stack Overflow's CC BY-SA 3.0.
 \end{boxquote}
@@
 
-%The visitors survey confirms the findings from the previous studies that Stack
-%Overflow code snippets can be problematic~\cite{Zhang2018,Acar2016,An2017,Fischer2017}. 
-%Sixty-six
-%percent of the visitors experienced a problem from reusing Stack Overflow code
-%snippets ranging from incorrect solutions, outdated solutions, mismatched
-%solutions, to buggy code. Although they are aware of the problems, half of them
-%(56\%) never reports back to the Stack Overflow discussions. On the other hand,
-%the visitors rarely give attributions to Stack Overflow when they reuse code
-%snippets from the website, similar to the findings reported
-%by~\cite{Baltes2017}. The visitors are generally not aware of the CC BY-SA 3.0
-%license, and more than half of them never check for license compatibility when
-%reusing Stack Overflow code snippets. 
-%Sixty-nine Stack Overflow visitors (79\%) who adopted code from Stack Overflow never 
-%check if the code snippet originated from a different source (e.g.,~an open source project) 
-%and if they had an incompatible license to their projects.
-%Moreover, we also found that 9\% of the participants
-%encountered legal issues by copying code from Stack Overflow.
-
 \begin{boxquote}
@@
 	and 59 Qualitas proejcts. 
-	%After the manual confirmation, 2,076 pairs as true positives, i.e.,~
-	%they are manually confirmed as clones, which 
-	%account for 59 Qualitas projects and
-	%443 Stack Overflow code snippets.
 \end{boxquote}
@@
 	\label{tab:classification_good_o}
-	%\small
-	%\resizebox{\columnwidth}{!}{%
 	\begin{tabular}{lrrrrrrrr}
@@
 	\end{tabular} 
-	%}
 \end{table*}
-
-%\begin{table}
-%	\centering
-%	\caption{Statistics of clone sizes}
-%	\label{tab:clone_stats}
-%	\begin{tabular}{lrrrr}
-%		\toprule
-%		Clones & Min & Max & Mean & Median \\
-%		\midrule
-%		QS & 10 & 135 & 18.6 & 14 \\
-%		SQ & 21 & 21 & 21.0 & 21 \\
-%		UD & 10 & 104 & 18.1 & 14 \\
-%		EX & 10 & 48 & 16.7 & 14 \\
-%		BP & 10 & 55 & 19.9 & 21 \\
-%		IN & 11 & 22 & 13.8 & 13.0 \\
-%		\bottomrule
-%	\end{tabular} 
-%\end{table}
 
@@
 	\label{tab:qs_qualitas_projects}
-	%\small
-	%\resizebox{\columnwidth}{!}{%
 	\begin{tabular}{lrlr}
@@
 	\end{tabular} 
-	%}
 \end{table}
@@
 \textit{``Copied shamelessly from
-	org.bouncycastle.crypto.generators.PKCS5S2ParametersGenerator''} which is an
+	org.bouncycastle.crypto.generators.PKCS5S2ParametersGene\-rator''} which is an
 open source project not included in the Qualitas corpus. Post 92962 includes a {\small\texttt{VerticalLabelUI}}
@@
 
-%There are other EX pairs which
-%are copied from open source libraries or Java SDK such as \textsf{Mozilla
-%	Rhino}, \textsf{java.util}, \textsf{javax.swing}, \textsf{javax.servlet}, and
-%the \textsf{bouncycastle} cryptography project.
-
 \textbf{UD: Unknown Direction.} We found 107 online clone pairs, reduced to 65
@@
 pairs, followed by 14 from \textsf{spring}, 13 from \textsf{eclipse}, and 9 from
-\textsf{hadoop}. Besides the two examples of outdated code in % \textsf{hadoop}'s
-{\small{\texttt{WritableComparator}}} and
+\textsf{hadoop}. Besides the two examples of outdated code in {\small{\texttt{WritableComparator}}} and
 {\small{\texttt{StringUtils}}} class from \textsf{hadoop} shown in
@@
 heavily modified on February 5, 2016.
-
-%\begin{figure}
-%	\centering
-%	\includegraphics[width=0.7\linewidth]{mod_types}
-%	\caption{Six code modification types found when comparing the outdated clone pairs to their latest versions}
-%	\label{fig:mod_types}
-%\end{figure}
 
@@
 					rewritten completely}}
-		\end{tabular} %
-	}
+		\end{tabular} 	}
 \end{table*}
@@
 	\label{tab:license_abc}
-	%\small
 	\resizebox{\linewidth}{!}{
@@
 
-%If developers copy and reuse these licensed pieces of code in their projects,
-% conflicts may happen without their realisation.
 In our study, we reveal another type of toxic code snippets which is software
@@
 the external sources. We found that 78 out of 93 EX clone pairs have
-incompatible licenses. %They are clones that have been identified to be copied
-% from an external source.
-Similarly, the license statement was removed from Stack Overflow snippets.
+incompatible licenses. Similarly, the license statement was removed from Stack Overflow snippets.
 
@@
 clones in Qualitas contain a license while the Stack Overflow snippets do not.
-%
-%\Cref{fig:sankey_license} shows the direction of changes in online code clone
-% license. The direction of the change is from left to right. The thickness of
-% the line reflects the number of clones for that relationship. In
-% \Cref{fig:sankey_license} (A), we can clearly see that most of the QS online
-% clones have their licenses changed from having a license to ``No license'' on
-% Stack Overflow. The same findings were found for EX online clones as depicted
-% in \Cref{fig:sankey_license} (B). We found that most of the EX clones have
-% their licensing information stripped of after copying to Stack Overflow. These
-% clones are instead covered by the default CC BY-NC-SA 3.0 license of Stack
-% Overflow which is strongly permissive. These used-to-be-licensed code are
-% dangerous for being reused because they can implicitly conflict with the
-% reused software's license.
 
@@
 
-\subsection{Overall Discussion} %What can we learn for the results? For example,
-% if a developer explicitly reports in his/her code that the snippet was copied
-% from stackoverfow, are there some benefits? We could notify - for instance -
-% the developer when some new issues related to the snippet are posted on
-% stackoverflow? Or could we force people posting code on SO to explicitly
-% report licensing information? Or, could we implement an intelligent IDE that
-% when pasting code from external resource checks for licensing violation? These
-% of course are only some (crazy?) ideas that could be developed on the top of
-% the results we have achieved with this study...
-
-%We discovered two issues regarding code snippets on Stack Overflow in this
-% study: (1)~outdated online clones on Stack Overflow and (2)~missing or
-% incompatible license in Stack Overflow snippets.
-%that there is a considerable amount of cloned code between Stack Overflow that
-% are cloned from 111 projects in the Qualitas corpus. 64 clone pairs are
-% outdated and 358 snippets have incompatible software licenses to their
-% originals.
+\subsection{Overall Discussion}
 
@@
 
-%The implementation and the evaluation of the
-%above actionable items is part of the agenda of our future work.
-
 \section{Threats to Validity}
@@
 found that 62,245 of them (86\%) are also the highest voted answers.
-%While most of the time they are also the highest voted answers, some
-%times they are not. 
 We plan to incorporate the highest voted answers in future work.
-% We also
-% applied the Bellon's clone agreement to 4 different combinations of
-% the tools' configurations.  For disagreed clone pairs, we applied
-% several filters to remove spurious and uninteresting clones.
-
-% The number of online clones we found are subject to the clone
-% detectors and their configurations.
-
-% We also
-% performed a pairwise matching between the default and EvaClone
-% configurations of the two clone detection tools.
 
@@
 investigator.
-
-%In addition, we are aware of voting mechanism in Stack Overflow and plan to
-%incorporate highest-vote answers in the future work.
 
@@
 research and
-% Its rich and developer-driven data are invaluable. Since
-% posts on Stack Overflow may contain code snippets embedded within
-% natural language text, they become a huge database for source code and
-% code-relevant information. 
-%The Stack Overflow data set 
 has been put to
@@
 e.g.,~\cite{Movshovitz-Attias2013,Rosen2016,Choetkiertikul2015,Bosu2013}.
-% , while some studies aim to improve Stack Overflow itself~\cite{Diamantopoulos2015, Wang2014}.
 
@@
 controversial~\cite{Sajnani2016,Kapser2003,Kapser2008,Krinke2008,Hotta2010,Gode2011,Harder2013}.
-% However, by only knowing how many code clones residing in software
-% and how they evolve~\cite{Pate2013,Mondal2011} can provide several
-% valuable insights into the software systems.
 Code clones have several
@@
 measurements~\cite{Roy2008, Ragkhitwetsagul2016,emse,Svajlenko2014}. 
-% Some tools use string comparison techniques such as Simian~\cite{simian}. 
-% NiCad~\cite{Roy2008,Cordy} exploits the Longest Common Subsequence
-% (LCS) string similarity measure after applying code pretty-printing
-% using TXL~\cite{Cordy2006}. 
 Many tools do not work on original source code directly but detect clones
@@
 \textbf{Clone agreement} is useful when a clone oracle is
-absent. %Since clone detectors are different in their detection
-%approaches, they may behave differently and report different clones
-%even on the same data set. 
-By exploiting the different behaviours of clone detectors,
+absent. By exploiting the different behaviours of clone detectors,
 one can look for their agreement and obtain
-highly-confident clones~\cite{Bellon2007,Wang2013}. %Using the same
-%data set, 
-Clone pairs that are agreed by multiple tools are more assured to be true
+highly-confident clones~\cite{Bellon2007,Wang2013}. Clone pairs that are agreed by multiple tools are more assured to be true
 clones than the ones reported by only a single
 tool~\cite{Wang2013,cr2016ssbse,Funaro2010}.
-% There are studies that report sensitivities of the tools'
-% configurations to the results~\cite{Wang2013,cr2016ssbse}, showing
-% that searching for an optimal configuration for every new data set
-% is preferred.
 
@@
 in our online clone license analysis.
-%We use Ninka to analyse software license from Stack 
-%Overflow snippets and Qualitas projects.
 
@@
 introduce vulnerabilities. Our study similarly finds the
-% on % the context of 
 outdated code on Stack Overflow.
@@
 crashes or resource leaks.
-%Our study presents another findings that the Stack Overflow code snippets
-%can be problematic due to being outdated or violating the original
-%licenses.
-%In our work, we defined seven patterns of online code cloning and 
-%performed a large-scale manual check of 3,632 clone pairs. 
-%We discovered 112 clone pairs with strong evidences, 
-%based on natural text in comments and post contents, that they 
-%were copied from Qualitas to Stack Overflow. By comparing the 
-%clones to their latest versions in the software, we found that 
-%64 code snippets on Stack Overflow are outdated and possibly harmful for reuse.
-
-%\section{Future Work}
-%Since this study is limited to only Java language, we are interested in expanding the study further to other popular programming languages such as C, C++, Python, and Javascript on Stack Overflow.
-The similar study of outdated code and software licensing violation can be repeated.
-It is interesting to compare the findings among different programming languages.
-Moreover, other popular software project corpora (e.g.,\ GitHub) can also be included to increase generalisation of the findings.
-%
-%We are eager to tackle the issues of outdated and license-violating online code clones with an automated tool.
-The tool should incorporate a scalable clone detection method of locate similar code from programming Q\&A websites such as Stack Overflow and online code repositories like GitHub.
-It analyses a software project under development and reports clones that are copied from Stack Overflow.
-The reported clones have traces to their origins in open source projects or websites along with their freshness (fresh/outdated/dead) so that the developer of the project can be aware of changes made to the copied code snippets.
-Lastly, the license of the original source code is also reported so the developer can make an informed decision of whether he or she will incorporate that code snippet into their own project.
 
@@
 such as Stack Overflow. 
-% They are similar to classical clones in software
-% projects where they can be outdated and violating software license but
-% are much harder to detect. 
 We classified 2,289 clone pairs using seven patterns of online code cloning. We
@@
 
-% use section* for acknowledgment
-\ifCLASSOPTIONcompsoc
-  % The Computer Society usually uses the plural form
 \section*{Acknowledgments}
-\else
-  % regular IEEE prefers the singular form
-  \section*{Acknowledgment}
-\fi
 
@@
 
-% biography section
-% 
-% If you have an EPS/PDF photo (graphicx package needed) extra braces are
-% needed around the contents of the optional argument to biography to prevent
-% the LaTeX parser from getting confused when it sees the complicated
-% \includegraphics command within an optional argument. (You could create
-% your own custom macro containing the \includegraphics command to make things
-% simpler here.)
-%\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mshell}}]{Michael Shell}
-% or if you just want to reserve a space for a photo:
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
-is working toward the PhD degree in Computer Science at University College London, where he is part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
-He is supervised by Dr.~Jens Krinke and Dr.~David Clark.
-His research interests include code search, code clone detection, software plagiarism, search-based software engineering, and mining software repository.
-\end{IEEEbiography}
-\vspace{-1cm}
-
-% % if you will not have a photo at all:
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.jpg}}]{Jens Krinke}
-is Senior Lecturer in the Software Systems Engineering
-Group at the University College London, where he is Director of CREST,
-the Centre for Research on Evolution, Search, and Testing.  His main
-focus is software analysis for software engineering purposes. His
-current research interests include software
-similarity, modern code review, and mutation testing.  He is well known for his work on
-program slicing and clone detection.
-\end{IEEEbiography}
-\vspace{-1cm}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
-is currently a PhD candidate in the Computer Science Department at University College London, where he is part of the CREST centre.~He is supervised by Dr.~Jens Krinke, Prof.~Mark Harman, Dr.~Emmanuel Letier and Dr.~Yuanyuan Zhang.
-His research interests include software architecture, search based software engineering, technical debt, empirical software engineering and modern code review.
-\end{IEEEbiography}
-\vspace{-1cm}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{giuseppe.png}}]{Giuseppe Bianco}
-  received his bachelor degree in Computer Science from the University
-  of Molise (Italy) under the supervision of Dr.~Rocco Oliveto. As
-  part of an Erasmus+ traineeship, he spent three month at the
-  CREST centre, University College London, UK, under the supervision
-  of Dr.~Jens Krinke.~He is now a project manager at Corsi.it.
-\end{IEEEbiography}
-\vspace{-0.5cm}
-
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{rocco.png}}]{Rocco Oliveto}
-is Associate Professor at University of Molise (Italy), where he is also the Director of the Computer Science Bachelor and Master programs and the Director of the Software and Knowledge Engineering Lab (STAKE Lab).
-He co-authored over 100 papers on topics related to software traceability, software maintenance and evolution, search-based software engineering, and empirical software engineering.
-His activities span various international software engineering research communities.
-He has served as organizing and program committee member of several international conferences in the field of software engineering.
-He was program co-chair of ICPC 2015, TEFSE 2009 and 2015, SCAM 2014, WCRE 2012, and 2013.
-He is general chair for SANER 2018 that will be held in Campobasso from March 20, 2018 to March 23, 2018.
-He is also one of the co-founders and CEO of DataSound, a spin-off of the University of Molise aiming at efficiently exploiting the priceless heritage that can be extracted from big data analysis via machine learning.
-More info at \url{https://dibt.unimol.it/staff/oliveto}.
-\end{IEEEbiography}
-\vfill
-
-% \begin{IEEEbiographynophoto}{Giuseppe Bianco}
-% Biography text here.
-% \end{IEEEbiographynophoto}
-
-% % insert where needed to balance the two columns on the last page with
-% % biographies
-% %\newpage
-
-% \begin{IEEEbiographynophoto}{Rocco Oliveto}
-% Biography text here.
-% \end{IEEEbiographynophoto}
-
-% You can push biographies down or up by placing
-% a \vfill before or after them. The appropriate
-% use of \vfill depends on what kind of text is
-% on the last page and whether or not the columns
-% are being equalized.
-
-%\vfill
-
-% Can be used to pull up biographies so that the bottom of the last one
-% is flush with the other column.
-%\enlargethispage{-5in}
-
-% that's all folks
 \end{document}

### 2018-06-20 cloverflow-tse/cover_letter/cover_letter.tex
Added the separated Abstract PDF (required by TSE) and updated the Novelty Statement + small fixes in the cover letter.

@@
 
-Lastly, we would also like to ask the reviewers to comment on how to address the
-newly established page limits of IEEE TSE that was enforced on 18 February 2018, after our previous
-submission (15 November 2017). After incorporating the suggestions from the reviewers and
-rewriting, our paper is now extended to 22 pages. Are there any elements that
-could or should be removed, or should a split into two separate papers be
-considered?
+%Lastly, we would also like to ask the reviewers to comment on how to address the
+%newly established page limits of IEEE TSE that was enforced on 18 February 2018, after our previous
+%submission (15 November 2017). After incorporating the suggestions from the reviewers and
+%rewriting, our paper is now extended to 22 pages. Are there any elements that
+%could or should be removed, or should a split into two separate papers be
+%considered?
 
@@
 	nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from
-	their report~\cite{CORSI2017} that while they check for code copied from open
+	their report~\citep{CORSI2017} that while they check for code copied from open
 	source projects including GitHub and Stack Overflow and analyse their license
@@
 	\item This is a great insight! We expanded the idea further and came up with a suggestion for an
-	automated technique to facilitate human investigator on finding provenance and
+	automated technique to facilitate human investigator on finding clone provenance and
 	included it in a section called Automated cloning direction detection in the

### 2018-06-20 cloverflow-arxiv/cloverflow.orig.tex

--- 2018-05-24 cloverflow-tse/cloverflow.tex
@@
-\documentclass[10pt,journal,compsoc]{IEEEtran}
-
-% *** CITATION PACKAGES ***
-%
-\ifCLASSOPTIONcompsoc
-  % IEEE Computer Society needs nocompress option
-  % requires cite.sty v4.0 or later (November 2003)
-  \usepackage[nocompress]{cite}
-\else
-  % normal IEEE
+\documentclass[10pt,journal]{IEEEtran}
+
 \usepackage{cite}
-\fi
-
 \usepackage{booktabs} % For formal tables
@@
 \usepackage{amsmath}
+%\usepackage{mathpazo}
 \usepackage{amsfonts}
 \usepackage{framed}
+\usepackage{cleveref}
+\usepackage{newtxtext}
+\usepackage{newtxmath}
 
@@
 times in 2,427 GitHub projects.
-
-%Online code clones are code fragments that are copied from software projects or
-%online sources to Stack Overflow as examples in questions and answers. % They
-%Due to an absence of a checking mechanism after the code has been copied to
-%Stack Overflow, they can become toxic code snippets, i.e.~they suffer from
-%being outdated or violating the original software license. We present a study
-%incorporating several state-of-the-art tools and techniques to automatically
-%extract and filter detected online clone pairs between 72,365 Java code snippets
-%on Stack Overflow and 111 Java open source projects in the curated Qualitas
-%corpus. We discovered and analysed 2,289 non-trivial online clone candidates.
-%Our investigation of the online clone pairs revealed strong evidence that 154
-%clones have been copied from a Qualitas project to Stack Overflow.  We found 101
-%of them (66\%) to be outdated and potentially harmful for reuse.  Furthermore,
-%we found 214 code snippets on Stack Overflow that could potentially violate the license of their
-%original software. To better understand the phenomenon, we also surveyed 201 high-reputation Stack Overflow answerers
-%(33\% response rate) and found that 131 of the answerers (65\%) have ever been notified of
-%outdated code in the answers and 26 of them (20\%) rarely or never fix the outdated
-%code. Only 3 answerers explicitly include software licenses in their answers and
-%138 answerers (69\%) never check for licensing conflicts between their copied code
-%snippets and Stack Overflow's CC BY-SA 3.0.
 \end{abstract}
 
-% Note that keywords are not normally used for peerreview papers.
-\begin{IEEEkeywords}
-Code Clone Detection, Stack Overflow, Outdated Code, Software Licensing
-\end{IEEEkeywords}}
-
-% make the title area
-\maketitle
-
-% To allow for easy dual compilation without having to reenter the
-% abstract/keywords data, the \IEEEtitleabstractindextext text will
-% not be used in maketitle, but will appear (i.e., to be "transported")
-% here as \IEEEdisplaynontitleabstractindextext when the compsoc 
-% or transmag modes are not selected <OR> if conference mode is selected 
-% - because all conference papers position the abstract like regular
-% papers do.
-\IEEEdisplaynontitleabstractindextext
-% \IEEEdisplaynontitleabstractindextext has no effect when using
-% compsoc or transmag under a non-conference mode.
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
-
-\IEEEraisesectionheading{\section{Introduction}\label{sec:introduction}}
+\section{Introduction}\label{sec:introduction}
 
@@
 
-\noindent%
+\noindent
 Two clone pairs $\textrm{\textit{CP}}_1$ and $\textrm{\textit{CP}}_2$

### 2018-06-20 cloverflow-tse/cloverflow.tex
Fixed fonts in math mode.
Added the separated Abstract PDF (required by TSE) and updated the Novelty Statement + small fixes in the cover letter.
Fixed the AC --> NC in the TSE version.
Last proof reading with typo fixes before submitting to TSE.

@@
 \usepackage{amsmath}
+\usepackage{mathpazo}
 \usepackage{amsfonts}
 \usepackage{framed}
+\usepackage{cleveref}
 
@@
 % The paper headers
-\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, Month~2017}%
+\markboth{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING,~Vol.~X, No.~Y, Month~2018}%
 {Ragkhitwetsagul \MakeLowercase{\textit{et al.}}: Toxic Code Snippets on Stack Overflow}
@@
 investigated the sampled clone pairs and classified them into three groups:
-non-clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
+not clones, trivial clones (\texttt{equals}, \texttt{hashCode}, or getter and
 setter methods), and non-trivial clones. The manual check found 26 non-clone
@@
 depicted in \Cref{fig:classification_process}. First, we look at a pair of clone
-fragments to see their similarity. If they are accidentally similar clones after
+fragments to see their similarity. If they are accidentally similar code fragments after
 code normalisation or false positive clones from the clone detection tools, we
@@
 Lastly, during the manual investigation of 2,289 clone pairs, we identified 226 pairs
-as being accidental clones (NC), i.e.,~false positives. After removing
+as not clones (NC), i.e.,~false positives. After removing
 them, the set still contains 2,063 true positive clone pairs between 443 Stack
@@
 method signature, i.e.,~API change (16 occurrences), and method rewriting (15
-occurrences). Moreover, in the 101 outdated pairs, we found 15 ``dead''
+occurrences). Moreover, in the 100 outdated pairs, we found 14 ``dead''
 snippets. These snippets cannot be located in the latest version of the
@@
 modifications applied to variable names or method names, added or deleted
-statements, to a fully rewritten code with new method signatures. 15~pairs are
+statements, to a fully rewritten code with new method signatures. 14~pairs are
 dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
@@
 potentially violate the license of their original software, and they
-occur in 7,112 projects on GitHub.
+occur in 7,112 times in 2,427 projects on GitHub.
 

### 2018-11-13 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Added the draft cover letter for the minor revision.

% Copyright Javier Sánchez-Monedero.
% Please report bugs and suggestions to (jsanchezm at uco.es)
%
% This document is released under a Creative Commons Licence 
% CC-BY-SA (http://creativecommons.org/licenses/by-sa/3.0/) 
%
% BASIC INSTRUCTIONS: 
% 1. Load and set up proper language packages
% 2. Complete the paper data commands
% 3. Use commands \rcomment and \newtext as shown in the example

\documentclass[a4paper,twoside,10pt]{reviewresponse}

% 1. Load and set up proper language packages
%\usepackage[utf8x]{inputenc}
\usepackage{newtxtext}
\usepackage{newtxmath}
\usepackage[latin9]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[english]{babel}
\usepackage{natbib}
\usepackage{float}
\usepackage{multirow}
\usepackage{booktabs} % For formal tables

% 2. Complete the paper data
\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul,~Jens Krinke,~Matheus Paixao,~Giuseppe Bianco,~Rocco Oliveto}
\newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
\newcommand{\myEmail}{{chaiyong.ragkhitwetsagul.14,j.krinke,matheus.paixao.14}@ucl.ac.uk, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
%\newcommand{\mySecEmail}{}
\newcommand{\myTitle}{Cover Letter for the Reviewers of the Paper \\ ``Toxic Code Snippets on Stack Overflow''}
\newcommand{\myShortTitle}{Cover Letter}
\newcommand{\myJournal}{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING}
\newcommand{\myDept}{University College London (UK), University of Molise (Italy)}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\usepackage[linktoc=all]{hyperref}
\usepackage[linktoc=all,bookmarks,bookmarksopen=true,bookmarksnumbered=true]{hyperref}

\hypersetup{
pdfauthor = {\myAuthorsShort},
pdftitle = {\myTitle},
pdfsubject = {\myJournal\xspace},
colorlinks = true,
linkcolor=blue,          % color of internal links
citecolor=black!70!green,        % color of links to bibliography
filecolor=magenta,      % color of file links
urlcolor=black           % color of external links
}

\newcommand\FIXME[1]{{\color{red}\textbf{FIXME: #1}}}

\begin{document}

\thispagestyle{plain}

\begin{center}
 {\LARGE\myTitle} \vspace{0.3cm} \\
 {\large\myJournal} \vspace{0.3cm} \\
 \today \vspace{0.3cm} \\
 \myAuthors \\
 \url{\myEmail} \\
 %\url{\mySecEmail} 
 \vspace{0.3cm} 
 \myDept \vspace{1cm}
\end{center}

%\tableofcontents

%\begin{abstract}
This paper is a journal-first submission to Transactions on Software
Engineering. This is a minor revision the previous submission
no.~TSE-2017-11-0335 and we would like to thank the anonymous reviewers for
taking their time to read our paper carefully. With their useful and
constructive reviews, we improved the work further by adding xxx minor
improvements as listed below to our previous submission as discussed later in this letter.

\begin{enumerate}
	\item A
	\item B
\end{enumerate}

We tried our best to address all the comments from the reviewers. Every
comment led to an improvement on this submission, and we discuss them in order as
shown in the next sections.

%Lastly, we would also like to ask the reviewers to comment on how to address the
%newly established page limits of IEEE TSE that was enforced on 18 February 2018, after our previous
%submission (15 November 2017). After incorporating the suggestions from the reviewers and
%rewriting, our paper is now extended to 22 pages. Are there any elements that
%could or should be removed, or should a split into two separate papers be
%considered?

\clearpage

\section{Reviewer 1}

\rcomment{The paper presents an interesting empirical analysis of what the authors refers to as toxic code clones on Stack Overflow. The paper presents a study using state-of the art clone detection tools and techniques to automatically extract and filter online clone pairs between Stack Overflow and projects in the curated Qualitas corpus. The paper also includes a user survey conducted on Stack Overflow users to assess their awareness of such potential toxic code fragments.he paper is well organized,  sound and the authors spend amount of work in their empirical analysis.
\vspace{0.2cm}

The authors did a very good job in explaining their methodology and the results they obtained from their user survey and the online clone detection experiment.
\vspace{0.2cm}

Probably the least convincing part of the paper is the study on toxic license violations. This limitations however is partially due to the grey zone these licenses proliferations have remained in. Even license violation detection tools only cover a subset of all possible license proliferations which might exist. This is a general issue for all open source developers and not limited to code reuse through Stack Overflow. Authors do acknowledge in their discussion this challenge, due to different legislation in different countries and their goal to increase the SO user awareness of this potential violations is welcome addition.
\vspace{0.2cm}

Threats to validity in terms of generalizability will basically always exist and the authors did a good job in mitigating these challenges or acknowledging the limitations of their studies.
\vspace{0.2cm}

Section 3.6.2 Actionable items is a good start to drive further research in this area. However, a general concern is that the potential overall impact of these toxic code snippets seems to be rather small in terms of number of posts on SO or even in terms of code reuse from SO. Should we really care about them? But then again, I guess any improvement to the overall quality of software is a desirable contribution.}

\rcomment{
\textbf{Minor issues}
Page 17, Col.1, L14-15
As shown in Table 23, the clones were found in highly starred projects (???  29,465 to 10 stars ???) to 1-star projects. Please rephrase
\vspace{0.2cm}

Page 17, Col.2, L11
Software auditing services such as Black Duck Software or nexB, which can effectively check for ...
Please provide the Reference for Black Duck Softwqre or nextB -- you have only later on Page 18
}

\section{Reviewer 2}

\rcomment{Thank you to the authors for the revised manuscript. I think the authors did a great job addressing most comments, specifically, R2C2, C6, C7, C9 and C10.
\vspace{0.2cm}

That said, I still would like more clarification on some of the other comments. My detailed comments are below:
\vspace{0.2cm}

R2C1: I am not sure the new definition fits well within your study context. It was more about technical debt and I would remove that definition and stick to the next sentence where you specifically say that toxic code snippets are snippets that are 1) outdated, ...etc.}

\rcomment{R2C3: After reading your response, I have a few questions - 1) what are these 100 posts you examined? how were they determined? how was the number 100 determined?}

\rcomment{Also, I am not sure that you answered my comment with your analysis. My point was that some may actually expect the code to be outdated and how do you deal with that, they will usually use newer posts/answers. I am not sure you addressed my comments with your analysis.}

\rcomment{R2C4: Again, what are the 100 posts (same issues/questions as above arise)? Also, from the table, I would say that only the deprecation posts (15/100) give an indication of outdated code. I am not sure what the rest of the categories in there tell me about the deprecated code.}

\rcomment{R2C5: This is a major issue for me, and I was really hoping that with this revision the authors would update their dataset. By the time this paper hits publication, your data will be 3 years old! In any case, I will leave the decision to the editor, but really, think about a reader of your paper who might question the findings since the data is old. Again, it was not clear to me what the 100 posts and their analysis provide.}

\rcomment{R2C8: Thank you for clarifying the manual analysis part. Can please provide more details on how this manual analysis determined that something actually originated from SO? Perhaps giving an example would help here. Also, who did this verification?}

\section{Reviewer 3}

\rcomment{I reviewed the previous submission and am impressed by the improvements to the paper. All of my major concerns are addressed in the new version, and I only have a few minor requests for further improvements:

\begin{itemize}
	\item The abstract states that ``We found 100 of them (66\%) to be outdated and potentially harmful for reuse.'' Given the word ``potentially'' this statement is technically true, but the conclusion of the paper is that only 12/100 are actually buggy/harmful. Please revise the abstract to make this clear. The same concern applies to item 3 near the end of Section 1.
\end{itemize}
}

\rcomment{
\begin{itemize}
	\item The introduction states that ``We found that the code snippets are usually not authored directly on the Stack Overflow website but copied from another location.'' To me, this is worded too strongly. Please revise.
\end{itemize}
}

\rcomment{
\begin{itemize}
	\item The new definition of ``toxic code snippets'' is better in terms of content, but the wording is awkward. Please try to express the current definition more clearly/succinctly.
\end{itemize}
}

\rcomment{
\begin{itemize}
	\item Regarding the previous Reviewer 1 Comment 5, please add a sentence or two to the paper that mentions point (c), even if only as potential future work.
\end{itemize}
}

Reviewer 1 Comment 5:
``\textit{(c) if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.}''

\rcomment{Typos, etc:
	\begin{itemize}
		\item In the second sentence of the abstract, ``i.e.'' should be ``e.g.''
		\item On page 14, the sentence ``The intent behind the changes are grouped into six categories as shown in Section 3.4.'' is spurious (as it appears in Section 3.4).
\end{itemize}}

\section{Conclusion}
We would like to thank the reviewers again for their comments.
We have tried our best to address every concern that has been pointed out by the reviewers. This result in several minor improvements throughout the paper.
We believe this new submission is an improvement from the previous version due to the insightful reviews and discussions. We are looking forward to the new reviews.

% Uncomment in case references are needed
%\bibliographystyle{plain}
\bibliographystyle{spbasic}
\bibliography{references}

\end{document}

### 2018-11-14 cloverflow-tse/cloverflow.tex
The almost-complete version of the response letter.

@@
 mechanism after the code has been copied to Stack Overflow, they can become
-toxic code snippets, i.e.,~they suffer from being outdated or violating the
+toxic code snippets, e.g.,~they suffer from being outdated or violating the
 original software license. We present a study of online code clones on Stack
@@
 	\centering
+	\caption{Intents of code changes in the 100 outdated code snippets}
+	\label{tab:intent_outdated}
 	\begin{tabular}{llr}
@@
 	\end{tabular}
-	\label{tab:intent_outdated}
-	\caption{Intents of code changes in 100 outdated code snippets}
 \end{table}
@@
 \Cref{tab:license_github}, the clones were found in highly-starred
-projects (29,465 to 10 stars) to 1-star projects.
+projects (29,465 stars) to lowly-starred star projects (1 star).
 We found 12 code snippets with attributions to Stack Overflow questions/answers and
@@
 an incompatible license, the software owner may face legal issues. Software
-auditing services such as Black Duck Software or nexB, which can effectively
+auditing services such as Black Duck Software\footnote{https://www.blackducksoftware.com} 
+or nexB\footnote{https://www.nexb.com}, which can effectively
 check for license compliance of code copied from open source projects, do not
@@
 platforms/services:~BlackDuck
-Software\footnote{https://www.blackducksoftware.com} and
-nexB\footnote{https://www.nexb.com}. For BlackDuck Software, we found from their
+Software and nexB. For BlackDuck Software, we found from their
 report~\cite{CORSI2017} that while they check for code copied from open source

### 2018-11-14 cloverflow-tse/cover_letter/second_round/cover_letter.tex
The almost-complete version of the response letter.

@@
 \usepackage{float}
+\usepackage{listings} 
 \usepackage{multirow}
@@
 
+\lstset{language=Java,
+	tabsize=2,
+	basicstyle=\ttfamily\footnotesize,
+	mathescape=true
+}
+
 % 2. Complete the paper data
-\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul,~Jens Krinke,~Matheus Paixao,~Giuseppe Bianco,~Rocco Oliveto}
+\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$,~Jens Krinke$^\dagger$,~Matheus Paixao$^\dagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
 \newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
-\newcommand{\myEmail}{{chaiyong.ragkhitwetsagul.14,j.krinke,matheus.paixao.14}@ucl.ac.uk, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
+%\newcommand{\myEmail}{cragkhit@gmail.com, {j.krinke,matheus.paixao.14}@ucl.ac.uk, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
 %\newcommand{\mySecEmail}{}
@@
 \newcommand{\myJournal}{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING}
-\newcommand{\myDept}{University College London (UK), University of Molise (Italy)}
+\newcommand{\myDept}{Mahidol University (Thailand)$^\ast$, University College London (UK)$^\dagger$, University of Molise (Italy)$^\star$}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
  \myAuthors \\
- \url{\myEmail} \\
+% \url{\myEmail} \\
  %\url{\mySecEmail} 
@@
 This paper is a journal-first submission to Transactions on Software
-Engineering. This is a minor revision the previous submission
-no.~TSE-2017-11-0335 and we would like to thank the anonymous reviewers for
+Engineering. This is a minor revision the submission
+no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for
 taking their time to read our paper carefully. With their useful and
@@
 
+Thank you for your insightful comment regarding the toxic license violations.
+As the reviewer has mentioned, software license violation is difficult to identify and validate due to various number of software licenses, differences in country's legislation, and amount of code to be considered copyrighted (vs.~fair use).
+Nevertheless, the case of copying a licensed code snippet from an open source project to Stack Overflow without its license shows a clear potential for software license violation.
+By detecting such case, we can alleviate the license issues by stopping the accidental conversion of strictly licensed code (such as GPL) to permissively licensed code (such as CC BY-SA 3.0 on Stack Overflow).
+We hope that our study will raise awareness about this issue to Stack Overflow and the developers.
+
+Regarding the few number of toxic code snippets in SO posts and code reuse in GitHub, this is partially due to the data set of 111 Java projects from the Qualitas corpus.
+The clones (and the discovered outdated code and potentially license-violating code snippets) reported in this paper are only subject to these 111 projects.
+The number may increase if we expand the amount of open source projects.
+Moreover, this study only focuses on Java, and the situation may be worse or better for other programming languages.
+We have added this discussion into the Threats to Validity.
+\FIXME{To do}
+
 \rcomment{
 \textbf{Minor issues}
-Page 17, Col.1, L14-15
-As shown in Table 23, the clones were found in highly starred projects (???  29,465 to 10 stars ???) to 1-star projects. Please rephrase
 \vspace{0.2cm}
 
+Page 17, Col.1, L14--15
+As shown in Table 23, the clones were found in highly starred projects (???  29,465 to 10 stars ???) to 1-star projects. Please rephrase
+}
+
+We rephrased the sentence to ``As shown in Table 23, the clones were found in highly- starred projects (29,465 stars) to lowly-starred star projects (1 star).''
+
+\rcomment{
 Page 17, Col.2, L11
@@
 }
+
+We have moved the references for Black Duck Software and nextB to their first appearance on Page 17.
 
@@
 
+The 100 posts we examined were the posts containing all the 100 outdated code snippets reported in RQ4, which were discovered by the clone detection tools and manually confirmed by the two investigators.
+
 \rcomment{Also, I am not sure that you answered my comment with your analysis.
@@
 
+We agree that our analysis may not fully answer your comment because we could not capture what the Stack Overflow visitors actually did when they found an outdated answer.
+However, our investigation compared the popularity of the outdated answer and the newer answers based on the number of votes.
+If Stack Overflow visitors reuse the code (or learn from the answers) and they like the answer, they can reward the answer with an upvote.
+In our investigation of the 100 outdated answers, we found that only 5 of the newer answers had higher votes than the outdated answers and 99\% of the outdated answers were still marked as accepted.
+\FIXME{Shall we also discuss the issue of ``accepted answers'' that they are totally relied on the questioner and not other visitors?} We are aware that this may be affected by the duration that the answers appear on a Stack Overflow post.
+The newer answers have less visibility compared to the older answers.
+
+An alternative solution might be directly comparing the number of code reuse from the outdated answers to their newer/higher-voted answers in open source projects (e.g., GitHub). 
+Nevertheless, although we had performed such comparison, we would still suffer from the same timing issue that the newer code snippets have less chance to be reused than the older ones.
+
+We have added this discussion in the Threats to Validity section \FIXME{To do}.
+
 \rcomment{R2C4: Again, what are the 100 posts (same issues/questions as above arise)?
@@
 I am not sure what the rest of the categories in there tell me about the deprecated code.}
+
+The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4.
+The 6 intents of changes in the 100 outdated code snippets shown in the table below (a copy of Table 3 in the previous response letter and Table 20 in the paper) cover \textbf{all} the cases of outdated code.
+
+\begin{table}[H]
+	\centering
+	\begin{tabular}{llr}
+		\toprule
+		Intent & Detail & Amount \\
+		\midrule
+		Enhancement & Add or update existing features & 64 \\
+		Deprecation & Delete dead/deprecated code & 15 \\
+		Bug & Fix bugs & 10 \\
+		Refactoring & Refactor code for better design & 6 \\
+		Coding style & Update to a new style guideline & 3 \\
+		Data change & Changes in the data format & 2 \\
+		\bottomrule
+	\end{tabular}
+	\label{tab:intent_outdated}
+	\caption{Intents of code changes in the 100 outdated code snippets}
+\end{table}
+
+The Deprecation intent partially indicates the cause of outdated code, but not all.
+It represents the code snippets that are outdated due to the use of deprecated functions or APIs.
+With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s).
+Other intents represent different cases of a code snippet being outdated.
+For example, the Bug intent represents a code snippet that previously contained buggy code statements, and was fixed in the newest version.
+The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
+To sum up, the table shows that outdated code can be caused by different intents and not all of them are harmful.
+Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow).
+We slightly modified the section explaining this table to be clearer \FIXME{To do}.
 
@@
 
+We understand your concern about the age of the data set.
+However, we do not expect large differences of the findings if we update the data set.
+The reason is that the Stack Overflow answers are rarely modified.
+As discussed in RQ4, we used this 2-year gap between the Stack Overflow snapshot that we analysed for clones, and the latest version on the web, as a chance to study the evolution of the 100 outdated answers.
+We found that 99\% of the outdated code are still marked as accepted.
+While there were a few newer posts in each of the 100 outdated answers, only 5 newer answers obtained higher votes than the outdated ones.
+Thus, updating the Stack Overflow data to the latest snapshot will mostly increase the chance of finding newer outdated code snippets.
+We have added this to the Threats to Validity section \FIXME{To do}.
+
+The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4.
+Their analysis shows that only a number of the outdated code snippets are harmful.
+47 of the 100 discovered outdated code are found in GitHub projects (12 are buggy code).
+So, according to the 111 Java projects in Qualitas, the outdated code snippets do not widely spread to open source projects.
+
 \rcomment{R2C8: Thank you for clarifying the manual analysis part.
@@
 Also, who did this verification?}
+
+In the case of cloning direction from Stack Overflow $\rightarrow$ Qualitas
+(SQ), we found only one pair with evidence of cloning from Stack Overflow post
+ID 698283 to {\small\texttt{POIUtils.java}} in \textsf{jstock} project (as shown below). 
+The Stack Overflow post can be seen from \url{https://stackoverflow.com/questions/698176/determine-correct-method-signature-during-runtime/698283#698283}.
+The user who asked the question (i.e., Cheok Yan Cheng) on Stack Overflow is an author of \textsf{jstock} (the author's GitHub profile can be seen from \url{https://github.com/yccheok}). The
+question is about determining the right method to call among 7 overloading
+methods of {\small\texttt{setCellValue}} during runtime. We could not find
+evidence of copying or attribution to Stack Overflow in \textsf{jstock}.
+However, considering that the 25 lines of code of
+{\small\texttt{findMethodToInvoke}} method depicted in  in Stack Overflow is
+very similar to the code in \textsf{jstock} including comments, it is almost
+certain that the two code snippets form a clone pair. In addition, the Stack
+Overflow answer was posted on March 30, 2009, while the code in
+{\small\texttt{POIUtils}} class in \textsf{jstock} was committed to GitHub on
+the next day of March 31, 2009. 
+The git blame of the file \texttt{POIUtils.java} 
+containing the clone can be found from \url{https://github.com/yccheok/jstock/blame/master/src/org/yccheok/jstock/gui/POIUtils.java} (line 99--123).
+
+\begin{figure}[H]
+	\begin{lstlisting}
+private Method findMethodToInvoke(Object test) {
+	Method method = parameterTypeMap.get(test.getClass());
+	  if (method != null) {
+	    return method;
+	  }
+
+	// Look for superclasses
+	Class<?> x = test.getClass().getSuperclass();
+	while (x != null && x != Object.class) {
+	  method = parameterTypeMap.get(x);
+	  if (method != null) {
+	    return method;
+	  }
+	  x = x.getSuperclass();
+	}
+
+	// Look for interfaces
+	for (Class<?> i : test.getClass().getInterfaces()) {
+	  method = parameterTypeMap.get(i);
+	  if (method != null) {
+	    return method;
+	  }
+	}
+	return null;
+}
+	\end{lstlisting}
+	\caption{The {\small\texttt{findMethodToInvoke}} that is found to be copied from Stack Overflow post 698283 to {\small\texttt{POIUtils}} class in \textsf{jstock}.}
+	\label{fig:jstock_code}
+\end{figure}
+
+The verification was performed by the first and
+the third authors. The two investigators separately went through each clone pair
+candidate, looked at the clones, and decided if they are a true positive or a
+false positive and classified them into an appropriate pattern. After the
+validation, the results from the two investigators were compared. 
+This discussion can be found in Section 2.2.3 (Manual investigation).
 
@@
 
+Thank you for the comment. We agree with your suggestion and we changed the statement in the abstract to:
+
+``We found 100 of them (66\%) to be outdated. \textbf{Ten of them were buggy and harmful for reuse.} ''
+
+Moreover, we modified the item 3 in the contributions to be:
+
+``100 of them were found to be outdated\textbf{, of which 12 were buggy code.}'' \FIXME{update in the paper}
+
 \rcomment{
@@
 }
+
+Again, we agree with your suggestion.
+The statement has been changed to ``We found that the code snippets are \textbf{often} not authored directly on the Stack Overflow website but copied from another location.''.
+\FIXME{update in the paper}
 
@@
 
+We have added a discussion of the point (c) in the ??? section. \FIXME{To do}
+
 Reviewer 1 Comment 5:
@@
 \end{itemize}}
+
+Thank you for spotting them. They are now fixed.
 

### 2018-11-15 cloverflow-tse/cloverflow.tex
Finalised the response letter. Ready for Jens to look at.

@@
 
-Toxic code snippets mean code snippets that, after incorporating into software,
-the cost of paying back the technical debt exceeds the value it generates in the long run.
+Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.
 Stack Overflow code snippets
@@
 We investigated the answers on three aspects: newer answers, higher-voted answers, and comments on the
-outdated answers. We found
+outdated answers.\footnote{We also found that the Stack Overflow question ID 22262310 that has an outdated code answer from \texttt{WritableComparator.java} (\Cref{fig:before-after}), has a negative score of -1.
+It is interesting to see if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.
+However, it is out of the scope of this study so we leave it as future work.} We found
 34 posts which contained newer answers and 5 posts which contained answers with a higher number of

### 2018-11-15 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Finalised the response letter. Ready for Jens to look at.

@@
 
-Thank you for your insightful comment regarding the toxic license violations.
+We would like to thank you for your insightful comment regarding the toxic license violations.
 As the reviewer has mentioned, software license violation is difficult to identify and validate due to various number of software licenses, differences in country's legislation, and amount of code to be considered copyrighted (vs.~fair use).
@@
 
-We have moved the references for Black Duck Software and nextB to their first appearance on Page 17.
+Thank you for the comment. We have moved the references for Black Duck Software and nextB to their first appearance on Page 17.
 
@@
 
+Thank you for the suggestion on the definition of toxic code snippets.
+Since Reviewer 3 also expresses his/her concern regarding the definition, we revised the definition by removing the technical debt part and shorting it as follows:
+
+``Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.
+Stack Overflow code snippets
+cloned from open source software or online sources can become toxic when they
+are (1)~outdated, (2)~violating their original software
+license, (3) exhibiting code smells, or (4) having security vulnerabilities.''
+
+We believe it is important to differentiate the definition of toxic code snippets from the concrete example of toxic code snippets on Stack Overflow since the idea of toxic code snippets can be applied to any other online sources (e.g., GitHub) as well.
+
 \rcomment{R2C3: After reading your response, I have a few questions - 1) what are these 100 posts you examined? how were they determined? how was the number 100 determined?}
@@
 
-We agree that our analysis may not fully answer your comment because we could not capture what the Stack Overflow visitors actually did when they found an outdated answer.
-However, our investigation compared the popularity of the outdated answer and the newer answers based on the number of votes.
+We agree that our analysis may not fully answer your comment because we could not capture what the Stack Overflow visitors actually did when they already expect an outdated answer.
+The most proper method for this may be doing another developer survey.
+However, our investigation tries to at least shade light on this by comparing the popularity of the outdated answer and the newer answers based on the number of votes.
 If Stack Overflow visitors reuse the code (or learn from the answers) and they like the answer, they can reward the answer with an upvote.
@@
 An alternative solution might be directly comparing the number of code reuse from the outdated answers to their newer/higher-voted answers in open source projects (e.g., GitHub). 
-Nevertheless, although we had performed such comparison, we would still suffer from the same timing issue that the newer code snippets have less chance to be reused than the older ones.
+Nevertheless, although we had performed such comparison, we would still suffer from the same timing issue as the newer answers have shorter window to be reused than the older ones.
 
@@
 The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4.
-The 6 intents of changes in the 100 outdated code snippets shown in the table below (a copy of Table 3 in the previous response letter and Table 20 in the paper) cover \textbf{all} the cases of outdated code.
+The 6 intents of changes in the 100 outdated code snippets, as shown in the table below (a copy of Table 3 in the previous response letter and Table 20 in the paper), cover \textbf{all} the cases of outdated code.
 
@@
 With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s).
-Other intents represent different cases of a code snippet being outdated.
+The five other intents represent other cases of a code snippet being outdated.
 For example, the Bug intent represents a code snippet that previously contained buggy code statements, and was fixed in the newest version.
@@
 Thus, updating the Stack Overflow data to the latest snapshot will mostly increase the chance of finding newer outdated code snippets.
-We have added this to the Threats to Validity section \FIXME{To do}.
+Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{To do}.
 
-The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4.
-Their analysis shows that only a number of the outdated code snippets are harmful.
-47 of the 100 discovered outdated code are found in GitHub projects (12 are buggy code).
-So, according to the 111 Java projects in Qualitas, the outdated code snippets do not widely spread to open source projects.
+The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4. Their analysis shows the following. 
+\begin{enumerate}
+	\item Although they are outdated, after 2 years they still have higher votes than other answers or they are still marked as accepted answers.
+	\item There is only 6\% of the outdated answers that have newer answers that mitigate or point out the toxicity of the outdated code snippets. 
+	\item 47 of the 100 discovered outdated code are found in GitHub projects, of which 12 are buggy code.
+So, based on the 111 Java projects in Qualitas, their outdated code snippets do not widely spread to open source projects.
+\end{enumerate}
 
@@
 
-The verification was performed by the first and
+The investigation was performed by the first and
 the third authors. The two investigators separately went through each clone pair
 candidate, looked at the clones, and decided if they are a true positive or a
-false positive and classified them into an appropriate pattern. After the
-validation, the results from the two investigators were compared. 
+false positive and classified them into an appropriate pattern by following the steps show in Figure 5. 
+After the validation, the results from the two investigators were compared. 
 This discussion can be found in Section 2.2.3 (Manual investigation).
@@
 
-``100 of them were found to be outdated\textbf{, of which 12 were buggy code.}'' \FIXME{update in the paper}
+``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}'' \FIXME{update in the paper}
 
@@
 
+After incorporating yours and Reviewer 2's comment, we revised the definition of toxic code snippets to be more concise and removed the focus on technical debt as follows.
+
+``Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.''
+
 \rcomment{
@@
 
-We have added a discussion of the point (c) in the ??? section. \FIXME{To do}
+We have added a discussion of the point (c) as a footnote in Section 4 as shown below.
 
-Reviewer 1 Comment 5:
-``\textit{(c) if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.}''
+``We also found that the Stack Overflow question ID 22262310 that has an outdated code answer from \texttt{WritableComparator.java} (Figure 1), has a negative score of -1.
+It is interesting to see if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.
+However, it is out of the scope of this study so we leave it as future work.''
 

### 2018-11-18 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Updated the cover letter.

@@
 %\begin{abstract}
-This paper is a journal-first submission to Transactions on Software
-Engineering. This is a minor revision the submission
-no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for
-taking their time to read our paper carefully. With their useful and
-constructive reviews, we improved the work further by adding xxx minor
-improvements as listed below to our previous submission as discussed later in this letter.
+This paper is a journal-first submission to Transactions on Software Engineering.
+This is a minor revision the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully.
+With their useful and constructive reviews, we improved the work further as listed below and as discussed later in this letter.
 
 \begin{enumerate}
-	\item A
-	\item B
+\item We have softened the claims as suggested by Reviewer~3.
+\item While we have considered updating the dataset, we chose not to do so as that would require to remove an important part of our study, the evolution of the identified outdated code snippets.
+Moreover, we don't expect that an update would change the results because Stack Overflow answers are rarely modified.
+\item All other points regarding the experimental method have been addressed carefully and completely.
 \end{enumerate}
 
-We tried our best to address all the comments from the reviewers. Every
-comment led to an improvement on this submission, and we discuss them in order as
-shown in the next sections.
+We tried our best to address all the comments from the reviewers as discussed in the following.
 
@@
 
-We would like to thank you for your insightful comment regarding the toxic license violations.
-As the reviewer has mentioned, software license violation is difficult to identify and validate due to various number of software licenses, differences in country's legislation, and amount of code to be considered copyrighted (vs.~fair use).
-Nevertheless, the case of copying a licensed code snippet from an open source project to Stack Overflow without its license shows a clear potential for software license violation.
-By detecting such case, we can alleviate the license issues by stopping the accidental conversion of strictly licensed code (such as GPL) to permissively licensed code (such as CC BY-SA 3.0 on Stack Overflow).
-We hope that our study will raise awareness about this issue to Stack Overflow and the developers.
+We would like to thank you for your insightful comments regarding the license violations.
+As you have mentioned, software license violations are difficult to identify and validate due to the large number of software licenses, differences in countries' legislation, and the amount of code to be considered copyrighted (vs.~fair use).
+Nevertheless, the case of copying a licensed code snippet from an open source project to Stack Overflow without its license shows a clear potential for violating the project's license.
+By detecting such case, we can alleviate the license issues by highlighting or stopping the accidental conversion of strictly licensed code (such as GPL) to permissively licensed code (such as CC BY-SA 3.0 on Stack Overflow).
+As we highlight in the Introduction, Page~2 (and Footnote~2), developers are worried about copyright issues.
+We hope that our study will increase awareness on this issue to Stack Overflow and the developers using Stack Overflow.
 
-Regarding the few number of toxic code snippets in SO posts and code reuse in GitHub, this is partially due to the data set of 111 Java projects from the Qualitas corpus.
+Regarding the few number of toxic code snippets in SO posts and code reuse in GitHub, this is partially due to the data set of (only) 111 Java projects from the Qualitas corpus.
 The clones (and the discovered outdated code and potentially license-violating code snippets) reported in this paper are only subject to these 111 projects.
@@
 
-We rephrased the sentence to ``As shown in Table 23, the clones were found in highly- starred projects (29,465 stars) to lowly-starred star projects (1 star).''
+We rephrased the sentence to ``As shown in Table 23, the clones were found in highly-starred projects (29,465 stars) to lowly-starred star projects (1 star).''
 
@@
 Thank you for the suggestion on the definition of toxic code snippets.
-Since Reviewer 3 also expresses his/her concern regarding the definition, we revised the definition by removing the technical debt part and shorting it as follows:
+Since Reviewer~3 also expresses his/her concern regarding the definition, we revised the definition by removing the technical debt part and shorting it as follows:
 
-``Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.
+``Toxic code snippets mean code snippets that, after incorporating into software, degrade the software quality.
 Stack Overflow code snippets
@@
 are (1)~outdated, (2)~violating their original software
-license, (3) exhibiting code smells, or (4) having security vulnerabilities.''
+license, (3)~exhibiting code smells, (4)~containing faults, or (5)~having security vulnerabilities.''
 
-We believe it is important to differentiate the definition of toxic code snippets from the concrete example of toxic code snippets on Stack Overflow since the idea of toxic code snippets can be applied to any other online sources (e.g., GitHub) as well.
+We believe it is important to differentiate the definition of toxic code snippets from the concrete example of toxic code snippets on Stack Overflow since the idea of toxic code snippets can be applied to any other online source (e.g., GitHub) as well.
 
@@
 
-We agree that our analysis may not fully answer your comment because we could not capture what the Stack Overflow visitors actually did when they already expect an outdated answer.
+We agree that our analysis may not fully answer your comment because we could not capture what Stack Overflow visitors actually do when they already expect an outdated answer.
 The most proper method for this may be doing another developer survey.
@@
 In our investigation of the 100 outdated answers, we found that only 5 of the newer answers had higher votes than the outdated answers and 99\% of the outdated answers were still marked as accepted.
-\FIXME{Shall we also discuss the issue of ``accepted answers'' that they are totally relied on the questioner and not other visitors?} We are aware that this may be affected by the duration that the answers appear on a Stack Overflow post.
+We are aware that this may be affected by the duration that the answers appear on a Stack Overflow post.
 The newer answers have less visibility compared to the older answers.
 
-An alternative solution might be directly comparing the number of code reuse from the outdated answers to their newer/higher-voted answers in open source projects (e.g., GitHub). 
-Nevertheless, although we had performed such comparison, we would still suffer from the same timing issue as the newer answers have shorter window to be reused than the older ones.
+An alternative solution might be directly comparing the number of code snippets reused from the outdated answers to their newer/higher-voted answers in open source projects (e.g., GitHub). 
+Nevertheless, if we had performed such comparison, we would still suffer from the same timing issue as the newer answers have shorter windows to be reused than the older ones.
 
@@
 The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4.
-The 6 intents of changes in the 100 outdated code snippets, as shown in the table below (a copy of Table 3 in the previous response letter and Table 20 in the paper), cover \textbf{all} the cases of outdated code.
+The 6 intents of changes in the 100 outdated code snippets, as shown in the table below (a copy of Table~3 in the previous response letter and Table~20 in the paper), cover \textbf{all} the cases of outdated code.
 
@@
 The reason is that the Stack Overflow answers are rarely modified.
-As discussed in RQ4, we used this 2-year gap between the Stack Overflow snapshot that we analysed for clones, and the latest version on the web, as a chance to study the evolution of the 100 outdated answers.
-We found that 99\% of the outdated code are still marked as accepted.
+Moreover, updating the dataset would eliminate the possibility to study the evolution of outdated answers.
+As discussed in RQ4, we used this 2-year gap between the Stack Overflow snapshot that we analysed for clones and the latest version on the web as a chance to study the evolution of the 100 outdated answers.
+We found that 99\% of the outdated answers are still marked as accepted.
 While there were a few newer posts in each of the 100 outdated answers, only 5 newer answers obtained higher votes than the outdated ones.
-Thus, updating the Stack Overflow data to the latest snapshot will mostly increase the chance of finding newer outdated code snippets.
-Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{To do}.
 
-The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4. Their analysis shows the following. 
+The 100 posts are the posts containing the 100 outdated code snippets reported in RQ4. Their analysis shows the following: 
 \begin{enumerate}
 	\item Although they are outdated, after 2 years they still have higher votes than other answers or they are still marked as accepted answers.
-	\item There is only 6\% of the outdated answers that have newer answers that mitigate or point out the toxicity of the outdated code snippets. 
-	\item 47 of the 100 discovered outdated code are found in GitHub projects, of which 12 are buggy code.
-So, based on the 111 Java projects in Qualitas, their outdated code snippets do not widely spread to open source projects.
+	\item Only 6 of the outdated answers have newer answers which mitigate or point out the toxicity of the outdated code snippets. 
+	\item 47 of the 100 discovered snippets from outdated answers are found in GitHub projects, of which 12 are buggy code. 
 \end{enumerate}
+
+Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{To do}.
 
@@
 (SQ), we found only one pair with evidence of cloning from Stack Overflow post
-ID 698283 to {\small\texttt{POIUtils.java}} in \textsf{jstock} project (as shown below). 
-The Stack Overflow post can be seen from \url{https://stackoverflow.com/questions/698176/determine-correct-method-signature-during-runtime/698283#698283}.
+ID 698283 to {\small\texttt{POIUtils.java}} in the \textsf{jstock} project (as shown below). 
+The Stack Overflow post can be seen at \url{https://stackoverflow.com/questions/698176/determine-correct-method-signature-during-runtime/698283#698283}.
 The user who asked the question (i.e., Cheok Yan Cheng) on Stack Overflow is an author of \textsf{jstock} (the author's GitHub profile can be seen from \url{https://github.com/yccheok}). The
@@
 The investigation was performed by the first and
-the third authors. The two investigators separately went through each clone pair
+the third author. The two investigators separately went through each clone pair
 candidate, looked at the clones, and decided if they are a true positive or a
-false positive and classified them into an appropriate pattern by following the steps show in Figure 5. 
+false positive and classified them into an appropriate pattern by following the steps show in Figure~5. 
 After the validation, the results from the two investigators were compared. 
-This discussion can be found in Section 2.2.3 (Manual investigation).
+The corresponding discussion can be found in Section~2.2.3 (Manual investigation).
 
@@
 
-Moreover, we modified the item 3 in the contributions to be:
+Moreover, we modified Item 3 in the contributions to be:
 
@@
 
-``Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.''
+``Toxic code snippets mean code snippets that, after incorporating into software, degrade the software quality.''
 
@@
 
-``We also found that the Stack Overflow question ID 22262310 that has an outdated code answer from \texttt{WritableComparator.java} (Figure 1), has a negative score of -1.
-It is interesting to see if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.
-However, it is out of the scope of this study so we leave it as future work.''
+``We also found that the Stack Overflow question ID 22262310, which has an outdated answer with a snippet from \texttt{WritableComparator.java} (Figure 1), has a negative score of -1.
+It would be interesting to see if the negative score for the question impacts the number of views and the trust that people place in the answer to a down-voted question.
+However, it is out of scope of this study and we leave it as future work.''
 
@@
 We have tried our best to address every concern that has been pointed out by the reviewers. This result in several minor improvements throughout the paper.
-We believe this new submission is an improvement from the previous version due to the insightful reviews and discussions. We are looking forward to the new reviews.
 

### 2018-11-18 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Updated the Intro.

--- 2018-11-15 cloverflow-tse/cover_letter/second_round/cover_letter.tex
@@
 This paper is a journal-first submission to Transactions on Software
-Engineering. This is a minor revision the submission
-no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for
-taking their time to read our paper carefully. With their useful and
-constructive reviews, we improved the work further by adding xxx minor
-improvements as listed below to our previous submission as discussed later in this letter.
+Engineering. This is a minor revision of the submission
+no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers again for
+taking their time to read our response letter and the paper carefully. With their useful and
+constructive reviews, we improved the work further by revising several sections in the paper, 
+specifically the two points listed below. Our full responses to the reviewers' comments can be found on the next pages in this letter.
 
 \begin{enumerate}
-	\item A
-	\item B
+	\item We softened the claims in the Abstract and Introduction to better reflect the results presented in the paper.
+	\item We revised the definition of ``toxic code snippets.''
+	\item We clarified the experimental method that we conducted regarding the validation and classification of outdated code snippets.
 \end{enumerate}

### 2018-11-18 cloverflow-tse/cloverflow.tex
+ Updated the paper to reflect the response letter. + Small typo fix in the response letter. + Update a few wording in the response letter.

@@
 Our investigation revealed strong evidence that 153 clones have been copied from
-a Qualitas project to Stack Overflow. We found 100 of them (66\%) to be outdated
-and potentially harmful for reuse. Furthermore, we found 214 code snippets that
+a Qualitas project to Stack Overflow. We found 100 of them (66\%) to be outdated,  
+of which 10 were buggy and harmful for reuse.
+Furthermore, we found 214 code snippets that
 could potentially violate the license of their original software and appear 7,112
@@
 least one code snippet as a solution to the question asked. We found that the
-code snippets are usually not authored directly on the Stack Overflow website
+code snippets are often not authored directly on the Stack Overflow website
 but copied from another location. A snippet in an answer could be copied and
@@
 
-Toxic code snippets mean code snippets that, after incorporating into software, degrades the software quality.
+Toxic code snippets mean code snippets that, after incorporating into software, degrade the software quality.
 Stack Overflow code snippets
@@
 are (1)~outdated, (2)~violating their original software
-license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
+license, (3)~exhibiting code smells, (4)~containing faults, or (5)~having security vulnerabilities.
 In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
@@
 	software licenses. For 153 of them, we found evidence that they have been copied
-	from a specific open source project. 100 of them were found to be outdated. %
-	% and questionable for being reused.
+	from a specific open source project. 
+	100 of them were found to be outdated, of which 10 were buggy code.
 
@@
 the changes are grouped into six categories as shown in \Cref{tab:intent_outdated}.
-Enhancement is the majority intent accounting for 65 of the 100 outdated code (65\%), followed 
-by code deprecation (15\%). There were 10 outdated code snippets (10\%) caused by bug fixing.
+Enhancement is the majority intent accounting for 65 of the 100 outdated code (65\%). 
+Next is code deprecation (15\%), which represents the code snippets that are outdated due to the use of
+deprecated functions or APIs. The code snippets that we analysed contained a few deprecated code statements while
+the newest version (based on the time we did the analysis) of the same code
+snippets no longer contain the deprecated part.
+There were 10 outdated code snippets (10\%) caused by bug fixing.
+They contained buggy code statements, and were later fixed in the newest version.
 The rest of the changes are because of code refactoring (6\%), changing coding style (3\%), and 
 the data format change (2\%).
-Not all outdated code is toxic. However, the 10 buggy and outdated code snippets 
-we found are toxic and are harmful to reuse.
+Not all outdated code is toxic. 
+However, the 10 buggy and outdated code snippets we found are toxic and are harmful to reuse.
 
@@
 \textbf{Internal validity:}
+
 We applied different mechanisms to ensure the validity of the clone pairs we
@@
 found that 62,245 of them (86\%) are also the highest voted answers.
-%While most of the time they are also the highest voted answers, some
-%times they are not. 
 We plan to incorporate the highest voted answers in future work.
-% We also
-% applied the Bellon's clone agreement to 4 different combinations of
-% the tools' configurations.  For disagreed clone pairs, we applied
-% several filters to remove spurious and uninteresting clones.
-
-% The number of online clones we found are subject to the clone
-% detectors and their configurations.
-
-% We also
-% performed a pairwise matching between the default and EvaClone
-% configurations of the two clone detection tools.
+We analysed the Stack Overflow data snapshot of January 2016. 
+The findings may be different based on the newer snapshots. 
+However, we do not expect large differences of the findings 
+if we update the data set. The reason is that the Stack Overflow answers 
+are rarely modified. Moreover, updating the dataset would eliminate the 
+possibility to study the evolution of outdated answers.
 
@@
 
-%In addition, we are aware of voting mechanism in Stack Overflow and plan to
-%incorporate highest-vote answers in the future work.
+The detailed investigation of the 100 outdated answers on Stack Overflow may not
+fully capture what Stack Overflow visitors actually do when they already expect
+an outdated answer. However, our investigation tries to at least shade light on
+this by comparing the popularity of the outdated answer and the newer answers
+based on the number of votes. This may be affected by the duration that the
+answers appear on a Stack Overflow post. The newer answers have less visibility
+compared to the older answers.
 
@@
 Qualitas corpus for Java open source projects containing 111 projects
-\cite{QualitasCorpus}.  The projects span several areas of software and have
-been used in several empirical
+\cite{QualitasCorpus}. 
+The projects span several areas of software and have been used in several empirical
 studies~\cite{Taube-Schock2011,Beckman2011,Vasilescu2011,Omar2012}. Although it
 is a curated and well-established corpus, it may not fully represent all Java
-open source software available. Lastly, we selected 130,703 GitHub Java projects
+open source software available.
+
+We selected 130,703 GitHub Java projects
 based on the number of stars they obtained to represent their popularity. They
@@
 found may differ from other project selection criteria.
+
+Regarding the few number of toxic code snippets in Stack Overflow posts and code reuse in
+GitHub, this is partially due to the data set of (only) 111 Java projects from
+the Qualitas corpus. The clones (and the discovered outdated code and
+potentially license-violating code snippets) reported in this paper are only
+subject to these 111 projects. The number may increase if we expand the amount
+of open source projects. Moreover, this study only focuses on Java, and the
+situation may be worse or better for other programming languages.
 

### 2018-11-18 cloverflow-tse/cover_letter/second_round/cover_letter.tex
+ Updated the paper to reflect the response letter. + Small typo fix in the response letter. + Update a few wording in the response letter.

--- 2018-11-18 cloverflow-tse/cover_letter/second_round/cover_letter.tex
@@
 %\begin{abstract}
+
 This paper is a journal-first submission to Transactions on Software Engineering.
-This is a minor revision the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully.
+This is a minor revision of the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully.
 With their useful and constructive reviews, we improved the work further as listed below and as discussed later in this letter.
@@
 We have added this discussion into the Threats to Validity.
-\FIXME{To do}
+\FIXME{Done}
 
@@
 
-We have added this discussion in the Threats to Validity section \FIXME{To do}.
+We have added this discussion in the Threats to Validity section \FIXME{Done}.
 
@@
 The five other intents represent other cases of a code snippet being outdated.
-For example, the Bug intent represents a code snippet that previously contained buggy code statements, and was fixed in the newest version.
+For example, the Bug intent represents a code snippet that previously contained buggy code statements, and were fixed in the newest version.
 The Refactoring intent represents a code snippet that was different from the newest version due to code refactoring.
@@
 Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow).
-We slightly modified the section explaining this table to be clearer \FIXME{To do}.
+We slightly modified the section explaining this table to be clearer \FIXME{Done}.
 
@@
 
-Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{To do}.
+Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{Done}.
 
@@
 
-``We found 100 of them (66\%) to be outdated. \textbf{Ten of them were buggy and harmful for reuse.} ''
+``We found 100 of them (66\%) to be outdated,  \textbf{of which 10 were buggy and harmful for reuse.}''
 
@@
 
-``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}'' \FIXME{update in the paper}
+``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}'' \FIXME{Done}
 
@@
 The statement has been changed to ``We found that the code snippets are \textbf{often} not authored directly on the Stack Overflow website but copied from another location.''.
-\FIXME{update in the paper}
+\FIXME{Done}
 

### 2018-11-21 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Incorporated Matheus's comments.

@@
 This paper is a journal-first submission to Transactions on Software Engineering.
-This is a minor revision of the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully.
+This is a minor revision to the submission no.~TSE-2018-06-0228 and we would like to thank the anonymous reviewers for taking their time to read our paper carefully.
 With their useful and constructive reviews, we improved the work further as listed below and as discussed later in this letter.
@@
 The most proper method for this may be doing another developer survey.
-However, our investigation tries to at least shade light on this by comparing the popularity of the outdated answer and the newer answers based on the number of votes.
+However, our investigation tries to shade light on this by comparing the popularity of the outdated answer and the newer answers based on the number of votes.
 If Stack Overflow visitors reuse the code (or learn from the answers) and they like the answer, they can reward the answer with an upvote.
@@
 We would like to thank the reviewers again for their comments.
-We have tried our best to address every concern that has been pointed out by the reviewers. This result in several minor improvements throughout the paper.
+We have tried our best to address every concern that has been pointed out by the reviewers. This result in several improvements throughout the paper.
 

### 2018-11-23 cloverflow-tse/cloverflow.tex
Updated Chaiyong's bio.

@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
-is working toward the PhD degree in Computer Science at University College London, where he is part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
-He is supervised by Dr.~Jens Krinke and Dr.~David Clark.
+is a lecturer at the Faculty of Information and Communication Technology, Mahidol University.
+He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
+He was supervised by Dr.~Jens Krinke and Dr.~David Clark.
 His research interests include code search, code clone detection, software plagiarism, search-based software engineering, and mining software repository.

### 2018-11-23 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Updated Chaiyong's bio.

@@
 % 2. Complete the paper data
-\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$,~Jens Krinke$^\dagger$,~Matheus Paixao$^\dagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
+\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$\footnote{This work has been done while Chaiyong was a PhD student at CREST, University College London},~Jens Krinke$^\dagger$,~Matheus Paixao$^\dagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
 \newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}

### 2018-11-24 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Updated the authors' affiliations in the response letter and completed the cross-check that all the changes in the response letter have been applied to the paper. Start proofreading the paper.

--- 2018-11-21 cloverflow-tse/cover_letter/second_round/cover_letter.tex
@@
 % 2. Complete the paper data
-\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$,~Jens Krinke$^\dagger$,~Matheus Paixao$^\dagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
+\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$\footnote{This work has been done while the first and the third author were PhD students at CREST, University College London},~Jens Krinke$^\dagger$,~Matheus Paixao$^\ddagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
 \newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
-%\newcommand{\myEmail}{cragkhit@gmail.com, {j.krinke,matheus.paixao.14}@ucl.ac.uk, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
+\newcommand{\myEmail}{chaiyong.rag@mahidol.ac.th, j.krinke@ucl.ac.uk, matheus.paixao@uece.br, giuseppebianco92@gmail.com, rocco.oliveto@unimol.it}
 %\newcommand{\mySecEmail}{}
@@
 \newcommand{\myJournal}{IEEE TRANSACTIONS ON SOFTWARE ENGINEERING}
-\newcommand{\myDept}{Mahidol University (Thailand)$^\ast$, University College London (UK)$^\dagger$, University of Molise (Italy)$^\star$}
+\newcommand{\myDept}{Mahidol University (Thailand)$^\ast$, University College London (UK)$^\dagger$, 
+	State University of Ceara (Brazil)$^\ddagger$,
+	University of Molise (Italy)$^\star$}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
  \myAuthors \\
-% \url{\myEmail} \\
+ \url{\myEmail} \\
  %\url{\mySecEmail} 
@@
 The paper presents a study using state-of the art clone detection tools and techniques to automatically extract and filter online clone pairs between Stack Overflow and projects in the curated Qualitas corpus.
-The paper also includes a user survey conducted on Stack Overflow users to assess their awareness of such potential toxic code fragments.he paper is well organized,  sound and the authors spend amount of work in their empirical analysis.
+The paper also includes a user survey conducted on Stack Overflow users to assess their awareness of such potential toxic code fragments.
+The paper is well organized, sound and the authors spend amount of work in their empirical analysis.
 \vspace{0.2cm}
@@
 We have added this discussion into the Threats to Validity.
-\FIXME{Done}
 
@@
 
-We have added this discussion in the Threats to Validity section \FIXME{Done}.
+We have added this discussion in the Threats to Validity section.
 
@@
 Outdated code snippets with Bug intent are clearly harmful if they are posted on the Internet (e.g., Stack Overflow).
-We slightly modified the section explaining this table to be clearer \FIXME{Done}.
+We slightly modified the section explaining this table to be clearer.
 
@@
 
-Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section \FIXME{Done}.
+Nonetheless, we have added a discussion of the age of the Stack Overflow data set to the Threats to Validity section.
 
 \rcomment{R2C8: Thank you for clarifying the manual analysis part.
-Can please provide more details on how this manual analysis determined that something actually originated from SO?
+Can you please provide more details on how this manual analysis determined that something actually originated from SO?
 Perhaps giving an example would help here.
@@
 However, considering that the 25 lines of code of
-{\small\texttt{findMethodToInvoke}} method depicted in  in Stack Overflow is
+{\small\texttt{findMethodToInvoke}} method (depicted in Figure \ref{fig:jstock_code} below) on Stack Overflow is
 very similar to the code in \textsf{jstock} including comments, it is almost
@@
 
-``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}'' \FIXME{Done}
+``100 of them were found to be outdated\textbf{, of which 10 were buggy code.}''
 
@@
 The statement has been changed to ``We found that the code snippets are \textbf{often} not authored directly on the Stack Overflow website but copied from another location.''.
-\FIXME{Done}
 

### 2018-11-24 cloverflow-tse/cloverflow.tex
Updated the authors' affiliations in the response letter and completed the cross-check that all the changes in the response letter have been applied to the paper. Start proofreading the paper.
Finished checking the added parts in the paper (with other minor fixes)

@@
 We analysed the Stack Overflow data snapshot of January 2016. 
-The findings may be different based on the newer snapshots. 
+The findings may differ from using the newer snapshots. 
 However, we do not expect large differences of the findings 
@@
 fully capture what Stack Overflow visitors actually do when they already expect
-an outdated answer. However, our investigation tries to at least shade light on
+an outdated answer. Our investigation tries to at least shade light on
 this by comparing the popularity of the outdated answer and the newer answers
-based on the number of votes. This may be affected by the duration that the
+based on the number of votes. Nonetheless, this may be affected by the duration that the
 answers appear on a Stack Overflow post. The newer answers have less visibility
@@
 GitHub, this is partially due to the data set of (only) 111 Java projects from
-the Qualitas corpus. The clones (and the discovered outdated code and
-potentially license-violating code snippets) reported in this paper are only
+the Qualitas corpus. The clones and the discovered outdated code and
+potentially license-violating code snippets reported in this paper are only
 subject to these 111 projects. The number may increase if we expand the amount
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
-is a lecturer at the Faculty of Information and Communication Technology, Mahidol University.
+is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand.
 He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
 He was supervised by Dr.~Jens Krinke and Dr.~David Clark.
-His research interests include code search, code clone detection, software plagiarism, search-based software engineering, and mining software repository.
+His research interests include code search, code clone detection, software plagiarism, modern code review, search-based software engineering, and mining software repository.
+More info at \url{http://mucc.mahidol.ac.th/~chaiyong.rag/}.
 \end{IEEEbiography}

### 2018-11-24 cloverflow-tse/cover_letter/second_round/cover_letter.tex
Finished checking the added parts in the paper (with other minor fixes)

@@
 % 2. Complete the paper data
-\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$\footnote{This work has been done while the first and the third author were PhD students at CREST, University College London},~Jens Krinke$^\dagger$,~Matheus Paixao$^\ddagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
+\newcommand{\myAuthors}{Chaiyong Ragkhitwetsagul$^\ast$\footnote{This work has been done while the first and the third author were PhD students at CREST, University College London, UK},~Jens Krinke$^\dagger$,~Matheus Paixao$^\ddagger$,~Giuseppe Bianco$^\star$,~Rocco Oliveto$^\star$}
 \newcommand{\myAuthorsShort}{Ragkhitwetsagul et. al}
@@
 It represents the code snippets that are outdated due to the use of deprecated functions or APIs.
-With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part(s).
+With this case of function/API deprecation, the code snippets that we analysed contained a few deprecated code statements while the newest version (based on the time we did the analysis) of the same code snippets no longer contain the deprecated part.
 The five other intents represent other cases of a code snippet being outdated.

### 2018-11-24 cloverflow-tse/cloverflow.tex
Injected some (self) citations. Updated the bios.

@@
 studies~\cite{Ragkhitwetsagul2016, emse, Wang2013, Mondal2011, Cheung2015,
-	Krinke2010}. Furthermore, it offers normalisation of variable names and literals
+  krinke11cloned, Krinke2010, krinke10distinguishing, Krinke2008,
+  krinke07study, ragkhitwetsagul18picture}. Furthermore, it offers normalisation of variable names and literals
 (strings and numbers) which enables Simian to detect literal clones (type-1) and
@@
 He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
-He was supervised by Dr.~Jens Krinke and Dr.~David Clark.
-His research interests include code search, code clone detection, software plagiarism, modern code review, search-based software engineering, and mining software repository.
+His research interests include code search, code clone detection, software plagiarism, modern code review, search-based software engineering, and mining software repositories.
 More info at \url{http://mucc.mahidol.ac.th/~chaiyong.rag/}.
 \end{IEEEbiography}
-\vspace{-1cm}
+%\vspace{-1cm}
 
@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.jpg}}]{Jens Krinke}
-is Senior Lecturer in the Software Systems Engineering
+is Associate Professor in the Software Systems Engineering
 Group at the University College London, where he is Director of CREST,
@@
 current research interests include software
-similarity, modern code review, and mutation testing.  He is well known for his work on
+similarity, modern code review, program analysis, and software testing.  He is well known for his work on
 program slicing and clone detection.
 \end{IEEEbiography}
-\vspace{-1cm}
+%\vspace{-1cm}
 
@@
 \end{IEEEbiography}
-\vspace{-1cm}
+%\vspace{-1cm}
 
@@
 \end{IEEEbiography}
-\vspace{-0.5cm}
+%\vspace{-0.5cm}
 
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{rocco.png}}]{Rocco Oliveto}
-is Associate Professor at University of Molise (Italy), where he is also the Director of the Computer Science Bachelor and Master programs and the Director of the Software and Knowledge Engineering Lab (STAKE Lab).
-He co-authored over 100 papers on topics related to software traceability, software maintenance and evolution, search-based software engineering, and empirical software engineering.
-His activities span various international software engineering research communities.
-He has served as organizing and program committee member of several international conferences in the field of software engineering.
-He was program co-chair of ICPC 2015, TEFSE 2009 and 2015, SCAM 2014, WCRE 2012, and 2013.
-He is general chair for SANER 2018 that will be held in Campobasso from March 20, 2018 to March 23, 2018.
+is Associate Professor at University of Molise (Italy), where he is
+also the Director of the Computer Science Bachelor and Master programs
+and the Director of the Software and Knowledge Engineering Lab (STAKE
+Lab).
 He is also one of the co-founders and CEO of DataSound, a spin-off of the University of Molise aiming at efficiently exploiting the priceless heritage that can be extracted from big data analysis via machine learning.
-More info at \url{https://dibt.unimol.it/staff/oliveto}.
 \end{IEEEbiography}

### 2018-11-25 cloverflow-tse/cloverflow.tex
Modified Rocco's bio a bit more.
Shortened Chaiyong's bio and restored Jens's change on Rocco's bio.

@@
 is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand.
-He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
-His research interests include code search, code clone detection, software plagiarism, modern code review, search-based software engineering, and mining software repositories.
-More info at \url{http://mucc.mahidol.ac.th/~chaiyong.rag/}.
+He received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST).
+His research interests include code search, code clone detection, software plagiarism, modern code review, and mining software repositories.
+%More info: \url{http://mucc.mahidol.ac.th/~chaiyong.rag}.
 \end{IEEEbiography}

### 2018-11-27 cloverflow-tse/cloverflow.tex
Updated Matheus's bio.

@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
-is currently a PhD candidate in the Computer Science Department at University College London, where he is part of the CREST centre.~He is supervised by Dr.~Jens Krinke, Prof.~Mark Harman, Dr.~Emmanuel Letier and Dr.~Yuanyuan Zhang.
-His research interests include software architecture, search based software engineering, technical debt, empirical software engineering and modern code review.
+is currently a Research Assistant in the Computer Science Department at State University of Ceara.
+He recently received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
+He was supervised by Prof.
+Mark Harman and Dr.
+Jens Krinke.
+His research interests include software architecture, search-based software engineering, mining software repositories, modern code review and empirical software engineering.
 \end{IEEEbiography}

### 2018-11-27 cloverflow-tse/cloverflow.tex
Minor fixes to the paper: 1) Removed the name of Chris Bean -- GDPR 2) Corrected the number of GitHub projects to be the same as in the thesis 3) Updated the status of the Apache Hive issue (now closed)

@@
 
-Lastly, we searched for the outdated code snippets in 130,703 GitHub projects to
+Lastly, we searched for the outdated code snippets in 130,719 GitHub projects to
 see how widespread is the outdated code in the wild. We mined GitHub
@@
 With this method, we retrieved the top 1,000 most starred projects for each project size. 
-As a result, we cloned 130,703 GitHub projects ranging from 29,465 stars to 1 star.
+As a result, we cloned 130,719 GitHub projects ranging from 29,465 stars to 1 star.
 A clone detection was then performed between the outdated code snippets and the GitHub
@@
 deleted in the commit
-{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} by Chris Beams on
+{\small{\texttt{02a4473c62d8240837bec297f0a1f3cb67ef8a7b}}} on
 January 20, 2012, two years after it was posted.
@@
 We performed a detailed investigation of the 100 outdated answers on Stack
-Overflow, on 6 May 2018, approximately two years after the snapshot we analysed was created
+Overflow, on May 6, 2018, approximately two years after the snapshot we analysed was created
 to look for any changes, warnings, or mitigations made to the outdated code snippets.
 We investigated the answers on three aspects: newer answers, higher-voted answers, and comments on the
-outdated answers.\footnote{We also found that the Stack Overflow question ID 22262310 that has an outdated code answer from \texttt{WritableComparator.java} (\Cref{fig:before-after}), has a negative score of -1.
+outdated answers.\footnote{We also found that the Stack Overflow question ID 22262310, which has an outdated answer from \texttt{WritableComparator.java} (\Cref{fig:before-after}), has a negative score of -1.
 It is interesting to see if the negative score for the question impacts both the number of views and the trust that people place in the answer to a down-voted question.
@@
 
-Then, we performed code clone detection between the 100 outdated code snippets and 130,703 GitHub projects.
+Then, we performed code clone detection between the 100 outdated code snippets and 130,719 GitHub projects.
 We found 102 cloned candidates, which were associated with 30 outdated code snippets, 
@@
 outdated version of the \texttt{humanReadableInt()} method and proposed a fix by
-using the newest version of the method in Hadoop. The issue has been fixed in
-deeplearning4j. The developers of deeplearning4j agreed that the method was
+using the newest version of the method in Hadoop. The issue has been fixed in both projects.
+The developers of deeplearning4j agreed that the method was
 problematic and decided to implement their own fix due to a concern of a
 potential software licensing conflict caused by copying the fix directly from
-the Hadoop code base. The bug report in Apache Hive is still open.
+the Hadoop code base. The developers of Apache Hive found that the method is not used anywhere
+in the project, so they decided to delete it.
 
@@
 statements, to a fully rewritten code with new method signatures. 14~pairs are
-dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
+dead snippets. 47 outdated code snippets are found in 130,719 GitHub projects
 without evidence of copying, which of 12 were buggy. A toxic 
@@
 code snippets with their original license missing (86 QS, 78 EX, and 50 UD)  and
-130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
+130,719 GitHub projects using SourcererCC with 80\% similarity threshold.
 Opposite to the outdated clones, we discovered a large number
@@
 
-We selected 130,703 GitHub Java projects
+We selected 130,719 GitHub Java projects
 based on the number of stars they obtained to represent their popularity. They
@@
 to reuse. Our large-scale clone detection between the outdated code snippets 
-and 130,703 GitHub projects finds 102 candidates of the outdated code being
+and 130,719 GitHub projects finds 102 candidates of the outdated code being
 used in the wild.

### 2018-11-28 cloverflow-tse/cloverflow.tex
Changed to past tense.
Updated the citation of Baltest et al. to EMSE paper and fixed the formatting of Qualitas project names to be consistent.

@@
 Although this activity of online code cloning is well-known, there are only a few
-empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2017}, especially
+empirical studies on the topic~\cite{An2017,Abdalkareem2017,Baltes2018}, especially
 on finding the origins of the clones on Q\&A websites.
@@
 Interestingly, we discovered that the buggy version of the
-\texttt{humanReadableInt()} method from Hadoop appeared in two popular Java
+\texttt{humanReadableInt()} method from \textsf{Hadoop} appeared in two popular Java
 projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
@@
 Stack Overflow, appears in the two projects. It is possible that the developers
-retrieved them from Stack Overflow, other websites, or from Hadoop code base
+retrieved them from Stack Overflow, other websites, or from \textsf{Hadoop} code base
 directly. Nevertheless, we reported them to the developers of the two projects
@@
 potential software licensing conflict caused by copying the fix directly from
-the Hadoop code base. The developers of Apache Hive found that the method is not used anywhere
+the \textsf{Hadoop} code base. The developers of Apache Hive found that the method was not used anywhere
 in the project, so they decided to delete it.
@@
 \textbf{QS} clone pairs have their licensing terms removed or changed when
-posted on Stack Overflow. One QS clone pair posted by a JFreeChart developer
+posted on Stack Overflow. One QS clone pair posted by a \textsf{JFreeChart} developer
 changed its license from Lesser GPL v2.1+ to New BSD 3-clause. The
@@
 	\end{tabular}
-	\caption{Clones of the 214 Stack Overflow missing-license code snippets in 131,703 GitHub projects}
+	\caption{Clones of the 214 Stack Overflow missing-license code snippets in 130,719 GitHub projects}
 	\label{tab:license_github}
@@
 Note that the code snippets could potentially violate the license, but do
-not necessarily do so. In the example where the JFreeChart
+not necessarily do so. In the example where the \textsf{JFreeChart}
 developer copied his own code, she or he was free to change the
@@
 validation to read the post, understand the context, and use multiple hints
-based on human judgement (comments in the code, natural text in the question and
+based on human judgement (e.g., comments in the code, natural text in the question and
 answers, date/time of the posts) to conclude that the code snippets are actually
@@
 must be ranked very high among the list of clone candidates of a code snippet
-from Hadoop since it contains two terms of the project name (Hadoop) and a class name (WritableComparator)
+from \textsf{Hadoop} since it contains two terms of the project name (Hadoop) and a class name (WritableComparator)
 in it.
@@
 Work similar to ours are studies by An et al.~\cite{An2017},
-Abdalkareem et al.~\cite{Abdalkareem2017}, Baltes et al.~\cite{Baltes2017},
+Abdalkareem et al.~\cite{Abdalkareem2017}, Baltes et al.~\cite{Baltes2018},
 and~Zhang et al.~\cite{Zhang2018}. 
@@
 with statistical significance.
-Baltes et al.~\cite{Baltes2017} discovered that two-thirds of the clones 
+Baltes et al.~\cite{Baltes2018} discovered that only 23.2\% of the clones in GitHub projects
 from the 10 most frequently referenced Java code snippets on Stack
-Overflow do not contain attributions.
+Overflow contain attributions.
 Zhang et al.~\cite{Zhang2018} study quality of code snippets on

### 2018-11-28 cloverflow-tse/cloverflow.tex
Shortened Matheus' bio.

@@
 \begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{mpaixao.png}}]{Matheus Paixao}
-is currently a Research Assistant in the Computer Science Department at State University of Ceara.
-He recently received the PhD degree in Computer Science at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
-He was supervised by Prof.
-Mark Harman and Dr.
-Jens Krinke.
-His research interests include software architecture, search-based software engineering, mining software repositories, modern code review and empirical software engineering.
+is Research Assistant in the Computer Science Department at State University of Ceara.
+He received his PhD degree at University College London, where he was part of the Centre for Research on Evolution, Search, and Testing (CREST) and Software Systems Engineering (SSE) Group.
+His research interests include software architecture, search-based software engineering, mining software repositories, and modern code review.
 \end{IEEEbiography}

### 2019-02-16 cloverflow-tse/submitted_version/16-Feb-2019_final_files_for_submission/cloverflow.tex
Added the modified version of the source files. TSE requires some specific file format for images (must be eps, ps, tiff, ppt, or png).

--- 2018-11-28 cloverflow-tse/cloverflow.tex
@@
 	To answer RQ2, we found 2,063 manually confirmed clone pairs between 443 Stack Overflow code snippets
-	and 59 Qualitas proejcts. 
+	and 59 Qualitas projects. 
 	%After the manual confirmation, 2,076 pairs as true positives, i.e.,~
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.jpg}}]{Chaiyong Ragkhitwetsagul}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{cragkhit.png}}]{Chaiyong Ragkhitwetsagul}
 is a lecturer at the Faculty of Information and Communication Technology, Mahidol University, Thailand.
@@
 % % if you will not have a photo at all:
-\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.jpg}}]{Jens Krinke}
+\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{jkrinke.png}}]{Jens Krinke}
 is Associate Professor in the Software Systems Engineering
